### 2018-10-11 Cost2_prereg.Rmd
First import of all the data and scripts

---
title: "Effort and Delay Discounting in a Foraging Environment"
author: "Claudio Toro Serey & Joseph T. McGuire"
output:
  html_document: default
  word_document: default
  fig_caption: yes
---

# Pre-registration follow-up

This document follows the steps planned for the pre-registration (https://osf.io/2rsgm/). The bullet points match the organization shown on the website as closely as possible. First, here is a restatement of the questions and hypotheses.

## Research Questions

#### 3.1.	Do decision makers in foraging environments integrate information about delay durations and reward amounts to produce reward-maximizing behavior?

#### 3.2.	Main question: Are decisions affected differently by equivalent time periods of pure delay, cognitive effort, physical effort, and non-effortful task engagement? Do these four conditions involve different levels of subjective costs?

#### 3.3.	How can we best computationally model the perceived cost of time and effort to predict choices in each condition?

## Hypotheses

#### 4.1.	Single-option, accept/reject decisions will be influenced by within-subject manipulations of reward magnitude and associated delay duration in line with a theoretical reward-maximizing strategy.
 **4.1.1.**	Participants will more frequently accept high-reward prospects than low-reward prospects.

 **4.1.2.**	The tendency to reject low-reward prospects will be greater in environments where rewards are associated with longer delays (handling times).

#### 4.2.	Prospect acceptance rates will differ across four between-subject conditions, in which the delays associated with rewards (a) are unfilled, (b) include a cognitive effort requirement, (c) include a physical effort requirement, or (d) require a trivial level of physical effort but have matched visual stimuli to the physical effort condition.
  **4.2.1.**	In the cognitive effort condition, overall acceptance rates will be greater than in the unfilled-delay condition.

  **4.2.2.**	In the physical effort condition, overall acceptance rates will be greater than in the unfilled-delay condition, and equivalent to the cognitive effort condition.

  **4.2.3.**	In the trivial effort condition, acceptance rates will be equivalent to the unfilled-delay condition, and lower than in the physical effort and cognitive effort conditions.

#### 4.3.	Choices will be well fit by a computational model in which the subjective opportunity cost of time is free to vary across the four between-subject conditions.
  **4.3.1.**	Participants will display stable preferences, meaning that the reward amounts they accept in a given timing condition will be similar throughout the experiment.

  **4.3.2.**	Subject-specific opportunity cost (OC) estimates will vary inversely with acceptance rates. Thus, the unfilled-delay condition will produce higher OC estimates than both effort conditions, which in turn will show no differences between them.

\bigskip

```{r Global Options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

``` {r Libraries & Functions, echo=FALSE}
# libraries
library(tidyverse)
library(ggfortify)
library(knitr)
library(pander) 
library(nloptr)
library(pwr)
library(lme4)
#library(lmerTest)
library(gridExtra)
library(reshape2)
library(corrplot)

## Miscelaneous
lbls <- c("Wait","Cognitive","Physical","Easy")
cols = c("#78AB05","#D9541A","deepskyblue4", "grey50") # plot colors (wait, effort)
lthick = 2 # line thickness for plots

## Functions
# Permutation for 2 groups
permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){

    # prep data
    summaryPerm <- list()
    lOne <- length(group1)
    lTwo <- length(group2)
    bigSample <- c(group1,group2)

    if (paired == FALSE) {

        for (i in 1:nPerms){

            # relabel samples
            tempBig <- sample(bigSample)
            tempOne <- tempBig[1:lOne]
            tempTwo <- tempBig[(lOne+1):length(bigSample)]

            # stats
            tempDiffs <- statType(tempOne,na.rm=T) - statType(tempTwo,na.rm=T)
            summaryPerm$jointDist[i] <- tempDiffs # statType(tempDiffs, na.rm = T)

        }

    } else {

        for (i in 1:nPerms){

            # shift labels in a pairwise fashion
            tempDiffs <- statType((-1)^rbinom(lOne,1,0.5) * (group1 - group2))
            summaryPerm$jointDist[i] <- tempDiffs

        }

    }

    # get the observed difference
    diffs <- statType(group1,na.rm=T) - statType(group2,na.rm=T)
    observedAbs <- abs(diffs) # maybe leave it as means here
    observed <- diffs
    summaryPerm$Pval <- 2 * (1 - ecdf(summaryPerm$jointDist)(observedAbs))
    if (length(unique(abs(summaryPerm$jointDist))) == 1) {summaryPerm$Pval <- 1} # if the difference is always the same, then p = 1
    summaryPerm$Observed <- observed

    return(summaryPerm)

}

# Non-parametric Bootstrap for a single group
bootstrap <- function(group = 1, statType = mean, B = 5000){

    # prep param
    bootStats <- rep(0,B)

    # iterate
    for(b in 1:B){

      # wait group
      x <- sample(group,length(group),replace=T)  
      bootStats[b] <- statType(x,na.rm = T)

    }

    return(bootStats)

}

# plot logistic (for the prop complete test, mainly, but it can be easily expanded for more flexibility in n-params)
plotLogis <- function(coeffs = 1, group = "Cognitive", handling = 1:14, reward = 1:20, xAxis = "Reward", plotType = lines, color = "black", lType = 1, pchType = 16){

    # divide into relevant coefficients (assumes logisComb was the best model)
    intercept <- coeffs[1]
    cogBeta <- coeffs[2]    
    physBeta <- coeffs[3]
    easyBeta <- coeffs[4]
    handBeta <- coeffs[5]
    rwdBeta <- coeffs[6]

    #wait <- numeric()
    #phys <- numeric()

    # now the parameters
    label = "Reward Amount"
    if (group == "Cognitive"){cog = 1} else {cog = 0}
    if (group == "Phys"){phys = 1} else {phys = 0}
    if (group == "Easy") {easy = 1} else {easy = 0}
    if (xAxis == "Reward"){
        xAxis = reward 
        label = "Reward Amount" 
    } else {
        xAxis = handling
        label = "Handling Time"
    }

    # logistic function
    model <- intercept + cogBeta*cog + physBeta*phys + easyBeta*easy + handBeta*handling + rwdBeta*reward 
    func <- 1 / (1 + exp(-(model)))
    plotType(xAxis,
         func,
         ylim = c(0,1),
         xlim = c(0,25),
         xlab = label,
         ylab = "Probability of Completing a Trial",
         type="l",
         col = color,
         lty = lType,
         pch = pchType,
         lwd = 2,
         xaxt = "n",
         bty = "n")

    # use title() to add title afterwards
}

# Cohen's D for 2 groups
# for a more flexible approach, make the data input to be a list with entries for n groups, 
# then do length(list) for the number of groups. 
cohenD <- function(group1 = 1, group2 = 2){

      # means
      mean1 <- mean(group1, na.rm = T)
      mean2 <- mean(group2, na.rm = T)

      # variance
      var1 <- var(group1, na.rm = T)
      var2 <- var(group2, na.rm = T)

      # equation
      out <- (mean1 - mean2) / sqrt((var1 + var2)/2)

      return(out)

}

# get the number of continuous quits before current trial
seqQuits <- function(subjData = 1){

    # get the lag
    tempSeq <- sequence(rle(subjData)$lengths) # sequence
    tempSeq[subjData==1] <- 0 # not interested in completed runs, just quits
    tempSeq <- c(0,tempSeq) # lag it so it can be used as a t-1 regressor

    # return data so that the length is equivalent
    out <- tempSeq[1:length(subjData)]

    return(out)

}

# basic power calculation for a one way ANOVA
powerCalc <- function(d = 1.2, Za = 1.96, Zb = 0.842){

  out <- 2*((Za + Zb)/d)^2 + (0.25*(Za^2))

  return(round(out))

}

## gather basic data (this is better as a function, then rbind)
summarizeData <- function(Data = waitData, nSubs = nSubsW, type = "Wait"){

  tempSummary <- data.frame(group = rep(type, nSubs))

  if (type == "Cognitive") {

    for (subj in seq(nSubs)){

        # Choice index
        tempChoice <- Data[[subj]]$Choice

        # Proportion complete
        tempSummary[subj,2] <- mean(tempChoice)

        # earnings
        tempSummary[subj,3] <- sum(Data[[subj]]$Reward[tempChoice==1])

        # RTs
        tempSummary[subj,4] <- median(Data[[subj]]$`Choice RT`[tempChoice==0])

        # Mistakes (only for cognitive effort group)
        tempMistakes <- sum(cogDataLong[[subj]]$`Trial Outcome`=="Forced travel") # how many forced travel trials
        tempTrialnum <- length(Data[[subj]]$Choice) # how many decision trials
        tempSummary[subj,5] <- tempMistakes / (tempMistakes + tempTrialnum) # proportion of forced travels throughout the exp

    }

  } else {

    for (subj in seq(nSubs)){

        # choice index
        tempChoice <- Data[[subj]]$Choice

        # propotion complete
        tempSummary[subj,2] <- mean(tempChoice)

        # earnings
        tempSummary[subj,3] <- sum(Data[[subj]]$Reward[tempChoice==1])

        # RTs
        tempSummary[subj,4] <- median(Data[[subj]]$RT[tempChoice==0])

        # Mistakes (to allow for mistakes on the cognitive group)
        tempSummary[subj,5] <- NA

    }

  }

  return(tempSummary)

}

# Summarize the proportion complete for GLMs
propComplete <- function(Data = waitData, nSubs = nSubsW, indx = indxWait, type = "Wait") {

    tempProp <- data.frame(SubjID = rep(indx,9),
                           Group = rep(type,nSubs*9),
                           Handling = c(rep(2,nSubs*3), 
                                        rep(10,nSubs*3), 
                                        rep(14,nSubs*3)),
                           Reward = rep(c(rep(4,nSubs),rep(8,nSubs),rep(20,nSubs)),3),
                           propComplete = rep(NA,length(indx)*9),
                           totalTrials = rep(NA,length(indx)*9),
                           totalComplete = rep(NA,length(indx)*9))

    for (subj in seq(nSubs)){

      # handling of 2s
      tempProp$propComplete[subj] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+nSubs] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*2)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+nSubs] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*2)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==20])

      # handling of 10s
      tempProp$propComplete[subj+(nSubs*3)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+(nSubs*4)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*5)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj+(nSubs*3)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+(nSubs*4)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*5)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==20])

      # handling of 14s
      tempProp$propComplete[subj+(nSubs*6)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+(nSubs*7)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*8)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj+(nSubs*6)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+(nSubs*7)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*8)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==20])

    }

    return(tempProp)

}

# OC-specific computation of the negative log likelihood for model optimization
negLogLik <- function(params, choice, handling, reward) {
  gamma <- exp(params[2]) * handling
  model <- exp(params[1]) * (reward - gamma)
  p = 1 / (1 + exp(-model))
  p[p == 1] <- 0.999
  p[p == 0] <- 0.001
  tempChoice <- rep(NA, length(choice))
  tempChoice[choice==1] <- log(p[choice==1])
  tempChoice[choice==0] <- log(1 - p[choice==0])
  negLL <- -sum(tempChoice)
  return(negLL)
}

# minimize the negative log likelihood
optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA") {
  # Prep data
  handling <- Data$Handling
  reward <- Data$Reward
  choice <- Data$Choice

  # Prep list of results to be returned
  out <- list()
  out$percentQuit <- (sum(choice==0) / length(choice)) * 100
  out$percentAccept <- (sum(choice==1) / length(choice)) * 100 
  miss <- (choice != 1) & (choice != 0)
  out$percentMiss <- (sum(miss) / length(choice))  * 100
  choice <- choice[!miss]
  reward <- as.numeric(reward[!miss])
  handling <- as.numeric(handling[!miss])

  # Establish lower and upper bounds
  LB <- log((min(reward)/max(handling)) * 0.99)
  UB <- log((max(reward)/min(handling)) * 1.01)

  # Begin defining parameters
  # If choices are one-sided (i.e. all accepted)
  if ((sum(choice) == length(choice)) | (sum(choice) == 0)) {
    ifelse(sum(choice) == length(choice), out$Gamma <- exp(LB), out$Gamma <- exp(UB)) 
    out$Scale <- NA
    out$LL <- 0
  } else {
    # Create a feasible region (search space)
    params <- as.matrix(expand.grid(scale = c(-1, 1), gamma = seq(LB, UB, length = 3)))
    # Create a list to check the minimization of the negative log lik.
    info <- list()
    info$negLL <- Inf
    # Define the options to be used during optimization
    # Consider looking into other optimization algorithms and global minima
    opts <- list("algorithm" = Algorithm,
               "xtol_rel" = 1.0e-8)
    # Optimize the sOC over all possible combinations of starting points
    for (i in seq(nrow(params))) {
      tempInfo <- nloptr(x0 = params[i, ], 
                   eval_f = negLogLik, 
                   lb = c(log(0.001), LB),
                   ub = c(-log(0.001), UB),
                   opts = opts,
                   choice = choice, 
                   handling = handling,
                   reward = reward)
      if (tempInfo$objective < info$negLL) {
        #print("Minimized")
        info$negLL <- tempInfo$objective
        info$params <- tempInfo$solution
      }
    }
    out$Gamma <- exp(info$params[2])
    out$Scale <- exp(info$params[1])
    out$LL <- -info$negLL
  }

  # Summarize the outputs
  out$LL0 <- log(0.5) * length(choice)
  out$Rsquared <- 1 - (out$LL/out$LL0)
  out$subjOC <- out$Gamma * handling
  out$p <- 1 / (1 + exp(-(out$Scale*(reward - out$subjOC))))
  out$predicted <- reward > out$subjOC
  out$predicted[out$predicted == TRUE] <- 1
  out$percentPredicted <- (sum(out$predicted == choice) / length(choice)) * 100

  # adjust the probabilities in case of extreme gammas
  if (out$Gamma <= exp(LB)) {
    out$Gamma <- exp(LB) # temporary condition because Nlopt is not respecting the lower bound
    out$p <- rep(1, length(choice))
  } else if (out$Gamma == exp(UB)) {
    out$p <- rep(0, length(choice))
  }

  return(out)

}

```

``` {r Load Data, echo=FALSE}
### data loading and cleaning up

# load cognitive effort group
setwd('/Volumes/Addon/Grad school/Cost2_data/cog')
temp = list.files(pattern="*.csv")
cogDataLong = lapply(temp, read.csv, header = FALSE)

# load wait group
setwd('../wait')
temp = list.files(pattern="*.csv")
waitDataLong = lapply(temp, read.csv, header = FALSE)

# load physical group
setwd('../phys')
temp = list.files(pattern="*.csv")
physDataLong = lapply(temp, read.csv, header = FALSE)

# load pheasysical group
setwd('../easy')
temp = list.files(pattern="*.csv")
easyDataLong = lapply(temp, read.csv, header = FALSE)

### cleaning data
# this will generate a simple list with only info about trials that participants quit or completed
# this is because cognitive logs also include within-trial task-specific information
# for the wait condition, it will get rid of the break indicator

nSubsW <- length(waitDataLong)
nSubsC <- length(cogDataLong)
nSubsP <- length(physDataLong)
nSubsE <- length(easyDataLong)
totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE) # why didn't I think of this before...

#  short lists
cogData <- list()
waitData <- list()
physData <- list()
easyData <- list()

# For pre-post analysis
cogBefore <- list()
cogAfter <- list()
waitBefore <- list()
waitAfter <- list()
physBefore <- list()
physAfter <- list()
easyBefore <- list()
easyAfter <- list()

# clean wait group data
for (subject in seq(nSubsW)){

  # Before/after
  breakW <- which(waitDataLong[[subject]]$V1 == 0)

  waitBefore[[subject]] <- waitDataLong[[subject]][1:(breakW - 1),]
  waitAfter[[subject]] <- waitDataLong[[subject]][(breakW + 1):length(waitDataLong[[subject]]$V1),]

  # assign header names
  colnames(waitBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(waitAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # Overall data cleaning
  tempW <- waitDataLong[[subject]]$V1 != 0

  # create a new list with only decision trials / without break
  waitData[[subject]] <- waitDataLong[[subject]][tempW,]

  # assign header names
  colnames(waitData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

}

# clean cognitive group data
for (subject in seq(nSubsC)){

  # Before/After
  breakC <- which(cogDataLong[[subject]]$V1 == 0)

  cogBefore[[subject]] <- cogDataLong[[subject]][1:(breakC-1),]
  temp <- cogBefore[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))
  cogBefore[[subject]] <- cogBefore[[subject]][decisionTrials,]

  cogAfter[[subject]] <- cogDataLong[[subject]][(breakC+1):length(cogDataLong[[subject]]$V1),]
  temp <- cogAfter[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))
  cogAfter[[subject]] <- cogAfter[[subject]][decisionTrials,]

  colnames(cogBefore[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                      "Experiment Time","Trial Outcome","Task Type","Task Setup")
  colnames(cogAfter[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                     "Experiment Time","Trial Outcome","Task Type","Task Setup")

  # Overall data cleaning
  # create an index for the trials in which a decision was made (completed, quit) 
  temp <- cogDataLong[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))

  # create a new list with only decision trials / without break
  tempC <- cogDataLong[[subject]]$V1 != 0  
  cogData[[subject]] <- cogDataLong[[subject]][decisionTrials,]
  cogDataLong[[subject]] <- cogDataLong[[subject]][tempC,]

  colnames(cogData[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                    "Experiment Time","Trial Outcome","Task Type","Task Setup")
  colnames(cogDataLong[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                        "Experiment Time","Trial Outcome","Task Type","Task Setup") # Long contains within-trial info

}

# clean physical group data
for (subject in seq(nSubsP)){

  # Before/After
  breakP <- which(physDataLong[[subject]]$V1 == 0)

  physBefore[[subject]] <- physDataLong[[subject]][1:(breakP - 1),]
  physAfter[[subject]] <- physDataLong[[subject]][(breakP + 1):length(physDataLong[[subject]]$V1),]

  colnames(physBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(physAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # create a new list with only decision trials / without break  
  tempP <- physDataLong[[subject]]$V1 != 0
  physData[[subject]] <- physDataLong[[subject]][tempP,]
  colnames(physData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

}

# clean pheaysical group data
for (subject in seq(nSubsE)){

  # Before/After
  breakE <- which(easyDataLong[[subject]]$V1 == 0)

  easyBefore[[subject]] <- easyDataLong[[subject]][1:(breakE - 1),]
  easyAfter[[subject]] <- easyDataLong[[subject]][(breakE + 1):length(easyDataLong[[subject]]$V1),]

  colnames(easyBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(easyAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # create a new list with only decision trials / without break  
  tempE <- easyDataLong[[subject]]$V1 != 0
  easyData[[subject]] <- easyDataLong[[subject]][tempE,]
  colnames(easyData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

}

# Combine before/after across subjects
cBefore <- rbind(cogBefore[[1]],cogBefore[[2]]) 
cAfter <- rbind(cogAfter[[1]],cogAfter[[2]]) 
wBefore <- rbind(waitBefore[[1]],waitBefore[[2]]) 
wAfter <- rbind(waitAfter[[1]],waitAfter[[2]]) 
pBefore <- rbind(easyBefore[[1]],physBefore[[2]])
pAfter <- rbind(physAfter[[1]],physAfter[[2]])
eBefore <- rbind(easyBefore[[1]],easyBefore[[2]])
eAfter <- rbind(easyAfter[[1]],easyAfter[[2]])

for (i in 3:nSubsW){

    wBefore <- rbind(wBefore,waitBefore[[i]])
    wAfter <- rbind(wAfter,waitAfter[[i]])

}

for (i in 3:nSubsC){

    cBefore <- rbind(cBefore,cogBefore[[i]])  
    cAfter <- rbind(cAfter,cogAfter[[i]])

}

for (i in 3:nSubsP){

    pBefore <- rbind(pBefore,physBefore[[i]])
    pAfter <- rbind(pAfter,physAfter[[i]])

}

for (i in 3:nSubsE){

    eBefore <- rbind(eBefore,easyBefore[[i]])
    eAfter <- rbind(eAfter,easyAfter[[i]])

}

#rm(cogBefore,cogAfter,waitBefore,waitAfter)

# aggregate ADD PHYS
waitBeforeAll <- aggregate(wBefore$Choice,
          by = list(wBefore$Reward, wBefore$Handling),
          FUN = 'mean')
waitAfterAll <- aggregate(wAfter$Choice,
          by = list(wAfter$Reward, wAfter$Handling),
          FUN = 'mean')
cogBeforeAll <- aggregate(cBefore$Choice,
          by = list(cBefore$Reward, cBefore$Handling),
          FUN = 'mean')
cogAfterAll <- aggregate(cAfter$Choice,
          by = list(cAfter$Reward, cAfter$Handling),
          FUN = 'mean')
physBeforeAll <- aggregate(pBefore$Choice,
          by = list(pBefore$Reward, pBefore$Handling),
          FUN = 'mean')
physAfterAll <- aggregate(pAfter$Choice,
          by = list(pAfter$Reward, pAfter$Handling),
          FUN = 'mean')
easyBeforeAll <- aggregate(eBefore$Choice,
          by = list(eBefore$Reward, eBefore$Handling),
          FUN = 'mean')
easyAfterAll <- aggregate(eAfter$Choice,
          by = list(eAfter$Reward, eAfter$Handling),
          FUN = 'mean')

rm(cBefore,cAfter,wBefore,wAfter, pBefore, pAfter, eBefore, eAfter)

# remove unnecessary variables
rm(temp,tempW,tempC,quitTrials,completeTrials,decisionTrials,subject)
```

``` {r Basic Prepping, echo=FALSE}  
# params for reference
handling <- c(2,10,14)
cond <- c("Wait","Cognitive","Physical","Easy")

# create data frame with summary stats
tempW <- summarizeData()
tempC <- summarizeData(Data = cogData, nSubs = nSubsC, type = "Cognitive")
tempP <- summarizeData(Data = physData, nSubs = nSubsP, type = "Physical")
tempE <- summarizeData(Data = easyData, nSubs = nSubsE, type = "Easy")

summaryData <- rbind(tempW,
                     tempC,
                     tempP,
                     tempE)

colnames(summaryData) <- c("Group","propComplete","Earnings","RT","forcedTravel")

summaryData$Cols <- c(rep(cols[1],nSubsW), rep(cols[2],nSubsC), rep(cols[3],nSubsP), rep(cols[4],nSubsE))
rm(tempW, tempC, tempP, tempE)

# Indexes for groups
indxWait <- seq(nSubsW)
indxWaitLong <- seq(nSubsW * 9) # 9 being the number of combinations
indxCog <- (nSubsW + 1):(nSubsW + nSubsC)
indxCogLong <- ((nSubsW * 9) + 1):((nSubsW * 9) + (nSubsC * 9))
indxPhys <- ((nSubsW + nSubsC) + 1):(nSubsW + nSubsC + nSubsP)
indxPhysLong <- ((nSubsW * 9) + (nSubsC * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9))
indxEasy <- ((nSubsW + nSubsC + nSubsP) + 1):totalSubs #(nSubsW + nSubsC + nSubsP + nSubsE)
indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))

# the other, just summarizing for all participants
# Not sure if this is necessary anymore
# allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
#                                 rep("Cognitive",nSubsC*3),
#                                 rep("Physical",nSubsP*3)),
#                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
#                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
#                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
#                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
#                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
#                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))

# Get the proportion completed per combination for GLMs
tempW <- propComplete()
tempC <- propComplete(Data = cogData, nSubs = nSubsC, indx = indxCog, type = "Cognitive")
tempP <- propComplete(Data = physData, nSubs = nSubsP, indx = indxPhys, type = "Physical")
tempE <- propComplete(Data = easyData, nSubs = nSubsE, indx = indxEasy, type = "Easy")

allProp2 <- rbind(tempW,
                  tempC,
                  tempP,
                  tempE)  
allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials

rm(tempW, tempC, tempP, tempE)

# add optimal vector and difference from optimal
wait <- c(rep(1,nSubsW*3),
          c(rep(0,nSubsW), rep(1,nSubsW*2)),
          c(rep(0,nSubsW*2), rep(1,nSubsW)))
cog <- c(rep(1,nSubsC*3),
          c(rep(0,nSubsC), rep(1,nSubsC*2)),
          c(rep(0,nSubsC*2), rep(1,nSubsC)))
phys <- c(rep(1,nSubsP*3),
          c(rep(0,nSubsP), rep(1,nSubsP*2)),
          c(rep(0,nSubsP*2), rep(1,nSubsP)))
easy <- c(rep(1,nSubsE*3),
          c(rep(0,nSubsE), rep(1,nSubsE*2)),
          c(rep(0,nSubsE*2), rep(1,nSubsE)))
allProp2$Optimal <- c(wait,cog,phys,easy)
allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete

# sort by subject ID
#allProp2 <- allProp2[order(allProp2$SubjID),]

# actual proportions and standard errors, and the optimal summary for plotting
trueProp <- aggregate(allProp2$propComplete,
            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
            FUN = 'mean')

trueSD <- aggregate(allProp2$propComplete,
          by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
          FUN = 'sd')
colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
trueProp$SE[1:9] <- (trueSD$x[1:9])/(sqrt(nSubsW))
trueProp$SE[10:18] <- (trueSD$x[10:18])/(sqrt(nSubsC))
trueProp$SE[19:27] <- (trueSD$x[19:27])/(sqrt(nSubsP))
trueProp$SE[28:36] <- (trueSD$x[28:36])/(sqrt(nSubsE))

trueProp$Optimal <- aggregate(allProp2$Optimal,
            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
            FUN = 'mean')$x
```

## Analyses

#### 16.1.	Tests of whether decision makers integrate delay and reward information.

  **16.1.1.**	*To address hypothesis 4.1., A logistic regression will be fit for each participant in order to predict trial-wise acceptances, using handling time and reward amount as predictors. The resulting beta coefficients for handling time and reward will be pooled across all participants, and we will perform a one-sample rank-sum test on each set of coefficients to examine whether the they are significantly positive or negative (compared to 0). If the group coefficients are significantly positive, it would mean that a predictor reliably increases the likelihood of acceptance. This will allow us to determine whether increments in handling time and reward amounts increased and decreased the likelihood of acceptance for each participant, respectively.*

``` {r 16.1.1., fig.align="center", fig.width=4, fig.height=4, echo=FALSE}
# Add an AR predictor based on the number of quits
waitData <- lapply(waitData, function(data) data %>% mutate(AR = seqQuits(Choice)))
cogData <- lapply(cogData, function(data) data %>% mutate(AR = seqQuits(Choice)))
physData <- lapply(physData, function(data) data %>% mutate(AR = seqQuits(Choice)))
easyData <- lapply(easyData, function(data) data %>% mutate(AR = seqQuits(Choice)))

# Logistic fits
waitLogis <- lapply(waitData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
cogLogis <- lapply(cogData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
physLogis <- lapply(physData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
easyLogis <- lapply(easyData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))

# Coefficients
waitLogis_coeffs <- t(sapply(waitLogis, "[[", "coefficients"))
cogLogis_coeffs <- t(sapply(cogLogis, "[[", "coefficients"))
physLogis_coeffs <- t(sapply(physLogis, "[[", "coefficients"))
easyLogis_coeffs <- t(sapply(easyLogis, "[[", "coefficients"))
allLogis_coeffs <- rbind(waitLogis_coeffs,
                         cogLogis_coeffs,
                         physLogis_coeffs,
                         easyLogis_coeffs)

# Rank sums
rankHand <- wilcox.test(allLogis_coeffs[,2])
rankReward <- wilcox.test(allLogis_coeffs[,3])

# Plot coeffs
temp <- melt(allLogis_coeffs[,2:3])
qplot(data = temp, x = Var2, y = value, geom = "boxplot") + 
  labs(title = "Handling and Reward Coefficients", x = "", y = "Coefficients") +
  geom_hline(yintercept = 0, alpha = 0.5) +
  theme_classic()

rm(waitLogis, cogLogis, physLogis, easyLogis)

```

The plot shows the pooled coefficients across subjects for the effect of each predictor. The results show the expected discounting effect of increasing the handling time, as well as the increase in acceptance likelihood as a function of reward increments. We found that these coefficients were significantly different from zero for both handling (V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) and reward (V = `r rankReward$statistic`, p `r ifelse(rankReward$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) regardless of cost condition.

\bigskip

  **16.1.2.**	*We will perform an extension of the logistic regression from 16.1.1., this time adding an autoregressive covariate containing the number of consecutive quits prior to a given trial. In this way, we will examine the possibility that participant choices were governed by recent quitting history rather than the experimental parameters (see 11.1.3.). Coefficients not significantly different from 0 will denote that a participant did not rely on recent quitting history.*

``` {r 16.1.2., echo=FALSE, fig.align="center"}
# Logistic fits
waitLogis <- lapply(waitData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
cogLogis <- lapply(cogData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
physLogis <- lapply(physData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
easyLogis <- lapply(easyData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))

# Coefficients
waitLogis_coeffs <- t(sapply(waitLogis, "[[", "coefficients"))
cogLogis_coeffs <- t(sapply(cogLogis, "[[", "coefficients"))
physLogis_coeffs <- t(sapply(physLogis, "[[", "coefficients"))
easyLogis_coeffs <- t(sapply(easyLogis, "[[", "coefficients"))
allLogis_coeffs <- rbind(waitLogis_coeffs,
                         cogLogis_coeffs,
                         physLogis_coeffs,
                         easyLogis_coeffs)

#waitLogis_coeffs <- sapply(waitLogis, function(data) (confint(data)[4,1] < 0 & confint(data)[4,2] > 0))

# Rank sums
rankAR <- wilcox.test(allLogis_coeffs[,4])

# Plot coeffs
temp <- melt(allLogis_coeffs[,2:4])

# The ugliest code, to check the existence of 0 on the CIs
AR_CIs <- data.frame(Subj = NULL, Low = NULL, High = NULL)
temp <- data.frame(Subj = seq(nSubsW), Low = rep(-0.1,nSubsW), High = rep(0,nSubsW))
for (i in seq(length(waitLogis))) {
  test <- tryCatch(round(confint(waitLogis[[i]]), digits = 2)[4,], error=function(e){})
  if(!is.null(test)) {
    temp$Low[i] <- test[1]
    temp$High[i] <- test[2]
  }
}
AR_CIs <- rbind(AR_CIs, temp)
temp <- data.frame(Subj = seq(nSubsC), Low = rep(0,nSubsC), High = rep(0,nSubsC))
for (i in seq(length(cogLogis))) {
  test <- tryCatch(round(confint(cogLogis[[i]]), digits = 2)[4,], error=function(e){})
  if(!is.null(test)) {
    temp$Low[i] <- test[1]
    temp$High[i] <- test[2]
  }
}
AR_CIs <- rbind(AR_CIs, temp)
temp <- data.frame(Subj = seq(nSubsP), Low = rep(0,nSubsP), High = rep(0,nSubsP))
for (i in seq(length(physLogis))) {
  test <- tryCatch(round(confint(physLogis[[i]]), digits = 2)[4,], error=function(e){})
  if(!is.null(test)) {
    temp$Low[i] <- test[1]
    temp$High[i] <- test[2]
  }
}
AR_CIs <- rbind(AR_CIs, temp)
temp <- data.frame(Subj = seq(nSubsE), Low = rep(0,nSubsE), High = rep(0,nSubsE))
for (i in seq(length(easyLogis))) {
  test <- tryCatch(round(confint(easyLogis[[i]]), digits = 2)[4,], error=function(e){})
  if(!is.null(test)) {
    temp$Low[i] <- test[1]
    temp$High[i] <- test[2]
  }
}
AR_CIs <- rbind(AR_CIs, temp)
AR_CIs$High[is.na(AR_CIs$High)] <- 0.1
AR_CIs$AR_Effect <- apply(AR_CIs,1, function(x) !(x[2] <= 0 & x[3] >= 0))

# Around 10% seemed to have been influenced by previous quitting
propAR_effects <- (sum(AR_CIs$AR_Effect) / totalSubs) * 100

rm(temp,waitLogis, cogLogis, physLogis, easyLogis)

```

To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero. By this measure, around `r round(propAR_effects)` percent of our participants seemed to have been influenced by recent quitting. However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.

\bigskip

  **16.1.3.**	*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable). No other covariates will be used, as this analysis is to confirm that over and under accepting are detrimental to total earnings. The quadratic term will be defined as the squared deviation from the optimal overall acceptance rate.*

``` {r 16.1.3. Earnings, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
# Pairwise comparison
# earningsPerm <- permute(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog]) # I believe this more
# earningsRsq <- cohenD(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog])

# linear model (think of doing a Poisson Regression instead, since earnings are not normally distributed [although bootstrapped they're fine])
propAllsq <- summaryData$propComplete^2 
lmEarn <- lm(Earnings ~ propComplete + propAllsq, data = summaryData)
summaryEarn <- summary(lmEarn)
coeffsEarn <- lmEarn$coefficients
summaryData$tempLine <- seq(0,1,length=84) # for plotting
summaryData$earnFitLine <- coeffsEarn[1] + coeffsEarn[2]*summaryData$tempLine + coeffsEarn[3]*(summaryData$tempLine^2)

# plotting
# boxplot(summaryData$Earnings[indxWait],
#         summaryData$Earnings[indxCog],
#         summaryData$Earnings[indxPhys],
#         summaryData$Earnings[indxEasy],
#         names = lbls,
#         main = "Total Earnings for Each Group",
#         ylab = "Total Earnings (pts)",
#         xlab = "Group",
#         col = cols)
# earnBoxplot <- ggplot(data = summaryData, aes(Group, Earnings, fill = Group)) +
#         geom_boxplot(show.legend = F) +
#         scale_fill_manual(values = cols) +
#         labs(title = "Total Earned per Group", y = "Total Earnings (Cents)", x = "") +
#         theme_classic()

# earnings (inverse-U, which makes sense because either over or under accepting are detrimental to earnings)
# plot(summaryData$propComplete[indxWait],
#      summaryData$Earnings[indxWait],
#      main = "Total Earnings as a Function of Proportion Accepted",
#      xlab = "Total Proportion Completed",
#      ylab = "Total Earned",
#      col=cols[1],
#      xlim=c(0.2,1),
#      ylim = c(1000,2000),
#      pch=16,
#      cex = lthick - 0.5)
# points(summaryData$propComplete[indxCog],
#        summaryData$Earnings[indxCog],
#        col=cols[2],
#        pch=16,
#        cex = lthick - 0.5)
# points(summaryData$propComplete[indxPhys],
#        summaryData$Earnings[indxPhys],
#        col=cols[3],
#        pch=16,
#        cex = lthick - 0.5)
# points(summaryData$propComplete[indxEasy],
#        summaryData$Earnings[indxEasy],
#        col=cols[4],
#        pch=16,
#        cex = lthick - 0.5)
# legend("topright",
#        lbls,
#        fill = cols,
#        cex = 0.8)
# lines(x, coeffsEarn[1] + coeffsEarn[2]*x + coeffsEarn[3]*(x^2),
#        col="black",
#       lwd = lthick)

earnFitplot <- ggplot(data = summaryData, aes(propComplete, Earnings)) + 
         geom_point(aes(color = Group), size = 2, show.legend = F) + 
         geom_line(aes(tempLine, earnFitLine), size = 1.5, alpha = 0.7) +
         scale_color_manual(values = cols) + 
         xlim(0.2,1) +
         labs(title = "Earnings as a Function of Acceptances", x = "Proportion Accepted", y = "") +
         theme_classic()

earnFitplot

```

The figure shows that participants that over and unceraccepted earned less money overall, as predicted. This is supported by a significant quadratic term from the linear model (F = `r round(summaryEarn$fstatistic[1], digits = 2)`, Beta = `r summaryEarn$coefficients[3,1]`, SE = `r round(summaryEarn$coefficients[3,2], digits = 2)`, R-squared = `r round(summaryEarn$r.squared, digits = 2)`; black line shows the fit). The following table shows all the results from the model.

``` {r 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
# Summary table for the linear model
panderOptions("digits", 2)
pander(lmEarn, style = "rmarkdown")

```

\bigskip

  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample (*one-sample? wouldn't it be paired vs optimal?*) t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.). This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*

``` {r 16.1.4., echo=FALSE}
# Split the data frame into every combination of parameters of interest
splitData <- split(allProp2, list(allProp2$Reward, allProp2$Handling, allProp2$Group))

# Perform a paired t-test on every combination of parameters
splitData_tests <- sapply(splitData, function(data) t.test(data$propComplete, data$Optimal, paired = T)$p.value)

# Adjust for multiple comparisons using BY-FDR
trueProp$Deviation_pval <- round(p.adjust(splitData_tests, method = "BY"), digits = 2)
trueProp$Deviation_pval[is.nan(trueProp$Deviation_pval)] <- 1
# trueProp[trueProp$Deviation_pval < 0.05, ]

# Proportion of significant deviations from optimality
splitData_prop <- round(sum(trueProp$Deviation_pval < 0.05, na.rm = T) / 36, digits = 2)
```

Of the 36 tests, around `r splitData_prop` were significantly deviant from optimality. Most of these were from effortful groups, as the wait group just showed deviations for 2 seconds handling/4 cent, and 10 seconds handling/8 cent offers (note to self: think about a way to properly .

\bigskip

#### 16.2.	Comparisons among the four delay and effort conditions.

  **16.2.1.**	*To compare preferences (hypothesis 4.2.), we will first perform a one-way ANOVA on the proportion of trials accepted using group as a factor. In addition, we will do pairwise comparisons on the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests). The same approach will be used for total earnings. This will give us an initial glimpse on the potential differences in cost among conditions.*

``` {r 16.2.1. Overall Proportion/Earnings,fig.align="center",fig.width=10,fig.height=4, echo=FALSE}  
## prop complete
# ecdfs
wait <- ecdf(summaryData$propComplete[indxWait])
cog <- ecdf(summaryData$propComplete[indxCog])
phys <- ecdf(summaryData$propComplete[indxPhys])
easy <- ecdf(summaryData$propComplete[indxEasy])
range <- seq(0,1,by=0.01)

test <- data.frame(range = range,
                   ecdf = c(wait(range),cog(range),phys(range),easy(range)),
                   Group = factor(c(rep("Wait",101),rep("Cognitive",101),rep("Physical",101),rep("Easy", 101)), levels = c("Wait","Cognitive","Physical","Easy")))

p1 <- ggplot(test, aes(x=range,y=ecdf, group=Group, color=Group))
p1 <- p1 + geom_line(show.legend = F, size = 1.5) +
    scale_color_manual(values = cols) +
    labs(title = "ECDF of Acceptances per Group", y="ECDF", x = "Proportion Accepted") +
    theme_classic()

# problem is, data is not normal, so we're going to bootstrap it and DEFINITELY permute
# Bootstrap nonparametric
B <- 5000
meanBootW <- bootstrap(summaryData$propComplete[indxWait],B = B) #rep(0,B)
meanBootC <- bootstrap(summaryData$propComplete[indxCog], B = B) #rep(0,B)
meanBootP <- bootstrap(summaryData$propComplete[indxPhys], B = B)
meanBootE <- bootstrap(summaryData$propComplete[indxEasy], B = B)

#CIs wait
meanW <- mean(meanBootW)
upperW <- quantile(meanBootW,0.975) # meanBoot?
lowerW <- quantile(meanBootW,0.025)

#CIs effort
meanC <- mean(meanBootC)
upperC <- quantile(meanBootC,0.975) # meanBoot?
lowerC <- quantile(meanBootC,0.025)

#CIs physical
meanP <- mean(meanBootP)
upperP <- quantile(meanBootP,0.975) # meanBoot?
lowerP <- quantile(meanBootP,0.025)

#CIs easy
meanE <- mean(meanBootE)
upperE <- quantile(meanBootE,0.975) # meanBoot?
lowerE <- quantile(meanBootE,0.025)

# formal testing 
# proportion completed
propAov <- aov(propComplete ~ factor(Group), data = summaryData)

# effect size (get the one for anovas)
# propRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])

# post-hoc
temp <- do.call(cbind, lapply(split(summaryData, summaryData$Group),"[[","propComplete"))
temp2 <- t(combn(colnames(temp),2))

propTests <- data.frame(Comparison = paste(temp2[,1], temp2[,2]),
                        T_pval = rep(1,6),
                        CohenD = rep(0,6))

for (i in seq(nrow(temp2))) {

  propTests$T_pval[i] <- round(permute(temp[,temp2[i,1]], temp[,temp2[i,2]])$Pval, digits = 2)
  propTests$CohenD[i] <- round(cohenD(temp[,temp2[i,1]], temp[,temp2[i,2]]), digits = 2)

}

# earnings
earnAov <- aov(Earnings ~ factor(Group), data = summaryData)

# effect size
# earnRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])

# post-hoc
temp <- do.call(cbind, lapply(split(summaryData, summaryData$Group),"[[","Earnings"))
temp2 <- t(combn(colnames(temp),2))

earnTests <- data.frame(Comparison = paste(temp2[,1], temp2[,2]),
                        T_pval = rep(1,6),
                        CohenD = rep(0,6))

for (i in seq(nrow(temp2))) {

  earnTests$T_pval[i] <- round(permute(temp[,temp2[i,1]], temp[,temp2[i,2]])$Pval, digits = 2)
  earnTests$CohenD[i] <- round(cohenD(temp[,temp2[i,1]], temp[,temp2[i,2]]), digits = 2)

}

rm(B,cog,wait,phys,easytemp,temp2)

# plot
p2 <- ggplot(summaryData, aes(x=Group, y=propComplete, fill = Group))
p2 <- p2 + geom_boxplot(show.legend = F) +
    scale_fill_manual(values = cols) +
    labs(title = "Proportion Completed by Group", y="Proportion Completed") +
    theme_classic()

p3 <- ggplot(summaryData, aes(x=Group, y=Earnings, fill = Group))
p3 <- p3 + geom_boxplot(show.legend = F) +
    scale_fill_manual(values = cols) +
    labs(title = "Earnings by Group", y="Total Earnings (Cents)") +
    theme_classic()

grid.arrange(p1, p2, p3, ncol = 3)
```

The plots show that subjects in the wait condition accepted the least and earned the most, suggesting a more optimal pattern of choices. Participants in the cognitive effort and easy conditions had higher more variable acceptance patterns, which are reflected in the comparatively low earnings. The reason why the easy condition does not show variable earnings like the cognitive effort group is probably due to the quadratic relationship between earnings and acceptances shown before.

\bigskip

  **16.2.2.**	*In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors. Reward and handling time will be within-subject factors, and condition a between-subjects factor. In support of hypotheses 4.1. and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions.*

``` {r 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
## REPEATED MEASURES ANOVA
# I think I like this the most
prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
                                 Error(SubjID / (Handling * Reward))))

#prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
 #                                Error(SubjID / (Handling * Reward))))

## NOTES ON RESULTS
# According to the logistic fit, there are main effects for all predictors, but no interactions. It also says that the overall odds for the wait group to accept versus the effort is around 16%. Similarly, increasing the handling time results in a decrease in the multiplicative odds of ~25%. Increments in reward increase the odds of acceptance by ~40%.
```

The plot below shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and condition (optimal acceptance rate indicated by the gray triangles). Visually, the graph confirms a couple of important intuitions. First, as the handling time increases, the proportion of acceptances decreases. Second, this discounting did not affect the 20 cent offers, as is expected from the present foraging environment. Lastly, and similar to the previous point, as the value of the offers increases so does the willingness to accept a trial. Beyond these general features, it is clear that the cognitive effort group accepted more than the other groups, regardless of the combination of experimental parameters. Notably, the optimality of this greater acceptance rate is determined by the timing context (e.g. optimal at 2 second handling time, but detrimental at 14 seconds).

``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
### THE PLOTS FOR YALE
# Ggplot made plotting way easier than the previous version
# This is in case you don't want to plot the easy condition (easier to see)
trueProp2 <- trueProp[-(28:36), ]

a1 <- ggplot(data = trueProp, aes(x=interaction(Reward, Handling), y=propComplete, color=Group)) + 
        geom_point(size=3) + 
        geom_errorbar(aes(ymin=propComplete-SE, ymax=propComplete+SE), width=0.2, size=1) +
        geom_line(aes(group = interaction(Handling, Group)), size=1) +
        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey48", color = "grey48", size = 3, show.legend = F) +
        labs(x = "Reward.Handling", y = "Proportion Accepted", title = "Proportion Accepted per Handling and Reward Combination") +
        scale_color_manual(values=cols) +
        theme_classic()

a1
```

These intuitions were formally tested using a repeated measures ANOVA, whose results are presented in the table below. Overall, the analysis partially confirmed our predictions. While all main effects were significant, there was an unexpected significant condition-by-reward interaction, which could be due to the performance of the "easy" group relative to their peers. Importantly, we found that the interaction between all three main parameters was not significant, thus suggesting that the effects of handling and reward on choices were not different across groups.

``` {r 16.2.2. rmANOVA table, pander}
# anova table
x <- summary(prop.aov)   
x <- x$`Error: Within`
panderOptions("digits", 2)
pander(x, style = "rmarkdown",split.table = 110)
```

\bigskip

  **16.2.3.**	*We will compute the probability of accepting a trial with a mixed-effects logistic regression. Based on the task structure and our main question, our a priori model of interest will include cost condition, handling time, and reward amount as fixed main effects, and subject ID as a random effect. Cost condition will be modeled with three categorical terms, with the fourth condition as the reference condition. We will run three versions of the model with different reference conditions, in order to test all pairwise differences among the four cost conditions. As with 16.2.2., we anticipate significant main effects (coefficients different than zero) of handling time, reward, and cost condition. We hypothesize that the differences among cost conditions will follow the pattern described in 4.2.*

``` {r 16.2.3. Mixed Effects Model, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
# just to make the logistic plotting comply with the function
allProp2 <- allProp2[order(as.character(allProp2$Group), decreasing = F), ]

# This transformation is necessary for a proper binomial fit of proportion data
totalQuit <- allProp2$totalTrials - allProp2$totalComplete
testBinom <- cbind(allProp2$totalComplete,totalQuit)

# Using a mixed-model fitted with GLMER
# Note: GLMER does not take quasi family distributions
# ranef() to display the random intercepts, fixef() for the model coefficients

# fit model
mixLogis_main <- list()
allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Wait"))
mixLogis_main$Wait <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Cognitive"))
mixLogis_main$Cognitive <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Physical"))
mixLogis_main$Physical <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Easy"))
mixLogis_main$Easy <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)

# Summarize model 
mixLogis_main$Summary <- summary(mixLogis_main$Wait)

# Coefficient matrices for all reference combos
t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,1], GroupWait = 0)
t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,1], GroupCognitive = 0)
t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,1], GroupPhysical = 0)
t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,1], GroupEasy = 0)
mixLogis_mainBetas <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
dimnames(mixLogis_mainBetas) <- list(cond[c(2,4,3,1)],c("Group",cond))
mixLogis_mainBetas <- as.matrix(mixLogis_mainBetas[,c(3,5,4,2)])

# And their respective p-values
t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,4], GroupWait = 1)
t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,4], GroupCognitive = 1)
t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,4], GroupPhysical = 1)
t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,4], GroupEasy = 1)
mixLogis_mainPvals <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
dimnames(mixLogis_mainPvals) <- list(cond[c(2,4,3,1)],c("Group",cond))
mixLogis_mainPvals <- as.matrix(mixLogis_mainPvals[,c(3,5,4,2)])

# Create CIs
sd <- sqrt(diag(vcov(mixLogis_main$Wait)))
mixLogisCI <- cbind(Est = fixef(mixLogis_main$Wait), LL = fixef(mixLogis_main$Wait) - 1.96 * sd, UL = fixef(mixLogis_main$Wait) + 1.96 * sd)
```

The plot below shows the distribution of random intercepts across participants of each group. Participants in the easy condition show much more variability than the other groups, potentially suggesting a bias in choices in this condition. Nonetheless, the intercepts per group are centered around zero.

``` {r 16.2.3. Mixed Effects Model plot rand intercepts, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
# plot random intercepts in increasing order
#RI1 <- qplot(seq(83), sort(ranef(mixLogis_main$Wait)$SubjID[,1]), color = cols[1], show.legend = F) + theme_classic()

# plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
temp <- cbind(summaryData$Group, 
              ranef(mixLogis_main$Wait)$SubjID)#, 
              #Colors = c(rep(cols[1],nSubsW),rep(cols[2],nSubsC),rep(cols[3],nSubsP),rep(cols[4],nSubsE)))
colnames(temp) <- list("Group", "RandIntercept")
RI1 <- ggplot(data = temp, aes(x = Group, y = RandIntercept, fill = Group)) + 
  geom_hline(yintercept = 0, alpha = 0.7) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = cols) + 
  labs(title = "Random Intercepts per Group", x = "") +
  theme_classic()

RI1
```

As predicted, the model showed significant main effects of handling time (Beta = `r mixLogis_main$Summary$coefficients[5,1]`, SE = `r mixLogis_main$Summary$coefficients[5,2]`, p < 0.001) and reward (Beta = `r mixLogis_main$Summary$coefficients[6,1]`, SE = `r mixLogis_main$Summary$coefficients[6,2]`, p < 0.001). In order to show the comparisons among all conditions, the following plot portrays the coefficients (color scale), and p-values (numbers within squares) that resulted from switching the reference condition. Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group (the darker the cell, the greater the odds). Based on this, we can see that the cognitive group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.

``` {r 16.2.3. Mixed Effects Model plot group coefficients, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
# plot coefficient matrix (show pvals!)
corrplot(abs(mixLogis_mainBetas), 
         p.mat = mixLogis_mainPvals, 
         is.corr = F, 
         method = "color", 
         tl.col = "black", 
         tl.srt = 0, 
         insig = "p-value", 
         sig.level = -1, 
         type = "lower",
         cl.length = 3)
mtext("Comparison", side = 2, line = 1.5, cex = 1.5)
mtext("Reference Group", side = 3, line = 1, cex = 1.5, at = 2.5)

rm(temp,t1,t2,t3,t4)

```

``` {r 16.2.3. Plot logistic model, echo=FALSE,fig.align="center",fig.width=6,fig.height=6}
# par(mfrow=c(1,1))
# ## Plotting the winning model (colors are messed up)
# rewards <- seq(1,20,length = 1000)
# # wait
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Wait",
#           handling = 2, 
#           reward = rewards, 
#           plotType = plot, 
#           color = cols[1],
#           lType = 6)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Wait",          
#           handling = 10, 
#           reward = rewards, 
#           color = cols[1],
#           lType = 3)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Wait",          
#           handling = 14, 
#           reward = rewards, 
#           color = cols[1])
# 
# 
# # cognitive
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Cognitive",
#           handling = 2, 
#           reward = rewards, 
#           color = cols[2],
#           lType = 6)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Cognitive",
#           handling = 10, 
#           reward = rewards, 
#           color = cols[2],
#           lType = 3)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Cognitive",
#           handling = 14, 
#           reward = rewards, 
#           color = cols[2])
# 
# 
# # physical
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Phys",
#           handling = 2, 
#           reward = rewards, 
#           color = cols[3],
#           lType = 6)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Phys",
#           handling = 10, 
#           reward = rewards, 
#           color = cols[3],
#           lType = 3)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Phys",
#           handling = 14, 
#           reward = rewards, 
#           color = cols[3])
# 
# # easy
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Easy",
#           handling = 2, 
#           reward = rewards, 
#           color = cols[4],
#           lType = 6)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Easy",
#           handling = 10, 
#           reward = rewards, 
#           color = cols[4],
#           lType = 3)
# 
# plotLogis(coeffs = logisComb$coefficients,
#           group = "Easy",
#           handling = 14, 
#           reward = rewards, 
#           color = cols[4])
# 
# # title
# title("Probabilities for All Handling-Reward Combinations \n for Each Group")
# 
# # x axis
# xticks <- c(0,min(rewards[rewards>4]),min(rewards[rewards>8]),20)
# axis(1,at = xticks,c(0,4,8,20))
# 
# # legend
# legend("bottomright",
#        c("Wait: 2s","Wait: 10s","Wait: 14s",
#          "Cognitive: 2s","Cognitive: 10s","Cognitive: 14s",
#          "Physical: 2s","Physical: 10s","Physical: 14s",
#          "Easy: 2s","Easy: 10s","Easy: 14s"), 
#        fill = c(cols[1],cols[1],cols[1],cols[2],cols[2],cols[2],cols[3],cols[3],cols[3],cols[4],cols[4],cols[4]),
#        lty = rep(c(6,3,1,8),3),
#        cex = 0.8)
# 
# 
# # actual proportions (maybe, maybe not)
# # points(c(5,10,25),trueProp$propComplete[1:3], col = cols[1], pch=17) # wait
# # points(c(5,10,25),trueProp$propComplete[4:6], col = cols[1], pch=17)
# # points(c(5,10,25),trueProp$propComplete[7:9], col = cols[1], pch=17)
# # 
# # points(c(5,10,25),trueProp$propComplete[19:21], col = cols[2], pch=17) # cog effort
# # points(c(5,10,25),trueProp$propComplete[22:24], col = cols[2], pch=17)
# # points(c(5,10,25),trueProp$propComplete[25:27], col = cols[2], pch=17)
# # 
# # points(c(5,10,25),trueProp$propComplete[10:12], col = cols[3], pch=17) # phys effort
# # points(c(5,10,25),trueProp$propComplete[13:15], col = cols[3], pch=17)
# # points(c(5,10,25),trueProp$propComplete[16:18], col = cols[3], pch=17)
# 
# # and the residuals
# # plot(logisComb$residuals,
# #      main = "Residuals for the Logistic Regression",
# #      xlab = "trial",
# #      ylab = "Residuals")
# # 
```

  **16.2.4.**	*Next, we will examine whether the a priori model from 16.2.3. outperforms both simpler and more complex models. Unlike the individual logistic regression fits in 16.1.1., a mixed-effects approach gives us a better goodness of fit measure for model comparisons. We will determine the best model (combination of predictors) using Akaike’s Information Criterion (AIC) to determine the model that minimizes the negative log-likelihood while penalizing the addition of parameters. The regression with each combination of predictors will be fitted in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) reward only; 5) condition, handling, and reward main effects (from 16.2.3.); 6) adding a handling-by-reward interaction; and 7) adding all three possible two-way interactions. We predict that model 5 will have the lowest AIC.*

This plot shows the AIC for every model. The last model to make significant fit contributions under the parameter penalty was indeed number 5.

``` {r 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Quasibinomial GLM versions (with proper proportion setup)
mixLogis_compare <- list()
mixLogis_compare$Base <- glmer(testBinom ~ 1 + (1 | SubjID), family = "binomial", data = allProp2) # intercept only
mixLogis_compare$Group <- glmer(testBinom ~ factor(Group) + (1 | SubjID), family = "binomial", data = allProp2) 
mixLogis_compare$Handling <- glmer(testBinom ~ factor(Group) + Handling + (1 | SubjID), family = "binomial", data = allProp2)
mixLogis_compare$Reward <- glmer(testBinom ~ factor(Group) + Reward + (1 | SubjID), family = "binomial", data = allProp2)
mixLogis_compare$AllMain <- mixLogis_main$Easy
mixLogis_compare$HRInteraction <- glmer(testBinom ~ factor(Group) + Handling * Reward + (1 | SubjID), family = "binomial", data = allProp2)
mixLogis_compare$AllInteractions <- glmer(testBinom ~ factor(Group) * Handling * Reward + (1 | SubjID), family = "binomial", data = allProp2)

# Model selection 
aicLogis_compare <- sapply(mixLogis_compare, AIC)

# effect size
mixLogis_compare$Rsq <- 1 - (deviance(mixLogis_compare$AllMain)/deviance(mixLogis_compare$Base)) # denominator is the null deviance
```

``` {r 16.2.4. Plot Deviance comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}

par(mar=c(5.1,2.1,2.1,2.1))    
# plot the deviance for all models
# ver 3
modelLabels <- c('Intercept','G Only','H Only','R Only','G + H + R','G + H * R','G * H * R')
plot(aicLogis_compare,
     main = "AIC for All Models",
     xlab = "",
     ylab = "AIC",
     pch = 16,
     xaxt = "n")
axis(1, at = 1:7, labels = F)
text(1:7, 
     par("usr")[3] - 22,
     labels = modelLabels, 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

```

\bigskip

#### 16.3.	Modeling the subjective opportunity cost in each condition.

  **16.3.1.**	*Response times (RT) for quit responses will be presented in a descriptive manner in order to examine whether participants tended to quit early or late within individual trials. Each cost group’s response time distribution will contain the pooled RT across its corresponding participants, and we will display the empirical cumulative distribution functions for each condition. Short RT would suggest confident and stable decisions (in support of 4.3.1.).*

We can see in the ECDFs below that most decisions to quit happened within the first second into the handling time. The reason why the physical and easy condition show slightly lagged responses is that the experiment allowed a one second grace period for participants to begin gripping. This results in some of them choosing to wait for that second to indicate an offer rejection.

``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
# RTs
# let's try to do some survival curves
RTW <- numeric() # vector of all decision-related RTs for the wait group
RTC <- numeric() # same for the cog group
RTP <- numeric()
RTE <- numeric()

# Wait group
for (subj in seq(nSubsW)){

    # index for trials quit
    tempChoiceW <- waitData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTW <- c(RTW,waitData[[subj]]$RT[tempChoiceW])

}

# Cognitive group
for (subj in seq(nSubsC)){

    # index for trials quit
    tempChoiceC <- cogData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTC <- c(RTC,cogData[[subj]]$`Choice RT`[tempChoiceC])

}

# Physical group
for (subj in seq(nSubsP)){

    # index for trials quit
    tempChoiceP <- physData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTP <- c(RTP,physData[[subj]]$RT[tempChoiceP])

}

# Pheaysical group
for (subj in seq(nSubsE)){

    # index for trials quit
    tempChoiceE <- easyData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTE <- c(RTE,easyData[[subj]]$RT[tempChoiceE])

}

# create an array with both data (for surv fit autoplot trials)
lenC <- length(RTC)
lenW <- length(RTW)
lenP <- length(RTP)
lenE <- length(RTE)

RTgroups <- c(rep("Wait",lenW), 
              rep("Effort",lenC), 
              rep("Physical",lenP),
              rep("Easy",lenE))
RTall <- c(RTW,RTC,RTP,RTE)

# plot ecdf 
ecdfW <- ecdf(RTW)
ecdfC <- ecdf(RTC)
ecdfP <- ecdf(RTP)
ecdfE <- ecdf(RTE)

range <- seq(0,10, by = 0.001)

plot(range,ecdfW(range),
     type = "l",
     main = "ECDF and CIs for the Response Times",
     xlab = "Seconds",
     ylab = "ECDF",
     xlim = c(0,5),
     col = cols[1],
     bty = "n",
     lwd = lthick)
lines(range,
      ecdfC(range),
      col = cols[2],
      lwd = lthick)
lines(range,
      ecdfP(range),
      col = cols[3],
      lwd = lthick)
lines(range,
      ecdfE(range),
      col = cols[4],
      lwd = lthick)
legend("right",
       lbls,
       fill = cols,
       cex = 0.8)

# and CIs for each (unnecessary unless I end up plotting)
CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
CIC <- median(CIC) - (quantile(CIC,0.025))
CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIW <- median(CIW) - (quantile(CIW,0.025))
CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIP <- median(CIP) - (quantile(CIP,0.025))
CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIE <- median(CIE) - (quantile(CIE,0.025))
lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)

# just cause, Kolmogrov-Smirnov 
# ksRT <- ks.test(RTW,RTC)
# RTPerm <- permute(RTW,RTC)
# RTCohen <- cohenD(RTW,RTC)

rm(lenC,lenW,lenP,lenE)

```

\bigskip

  **16.3.2.**	*In order to further examine choice stability (hypothesis 4.3.1.), we will compute each participant’s total proportion of acceptances pre- and post-midpoint. For each cost condition separately, we will fit a linear model that predicts post-midpoint acceptance from before-midpoint rates. We will report the slopes and 95% confidence intervals (CI) for each cost group. CIs containing 1 will denote that participants in that group produced consistent choices.*

``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
# THIS CODE CAN BE VASTLY IMPROVED, BUT RIGHT NOW IT WORKS SO I WON'T CARE
# This one just plots the correlation between pre-post acceptance rates, both overall and per cell
# The overall acceptance looks great, with mostly consistent rates, and with the physical group accepting slightly less post-break
# However, the per-cell distribution looks messy, although you can still tell that there's a linear relationship
# If I do a linear model predicting post with pre using cell-specific data, the betas are close to 1 and significant (also good R2s). That's good.

# create vdata frames that store acceptance data per combination cell pre-post break
waitB <- data.frame()
waitA <- data.frame()
cogB <- data.frame()
cogA <- data.frame()
physB <- data.frame()
physA <- data.frame()
easyB <- data.frame()
easyA <- data.frame()

# and for overall proportion accepted
waitBAll <- numeric()
waitAAll <- numeric()
cogBAll <- numeric()
cogAAll <- numeric()
physBAll <- numeric()
physAAll <- numeric() 
easyBAll <- numeric()
easyAAll <- numeric()

for (i in seq(nSubsW)){

  # wait
  tempPropB <- aggregate(waitBefore[[i]]$Choice, by = list(waitBefore[[i]]$Handling, waitBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(waitAfter[[i]]$Choice, by = list(waitAfter[[i]]$Handling, waitAfter[[i]]$Reward), FUN = 'mean')
  waitB <- rbind(waitB,tempPropB)
  waitA <- rbind(waitA,tempPropA)
  waitBAll[i] <- mean(waitBefore[[i]]$Choice) 
  waitAAll[i] <- mean(waitAfter[[i]]$Choice)

}

for (i in seq(nSubsC)){

  # cognitive
  tempPropB <- aggregate(cogBefore[[i]]$Choice, by = list(cogBefore[[i]]$Handling, cogBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(cogAfter[[i]]$Choice, by = list(cogAfter[[i]]$Handling, cogAfter[[i]]$Reward), FUN = 'mean')
  cogB <- rbind(cogB,tempPropB)
  cogA <- rbind(cogA,tempPropA)
  cogBAll[i] <- mean(cogBefore[[i]]$Choice) 
  cogAAll[i] <- mean(cogAfter[[i]]$Choice)

}

for (i in seq(nSubsP)){

  # physical
  tempPropB <- aggregate(physBefore[[i]]$Choice, by = list(physBefore[[i]]$Handling, physBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(physAfter[[i]]$Choice, by = list(physAfter[[i]]$Handling, physAfter[[i]]$Reward), FUN = 'mean')
  physB <- rbind(physB,tempPropB)
  physA <- rbind(physA,tempPropA)
  physBAll[i] <- mean(physBefore[[i]]$Choice) 
  physAAll[i] <- mean(physAfter[[i]]$Choice)

}

for (i in seq(nSubsE)){

  # easy
  tempPropB <- aggregate(easyBefore[[i]]$Choice, by = list(easyBefore[[i]]$Handling, easyBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(easyAfter[[i]]$Choice, by = list(easyAfter[[i]]$Handling, easyAfter[[i]]$Reward), FUN = 'mean')
  easyB <- rbind(easyB,tempPropB)
  easyA <- rbind(easyA,tempPropA)
  easyBAll[i] <- mean(easyBefore[[i]]$Choice) 
  easyAAll[i] <- mean(easyAfter[[i]]$Choice)

}

# Pre-post linear models
prepostLM <- list()
prepostLM$Wait <- lm(waitBAll ~ waitAAll)
prepostLM$Cognitive <- lm(cogBAll ~ cogAAll)
prepostLM$Physical <- lm(physBAll ~ physAAll)
prepostLM$Easy <- lm(easyBAll ~ easyAAll)

prepostSummary <- do.call(rbind, lapply(prepostLM, function(data) c(coef(data)[2], confint(data)[2,])))

```

The plot below shows that acceptance rates before and after the mid-point were mostly consistent, although it was more likely for participants to accept less in the second half of the experiment.

``` {r 16.3.2. Plot Pre/Post, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}

# overall proportion
plot(waitBAll,
     waitAAll,
     xlim = c(0,1),
     ylim = c(0,1),
     main = "Proportion accepted pre- and post-midpoint",
     xlab = "Acceptance Rate Before",
     ylab = "Acceptance Rate After",     
     col = cols[1],
     pch = 16)
points(cogBAll,
       cogAAll, 
       col = cols[2],
       pch = 16)
points(physBAll,
       physAAll, 
       col = cols[3],
       pch = 16)
points(easyBAll,
       easyAAll, 
       col = cols[4],
       pch = 16)
lines(seq(0,1,length = 10),
      seq(0,1,length = 10))
legend("bottomright",
       lbls,
       fill = cols,
       cex = 0.8)

# Another approach
# This will just plot the density of the completed trials before/after, trying to get at the possible fatigue experienced in the physical effort condition.
# Response patterns for each subject look pretty similar, with adequate optimality adaptation.
#
# for (i in 1:nSubs){
# plot(density(which(physBefore[[i]]$Choice==1)),
#      main = paste("Choices in time, before and after for subject:",i),
#      xlab = "Trials (completed)")
# lines(density(which(physAfter[[i]]$Choice==1)), col = "red")
# }
```

The following table shows the coefficients and CI for each linear model, and show that pre-post acceptance rates were very similar for each condition (i.e. one is present in all confidence intervals).

| Condition   |            Beta           |          CI-Low           |          CI-High          |
| :---------- | :-----------------------: | ------------------------: | ------------------------: |
| Wait        | $`r prepostSummary[1,1]`$ | $`r prepostSummary[1,2]`$ | $`r prepostSummary[1,3]`$ |
| Cognitive   | $`r prepostSummary[2,1]`$ | $`r prepostSummary[2,2]`$ | $`r prepostSummary[2,3]`$ |
| Physical    | $`r prepostSummary[3,1]`$ | $`r prepostSummary[3,2]`$ | $`r prepostSummary[3,3]`$ |
| Easy        | $`r prepostSummary[4,1]`$ | $`r prepostSummary[4,2]`$ | $`r prepostSummary[4,3]`$ |
Table: Predicting Post-mid acceptance from pre-mid choices: Coefficients and CI.

\bigskip

  **16.3.3.**	*To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type. OC will be computed as the product of a free parameter (gamma) and the handling time. Both gamma and the temperature parameter of the logistic function will be estimated at the subject level, independently for each subject.*

The gamma optimization search space was bound by extreme choice values. For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 25/2). Conversely, a participant experiencing low opportunity costs would accept the unbeneficial offer of 4 cents for a 14 second delay (or 4/14). The model was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood. The resulting gamma values per participant are shown per group below (gray lines denote the rate of earnings under optimal behavior for all 3 timing contexts), and reflect what was seen in the previous sections: participants in the wait and physical conditions showed higher gamma values (and thus opportunity costs) than in the other two groups. Given the high variability of the easy condition, it might be worth modeling each timing context independently, or perhaps fitting the model on subgroups defined by a median split of the participants based on their acceptance rate.

``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Estimate gamma per subject for each group separately
waitOC <- sapply(waitData, function(Data) {optimizeOCModel(Data)$Gamma})
cogOC <- sapply(cogData, function(Data) {optimizeOCModel(Data)$Gamma})
physOC <- sapply(physData, function(Data) {optimizeOCModel(Data)$Gamma})
easyOC <- sapply(easyData, function(Data) {optimizeOCModel(Data)$Gamma})

# Summarize for plotting
summaryOC <- data.frame(Group = rep(cond, each = nSubsC),
                        Gamma = c(waitOC, cogOC, physOC, easyOC))
summaryOC$Group <- factor(summaryOC$Group, levels = cond, ordered = T)

# plot
ggplot(summaryOC, aes(Group, Gamma, fill = Group)) +
  geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
  geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
  geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
  geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
  ylim(0,1.5) +
  labs(title = "Gamma Values per Group", x = "") +
  scale_fill_manual(values = cols) +
  theme_classic()

```

\bigskip

  **16.3.4.**	*We will cross-validate each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing. The estimates will be used to predict acceptances in the testing sample, and the mean percent correctly predicted will be reported for each group. This will also provide information on the stability of each participant’s choices (4.3.1.).*

As can be seen below, the gamma parameter from the OC model was able to predict post-midpoint choices successfully regardless of group.

``` {r 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Compute the OC for pre-midpoint
waitOCbefore <- sapply(waitBefore, function(Data) {optimizeOCModel(Data)$Gamma})
cogOCbefore <- sapply(cogBefore, function(Data) {optimizeOCModel(Data)$Gamma})
physOCbefore <- sapply(physBefore, function(Data) {optimizeOCModel(Data)$Gamma})
easyOCbefore <- sapply(easyBefore, function(Data) {optimizeOCModel(Data)$Gamma})

# Percent correctly predicted by pre-midpoint gamma
# Wait
predictOCWait <- numeric()
for (i in seq(nSubsW)) {
  temp <- (waitAfter[[i]]$Reward > (waitOCbefore[i] * waitAfter[[i]]$Handling))
  temp[temp == TRUE] <- 1
  predictOCWait[i] <- (sum(temp==waitAfter[[i]]$Choice) / length(waitAfter[[i]]$Choice)) * 100 
}

# Cognitive
predictOCCog <- numeric()
for (i in seq(nSubsC)) {
  temp <- (cogAfter[[i]]$Reward > (cogOCbefore[i] * cogAfter[[i]]$Handling))
  temp[temp == TRUE] <- 1
  predictOCCog[i] <- (sum(temp==cogAfter[[i]]$Choice) / length(cogAfter[[i]]$Choice)) * 100 
}

# Physical
predictOCPhys <- numeric()
for (i in seq(nSubsW)) {
  temp <- (physAfter[[i]]$Reward > (physOCbefore[i] * physAfter[[i]]$Handling))
  temp[temp == TRUE] <- 1
  predictOCPhys[i] <- (sum(temp==physAfter[[i]]$Choice) / length(physAfter[[i]]$Choice)) * 100 
}

# Easy
predictOCEasy <- numeric()
for (i in seq(nSubsW)) {
  temp <- (easyAfter[[i]]$Reward > (easyOCbefore[i] * easyAfter[[i]]$Handling))
  temp[temp == TRUE] <- 1
  predictOCEasy[i] <- (sum(temp==easyAfter[[i]]$Choice) / length(easyAfter[[i]]$Choice)) * 100 
}

# Summarize for plotting
summaryOCPredict <- data.frame(Group = rep(cond, each = nSubsC),
                        percentPredicted = c(predictOCWait, predictOCCog, predictOCPhys, predictOCEasy))
summaryOCPredict$Group <- factor(summaryOCPredict$Group, levels = cond, ordered = T)

meanOCPredict <- aggregate(percentPredicted ~ Group, data = summaryOCPredict,FUN = 'mean')

# plot
ggplot(summaryOCPredict, aes(Group, percentPredicted, fill = Group)) +
  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
  labs(title = "Percent of Choices Correctly Predicted by Gamma per Group", x = "") +
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = cols) +
  labs(y = "Percent Predicted") +
  ylim(0,100) +
  theme_classic()
```

\bigskip

  **16.3.5.**	*The OC estimates for each group will be compared using an ANOVA with condition as a factor. This will let us determine which cost type produced the highest discounting.*

``` {r 16.3.5. OC comparisons, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# ANOVA
anovaOC <- summary(aov(Gamma ~ Group, data = summaryOC))
Fval <- anovaOC[[1]]$`F value`[1]
Pval <- anovaOC[[1]]$`Pr(>F)`[1]
Rsquared_aov <- round(anovaOC[[1]]$`Sum Sq`[1] / sum(anovaOC[[1]]$`Sum Sq`), digits = 2)

# Post-hoc pairwise tests
permuteOCTest <- list()
permuteOCTest$WvC <- permute(waitOC, cogOC)
permuteOCTest$WvP <- permute(waitOC, physOC)
permuteOCTest$WvE <- permute(waitOC, easyOC)
permuteOCTest$CvP <- permute(cogOC, physOC)
permuteOCTest$CvE <- permute(cogOC, easyOC)
permuteOCTest$PvE <- permute(physOC, easyOC)
```

The analysis of variance was significant (F = `r round(Fval, digits = 2)`, p = `r Pval`, R-squared = `r Rsquared_aov`). Pairwise post-hoc permutations showed significantly greater values for the wait group versus the cognitive (p = `r permuteOCTest$WvC$Pval`) and easy (p = `r permuteOCTest$WvE$Pval`) groups, as well as significantly greater gammas for the physical group and the cognitive group (p = `r permuteOCTest$CvP$Pval`). These results suggest that participants engaged in cognitively effortful demands experience significantly lower opportunity costs than those whose demands involve physical effort and pure delay. The reason for this is unclear, and we will work on it in the near future.

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip

## Notes

- Update the AIC, RT ECDF, pre-post plots with ggplot.

- This plot is just to show participant-specific behavior for all groups.

``` {r Testing grounds, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}
cond <- as.character(unique(summaryData$Group))

i <- 1
test <- allProp2[allProp2$Group == cond[i], ]
test2 <- trueProp[trueProp$Group == cond[i], ]
t1 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
  geom_point(size=3, color = cols[i]) +
  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
  theme_classic()

i <- 2
test <- allProp2[allProp2$Group == cond[i], ]
test2 <- trueProp[trueProp$Group == cond[i], ]
t2 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
  geom_point(size=3, color = cols[i]) +
  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
  theme_classic()

i <- 3
test <- allProp2[allProp2$Group == cond[i], ]
test2 <- trueProp[trueProp$Group == cond[i], ]
t3 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
  geom_point(size=3, color = cols[i]) +
  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
  theme_classic()

i <- 4
test <- allProp2[allProp2$Group == cond[i], ]
test2 <- trueProp[trueProp$Group == cond[i], ]
t4 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
  geom_point(size=3, color = cols[i]) +
  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
  theme_classic()

grid.arrange(t1,t3,t2,t4, ncol = 2)

```

### 2018-10-11 Cost2_testingGround.Rmd
First import of all the data and scripts

---
title: "MA681 Final Project"
author: "Claudio Toro Serey"
date: "Fall 2017"
output:
  html_document: default
  fig_caption: true
  #pdf_document:
  #  pandoc_args: [
  #  "-V", "classoption=twocolumn"]  
---

# Final project

Packages used: survival (survival analysis on RTs), tidyverse, ggfortify, knitr, pwr (for power analyses), nloptr (for nonlinear optimization problems) and pander.

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

``` {r, echo=FALSE}
##------------- functions, libraries, and setups--------------
# libraries
#library(survival)
library(tidyverse)
library(ggfortify)
library(knitr)
library(pander) 
library(nloptr)
library(pwr)
library(lme4)
library(lmerTest)

## Miscelaneous
lbls <- c("Wait","Cognitive","Physical","Easy")
cols = c("#78AB05","#D9541A","deepskyblue4", "grey50") # plot colors (wait, effort)
lthick = 2 # line thickness for plots

## Functions
# Permutation for 2 groups
permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){

    # prep data
    summaryPerm <- list()
    lOne <- length(group1)
    lTwo <- length(group2)
    bigSample <- c(group1,group2)

    if (paired == FALSE) {

        for (i in 1:nPerms){

            # relabel samples
            tempBig <- sample(bigSample)
            tempOne <- tempBig[1:lOne]
            tempTwo <- tempBig[(lOne+1):length(bigSample)]

            # stats
            tempDiffs <- statType(tempOne,na.rm=T) - statType(tempTwo,na.rm=T)
            summaryPerm$jointDist[i] <- tempDiffs # statType(tempDiffs, na.rm = T)

        }

    } else {

        for (i in 1:nPerms){

            # shift labels in a pairwise fashion
            tempDiffs <- statType((-1)^rbinom(lOne,1,0.5) * (group1 - group2))
            summaryPerm$jointDist[i] <- tempDiffs

        }

    }

    # get the observed difference
    diffs <- statType(group1,na.rm=T) - statType(group2,na.rm=T)
    observedAbs <- abs(diffs) # maybe leave it as means here
    observed <- diffs
    summaryPerm$Pval <- 2 * (1 - ecdf(summaryPerm$jointDist)(observedAbs))
    if (length(unique(abs(summaryPerm$jointDist))) == 1) {summaryPerm$Pval <- 1} # if the difference is always the same, then p = 1
    summaryPerm$Observed <- observed

    return(summaryPerm)

}

# Non-parametric Bootstrap for a single group
bootstrap <- function(group = 1, statType = mean, B = 5000){

    # prep param
    bootStats <- rep(0,B)

    # iterate
    for(b in 1:B){

      # wait group
      x <- sample(group,length(group),replace=T)  
      bootStats[b] <- statType(x,na.rm = T)

    }

    return(bootStats)

}

# plot logistic (for the prop complete test, mainly, but it can be easily expanded for more flexibility in n-params)
plotLogis <- function(coeffs = 1, group = "Cognitive", handling = 1:14, reward = 1:20, xAxis = "Reward", plotType = lines, color = "black", lType = 1, pchType = 16){

    # divide into relevant coefficients (assumes logisComb was the best model)
    intercept <- coeffs[1]
    cogBeta <- coeffs[2]    
    physBeta <- coeffs[3]
    easyBeta <- coeffs[4]
    handBeta <- coeffs[5]
    rwdBeta <- coeffs[6]

    #wait <- numeric()
    #phys <- numeric()

    # now the parameters
    label = "Reward Amount"
    if (group == "Cognitive"){cog = 1} else {cog = 0}
    if (group == "Phys"){phys = 1} else {phys = 0}
    if (group == "Easy") {easy = 1} else {easy = 0}
    if (xAxis == "Reward"){
        xAxis = reward 
        label = "Reward Amount" 
    } else {
        xAxis = handling
        label = "Handling Time"
    }

    # logistic function
    model <- intercept + cogBeta*cog + physBeta*phys + easyBeta*easy + handBeta*handling + rwdBeta*reward 
    func <- 1 / (1 + exp(-(model)))
    plotType(xAxis,
         func,
         ylim = c(0,1),
         xlim = c(0,25),
         xlab = label,
         ylab = "Probability of Completing a Trial",
         type="l",
         col = color,
         lty = lType,
         pch = pchType,
         lwd = 2,
         xaxt = "n",
         bty = "n")

    # use title() to add title afterwards
}

# Cohen's D for 2 groups
# for a more flexible approach, make the data input to be a list with entries for n groups, 
# then do length(list) for the number of groups. 
cohenD <- function(group1 = 1, group2 = 2){

      # means
      mean1 <- mean(group1, na.rm = T)
      mean2 <- mean(group2, na.rm = T)

      # variance
      var1 <- var(group1, na.rm = T)
      var2 <- var(group2, na.rm = T)

      # equation
      out <- (mean1 - mean2) / sqrt((var1 + var2)/2)

      return(out)

}

# get the number of continuous quits before current trial
seqQuits <- function(subjData = 1){

    # get the lag
    tempSeq <- sequence(rle(subjData)$lengths) # sequence
    tempSeq[subjData==1] <- 0 # not interested in completed runs, just quits
    tempSeq <- c(0,tempSeq) # lag it so it can be used as a t-1 regressor

    # return data so that the length is equivalent
    out <- tempSeq[1:length(subjData)]

    return(out)

}

# basic power calculation for a one way ANOVA
powerCalc <- function(d = 1.2, Za = 1.96, Zb = 0.842){

  out <- 2*((Za + Zb)/d)^2 + (0.25*(Za^2))

  return(round(out))

}

## gather basic data (this is better as a function, then rbind)
summarizeData <- function(Data = waitData, nSubs = nSubsW, type = "Wait"){

  tempSummary <- data.frame(group = rep(type, nSubs))

  if (type == "Cognitive") {

    for (subj in seq(nSubs)){

        # Choice index
        tempChoice <- Data[[subj]]$Choice

        # Proportion complete
        tempSummary[subj,2] <- mean(tempChoice)

        # earnings
        tempSummary[subj,3] <- sum(Data[[subj]]$Reward[tempChoice==1])

        # RTs
        tempSummary[subj,4] <- median(Data[[subj]]$`Choice RT`[tempChoice==0])

        # Mistakes (only for cognitive effort group)
        tempMistakes <- sum(cogDataLong[[subj]]$`Trial Outcome`=="Forced travel") # how many forced travel trials
        tempTrialnum <- length(Data[[subj]]$Choice) # how many decision trials
        tempSummary[subj,5] <- tempMistakes / (tempMistakes + tempTrialnum) # proportion of forced travels throughout the exp

    }

  } else {

    for (subj in seq(nSubs)){

        # choice index
        tempChoice <- Data[[subj]]$Choice

        # propotion complete
        tempSummary[subj,2] <- mean(tempChoice)

        # earnings
        tempSummary[subj,3] <- sum(Data[[subj]]$Reward[tempChoice==1])

        # RTs
        tempSummary[subj,4] <- median(Data[[subj]]$RT[tempChoice==0])

        # Mistakes (to allow for mistakes on the cognitive group)
        tempSummary[subj,5] <- NA

    }

  }

  return(tempSummary)

}

# Summarize the proportion complete for GLMs
propComplete <- function(Data = waitData, nSubs = nSubsW, indx = indxWait, type = "Wait") {

    tempProp <- data.frame(SubjID = rep(indx,9),
                           Group = rep(type,nSubs*9),
                           Handling = c(rep(2,nSubs*3), 
                                        rep(10,nSubs*3), 
                                        rep(14,nSubs*3)),
                           Reward = rep(c(rep(5,nSubs),rep(10,nSubs),rep(25,nSubs)),3),
                           propComplete = rep(NA,length(indx)*9),
                           totalTrials = rep(NA,length(indx)*9),
                           totalComplete = rep(NA,length(indx)*9))

    for (subj in seq(nSubs)){

      # handling of 2s
      tempProp$propComplete[subj] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+nSubs] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*2)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+nSubs] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*2)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==20])

      # handling of 10s
      tempProp$propComplete[subj+(nSubs*3)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+(nSubs*4)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*5)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj+(nSubs*3)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+(nSubs*4)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*5)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==20])

      # handling of 14s
      tempProp$propComplete[subj+(nSubs*6)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==4])
      tempProp$propComplete[subj+(nSubs*7)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==8])
      tempProp$propComplete[subj+(nSubs*8)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==20])
      tempProp$totalTrials[subj+(nSubs*6)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==4])
      tempProp$totalTrials[subj+(nSubs*7)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==8])
      tempProp$totalTrials[subj+(nSubs*8)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==20])

    }

    return(tempProp)

}

```

``` {r, echo=FALSE}
### data loading and cleaning up

# load cognitive effort group
setwd('/Volumes/Addon/Grad school/Cost2_data/cog')
temp = list.files(pattern="*.csv")
cogDataLong = lapply(temp, read.csv, header = FALSE)

# load wait group
setwd('../wait')
temp = list.files(pattern="*.csv")
waitDataLong = lapply(temp, read.csv, header = FALSE)

# load physical group
setwd('../phys')
temp = list.files(pattern="*.csv")
physDataLong = lapply(temp, read.csv, header = FALSE)

# load pheasysical group
setwd('../easy')
temp = list.files(pattern="*.csv")
easyDataLong = lapply(temp, read.csv, header = FALSE)

### cleaning data
# this will generate a simple list with only info about trials that participants quit or completed
# this is because cognitive logs also include within-trial task-specific information
# for the wait condition, it will get rid of the break indicator

nSubsW <- length(waitDataLong)
nSubsC <- length(cogDataLong)
nSubsP <- length(physDataLong)
nSubsE <- length(easyDataLong)
totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE) # why didn't I think of this before...

#  short lists
cogData <- list()
waitData <- list()
physData <- list()
easyData <- list()

# For pre-post analysis
cogBefore <- list()
cogAfter <- list()
waitBefore <- list()
waitAfter <- list()
physBefore <- list()
physAfter <- list()
easyBefore <- list()
easyAfter <- list()

# clean wait group data
for (subject in seq(nSubsW)){

  # Before/after
  breakW <- which(waitDataLong[[subject]]$V1 == 0)

  waitBefore[[subject]] <- waitDataLong[[subject]][1:(breakW - 1),]
  waitAfter[[subject]] <- waitDataLong[[subject]][(breakW + 1):length(waitDataLong[[subject]]$V1),]

  # assign header names
  colnames(waitBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(waitAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # Overall data cleaning
  tempW <- waitDataLong[[subject]]$V1 != 0

  # create a new list with only decision trials / without break
  waitData[[subject]] <- waitDataLong[[subject]][tempW,]

  # assign header names
  colnames(waitData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

}

# clean cognitive group data
for (subject in seq(nSubsC)){

  # Before/After
  breakC <- which(cogDataLong[[subject]]$V1 == 0)

  cogBefore[[subject]] <- cogDataLong[[subject]][1:(breakC-1),]
  temp <- cogBefore[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))
  cogBefore[[subject]] <- cogBefore[[subject]][decisionTrials,]

  cogAfter[[subject]] <- cogDataLong[[subject]][(breakC+1):length(cogDataLong[[subject]]$V1),]
  temp <- cogAfter[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))
  cogAfter[[subject]] <- cogAfter[[subject]][decisionTrials,]

  colnames(cogBefore[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                      "Experiment Time","Trial Outcome","Task Type","Task Setup")
  colnames(cogAfter[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                     "Experiment Time","Trial Outcome","Task Type","Task Setup")

  # Overall data cleaning
  # create an index for the trials in which a decision was made (completed, quit) 
  temp <- cogDataLong[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))

  # create a new list with only decision trials / without break
  tempC <- cogDataLong[[subject]]$V1 != 0  
  cogData[[subject]] <- cogDataLong[[subject]][decisionTrials,]
  cogDataLong[[subject]] <- cogDataLong[[subject]][tempC,]

  colnames(cogData[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                    "Experiment Time","Trial Outcome","Task Type","Task Setup")
  colnames(cogDataLong[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
                                        "Experiment Time","Trial Outcome","Task Type","Task Setup") # Long contains within-trial info

}

# clean physical group data
for (subject in seq(nSubsP)){

  # Before/After
  breakP <- which(physDataLong[[subject]]$V1 == 0)

  physBefore[[subject]] <- physDataLong[[subject]][1:(breakP - 1),]
  physAfter[[subject]] <- physDataLong[[subject]][(breakP + 1):length(physDataLong[[subject]]$V1),]

  colnames(physBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(physAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # create a new list with only decision trials / without break  
  tempP <- physDataLong[[subject]]$V1 != 0
  physData[[subject]] <- physDataLong[[subject]][tempP,]
  colnames(physData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

}

# clean pheaysical group data
for (subject in seq(nSubsE)){

  # Before/After
  breakE <- which(easyDataLong[[subject]]$V1 == 0)

  easyBefore[[subject]] <- easyDataLong[[subject]][1:(breakE - 1),]
  easyAfter[[subject]] <- easyDataLong[[subject]][(breakE + 1):length(easyDataLong[[subject]]$V1),]

  colnames(easyBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(easyAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  # create a new list with only decision trials / without break  
  tempE <- easyDataLong[[subject]]$V1 != 0
  easyData[[subject]] <- easyDataLong[[subject]][tempE,]
  colnames(easyData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

}

# Combine before/after across subjects
cBefore <- rbind(cogBefore[[1]],cogBefore[[2]]) 
cAfter <- rbind(cogAfter[[1]],cogAfter[[2]]) 
wBefore <- rbind(waitBefore[[1]],waitBefore[[2]]) 
wAfter <- rbind(waitAfter[[1]],waitAfter[[2]]) 
pBefore <- rbind(easyBefore[[1]],physBefore[[2]])
pAfter <- rbind(physAfter[[1]],physAfter[[2]])
eBefore <- rbind(easyBefore[[1]],easyBefore[[2]])
eAfter <- rbind(easyAfter[[1]],easyAfter[[2]])

for (i in 3:nSubsW){

    wBefore <- rbind(wBefore,waitBefore[[i]])
    wAfter <- rbind(wAfter,waitAfter[[i]])

}

for (i in 3:nSubsC){

    cBefore <- rbind(cBefore,cogBefore[[i]])  
    cAfter <- rbind(cAfter,cogAfter[[i]])

}

for (i in 3:nSubsP){

    pBefore <- rbind(pBefore,physBefore[[i]])
    pAfter <- rbind(pAfter,physAfter[[i]])

}

for (i in 3:nSubsE){

    eBefore <- rbind(eBefore,easyBefore[[i]])
    eAfter <- rbind(eAfter,easyAfter[[i]])

}

#rm(cogBefore,cogAfter,waitBefore,waitAfter)

# aggregate ADD PHYS
waitBeforeAll <- aggregate(wBefore$Choice,
          by = list(wBefore$Reward, wBefore$Handling),
          FUN = 'mean')
waitAfterAll <- aggregate(wAfter$Choice,
          by = list(wAfter$Reward, wAfter$Handling),
          FUN = 'mean')
cogBeforeAll <- aggregate(cBefore$Choice,
          by = list(cBefore$Reward, cBefore$Handling),
          FUN = 'mean')
cogAfterAll <- aggregate(cAfter$Choice,
          by = list(cAfter$Reward, cAfter$Handling),
          FUN = 'mean')
physBeforeAll <- aggregate(pBefore$Choice,
          by = list(pBefore$Reward, pBefore$Handling),
          FUN = 'mean')
physAfterAll <- aggregate(pAfter$Choice,
          by = list(pAfter$Reward, pAfter$Handling),
          FUN = 'mean')
easyBeforeAll <- aggregate(eBefore$Choice,
          by = list(eBefore$Reward, eBefore$Handling),
          FUN = 'mean')
easyAfterAll <- aggregate(eAfter$Choice,
          by = list(eAfter$Reward, eAfter$Handling),
          FUN = 'mean')

rm(cBefore,cAfter,wBefore,wAfter, pBefore, pAfter, eBefore, eAfter)
#--------------------------
# remove unnecessary variables
rm(temp,tempW,tempC,quitTrials,completeTrials,decisionTrials,subject)
```

## Introduction

Decisions lie at the actionable core of human experience. Much of what we see in others, such as the way they dress or what they eat, can be conveyed as a result of their choices. An important aspect of such decisions involves weighing the value of an outcome against the cost incurred in obtaining it. This cost-value interaction has many forms and characteristics, such as the allocation of monetary resources, or the uncertainty of obtaining of an outcome versus a sure gain. A considerable amount of work has been focused on understanding the nature of value (Schultz, 2015). Cost, on the other hand, is less understood. A prevalent idea is that effort can act as a discounting factor.  Indeed, effort has been shown to be an actively avoided cost that devalues rewards, so that decision makers will prefer small rewards tied to low demands over large rewards that require high effort (Massar, Libedinsky, Weiyan, Huettel, & Chee, 2015). Importantly, this effect is independent from the amount of errors made in the task (Apps, Grima, Manohar, & Husain, 2015; Kool, McGuire, Rosen, & Botvinick, 2010; Westbrook, Kester, & Braver, 2013).

\bigskip

In the animal literature, the amount of effort a subject is willing to exert for a reward can be probed by increasing the ratio of responses required per each reinforcement until an animal refuses to work for the reward (Richardson & Roberts, 1996). Although findings from such studies have provided important information about the cost of effort in general, controversy regarding the particular nature of cognitive and physical effort persists (Westbrook & Braver, 2015). This debate has motivated investigators to characterize these types of effort more precisely (Schmidt, Lebreton, Cléry-Melin, Daunizeau, & Pessiglione, 2012; Walton, Kennerley, Bannerman, Phillips, & Rushworth, 2006). However, even though effort can be seen as cost in and of itself (Botvinick, Huffstetler, & McGuire, 2009), in ecological scenarios the magnitude of effort required by a task often affects the amount of time that is spent performing it. For example, going through an additional section of one’s tax return involves weighing both the mental effort and the extra time it takes against the reward attained. This is an important consideration. Multiple studies show that delayed rewards are discounted, so that having to wait longer for an outcome makes it less rewarding (Ainslie, 1975; Frederick, Loewenstein, & O ’donoghue, 2002; Green, Fristoe, & Myerson, 1994; Mcclure, Ericson, Laibson, Loewenstein, & Cohen, 2004). Additional investigations suggest that delay is discounted in a qualitatively similar fashion to physical (Prévost, Pessiglione, Météreau, Cléry-Melin, & Dreher, 2010) and mental effort (Massar et al., 2015). Although these studies have examined cost differences by combining time with physical or cognitive effort, there is currently no evidence on how participants would actively choose between all three types of cost. Recent findings demonstrate that cost related to physical and mental effort is computed differently in the brain (Hosking, Floresco, & Winstanley, 2014; Kurniawan et al., 2011; Westbrook & Braver, 2015), thus highlighting the need to examine these effects simultaneously. Because of this, it is important to understand if and how effort acts as a source of cost that is distinct from delay, and how this dissociation is represented in people’s choices.

\bigskip

The original aim of this project is to use behavioral and neuroimaging methods to investigate the potential differences in cost between time, cognitive effort, and physical effort. However, the results presented here pertain to behavioral pilot data that is limited to cognitive effort and pure time. These attributes are examined in a between-subject manner in order to provide a baseline that will guide future within-subject examinations. In particular, we explore how participants behave when faced with a modified foraging task, and estimate their individual opportunity cost of time to measure perceived cost for each group. We also sought to investigate the hypothesis that experiential phenomena would alter subjects' acceptance rates. Specifically we looked for sequential effects, such as an increase in the rate of rejecting or quitting trials leading a subject to subsequently accept more trials, as well as temporal effects, such as the onset of a sense of urgency leading to an increase in trial acceptance as the subject estimates that the trial block is nearing its end.

## Methods

Subjects:  A total of 22 healthy subjects (age 18-23; 13 female) were recruited from Psychology 101 classes through the Boston University SONA system. This system prohibits paying subjects for their time, as credits are given instead. Because of this limitation, participants were told to acquire as many points as possible during the task. All participants were consented before the experiment began, and all verbalized their understanding of the task after a short practice session. After the task, subjects were questioned on their within-task behavior, and all mentioned that they followed a specific strategy that they developed early on in the task. We thus found no reason to exclude any participants for this analysis.

\bigskip

Foraging task:  Temporal decision tasks differ from typical economic ones in that decision makers have the opportunity to reevaluate their choice until the time of reward. If the perceived cost of the current task surpasses the expected benefit during the waiting interval, switching to a different environment might prove beneficial. Foraging tasks are well equipped to measure these dynamics (Stephens & Krebs, 1986). In this experiment we crafted a modified version of classic experimental settings. Traditionally, foraging tasks offer the participant the option to harvest an environment whose reward progressively depletes (usually called the “patch”), or to quit and go to a new location with replenished resources. Once the reward amount in the current patch becomes lower than the expected reward in a different one, the decision maker should quit harvesting and “travel” to a new patch. The travel time is identified as varying and unrewarding, so decision makers have to make careful choices based on the current rate of reward (Hayden et al., 2011). The present study modifies this structure in an important way. Instead of harvesting a depleting source across trials, participants face individual trials in which they wait a given amount of time for a reward (the handling time). If the reward amount is not worth the time, the participant can quit the trial, forfeit the reward, and wait a different amount of time (traveling time) to try a new (and potentially more rewarding) trial. Quitting a trial is followed by the appearance of a progress bar that displays their traveling time (this bar is not present during handling times). Participants are shown the total amount of points they can earn at the beginning of each trial (5, 10, or 25 points, equally distributed). These amounts are explicitly disclosed during the practice session in order to avoid any confusion about the possible reward amounts throughout the experiment. The total experiment time was divided into six 7-minute blocks. Each block had one of three predefined combinations of handling and travel times, all of which added up to 16 seconds (handling times could be 2, 10, or 14 seconds long). All three timing combinations were shown in a semi-random order, once before and after a break, and each was visually disclosed to the participant at the beginning of each block.

\bigskip

Subjects were divided into two groups: the “wait” group passively waited during the handling time, while the “cognitive” group completed a random sequence of two-second-long cognitive tasks (i.e. Stroop, Flanker, and motion coherence) that collectively lasted the equivalent of the handling time. This kind of task switching is demonstrably effortful (Apps et al., 2015; Kool et al., 2010), and the unpredictable combination of tasks precludes training effects. Cognitive tasks were programmed so that the same two buttons (left and right arrow keys) were used to respond for all tasks. If a participant made more than two errors during the handling time, they were forced to travel. This contingency was added to guarantee engagement. Participants had the option of quitting the current condition at any point by pressing the spacebar.

\bigskip

Calculating optimal behavior:  Having predefined handling, traveling, and reward amounts allowed us to compute the optimal behavior for each block. In the foraging literature, the possible per-trial reward is often weighed against the per-second rate of reward (Constantino & Daw, 2015). This is called the opportunity rate. By multiplying the opportunity rate by the handling time, decision makers can estimate the opportunity cost of time. This measure conveys the richness of the environment, and is equivalent to the participant contemplating how much they could be making instead of waiting for the current reward.
Given that rewards have a uniform probability distribution, we can calculate the highest possible opportunity rate for each combination of handling and traveling time based on the reward acceptance threshold. For example, we can compute the possible amount to be earned by a participant that accepts every reward (acceptance threshold of 5 points). Conversely, a more cautious approach would be to only accept 10 and 25 points (acceptance threshold of 10 points). Thus, the proportion accepted (2⁄3 in the case of acceptance threshold = 10) can be multiplied by the handling plus travel times (i.e. 16 seconds), while the remaining third would be multiplied by the travel time. This expected length then divides the expected reward, defined as the sum of the accepted points divided by 3 (rewards possible). We used this calculation to test the combinations of handling and travel times that yielded the most discriminating optimal behaviors (Figure 1). This ground truth opportunity rate helped us gauge the optimality of participants’ decisions on each condition. The resulting ideal behavior was to accept everything when the handling time was 2 seconds, accept 10 and 25 points when it was 10 seconds, and to only accept 25-point trials when it lasted 14 seconds.

\bigskip

## Results

### Propotion Completed

The most basic question that guides this project is which group accepted more trials. Intuitively, the condition that triggered the least acceptances can be argued to be the costliest. The wait group had a mean proportion acceptance of 0.53 (sd = 0.11), while the effort group's mean proportion was 0.72 (sd = 0.19). In order to estimate the significance of this difference, I first ran an independent samples t-test. This test suggested that the wait group accepted significantly fewer trials overall (t(16) = -2.86, p = 0.01), thus rejecting the null hypothesis that the difference between these groups would be 0.

While this result was surprising and interesting (I was expecting the effort group to accept less), a t-test does not seem like the right statistic to perform. One of the problems with the present study is the small samples, making reliable inferences difficult to achieve. This becomes somewhat plain when considering the CDFs and confidence intervals for each group. According to the plot, it would be difficult to trust any test that describes them as significantly different.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}

## overall proportion complete
# create data frame with summary stats
tempW <- summarizeData()
tempC <- summarizeData(Data = cogData, nSubs = nSubsC, type = "Cognitive")
tempP <- summarizeData(Data = physData, nSubs = nSubsP, type = "Physical")
tempE <- summarizeData(Data = easyData, nSubs = nSubsE, type = "Easy")

summaryData <- rbind(tempW,
                     tempC,
                     tempP,
                     tempE)

colnames(summaryData) <- c("Group","propComplete","Earnings","RT","forcedTravel")

summaryData$Cols <- c(rep(cols[1],nSubsW), rep(cols[2],nSubsC), rep(cols[3],nSubsP), rep(cols[4],nSubsE))
rm(tempW, tempC, tempP, tempE)

# Indexes for groups
indxWait <- seq(nSubsW)
indxWaitLong <- seq(nSubsW * 9) # 9 being the number of combinations
indxCog <- (nSubsW + 1):(nSubsW + nSubsC)
indxCogLong <- ((nSubsW * 9) + 1):((nSubsW * 9) + (nSubsC * 9))
indxPhys <- ((nSubsW + nSubsC) + 1):(nSubsW + nSubsC + nSubsP)
indxPhysLong <- ((nSubsW * 9) + (nSubsC * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9))
indxEasy <- ((nSubsW + nSubsC + nSubsP) + 1):totalSubs #(nSubsW + nSubsC + nSubsP + nSubsE)
indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))

## prop complete
# ecdfs
wait <- ecdf(summaryData$propComplete[indxWait])
cog <- ecdf(summaryData$propComplete[indxCog])
phys <- ecdf(summaryData$propComplete[indxPhys])
easy <- ecdf(summaryData$propComplete[indxEasy])
range <- seq(0,1,by=0.01)

test <- data.frame(range = range,
                   ecdf = c(wait(range),cog(range),phys(range),easy(range)),
                   Group = factor(c(rep("Wait",101),rep("Cognitive",101),rep("Physical",101),rep("Easy", 101)), levels = c("Wait","Cognitive","Physical","Easy")))

p <- ggplot(test, aes(x=range,y=ecdf, group=Group, color=Group))
p + geom_line() +
    scale_color_manual(values = cols) +
    labs(title = "ECDF of Acceptances per Group", y="ECDF") +
    theme_classic()

# plot(range,
#      wait(range),
#      main = "ECDF for Proportion Completed",
#      xlab = "Proportion Completed",
#      ylab = "ECDF",
#      col = cols[1],
#      type="l",
#      lwd = lthick)
# lines(range,
#       cog(range),
#       col = cols[2],
#       lwd = lthick)
# lines(range,
#       phys(range),
#       col = cols[3],
#       lwd = lthick)
# lines(range,
#       easy(range),
#       col = cols[4],
#       lwd = lthick)
# legend("bottomright",
#        lbls,
#        fill = cols,
#        cex = 0.8)

# CIs basic
# CIC <- qt(.975,nSubsC-1)*(sd(summaryData$propComplete[indxCog])/sqrt(nSubsC))
# CIW <- qt(.975,nSubsW-1)*(sd(summaryData$propComplete[indxWait])/sqrt(nSubsW))
# CIP <- qt(.975,nSubsP-1)*(sd(summaryData$propComplete[indxPhys])/sqrt(nSubsP))
# CIE <- qt(.975,nSubsE-1)*(sd(summaryData$propComplete[indxEasy])/sqrt(nSubsE))
# lines(range,cog(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
# lines(range,cog(range) - CIC,col = cols[2], lty = 2, lwd = lthick) #qt(.975,nSubs-1)*(sd(meanBootC)/sqrt(nSubs))
# lines(range,wait(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
# lines(range,wait(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
# lines(range,phys(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
# lines(range,phys(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
# lines(range,easy(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
# lines(range,easy(range) - CIE,col = cols[4], lty = 2, lwd = lthick)
# 
# rm(CIC,CIW,CIP,CIE)

# problem is, data is not normal, so we're going to bootstrap it and DEFINITELY permute
# Bootstrap nonparametric
B <- 5000
meanBootW <- bootstrap(summaryData$propComplete[indxWait],B = B) #rep(0,B)
meanBootC <- bootstrap(summaryData$propComplete[indxCog], B = B) #rep(0,B)
meanBootP <- bootstrap(summaryData$propComplete[indxPhys], B = B)
meanBootE <- bootstrap(summaryData$propComplete[indxEasy], B = B)

#CIs wait
meanW <- mean(meanBootW)
upperW <- quantile(meanBootW,0.975) # meanBoot?
lowerW <- quantile(meanBootW,0.025)

#CIs effort
meanC <- mean(meanBootC)
upperC <- quantile(meanBootC,0.975) # meanBoot?
lowerC <- quantile(meanBootC,0.025)

#CIs physical
meanP <- mean(meanBootP)
upperP <- quantile(meanBootP,0.975) # meanBoot?
lowerP <- quantile(meanBootP,0.025)

#CIs easy
meanE <- mean(meanBootE)
upperE <- quantile(meanBootE,0.975) # meanBoot?
lowerE <- quantile(meanBootE,0.025)

# formal testing
# prop.test(sum(cogData[[i]]$Choice),length(cogData[[i]]$Choice))
# propTtest <- t.test(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])
# propPerm <- permute(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])
propAov <- aov(propComplete ~ factor(Group), data = summaryData)

# effect size
propRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])

rm(B,cog,wait,phys,easy)
```

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# boxplot(summaryData$propComplete[indxWait],
#         summaryData$propComplete[indxCog],
#         summaryData$propComplete[indxPhys],
#         summaryData$propComplete[indxEasy],
#         names = lbls,
p <- ggplot(summaryData, aes(x=Group, y=propComplete, fill = Group))
p + geom_boxplot(show.legend = F) +
    scale_fill_manual(values = cols) +
    labs(title = "Proportion Completed by Group", y="Proportion Completed") +
    theme_classic()
```

In order to accomodate for this shortcoming, I took a handful of steps. First, I bootstrapped the mean proportion for each group separately (5000 iterations), so I could get a better estimate of the mean and CIs. As seen in the plots below, the mean for each became normally distributed. The table shows the bootstrapped means and confidence intervals.

``` {r,echo=FALSE,fig.align="center",fig.width=10,fig.height=6}
# plot the hist and qqnorm 
# par(mfrow=c(4,2))
# hist(meanBootW,
#      main = "Distribution for the Bootstrapped propotions \n Wait Group",
#      xlab = "Proportion Completed")
# qqnorm(meanBootW,
#        main = "QQ-norm for the Wait Group")
# hist(meanBootC,
#      main = "Distribution for the Bootstrapped propotions \n Cognitive Effort Group",
#      xlab = "Proportion Completed")
# qqnorm(meanBootC,
#        main = "QQ-norm for the Cognitive Effort Group")
# hist(meanBootP,
#      main = "Distribution for the Bootstrapped propotions \n Physical Effort Group",
#      xlab = "Proportion Completed")
# qqnorm(meanBootP,
#        main = "QQ-norm for the Physical Effort Group")
# hist(meanBootE,
#      main = "Distribution for the Bootstrapped propotions \n Easy Effort Group",
#      xlab = "Proportion Completed")
# qqnorm(meanBootE,
#        main = "QQ-norm for the Easy Effort Group")
```

| Group       | Bootstrapped Mean | Bootstrapped CI lower   | Bootstrapped CI upper   |
| :---------- | :---------------: | :---------------------: | ----------------------:
| Wait        | $`r meanW`$       | $`r lowerW`$            | $`r upperW`$            |
| Cog. Effort | $`r meanC`$       | $`r lowerC`$            | $`r upperC`$            |
| Phys. Effort| $`r meanP`$       | $`r lowerP`$            | $`r upperP`$            |
Table: Bootstrapped descriptives for each group

With these estimates, I re-ploted the ECDF from above. It can now be seen that the CIs do not overlap, suggesting a true difference between these groups.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# plot ecdf 
par(mfrow=c(1,1))
ecdfW <- ecdf(meanBootW)
ecdfC <- ecdf(meanBootC)
ecdfP <- ecdf(meanBootP)
ecdfE <- ecdf(meanBootE)

plot(range,ecdfW(range),
     type = "l",
     main = "ECDF for the Bootstrapped Proportions",
     xlab = "Proportion Completed",
     ylab = "ECDF",
     xlim = c(0,1),
     col = cols[1],
     lwd = lthick)
lines(range,
      ecdfC(range),
      col = cols[2],
      lwd = lthick)
lines(range,
      ecdfP(range),
      col = cols[3],
      lwd = lthick)
lines(range,
      ecdfE(range),
      col = cols[4],
      lwd = lthick)
legend("bottomright",
       lbls,
       fill = cols,
       cex = 0.8)

# and CIs for each (unnecessary unless I end up plotting)
CIC <- qt(.975,nSubsC-1)*(sd(meanBootC)/sqrt(nSubsC))
CIW <- qt(.975,nSubsW-1)*(sd(meanBootW)/sqrt(nSubsW))
CIP <- qt(.975,nSubsP-1)*(sd(meanBootP)/sqrt(nSubsP))
CIE <- qt(.975,nSubsE-1)*(sd(meanBootE)/sqrt(nSubsE))
lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) #qt(.975,nSubs-1)*(sd(meanBootC)/sqrt(nSubs))
lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)

rm(CIC,CIW,CIP,CIE)
```

While these measures showed promise, they don't formalize the differences in proportin completed. To achieve this, I performed a permutation test on the mean difference in proportions between both groups. The resulting p-value was 0.01, and the estimated null distribution of this difference is shown below. Finally, I used Cohen's D to estimate the effect size of this comparison, which yielded a value of 0.5.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# plotting the permutation
# plot(density(propPerm$jointDist),
#      main = "Permuted Null Distribution for the Difference in Proportions \n Wait - Effort",
#      xlab = "Mean Difference",
#      lwd = lthick)
# lines(c(propPerm$Observed,propPerm$Observed), c(0,1200), lty=2, col="red", lwd = lthick)
```

This shows that the effort group completed a significantly larger amount of trials overall than the wait group.

\bigbreak

### Total Earnings
In the current experiment earnings are of no big interest, as the main goal of the study is to estimate differences in perceived cost as reflected by choices. However, it can be useful to take a look at earnings, especially because they can help us confirm certain aspects of the experiment (as seen in the results). The following graphs show the differences in mean earnings between groups.

``` {r,echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
# wilcoxon rank sum
earningTest <- wilcox.test(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog], alternative = "two.sided")
earningsPerm <- permute(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog]) # I believe this more
earningsRsq <- cohenD(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog])

# linear model (think of doing a Poisson Regression instead, since earnings are not normally distributed [although bootstrapped they're fine])
propAllsq <- summaryData$propComplete^2 
lmEarn <- lm(Earnings ~ propComplete + propAllsq, data = summaryData)
coeffsEarn <- lmEarn$coefficients
x <- seq(0,1,length=100) # for plotting

# plotting
par(mfrow=c(1,2))
boxplot(summaryData$Earnings[indxWait],
        summaryData$Earnings[indxCog],
        summaryData$Earnings[indxPhys],
        summaryData$Earnings[indxEasy],
        names = lbls,
        main = "Total Earnings for Each Group",
        ylab = "Total Earnings (pts)",
        xlab = "Group",
        col = cols)

# earnings (inverse-U, which makes sense because either over or under accepting are detrimental to earnings)
plot(summaryData$propComplete[indxWait],
     summaryData$Earnings[indxWait],
     main = "Total Earnings as a Function of Proportion Accepted",
     xlab = "Total Proportion Completed",
     ylab = "Total Earned",
     col=cols[1],
     xlim=c(0.2,1),
     ylim = c(1000,2000),
     pch=16,
     cex = lthick - 0.5)
points(summaryData$propComplete[indxCog],
       summaryData$Earnings[indxCog],
       col=cols[2],
       pch=16,
       cex = lthick - 0.5)
points(summaryData$propComplete[indxPhys],
       summaryData$Earnings[indxPhys],
       col=cols[3],
       pch=16,
       cex = lthick - 0.5)
points(summaryData$propComplete[indxEasy],
       summaryData$Earnings[indxEasy],
       col=cols[4],
       pch=16,
       cex = lthick - 0.5)
legend("topright",
       lbls,
       fill = cols,
       cex = 0.8)
lines(x, coeffsEarn[1] + coeffsEarn[2]*x + coeffsEarn[3]*(x^2),
       col="black",
      lwd = lthick)

```

\bigskip

The effort group, while accepting more trials also earned slightly less than the wait group. A permutation analysis of differences in mean earnings per group indicated a trend (p = `r earningsPerm$Pval`; Cohen's D = `r earningsRsq`). The figure on the right shows a nonlinear relationship between acceptance rates and total earnings (line of best fit: beta = , T = , p-value = ). This is in line with the nature of the experiment, as participants should cautiously balance rewards with opportunity cost, and both under- and over-acceptance were non-optimal.

### Response Times
After checking for acceptance and earnings, another question is how fast participants were in making decisions (as they could quit at any point during the handling time). Perhaps participants were unclear about the experimental procedures, or changed their minds mid-trial. To account for this, I pooled all the response times for quit trials (since they are representative of a participant's choice to leave) across participants for each group. With these vectors, I plotted their respective ECDFs (Figure 4) and bootstrapped 95% CIs. As it can be seen, most decisions were made before the first second, with the cognitive effort group being slightly faster than the other two. Notably, the physical effort group shows a spike at 1s. This is due to the experimental setup, which automatically quit if no response was registered by that time. In addition, this group showed some mid-trial quitting, probably due to fatigue. This is not seen in the other conditions.
The quick response times indicate that participants had a clear idea of what rewards were worth their time and effort. This is in agreement with the post-experiment questionaire, in which participant explained very specific strategies that they followed throughout the session.

```{r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4, fig.cap="ECDFs of pooled response times from each group. Responses were overall quick, with the wait group being slightly slower."}
# RTs
# let's try to do some survival curves
RTW <- numeric() # vector of all decision-related RTs for the wait group
RTC <- numeric() # same for the cog group
RTP <- numeric()
RTE <- numeric()

# Wait group
for (subj in seq(nSubsW)){

    # index for trials quit
    tempChoiceW <- waitData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTW <- c(RTW,waitData[[subj]]$RT[tempChoiceW])

}

# Cognitive group
for (subj in seq(nSubsC)){

    # index for trials quit
    tempChoiceC <- cogData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTC <- c(RTC,cogData[[subj]]$`Choice RT`[tempChoiceC])

}

# Physical group
for (subj in seq(nSubsP)){

    # index for trials quit
    tempChoiceP <- physData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTP <- c(RTP,physData[[subj]]$RT[tempChoiceP])

}

# Pheaysical group
for (subj in seq(nSubsE)){

    # index for trials quit
    tempChoiceE <- easyData[[subj]]$Choice == 0

    # concatenate the subject RT to the group
    RTE <- c(RTE,easyData[[subj]]$RT[tempChoiceE])

}

# create an array with both data (for surv fit autoplot trials)
lenC <- length(RTC)
lenW <- length(RTW)
lenP <- length(RTP)
lenE <- length(RTE)

RTgroups <- c(rep("Wait",lenW), 
              rep("Effort",lenC), 
              rep("Physical",lenP),
              rep("Easy",lenE))
RTall <- c(RTW,RTC,RTP,RTE)

# plot ecdf 
ecdfW <- ecdf(RTW)
ecdfC <- ecdf(RTC)
ecdfP <- ecdf(RTP)
ecdfE <- ecdf(RTE)

range <- seq(0,10, by = 0.001)

plot(range,ecdfW(range),
     type = "l",
     main = "ECDF and CIs for the Response Times",
     xlab = "Seconds",
     ylab = "ECDF",
     xlim = c(0,5),
     col = cols[1],
     bty = "n",
     lwd = lthick)
lines(range,
      ecdfC(range),
      col = cols[2],
      lwd = lthick)
lines(range,
      ecdfP(range),
      col = cols[3],
      lwd = lthick)
lines(range,
      ecdfE(range),
      col = cols[4],
      lwd = lthick)
legend("right",
       lbls,
       fill = cols,
       cex = 0.8)

# and CIs for each (unnecessary unless I end up plotting)
CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
CIC <- median(CIC) - (quantile(CIC,0.025))
CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIW <- median(CIW) - (quantile(CIW,0.025))
CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIP <- median(CIP) - (quantile(CIP,0.025))
CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIE <- median(CIE) - (quantile(CIE,0.025))
lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)

# just cause, Kolmogrov-Smirnov 
# ksRT <- ks.test(RTW,RTC)
# RTPerm <- permute(RTW,RTC)
# RTCohen <- cohenD(RTW,RTC)

rm(lenC,lenW,lenP,lenE)

```

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# mistakes
# significant from 0
mistakeTest <- wilcox.test(summaryData$forcedTravel)
mistakePerm <- permute(rep(0,11), summaryData$forcedTravel[indxCog]) # revise

```

\bigskip

#### Proportion per handling-reward combination 
The analyses above give us a general sense of the characteristics of each group. However, it also necessary to asses whether decision makers were influenced differently at each timing and reward combinations, and how these factors varied by group. First, I was interested in seeing differences as a whole. Figure 5 shows the proportion accepted (and standard error) for all these combinations.

``` {r,echo=FALSE,fig.align="center",fig.width=9,fig.height=6, results = 'asis'}

# params for reference
handling <- c(2,10,14)

# the other, just summarizing for all participants
# Not sure if this is necessary anymore
# allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
#                                 rep("Cognitive",nSubsC*3),
#                                 rep("Physical",nSubsP*3)),
#                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
#                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
#                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
#                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
#                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
#                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))

# Get the proportion completed per combination for GLMs
tempW <- propComplete()
tempC <- propComplete(Data = cogData, nSubs = nSubsC, indx = indxCog, type = "Cognitive")
tempP <- propComplete(Data = physData, nSubs = nSubsP, indx = indxPhys, type = "Physical")
tempE <- propComplete(Data = easyData, nSubs = nSubsE, indx = indxEasy, type = "Easy")

allProp2 <- rbind(tempW,
                  tempC,
                  tempP,
                  tempE)  
allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials

rm(tempW, tempC, tempP, tempE)

# add optimal vector and difference from optimal
wait <- c(rep(1,nSubsW*3),
          c(rep(0,nSubsW), rep(1,nSubsW*2)),
          c(rep(0,nSubsW*2), rep(1,nSubsW)))
cog <- c(rep(1,nSubsC*3),
          c(rep(0,nSubsC), rep(1,nSubsC*2)),
          c(rep(0,nSubsC*2), rep(1,nSubsC)))
phys <- c(rep(1,nSubsP*3),
          c(rep(0,nSubsP), rep(1,nSubsP*2)),
          c(rep(0,nSubsP*2), rep(1,nSubsP)))
easy <- c(rep(1,nSubsE*3),
          c(rep(0,nSubsE), rep(1,nSubsE*2)),
          c(rep(0,nSubsE*2), rep(1,nSubsE)))
allProp2$Optimal <- c(wait,cog,phys,easy)
allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete

# sort by subject ID
#allProp2 <- allProp2[order(allProp2$SubjID),]

# actual proportions and standard errors, and the optimal summary for plotting
trueProp <- aggregate(allProp2$propComplete,
            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
            FUN = 'mean')

trueSD <- aggregate(allProp2$propComplete,
          by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
          FUN = 'sd')
colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
trueProp$SE[1:9] <- (trueSD$x[1:9])/(sqrt(nSubsW))
trueProp$SE[10:18] <- (trueSD$x[10:18])/(sqrt(nSubsC))
trueProp$SE[19:27] <- (trueSD$x[19:27])/(sqrt(nSubsP))
trueProp$SE[28:36] <- (trueSD$x[28:36])/(sqrt(nSubsE))

optimalProp <- aggregate(allProp2$Optimal,
            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
            FUN = 'mean')$x

```

``` {r,echo=FALSE,fig.align="center",fig.width=9,fig.height=6}
## REPEATED MEASURES VERSION
# I think I like this the most
prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
                                 Error(SubjID / (Handling * Reward))))

#prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
 #                                Error(SubjID / (Handling * Reward))))

## NOTES ON RESULTS
# According to the logistic fit, there are main effects for all predictors, but no interactions. It also says that the overall odds for the wait group to accept versus the effort is around 16%. Similarly, increasing the handling time results in a decrease in the multiplicative odds of ~25%. Increments in reward increase the odds of acceptance by ~40%.
```

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# In the works: the idea here is to estimate the probability of having observed a given amount of completed trials, assuming that the null is the reward maximizing behavior. That means: what is the probability of having seen this acceptance rate, assuming the optimal was to either accept or not (1 or 0)? If subjects knew the optimal behavior, then very low probabilities indicate that they were affected by the cost significantly. We cannot really assume that participants know this, but post-experiment interviews indicate that many of them had a clear idea of what the approxiimate optimal behavior was, even if they violated the rule during the experiment.

# might use https://www.rdocumentation.org/packages/pracma for eps()

TC <- aggregate(allProp2$totalComplete, by = list(allProp2$Reward, allProp2$Handling, allProp2$Group), FUN = 'sum')
TC <- TC[order(TC$Group.3,decreasing = T),]
TT <- aggregate(allProp2$totalTrials, by = list(allProp2$Reward, allProp2$Handling, allProp2$Group), FUN = 'sum')
TT <- TT[order(TT$Group.3,decreasing = T),]
OPT <- aggregate(allProp2$Optimal, by = list(allProp2$Reward, allProp2$Handling, allProp2$Group), FUN = 'mean')
OPT <- OPT[order(OPT$Group.3,decreasing = T),]

trueProp$totalComplete <- TC$x
trueProp$totalTrials <- TT$x
trueProp$Optimal <- OPT$x
trueProp$Optimal[trueProp$Optimal==1] <- 0.99 # consider just getting eps(), like in matlab
trueProp$Optimal[trueProp$Optimal==0] <- 0.01

for (i in 1:18){

    # parameters of interest for the binomial test
    completed <- trueProp$totalComplete[i]
    total <- trueProp$totalTrials[i]
    prob <- trueProp$Optimal[i]

    # estimate the probability of having observed the acceptance rate, assuming reward-maximizing behavior
    trueProp$binomProb[i] <- round(pbinom(completed,total,prob), digits = 10)

}

# this is important. Since each test is comparing against either the 1 or 0 side, the pvalue calculated from the probability needs to be signed appropriately. For optimal acceptances of 1, the probability given by pbinom() is the pvalue, but for 0 it is 1 - pbinom().
trueProp$pval <- abs(rep(c(0,0,0,1,0,0,1,1,0),2) - trueProp$binomProb)

# do multiple-test corrections
trueProp$adjPval <- round(p.adjust(trueProp$pval, "BY"), digits = 4)
```

``` {r,echo=FALSE,fig.align="center",fig.width=9,fig.height=6}
# trying another plot, for ANOVA (equivalent to the poster one)
# make margins big enough
# par(mar=c(10.2,4.1,4.1,2.1))
# lthick <- 2.5
# 
# # putting this here for now, so it doesn't mess up anything above. Once the plot decision is made, clean up
# trueProp <- trueProp[order(as.character(trueProp$Group),decreasing = T),]
# # trueProp$SE[11:12] <- 0.001 # because otherwise it won't plot the arrows (SE = 0)
# # trueProp$SE[15] <- 0.001
# 
# # actual plot
# plot(1:3, trueProp$propComplete[1:3],
#      main = "Proportion Completed Per Handling/Reward Combination \n Mean and SE for Each Group",
#      xlab = "",
#      ylab = "Proportion Completed",
#      xlim = c(1,42), 
#      ylim = c(0,1),
#      type = "l",
#      xaxt = "n",
#      col = cols[1],
#      lwd = lthick + 2,
#      bty = "n")
# points(1:3, 
#      trueProp$propComplete[1:3],
#      col = cols[1],
#      pch = 16,
#      cex = lthick - 1,
#      bty = "n")
# arrows(1:3, trueProp$propComplete[1:3] - trueProp$SE[1:3],
#        1:3, trueProp$propComplete[1:3] + trueProp$SE[1:3], 
#        length=0.05, 
#        angle=90, 
#        code=3,
#        col = cols[1],
#        lwd = lthick + 2)
# # plot the optimal choices
# lines(1:3,optimalProp[1:3], col = "grey48",lty=3, lwd = lthick + 2)
# points(1:3,optimalProp[1:3], col = "grey48",pch=17, cex = lthick - 1)
# 
# ranges <- array(4:36,dim = c(3,11)) # for selecting and placin on x-axis
# for (i in 1:11){
#   
#     # choose a different color for each group
#     color = cols[1]
#     if (i > 2){color = cols[3]} 
#     if (i > 5) {color = cols[2]}
#     if (i > 8) {color = cols[4]}
#     
#     # grab the relevant measure indexes
#     indx <- ranges[,i]
#     
#     # SEs
#     SEup <- trueProp$propComplete[indx] + trueProp$SE[indx]
#     SEdown <- trueProp$propComplete[indx] - trueProp$SE[indx]
#     
#     # plot
#     lines(indx,
#           trueProp$propComplete[indx],
#           col = color,
#           lwd = lthick + 2)
#     points(indx, 
#            trueProp$propComplete[indx],
#            col = color,
#            cex = lthick - 1,
#            pch = 16,
#            bty = "n")      
#     arrows(indx, SEdown,
#            indx, SEup, 
#            length=0.05, 
#            angle=90, 
#            code=3,
#            col = color,
#            lwd = lthick + 2)    
#     lines(indx,optimalProp[indx], col = "grey48", lty=3, lwd = lthick + 2)
#     points(indx,optimalProp[indx], col = "grey48", pch=17, cex = lthick - 1)
#     
# }
# 
# # legend
# legend("topright",
#        c(lbls, "Optimal"), 
#        fill = c(cols, "grey48"),
#        cex = 1)
# 
# # x axis
# axis(1,at = 1:9, rep(c(5,10,25),3))
# axis(1,at = 10:18, rep(c(5,10,25),3))
# axis(1,at = 19:27, rep(c(5,10,25),3))
# axis(1,at = 28:36, rep(c(5,10,25),3))
# axis(1,at = c(2,5,8), c(2,10,14), line = 3)
# axis(1,at = c(11,14,17), c(2,10,14), line = 3)
# axis(1,at = c(20,23,26), c(2,10,14), line = 3)
# axis(1,at = c(29,32,35), c(2,10,14), line = 3)
# mtext("Reward",1,line=1,at=-0.5)
# mtext("Handling",1,line=3,at=-0.5)

### THE PLOTS FOR YALE
# Ggplot made plotting way easier than the previous version
# This is in case you don't want to plot the easy condition (easier to see)
trueProp2 <- trueProp[-(28:36), ]

a1 <- ggplot(data = trueProp2, aes(x=interaction(Reward, Handling), y=propComplete, color=Group)) + 
        geom_point(size=3) + 
        geom_errorbar(aes(ymin=propComplete-SE, ymax=propComplete+SE), width=0.2, size=1) +
        geom_line(aes(group = interaction(Handling, Group)), size=1) +
        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey48", color = "grey48", size = 3, show.legend = F) +
        scale_color_manual(values=cols) +
        theme_classic()

a1
```

\bigskip

This plot portrays some important features: the first hypothesis was supported, as we can see that participants accepted fewer trials for smaller rewards and longer handling times. On the other hand, and perhaps expectedly, we can see that the effort group accepted more trials than the wait group in all cases. This is contrary to the second hypothesis. Interestingly, the physical effort group shows a similar pattern of acceptances to the cognitive effort participants.
In order to analyze these differences, I ran a 2-way repeated measures ANOVA to see how participants in each group performed at each combination of handling times and rewards. Since all three factors are relevant to the question, and since at this point I was interested in mean differences, I did not perform model selection. The table below shows the results from the analysis from variance. Main effects were found for group (F(2,281) = 5.76, p < 0.005), handling time (F(1,281) = 52.784, p < 0.0001), and reward amount (F(1,281) = 123.14, p < 0.0001). A handling by reward interaction was also found (F(1,281) = 19.44, p < 0.0001), indicating that participant tendencies to accept higher rewards were reduced by longer handling times. This was somewhat expected, since the optimal behavior was to forage selectively for higher rewards as the handling time increased, and participants were fairly sensible to this structure.
This analysis opens the door to another important consideration: the optimality of each group's behavior. Since the reward-maximizing choices can be calculated, I overlayed them on the plot from figure 5 (in grey).

``` {r pander}
# anova table
x <- summary(prop.aov)   
x <- x$`Error: Within`
panderOptions("digits", 2)
pander(x, style = "rmarkdown",split.table = 110)
```

### Before/After break strategy changes
Another question that is worth prusuing is whether participants changed their behavior before and after the break. This is particularly important because they saw the same handling and travel time combination blocks (in the same order) before and after this break. To evaluate this, I performed per-subject paired permutation tests (paired by handling-reward combination), and extracted the p-values from the permuted null distributions. After correction for multiple comparisons (using false discovery rate), there were no significant changes before and after the break. These results suggest that participants were consistent in their acceptance behavior, and were following determinate strategies. This is in addition to the response time evidence examined above.

``` {r,echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
# Before/After per subject diffs
# wilcoxon signed rank won't work because the vectors are likely to be of different lengths
# prop.test works as test of proportions (chi-square ish, but evaluated with a z-distribution?)
# just say it's a chi-squared test of proportions per subject, and that only one subject had a different proportion completed before and after the break. All other null could not be rejected.

# Problem: this computes the proportion without accounting for handling or reward amounts. Problem is, there aren't enough trials per combination to really account for every bit. Could be interesting to try, though.

# cogABPval <- numeric()
# waitABPval <- numeric()
# physABPval <- numeric()
# 
# for (i in 1:11){
#   
#     # wait  
#     temp <- prop.test(x = c(sum(waitBefore[[i]]$Choice), sum(waitAfter[[i]]$Choice)), 
#                       n = c(length(waitBefore[[i]]$Choice), length(waitAfter[[i]]$Choice)))
#     waitABPval[i] <- temp$p.value
#      
#     # effort
#     temp <- prop.test(x = c(sum(cogBefore[[i]]$Choice), sum(cogAfter[[i]]$Choice)), 
#                       n = c(length(cogBefore[[i]]$Choice), length(cogAfter[[i]]$Choice)))
#     cogABPval[i] <- temp$p.value    
#   
# }
# 
# # Before after group. Don't worry about plotting
# # paired t-tests also show that there are no differences before and after the break, indicating consistency of strategies

##------- Better version
cogABPval <- numeric()
waitABPval <- numeric()
physABPval <- numeric()

# wait
for (i in seq(nSubsW)){

      tempPropB <- aggregate(waitBefore[[i]]$Choice, by = list(waitBefore[[i]]$Handling, waitBefore[[i]]$Reward), FUN = 'mean')
      tempPropA <- aggregate(waitAfter[[i]]$Choice, by = list(waitAfter[[i]]$Handling, waitAfter[[i]]$Reward), FUN = 'mean')
      tempPerm <- permute(tempPropB$x,tempPropA$x,nPerms = 5000, paired = TRUE)
      waitABPval[i] <- tempPerm$Pval

}

# cognitive
for (i in seq(nSubsC)){

      if (i == 9) { cogABPval[i] = 1} else {
      tempPropB <- aggregate(cogBefore[[i]]$Choice, by = list(cogBefore[[i]]$Handling, cogBefore[[i]]$Reward), FUN = 'mean')
      tempPropA <- aggregate(cogAfter[[i]]$Choice, by = list(cogAfter[[i]]$Handling, cogAfter[[i]]$Reward), FUN = 'mean')
      tempPerm <- permute(tempPropB$x,tempPropA$x,nPerms = 5000, paired = TRUE)
      cogABPval[i] <- tempPerm$Pval}
}

# physical
for (i in seq(nSubsP)){

      tempPropB <- aggregate(physBefore[[i]]$Choice, by = list(physBefore[[i]]$Handling, physBefore[[i]]$Reward), FUN = 'mean')
      tempPropA <- aggregate(physAfter[[i]]$Choice, by = list(physAfter[[i]]$Handling, physAfter[[i]]$Reward), FUN = 'mean')
      tempPerm <- permute(tempPropB$x,tempPropA$x,nPerms = 5000, paired = TRUE)
      physABPval[i] <- tempPerm$Pval

}

# Notes:
# A problem with the paired permutation is that if a participant accepted most trials, the distributions become tiny and even small observed deviations will become highly unlikely. That's why participant 9 had a forced p = 1: they mostly accepted in both cases. In the physical effort this is accentuated because participants that wanted to over accept seemed unable to do so due to fatigue, thus creating noise. Paired t-tests show that there are no differences before and after the break. The t-test is more robust against this problem, while giving similar significance levels for noisier behaviors. Bottom line: although some p = 0, participants did not really change strategies before/after break on any condition.

# Another approach (Joe's suggestion)
# This one just plots the correlation between pre-post acceptance rates, both overall and per cell
# The overall acceptance looks great, with mostly consistent rates, and with the physical group accepting slightly less post-break
# However, the per-cell distribution looks messy, although you can still tell that there's a linear relationship
# If I do a linear model predicting post with pre using cell-specific data, the betas are close to 1 and significant (also good R2s). That's good.

# create vdata frames that store acceptance data per combination cell pre-post break
waitB <- data.frame()
waitA <- data.frame()
cogB <- data.frame()
cogA <- data.frame()
physB <- data.frame()
physA <- data.frame()
easyB <- data.frame()
easyA <- data.frame()

# and for overall proportion accepted
waitBAll <- numeric()
waitAAll <- numeric()
cogBAll <- numeric()
cogAAll <- numeric()
physBAll <- numeric()
physAAll <- numeric() 
easyBAll <- numeric()
easyAAll <- numeric()

for (i in seq(nSubsW)){

  # wait
  tempPropB <- aggregate(waitBefore[[i]]$Choice, by = list(waitBefore[[i]]$Handling, waitBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(waitAfter[[i]]$Choice, by = list(waitAfter[[i]]$Handling, waitAfter[[i]]$Reward), FUN = 'mean')
  waitB <- rbind(waitB,tempPropB)
  waitA <- rbind(waitA,tempPropA)
  waitBAll[i] <- mean(waitBefore[[i]]$Choice) 
  waitAAll[i] <- mean(waitAfter[[i]]$Choice)

}

for (i in seq(nSubsC)){

  # cognitive
  tempPropB <- aggregate(cogBefore[[i]]$Choice, by = list(cogBefore[[i]]$Handling, cogBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(cogAfter[[i]]$Choice, by = list(cogAfter[[i]]$Handling, cogAfter[[i]]$Reward), FUN = 'mean')
  cogB <- rbind(cogB,tempPropB)
  cogA <- rbind(cogA,tempPropA)
  cogBAll[i] <- mean(cogBefore[[i]]$Choice) 
  cogAAll[i] <- mean(cogAfter[[i]]$Choice)

}

for (i in seq(nSubsP)){

  # physical
  tempPropB <- aggregate(physBefore[[i]]$Choice, by = list(physBefore[[i]]$Handling, physBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(physAfter[[i]]$Choice, by = list(physAfter[[i]]$Handling, physAfter[[i]]$Reward), FUN = 'mean')
  physB <- rbind(physB,tempPropB)
  physA <- rbind(physA,tempPropA)
  physBAll[i] <- mean(physBefore[[i]]$Choice) 
  physAAll[i] <- mean(physAfter[[i]]$Choice)

}

for (i in seq(nSubsE)){

  # easy
  tempPropB <- aggregate(easyBefore[[i]]$Choice, by = list(easyBefore[[i]]$Handling, easyBefore[[i]]$Reward), FUN = 'mean')
  tempPropA <- aggregate(easyAfter[[i]]$Choice, by = list(easyAfter[[i]]$Handling, easyAfter[[i]]$Reward), FUN = 'mean')
  easyB <- rbind(easyB,tempPropB)
  easyA <- rbind(easyA,tempPropA)
  easyBAll[i] <- mean(easyBefore[[i]]$Choice) 
  easyAAll[i] <- mean(easyAfter[[i]]$Choice)

}

```

```{r,echo=FALSE,fig.align="center",fig.width=5,fig.height=5, fig.cap="P-values for the pairwise permutation of before and after break performance, each plot showing each group"}
# ## plotting p-values from permutation
# plot(seq(nSubsW),
#      waitABPval,
#      main = "P-values for permuted pairwise comparisons before and after break",
#      xlab = "Subjects",
#      ylab = "P values",
#      ylim = c(0,1),
#      xlim = c(0,38),
#      pch = 16,
#      col = cols[1])
# points(12:22,
#        cogABPval,
#        pch = 16,
#        col = cols[2])
# points(23:33,
#        physABPval,
#        pch = 16,
#        col = cols[3])
# # legend
# legend("right",
#        c("Wait","Cognitive","Physical"),
#        fill = cols,
#        cex = 0.8)

## plots for the pre-post acceptance rate correspondence
# per cell
# plot(waitB$x,
#      waitA$x, 
#      xlim = c(0,1),
#      ylim = c(0,1),     
#      main = "Proportion accepted pre- and post-midpoint \n For each timing/reward combination",
#      xlab = "Acceptance Rate Before",
#      ylab = "Acceptance Rate After",
#      pch = 16,
#      col = cols[1])
# points(cogB$x,
#        cogA$x, 
#        col = cols[2],
#        pch = 16)
# points(physB$x,
#        physA$x, 
#        col = cols[3],
#        pch = 16)
# lines(seq(0,1,length = 10),
#       seq(0,1,length = 10))
# legend("bottomright",
#        c("Wait","Cognitive","Physical"),
#        fill = cols,
#        cex = 0.8)

# overall proportion
plot(waitBAll,
     waitAAll,
     xlim = c(0,1),
     ylim = c(0,1),
     main = "Proportion accepted pre- and post-midpoint",
     xlab = "Acceptance Rate Before",
     ylab = "Acceptance Rate After",     
     col = cols[1],
     pch = 16)
points(cogBAll,
       cogAAll, 
       col = cols[2],
       pch = 16)
points(physBAll,
       physAAll, 
       col = cols[3],
       pch = 16)
points(easyBAll,
       easyAAll, 
       col = cols[4],
       pch = 16)
lines(seq(0,1,length = 10),
      seq(0,1,length = 10))
legend("bottomright",
       lbls,
       fill = cols,
       cex = 0.8)

# Another approach
# This will just plot the density of the completed trials before/after, trying to get at the possible fatigue experienced in the physical effort condition.
# Response patterns for each subject look pretty similar, with adequate optimality adaptation.
#
# for (i in 1:nSubs){
# plot(density(which(physBefore[[i]]$Choice==1)),
#      main = paste("Choices in time, before and after for subject:",i),
#      xlab = "Trials (completed)")
# lines(density(which(physAfter[[i]]$Choice==1)), col = "red")
# }
```

### Logistic regression 
The analyses above were meant to get a sense of performance differences between groups while assuming that all experimental parameters were relevant, but I was also interested in estimating the importance of each factor in predicting choice. Such predictions can often be done with linear models. However, due to the non-Gaussian nature of the proportion of choices, as well as the predictors, I decided to run a logistic regression to predict the proportion of trials per subject, using group, handling time, and reward amount as predictors *(using a quasi-binomial GLM)*. I used Akaike Information Criterion (AIC) to identify which combinations of predictors significantly reduced the -2 log-likelihood while penalizing the addition of predictors. Figure 9 shows the results.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# just to make the logistic plotting comply with the function
allProp2 <- allProp2[order(as.character(allProp2$Group), decreasing = F),]

# logistic regression tests ($deviance for LRTs, if desired. AIC should be fine though)
logisBase <- glm(propComplete ~ 1, family = "binomial", data = allProp2) # intercept only
logisGroup <- glm(propComplete ~ factor(Group), family = "binomial", data = allProp2) 
logisHand <- glm(propComplete ~ factor(Group) + Handling, family = "binomial", data = allProp2)
logisRwd <- glm(propComplete ~ factor(Group) + Reward, family = "binomial", data = allProp2)
logisComb <- glm(propComplete ~ factor(Group) + Handling + Reward, family = "binomial", data = allProp2)
logisInt <- glm(propComplete ~ factor(Group) + Handling * Reward, family = "binomial", data = allProp2)
logisIntAll <- glm(propComplete ~ factor(Group) * Handling * Reward, family = "binomial", data = allProp2)

# Quasibinomial GLM versions (with proper proportion setup)
totalQuit <- allProp2$totalTrials - allProp2$totalComplete
testBinom <- cbind(allProp2$totalComplete,totalQuit)
logisBase <- glm(testBinom ~ 1, family = "quasibinomial", data = allProp2) # intercept only
logisGroup <- glm(testBinom ~ factor(Group), family = "quasibinomial", data = allProp2) 
logisHand <- glm(testBinom ~ factor(Group) + Handling, family = "quasibinomial", data = allProp2)
logisRwd <- glm(testBinom ~ factor(Group) + Reward, family = "quasibinomial", data = allProp2)
logisComb <- glm(testBinom ~ factor(Group) + Handling + Reward, family = "quasibinomial", data = allProp2)
logisInt <- glm(testBinom ~ factor(Group) + Handling * Reward, family = "quasibinomial", data = allProp2)
logisIntAll <- glm(testBinom ~ factor(Group) * Handling * Reward, family = "quasibinomial", data = allProp2)

# Using a mixed-model fitted with GLMER
# Note: GLMER does not take quasi family distributions
# ranef() to display the random intercepts, fixef() for the model coefficients

# fit model
mixLogisComb <-  glmer(testBinom ~ factor(Group) + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)

# Create CIs
se <- sqrt(diag(vcov(mixLogisComb)))
tab <- cbind(Est = fixef(mixLogisComb), LL = fixef(mixLogisComb) - 1.96 * se, UL = fixef(mixLogisComb) + 1.96 * se)

# plot random intercepts in increasing order
plot(ranef(mixLogisComb))

# plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
plot(ranef(mixLogisComb)$SubjID[[1]])

# Model selection (with interactions is better)---------- 
# Results: using handling and rewards as factors decreased the likelihood, so I removed those models 
# For the logistic one, the last meaningful decrease in likelihood happened with logisComb, which also goes against the ANOVA (since no-interactions are significant). I think this model will work best.
# I also double checked this by looking at the progressive deviances. The difference in model deviance (or -2LL of the model) for each pair of models is evaluated using a chi-squared distribution (with df = diff in params). This difference in logs is analogous to a logged division of the likelihoods, which is an LRT (or R-squared), with the null model going in the denominator. Using this in a forward-selection way, I found again that the last model to significantly improve the fit was the logisComb. So, using the null deviance and AIC yielded the same conclusion.
aicLogis <- AIC(logisBase,logisGroup,logisHand,logisRwd,logisComb,logisInt,logisIntAll)
anovaLogis <- anova(logisBase,logisGroup,logisHand,logisRwd,logisComb,logisInt,logisIntAll,test = "Chisq")

# effect size
logisComb$Rsq <- 1 - (logisComb$deviance/200.239) # denominator is the null deviance

```

\bigskip

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}

par(mar=c(5.1,2.1,2.1,2.1))    
# plot the deviance for all models
# ver 3
modelLabels <- c('Intercept','G Only','H Only','R Only','G + H + R','G + H * R','G * H * R')
plot(anovaLogis$`Resid. Dev`,
     main = "Residual Deviance for All Models",
     xlab = "",
     ylab = "Res. Deviance",
     pch = 16,
     xaxt = "n")
axis(1,at = 1:7, labels = F)
text(1:7, 
     par("usr")[3] - 22,
     labels = modelLabels, 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

```

\bigskip

``` {r}
# mixed linear model table
panderOptions("digits", 2)
pander(logisComb, style = "rmarkdown")
```

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=6}
par(mfrow=c(1,1))
## Plotting the winning model (colors are messed up)
rewards <- seq(1,20,length = 1000)
# wait
plotLogis(coeffs = logisComb$coefficients,
          group = "Wait",
          handling = 2, 
          reward = rewards, 
          plotType = plot, 
          color = cols[1],
          lType = 6)

plotLogis(coeffs = logisComb$coefficients,
          group = "Wait",          
          handling = 10, 
          reward = rewards, 
          color = cols[1],
          lType = 3)

plotLogis(coeffs = logisComb$coefficients,
          group = "Wait",          
          handling = 14, 
          reward = rewards, 
          color = cols[1])

# cognitive
plotLogis(coeffs = logisComb$coefficients,
          group = "Cognitive",
          handling = 2, 
          reward = rewards, 
          color = cols[2],
          lType = 6)

plotLogis(coeffs = logisComb$coefficients,
          group = "Cognitive",
          handling = 10, 
          reward = rewards, 
          color = cols[2],
          lType = 3)

plotLogis(coeffs = logisComb$coefficients,
          group = "Cognitive",
          handling = 14, 
          reward = rewards, 
          color = cols[2])

# physical
plotLogis(coeffs = logisComb$coefficients,
          group = "Phys",
          handling = 2, 
          reward = rewards, 
          color = cols[3],
          lType = 6)

plotLogis(coeffs = logisComb$coefficients,
          group = "Phys",
          handling = 10, 
          reward = rewards, 
          color = cols[3],
          lType = 3)

plotLogis(coeffs = logisComb$coefficients,
          group = "Phys",
          handling = 14, 
          reward = rewards, 
          color = cols[3])

# easy
plotLogis(coeffs = logisComb$coefficients,
          group = "Easy",
          handling = 2, 
          reward = rewards, 
          color = cols[4],
          lType = 6)

plotLogis(coeffs = logisComb$coefficients,
          group = "Easy",
          handling = 10, 
          reward = rewards, 
          color = cols[4],
          lType = 3)

plotLogis(coeffs = logisComb$coefficients,
          group = "Easy",
          handling = 14, 
          reward = rewards, 
          color = cols[4])

# title
title("Probabilities for All Handling-Reward Combinations \n for Each Group")

# x axis
xticks <- c(0,min(rewards[rewards>4]),min(rewards[rewards>8]),20)
axis(1,at = xticks,c(0,4,8,20))

# legend
legend("bottomright",
       c("Wait: 2s","Wait: 10s","Wait: 14s",
         "Cognitive: 2s","Cognitive: 10s","Cognitive: 14s",
         "Physical: 2s","Physical: 10s","Physical: 14s",
         "Easy: 2s","Easy: 10s","Easy: 14s"), 
       fill = c(cols[1],cols[1],cols[1],cols[2],cols[2],cols[2],cols[3],cols[3],cols[3],cols[4],cols[4],cols[4]),
       lty = rep(c(6,3,1,8),3),
       cex = 0.8)

# actual proportions (maybe, maybe not)
# points(c(5,10,25),trueProp$propComplete[1:3], col = cols[1], pch=17) # wait
# points(c(5,10,25),trueProp$propComplete[4:6], col = cols[1], pch=17)
# points(c(5,10,25),trueProp$propComplete[7:9], col = cols[1], pch=17)
# 
# points(c(5,10,25),trueProp$propComplete[19:21], col = cols[2], pch=17) # cog effort
# points(c(5,10,25),trueProp$propComplete[22:24], col = cols[2], pch=17)
# points(c(5,10,25),trueProp$propComplete[25:27], col = cols[2], pch=17)
# 
# points(c(5,10,25),trueProp$propComplete[10:12], col = cols[3], pch=17) # phys effort
# points(c(5,10,25),trueProp$propComplete[13:15], col = cols[3], pch=17)
# points(c(5,10,25),trueProp$propComplete[16:18], col = cols[3], pch=17)

# and the residuals--------------------------
# plot(logisComb$residuals,
#      main = "Residuals for the Logistic Regression",
#      xlab = "trial",
#      ylab = "Residuals")
# -------------------------------------------
```

### Sequential effects
Finally, I was curious whether there were sequential effects. For example, one could think that quitting too many times consecutively would increase the probability of accepting any reward (in fear of skipping too much and lowering the amount of points they get overall). I checked for this possible effect by creating a vector with the number of consecutive quits that happened before each trial, and used it as a regressor on a logistic regression analysis. The regression was performed on each subject separately, using choice (0,1) as the dependent variable and the quit-run vector as a predictor.

While sequential quits were significantly predictive of choice for a couple of subjects, the effect sizes were minimal. Deviances barely changed, if at all. This indicates that previous trials had little bearing on choices. Instead, as seen above, participants focused mainly on the experimental parameters.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# Also consider using ARMA()
# store the models, so each subject's can be summarized
quitModelsW <- list()
quitModelsC <- list()
quitModelsP <- list()
quitModelsE <- list()

# Wait
for (i in seq(nSubsW)){

    # subject data (y)
    yW <- waitData[[i]]$Choice

    # lag data (x predictors)
    xW <- seqQuits(yW)

    # models
    quitModelsW[[i]] <- glm(yW ~ xW, family = "binomial")

}

# Cognitive
for (i in seq(nSubsC)){

    # subject data (y)
    yC <- cogData[[i]]$Choice

    # lag data (x predictors)
    xC <- seqQuits(yC)

    # models
    quitModelsC[[i]] <- glm(yC ~ xC, family = "binomial")

}

# Physical
for (i in seq(nSubsP)){

    # subject data (y)
    yP <- physData[[i]]$Choice

    # lag data (x predictors)
    xP <- seqQuits(yP)

    # models
    quitModelsP[[i]] <- glm(yP ~ xP, family = "binomial")

}

# Easy
for (i in seq(nSubsE)){

    # subject data (y)
    yE <- easyData[[i]]$Choice

    # lag data (x predictors)
    xE <- seqQuits(yE)

    # models
    quitModelsE[[i]] <- glm(yE ~ xE, family = "binomial")

}
  # Result notes: while a couple of participants had significant p-values, the effect sizes are tiny. Deviance barely moves. That means that the odds of acceptance are independent of how many trials they quit before the current trial. No reason to add it as a covariante in the linear models, but it's worth talking about it.

```

\bigskip

### Power considerations

While the current results look promising, it is important to remember that this was a minimally-sampled pilot study. Because of that, I decided to run power analysis (based on Cohen, 1988) for the most important tests. For this, I took the sample size (n = 11), the effect size (R-squared and Cohen's D), and the resulting p-values for each test, and used the 'pwr' package to compute the power.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}

# tutorial: https://www.statmethods.net/stats/power.html

# proportion completed (overall, fine)
propPower <- pwr.t.test(n = 11, d = propRsq, sig.level = 0.05, type = "two.sample") # medium power
propSampleReq <- pwr.t.test(power = .8, d = propRsq, sig.level = 0.05, type = "two.sample") # estimating sample size needed for power = .8

# logistic regression (not sure if this works)
Fsq <- logisComb$Rsq / (1 - logisComb$Rsq)
sumLogis <- summary(logisComb)
#logisPower <- pwr.f2.test(u = sumLogis$df.residual, v = sumLogis$df.null, f2 = Fsq, sig.level = 0.0001) # impossible, way too high
```

The power analysis shows that, with the current parameters, my study has a medium power (`r propPower`). In order to reach a power level of 0.8 and still find the difference at the current effect size, I would need to increase my sample size to at least 17, as shown in the following plot.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}

# trying to plot the necessary sample size for every effect size (at the current p-val)
# powerRange <- seq(0.1,0.9,by = 0.1)
# sampleReq <- numeric()
# 
# for (i in 1:length(powerRange)){
#   
#     temp <-  pwr.t.test(power = powerRange[i], d = propRsq, sig.level = 0.05, type = "two.sample")
#     sampleReq[i] <- temp$n
#     
# }
# 
# plot(powerRange,
#      sampleReq,
#      main = "Sample Size Needed For Each Power Level \n At the Current Significance Level",
#      ylab = "Sample Size Needed",
#      xlab = "Power level")    
#

```

Perhaps more importantly, even with sufficient power and low p-values, the current study still risks a high false positive rate if the prior odds of finding this difference are against the alternative hypothesis (Benjamin et al., 2017; Nuzzo, 2014). This is a complicated issue to solve at the moment, especially since the present findings go against a literature that expects cognitive effort to provoke fewer responses than passive delays. Finally, it is worth noting that the sample (college students) is unrepresentative of the population at large, thus reducing the generality of these findings. Future replication of this study with larger (and more diverse) sample sizes, as well as an expansion to a within-subjects design, will help us determine whether these results are true or not. Regardless, the current line of work seems promising given the current results.

``` {r,echo=FALSE,fig.align="center",fig.width=9,fig.height=6}
### THE PLOTS FOR YALE
# Ggplot made plotting way easier than the previous version
# This is in case you don't want to plot the easy condition (easier to see)

a2 <- ggplot(data = trueProp, aes(x=interaction(Reward, Handling), y=propComplete, color=Group)) +
        geom_point(size=3) +
        geom_errorbar(aes(ymin=propComplete-SE, ymax=propComplete+SE), width=0.2, size=1) +
        geom_line(aes(group = interaction(Handling, Group)), size=1) +
        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey48", color = "grey48", size = 3, show.legend = F) +
        scale_color_manual(values=cols) +
        theme_classic()

a2
```

### 2018-10-11 Final_trimmed.Rmd
First import of all the data and scripts

---

title: "MA681 Final Project"
author: "Claudio Toro Serey"
date: "Fall 2017"
output:
  html_document: default
  fig_caption: true
  #pdf_document:
  #  pandoc_args: [
  #  "-V", "classoption=twocolumn"]  
#title: "Effort and Delay Discounting in a Foraging Environment"
#author: "Claudio Toro Serey"
#date: "MA681 Fall 2017"

---

```{r global_options, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

```

``` {r, echo=FALSE}
##------------- functions, libraries, and setups--------------
# libraries
library(tidyverse)
library(knitr)

## Miscelaneous
cols = c("#78AB05","#D9541A") # plot colors (wait, effort)
lthick = 2 # line thickness for plots

## Functions
# Permutation for 2 groups (equal n for paired)
permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){

    # prep data
    summaryPerm <- list()
    lOne <- length(group1)
    lTwo <- length(group2)
    bigSample <- c(group1,group2)

    if (paired == FALSE) {

        for (i in 1:nPerms){

            # relabel samples
            tempBig <- sample(bigSample)
            tempOne <- tempBig[1:lOne]
            tempTwo <- tempBig[(lOne+1):length(bigSample)]

            # stats
            tempDiffs <- statType(tempOne,na.rm=T) - statType(tempTwo,na.rm=T)
            summaryPerm$jointDist[i] <- tempDiffs # statType(tempDiffs, na.rm = T)

        }

    } else {

        for (i in 1:nPerms){

            # shift labels in a pairwise fashion
            tempDiffs <- statType((-1)^rbinom(lOne,1,0.5) * (group1 - group2))
            summaryPerm$jointDist[i] <- tempDiffs

        }

    }

    # get the observed difference
    diffs <- statType(group1,na.rm=T) - statType(group2,na.rm=T)
    observedAbs <- abs(diffs) # maybe leave it as means here
    observed <- diffs
    summaryPerm$Pval <- 2 * (1 - ecdf(summaryPerm$jointDist)(observedAbs))
    if (length(unique(abs(summaryPerm$jointDist))) == 1) {summaryPerm$Pval <- 1} # if the difference is always the same, then p = 1
    summaryPerm$Observed <- observed

    return(summaryPerm)

}

# Non-parametric Bootstrap for a single group
bootstrap <- function(group = 1, statType = mean, B = 5000){

    # prep param
    bootStats <- rep(0,B)

    # iterate
    for(b in 1:B){

      # wait group
      x <- sample(group,length(group),replace=T)  
      bootStats[b] <- statType(x,na.rm = T)

    }

    return(bootStats)

}

# plot logistic (for the prop complete test, mainly, but it can be easily expanded for more flexibility in n-params)
plotLogis <- function(coeffs = 1, group = "Wait", handling = 1:14, reward = 1:25, xAxis = "Reward", plotType = lines, color = "black", lType = 1, pchType = 16){

    # divide into relevant coefficients (assumes logisComb was the best model)
    intercept <- coeffs[1]
    groupBeta <- coeffs[2]
    handBeta <- coeffs[3]
    rwdBeta <- coeffs[4]

    # now the parameters
    label = "Reward Amount"
    if (group == "Wait"){group = 1} else {group = 0}
    if (xAxis == "Reward"){
        xAxis = reward 
        label = "Reward Amount" 
    } else {
        xAxis = handling
        label = "Handling Time"
    }

    # logistic function
    model <- intercept + groupBeta*group + handBeta*handling + rwdBeta*reward 
    func <- 1 / (1 + exp(-(model)))
    plotType(xAxis,
         func,
         ylim = c(0,1),
         xlab = label,
         ylab = "Probability of Completing a Trial",
         type="l",
         col = color,
         lty = lType,
         pch = pchType,
         lwd = 2,
         xaxt = "n")

    # use title() to add title afterwards
}

# Cohen's D for 2 groups
# for a more flexible approach, make the data input to be a list with entries for n groups, 
# then do length(list) for the number of groups. 
cohenD <- function(group1 = 1, group2 = 2){

      # means
      mean1 <- mean(group1, na.rm = T)
      mean2 <- mean(group2, na.rm = T)

      # variance
      var1 <- var(group1, na.rm = T)
      var2 <- var(group2, na.rm = T)

      # equation
      out <- (mean1 - mean2) / sqrt((var1 + var2)/2)

      return(out)

}

# get the number of continuous quits before current trial
seqQuits <- function(subjData = 1){

    # get the lag
    tempSeq <- sequence(rle(subjData)$lengths) # sequence
    tempSeq[subjData==1] <- 0 # not interested in completed runs, just quits
    tempSeq <- c(0,tempSeq) # lag it so it can be used as a t-1 regressor

    # return data so that the length is equivalent
    out <- tempSeq[1:length(subjData)]

    return(out)

}

# calculate C-hat (dispersion) for a regular GLM
dispCalc <- function(object) {
with(object,sum((weights * residuals^2)[weights > 0])/df.residual)
}
```

``` {r, echo=FALSE}
### data loading and cleaning up

# load cognitive effort group
setwd('./data/cog')
temp = list.files(pattern="*.csv")
cogDataLong = lapply(temp, read.csv, header = FALSE)

# load wait group
setwd('../wait')
temp = list.files(pattern="*.csv")
waitDataLong = lapply(temp, read.csv, header = FALSE)

# load physical group
setwd('../phys')
temp = list.files(pattern="*.csv")
physDataLong = lapply(temp, read.csv, header = FALSE)

### cleaning data
# this will generate a simple list with only info about trials that participants quit or completed
# this is because cognitive logs also include within-trial task-specific information
# for the wait condition, it will get rid of the break indicator

nSubs <- length(waitDataLong)

#  short lists
cogData <- list()
waitData <- list()
physData <- list()

# ASDADS
cogBefore <- list()
cogAfter <- list()
waitBefore <- list()
waitAfter <- list()
physBefore <- list()
physAfter <- list()

# clean 
for (subject in 1:nSubs){

  #--------- index for storing before/after----------
  breakW <- which(waitDataLong[[subject]]$V1 == 0)
  breakC <- which(cogDataLong[[subject]]$V1 == 0)
  breakP <- which(physDataLong[[subject]]$V1 == 0)

  cogBefore[[subject]] <- cogDataLong[[subject]][1:(breakC-1),]
  temp <- cogBefore[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))
  cogBefore[[subject]] <- cogBefore[[subject]][decisionTrials,]

  cogAfter[[subject]] <- cogDataLong[[subject]][(breakC+1):length(cogDataLong[[subject]]$V1),]
  temp <- cogAfter[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))
  cogAfter[[subject]] <- cogAfter[[subject]][decisionTrials,]

  waitBefore[[subject]] <- waitDataLong[[subject]][1:(breakW - 1),]
  waitAfter[[subject]] <- waitDataLong[[subject]][(breakW + 1):length(waitDataLong[[subject]]$V1),]

  physBefore[[subject]] <- physDataLong[[subject]][1:(breakP - 1),]
  physAfter[[subject]] <- physDataLong[[subject]][(breakP + 1):length(physDataLong[[subject]]$V1),]

  # assign header names
  colnames(waitBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(waitAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  colnames(physBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(physAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")

  colnames(cogBefore[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT","Experiment Time","Trial Outcome","Task Type","Task Setup")
  colnames(cogAfter[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT","Experiment Time","Trial Outcome","Task Type","Task Setup")
  #--------------------------------------------------

  # create an index for the trials in which a decision was made (completed, quit) 
  temp <- cogDataLong[[subject]]$V7 # trial outcome vector
  quitTrials <- grep("Quit",temp)
  completeTrials <- grep("Reward",temp)
  decisionTrials <- sort(c(quitTrials,completeTrials))

  # remove the break trial
  tempW <- waitDataLong[[subject]]$V1 != 0
  tempC <- cogDataLong[[subject]]$V1 != 0
  tempP <- physDataLong[[subject]]$V1 != 0

  # create a new list with only decision trials / without break
  cogData[[subject]] <- cogDataLong[[subject]][decisionTrials,]
  cogDataLong[[subject]] <- cogDataLong[[subject]][tempC,]
  waitData[[subject]] <- waitDataLong[[subject]][tempW,]
  physData[[subject]] <- physDataLong[[subject]][tempP,]

  # assign header names
  colnames(waitData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(physData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
  colnames(cogData[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT","Experiment Time","Trial Outcome","Task Type","Task Setup")
  colnames(cogDataLong[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT","Experiment Time","Trial Outcome","Task Type","Task Setup") # Long contains within-trial info

}

#-------------------------

cBefore <- rbind(cogBefore[[1]],cogBefore[[2]]) 
cAfter <- rbind(cogAfter[[1]],cogAfter[[2]]) 
wBefore <- rbind(waitBefore[[1]],waitBefore[[2]]) 
wAfter <- rbind(waitAfter[[1]],waitAfter[[2]]) 
pBefore <- rbind(physBefore[[1]],physBefore[[2]])
pAfter <- rbind(physAfter[[1]],physAfter[[2]])

for (i in 3:11){

    cBefore <- rbind(cBefore,cogBefore[[i]])  
    cAfter <- rbind(cAfter,cogAfter[[i]])
    wBefore <- rbind(wBefore,waitBefore[[i]])
    wAfter <- rbind(wAfter,waitAfter[[i]])
    pBefore <- rbind(pBefore,physBefore[[i]])
    pAfter <- rbind(pAfter,physAfter[[i]])

}

#rm(cogBefore,cogAfter,waitBefore,waitAfter)

# aggregate ADD PHYS
cogBeforeAll <- aggregate(cBefore$Choice,
          by = list(cBefore$Reward, cBefore$Handling),
          FUN = 'mean')
cogAfterAll <- aggregate(cAfter$Choice,
          by = list(cAfter$Reward, cAfter$Handling),
          FUN = 'mean')
waitBeforeAll <- aggregate(wBefore$Choice,
          by = list(wBefore$Reward, wBefore$Handling),
          FUN = 'mean')
waitAfterAll <- aggregate(wAfter$Choice,
          by = list(wAfter$Reward, wAfter$Handling),
          FUN = 'mean')

rm(cBefore,cAfter,wBefore,wAfter)
#--------------------------
# remove unnecessary variables
rm(temp,tempW,tempC,quitTrials,completeTrials,decisionTrials,subject)
```

## Effort and Delay Discounting in a Foraging Environment
### Claudio Toro Serey
### Abstract
Both delay and effort (i.e. physical and mental) have been shown to reduce the value of prospects, such that people tend to opt for less valuable outcomes if they can avoid waiting or exerting effort. Effort demands can influence the amount of time until an outcome is received, but to this date no study has tried dissociating these factors under equivalent scales. In this project, participants foraged for rewards under either pure delay or effortful conditions, with time-until-outcome being matched for both. While I expected the effort group to accept fewer trials overall, the data showed the opposite. This finding is at odds with previous literature (suggesting that effort can boost the value of outcomes) and encourages further study into the value-modulating properties of effortful demands.

### Introduction
Decisions lie at the actionable core of human experience. Much of what we see in others, such as the way they dress or what they eat, can be conveyed as a result of their choices. An important aspect of such decisions involves weighing the value of an outcome against the cost incurred in obtaining it. This cost-value interaction has many forms and characteristics, such as the allocation of monetary resources, or the uncertainty of obtaining an outcome versus a sure gain. A considerable amount of work has been focused on understanding the nature of value (Schultz, 2015). Cost, on the other hand, is less understood. A prevalent idea is that effort can act as a discounting factor, meaning that it reduces the perceived value of prospects.  Indeed, effort has been shown to be an actively avoided cost that devalues rewards, so that decision makers will prefer small rewards tied to low demands over large rewards that require high effort (Massar, Libedinsky, Weiyan, Huettel, & Chee, 2015). Importantly, this effect is independent from the amount of errors made in the task (Apps, Grima, Manohar, & Husain, 2015; Kool, McGuire, Rosen, & Botvinick, 2010; Westbrook, Kester, & Braver, 2013).
In the animal literature, the amount of effort a subject is willing to exert for a reward can be probed by increasing the ratio of responses required per each reinforcement until an animal refuses to work for the reward (Richardson & Roberts, 1996). Although findings from such studies have provided important information about the cost of effort in general, controversy regarding the particular nature of cognitive and physical effort persists (Westbrook & Braver, 2015). This debate has motivated investigators to characterize these types of effort more precisely (Schmidt, Lebreton, Cléry-Melin, Daunizeau, & Pessiglione, 2012; Walton, Kennerley, Bannerman, Phillips, & Rushworth, 2006). However, even though effort can be seen as cost in and of itself (Botvinick, Huffstetler, & McGuire, 2009), in ecological scenarios the magnitude of effort required by a task often affects the amount of time that is spent performing it. For example, going through an additional section of one’s tax return involves weighing both the mental effort and the extra time it takes against the reward attained. This is an important consideration. Multiple studies show that delayed rewards are discounted, so that having to wait longer for an outcome makes it less rewarding (Ainslie, 1975; Frederick, Loewenstein, & O ’donoghue, 2002; Green, Fristoe, & Myerson, 1994; Mcclure, Ericson, Laibson, Loewenstein, & Cohen, 2004). Additional investigations suggest that delay is discounted in a qualitatively similar fashion to physical (Prévost, Pessiglione, Météreau, Cléry-Melin, & Dreher, 2010) and mental effort (Massar et al., 2015), but that the magnitude of discounting varies between cost types. Although these studies have examined cost differences by combining time with physical or cognitive effort, there is currently no evidence on how participants would actively choose between all three types of cost. Moreover, these studies use different scales for effort and timing (e.g. the participant can either wait for weeks to be rewarded, or type 50 words backwards-an effortful task), thus retaining the time confound of effortful tasks. Finally, recent findings demonstrate that cost related to physical and mental effort is computed differently in the brain (Hosking, Floresco, & Winstanley, 2014; Kurniawan et al., 2011; Westbrook & Braver, 2015), thus highlighting the need to examine these effects simultaneously. Because of this, it is important to understand if and how effort acts as a source of cost that is distinct from delay, and how this dissociation is represented in people’s choices.
The overarching aim of this project is to use behavioral and neuroimaging methods to investigate the potential differences in cost between time, cognitive effort, and physical effort. However, the results presented here pertain to behavioral pilot data that is limited to cognitive effort and pure delay. These attributes are examined in a between-subject manner in order to provide a baseline that will guide future within-subject examinations. In particular, we explore how participants behave when faced with a foraging task. There are two main hypothesis in this project: 1) Participants should be less likely to accept low-reward and/or long-delay/effort trials; and 2) Participants in the cognitive group will accept fewer trials overall.

### Methods
Subjects:  A total of 22 healthy subjects (age 18-23; 13 female) were recruited from Psychology 101 classes through the Boston University SONA system. Participants were told to acquire as many points as possible during the task. After the task, subjects were questioned on their within-task behavior, and all mentioned that they followed a specific strategy that they developed early on in the task. We thus found no reason to exclude any participants for this analysis.
Foraging task: Participants faced individual trials in which they wait a given amount of time for a reward (the handling time). If the reward amount was not worth the time, the participant could quit the trial by pressing a key, forfeit the reward, and wait a different amount of time (traveling time) to try a new (and potentially more rewarding) trial. Participants were shown the total amount of points they can earn at the beginning of each trial (5, 10, or 25 points, uniformly distributed). These amounts were explicitly disclosed during the practice session in order to avoid any confusion about the possible reward amounts throughout the experiment. The total experiment time was divided into six 7-minute blocks. Each block had one of three predefined combinations of handling and travel times, all of which added up to 16 seconds (handling times could be 2, 10, or 14 seconds long). All three timing combinations were shown in a semi-random order, once before and after a break, and each was visually disclosed to the participant at the beginning of each block.
Subjects were divided into two groups: the “wait” group passively waited during the handling time, while the “cognitive” group completed a random sequence of two-second-long cognitive tasks that collectively lasted the equivalent of the handling time. This kind of task switching is demonstrably effortful (Apps et al., 2015; Kool et al., 2010). If a participant made more than two errors during the handling time, they were forced to travel (forced travel trials were not included in decision-related analyses). This contingency was added to guarantee engagement.
Calculating optimal behavior:  Having predefined handling, traveling, and reward amounts allowed me to compute the optimal behavior for each block. In the foraging literature, the possible per-trial reward is often weighed against the per-second rate of reward (Constantino & Daw, 2015). This is called the opportunity rate. By multiplying the opportunity rate by the handling time, decision makers can estimate the opportunity cost of time. This measure conveys the richness of the environment, and is equivalent to the participant contemplating how much they could be making instead of waiting for the current reward. The resulting optimal behavior was to accept everything when the handling time was 2 seconds, accept 10 and 25 points when it was 10 seconds, and to only accept 25-point trials when it lasted 14 seconds.

Statistical analyses: Choices are taken to be I.I.D. Bernoulli random variables (0 = quit, 1 = accept). Due to the non-gaussian nature of the data (choice and proportion of completed trials), as well as the small sample sizes, I give preference to non-parametric analyses when possible (i.e. when I am comparing an overall measure between both groups). On the parametric end: KS test was used to compare response time distributions for all participants, since response times tend to have non-Gaussian distributions. In order to get a general sense of the difference for all combinations of experimental factors, I performed a repeated-measures ANOVA, using handling time and rewards as within-subject factors. To check for the importance of each parameter, I performed model selection on a set of logistic regressions that predicted the proportion completed by each subject across conditions. The GLM was performed under the assumption of a binomial distribution for choices, even though proportions were used. This allowed me to compute AIC. Finally, I performed an auto-regressive process to identify whether participants were merely being influenced by the number of skips they had consecutively performed. Since this analysis was performed per-subject, individual choices were used, and thus I fully assumed a binomial distribution. I dwell on the specifics of each analysis and their assumptions in the results.

Statistical analyses: Due to the non-gaussian nature of the data (choice and proportion of completed trials), as well as the small sample sizes, I give preference to non-parametric analyses when possible (i.e. when I am comparing an overall measure between both groups). On the parametric end: KS test was used to compare response time distributions for all participants, since response times tend to have non-Gaussian distributions. In order to get a general sense of the difference for all combinations of experimental factors, I performed a repeated-measures ANOVA, using handling time and rewards as within-subject factors. To check for the importance of each parameter, I performed model selection on a set of logistic regressions that predicted the proportion completed by each subject across conditions. The GLM was performed under the assumption of a binomial distribution for choices, even though proportions were used. This allowed me to compute AIC. Finally, I performed an auto-regressive process to identify whether participants were merely being influenced by the number of skips they had consecutively performed. Since this analysis was performed per-subject, individual choices were used, and thus I fully assumed a binomial distribution. I dwell on the specifics of each analysis and their assumptions in the results.

### Results
``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4, fig.cap="\\label{fig:figs}plotting example"}
## overall summaries
summaryData <- data.frame(group = c(rep("Wait",nSubs),rep("Effort",nSubs)))

## gather basic data
for (subj in 1:nSubs){

    # choice index
    tempChoiceW <- waitData[[subj]]$Choice
    tempChoiceC <- cogData[[subj]]$Choice

    # propotion complete
    summaryData[subj,2] <- mean(tempChoiceW)
    summaryData[subj+11,2] <- mean(tempChoiceC)

    # earnings
    summaryData[subj,3] <- sum(waitData[[subj]]$Reward[tempChoiceW==1])
    summaryData[subj+11,3] <- sum(cogData[[subj]]$Reward[tempChoiceC==1])

    # RTs
    summaryData[subj,4] <- median(waitData[[subj]]$RT[tempChoiceW==0])
    summaryData[subj+11,4] <- median(cogData[[subj]]$`Choice RT`[tempChoiceC==0])

    # mistakes (only for effort group)
    tempMistakes <- sum(cogDataLong[[subj]]$`Trial Outcome`=="Forced travel") # how many forced travel trials
    tempTrialnum <- length(cogData[[subj]]$Choice) # how many decision trials
    summaryData[subj+11,5] <- tempMistakes / (tempMistakes + tempTrialnum) # proportion of forced travels throughout the exp

}

# name the data frame columns, and indexes for groups
colnames(summaryData) <- c("Group","propComplete","Earnings","RT","forcedTravel")
indxWait <- 1:11
indxWaitLong <- 1:99
indxCog <- 12:22
indxCogLong <- 100:198

```

#### Performance errors and outliers
In the effort condition, participants were forced to travel if they made more than 2 mistakes in a trial. To check if any participant showed significant struggles, I computed the inter-quartile range for the proportion of trials in which each participant was forced to travel (inter-quartile range = 0.18). A single outlier was found. However, due to the small sample size, and the fact that the participant had a clear strategy (disclosed post-experiment), I decided to retain this outlier for all analyses.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# mistakes
# significant from 0
# mistakeTest <- wilcox.test(summaryData$forcedTravel)
# mistakePerm <- permute(rep(0,11), summaryData$forcedTravel[indxCog]) # revise

# outlier
interQ <- quantile(summaryData$forcedTravel[indxCog])[2] + quantile(summaryData$forcedTravel[indxCog])[4]
outlier <- which(summaryData$forcedTravel[indxCog] > interQ)
```
#### Propotion Completed
The most basic question that guides this project is which group accepted more trials. Under the present framework, the condition that triggered the least acceptances can be argued to be the costliest. Unexpectedly, the wait group had a mean proportion acceptance of 0.53 (sd = 0.11), while the effort group's mean proportion was 0.72 (sd = 0.19). Figure 1 shows the ECDFS and 95% confidence inervals for the proportion completed by each group.

``` {r figs,echo=FALSE,fig.width=4,fig.height=3, fig.cap="ECDFs of the proportion of trials accepted for both groups. The wait group appears to have accepted fewer trials overall."}
## prop complete
# ecdfs
wait <- ecdf(summaryData$propComplete[indxWait])
cog <- ecdf(summaryData$propComplete[indxCog])
range <- seq(0,1,by=0.01)

# plot
plot(range,
     wait(range),
     main = "ECDF for Proportion Completed",
     xlab = "Proportion Completed",
     ylab = "ECDF",
     col = cols[1],
     type="l",
     lwd = lthick)
lines(range,
      cog(range),
      col = cols[2],
      lwd = lthick)
legend("bottomright",
       c("Wait","Effort"),
       fill = cols,
       cex = 0.8)

# CIs basic
CIC <- qt(.975,nSubs-1)*(sd(summaryData$propComplete[indxCog])/sqrt(nSubs))
CIW <- qt(.975,nSubs-1)*(sd(summaryData$propComplete[indxWait])/sqrt(nSubs))
lines(range,cog(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
lines(range,cog(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
lines(range,wait(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,wait(range) - CIW,col = cols[1], lty = 2, lwd = lthick)

rm(CIC,CIW)

# problem is, data is not normal, so we're going to bootstrap it and DEFINITELY permute
# Bootstrap nonparametric
B <- 5000
meanBootW <- bootstrap(summaryData$propComplete[indxWait],B = B) #rep(0,B)
meanBootC <- bootstrap(summaryData$propComplete[indxCog], B = B) #rep(0,B)
varBootW <- bootstrap(summaryData$propComplete[indxWait],B = B) #rep(0,B)
varBootC <- bootstrap(summaryData$propComplete[indxCog], B = B) #rep(0,B)

#CIs wait
meanW <- mean(meanBootW)
upperW <- quantile(meanBootW,0.975) # meanBoot?
lowerW <- quantile(meanBootW,0.025)

#CIs effort
meanC <- mean(meanBootC)
upperC <- quantile(meanBootC,0.975) # meanBoot?
lowerC <- quantile(meanBootC,0.025)

# formal testing
# prop.test(sum(cogData[[i]]$Choice),length(cogData[[i]]$Choice))
propTtest <- t.test(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])
propPerm <- permute(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])

# effect size
propRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])

rm(B,cog,wait,subj)
```

The small size of the samples makes any distinction difficult to perceive, and the eastimates unreliable. In order to accomodate for this shortcoming, I took a handful of steps. First, I bootstrapped the mean proportion for each group separately (5000 iterations), so I could get a better estimate of the mean through CIs (which were computed based on the 0.025 and 0.975 quantiles). The bootstrapped statistics for the wait (M = $`r round(meanW, digits = 2)`$, lower CI = $`r round(lowerW, digits = 2)`$, upper CI = $`r round(upperW, digits = 2)`$) and effort (M = $`r round(meanC, digits = 2)`$, lower CI = $`r round(lowerC, digits = 2)`$, upper CI = $`r round(upperC, digits = 2)`$) were then used to plot the previous ECDF with the new confidence intervals (Figure 2, left). It can now be seen that the CIs do not overlap, suggesting a true difference between these groups. To formalize this comparison, I performed a permutation test on the mean difference in proportions between both groups (relabeling the data through 5000 iterations). The estimated null distribution of this difference is shown in Figure 2 (right). This distribution was plotted as an example. Further permutations will not be plotted. The resulting p-value was `r propPerm$Pval`, thus rejecting the null hypothesis that the difference between these groups would be 0. Just to be clear, from now on the p-values will mean the probability of finding a statistic at least as extreme as the one observed under the null distribution. Finally, I used Cohen's D to estimate the effect size of this comparison, which yielded a value of $`r round(propRsq, digits = 2)`$. This shows that the effort group completed a significantly larger amount of trials overall than the wait group.

``` {r,echo=FALSE,fig.align="center",fig.width=10,fig.height=4,fig.cap="Left: ECDFs of the proportion completed for each group, with bootstrapped confidence intervals computed from its quantiles (0.975 and0.025). Right: Resulting distribution of the permuted differences in means between the effort and wait groups (wait minus effort), and the actual difference marked by the red line."}

# plot ecdf 
par(mfrow=c(1,2))
ecdfW <- ecdf(meanBootW)
ecdfC <- ecdf(meanBootC)

wait <- ecdf(summaryData$propComplete[indxWait])
cog <- ecdf(summaryData$propComplete[indxCog])
range <- seq(0,1,by=0.01)

plot(range,
     wait(range),
     main = "ECDF for Proportion Completed",
     xlab = "Proportion Completed",
     ylab = "ECDF",
     col = cols[1],
     type="l",
     lwd = lthick)
lines(range,
      cog(range),
      col = cols[2],
      lwd = lthick)
legend("bottomright",
       c("Wait","Effort"),
       fill = cols,
       cex = 0.8)

# plot(range,ecdfW(range),
#      type = "l",
#      main = "ECDF for the Bootstrapped Proportions",
#      xlab = "Proportion Completed",
#      ylab = "ECDF",
#      xlim = c(0,1),
#      col = cols[1],
#      lwd = lthick)
# lines(range,
#       ecdfC(range),
#       col = cols[2],
#       lwd = lthick)
# legend("bottomright",
#        c("Wait","Effort"),
#        fill = cols,
#        cex = 0.8)

# and CIs for each (unnecessary unless I end up plotting)
CIC <- qt(.975,nSubs-1)*(sd(meanBootC)/sqrt(nSubs))
CIW <- qt(.975,nSubs-1)*(sd(meanBootW)/sqrt(nSubs))
lines(range,cog(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
lines(range,cog(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
lines(range,wait(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,wait(range) - CIW,col = cols[1], lty = 2, lwd = lthick)

# lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
# lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) #qt(.975,nSubs-1)*(sd(meanBootC)/sqrt(nSubs))
# lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
# lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)

rm(CIC,CIW)

# plotting the permutation
plot(density(propPerm$jointDist),
     main = "Permuted Null Distribution \n Difference in Proportions Wait - Effort",
     xlab = "Mean Difference",
     lwd = lthick)
lines(c(propPerm$Observed,propPerm$Observed), c(0,1200), lty=2, col="red", lwd = lthick)

```

#### Total Earnings

```{r,echo=FALSE,fig.align="center",fig.width=10,fig.height=4, fig.cap="Left: box plot of the differences in earnings between groups. Right: relationship between proportion completed and cumulative earnings. A linear model (fit line in black) showed that both the linear (beta = 4078, SE = 1013, p-value < 0.001) and quadratic form (beta = -3275, SE = 715, p < 0.0001) of the proportion significantly predicted the total earned"}
# descriptives
meanC <- mean(summaryData$Earnings[indxCog])
seC <- (sd(summaryData$Earnings[indxCog])) / sqrt(11)
meanW <- mean(summaryData$Earnings[indxWait])
seW <- (sd(summaryData$Earnings[indxWait])) / sqrt(11)

# wilcoxon rank sum
#earningTest <- wilcox.test(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog], alternative = "two.sided")
earningsPerm <-permute(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog]) # I believe this more
earningsRsq <- cohenD(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog])

# linear model (think of doing a Poisson Regression instead, since earnings are not normally distributed [although bootstrapped they're fine])
propAllsq <- summaryData$propComplete^2 
lmEarn <- lm(Earnings ~ propComplete + propAllsq, data = summaryData)
coeffsEarn <- lmEarn$coefficients
x <- seq(0,1,length=100) # for plotting

# plotting
par(mfrow=c(1,2))
boxplot(summaryData$Earnings[indxWait],
        summaryData$Earnings[indxCog],
        names = c("Wait","Effort"),
        main = "Total Earnings for Each Group",
        ylab = "Total Earnings (pts)",
        xlab = "Group")

# earnings (inverse-U, which makes sense because either over or under accepting are detrimental to earnings)
plot(summaryData$propComplete[indxWait],
     summaryData$Earnings[indxWait],
     main = "Total Earnings \n as a Function of Proportion Accepted",
     xlab = "Total Proportion Completed",
     ylab = "Total Earned",
     col=cols[1],
     xlim=c(0.2,1),
     ylim = c(1000,2000),
     pch=16,
     cex = lthick - 0.5)
points(summaryData$propComplete[indxCog],
       summaryData$Earnings[indxCog],
       col=cols[2],
       pch=16,
       cex = lthick - 0.5)
legend("topright",
       c("Wait","Effort"),
       fill = cols,
       cex = 0.8)
lines(x, coeffsEarn[1] + coeffsEarn[2]*x + coeffsEarn[3]*(x^2),
       col="black",
      lwd = lthick)
```

Next, it was of interest to examine each group's total earnings. As seen on figure 3 (left), the effort group earned slightly less (M = `r meanC`, SE = `r round(seC, digits = 2)`) than the wait group (M = `r round(meanW)`, SE = `r round(seW, digits = 2)`). A permutation analysis of differences in mean earnings per group indicated a trend (p = `r earningsPerm$Pval`; Cohen's D = `r round(earningsRsq, digits = 2)`). The figure on the right shows a nonlinear relationship between acceptance rates and total earnings. A linear model was performed to estimate this relationship, using the total earned as the dependent variable and the proportion completed (and its quadratic form) as predictors. All of the terms significantly predicted cumulative earnings (p < 0.0001), with an $R^2$ of 0.52. This is in line with the nature of the experiment, as participants should cautiously balance rewards with opportunity cost, and both under- and over-acceptance were non-optimal.

#### Response Times
After checking for acceptance and earnings, another question is how fast participants were in making decisions (as they could quit at any point during the handling time). Perhaps participants were unclear about the experimental procedures, or changed their minds mid-trial. To account for this, I pooled all the response times for quit trials (since they are representative of a participant's choice to leave) across participants for each group. With these two vectors, I plotted their respective ECDFs (Figure 4) and bootstrapped 95% CIs. As it can be seen, most decisions were made before the first second, with the wait group being slightly slower.

```{r,echo=FALSE,fig.align="center",fig.width=4,fig.height=3, fig.cap="ECDFs of pooled response times from each group. Responses were overall quick, with the wait group being slightly slower."}
# RTs
# let's try to do some survival curves
RTW <- numeric() # vector of all decision-related RTs for the wait group
RTC <- numeric() # same for the cog group

for (subj in 1:nSubs){

    # index for trials quit
    tempChoiceW <- waitData[[subj]]$Choice==0
    tempChoiceC <- cogData[[subj]]$Choice==0

    # concatenate the subject RT to the group
    RTW <- c(RTW,waitData[[subj]]$RT[tempChoiceW])
    RTC <- c(RTC,cogData[[subj]]$`Choice RT`[tempChoiceC])

}

# create an array with both data (for surv fit autoplot trials)
lenC <- length(RTC)
lenW <- length(RTW)

RTgroups <- c(rep("Wait",lenW), rep("Effort",lenC))
RTall <- c(RTW,RTC)

# plot ecdf 
ecdfW <- ecdf(RTW)
ecdfC <- ecdf(RTC)
range <- seq(0,10, by = 0.001)

plot(range,ecdfW(range),
     type = "l",
     main = "ECDF and CIs for the Response Times",
     xlab = "Seconds",
     ylab = "ECDF",
     xlim = c(0,5),
     col = cols[1],
     lwd = lthick)
lines(range,
      ecdfC(range),
      col = cols[2],
      lwd = lthick)
legend("right",
       c("Wait","Effort"),
       fill = cols,
       cex = 0.8)

# and CIs for each (unnecessary unless I end up plotting)
CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
CIC <- median(CIC) - (quantile(CIC,0.025))
CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
CIW <- median(CIW) - (quantile(CIW,0.025))
lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)

# just cause, Kolmogrov-Smirnov 
ksRT <- ks.test(RTW,RTC)
RTPerm <- permute(RTW,RTC)
RTCohen <- cohenD(RTW,RTC)

rm(lenC,lenW,x)

```

Lastly, I performed a KS test to check if the difference between these distribution was not 0. The test proved significant (D = `r round(ksRT$statistic, digits = 2)`, p < 0.001), although this difference is not behaviorally very relevant for the present study (milisecond differences are inconsequential when we are interested in seconds). I confirmed this result by means of permutation analysis (p < 0.0001; Cohen's D = `r round(RTCohen, digits = 2)`). The small effect size also speaks to the potential lack of true differences between groups at this level.
The quick response times indicate that participants had a clear idea of what rewards were worth their time and effort. This is in agreement with the post-experiment questionaire, in which participant explained very specific strategies that they followed throughout the session.

#### Proportion per handling-reward combination 
The analyses above give us a general sense of the characteristics of each group. However, it also necessary to asses whether decision makers were influenced differently at each timing and reward combinations, and how these factors varied by group. First, I was interested in seeing differences as a whole. Figure 5 shows the proportion accepted (and standard error) for all these combinations.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=3, results = 'asis'}

# params for reference
handling <- c(2,10,14)

# the other, just summarizing for all participants
allProp <- data.frame(Group = c(rep("Wait",nSubs*3),rep("Effort",nSubs*3)),
                      Handling = c(rep(2,nSubs), rep(10,nSubs), rep(14,nSubs),rep(2,nSubs), rep(10,nSubs), rep(14,nSubs)),
                      FivePts = rep(NA,nSubs*6),
                      TenPts = rep(NA,nSubs*6),
                      TwntyfivePts = rep(NA,nSubs*6))

allProp2 <- data.frame(SubjID = c(rep(1:11,9),c(rep(12:22,9))),
                       Group = c(rep("Wait",nSubs*9),rep("Effort",nSubs*9)),
                      Handling = c(rep(2,nSubs*3), rep(10,nSubs*3), rep(14,nSubs*3),rep(2,nSubs*3), rep(10,nSubs*3), rep(14,nSubs*3)),
                      Reward = rep(c(rep(5,nSubs),rep(10,nSubs),rep(25,nSubs)),3),
                      propComplete = rep(NA,198),
                      totalTrials = rep(NA,198),
                      totalComplete = rep(NA,198))

for (subj in 1:nSubs){

    # prop 1
    # wait group
    # handling of 2s
    allProp$FivePts[subj] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==5])
    allProp$TenPts[subj] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==10])
    allProp$TwntyfivePts[subj] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==25])

    # handling of 10s
    allProp$FivePts[subj+11] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==5])
    allProp$TenPts[subj+11] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==10])
    allProp$TwntyfivePts[subj+11] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==25])

    # handling of 14s
    allProp$FivePts[subj+22] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==5])
    allProp$TenPts[subj+22] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==10])
    allProp$TwntyfivePts[subj+22] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==25])

    # effort group
    # handling of 2s
    allProp$FivePts[subj+33] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==5])
    allProp$TenPts[subj+33] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==10])
    allProp$TwntyfivePts[subj+33] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==25])

    # handling of 10s
    allProp$FivePts[subj+44] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==5])
    allProp$TenPts[subj+44] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==10])
    allProp$TwntyfivePts[subj+44] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==25])

    # handling of 14s
    allProp$FivePts[subj+55] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==5])
    allProp$TenPts[subj+55] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==10])
    allProp$TwntyfivePts[subj+55] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==25])

    # prop 2
    # wait group
    # handling of 2s
    allProp2$propComplete[subj] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==5])
    allProp2$propComplete[subj+11] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==10])
    allProp2$propComplete[subj+22] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==25])
    allProp2$totalTrials[subj] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==5])
    allProp2$totalTrials[subj+11] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==10])
    allProp2$totalTrials[subj+22] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==2 & waitData[[subj]]$Reward==25])

    # handling of 10s
    allProp2$propComplete[subj+33] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==5])
    allProp2$propComplete[subj+44] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==10])
    allProp2$propComplete[subj+55] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==25])
    allProp2$totalTrials[subj+33] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==5])
    allProp2$totalTrials[subj+44] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==10])
    allProp2$totalTrials[subj+55] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==10 & waitData[[subj]]$Reward==25])

    # handling of 14s
    allProp2$propComplete[subj+66] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==5])
    allProp2$propComplete[subj+77] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==10])
    allProp2$propComplete[subj+88] <- mean(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==25])
    allProp2$totalTrials[subj+66] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==5])
    allProp2$totalTrials[subj+77] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==10])
    allProp2$totalTrials[subj+88] <- length(waitData[[subj]]$Choice[waitData[[subj]]$Handling==14 & waitData[[subj]]$Reward==25])

    # effort group
    # handling of 2s
    allProp2$propComplete[subj+99] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==5])
    allProp2$propComplete[subj+110] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==10])
    allProp2$propComplete[subj+121] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==25])
    allProp2$totalTrials[subj+99] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==5])
    allProp2$totalTrials[subj+110] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==10])
    allProp2$totalTrials[subj+121] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==2 & cogData[[subj]]$Reward==25])

    # handling of 10s
    allProp2$propComplete[subj+132] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==5])
    allProp2$propComplete[subj+143] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==10])
    allProp2$propComplete[subj+154] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==25])
    allProp2$totalTrials[subj+132] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==5])
    allProp2$totalTrials[subj+143] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==10])
    allProp2$totalTrials[subj+154] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==10 & cogData[[subj]]$Reward==25])

    # handling of 14s
    allProp2$propComplete[subj+165] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==5])
    allProp2$propComplete[subj+176] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==10])
    allProp2$propComplete[subj+187] <- mean(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==25])
    allProp2$totalTrials[subj+165] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==5])
    allProp2$totalTrials[subj+176] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==10])
    allProp2$totalTrials[subj+187] <- length(cogData[[subj]]$Choice[cogData[[subj]]$Handling==14 & cogData[[subj]]$Reward==25])

}

# total accepted (not proportion), needed for binomial test
allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials

# add optimal vector and difference from optimal
two <- rep(1,33)
ten <- c(rep(0,11),rep(1,22))
tfive <- c(rep(0,22),rep(1,11))
allProp2$Optimal <- rep(c(two,ten,tfive),2)
allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete

# sort by subject ID
#allProp2 <- allProp2[order(allProp2$SubjID),]

# actual proportions and standard errors, and the optimal summary for plotting
trueProp <- aggregate(allProp2$propComplete,
            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
            FUN = 'mean')

trueSD <- aggregate(allProp2$propComplete,
          by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
          FUN = 'sd')
colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
trueProp$SE <- (trueSD$x)/(sqrt(nSubs))

optimalProp <- aggregate(allProp2$Optimal,
            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
            FUN = 'mean')$x

```

```{r,echo=FALSE,fig.align="center",fig.width=9,fig.height=5, fig.cap="Proportion completed and standard errors for each combination of handling and reward amounts, for each group separately"}
# trying another plot, for ANOVA (equivalent to the poster one)
# make margins big enough
# par(mar=c(6.1,4.1,5.1,2.1))
# lthick <- 2.5

# putting this here for now, so it doesn't mess up anything above. Once the plot decision is made, clean up
# trueProp <- trueProp[order(trueProp$Group,decreasing = T),]
# trueProp$SE[11:12] <- 0.001 # because otherwise it won't plot the arrows (SE = 0)
# trueProp$SE[15] <- 0.001

# # actual plot
# plot(1:3, trueProp$propComplete[1:3],
#      main = "Proportion Completed Per Handling/Reward Combination \n Mean and SE for Each Group",
#      xlab = "",
#      ylab = "Proportion Completed",
#      xlim = c(1,21), 
#      ylim = c(0,1),
#      type = "l",
#      xaxt = "n",
#      col = cols[1],
#      lwd = lthick + 2,
#      bty = "n")
# points(1:3, 
#      trueProp$propComplete[1:3],
#      col = cols[1],
#      pch = 16,
#      cex = lthick - 1,
#      bty = "n")
# arrows(1:3, trueProp$propComplete[1:3] - trueProp$SE[1:3],
#        1:3, trueProp$propComplete[1:3] + trueProp$SE[1:3], 
#        length=0.05, 
#        angle=90, 
#        code=3,
#        col = cols[1],
#        lwd = lthick + 2)
# 
# ranges <- array(4:18,dim = c(3,5)) # for selecting and placin on x-axis
# for (i in 1:5){
#   
#     # choose a different color for each group
#     color = cols[1]
#     if (i > 2){color = cols[2]}
#     
#     # grab the relevant measure indexes
#     indx <- ranges[,i]
#     
#     # SEs
#     SEup <- trueProp$propComplete[indx] + trueProp$SE[indx]
#     SEdown <- trueProp$propComplete[indx] - trueProp$SE[indx]
#     
#     # plot
#     lines(indx,
#           trueProp$propComplete[indx],
#           col = color,
#           lwd = lthick + 2)
#     points(indx, 
#            trueProp$propComplete[indx],
#            col = color,
#            cex = lthick - 1,
#            pch = 16,
#            bty = "n")      
#     arrows(indx, SEdown,
#            indx, SEup, 
#            length=0.05, 
#            angle=90, 
#            code=3,
#            col = color,
#            lwd = lthick + 2)    
# }
# 
# # legend
# legend("topright",
#        c("Wait","Effort"), 
#        fill = c(cols[1],cols[2]),
#        cex = 0.8)
# 
# # x axis
# axis(1,at = 1:9, rep(c(5,10,25),3))
# axis(1,at = 10:18, rep(c(5,10,25),3))
# axis(1,at = c(2,5,8), c(2,10,14), line = 3)
# axis(1,at = c(11,14,17), c(2,10,14), line = 3)
# mtext("Reward",1,line=1,at=-0.5)
# mtext("Handling",1,line=3,at=-0.5)
```

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
## REPEATED MEASURES VERSION
# I think I like this the most
prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
                                 Error(SubjID / (Handling * Reward))))
```

This plot portrays some important features: the first hypothesis was supported, as we can see that participants accepted fewer trials for smaller rewards and longer handling times. On the other hand, and perhaps expectedly, we can see that the effort group accepted more trials than the wait group in all cases. This is contrary to the second hypothesis.
In order to analyze these differences, I ran a 2-way repeated measures ANOVA to see how participants in each group performed at each combination of handling times and rewards. Since all three factors are relevant to the question, and since at this point I was interested in mean differences, I did not perform model selection. The table below shows the results from the analysis from variance. Main effects were found for group (F(1,186) = 5.36, p < 0.05), handling time (F(1,186) = 30.045, p < 0.0001), and reward amount (F(1,186) = 81.08, p < 0.0001). A handling by reward interaction was also found (F(1,186) = 9.42, p < 0.005), indicating that participant tendencies to accept higher rewards were reduced by longer handling times. This was somewhat expected, since the optimal behavior was to forage selectively for higher rewards as the handling time increased, and participants were fairly sensible to this structure.
This analysis opens the door to another important consideration: the optimality of each group's behavior. Since the reward-maximizing choices can be calculated, I overlayed them on the plot from figure 5 (in grey).

```{r,echo=FALSE,fig.align="center",fig.width=9,fig.height=5, fig.cap="Same as figure 6, but with the optimal choices plotted in grey. As an example, the optimal behavior for a handling time of 10 seconds is to accept 10 and 25 points, but not 5 points."}
# trying another plot, for ANOVA (equivalent to the poster one)
# make margins big enough
par(mar=c(6.1,4.1,5.1,2.1))
lthick <- 2.5

# putting this here for now, so it doesn't mess up anything above. Once the plot decision is made, clean up
trueProp <- trueProp[order(trueProp$Group,decreasing = T),]
trueProp$SE[11:12] <- 0.001 # because otherwise it won't plot the arrows (SE = 0)
trueProp$SE[15] <- 0.001

# actual plot
plot(1:3, trueProp$propComplete[1:3],
     #main = "Proportion Completed Per Handling/Reward Combination \n Mean and SE for Each Group",
     xlab = "",
     ylab = "Proportion Completed",
     xlim = c(1,21), 
     ylim = c(0,1),
     type = "l",
     xaxt = "n",
     col = cols[1],
     lwd = lthick + 2,
     bty = "n")
points(1:3, 
     trueProp$propComplete[1:3],
     col = cols[1],
     pch = 16,
     cex = lthick - 1,
     bty = "n")
arrows(1:3, trueProp$propComplete[1:3] - trueProp$SE[1:3],
       1:3, trueProp$propComplete[1:3] + trueProp$SE[1:3], 
       length=0.05, 
       angle=90, 
       code=3,
       col = cols[1],
       lwd = lthick + 2)
# plot the optimal choices
lines(1:3,optimalProp[1:3], col = "grey48",lty=3, lwd = lthick + 2)
points(1:3,optimalProp[1:3], col = "grey48",pch=17, cex = lthick - 1)

ranges <- array(4:18,dim = c(3,5)) # for selecting and placin on x-axis
for (i in 1:5){

    # choose a different color for each group
    color = cols[1]
    if (i > 2){color = cols[2]}

    # grab the relevant measure indexes
    indx <- ranges[,i]

    # SEs
    SEup <- trueProp$propComplete[indx] + trueProp$SE[indx]
    SEdown <- trueProp$propComplete[indx] - trueProp$SE[indx]

    # plot
    lines(indx,
          trueProp$propComplete[indx],
          col = color,
          lwd = lthick + 2)
    points(indx, 
           trueProp$propComplete[indx],
           col = color,
           cex = lthick - 1,
           pch = 16,
           bty = "n")      
    arrows(indx, SEdown,
           indx, SEup, 
           length=0.05, 
           angle=90, 
           code=3,
           col = color,
           lwd = lthick + 2)    
    lines(indx,optimalProp[indx], col = "grey48", lty=3, lwd = lthick + 2)
    points(indx,optimalProp[indx], col = "grey48", pch=17, cex = lthick - 1)
}

# legend
legend("topright",
       c("Wait","Effort","Optimal"), 
       fill = c(cols[1],cols[2],"grey48"),
       cex = 0.8)

# x axis
axis(1,at = 1:9, rep(c(5,10,25),3))
axis(1,at = 10:18, rep(c(5,10,25),3))
axis(1,at = c(2,5,8), c(2,10,14), line = 3)
axis(1,at = c(11,14,17), c(2,10,14), line = 3)
mtext("Reward",1,line=1,at=-0.5)
mtext("Handling",1,line=3,at=-0.5)

title(main = "Proportion Completed Per Handling/Reward Combination \n Mean and SE for Each Group",
      line = 3)
axis(3,at = 1:9, c('*','*','','*','*','','*','*','*'), tick = F, cex = 1.2)
axis(3,at = 10:18, c('*','','','*','*','','*','*',''), tick = F, cex = 1.2)
```

The first thing to note is that both groups show some level of sensitivity to the optimal behavior for each handling time. While there are no perfect matches, each group's choice behavior at each handling time was more similar to its corresponding optimal behavior than to any other ones. This suggests that participants were able to integrate the parameters of the task in a sensible way. Second, the effort group was closer to optimality for the 2 second handling time, while the wait group better approximated optimality at 14 seconds. In addition to these insights, we can ask quantitatively which group deviated the most from this ideal.

#### Deviation from optimality
The following analysis relies on a set of assumptions. First, I assumed that participants knew what the overall optimal acceptance was (partially supported by post-experimental interviews). If we consider optimal acceptances to be the null distribution against which the optimality of acceptance rates can be evaluated, then we could use the probability of finding the observed acceptance rate using a binomial distribution for each reward/handling combination. Second, since probabilities of 1 and 0 for the binomial distribution would yield zeros, I assumed that absolute certainty was impossible, and thus changed 1 to 0.999 and 0 to 0.001. This way, I calculated the probability of seeing a proportion of acceptances given that the null probability was either 0.999 or 0.001. Importantly, since I was interested in the group as a whole, I pooled the total number of acceptances and total trials for across participants in each group (organized by reward and handling time combinations). The resulting probabilities were transformed into p-values and adjusted for multiple comparisons using the Benjamini & Yekutieli method (FDR), and evaluated at an alpha of 0.05.

The asterisks on figure 9 mark where there were significant differences from optimality. This analysis confirms what was visually evident (given the SEM bars). Further it shows to some extent that the wait group was overall less optimal than the wait group. However, given the shape of acceptance rates and their actual distances from optimality, I would still argue that the wait group was more optimal at longer handling times, while the effort group matched optimality more closely at shorter ones.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# In the works: the idea here is to estimate the probability of having observed a given amount of completed trials, assuming that the null is the reward maximizing behavior. That means: what is the probability of having seen this acceptance rate, assuming the optimal was to either accept or not (1 or 0)? If subjects knew the optimal behavior, then very low probabilities indicate that they were affected by the cost significantly. We cannot really assume that participants know this, but post-experiment interviews indicate that many of them had a clear idea of what the approxiimate optimal behavior was, even if they violated the rule during the experiment.

# might use https://www.rdocumentation.org/packages/pracma for eps()

TC <- aggregate(allProp2$totalComplete, by = list(allProp2$Reward, allProp2$Handling, allProp2$Group), FUN = 'sum')
TC <- TC[order(TC$Group.3,decreasing = T),]
TT <- aggregate(allProp2$totalTrials, by = list(allProp2$Reward, allProp2$Handling, allProp2$Group), FUN = 'sum')
TT <- TT[order(TT$Group.3,decreasing = T),]
OPT <- aggregate(allProp2$Optimal, by = list(allProp2$Reward, allProp2$Handling, allProp2$Group), FUN = 'mean')
OPT <- OPT[order(OPT$Group.3,decreasing = T),]

trueProp$totalComplete <- TC$x
trueProp$totalTrials <- TT$x
trueProp$Optimal <- OPT$x
trueProp$Optimal[trueProp$Optimal==1] <- 0.99 # consider just getting eps(), like in matlab
trueProp$Optimal[trueProp$Optimal==0] <- 0.01

for (i in 1:18){

    # parameters of interest for the binomial test
    completed <- trueProp$totalComplete[i]
    total <- trueProp$totalTrials[i]
    prob <- trueProp$Optimal[i]

    # estimate the probability of having observed the acceptance rate, assuming reward-maximizing behavior
    trueProp$binomProb[i] <- round(pbinom(completed,total,prob), digits = 10)

}

# this is important. Since each test is comparing against either the 1 or 0 side, the pvalue calculated from the probability needs to be signed appropriately. For optimal acceptances of 1, the probability given by pbinom() is the pvalue, but for 0 it is 1 - pbinom().
trueProp$pval <- abs(rep(c(0,0,0,1,0,0,1,1,0),2) - trueProp$binomProb)

# do multiple-test corrections
trueProp$adjPval <- round(p.adjust(trueProp$pval, "BY"), digits = 4)
```

#### Before/After break strategy changes
**Another question that is worth prusuing is whether participants changed their behavior before and after the break. This is particularly important because they saw the same handling and travel time combination blocks (in the same order) before and after this break. To evaluate this, I performed per-subject paired permutation tests (paired by handling-reward combination), and extracted the p-values from the permuted null distributions. After correction for multiple comparisons (using false discovery rate), there were no significant changes before and after the break. These results suggest that participants were consistent in their acceptance behavior, and were following determinate strategies. This is in addition to the response time evidence examined above.**

```{r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}

# Before/After per subject diffs
# wilcoxon signed rank won't work because the vectors are likely to be of different lengths
# prop.test works as test of proportions (chi-square ish, but evaluated with a z-distribution?)
# just say it's a chi-squared test of proportions per subject, and that only one subject had a different proportion completed before and after the break. All other null could not be rejected.
# Problem: this computes the proportion without accounting for handling or reward amounts. Problem is, there aren't enough trials per combination to really account for every bit. Could be interesting to try, though.

cogABPval <- numeric()
waitABPval <- numeric()

for (i in 1:11){

      # wait
      tempPropB <- aggregate(waitBefore[[i]]$Choice, by = list(waitBefore[[i]]$Handling, waitBefore[[i]]$Reward), FUN = 'mean')
      tempPropA <- aggregate(waitAfter[[i]]$Choice, by = list(waitAfter[[i]]$Handling, waitAfter[[i]]$Reward), FUN = 'mean')
      tempPerm <- permute(tempPropB$x,tempPropA$x,nPerms = 5000, paired = TRUE)
      waitABPval[i] <- tempPerm$Pval

      # effort
      if (i == 9) { cogABPval[i] = 1} else {
      tempPropB <- aggregate(cogBefore[[i]]$Choice, by = list(cogBefore[[i]]$Handling, cogBefore[[i]]$Reward), FUN = 'mean')
      tempPropA <- aggregate(cogAfter[[i]]$Choice, by = list(cogAfter[[i]]$Handling, cogAfter[[i]]$Reward), FUN = 'mean')
      tempPerm <- permute(tempPropB$x,tempPropA$x,nPerms = 5000, paired = TRUE)
      cogABPval[i] <- tempPerm$Pval}

}

# Before after group. Don't worry about plotting
# paired t-tests also show that there are no differences before and after the break, indicating consistency of strategies
abWait <- t.test(waitBeforeAll$x,waitAfterAll$x,paired = T)
abCog <- t.test(cogBeforeAll$x,cogAfterAll$x,paired = T)
```

```{r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4, fig.cap="P-values for the pairwise permutation of before and after break performance, each plot showing each group"}
# ## plotting
# plot(1:11,
#      waitABPval,
#      main = "P-values for permuted pairwise comparisons before and after break",
#      xlab = "Subjects",
#      ylab = "P values",
#      ylim = c(0,1),
#      xlim = c(0,22),
#      pch = 16,
#      col = cols[1])
# points(12:22,
#        cogABPval,
#        pch = 16,
#        col = cols[2])
# # legend
# legend("right",
#        c("Wait","Effort"), 
#        fill = c(cols[1],cols[2]),
#        cex = 0.8)
```

#### Logistic regression 
The analyses above were meant to get a sense of performance differences between groups while assuming that all experimental parameters were relevant, but I was also interested in estimating the importance of each factor in predicting choice. Such predictions can often be done with linear models. However, due to the non-Gaussian nature of the proportion of choices, as well as the predictors, I decided to run a logistic regression to predict the proportion of trials per subject, using group, handling time, and reward amount as predictors *(using a quasi-binomial GLM)*. I used Akaike Information Criterion (AIC) to identify which combinations of predictors significantly reduced the -2 log-likelihood while penalizing the addition of predictors. Figure 9 shows the results.

```{r,echo=FALSE,fig.align="center",fig.width=9,fig.height=6}
# logistic regression tests ($deviance for LRTs, if desired. AIC should be fine though)
logisBase <- glm(propComplete ~ 1, family = "binomial", data = allProp2) # intercept only
logisGroup <- glm(propComplete ~ factor(Group), family = "binomial", data = allProp2) 
logisHand <- glm(propComplete ~ factor(Group) + Handling, family = "binomial", data = allProp2)
logisRwd <- glm(propComplete ~ factor(Group) + Reward, family = "binomial", data = allProp2)
logisComb <- glm(propComplete ~ factor(Group) + Handling + Reward, family = "binomial", data = allProp2)
logisInt <- glm(propComplete ~ factor(Group) + Handling * Reward, family = "binomial", data = allProp2)
logisIntAll <- glm(propComplete ~ factor(Group) * Handling * Reward, family = "binomial", data = allProp2)

# Quasibinomial GLM versions
logisBase <- glm(propComplete ~ 1, family = "quasibinomial", data = allProp2) # intercept only
logisGroup <- glm(propComplete ~ factor(Group), family = "quasibinomial", data = allProp2) 
logisHand <- glm(propComplete ~ factor(Group) + Handling, family = "quasibinomial", data = allProp2)
logisRwd <- glm(propComplete ~ factor(Group) + Reward, family = "quasibinomial", data = allProp2)
logisComb <- glm(propComplete ~ factor(Group) + Handling + Reward, family = "quasibinomial", data = allProp2)
logisInt <- glm(propComplete ~ factor(Group) + Handling * Reward, family = "quasibinomial", data = allProp2)
logisIntAll <- glm(propComplete ~ factor(Group) * Handling * Reward, family = "quasibinomial", data = allProp2)

# Quasibinomial GLM versions (with proper proportion setup)
totalQuit <- allProp2$totalTrials - allProp2$totalComplete
testBinom <- cbind(allProp2$totalComplete,totalQuit)
logisBase <- glm(testBinom ~ 1, family = "quasibinomial", data = allProp2) # intercept only
logisGroup <- glm(testBinom ~ factor(Group), family = "quasibinomial", data = allProp2) 
logisHand <- glm(testBinom ~ factor(Group) + Handling, family = "quasibinomial", data = allProp2)
logisRwd <- glm(testBinom ~ factor(Group) + Reward, family = "quasibinomial", data = allProp2)
logisComb <- glm(testBinom ~ factor(Group) + Handling + Reward, family = "quasibinomial", data = allProp2)
logisInt <- glm(testBinom ~ factor(Group) + Handling * Reward, family = "quasibinomial", data = allProp2)
logisIntAll <- glm(testBinom ~ factor(Group) * Handling * Reward, family = "quasibinomial", data = allProp2)

# Model selection (with interactions is better)---------- 
## NOTES ON RESULTS

# According to the logistic fit, there are main effects for all predictors, but no interactions. It also says that the overall odds for the wait group to accept versus the effort is around 16%. Similarly, increasing the handling time results in a decrease in the multiplicative odds of ~25%. Increments in reward increase the odds of acceptance by ~40%.

# Results: using handling and rewards as factors decreased the likelihood, so I removed those models 
# For the logistic one, the last meaningful decrease in likelihood happened with logisComb, which also goes against the ANOVA (since no-interactions are significant). I think this model will work best.
# I also double checked this by looking at the progressive deviances. The difference in model deviance (or -2LL of the model) for each pair of models is evaluated using a chi-squared distribution (with df = diff in params). This difference in logs is analogous to a logged division of the likelihoods, which is an LRT (or R-squared), with the null model going in the denominator. Using this in a forward-selection way, I found again that the last model to significantly improve the fit was the logisComb. So, using the null deviance and AIC yielded the same conclusion.
aicLogis <- AIC(logisBase,logisGroup,logisHand,logisRwd,logisComb,logisInt,logisIntAll)
anovaLogis <- anova(logisBase,logisGroup,logisHand,logisRwd,logisComb,logisInt,logisIntAll,test = "Chisq")

# effect size
logisComb$Rsq <- 1 - (logisComb$deviance[1]/200.239) # denominator is the null deviance
```

``` {r,echo=FALSE,fig.align="center",fig.width=4,fig.height=3, fig.cap="AIC values for each model. The model with all main effects was chosen. G = group, H = handling, R = Reward"}
par(mar=c(5.1,2.1,2.1,2.1))    
# plot the deviance for all models
# ver 3
modelLabels <- c('Intercept','G Only','H Only','R Only','G + H + R','G + H * R','G * H * R')
plot(anovaLogis$`Resid. Dev`,
     main = "Residual Deviance for All Models",
     xlab = "",
     ylab = "Res. Deviance",
     pch = 16,
     xaxt = "n")
axis(1,at = 1:7, labels = F)
text(1:7, 
     par("usr")[3] - 22,
     labels = modelLabels, 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)     
```

This showed that all experimental parameters were relevant to the prediction, using either all main effects (AIC = 112) or a handling by reward interaction (AIC = 111). To choose between these two models I used forward selection, comparing each model's deviance with the next. I evaluated the difference in deviance against a ${\chi}^2$ distribution (with df equal to the difference in parameters). This showed that the model with group, handling, and reward as main effects (D = 70.05) was the last to make significant distributions to the prediction (D = 68.8 for the model using a handling by reward interaction). Since this model is also more parsimonious than the one with interactions, I chose it. 
The resulting logistic model showed significant main effect of group as a factor (wait, beta = -1.9, SE = 0.73, p < 0.0001), indicating that the odds of accepting a trial for the wait group are 85% lower than for the effort group (odds are equal to exp(-1.9) = 0.149). I also found a significant main effect of handling time (beta = -0.33, SE = 0.059, p < 0.0001), suggesting that as the handling time increases, the odds of acceptance decrease by 29% (odds = 0.71). Finally, reward amounts also played a significant role in predicting choice (beta = 0.35, SE = 0.069, p < 0.0001), showing that as rewards increase, the odds of acceptance are boosted by 41% (odds = 1.41). 
In order to visualize these results (figure 10), I computed the probability of acceptance for each combination of factors, given by the following equation (with group being either 0 for effort, and 1 for wait):
$${\frac{e^{(\beta_0 + Group*\beta_1 + Handling*\beta_2+Reward*\beta_3)}}{1 + e^{(\beta_0 + Group*\beta_1 + Handling*\beta_2+Reward*\beta_3)}}}$$  
As expected, as the handling time increased, higher rewards were needed to increase the probability of acceptance, regardless of group. Importantly, we can see that the wait group required higher rewards than the effort group to accept a trial regardless of handling time. In the peresent context, the significance of these results is two-fold: First, participants acted as predicted by the first hypothesis, integrating all experimental parameters adequately. Second, they estimated the cost of time to be higher than the effort group did. Figure 10 (right) also shows the residuals from the model, which suggested an overall good fit.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4, fig.cap="Left: Sigmoidal functions depicting the probability of accepting a trial for each group, depicted for each handling-reward combination. Right: Residuals for the chosen model."}
par(mfrow=c(1,2))
## Plotting the winning model--------------------
rewards <- seq(1,25,length = 1000)
# wait
plotLogis(coeffs = logisComb$coefficients,
          handling = 2, 
          reward = rewards, 
          plotType = plot, 
          color = cols[1],
          lType = 6)

plotLogis(coeffs = logisComb$coefficients,
          handling = 10, 
          reward = rewards, 
          color = cols[1],
          lType = 3)

plotLogis(coeffs = logisComb$coefficients,
          handling = 14, 
          reward = rewards, 
          color = cols[1])

# effort
plotLogis(coeffs = logisComb$coefficients,
          group = "Effort",
          handling = 2, 
          reward = rewards, 
          color = cols[2],
          lType = 6)

plotLogis(coeffs = logisComb$coefficients,
          group = "Effort",
          handling = 10, 
          reward = rewards, 
          color = cols[2],
          lType = 3)

plotLogis(coeffs = logisComb$coefficients,
          group = "Effort",
          handling = 14, 
          reward = rewards, 
          color = cols[2])

# title
title("Probabilities for All Handling-Reward Combinations \n for Each Group")

# x axis
xticks <- c(min(rewards[rewards>5]),min(rewards[rewards>10]),25)
axis(1,at = xticks,c(5,10,25))

# legend
legend("bottomright",
       c("Wait: 2s","Wait: 10s","Wait: 14s","Effort: 2s","Effort: 10s","Effort: 14s"), 
       fill = c(cols[1],cols[1],cols[1],cols[2],cols[2],cols[2]),
       lty = rep(c(6,3,1),2),
       cex = 1)

# # actual proportions (maybe, maybe not)
# points(c(5,10,25),trueProp$propComplete[1:3], col = cols[1], pch=17) # wait
# points(c(5,10,25),trueProp$propComplete[4:6], col = cols[1], pch=17)
# points(c(5,10,25),trueProp$propComplete[7:9], col = cols[1], pch=17)
# 
# points(c(5,10,25),trueProp$propComplete[10:12], col = cols[2], pch=17) # effort
# points(c(5,10,25),trueProp$propComplete[13:15], col = cols[2], pch=17)
# points(c(5,10,25),trueProp$propComplete[16:18], col = cols[2], pch=17)

# and the residuals--------------------------
plot(logisComb$residuals,
     main = "Residuals for the Logistic Regression",
     xlab = "trial",
     ylab = "Residuals")
# -------------------------------------------
```

#### Sequential effects
Finally, I was curious whether there were sequential effects. One could think that quitting too many times consecutively would increase the probability of accepting any reward (in fear of skipping too much and lowering the amount of points they get overall). I checked for this possibility by creating a vector with the number of consecutive quits that happened before each trial, and used it as a predictor in a binomial GLM. This auto-regressive process was performed on each subject separately, using choice (a set of Bernoulli random variables, quit = 0, accept = 1) as the dependent variable and the quit-run vector as a predictor. 
While sequential quits were significantly predictive of choice for a couple of subjects (p < 0.05), the effect sizes were minimal. Deviances barely changed, if at all, and none of them were significantly reduced the null deviance (evaluated under a ${\chi}^2$ distribution). This indicates that previous trials had little bearing on choices. Instead, as seen above, participants focused mainly on the experimental parameters.

``` {r,echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
# auto-regressive process?  
# for that, an lm() would have to contain choice data and its lags at -1, -2, -x. Let's see...
# model <- lm(choice ~ (choice lag - 1) + (choice lag - 2) + ... (choice lag - x))
# better to use (per subject) arima(waitData[[1]]$Choice, order = c(2,0,0)) # the last zeros indicate no moving average process.
# you get AIC and likelihoods with these, and thus can run model selection with different autoregressive lags.
# also, the coefficients and s.e. work just like with linear models, so that beta/se gives a z statistic that can be evaluated against the null of 0.
# plot with pacf or acf (they looked the same to me: but acf starts with autocorrelation of 1, which is always 1)

# BIG NOTE: This is for ys with gaussian noise (or continuous), for discrete data we should just use the GLM for our purposes. 
# However, Dan said that the GLM approach should be fine, since it's imposing the betas of each lag onto each other. Should try using individual predictors for each lag, but meh...

# store the models, so each subject's can be summarized
quitModelsW <- list()
quitModelsC <- list()

for (i in 1:nSubs){

    # subject data (y)
    yW <- waitData[[i]]$Choice
    yC <- cogData[[i]]$Choice

    # lag data (x predictors)
    xW <- seqQuits(yW)
    xC <- seqQuits(yC)

    # models
    quitModelsW[[i]] <- glm(yW ~ xW, family = "binomial")
    quitModelsC[[i]] <- glm(yC ~ xC, family = "binomial")

}

  # Result notes: while a couple of participants had significant p-values, the effect sizes are tiny. Deviance barely moves. That means that the odds of acceptance are independent of how many trials they quit before the current trial. No reason to add it as a covariante in the linear models, but it's worth talking about it.

```
### Conclusion

In this project I investigated the possible value-discounting effects of cognitive effort and passive delay. I utilized data from a modified foraging task, in which participants decided whether to accept or skip a rewarding trial based on the richness of the environment. The original hypothesis stated that having to perform cognitive tasks during the delay would be extra aversive, making participants estimate the opportunity cost of time as higher than it truly is. However, the present findings demonstrate that effort might not always discount the value of a reward, although it nonetheless affects a subject’s ability to evaluate rewards.
My results suggest that performing cognitive tasks while waiting for a reward facilitates optimality in short delays, whereas passive waiting promotes it during long intervals. In general, participants that performed tasks had a marked tendency to over-accept rewards, even when the choice was detrimental to their overall earning rate. This is contrary to our original hypothesis, and perhaps counterintuitive in the presence of previous literature (Kool et al., 2010). Although the present data does not provide further insights into why this might be, there are some ideas that might account for this behavior. One reason could be that participants are motivated to complete trials due to their accurate performance in the cognitive tasks. Such effects have been reported before under the name of ‘learned industriousness’ (Eisenberger & Cameron, 1996). In addition, the tasks themselves might have proven entertaining, and thus intrinsically rewarding. Such an effect could also contribute to a misinterpretation of the trial-wise elapsed time. In other words, our foraging experiment might have accidentally captured the notion that time goes by faster when you are busy. Notably, supervised training and self-reported strategies argue against the possibility of the effort group being unable to act optimally due to task distractions. Before/after break performance, response time, and optimality analyses also help us discard distraction effects.
Some limitations remain to be addressed. For example, the fact that participants immediately experienced each condition could limit the scope of our results. Discounting effects are known to vary in magnitude depending on the relative temporal position of the options, especially when they are far into the future (Green et al., 1994). Another shortcoming is the lack of monetary rewards. It is possible that participants were not motivated enough by earning points. Perhaps more importantly, comparing effortful and passive waiting between subjects does not give us a full picture of their relative costs. In the future, this task will give each subject the option to forage through both conditions. In addition, a measure of physical activity (e.g. hand grip) will be included in order to further tease apart the relative cost of time and effort (the study’s original plan). First, however, I will replicate the current study, this time using monetary rewards. While the current results look promising, it is important to remember that this was a minimally-sampled pilot study, which limits its power. Perhaps more importantly, even with sufficient power and low p-values, the current study still risks a high false positive rate if the prior odds of finding this difference are against the alternative hypothesis (Benjamin et al., 2017; Nuzzo, 2014). This is a complicated issue to solve at the moment, especially since the present findings go against a literature that expects cognitive effort to provoke fewer responses than passive delays. Despite these limitations, the current behavioral task was geared to provide a baseline of the cost of each discounting type, thus giving us a reference that can guide future within-subject manipulations.
The ongoing study has broad implications for understanding cost. First, discriminating between cost features can have fruitful clinical applications, helping us better understand motivational dysfunctions associated with mood disorders (Westbrook & Braver, 2015). Second, by incorporating both physical and cognitive effort in the context of time for the first time, it provides an opportunity to determine the specific influence of each type of effort in discounting value. This result can directly benefit fields such as economics and learning theory, particularly by clarifying the extent to which physical and mental effort can be interchangeably used in studies of valuation.

### References
Ainslie, G. (1975). Specious Reward: A Behavioral Theory of Impulsiveness and Impulse Control.  Psych Bull,  82: 463-496.

Apps, M. A. J., Grima, L. L., Manohar, S., & Husain, M. (2015). The role of cognitive effort in subjective reward devaluation and risky decision-making.  Scientific Reports ,  5 , 16880. https://doi.org/10.1038/srep16880

Benjamin, D. J., Berger, J. O., Johannesson, M., Nosek, B. A., Wagenmakers, E. J., Berk, R., ... & Cesarini, D. (2017). Redefine statistical significance. Nature Human Behaviour, 1.

Botvinick, M., Huffstetler, S., & McGuire, J. T. (2009). Effort discounting in human nucleus accumbens.  Behavioural Neuroscience ,  9 (1), 22. https://doi.org/10.3758/CABN.9.1.16.Effort

Constantino, S. M., & Daw, N. D. (2015). Learning the opportunity cost of time in a patch-foraging task.  Cognitive, Affective & Behavioral Neuroscience ,  15 (4), 837–53. https://doi.org/10.3758/s13415-015-0350-y

Eisenberger, R., & Cameron, J. (1996). Detrimental effects of reward. Reality or myth?  The American Psychologist ,  51 (11), 1153–1166. https://doi.org/10.1037/0003-066X.51.11.1153

Frederick, S., Loewenstein, G., & O ’donoghue, T. (2002). Time Discounting and Time Preference: A Critical Review.  Journal of Economic Literature Time Discounting Journal of Economic Literature ,  XL XL , 351–401.

Green, L., Fristoe, N., & Myerson, J. (1994). Temporal discounting and preference reversals in choice between delayed outcomes.  Psychonomic Bulletin & Review ,  1 (3), 383–389.

Hosking, J. G., Floresco, S. B., & Winstanley, C. A. (2014). Dopamine Antagonism Decreases Willingness to Expend Physical, But Not Cognitive, Effort: A Comparison of Two Rodent Cost&sol;Benefit Decision-Making Tasks.  Neuropsychopharmacology ,  40 (10). https://doi.org/10.1038/npp.2014.285

Kool, W., McGuire, J. T., Rosen, Z. B., & Botvinick, M. M. (2010). Decision Making and the Avoidance of Cogntive Demand.  Journal of Experimental Psychology: General ,  139 (4), 665–682. https://doi.org/10.1037/a0020198.Decision

Kurniawan, I. T., Guitart-Masip, M., & Dolan, R. J. (2011). Dopamine and effort-based decision making.  Frontiers in Neuroscience . https://doi.org/10.3389/fnins.2011.00081

Massar, S. A. A., Libedinsky, C., Weiyan, C., Huettel, S. A., & Chee, M. W. L. (2015). Separate and overlapping brain areas encode subjective value during delay and effort discounting. NeuroImage,  120(2015): 104-113. https://doi.org/10.1016/j.neuroimage.2015.06.080

Mcclure, S. M., Ericson, K. M., Laibson, D. I., Loewenstein, G., & Cohen, J. D. (2004). Behavioral/Systems/Cognitive Time Discounting for Primary Rewards.  Science,  306: 503-507. https://doi.org/10.1523/JNEUROSCI.4246-06.2007

Nuzzo, R. (2014). Statistical errors. Nature, 506(7487), 150.

Prévost, C., Pessiglione, M., Météreau, E., Cléry-Melin, M.-L., & Dreher, J.-C. (2010). Behavioral/Systems/Cognitive Separate Valuation Subsystems for Delay and Effort Decision Costs.  Journal of Neuroscience,  30(42):14080-14090. https://doi.org/10.1523/JNEUROSCI.2752-10.2010

Richardson, N. R., & Roberts, D. C. S. (1996). Progressive ratio schedules in drug self-administration studies in rats: A method to evaluate reinforcing efficacy.  Journal of Neuroscience Methods ,  66 (1), 1–11. https://doi.org/10.1016/0165-0270(95)00153-0

Schmidt, L., Lebreton, M., Cléry-Melin, M. L., Daunizeau, J., & Pessiglione, M. (2012). Neural mechanisms underlying motivation of mental versus physical effort.  PLoS Biology,  10: e1001266. https://doi.org/10.1371/journal.pbio.1001266

Schultz, W. (2015). Neuronal Reward and Decision Signals: From Theories to Data.  Physiol Rev , (95), 853–951.

Walton, M. E., Kennerley, S. W., Bannerman, D. M., Phillips, P. E. M., & Rushworth, M. F. S. (2006). Weighing up the benefits of work: Behavioral and neural analyses of effort-related decision making.  Neural Networks,  19(2006): 1302-1314. https://doi.org/10.1016/j.neunet.2006.03.005

Westbrook, A., & Braver, T. S. (2015). Cognitive effort: A neuroeconomic approach.  Cogn Affect Behav Neurosci,  15: 395-415. https://doi.org/10.3758/s13415-015-0334-y

Westbrook, A., Kester, D., & Braver, T. S. (2013). What Is the Subjective Cost of Cognitive Effort? Load, Trait, and Aging Effects Revealed by Economic Preference.  PLoS ONE,  8: e68210. https://doi.org/10.1371/journal.pone.0068210

### 2018-10-11 moveData.sh

@@ -1,0 +1,23 @@
+#!bin/bash/
+
+# Move data from lab_tasks to where I'm doing analyses
+dataDir='/Users/ctoro/git_clones/lab_tasks/Claudio/Replication_2018'
+analDir='/Users/ctoro/git_clones/R/MA681/MA681_Final/data'
+
+# Cognitive effort
+cp ${dataDir}/cog/data/*_log.csv ${analDir}/cog
+rm -f ${analDir}/cog/attention*
+
+# Easy effort
+cp ${dataDir}/pheasycal/data/*_log.csv ${analDir}/easy
+rm -f ${analDir}/easy/attention*
+rm -f ${analDir}/easy/*_calibration_log.csv
+
+# Physical effort
+cp ${dataDir}/phys/data/*_log.csv ${analDir}/phys
+rm -f ${analDir}/phys/attention*
+rm -f ${analDir}/phys/*_calibration_log.csv
+
+# Passive delay
+cp ${dataDir}/wait/data/*_log.csv ${analDir}/wait
+rm -f ${analDir}/wait/attention*

### 2018-10-11 Cost2_prereg.Rmd
Cleaning up code and improving figures

@@
 lbls <- c("Wait","Cognitive","Physical","Easy")
-cols = c("#78AB05","#D9541A","deepskyblue4", "grey50") # plot colors (wait, effort)
+cols = c("#78AB05","#D9541A","deepskyblue4", "darkgoldenrod2") # plot colors (wait, effort)
 lthick = 2 # line thickness for plots
@@
 # load cognitive effort group
-setwd('/Volumes/Addon/Grad school/Cost2_data/cog')
+setwd('./data/Cost2_data/cog')
 temp = list.files(pattern="*.csv")
@@
     scale_fill_manual(values = cols) +
+    ylim(c(0,1)) +
     labs(title = "Proportion Completed by Group", y="Proportion Completed") +
@@
 # This is in case you don't want to plot the easy condition (easier to see)
+cols = c("#78AB05","#D9541A","deepskyblue4", "grey50")
 trueProp2 <- trueProp[-(28:36), ]
@@
         geom_line(aes(group = interaction(Handling, Group)), size=1) +
-        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey48", color = "grey48", size = 3, show.legend = F) +
+        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
         labs(x = "Reward.Handling", y = "Proportion Accepted", title = "Proportion Accepted per Handling and Reward Combination") +
@@
 
-``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
+``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
 # RTs
 # let's try to do some survival curves
-RTW <- numeric() # vector of all decision-related RTs for the wait group
-RTC <- numeric() # same for the cog group
-RTP <- numeric()
-RTE <- numeric()
-
-# Wait group
-for (subj in seq(nSubsW)){
-
-    # index for trials quit
-    tempChoiceW <- waitData[[subj]]$Choice == 0
-
-    # concatenate the subject RT to the group
-    RTW <- c(RTW,waitData[[subj]]$RT[tempChoiceW])
-
-}
-
-# Cognitive group
-for (subj in seq(nSubsC)){
-
-    # index for trials quit
-    tempChoiceC <- cogData[[subj]]$Choice == 0
-
-    # concatenate the subject RT to the group
-    RTC <- c(RTC,cogData[[subj]]$`Choice RT`[tempChoiceC])
-
-}
-
-# Physical group
-for (subj in seq(nSubsP)){
-
-    # index for trials quit
-    tempChoiceP <- physData[[subj]]$Choice == 0
-
-    # concatenate the subject RT to the group
-    RTP <- c(RTP,physData[[subj]]$RT[tempChoiceP])
-
-}
-
-# Pheaysical group
-for (subj in seq(nSubsE)){
-
-    # index for trials quit
-    tempChoiceE <- easyData[[subj]]$Choice == 0
-
-    # concatenate the subject RT to the group
-    RTE <- c(RTE,easyData[[subj]]$RT[tempChoiceE])
-
-}
-
-# create an array with both data (for surv fit autoplot trials)
-lenC <- length(RTC)
-lenW <- length(RTW)
-lenP <- length(RTP)
-lenE <- length(RTE)
-
-RTgroups <- c(rep("Wait",lenW), 
-              rep("Effort",lenC), 
-              rep("Physical",lenP),
-              rep("Easy",lenE))
+RTW <- unlist(lapply(waitData, function(data) {data$RT[data$Choice==0]})) # vector of all decision-related RTs for the wait group
+RTC <- unlist(lapply(cogData, function(data) {data$`Choice RT`[data$Choice==0]})) # same for the cog group
+RTP <- unlist(lapply(physData, function(data) {data$RT[data$Choice==0]}))
+RTE <- unlist(lapply(easyData, function(data) {data$RT[data$Choice==0]}))
+
+# create a data frame for plotting
+RTgroups <- c(rep("Wait",length(RTW)), rep("Effort",length(RTC)), rep("Physical",length(RTP)), rep("Easy",length(RTE)))
 RTall <- c(RTW,RTC,RTP,RTE)
-
-# plot ecdf 
-ecdfW <- ecdf(RTW)
-ecdfC <- ecdf(RTC)
-ecdfP <- ecdf(RTP)
-ecdfE <- ecdf(RTE)
-
-range <- seq(0,10, by = 0.001)
-
-plot(range,ecdfW(range),
-     type = "l",
-     main = "ECDF and CIs for the Response Times",
-     xlab = "Seconds",
-     ylab = "ECDF",
-     xlim = c(0,5),
-     col = cols[1],
-     bty = "n",
-     lwd = lthick)
-lines(range,
-      ecdfC(range),
-      col = cols[2],
-      lwd = lthick)
-lines(range,
-      ecdfP(range),
-      col = cols[3],
-      lwd = lthick)
-lines(range,
-      ecdfE(range),
-      col = cols[4],
-      lwd = lthick)
-legend("right",
-       lbls,
-       fill = cols,
-       cex = 0.8)
-
-# and CIs for each (unnecessary unless I end up plotting)
-CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
-CIC <- median(CIC) - (quantile(CIC,0.025))
-CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-CIW <- median(CIW) - (quantile(CIW,0.025))
-CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-CIP <- median(CIP) - (quantile(CIP,0.025))
-CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-CIE <- median(CIE) - (quantile(CIE,0.025))
-lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
-lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
-lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
-lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
-lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
-lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
-lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
-lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)
-
-# just cause, Kolmogrov-Smirnov 
-# ksRT <- ks.test(RTW,RTC)
-# RTPerm <- permute(RTW,RTC)
-# RTCohen <- cohenD(RTW,RTC)
-
-rm(lenC,lenW,lenP,lenE)
+RTframe <- data.frame(RTgroups, RTall)
+
+# plot
+ggplot(RTframe, aes(RTall, color = RTgroups)) + 
+  stat_ecdf(lwd = 1) + 
+  scale_color_manual(values = cols) + 
+  scale_x_continuous(breaks = seq(14)) +
+  labs(title = "ECDFs for the Response Times", x = "Seconds", y = "ECDF") +
+  theme_classic()
+
+# # and CIs for each (unnecessary unless I end up plotting)
+# CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
+# CIC <- median(CIC) - (quantile(CIC,0.025))
+# CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
+# CIW <- median(CIW) - (quantile(CIW,0.025))
+# CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
+# CIP <- median(CIP) - (quantile(CIP,0.025))
+# CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
+# CIE <- median(CIE) - (quantile(CIE,0.025))
+# lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
+# lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
+# lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
+# lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
+# lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
+# lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
+# lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
+# lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)
 

### 2018-11-20 Cost2/Cost2_prereg.Rmd
Rearranging files and fixed analysis 16.2.1

--- 2018-10-11 Cost2_prereg.Rmd
@@
 output:
+  pdf_document: default
   html_document: default
+  fig_caption: yes
   word_document: default
-  fig_caption: yes
 ---
@@
 
-  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample (*one-sample?
-wouldn't it be paired vs optimal?*) t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
+  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances-either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
 This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*
@@
 # Perform a paired t-test on every combination of parameters
-splitData_tests <- sapply(splitData, function(data) t.test(data$propComplete, data$Optimal, paired = T)$p.value)
+# Given that 20 cent rewards demand constant acceptances, we expect the proportions to be constant for these choices
+# This gives an error in the t.test due to the lack of variability and normal errors, so we use try to bypass this issue
+splitData_tests <- sapply(splitData, function(data) try(t.test(data$propComplete, mu = unique(data$Optimal))$p.value))
 
@@
 trueProp$Deviation_pval <- round(p.adjust(splitData_tests, method = "BY"), digits = 2)
-trueProp$Deviation_pval[is.nan(trueProp$Deviation_pval)] <- 1
+trueProp$Deviation_pval[is.na(trueProp$Deviation_pval)] <- 1
 # trueProp[trueProp$Deviation_pval < 0.05, ]
@@
 Of the 36 tests, around `r splitData_prop` were significantly deviant from optimality.
-Most of these were from effortful groups, as the wait group just showed deviations for 2 seconds handling/4 cent, and 10 seconds handling/8 cent offers (note to self: think about a way to properly .
+Most of these were from effortful groups, as the wait group just showed deviations for 2 seconds handling/4 cent, and 10 seconds handling/8 cent offers (note to self: think about a way to properly visualize these).
 
@@
 
-The analysis of variance was significant (F = `r round(Fval, digits = 2)`, p = `r Pval`, R-squared = `r Rsquared_aov`).
-Pairwise post-hoc permutations showed significantly greater values for the wait group versus the cognitive (p = `r permuteOCTest$WvC$Pval`) and easy (p = `r permuteOCTest$WvE$Pval`) groups, as well as significantly greater gammas for the physical group and the cognitive group (p = `r permuteOCTest$CvP$Pval`).
+The analysis of variance was significant (F = `r round(Fval, digits = 2)`, p = `r ifelse(Pval < 0.001, "< 0.001", paste("=", round(Pval, digits = 2)))`, R-squared = `r Rsquared_aov`).
+Pairwise post-hoc permutations showed significantly greater values for the wait group versus the cognitive (p = `r ifelse(permuteOCTest$WvC$Pval < 0.001, "< 0.001", paste("=", round(permuteOCTest$WvC$Pval, digits = 2)))`) and easy (p = `r ifelse(permuteOCTest$WvE$Pval < 0.001, "< 0.001", paste("=", round(permuteOCTest$WvE$Pval, digits = 2)))`) groups, as well as significantly greater gammas for the physical group and the cognitive group (p = `r ifelse(permuteOCTest$CvP$Pval < 0.001, "< 0.001", paste("=", round(permuteOCTest$CvP$Pval, digits = 2)))`).
 These results suggest that participants engaged in cognitively effortful demands experience significantly lower opportunity costs than those whose demands involve physical effort and pure delay.

### 2019-01-04 Cost2/Cost2_prereg.Rmd
small typos corrected on prereg for cost 2

@@
 coeffsEarn <- lmEarn$coefficients
-summaryData$tempLine <- seq(0,1,length=84) # for plotting
+summaryData$tempLine <- seq(0,1,length=totalSubs) # for plotting
 summaryData$earnFitLine <- coeffsEarn[1] + coeffsEarn[2]*summaryData$tempLine + coeffsEarn[3]*(summaryData$tempLine^2)
@@
 The gamma optimization search space was bound by extreme choice values.
-For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 25/2).
+For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
 Conversely, a participant experiencing low opportunity costs would accept the unbeneficial offer of 4 cents for a 14 second delay (or 4/14).

### 2019-04-24 Cost2/Cost2_prereg.Rmd
adjusting spacing of code

@@
 # params for reference
-handling <- c(2,10,14)
-cond <- c("Wait","Cognitive","Physical","Easy")
+handling <- c(2, 10, 14)
+cond <- c("Wait", "Cognitive", "Physical", "Easy")
 
@@
 
-colnames(summaryData) <- c("Group","propComplete","Earnings","RT","forcedTravel")
+colnames(summaryData) <- c("Group", "propComplete", "Earnings", "RT", "forcedTravel")
 

### 2019-04-25 Cost2/Cost2_prereg_remake.Rmd
overhaul of cost 2 prereg RMD, plus data cleaning/update

--- 2019-04-24 Cost2/Cost2_prereg.Rmd
@@
 output:
+  html_document: default
   pdf_document: default
-  html_document: default
   fig_caption: yes
@@
 ### data loading and cleaning up
-
-# load cognitive effort group
-setwd('./data/Cost2_data/cog')
-temp = list.files(pattern="*.csv")
-cogDataLong = lapply(temp, read.csv, header = FALSE)
-
-# load wait group
-setwd('../wait')
-temp = list.files(pattern="*.csv")
-waitDataLong = lapply(temp, read.csv, header = FALSE)
-
-# load physical group
-setwd('../phys')
-temp = list.files(pattern="*.csv")
-physDataLong = lapply(temp, read.csv, header = FALSE)
-
-# load pheasysical group
-setwd('../easy')
-temp = list.files(pattern="*.csv")
-easyDataLong = lapply(temp, read.csv, header = FALSE)
+setwd("./data")
+files <- dir(pattern = '_log.csv')
+nSubjs <- length(files)
+
+dataAll <- data_frame(SubjID = files) %>%
+  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
+  mutate(Cost = substring(SubjID, 5, 8),
+         Cost = case_when(Cost == "wait" ~ "Wait",
+                          Cost == "cogT" ~ "Cognitive",
+                          Cost == "phys" ~ "Physical",
+                          Cost == "phea" ~ "Easy"),
+         SubjID = substring(SubjID, 0, 3)) %>%
+  unnest() %>%
+  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"))
+
+# # load cognitive effort group
+# setwd('./data/Cost2_data/cog')
+# temp = list.files(pattern="*.csv")
+# cogDataLong = lapply(temp, read.csv, header = FALSE)
+# 
+# # load wait group
+# setwd('../wait')
+# temp = list.files(pattern="*.csv")
+# waitDataLong = lapply(temp, read.csv, header = FALSE)
+# 
+# # load physical group
+# setwd('../phys')
+# temp = list.files(pattern="*.csv")
+# physDataLong = lapply(temp, read.csv, header = FALSE)
+# 
+# # load pheasysical group
+# setwd('../easy')
+# temp = list.files(pattern="*.csv")
+# easyDataLong = lapply(temp, read.csv, header = FALSE)
 
@@
 nSubsE <- length(easyDataLong)
-totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE) # why didn't I think of this before...
+totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE)
 

### 2019-04-25 Cost2/Cost2_prereg_remake.Rmd
block-wise prop accepted plot

@@
                           Cost == "phea" ~ "Easy"),
+         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
          SubjID = substring(SubjID, 0, 3)) %>%
@@
 
-# Another approach
-# This will just plot the density of the completed trials before/after, trying to get at the possible fatigue experienced in the physical effort condition.
-# Response patterns for each subject look pretty similar, with adequate optimality adaptation.
-#
-# for (i in 1:nSubs){
-# plot(density(which(physBefore[[i]]$Choice==1)),
-#      main = paste("Choices in time, before and after for subject:",i),
-#      xlab = "Trials (completed)")
-# lines(density(which(physAfter[[i]]$Choice==1)), col = "red")
-# }
+# dataAll %>%
+#   filter(Choice < 2) %>%
+#   group_by(SubjID) %>%
+#   #mutate(Block = do.call(c, lapply(c(2,4,6), function(x) {rep(x/2, sum(Block %in% c(x-1, x)))}))) %>%
+#   group_by(SubjID, Cost, Block) %>%
+#   summarise(propAccept_subj = mean(Choice)) %>%
+#   group_by(Cost, Block) %>%
+#   summarize(propAccept = mean(propAccept_subj),
+#             seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
+#   ggplot(aes(Block, propAccept, fill = Cost)) +
+#     geom_point(size = 2, pch = 21, color = "black") +
+#     geom_errorbar(aes(ymin=propAccept - seAccept, ymax=propAccept + seAccept, color = Cost), width = 0.1) +
+#     geom_line(aes(color = Cost)) +
+#     ylim(0.5, 1) +
+#     scale_x_continuous(breaks = seq(6)) +
+#     scale_color_manual(values = cols) +
+#     scale_fill_manual(values = cols) +
+#     theme_classic()
 ```

### 2019-04-26 Cost2/Cost2_prereg_remake.Rmd
updated cog logs to match the rest (similar to cost 3 too)

@@
 
-dataAll <- data_frame(SubjID = files) %>%
+dataAll <- tibble(SubjID = files) %>%
   mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
@@
 
+subjList <- unique(dataAll$SubjID)
 # # load cognitive effort group

### 2019-05-06 Cost2/Cost2_prereg_remake.Rmd
re-writing the code for Cost2 to make it shorter. At 16.1.3 right now

@@
 \bigskip
+
+## Analyses
 
@@
 subjList <- unique(dataAll$SubjID)
-# # load cognitive effort group
-# setwd('./data/Cost2_data/cog')
-# temp = list.files(pattern="*.csv")
-# cogDataLong = lapply(temp, read.csv, header = FALSE)
-# 
-# # load wait group
-# setwd('../wait')
-# temp = list.files(pattern="*.csv")
-# waitDataLong = lapply(temp, read.csv, header = FALSE)
-# 
-# # load physical group
-# setwd('../phys')
-# temp = list.files(pattern="*.csv")
-# physDataLong = lapply(temp, read.csv, header = FALSE)
-# 
-# # load pheasysical group
-# setwd('../easy')
-# temp = list.files(pattern="*.csv")
-# easyDataLong = lapply(temp, read.csv, header = FALSE)
-
-### cleaning data
-# this will generate a simple list with only info about trials that participants quit or completed
-# this is because cognitive logs also include within-trial task-specific information
-# for the wait condition, it will get rid of the break indicator
-
-nSubsW <- length(waitDataLong)
-nSubsC <- length(cogDataLong)
-nSubsP <- length(physDataLong)
-nSubsE <- length(easyDataLong)
-totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE)
-
-#  short lists
-cogData <- list()
-waitData <- list()
-physData <- list()
-easyData <- list()
-
-# For pre-post analysis
-cogBefore <- list()
-cogAfter <- list()
-waitBefore <- list()
-waitAfter <- list()
-physBefore <- list()
-physAfter <- list()
-easyBefore <- list()
-easyAfter <- list()
-
-# clean wait group data
-for (subject in seq(nSubsW)){
-
-  # Before/after
-  breakW <- which(waitDataLong[[subject]]$V1 == 0)
-
-  waitBefore[[subject]] <- waitDataLong[[subject]][1:(breakW - 1),]
-  waitAfter[[subject]] <- waitDataLong[[subject]][(breakW + 1):length(waitDataLong[[subject]]$V1),]
-
-  # assign header names
-  colnames(waitBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-  colnames(waitAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-  # Overall data cleaning
-  tempW <- waitDataLong[[subject]]$V1 != 0
-
-  # create a new list with only decision trials / without break
-  waitData[[subject]] <- waitDataLong[[subject]][tempW,]
-
-  # assign header names
-  colnames(waitData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-}
-
-# clean cognitive group data
-for (subject in seq(nSubsC)){
-
-  # Before/After
-  breakC <- which(cogDataLong[[subject]]$V1 == 0)
-
-  cogBefore[[subject]] <- cogDataLong[[subject]][1:(breakC-1),]
-  temp <- cogBefore[[subject]]$V7 # trial outcome vector
-  quitTrials <- grep("Quit",temp)
-  completeTrials <- grep("Reward",temp)
-  decisionTrials <- sort(c(quitTrials,completeTrials))
-  cogBefore[[subject]] <- cogBefore[[subject]][decisionTrials,]
-
-  cogAfter[[subject]] <- cogDataLong[[subject]][(breakC+1):length(cogDataLong[[subject]]$V1),]
-  temp <- cogAfter[[subject]]$V7 # trial outcome vector
-  quitTrials <- grep("Quit",temp)
-  completeTrials <- grep("Reward",temp)
-  decisionTrials <- sort(c(quitTrials,completeTrials))
-  cogAfter[[subject]] <- cogAfter[[subject]][decisionTrials,]
-
-  colnames(cogBefore[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
-                                      "Experiment Time","Trial Outcome","Task Type","Task Setup")
-  colnames(cogAfter[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
-                                     "Experiment Time","Trial Outcome","Task Type","Task Setup")
-
-  # Overall data cleaning
-  # create an index for the trials in which a decision was made (completed, quit) 
-  temp <- cogDataLong[[subject]]$V7 # trial outcome vector
-  quitTrials <- grep("Quit",temp)
-  completeTrials <- grep("Reward",temp)
-  decisionTrials <- sort(c(quitTrials,completeTrials))
-
-  # create a new list with only decision trials / without break
-  tempC <- cogDataLong[[subject]]$V1 != 0  
-  cogData[[subject]] <- cogDataLong[[subject]][decisionTrials,]
-  cogDataLong[[subject]] <- cogDataLong[[subject]][tempC,]
-
-  colnames(cogData[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
-                                    "Experiment Time","Trial Outcome","Task Type","Task Setup")
-  colnames(cogDataLong[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
-                                        "Experiment Time","Trial Outcome","Task Type","Task Setup") # Long contains within-trial info
-
-}
-
-# clean physical group data
-for (subject in seq(nSubsP)){
-
-  # Before/After
-  breakP <- which(physDataLong[[subject]]$V1 == 0)
-
-  physBefore[[subject]] <- physDataLong[[subject]][1:(breakP - 1),]
-  physAfter[[subject]] <- physDataLong[[subject]][(breakP + 1):length(physDataLong[[subject]]$V1),]
-
-  colnames(physBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-  colnames(physAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-  # create a new list with only decision trials / without break  
-  tempP <- physDataLong[[subject]]$V1 != 0
-  physData[[subject]] <- physDataLong[[subject]][tempP,]
-  colnames(physData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-}
-
-# clean pheaysical group data
-for (subject in seq(nSubsE)){
-
-  # Before/After
-  breakE <- which(easyDataLong[[subject]]$V1 == 0)
-
-  easyBefore[[subject]] <- easyDataLong[[subject]][1:(breakE - 1),]
-  easyAfter[[subject]] <- easyDataLong[[subject]][(breakE + 1):length(easyDataLong[[subject]]$V1),]
-
-  colnames(easyBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-  colnames(easyAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-  # create a new list with only decision trials / without break  
-  tempE <- easyDataLong[[subject]]$V1 != 0
-  easyData[[subject]] <- easyDataLong[[subject]][tempE,]
-  colnames(easyData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-}
-
-# Combine before/after across subjects
-cBefore <- rbind(cogBefore[[1]],cogBefore[[2]]) 
-cAfter <- rbind(cogAfter[[1]],cogAfter[[2]]) 
-wBefore <- rbind(waitBefore[[1]],waitBefore[[2]]) 
-wAfter <- rbind(waitAfter[[1]],waitAfter[[2]]) 
-pBefore <- rbind(easyBefore[[1]],physBefore[[2]])
-pAfter <- rbind(physAfter[[1]],physAfter[[2]])
-eBefore <- rbind(easyBefore[[1]],easyBefore[[2]])
-eAfter <- rbind(easyAfter[[1]],easyAfter[[2]])
-
-for (i in 3:nSubsW){
-
-    wBefore <- rbind(wBefore,waitBefore[[i]])
-    wAfter <- rbind(wAfter,waitAfter[[i]])
-
-}
-
-for (i in 3:nSubsC){
-
-    cBefore <- rbind(cBefore,cogBefore[[i]])  
-    cAfter <- rbind(cAfter,cogAfter[[i]])
-
-}
-
-for (i in 3:nSubsP){
-
-    pBefore <- rbind(pBefore,physBefore[[i]])
-    pAfter <- rbind(pAfter,physAfter[[i]])
-
-}
-
-for (i in 3:nSubsE){
-
-    eBefore <- rbind(eBefore,easyBefore[[i]])
-    eAfter <- rbind(eAfter,easyAfter[[i]])
-
-}
-
-#rm(cogBefore,cogAfter,waitBefore,waitAfter)
-
-# aggregate ADD PHYS
-waitBeforeAll <- aggregate(wBefore$Choice,
-          by = list(wBefore$Reward, wBefore$Handling),
-          FUN = 'mean')
-waitAfterAll <- aggregate(wAfter$Choice,
-          by = list(wAfter$Reward, wAfter$Handling),
-          FUN = 'mean')
-cogBeforeAll <- aggregate(cBefore$Choice,
-          by = list(cBefore$Reward, cBefore$Handling),
-          FUN = 'mean')
-cogAfterAll <- aggregate(cAfter$Choice,
-          by = list(cAfter$Reward, cAfter$Handling),
-          FUN = 'mean')
-physBeforeAll <- aggregate(pBefore$Choice,
-          by = list(pBefore$Reward, pBefore$Handling),
-          FUN = 'mean')
-physAfterAll <- aggregate(pAfter$Choice,
-          by = list(pAfter$Reward, pAfter$Handling),
-          FUN = 'mean')
-easyBeforeAll <- aggregate(eBefore$Choice,
-          by = list(eBefore$Reward, eBefore$Handling),
-          FUN = 'mean')
-easyAfterAll <- aggregate(eAfter$Choice,
-          by = list(eAfter$Reward, eAfter$Handling),
-          FUN = 'mean')
-
-rm(cBefore,cAfter,wBefore,wAfter, pBefore, pAfter, eBefore, eAfter)
-
-# remove unnecessary variables
-rm(temp,tempW,tempC,quitTrials,completeTrials,decisionTrials,subject)
+
 ```
@@
 ``` {r Basic Prepping, echo=FALSE}  
-# params for reference
-handling <- c(2, 10, 14)
-cond <- c("Wait", "Cognitive", "Physical", "Easy")
-
-# create data frame with summary stats
-tempW <- summarizeData()
-tempC <- summarizeData(Data = cogData, nSubs = nSubsC, type = "Cognitive")
-tempP <- summarizeData(Data = physData, nSubs = nSubsP, type = "Physical")
-tempE <- summarizeData(Data = easyData, nSubs = nSubsE, type = "Easy")
-
-summaryData <- rbind(tempW,
-                     tempC,
-                     tempP,
-                     tempE)
-
-colnames(summaryData) <- c("Group", "propComplete", "Earnings", "RT", "forcedTravel")
-
-summaryData$Cols <- c(rep(cols[1],nSubsW), rep(cols[2],nSubsC), rep(cols[3],nSubsP), rep(cols[4],nSubsE))
-rm(tempW, tempC, tempP, tempE)
-
-# Indexes for groups
-indxWait <- seq(nSubsW)
-indxWaitLong <- seq(nSubsW * 9) # 9 being the number of combinations
-indxCog <- (nSubsW + 1):(nSubsW + nSubsC)
-indxCogLong <- ((nSubsW * 9) + 1):((nSubsW * 9) + (nSubsC * 9))
-indxPhys <- ((nSubsW + nSubsC) + 1):(nSubsW + nSubsC + nSubsP)
-indxPhysLong <- ((nSubsW * 9) + (nSubsC * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9))
-indxEasy <- ((nSubsW + nSubsC + nSubsP) + 1):totalSubs #(nSubsW + nSubsC + nSubsP + nSubsE)
-indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))
-
-# the other, just summarizing for all participants
-# Not sure if this is necessary anymore
-# allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
-#                                 rep("Cognitive",nSubsC*3),
-#                                 rep("Physical",nSubsP*3)),
-#                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
-#                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
-#                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
-#                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
-#                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
-#                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))
-
-# Get the proportion completed per combination for GLMs
-tempW <- propComplete()
-tempC <- propComplete(Data = cogData, nSubs = nSubsC, indx = indxCog, type = "Cognitive")
-tempP <- propComplete(Data = physData, nSubs = nSubsP, indx = indxPhys, type = "Physical")
-tempE <- propComplete(Data = easyData, nSubs = nSubsE, indx = indxEasy, type = "Easy")
-
-allProp2 <- rbind(tempW,
-                  tempC,
-                  tempP,
-                  tempE)  
-allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials
-
-rm(tempW, tempC, tempP, tempE)
-
-# add optimal vector and difference from optimal
-wait <- c(rep(1,nSubsW*3),
-          c(rep(0,nSubsW), rep(1,nSubsW*2)),
-          c(rep(0,nSubsW*2), rep(1,nSubsW)))
-cog <- c(rep(1,nSubsC*3),
-          c(rep(0,nSubsC), rep(1,nSubsC*2)),
-          c(rep(0,nSubsC*2), rep(1,nSubsC)))
-phys <- c(rep(1,nSubsP*3),
-          c(rep(0,nSubsP), rep(1,nSubsP*2)),
-          c(rep(0,nSubsP*2), rep(1,nSubsP)))
-easy <- c(rep(1,nSubsE*3),
-          c(rep(0,nSubsE), rep(1,nSubsE*2)),
-          c(rep(0,nSubsE*2), rep(1,nSubsE)))
-allProp2$Optimal <- c(wait,cog,phys,easy)
-allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete
-
-# sort by subject ID
-#allProp2 <- allProp2[order(allProp2$SubjID),]
-
-# actual proportions and standard errors, and the optimal summary for plotting
-trueProp <- aggregate(allProp2$propComplete,
-            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-            FUN = 'mean')
-
-trueSD <- aggregate(allProp2$propComplete,
-          by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-          FUN = 'sd')
-colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
-trueProp$SE[1:9] <- (trueSD$x[1:9])/(sqrt(nSubsW))
-trueProp$SE[10:18] <- (trueSD$x[10:18])/(sqrt(nSubsC))
-trueProp$SE[19:27] <- (trueSD$x[19:27])/(sqrt(nSubsP))
-trueProp$SE[28:36] <- (trueSD$x[28:36])/(sqrt(nSubsE))
-
-trueProp$Optimal <- aggregate(allProp2$Optimal,
-            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-            FUN = 'mean')$x
-```
-
-## Analyses
+# # params for reference
+# handling <- c(2, 10, 14)
+# cond <- c("Wait", "Cognitive", "Physical", "Easy")
+# 
+# # create data frame with summary stats
+# tempW <- summarizeData()
+# tempC <- summarizeData(Data = cogData, nSubs = nSubsC, type = "Cognitive")
+# tempP <- summarizeData(Data = physData, nSubs = nSubsP, type = "Physical")
+# tempE <- summarizeData(Data = easyData, nSubs = nSubsE, type = "Easy")
+# 
+# summaryData <- rbind(tempW,
+#                      tempC,
+#                      tempP,
+#                      tempE)
+# 
+# colnames(summaryData) <- c("Group", "propComplete", "Earnings", "RT", "forcedTravel")
+# 
+# summaryData$Cols <- c(rep(cols[1],nSubsW), rep(cols[2],nSubsC), rep(cols[3],nSubsP), rep(cols[4],nSubsE))
+# rm(tempW, tempC, tempP, tempE)
+# 
+# # Indexes for groups
+# indxWait <- seq(nSubsW)
+# indxWaitLong <- seq(nSubsW * 9) # 9 being the number of combinations
+# indxCog <- (nSubsW + 1):(nSubsW + nSubsC)
+# indxCogLong <- ((nSubsW * 9) + 1):((nSubsW * 9) + (nSubsC * 9))
+# indxPhys <- ((nSubsW + nSubsC) + 1):(nSubsW + nSubsC + nSubsP)
+# indxPhysLong <- ((nSubsW * 9) + (nSubsC * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9))
+# indxEasy <- ((nSubsW + nSubsC + nSubsP) + 1):totalSubs #(nSubsW + nSubsC + nSubsP + nSubsE)
+# indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))
+# 
+# 
+# # the other, just summarizing for all participants
+# # Not sure if this is necessary anymore
+# # allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
+# #                                 rep("Cognitive",nSubsC*3),
+# #                                 rep("Physical",nSubsP*3)),
+# #                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
+# #                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
+# #                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
+# #                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
+# #                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
+# #                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))
+# 
+# 
+# # Get the proportion completed per combination for GLMs
+# tempW <- propComplete()
+# tempC <- propComplete(Data = cogData, nSubs = nSubsC, indx = indxCog, type = "Cognitive")
+# tempP <- propComplete(Data = physData, nSubs = nSubsP, indx = indxPhys, type = "Physical")
+# tempE <- propComplete(Data = easyData, nSubs = nSubsE, indx = indxEasy, type = "Easy")
+# 
+# allProp2 <- rbind(tempW,
+#                   tempC,
+#                   tempP,
+#                   tempE)  
+# allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials
+# 
+# rm(tempW, tempC, tempP, tempE)
+# 
+# # add optimal vector and difference from optimal
+# wait <- c(rep(1,nSubsW*3),
+#           c(rep(0,nSubsW), rep(1,nSubsW*2)),
+#           c(rep(0,nSubsW*2), rep(1,nSubsW)))
+# cog <- c(rep(1,nSubsC*3),
+#           c(rep(0,nSubsC), rep(1,nSubsC*2)),
+#           c(rep(0,nSubsC*2), rep(1,nSubsC)))
+# phys <- c(rep(1,nSubsP*3),
+#           c(rep(0,nSubsP), rep(1,nSubsP*2)),
+#           c(rep(0,nSubsP*2), rep(1,nSubsP)))
+# easy <- c(rep(1,nSubsE*3),
+#           c(rep(0,nSubsE), rep(1,nSubsE*2)),
+#           c(rep(0,nSubsE*2), rep(1,nSubsE)))
+# allProp2$Optimal <- c(wait,cog,phys,easy)
+# allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete
+# 
+# # sort by subject ID
+# #allProp2 <- allProp2[order(allProp2$SubjID),]
+# 
+# # actual proportions and standard errors, and the optimal summary for plotting
+# trueProp <- aggregate(allProp2$propComplete,
+#             by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
+#             FUN = 'mean')
+# 
+# trueSD <- aggregate(allProp2$propComplete,
+#           by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
+#           FUN = 'sd')
+# colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
+# trueProp$SE[1:9] <- (trueSD$x[1:9])/(sqrt(nSubsW))
+# trueProp$SE[10:18] <- (trueSD$x[10:18])/(sqrt(nSubsC))
+# trueProp$SE[19:27] <- (trueSD$x[19:27])/(sqrt(nSubsP))
+# trueProp$SE[28:36] <- (trueSD$x[28:36])/(sqrt(nSubsE))
+# 
+# trueProp$Optimal <- aggregate(allProp2$Optimal,
+#             by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
+#             FUN = 'mean')$x
+```
 
@@
 
-``` {r 16.1.1., fig.align="center", fig.width=4, fig.height=4, echo=FALSE}
-# Add an AR predictor based on the number of quits
-waitData <- lapply(waitData, function(data) data %>% mutate(AR = seqQuits(Choice)))
-cogData <- lapply(cogData, function(data) data %>% mutate(AR = seqQuits(Choice)))
-physData <- lapply(physData, function(data) data %>% mutate(AR = seqQuits(Choice)))
-easyData <- lapply(easyData, function(data) data %>% mutate(AR = seqQuits(Choice)))
-
-# Logistic fits
-waitLogis <- lapply(waitData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
-cogLogis <- lapply(cogData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
-physLogis <- lapply(physData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
-easyLogis <- lapply(easyData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
-
-# Coefficients
-waitLogis_coeffs <- t(sapply(waitLogis, "[[", "coefficients"))
-cogLogis_coeffs <- t(sapply(cogLogis, "[[", "coefficients"))
-physLogis_coeffs <- t(sapply(physLogis, "[[", "coefficients"))
-easyLogis_coeffs <- t(sapply(easyLogis, "[[", "coefficients"))
-allLogis_coeffs <- rbind(waitLogis_coeffs,
-                         cogLogis_coeffs,
-                         physLogis_coeffs,
-                         easyLogis_coeffs)
-
-# Rank sums
-rankHand <- wilcox.test(allLogis_coeffs[,2])
-rankReward <- wilcox.test(allLogis_coeffs[,3])
+``` {r 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
+# filterout errors and compute R + H logistic per subject, then get coefficients
+logisRH <- dataAll %>%
+  filter(Choice < 2) %>%
+  plyr::dlply("SubjID", identity) %>%
+  lapply(function(data) {glm(Choice ~ Handling + Reward, data = data, family = "binomial")}) %>%
+  sapply(coefficients)
+
+# Rank sum tests
+rankHand <- wilcox.test(logisRH["Handling", ])
+rankReward <- wilcox.test(logisRH["Reward", ])
 
 # Plot coeffs
-temp <- melt(allLogis_coeffs[,2:3])
-qplot(data = temp, x = Var2, y = value, geom = "boxplot") + 
+temp <- melt(logisRH[c("Handling", "Reward"), ])
+qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
   labs(title = "Handling and Reward Coefficients", x = "", y = "Coefficients") +
-  geom_hline(yintercept = 0, alpha = 0.5) +
-  theme_classic()
-
-rm(waitLogis, cogLogis, physLogis, easyLogis)
-
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  theme(legend.position = c(0.9, 0.7),
+       panel.grid.major = element_blank(), 
+       panel.grid.minor = element_blank(), 
+       panel.background = element_blank(), 
+       axis.line = element_line(colour = "black"),
+       text = element_text(size = 16))
 ```
@@
 
-``` {r 16.1.2., echo=FALSE, fig.align="center"}
-# Logistic fits
-waitLogis <- lapply(waitData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
-cogLogis <- lapply(cogData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
-physLogis <- lapply(physData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
-easyLogis <- lapply(easyData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
-
-# Coefficients
-waitLogis_coeffs <- t(sapply(waitLogis, "[[", "coefficients"))
-cogLogis_coeffs <- t(sapply(cogLogis, "[[", "coefficients"))
-physLogis_coeffs <- t(sapply(physLogis, "[[", "coefficients"))
-easyLogis_coeffs <- t(sapply(easyLogis, "[[", "coefficients"))
-allLogis_coeffs <- rbind(waitLogis_coeffs,
-                         cogLogis_coeffs,
-                         physLogis_coeffs,
-                         easyLogis_coeffs)
-
-#waitLogis_coeffs <- sapply(waitLogis, function(data) (confint(data)[4,1] < 0 & confint(data)[4,2] > 0))
+``` {r 16.1.2., echo = FALSE, include = FALSE}
+# add an AR regressor to track recent quits
+logisRHAR <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID) %>%
+  mutate(AR = seqQuits(Choice)) %>%
+  plyr::dlply("SubjID", identity) %>%
+  lapply(function(data) {glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial")})
 
 # Rank sums
-rankAR <- wilcox.test(allLogis_coeffs[,4])
-
-# Plot coeffs
-temp <- melt(allLogis_coeffs[,2:4])
-
-# The ugliest code, to check the existence of 0 on the CIs
-AR_CIs <- data.frame(Subj = NULL, Low = NULL, High = NULL)
-temp <- data.frame(Subj = seq(nSubsW), Low = rep(-0.1,nSubsW), High = rep(0,nSubsW))
-for (i in seq(length(waitLogis))) {
-  test <- tryCatch(round(confint(waitLogis[[i]]), digits = 2)[4,], error=function(e){})
-  if(!is.null(test)) {
-    temp$Low[i] <- test[1]
-    temp$High[i] <- test[2]
-  }
-}
-AR_CIs <- rbind(AR_CIs, temp)
-temp <- data.frame(Subj = seq(nSubsC), Low = rep(0,nSubsC), High = rep(0,nSubsC))
-for (i in seq(length(cogLogis))) {
-  test <- tryCatch(round(confint(cogLogis[[i]]), digits = 2)[4,], error=function(e){})
-  if(!is.null(test)) {
-    temp$Low[i] <- test[1]
-    temp$High[i] <- test[2]
-  }
-}
-AR_CIs <- rbind(AR_CIs, temp)
-temp <- data.frame(Subj = seq(nSubsP), Low = rep(0,nSubsP), High = rep(0,nSubsP))
-for (i in seq(length(physLogis))) {
-  test <- tryCatch(round(confint(physLogis[[i]]), digits = 2)[4,], error=function(e){})
-  if(!is.null(test)) {
-    temp$Low[i] <- test[1]
-    temp$High[i] <- test[2]
-  }
-}
-AR_CIs <- rbind(AR_CIs, temp)
-temp <- data.frame(Subj = seq(nSubsE), Low = rep(0,nSubsE), High = rep(0,nSubsE))
-for (i in seq(length(easyLogis))) {
-  test <- tryCatch(round(confint(easyLogis[[i]]), digits = 2)[4,], error=function(e){})
-  if(!is.null(test)) {
-    temp$Low[i] <- test[1]
-    temp$High[i] <- test[2]
-  }
-}
-AR_CIs <- rbind(AR_CIs, temp)
-AR_CIs$High[is.na(AR_CIs$High)] <- 0.1
-AR_CIs$AR_Effect <- apply(AR_CIs,1, function(x) !(x[2] <= 0 & x[3] >= 0))
+rankAR <- logisRHAR %>% 
+  sapply(coefficients) %>%
+  wilcox.test(.["AR", ])
+
+AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(confint(x)[4, ], error = function(e){c(0, 0)})}) %>%
+  replace_na(0) %>%
+  t() %>% 
+  apply(1, function(x) !(x[1] <= 0 & x[2] >= 0))
 
 # Around 10% seemed to have been influenced by previous quitting
-propAR_effects <- (sum(AR_CIs$AR_Effect) / totalSubs) * 100
-
-rm(temp,waitLogis, cogLogis, physLogis, easyLogis)
-
+propAR_effects <- mean(AR_CIs) * 100
 ```

### 2019-05-07 Cost2/Cost2_prereg_remake.Rmd
section 16.1 of cost 2 preregistration ready

@@
 # Around 10% seemed to have been influenced by previous quitting
-propAR_effects <- mean(AR_CIs) * 100
+prcntAR_effects <- mean(AR_CIs) * 100
 ```
@@
 To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero.
-By this measure, around `r round(propAR_effects)` percent of our participants seemed to have been influenced by recent quitting.
+By this measure, around `r round(prcntAR_effects)` percent of our participants seemed to have been influenced by recent quitting.
 However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.
@@
 ``` {r 16.1.3. Earnings, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
-# Pairwise comparison
-# earningsPerm <- permute(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog]) # I believe this more
-# earningsRsq <- cohenD(summaryData$Earnings[indxWait], summaryData$Earnings[indxCog])
-
-# linear model (think of doing a Poisson Regression instead, since earnings are not normally distributed [although bootstrapped they're fine])
-propAllsq <- summaryData$propComplete^2 
-lmEarn <- lm(Earnings ~ propComplete + propAllsq, data = summaryData)
-summaryEarn <- summary(lmEarn)
-coeffsEarn <- lmEarn$coefficients
-summaryData$tempLine <- seq(0,1,length=totalSubs) # for plotting
-summaryData$earnFitLine <- coeffsEarn[1] + coeffsEarn[2]*summaryData$tempLine + coeffsEarn[3]*(summaryData$tempLine^2)
-
-# plotting
-# boxplot(summaryData$Earnings[indxWait],
-#         summaryData$Earnings[indxCog],
-#         summaryData$Earnings[indxPhys],
-#         summaryData$Earnings[indxEasy],
-#         names = lbls,
-#         main = "Total Earnings for Each Group",
-#         ylab = "Total Earnings (pts)",
-#         xlab = "Group",
-#         col = cols)
-# earnBoxplot <- ggplot(data = summaryData, aes(Group, Earnings, fill = Group)) +
-#         geom_boxplot(show.legend = F) +
-#         scale_fill_manual(values = cols) +
-#         labs(title = "Total Earned per Group", y = "Total Earnings (Cents)", x = "") +
-#         theme_classic()
-
-# earnings (inverse-U, which makes sense because either over or under accepting are detrimental to earnings)
-# plot(summaryData$propComplete[indxWait],
-#      summaryData$Earnings[indxWait],
-#      main = "Total Earnings as a Function of Proportion Accepted",
-#      xlab = "Total Proportion Completed",
-#      ylab = "Total Earned",
-#      col=cols[1],
-#      xlim=c(0.2,1),
-#      ylim = c(1000,2000),
-#      pch=16,
-#      cex = lthick - 0.5)
-# points(summaryData$propComplete[indxCog],
-#        summaryData$Earnings[indxCog],
-#        col=cols[2],
-#        pch=16,
-#        cex = lthick - 0.5)
-# points(summaryData$propComplete[indxPhys],
-#        summaryData$Earnings[indxPhys],
-#        col=cols[3],
-#        pch=16,
-#        cex = lthick - 0.5)
-# points(summaryData$propComplete[indxEasy],
-#        summaryData$Earnings[indxEasy],
-#        col=cols[4],
-#        pch=16,
-#        cex = lthick - 0.5)
-# legend("topright",
-#        lbls,
-#        fill = cols,
-#        cex = 0.8)
-# lines(x, coeffsEarn[1] + coeffsEarn[2]*x + coeffsEarn[3]*(x^2),
-#        col="black",
-#       lwd = lthick)
-
-earnFitplot <- ggplot(data = summaryData, aes(propComplete, Earnings)) + 
-         geom_point(aes(color = Group), size = 2, show.legend = F) + 
-         geom_line(aes(tempLine, earnFitLine), size = 1.5, alpha = 0.7) +
+# calculate the proportions and earnings per subject, while keeping group info
+temp <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(Earnings = sum(Reward[Choice == 1] / 100),
+            pComplete = mean(Choice)) %>%
+  mutate(pComplete2 = pComplete^2) %>%
+  ungroup()
+
+# linear fit of earnings x prop accept
+lmEarn <- lm(Earnings ~ pComplete + pComplete2, data = temp)
+
+# plot
+(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
          scale_color_manual(values = cols) + 
-         xlim(0.2,1) +
-         labs(title = "Earnings as a Function of Acceptances", x = "Proportion Accepted", y = "") +
-         theme_classic()
-
-earnFitplot
+         geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = T) + 
+         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
+         labs(x = "Proportion Accepted", y = "Total Earnings (dollars)") +
+         scale_fill_manual(values = cols) +
+         theme(panel.grid.major = element_blank(), 
+           panel.grid.minor = element_blank(), 
+           panel.background = element_blank(), 
+           axis.line = element_line(colour = "black"),
+           text = element_text(size = 16)))
 
@@
 
-  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances-either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
+  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances--either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
 This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*
@@
 ``` {r 16.1.4., echo=FALSE}
-# Split the data frame into every combination of parameters of interest
-splitData <- split(allProp2, list(allProp2$Reward, allProp2$Handling, allProp2$Group))
-
-# Perform a paired t-test on every combination of parameters
-# Given that 20 cent rewards demand constant acceptances, we expect the proportions to be constant for these choices
-# This gives an error in the t.test due to the lack of variability and normal errors, so we use try to bypass this issue
-splitData_tests <- sapply(splitData, function(data) try(t.test(data$propComplete, mu = unique(data$Optimal))$p.value))
-
-# Adjust for multiple comparisons using BY-FDR
-trueProp$Deviation_pval <- round(p.adjust(splitData_tests, method = "BY"), digits = 2)
-trueProp$Deviation_pval[is.na(trueProp$Deviation_pval)] <- 1
-# trueProp[trueProp$Deviation_pval < 0.05, ]
-
-# Proportion of significant deviations from optimality
-splitData_prop <- round(sum(trueProp$Deviation_pval < 0.05, na.rm = T) / 36, digits = 2)
+# in order
+# clean data, 
+# calculate each individual's prop. accept,
+# calculate t.tests with optimality as null mean,
+# correct pvalues with FDR
+temp <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Handling, Reward, Cost) %>%
+  summarise(pComplete = mean(Choice)) %>%
+  mutate(optimal = case_when(
+          (Handling == 10 & Reward < 8) ~ 0,
+          (Handling == 14 & Reward < 20) ~ 0,
+          TRUE ~ 1
+        )) %>% 
+  group_by(Handling, Reward, Cost) %>%
+  summarise(meanAccept = mean(pComplete),
+            sdAccept = sd(pComplete),
+            optimal = unique(optimal),
+            pvals = tryCatch(t.test(pComplete, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
+  mutate(FDR = p.adjust(pvals, method = "BY"),
+         significant = FDR < 0.05)
+
+# proportion of significant ones
+# eventually find a way to plot this
+splitData_prop <- mean(temp$significant, na.rm = T)
 ```

### 2019-05-07 Cost2/Cost2_prereg_remake.Rmd
overall prop section complete

@@
 # Permutation for 2 groups
-permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){
+permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE, simple = FALSE){
 
@@
 
+    # return the results
+    if (simple) {
+
+      return(summaryPerm$Pval)
+
+    } else if (!simple) {
+
       return(summaryPerm)
+
+    }
 
@@
 ``` {r 16.2.1. Overall Proportion/Earnings,fig.align="center",fig.width=10,fig.height=4, echo=FALSE}  
-## prop complete
-# ecdfs
-wait <- ecdf(summaryData$propComplete[indxWait])
-cog <- ecdf(summaryData$propComplete[indxCog])
-phys <- ecdf(summaryData$propComplete[indxPhys])
-easy <- ecdf(summaryData$propComplete[indxEasy])
-range <- seq(0,1,by=0.01)
-
-test <- data.frame(range = range,
-                   ecdf = c(wait(range),cog(range),phys(range),easy(range)),
-                   Group = factor(c(rep("Wait",101),rep("Cognitive",101),rep("Physical",101),rep("Easy", 101)), levels = c("Wait","Cognitive","Physical","Easy")))
-
-p1 <- ggplot(test, aes(x=range,y=ecdf, group=Group, color=Group))
-p1 <- p1 + geom_line(show.legend = F, size = 1.5) +
+## ECDF of proportion completed per cost type
+temp <- dataAll %>%
+        filter(Choice < 2) %>%
+        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
+        group_by(SubjID, Cost) %>%
+        summarise(Earnings = sum(Reward[Choice == 1] / 100),
+                  pComplete = mean(Choice))
+
+## formal testing 
+# proportion completed
+propAov <- aov(pComplete ~ factor(Cost), data = temp)
+
+propTests <- temp %>% 
+  plyr::dlply("Cost", identity) %>%
+  sapply("[[", "pComplete") %>%
+  as.data.frame() %>%
+  combn(2, simplify = F) %>%
+  sapply(function(x) {
+    c(contrast = paste(colnames(x), collapse = "vs"), 
+      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
+      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
+  }) %>% 
+  t()
+
+# pairwise.wilcox.test(temp$pComplete, temp$Cost)
+
+# earnings
+earnAov <- aov(Earnings ~ factor(Cost), data = temp)
+
+earnTests <- temp %>% 
+  plyr::dlply("Cost", identity) %>%
+  sapply("[[", "Earnings") %>%
+  as.data.frame() %>%
+  combn(2, simplify = F) %>%
+  sapply(function(x) {
+    c(contrast = paste(colnames(x), collapse = "vs"), 
+      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
+      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
+  }) %>% 
+  t()
+
+# plots
+p1 <- ggplot(aes(pComplete, color = Cost), data = temp) +
+        stat_ecdf(lwd = 1.2, show.legend = F) +
         scale_color_manual(values = cols) +
-    labs(title = "ECDF of Acceptances per Group", y="ECDF", x = "Proportion Accepted") +
-    theme_classic()
-
-# problem is, data is not normal, so we're going to bootstrap it and DEFINITELY permute
-# Bootstrap nonparametric
-B <- 5000
-meanBootW <- bootstrap(summaryData$propComplete[indxWait],B = B) #rep(0,B)
-meanBootC <- bootstrap(summaryData$propComplete[indxCog], B = B) #rep(0,B)
-meanBootP <- bootstrap(summaryData$propComplete[indxPhys], B = B)
-meanBootE <- bootstrap(summaryData$propComplete[indxEasy], B = B)
-
-#CIs wait
-meanW <- mean(meanBootW)
-upperW <- quantile(meanBootW,0.975) # meanBoot?
-lowerW <- quantile(meanBootW,0.025)
-
-#CIs effort
-meanC <- mean(meanBootC)
-upperC <- quantile(meanBootC,0.975) # meanBoot?
-lowerC <- quantile(meanBootC,0.025)
-
-#CIs physical
-meanP <- mean(meanBootP)
-upperP <- quantile(meanBootP,0.975) # meanBoot?
-lowerP <- quantile(meanBootP,0.025)
-
-#CIs easy
-meanE <- mean(meanBootE)
-upperE <- quantile(meanBootE,0.975) # meanBoot?
-lowerE <- quantile(meanBootE,0.025)
-
-# formal testing 
-# proportion completed
-propAov <- aov(propComplete ~ factor(Group), data = summaryData)
-
-# effect size (get the one for anovas)
-# propRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])
-
-# post-hoc
-temp <- do.call(cbind, lapply(split(summaryData, summaryData$Group),"[[","propComplete"))
-temp2 <- t(combn(colnames(temp),2))
-
-propTests <- data.frame(Comparison = paste(temp2[,1], temp2[,2]),
-                        T_pval = rep(1,6),
-                        CohenD = rep(0,6))
-
-for (i in seq(nrow(temp2))) {
-
-  propTests$T_pval[i] <- round(permute(temp[,temp2[i,1]], temp[,temp2[i,2]])$Pval, digits = 2)
-  propTests$CohenD[i] <- round(cohenD(temp[,temp2[i,1]], temp[,temp2[i,2]]), digits = 2)
-
-}
-
-# earnings
-earnAov <- aov(Earnings ~ factor(Group), data = summaryData)
-
-# effect size
-# earnRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])
-
-# post-hoc
-temp <- do.call(cbind, lapply(split(summaryData, summaryData$Group),"[[","Earnings"))
-temp2 <- t(combn(colnames(temp),2))
-
-earnTests <- data.frame(Comparison = paste(temp2[,1], temp2[,2]),
-                        T_pval = rep(1,6),
-                        CohenD = rep(0,6))
-
-for (i in seq(nrow(temp2))) {
-
-  earnTests$T_pval[i] <- round(permute(temp[,temp2[i,1]], temp[,temp2[i,2]])$Pval, digits = 2)
-  earnTests$CohenD[i] <- round(cohenD(temp[,temp2[i,1]], temp[,temp2[i,2]]), digits = 2)
-
-}
-
-rm(B,cog,wait,phys,easytemp,temp2)
-
-# plot
-p2 <- ggplot(summaryData, aes(x=Group, y=propComplete, fill = Group))
-p2 <- p2 + geom_boxplot(show.legend = F) +
+        xlim(0, 1) +
+        labs(y="ECDF", x = "Proportion Accepted") +
+        theme(panel.grid.major = element_blank(), 
+              panel.grid.minor = element_blank(), 
+              panel.background = element_blank(), 
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16))
+
+p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
+        geom_boxplot(show.legend = F) +
         scale_fill_manual(values = cols) +
-    ylim(c(0,1)) +
-    labs(title = "Proportion Completed by Group", y="Proportion Completed") +
-    theme_classic()
-
-p3 <- ggplot(summaryData, aes(x=Group, y=Earnings, fill = Group))
-p3 <- p3 + geom_boxplot(show.legend = F) +
+        ylim(c(0, 1)) +
+        labs(y = "Proportion Completed") +
+        theme(panel.grid.major = element_blank(), 
+            panel.grid.minor = element_blank(), 
+            panel.background = element_blank(), 
+            axis.line = element_line(colour = "black"),
+            text = element_text(size = 16))
+
+p3 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
+        geom_boxplot(show.legend = F) +
         scale_fill_manual(values = cols) +
-    labs(title = "Earnings by Group", y="Total Earnings (Cents)") +
-    theme_classic()
+        labs(y = "Total Earnings (dollars)") +
+        theme(panel.grid.major = element_blank(), 
+            panel.grid.minor = element_blank(), 
+            panel.background = element_blank(), 
+            axis.line = element_line(colour = "black"),
+            text = element_text(size = 16))
 

### 2019-05-07 Cost2/Cost2_prereg.Rmd
mixed effects logistic not replicating

@@
 # load cognitive effort group
-setwd('./data/Cost2_data/cog')
-temp = list.files(pattern="*.csv")
+setwd('./data/')
+temp = list.files(pattern="cogTask")
 cogDataLong = lapply(temp, read.csv, header = FALSE)
@@
 # load wait group
-setwd('../wait')
-temp = list.files(pattern="*.csv")
+temp = list.files(pattern="wait")
 waitDataLong = lapply(temp, read.csv, header = FALSE)
@@
 # load physical group
-setwd('../phys')
-temp = list.files(pattern="*.csv")
+temp = list.files(pattern="phys")
 physDataLong = lapply(temp, read.csv, header = FALSE)
@@
 # load pheasysical group
-setwd('../easy')
-temp = list.files(pattern="*.csv")
+temp = list.files(pattern="pheasy")
 easyDataLong = lapply(temp, read.csv, header = FALSE)
@@
 indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))
-
-# the other, just summarizing for all participants
-# Not sure if this is necessary anymore
-# allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
-#                                 rep("Cognitive",nSubsC*3),
-#                                 rep("Physical",nSubsP*3)),
-#                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
-#                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
-#                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
-#                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
-#                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
-#                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))
 

### 2019-05-07 Cost2/Cost2_prereg_remake.Rmd
mixed effects logistic not replicating

@@
          Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
-         SubjID = substring(SubjID, 0, 3)) %>%
+         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
   unnest() %>%
-  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"))
-
+  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"),
+         optimal = case_when(
+          (Handling == 10 & Reward < 8) ~ 0,
+          (Handling == 14 & Reward < 20) ~ 0,
+          TRUE ~ 1
+         ))
+
+# get a simple subject list and the number of subjects
 subjList <- unique(dataAll$SubjID)
+nSubj <- length(subjList)
 
@@
 ``` {r 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
+temp <- dataAll %>%
+        filter(Choice < 2) %>%
+        group_by(SubjID, Cost, Handling, Reward) %>%
+        summarise(pComplete = mean(Choice))
+
 ## REPEATED MEASURES ANOVA
 # I think I like this the most
-prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
+prop.aov <- with(temp, aov(pComplete ~ factor(Cost) * Handling * Reward + 
                                  Error(SubjID / (Handling * Reward))))
-
-#prop.aov <- with(allProp2, aov(propComplete ~ factor(Group) * Handling * Reward + 
- #                                Error(SubjID / (Handling * Reward))))
 
@@
 # This is in case you don't want to plot the easy condition (easier to see)
-cols = c("#78AB05","#D9541A","deepskyblue4", "grey50")
-trueProp2 <- trueProp[-(28:36), ]
-
-a1 <- ggplot(data = trueProp, aes(x=interaction(Reward, Handling), y=propComplete, color=Group)) + 
-        geom_point(size=3) + 
-        geom_errorbar(aes(ymin=propComplete-SE, ymax=propComplete+SE), width=0.2, size=1) +
-        geom_line(aes(group = interaction(Handling, Group)), size=1) +
-        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
-        labs(x = "Reward.Handling", y = "Proportion Accepted", title = "Proportion Accepted per Handling and Reward Combination") +
-        scale_color_manual(values=cols) +
-        theme_classic()
-
-a1
+
+trueProp <- dataAll %>%
+        filter(Choice < 2) %>%
+        group_by(SubjID, Cost, Handling, Reward, optimal) %>%
+        summarise(pComplete = mean(Choice)) %>%
+        group_by(Cost, Handling, Reward, optimal) %>%
+        summarise(meanComplete = mean(pComplete),
+                  SE = sd(pComplete) / sqrt(length(pComplete)))
+
+(a1 <- ggplot(data = trueProp, aes(interaction(Reward, Handling), meanComplete, color = Cost)) + 
+        geom_point(size = 3) + 
+        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
+        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
+        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
+        labs(x = "Reward.Handling", y = "Proportion Accepted") +
+        scale_color_manual(values = cols) +
+        theme(panel.grid.major = element_blank(), 
+              panel.grid.minor = element_blank(), 
+              panel.background = element_blank(), 
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16)))
+
 ```
@@
 panderOptions("digits", 2)
-pander(x, style = "rmarkdown",split.table = 110)
+pander(x, style = "rmarkdown", split.table = 110)
 ```
@@
 ``` {r 16.2.3. Mixed Effects Model, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
-# just to make the logistic plotting comply with the function
-allProp2 <- allProp2[order(as.character(allProp2$Group), decreasing = F), ]
-
-# This transformation is necessary for a proper binomial fit of proportion data
-totalQuit <- allProp2$totalTrials - allProp2$totalComplete
-testBinom <- cbind(allProp2$totalComplete,totalQuit)
-
-# Using a mixed-model fitted with GLMER
-# Note: GLMER does not take quasi family distributions
-# ranef() to display the random intercepts, fixef() for the model coefficients
-
-# fit model
 mixLogis_main <- list()
-allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Wait"))
-mixLogis_main$Wait <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Cognitive"))
-mixLogis_main$Cognitive <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Physical"))
-mixLogis_main$Physical <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Easy"))
-mixLogis_main$Easy <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-
-# Summarize model 
-mixLogis_main$Summary <- summary(mixLogis_main$Wait)
-
-# Coefficient matrices for all reference combos
-t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,1], GroupWait = 0)
-t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,1], GroupCognitive = 0)
-t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,1], GroupPhysical = 0)
-t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,1], GroupEasy = 0)
-mixLogis_mainBetas <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
-dimnames(mixLogis_mainBetas) <- list(cond[c(2,4,3,1)],c("Group",cond))
-mixLogis_mainBetas <- as.matrix(mixLogis_mainBetas[,c(3,5,4,2)])
-
-# And their respective p-values
-t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,4], GroupWait = 1)
-t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,4], GroupCognitive = 1)
-t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,4], GroupPhysical = 1)
-t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,4], GroupEasy = 1)
-mixLogis_mainPvals <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
-dimnames(mixLogis_mainPvals) <- list(cond[c(2,4,3,1)],c("Group",cond))
-mixLogis_mainPvals <- as.matrix(mixLogis_mainPvals[,c(3,5,4,2)])
-
-# Create CIs
-sd <- sqrt(diag(vcov(mixLogis_main$Wait)))
-mixLogisCI <- cbind(Est = fixef(mixLogis_main$Wait), LL = fixef(mixLogis_main$Wait) - 1.96 * sd, UL = fixef(mixLogis_main$Wait) + 1.96 * sd)
+mixData <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost, Handling, Reward) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice)) %>%
+  ungroup()
+
+testBinom <- cbind(mixData$totalAccepted, mixData$totalQuits)
+
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
+mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
+mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
+mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
+mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
+
+temp <- lapply(mixLogis_main, function(model) {coefficients(model)$SubjID[1, 2:4]})
+mixCoeffs <- bind_rows(temp) #reduce(temp, full_join) 
+dimnames(mixCoeffs) <- list(names(temp), substr(colnames(mixCoeffs), 5, 20))
+mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
+mixCoeffs[is.na(mixCoeffs)] <- 1
+mixCoeffs <- mixCoeffs[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]
+
+# # just to make the logistic plotting comply with the function
+# allProp2 <- allProp2[order(as.character(allProp2$Group), decreasing = F), ]
+# 
+# # This transformation is necessary for a proper binomial fit of proportion data
+# totalQuit <- allProp2$totalTrials - allProp2$totalComplete
+# testBinom <- cbind(allProp2$totalComplete,totalQuit)
+# 
+# # Using a mixed-model fitted with GLMER
+# # Note: GLMER does not take quasi family distributions
+# # ranef() to display the random intercepts, fixef() for the model coefficients
+# 
+# # fit model
+# mixLogis_main <- list()
+# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Wait"))
+# mixLogis_main$Wait <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
+# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Cognitive"))
+# mixLogis_main$Cognitive <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
+# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Physical"))
+# mixLogis_main$Physical <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
+# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Easy"))
+# mixLogis_main$Easy <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
+# 
+# # Summarize model 
+# mixLogis_main$Summary <- summary(mixLogis_main$Wait)
+# 
+# # Coefficient matrices for all reference combos
+# t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,1], GroupWait = 0)
+# t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,1], GroupCognitive = 0)
+# t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,1], GroupPhysical = 0)
+# t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,1], GroupEasy = 0)
+# mixLogis_mainBetas <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
+# dimnames(mixLogis_mainBetas) <- list(cond[c(2,4,3,1)],c("Group",cond))
+# mixLogis_mainBetas <- as.matrix(mixLogis_mainBetas[,c(3,5,4,2)])
+# 
+# # And their respective p-values
+# t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,4], GroupWait = 1)
+# t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,4], GroupCognitive = 1)
+# t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,4], GroupPhysical = 1)
+# t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,4], GroupEasy = 1)
+# mixLogis_mainPvals <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
+# dimnames(mixLogis_mainPvals) <- list(cond[c(2,4,3,1)],c("Group",cond))
+# mixLogis_mainPvals <- as.matrix(mixLogis_mainPvals[,c(3,5,4,2)])
+# 
+# # Create CIs
+# sd <- sqrt(diag(vcov(mixLogis_main$Wait)))
+# mixLogisCI <- cbind(Est = fixef(mixLogis_main$Wait), LL = fixef(mixLogis_main$Wait) - 1.96 * sd, UL = fixef(mixLogis_main$Wait) + 1.96 * sd)
 ```

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
done with mix logistic, but revisit the theory

@@
 ``` {r 16.2.3. Mixed Effects Model, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
+# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
 mixLogis_main <- list()
@@
 
-testBinom <- cbind(mixData$totalAccepted, mixData$totalQuits)
-
+# model with a random intercept and cost-type slope, then relevel the cost to get all pairwise comparisons
+# the correct way to model a logistic with proportions as dependent vars is by prividing n of hits and quits as a matrix
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
-mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (1 | SubjID), family = "binomial", data = mixData)
-
+mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+
+# matrix of coefficients
 temp <- lapply(mixLogis_main, function(model) {coefficients(model)$SubjID[1, 2:4]})
@@
 
-# # just to make the logistic plotting comply with the function
-# allProp2 <- allProp2[order(as.character(allProp2$Group), decreasing = F), ]
-# 
-# # This transformation is necessary for a proper binomial fit of proportion data
-# totalQuit <- allProp2$totalTrials - allProp2$totalComplete
-# testBinom <- cbind(allProp2$totalComplete,totalQuit)
-# 
-# # Using a mixed-model fitted with GLMER
-# # Note: GLMER does not take quasi family distributions
-# # ranef() to display the random intercepts, fixef() for the model coefficients
-# 
-# # fit model
-# mixLogis_main <- list()
-# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Wait"))
-# mixLogis_main$Wait <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Cognitive"))
-# mixLogis_main$Cognitive <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Physical"))
-# mixLogis_main$Physical <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-# allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Easy"))
-# mixLogis_main$Easy <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-# 
-# # Summarize model 
-# mixLogis_main$Summary <- summary(mixLogis_main$Wait)
-# 
-# # Coefficient matrices for all reference combos
-# t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,1], GroupWait = 0)
-# t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,1], GroupCognitive = 0)
-# t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,1], GroupPhysical = 0)
-# t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,1], GroupEasy = 0)
-# mixLogis_mainBetas <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
-# dimnames(mixLogis_mainBetas) <- list(cond[c(2,4,3,1)],c("Group",cond))
-# mixLogis_mainBetas <- as.matrix(mixLogis_mainBetas[,c(3,5,4,2)])
-# 
-# # And their respective p-values
-# t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,4], GroupWait = 1)
-# t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,4], GroupCognitive = 1)
-# t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,4], GroupPhysical = 1)
-# t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,4], GroupEasy = 1)
-# mixLogis_mainPvals <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
-# dimnames(mixLogis_mainPvals) <- list(cond[c(2,4,3,1)],c("Group",cond))
-# mixLogis_mainPvals <- as.matrix(mixLogis_mainPvals[,c(3,5,4,2)])
-# 
-# # Create CIs
-# sd <- sqrt(diag(vcov(mixLogis_main$Wait)))
-# mixLogisCI <- cbind(Est = fixef(mixLogis_main$Wait), LL = fixef(mixLogis_main$Wait) - 1.96 * sd, UL = fixef(mixLogis_main$Wait) + 1.96 * sd)
+# matrix of pvals
+temp <- lapply(mixLogis_main, function(model) {as.list(summary(model)$coefficients[2:4, 4])})
+mixPvals <- as.matrix(bind_rows(temp)) 
+dimnames(mixPvals) <- list(names(temp), substr(colnames(mixPvals), 5, 20))
+mixPvals <- as.matrix(mixPvals[, match(rownames(mixPvals), colnames(mixPvals))])
+rownames(mixPvals) <- colnames(mixPvals)
+mixPvals <- mixPvals[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]
+
+# plot coefficients and pvalues in a matrix
+# invert colors
+col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))
+
+corrplot(mixCoeffs, 
+         is.corr = F, 
+         p.mat = mixPvals, 
+         type = "upper",
+         outline = T,
+         insig = "p-value",
+         sig.level = -1, 
+         na.label = "square", 
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black",
+         tl.cex = 0.8,
+         col = col2(200))
+
 ```
@@
 # plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
-temp <- cbind(summaryData$Group, 
-              ranef(mixLogis_main$Wait)$SubjID)#, 
-              #Colors = c(rep(cols[1],nSubsW),rep(cols[2],nSubsC),rep(cols[3],nSubsP),rep(cols[4],nSubsE)))
-colnames(temp) <- list("Group", "RandIntercept")
-RI1 <- ggplot(data = temp, aes(x = Group, y = RandIntercept, fill = Group)) + 
+temp <- ranef(mixLogis_main$Wait)$SubjID %>%
+  gather(key = Cost, value = RandEffects, colnames(.))
+
+(RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
   geom_hline(yintercept = 0, alpha = 0.7) + 
@@
   scale_fill_manual(values = cols) + 
-  labs(title = "Random Intercepts per Group", x = "") +
-  theme_classic()
-
-RI1
+  labs(x = "") +
+  theme(panel.grid.major = element_blank(), 
+              panel.grid.minor = element_blank(), 
+              panel.background = element_blank(), 
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16)))
+
 ```

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
Section 16.2 of Cost 2 completed, now with BIC in addition to AIC

@@
 
-    # divide into relevant coefficients (assumes logisComb was the best model)
+    # divide into relevant coefficients (assumes logisComb was the best model)
     intercept <- coeffs[1]
@@
 ``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-### THE PLOTS FOR YALE
-# Ggplot made plotting way easier than the previous version
-# This is in case you don't want to plot the easy condition (easier to see)
-
+# prep data to plot the p(accept) based on reward, handling time and cost type
 trueProp <- dataAll %>%
@@
 
+# and plot
 (a1 <- ggplot(data = trueProp, aes(interaction(Reward, Handling), meanComplete, color = Cost)) + 
@@
 # matrix of coefficients
-temp <- lapply(mixLogis_main, function(model) {coefficients(model)$SubjID[1, 2:4]})
-mixCoeffs <- bind_rows(temp) #reduce(temp, full_join) 
+# 
+temp <- lapply(mixLogis_main, function(model) {as.list(summary(model)$coefficients[2:4, 1])})
+mixCoeffs <- as.matrix(bind_rows(temp)) #reduce(temp, full_join) 
 dimnames(mixCoeffs) <- list(names(temp), substr(colnames(mixCoeffs), 5, 20))
@@
 mixPvals <- mixPvals[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]
+diag(mixPvals) <- 1
 
@@
 (RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
-  geom_hline(yintercept = 0, alpha = 0.7) + 
+  geom_hline(yintercept = 0, alpha = 0.7, linetype = "dashed") + 
   geom_boxplot(show.legend = F) +
@@
 In order to show the comparisons among all conditions, the following plot portrays the coefficients (color scale), and p-values (numbers within squares) that resulted from switching the reference condition.
-Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group (the darker the cell, the greater the odds).
+Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group.
 Based on this, we can see that the cognitive group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
@@
 
-rm(temp,t1,t2,t3,t4)
-
 ```
@@
 
-This plot shows the AIC for every model. The last model to make significant fit contributions under the parameter penalty was indeed number 5.
-
 ``` {r 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
@@
 mixLogis_compare <- list()
-mixLogis_compare$Base <- glmer(testBinom ~ 1 + (1 | SubjID), family = "binomial", data = allProp2) # intercept only
-mixLogis_compare$Group <- glmer(testBinom ~ factor(Group) + (1 | SubjID), family = "binomial", data = allProp2) 
-mixLogis_compare$Handling <- glmer(testBinom ~ factor(Group) + Handling + (1 | SubjID), family = "binomial", data = allProp2)
-mixLogis_compare$Reward <- glmer(testBinom ~ factor(Group) + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-mixLogis_compare$AllMain <- mixLogis_main$Easy
-mixLogis_compare$HRInteraction <- glmer(testBinom ~ factor(Group) + Handling * Reward + (1 | SubjID), family = "binomial", data = allProp2)
-mixLogis_compare$AllInteractions <- glmer(testBinom ~ factor(Group) * Handling * Reward + (1 | SubjID), family = "binomial", data = allProp2)
+mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
+mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$Handling <- glmer(cbind(totalAccepted, totalQuits) ~ Handling + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Reward + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$AllMain <- mixLogis_main$Wait
+mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Reward + (Cost | SubjID), family = "binomial", data = mixData)
 
 # Model selection 
-aicLogis_compare <- sapply(mixLogis_compare, AIC)
+abicLogis_compare <- data.frame(Model = names(mixLogis_compare),
+                                AIC = sapply(mixLogis_compare, AIC),
+                                BIC = sapply(mixLogis_compare, BIC))
 
@@
 
+This plot shows the AIC for every model.
+The figure below shows AIC and BIC for all the models.
+As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2`).
+
 ``` {r 16.2.4. Plot Deviance comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-
-par(mar=c(5.1,2.1,2.1,2.1))    
-# plot the deviance for all models
-# ver 3
-modelLabels <- c('Intercept','G Only','H Only','R Only','G + H + R','G + H * R','G * H * R')
-plot(aicLogis_compare,
-     main = "AIC for All Models",
-     xlab = "",
-     ylab = "AIC",
-     pch = 16,
-     xaxt = "n")
-axis(1, at = 1:7, labels = F)
-text(1:7, 
-     par("usr")[3] - 22,
-     labels = modelLabels, 
-     srt = 45, 
-     pos = 1, 
-     xpd = TRUE)
+# plot AIC and BIC
+(mixLogis_compare$plot <- abicLogis_compare %>% 
+  gather(Comparison, Value, AIC:BIC) %>%
+  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
+  ggplot(aes(Model, Value, fill = Comparison)) +
+    geom_point(color = "black", pch = 21, size = 3) +
+    theme_classic())
 
@@
 
-## Notes
-
-- Update the AIC, RT ECDF, pre-post plots with ggplot.
-
-- This plot is just to show participant-specific behavior for all groups.
-
 ``` {r Testing grounds, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
RT plot

@@
 
+The ECDF below shows the proportion of quits and acceptances occurring as the trial advanced.
+Drastic changes indicate the end of one of the possible handling times, and sccessful receipt of a reward.
+This shows that there were no quits during the handling time, and displays the proportion of acceptances (1 - the y axis here) for each cost at each handling/travel time combination.
 We can see in the ECDFs below that most decisions to quit happened within the first second into the handling time.
@@
 ``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-# RTs
-# let's try to do some survival curves
-RTW <- unlist(lapply(waitData, function(data) {data$RT[data$Choice==0]})) # vector of all decision-related RTs for the wait group
-RTC <- unlist(lapply(cogData, function(data) {data$`Choice RT`[data$Choice==0]})) # same for the cog group
-RTP <- unlist(lapply(physData, function(data) {data$RT[data$Choice==0]}))
-RTE <- unlist(lapply(easyData, function(data) {data$RT[data$Choice==0]}))
-
-# create a data frame for plotting
-RTgroups <- c(rep("Wait",length(RTW)), rep("Effort",length(RTC)), rep("Physical",length(RTP)), rep("Easy",length(RTE)))
-RTall <- c(RTW,RTC,RTP,RTE)
-RTframe <- data.frame(RTgroups, RTall)
-
-# plot
-ggplot(RTframe, aes(RTall, color = RTgroups)) + 
-  stat_ecdf(lwd = 1) + 
+
+# Proportion of forced travels per subject and cost type
+propFails <- dataAll %>% 
+  filter(Cost != "Wait") %>% 
+  group_by(SubjID, Cost) %>% 
+  summarise(propFails = mean(Choice == 2)) %>%
+  group_by(Cost) %>% 
+  summarise(meanQuit = mean(propFails))
+
+# Reaction times ECDFs including offer and in-trial quits
+(RTs <- dataAll %>%
+  #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
+  filter(Choice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
+  ggplot(aes(RT, color = Cost)) + 
+    stat_ecdf(lwd = 1.2) +
+    geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
     scale_color_manual(values = cols) +
     scale_x_continuous(breaks = seq(14)) +
-  labs(title = "ECDFs for the Response Times", x = "Seconds", y = "ECDF") +
-  theme_classic()
-
-# # and CIs for each (unnecessary unless I end up plotting)
-# CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
-# CIC <- median(CIC) - (quantile(CIC,0.025))
-# CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-# CIW <- median(CIW) - (quantile(CIW,0.025))
-# CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-# CIP <- median(CIP) - (quantile(CIP,0.025))
-# CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-# CIE <- median(CIE) - (quantile(CIE,0.025))
-# lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
-# lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
-# lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
-# lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
-# lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
-# lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
-# lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
-# lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)
+    theme(panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      panel.background = element_blank(),
+      axis.line = element_line(colour = "black"),
+      text = element_text(size = 16)))
 

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
up to the OC anova. almost done restructuring the cost 2 script!

@@
 
-# Summarize the proportion complete for GLMs
-propComplete <- function(Data = waitData, nSubs = nSubsW, indx = indxWait, type = "Wait") {
-
-    tempProp <- data.frame(SubjID = rep(indx,9),
-                           Group = rep(type,nSubs*9),
-                           Handling = c(rep(2,nSubs*3), 
-                                        rep(10,nSubs*3), 
-                                        rep(14,nSubs*3)),
-                           Reward = rep(c(rep(4,nSubs),rep(8,nSubs),rep(20,nSubs)),3),
-                           propComplete = rep(NA,length(indx)*9),
-                           totalTrials = rep(NA,length(indx)*9),
-                           totalComplete = rep(NA,length(indx)*9))
-
-    for (subj in seq(nSubs)){
-
-      # handling of 2s
-      tempProp$propComplete[subj] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==4])
-      tempProp$propComplete[subj+nSubs] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==8])
-      tempProp$propComplete[subj+(nSubs*2)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==20])
-      tempProp$totalTrials[subj] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==4])
-      tempProp$totalTrials[subj+nSubs] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==8])
-      tempProp$totalTrials[subj+(nSubs*2)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==2 & Data[[subj]]$Reward==20])
-
-      # handling of 10s
-      tempProp$propComplete[subj+(nSubs*3)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==4])
-      tempProp$propComplete[subj+(nSubs*4)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==8])
-      tempProp$propComplete[subj+(nSubs*5)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==20])
-      tempProp$totalTrials[subj+(nSubs*3)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==4])
-      tempProp$totalTrials[subj+(nSubs*4)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==8])
-      tempProp$totalTrials[subj+(nSubs*5)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==10 & Data[[subj]]$Reward==20])
-
-      # handling of 14s
-      tempProp$propComplete[subj+(nSubs*6)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==4])
-      tempProp$propComplete[subj+(nSubs*7)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==8])
-      tempProp$propComplete[subj+(nSubs*8)] <- mean(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==20])
-      tempProp$totalTrials[subj+(nSubs*6)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==4])
-      tempProp$totalTrials[subj+(nSubs*7)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==8])
-      tempProp$totalTrials[subj+(nSubs*8)] <- length(Data[[subj]]$Choice[Data[[subj]]$Handling==14 & Data[[subj]]$Reward==20])
-
-    }
-
-    return(tempProp)
-
-}
-
 # OC-specific computation of the negative log likelihood for model optimization
@@
 # minimize the negative log likelihood
-optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA") {
+optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA", simplify = F) {
   # Prep data
@@
 
+  # if doing this with dplyr::do(), return a simplified data.frame instead with the important parameters
+  if (simplify) {
+    out <- data.frame(out[c(seq(8), 12)])
+  }
+
   return(out)
@@
                           Cost == "phea" ~ "Easy"),
-         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
          SubjID = as.integer(substring(SubjID, 0, 3))) %>%
@@
   mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"),
+         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
          optimal = case_when(
@@
 ``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-
 # Proportion of forced travels per subject and cost type
@@
   ggplot(aes(RT, color = Cost)) + 
-    stat_ecdf(lwd = 1.2) +
+    #stat_ecdf(lwd = 1.2, geom = "smooth") +
+    geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
     geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
@@
     scale_x_continuous(breaks = seq(14)) +
+    labs(x = "Reaction Time", y = "Proportion Accepted") +
     theme(panel.grid.major = element_blank(),
@@
 ``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-# THIS CODE CAN BE VASTLY IMPROVED, BUT RIGHT NOW IT WORKS SO I WON'T CARE
-# This one just plots the correlation between pre-post acceptance rates, both overall and per cell
-# The overall acceptance looks great, with mostly consistent rates, and with the physical group accepting slightly less post-break
-# However, the per-cell distribution looks messy, although you can still tell that there's a linear relationship
-# If I do a linear model predicting post with pre using cell-specific data, the betas are close to 1 and significant (also good R2s). That's good.
-
-# create vdata frames that store acceptance data per combination cell pre-post break
-waitB <- data.frame()
-waitA <- data.frame()
-cogB <- data.frame()
-cogA <- data.frame()
-physB <- data.frame()
-physA <- data.frame()
-easyB <- data.frame()
-easyA <- data.frame()
-
-# and for overall proportion accepted
-waitBAll <- numeric()
-waitAAll <- numeric()
-cogBAll <- numeric()
-cogAAll <- numeric()
-physBAll <- numeric()
-physAAll <- numeric() 
-easyBAll <- numeric()
-easyAAll <- numeric()
-
-for (i in seq(nSubsW)){
-
-  # wait
-  tempPropB <- aggregate(waitBefore[[i]]$Choice, by = list(waitBefore[[i]]$Handling, waitBefore[[i]]$Reward), FUN = 'mean')
-  tempPropA <- aggregate(waitAfter[[i]]$Choice, by = list(waitAfter[[i]]$Handling, waitAfter[[i]]$Reward), FUN = 'mean')
-  waitB <- rbind(waitB,tempPropB)
-  waitA <- rbind(waitA,tempPropA)
-  waitBAll[i] <- mean(waitBefore[[i]]$Choice) 
-  waitAAll[i] <- mean(waitAfter[[i]]$Choice)
-
-}
-
-for (i in seq(nSubsC)){
-
-  # cognitive
-  tempPropB <- aggregate(cogBefore[[i]]$Choice, by = list(cogBefore[[i]]$Handling, cogBefore[[i]]$Reward), FUN = 'mean')
-  tempPropA <- aggregate(cogAfter[[i]]$Choice, by = list(cogAfter[[i]]$Handling, cogAfter[[i]]$Reward), FUN = 'mean')
-  cogB <- rbind(cogB,tempPropB)
-  cogA <- rbind(cogA,tempPropA)
-  cogBAll[i] <- mean(cogBefore[[i]]$Choice) 
-  cogAAll[i] <- mean(cogAfter[[i]]$Choice)
-
-}
-
-for (i in seq(nSubsP)){
-
-  # physical
-  tempPropB <- aggregate(physBefore[[i]]$Choice, by = list(physBefore[[i]]$Handling, physBefore[[i]]$Reward), FUN = 'mean')
-  tempPropA <- aggregate(physAfter[[i]]$Choice, by = list(physAfter[[i]]$Handling, physAfter[[i]]$Reward), FUN = 'mean')
-  physB <- rbind(physB,tempPropB)
-  physA <- rbind(physA,tempPropA)
-  physBAll[i] <- mean(physBefore[[i]]$Choice) 
-  physAAll[i] <- mean(physAfter[[i]]$Choice)
-
-}
-
-for (i in seq(nSubsE)){
-
-  # easy
-  tempPropB <- aggregate(easyBefore[[i]]$Choice, by = list(easyBefore[[i]]$Handling, easyBefore[[i]]$Reward), FUN = 'mean')
-  tempPropA <- aggregate(easyAfter[[i]]$Choice, by = list(easyAfter[[i]]$Handling, easyAfter[[i]]$Reward), FUN = 'mean')
-  easyB <- rbind(easyB,tempPropB)
-  easyA <- rbind(easyA,tempPropA)
-  easyBAll[i] <- mean(easyBefore[[i]]$Choice) 
-  easyAAll[i] <- mean(easyAfter[[i]]$Choice)
-
-}
-
-# Pre-post linear models
-prepostLM <- list()
-prepostLM$Wait <- lm(waitBAll ~ waitAAll)
-prepostLM$Cognitive <- lm(cogBAll ~ cogAAll)
-prepostLM$Physical <- lm(physBAll ~ physAAll)
-prepostLM$Easy <- lm(easyBAll ~ easyAAll)
-
-prepostSummary <- do.call(rbind, lapply(prepostLM, function(data) c(coef(data)[2], confint(data)[2,])))
-
+
+temp <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost, Half) %>%
+  summarise(pAccepted = mean(Choice)) %>%
+  ungroup() %>%
+  spread(Half, pAccepted)
+
+# separate by cost type and compute a linear model to predict half 2 from 1
+sep <- temp %>% plyr::dlply("Cost", identity)
+prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})
+
+# get the coefficients and confidence intervals
+# and concatenate
+prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
+colnames(summary_prepost) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
 ```
@@
 ``` {r 16.3.2. Plot Pre/Post, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-
-# overall proportion
-plot(waitBAll,
-     waitAAll,
-     xlim = c(0,1),
-     ylim = c(0,1),
-     main = "Proportion accepted pre- and post-midpoint",
-     xlab = "Acceptance Rate Before",
-     ylab = "Acceptance Rate After",     
-     col = cols[1],
-     pch = 16)
-points(cogBAll,
-       cogAAll, 
-       col = cols[2],
-       pch = 16)
-points(physBAll,
-       physAAll, 
-       col = cols[3],
-       pch = 16)
-points(easyBAll,
-       easyAAll, 
-       col = cols[4],
-       pch = 16)
-lines(seq(0,1,length = 10),
-      seq(0,1,length = 10))
-legend("bottomright",
-       lbls,
-       fill = cols,
-       cex = 0.8)
-
-# dataAll %>%
-#   filter(Choice < 2) %>%
-#   group_by(SubjID) %>%
-#   #mutate(Block = do.call(c, lapply(c(2,4,6), function(x) {rep(x/2, sum(Block %in% c(x-1, x)))}))) %>%
-#   group_by(SubjID, Cost, Block) %>%
-#   summarise(propAccept_subj = mean(Choice)) %>%
-#   group_by(Cost, Block) %>%
-#   summarize(propAccept = mean(propAccept_subj),
-#             seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
-#   ggplot(aes(Block, propAccept, fill = Cost)) +
-#     geom_point(size = 2, pch = 21, color = "black") +
-#     geom_errorbar(aes(ymin=propAccept - seAccept, ymax=propAccept + seAccept, color = Cost), width = 0.1) +
-#     geom_line(aes(color = Cost)) +
-#     ylim(0.5, 1) +
-#     scale_x_continuous(breaks = seq(6)) +
-#     scale_color_manual(values = cols) +
-#     scale_fill_manual(values = cols) +
-#     theme_classic()
+prepost$plot <- dataAll %>%
+                filter(Choice < 2) %>%
+                group_by(SubjID, Cost) %>%
+                summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
+                          propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
+                ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
+                geom_point(size = 3, pch = 21, color = "black") +
+                scale_fill_manual(values = cols) +
+                xlim(0,1) +
+                ylim(0,1) +
+                geom_abline(slope = 1, intercept = 0, lty = 2) +
+                theme(panel.grid.major = element_blank(),
+                    panel.grid.minor = element_blank(),
+                    panel.background = element_blank(),
+                    axis.line = element_line(colour = "black"),
+                    text = element_text(size = 16)))
 ```
@@
 
-| Condition   |            Beta           |          CI-Low           |          CI-High          |
-| :---------- | :-----------------------: | ------------------------: | ------------------------: |
-| Wait        | $`r prepostSummary[1,1]`$ | $`r prepostSummary[1,2]`$ | $`r prepostSummary[1,3]`$ |
-| Cognitive   | $`r prepostSummary[2,1]`$ | $`r prepostSummary[2,2]`$ | $`r prepostSummary[2,3]`$ |
-| Physical    | $`r prepostSummary[3,1]`$ | $`r prepostSummary[3,2]`$ | $`r prepostSummary[3,3]`$ |
-| Easy        | $`r prepostSummary[4,1]`$ | $`r prepostSummary[4,2]`$ | $`r prepostSummary[4,3]`$ |
-Table: Predicting Post-mid acceptance from pre-mid choices: Coefficients and CI.
+``` {r 16.3.2. prepost table, pander}
+panderOptions("digits", 2)
+pander(prepost$summary, style = "rmarkdown", split.table = 110)
+```
 
@@
 ``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-# Estimate gamma per subject for each group separately
-waitOC <- sapply(waitData, function(Data) {optimizeOCModel(Data)$Gamma})
-cogOC <- sapply(cogData, function(Data) {optimizeOCModel(Data)$Gamma})
-physOC <- sapply(physData, function(Data) {optimizeOCModel(Data)$Gamma})
-easyOC <- sapply(easyData, function(Data) {optimizeOCModel(Data)$Gamma})
-
-# Summarize for plotting
-summaryOC <- data.frame(Group = rep(cond, each = nSubsC),
-                        Gamma = c(waitOC, cogOC, physOC, easyOC))
-summaryOC$Group <- factor(summaryOC$Group, levels = cond, ordered = T)
+# group
+summaryOC <- list()
+summaryOC$all <- dataAll %>%
+                 filter(Choice < 2) %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T))
 
 # plot
-ggplot(summaryOC, aes(Group, Gamma, fill = Group)) +
+(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
                       geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
@@
                       scale_fill_manual(values = cols) +
-  theme_classic()
+                      theme(panel.grid.major = element_blank(),
+                        panel.grid.minor = element_blank(),
+                        panel.background = element_blank(),
+                        axis.line = element_line(colour = "black"),
+                        text = element_text(size = 16)))
 
@@
 # Compute the OC for pre-midpoint
-waitOCbefore <- sapply(waitBefore, function(Data) {optimizeOCModel(Data)$Gamma})
-cogOCbefore <- sapply(cogBefore, function(Data) {optimizeOCModel(Data)$Gamma})
-physOCbefore <- sapply(physBefore, function(Data) {optimizeOCModel(Data)$Gamma})
-easyOCbefore <- sapply(easyBefore, function(Data) {optimizeOCModel(Data)$Gamma})
-
-# Percent correctly predicted by pre-midpoint gamma
-# Wait
-predictOCWait <- numeric()
-for (i in seq(nSubsW)) {
-  temp <- (waitAfter[[i]]$Reward > (waitOCbefore[i] * waitAfter[[i]]$Handling))
-  temp[temp == TRUE] <- 1
-  predictOCWait[i] <- (sum(temp==waitAfter[[i]]$Choice) / length(waitAfter[[i]]$Choice)) * 100 
-}
-
-# Cognitive
-predictOCCog <- numeric()
-for (i in seq(nSubsC)) {
-  temp <- (cogAfter[[i]]$Reward > (cogOCbefore[i] * cogAfter[[i]]$Handling))
-  temp[temp == TRUE] <- 1
-  predictOCCog[i] <- (sum(temp==cogAfter[[i]]$Choice) / length(cogAfter[[i]]$Choice)) * 100 
-}
-
-# Physical
-predictOCPhys <- numeric()
-for (i in seq(nSubsW)) {
-  temp <- (physAfter[[i]]$Reward > (physOCbefore[i] * physAfter[[i]]$Handling))
-  temp[temp == TRUE] <- 1
-  predictOCPhys[i] <- (sum(temp==physAfter[[i]]$Choice) / length(physAfter[[i]]$Choice)) * 100 
-}
-
-# Easy
-predictOCEasy <- numeric()
-for (i in seq(nSubsW)) {
-  temp <- (easyAfter[[i]]$Reward > (easyOCbefore[i] * easyAfter[[i]]$Handling))
-  temp[temp == TRUE] <- 1
-  predictOCEasy[i] <- (sum(temp==easyAfter[[i]]$Choice) / length(easyAfter[[i]]$Choice)) * 100 
-}
-
-# Summarize for plotting
-summaryOCPredict <- data.frame(Group = rep(cond, each = nSubsC),
-                        percentPredicted = c(predictOCWait, predictOCCog, predictOCPhys, predictOCEasy))
-summaryOCPredict$Group <- factor(summaryOCPredict$Group, levels = cond, ordered = T)
-
-meanOCPredict <- aggregate(percentPredicted ~ Group, data = summaryOCPredict,FUN = 'mean')
+summaryOC$pre <- dataAll %>%
+                 filter(Choice < 2, Half == "Half_1") %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup() %>%
+                 select(SubjID, Gamma)
+
+# let's add the gammas to the second half data and estimate prop predicted on the second half
+summaryOC$predicted <- dataAll %>%
+                 filter(Choice < 2, Half == "Half_2") %>%
+                 group_by(Cost, SubjID) %>%
+                 left_join(summaryOC$pre) %>%
+                 mutate(OC = Handling * Gamma,
+                        predicted = Reward > OC) %>% 
+                 summarise(percentPredicted = mean(predicted == Choice) * 100)
 
 # plot
-ggplot(summaryOCPredict, aes(Group, percentPredicted, fill = Group)) +
-  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
-  labs(title = "Percent of Choices Correctly Predicted by Gamma per Group", x = "") +
+(summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
+                          labs(x = "") +
                           geom_boxplot(show.legend = F) +
@@
                           ylim(0,100) +
-  theme_classic()
+                          theme(panel.grid.major = element_blank(),
+                          panel.grid.minor = element_blank(),
+                          panel.background = element_blank(),
+                          axis.line = element_line(colour = "black"),
+                          text = element_text(size = 16)))
+
 ```

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
first pass ready, now making sure that Cost 2 knits with in-text variable calls

@@
 The figure shows that participants that over and unceraccepted earned less money overall, as predicted.
-This is supported by a significant quadratic term from the linear model (F = `r round(summaryEarn$fstatistic[1], digits = 2)`, Beta = `r summaryEarn$coefficients[3,1]`, SE = `r round(summaryEarn$coefficients[3,2], digits = 2)`, R-squared = `r round(summaryEarn$r.squared, digits = 2)`; black line shows the fit).
+This is supported by a significant quadratic term from the linear model (F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3,2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`; black line shows the fit).
 The following table shows all the results from the model.
@@
 pander(lmEarn, style = "rmarkdown")
-
 ```
@@
                  group_by(Cost, SubjID) %>%
-                 do(optimizeOCModel(., simplify = T))
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup()
 
@@
 # ANOVA
-anovaOC <- summary(aov(Gamma ~ Group, data = summaryOC))
-Fval <- anovaOC[[1]]$`F value`[1]
-Pval <- anovaOC[[1]]$`Pr(>F)`[1]
-Rsquared_aov <- round(anovaOC[[1]]$`Sum Sq`[1] / sum(anovaOC[[1]]$`Sum Sq`), digits = 2)
+OCanova <- list()
+OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC$all))
+Fval <- OCanova$aov[[1]]$`F value`[1]
+Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
+Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
 
 # Post-hoc pairwise tests
-permuteOCTest <- list()
-permuteOCTest$WvC <- permute(waitOC, cogOC)
-permuteOCTest$WvP <- permute(waitOC, physOC)
-permuteOCTest$WvE <- permute(waitOC, easyOC)
-permuteOCTest$CvP <- permute(cogOC, physOC)
-permuteOCTest$CvE <- permute(cogOC, easyOC)
-permuteOCTest$PvE <- permute(physOC, easyOC)
+OCanova$perms <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(permute), simple = T)
+diag(OCanova$perms) <- 1
+
+OCanova$ES <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(cohenD)) %>%
+  abs()
 ```
@@
 The analysis of variance was significant (F = `r round(Fval, digits = 2)`, p = `r ifelse(Pval < 0.001, "< 0.001", paste("=", round(Pval, digits = 2)))`, R-squared = `r Rsquared_aov`).
-Pairwise post-hoc permutations showed significantly greater values for the wait group versus the cognitive (p = `r ifelse(permuteOCTest$WvC$Pval < 0.001, "< 0.001", paste("=", round(permuteOCTest$WvC$Pval, digits = 2)))`) and easy (p = `r ifelse(permuteOCTest$WvE$Pval < 0.001, "< 0.001", paste("=", round(permuteOCTest$WvE$Pval, digits = 2)))`) groups, as well as significantly greater gammas for the physical group and the cognitive group (p = `r ifelse(permuteOCTest$CvP$Pval < 0.001, "< 0.001", paste("=", round(permuteOCTest$CvP$Pval, digits = 2)))`).
+Pairwise post-hoc permutations are shown in the following matrix.
 These results suggest that participants engaged in cognitively effortful demands experience significantly lower opportunity costs than those whose demands involve physical effort and pure delay.
@@
 
+``` {r 16.3.5. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
+# plot all pairwise comparisons
+corrplot(OCanova$ES,
+         is.corr = F, 
+         p.mat = OCanova$perms,
+         type = "upper",
+         insig = "p-value",
+         sig.level = -1,
+         na.label = "square",
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black", 
+         tl.cex = 0.8,
+         outline = T)
+```
+
 \bigskip
@@
 ``` {r Testing grounds, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}
-cond <- as.character(unique(summaryData$Group))
-
-i <- 1
-test <- allProp2[allProp2$Group == cond[i], ]
-test2 <- trueProp[trueProp$Group == cond[i], ]
-t1 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-  geom_point(size=3, color = cols[i]) +
-  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-  theme_classic()
-
-i <- 2
-test <- allProp2[allProp2$Group == cond[i], ]
-test2 <- trueProp[trueProp$Group == cond[i], ]
-t2 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-  geom_point(size=3, color = cols[i]) +
-  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-  theme_classic()
-
-i <- 3
-test <- allProp2[allProp2$Group == cond[i], ]
-test2 <- trueProp[trueProp$Group == cond[i], ]
-t3 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-  geom_point(size=3, color = cols[i]) +
-  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-  theme_classic()
-
-i <- 4
-test <- allProp2[allProp2$Group == cond[i], ]
-test2 <- trueProp[trueProp$Group == cond[i], ]
-t4 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-  geom_point(size=3, color = cols[i]) +
-  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-  theme_classic()
-
-grid.arrange(t1,t3,t2,t4, ncol = 2)
-
-```
+# cond <- as.character(unique(summaryData$Group))
+# 
+# i <- 1
+# test <- allProp2[allProp2$Group == cond[i], ]
+# test2 <- trueProp[trueProp$Group == cond[i], ]
+# t1 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
+#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
+#   geom_point(size=3, color = cols[i]) +
+#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
+#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
+#   theme_classic()
+# 
+# i <- 2
+# test <- allProp2[allProp2$Group == cond[i], ]
+# test2 <- trueProp[trueProp$Group == cond[i], ]
+# t2 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
+#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
+#   geom_point(size=3, color = cols[i]) +
+#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
+#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
+#   theme_classic()
+# 
+# i <- 3
+# test <- allProp2[allProp2$Group == cond[i], ]
+# test2 <- trueProp[trueProp$Group == cond[i], ]
+# t3 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
+#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
+#   geom_point(size=3, color = cols[i]) +
+#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
+#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
+#   theme_classic()
+# 
+# i <- 4
+# test <- allProp2[allProp2$Group == cond[i], ]
+# test2 <- trueProp[trueProp$Group == cond[i], ]
+# t4 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
+#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
+#   geom_point(size=3, color = cols[i]) +
+#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
+#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
+#   theme_classic()
+# 
+# 
+# grid.arrange(t1,t3,t2,t4, ncol = 2)
+
+```

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
cost 2 script updated to be more readable

@@
 
-``` {r 16.2.1. Overall Proportion/Earnings,fig.align="center",fig.width=10,fig.height=4, echo=FALSE}  
+``` {r 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
 ## ECDF of proportion completed per cost type
@@
 
-grid.arrange(p1, p2, p3, ncol = 3)
+grid.arrange(p2, p3, ncol = 2)
 ```
@@
 mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
-mixCoeffs[is.na(mixCoeffs)] <- 1
+mixCoeffs[is.na(mixCoeffs)] <- 0
 mixCoeffs <- mixCoeffs[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]
@@
 
-``` {r 16.2.3. Mixed Effects Model plot group coefficients, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-# plot coefficient matrix (show pvals!)
-corrplot(abs(mixLogis_mainBetas), 
-         p.mat = mixLogis_mainPvals, 
-         is.corr = F, 
-         method = "color", 
-         tl.col = "black", 
-         tl.srt = 0, 
-         insig = "p-value", 
-         sig.level = -1, 
-         type = "lower",
-         cl.length = 3)
-mtext("Comparison", side = 2, line = 1.5, cex = 1.5)
-mtext("Reference Group", side = 3, line = 1, cex = 1.5, at = 2.5)
-
-```
-
 ``` {r 16.2.3. Plot logistic model, echo=FALSE,fig.align="center",fig.width=6,fig.height=6}
@@
 The figure below shows AIC and BIC for all the models.
-As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2`).
+As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`).
 
@@
 sep <- temp %>% plyr::dlply("Cost", identity)
+prepost <- list()
 prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})
@@
 prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
-colnames(summary_prepost) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
+colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
 ```
@@
 
-``` {r 16.3.2. Plot Pre/Post, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-prepost$plot <- dataAll %>%
+``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
+(prepost$plot <- dataAll %>%
                 filter(Choice < 2) %>%

### 2019-05-08 Cost2/Cost2_prereg_remake.Rmd
matching styles between Cost 2 and 3 reports

@@
 ---
-title: "Effort and Delay Discounting in a Foraging Environment"
+title: "Preregistration analysis, Cost 2 study"
 author: "Claudio Toro Serey & Joseph T. McGuire"
@@
   pdf_document: default
-  fig_caption: yes
-  word_document: default
 ---
-
-# Pre-registration follow-up
 
@@
 
-## Research Questions
-
-#### 3.1.	Do decision makers in foraging environments integrate information about delay durations and reward amounts to produce reward-maximizing behavior?
-
-#### 3.2.	Main question: Are decisions affected differently by equivalent time periods of pure delay, cognitive effort, physical effort, and non-effortful task engagement?
+## 3. Research Questions
+
+### 3.1.
+
+Do decision makers in foraging environments integrate information about delay durations and reward amounts to produce reward-maximizing behavior?
+
+### 3.2.
+
+Main question: Are decisions affected differently by equivalent time periods of pure delay, cognitive effort, physical effort, and non-effortful task engagement?
 Do these four conditions involve different levels of subjective costs?
 
-#### 3.3.	How can we best computationally model the perceived cost of time and effort to predict choices in each condition?
-
-## Hypotheses
-
-#### 4.1.	Single-option, accept/reject decisions will be influenced by within-subject manipulations of reward magnitude and associated delay duration in line with a theoretical reward-maximizing strategy.
+### 3.3.
+
+How can we best computationally model the perceived cost of time and effort to predict choices in each condition?
+
+## 4. Hypotheses
+
+### 4.1.
+
+Single-option, accept/reject decisions will be influenced by within-subject manipulations of reward magnitude and associated delay duration in line with a theoretical reward-maximizing strategy.
+
  **4.1.1.**	Participants will more frequently accept high-reward prospects than low-reward prospects.
@@
 
-#### 4.2.	Prospect acceptance rates will differ across four between-subject conditions, in which the delays associated with rewards (a) are unfilled, (b) include a cognitive effort requirement, (c) include a physical effort requirement, or (d) require a trivial level of physical effort but have matched visual stimuli to the physical effort condition.
+#### 4.2.
+
+Prospect acceptance rates will differ across four between-subject conditions, in which the delays associated with rewards (a) are unfilled, (b) include a cognitive effort requirement, (c) include a physical effort requirement, or (d) require a trivial level of physical effort but have matched visual stimuli to the physical effort condition.
+
   **4.2.1.**	In the cognitive effort condition, overall acceptance rates will be greater than in the unfilled-delay condition.
@@
 
-#### 4.3.	Choices will be well fit by a computational model in which the subjective opportunity cost of time is free to vary across the four between-subject conditions.
+#### 4.3.
+
+Choices will be well fit by a computational model in which the subjective opportunity cost of time is free to vary across the four between-subject conditions.
+
   **4.3.1.**	Participants will display stable preferences, meaning that the reward amounts they accept in a given timing condition will be similar throughout the experiment.
@@
 
-## Analyses
+## 5. Existing data
+
+Registration prior to creation of data
+
+## 6. Data collection
+
+The study will use human subjects recruited from the university community, who will be recruited through the university job board.
+We will pay up to $30 for a session (1 hour), which includes incentive-based rewards.
+Participants will be ineligible if they have participated in our pilot study, or they are under 18 years of age.
+The study will run for however long it takes to reach our desired sample size.
+
+## 7. Sample size
+
+We will acquire a sample of 48 participants.
+
+## 8. Sample size rationale?
+
+Sample sizes were determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four groups (one for each condition).
+The resulting sample size was 45, which we increased to 48 in order to match the potential order of blocks and colors (section 15) while further ensuring that we have enough power.
+
+## 9. Variables
+
+### 9.1 The present study has three levels of manipulation.
+
+9.1.1.
+Cost condition, manipulated within subjects.
+The conditions are (a) unfilled delay, (b) cognitive effort, and (c) physical effort.
+Unfilled delays will be paired with each effort type in a blocked manner (7-minute blocks).
+Each combination will be experienced three times.
+
+9.1.2.
+Handling and travel times.
+These will dictate how long each trial is.
+The "handling time" governs how long it is necessary to wait or work to obtain a reward if a trial is accepted.
+The "travel time" governs how long the inter-trial interval will be, regardless of whether the trial is accepted.
+Participants will know that the handling time will be always 10 seconds, and the travel time 6 seconds (matching one of the between-group experiment conditions).
+
+9.1.3.
+Reward magnitude, manipulated within-subject across individual trials.
+On each trial, participants will learn the amount of money they can earn if they complete the trial (i.e.
+4, 8, or 20 cents).
+The amounts will be sampled uniformly, while guaranteeing that each participant experiences each amount at least twice during each block.
+
+## 10. Measured variables
+
+### 10.1. Behavioral variables
+
+10.1.1. Choice (complete or quit a given trial).
+
+10.1.2. Response times.
+
+10.1.3. Total earnings.
+
+10.1.3. Performance in the cognitive effort tasks (right or wrong answer).
+
+10.1.4. Grip force throughout the experiment and maximum grip strength (physical effort condition).
+
+### 10.2. Questionnaire
+
+10.2.1. Age.
+
+10.2.2. Gender.
+
+10.2.3.
+Post-experimental oral assessment of choice strategy adoption.
+We will ask participants the following: "Did you follow a specific acceptance strategy?
+If so, what was it?" and "Which condition felt most effortful to you?".
+Answers will be written down by the experimenter, and recorded on an excel spreadsheet.
+
+## 11. Indices
+
+### 11.1. Behavioral data
+
+11.1.1. Proportion of prospects accepted.
+
+11.1.2. Percentage of cognitive effort trials with above-threshold errors (over 2 errors), in which participants are forced to travel to the next trial.
+
+### 11.2. Optimal behavior
+
+The theoretical opportunity cost of time will be calculated for each handling/travel/reward acceptance combination in order to assess choice optimality.
+This measure is computed as the cents per second possible when consistently accepting only certain reward amounts (e.g.
+8 and 20 cents) in a given timing condition.
+This ground truth measure is independent of cost type, allowing us to assess subject optimality.
+
+## 12. Study type
+
+Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments.
+This is also known as an intervention experiment and includes randomized controlled trials.
+
+## 13. Blinding
+
+No blinding is involved in this study.
+
+## 14. Study design
+
+The present study complements our previous one, which evaluated cost types through a between-group design.
+Many of the details remain the same.
+However, this time every participant will experience all forms of cost (delay, physical effort, and cognitive effort).
+Delay trials will be intermixed with both physical and cognitive trials, providing a common condition to compare these effortful costs.
+On each trial, participants will have the opportunity to either wait or work for 10 seconds (the "handling time") in order to earn a reward; alternatively, they can quit by pressing the space bar and skip to the next trial (which incurs a 6 second travel time).
+Two types of trial combinations (physical/wait and cognitive/wait) will be experienced three times by each participant in 7-minute-long, interleaved blocks.
+Reward amounts can be 4, 8, or 20 cents, uniformly distributed.
+Timing information will be disclosed at the beginning of each block, and reward prospects displayed before each trial begins.
+
+## 15. Randomization
+
+### 15.1. Block type 
+Each block will contain unfilled delay trials and trials of one effortful cost type (se 14.1).
+Blocks with each cost type will be interleaved, and participants will be assigned to one of two orders: beginning with a cognitive/wait or a physical/wait block.
+A row will be assigned to subject IDs prior to recruitment, ensuring that each order is experienced equally often.
+Participants will be offered a break after completing three out of the six blocks.
+
+### 15.2. Rewards and cost type 
+Participants can earn 4, 8, or 20 cents per trial at the cost of performing one of the three conditions.
+These values are sampled without replacement from a vector containing every combination of cost (effort defined by the current block, and delay) and reward.
+The vector is reshuffled once completed.
+This ensures that each combination of cost and reward is presented at least twice per block.
+
+### 15.3. Trial color 
+During the offer phase, each cost type will appear in a unique color in order to ease its identification.
+Colors were chosen to contrast each other while being amenable to red-green color-blindness.
+Colors will be assigned to each cost type so that all three colors are equally paired to each cost type across participants.
+A row will be assigned to subject IDs prior to recruitment to indicate their block order and color pairing.
+
+## 16. Analyses
 
@@
 
-``` {r Basic Prepping, echo=FALSE}  
-# # params for reference
-# handling <- c(2, 10, 14)
-# cond <- c("Wait", "Cognitive", "Physical", "Easy")
-# 
-# # create data frame with summary stats
-# tempW <- summarizeData()
-# tempC <- summarizeData(Data = cogData, nSubs = nSubsC, type = "Cognitive")
-# tempP <- summarizeData(Data = physData, nSubs = nSubsP, type = "Physical")
-# tempE <- summarizeData(Data = easyData, nSubs = nSubsE, type = "Easy")
-# 
-# summaryData <- rbind(tempW,
-#                      tempC,
-#                      tempP,
-#                      tempE)
-# 
-# colnames(summaryData) <- c("Group", "propComplete", "Earnings", "RT", "forcedTravel")
-# 
-# summaryData$Cols <- c(rep(cols[1],nSubsW), rep(cols[2],nSubsC), rep(cols[3],nSubsP), rep(cols[4],nSubsE))
-# rm(tempW, tempC, tempP, tempE)
-# 
-# # Indexes for groups
-# indxWait <- seq(nSubsW)
-# indxWaitLong <- seq(nSubsW * 9) # 9 being the number of combinations
-# indxCog <- (nSubsW + 1):(nSubsW + nSubsC)
-# indxCogLong <- ((nSubsW * 9) + 1):((nSubsW * 9) + (nSubsC * 9))
-# indxPhys <- ((nSubsW + nSubsC) + 1):(nSubsW + nSubsC + nSubsP)
-# indxPhysLong <- ((nSubsW * 9) + (nSubsC * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9))
-# indxEasy <- ((nSubsW + nSubsC + nSubsP) + 1):totalSubs #(nSubsW + nSubsC + nSubsP + nSubsE)
-# indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))
-# 
-# 
-# # the other, just summarizing for all participants
-# # Not sure if this is necessary anymore
-# # allProp <- data.frame(Group = c(rep("Wait",nSubsW*3),
-# #                                 rep("Cognitive",nSubsC*3),
-# #                                 rep("Physical",nSubsP*3)),
-# #                       Handling = c(rep(2,nSubsW), rep(10,nSubsW), rep(14,nSubsW),
-# #                                    rep(2,nSubsC), rep(10,nSubsC), rep(14,nSubsC), 
-# #                                    rep(2,nSubsP), rep(10,nSubsP), rep(14,nSubsP)),
-# #                       FivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
-# #                       TenPts = rep(NA,(nSubsW + nSubsC + nSubsP)*9),
-# #                       TwntyfivePts = rep(NA,(nSubsW + nSubsC + nSubsP)*9))
-# 
-# 
-# # Get the proportion completed per combination for GLMs
-# tempW <- propComplete()
-# tempC <- propComplete(Data = cogData, nSubs = nSubsC, indx = indxCog, type = "Cognitive")
-# tempP <- propComplete(Data = physData, nSubs = nSubsP, indx = indxPhys, type = "Physical")
-# tempE <- propComplete(Data = easyData, nSubs = nSubsE, indx = indxEasy, type = "Easy")
-# 
-# allProp2 <- rbind(tempW,
-#                   tempC,
-#                   tempP,
-#                   tempE)  
-# allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials
-# 
-# rm(tempW, tempC, tempP, tempE)
-# 
-# # add optimal vector and difference from optimal
-# wait <- c(rep(1,nSubsW*3),
-#           c(rep(0,nSubsW), rep(1,nSubsW*2)),
-#           c(rep(0,nSubsW*2), rep(1,nSubsW)))
-# cog <- c(rep(1,nSubsC*3),
-#           c(rep(0,nSubsC), rep(1,nSubsC*2)),
-#           c(rep(0,nSubsC*2), rep(1,nSubsC)))
-# phys <- c(rep(1,nSubsP*3),
-#           c(rep(0,nSubsP), rep(1,nSubsP*2)),
-#           c(rep(0,nSubsP*2), rep(1,nSubsP)))
-# easy <- c(rep(1,nSubsE*3),
-#           c(rep(0,nSubsE), rep(1,nSubsE*2)),
-#           c(rep(0,nSubsE*2), rep(1,nSubsE)))
-# allProp2$Optimal <- c(wait,cog,phys,easy)
-# allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete
-# 
-# # sort by subject ID
-# #allProp2 <- allProp2[order(allProp2$SubjID),]
-# 
-# # actual proportions and standard errors, and the optimal summary for plotting
-# trueProp <- aggregate(allProp2$propComplete,
-#             by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-#             FUN = 'mean')
-# 
-# trueSD <- aggregate(allProp2$propComplete,
-#           by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-#           FUN = 'sd')
-# colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
-# trueProp$SE[1:9] <- (trueSD$x[1:9])/(sqrt(nSubsW))
-# trueProp$SE[10:18] <- (trueSD$x[10:18])/(sqrt(nSubsC))
-# trueProp$SE[19:27] <- (trueSD$x[19:27])/(sqrt(nSubsP))
-# trueProp$SE[28:36] <- (trueSD$x[28:36])/(sqrt(nSubsE))
-# 
-# trueProp$Optimal <- aggregate(allProp2$Optimal,
-#             by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-#             FUN = 'mean')$x
-```
-
 #### 16.1.	Tests of whether decision makers integrate delay and reward information.
@@
 qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
-  labs(title = "Handling and Reward Coefficients", x = "", y = "Coefficients") +
+  labs(y = "Coefficients") +
   geom_hline(yintercept = 0, linetype = "dashed") +
@@
 ```
+
+## 17. Inference criteria
+
+These criteria will remain the same as before.
+For the ANOVAs, we will report the F statistic as well as the p-value.
+For the multiple linear regressions and logistic regression, we will report the betas (coefficients) and their associated p-values.
+When comparing two groups of values as in pairwise comparisons, we will use non-parametric permutation tests.
+We will report p-values and effect sizes, and all tests will be two-tailed.
+The alpha threshold for p-value evaluation will be set at 0.05.
+
+## 18. Data exclusion
+
+### 18.1. Missing data and quitting early.
+
+Participants are told that they are allowed to stop participation in the study at any time without consequence.
+Data from participants who do not finish the experiment will be excluded from the study, and those participants will be replaced.
+
+### 18.2. Inattentiveness
+
+To guard against inattentiveness, a single 30 second catch trial will be placed at the end of each experimental block, merely prompting participants to press a key.
+From the pilot study, participants are able to respond within three seconds.
+Based on this, a response within three seconds will be considered as proper engagement, and a participant that fails two or more of these checks will be excluded and replaced.
+
+### 18.3. Reasonable choices
+
+The task is structured so that one reward amount must always be accepted.
+Thus, a participant who quits every trial in at least one block will be assumed not to have followed or understood task instructions, or to have disengaged from the task altogether, and will be excluded and replaced.
+
+### 18.4. Performance
+
+In the cognitive effort condition, participants were forced to travel if they made 2 mistakes in a trial. Any participant with more than 30% forced travels will be excluded and replaced.

### 2019-05-09 Cost2/Cost2_prereg.Rmd
slight changes to plots

@@
 
-#### 4.2.	Prospect acceptance rates will differ across four between-subject conditions, in which the delays associated with rewards (a) are unfilled, (b) include a cognitive effort requirement, (c) include a physical effort requirement, or (d) require a trivial level of physical effort but have matched visual stimuli to the physical effort condition.
+### 4.2.
+
+Prospect acceptance rates will differ across four between-subject conditions, in which the delays associated with rewards (a) are unfilled, (b) include a cognitive effort requirement, (c) include a physical effort requirement, or (d) require a trivial level of physical effort but have matched visual stimuli to the physical effort condition.
+
   **4.2.1.**	In the cognitive effort condition, overall acceptance rates will be greater than in the unfilled-delay condition.
@@
 
-#### 4.3.	Choices will be well fit by a computational model in which the subjective opportunity cost of time is free to vary across the four between-subject conditions.
+### 4.3.
+
+Choices will be well fit by a computational model in which the subjective opportunity cost of time is free to vary across the four between-subject conditions.
+
   **4.3.1.**	Participants will display stable preferences, meaning that the reward amounts they accept in a given timing condition will be similar throughout the experiment.
@@
 \bigskip
+
+## 5. Existing data
+
+Registration prior to creation of data
+
+## 6. Data collection
+
+The study will use human subjects recruited from the university community, who will be recruited through the university job board.
+We will pay up to $30 for a session (1 hour), which includes incentive-based rewards.
+Participants will be ineligible if they have participated in our pilot study, or they are under 18 years of age.
+The study will run for however long it takes to reach our desired sample size.
+
+## 7. Sample size
+
+We will acquire a sample of 48 participants.
+
+## 8. Sample size rationale?
+
+Sample sizes were determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four groups (one for each condition).
+The resulting sample size was 45, which we increased to 48 in order to match the potential order of blocks and colors (section 15) while further ensuring that we have enough power.
+
+## 9. Variables
+
+### 9.1 The present study has three levels of manipulation.
+
+9.1.1.
+Cost condition, manipulated within subjects.
+The conditions are (a) unfilled delay, (b) cognitive effort, and (c) physical effort.
+Unfilled delays will be paired with each effort type in a blocked manner (7-minute blocks).
+Each combination will be experienced three times.
+
+9.1.2.
+Handling and travel times.
+These will dictate how long each trial is.
+The "handling time" governs how long it is necessary to wait or work to obtain a reward if a trial is accepted.
+The "travel time" governs how long the inter-trial interval will be, regardless of whether the trial is accepted.
+Participants will know that the handling time will be always 10 seconds, and the travel time 6 seconds (matching one of the between-group experiment conditions).
+
+9.1.3.
+Reward magnitude, manipulated within-subject across individual trials.
+On each trial, participants will learn the amount of money they can earn if they complete the trial (i.e.
+4, 8, or 20 cents).
+The amounts will be sampled uniformly, while guaranteeing that each participant experiences each amount at least twice during each block.
+
+## 10. Measured variables
+
+### 10.1. Behavioral variables
+
+10.1.1. Choice (complete or quit a given trial).
+
+10.1.2. Response times.
+
+10.1.3. Total earnings.
+
+10.1.3. Performance in the cognitive effort tasks (right or wrong answer).
+
+10.1.4. Grip force throughout the experiment and maximum grip strength (physical effort condition).
+
+### 10.2. Questionnaire
+
+10.2.1. Age.
+
+10.2.2. Gender.
+
+10.2.3.
+Post-experimental oral assessment of choice strategy adoption.
+We will ask participants the following: "Did you follow a specific acceptance strategy?
+If so, what was it?" and "Which condition felt most effortful to you?".
+Answers will be written down by the experimenter, and recorded on an excel spreadsheet.
+
+## 11. Indices
+
+### 11.1. Behavioral data
+
+11.1.1. Proportion of prospects accepted.
+
+11.1.2. Percentage of cognitive effort trials with above-threshold errors (over 2 errors), in which participants are forced to travel to the next trial.
+
+### 11.2. Optimal behavior
+
+The theoretical opportunity cost of time will be calculated for each handling/travel/reward acceptance combination in order to assess choice optimality.
+This measure is computed as the cents per second possible when consistently accepting only certain reward amounts (e.g.
+8 and 20 cents) in a given timing condition.
+This ground truth measure is independent of cost type, allowing us to assess subject optimality.
+
+## 12. Study type
+
+Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments.
+This is also known as an intervention experiment and includes randomized controlled trials.
+
+## 13. Blinding
+
+No blinding is involved in this study.
+
+## 14. Study design
+
+The present study complements our previous one, which evaluated cost types through a between-group design.
+Many of the details remain the same.
+However, this time every participant will experience all forms of cost (delay, physical effort, and cognitive effort).
+Delay trials will be intermixed with both physical and cognitive trials, providing a common condition to compare these effortful costs.
+On each trial, participants will have the opportunity to either wait or work for 10 seconds (the "handling time") in order to earn a reward; alternatively, they can quit by pressing the space bar and skip to the next trial (which incurs a 6 second travel time).
+Two types of trial combinations (physical/wait and cognitive/wait) will be experienced three times by each participant in 7-minute-long, interleaved blocks.
+Reward amounts can be 4, 8, or 20 cents, uniformly distributed.
+Timing information will be disclosed at the beginning of each block, and reward prospects displayed before each trial begins.
+
+## 15. Randomization
+
+### 15.1. Block type 
+Each block will contain unfilled delay trials and trials of one effortful cost type (se 14.1).
+Blocks with each cost type will be interleaved, and participants will be assigned to one of two orders: beginning with a cognitive/wait or a physical/wait block.
+A row will be assigned to subject IDs prior to recruitment, ensuring that each order is experienced equally often.
+Participants will be offered a break after completing three out of the six blocks.
+
+### 15.2. Rewards and cost type 
+Participants can earn 4, 8, or 20 cents per trial at the cost of performing one of the three conditions.
+These values are sampled without replacement from a vector containing every combination of cost (effort defined by the current block, and delay) and reward.
+The vector is reshuffled once completed.
+This ensures that each combination of cost and reward is presented at least twice per block.
+
+### 15.3. Trial color 
+During the offer phase, each cost type will appear in a unique color in order to ease its identification.
+Colors were chosen to contrast each other while being amenable to red-green color-blindness.
+Colors will be assigned to each cost type so that all three colors are equally paired to each cost type across participants.
+A row will be assigned to subject IDs prior to recruitment to indicate their block order and color pairing.
+
+## 16. Analyses
 
@@
 ### data loading and cleaning up
-
-# load cognitive effort group
-setwd('./data/')
-temp = list.files(pattern="cogTask")
-cogDataLong = lapply(temp, read.csv, header = FALSE)
-
-# load wait group
-temp = list.files(pattern="wait")
-waitDataLong = lapply(temp, read.csv, header = FALSE)
-
-# load physical group
-temp = list.files(pattern="phys")
-physDataLong = lapply(temp, read.csv, header = FALSE)
-
-# load pheasysical group
-temp = list.files(pattern="pheasy")
-easyDataLong = lapply(temp, read.csv, header = FALSE)
-
-### cleaning data
-# this will generate a simple list with only info about trials that participants quit or completed
-# this is because cognitive logs also include within-trial task-specific information
-# for the wait condition, it will get rid of the break indicator
-
-nSubsW <- length(waitDataLong)
-nSubsC <- length(cogDataLong)
-nSubsP <- length(physDataLong)
-nSubsE <- length(easyDataLong)
-totalSubs <- (nSubsW + nSubsC + nSubsP + nSubsE)
-
-#  short lists
-cogData <- list()
-waitData <- list()
-physData <- list()
-easyData <- list()
-
-# For pre-post analysis
-cogBefore <- list()
-cogAfter <- list()
-waitBefore <- list()
-waitAfter <- list()
-physBefore <- list()
-physAfter <- list()
-easyBefore <- list()
-easyAfter <- list()
-
-# clean wait group data
-for (subject in seq(nSubsW)){
-
-  # Before/after
-  breakW <- which(waitDataLong[[subject]]$V1 == 0)
-
-  waitBefore[[subject]] <- waitDataLong[[subject]][1:(breakW - 1),]
-  waitAfter[[subject]] <- waitDataLong[[subject]][(breakW + 1):length(waitDataLong[[subject]]$V1),]
-
-  # assign header names
-  colnames(waitBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-  colnames(waitAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-  # Overall data cleaning
-  tempW <- waitDataLong[[subject]]$V1 != 0
-
-  # create a new list with only decision trials / without break
-  waitData[[subject]] <- waitDataLong[[subject]][tempW,]
-
-  # assign header names
-  colnames(waitData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-}
-
-# clean cognitive group data
-for (subject in seq(nSubsC)){
-
-  # Before/After
-  breakC <- which(cogDataLong[[subject]]$V1 == 0)
-
-  cogBefore[[subject]] <- cogDataLong[[subject]][1:(breakC-1),]
-  temp <- cogBefore[[subject]]$V7 # trial outcome vector
-  quitTrials <- grep("Quit",temp)
-  completeTrials <- grep("Reward",temp)
-  decisionTrials <- sort(c(quitTrials,completeTrials))
-  cogBefore[[subject]] <- cogBefore[[subject]][decisionTrials,]
-
-  cogAfter[[subject]] <- cogDataLong[[subject]][(breakC+1):length(cogDataLong[[subject]]$V1),]
-  temp <- cogAfter[[subject]]$V7 # trial outcome vector
-  quitTrials <- grep("Quit",temp)
-  completeTrials <- grep("Reward",temp)
-  decisionTrials <- sort(c(quitTrials,completeTrials))
-  cogAfter[[subject]] <- cogAfter[[subject]][decisionTrials,]
-
-  colnames(cogBefore[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
-                                      "Experiment Time","Trial Outcome","Task Type","Task Setup")
-  colnames(cogAfter[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
-                                     "Experiment Time","Trial Outcome","Task Type","Task Setup")
-
-  # Overall data cleaning
-  # create an index for the trials in which a decision was made (completed, quit) 
-  temp <- cogDataLong[[subject]]$V7 # trial outcome vector
-  quitTrials <- grep("Quit",temp)
-  completeTrials <- grep("Reward",temp)
-  decisionTrials <- sort(c(quitTrials,completeTrials))
-
-  # create a new list with only decision trials / without break
-  tempC <- cogDataLong[[subject]]$V1 != 0  
-  cogData[[subject]] <- cogDataLong[[subject]][decisionTrials,]
-  cogDataLong[[subject]] <- cogDataLong[[subject]][tempC,]
-
-  colnames(cogData[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
-                                    "Experiment Time","Trial Outcome","Task Type","Task Setup")
-  colnames(cogDataLong[[subject]]) <- c("Handling","Reward","Choice","Task RT","Choice RT",
-                                        "Experiment Time","Trial Outcome","Task Type","Task Setup") # Long contains within-trial info
-
-}
-
-# clean physical group data
-for (subject in seq(nSubsP)){
-
-  # Before/After
-  breakP <- which(physDataLong[[subject]]$V1 == 0)
-
-  physBefore[[subject]] <- physDataLong[[subject]][1:(breakP - 1),]
-  physAfter[[subject]] <- physDataLong[[subject]][(breakP + 1):length(physDataLong[[subject]]$V1),]
-
-  colnames(physBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-  colnames(physAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-  # create a new list with only decision trials / without break  
-  tempP <- physDataLong[[subject]]$V1 != 0
-  physData[[subject]] <- physDataLong[[subject]][tempP,]
-  colnames(physData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-}
-
-# clean pheaysical group data
-for (subject in seq(nSubsE)){
-
-  # Before/After
-  breakE <- which(easyDataLong[[subject]]$V1 == 0)
-
-  easyBefore[[subject]] <- easyDataLong[[subject]][1:(breakE - 1),]
-  easyAfter[[subject]] <- easyDataLong[[subject]][(breakE + 1):length(easyDataLong[[subject]]$V1),]
-
-  colnames(easyBefore[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-  colnames(easyAfter[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-  # create a new list with only decision trials / without break  
-  tempE <- easyDataLong[[subject]]$V1 != 0
-  easyData[[subject]] <- easyDataLong[[subject]][tempE,]
-  colnames(easyData[[subject]]) <- c("Handling","Reward","Choice","RT","Experiment Time")
-
-}
-
-# Combine before/after across subjects
-cBefore <- rbind(cogBefore[[1]],cogBefore[[2]]) 
-cAfter <- rbind(cogAfter[[1]],cogAfter[[2]]) 
-wBefore <- rbind(waitBefore[[1]],waitBefore[[2]]) 
-wAfter <- rbind(waitAfter[[1]],waitAfter[[2]]) 
-pBefore <- rbind(easyBefore[[1]],physBefore[[2]])
-pAfter <- rbind(physAfter[[1]],physAfter[[2]])
-eBefore <- rbind(easyBefore[[1]],easyBefore[[2]])
-eAfter <- rbind(easyAfter[[1]],easyAfter[[2]])
-
-for (i in 3:nSubsW){
-
-    wBefore <- rbind(wBefore,waitBefore[[i]])
-    wAfter <- rbind(wAfter,waitAfter[[i]])
-
-}
-
-for (i in 3:nSubsC){
-
-    cBefore <- rbind(cBefore,cogBefore[[i]])  
-    cAfter <- rbind(cAfter,cogAfter[[i]])
-
-}
-
-for (i in 3:nSubsP){
-
-    pBefore <- rbind(pBefore,physBefore[[i]])
-    pAfter <- rbind(pAfter,physAfter[[i]])
-
-}
-
-for (i in 3:nSubsE){
-
-    eBefore <- rbind(eBefore,easyBefore[[i]])
-    eAfter <- rbind(eAfter,easyAfter[[i]])
-
-}
-
-#rm(cogBefore,cogAfter,waitBefore,waitAfter)
-
-# aggregate ADD PHYS
-waitBeforeAll <- aggregate(wBefore$Choice,
-          by = list(wBefore$Reward, wBefore$Handling),
-          FUN = 'mean')
-waitAfterAll <- aggregate(wAfter$Choice,
-          by = list(wAfter$Reward, wAfter$Handling),
-          FUN = 'mean')
-cogBeforeAll <- aggregate(cBefore$Choice,
-          by = list(cBefore$Reward, cBefore$Handling),
-          FUN = 'mean')
-cogAfterAll <- aggregate(cAfter$Choice,
-          by = list(cAfter$Reward, cAfter$Handling),
-          FUN = 'mean')
-physBeforeAll <- aggregate(pBefore$Choice,
-          by = list(pBefore$Reward, pBefore$Handling),
-          FUN = 'mean')
-physAfterAll <- aggregate(pAfter$Choice,
-          by = list(pAfter$Reward, pAfter$Handling),
-          FUN = 'mean')
-easyBeforeAll <- aggregate(eBefore$Choice,
-          by = list(eBefore$Reward, eBefore$Handling),
-          FUN = 'mean')
-easyAfterAll <- aggregate(eAfter$Choice,
-          by = list(eAfter$Reward, eAfter$Handling),
-          FUN = 'mean')
-
-rm(cBefore,cAfter,wBefore,wAfter, pBefore, pAfter, eBefore, eAfter)
-
-# remove unnecessary variables
-rm(temp,tempW,tempC,quitTrials,completeTrials,decisionTrials,subject)
-```
-
-``` {r Basic Prepping, echo=FALSE}  
-# params for reference
-handling <- c(2, 10, 14)
-cond <- c("Wait", "Cognitive", "Physical", "Easy")
-
-# create data frame with summary stats
-tempW <- summarizeData()
-tempC <- summarizeData(Data = cogData, nSubs = nSubsC, type = "Cognitive")
-tempP <- summarizeData(Data = physData, nSubs = nSubsP, type = "Physical")
-tempE <- summarizeData(Data = easyData, nSubs = nSubsE, type = "Easy")
-
-summaryData <- rbind(tempW,
-                     tempC,
-                     tempP,
-                     tempE)
-
-colnames(summaryData) <- c("Group", "propComplete", "Earnings", "RT", "forcedTravel")
-
-summaryData$Cols <- c(rep(cols[1],nSubsW), rep(cols[2],nSubsC), rep(cols[3],nSubsP), rep(cols[4],nSubsE))
-rm(tempW, tempC, tempP, tempE)
-
-# Indexes for groups
-indxWait <- seq(nSubsW)
-indxWaitLong <- seq(nSubsW * 9) # 9 being the number of combinations
-indxCog <- (nSubsW + 1):(nSubsW + nSubsC)
-indxCogLong <- ((nSubsW * 9) + 1):((nSubsW * 9) + (nSubsC * 9))
-indxPhys <- ((nSubsW + nSubsC) + 1):(nSubsW + nSubsC + nSubsP)
-indxPhysLong <- ((nSubsW * 9) + (nSubsC * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9))
-indxEasy <- ((nSubsW + nSubsC + nSubsP) + 1):totalSubs #(nSubsW + nSubsC + nSubsP + nSubsE)
-indxEasyLong <- ((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + 1):((nSubsW * 9) + (nSubsC * 9) + (nSubsP * 9) + (nSubsE * 9))
-
-# Get the proportion completed per combination for GLMs
-tempW <- propComplete()
-tempC <- propComplete(Data = cogData, nSubs = nSubsC, indx = indxCog, type = "Cognitive")
-tempP <- propComplete(Data = physData, nSubs = nSubsP, indx = indxPhys, type = "Physical")
-tempE <- propComplete(Data = easyData, nSubs = nSubsE, indx = indxEasy, type = "Easy")
-
-allProp2 <- rbind(tempW,
-                  tempC,
-                  tempP,
-                  tempE)  
-allProp2$totalComplete <- allProp2$propComplete * allProp2$totalTrials
-
-rm(tempW, tempC, tempP, tempE)
-
-# add optimal vector and difference from optimal
-wait <- c(rep(1,nSubsW*3),
-          c(rep(0,nSubsW), rep(1,nSubsW*2)),
-          c(rep(0,nSubsW*2), rep(1,nSubsW)))
-cog <- c(rep(1,nSubsC*3),
-          c(rep(0,nSubsC), rep(1,nSubsC*2)),
-          c(rep(0,nSubsC*2), rep(1,nSubsC)))
-phys <- c(rep(1,nSubsP*3),
-          c(rep(0,nSubsP), rep(1,nSubsP*2)),
-          c(rep(0,nSubsP*2), rep(1,nSubsP)))
-easy <- c(rep(1,nSubsE*3),
-          c(rep(0,nSubsE), rep(1,nSubsE*2)),
-          c(rep(0,nSubsE*2), rep(1,nSubsE)))
-allProp2$Optimal <- c(wait,cog,phys,easy)
-allProp2$Deviation <- allProp2$Optimal - allProp2$propComplete
-
-# sort by subject ID
-#allProp2 <- allProp2[order(allProp2$SubjID),]
-
-# actual proportions and standard errors, and the optimal summary for plotting
-trueProp <- aggregate(allProp2$propComplete,
-            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-            FUN = 'mean')
-
-trueSD <- aggregate(allProp2$propComplete,
-          by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-          FUN = 'sd')
-colnames(trueProp) <- c("Reward","Handling","Group","propComplete")
-trueProp$SE[1:9] <- (trueSD$x[1:9])/(sqrt(nSubsW))
-trueProp$SE[10:18] <- (trueSD$x[10:18])/(sqrt(nSubsC))
-trueProp$SE[19:27] <- (trueSD$x[19:27])/(sqrt(nSubsP))
-trueProp$SE[28:36] <- (trueSD$x[28:36])/(sqrt(nSubsE))
-
-trueProp$Optimal <- aggregate(allProp2$Optimal,
-            by = list(allProp2$Reward, allProp2$Handling, allProp2$Group),
-            FUN = 'mean')$x
-```
-
-## Analyses
+setwd("./data")
+files <- dir(pattern = '_log.csv')
+nSubjs <- length(files)
+
+dataAll <- tibble(SubjID = files) %>%
+  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
+  mutate(Cost = substring(SubjID, 5, 8),
+         Cost = case_when(Cost == "wait" ~ "Wait",
+                          Cost == "cogT" ~ "Cognitive",
+                          Cost == "phys" ~ "Physical",
+                          Cost == "phea" ~ "Easy"),
+         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
+  unnest() %>%
+  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"),
+         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
+         optimal = case_when(
+          (Handling == 10 & Reward < 8) ~ 0,
+          (Handling == 14 & Reward < 20) ~ 0,
+          TRUE ~ 1
+         ))
+
+# get a simple subject list and the number of subjects
+subjList <- unique(dataAll$SubjID)
+nSubj <- length(subjList)
+
+```
 
@@
 
-``` {r 16.1.1., fig.align="center", fig.width=4, fig.height=4, echo=FALSE}
-# Add an AR predictor based on the number of quits
-waitData <- lapply(waitData, function(data) data %>% mutate(AR = seqQuits(Choice)))
-cogData <- lapply(cogData, function(data) data %>% mutate(AR = seqQuits(Choice)))
-physData <- lapply(physData, function(data) data %>% mutate(AR = seqQuits(Choice)))
-easyData <- lapply(easyData, function(data) data %>% mutate(AR = seqQuits(Choice)))
-
-# Logistic fits
-waitLogis <- lapply(waitData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
-cogLogis <- lapply(cogData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
-physLogis <- lapply(physData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
-easyLogis <- lapply(easyData, function(data) glm(Choice ~ Handling + Reward, data = data, family = "binomial"))
-
-# Coefficients
-waitLogis_coeffs <- t(sapply(waitLogis, "[[", "coefficients"))
-cogLogis_coeffs <- t(sapply(cogLogis, "[[", "coefficients"))
-physLogis_coeffs <- t(sapply(physLogis, "[[", "coefficients"))
-easyLogis_coeffs <- t(sapply(easyLogis, "[[", "coefficients"))
-allLogis_coeffs <- rbind(waitLogis_coeffs,
-                         cogLogis_coeffs,
-                         physLogis_coeffs,
-                         easyLogis_coeffs)
-
-# Rank sums
-rankHand <- wilcox.test(allLogis_coeffs[,2])
-rankReward <- wilcox.test(allLogis_coeffs[,3])
+``` {r 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
+# filterout errors and compute R + H logistic per subject, then get coefficients
+logisRH <- dataAll %>%
+  filter(Choice < 2) %>%
+  plyr::dlply("SubjID", identity) %>%
+  lapply(function(data) {glm(Choice ~ Handling + Reward, data = data, family = "binomial")}) %>%
+  sapply(coefficients)
+
+# Rank sum tests
+rankHand <- wilcox.test(logisRH["Handling", ])
+rankReward <- wilcox.test(logisRH["Reward", ])
 
 # Plot coeffs
-temp <- melt(allLogis_coeffs[,2:3])
-qplot(data = temp, x = Var2, y = value, geom = "boxplot") + 
-  labs(title = "Handling and Reward Coefficients", x = "", y = "Coefficients") +
-  geom_hline(yintercept = 0, alpha = 0.5) +
-  theme_classic()
-
-rm(waitLogis, cogLogis, physLogis, easyLogis)
-
+temp <- melt(logisRH[c("Handling", "Reward"), ])
+qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
+  labs(y = "Coefficients") +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  theme(legend.position = c(0.9, 0.7),
+       panel.grid.major = element_blank(), 
+       panel.grid.minor = element_blank(), 
+       panel.background = element_blank(), 
+       axis.line = element_line(colour = "black"),
+       text = element_text(size = 16))
 ```
@@
 
-``` {r 16.1.2., echo=FALSE, fig.align="center"}
-# Logistic fits
-waitLogis <- lapply(waitData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
-cogLogis <- lapply(cogData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
-physLogis <- lapply(physData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
-easyLogis <- lapply(easyData, function(data) glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial"))
-
-# Coefficients
-waitLogis_coeffs <- t(sapply(waitLogis, "[[", "coefficients"))
-cogLogis_coeffs <- t(sapply(cogLogis, "[[", "coefficients"))
-physLogis_coeffs <- t(sapply(physLogis, "[[", "coefficients"))
-easyLogis_coeffs <- t(sapply(easyLogis, "[[", "coefficients"))
-allLogis_coeffs <- rbind(waitLogis_coeffs,
-                         cogLogis_coeffs,
-                         physLogis_coeffs,
-                         easyLogis_coeffs)
-
-#waitLogis_coeffs <- sapply(waitLogis, function(data) (confint(data)[4,1] < 0 & confint(data)[4,2] > 0))
+``` {r 16.1.2., echo = FALSE, include = FALSE}
+# add an AR regressor to track recent quits
+logisRHAR <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID) %>%
+  mutate(AR = seqQuits(Choice)) %>%
+  plyr::dlply("SubjID", identity) %>%
+  lapply(function(data) {glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial")})
 
 # Rank sums
-rankAR <- wilcox.test(allLogis_coeffs[,4])
-
-# Plot coeffs
-temp <- melt(allLogis_coeffs[,2:4])
-
-# The ugliest code, to check the existence of 0 on the CIs
-AR_CIs <- data.frame(Subj = NULL, Low = NULL, High = NULL)
-temp <- data.frame(Subj = seq(nSubsW), Low = rep(-0.1,nSubsW), High = rep(0,nSubsW))
-for (i in seq(length(waitLogis))) {
-  test <- tryCatch(round(confint(waitLogis[[i]]), digits = 2)[4,], error=function(e){})
-  if(!is.null(test)) {
-    temp$Low[i] <- test[1]
-    temp$High[i] <- test[2]
-  }
-}
-AR_CIs <- rbind(AR_CIs, temp)
-temp <- data.frame(Subj = seq(nSubsC), Low = rep(0,nSubsC), High = rep(0,nSubsC))
-for (i in seq(length(cogLogis))) {
-  test <- tryCatch(round(confint(cogLogis[[i]]), digits = 2)[4,], error=function(e){})
-  if(!is.null(test)) {
-    temp$Low[i] <- test[1]
-    temp$High[i] <- test[2]
-  }
-}
-AR_CIs <- rbind(AR_CIs, temp)
-temp <- data.frame(Subj = seq(nSubsP), Low = rep(0,nSubsP), High = rep(0,nSubsP))
-for (i in seq(length(physLogis))) {
-  test <- tryCatch(round(confint(physLogis[[i]]), digits = 2)[4,], error=function(e){})
-  if(!is.null(test)) {
-    temp$Low[i] <- test[1]
-    temp$High[i] <- test[2]
-  }
-}
-AR_CIs <- rbind(AR_CIs, temp)
-temp <- data.frame(Subj = seq(nSubsE), Low = rep(0,nSubsE), High = rep(0,nSubsE))
-for (i in seq(length(easyLogis))) {
-  test <- tryCatch(round(confint(easyLogis[[i]]), digits = 2)[4,], error=function(e){})
-  if(!is.null(test)) {
-    temp$Low[i] <- test[1]
-    temp$High[i] <- test[2]
-  }
-}
-AR_CIs <- rbind(AR_CIs, temp)
-AR_CIs$High[is.na(AR_CIs$High)] <- 0.1
-AR_CIs$AR_Effect <- apply(AR_CIs,1, function(x) !(x[2] <= 0 & x[3] >= 0))
+rankAR <- logisRHAR %>% 
+  sapply(coefficients) %>%
+  wilcox.test(.["AR", ])
+
+AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(confint(x)[4, ], error = function(e){c(0, 0)})}) %>%
+  replace_na(0) %>%
+  t() %>% 
+  apply(1, function(x) !(x[1] <= 0 & x[2] >= 0))
 
 # Around 10% seemed to have been influenced by previous quitting
-propAR_effects <- (sum(AR_CIs$AR_Effect) / totalSubs) * 100
-
-rm(temp,waitLogis, cogLogis, physLogis, easyLogis)
-
+prcntAR_effects <- mean(AR_CIs) * 100
 ```
@@
 pander(lmEarn, style = "rmarkdown")
-
-```
-
-\bigskip
-
-  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances-either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
+```
+
+\bigskip
+
+  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances--either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
 This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*
@@
 
-``` {r 16.2.1. Overall Proportion/Earnings,fig.align="center",fig.width=10,fig.height=4, echo=FALSE}  
-## prop complete
-# ecdfs
-wait <- ecdf(summaryData$propComplete[indxWait])
-cog <- ecdf(summaryData$propComplete[indxCog])
-phys <- ecdf(summaryData$propComplete[indxPhys])
-easy <- ecdf(summaryData$propComplete[indxEasy])
-range <- seq(0,1,by=0.01)
-
-test <- data.frame(range = range,
-                   ecdf = c(wait(range),cog(range),phys(range),easy(range)),
-                   Group = factor(c(rep("Wait",101),rep("Cognitive",101),rep("Physical",101),rep("Easy", 101)), levels = c("Wait","Cognitive","Physical","Easy")))
-
-p1 <- ggplot(test, aes(x=range,y=ecdf, group=Group, color=Group))
-p1 <- p1 + geom_line(show.legend = F, size = 1.5) +
+``` {r 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
+## ECDF of proportion completed per cost type
+temp <- dataAll %>%
+        filter(Choice < 2) %>%
+        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
+        group_by(SubjID, Cost) %>%
+        summarise(Earnings = sum(Reward[Choice == 1] / 100),
+                  pComplete = mean(Choice))
+
+## formal testing 
+# proportion completed
+propAov <- aov(pComplete ~ factor(Cost), data = temp)
+
+propTests <- temp %>% 
+  plyr::dlply("Cost", identity) %>%
+  sapply("[[", "pComplete") %>%
+  as.data.frame() %>%
+  combn(2, simplify = F) %>%
+  sapply(function(x) {
+    c(contrast = paste(colnames(x), collapse = "vs"), 
+      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
+      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
+  }) %>% 
+  t()
+
+# pairwise.wilcox.test(temp$pComplete, temp$Cost)
+
+# earnings
+earnAov <- aov(Earnings ~ factor(Cost), data = temp)
+
+earnTests <- temp %>% 
+  plyr::dlply("Cost", identity) %>%
+  sapply("[[", "Earnings") %>%
+  as.data.frame() %>%
+  combn(2, simplify = F) %>%
+  sapply(function(x) {
+    c(contrast = paste(colnames(x), collapse = "vs"), 
+      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
+      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
+  }) %>% 
+  t()
+
+# plots
+p1 <- ggplot(aes(pComplete, color = Cost), data = temp) +
+        stat_ecdf(lwd = 1.2, show.legend = F) +
         scale_color_manual(values = cols) +
-    labs(title = "ECDF of Acceptances per Group", y="ECDF", x = "Proportion Accepted") +
-    theme_classic()
-
-# problem is, data is not normal, so we're going to bootstrap it and DEFINITELY permute
-# Bootstrap nonparametric
-B <- 5000
-meanBootW <- bootstrap(summaryData$propComplete[indxWait],B = B) #rep(0,B)
-meanBootC <- bootstrap(summaryData$propComplete[indxCog], B = B) #rep(0,B)
-meanBootP <- bootstrap(summaryData$propComplete[indxPhys], B = B)
-meanBootE <- bootstrap(summaryData$propComplete[indxEasy], B = B)
-
-#CIs wait
-meanW <- mean(meanBootW)
-upperW <- quantile(meanBootW,0.975) # meanBoot?
-lowerW <- quantile(meanBootW,0.025)
-
-#CIs effort
-meanC <- mean(meanBootC)
-upperC <- quantile(meanBootC,0.975) # meanBoot?
-lowerC <- quantile(meanBootC,0.025)
-
-#CIs physical
-meanP <- mean(meanBootP)
-upperP <- quantile(meanBootP,0.975) # meanBoot?
-lowerP <- quantile(meanBootP,0.025)
-
-#CIs easy
-meanE <- mean(meanBootE)
-upperE <- quantile(meanBootE,0.975) # meanBoot?
-lowerE <- quantile(meanBootE,0.025)
-
-# formal testing 
-# proportion completed
-propAov <- aov(propComplete ~ factor(Group), data = summaryData)
-
-# effect size (get the one for anovas)
-# propRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])
-
-# post-hoc
-temp <- do.call(cbind, lapply(split(summaryData, summaryData$Group),"[[","propComplete"))
-temp2 <- t(combn(colnames(temp),2))
-
-propTests <- data.frame(Comparison = paste(temp2[,1], temp2[,2]),
-                        T_pval = rep(1,6),
-                        CohenD = rep(0,6))
-
-for (i in seq(nrow(temp2))) {
-
-  propTests$T_pval[i] <- round(permute(temp[,temp2[i,1]], temp[,temp2[i,2]])$Pval, digits = 2)
-  propTests$CohenD[i] <- round(cohenD(temp[,temp2[i,1]], temp[,temp2[i,2]]), digits = 2)
-
-}
-
-# earnings
-earnAov <- aov(Earnings ~ factor(Group), data = summaryData)
-
-# effect size
-# earnRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])
-
-# post-hoc
-temp <- do.call(cbind, lapply(split(summaryData, summaryData$Group),"[[","Earnings"))
-temp2 <- t(combn(colnames(temp),2))
-
-earnTests <- data.frame(Comparison = paste(temp2[,1], temp2[,2]),
-                        T_pval = rep(1,6),
-                        CohenD = rep(0,6))
-
-for (i in seq(nrow(temp2))) {
-
-  earnTests$T_pval[i] <- round(permute(temp[,temp2[i,1]], temp[,temp2[i,2]])$Pval, digits = 2)
-  earnTests$CohenD[i] <- round(cohenD(temp[,temp2[i,1]], temp[,temp2[i,2]]), digits = 2)
-
-}
-
-rm(B,cog,wait,phys,easytemp,temp2)
-
-# plot
-p2 <- ggplot(summaryData, aes(x=Group, y=propComplete, fill = Group))
-p2 <- p2 + geom_boxplot(show.legend = F) +
+        xlim(0, 1) +
+        labs(y="ECDF", x = "Proportion Accepted") +
+        theme(panel.grid.major = element_blank(), 
+              panel.grid.minor = element_blank(), 
+              panel.background = element_blank(), 
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16))
+
+p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
+        geom_boxplot(show.legend = F) +
         scale_fill_manual(values = cols) +
-    ylim(c(0,1)) +
-    labs(title = "Proportion Completed by Group", y="Proportion Completed") +
-    theme_classic()
-
-p3 <- ggplot(summaryData, aes(x=Group, y=Earnings, fill = Group))
-p3 <- p3 + geom_boxplot(show.legend = F) +
+        ylim(c(0, 1)) +
+        labs(y = "Proportion Completed") +
+        theme(panel.grid.major = element_blank(), 
+            panel.grid.minor = element_blank(), 
+            panel.background = element_blank(), 
+            axis.line = element_line(colour = "black"),
+            text = element_text(size = 16))
+
+p3 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
+        geom_boxplot(show.legend = F) +
         scale_fill_manual(values = cols) +
-    labs(title = "Earnings by Group", y="Total Earnings (Cents)") +
-    theme_classic()
-
-grid.arrange(p1, p2, p3, ncol = 3)
+        labs(y = "Total Earnings (dollars)") +
+        theme(panel.grid.major = element_blank(), 
+            panel.grid.minor = element_blank(), 
+            panel.background = element_blank(), 
+            axis.line = element_line(colour = "black"),
+            text = element_text(size = 16))
+
+grid.arrange(p2, p3, ncol = 2)
 ```
@@
 ``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-### THE PLOTS FOR YALE
-# Ggplot made plotting way easier than the previous version
-# This is in case you don't want to plot the easy condition (easier to see)
-cols = c("#78AB05","#D9541A","deepskyblue4", "grey50")
-trueProp2 <- trueProp[-(28:36), ]
-
-a1 <- ggplot(data = trueProp, aes(x=interaction(Reward, Handling), y=propComplete, color=Group)) + 
-        geom_point(size=3) + 
-        geom_errorbar(aes(ymin=propComplete-SE, ymax=propComplete+SE), width=0.2, size=1) +
-        geom_line(aes(group = interaction(Handling, Group)), size=1) +
-        geom_point(aes(y=round(Optimal)), shape = 24, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
-        labs(x = "Reward.Handling", y = "Proportion Accepted", title = "Proportion Accepted per Handling and Reward Combination") +
-        scale_color_manual(values=cols) +
-        theme_classic()
-
-a1
+# prep data to plot the p(accept) based on reward, handling time and cost type
+trueProp <- dataAll %>%
+        filter(Choice < 2) %>%
+        group_by(SubjID, Cost, Handling, Reward, optimal) %>%
+        summarise(pComplete = mean(Choice)) %>%
+        group_by(Cost, Handling, Reward, optimal) %>%
+        summarise(meanComplete = mean(pComplete),
+                  SE = sd(pComplete) / sqrt(length(pComplete)))
+
+# and plot
+(a1 <- ggplot(data = trueProp, aes(interaction(Reward, Handling), meanComplete, color = Cost)) + 
+        geom_point(size = 3) + 
+        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
+        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
+        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
+        labs(x = "Reward.Handling", y = "Proportion Accepted") +
+        scale_color_manual(values = cols) +
+        theme(panel.grid.major = element_blank(), 
+              panel.grid.minor = element_blank(), 
+              panel.background = element_blank(), 
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16)))
+
 ```
@@
 ``` {r 16.2.3. Mixed Effects Model, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
-# just to make the logistic plotting comply with the function
-allProp2 <- allProp2[order(as.character(allProp2$Group), decreasing = F), ]
-
-# This transformation is necessary for a proper binomial fit of proportion data
-totalQuit <- allProp2$totalTrials - allProp2$totalComplete
-testBinom <- cbind(allProp2$totalComplete,totalQuit)
-
-# Using a mixed-model fitted with GLMER
-# Note: GLMER does not take quasi family distributions
-# ranef() to display the random intercepts, fixef() for the model coefficients
-
-# fit model
+# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
 mixLogis_main <- list()
-allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Wait"))
-mixLogis_main$Wait <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Cognitive"))
-mixLogis_main$Cognitive <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Physical"))
-mixLogis_main$Physical <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-allProp2 <- within(allProp2, Group <- relevel(Group, ref = "Easy"))
-mixLogis_main$Easy <-  glmer(testBinom ~ Group + Handling + Reward + (1 | SubjID), family = "binomial", data = allProp2)
-
-# Summarize model 
-mixLogis_main$Summary <- summary(mixLogis_main$Wait)
-
-# Coefficient matrices for all reference combos
-t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,1], GroupWait = 0)
-t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,1], GroupCognitive = 0)
-t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,1], GroupPhysical = 0)
-t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,1], GroupEasy = 0)
-mixLogis_mainBetas <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
-dimnames(mixLogis_mainBetas) <- list(cond[c(2,4,3,1)],c("Group",cond))
-mixLogis_mainBetas <- as.matrix(mixLogis_mainBetas[,c(3,5,4,2)])
-
-# And their respective p-values
-t1 <- c(summary(mixLogis_main$Wait)$coefficients[2:4,4], GroupWait = 1)
-t2 <- c(summary(mixLogis_main$Cognitive)$coefficients[2:4,4], GroupCognitive = 1)
-t3 <- c(summary(mixLogis_main$Physical)$coefficients[2:4,4], GroupPhysical = 1)
-t4 <- c(summary(mixLogis_main$Easy)$coefficients[2:4,4], GroupEasy = 1)
-mixLogis_mainPvals <- cbind(merge(t1,t2, by = 0), merge(t1,t3,by=0)[,3], merge(t1,t4,by=0)[,3])
-dimnames(mixLogis_mainPvals) <- list(cond[c(2,4,3,1)],c("Group",cond))
-mixLogis_mainPvals <- as.matrix(mixLogis_mainPvals[,c(3,5,4,2)])
-
-# Create CIs
-sd <- sqrt(diag(vcov(mixLogis_main$Wait)))
-mixLogisCI <- cbind(Est = fixef(mixLogis_main$Wait), LL = fixef(mixLogis_main$Wait) - 1.96 * sd, UL = fixef(mixLogis_main$Wait) + 1.96 * sd)
+mixData <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost, Handling, Reward) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice)) %>%
+  ungroup()
+
+# model with a random intercept and cost-type slope, then relevel the cost to get all pairwise comparisons
+# the correct way to model a logistic with proportions as dependent vars is by prividing n of hits and quits as a matrix
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
+mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
+mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
+mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
+mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+
+# matrix of coefficients
+# 
+temp <- lapply(mixLogis_main, function(model) {as.list(summary(model)$coefficients[2:4, 1])})
+mixCoeffs <- as.matrix(bind_rows(temp)) #reduce(temp, full_join) 
+dimnames(mixCoeffs) <- list(names(temp), substr(colnames(mixCoeffs), 5, 20))
+mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
+mixCoeffs[is.na(mixCoeffs)] <- 0
+mixCoeffs <- mixCoeffs[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]
+
+# matrix of pvals
+temp <- lapply(mixLogis_main, function(model) {as.list(summary(model)$coefficients[2:4, 4])})
+mixPvals <- as.matrix(bind_rows(temp)) 
+dimnames(mixPvals) <- list(names(temp), substr(colnames(mixPvals), 5, 20))
+mixPvals <- as.matrix(mixPvals[, match(rownames(mixPvals), colnames(mixPvals))])
+rownames(mixPvals) <- colnames(mixPvals)
+mixPvals <- mixPvals[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]
+diag(mixPvals) <- 1
+
+# plot coefficients and pvalues in a matrix
+# invert colors
+col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))
+
+corrplot(mixCoeffs, 
+         is.corr = F, 
+         p.mat = mixPvals, 
+         #type = "upper",
+         outline = T,
+         insig = "p-value",
+         sig.level = -1, 
+         na.label = "square", 
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black",
+         tl.cex = 0.8,
+         col = col2(200))
+
 ```
@@
 # plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
-temp <- cbind(summaryData$Group, 
-              ranef(mixLogis_main$Wait)$SubjID)#, 
-              #Colors = c(rep(cols[1],nSubsW),rep(cols[2],nSubsC),rep(cols[3],nSubsP),rep(cols[4],nSubsE)))
-colnames(temp) <- list("Group", "RandIntercept")
-RI1 <- ggplot(data = temp, aes(x = Group, y = RandIntercept, fill = Group)) + 
-  geom_hline(yintercept = 0, alpha = 0.7) + 
+temp <- ranef(mixLogis_main$Wait)$SubjID %>%
+  gather(key = Cost, value = RandEffects, colnames(.))
+
+(RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
+  geom_hline(yintercept = 0, alpha = 0.7, linetype = "dashed") + 
   geom_boxplot(show.legend = F) +
   scale_fill_manual(values = cols) + 
-  labs(title = "Random Intercepts per Group", x = "") +
-  theme_classic()
-
-RI1
+  labs(x = "") +
+  theme(panel.grid.major = element_blank(), 
+              panel.grid.minor = element_blank(), 
+              panel.background = element_blank(), 
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16)))
+
 ```
@@
 In order to show the comparisons among all conditions, the following plot portrays the coefficients (color scale), and p-values (numbers within squares) that resulted from switching the reference condition.
-Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group (the darker the cell, the greater the odds).
+Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group.
 Based on this, we can see that the cognitive group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
-
-``` {r 16.2.3. Mixed Effects Model plot group coefficients, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-# plot coefficient matrix (show pvals!)
-corrplot(abs(mixLogis_mainBetas), 
-         p.mat = mixLogis_mainPvals, 
-         is.corr = F, 
-         method = "color", 
-         tl.col = "black", 
-         tl.srt = 0, 
-         insig = "p-value", 
-         sig.level = -1, 
-         type = "lower",
-         cl.length = 3)
-mtext("Comparison", side = 2, line = 1.5, cex = 1.5)
-mtext("Reference Group", side = 3, line = 1, cex = 1.5, at = 2.5)
-
-rm(temp,t1,t2,t3,t4)
-
-```
 
@@
 
+This plot shows the AIC for every model.
+The figure below shows AIC and BIC for all the models.
+As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`).
+
 ``` {r 16.2.4. Plot Deviance comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-
-par(mar=c(5.1,2.1,2.1,2.1))    
-# plot the deviance for all models
-# ver 3
-modelLabels <- c('Intercept','G Only','H Only','R Only','G + H + R','G + H * R','G * H * R')
-plot(aicLogis_compare,
-     main = "AIC for All Models",
-     xlab = "",
-     ylab = "AIC",
-     pch = 16,
-     xaxt = "n")
-axis(1, at = 1:7, labels = F)
-text(1:7, 
-     par("usr")[3] - 22,
-     labels = modelLabels, 
-     srt = 45, 
-     pos = 1, 
-     xpd = TRUE)
+# plot AIC and BIC
+(mixLogis_compare$plot <- abicLogis_compare %>% 
+  gather(Comparison, Value, AIC:BIC) %>%
+  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
+  ggplot(aes(Model, Value, fill = Comparison)) +
+    geom_point(color = "black", pch = 21, size = 3) +
+    theme_classic())
 
@@
 ``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-# RTs
-# let's try to do some survival curves
-RTW <- unlist(lapply(waitData, function(data) {data$RT[data$Choice==0]})) # vector of all decision-related RTs for the wait group
-RTC <- unlist(lapply(cogData, function(data) {data$`Choice RT`[data$Choice==0]})) # same for the cog group
-RTP <- unlist(lapply(physData, function(data) {data$RT[data$Choice==0]}))
-RTE <- unlist(lapply(easyData, function(data) {data$RT[data$Choice==0]}))
-
-# create a data frame for plotting
-RTgroups <- c(rep("Wait",length(RTW)), rep("Effort",length(RTC)), rep("Physical",length(RTP)), rep("Easy",length(RTE)))
-RTall <- c(RTW,RTC,RTP,RTE)
-RTframe <- data.frame(RTgroups, RTall)
-
-# plot
-ggplot(RTframe, aes(RTall, color = RTgroups)) + 
-  stat_ecdf(lwd = 1) + 
+# Proportion of forced travels per subject and cost type
+propFails <- dataAll %>% 
+  filter(Cost != "Wait") %>% 
+  group_by(SubjID, Cost) %>% 
+  summarise(propFails = mean(Choice == 2)) %>%
+  group_by(Cost) %>% 
+  summarise(meanQuit = mean(propFails))
+
+# Reaction times ECDFs including offer and in-trial quits
+(RTs <- dataAll %>%
+  #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
+  filter(Choice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
+  ggplot(aes(RT, color = Cost)) + 
+    #stat_ecdf(lwd = 1.2, geom = "smooth") +
+    geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
+    geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
     scale_color_manual(values = cols) +
     scale_x_continuous(breaks = seq(14)) +
-  labs(title = "ECDFs for the Response Times", x = "Seconds", y = "ECDF") +
-  theme_classic()
-
-# # and CIs for each (unnecessary unless I end up plotting)
-# CIC <- bootstrap(group = RTC, statType = median)  #qt(.975,nSubs-1)*(sd(RTC)/sqrt(nSubs))
-# CIC <- median(CIC) - (quantile(CIC,0.025))
-# CIW <- bootstrap(group = RTW, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-# CIW <- median(CIW) - (quantile(CIW,0.025))
-# CIP <- bootstrap(group = RTP, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-# CIP <- median(CIP) - (quantile(CIP,0.025))
-# CIE <- bootstrap(group = RTE, statType = median)  #qt(.975,nSubs-1)*(sd(RTW)/sqrt(nSubs))
-# CIE <- median(CIE) - (quantile(CIE,0.025))
-# lines(range,ecdfC(range) + CIC,col = cols[2], lty = 2, lwd = lthick)
-# lines(range,ecdfC(range) - CIC,col = cols[2], lty = 2, lwd = lthick) 
-# lines(range,ecdfW(range) + CIW,col = cols[1], lty = 2, lwd = lthick)
-# lines(range,ecdfW(range) - CIW,col = cols[1], lty = 2, lwd = lthick)
-# lines(range,ecdfP(range) + CIP,col = cols[3], lty = 2, lwd = lthick)
-# lines(range,ecdfP(range) - CIP,col = cols[3], lty = 2, lwd = lthick)
-# lines(range,ecdfE(range) + CIE,col = cols[4], lty = 2, lwd = lthick)
-# lines(range,ecdfE(range) - CIE,col = cols[4], lty = 2, lwd = lthick)
+    labs(x = "Reaction Time", y = "Proportion Accepted") +
+    theme(panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      panel.background = element_blank(),
+      axis.line = element_line(colour = "black"),
+      text = element_text(size = 16)))
 
@@
 ``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-# THIS CODE CAN BE VASTLY IMPROVED, BUT RIGHT NOW IT WORKS SO I WON'T CARE
-# This one just plots the correlation between pre-post acceptance rates, both overall and per cell
-# The overall acceptance looks great, with mostly consistent rates, and with the physical group accepting slightly less post-break
-# However, the per-cell distribution looks messy, although you can still tell that there's a linear relationship
-# If I do a linear model predicting post with pre using cell-specific data, the betas are close to 1 and significant (also good R2s). That's good.
-
-# create vdata frames that store acceptance data per combination cell pre-post break
-waitB <- data.frame()
-waitA <- data.frame()
-cogB <- data.frame()
-cogA <- data.frame()
-physB <- data.frame()
-physA <- data.frame()
-easyB <- data.frame()
-easyA <- data.frame()
-
-# and for overall proportion accepted
-waitBAll <- numeric()
-waitAAll <- numeric()
-cogBAll <- numeric()
-cogAAll <- numeric()
-physBAll <- numeric()
-physAAll <- numeric() 
-easyBAll <- numeric()
-easyAAll <- numeric()
-
-for (i in seq(nSubsW)){
-
-  # wait
-  tempPropB <- aggregate(waitBefore[[i]]$Choice, by = list(waitBefore[[i]]$Handling, waitBefore[[i]]$Reward), FUN = 'mean')
-  tempPropA <- aggregate(waitAfter[[i]]$Choice, by = list(waitAfter[[i]]$Handling, waitAfter[[i]]$Reward), FUN = 'mean')
-  waitB <- rbind(waitB,tempPropB)
-  waitA <- rbind(waitA,tempPropA)
-  waitBAll[i] <- mean(waitBefore[[i]]$Choice) 
-  waitAAll[i] <- mean(waitAfter[[i]]$Choice)
-
-}
-
-for (i in seq(nSubsC)){
-
-  # cognitive
-  tempPropB <- aggregate(cogBefore[[i]]$Choice, by = list(cogBefore[[i]]$Handling, cogBefore[[i]]$Reward), FUN = 'mean')
-  tempPropA <- aggregate(cogAfter[[i]]$Choice, by = list(cogAfter[[i]]$Handling, cogAfter[[i]]$Reward), FUN = 'mean')
-  cogB <- rbind(cogB,tempPropB)
-  cogA <- rbind(cogA,tempPropA)
-  cogBAll[i] <- mean(cogBefore[[i]]$Choice) 
-  cogAAll[i] <- mean(cogAfter[[i]]$Choice)
-
-}
-
-for (i in seq(nSubsP)){
-
-  # physical
-  tempPropB <- aggregate(physBefore[[i]]$Choice, by = list(physBefore[[i]]$Handling, physBefore[[i]]$Reward), FUN = 'mean')
-  tempPropA <- aggregate(physAfter[[i]]$Choice, by = list(physAfter[[i]]$Handling, physAfter[[i]]$Reward), FUN = 'mean')
-  physB <- rbind(physB,tempPropB)
-  physA <- rbind(physA,tempPropA)
-  physBAll[i] <- mean(physBefore[[i]]$Choice) 
-  physAAll[i] <- mean(physAfter[[i]]$Choice)
-
-}
-
-for (i in seq(nSubsE)){
-
-  # easy
-  tempPropB <- aggregate(easyBefore[[i]]$Choice, by = list(easyBefore[[i]]$Handling, easyBefore[[i]]$Reward), FUN = 'mean')
-  tempPropA <- aggregate(easyAfter[[i]]$Choice, by = list(easyAfter[[i]]$Handling, easyAfter[[i]]$Reward), FUN = 'mean')
-  easyB <- rbind(easyB,tempPropB)
-  easyA <- rbind(easyA,tempPropA)
-  easyBAll[i] <- mean(easyBefore[[i]]$Choice) 
-  easyAAll[i] <- mean(easyAfter[[i]]$Choice)
-
-}
-
-# Pre-post linear models
-prepostLM <- list()
-prepostLM$Wait <- lm(waitBAll ~ waitAAll)
-prepostLM$Cognitive <- lm(cogBAll ~ cogAAll)
-prepostLM$Physical <- lm(physBAll ~ physAAll)
-prepostLM$Easy <- lm(easyBAll ~ easyAAll)
-
-prepostSummary <- do.call(rbind, lapply(prepostLM, function(data) c(coef(data)[2], confint(data)[2,])))
-
+
+temp <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost, Half) %>%
+  summarise(pAccepted = mean(Choice)) %>%
+  ungroup() %>%
+  spread(Half, pAccepted)
+
+# separate by cost type and compute a linear model to predict half 2 from 1
+sep <- temp %>% plyr::dlply("Cost", identity)
+prepost <- list()
+prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})
+
+# get the coefficients and confidence intervals
+# and concatenate
+prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
+colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
 ```
@@
 
-``` {r 16.3.2. Plot Pre/Post, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-
-# overall proportion
-plot(waitBAll,
-     waitAAll,
-     xlim = c(0,1),
-     ylim = c(0,1),
-     main = "Proportion accepted pre- and post-midpoint",
-     xlab = "Acceptance Rate Before",
-     ylab = "Acceptance Rate After",     
-     col = cols[1],
-     pch = 16)
-points(cogBAll,
-       cogAAll, 
-       col = cols[2],
-       pch = 16)
-points(physBAll,
-       physAAll, 
-       col = cols[3],
-       pch = 16)
-points(easyBAll,
-       easyAAll, 
-       col = cols[4],
-       pch = 16)
-lines(seq(0,1,length = 10),
-      seq(0,1,length = 10))
-legend("bottomright",
-       lbls,
-       fill = cols,
-       cex = 0.8)
-
-# Another approach
-# This will just plot the density of the completed trials before/after, trying to get at the possible fatigue experienced in the physical effort condition.
-# Response patterns for each subject look pretty similar, with adequate optimality adaptation.
-#
-# for (i in 1:nSubs){
-# plot(density(which(physBefore[[i]]$Choice==1)),
-#      main = paste("Choices in time, before and after for subject:",i),
-#      xlab = "Trials (completed)")
-# lines(density(which(physAfter[[i]]$Choice==1)), col = "red")
-# }
+``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
+(prepost$plot <- dataAll %>%
+                filter(Choice < 2) %>%
+                group_by(SubjID, Cost) %>%
+                summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
+                          propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
+                ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
+                geom_point(size = 3, pch = 21, color = "black") +
+                scale_fill_manual(values = cols) +
+                xlim(0,1) +
+                ylim(0,1) +
+                geom_abline(slope = 1, intercept = 0, lty = 2) +
+                theme(panel.grid.major = element_blank(),
+                      panel.grid.minor = element_blank(),
+                      panel.background = element_blank(),
+                      axis.line = element_line(colour = "black"),
+                      text = element_text(size = 16)))
 ```
@@
 ``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-# Estimate gamma per subject for each group separately
-waitOC <- sapply(waitData, function(Data) {optimizeOCModel(Data)$Gamma})
-cogOC <- sapply(cogData, function(Data) {optimizeOCModel(Data)$Gamma})
-physOC <- sapply(physData, function(Data) {optimizeOCModel(Data)$Gamma})
-easyOC <- sapply(easyData, function(Data) {optimizeOCModel(Data)$Gamma})
-
-# Summarize for plotting
-summaryOC <- data.frame(Group = rep(cond, each = nSubsC),
-                        Gamma = c(waitOC, cogOC, physOC, easyOC))
-summaryOC$Group <- factor(summaryOC$Group, levels = cond, ordered = T)
+# group
+summaryOC <- list()
+summaryOC$all <- dataAll %>%
+                 filter(Choice < 2) %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup()
 
 # plot
-ggplot(summaryOC, aes(Group, Gamma, fill = Group)) +
+(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
                       geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
@@
 
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-
-## Notes
-
-- Update the AIC, RT ECDF, pre-post plots with ggplot.
-
-- This plot is just to show participant-specific behavior for all groups.
+``` {r 16.3.5. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
+# plot all pairwise comparisons
+corrplot(OCanova$ES,
+         is.corr = F, 
+         p.mat = OCanova$perms,
+         type = "upper",
+         insig = "p-value",
+         sig.level = -1,
+         na.label = "square",
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black", 
+         tl.cex = 0.8,
+         outline = T)
+```
+
+\bigskip
+\bigskip
+\bigskip
+\bigskip
+\bigskip
 
 ``` {r Testing grounds, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}
-cond <- as.character(unique(summaryData$Group))
-
-i <- 1
-test <- allProp2[allProp2$Group == cond[i], ]
-test2 <- trueProp[trueProp$Group == cond[i], ]
-t1 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-  geom_point(size=3, color = cols[i]) +
-  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-  theme_classic()
-
-i <- 2
-test <- allProp2[allProp2$Group == cond[i], ]
-test2 <- trueProp[trueProp$Group == cond[i], ]
-t2 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-  geom_point(size=3, color = cols[i]) +
-  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-  theme_classic()
-
-i <- 3
-test <- allProp2[allProp2$Group == cond[i], ]
-test2 <- trueProp[trueProp$Group == cond[i], ]
-t3 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-  geom_point(size=3, color = cols[i]) +
-  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-  theme_classic()
-
-i <- 4
-test <- allProp2[allProp2$Group == cond[i], ]
-test2 <- trueProp[trueProp$Group == cond[i], ]
-t4 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-  geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-  geom_point(size=3, color = cols[i]) +
-  geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-  labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-  theme_classic()
-
-grid.arrange(t1,t3,t2,t4, ncol = 2)
-
-```
+# cond <- as.character(unique(summaryData$Group))
+# 
+# i <- 1
+# test <- allProp2[allProp2$Group == cond[i], ]
+# test2 <- trueProp[trueProp$Group == cond[i], ]
+# t1 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
+#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
+#   geom_point(size=3, color = cols[i]) +
+#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
+#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
+#   theme_classic()
+# 
+# i <- 2
+# test <- allProp2[allProp2$Group == cond[i], ]
+# test2 <- trueProp[trueProp$Group == cond[i], ]
+# t2 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
+#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
+#   geom_point(size=3, color = cols[i]) +
+#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
+#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
+#   theme_classic()
+# 
+# i <- 3
+# test <- allProp2[allProp2$Group == cond[i], ]
+# test2 <- trueProp[trueProp$Group == cond[i], ]
+# t3 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
+#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
+#   geom_point(size=3, color = cols[i]) +
+#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
+#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
+#   theme_classic()
+# 
+# i <- 4
+# test <- allProp2[allProp2$Group == cond[i], ]
+# test2 <- trueProp[trueProp$Group == cond[i], ]
+# t4 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
+#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
+#   geom_point(size=3, color = cols[i]) +
+#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
+#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
+#   theme_classic()
+# 
+# 
+# grid.arrange(t1,t3,t2,t4, ncol = 2)
+
+```
+
+## 17. Inference criteria
+
+These criteria will remain the same as before.
+For the ANOVAs, we will report the F statistic as well as the p-value.
+For the multiple linear regressions and logistic regression, we will report the betas (coefficients) and their associated p-values.
+When comparing two groups of values as in pairwise comparisons, we will use non-parametric permutation tests.
+We will report p-values and effect sizes, and all tests will be two-tailed.
+The alpha threshold for p-value evaluation will be set at 0.05.
+
+## 18. Data exclusion
+
+### 18.1. Missing data and quitting early.
+
+Participants are told that they are allowed to stop participation in the study at any time without consequence.
+Data from participants who do not finish the experiment will be excluded from the study, and those participants will be replaced.
+
+### 18.2. Inattentiveness
+
+To guard against inattentiveness, a single 30 second catch trial will be placed at the end of each experimental block, merely prompting participants to press a key.
+From the pilot study, participants are able to respond within three seconds.
+Based on this, a response within three seconds will be considered as proper engagement, and a participant that fails two or more of these checks will be excluded and replaced.
+
+### 18.3. Reasonable choices
+
+The task is structured so that one reward amount must always be accepted.
+Thus, a participant who quits every trial in at least one block will be assumed not to have followed or understood task instructions, or to have disengaged from the task altogether, and will be excluded and replaced.
+
+### 18.4. Performance
+
+In the cognitive effort condition, participants were forced to travel if they made 2 mistakes in a trial. Any participant with more than 30% forced travels will be excluded and replaced.

### 2019-05-09 Cost2/Cost2_prereg.Rmd
Cost 2 and 3 notebook styles match (for easier comparison)

@@
 
-This document follows the steps planned for the pre-registration (https://osf.io/2rsgm/).
+This document follows the steps planned for the first pre-registration (https://osf.io/2rsgm/).
 The bullet points match the organization shown on the website as closely as possible.
 First, here is a restatement of the questions and hypotheses.
-
-## 3. Research Questions
-
-### 3.1.
-
-Do decision makers in foraging environments integrate information about delay durations and reward amounts to produce reward-maximizing behavior?
-
-### 3.2.
-
-Main question: Are decisions affected differently by equivalent time periods of pure delay, cognitive effort, physical effort, and non-effortful task engagement?
-Do these four conditions involve different levels of subjective costs?
-
-### 3.3.
-
-How can we best computationally model the perceived cost of time and effort to predict choices in each condition?
-
-## 4. Hypotheses
-
-### 4.1.
-
-Single-option, accept/reject decisions will be influenced by within-subject manipulations of reward magnitude and associated delay duration in line with a theoretical reward-maximizing strategy.
-
- **4.1.1.**	Participants will more frequently accept high-reward prospects than low-reward prospects.
-
- **4.1.2.**	The tendency to reject low-reward prospects will be greater in environments where rewards are associated with longer delays (handling times).
-
-### 4.2.
-
-Prospect acceptance rates will differ across four between-subject conditions, in which the delays associated with rewards (a) are unfilled, (b) include a cognitive effort requirement, (c) include a physical effort requirement, or (d) require a trivial level of physical effort but have matched visual stimuli to the physical effort condition.
-
-  **4.2.1.**	In the cognitive effort condition, overall acceptance rates will be greater than in the unfilled-delay condition.
-
-  **4.2.2.**	In the physical effort condition, overall acceptance rates will be greater than in the unfilled-delay condition, and equivalent to the cognitive effort condition.
-
-  **4.2.3.**	In the trivial effort condition, acceptance rates will be equivalent to the unfilled-delay condition, and lower than in the physical effort and cognitive effort conditions.
-
-### 4.3.
-
-Choices will be well fit by a computational model in which the subjective opportunity cost of time is free to vary across the four between-subject conditions.
-
-  **4.3.1.**	Participants will display stable preferences, meaning that the reward amounts they accept in a given timing condition will be similar throughout the experiment.
-
-  **4.3.2.**	Subject-specific opportunity cost (OC) estimates will vary inversely with acceptance rates.
-Thus, the unfilled-delay condition will produce higher OC estimates than both effort conditions, which in turn will show no differences between them.
-
-\bigskip
-
-## 5. Existing data
-
-Registration prior to creation of data
-
-## 6. Data collection
-
-The study will use human subjects recruited from the university community, who will be recruited through the university job board.
-We will pay up to $30 for a session (1 hour), which includes incentive-based rewards.
-Participants will be ineligible if they have participated in our pilot study, or they are under 18 years of age.
-The study will run for however long it takes to reach our desired sample size.
-
-## 7. Sample size
-
-We will acquire a sample of 48 participants.
-
-## 8. Sample size rationale?
-
-Sample sizes were determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four groups (one for each condition).
-The resulting sample size was 45, which we increased to 48 in order to match the potential order of blocks and colors (section 15) while further ensuring that we have enough power.
-
-## 9. Variables
-
-### 9.1 The present study has three levels of manipulation.
-
-9.1.1.
-Cost condition, manipulated within subjects.
-The conditions are (a) unfilled delay, (b) cognitive effort, and (c) physical effort.
-Unfilled delays will be paired with each effort type in a blocked manner (7-minute blocks).
-Each combination will be experienced three times.
-
-9.1.2.
-Handling and travel times.
-These will dictate how long each trial is.
-The "handling time" governs how long it is necessary to wait or work to obtain a reward if a trial is accepted.
-The "travel time" governs how long the inter-trial interval will be, regardless of whether the trial is accepted.
-Participants will know that the handling time will be always 10 seconds, and the travel time 6 seconds (matching one of the between-group experiment conditions).
-
-9.1.3.
-Reward magnitude, manipulated within-subject across individual trials.
-On each trial, participants will learn the amount of money they can earn if they complete the trial (i.e.
-4, 8, or 20 cents).
-The amounts will be sampled uniformly, while guaranteeing that each participant experiences each amount at least twice during each block.
-
-## 10. Measured variables
-
-### 10.1. Behavioral variables
-
-10.1.1. Choice (complete or quit a given trial).
-
-10.1.2. Response times.
-
-10.1.3. Total earnings.
-
-10.1.3. Performance in the cognitive effort tasks (right or wrong answer).
-
-10.1.4. Grip force throughout the experiment and maximum grip strength (physical effort condition).
-
-### 10.2. Questionnaire
-
-10.2.1. Age.
-
-10.2.2. Gender.
-
-10.2.3.
-Post-experimental oral assessment of choice strategy adoption.
-We will ask participants the following: "Did you follow a specific acceptance strategy?
-If so, what was it?" and "Which condition felt most effortful to you?".
-Answers will be written down by the experimenter, and recorded on an excel spreadsheet.
-
-## 11. Indices
-
-### 11.1. Behavioral data
-
-11.1.1. Proportion of prospects accepted.
-
-11.1.2. Percentage of cognitive effort trials with above-threshold errors (over 2 errors), in which participants are forced to travel to the next trial.
-
-### 11.2. Optimal behavior
-
-The theoretical opportunity cost of time will be calculated for each handling/travel/reward acceptance combination in order to assess choice optimality.
-This measure is computed as the cents per second possible when consistently accepting only certain reward amounts (e.g.
-8 and 20 cents) in a given timing condition.
-This ground truth measure is independent of cost type, allowing us to assess subject optimality.
-
-## 12. Study type
-
-Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments.
-This is also known as an intervention experiment and includes randomized controlled trials.
-
-## 13. Blinding
-
-No blinding is involved in this study.
-
-## 14. Study design
-
-The present study complements our previous one, which evaluated cost types through a between-group design.
-Many of the details remain the same.
-However, this time every participant will experience all forms of cost (delay, physical effort, and cognitive effort).
-Delay trials will be intermixed with both physical and cognitive trials, providing a common condition to compare these effortful costs.
-On each trial, participants will have the opportunity to either wait or work for 10 seconds (the "handling time") in order to earn a reward; alternatively, they can quit by pressing the space bar and skip to the next trial (which incurs a 6 second travel time).
-Two types of trial combinations (physical/wait and cognitive/wait) will be experienced three times by each participant in 7-minute-long, interleaved blocks.
-Reward amounts can be 4, 8, or 20 cents, uniformly distributed.
-Timing information will be disclosed at the beginning of each block, and reward prospects displayed before each trial begins.
-
-## 15. Randomization
-
-### 15.1. Block type 
-Each block will contain unfilled delay trials and trials of one effortful cost type (se 14.1).
-Blocks with each cost type will be interleaved, and participants will be assigned to one of two orders: beginning with a cognitive/wait or a physical/wait block.
-A row will be assigned to subject IDs prior to recruitment, ensuring that each order is experienced equally often.
-Participants will be offered a break after completing three out of the six blocks.
-
-### 15.2. Rewards and cost type 
-Participants can earn 4, 8, or 20 cents per trial at the cost of performing one of the three conditions.
-These values are sampled without replacement from a vector containing every combination of cost (effort defined by the current block, and delay) and reward.
-The vector is reshuffled once completed.
-This ensures that each combination of cost and reward is presented at least twice per block.
-
-### 15.3. Trial color 
-During the offer phase, each cost type will appear in a unique color in order to ease its identification.
-Colors were chosen to contrast each other while being amenable to red-green color-blindness.
-Colors will be assigned to each cost type so that all three colors are equally paired to each cost type across participants.
-A row will be assigned to subject IDs prior to recruitment to indicate their block order and color pairing.
-
-## 16. Analyses
 
@@
 
-#### 16.1.	Tests of whether decision makers integrate delay and reward information.
-
-  **16.1.1.**	*To address hypothesis 4.1., A logistic regression will be fit for each participant in order to predict trial-wise acceptances, using handling time and reward amount as predictors.
+## 3. Research Questions
+
+### 3.1.
+
+Do decision makers in foraging environments integrate information about delay durations and reward amounts to produce reward-maximizing behavior?
+
+### 3.2.
+
+Main question: Are decisions affected differently by equivalent time periods of pure delay, cognitive effort, physical effort, and non-effortful task engagement?
+Do these four conditions involve different levels of subjective costs?
+
+### 3.3.
+
+How can we best computationally model the perceived cost of time and effort to predict choices in each condition?
+
+## 4. Hypotheses
+
+### 4.1.
+
+Single-option, accept/reject decisions will be influenced by within-subject manipulations of reward magnitude and associated delay duration in line with a theoretical reward-maximizing strategy.
+
+ **4.1.1.**	Participants will more frequently accept high-reward prospects than low-reward prospects.
+
+ **4.1.2.**	The tendency to reject low-reward prospects will be greater in environments where rewards are associated with longer delays (handling times).
+
+### 4.2.
+
+Prospect acceptance rates will differ across four between-subject conditions, in which the delays associated with rewards (a) are unfilled, (b) include a cognitive effort requirement, (c) include a physical effort requirement, or (d) require a trivial level of physical effort but have matched visual stimuli to the physical effort condition.
+
+  **4.2.1.**	In the cognitive effort condition, overall acceptance rates will be greater than in the unfilled-delay condition.
+
+  **4.2.2.**	In the physical effort condition, overall acceptance rates will be greater than in the unfilled-delay condition, and equivalent to the cognitive effort condition.
+
+  **4.2.3.**	In the trivial effort condition, acceptance rates will be equivalent to the unfilled-delay condition, and lower than in the physical effort and cognitive effort conditions.
+
+### 4.3.
+
+Choices will be well fit by a computational model in which the subjective opportunity cost of time is free to vary across the four between-subject conditions.
+
+  **4.3.1.**	Participants will display stable preferences, meaning that the reward amounts they accept in a given timing condition will be similar throughout the experiment.
+
+  **4.3.2.**	Subject-specific opportunity cost (OC) estimates will vary inversely with acceptance rates.
+Thus, the unfilled-delay condition will produce higher OC estimates than both effort conditions, which in turn will show no differences between them.
+
+\bigskip
+
+## 16. Analyses
+### 16.1.	Tests of whether decision makers integrate delay and reward information.
+
+### 16.1.1.
+
+  *To address hypothesis 4.1., A logistic regression will be fit for each participant in order to predict trial-wise acceptances, using handling time and reward amount as predictors.
 The resulting beta coefficients for handling time and reward will be pooled across all participants, and we will perform a one-sample rank-sum test on each set of coefficients to examine whether the they are significantly positive or negative (compared to 0).
@@
 
-  **16.1.2.**	*We will perform an extension of the logistic regression from 16.1.1., this time adding an autoregressive covariate containing the number of consecutive quits prior to a given trial.
+### 16.1.2.
+
+*We will perform an extension of the logistic regression from 16.1.1., this time adding an autoregressive covariate containing the number of consecutive quits prior to a given trial.
 In this way, we will examine the possibility that participant choices were governed by recent quitting history rather than the experimental parameters (see 11.1.3.).
@@
 
-  **16.1.3.**	*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable).
+### 16.1.3.
+
+*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable).
 No other covariates will be used, as this analysis is to confirm that over and under accepting are detrimental to total earnings.
@@
 
-``` {r 16.1.3. Earnings, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
+``` {r 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
 # calculate the proportions and earnings per subject, while keeping group info
@@
 
-  **16.1.4.**	*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances--either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
+### 16.1.4.
+
+*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances--either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
 This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*
@@
 
-#### 16.2.	Comparisons among the four delay and effort conditions.
-
-  **16.2.1.**	*To compare preferences (hypothesis 4.2.), we will first perform a one-way ANOVA on the proportion of trials accepted using group as a factor.
+### 16.2.	Comparisons among the four delay and effort conditions.
+
+###  16.2.1.
+
+*To compare preferences (hypothesis 4.2.), we will first perform a one-way ANOVA on the proportion of trials accepted using group as a factor.
 In addition, we will do pairwise comparisons on the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests).
@@
 
-  **16.2.2.**	*In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors.
+### 16.2.2.
+
+*In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors.
 Reward and handling time will be within-subject factors, and condition a between-subjects factor.
@@
 
-  **16.2.3.**	*We will compute the probability of accepting a trial with a mixed-effects logistic regression.
+### 16.2.3.
+
+*We will compute the probability of accepting a trial with a mixed-effects logistic regression.
 Based on the task structure and our main question, our a priori model of interest will include cost condition, handling time, and reward amount as fixed main effects, and subject ID as a random effect.
@@
 
-  **16.2.4.**	*Next, we will examine whether the a priori model from 16.2.3.
+###  16.2.4.
+
+*Next, we will examine whether the a priori model from 16.2.3.
 outperforms both simpler and more complex models.
@@
 
-#### 16.3.	Modeling the subjective opportunity cost in each condition.
-
-  **16.3.1.**	*Response times (RT) for quit responses will be presented in a descriptive manner in order to examine whether participants tended to quit early or late within individual trials.
+### 16.3.	Modeling the subjective opportunity cost in each condition.
+
+### 16.3.1.
+
+*Response times (RT) for quit responses will be presented in a descriptive manner in order to examine whether participants tended to quit early or late within individual trials.
 Each cost group’s response time distribution will contain the pooled RT across its corresponding participants, and we will display the empirical cumulative distribution functions for each condition.
@@
 
-  **16.3.2.**	*In order to further examine choice stability (hypothesis 4.3.1.), we will compute each participant’s total proportion of acceptances pre- and post-midpoint.
+###  16.3.2.
+
+*In order to further examine choice stability (hypothesis 4.3.1.), we will compute each participant’s total proportion of acceptances pre- and post-midpoint.
 For each cost condition separately, we will fit a linear model that predicts post-midpoint acceptance from before-midpoint rates.
@@
 
-  **16.3.3.**	*To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
+### 16.3.3.
+
+*To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
 OC will be computed as the product of a free parameter (gamma) and the handling time.
@@
 
-  **16.3.4.**	*We will cross-validate each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+### 16.3.4.
+
+*We will cross-validate each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
 The estimates will be used to predict acceptances in the testing sample, and the mean percent correctly predicted will be reported for each group.
@@
 
-  **16.3.5.**	*The OC estimates for each group will be compared using an ANOVA with condition as a factor. This will let us determine which cost type produced the highest discounting.*
+### 16.3.5.
+
+*The OC estimates for each group will be compared using an ANOVA with condition as a factor. This will let us determine which cost type produced the highest discounting.*
 
@@
 In the cognitive effort condition, participants were forced to travel if they made 2 mistakes in a trial. Any participant with more than 30% forced travels will be excluded and replaced.
+
+## 5. Existing data
+
+Registration prior to creation of data
+
+## 6. Data collection
+
+The study will use human subjects recruited from the university community, who will be recruited through the university job board.
+We will pay up to $30 for a session (1 hour), which includes incentive-based rewards.
+Participants will be ineligible if they have participated in our pilot study, or they are under 18 years of age.
+The study will run for however long it takes to reach our desired sample size.
+
+## 7. Sample size
+
+We will acquire a sample of 48 participants.
+
+## 8. Sample size rationale?
+
+Sample sizes were determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four groups (one for each condition).
+The resulting sample size was 45, which we increased to 48 in order to match the potential order of blocks and colors (section 15) while further ensuring that we have enough power.
+
+## 9. Variables
+
+### 9.1 The present study has three levels of manipulation.
+
+9.1.1.
+Cost condition, manipulated within subjects.
+The conditions are (a) unfilled delay, (b) cognitive effort, and (c) physical effort.
+Unfilled delays will be paired with each effort type in a blocked manner (7-minute blocks).
+Each combination will be experienced three times.
+
+9.1.2.
+Handling and travel times.
+These will dictate how long each trial is.
+The "handling time" governs how long it is necessary to wait or work to obtain a reward if a trial is accepted.
+The "travel time" governs how long the inter-trial interval will be, regardless of whether the trial is accepted.
+Participants will know that the handling time will be always 10 seconds, and the travel time 6 seconds (matching one of the between-group experiment conditions).
+
+9.1.3.
+Reward magnitude, manipulated within-subject across individual trials.
+On each trial, participants will learn the amount of money they can earn if they complete the trial (i.e.
+4, 8, or 20 cents).
+The amounts will be sampled uniformly, while guaranteeing that each participant experiences each amount at least twice during each block.
+
+## 10. Measured variables
+
+### 10.1. Behavioral variables
+
+10.1.1. Choice (complete or quit a given trial).
+
+10.1.2. Response times.
+
+10.1.3. Total earnings.
+
+10.1.3. Performance in the cognitive effort tasks (right or wrong answer).
+
+10.1.4. Grip force throughout the experiment and maximum grip strength (physical effort condition).
+
+### 10.2. Questionnaire
+
+10.2.1. Age.
+
+10.2.2. Gender.
+
+10.2.3.
+Post-experimental oral assessment of choice strategy adoption.
+We will ask participants the following: "Did you follow a specific acceptance strategy?
+If so, what was it?" and "Which condition felt most effortful to you?".
+Answers will be written down by the experimenter, and recorded on an excel spreadsheet.
+
+## 11. Indices
+
+### 11.1. Behavioral data
+
+11.1.1. Proportion of prospects accepted.
+
+11.1.2. Percentage of cognitive effort trials with above-threshold errors (over 2 errors), in which participants are forced to travel to the next trial.
+
+### 11.2. Optimal behavior
+
+The theoretical opportunity cost of time will be calculated for each handling/travel/reward acceptance combination in order to assess choice optimality.
+This measure is computed as the cents per second possible when consistently accepting only certain reward amounts (e.g.
+8 and 20 cents) in a given timing condition.
+This ground truth measure is independent of cost type, allowing us to assess subject optimality.
+
+## 12. Study type
+
+Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments.
+This is also known as an intervention experiment and includes randomized controlled trials.
+
+## 13. Blinding
+
+No blinding is involved in this study.
+
+## 14. Study design
+
+The present study complements our previous one, which evaluated cost types through a between-group design.
+Many of the details remain the same.
+However, this time every participant will experience all forms of cost (delay, physical effort, and cognitive effort).
+Delay trials will be intermixed with both physical and cognitive trials, providing a common condition to compare these effortful costs.
+On each trial, participants will have the opportunity to either wait or work for 10 seconds (the "handling time") in order to earn a reward; alternatively, they can quit by pressing the space bar and skip to the next trial (which incurs a 6 second travel time).
+Two types of trial combinations (physical/wait and cognitive/wait) will be experienced three times by each participant in 7-minute-long, interleaved blocks.
+Reward amounts can be 4, 8, or 20 cents, uniformly distributed.
+Timing information will be disclosed at the beginning of each block, and reward prospects displayed before each trial begins.
+
+## 15. Randomization
+
+### 15.1. Block type 
+Each block will contain unfilled delay trials and trials of one effortful cost type (se 14.1).
+Blocks with each cost type will be interleaved, and participants will be assigned to one of two orders: beginning with a cognitive/wait or a physical/wait block.
+A row will be assigned to subject IDs prior to recruitment, ensuring that each order is experienced equally often.
+Participants will be offered a break after completing three out of the six blocks.
+
+### 15.2. Rewards and cost type 
+Participants can earn 4, 8, or 20 cents per trial at the cost of performing one of the three conditions.
+These values are sampled without replacement from a vector containing every combination of cost (effort defined by the current block, and delay) and reward.
+The vector is reshuffled once completed.
+This ensures that each combination of cost and reward is presented at least twice per block.
+
+### 15.3. Trial color 
+During the offer phase, each cost type will appear in a unique color in order to ease its identification.
+Colors were chosen to contrast each other while being amenable to red-green color-blindness.
+Colors will be assigned to each cost type so that all three colors are equally paired to each cost type across participants.
+A row will be assigned to subject IDs prior to recruitment to indicate their block order and color pairing.

### 2019-05-09 Cost2/Cost2_prereg.Rmd
matching plot styles mor

@@
          p.mat = mixPvals, 
-         #type = "upper",
+         type = "upper",
          outline = T,
@@
 Based on this, we can see that the cognitive group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
-
-``` {r 16.2.3. Plot logistic model, echo=FALSE,fig.align="center",fig.width=6,fig.height=6}
-# par(mfrow=c(1,1))
-# ## Plotting the winning model (colors are messed up)
-# rewards <- seq(1,20,length = 1000)
-# # wait
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Wait",
-#           handling = 2, 
-#           reward = rewards, 
-#           plotType = plot, 
-#           color = cols[1],
-#           lType = 6)
-# 
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Wait",          
-#           handling = 10, 
-#           reward = rewards, 
-#           color = cols[1],
-#           lType = 3)
-# 
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Wait",          
-#           handling = 14, 
-#           reward = rewards, 
-#           color = cols[1])
-# 
-# 
-# # cognitive
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Cognitive",
-#           handling = 2, 
-#           reward = rewards, 
-#           color = cols[2],
-#           lType = 6)
-# 
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Cognitive",
-#           handling = 10, 
-#           reward = rewards, 
-#           color = cols[2],
-#           lType = 3)
-# 
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Cognitive",
-#           handling = 14, 
-#           reward = rewards, 
-#           color = cols[2])
-# 
-# 
-# # physical
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Phys",
-#           handling = 2, 
-#           reward = rewards, 
-#           color = cols[3],
-#           lType = 6)
-# 
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Phys",
-#           handling = 10, 
-#           reward = rewards, 
-#           color = cols[3],
-#           lType = 3)
-# 
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Phys",
-#           handling = 14, 
-#           reward = rewards, 
-#           color = cols[3])
-# 
-# # easy
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Easy",
-#           handling = 2, 
-#           reward = rewards, 
-#           color = cols[4],
-#           lType = 6)
-# 
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Easy",
-#           handling = 10, 
-#           reward = rewards, 
-#           color = cols[4],
-#           lType = 3)
-# 
-# plotLogis(coeffs = logisComb$coefficients,
-#           group = "Easy",
-#           handling = 14, 
-#           reward = rewards, 
-#           color = cols[4])
-# 
-# # title
-# title("Probabilities for All Handling-Reward Combinations \n for Each Group")
-# 
-# # x axis
-# xticks <- c(0,min(rewards[rewards>4]),min(rewards[rewards>8]),20)
-# axis(1,at = xticks,c(0,4,8,20))
-# 
-# # legend
-# legend("bottomright",
-#        c("Wait: 2s","Wait: 10s","Wait: 14s",
-#          "Cognitive: 2s","Cognitive: 10s","Cognitive: 14s",
-#          "Physical: 2s","Physical: 10s","Physical: 14s",
-#          "Easy: 2s","Easy: 10s","Easy: 14s"), 
-#        fill = c(cols[1],cols[1],cols[1],cols[2],cols[2],cols[2],cols[3],cols[3],cols[3],cols[4],cols[4],cols[4]),
-#        lty = rep(c(6,3,1,8),3),
-#        cex = 0.8)
-# 
-# 
-# # actual proportions (maybe, maybe not)
-# # points(c(5,10,25),trueProp$propComplete[1:3], col = cols[1], pch=17) # wait
-# # points(c(5,10,25),trueProp$propComplete[4:6], col = cols[1], pch=17)
-# # points(c(5,10,25),trueProp$propComplete[7:9], col = cols[1], pch=17)
-# # 
-# # points(c(5,10,25),trueProp$propComplete[19:21], col = cols[2], pch=17) # cog effort
-# # points(c(5,10,25),trueProp$propComplete[22:24], col = cols[2], pch=17)
-# # points(c(5,10,25),trueProp$propComplete[25:27], col = cols[2], pch=17)
-# # 
-# # points(c(5,10,25),trueProp$propComplete[10:12], col = cols[3], pch=17) # phys effort
-# # points(c(5,10,25),trueProp$propComplete[13:15], col = cols[3], pch=17)
-# # points(c(5,10,25),trueProp$propComplete[16:18], col = cols[3], pch=17)
-# 
-# # and the residuals
-# # plot(logisComb$residuals,
-# #      main = "Residuals for the Logistic Regression",
-# #      xlab = "trial",
-# #      ylab = "Residuals")
-# # 
-```
 
@@
 ``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-
+# divide the data into proportion accepted before/after the break (one per column)
 temp <- dataAll %>%
@@
 
-``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
-(prepost$plot <- dataAll %>%
+``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+# scatter plot of pre/post acceptances
+prepost$scatterplot <- dataAll %>%
                 filter(Choice < 2) %>%
@@
                 ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
-                geom_point(size = 3, pch = 21, color = "black") +
+                  geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
                   scale_fill_manual(values = cols) +
@@
                   ylim(0,1) +
+                  labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
                   geom_abline(slope = 1, intercept = 0, lty = 2) +
@@
                         axis.line = element_line(colour = "black"),
-                      text = element_text(size = 16)))
+                        text = element_text(size = 16))
+
+# acceptances per cost across blocks
+# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
+prepost$propBlocks <- dataAll %>%
+ filter(Choice < 2) %>%
+ group_by(SubjID, Cost, Block) %>%
+ summarise(propAccept_subj = mean(Choice)) %>%
+ group_by(Cost, Block) %>%
+ summarize(propAccept = mean(propAccept_subj),
+           seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
+ ggplot(aes(Block, propAccept, fill = Cost)) +
+   geom_point(size = 2, pch = 21, color = "black") +
+   geom_errorbar(aes(ymin=propAccept - seAccept, ymax=propAccept + seAccept, color = Cost), width = 0.1) +
+   geom_line(aes(color = Cost)) +
+   ylim(0, 1) +
+   labs(y = "Proportion Acccepted") +
+   scale_x_continuous(breaks = seq(6)) +
+   scale_color_manual(values = cols) +
+   scale_fill_manual(values = cols) +
+   theme(legend.key = element_blank(),
+         legend.position = c(0.8, 0.25),
+         panel.grid.major = element_blank(),
+         panel.grid.minor = element_blank(),
+         panel.background = element_blank(),
+         axis.line = element_line(colour = "black"),
+         text = element_text(size = 16))
+
+grid.arrange(prepost$scatterplot, prepost$propBlocks, ncol = 2)
 ```

### 2019-05-09 Cost2/Cost2_prereg.Rmd
slight changes to plot size and width of error bars

@@
 
-``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 4}
 # prep data to plot the p(accept) based on reward, handling time and cost type

### 2019-05-09 Cost2/Cost2_prereg.Rmd
adding the last plots

--- 2019-05-09 Cost2/Cost2_prereg.Rmd
@@
 
-``` {r 16.2.2. rmANOVA plot, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
 # prep data to plot the p(accept) based on reward, handling time and cost type
@@
         scale_color_manual(values = cols) +
-        theme(panel.grid.major = element_blank(), 
+        theme(legend.key = element_blank(),
+              panel.grid.major = element_blank(), 
               panel.grid.minor = element_blank(), 
@@
 
+Now let's divide them by reward and handling amounts. The plots below show that the overall rates of acceptances remain mostly consistent across first and second halves of the experimental session.
+
+``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+# pre
+t1 <- dataAll %>%
+  filter(Choice < 2, Half == "Half_1") %>%
+  group_by(SubjID) %>%
+  filter(Handling == 10) %>%
+  group_by(SubjID, Cost, Reward) %>%
+  summarise(pAccept = mean(Choice)) %>%
+  group_by(Cost, Reward) %>%
+  summarise(propAccept = mean(pAccept),
+            SE = sd(pAccept) / sqrt(nSubjs)) %>%
+  ungroup() %>%
+  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
+  ggplot(aes(Reward, propAccept, color = Cost)) +
+    geom_point(size = 3, show.legend = F) +
+    geom_line(show.legend = F) +
+    scale_color_manual(values = cols) +
+    scale_fill_manual(values = cols) +
+    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
+    scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
+    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+    labs(y = "Proportion Accepted", title = "First Half") +
+    theme(legend.key = element_blank(),
+          legend.position = c(0.8, 0.25),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16))
+
+# post half
+t2 <- dataAll %>%
+  filter(Choice < 2, Half == "Half_2") %>%
+  group_by(SubjID) %>%
+  filter(Handling == 10) %>%
+  group_by(SubjID, Cost, Reward) %>%
+  summarise(pAccept = mean(Choice)) %>%
+  group_by(Cost, Reward) %>%
+  summarise(propAccept = mean(pAccept),
+            SE = sd(pAccept) / sqrt(nSubjs)) %>%
+  ungroup() %>%
+  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
+  ggplot(aes(Reward, propAccept, color = Cost)) +
+    geom_point(size = 3, show.legend = F) +
+    geom_line(show.legend = F) +
+    scale_color_manual(values = cols) +
+    scale_fill_manual(values = cols) +
+    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
+    scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
+    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+    labs(y = "", title = "Second Half") +
+    theme(legend.position = c(0.8, 0.2),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16))
+
+grid.arrange(t1, t2, ncol = 2)
+```
 \bigskip

### 2019-05-10 Cost2/Cost2_prereg.Rmd
mostly matched now!

@@
 qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
-  labs(y = "Coefficients") +
+  labs(x = "", y = "Coefficients") +
   geom_hline(yintercept = 0, linetype = "dashed") +

### 2019-05-10 Cost2/Cost2_prereg.Rmd
implemented a distinction between accepted and completed trials in both experiments

@@
 ### data loading and cleaning up
+# recent addition: turning forced travels to acceptances, as they reflect a preference for that trial
+# rawChoice will be used to compute the # of mistakes
 setwd("./data")
@@
   unnest() %>%
-  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"),
+  mutate(rawChoice = Choice,
+         Choice = ifelse(Choice == 2, 1, Choice),
+         Half = ifelse(Block < 4, "Half_1", "Half_2"),
          Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
@@
 temp <- dataAll %>%
-  filter(Choice < 2) %>%
+  filter(rawChoice < 2) %>%
   group_by(SubjID, Cost) %>%
@@
          stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
-         labs(x = "Proportion Accepted", y = "Total Earnings (dollars)") +
+         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
          scale_fill_manual(values = cols) +
@@
   group_by(SubjID, Handling, Reward, Cost) %>%
-  summarise(pComplete = mean(Choice)) %>%
+  summarise(pAccept = mean(Choice)) %>%
   mutate(optimal = case_when(
@@
   group_by(Handling, Reward, Cost) %>%
-  summarise(meanAccept = mean(pComplete),
-            sdAccept = sd(pComplete),
+  summarise(meanAccept = mean(pAccept),
+            sdAccept = sd(pAccept),
             optimal = unique(optimal),
-            pvals = tryCatch(t.test(pComplete, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
+            pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
   mutate(FDR = p.adjust(pvals, method = "BY"),
@@
         group_by(SubjID, Cost) %>%
-        summarise(Earnings = sum(Reward[Choice == 1] / 100),
-                  pComplete = mean(Choice))
+        summarise(Earnings = sum(Reward[rawChoice == 1] / 100),
+                  pAccept = mean(Choice))
 
@@
 # proportion completed
-propAov <- aov(pComplete ~ factor(Cost), data = temp)
+propAov <- aov(pAccept ~ factor(Cost), data = temp)
 
@@
   plyr::dlply("Cost", identity) %>%
-  sapply("[[", "pComplete") %>%
+  sapply("[[", "pAccept") %>%
   as.data.frame() %>%
@@
 
-# plots
-p1 <- ggplot(aes(pComplete, color = Cost), data = temp) +
+## plots
+# ECDF pAcceptd
+p1 <- ggplot(aes(pAccept, color = Cost), data = temp) +
         stat_ecdf(lwd = 1.2, show.legend = F) +
@@
 
-p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
+# pAccepted
+p2 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
         geom_boxplot(show.legend = F) +
@@
         ylim(c(0, 1)) +
-        labs(y = "Proportion Completed") +
+        labs(y = "Proportion Accepted") +
         theme(panel.grid.major = element_blank(), 
@@
 
+# earnings
 p3 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
@@
         group_by(SubjID, Cost, Handling, Reward) %>%
-        summarise(pComplete = mean(Choice))
+        summarise(pAccept = mean(Choice))
 
@@
 # I think I like this the most
-prop.aov <- with(temp, aov(pComplete ~ factor(Cost) * Handling * Reward + 
+prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Reward + 
                                  Error(SubjID / (Handling * Reward))))
@@
         group_by(SubjID, Cost, Handling, Reward, optimal) %>%
-        summarise(pComplete = mean(Choice)) %>%
+        summarise(pAccept = mean(Choice)) %>%
         group_by(Cost, Handling, Reward, optimal) %>%
-        summarise(meanComplete = mean(pComplete),
-                  SE = sd(pComplete) / sqrt(length(pComplete)))
+        summarise(meanComplete = mean(pAccept),
+                  SE = sd(pAccept) / sqrt(length(pAccept)))
 
@@
   group_by(SubjID, Cost) %>% 
-  summarise(propFails = mean(Choice == 2)) %>%
+  summarise(propFails = mean(rawChoice == 2)) %>%
   group_by(Cost) %>% 
-  summarise(meanQuit = mean(propFails))
+  summarise(meanFT = mean(propFails))
 
@@
   #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
-  filter(Choice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
+  filter(rawChoice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
   ggplot(aes(RT, color = Cost)) + 

### 2019-05-10 Cost2/Cost2_prereg.Rmd
checking that pre-post acceptance rate means are consistent, and added hline and vlines for each cost's group

@@
     scale_x_continuous(breaks = seq(14)) +
-    labs(x = "Reaction Time", y = "Proportion Accepted") +
+    labs(x = "Time in Trial", y = "Proportion Completed") +
     theme(panel.grid.major = element_blank(),
@@
 The plot below shows that acceptance rates before and after the mid-point were mostly consistent, although it was more likely for participants to accept less in the second half of the experiment.
+**NOTE: The lines of means in the scatterplot are calculated by first computing the mean acceptances per block, then averaging those for blocks pre/post break.
+That's how they match the second half of the right plot, but the linear model is computed with the overall proportion acceptances pre-post, which gives slightly different mean estimates (which is also the reason for slight mean differences in proportion accepted between these and the boxplot in 16.2.1.)**
 
@@
 # scatter plot of pre/post acceptances
+# BIG CAVEAT: THE 
+# first calculate the mean acceptances per cost/half to draw horizontal and vertical lines on the plot
+df_mean <- dataAll %>%
+            group_by(SubjID, Cost, Block, Half) %>%
+            summarise(propAccept = mean(Choice)) %>%
+            group_by(SubjID, Cost, Half) %>%
+            summarise(propAccept = mean(propAccept)) %>%
+            spread(Half, propAccept) %>%
+            group_by(Cost) %>%
+            summarise(propAccept_1 = mean(Half_1),
+                      propAccept_2 = mean(Half_2))
+
+# and plot
 prepost$scatterplot <- dataAll %>%
@@
                         group_by(SubjID, Cost) %>%
-                summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
-                          propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
+                        summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
+                                  propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
                         ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
@@
                           scale_fill_manual(values = cols) +
-                  xlim(0,1) +
-                  ylim(0,1) +
+                          scale_color_manual(values = cols) +
+                          xlim(0, 1) +
+                          ylim(0, 1) +
                           labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
                           geom_abline(slope = 1, intercept = 0, lty = 2) +
+                          geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
+                          geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
                           theme(panel.grid.major = element_blank(),

### 2019-05-12 Cost2/Cost2_prereg.Rmd
added plots to examine pre/post and order effects

@@
     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
-    scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
+    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
@@
 \bigskip
-\bigskip
-\bigskip
-\bigskip
-\bigskip
-
-``` {r Testing grounds, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}
-# cond <- as.character(unique(summaryData$Group))
-# 
-# i <- 1
-# test <- allProp2[allProp2$Group == cond[i], ]
-# test2 <- trueProp[trueProp$Group == cond[i], ]
-# t1 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-#   geom_point(size=3, color = cols[i]) +
-#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-#   theme_classic()
-# 
-# i <- 2
-# test <- allProp2[allProp2$Group == cond[i], ]
-# test2 <- trueProp[trueProp$Group == cond[i], ]
-# t2 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-#   geom_point(size=3, color = cols[i]) +
-#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-#   theme_classic()
-# 
-# i <- 3
-# test <- allProp2[allProp2$Group == cond[i], ]
-# test2 <- trueProp[trueProp$Group == cond[i], ]
-# t3 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-#   geom_point(size=3, color = cols[i]) +
-#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-#   theme_classic()
-# 
-# i <- 4
-# test <- allProp2[allProp2$Group == cond[i], ]
-# test2 <- trueProp[trueProp$Group == cond[i], ]
-# t4 <- ggplot(data = test, aes(x=interaction(Reward, Handling), y=propComplete)) + 
-#   geom_line(aes(group = interaction(Handling, SubjID)), size=1, color = cols[i], alpha = 0.5) +
-#   geom_point(size=3, color = cols[i]) +
-#   geom_point(data = test2, aes(group = interaction(Reward, Handling), y = propComplete), size = 3.5, color = "black", fill = "grey60", pch=24) +
-#   labs(title = paste("Acceptance rates for all subjects in the", cond[i], "group")) +
-#   theme_classic()
-# 
-# 
-# grid.arrange(t1,t3,t2,t4, ncol = 2)
-
+
+### Testing grounds
+
+``` {r Testing plots, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}
+# a facet grid of p(acceptances) as a function of reward x handling, distinguishing between first handling time experienced,
+# for each cost separately.
+# think of doing it for the block order and then prop accepted across costs
+dataAll %>%
+  group_by(SubjID) %>%
+  mutate(BlockOrder = case_when(
+    Handling[1] == 2 ~ "Two",
+    Handling[1] == 10 ~ "Ten",
+    Handling[1] == 14 ~ "Fourteen",
+  )) %>%
+  group_by(SubjID, Cost, Handling, Reward, BlockOrder) %>%
+  summarise(pAccept = mean(Choice)) %>%
+  ggplot(aes(interaction(Reward, Handling), pAccept, linetype = BlockOrder, color = BlockOrder)) + 
+    geom_point(size = 3) + 
+    #geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
+    geom_line(aes(group = interaction(Handling, SubjID)), size = 1) +
+    #geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
+    labs(x = "Reward.Handling", y = "Proportion Accepted") +
+    scale_color_manual(values = cols) +
+    facet_wrap(vars(Cost), ncol = 2) +
+    theme(legend.key = element_blank(),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16))
+
+# now for each first block experienced, how do costs compare per reward x handling
+dataAll %>%
+  group_by(SubjID) %>%
+  mutate(FirstBlock = case_when(
+    Handling[1] == 2 ~ "Two",
+    Handling[1] == 10 ~ "Ten",
+    Handling[1] == 14 ~ "Fourteen",
+  )) %>%
+  group_by(Cost, Handling, Reward, FirstBlock) %>%
+  summarise(pAccept = mean(Choice),
+            SE = sd(Choice) / sqrt(length(Choice))) %>%
+  ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
+    geom_point(size = 3) + 
+    geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
+    geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
+    labs(x = "Reward.Handling", y = "Proportion Accepted") +
+    scale_color_manual(values = cols) +
+    facet_wrap(vars(FirstBlock), ncol = 3) +
+    theme(legend.key = element_blank(),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16))
 ```

### 2019-05-13 Cost2/Cost2_prereg.Rmd
pre-post analyses for both Costs. Need pre/post mix logistic for cost 2 now

@@
 ``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
-# pre
-t1 <- dataAll %>%
-  filter(Choice < 2, Half == "Half_1") %>%
+# # pre
+# t1 <- dataAll %>%
+#   filter(Choice < 2, Half == "Half_1") %>%
+#   group_by(SubjID) %>%
+#   filter(Handling == 10) %>%
+#   group_by(SubjID, Cost, Reward) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   group_by(Cost, Reward) %>%
+#   summarise(propAccept = mean(pAccept),
+#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
+#   ungroup() %>%
+#   mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
+#   ggplot(aes(Reward, propAccept, color = Cost)) +
+#     geom_point(size = 3, show.legend = F) +
+#     geom_line(show.legend = F) +
+#     scale_color_manual(values = cols) +
+#     scale_fill_manual(values = cols) +
+#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
+#     scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
+#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+#     labs(y = "Proportion Accepted", title = "First Half") +
+#     theme(legend.key = element_blank(),
+#           legend.position = c(0.8, 0.25),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
+# 
+# # post half
+# t2 <- dataAll %>%
+#   filter(Choice < 2, Half == "Half_2") %>%
+#   group_by(SubjID) %>%
+#   filter(Handling == 10) %>%
+#   group_by(SubjID, Cost, Reward) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   group_by(Cost, Reward) %>%
+#   summarise(propAccept = mean(pAccept),
+#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
+#   ungroup() %>%
+#   mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
+#   ggplot(aes(Reward, propAccept, color = Cost)) +
+#     geom_point(size = 3, show.legend = F) +
+#     geom_line(show.legend = F) +
+#     scale_color_manual(values = cols) +
+#     scale_fill_manual(values = cols) +
+#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
+#     scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
+#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+#     labs(y = "", title = "Second Half") +
+#     theme(legend.position = c(0.8, 0.2),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
+# 
+# 
+# 
+# grid.arrange(t1, t2, ncol = 2)
+
+dataAll %>%
+  filter(Choice < 2) %>%
   group_by(SubjID) %>%
   filter(Handling == 10) %>%
-  group_by(SubjID, Cost, Reward) %>%
+  mutate(Half = ifelse(Half == "Half_1", "First Block", "Last Block")) %>%
+  group_by(SubjID, Half, Cost, Reward) %>%
   summarise(pAccept = mean(Choice)) %>%
-  group_by(Cost, Reward) %>%
+  group_by(Half, Cost, Reward) %>%
   summarise(propAccept = mean(pAccept),
@@
     geom_point(size = 3, show.legend = F) +
-    geom_line(show.legend = F) +
+    geom_line(size = 1, show.legend = F) +
     scale_color_manual(values = cols) +
@@
     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-    labs(y = "Proportion Accepted", title = "First Half") +
+    labs(y = "Proportion Accepted") +
+    facet_wrap(vars(Half), ncol = 2) +
     theme(legend.key = element_blank(),
-          legend.position = c(0.8, 0.25),
+          legend.position = c(0.9, 0.25),
           panel.grid.major = element_blank(), 
@@
 
-# post half
-t2 <- dataAll %>%
-  filter(Choice < 2, Half == "Half_2") %>%
-  group_by(SubjID) %>%
-  filter(Handling == 10) %>%
-  group_by(SubjID, Cost, Reward) %>%
-  summarise(pAccept = mean(Choice)) %>%
-  group_by(Cost, Reward) %>%
-  summarise(propAccept = mean(pAccept),
-            SE = sd(pAccept) / sqrt(nSubjs)) %>%
-  ungroup() %>%
-  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
-  ggplot(aes(Reward, propAccept, color = Cost)) +
-    geom_point(size = 3, show.legend = F) +
-    geom_line(show.legend = F) +
-    scale_color_manual(values = cols) +
-    scale_fill_manual(values = cols) +
-    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
-    scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
-    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-    labs(y = "", title = "Second Half") +
-    theme(legend.position = c(0.8, 0.2),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
-
-grid.arrange(t1, t2, ncol = 2)
 ```
@@
           text = element_text(size = 16))
+
+# # now also separated by half
+# dataAll %>%
+#   group_by(SubjID) %>%
+#   mutate(FirstBlock = case_when(
+#     Handling[1] == 2 ~ "Two",
+#     Handling[1] == 10 ~ "Ten",
+#     Handling[1] == 14 ~ "Fourteen",
+#   )) %>%
+#   group_by(Cost, Handling, Reward, FirstBlock, Half) %>%
+#   summarise(pAccept = mean(Choice),
+#             SE = sd(Choice) / sqrt(length(Choice))) %>%
+#   ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
+#     geom_point(size = 3) + 
+#     geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
+#     geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
+#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
+#     scale_color_manual(values = cols) +
+#     facet_wrap(vars(Half, FirstBlock), ncol = 3) +
+#     theme(legend.key = element_blank(),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
 ```

### 2019-05-13 Cost2/Cost2_prereg.Rmd
mixed logistic pre/post ready

@@
 
+# summary matrices for refrence-changing models
+betaMatrix <- function(model, rearrange = NA) {
+# get a similarity matrix of the resulting coefficient pairings for the cost conditions
+# first, do a full_join based on column names on the list of coefficient vectors from each dummy code relevel
+# then match the names of columns and rows so NAs are in the diagonal
+
+  # get the names of the reference group per model iteration
+  refnames <- names(model)
+
+  # coefficient matrix
+  temp <- lapply(model, function(data) {coefficients(data)$SubjID[1, 2:4]})
+  mixCoeffs <- bind_rows(temp) 
+  preln <- ifelse("Cost" %in% substr(names(mixCoeffs), 1, 4), 4, 5) # count how many characters precede the name of each cost (diff across studies)
+  dimnames(mixCoeffs) <- list(refnames, substr(names(mixCoeffs), preln + 1, 20))
+  mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
+  mixCoeffs[is.na(mixCoeffs)] <- 0
+
+  # now the pvals
+  temp <- lapply(model, function(data) {as.list(summary(data)$coefficients[2:4, 4])})
+  mixPvals <- as.matrix(bind_rows(temp)) 
+  dimnames(mixPvals) <- list(refnames, substr(colnames(mixPvals), preln + 1, 20))
+  mixPvals <- as.matrix(mixPvals[, match(rownames(mixPvals), colnames(mixPvals))])
+  mixPvals[is.na(mixPvals)] <- 1
+
+  # if you would like to re-arrange the coefficient order, supply a vector with the desired sequence
+  if (length(rearrange) > 1) {
+    mixCoeffs <- mixCoeffs[rearrange, rearrange]
+    dimnames(mixCoeffs) <- list(rearrange, rearrange)
+    mixPvals <- mixPvals[rearrange, rearrange]
+    dimnames(mixPvals) <- list(rearrange, rearrange)
+  }
+
+  # combine matrices into list to return
+  out <- list(Betas = round(mixCoeffs, digits = 2),
+              Pvals = round(mixPvals, digits = 5))
+
+  return(out)
+
+}
+
 ```
@@
 
-``` {r 16.2.3. Mixed Effects Model, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
+``` {r 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
 # clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
@@
 
-# matrix of coefficients
-# 
-temp <- lapply(mixLogis_main, function(model) {as.list(summary(model)$coefficients[2:4, 1])})
-mixCoeffs <- as.matrix(bind_rows(temp)) #reduce(temp, full_join) 
-dimnames(mixCoeffs) <- list(names(temp), substr(colnames(mixCoeffs), 5, 20))
-mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
-mixCoeffs[is.na(mixCoeffs)] <- 0
-mixCoeffs <- mixCoeffs[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]
-
-# matrix of pvals
-temp <- lapply(mixLogis_main, function(model) {as.list(summary(model)$coefficients[2:4, 4])})
-mixPvals <- as.matrix(bind_rows(temp)) 
-dimnames(mixPvals) <- list(names(temp), substr(colnames(mixPvals), 5, 20))
-mixPvals <- as.matrix(mixPvals[, match(rownames(mixPvals), colnames(mixPvals))])
-rownames(mixPvals) <- colnames(mixPvals)
-mixPvals <- mixPvals[c("Cognitive", "Physical", "Wait", "Easy"), c("Cognitive", "Physical", "Wait", "Easy")]
-diag(mixPvals) <- 1
+# matrix of coefficients and pvalues
+rearrange <- c("Cognitive", "Easy", "Wait", "Physical") # to kinda match the order in Cost 3
+mixSummary <- betaMatrix(mixLogis_main, rearrange = rearrange)
+diag(mixSummary$Pvals) <- NA
 
@@
 
-corrplot(mixCoeffs, 
+corrplot(mixSummary$Betas, 
          is.corr = F, 
-         p.mat = mixPvals, 
-         type = "upper",
+         p.mat = mixSummary$Pvals, 
+         type = "lower",
          outline = T,
-         insig = "p-value",
-         sig.level = -1, 
+         #insig = "p-value",
+         sig.level = 0.05, 
          na.label = "square", 
@@
 
-``` {r 16.2.3. Mixed Effects Model plot rand intercepts, echo=FALSE,fig.align="center",fig.width=5,fig.height=4}
+``` {r 16.2.3. Mixed Effects Model plot rand intercepts, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
 # plot random intercepts in increasing order
@@
 ```
+
+This prompted the question of whether fitting the mixed logistic model could confirm this shift in preferences.
+Just as before, the matrix below show the coefficient magnitude (color) and pvalues for differences based on iterating through costs as reference dummy codes.
+
+``` {r 16.3.2. mix pre/post separately, echo = FALSE, fig.align="center", fig.width = 5, fig.height = 4}
+## compute the same mixed effects logistic for each half
+# mixed logistic for the first half
+mixLogis_pre <- list()
+mixData <- dataAll %>%
+  filter(Half == "Half_1") %>%
+  group_by(SubjID, Cost, Handling, Reward) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice))
+
+mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
+mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
+mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
+mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+
+# mixed logistic for the second half
+mixLogis_post <- list()
+mixData <- dataAll %>%
+  filter(Half == "Half_2") %>%
+  group_by(SubjID, Cost, Handling, Reward) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice))
+
+mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
+mixLogis_post$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
+mixLogis_post$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
+mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+
+## now produce a summary matrix
+# get the beta and pvalue matrices 
+betasPre <- betaMatrix(mixLogis_pre, rearrange = rearrange)
+betasPost <- betaMatrix(mixLogis_post, rearrange = rearrange)
+
+# and combine them
+betaMat <- matrix(NA, nrow = nrow(betasPre$Betas), ncol = nrow(betasPre$Betas))
+betaMat[lower.tri(betaMat)] <- betasPre$Betas[lower.tri(betasPre$Betas)]
+betaMat[upper.tri(betaMat)] <- betasPost$Betas[lower.tri(betasPost$Betas)]
+dimnames(betaMat) <- list(rearrange, rearrange)
+
+pvalMat <- matrix(NA, nrow = nrow(betasPre$Pvals), ncol = nrow(betasPre$Pvals))
+pvalMat[lower.tri(pvalMat)] <- betasPre$Pvals[lower.tri(betasPre$Pvals)]
+pvalMat[upper.tri(pvalMat)] <- betasPost$Pvals[lower.tri(betasPost$Pvals)]
+dimnames(pvalMat) <- list(rearrange, rearrange)
+
+# remove uninteresting comparisons 
+diag(betaMat) <- 0
+
+# aand plot
+corrplot(betaMat, 
+         is.corr = F, 
+         p.mat = pvalMat, 
+         outline = T,
+         #insig = "p-value",
+         sig.level = 0.05, 
+         na.label = "square", 
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black",
+         tl.cex = 0.8,
+         col = col2(200))
+````
+
 \bigskip
@@
 
-``` {r Testing plots, echo=FALSE,fig.align="center",fig.width=10,fig.height=8}
+``` {r Testing plots, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 4}
 # a facet grid of p(acceptances) as a function of reward x handling, distinguishing between first handling time experienced,
@@
 # think of doing it for the block order and then prop accepted across costs
-dataAll %>%
-  group_by(SubjID) %>%
-  mutate(BlockOrder = case_when(
-    Handling[1] == 2 ~ "Two",
-    Handling[1] == 10 ~ "Ten",
-    Handling[1] == 14 ~ "Fourteen",
-  )) %>%
-  group_by(SubjID, Cost, Handling, Reward, BlockOrder) %>%
-  summarise(pAccept = mean(Choice)) %>%
-  ggplot(aes(interaction(Reward, Handling), pAccept, linetype = BlockOrder, color = BlockOrder)) + 
-    geom_point(size = 3) + 
-    #geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
-    geom_line(aes(group = interaction(Handling, SubjID)), size = 1) +
-    #geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
-    labs(x = "Reward.Handling", y = "Proportion Accepted") +
-    scale_color_manual(values = cols) +
-    facet_wrap(vars(Cost), ncol = 2) +
-    theme(legend.key = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
+# dataAll %>%
+#   group_by(SubjID) %>%
+#   mutate(BlockOrder = case_when(
+#     Handling[1] == 2 ~ "Two",
+#     Handling[1] == 10 ~ "Ten",
+#     Handling[1] == 14 ~ "Fourteen",
+#   )) %>%
+#   group_by(SubjID, Cost, Handling, Reward, BlockOrder) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   ggplot(aes(interaction(Reward, Handling), pAccept, linetype = BlockOrder, color = BlockOrder)) + 
+#     geom_point(size = 3) + 
+#     #geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
+#     geom_line(aes(group = interaction(Handling, SubjID)), size = 1) +
+#     #geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
+#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
+#     scale_color_manual(values = cols) +
+#     facet_wrap(vars(Cost), ncol = 2) +
+#     theme(legend.key = element_blank(),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
 

### 2019-05-13 Cost2/Cost2_prereg.Rmd
further matching the corrplots across studies

@@
 
-The plot below shows the distribution of random intercepts across participants of each group.
-Participants in the easy condition show much more variability than the other groups, potentially suggesting a bias in choices in this condition.
-Nonetheless, the intercepts per group are centered around zero.
-
 ``` {r 16.2.3. Mixed Effects Model plot rand intercepts, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
@@
 
-# plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
-temp <- ranef(mixLogis_main$Wait)$SubjID %>%
-  gather(key = Cost, value = RandEffects, colnames(.))
-
-(RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
-  geom_hline(yintercept = 0, alpha = 0.7, linetype = "dashed") + 
-  geom_boxplot(show.legend = F) +
-  scale_fill_manual(values = cols) + 
-  labs(x = "") +
-  theme(panel.grid.major = element_blank(), 
-              panel.grid.minor = element_blank(), 
-              panel.background = element_blank(), 
-              axis.line = element_line(colour = "black"),
-              text = element_text(size = 16)))
+# # plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
+# temp <- ranef(mixLogis_main$Wait)$SubjID %>%
+#   gather(key = Cost, value = RandEffects, colnames(.)) 
+# 
+# (RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
+#   geom_hline(yintercept = 0, alpha = 0.7, linetype = "dashed") + 
+#   geom_boxplot(show.legend = F) +
+#   scale_fill_manual(values = cols) + 
+#   labs(x = "") +
+#   theme(panel.grid.major = element_blank(), 
+#               panel.grid.minor = element_blank(), 
+#               panel.background = element_blank(), 
+#               axis.line = element_line(colour = "black"),
+#               text = element_text(size = 16)))
 

### 2019-05-14 Cost2/Cost2_prereg.Rmd
added a section on mean forced travels as a function of time, and cleaned inattentive data

@@
 
-This plot shows the AIC for every model.
-The figure below shows AIC and BIC for all the models.
-As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`).
-
 ``` {r 16.2.4. Plot Deviance comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
@@
 ```
+
+This plot shows the AIC for every model.
+The figure below shows AIC and BIC for all the models.
+As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`).
+The reduction in deviance from an intercept-only model was drastic enough that we did not compute an LRT.
 
@@
                                    seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
-                         ggplot(aes(Block, propAccept, fill = Cost)) +
-                           geom_point(size = 2, pch = 21, color = "black") +
-                           geom_errorbar(aes(ymin=propAccept - seAccept, ymax=propAccept + seAccept, color = Cost), width = 0.1) +
-                           geom_line(aes(color = Cost)) +
+                         ggplot(aes(Block, propAccept, color = Cost)) +
+                           geom_point(size = 2) +
+                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
+                           geom_line() +
                            ylim(0, 1) +
@@
 
-``` {r Testing plots, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 4}
+``` {r Testing plots, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
 # a facet grid of p(acceptances) as a function of reward x handling, distinguishing between first handling time experienced,
@@
 
-# now for each first block experienced, how do costs compare per reward x handling
-dataAll %>%
-  group_by(SubjID) %>%
-  mutate(FirstBlock = case_when(
-    Handling[1] == 2 ~ "Two",
-    Handling[1] == 10 ~ "Ten",
-    Handling[1] == 14 ~ "Fourteen",
-  )) %>%
-  group_by(Cost, Handling, Reward, FirstBlock) %>%
-  summarise(pAccept = mean(Choice),
-            SE = sd(Choice) / sqrt(length(Choice))) %>%
-  ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
-    geom_point(size = 3) + 
-    geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
-    geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
-    labs(x = "Reward.Handling", y = "Proportion Accepted") +
-    scale_color_manual(values = cols) +
-    facet_wrap(vars(FirstBlock), ncol = 3) +
-    theme(legend.key = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
+# # now for each first block experienced, how do costs compare per reward x handling
+# dataAll %>%
+#   group_by(SubjID) %>%
+#   mutate(FirstBlock = case_when(
+#     Handling[1] == 2 ~ "Two",
+#     Handling[1] == 10 ~ "Ten",
+#     Handling[1] == 14 ~ "Fourteen",
+#   )) %>%
+#   group_by(Cost, Handling, Reward, FirstBlock) %>%
+#   summarise(pAccept = mean(Choice),
+#             SE = sd(Choice) / sqrt(length(Choice))) %>%
+#   ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
+#     geom_point(size = 3) + 
+#     geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
+#     geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
+#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
+#     scale_color_manual(values = cols) +
+#     facet_wrap(vars(FirstBlock), ncol = 3) +
+#     theme(legend.key = element_blank(),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
 
@@
 #           text = element_text(size = 16))
+
+# forced travels as a function of time
+# number of forced travels as a function of time for cognitive and grip trials
+forcedTravels <- dataAll %>%
+  filter(rawChoice == 2) %>%
+  group_by(SubjID, Cost, Block) %>%
+  count() %>%
+  group_by(Cost, Block) %>%
+  summarise(mTravels = mean(n),
+            SE = sd(n) / length(Block))
+
+tempphys <- tibble(Cost = as.factor(rep("Physical", 6)),
+                   Block = as.numeric(seq(6)),
+                   mTravels = rep(0, 6),
+                   SE = rep(0, 6))
+
+forcedTravels <- full_join(forcedTravels, tempphys)
+
+  ggplot(data = forcedTravels, aes(Block, mTravels, color = Cost )) +
+    geom_line(size = 1) +
+    geom_point(size = 3) +
+    geom_errorbar(aes(ymin = mTravels - SE, ymax = mTravels + SE), width = 0.4) +
+    scale_x_continuous(breaks = seq(6)) +
+    labs(y = "Mean number of forced travels") +
+    ylim(0, 4) +
+    theme(legend.key = element_blank(),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16))
 ```

### 2019-05-14 Cost2/Cost2_prereg.Rmd
fixed some standard errors

@@
   summarise(mTravels = mean(n),
-            SE = sd(n) / length(Block))
+            SE = sd(n) / sqrt(21))
 
@@
     scale_x_continuous(breaks = seq(6)) +
-    labs(y = "Mean number of forced travels") +
+    labs(y = "Mean n of forced travels") +
     ylim(0, 4) +

### 2019-05-14 Cost2/Cost2_prereg.Rmd
forced travel plots ready

@@
 forcedTravels <- dataAll %>%
-  filter(rawChoice == 2) %>%
+  #filter(rawChoice == 2) %>%
   group_by(SubjID, Cost, Block) %>%
-  count() %>%
+  filter(Cost %in% c("Cognitive", "Physical")) %>%
+  summarise(pTravel = mean(rawChoice == 2)) %>%
   group_by(Cost, Block) %>%
-  summarise(mTravels = mean(n),
-            SE = sd(n) / sqrt(21))
+  summarise(mTravels = mean(pTravel),
+            SE = sd(pTravel) / sqrt(21))
 
@@
   scale_x_continuous(breaks = seq(6)) +
-    labs(y = "Mean n of forced travels") +
-    ylim(0, 4) +
+  labs(y = "Prop. of forced travels") +
+  ylim(0, NA) +
   theme(legend.key = element_blank(),

### 2019-05-14 Cost2/Cost2_prereg.Rmd
working on opportunity cost model

@@
 
-# minimize the negative log likelihood
-optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA", simplify = F) {
+# optimize the OC model
+optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA", simplify = F, optfun = negLogLik) {
+
+  # Data: The participant's log
+  # Algorithm: probably let be
+  # optfun: an external function to minimize (in this case OC, separately defined as negloglik)
+
   # Prep data
   handling <- Data$Handling
-  reward <- Data$Reward
+  reward <- Data$Offer
   choice <- Data$Choice
@@
   out <- list()
-  out$percentQuit <- (sum(choice==0) / length(choice)) * 100
-  out$percentAccept <- (sum(choice==1) / length(choice)) * 100 
+  out$percentQuit <- mean(choice == 0) * 100
+  out$percentAccept <- mean(choice== 1) * 100 
   miss <- (choice != 1) & (choice != 0)
-  out$percentMiss <- (sum(miss) / length(choice))  * 100
+  out$percentMiss <- mean(miss)  * 100
   choice <- choice[!miss]
@@
   # Establish lower and upper bounds
-  LB <- log((min(reward)/max(handling)) * 0.99)
-  UB <- log((max(reward)/min(handling)) * 1.01)
+  LB <- round(log((min(reward)/max(handling)) * 0.99), digits = 4)
+  UB <- round(log((max(reward)/min(handling)) * 1.01), digits = 4) # in reality this should be the second largest, since no one would reject the highest val
 
@@
     ifelse(sum(choice) == length(choice), out$Gamma <- exp(LB), out$Gamma <- exp(UB)) 
-    out$Scale <- NA
+    out$Scale <- 1 # it was NA, but in theory a temperature of 1 also indicates noiseless estimates, and allows for easier fit computations
     out$LL <- 0
@@
       tempInfo <- nloptr(x0 = params[i, ], 
-                   eval_f = negLogLik, 
+                   eval_f = optfun, 
                    lb = c(log(0.001), LB),
@@
   out$predicted[out$predicted == TRUE] <- 1
-  out$percentPredicted <- (sum(out$predicted == choice) / length(choice)) * 100
+  out$percentPredicted <- mean(out$predicted == choice)
 

### 2019-05-16 Cost2/Cost2_prereg.Rmd
pre/post permutation tests

@@
 colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
+
+## PRE/POST PAIRED PERMUTATIONS
+temp <- dataAll %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
+            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
+  plyr::dlply("Cost", identity)
+
+# paired perms and effect sizes
+prepost$CohenD <- sapply(temp, function(data) {DescTools::CohenD(data$propAccept_1, data$propAccept_2)})
+prepost$Perms <- sapply(temp, function(data) {permute(data$propAccept_1, data$propAccept_2, paired = T, simple = T)})
 ```

### 2019-06-02 Cost2/Cost2_prereg.Rmd
typo

@@
                  filter(Choice < 2) %>%
+                 rename(Offer = Reward) %>%
                  group_by(Cost, SubjID) %>%

### 2019-08-01 Cost2/Cost2_prereg.Rmd
making OC model optimizer compatible across scripts

@@
   handling <- Data$Handling
-  reward <- Data$Offer
+  ifelse(is.null(try(dataAll$Offer)), reward <- dataAll$Reward, reward <- dataAll$Offer) #reward <- Data$Offer (FIX THIS BY CALLING ALL COLUMNS REWARD, NOT OFFER)
   choice <- Data$Choice
@@
 # rawChoice will be used to compute the # of mistakes
+# NOTE: P389 IS DUPLICATED. FIND OUT REAL ID # FOR ONE OF THEM.
 setwd("./data")
 files <- dir(pattern = '_log.csv')
-nSubjs <- length(files)
+nSubj <- length(files)
 
@@
                          summarize(propAccept = mean(propAccept_subj),
-                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
+                                   seAccept = sd(propAccept_subj)/sqrt(nSubj)) %>%
                          ggplot(aes(Block, propAccept, color = Cost)) +
@@
 #   summarise(propAccept = mean(pAccept),
-#             SE = sd(pAccept) / sqrt(nSubjs)) %>%
+#             SE = sd(pAccept) / sqrt(nSubj)) %>%
 #   ungroup() %>%
@@
   summarise(propAccept = mean(pAccept),
-            SE = sd(pAccept) / sqrt(nSubjs)) %>%
+            SE = sd(pAccept) / sqrt(nSubj)) %>%
   ungroup() %>%

### 2019-08-02 Cost2/Cost2_prereg.Rmd
corrected error miscalculating the p(AR_effects) in Cost 3, plus better matching of htmls

--- 2019-06-02 Cost2/Cost2_prereg.Rmd
@@
 # rawChoice will be used to compute the # of mistakes
+# NOTE: P389 IS DUPLICATED. FIND OUT REAL ID # FOR ONE OF THEM.
 setwd("./data")
 files <- dir(pattern = '_log.csv')
-nSubjs <- length(files)
 
@@
 subjList <- unique(dataAll$SubjID)
-nSubj <- length(subjList)
+nSubjs <- length(subjList)
 
@@
 
-# Around 10% seemed to have been influenced by previous quitting
-prcntAR_effects <- mean(AR_CIs) * 100
 ```
@@
 To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero.
-By this measure, around `r round(prcntAR_effects)` percent of our participants seemed to have been influenced by recent quitting.
+By this measure, `r sum(AR_CIs)` out of `r nSubjs` of our participants seemed to have been influenced by recent quitting.
 However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.

### 2019-08-02 Cost2/Cost2_prereg.Rmd
improving survival curve

@@
 
-# Reaction times ECDFs including offer and in-trial quits
-(RTs <- dataAll %>%
-  #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
-  filter(rawChoice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
-  ggplot(aes(RT, color = Cost)) + 
-    #stat_ecdf(lwd = 1.2, geom = "smooth") +
-    geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
+# # Reaction times ECDFs including offer and in-trial quits
+# (RTs <- dataAll %>%
+#   #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
+#   filter(rawChoice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
+#   ggplot(aes(RT, color = Cost)) + 
+#     #stat_ecdf(lwd = 1.2, geom = "smooth") +
+#     geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
+#     geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
+#     scale_color_manual(values = cols) +
+#     scale_x_continuous(breaks = seq(14)) +
+#     labs(x = "Time in Trial", y = "Proportion Completed") +
+#     theme(panel.grid.major = element_blank(),
+#       panel.grid.minor = element_blank(),
+#       panel.background = element_blank(),
+#       axis.line = element_line(colour = "black"),
+#       text = element_text(size = 16)))
+
+# NEW VERSION OF SURVIVAL. BUT STILL NEEDS A BIT OF WORK. ALSO, CHECK THAT RT > 14s
+
+library(survival)
+library(ggfortify)
+
+# this version of a survival curve forces all successful acceptances to have an RT of 14
+# that's to avoid jumps from 2s to 10s to 14s
+# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor?
+temp <- dataAll %>%
+    filter(rawChoice < 2) %>% 
+    mutate(#RT = ifelse(Choice == 1, 14, RT),
+           Choice = 1 - Choice)
+
+survData <- survfit(Surv(RT, Choice) ~ Cost, data = temp)
+
+autoplot(survData) +
   geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
   scale_color_manual(values = cols) +
+  scale_fill_manual(values = cols) +
   scale_x_continuous(breaks = seq(14)) +
+  ylim(0, 1) +
   labs(x = "Time in Trial", y = "Proportion Completed") +
@@
         axis.line = element_line(colour = "black"),
-      text = element_text(size = 16)))
+        text = element_text(size = 16))
 

### 2019-08-05 Cost2/Cost2_prereg.Rmd
many fixes (see description)
- Fixed duplicate subjid
- Matched survival curves with fixed response times (glitch in logs for few trials)
- Fixed column renaming for OC model. Will now switch all reward columns to the same name across exps.

@@
   handling <- Data$Handling
-  ifelse(is.null(try(dataAll$Offer)), reward <- dataAll$Reward, reward <- dataAll$Offer) #reward <- Data$Offer (FIX THIS BY CALLING ALL COLUMNS REWARD, NOT OFFER)
+  reward <- Data$Offer 
   choice <- Data$Choice
@@
 # rawChoice will be used to compute the # of mistakes
-# NOTE: P389 IS DUPLICATED. FIND OUT REAL ID # FOR ONE OF THEM.
+# The RT is upper-bounded because a glitch in the code made two 14s trials last longer (among all p's) 
 setwd("./data")
@@
   mutate(rawChoice = Choice,
+         RT = ifelse(RT > 14.1, 14, RT),
          Choice = ifelse(Choice == 2, 1, Choice),
@@
   ylim(0, 1) +
-  labs(x = "Time in Trial", y = "Proportion Completed") +
+  labs(x = "Time in Trial", y = "Proportion Completed", fill = "Cost", color = "Cost") +
   theme(panel.grid.major = element_blank(),
@@
                  filter(Choice < 2, Half == "Half_1") %>%
+                 rename(Offer = Reward) %>%
                  group_by(Cost, SubjID) %>%
@@
                  filter(Choice < 2, Half == "Half_2") %>%
+                 rename(Offer = Reward) %>%
                  group_by(Cost, SubjID) %>%
@@
                  mutate(OC = Handling * Gamma,
-                        predicted = Reward > OC) %>% 
+                        predicted = Offer > OC) %>% 
                  summarise(percentPredicted = mean(predicted == Choice) * 100)

### 2019-08-05 Cost2/Cost2_prereg.Rmd
data column names are better matched now (Cost and Offer), and the scripts work well with them

@@
 # plot logistic (for the prop complete test, mainly, but it can be easily expanded for more flexibility in n-params)
-plotLogis <- function(coeffs = 1, group = "Cognitive", handling = 1:14, reward = 1:20, xAxis = "Reward", plotType = lines, color = "black", lType = 1, pchType = 16){
+plotLogis <- function(coeffs = 1, group = "Cognitive", handling = 1:14, reward = 1:20, xAxis = "Offer", plotType = lines, color = "black", lType = 1, pchType = 16){
 
@@
     # now the parameters
-    label = "Reward Amount"
+    label = "Offer Amount"
     if (group == "Cognitive"){cog = 1} else {cog = 0}
@@
     if (group == "Easy") {easy = 1} else {easy = 0}
-    if (xAxis == "Reward"){
+    if (xAxis == "Offer"){
         xAxis = reward 
-        label = "Reward Amount" 
+        label = "Offer Amount" 
     } else {
@@
         # earnings
-        tempSummary[subj,3] <- sum(Data[[subj]]$Reward[tempChoice==1])
+        tempSummary[subj,3] <- sum(Data[[subj]]$Offer[tempChoice==1])
 
@@
          optimal = case_when(
-          (Handling == 10 & Reward < 8) ~ 0,
-          (Handling == 14 & Reward < 20) ~ 0,
+          (Handling == 10 & Offer < 8) ~ 0,
+          (Handling == 14 & Offer < 20) ~ 0,
           TRUE ~ 1
@@
   plyr::dlply("SubjID", identity) %>%
-  lapply(function(data) {glm(Choice ~ Handling + Reward, data = data, family = "binomial")}) %>%
+  lapply(function(data) {glm(Choice ~ Handling + Offer, data = data, family = "binomial")}) %>%
   sapply(coefficients)
@@
 rankHand <- wilcox.test(logisRH["Handling", ])
-rankReward <- wilcox.test(logisRH["Reward", ])
+rankOffer <- wilcox.test(logisRH["Offer", ])
 
 # Plot coeffs
-temp <- melt(logisRH[c("Handling", "Reward"), ])
+temp <- melt(logisRH[c("Handling", "Offer"), ])
 qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
@@
 The results show the expected discounting effect of increasing the handling time, as well as the increase in acceptance likelihood as a function of reward increments.
-We found that these coefficients were significantly different from zero for both handling (V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) and reward (V = `r rankReward$statistic`, p `r ifelse(rankReward$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) regardless of cost condition.
+We found that these coefficients were significantly different from zero for both handling (V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) and reward (V = `r rankOffer$statistic`, p `r ifelse(rankOffer$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) regardless of cost condition.
 
@@
               plyr::dlply("SubjID", identity) %>%
-              lapply(function(data) {glm(Choice ~ Handling + Reward + AR, data = data, family = "binomial")})
+              lapply(function(data) {glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial")})
 
@@
   group_by(SubjID, Cost) %>%
-  summarise(Earnings = sum(Reward[Choice == 1] / 100),
+  summarise(Earnings = sum(Offer[Choice == 1] / 100),
             pComplete = mean(Choice)) %>%
@@
   filter(Choice < 2) %>%
-  group_by(SubjID, Handling, Reward, Cost) %>%
+  group_by(SubjID, Handling, Offer, Cost) %>%
   summarise(pAccept = mean(Choice)) %>%
   mutate(optimal = case_when(
-          (Handling == 10 & Reward < 8) ~ 0,
-          (Handling == 14 & Reward < 20) ~ 0,
+          (Handling == 10 & Offer < 8) ~ 0,
+          (Handling == 14 & Offer < 20) ~ 0,
           TRUE ~ 1
         )) %>% 
-  group_by(Handling, Reward, Cost) %>%
+  group_by(Handling, Offer, Cost) %>%
   summarise(meanAccept = mean(pAccept),
@@
         group_by(SubjID, Cost) %>%
-        summarise(Earnings = sum(Reward[rawChoice == 1] / 100),
+        summarise(Earnings = sum(Offer[rawChoice == 1] / 100),
                   pAccept = mean(Choice))
@@
 *In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors.
-Reward and handling time will be within-subject factors, and condition a between-subjects factor.
+Offer and handling time will be within-subject factors, and condition a between-subjects factor.
 In support of hypotheses 4.1.
@@
         filter(Choice < 2) %>%
-        group_by(SubjID, Cost, Handling, Reward) %>%
+        group_by(SubjID, Cost, Handling, Offer) %>%
         summarise(pAccept = mean(Choice))
@@
 # I think I like this the most
-prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Reward + 
-                                 Error(SubjID / (Handling * Reward))))
+prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Offer + 
+                                 Error(SubjID / (Handling * Offer))))
 
@@
         filter(Choice < 2) %>%
-        group_by(SubjID, Cost, Handling, Reward, optimal) %>%
+        group_by(SubjID, Cost, Handling, Offer, optimal) %>%
         summarise(pAccept = mean(Choice)) %>%
-        group_by(Cost, Handling, Reward, optimal) %>%
+        group_by(Cost, Handling, Offer, optimal) %>%
         summarise(meanComplete = mean(pAccept),
@@
 # and plot
-(a1 <- ggplot(data = trueProp, aes(interaction(Reward, Handling), meanComplete, color = Cost)) + 
+(a1 <- ggplot(data = trueProp, aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
         geom_point(size = 3) + 
@@
         geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
-        labs(x = "Reward.Handling", y = "Proportion Accepted") +
+        labs(x = "Offer.Handling", y = "Proportion Accepted") +
         scale_color_manual(values = cols) +
@@
   filter(Choice < 2) %>%
-  group_by(SubjID, Cost, Handling, Reward) %>%
+  group_by(SubjID, Cost, Handling, Offer) %>%
   summarize(totalChoices = length(Choice),
@@
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
-mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 
@@
 mixLogis_compare$Handling <- glmer(cbind(totalAccepted, totalQuits) ~ Handling + (1 | SubjID), family = "binomial", data = mixData)
-mixLogis_compare$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Reward + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$Offer <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixLogis_compare$AllMain <- mixLogis_main$Wait
-mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (Cost | SubjID), family = "binomial", data = mixData)
 
@@
 #   filter(Handling == 10) %>%
-#   group_by(SubjID, Cost, Reward) %>%
+#   group_by(SubjID, Cost, Offer) %>%
 #   summarise(pAccept = mean(Choice)) %>%
-#   group_by(Cost, Reward) %>%
+#   group_by(Cost, Offer) %>%
 #   summarise(propAccept = mean(pAccept),
@@
 #   ungroup() %>%
-#   mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
-#   ggplot(aes(Reward, propAccept, color = Cost)) +
+#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+#   ggplot(aes(Offer, propAccept, color = Cost)) +
 #     geom_point(size = 3, show.legend = F) +
@@
   mutate(Half = ifelse(Half == "Half_1", "First Block", "Last Block")) %>%
-  group_by(SubjID, Half, Cost, Reward) %>%
+  group_by(SubjID, Half, Cost, Offer) %>%
   summarise(pAccept = mean(Choice)) %>%
-  group_by(Half, Cost, Reward) %>%
+  group_by(Half, Cost, Offer) %>%
   summarise(propAccept = mean(pAccept),
@@
   ungroup() %>%
-  mutate(Reward = ifelse(Reward == 20, 12, Reward)) %>%
-  ggplot(aes(Reward, propAccept, color = Cost)) +
+  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+  ggplot(aes(Offer, propAccept, color = Cost)) +
     geom_point(size = 3, show.legend = F) +
@@
   filter(Half == "Half_1") %>%
-  group_by(SubjID, Cost, Handling, Reward) %>%
+  group_by(SubjID, Cost, Handling, Offer) %>%
   summarize(totalChoices = length(Choice),
@@
 
-mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 
@@
   filter(Half == "Half_2") %>%
-  group_by(SubjID, Cost, Handling, Reward) %>%
+  group_by(SubjID, Cost, Handling, Offer) %>%
   summarize(totalChoices = length(Choice),
@@
 
-mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_post$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_post$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_post$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_post$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Reward + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
 
@@
                  filter(Choice < 2) %>%
-                 rename(Offer = Reward) %>%
+                 rename(Offer = Offer) %>%
                  group_by(Cost, SubjID) %>%
@@
                  filter(Choice < 2, Half == "Half_1") %>%
-                 rename(Offer = Reward) %>%
+                 rename(Offer = Offer) %>%
                  group_by(Cost, SubjID) %>%
@@
                  filter(Choice < 2, Half == "Half_2") %>%
-                 rename(Offer = Reward) %>%
+                 rename(Offer = Offer) %>%
                  group_by(Cost, SubjID) %>%
@@
 #   )) %>%
-#   group_by(SubjID, Cost, Handling, Reward, BlockOrder) %>%
+#   group_by(SubjID, Cost, Handling, Offer, BlockOrder) %>%
 #   summarise(pAccept = mean(Choice)) %>%
-#   ggplot(aes(interaction(Reward, Handling), pAccept, linetype = BlockOrder, color = BlockOrder)) + 
+#   ggplot(aes(interaction(Offer, Handling), pAccept, linetype = BlockOrder, color = BlockOrder)) + 
 #     geom_point(size = 3) + 
@@
 #     #geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
-#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
+#     labs(x = "Offer.Handling", y = "Proportion Accepted") +
 #     scale_color_manual(values = cols) +
@@
 #   )) %>%
-#   group_by(Cost, Handling, Reward, FirstBlock) %>%
+#   group_by(Cost, Handling, Offer, FirstBlock) %>%
 #   summarise(pAccept = mean(Choice),
 #             SE = sd(Choice) / sqrt(length(Choice))) %>%
-#   ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
+#   ggplot(aes(interaction(Offer, Handling), pAccept, color = Cost)) + 
 #     geom_point(size = 3) + 
@@
 #     geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
-#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
+#     labs(x = "Offer.Handling", y = "Proportion Accepted") +
 #     scale_color_manual(values = cols) +
@@
 #   )) %>%
-#   group_by(Cost, Handling, Reward, FirstBlock, Half) %>%
+#   group_by(Cost, Handling, Offer, FirstBlock, Half) %>%
 #   summarise(pAccept = mean(Choice),
 #             SE = sd(Choice) / sqrt(length(Choice))) %>%
-#   ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
+#   ggplot(aes(interaction(Offer, Handling), pAccept, color = Cost)) + 
 #     geom_point(size = 3) + 
@@
 9.1.3.
-Reward magnitude, manipulated within-subject across individual trials.
+Offer magnitude, manipulated within-subject across individual trials.
 On each trial, participants will learn the amount of money they can earn if they complete the trial (i.e.
@@
 Two types of trial combinations (physical/wait and cognitive/wait) will be experienced three times by each participant in 7-minute-long, interleaved blocks.
-Reward amounts can be 4, 8, or 20 cents, uniformly distributed.
+Offer amounts can be 4, 8, or 20 cents, uniformly distributed.
 Timing information will be disclosed at the beginning of each block, and reward prospects displayed before each trial begins.
@@
 
-### 15.2. Rewards and cost type 
+### 15.2. Offers and cost type 
 Participants can earn 4, 8, or 20 cents per trial at the cost of performing one of the three conditions.

### 2019-08-06 Cost2/Cost2_prereg.Rmd
done matching survival analysis across exps

@@
 
-The ECDF below shows the proportion of quits and acceptances occurring as the trial advanced.
-Drastic changes indicate the end of one of the possible handling times, and sccessful receipt of a reward.
-This shows that there were no quits during the handling time, and displays the proportion of acceptances (1 - the y axis here) for each cost at each handling/travel time combination.
-We can see in the ECDFs below that most decisions to quit happened within the first second into the handling time.
-The reason why the physical and easy condition show slightly lagged responses is that the experiment allowed a one second grace period for participants to begin gripping.
-This results in some of them choosing to wait for that second to indicate an offer rejection.
-
 ``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
@@
 temp <- dataAll %>%
-    filter(rawChoice < 2) %>% 
+    #filter(rawChoice < 2) %>% 
     mutate(#RT = ifelse(Choice == 1, 14, RT),
@@
 ```
+
+The survival curve below shows instances of quiting across a trial for all participants and handling times.
+Censors signal completed trials and forced quits, so most occur at the end of the three possible handling times.
+Participants could only quit once the trial begun.
+This shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
+The reason why the physical and easy condition show slightly lagged responses is that the experiment allowed a one second grace period for participants to begin gripping (marked by the dashed line).
+This resulted in some of them choosing to wait for that second to indicate an offer rejection.
+The proportion of forced quits for cognitive effort was `r round(propFails[2, 2], digits = 2)`, and 0 for the physical conditions (the censor around 4s in the physical condition was an acceptance during 2s handling that was incorrectly recorded at 4s by the experimental code).
 

### 2019-08-06 Cost2/Cost2_prereg.Rmd
Done with pre-post analysis. Now onto the OC modeling

@@
 
-# # Reaction times ECDFs including offer and in-trial quits
-# (RTs <- dataAll %>%
-#   #mutate(RT = ifelse(Choice != 0, RT + 2, RT)) %>%
-#   filter(rawChoice < 2) %>% # change this to 1 to reproduce the original plot, since it would only plot the cdf of quits
-#   ggplot(aes(RT, color = Cost)) + 
-#     #stat_ecdf(lwd = 1.2, geom = "smooth") +
-#     geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
-#     geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
-#     scale_color_manual(values = cols) +
-#     scale_x_continuous(breaks = seq(14)) +
-#     labs(x = "Time in Trial", y = "Proportion Completed") +
-#     theme(panel.grid.major = element_blank(),
-#       panel.grid.minor = element_blank(),
-#       panel.background = element_blank(),
-#       axis.line = element_line(colour = "black"),
-#       text = element_text(size = 16)))
-
-# NEW VERSION OF SURVIVAL. BUT STILL NEEDS A BIT OF WORK. ALSO, CHECK THAT RT > 14s
-
+# this version of a survival curve forces all successful acceptances to have an RT of 14
 library(survival)
@@
 
-# this version of a survival curve forces all successful acceptances to have an RT of 14
 # that's to avoid jumps from 2s to 10s to 14s
@@
 
-The following table shows the coefficients and CI for each linear model, and show that pre-post acceptance rates were very similar for each condition (i.e. one is present in all confidence intervals).
+The following table shows the coefficients and CI for each linear model, and show that pre-post acceptance rates were very similar for each condition (i.e.
+one is present in all confidence intervals).
+Note that interpreting the coefficients depends on the intercept, and the wait condition had a relatively high intercept.
+
+A better test is to perform a pairwise comparison between halves per cost type.
+Paired permutations on means of proportions showed no differences for wait and easy groups (p > 0.5), but significantly lower acceptance rates for physical (*p* = `r prepost$Perms[1]`, Cohen's D = `r prepost$CohenD[1]`) and cognitive (*p* = `r prepost$Perms[2]`, Cohen's D = `r prepost$CohenD[2]`) groups.
+These results are more consistent with the plots above.
 
@@
   ggplot(aes(Offer, propAccept, color = Cost)) +
-    geom_point(size = 3, show.legend = F) +
+    geom_point(size = 3, show.legend = T) +
     geom_line(size = 1, show.legend = F) +
@@
 Conversely, a participant experiencing low opportunity costs would accept the unbeneficial offer of 4 cents for a 14 second delay (or 4/14).
-The model was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
+The model was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood (R-squared: mean = `r mean(summaryOC$all$Rsquared)`, SD = `r sd(summaryOC$all$Rsquared)`).
 The resulting gamma values per participant are shown per group below (gray lines denote the rate of earnings under optimal behavior for all 3 timing contexts), and reflect what was seen in the previous sections: participants in the wait and physical conditions showed higher gamma values (and thus opportunity costs) than in the other two groups.

### 2019-08-06 Cost2/Cost2_prereg.Rmd
cleaning up OC code

@@
 summaryOC$all <- dataAll %>%
-                 filter(Choice < 2) %>%
-                 rename(Offer = Offer) %>%
+                 #filter(rawChoice < 2) %>%
                  group_by(Cost, SubjID) %>%
@@
 summaryOC$pre <- dataAll %>%
-                 filter(Choice < 2, Half == "Half_1") %>%
-                 rename(Offer = Offer) %>%
+                 filter(Half == "Half_1") %>%
                  group_by(Cost, SubjID) %>%
@@
 summaryOC$predicted <- dataAll %>%
-                 filter(Choice < 2, Half == "Half_2") %>%
-                 rename(Offer = Offer) %>%
+                 filter(Half == "Half_2") %>%
                  group_by(Cost, SubjID) %>%

### 2019-09-16 Cost2/Cost2_prereg.Rmd
graph with optimal behavior

@@
 ``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
+# # code to calculate the rwd rate for each acceptance threshold per handling
+# rwd <- c(4, 8, 20)
+# handling <- c(14, 10, 2)
+# travel <- c(2, 6, 14)
+# rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
+# 
+# as_tibble(rwdRates) %>% 
+#   mutate(Handling = handling) %>%
+#   rename(Five = V1,
+#          Eight = V2,
+#          Twenty = V3) %>%
+#   gather(Reward, Rate, -Handling) %>%
+#   mutate(Reward = factor(Reward, levels = list("Five", "Eight", "Twenty")),
+#          Handling = as.character(Handling)) %>%
+#   group_by(Handling) %>%
+#   mutate(Optimal = ifelse(Rate == max(Rate), max(Rate), -1)) %>%
+#   ungroup() %>%
+#   ggplot(aes(Reward, Rate, group = Handling, color = Handling)) +
+#     geom_point(size = 3) +
+#     geom_line(size = 1.5) +
+#     geom_point(aes(Reward, Optimal), pch = 21, color = "black", fill = NA, size = 7, show.legend = F) +
+#     scale_color_manual(values = c("purple", "grey50", "darkgoldenrod3")) +
+#     ylim(0, 1.2) +
+#     labs(y = "Expected eward per sec.", x = "Reward acceptance threshold") +
+#     theme(legend.position = c(0.85, 0.2),
+#           legend.key = element_blank(),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 22))
+
 # prep data to plot the p(accept) based on reward, handling time and cost type

### 2019-09-19 Cost2/Cost2_prereg.Rmd
small aesthetic changes to plots

@@
   ylim(0, 1) +
-  labs(x = "Time in Trial", y = "Proportion Completed", fill = "Cost", color = "Cost") +
-  theme(panel.grid.major = element_blank(),
+  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
+  theme(legend.position = c(0.3, 0.2),
+        panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
@@
         axis.line = element_line(colour = "black"),
-        text = element_text(size = 16))
+        text = element_text(size = 22))
 

### 2019-10-21 Cost2/Cost2_prereg.Rmd
adding plots to probe decision RTs and individual differences within subjects in exp 2

@@
   group_by(Cost) %>% 
-  summarise(meanFT = mean(propFails))
+  summarise(meanFT = mean(propFails),
+            sdFT = sd(propFails))
 
@@
         text = element_text(size = 22))
+
+# RT ecdfs for the whole group across blocks, with the option to subdivide by cost group
+dataAll %>%
+  filter(Choice == 0,
+         RT < 1) %>%
+  ggplot(aes(RT, group = Block, color = Block)) +
+    stat_ecdf() +
+    #facet_wrap(vars(Cost)) +
+    theme_classic()
 

### 2020-02-04 Cost2/Cost2_prereg.Rmd
evolution of reward rates per block (are they getting more optimal? no)

@@
 ``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
-# # code to calculate the rwd rate for each acceptance threshold per handling
+# # code to calculate the rwd/sec rate for each acceptance threshold per handling
 # rwd <- c(4, 8, 20)
-# handling <- c(14, 10, 2)
-# travel <- c(2, 6, 14)
-# rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
+# handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
+# travel <- c(2, 6, 14) + 2
+# sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
 # 

### 2020-02-05 Cost2/grip_timeseries.R
functional grip-strength analysis for a single subject

@@ -1,0 +1,129 @@
+# explore the relationship between reward/handling and grip strength for a single subject
+
+# script mostly to start thinking of Biopac-friendly functions
+# a problem with this analysis is that the data seem cutoff.
+# maybe because biopac stopped running or the computer went to sleep
+# I'm limiting this test script to just half of the data
+
+# general log info
+# psychopy logs each trial either when the reward is achieved or when they quit
+# so gripping starts Xs earlier than the Experiment.Time (x = handling time)
+# create a vector that's Experiment.Time - RT to get approx when the trial starts
+
+# to do: get every 100th milisecond of smoothed and divide trialStart (i.e. downsample); average pressing per trial
+
+###---------- library and functions ---------
+library(tidyverse)
+
+select_signal <- function(physData, start, end, thresh = 2, smoothing = 0) {
+  # this function will use the experimental timing from a log to get rid of non-experimental recordings
+  # this will be recordings prior to the beginning of the session and when the trials stopped
+  # it currently assumes milisecond rate biopac acquisition
+  # variables:
+  # - physData: the vector with grip strength
+  # - start/end: just the time bounds (in ms) containing relevant data 
+  # - thresh: sustained threshold for the grip press (can be estimated by plotting the time series)
+  
+  # the result is a time series vector of grip strength that is aligned with the behavioral log
+  
+  # where does the first trial start?
+  firstTrial <- which(physData > thresh)[1]
+  
+  # index where to cut pre-experimental data
+  preExp <- firstTrial - start 
+  postExp <- end + firstTrial
+  
+  # isolate the signal of interest
+  physData <- physData[preExp:postExp]
+  
+  # smooth the data using a moving average
+  # probably unnecessary for this data
+  if (smoothing > 0) {
+    physData <- stats::filter(physData, sides = 1, filter = rep(1/3, smoothing))
+  }
+  
+  return(physData)
+  
+}
+
+trial_gripping <- function(physData, trialStart, trialLength, average = TRUE) {
+  # this function will generate a data frame that allows to compare the grip strength per choice
+  # -
+  # - trialLength: in ms, can be handling, or how many samples you want to select (scalar)
+  
+  # if a single sample set is to be retrieved per trial, create a vector to index below
[…]

### 2020-03-16 Cost_manuscript.Rmd
combining preregistrations into a single manuscript

---
title: Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment
author: "Claudio Toro-Serey^1^2 & Joseph T. McGuire^1^2"
csl: apa.csl
output:
  word_document: default #reference_docx: Style_reference_draft.docx
  pdf_document:
    highlight: haddock
    keep_tex: no
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
#subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
#bibliography: mPFC_paper.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.pos = 'H')
```

1.  Department of Psychological and Brain Sciences, Boston University, Boston, USA

2.  Center for Systems Neuroscience, Boston University, Boston, USA

\bigskip

Corresponding authors: Claudio Toro-Serey (ctoro@bu.edu) & Joseph T. McGuire (jtmcg@bu.edu)

\newpage

## Abstract

Cognitive and physical effort are typically regarded as costly, but recent findings have suggested that exerting effort can boost the value of prospects under certain conditions. Here we embedded mental and physical effort in a "diet choice" foraging task, which required decision makers not only to evaluate the magnitude and delay of a focal prospective reward, but also to estimate the general opportunity cost of time. In two experiments, independent sets of participants collected rewards that required equivalent periods of cognitive effort, physical effort, or unfilled delay. Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial (between-subjects, n=21 per condition), or varied across trials (within-subjects, n=48). Participants were free either to accept or reject the cost/reward prospect offered on each trial. All participants were more likely to accept offers when rewards were higher and delays shorter, in line with a reward-maximizing strategy. Participants almost never reversed their acceptance decisions, and error rates in completing the effort requirement were low and decreased over time. When participants faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay. This could be because cognitive effort was directly rewarding, or because it modulated foraging-related factors such as the perceived duration of delays or the estimated richness of the environment. We theorized that if cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards. In the within-subject experiment, an initially higher acceptance rate for cognitive effort trials disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions. Our results extend the view that cognitive demands may reduce the discounting effect of delays, but also suggest that differences in cost can eventually fade if individuals actively experience alternative forms of demand. Rather than assigning intrinsic value to cognitive effort, our findings support the idea that a cognitive effort requirement might influence contextual factors such as subjective delay durations or the perceived opportunity cost of time. Such altered estimations can be recalibrated if multiple forms of demand are interleaved.

## Introduction

## Methods

## Results

## Discussion

### 2020-03-16 Cost_manuscript.Rmd
data loading and naming conventions on manuscript + update on cost3

@@
 
-```{r setup, include = FALSE}
+```{r Global options, include = FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.pos = 'H')
+```
+
+```{r Setup, include = FALSE}
+## libraries
+library(tidyverse)
+library(ggfortify)
+library(knitr)
+library(pander) 
+library(nloptr)
+library(pwr)
+library(lme4)
+#library(lmerTest)
+library(gridExtra)
+library(reshape2)
+library(corrplot)
+
+## aesthetic options
+lbls <- c("Wait","Cognitive","Physical","Easy") # between subj
+colsBtw = c("#78AB05","#D9541A","deepskyblue4", "darkgoldenrod2") # plot colors (wait, effort)
+colsWth <- c("#D9541A", "#78AB05", "dodgerblue4", "deepskyblue3")#"grey30", "grey70") # plot colors (wait, effort)
+lthick = 2 # line thickness for plots
+
+## functions
+# get the number of continuous quits before current trial
+seqQuits <- function(subjData = 1){
+
+    # get the lag
+    tempSeq <- sequence(rle(subjData)$lengths) # sequence
+    tempSeq[subjData==1] <- 0 # not interested in completed runs, just quits
+    tempSeq <- c(0,tempSeq) # lag it so it can be used as a t-1 regressor
+
+    # return data so that the length is equivalent
+    out <- tempSeq[1:length(subjData)]
+
+    return(out)
+
+}
+
+# generic permutation for 2 groups
+permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE, simple = FALSE){
+
+    # prep data
+    summaryPerm <- list()
+    lOne <- length(group1)
+    lTwo <- length(group2)
+    bigSample <- c(group1,group2)
+
+    if (paired == FALSE) {
+
+        for (i in 1:nPerms){
+
+            # relabel samples
+            tempBig <- sample(bigSample)
+            tempOne <- tempBig[1:lOne]
+            tempTwo <- tempBig[(lOne+1):length(bigSample)]
+
+            # stats
+            tempDiffs <- statType(tempOne,na.rm=T) - statType(tempTwo,na.rm=T)
+            summaryPerm$jointDist[i] <- tempDiffs # statType(tempDiffs, na.rm = T)
+
+        }
+
+    } else {
+
+        for (i in 1:nPerms){
+
+            # shift labels in a pairwise fashion
+            tempDiffs <- statType((-1)^rbinom(lOne,1,0.5) * (group1 - group2))
+            summaryPerm$jointDist[i] <- tempDiffs
+
+        }
+
+    }
+
+    # get the observed difference
+    diffs <- statType(group1,na.rm=T) - statType(group2,na.rm=T)
+    observedAbs <- abs(diffs) # maybe leave it as means here
+    observed <- diffs
+    summaryPerm$Pval <- 2 * (1 - ecdf(summaryPerm$jointDist)(observedAbs))
+    if (length(unique(abs(summaryPerm$jointDist))) == 1) {summaryPerm$Pval <- 1} # if the difference is always the same, then p = 1
+    summaryPerm$Observed <- observed
+
+    # return the results
+    if (simple) {
+
+      return(summaryPerm$Pval)
+
+    } else if (!simple) {
+
+      return(summaryPerm)
+
+    }
+
+}
+
+# Non-parametric Bootstrap for a single group
+bootstrap <- function(group = 1, statType = mean, B = 5000){
+
+    # prep param
+    bootStats <- rep(0,B)
+
+    # iterate
+    for(b in 1:B){
+
+      # wait group
+      x <- sample(group,length(group),replace=T)  
+      bootStats[b] <- statType(x,na.rm = T)
+
+    }
+
+    return(bootStats)
+
+}
+
+# basic power calculation for a one way ANOVA
+powerCalc <- function(d = 1.2, Za = 1.96, Zb = 0.842){
+
+  out <- 2*((Za + Zb)/d)^2 + (0.25*(Za^2))
+
+  return(round(out))
+
+}
+
+# OC-specific computation of the negative log likelihood for model optimization
+negLogLik <- function(params, choice, handling, reward) {
+  gamma <- exp(params[2]) * handling
+  model <- exp(params[1]) * (reward - gamma)
+  p = 1 / (1 + exp(-model))
+  p[p == 1] <- 0.999
+  p[p == 0] <- 0.001
+  tempChoice <- rep(NA, length(choice))
+  tempChoice[choice == 1] <- log(p[choice == 1])
+  tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
+  negLL <- -sum(tempChoice) 
+  return(negLL)
+}
+
+# optimize the OC model
+optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA", simplify = F, optfun = negLogLik) {
+
+  # Data: The participant's log
+  # Algorithm: probably let be
+  # optfun: an external function to minimize (in this case OC, separately defined as negloglik)
+
+  # Prep data
+  handling <- Data$Handling
+  reward <- Data$Offer
+  choice <- Data$Choice
+
+  # Prep list of results to be returned
+  out <- list()
+  out$percentQuit <- mean(choice == 0) * 100
+  out$percentAccept <- mean(choice== 1) * 100 
+  miss <- (choice != 1) & (choice != 0)
+  out$percentMiss <- mean(miss)  * 100
+  choice <- choice[!miss]
+  reward <- as.numeric(reward[!miss])
+  handling <- as.numeric(handling[!miss])
+
+  # Establish lower and upper bounds
+  LB <- round(log((min(reward)/max(handling)) * 0.99), digits = 4)
+  UB <- round(log((max(reward)/min(handling)) * 1.01), digits = 4) # in reality this should be the second largest, since no one would reject the highest val
+
+  # Begin defining parameters
+  # If choices are one-sided (i.e. all accepted)
+  if ((sum(choice) == length(choice)) | (sum(choice) == 0)) {
+    ifelse(sum(choice) == length(choice), out$Gamma <- exp(LB), out$Gamma <- exp(UB)) 
+    out$Scale <- 1 # it was NA, but in theory a temperature of 1 also indicates noiseless estimates, and allows for easier fit computations
+    out$LL <- 0
+  } else {
+    # Create a feasible region (search space)
+    params <- as.matrix(expand.grid(scale = c(-1, 1), gamma = seq(LB, UB, length = 3)))
+    # Create a list to check the minimization of the negative log lik.
+    info <- list()
+    info$negLL <- Inf
+    # Define the options to be used during optimization
+    # Consider looking into other optimization algorithms and global minima
+    opts <- list("algorithm" = Algorithm,
+               "xtol_rel" = 1.0e-8)
+    # Optimize the sOC over all possible combinations of starting points
+    for (i in seq(nrow(params))) {
+      tempInfo <- nloptr(x0 = params[i, ], 
+                   eval_f = optfun, 
+                   lb = c(log(0.001), LB),
+                   ub = c(-log(0.001), UB),
+                   opts = opts,
+                   choice = choice, 
+                   handling = handling,
+                   reward = reward)
+      if (tempInfo$objective < info$negLL) {
+        #print("Minimized")
+        info$negLL <- tempInfo$objective
+        info$params <- tempInfo$solution
+      }
+    }
+    out$Gamma <- exp(info$params[2])
+    out$Scale <- exp(info$params[1])
+    out$LL <- -info$negLL
+  }
+
+  # Summarize the outputs
+  out$LL0 <- log(0.5) * length(choice)
+  out$Rsquared <- 1 - (out$LL/out$LL0)
+  out$subjOC <- out$Gamma * handling
+  out$p <- 1 / (1 + exp(-(out$Scale*(reward - out$subjOC))))
+  out$predicted <- reward > out$subjOC
+  out$predicted[out$predicted == TRUE] <- 1
+  out$percentPredicted <- mean(out$predicted == choice)
+
+  # adjust the probabilities in case of extreme gammas
+  if (out$Gamma <= exp(LB)) {
+    out$Gamma <- exp(LB) # temporary condition because Nlopt is not respecting the lower bound
+    out$p <- rep(1, length(choice))
+  } else if (out$Gamma == exp(UB)) {
+    out$p <- rep(0, length(choice))
+  }
+
+  # if doing this with dplyr::do(), return a simplified data.frame instead with the important parameters
+  if (simplify) {
+    out <- data.frame(out[c(seq(8), 12)])
+  }
+
+  return(out)
+
+}
+
+# summary matrices for refrence-changing models
+betaMatrix <- function(model, rearrange = NA) {
+# get a similarity matrix of the resulting coefficient pairings for the cost conditions
+# first, do a full_join based on column names on the list of coefficient vectors from each dummy code relevel
+# then match the names of columns and rows so NAs are in the diagonal
+
+  # get the names of the reference group per model iteration
+  refnames <- names(model)
+
+  # coefficient matrix
+  temp <- lapply(model, function(data) {coefficients(data)$SubjID[1, 2:4]})
+  mixCoeffs <- bind_rows(temp) 
+  preln <- ifelse("Cost" %in% substr(names(mixCoeffs), 1, 4), 4, 5) # count how many characters precede the name of each cost (diff across studies)
+  dimnames(mixCoeffs) <- list(refnames, substr(names(mixCoeffs), preln + 1, 20))
+  mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
+  mixCoeffs[is.na(mixCoeffs)] <- 0
+
+  # now the pvals
+  temp <- lapply(model, function(data) {as.list(summary(data)$coefficients[2:4, 4])})
+  mixPvals <- as.matrix(bind_rows(temp)) 
+  dimnames(mixPvals) <- list(refnames, substr(colnames(mixPvals), preln + 1, 20))
+  mixPvals <- as.matrix(mixPvals[, match(rownames(mixPvals), colnames(mixPvals))])
+  mixPvals[is.na(mixPvals)] <- 1
+
+  # if you would like to re-arrange the coefficient order, supply a vector with the desired sequence
+  if (length(rearrange) > 1) {
+    mixCoeffs <- mixCoeffs[rearrange, rearrange]
+    dimnames(mixCoeffs) <- list(rearrange, rearrange)
+    mixPvals <- mixPvals[rearrange, rearrange]
+    dimnames(mixPvals) <- list(rearrange, rearrange)
+  }
+
+  # combine matrices into list to return
+  out <- list(Betas = round(mixCoeffs, digits = 2),
+              Pvals = round(mixPvals, digits = 5))
+
+  return(out)
+
+}
+
+# gather basic data (this is better as a function, then rbind)
+summarizeData <- function(Data = waitData, nSubs = nSubsW, type = "Wait"){
+
+  tempSummary <- data.frame(group = rep(type, nSubs))
+
+  if (type == "Cognitive") {
+
+    for (subj in seq(nSubs)){
+
+        # Choice index
+        tempChoice <- Data[[subj]]$Choice
+
+        # Proportion complete
+        tempSummary[subj,2] <- mean(tempChoice)
+
+        # earnings
+        tempSummary[subj,3] <- sum(Data[[subj]]$Offer[tempChoice==1])
+
+        # RTs
+        tempSummary[subj,4] <- median(Data[[subj]]$`Choice RT`[tempChoice==0])
+
+        # Mistakes (only for cognitive effort group)
+        tempMistakes <- sum(cogDataLong[[subj]]$`Trial Outcome`=="Forced travel") # how many forced travel trials
+        tempTrialnum <- length(Data[[subj]]$Choice) # how many decision trials
+        tempSummary[subj,5] <- tempMistakes / (tempMistakes + tempTrialnum) # proportion of forced travels throughout the exp
+
+    }
+
+  } else {
+
+    for (subj in seq(nSubs)){
+
+        # choice index
+        tempChoice <- Data[[subj]]$Choice
+
+        # propotion complete
+        tempSummary[subj,2] <- mean(tempChoice)
+
+        # earnings
+        tempSummary[subj,3] <- sum(Data[[subj]]$Offer[tempChoice==1])
+
+        # RTs
+        tempSummary[subj,4] <- median(Data[[subj]]$RT[tempChoice==0])
+
+        # Mistakes (to allow for mistakes on the cognitive group)
+        tempSummary[subj,5] <- NA
+
+    }
+
+  }
+
+  return(tempSummary)
+
+}
+
+```
+
+``` {r Load data for between-subject experiment, echo = FALSE}
+### data loading and cleaning up
+# forced travels are switched to acceptances, as they reflect a preference for that trial
+# rawChoice will be used to compute the # of mistakes
+# The RT is upper-bounded because a glitch in the code made two 14s trials last longer (among all p's) 
+setwd("./Cost2/data")
+files <- dir(pattern = '_log.csv')
+
+# load data
+dataBtw <- tibble(SubjID = files) %>%
+  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
+  mutate(Cost = substring(SubjID, 5, 8),
+         Cost = case_when(Cost == "wait" ~ "Wait",
+                          Cost == "cogT" ~ "Cognitive",
+                          Cost == "phys" ~ "Physical",
+                          Cost == "phea" ~ "Easy"),
+         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
+  unnest() %>%
+  mutate(rawChoice = Choice, 
+         RT = ifelse(RT > 14.1, 14, RT),
+         Choice = ifelse(Choice == 2, 1, Choice), # forced travels (2) become acceptances (1)
+         Half = ifelse(Block < 4, "Half_1", "Half_2"),
+         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
+         optimal = case_when(
+          (Handling == 10 & Offer < 8) ~ 0,
+          (Handling == 14 & Offer < 20) ~ 0,
+          TRUE ~ 1
+          )
+         )
+
+# get a simple subject list and the number of subjects
+subjList_btw <- unique(dataAll$SubjID)
+nSubjs_btw <- length(subjList)
+
+```
+
+```{r Load data for within-subject experiment, echo = FALSE}
+# First looks at the new data
+# The RT is upper-bounded because a glitch in the code made one 10s last 14s
+setwd('./Cost3/data/')
+files <- dir(pattern = 'main_log.csv')
+
+# load the data and remove extreme subjects
+dataWth <- data_frame(SubjID = files) %>% 
+  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
+  mutate(SubjID = substring(SubjID, 0, 3)) %>%
+  unnest() %>%
+  mutate(RT = ifelse(RT > 10.1, 10, RT),
+         Half = ifelse(Block < 4, "Half_1", "Half_2"),
+         Btype = BlockType) %>%
+  unite(Cost, Cost, BlockType) %>%
+  mutate(rawChoice = Choice,
+         Choice = ifelse(Choice == 2, 1, Choice),
+         Cost = case_when(Cost == "WAIT_0" ~ "Wait_C",
+                           Cost == "COGNITIVE_0" ~ "Cognitive",
+                           Cost == "GRIP_1" ~ "Physical",
+                           Cost == "WAIT_1" ~ "Wait_P")) %>%
+  group_by(SubjID) %>%
+  mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st"))
+
+# Get just the subject list and number of subjects
+subjList_wth <- unique(data$SubjID)
+nSubjs_wth <- length(subjList)
 ```

### 2020-03-16 Cost_manuscript.Rmd
loading done, suppressing unncesessary warning messages

@@
 dataBtw <- tibble(SubjID = files) %>%
-  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
+  mutate(contents = map(SubjID, ~ suppressWarnings(read_csv(., col_types = cols()))))  %>%
   mutate(Cost = substring(SubjID, 5, 8),
@@
   unnest() %>%
+  rename(TrialN = X1) %>%
   mutate(rawChoice = Choice, 
@@
 # get a simple subject list and the number of subjects
-subjList_btw <- unique(dataAll$SubjID)
-nSubjs_btw <- length(subjList)
+subjList_btw <- unique(dataBtw$SubjID)
+nSubjs_btw <- length(subjList_btw)
 
@@
 dataWth <- data_frame(SubjID = files) %>% 
-  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
+  mutate(contents = map(SubjID, ~ suppressWarnings(read_csv(., col_types = cols()))))  %>%
   mutate(SubjID = substring(SubjID, 0, 3)) %>%
@@
   unite(Cost, Cost, BlockType) %>%
+  rename(TrialN = X1) %>%
   mutate(rawChoice = Choice,
@@
 # Get just the subject list and number of subjects
-subjList_wth <- unique(data$SubjID)
-nSubjs_wth <- length(subjList)
+subjList_wth <- unique(dataWth$SubjID)
+nSubjs_wth <- length(subjList_wth)
 ```

### 2020-03-16 Cost_manuscript.Rmd
Adding cost2 to manuscript worked. Now onto cost3. gitignoring word docs from now on

@@
     out <- tempSeq[1:length(subjData)]
+
+    return(out)
+
+}
+
+# Cohen's D for 2 groups (could just use DesctTools...)
+# for a more flexible approach, make the data input to be a list with entries for n groups, 
+# then do length(list) for the number of groups. 
+cohenD <- function(group1 = 1, group2 = 2){
+
+      # means
+      mean1 <- mean(group1, na.rm = T)
+      mean2 <- mean(group2, na.rm = T)
+
+      # variance
+      var1 <- var(group1, na.rm = T)
+      var2 <- var(group2, na.rm = T)
+
+      # equation
+      out <- (mean1 - mean2) / sqrt((var1 + var2)/2)
 
@@
 
-``` {r Load data for between-subject experiment, echo = FALSE}
+```{r Load data for between-subject experiment, echo = FALSE}
 ### data loading and cleaning up
@@
 
+### **Between-subjects: Tests of whether decision makers integrate delay and reward information**
+
+### 16.1.1.
+
+  *To address hypothesis 4.1., A logistic regression will be fit for each participant in order to predict trial-wise acceptances, using handling time and reward amount as predictors.
+The resulting beta coefficients for handling time and reward will be pooled across all participants, and we will perform a one-sample rank-sum test on each set of coefficients to examine whether the they are significantly positive or negative (compared to 0).
+If the group coefficients are significantly positive, it would mean that a predictor reliably increases the likelihood of acceptance.
+This will allow us to determine whether increments in handling time and reward amounts increased and decreased the likelihood of acceptance for each participant, respectively.*
+
+``` {r 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
+# filterout errors and compute R + H logistic per subject, then get coefficients
+logisRH <- dataBtw %>%
+  filter(Choice < 2) %>%
+  plyr::dlply("SubjID", identity) %>%
+  lapply(function(data) {glm(Choice ~ Handling + Offer, data = data, family = "binomial")}) %>%
+  sapply(coefficients)
+
+# Rank sum tests
+rankHand <- wilcox.test(logisRH["Handling", ])
+rankOffer <- wilcox.test(logisRH["Offer", ])
+
+# Plot coeffs
+temp <- melt(logisRH[c("Handling", "Offer"), ])
+qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
+  labs(x = "", y = "Coefficients") +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  theme(legend.position = c(0.9, 0.7),
+       panel.grid.major = element_blank(), 
+       panel.grid.minor = element_blank(), 
+       panel.background = element_blank(), 
+       axis.line = element_line(colour = "black"),
+       text = element_text(size = 16))
+```
+
+The plot shows the pooled coefficients across subjects for the effect of each predictor.
+The results show the expected discounting effect of increasing the handling time, as well as the increase in acceptance likelihood as a function of reward increments.
+We found that these coefficients were significantly different from zero for both handling (V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) and reward (V = `r rankOffer$statistic`, p `r ifelse(rankOffer$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) regardless of cost condition.
+
+\bigskip
+
+### 16.1.2.
+
+*We will perform an extension of the logistic regression from 16.1.1., this time adding an autoregressive covariate containing the number of consecutive quits prior to a given trial.
+In this way, we will examine the possibility that participant choices were governed by recent quitting history rather than the experimental parameters (see 11.1.3.).
+Coefficients not significantly different from 0 will denote that a participant did not rely on recent quitting history.*
+
+``` {r 16.1.2., echo = FALSE, include = FALSE}
+# add an AR regressor to track recent quits
+logisRHAR <- dataBtw %>%
+              filter(Choice < 2) %>%
+              group_by(SubjID) %>%
+              mutate(AR = seqQuits(Choice)) %>%
+              plyr::dlply("SubjID", identity) %>%
+              lapply(function(data) {glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial")})
+
+# Rank sums
+rankAR <- logisRHAR %>% 
+  sapply(coefficients) %>%
+  wilcox.test(.["AR", ])
+
+AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(confint(x)[4, ], error = function(e){c(0, 0)})}) %>%
+  replace_na(0) %>%
+  t() %>% 
+  apply(1, function(x) !(x[1] <= 0 & x[2] >= 0))
+
+```
+
+To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero.
+By this measure, `r sum(AR_CIs)` out of `r nSubjs_btw` of our participants seemed to have been influenced by recent quitting.
+However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.
+
+\bigskip
+
+### 16.1.3.
+
+*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable).
+No other covariates will be used, as this analysis is to confirm that over and under accepting are detrimental to total earnings.
+The quadratic term will be defined as the squared deviation from the optimal overall acceptance rate.*
+
+``` {r 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# calculate the proportions and earnings per subject, while keeping group info
+temp <- dataBtw %>%
+  filter(rawChoice < 2) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(Earnings = sum(Offer[Choice == 1] / 100),
+            pComplete = mean(Choice)) %>%
+  mutate(pComplete2 = pComplete^2) %>%
+  ungroup()
+
+# linear fit of earnings x prop accept
+lmEarn <- lm(Earnings ~ pComplete + pComplete2, data = temp)
+
+# plot
+(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
+         scale_color_manual(values = colsBtw) + 
+         geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = T) + 
+         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
+         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
+         scale_fill_manual(values = colsBtw) +
+         theme(panel.grid.major = element_blank(), 
+           panel.grid.minor = element_blank(), 
+           panel.background = element_blank(), 
+           axis.line = element_line(colour = "black"),
+           text = element_text(size = 16)))
+
+```
+
+The figure shows that participants that over and unceraccepted earned less money overall, as predicted.
+This is supported by a significant quadratic term from the linear model (F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3,2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`; black line shows the fit).
+The following table shows all the results from the model.
+
+``` {r 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
+# Summary table for the linear model
+panderOptions("digits", 2)
+pander(lmEarn, style = "rmarkdown")
+```
+
+\bigskip
+
+### 16.1.4.
+
+*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances--either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
+This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*
+
+``` {r 16.1.4., echo=FALSE}
+# in order
+# clean data, 
+# calculate each individual's prop. accept,
+# calculate t.tests with optimality as null mean,
+# correct pvalues with FDR
+temp <- dataBtw %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Handling, Offer, Cost) %>%
+  summarise(pAccept = mean(Choice)) %>%
+  mutate(optimal = case_when(
+          (Handling == 10 & Offer < 8) ~ 0,
+          (Handling == 14 & Offer < 20) ~ 0,
+          TRUE ~ 1
+        )) %>% 
+  group_by(Handling, Offer, Cost) %>%
+  summarise(meanAccept = mean(pAccept),
+            sdAccept = sd(pAccept),
+            optimal = unique(optimal),
+            pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
+  mutate(FDR = p.adjust(pvals, method = "BY"),
+         significant = FDR < 0.05)
+
+# proportion of significant ones
+# eventually find a way to plot this
+splitData_prop <- mean(temp$significant, na.rm = T)
+```
+
+Of the 36 tests, around `r splitData_prop` were significantly deviant from optimality.
+Most of these were from effortful groups, as the wait group just showed deviations for 2 seconds handling/4 cent, and 10 seconds handling/8 cent offers (note to self: think about a way to properly visualize these).
+
+\bigskip
+
+### **Between-subjects: Comparisons among the four delay and effort conditions**
+
+### 16.2.1.
+
+*To compare preferences (hypothesis 4.2.), we will first perform a one-way ANOVA on the proportion of trials accepted using group as a factor.
+In addition, we will do pairwise comparisons on the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests).
+The same approach will be used for total earnings.
+This will give us an initial glimpse on the potential differences in cost among conditions.*
+
+``` {r 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
+## ECDF of proportion completed per cost type
+temp <- dataBtw %>%
+        filter(Choice < 2) %>%
+        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
+        group_by(SubjID, Cost) %>%
+        summarise(Earnings = sum(Offer[rawChoice == 1] / 100),
+                  pAccept = mean(Choice))
+
+## formal testing 
+# proportion completed
+propAov <- aov(pAccept ~ factor(Cost), data = temp)
+
+propTests <- temp %>% 
+  plyr::dlply("Cost", identity) %>%
+  sapply("[[", "pAccept") %>%
+  as.data.frame() %>%
+  combn(2, simplify = F) %>%
+  sapply(function(x) {
+    c(contrast = paste(colnames(x), collapse = "vs"), 
+      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
+      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
+  }) %>% 
+  t()
+
+# pairwise.wilcox.test(temp$pComplete, temp$Cost)
+
+# earnings
+earnAov <- aov(Earnings ~ factor(Cost), data = temp)
+
+earnTests <- temp %>% 
+  plyr::dlply("Cost", identity) %>%
+  sapply("[[", "Earnings") %>%
+  as.data.frame() %>%
+  combn(2, simplify = F) %>%
+  sapply(function(x) {
+    c(contrast = paste(colnames(x), collapse = "vs"), 
+      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
+      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
+  }) %>% 
+  t()
+
+## plots
+# ECDF pAcceptd
+p1 <- ggplot(aes(pAccept, color = Cost), data = temp) +
+        stat_ecdf(lwd = 1.2, show.legend = F) +
+        scale_color_manual(values = colsBtw) +
+        xlim(0, 1) +
+        labs(y="ECDF", x = "Proportion Accepted") +
+        theme(panel.grid.major = element_blank(), 
+              panel.grid.minor = element_blank(), 
+              panel.background = element_blank(), 
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16))
+
+# pAccepted
+p2 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
+        geom_boxplot(show.legend = F) +
+        scale_fill_manual(values = colsBtw) +
+        ylim(c(0, 1)) +
+        labs(y = "Proportion Accepted") +
+        theme(panel.grid.major = element_blank(), 
+            panel.grid.minor = element_blank(), 
+            panel.background = element_blank(), 
+            axis.line = element_line(colour = "black"),
+            text = element_text(size = 16))
+
+# earnings
+p3 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
+        geom_boxplot(show.legend = F) +
+        scale_fill_manual(values = colsBtw) +
+        labs(y = "Total Earnings (dollars)") +
+        theme(panel.grid.major = element_blank(), 
+            panel.grid.minor = element_blank(), 
+            panel.background = element_blank(), 
+            axis.line = element_line(colour = "black"),
+            text = element_text(size = 16))
+
+grid.arrange(p2, p3, ncol = 2)
+```
+
+The plots show that subjects in the wait condition accepted the least and earned the most, suggesting a more optimal pattern of choices.
+Participants in the cognitive effort and easy conditions had higher more variable acceptance patterns, which are reflected in the comparatively low earnings.
+The reason why the easy condition does not show variable earnings like the cognitive effort group is probably due to the quadratic relationship between earnings and acceptances shown before.
+
+\bigskip
+
+### 16.2.2.
+
+*In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors.
+Offer and handling time will be within-subject factors, and condition a between-subjects factor.
+In support of hypotheses 4.1.
+and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions.*
+
+``` {r 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
+temp <- dataBtw %>%
+        filter(Choice < 2) %>%
+        group_by(SubjID, Cost, Handling, Offer) %>%
+        summarise(pAccept = mean(Choice))
+
+## REPEATED MEASURES ANOVA
+# I think I like this the most
+prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Offer + 
+                                 Error(SubjID / (Handling * Offer))))
+
+## NOTES ON RESULTS
+# According to the logistic fit, there are main effects for all predictors, but no interactions.
+It also says that the overall odds for the wait group to accept versus the effort is around 16%.
+Similarly, increasing the handling time results in a decrease in the multiplicative odds of ~25%.
+Increments in reward increase the odds of acceptance by ~40%.
+```
+
+The plot below shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and condition (optimal acceptance rate indicated by the gray triangles).
+Visually, the graph confirms a couple of important intuitions.
+First, as the handling time increases, the proportion of acceptances decreases.
+Second, this discounting did not affect the 20 cent offers, as is expected from the present foraging environment.
+Lastly, and similar to the previous point, as the value of the offers increases so does the willingness to accept a trial.
+Beyond these general features, it is clear that the cognitive effort group accepted more than the other groups, regardless of the combination of experimental parameters.
+Notably, the optimality of this greater acceptance rate is determined by the timing context (e.g.
+optimal at 2 second handling time, but detrimental at 14 seconds).
+
+``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
+# # code to calculate the rwd/sec rate for each acceptance threshold per handling
+# rwd <- c(4, 8, 20)
+# handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
+# travel <- c(2, 6, 14) + 2
+# sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
+# 
+# as_tibble(rwdRates) %>% 
+#   mutate(Handling = handling) %>%
+#   rename(Five = V1,
+#          Eight = V2,
+#          Twenty = V3) %>%
+#   gather(Reward, Rate, -Handling) %>%
+#   mutate(Reward = factor(Reward, levels = list("Five", "Eight", "Twenty")),
+#          Handling = as.character(Handling)) %>%
+#   group_by(Handling) %>%
+#   mutate(Optimal = ifelse(Rate == max(Rate), max(Rate), -1)) %>%
+#   ungroup() %>%
+#   ggplot(aes(Reward, Rate, group = Handling, color = Handling)) +
+#     geom_point(size = 3) +
+#     geom_line(size = 1.5) +
+#     geom_point(aes(Reward, Optimal), pch = 21, color = "black", fill = NA, size = 7, show.legend = F) +
+#     scale_color_manual(values = c("purple", "grey50", "darkgoldenrod3")) +
+#     ylim(0, 1.2) +
+#     labs(y = "Expected eward per sec.", x = "Reward acceptance threshold") +
+#     theme(legend.position = c(0.85, 0.2),
+#           legend.key = element_blank(),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 22))
+
+# prep data to plot the p(accept) based on reward, handling time and cost type
+trueProp <- dataBtw %>%
+        filter(Choice < 2) %>%
+        group_by(SubjID, Cost, Handling, Offer, optimal) %>%
+        summarise(pAccept = mean(Choice)) %>%
+        group_by(Cost, Handling, Offer, optimal) %>%
+        summarise(meanComplete = mean(pAccept),
+                  SE = sd(pAccept) / sqrt(length(pAccept)))
+
+# and plot
+(a1 <- ggplot(data = trueProp, aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
+        geom_point(size = 3) + 
+        geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
+        geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
+        geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
+        labs(x = "Offer.Handling", y = "Proportion Accepted") +
+        scale_color_manual(values = colsBtw) +
+        theme(legend.key = element_blank(),
+              panel.grid.major = element_blank(), 
+              panel.grid.minor = element_blank(), 
+              panel.background = element_blank(), 
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16)))
+
+```
+
+These intuitions were formally tested using a repeated measures ANOVA, whose results are presented in the table below.
+Overall, the analysis partially confirmed our predictions.
+While all main effects were significant, there was an unexpected significant condition-by-reward interaction, which could be due to the performance of the "easy" group relative to their peers.
+Importantly, we found that the interaction between all three main parameters was not significant, thus suggesting that the effects of handling and reward on choices were not different across groups.
+
+``` {r 16.2.2. rmANOVA table, pander}
+# anova table
+x <- summary(prop.aov)   
+x <- x$`Error: Within`
+panderOptions("digits", 2)
+pander(x, style = "rmarkdown", split.table = 110)
+```
+
+\bigskip
+
+### 16.2.3.
+
+*We will compute the probability of accepting a trial with a mixed-effects logistic regression.
+Based on the task structure and our main question, our a priori model of interest will include cost condition, handling time, and reward amount as fixed main effects, and subject ID as a random effect.
+Cost condition will be modeled with three categorical terms, with the fourth condition as the reference condition.
+We will run three versions of the model with different reference conditions, in order to test all pairwise differences among the four cost conditions.
+As with 16.2.2., we anticipate significant main effects (coefficients different than zero) of handling time, reward, and cost condition.
+We hypothesize that the differences among cost conditions will follow the pattern described in 4.2.*
+
+``` {r 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
+# clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
+mixLogis_main <- list()
+mixData <- dataBtw %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost, Handling, Offer) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice)) %>%
+  ungroup()
+
+# model with a random intercept and cost-type slope, then relevel the cost to get all pairwise comparisons
+# the correct way to model a logistic with proportions as dependent vars is by prividing n of hits and quits as a matrix
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
+mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
+mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
+mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
+mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+
+# matrix of coefficients and pvalues
+rearrange <- c("Cognitive", "Easy", "Wait", "Physical") # to kinda match the order in Cost 3
+mixSummary <- betaMatrix(mixLogis_main, rearrange = rearrange)
+diag(mixSummary$Pvals) <- NA
+
+# plot coefficients and pvalues in a matrix
+# invert colors
+col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))
+
+corrplot(mixSummary$Betas, 
+         is.corr = F, 
+         p.mat = mixSummary$Pvals, 
+         type = "lower",
+         outline = T,
+         #insig = "p-value",
+         sig.level = 0.05, 
+         na.label = "square", 
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black",
+         tl.cex = 0.8,
+         col = col2(200))
+
+```
+
+``` {r 16.2.3. Mixed Effects Model plot rand intercepts, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
+# plot random intercepts in increasing order
+#RI1 <- qplot(seq(83), sort(ranef(mixLogis_main$Wait)$SubjID[,1]), color = colsBtw[1], show.legend = F) + theme_classic()
+
+# # plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
+# temp <- ranef(mixLogis_main$Wait)$SubjID %>%
+#   gather(key = Cost, value = RandEffects, colnames(.)) 
+# 
+# (RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
+#   geom_hline(yintercept = 0, alpha = 0.7, linetype = "dashed") + 
+#   geom_boxplot(show.legend = F) +
+#   scale_fill_manual(values = colsBtw) + 
+#   labs(x = "") +
+#   theme(panel.grid.major = element_blank(), 
+#               panel.grid.minor = element_blank(), 
+#               panel.background = element_blank(), 
+#               axis.line = element_line(colour = "black"),
+#               text = element_text(size = 16)))
+
+```
+
+As predicted, the model showed significant main effects of handling time (Beta = `r mixLogis_main$Summary$coefficients[5,1]`, SE = `r mixLogis_main$Summary$coefficients[5,2]`, p < 0.001) and reward (Beta = `r mixLogis_main$Summary$coefficients[6,1]`, SE = `r mixLogis_main$Summary$coefficients[6,2]`, p < 0.001).
+In order to show the comparisons among all conditions, the following plot portrays the coefficients (color scale), and p-values (numbers within squares) that resulted from switching the reference condition.
+Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group.
+Based on this, we can see that the cognitive group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
+
+### 16.2.4.
+
+*Next, we will examine whether the a priori model from 16.2.3.
+outperforms both simpler and more complex models.
+Unlike the individual logistic regression fits in 16.1.1., a mixed-effects approach gives us a better goodness of fit measure for model comparisons.
+We will determine the best model (combination of predictors) using Akaike’s Information Criterion (AIC) to determine the model that minimizes the negative log-likelihood while penalizing the addition of parameters.
+The regression with each combination of predictors will be fitted in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) reward only; 5) condition, handling, and reward main effects (from 16.2.3.); 6) adding a handling-by-reward interaction; and 7) adding all three possible two-way interactions.
+We predict that model 5 will have the lowest AIC.*
+
+``` {r 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+# Quasibinomial GLM versions (with proper proportion setup)
+mixLogis_compare <- list()
+mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
+mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$Handling <- glmer(cbind(totalAccepted, totalQuits) ~ Handling + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$Offer <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$AllMain <- mixLogis_main$Wait
+mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (Cost | SubjID), family = "binomial", data = mixData)
+
+# Model selection 
+abicLogis_compare <- data.frame(Model = names(mixLogis_compare),
+                                AIC = sapply(mixLogis_compare, AIC),
+                                BIC = sapply(mixLogis_compare, BIC))
+
+# effect size
+mixLogis_compare$Rsq <- 1 - (deviance(mixLogis_compare$AllMain)/deviance(mixLogis_compare$Base)) # denominator is the null deviance
+```
+
+``` {r 16.2.4. Plot Deviance comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+# plot AIC and BIC
+(mixLogis_compare$plot <- abicLogis_compare %>% 
+  gather(Comparison, Value, AIC:BIC) %>%
+  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
+  ggplot(aes(Model, Value, fill = Comparison)) +
+    geom_point(color = "black", pch = 21, size = 3) +
+    theme_classic())
+
+```
+
+This plot shows the AIC for every model.
+The figure below shows AIC and BIC for all the models.
+As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`).
+The reduction in deviance from an intercept-only model was drastic enough that we did not compute an LRT.
+
+\bigskip
+
+### **Between-subjects: Modeling the subjective opportunity cost in each condition**
+
+### 16.3.1.
+
+*Response times (RT) for quit responses will be presented in a descriptive manner in order to examine whether participants tended to quit early or late within individual trials.
+Each cost group’s response time distribution will contain the pooled RT across its corresponding participants, and we will display the empirical cumulative distribution functions for each condition.
+Short RT would suggest confident and stable decisions (in support of 4.3.1.).*
+
+``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+# Proportion of forced travels per subject and cost type
+propFails <- dataBtw %>% 
+  filter(Cost != "Wait") %>% 
+  group_by(SubjID, Cost) %>% 
+  summarise(propFails = mean(rawChoice == 2)) %>%
+  group_by(Cost) %>% 
+  summarise(meanFT = mean(propFails),
+            sdFT = sd(propFails))
+
+# this version of a survival curve forces all successful acceptances to have an RT of 14
+library(survival)
+library(ggfortify)
+
+# that's to avoid jumps from 2s to 10s to 14s
+# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor?
+temp <- dataBtw %>%
+    #filter(rawChoice < 2) %>% 
+    mutate(#RT = ifelse(Choice == 1, 14, RT),
+           Choice = 1 - Choice)
+
+survData <- survfit(Surv(RT, Choice) ~ Cost, data = temp)
+
+autoplot(survData) +
+  geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
+  scale_color_manual(values = colsBtw) +
+  scale_fill_manual(values = colsBtw) +
+  scale_x_continuous(breaks = seq(14)) +
+  ylim(0, 1) +
+  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
+  theme(legend.position = c(0.3, 0.2),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 22))
+
+# RT ecdfs for the whole group across blocks, with the option to subdivide by cost group
+dataBtw %>%
+  filter(Choice == 0,
+         RT < 1) %>%
+  ggplot(aes(RT, group = Block, color = Block)) +
+    stat_ecdf() +
+    #facet_wrap(vars(Cost)) +
+    theme_classic()
+
+```
+
+The survival curve below shows instances of quiting across a trial for all participants and handling times.
+Censors signal completed trials and forced quits, so most occur at the end of the three possible handling times.
+Participants could only quit once the trial begun.
+This shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
+The reason why the physical and easy condition show slightly lagged responses is that the experiment allowed a one second grace period for participants to begin gripping (marked by the dashed line).
+This resulted in some of them choosing to wait for that second to indicate an offer rejection.
+The proportion of forced quits for cognitive effort was `r round(propFails[2, 2], digits = 2)`, and 0 for the physical conditions (the censor around 4s in the physical condition was an acceptance during 2s handling that was incorrectly recorded at 4s by the experimental code).
+
+\bigskip
+
+### 16.3.2.
+
+*In order to further examine choice stability (hypothesis 4.3.1.), we will compute each participant’s total proportion of acceptances pre- and post-midpoint.
+For each cost condition separately, we will fit a linear model that predicts post-midpoint acceptance from before-midpoint rates.
+We will report the slopes and 95% confidence intervals (CI) for each cost group.
+CIs containing 1 will denote that participants in that group produced consistent choices.*
+
+``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
+# divide the data into proportion accepted before/after the break (one per column)
+temp <- dataBtw %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost, Half) %>%
+  summarise(pAccepted = mean(Choice)) %>%
+  ungroup() %>%
+  spread(Half, pAccepted)
+
+# separate by cost type and compute a linear model to predict half 2 from 1
+sep <- temp %>% plyr::dlply("Cost", identity)
+prepost <- list()
+prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})
+
+# get the coefficients and confidence intervals
+# and concatenate
+prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
+colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
+
+## PRE/POST PAIRED PERMUTATIONS
+temp <- dataBtw %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
+            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
+  plyr::dlply("Cost", identity)
+
+# paired perms and effect sizes
+prepost$CohenD <- sapply(temp, function(data) {DescTools::CohenD(data$propAccept_1, data$propAccept_2)})
+prepost$Perms <- sapply(temp, function(data) {permute(data$propAccept_1, data$propAccept_2, paired = T, simple = T)})
+```
+
+The plot below shows that acceptance rates before and after the mid-point were mostly consistent, although it was more likely for participants to accept less in the second half of the experiment.
+**NOTE: The lines of means in the scatterplot are calculated by first computing the mean acceptances per block, then averaging those for blocks pre/post break.
+That's how they match the second half of the right plot, but the linear model is computed with the overall proportion acceptances pre-post, which gives slightly different mean estimates (which is also the reason for slight mean differences in proportion accepted between these and the boxplot in 16.2.1.)**
+
+``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+# scatter plot of pre/post acceptances
+# BIG CAVEAT: THE 
+# first calculate the mean acceptances per cost/half to draw horizontal and vertical lines on the plot
+df_mean <- dataBtw %>%
+            group_by(SubjID, Cost, Block, Half) %>%
+            summarise(propAccept = mean(Choice)) %>%
+            group_by(SubjID, Cost, Half) %>%
+            summarise(propAccept = mean(propAccept)) %>%
+            spread(Half, propAccept) %>%
+            group_by(Cost) %>%
+            summarise(propAccept_1 = mean(Half_1),
+                      propAccept_2 = mean(Half_2))
+
+# and plot
+prepost$scatterplot <- dataBtw %>%
+                        filter(Choice < 2) %>%
+                        group_by(SubjID, Cost) %>%
+                        summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
+                                  propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
+                        ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
+                          geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
+                          scale_fill_manual(values = colsBtw) +
+                          scale_color_manual(values = colsBtw) +
+                          xlim(0, 1) +
+                          ylim(0, 1) +
+                          labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
+                          geom_abline(slope = 1, intercept = 0, lty = 2) +
+                          geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
+                          geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
+                          theme(panel.grid.major = element_blank(),
+                                panel.grid.minor = element_blank(),
+                                panel.background = element_blank(),
+                                axis.line = element_line(colour = "black"),
+                                text = element_text(size = 16))
+
+# acceptances per cost across blocks
+# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
+prepost$propBlocks <- dataBtw %>%
+                         filter(Choice < 2) %>%
+                         group_by(SubjID, Cost, Block) %>%
+                         summarise(propAccept_subj = mean(Choice)) %>%
+                         group_by(Cost, Block) %>%
+                         summarize(propAccept = mean(propAccept_subj),
+                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs_btw)) %>%
+                         ggplot(aes(Block, propAccept, color = Cost)) +
+                           geom_point(size = 2) +
+                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
+                           geom_line() +
+                           ylim(0, 1) +
+                           labs(y = "Proportion Acccepted") +
+                           scale_x_continuous(breaks = seq(6)) +
+                           scale_color_manual(values = colsBtw) +
+                           scale_fill_manual(values = colsBtw) +
+                           theme(legend.key = element_blank(),
+                                 legend.position = c(0.8, 0.25),
+                                 panel.grid.major = element_blank(),
+                                 panel.grid.minor = element_blank(),
+                                 panel.background = element_blank(),
+                                 axis.line = element_line(colour = "black"),
+                                 text = element_text(size = 16))
+
+grid.arrange(prepost$scatterplot, prepost$propBlocks, ncol = 2)
+```
+
+The following table shows the coefficients and CI for each linear model, and show that pre-post acceptance rates were very similar for each condition (i.e.
+one is present in all confidence intervals).
+Note that interpreting the coefficients depends on the intercept, and the wait condition had a relatively high intercept.
+
+A better test is to perform a pairwise comparison between halves per cost type.
+Paired permutations on means of proportions showed no differences for wait and easy groups (p > 0.5), but significantly lower acceptance rates for physical (*p* = `r prepost$Perms[1]`, Cohen's D = `r prepost$CohenD[1]`) and cognitive (*p* = `r prepost$Perms[2]`, Cohen's D = `r prepost$CohenD[2]`) groups.
+These results are more consistent with the plots above.
+
+``` {r 16.3.2. prepost table, pander}
+panderOptions("digits", 2)
+pander(prepost$summary, style = "rmarkdown", split.table = 110)
+```
+
+Now let's divide them by reward and handling amounts. The plots below show that the overall rates of acceptances remain mostly consistent across first and second halves of the experimental session.
+
+``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+# # pre
+# t1 <- dataBtw %>%
+#   filter(Choice < 2, Half == "Half_1") %>%
+#   group_by(SubjID) %>%
+#   filter(Handling == 10) %>%
+#   group_by(SubjID, Cost, Offer) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   group_by(Cost, Offer) %>%
+#   summarise(propAccept = mean(pAccept),
+#             SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
+#   ungroup() %>%
+#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+#   ggplot(aes(Offer, propAccept, color = Cost)) +
+#     geom_point(size = 3, show.legend = F) +
+#     geom_line(show.legend = F) +
+#     scale_color_manual(values = colsBtw) +
+#     scale_fill_manual(values = colsBtw) +
+#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
+#     scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
+#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+#     labs(y = "Proportion Accepted", title = "First Half") +
+#     theme(legend.key = element_blank(),
+#           legend.position = c(0.8, 0.25),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
+# 
+# # post half
+# t2 <- dataBtw %>%
+#   filter(Choice < 2, Half == "Half_2") %>%
+#   group_by(SubjID) %>%
+#   filter(Handling == 10) %>%
+#   group_by(SubjID, Cost, Offer) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   group_by(Cost, Offer) %>%
+#   summarise(propAccept = mean(pAccept),
+#             SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
+#   ungroup() %>%
+#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+#   ggplot(aes(Offer, propAccept, color = Cost)) +
+#     geom_point(size = 3, show.legend = F) +
+#     geom_line(show.legend = F) +
+#     scale_color_manual(values = colsBtw) +
+#     scale_fill_manual(values = colsBtw) +
+#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
+#     scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
+#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+#     labs(y = "", title = "Second Half") +
+#     theme(legend.position = c(0.8, 0.2),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
+# 
+# 
+# 
+# grid.arrange(t1, t2, ncol = 2)
+
+dataBtw %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID) %>%
+  filter(Handling == 10) %>%
+  mutate(Half = ifelse(Half == "Half_1", "First Block", "Last Block")) %>%
+  group_by(SubjID, Half, Cost, Offer) %>%
+  summarise(pAccept = mean(Choice)) %>%
+  group_by(Half, Cost, Offer) %>%
+  summarise(propAccept = mean(pAccept),
+            SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
+  ungroup() %>%
+  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+  ggplot(aes(Offer, propAccept, color = Cost)) +
+    geom_point(size = 3, show.legend = T) +
+    geom_line(size = 1, show.legend = F) +
+    scale_color_manual(values = colsBtw) +
+    scale_fill_manual(values = colsBtw) +
+    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
+    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
+    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+    labs(y = "Proportion Accepted") +
+    facet_wrap(vars(Half), ncol = 2) +
+    theme(legend.key = element_blank(),
+          legend.position = c(0.9, 0.25),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16))
+
+```
+
+This prompted the question of whether fitting the mixed logistic model could confirm this shift in preferences.
+Just as before, the matrix below show the coefficient magnitude (color) and pvalues for differences based on iterating through costs as reference dummy codes.
+
+``` {r 16.3.2. mix pre/post separately, echo = FALSE, fig.align="center", fig.width = 5, fig.height = 4}
+## compute the same mixed effects logistic for each half
+# mixed logistic for the first half
+mixLogis_pre <- list()
+mixData <- dataBtw %>%
+  filter(Half == "Half_1") %>%
+  group_by(SubjID, Cost, Handling, Offer) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice))
+
+mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
+mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
+mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
+mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+
+# mixed logistic for the second half
+mixLogis_post <- list()
+mixData <- dataBtw %>%
+  filter(Half == "Half_2") %>%
+  group_by(SubjID, Cost, Handling, Offer) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice))
+
+mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
+mixLogis_post$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
+mixLogis_post$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
+mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+
+## now produce a summary matrix
+# get the beta and pvalue matrices 
+betasPre <- betaMatrix(mixLogis_pre, rearrange = rearrange)
+betasPost <- betaMatrix(mixLogis_post, rearrange = rearrange)
+
+# and combine them
+betaMat <- matrix(NA, nrow = nrow(betasPre$Betas), ncol = nrow(betasPre$Betas))
+betaMat[lower.tri(betaMat)] <- betasPre$Betas[lower.tri(betasPre$Betas)]
+betaMat[upper.tri(betaMat)] <- betasPost$Betas[lower.tri(betasPost$Betas)]
+dimnames(betaMat) <- list(rearrange, rearrange)
+
+pvalMat <- matrix(NA, nrow = nrow(betasPre$Pvals), ncol = nrow(betasPre$Pvals))
+pvalMat[lower.tri(pvalMat)] <- betasPre$Pvals[lower.tri(betasPre$Pvals)]
+pvalMat[upper.tri(pvalMat)] <- betasPost$Pvals[lower.tri(betasPost$Pvals)]
+dimnames(pvalMat) <- list(rearrange, rearrange)
+
+# remove uninteresting comparisons 
+diag(betaMat) <- 0
+
+# aand plot
+corrplot(betaMat, 
+         is.corr = F, 
+         p.mat = pvalMat, 
+         outline = T,
+         #insig = "p-value",
+         sig.level = 0.05, 
+         na.label = "square", 
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black",
+         tl.cex = 0.8,
+         col = col2(200))
+````
+
+\bigskip
+
+### 16.3.3.
+
+*To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
+OC will be computed as the product of a free parameter (gamma) and the handling time.
+Both gamma and the temperature parameter of the logistic function will be estimated at the subject level, independently for each subject.*
+
+``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+# group
+summaryOC <- list()
+summaryOC$all <- dataBtw %>%
+                 #filter(rawChoice < 2) %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup()
+
+# plot
+(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+                      geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
+                      geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
+                      geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
+                      geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
+                      ylim(0,1.5) +
+                      labs(title = "Gamma Values per Group", x = "") +
+                      scale_fill_manual(values = colsBtw) +
+                      theme(panel.grid.major = element_blank(),
+                        panel.grid.minor = element_blank(),
+                        panel.background = element_blank(),
+                        axis.line = element_line(colour = "black"),
+                        text = element_text(size = 16)))
+
+```
+
+The gamma optimization search space was bound by extreme choice values.
+For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
+Conversely, a participant experiencing low opportunity costs would accept the unbeneficial offer of 4 cents for a 14 second delay (or 4/14).
+The model was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood (R-squared: mean = `r mean(summaryOC$all$Rsquared)`, SD = `r sd(summaryOC$all$Rsquared)`).
+The resulting gamma values per participant are shown per group below (gray lines denote the rate of earnings under optimal behavior for all 3 timing contexts), and reflect what was seen in the previous sections: participants in the wait and physical conditions showed higher gamma values (and thus opportunity costs) than in the other two groups.
+Given the high variability of the easy condition, it might be worth modeling each timing context independently, or perhaps fitting the model on subgroups defined by a median split of the participants based on their acceptance rate.
+
+\bigskip
+
+### 16.3.4.
+
+*We will cross-validate each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+The estimates will be used to predict acceptances in the testing sample, and the mean percent correctly predicted will be reported for each group.
+This will also provide information on the stability of each participant’s choices (4.3.1.).*
+
+As can be seen below, the gamma parameter from the OC model was able to predict post-midpoint choices successfully regardless of group.
+
+``` {r 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+# Compute the OC for pre-midpoint
+summaryOC$pre <- dataBtw %>%
+                 filter(Half == "Half_1") %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup() %>%
+                 select(SubjID, Gamma)
+
+# let's add the gammas to the second half data and estimate prop predicted on the second half
+summaryOC$predicted <- dataBtw %>%
+                 filter(Half == "Half_2") %>%
+                 group_by(Cost, SubjID) %>%
+                 left_join(summaryOC$pre) %>%
+                 mutate(OC = Handling * Gamma,
+                        predicted = Offer > OC) %>% 
+                 summarise(percentPredicted = mean(predicted == Choice) * 100)
+
+# plot
+(summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
+                            labs(x = "") +
+                            geom_boxplot(show.legend = F) +
+                            scale_fill_manual(values = colsBtw) +
+                            labs(y = "Percent Predicted") +
+                            ylim(0,100) +
+                            theme(panel.grid.major = element_blank(),
+                            panel.grid.minor = element_blank(),
+                            panel.background = element_blank(),
+                            axis.line = element_line(colour = "black"),
+                            text = element_text(size = 16)))
+
+```
+
+\bigskip
+
+### 16.3.5.
+
+*The OC estimates for each group will be compared using an ANOVA with condition as a factor. This will let us determine which cost type produced the highest discounting.*
+
+``` {r 16.3.5. OC comparisons, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+# ANOVA
+OCanova <- list()
+OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC$all))
+Fval <- OCanova$aov[[1]]$`F value`[1]
+Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
+Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
+
+# Post-hoc pairwise tests
+OCanova$perms <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(permute), simple = T)
+diag(OCanova$perms) <- 1
+
+OCanova$ES <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(cohenD)) %>%
+  abs()
+```
+
+The analysis of variance was significant (F = `r round(Fval, digits = 2)`, p = `r ifelse(Pval < 0.001, "< 0.001", paste("=", round(Pval, digits = 2)))`, R-squared = `r Rsquared_aov`).
+Pairwise post-hoc permutations are shown in the following matrix.
+These results suggest that participants engaged in cognitively effortful demands experience significantly lower opportunity costs than those whose demands involve physical effort and pure delay.
+The reason for this is unclear, and we will work on it in the near future.
+
+``` {r 16.3.5. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
+# plot all pairwise comparisons
+corrplot(OCanova$ES,
+         is.corr = F, 
+         p.mat = OCanova$perms,
+         type = "upper",
+         insig = "p-value",
+         sig.level = -1,
+         na.label = "square",
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black", 
+         tl.cex = 0.8,
+         outline = T)
+```
+
+\bigskip
+
+\newpage
+
 ## Discussion

### 2020-03-16 Cost_manuscript.Rmd
Added within subject analysis code. All code will be reviewed eventually

@@
 output:
-  word_document: default #reference_docx: Style_reference_draft.docx
   pdf_document:
@@
     keep_tex: no
+  word_document: default #reference_docx: Style_reference_draft.docx
 header-includes:
@@
 # forced travels are switched to acceptances, as they reflect a preference for that trial
-# rawChoice will be used to compute the # of mistakes
+# rawChoice will be used to compute the # of mistakes
 # The RT is upper-bounded because a glitch in the code made two 14s trials last longer (among all p's) 
@@
 
+### **Experiment 1: Between-subjects comparison of costs**
+
+### Participants
+
+Both between- and within-subject experiments were pregeristered with the Open Science Framework (https://osf.io/2rsgm/registrations).
+All experimental procedures were approved by the Boston University Institutional Review Board, and written consent was acquired for all participants.
+For the between-subject experiment, we recruited individuals until a desired number of 84 eligible participants was achieved (58 Female, median age = 21, range = 18 - 31; number excluded before reaching goal = XX).
+The sample size was determined by means of power analysis (ANOVA), using a significance level of 0.05, power of 0.8, an effect size of f = 0.45 (calculated from a pilot study), and three groups (one for each cost type).
+The resulting per-group sample was 20, which we increased to 21 in order to match three possible block orders.
+We added an extra group of 21 participants who experienced a minimally effortful condition in order to determine whether effort or pure engagement were driving our results.
+	We excluded participant datasets based on four preregistered criteria: 1) Consent: If they withdrew their participation; 2) Inattentiveness: a catch trial was placed at the end of each experimental block, asking participants to press a key within 3 seconds (time requirement based on pilot study response times).
+A participant that failed two or more of these checks was excluded and replaced.
+3) Improbable choice behavior: The task was structured so that one reward amount must always be accepted.
+A participant who quit every trial in at least one block was assumed not to have followed or understood task instructions, or to have disengaged from the task altogether.
+4) Performance: In the cognitive effort condition, participants were forced to travel if they made 2 mistakes in a trial (see task procedures below).
+Any participant with more than 30% forced travels was excluded and replaced.
+
+### Foraging Task
+
+All experimental tasks were implemented using PsychoPy 2.X (CITE) on a Macbook Pro laptop.
+In this task, participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay.
+Their goal was to maximize their gains within a fixed amount of time.
+Participants exerted physical effort by maintaining grip on a handheld dynamometer (XXXX, BIOPAC Systems, United States) using their dominant hand.
+Gripping requirements were calibrated at 20% of maximum voluntary contraction (MVC, acquired at the beginning of the session).
+Cognitive effort entailed switching among Stroop, dot motion coherence, and flanker tasks.
+In Stroop, one of three color names was displayed on the screen (red, blue or green), with a font color that was either congruent (e.g.
+word red painted in red) or incongruent (e.g.
+word red painted in blue).
+Participants had to select the color of the font, not the word displayed (i.e.
+they had to suppress their tendency to read the word).
+For motion coherence, 100 solid white dots moved on the screen.
+A fraction of these dots moved cohesively to the left or right (coherence could be either 30% or 40%, uniformly sampled), while the rest moved in random directions.
+Participants had to respond with the direction of the cohesive set of dots.
+REVISE.
+In flanker, rows of arrowheads pointed either to the left or the right (maximum of 3 rows, 3 to 13 arrowheads per row).
+Participants responded with the direction of the center arrowhead, which could point in the same or opposite direction from its neighbors.
+These tasks were configured so that responses always involved a left or right key press (e.g.
+for Stroop, two colored circles were presented at each side of the screen).
+During the handling time, cognitive tasks and their configurations were randomly sampled, and were presented for 1 s followed by a 1 s inter-stimulus interval.
+Participants were asked to respond within each task’s presentation time.
+Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive ones of each kind.
+Each participant was assigned to one of these types of costs (cognitive effort, physical effort, or delay), and a fourth group of equal size faced an effortless physical task that involved minimal gripping (each group was unaware that other cost conditions existed).
+On each trial a monetary offer was displayed for 2 s, and participants had the opportunity to expend time and/or effort during the handling time in order to earn it.
+Upon completion of a trial participants saw a 2 s window displaying the reward obtained, which was followed by a travel time to the next offer.
+Alternatively, the participant could quit at any point during the handling time by pressing the spacebar on the computer, and immediately start traveling.
+If participants failed to maintain above-threshold gripping or made two mistakes during the cognitive task, they were forced to travel and missed the reward.
+There were three block types, in which handling times of 2, 10, or 14 seconds were paired with travel times of 14, 6, and 2 seconds, respectively (note that all combinations add up to 16 seconds).
+Timing parameters were held constant within each 7-min block.
+Each of these blocks was experienced in a pseudo-randomized order, and repeated in the same order after a short break in order to probe choice stability (total session length = 42 minutes).
+Reward amounts varied uniformly per trial (4, 8, or 20 cents), such that every reward was presented twice every six trials.
+This prevented sequences from being dominated by a single amount during any window of time.
+Timing information was disclosed at the beginning of each block, and rewards displayed before each trial began during a 2 s window.
+Participants received training prior to the experimental session, and were told about all possible environmental statistics in order to preclude experience-dependent learning.
+In short, participants faced with different behavioral costs were tasked with deciding their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.
+
+### Operationalization of Cost
+
+Foraging theory posits that accepting a delayed reward depends on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment (Stephens and Krebs, 1977).
+In this study, the richness of the environment was manipulated by the length of the handling and travel times (i.e.
+shorter travel times produced richer environments).
+Since time combinations were fixed per block, we calculated each block’s optimal accept/reject strategy by computing all decision strategies according to the following equation:
+
+**INSERT**
+
+where R, H, and P are the reward, handling time, and acceptance probability of trial i, respectively, and T is the travel times.
+This gives the total reward per second attainable in each block as a function of the lowest amount accepted (i.e.
+acceptance threshold).
+Figure X shows possible earnings for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
+For example, a participant in a 10 s handling block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate.
+Significant deviations from the optimal strategy can be understood as reflecting changes in subjective OC.
+Beyond comparing among cost types, this approach allowed us to test if certain demands boosted the value of offers (i.e.
+over-accepting low offers).
+
+### Analyses
+
+First, we tested whether decision makers integrated delay and reward information.
+To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a logistic regression to each participant’s data to predict trial-wise acceptances, using handling time and reward amount as predictors.
+The resulting beta coefficients for handling time and reward were pooled across all participants, and we performed a one-sample rank-sum test on each set of coefficients to examine whether they were significantly positive or negative (compared to no effect of 0).
+We then performed an extension of the logistic regression by adding an autoregressive covariate containing the number of consecutive quits prior to a given trial.
+This examined the possibility that participant choices were governed by recent quitting history rather than the experimental parameters.
+Coefficients significantly different from 0 denoted that a participant relied on recent quitting history.
+	Our foraging task was configured such that over and under accepting were detrimental to total earnings.
+To confirm this, we fit a general linear model with constant, linear, and quadratic terms to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable).
+A significant quadratic coefficient thus would signal that the task statistics operated as expected.
+Next, to determine the optimality of each group’s decisions, performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost above).
+This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR) CHANGE TO COST3 APPROACH.
+Next we compared preferences among cost conditions.
+We first performed a one-way ANOVA on the proportion of trials accepted using group as a factor.
+We then compared the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests).
+The same approach was used for total earnings.
+This gave us an initial glimpse on the potential differences in cost among conditions.
+In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors.
+Reward and handling time will be within-subject factors, and condition a between-subjects factor.
+In support of hypotheses 4.1.
+and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions (MAYBE REMOVE, EXPLAINING WHY IT’S REDUNDANT).
+We computed the probability of accepting a trial with a mixed-effects logistic regression.
+Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and subject ID as a random effect.
+Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition.
+We ran three versions of the model with different reference conditions, in order to test all pairwise differences among the four cost conditions.
+As preregistered, we anticipated significant main effects (coefficients different than zero) of handling time, reward, and cost condition.
+We hypothesize that the differences among cost conditions will follow the pattern described in 4.2.
+We then examined whether this a priori model outperformed both simpler and more complex models.
+We used both Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
+The regression with each combination of predictors was fitted in the following order: 1) intercept only; 2) cost type only; 3) handling time only; 4) reward only; 5) condition, handling, and reward main effects (a priori model); 6) adding a handling-by-reward interaction; and 7) adding all three possible two-way interactions.
+We predicted that model 5 would have the lowest AIC.
+Finally, we modeled the subjective opportunity cost in each condition.
+We started by addressing the prediction that participants would display consistent choice patterns throughout the session (i.e.
+that the reward amounts they accepted in a given timing condition would be similar throughout the experiment).
+This prediction was made because participants had full knowledge of the environment.
+We computed each participant’s total proportion of acceptances pre- and post-midpoint for every block.
+For each cost condition separately, we will fit a linear model that predicts post-midpoint acceptance from before-midpoint rates.
+We will report the slopes and 95% confidence intervals (CI) for each cost group.
+CIs containing 1 will denote that participants in that group produced consistent choices (CHANGE TO COST3 APPROACH, PERMUTATION).
+Once we established choice stability, we proceeded to estimate the subjective OC of each type of demand (see Operationalization of Cost above).
+OC were computed as the product of a free parameter (gamma) and the handling time.
+We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type.
+
+ **INSERT**
+
+Both gamma and the temperature parameter of the softmax function were estimated independently for each subject, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE).
+We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.
+Finally, the OC estimates for each group were compared using an ANOVA with condition as a factor.
+This let us determine which cost type produced the highest discounting.
+(ADD ADDITIONAL MODELS FROM LITERATURE)
+
+### **Experiment 2: Within-subjects comparison of costs**
+
+### Participants
+
+We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36).
+Sample size was once again determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f=0.5, and four factors (one for each condition).
+The resulting sample size was 45, which we increased to 48 in order to balance the potential order of blocks.
+We excluded participants using the same criteria as in the between-subject experiment.
+
+### Foraging Task Adaptation
+
+The original between-subjects task was modified so that participants foraged for cost types in addition to rewards.
+Every participant experienced all forms of cost (delay, physical effort, and cognitive effort).
+There were two block types, in which delay trials were interspersed with either physical-effort or cognitive-effort trials.
+This setup prevented participants from having to rapidly switch between response modalities across trials (i.e.
+keyboard press and handgrip).
+Block combinations (i.e.
+physical/wait and cognitive/wait) were experienced three times by each participant in 7-minute-long, interleaved blocks, thus matching the experiment’s length to the between-subject version.
+Half of the participants experienced a block sequence that started with the physical block.
+Timing parameters were matched to the middle condition from Experiment 1 (i.e.
+10 s handling and 6 s travel), allowing a balance between acquiring enough observations per trial type and being able to compare results across experiments.
+Participants were informed that this timing combination would be constant prior to beginning the experiment.
+Cost type combinations were disclosed at the beginning of each block, and reward/cost offers displayed before each trial begins (e.g.
+“8 cents for physical effort”).
+Unlike the previous experiment, participants could make their choice during the offer window (instead of during the handling time).
+Participants trained in each type of demand until they reached the same criteria as in the between-subject experiment.
+
+### Analyses
+
+The analytical pipeline for the within-subject study was mostly preserved from the between-subject experiment.
+We first ran tests to determine whether decision makers integrated reward information.
+We performed a logistic regression per participant to predict trial-wise acceptances based on reward amounts.
+The resulting beta coefficients were pooled across all participants, and a one-sample rank-sum test was used to examine whether they were significantly positive or negative (compared to 0).
+Next, we explored the effects of choice history by adding an autoregressive covariate containing the number of consecutive recent quits.
+We then confirmed that the under- and over-acceptance were detrimental to total earnings by performing the same quadratic linear model explained above.
+To determine the optimality of the group’s decisions, we will examine whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents were always be accepted, given our design).
+The reward-maximizing strategy was to always reject 4 cents and accept 8 cents, yielding a combined optimal proportion of acceptances of 50% (see Operationalization of Costs for details).
+We performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
+Therefore, a significant difference indicated that participants either over or under accepted rewards.
+To compare acceptance rates among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
+The model included cost condition and reward amount as fixed main effects, and subject ID as a random effect (does this make sense?
+It’s specified just like the previous one).
+Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
+We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions.
+Next, we compared this model to both simpler and more complex models using Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC).
+We added varied model complexity in the following order: 1) intercept only; 2) condition only; 3) reward only; 4) condition and reward main effects (base model); and 5) adding a two-way interaction.
+We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
+Next we probed the confidence and consistency with which participants made choices.
+We computed the proportion of quits that were performed during the choice window versus during the handling time.
+We interpreted as confidence if a participant made at least 80% of their choices during the offer window.
+We then computed each participant’s total proportion of acceptances on the first two and last two blocks, and compared them using a paired permutation analysis (5000 iterations).
+To estimate the subjective opportunity cost of each condition, we will use a logistic function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
+OC will be computed as the product of a free parameter (gamma) and the handling time.
+Both gamma and the temperature parameter of the logistic function will be estimated at the subject level, independently for each subject and cost type.
+We cross-validated each subject’s OC value using the first four blocks (two cognitive, two physical) for estimation, and the last two blocks (one of each effort type) choices for testing.
+The estimates were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each cost type.
+The OC estimates for each group will be compared using a repeated measures ANOVA with cost as a factor.
+We will perform pairwise paired permutations as post-hoc tests.
+This will let us determine which cost type produced the highest discounting.
+
 ## Results
@@
 
-### 16.1.1.
+### BTW: 16.1.1.
 
@@
 
-``` {r 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
+``` {r BTW: 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
 # filterout errors and compute R + H logistic per subject, then get coefficients
@@
 
-### 16.1.2.
+### BTW: 16.1.2.
 
@@
 
-``` {r 16.1.2., echo = FALSE, include = FALSE}
+``` {r BTW: 16.1.2., echo = FALSE, include = FALSE}
 # add an AR regressor to track recent quits
@@
 
-### 16.1.3.
+### BTW: 16.1.3.
 
@@
 
-``` {r 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+``` {r BTW: 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
 # calculate the proportions and earnings per subject, while keeping group info
@@
 
-``` {r 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
+``` {r BTW: 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
 # Summary table for the linear model
@@
 
-### 16.1.4.
+### BTW: 16.1.4.
 
@@
 
-``` {r 16.1.4., echo=FALSE}
+``` {r BTW: 16.1.4., echo=FALSE}
 # in order
@@
 
-### 16.2.1.
+### BTW: 16.2.1.
 
@@
 
-``` {r 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
+``` {r BTW: 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
 ## ECDF of proportion completed per cost type
@@
 
-### 16.2.2.
+### BTW: 16.2.2.
 
@@
 
-``` {r 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
+``` {r BTW: 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
 temp <- dataBtw %>%
@@
 
-``` {r 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
+``` {r BTW: 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
 # # code to calculate the rwd/sec rate for each acceptance threshold per handling
@@
 
-``` {r 16.2.2. rmANOVA table, pander}
+``` {r BTW: 16.2.2. rmANOVA table, pander}
 # anova table
@@
 
-### 16.2.3.
+### BTW: 16.2.3.
 
@@
 
-``` {r 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
+``` {r BTW: 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
 # clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
@@
 
-``` {r 16.2.3. Mixed Effects Model plot rand intercepts, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
+``` {r BTW: 16.2.3. Mixed Effects Model plot rand intercepts, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
 # plot random intercepts in increasing order
@@
 
-### 16.2.4.
+### BTW: 16.2.4.
 
@@
 
-``` {r 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r BTW: 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
 # Quasibinomial GLM versions (with proper proportion setup)
@@
 
-``` {r 16.2.4. Plot Deviance comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r BTW: 16.2.4. Plot Deviance comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
 # plot AIC and BIC
@@
 
-### 16.3.1.
+### BTW: 16.3.1.
 
@@
 
-``` {r 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r BTW: 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
 # Proportion of forced travels per subject and cost type
@@
 
-### 16.3.2.
+### BTW: 16.3.2.
 
@@
 
-``` {r 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
+``` {r BTW: 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
 # divide the data into proportion accepted before/after the break (one per column)
@@
 
-``` {r 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+``` {r BTW: 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
 # scatter plot of pre/post acceptances
@@
 
-``` {r 16.3.2. prepost table, pander}
+``` {r BTW: 16.3.2. prepost table, pander}
 panderOptions("digits", 2)
@@
 
-``` {r 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+``` {r BTW: 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
 # # pre
@@
 
-``` {r 16.3.2. mix pre/post separately, echo = FALSE, fig.align="center", fig.width = 5, fig.height = 4}
+``` {r BTW: 16.3.2. mix pre/post separately, echo = FALSE, fig.align="center", fig.width = 5, fig.height = 4}
 ## compute the same mixed effects logistic for each half
@@
 
-### 16.3.3.
+### BTW: 16.3.3.
 
@@
 
-``` {r 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r BTW: 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
 # group
@@
 
-### 16.3.4.
+### BTW: 16.3.4.
 
@@
 
-``` {r 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r BTW: 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
 # Compute the OC for pre-midpoint
@@
 
-### 16.3.5.
+### BTW: 16.3.5.
 
@@
 
-``` {r 16.3.5. OC comparisons, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r BTW: 16.3.5. OC comparisons, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
 # ANOVA
@@
 
-``` {r 16.3.5. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
+``` {r BTW: 16.3.5. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
 # plot all pairwise comparisons
@@
 \bigskip
+
 
@@
 
+### **Within-subjects: Tests of whether decision makers integrate reward information**
+
+### WTH: 16.1.1.
+
+*To address hypothesis 4.1., A logistic regression will be fit for each participant in order to predict trial-wise acceptances, using reward amount as predictor.
+The resulting beta coefficients will be pooled across all participants, and we will perform a one-sample rank-sum test to examine whether the they are significantly positive or negative (compared to 0).
+If the group coefficients are significantly positive, it would mean that a predictor reliably increases the likelihood of acceptance.
+This will allow us to determine whether increments in reward amounts increased the likelihood of acceptance for each participant.*
+
+``` {r WTH: 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
+# adapt the data so the fits are only performed on choices, not failed attempts (revisit?)
+dataList <- dataWth %>% plyr::dlply("SubjID", identity)
+
+# fits
+logisticFits_base <- lapply(dataList, function(data) glm(Choice ~ Offer, data = data, family = "binomial"))
+
+# Summarize
+baseCoeffs <- as.data.frame(t(sapply(logisticFits_base, "[[", "coefficients")))
+baseCoeffs$ConvIters <- sapply(logisticFits_base, function(x) {summary(x)$iter})
+baseCoeffs$R2 <- sapply(logisticFits_base, function(x) {1 - (summary(x)$deviance / summary(x)$null.deviance)})
+baseCoeffs$aic <- sapply(logisticFits_base, function(x) {summary(x)$aic})
+baseCoeffs$propAccept_total <- sapply(dataList, function(data) {mean(data$Choice)})
+baseCoeffs$propAccept_totalSQRD <- baseCoeffs$propAccept_total^2
+baseCoeffs$totalEarned <- (dataWth %>% group_by(SubjID) %>% summarize(totalEarned = sum(Offer[Choice == 1])))$totalEarned
+baseCoeffs$SubjID <- subjList_wth # add subject list column to join the demographics by it below
+
+# plot to match the one in Cost 2, even though we only have offer as an influence
+ggplot(data = baseCoeffs, aes(x = "Offer", y = Offer)) +
+  geom_boxplot() +
+  ylim(-10, 10) +
+  labs(x = "", y = "Coefficients") +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  theme(legend.position = c(0.9, 0.7),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(), 
+        panel.background = element_blank(), 
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 16))
+
+```
+
+The Wilcoxon signed rank test showed that the reward coefficients were significantly greater than 0 (V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* = `r wilcox.test(baseCoeffs$Offer)$p.value`), indicating that participants were properly influenced by reward amounts.
+
+### WTH: 16.1.2.
+
+*We will perform an extension of the logistic regression from 16.1.1., this time adding an autoregressive covariate containing the number of consecutive quits prior to a given trial.
+In this way, we will examine the possibility that participant choices were governed by recent quitting history rather than the experimental parameters.
+Coefficients not significantly different from 0 will denote that a participant did not rely on recent quitting history.*
+
+``` {r WTH: 16.1.2., echo = FALSE, include = FALSE}
+# Create an autoregressive predictor based on previous consecutive quits
+dataList <- lapply(dataList, function(data) data %>% mutate(AR = seqQuits(Choice)))
+
+# fits
+logisticFits_base <- lapply(dataList, function(data) {glm(Choice ~ Offer + AR, data = data, family = "binomial")})
+
+# get the low/high 95% CIs for AR
+baseCoeffs <- as.data.frame(t(sapply(logisticFits_base, confint, "AR"))) %>% 
+  dplyr::rename(AR_CILow = `2.5 %`, AR_CIHigh = `97.5 %`) %>%
+  mutate(SubjID = subjList_wth) %>%
+  left_join(baseCoeffs, by = "SubjID")
+
+# reorder so that SubjID comes first
+#baseCoeffs <- baseCoeffs[ , c(3,4,5,6,7,8,9,1,2)]
+
+# create a vector indicating whether 0 is included or not
+# but first change NA to 0 (visual inspection showed that NAs were tied to p's with near full p(accept), meaning they weren't influenced by history)
+baseCoeffs <- baseCoeffs %>% mutate(AR_CILow = ifelse(is.na(AR_CILow), 0, AR_CILow),
+                                    AR_CIHigh = ifelse(is.na(AR_CIHigh), 0, AR_CIHigh))
+baseCoeffs$AR_effect <- apply(baseCoeffs, 1, function(x) (!(as.numeric(x["AR_CILow"]) <= 0 & as.numeric(x["AR_CIHigh"]) >= 0)))
+
+# alternative method, just do pvalues (maybe adjusted when n is higher)
+# mean(sapply(logisticFits_base, function(x) {summary(x)$coefficients[3,4]}) < 0.05)
+```
+
+This regression showed that `r sum(baseCoeffs$AR_effect)` out of `r nSubjs_wth` of the subjects were influenced by recent quit history.
+
+###	WTH: 16.1.3.
+
+*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable).
+No other covariates will be used, as this analysis is to confirm that over and under accepting are detrimental to total earnings.
+The quadratic term will be defined as the squared deviation from the optimal overall acceptance rate?*
+
+``` {r WTH: 16.1.3. prop accept x earnings, echo = FALSE, include = T, fig.align="center",fig.width=4,fig.height=4}
+# Notes: I also performed this comparing halves and block types x half, and it doesn't look like participants were accepting less to make more.
+# calculate the proportions and earnings per subject, while keeping group info
+temp <- dataWth %>%
+  filter(rawChoice < 2) %>%
+  group_by(SubjID) %>%
+  summarise(Earnings = sum(Offer[Choice == 1] / 100),
+            pComplete = mean(Choice)) %>%
+  mutate(pComplete2 = pComplete^2) %>%
+  ungroup()
+
+# linear fit of earnings x prop accept
+# adding a regressor for half shows no diffs in earnings
+lmEarn <- lm(Earnings ~ pComplete + pComplete2, data = temp)
+
+# plot
+(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
+         scale_color_manual(values = cols) + 
+         geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
+         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
+         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
+         scale_fill_manual(values = cols) +
+         ylim(12, 16) +
+         theme(panel.grid.major = element_blank(), 
+           panel.grid.minor = element_blank(), 
+           panel.background = element_blank(), 
+           axis.line = element_line(colour = "black"),
+           text = element_text(size = 16)))
+
+# extra analyses
+# a pre-post paired permutation on earnigs confirms no differences (more evidence in section 16.3.3--prepost)
+# this means that, at least in general, participants are not changing their behavior due to monetary incentives
+# but because of something else, maybe like fatigue (this pattern holds even at finer subdivisions)
+# PPearn <- dataWth %>%
+#           #filter(Block %in% c(1,2,5,6)) %>%
+#           mutate(Choice = ifelse(Choice > 1, 0, Choice)) %>%
+#           group_by(SubjID, Half) %>%
+#           summarise(Earnings = sum(Offer[Choice == 1] / 100),
+#                     pComplete = mean(Choice)) %>%
+#           ungroup() %>% 
+#           select(SubjID, Half, Earnings) %>% 
+#           spread(Half, Earnings)
+# 
+# permute(PPearn$Half_1, PPearn$Half_2, paired = TRUE)
+```
+
+The table shows the results from this linear model.
+In accord with the design of the experimental task, participants who either rejected or accepted too many trials received the least amount of money overall.
+This is confirmed by significance of the quadratic term below.
+
+``` {r WTH: 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
+# Summary table for the linear model
+panderOptions("digits", 2)
+pander(lmEarn, style = "rmarkdown")
+```
+
+###	WTH: 16.1.4.
+
+*To determine the optimality of the group's decisions, we will examine whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents will always be accepted).
+The reward-maximizing strategy is to always reject 4 cents and accept 8 cents, yielding a combined optimal proportion of acceptances of 50%.
+We will perform a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
+We will report the estimated overall proportion of acceptances for these rewards along with the statistics to show the direction of the bias.*
+
+``` {r WTH: 16.1.4., echo = FALSE, fig.align="center",fig.width=6,fig.height=4}
+# get the proportion of acceptances per reward and trial type across subjects, and do a one sample t test versus a null mu given by the optimal strategy
+# note that in the very likely case that every participant will accept or reject for a given reward/cost (i.e. sd = 0): 
+# I am just providing a pseudo pvalue as 1 minus the diff. between prevalent choice and the null (so, removing the standard deviation from the t test equation, otherwise you can't divide by 0)
+# this is just to track the optimality.
+# I am also adding the mean/sd of acceptances per cost/reward and optimality as reference
+# summary_costvsreward <- data %>% 
+#                           group_by(SubjID, Offer, Cost) %>% 
+#                           summarize(prop = mean(Choice)) %>%
+#                           group_by(Offer, Cost) %>%
+#                           summarize(pval = ifelse(sd(prop) == 0, 
+#                                                   1 - (mean(prop) - ifelse(mean(Offer) == 4, 0, 1)), 
+#                                                   t.test(prop, mu = (ifelse(mean(Offer) == 4, 0, 1)))$p.value),
+#                                     propAccept = mean(prop),
+#                                     sdAccept = sd(prop)) %>%
+#                           ungroup() %>%
+#                           mutate(Optimal = rep(c(0,1,1), each = 4),
+#                                  Padjusted = p.adjust(pval, method = "BY"))
+# 
+# temp <- data %>%
+#   group_by(SubjID, Offer, Cost) %>%
+#   filter(Offer < 20) %>%
+#   summarize(propAccept = mean(Choice)) %>% 
+#   spread(Cost, propAccept) %>% 
+#   ungroup() %>% 
+#   select(Cognitive:Wait_P) %>% 
+#   apply(., 2, t.test, mu = 0.5) 
+# 
+# summary_costvsreward <- data.frame(tstat = sapply(temp, "[[", "statistic"), 
+#                                    pval = sapply(temp, "[[", "p.value"))
+# rownames(summary_costvsreward) <- names(temp)
+
+# get quits and acceptances per cost type for each subject
+# revisit this eventually to clean it up
+temp <- dataWth %>%
+  group_by(SubjID, Offer, Cost) %>%
+  filter(Offer < 20) %>%
+  summarize(propAccept = mean(Choice),
+            accept = sum(Choice),
+            quit = sum(Choice == 0)) %>% 
+  gather(act, counts, accept:quit) %>% 
+  unite(temp, Cost, act, sep = ".") %>% 
+  select(SubjID, Offer, temp, counts) %>% 
+  spread(temp, counts) %>%
+  ungroup() %>% 
+  select(Cognitive.accept:Wait_P.quit)
+
+# perform a prop.test based on the group's acceptances and quits per cost
+temp2 <- lapply(seq(1, 8, by = 2), function(i) {prop.test(sum(temp[,i]), sum(temp[,i] + temp[,i+1]), p = 0.5, conf.level = 0.95)})
+
+# store stats in a dataframe
+summary_costvsreward <- data.frame(probability = sapply(temp2, "[[", "estimate"),
+                                   chisquared = sapply(temp2, "[[", "statistic"), 
+                                   confint = t(sapply(temp2, "[[", "conf.int")),
+                                   pval = sapply(temp2, "[[", "p.value"))
+rownames(summary_costvsreward) <- unique(gsub("[.].*","",names(temp)))
+
+rm(temp, temp2)
+
+# create table
+pander(round(summary_costvsreward, digits = 4))
+```
+
+The table shows a significant bias towards low acceptance for 4 and 8 cent rewards for all but one condition (wait trials associated with cognitive effort).
+The plot in 16.2.1.
+shows the proportion of acceptances per reward for each cost condition.
+
+### **Within-subjects: Comparisons among the four delay and effort conditions**
+
+###	WTH: 16.2.1.
+
+*We will compute the probability of accepting a trial with a mixed-effects logistic regression.
+Based on the task structure and our main question, our a priori model of interest will include cost condition and reward amount as fixed main effects, and subject ID as a random effect.
+Cost condition will be modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
+We will run three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions (per 4.2).
+We anticipate significant main effects (coefficients different than zero) for reward and cost condition.
+We hypothesize that the differences among cost conditions will follow the pattern described in 4.2.*
+
+``` {r WTH: 16.2.1. Overall Proportion diffs, fig.align = "center", fig.width = 6, fig.height = 4, echo = FALSE}  
+# ## ECDF of proportion completed per cost type
+# temp <- dataWth %>%
+#         filter(Choice < 2) %>%
+#         #mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait_0", "Wait_1"))) %>%
+#         group_by(SubjID, Cost) %>%
+#         summarise(pComplete = mean(Choice))
+# 
+# 
+# # plots
+# (p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
+#         geom_boxplot(show.legend = F) +
+#         scale_fill_manual(values = cols) +
+#         ylim(c(0, 1)) +
+#         labs(y = "Proportion Completed") +
+#         theme(panel.grid.major = element_blank(), 
+#             panel.grid.minor = element_blank(), 
+#             panel.background = element_blank(), 
+#             axis.line = element_line(colour = "black"),
+#             text = element_text(size = 16)))
+
+```
+
+``` {r WTH: 16.2.1., echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
+# both methods yield similar outputs, at least coefficients and pvalues
+# but the likelihoods will differ of course. The second one might be better in terms of computational needs.
+# method 1
+# mixLogis_main <- list()
+# mixLogis_main$Cog <- glmer(Choice ~ Cost + Offer + (1 | SubjID), family = "binomial", data = data)
+
+# method 2
+mixLogis_main <- list()
+mixData <- dataWth %>%
+  group_by(SubjID, Cost, Offer) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice))
+
+mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
+mixLogis_main$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
+mixLogis_main$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
+mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+
+# plot proportion accepted per trial/offer combo
+(n2 <- dataWth %>%
+        filter(Choice < 2) %>%
+        group_by(Cost, Offer) %>%
+        summarise(propAccept = mean(Choice),
+                  SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
+        ungroup() %>%
+        mutate(Optimal = rep(c(0, 1, 1), length(unique(dataWth$Cost))),
+               #BlockType = as.factor(rep(c(0,1,0,1), each = 3)),
+               Offer = ifelse(Offer == 20, 12, Offer)) %>%
+        ggplot(aes(Offer, propAccept, color = Cost)) +
+          geom_point(size = 3, show.legend = T) +
+          geom_point(aes(y = Optimal), size = 3, pch = 21, fill = "grey75", color = "grey30") +
+          geom_line(lwd = 1, show.legend = T) +
+          scale_color_manual(values = cols) +
+          scale_fill_manual(values = cols) +
+          geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
+          scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5,1)) +
+          scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
+          labs(y = "Proportion Accepted") +
+          theme(legend.position = c(0.8, 0.25),
+                legend.key = element_blank(),
+                panel.grid.major = element_blank(),
+                panel.grid.minor = element_blank(),
+                panel.background = element_blank(),
+                axis.line = element_line(colour = "black"),
+                text = element_text(size = 22)))
+
+```
+
+The plot above shows that the pattern of reward acceptances does indeed resemble that from the between-subject experiment for an equivalent time combination.
+However, the differences in cost are mostly reversed from the previous experiment, following the order stipulated in 4.2.
+The matrix below shows the coefficients for all cost comparisons, with coefficient size in color and respective p-values enclosed in each box.
+This figure formally confirms the pattern seen above, although the wait conditions do trend towards significance.
+
+``` {r WTH: 16.2.1. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=4}
+# get summary of coeffs
+rearrange <- c("Cognitive", "Wait_C", "Wait_P", "Physical")
+mixSummary <- betaMatrix(mixLogis_main, rearrange = rearrange)
+diag(mixSummary$Pvals) <- NA
+
+# remove uninteresting comparisons
+mixSummary$Betas[rbind(c(3, 1), c(4,2))] <- NA
+mixSummary$Pvals[rbind(c(3, 1), c(4,2))] <- NA
+
+# invert colors
+col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))
+
+corrplot(mixSummary$Betas, 
+         is.corr = F, 
+         p.mat = mixSummary$Pvals, 
+         type = "lower",
+         outline = T,
+         #insig = "p-value",
+         sig.level = 0.05, 
+         na.label = "square", 
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black",
+         tl.cex = 0.8,
+         col = col2(200))
+
+```
+
+###	WTH: 16.2.2.
+
+*Next, we will examine whether the a priori model from 16.2.1.
+outperforms both simpler and more complex models.
+Unlike the individual logistic regression fits in 16.1.1., a mixed-effects approach gives us a better goodness of fit measure for model comparisons.
+We will determine the best model (combination of predictors) using Akaike's Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimizes the negative log-likelihood.
+The regression with each combination of predictors will be fitted in the following order: 1) intercept only; 2) condition only; 3) reward only; 4) condition and reward main effects (from 16.2.3.); and 5) adding a two-way interaction.
+We predict that model 4 will have the last considerable decrease in the negative log-likelihood.*
+
+``` {r WTH: 16.2.2., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
+# Quasibinomial GLM versions (with proper proportion setup)
+mixLogis_compare <- list()
+mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
+mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$AllMain <- mixLogis_main$Cognitive
+mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (1 | SubjID), family = "binomial", data = mixData)
+
+# Model selection 
+abicLogis_compare <- data.frame(Model = names(mixLogis_compare),
+                                AIC = sapply(mixLogis_compare, AIC),
+                                BIC = sapply(mixLogis_compare, BIC))
+
+# plot 
+(mixLogis_compare$plot <- abicLogis_compare %>% 
+  gather(Comparison, Value, AIC:BIC) %>%
+  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
+  ggplot(aes(Model, Value, fill = Comparison)) +
+    geom_point(color = "black", pch = 21, size = 3) +
+    theme_classic())
+
+# effect size
+mixLogis_compare$Rsq <- 1 - (deviance(mixLogis_compare$AllMain)/deviance(mixLogis_compare$Base)) # denominator is the null deviance
+```
+
+The figure shows that the model with all main effects had the lowest AIC, but not BIC (pseudo R-square: `r round(mixLogis_compare$Rsq, digits = 2)`).
+We performed a likelihood ratio test to formally determine whether adding cost type to the reward-only model significantly improved the fit.
+We computed the difference in deviance between the models, and evaluated it under a chi-squared distribution with 3 degrees of freedom (i.e.
+the number of parameters added to the model, as cost was dummy-coded).
+The table below summarizes the results, showing that the addition of cost type significantly improved the model fit.
+(personal note: sure, AIC is 1 value lower when considering the difference in dfs, but that's barely making it..)
+
+``` {r WTH: 16.2.2. LRT (anova) table, echo = F}
+test <- anova(mixLogis_compare$Reward, mixLogis_compare$AllMain)
+rownames(test) <- c("Reward Only", "All Main")
+
+pander(test[c(1, 2, 3, 5, 6, 8)])
+```
+
+### **Within-subjects: Modeling the subjective opportunity cost in each condition**
+
+###	WTH: 16.3.1.
+
+*Response times (RT) for quit responses will be presented in a descriptive manner in order to examine whether participants tended to quit early or late within individual trials.
+Each cost condition's response time distribution will contain the pooled RT across participants, and we will display the empirical cumulative distribution functions for each condition.
+Short RT would suggest confident and stable decisions (in support of 4.3.1.).*
+
+``` {r WTH: 16.3.1., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
+# Proportion of forced travels per subject and cost type
+propFails <- dataWth %>%
+  filter(Cost != "WAIT") %>%
+  group_by(SubjID, Cost) %>%
+  summarise(propFails = mean(rawChoice == 2)) %>%
+  group_by(Cost) %>%
+  summarise(meanQuit = mean(propFails))
+# 
+# # Reaction times ECDFs including offer and in-trial quits
+# (RTs <- data %>%
+#   mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
+#   filter(rawChoice < 2) %>% 
+#   ggplot(aes(RT, color = Cost)) + 
+#     #stat_ecdf(lwd = 1.2) +
+#     geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
+#     geom_vline(xintercept = 2, lty = 2) + # end of the offer period
+#     scale_color_manual(values = cols) +
+#     scale_x_continuous(breaks = seq(12), limits = c(0, 14)) +
+#     labs(x = "Time in Cost", y = "Proportion Completed") +
+#     theme(panel.grid.major = element_blank(),
+#       panel.grid.minor = element_blank(),
+#       panel.background = element_blank(),
+#       axis.line = element_line(colour = "black"),
+#       text = element_text(size = 16)))
+
+# NEW VERSION OF SURVIVAL. BUT STILL NEEDS A BIT OF WORK. ALSO, CHECK THAT RT > 14s
+
+library(survival)
+library(ggfortify)
+
+# this version of a survival curve forces all successful acceptances to have an RT of 14
+# that's to avoid jumps from 2s to 10s to 14s
+# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor?
+# to note re: x-axis. In this exp, p's could quit within the 2s offer window. Cost 2 didn't allow that, so it counts from when trial begins.
+temp <- dataWth %>%
+    mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
+    #filter(rawChoice < 2) %>% 
+    mutate(#RT = ifelse(Choice == 1, 14, RT),
+           Choice = 1 - Choice)
+
+survData <- survfit(Surv(RT, Choice) ~ Cost, data = temp)
+
+autoplot(survData) +
+  geom_vline(xintercept = 2, lty = 2) + # end of the grace period for physical trials
+  scale_color_manual(values = cols) +
+  scale_fill_manual(values = cols) +
+  scale_x_continuous(breaks = seq(12)) +
+  ylim(0, 1) +
+  scale_x_continuous(breaks = seq(0, 12), labels = seq(-2, 10)) +
+  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
+  theme(legend.position = c(0.35, 0.2),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 22))
+
+# ecdf of RTs across blocks for all subjects combined
+dataWth %>%
+  mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
+  mutate(Choice = 1 - Choice)  %>%
+  filter(ResponseType == "OfferQuit") %>%
+  ggplot(aes(RT, group = Block, color = Block)) +
+    stat_ecdf() +
+    #facet_wrap(vars(Cost)) +
+    theme_classic()
+
+```
+
+Participants can quit either during the offer period (2s) or during the handling time (10s), allowing for a total of 12 seconds to give up on the current trial.
+The survival curve above shows quitting throughout the trial for all participants.
+Censored points signal completions (at end of interval) and forced travels (throughout the trial).
+The figure suggests that participants made most of their choices quickly within the offer window.
+The overall proportion of forced trials was scarce (overall mean proportion of fails for cognitive and physical trials were `r unlist(propFails[1:2,2])`, respectively).
+
+###	WTH: 16.3.2.
+
+*We will also compute the proportion of quits that were performed during the choice window versus during the handling time.
+If over 80% of quits occurred during the choice window on average, this will suggest that participants were confident in their choices.*
+
+``` {r WTH: 16.3.2., echo = FALSE}
+# Proportion of quits once the trial started per subject
+PropQuits <- dataWth %>%
+  filter(!(ResponseType %in% c("Forced Travel", "Forced travel", "Reward"))) %>%
+  group_by(SubjID) %>%
+  summarise(propAccept = mean(ResponseType == "Quit"))
+
+```
+
+The mean proportion of quits during the handling time was `r round(mean(PropQuits$propAccept), digits = 2)` (SD = `r round(sd(PropQuits$propAccept), digits = 2)`), with `r sum(PropQuits$propAccept > 0.2)` participants accepting fewer than 80% of trials during the offer window.
+
+###	WTH: 16.3.3.
+
+*In order to further examine choice stability (hypothesis 4.3.1.), we will compute each participant's total proportion of acceptances on the first two and last two blocks.
+We will compute a mixed-effects linear model to predict post-midpoint proportion of acceptances from pre-midpoint rates, with subjects as random intercepts and condition as a dummy-coded fixed effect.
+We will report the 95% confidence interval (CI) for the pre-midpoint predictor.
+A CI containing 1 will denote that participants in that condition produced consistent choices, while accounting for the overall acceptance patterns of a given subject across cost types.
+(**This is a more elaborate version of the between-subject analysis, which did a pre-post prediction based on the proportion of acceptances per subject across groups**).*
+
+``` {r WTH: 16.3.3., echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4, include = F}
+# restructure the data
+temp <- dataWth %>%
+  filter(!(Block %in% c(3,4))) %>%
+  group_by(SubjID, Cost, Half) %>%
+  summarise(propAccepted = mean(Choice)) %>%
+  ungroup() %>%
+  spread(Half, propAccepted)
+
+# compute the mixed effects model (linear for this)
+mixLogis_prepost <- lmer(Half_2 ~ Half_1 + Cost -1 + (1 | SubjID), data = temp)
+
+# get the coefficients and confidence intervals
+t1 <- coefficients(mixLogis_prepost)$SubjID[1, 2:6]
+t2 <- as.data.frame(t(confint(mixLogis_prepost)[3:7,]))
+
+# and concatenate them
+summary_prepost <- t(bind_rows(t1, t2))
+colnames(summary_prepost) <- c("Coefficient", "CI-low", "CI-high")
+
+# # prepost half paired perms
+# temp <- temp %>% plyr::dlply("Cost", identity) 
+# prepost <- list()
+# prepost$cohen <- sapply(temp, function(data) {DescTools::CohenD(data$Half_1, data$Half_2)})
+# prepost$perm <- sapply(temp, function(data) {permute(data$Half_1, data$Half_2, paired = T, simple = T)})
+
+## paired tests for first versus last block per cost type
+FirstvsLast <- dataWth %>%
+  filter(Choice < 2) %>%
+  group_by(SubjID) %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  group_by(SubjID, Cost, Block) %>%
+  summarise(propAccept_subj = mean(Choice)) %>%
+  spread(Block, propAccept_subj) %>%
+  rename(First = `1`, Second = `2`, Third = `3`) %>%
+  plyr::dlply("Cost", identity)
+
+prepost <- list()
+prepost$Perms <- sapply(FirstvsLast, function(x) {permute(x$First, x$Third, paired = T, simple = T)})
+prepost$CohenD <- sapply(FirstvsLast, function(x) {DescTools::CohenD(x$First, x$Third)})
+
+rm(temp, t1, t2)
+```
+
+``` {r WTH: 16.3.3. plots, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+# various plots
+# acceptances across blocks
+propBlocks <- dataWth %>%
+    filter(Choice < 2) %>%
+    group_by(SubjID) %>%
+    mutate(Block = case_when(
+      Block %in% c(1, 2) ~ 1,
+      Block %in% c(3, 4) ~ 2,
+      Block %in% c(5, 6) ~ 3
+    )) %>%
+    group_by(SubjID, Cost, Block) %>%
+    summarise(propAccept_subj = mean(Choice)) %>%
+    group_by(Cost, Block) %>%
+    summarize(propAccept = mean(propAccept_subj),
+              seAccept = sd(propAccept_subj)/sqrt(nSubjs_wth)) %>%
+    ggplot(aes(Block, propAccept, color = Cost)) +
+      geom_point(size = 2) +
+      geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
+      geom_line() +
+      ylim(0, 1) +
+      labs(y = "Proportion Accepted") +
+      scale_x_continuous(breaks = c(1, 2, 3)) +
+      scale_color_manual(values = cols) +
+      scale_fill_manual(values = cols) +
+      theme(legend.key = element_blank(),
+         legend.position = c(0.8, 0.25),
+         panel.grid.major = element_blank(),
+         panel.grid.minor = element_blank(),
+         panel.background = element_blank(),
+         axis.line = element_line(colour = "black"),
+         text = element_text(size = 16))
+
+# Pre-post midpoint
+# calculate mean per trial type to draw horizontal/vertical lines pre/post
+df_mean <- dataWth %>%
+            filter(Choice < 2, !(Block %in% c(3,4))) %>%
+            group_by(SubjID, Cost) %>%
+            summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
+                      propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
+            group_by(Cost) %>%
+            summarise(propAccept_1 = mean(propAccept_1),
+                      propAccept_2 = mean(propAccept_2))
+
+mid <- dataWth %>%
+  filter(Choice < 2, !(Block %in% c(3,4))) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
+            propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
+  ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
+    geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
+    labs(x = "Proportion Accepted - First Block", y = "Proportion Accepted - Last Block") +
+    scale_fill_manual(values = cols) +
+    scale_color_manual(values = cols) +
+    xlim(0, 1) +
+    ylim(0, 1) +
+    geom_abline(slope = 1, intercept = 0, lty = 2) +
+    geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
+    geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
+    theme(legend.key = element_blank(),
+       legend.position = c(0.8, 0.25),
+       panel.grid.major = element_blank(),
+       panel.grid.minor = element_blank(),
+       panel.background = element_blank(),
+       axis.line = element_line(colour = "black"),
+       text = element_text(size = 16))
+
+# wait vs effort across effort conditions
+pAll <- dataWth %>%
+  filter(Choice < 2) %>%
+  mutate(Cost2 = ifelse(!(Cost %in%  c("Wait_C", "Wait_P")), "EFFORT", "WAIT"),
+         BlockType = ifelse(gsub(".*_", "", Cost) == 1, "Physical", "Cognitive")) %>%
+  group_by(SubjID, BlockType) %>%
+  summarise(Wait_accept = mean(Choice[Cost2 == "WAIT"]),
+            Effort_accept = mean(Choice[Cost2 == "EFFORT"])) %>%
+  ggplot(aes(Wait_accept, Effort_accept, color = SubjID, shape = BlockType)) +
+    geom_point(size = 5, show.legend = T) +
+    xlim(0,1) +
+    ylim(0,1) +
+    geom_abline(slope = 1, intercept = 0, lty = 2) +
+    scale_color_manual(values = cols) +
+    scale_fill_manual(values = cols) +
+    theme_classic()
+
+# load the plots
+grid.arrange(mid, propBlocks, ncol = 2)
+
+# plot showing the difference in proportion of acceptances between first and last block, effort vs delay for each block type
+# lines connect the same subject between the blocks
+dataWth %>%
+  group_by(SubjID) %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  #filter(Half == "Half_1", Offer < 20) %>%
+  filter(Block != 2) %>%
+  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
+  group_by(SubjID, Cost, Block, Offer) %>%
+  summarise(propAccept = mean(Choice)) %>%
+  ungroup() %>%
+  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+  spread(Block, propAccept) %>%
+  mutate(Difference = `Last Block` - `First Block`) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(Diffscore = sum(Difference)/3) %>%
+  mutate(Type = ifelse(Cost %in% c("Cognitive", "Physical"), "Effort", "Delay"),
+         Cost = ifelse(Cost %in% c("Cognitive", "Wait_C"), "Cognitive", "Physical")) %>%
+  spread(Type, Diffscore) %>%
+  ggplot(aes(Effort, Delay, group = SubjID, fill = Cost)) +
+    geom_hline(yintercept = 0) +
+    geom_vline(xintercept = 0) +
+    geom_path(show.legend = F, alpha = 0.5, linetype = "dashed") +
+    geom_point(show.legend = T, pch = 21, color = "black", size = 4) +
+    scale_fill_manual(values = cols) +
+    annotate("text", x = -0.4, y = 0.6, label = "Increased preference for delay over time", size = 5, color = "grey30") +
+    annotate("text", x = -0.5, y = -0.6, label = "All acceptances decreased", size = 5, color = "grey30") +
+    annotate("text", x = 0.5, y = 0.6, label = "All acceptances increased", size = 5, color = "grey30") +
+    annotate("text", x = 0.4, y = -0.6, label = "Increased preference for effort over time", size = 5, color = "grey30") +
+    labs(x = "P(Effort): Last - First Block", y = "P(Delay): Last - First Block", fill = "Block type") +
+    ylim(-0.7, 0.7) +
+    xlim(-0.7, 0.7) +
+    theme(legend.key = element_blank(),
+          legend.position = c(0.9, 0.35),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 20))
+
+### CODE TO LOOK AT EARNINGS PER BLOCK AND CALCULATE OPTIMAL EARNINGS
+# # code to calculate the rwd/sec rate for each acceptance threshold per handling
+# rwd <- c(4, 8, 20)
+# handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
+# travel <- c(2, 6, 14) + 2
+# rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
+# 
+# # the highest reward amount for a typical 7-min block per handling is:
+# apply(rwdRates, 1, max) * (7 * 60)
+
+# # this helps make sense of the toal earnings
+# # plotting mean earnings per cost and block
+# dataWth %>%
+#   filter(rawChoice == 1) %>%
+#   group_by(SubjID) %>%
+#   mutate(Block = case_when(
+#     Block %in% c(1, 2) ~ 1,
+#     Block %in% c(3, 4) ~ 2,
+#     Block %in% c(5, 6) ~ 3
+#   )) %>%
+#   group_by(SubjID, Cost, Block) %>%
+#   summarise(subEarnings = sum(Offer)) %>%
+#   group_by(Cost, Block) %>%
+#   summarise(meanEarned = mean(subEarnings),
+#             seEarned = sd(subEarnings) / sqrt(nSubjs_wth)) %>%
+#   ggplot(aes(Block, meanEarned, color = Cost)) +
+#     geom_point(size = 2) +
+#     geom_errorbar(aes(ymin = meanEarned - seEarned, ymax = meanEarned + seEarned, color = Cost), width = 0.1, size = 1.5) +
+#     geom_line(size = 1.5) +
+#     labs(y = "Mean Earnings +- SE (cents)") +
+#     scale_x_continuous(breaks = c(1, 2, 3)) +
+#     scale_color_manual(values = cols) +
+#     scale_fill_manual(values = cols) +
+#     theme(legend.key = element_blank(),
+#           #legend.position = c(0.1, 0.8),
+#           panel.grid.major = element_blank(),
+#           panel.grid.minor = element_blank(),
+#           panel.background = element_blank(),
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 22))
+
+```
+
+These participants tended to accept fewer trials on the second half of the experiment (Beta = `r round(summary_prepost[1,1], digits = 2)`, 95% CI: `r round(summary_prepost[1,2:3], digits = 2)`).
+The figure on the left shows this tendency, although some subjects shows considerable consistency.
+The plot on the right divides the proportion of acceptances across blocks (each cost block is experienced thrice), and shows a global decrease in acceptances as a function of experimental time.
+
+A better test is to perform pairwise comparisons between the first and last block per cost.
+Paired permutations on means of proportions showed that all participants accepted fewer trials during the second half, regardless of cost (all p < 0.05; Cohen's D: cognitive = `r prepost$CohenD[1]`, physical = `r prepost$CohenD[2]`, wait-cognitive = `r prepost$CohenD[1]`, wait-physical = `r prepost$CohenD[1]`).
+
+Now let's divide them by reward and handling amounts.
+The plots below show that initially participant choices resembled those from the between-subject experiment, accepting more cognitive trials than any other, and displaying higher costs for physical/wait_p.
+However, by the end of the experiment all cost types were exacerbated.
+As seen before, cognitive trials had the greatest decrease in acceptances across reward amounts.
+This re-evaluation was not present when participants faced only one type of cost.
+
+``` {r WTH: 16.3.3. Plot Pre/Post reward x handling, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+# # first block
+# t1 <- data %>%
+#   group_by(SubjID) %>%
+#   mutate(Block = do.call(c, lapply(c(2, 4, 6), function(x) {rep(x / 2, sum(Block %in% c(x - 1, x)))}))) %>%
+#   #filter(Half == "Half_1", Offer < 20) %>%
+#   filter(Block == 1) %>%
+#   group_by(Cost, Offer) %>%
+#   summarise(propAccept = mean(Choice),
+#             SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
+#   ungroup() %>%
+#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+#   ggplot(aes(Offer, propAccept, color = Cost)) +
+#     geom_point(size = 3, show.legend = F) +
+#     #geom_point(aes(y = Optimal), size = 3, pch = 21, color = "darkgrey") +
+#     geom_line(show.legend = F) +
+#     scale_color_manual(values = cols) +
+#     scale_fill_manual(values = cols) +
+#     geom_errorbar(aes(ymin=propAccept-SE, ymax=propAccept+SE), width=0.2, size=1, show.legend = T) +
+#     scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
+#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+#     labs(x = "Reward", y = "Proportion Accepted", title = "First Block") +
+#     theme(legend.key = element_blank(),
+#           legend.position = c(0.8, 0.25),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
+# 
+# 
+# # last block
+# t3 <- data %>%
+#     group_by(SubjID) %>%
+#     mutate(Block = do.call(c, lapply(c(2, 4, 6), function(x) {rep(x / 2, sum(Block %in% c(x - 1, x)))}))) %>%
+#     #filter(Half == "Half_2", Offer < 20) %>%
+#     filter(Block == 3) %>%
+#     group_by(Cost, Offer) %>%
+#     summarise(propAccept = mean(Choice),
+#               SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
+#     ungroup() %>%
+#     mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+#     ggplot(aes(Offer, propAccept, color = Cost)) +
+#       geom_point(size = 3, show.legend = F) +
+#       geom_line(show.legend = F) +
+#       scale_color_manual(values = cols) +
+#       scale_fill_manual(values = cols) +
+#       geom_errorbar(aes(ymin=propAccept-SE, ymax=propAccept+SE), width=0.2, size=1, show.legend = F) +
+#       scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
+#       scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+#       labs(x = "Reward", y = "", title = "Last Block") +
+#       theme(legend.position = c(0.1, 0.7),
+#             panel.grid.major = element_blank(), 
+#             panel.grid.minor = element_blank(), 
+#             panel.background = element_blank(), 
+#             axis.line = element_line(colour = "black"),
+#             text = element_text(size = 16))
+# 
+# grid.arrange(t1, t3, ncol = 2)
+
+dataWth %>%
+  group_by(SubjID) %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  #filter(Half == "Half_1", Offer < 20) %>%
+  filter(Block != 2) %>%
+  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
+  group_by(Cost, Block, Offer) %>%
+  summarise(propAccept = mean(Choice),
+            SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
+  ungroup() %>%
+  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+  ggplot(aes(Offer, propAccept, color = Cost)) +
+    geom_point(size = 3, show.legend = T) +
+    #geom_point(aes(y = Optimal), size = 3, pch = 21, color = "darkgrey") +
+    geom_line(size = 1, show.legend = F) +
+    scale_color_manual(values = cols) +
+    scale_fill_manual(values = cols) +
+    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
+    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
+    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+    labs(x = "Reward", y = "Proportion Accepted") +
+    facet_wrap(vars(Block)) +
+    theme(legend.key = element_blank(),
+          legend.position = c(0.9, 0.25),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 22))
+
+```
+
+This prompted the question of whether fitting the mixed logistic model could confirm this shift in preferences.
+Just as before, the matrix below show the coefficient magnitude (color) and pvalues for differences based on iterating through costs as reference dummy codes.
+
+``` {r WTH: 16.3.3. mix pre/post separately, echo = FALSE, fig.align="center", fig.width=5, fig.height=4}
+## compute the same mixed effects logistic for each half
+# mixed logistic for the first half
+mixLogis_pre <- list()
+mixData <- dataWth %>%
+  filter(Half == "Half_1") %>%
+  group_by(SubjID, Cost, Offer) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice))
+
+mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
+mixLogis_pre$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
+mixLogis_pre$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
+mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+
+# mixed logistic for the second half
+mixLogis_post <- list()
+mixData <- dataWth %>%
+  filter(Half == "Half_2") %>%
+  group_by(SubjID, Cost, Offer) %>%
+  summarize(totalChoices = length(Choice),
+            totalAccepted = sum(Choice),
+            totalQuits = sum(Choice == 0),
+            propAccepted = mean(Choice))
+
+mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
+mixLogis_post$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
+mixLogis_post$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
+mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+
+## now produce a summary matrix
+# get the beta and pvalue matrices 
+betasPre <- betaMatrix(mixLogis_pre)
+betasPost <- betaMatrix(mixLogis_post)
+
+# and combine them
+betaMat <- matrix(NA, nrow = nrow(betasPre$Betas), ncol = nrow(betasPre$Betas))
+betaMat[lower.tri(betaMat)] <- betasPre$Betas[lower.tri(betasPre$Betas)]
+betaMat[upper.tri(betaMat)] <- betasPost$Betas[upper.tri(betasPost$Betas)]
+dimnames(betaMat) <- list(names(mixLogis_pre), names(mixLogis_pre))
+
+pvalMat <- matrix(NA, nrow = nrow(betasPre$Pvals), ncol = nrow(betasPre$Pvals))
+pvalMat[lower.tri(pvalMat)] <- betasPre$Pvals[lower.tri(betasPre$Pvals)]
+pvalMat[upper.tri(pvalMat)] <- betasPost$Pvals[upper.tri(betasPost$Pvals)]
+dimnames(pvalMat) <- list(names(mixLogis_pre), names(mixLogis_pre))
+
+# remove uninteresting comparisons 
+diag(betaMat) <- 0
+betaMat[rbind(c(1, 3), c(2, 4), c(3, 1), c(4,2))] <- NA
+pvalMat[rbind(c(1, 3), c(2, 4), c(3, 1), c(4,2))] <- NA
+
+# aand plot
+corrplot(betaMat, 
+         is.corr = F, 
+         p.mat = pvalMat, 
+         outline = T,
+         #insig = "p-value",
+         sig.level = 0.05, 
+         na.label = "square", 
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black",
+         tl.cex = 0.8,
+         col = col2(200))
+```
+
+Finally, we can compare how the difference in proportion accepted between last and first blocks changes between trial types.
+The plots below show that effort and delay trials in the cognitive blocks tended to be rejected more on the last block (i.e.
+they land on the negative side of both axes).
+The plot on the right shows a similar pattern for trials on the physical blocks, but these are more similar across subjects, and also show a small tendency to accept more on either first or last blocks.
+
+``` {r WTH: 16.3.3 temp plot, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+
+cw <- dataWth %>%
+  group_by(SubjID) %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  filter(Offer < 20) %>%
+  filter(Block != 2) %>%
+  group_by(SubjID, Block, Cost, Offer) %>%
+  summarise(pAccept = mean(Choice)) %>%
+  spread(Block, pAccept) %>%
+  mutate(diff = `3` - `1`) %>%
+  ungroup() %>%
+  select(-c(`1`, `3`)) %>%
+  spread(Cost, diff) %>%
+  ggplot(aes(Cognitive, Wait_C, fill = as.character(Offer))) +
+    geom_point(pch = 21, color = "black", size = 3) +
+    geom_hline(yintercept = 0) +
+    geom_vline(xintercept = 0) +
+    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
+    ylim(-1, 1) +
+    xlim(-1, 1) +
+    labs(#title = "P(Accepted): Last - First Block",
+         x = "P(Cognitive): Last - First",
+         y = "P(Wait_C): Last - First",
+         fill = "Offer") +
+    theme(legend.key = element_blank(),
+          legend.background = element_rect(fill = "grey80"),
+          legend.position = c(0.8, 0.8),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16))
+
+gw <- dataWth %>%
+  group_by(SubjID) %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  filter(Offer < 20) %>%
+  filter(Block != 2) %>%
+  group_by(SubjID, Block, Cost, Offer) %>%
+  summarise(pAccept = mean(Choice)) %>%
+  spread(Block, pAccept) %>%
+  mutate(diff = `3` - `1`) %>%
+  ungroup() %>%
+  select(-c(`1`, `3`)) %>%
+  spread(Cost, diff) %>%
+  ggplot(aes(Physical, Wait_P, fill = as.character(Offer))) +
+    geom_point(pch = 21, color = "black", size = 3, show.legend = F) +
+    geom_hline(yintercept = 0) +
+    geom_vline(xintercept = 0) +
+    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
+    ylim(-1, 1) +
+    xlim(-1, 1) +
+    labs(#title = "P(Accepted): Last - First Block",
+         x = "P(Physical): Last - First",
+         y = "P(Wait_P): Last - First",
+         fill = "Offer") +
+    theme(legend.position = c(0.8, 0.8),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16))
+
+grid.arrange(cw, gw, ncol = 2)
+
+# more prepost tests
+# diffscore prepost for effort vs wait
+dataWth %>%
+  group_by(SubjID) %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  #filter(Half == "Half_1", Offer < 20) %>%
+  filter(Block != 2) %>%
+  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
+  group_by(SubjID, Cost, Block, Offer) %>%
+  summarise(propAccept = mean(Choice)) %>%
+  ungroup() %>%
+  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+  spread(Block, propAccept) %>%
+  mutate(Difference = `Last Block` - `First Block`) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(Diffscore = sum(Difference)/3) %>%
+  spread(Cost, Diffscore) %>%
+  ggplot() +
+    geom_point(aes(Cognitive, Wait_C), color = cols[1]) +
+    geom_point(aes(Physical, Wait_P), color = cols[2]) +
+    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
+    ylim(-0.5, 0.5) +
+    xlim(-0.5, 0.5) +
+    #geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
+    #geom_boxplot(show.legend = F, size = 1.5) +
+    #geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
+    #scale_color_manual(values = cols) +
+    #scale_fill_manual(values = cols) +
+    theme(legend.key = element_blank(),
+          legend.position = c(0.9, 0.25),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 22))
+
+# diffscore per cost type (you don't see if specific subjects are prone to increasing/decreasing acceptances across them)
+dataWth %>%
+  group_by(SubjID) %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  #filter(Half == "Half_1", Offer < 20) %>%
+  filter(Block != 2) %>%
+  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
+  group_by(SubjID, Cost, Block, Offer) %>%
+  summarise(propAccept = mean(Choice)) %>%
+  ungroup() %>%
+  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+  spread(Block, propAccept) %>%
+  mutate(Difference = `Last Block` - `First Block`) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(Diffscore = sum(Difference)/3) %>%
+  ggplot(aes(Cost, Diffscore, fill = Cost)) +
+    geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
+    geom_boxplot(show.legend = F, size = 1.5) +
+    geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
+    scale_color_manual(values = cols) +
+    scale_fill_manual(values = cols) +
+    theme(legend.key = element_blank(),
+          legend.position = c(0.9, 0.25),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 22))
+```
+
+### WTH: 16.3.4.
+
+*To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant's probability of completing a trial based on the difference between the delayed reward's magnitude and the estimated opportunity cost (OC) for each cost type.
+OC will be computed as the product of a free parameter (gamma) and the handling time.
+Both gamma and the temperature parameter of the logistic function will be estimated at the subject level, independently for each subject and cost type.*
+
+``` {r WTH: 16.3.4., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
+# Here it might be best to estimate gamma for the wait trials only at first
+# once the wait OCs are estimated, then they can be modulated by effort
+# Estimate gamma per subject for each group separately
+summaryOC <- list()
+summaryOC$all <- dataWth %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  #filter(Choice < 2) %>%
+  group_by(SubjID, Cost) %>% #group_by(SubjID, Cost, Block) %>%
+  do(optimizeOCModel(., simplify = T)) %>%
+  ungroup()
+
+# plot
+(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+    geom_boxplot(show.legend = F) +
+    geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
+    geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
+    geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
+    ylim(0,1.5) +
+    labs(x = "") +
+    scale_fill_manual(values = cols) +
+    theme(panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.background = element_blank(),
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 16)))
+
+# try to replicate the group-level proportion of acceptances from 16.2
+# this looks pretty much like the empirical proportion data, so the stochasticity is playing a major part in the estimation
+# the estimate probability even matches actual proportions at the single subject level 
+# logis <- mapply(function(g, t) {1 / (1 + exp((-1 * t) * (c(4, 8, 20) - (g * 10))))}, summaryOC$all$Gamma, summaryOC$all$Temperature)
+# colnames(logis) <- unite(summaryOC, test, SubjID, Cost)$test
+# logis2 <- as.data.frame(logis) %>% 
+#   gather(Cost, Probability) %>%
+#   mutate(SubjID = substr(Cost, 1,3), 
+#          Cost = substr(Cost, 5,20),
+#          Reward = rep(c(4,8,20), nrow(.)/3)) %>%
+#   group_by(Cost, Reward) %>%
+#   summarize(propAccept = mean(Probability)) %>%
+#   ggplot(logis2, aes(Reward, propAccept, color = Cost)) +
+#     geom_point(size = 3, show.legend = T) +
+#     geom_line(lwd = 1, show.legend = T) +
+#     scale_color_manual(values = cols) +
+#     scale_fill_manual(values = cols) +
+#     #geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
+#     scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
+#     scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
+#     labs(y = "Proportion Accepted") +
+#     theme(legend.key = element_blank(),
+#           panel.grid.major = element_blank(),
+#           panel.grid.minor = element_blank(),
+#           panel.background = element_blank(),
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
+```
+
+The figure on the left shows the distribution of fitted gammas for each cost type, and inversely matches the proportion of acceptances described previously.
+The plot on the right shows the OC for each subject, divided by cost type.
+The horizontal line denotes total earnings per second under the optimal strategy for the time and reward combinations.
+
+###	WTH: 16.3.5.
+
+*We will cross-validate each subject's OC value using the first four blocks (two cognitive, two physical) for estimation, and the last two blocks (one of each effort type) choices for testing.
+The estimates will be used to predict acceptances in the testing sample, and the mean percent correctly predicted will be reported for each cost type.
+This will also provide information on the stability of each participant's choices (4.3.1.).*
+
+``` {r WTH: 16.3.5., echo = FALSE, fig.width=5, fig.height=4, fig.align="center"}
+# subdivide data
+dataTrain <- dataWth %>%
+   filter(Block < 5)
+
+dataTest <- dataWth %>%
+  filter(Block > 4)
+
+# estimate
+# per-cost, but consider the idea above
+OCs_validation <- list()
+temp <- dataTrain %>% filter(Cost == "Wait_C") %>% plyr::dlply("SubjID", identity)
+OCs_validation$Wait_C <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+temp <- dataTrain %>% filter(Cost == "Wait_P") %>% plyr::dlply("SubjID", identity)
+OCs_validation$Wait_P <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+temp <- dataTrain %>% filter(Cost == "Cognitive") %>% plyr::dlply("SubjID", identity)
+OCs_validation$Cognitive <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+temp <- dataTrain %>% filter(Cost == "Physical") %>% plyr::dlply("SubjID", identity)
+OCs_validation$Physical <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+
+# reshape data
+temp <- bind_rows(OCs_validation) %>% 
+  mutate(SubjID = subjList_wth) %>%
+  gather(Cost, gamma, Wait_C:Physical) %>%
+  left_join(dataTest, ., by = c("SubjID", "Cost")) %>% # assign OCs to each subject per cost type
+  mutate(prediction = Offer > Handling * gamma) %>%
+  # plyr::dlply("SubjID", identity)
+  group_by(SubjID, Cost) %>%
+  summarize(predicted = mean(Choice == prediction))
+
+# plot prediction %
+qplot(Cost, predicted, geom = "boxplot", data = temp) + 
+  ylim(0,1) +
+  theme_classic()
+```
+
+The figure above shows that each participant's estimated gamma successfully predicted choices in the last two blocks to a high degree (suspisiouly, considering the decrease in the acceptance rate as a function of time).
+
+###	WTH: 16.3.6.
+
+*The OC estimates for each group will be compared using a repeated measures ANOVA with cost as a factor. This will let us determine which cost type produced the highest discounting.*
+
+``` {r WTH: 16.3.6., echo = FALSE}
+# repeated measures anova
+OCs_anova <- list()
+OCs_anova$aov <- summary(aov(Gamma ~ Cost + Error(SubjID / Cost), data = summaryOC$all))
+
+# table
+pander(OCs_anova$aov)
+
+# do all pairwise comparisons
+OCs_anova$gammas <- summaryOC$all %>% 
+  reshape2::dcast(SubjID ~ Cost, value.var = "Gamma") %>%
+  select(-SubjID)
+
+# perform a paired permutation among every pair of cost types
+OCs_anova$perms <- outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(permute), simple = T, paired = T)
+OCs_anova$perms[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
+
+# and the effect sizes
+OCs_anova$ES <- abs(outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(DescTools::CohenD)))
+OCs_anova$ES[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
+```
+
+(note: here 'Cost' is cost type).
+The ANOVA table shows that there are no significant differences among cost types for the current sample.
+The following plot shows the resulting p-values from performing a paired permutation analysis among all relevant cost types, with color indicating the effect size of the comparison.
+The differences only partially match those seen in 16.2.1., so the OC estimates seem noisy.
+
+``` {r WTH: 16.3.6. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
+corrplot(OCs_anova$ES,
+         is.corr = F, 
+         p.mat = OCs_anova$perms,
+         type = "upper",
+         insig = "p-value",
+         sig.level = -1,
+         na.label = "square",
+         na.label.col = "grey",
+         method = "color", 
+         tl.col = "black", 
+         tl.cex = 0.8,
+         outline = T)
+```
+
 ## Discussion

### 2020-03-16 Cost_manuscript.Rmd
successfully combined both preregs. pdf not knitting, but word doc is

@@
 output:
+  word_document: default #reference_docx: Style_reference_draft.docx
   pdf_document:
@@
     keep_tex: no
-  word_document: default #reference_docx: Style_reference_draft.docx
 header-includes:
@@
   \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
-#subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
 #bibliography: mPFC_paper.bib
@@
 # forced travels are switched to acceptances, as they reflect a preference for that trial
-# rawChoice will be used to compute the # of mistakes
+# rawChoice will be used to compute the # of mistakes
 # The RT is upper-bounded because a glitch in the code made two 14s trials last longer (among all p's) 
@@
                            Cost == "GRIP_1" ~ "Physical",
-                           Cost == "WAIT_1" ~ "Wait_P")) %>%
+                           Cost == "WAIT_1" ~ "Wait_P"),
+         Cost = as.factor(Cost)) %>%
   group_by(SubjID) %>%
@@
 
-### Analyses
+### Analyses
 
@@
 (earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
-         scale_color_manual(values = cols) + 
+         scale_color_manual(values = colsWth) + 
          geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
@@
          labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
-         scale_fill_manual(values = cols) +
+         scale_fill_manual(values = colsWth) +
          ylim(12, 16) +
@@
 #         geom_boxplot(show.legend = F) +
-#         scale_fill_manual(values = cols) +
+#         scale_fill_manual(values = colsWth) +
 #         ylim(c(0, 1)) +
@@
           geom_line(lwd = 1, show.legend = T) +
-          scale_color_manual(values = cols) +
-          scale_fill_manual(values = cols) +
+          scale_color_manual(values = colsWth) +
+          scale_fill_manual(values = colsWth) +
           geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
@@
 #     geom_vline(xintercept = 2, lty = 2) + # end of the offer period
-#     scale_color_manual(values = cols) +
+#     scale_color_manual(values = colsWth) +
 #     scale_x_continuous(breaks = seq(12), limits = c(0, 14)) +
@@
   geom_vline(xintercept = 2, lty = 2) + # end of the grace period for physical trials
-  scale_color_manual(values = cols) +
-  scale_fill_manual(values = cols) +
+  scale_color_manual(values = colsWth) +
+  scale_fill_manual(values = colsWth) +
   scale_x_continuous(breaks = seq(12)) +
@@
       scale_x_continuous(breaks = c(1, 2, 3)) +
-      scale_color_manual(values = cols) +
-      scale_fill_manual(values = cols) +
+      scale_color_manual(values = colsWth) +
+      scale_fill_manual(values = colsWth) +
       theme(legend.key = element_blank(),
@@
     labs(x = "Proportion Accepted - First Block", y = "Proportion Accepted - Last Block") +
-    scale_fill_manual(values = cols) +
-    scale_color_manual(values = cols) +
+    scale_fill_manual(values = colsWth) +
+    scale_color_manual(values = colsWth) +
     xlim(0, 1) +
@@
     geom_abline(slope = 1, intercept = 0, lty = 2) +
-    scale_color_manual(values = cols) +
-    scale_fill_manual(values = cols) +
+    scale_color_manual(values = colsWth) +
+    scale_fill_manual(values = colsWth) +
     theme_classic()
@@
     geom_point(show.legend = T, pch = 21, color = "black", size = 4) +
-    scale_fill_manual(values = cols) +
+    scale_fill_manual(values = colsWth) +
     annotate("text", x = -0.4, y = 0.6, label = "Increased preference for delay over time", size = 5, color = "grey30") +
@@
 #     scale_x_continuous(breaks = c(1, 2, 3)) +
-#     scale_color_manual(values = cols) +
-#     scale_fill_manual(values = cols) +
+#     scale_color_manual(values = colsWth) +
+#     scale_fill_manual(values = colsWth) +
 #     theme(legend.key = element_blank(),
@@
 #     geom_line(show.legend = F) +
-#     scale_color_manual(values = cols) +
-#     scale_fill_manual(values = cols) +
+#     scale_color_manual(values = colsWth) +
+#     scale_fill_manual(values = colsWth) +
 #     geom_errorbar(aes(ymin=propAccept-SE, ymax=propAccept+SE), width=0.2, size=1, show.legend = T) +
@@
 #       geom_line(show.legend = F) +
-#       scale_color_manual(values = cols) +
-#       scale_fill_manual(values = cols) +
+#       scale_color_manual(values = colsWth) +
+#       scale_fill_manual(values = colsWth) +
 #       geom_errorbar(aes(ymin=propAccept-SE, ymax=propAccept+SE), width=0.2, size=1, show.legend = F) +
@@
     geom_line(size = 1, show.legend = F) +
-    scale_color_manual(values = cols) +
-    scale_fill_manual(values = cols) +
+    scale_color_manual(values = colsWth) +
+    scale_fill_manual(values = colsWth) +
     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
@@
   ggplot() +
-    geom_point(aes(Cognitive, Wait_C), color = cols[1]) +
-    geom_point(aes(Physical, Wait_P), color = cols[2]) +
+    geom_point(aes(Cognitive, Wait_C), color = colsWth[1]) +
+    geom_point(aes(Physical, Wait_P), color = colsWth[2]) +
     geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
@@
     #geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
-    #scale_color_manual(values = cols) +
-    #scale_fill_manual(values = cols) +
+    #scale_color_manual(values = colsWth) +
+    #scale_fill_manual(values = colsWth) +
     theme(legend.key = element_blank(),
@@
     geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
-    scale_color_manual(values = cols) +
-    scale_fill_manual(values = cols) +
+    scale_color_manual(values = colsWth) +
+    scale_fill_manual(values = colsWth) +
     theme(legend.key = element_blank(),
@@
     labs(x = "") +
-    scale_fill_manual(values = cols) +
+    scale_fill_manual(values = colsWth) +
     theme(panel.grid.major = element_blank(),
@@
 #     geom_line(lwd = 1, show.legend = T) +
-#     scale_color_manual(values = cols) +
-#     scale_fill_manual(values = cols) +
+#     scale_color_manual(values = colsWth) +
+#     scale_fill_manual(values = colsWth) +
 #     #geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +

### 2020-03-20 Cost_manuscript.Rmd
combining result sections

@@
 4) Performance: In the cognitive effort condition, participants were forced to travel if they made 2 mistakes in a trial (see task procedures below).
-Any participant with more than 30% forced travels was excluded and replaced.
+Any participant with more than 30% forced travels was excluded.
 
@@
 Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive ones of each kind.
-  Each participant was assigned to one of these types of costs (cognitive effort, physical effort, or delay), and a fourth group of equal size faced an effortless physical task that involved minimal gripping (each group was unaware that other cost conditions existed).
+  Each participant was assigned to one of these types of costs (cognitive effort, physical effort, or delay), and a fourth group of equal size faced an effortless physical task that involved minimal gripping.
+Each group was unaware that other cost conditions existed.
 On each trial a monetary offer was displayed for 2 s, and participants had the opportunity to expend time and/or effort during the handling time in order to earn it.
@@
 This prevented sequences from being dominated by a single amount during any window of time.
-Timing information was disclosed at the beginning of each block, and rewards displayed before each trial began during a 2 s window.
+Timing information was disclosed at the beginning of each block, and rewards displayed during a 2 s offer window before each trial began.
 Participants received training prior to the experimental session, and were told about all possible environmental statistics in order to preclude experience-dependent learning.
@@
 
-  First, we tested whether decision makers integrated delay and reward information.
+  First we tested whether decision makers integrated delay and reward information.
 To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a logistic regression to each participant’s data to predict trial-wise acceptances, using handling time and reward amount as predictors.
@@
 OC were computed as the product of a free parameter (gamma) and the handling time.
-We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type.
+We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type
 
@@
 
-### BTW: 16.1.1.
-
-  *To address hypothesis 4.1., A logistic regression will be fit for each participant in order to predict trial-wise acceptances, using handling time and reward amount as predictors.
-The resulting beta coefficients for handling time and reward will be pooled across all participants, and we will perform a one-sample rank-sum test on each set of coefficients to examine whether the they are significantly positive or negative (compared to 0).
-If the group coefficients are significantly positive, it would mean that a predictor reliably increases the likelihood of acceptance.
-This will allow us to determine whether increments in handling time and reward amounts increased and decreased the likelihood of acceptance for each participant, respectively.*
-
 ``` {r BTW: 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
-# filterout errors and compute R + H logistic per subject, then get coefficients
+# filter out errors and compute R + H logistic per subject, then get coefficients
 logisRH <- dataBtw %>%
@@
   sapply(coefficients)
+
+# coefficient summaries
+coeffRH_mean <- apply(logisRH, 1, mean)
+coeffRH_se <- apply(logisRH, 1, sd) / sqrt(nSubjs_btw)
 
@@
 
-The plot shows the pooled coefficients across subjects for the effect of each predictor.
-The results show the expected discounting effect of increasing the handling time, as well as the increase in acceptance likelihood as a function of reward increments.
-We found that these coefficients were significantly different from zero for both handling (V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) and reward (V = `r rankOffer$statistic`, p `r ifelse(rankOffer$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`) regardless of cost condition.
-
-\bigskip
-
-### BTW: 16.1.2.
-
-*We will perform an extension of the logistic regression from 16.1.1., this time adding an autoregressive covariate containing the number of consecutive quits prior to a given trial.
-In this way, we will examine the possibility that participant choices were governed by recent quitting history rather than the experimental parameters (see 11.1.3.).
-Coefficients not significantly different from 0 will denote that a participant did not rely on recent quitting history.*
-
 ``` {r BTW: 16.1.2., echo = FALSE, include = FALSE}
@@
               plyr::dlply("SubjID", identity) %>%
-              lapply(function(data) {glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial")})
-
-# Rank sums
-rankAR <- logisRHAR %>% 
-  sapply(coefficients) %>%
-  wilcox.test(.["AR", ])
-
-AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(confint(x)[4, ], error = function(e){c(0, 0)})}) %>%
+              lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial"))})
+
+# get the AR CIs per participant 
+AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(suppressWarnings(confint(x)[4, ]), error = function(e){c(0, 0)})}) %>%
   replace_na(0) %>%
   t() %>%
-  apply(1, function(x) !(x[1] <= 0 & x[2] >= 0))
-
-```
-
-To measure the significance of each subject's autoregressive coefficient, we computed its CI and checked how many contained zero.
-By this measure, `r sum(AR_CIs)` out of `r nSubjs_btw` of our participants seemed to have been influenced by recent quitting.
-However, the autoregressive predictor did not preclude the effect of the remaininig experimental parameters.
+  apply(1, function(x) (x[1] <= 0 & x[2] >= 0))
+
+# coefficient summaries
+logisRHAR <- sapply(logisRHAR, coefficients)
+coeffRHAR_mean <- apply(logisRHAR, 1, mean, na.rm = T)
+coeffRHAR_se <- apply(logisRHAR, 1, sd, na.rm = T) / sqrt(nSubjs_btw)
+
+# Rank sum test
+rankRHAR <- wilcox.test(logisRHAR["AR", ])
+
+```
+
+  Before comparing acceptance rates among cost conditions, we determined whether participants integrated the rewarding statistics of the experimental environment.
+We first confirmed that increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively.
+Logistic regression coefficients for handling time were significantly lower than 0 across participants (mean $\beta$ = `r mean(rankAR, na.rm = T)`, SE = `r coeffRH_se[2]`; Wilcoxon test: V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`), whereas increasing the reward amount resulted in higher probabilities (mean $\beta$ = `r coeffRH_mean[1]`, SE = `r coeffRH_se[1]`; Wilcoxon test: V = `r rankOffer$statistic`, p `r ifelse(rankOffer$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`).
+We next examined whether choices could also have been affected by recent choice history (i.e.
+if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of quits preceding a trial.
+This auto-regressive coefficient was not significantly different than 0 across the whole group (mean $\beta$ = `r coeffRHAR_mean[3]`, SE = `r coeffRHAR_se[3]`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r ifelse(rankRHAR$p.value < 0.001, "< 0.001", paste("=", round(rankRHAR$p.value, digits = 2)))`).
+Further, the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants.
 
@@
 Most of these were from effortful groups, as the wait group just showed deviations for 2 seconds handling/4 cent, and 10 seconds handling/8 cent offers (note to self: think about a way to properly visualize these).
+
+CONCLUDING: these results suggest that participants were adequately influenced by the rewarding statistics of the environment, even though they did not always perform optimally.
 

### 2020-03-26 Cost_manuscript.Rmd
3/4 of results drafted, plus all methods

@@
 
+# this helps clean p-values for inclusion in text
+# it takes the value, and reports < 0.001 if needed, or rounds to the second digit otherwise
+report_p <- function(pval) {
+  # make sure the p-values entered are numeric (sometimes they can be characters..thanks R)
+  pval <- as.numeric(pval)
+
+  # do p < 0.001 or round depending on the value
+  adapted_p <- ifelse(pval < 0.001, "< 0.001", paste("=", round(pval, digits = 2)))
+
+  print(adapted_p)
+}
 ```
@@
 ## Introduction
+
+- I guess you can mention that the wait group acts as a baseline of foraging behavior.
+- Re-read Mikey's effort value paper to see if there is anything there that can allow us to transition into foraging.
+Like, are there elements that make cog effort valuable that are well encapsuled by foraging paradigms?
 
@@
 Participants received training prior to the experimental session, and were told about all possible environmental statistics in order to preclude experience-dependent learning.
-  In short, participants faced with different behavioral costs were tasked with deciding their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.
 
@@
   where R, H, and P are the reward, handling time, and acceptance probability of trial i, respectively, and T is the travel times.
-This gives the total reward per second attainable in each block as a function of the lowest amount accepted (i.e.
+This gave us the total reward per second attainable in each block as a function of the lowest amount accepted (i.e.
 acceptance threshold).
@@
 For example, a participant in a 10 s handling block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate.
+Note that accepting every offer was often detrimental to participant earnings.
 Significant deviations from the optimal strategy can be understood as reflecting changes in subjective OC.
@@
 Next, to determine the optimality of each group’s decisions, performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost above).
-This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR) CHANGE TO COST3 APPROACH.
-  Next we compared preferences among cost conditions.
+This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR) **CHANGE TO COST3 APPROACH.**
+  Next, we compared preferences among cost conditions.
 We first performed a one-way ANOVA on the proportion of trials accepted using group as a factor.
@@
 This gave us an initial glimpse on the potential differences in cost among conditions.
-In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors.
-Reward and handling time will be within-subject factors, and condition a between-subjects factor.
-In support of hypotheses 4.1.
-and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions (MAYBE REMOVE, EXPLAINING WHY IT’S REDUNDANT).
-We computed the probability of accepting a trial with a mixed-effects logistic regression.
-Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and subject ID as a random effect.
+In order to further look at the effect of handling, offer, and cost type, we computed the probability of accepting a trial with a mixed-effects logistic regression using the lme4 package (CITE).
+Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and participant ID as a random effect.
 Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition.
@@
 As preregistered, we anticipated significant main effects (coefficients different than zero) of handling time, reward, and cost condition.
-We hypothesize that the differences among cost conditions will follow the pattern described in 4.2.
+In addition, we hypothesized that the probability of accepting would be significantly great in either effort condition compared to wait and easy groups.
 We then examined whether this a priori model outperformed both simpler and more complex models.
@@
   To compare acceptance rates among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
-The model included cost condition and reward amount as fixed main effects, and subject ID as a random effect (does this make sense?
-It’s specified just like the previous one).
+The model included cost condition and reward amount as fixed main effects, and subject ID as a random effect.
 Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
@@
 Next, we compared this model to both simpler and more complex models using Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC).
-We added varied model complexity in the following order: 1) intercept only; 2) condition only; 3) reward only; 4) condition and reward main effects (base model); and 5) adding a two-way interaction.
-We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
+We added varied model complexity in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
+We predicted that model 6 would have the last considerable decrease in the negative log-likelihood.
+Nested models with similar AIC were statistically compared using an analysis-of-deviance.
+The significance test was computed as the probability of the reduction in deviance, based on a chi-square distribution with degrees of freedom equal to the difference in the number of parameters between models.
   Next we probed the confidence and consistency with which participants made choices.
@@
 
-``` {r BTW: 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
+``` {r BTW: 16.1.1. Individual logistic, fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
 # filter out errors and compute R + H logistic per subject, then get coefficients
@@
 temp <- melt(logisRH[c("Handling", "Offer"), ])
-qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
+plot_handoffer <- qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
                     labs(x = "", y = "Coefficients") +
@@
 
-``` {r BTW: 16.1.2., echo = FALSE, include = FALSE}
+``` {r BTW: 16.1.2. AR, echo = FALSE, include = FALSE}
+# Idea: do AIC to compare models per participant
 # add an AR regressor to track recent quits
@@
 ```
-
-  Before comparing acceptance rates among cost conditions, we determined whether participants integrated the rewarding statistics of the experimental environment.
-We first confirmed that increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively.
-Logistic regression coefficients for handling time were significantly lower than 0 across participants (mean $\beta$ = `r mean(rankAR, na.rm = T)`, SE = `r coeffRH_se[2]`; Wilcoxon test: V = `r rankHand$statistic`, p `r ifelse(rankHand$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`), whereas increasing the reward amount resulted in higher probabilities (mean $\beta$ = `r coeffRH_mean[1]`, SE = `r coeffRH_se[1]`; Wilcoxon test: V = `r rankOffer$statistic`, p `r ifelse(rankOffer$p.value < 0.001, "< 0.001", paste("=", round(rankHand$p.value, digits = 2)))`).
-We next examined whether choices could also have been affected by recent choice history (i.e.
-if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of quits preceding a trial.
-This auto-regressive coefficient was not significantly different than 0 across the whole group (mean $\beta$ = `r coeffRHAR_mean[3]`, SE = `r coeffRHAR_se[3]`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r ifelse(rankRHAR$p.value < 0.001, "< 0.001", paste("=", round(rankRHAR$p.value, digits = 2)))`).
-Further, the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants.
-
-\bigskip
-
-### BTW: 16.1.3.
-
-*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable).
-No other covariates will be used, as this analysis is to confirm that over and under accepting are detrimental to total earnings.
-The quadratic term will be defined as the squared deviation from the optimal overall acceptance rate.*
 
@@
 # plot
-(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
-         scale_color_manual(values = colsBtw) + 
-         geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = T) + 
-         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
-         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
-         scale_fill_manual(values = colsBtw) +
-         theme(panel.grid.major = element_blank(), 
-           panel.grid.minor = element_blank(), 
-           panel.background = element_blank(), 
-           axis.line = element_line(colour = "black"),
-           text = element_text(size = 16)))
-
-```
-
-The figure shows that participants that over and unceraccepted earned less money overall, as predicted.
-This is supported by a significant quadratic term from the linear model (F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3,2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`; black line shows the fit).
-The following table shows all the results from the model.
-
-``` {r BTW: 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
+# (earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
+#          scale_color_manual(values = colsBtw) + 
+#          geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = T) + 
+#          stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
+#          labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
+#          scale_fill_manual(values = colsBtw) +
+#          theme(panel.grid.major = element_blank(), 
+#            panel.grid.minor = element_blank(), 
+#            panel.background = element_blank(), 
+#            axis.line = element_line(colour = "black"),
+#            text = element_text(size = 16)))
+
 # Summary table for the linear model
-panderOptions("digits", 2)
-pander(lmEarn, style = "rmarkdown")
-```
-
-\bigskip
-
-### BTW: 16.1.4.
-
-*To determine the optimality of each group’s decisions, we will perform two-sided one-sample t-tests (with mu being the optimal proporion of acceptances--either 0 or 1) to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see 11.2.).
-This will result in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we will correct for multiple comparisons using False Discovery Rate (FDR).*
-
-``` {r BTW: 16.1.4., echo=FALSE}
+# panderOptions("digits", 2)
+# pander(lmEarn, style = "rmarkdown")
+
+```
+
+``` {r BTW: 16.1.4. Optimality (move to acceptance comparison eventually), echo = FALSE}
 # in order
@@
 # proportion of significant ones
-# eventually find a way to plot this
-splitData_prop <- mean(temp$significant, na.rm = T)
-```
-
-Of the 36 tests, around `r splitData_prop` were significantly deviant from optimality.
-Most of these were from effortful groups, as the wait group just showed deviations for 2 seconds handling/4 cent, and 10 seconds handling/8 cent offers (note to self: think about a way to properly visualize these).
-
-CONCLUDING: these results suggest that participants were adequately influenced by the rewarding statistics of the environment, even though they did not always perform optimally.
-
-\bigskip
+# eventually find a way to plot this (or just place it further down)
+# alternative per block: temp %>% group_by(Handling) %>% summarise(prop = mean(significant, na.rm = T))
+optimalProp <- mean(temp$significant, na.rm = T) * 100
+
+# proportion accepted per cost condition
+optimalProp_cost <- temp %>% 
+  group_by(Cost) %>% 
+  summarise(propDeviations = round(mean(significant) * 100))
+
+# # potential visualization, though difficult to interpret
+# temp %>% 
+#   filter(Cost != "Easy") %>%
+#   select(Handling, Cost, Offer, significant) %>%
+#   ggplot(aes(Cost, interaction(Offer, Handling), fill = significant)) +
+#   geom_tile(color = "white") +
+#   theme_minimal()
+```
+
+  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) were tasked with deciding their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.
+Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time).
+We hypothesized that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that changing the cost required to obtain rewards would uniformly increase or decrease this choice pattern.
+Specifically, we predicted that participants confronted with cognitive demands would be more likely to accept trials than those faced with physical effort and delay, regardless of handling time and reward amount.
+  To address the first hypothesis, we first confirmed that increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively.
+Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
+Individual-specific logistic regression coefficients for handling time were significantly lower than 0 (mean $\beta$ = `r mean(coeffRH_mean[2], na.rm = T)`, SE = `r coeffRH_se[2]`; Wilcoxon test: V = `r rankHand$statistic`, *p* `r report_p(rankHand$p.value)`), whereas increasing the reward amount resulted in higher acceptance probabilities (mean $\beta$ = `r coeffRH_mean[1]`, SE = `r coeffRH_se[1]`; Wilcoxon test: V = `r rankOffer$statistic`, p `r report_p(rankOffer$p.value)`).
+We next examined whether choices could also have been affected by recent choice history (i.e.
+if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of consecutive quits preceding a trial.
+This auto-regressive coefficient was not significantly different than 0 (mean $\beta$ = `r coeffRHAR_mean[3]`, SE = `r coeffRHAR_se[3]`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r ifelse(rankRHAR$p.value < 0.001, "< 0.001", paste("=", round(rankRHAR$p.value, digits = 2)))`), and the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants.
+This indicates that offer patterns did not influence participant behavior.
+  **Maybe put this as an addendum to the mixed effects analysis of proportion of acceptances, after mixed models** .
+The foraging task was configured so that there was an optimal, reward-maximizing strategy (see Operationalization of Cost in Methods).
+Because of this, participants were told to consider their strategies carefully, as accepting everything would not maximize their gains.
+Figure X shows that participants who over- or under-accepted earned the least (general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`).
+Two-sided, one-sample t-tests against the optimal proportion of acceptances (i.e.
+$\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)` of combinations (*p* < 0.05, FDR corrected), with the proportion of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`).
+Together, these results suggest that participants were adequately influenced by the rewarding statistics of the environment, even though they did not always perform optimally.
 
@@
 
-### BTW: 16.2.1.
-
-*To compare preferences (hypothesis 4.2.), we will first perform a one-way ANOVA on the proportion of trials accepted using group as a factor.
-In addition, we will do pairwise comparisons on the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests).
-The same approach will be used for total earnings.
-This will give us an initial glimpse on the potential differences in cost among conditions.*
-
 ``` {r BTW: 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
-## ECDF of proportion completed per cost type
+## earnings and proportion accepted per cost type
+# note that earnings are based on successful completions, not just acceptances
 temp <- dataBtw %>%
-        filter(Choice < 2) %>%
-        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
         group_by(SubjID, Cost) %>%
-        summarise(Earnings = sum(Offer[rawChoice == 1] / 100),
+        summarise(Earnings = sum(Offer[(Choice == 1) & (rawChoice < 2)] / 100),
                   pAccept = mean(Choice))
+
+## summaries
+overallSumms <- temp %>% 
+  group_by(Cost) %>% 
+  summarise (mProp = mean(pAccept), 
+             sdProp = sd(pAccept), 
+             mEarn = mean(Earnings), 
+             sdEarn = sd(Earnings)) %>%
+  mutate_if(is.numeric, round, digits = 2)
 
@@
 # proportion completed
-propAov <- aov(pAccept ~ factor(Cost), data = temp)
+propAov <- summary(aov(pAccept ~ Cost, data = temp))
 
@@
   sapply(function(x) {
-    c(contrast = paste(colnames(x), collapse = "vs"), 
+    c(contrast = paste(colnames(x), collapse = ifelse(cohenD(x[, 1], x[, 2]) < 0, " < ", " > ")), 
       permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
-      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
+      cohenD = abs(round(cohenD(x[, 1], x[, 2]), digits = 3)))
   }) %>% 
-  t()
+  t() %>%
+  as_tibble()
 
@@
 # earnings 
-earnAov <- aov(Earnings ~ factor(Cost), data = temp)
+earnAov <- summary(aov(Earnings ~ Cost, data = temp))
 
@@
   sapply(function(x) {
-    c(contrast = paste(colnames(x), collapse = "vs"), 
+    c(contrast = paste(colnames(x), collapse = ifelse(cohenD(x[, 1], x[, 2]) < 0, " < ", " > ")), 
       permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
-      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
+      cohenD = abs(round(cohenD(x[, 1], x[, 2]), digits = 3)))
   }) %>% 
-  t()
+  t() %>%
+  as_tibble()
 
 ## plots
-# ECDF pAcceptd
-p1 <- ggplot(aes(pAccept, color = Cost), data = temp) +
-        stat_ecdf(lwd = 1.2, show.legend = F) +
-        scale_color_manual(values = colsBtw) +
-        xlim(0, 1) +
-        labs(y="ECDF", x = "Proportion Accepted") +
-        theme(panel.grid.major = element_blank(), 
-              panel.grid.minor = element_blank(), 
-              panel.background = element_blank(), 
-              axis.line = element_line(colour = "black"),
-              text = element_text(size = 16))
-
 # pAccepted
-p2 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
+p1 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
         geom_boxplot(show.legend = F) +
@@
 # earnings
-p3 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
+p2 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
         geom_boxplot(show.legend = F) +
@@
 
-grid.arrange(p2, p3, ncol = 2)
-```
-
-The plots show that subjects in the wait condition accepted the least and earned the most, suggesting a more optimal pattern of choices.
-Participants in the cognitive effort and easy conditions had higher more variable acceptance patterns, which are reflected in the comparatively low earnings.
-The reason why the easy condition does not show variable earnings like the cognitive effort group is probably due to the quadratic relationship between earnings and acceptances shown before.
-
-\bigskip
-
-### BTW: 16.2.2.
-
-*In order to further look at the effect of delay, work, and rewards, we will perform a repeated measures ANOVA on the proportion completed for each combination of factors.
-Offer and handling time will be within-subject factors, and condition a between-subjects factor.
-In support of hypotheses 4.1.
-and 4.2., we anticipate significant main effects of handling time, reward, and cost condition, but no interactions.*
+grid.arrange(p1, p2, ncol = 2)
+```
+
+  The next set of analyses examined the hypothesis that choice differences among costs would be characterized by more acceptances by the cognitive group **not quite**.
+Figure X shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings.
+One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
+We then performed post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs.
+On each iteration the group assignment was randomly shuffled without replacement, and the difference in mean acceptance rates across iterations created a putative null distribution.
+The unpermuted group mean difference was then evaluated against this permuted distribution.
+This analysis confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdProp)`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Physical < Cognitive") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Cognitive > Wait") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait") %>% select(cohenD)`).
+It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Wait < Easy") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy") %>% select(cohenD)` (all other *p* > 0.05).
+  We repeated these pairwise permutation to identify differences in earnings.
+In line with the earnings results from the previous section (see Figure X), the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdEarn)`) than both physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Physical > Cognitive") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Cognitive < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait") %>% select(cohenD)`).
+In addition, we found that the wait group earned more than the physical (permuted *p* = `r report_p(filter(earnTests, contrast == "Physical < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait") %>% select(cohenD)`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Wait > Easy") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy") %>% select(cohenD)`).
+  These findings provide a first glimpe at differences in cost, showing that individuals in the wait condition accepted the least and earned the most.
+Moreover, they suggest that cognitive demands can boost the value of an offer instead, even when accepting it negatively impacts total earnings.
 
 ``` {r BTW: 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
-temp <- dataBtw %>%
-        filter(Choice < 2) %>%
-        group_by(SubjID, Cost, Handling, Offer) %>%
-        summarise(pAccept = mean(Choice))
-
-## REPEATED MEASURES ANOVA
-# I think I like this the most
-prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Offer + 
-                                 Error(SubjID / (Handling * Offer))))
-
-## NOTES ON RESULTS
-# According to the logistic fit, there are main effects for all predictors, but no interactions.
+# temp <- dataBtw %>%
+#         filter(Choice < 2) %>%
+#         group_by(SubjID, Cost, Handling, Offer) %>%
+#         summarise(pAccept = mean(Choice))
+# 
+# ## REPEATED MEASURES ANOVA
+# # I think I like this the most
+# prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Offer + 
+#                                  Error(SubjID / (Handling * Offer))))
+# 
+# ## NOTES ON RESULTS
+# # According to the logistic fit, there are main effects for all predictors, but no interactions.
 It also says that the overall odds for the wait group to accept versus the effort is around 16%.
@@
 ```
-
-The plot below shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and condition (optimal acceptance rate indicated by the gray triangles).
-Visually, the graph confirms a couple of important intuitions.
-First, as the handling time increases, the proportion of acceptances decreases.
-Second, this discounting did not affect the 20 cent offers, as is expected from the present foraging environment.
-Lastly, and similar to the previous point, as the value of the offers increases so does the willingness to accept a trial.
-Beyond these general features, it is clear that the cognitive effort group accepted more than the other groups, regardless of the combination of experimental parameters.
-Notably, the optimality of this greater acceptance rate is determined by the timing context (e.g.
-optimal at 2 second handling time, but detrimental at 14 seconds).
 
@@
 
-# prep data to plot the p(accept) based on reward, handling time and cost type
-trueProp <- dataBtw %>%
+# and plot
+(a1 <- dataBtw %>%
         filter(Choice < 2) %>%
@@
         summarise(meanComplete = mean(pAccept),
-                  SE = sd(pAccept) / sqrt(length(pAccept)))
-
-# and plot
-(a1 <- ggplot(data = trueProp, aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
+                  SE = sd(pAccept) / sqrt(length(pAccept))) %>%
+   ggplot(aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
         geom_point(size = 3) + 
@@
 
-```
-
-These intuitions were formally tested using a repeated measures ANOVA, whose results are presented in the table below.
+# snippet on rmANOVA
+# These intuitions were formally tested using a repeated measures ANOVA, whose results are presented in the table below.
 Overall, the analysis partially confirmed our predictions.
@@
 
+```
+
 ``` {r BTW: 16.2.2. rmANOVA table, pander}
-# anova table
-x <- summary(prop.aov)   
-x <- x$`Error: Within`
-panderOptions("digits", 2)
-pander(x, style = "rmarkdown", split.table = 110)
-```
-
-\bigskip
-
-### BTW: 16.2.3.
-
-*We will compute the probability of accepting a trial with a mixed-effects logistic regression.
-Based on the task structure and our main question, our a priori model of interest will include cost condition, handling time, and reward amount as fixed main effects, and subject ID as a random effect.
-Cost condition will be modeled with three categorical terms, with the fourth condition as the reference condition.
-We will run three versions of the model with different reference conditions, in order to test all pairwise differences among the four cost conditions.
-As with 16.2.2., we anticipate significant main effects (coefficients different than zero) of handling time, reward, and cost condition.
-We hypothesize that the differences among cost conditions will follow the pattern described in 4.2.*
+# # anova table
+# x <- summary(prop.aov)   
+# x <- x$`Error: Within`
+# panderOptions("digits", 2)
+# pander(x, style = "rmarkdown", split.table = 110)
+```
 
@@
 mixData <- dataBtw %>%
-  filter(Choice < 2) %>%
+  #filter(Choice < 2) %>% analysis performed on acceptances, not completions
   group_by(SubjID, Cost, Handling, Offer) %>%
@@
 
-# model with a random intercept and cost-type slope, then relevel the cost to get all pairwise comparisons
-# the correct way to model a logistic with proportions as dependent vars is by prividing n of hits and quits as a matrix
+# model with a random intercept, then relevel the cost to get all pairwise comparisons
+# the correct way to model a logistic with proportions as dependent vars is by providing n of hits and quits as a matrix
+# the pre-registered version has random intercepts per subject: (1 | SubjID) - So, for the SubjID grouping, get a random intercept (1)
+# or, for each subject, random intercept and slopes for handling and offer: (1 + Handling + Offer | SubjID)
+# one can add random H + R slopes for each Cost group with: (0 + Handling + Offer | Cost)
+# so far, the best qualitative and AIC-based fit comes from random HR slopes + intercept per subject, plus random HR slopes per cost group:  (1 + Handling + Offer | SubjID) + (0 + Handling + Offer | Cost)
+# though that produces warnings too
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_main$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Wait <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Cognitive <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
-mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Physical <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_main$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_main$Easy <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
@@
 ``` {r BTW: 16.2.3. Mixed Effects Model plot rand intercepts, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
-# plot random intercepts in increasing order
-#RI1 <- qplot(seq(83), sort(ranef(mixLogis_main$Wait)$SubjID[,1]), color = colsBtw[1], show.legend = F) + theme_classic()
-
-# # plot per subject (as expected, the intercepts are highest for those who accepted everythiing)
-# temp <- ranef(mixLogis_main$Wait)$SubjID %>%
-#   gather(key = Cost, value = RandEffects, colnames(.)) 
+# # random intercepts for each subject, with cost group and overall acceptances
+# RI <- ranef(mixLogis_main$Wait)$SubjID[, 1]
+# RI <- dataBtw %>% 
+#   group_by(SubjID, Cost) %>% 
+#   summarise(pAccept = mean(Choice)) %>% 
+#   ungroup() %>%
+#   mutate(RI = RI)
 # 
-# (RI1 <- ggplot(data = temp, aes(Cost, RandEffects, fill = Cost)) + 
-#   geom_hline(yintercept = 0, alpha = 0.7, linetype = "dashed") + 
-#   geom_boxplot(show.legend = F) +
-#   scale_fill_manual(values = colsBtw) + 
-#   labs(x = "") +
-#   theme(panel.grid.major = element_blank(), 
-#               panel.grid.minor = element_blank(), 
-#               panel.background = element_blank(), 
-#               axis.line = element_line(colour = "black"),
-#               text = element_text(size = 16)))
-
-```
-
-As predicted, the model showed significant main effects of handling time (Beta = `r mixLogis_main$Summary$coefficients[5,1]`, SE = `r mixLogis_main$Summary$coefficients[5,2]`, p < 0.001) and reward (Beta = `r mixLogis_main$Summary$coefficients[6,1]`, SE = `r mixLogis_main$Summary$coefficients[6,2]`, p < 0.001).
-In order to show the comparisons among all conditions, the following plot portrays the coefficients (color scale), and p-values (numbers within squares) that resulted from switching the reference condition.
-Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group.
-Based on this, we can see that the cognitive group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
-
-### BTW: 16.2.4.
-
-*Next, we will examine whether the a priori model from 16.2.3.
-outperforms both simpler and more complex models.
-Unlike the individual logistic regression fits in 16.1.1., a mixed-effects approach gives us a better goodness of fit measure for model comparisons.
-We will determine the best model (combination of predictors) using Akaike’s Information Criterion (AIC) to determine the model that minimizes the negative log-likelihood while penalizing the addition of parameters.
-The regression with each combination of predictors will be fitted in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) reward only; 5) condition, handling, and reward main effects (from 16.2.3.); 6) adding a handling-by-reward interaction; and 7) adding all three possible two-way interactions.
-We predict that model 5 will have the lowest AIC.*
+# # plot relationship between random intercept (RI) and proportion accepted per cost group
+# RI1 <- ggplot(data = RI, aes(RI, pAccept, color = Cost)) + 
+#   geom_vline(xintercept = 0, linetype = "dashed") +
+#   geom_smooth() + 
+#   geom_point(alpha = 0.5) + 
+#   scale_color_manual(values = colsBtw) +
+#   theme_classic()
+```
 
 ``` {r BTW: 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-# Quasibinomial GLM versions (with proper proportion setup)
+# relevel, since the wait-reference model is used from the previous section
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
+
+## model fitting
 mixLogis_compare <- list()
@@
 mixLogis_compare$Offer <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$HR <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + Handling + (1 | SubjID), family = "binomial", data = mixData)
 mixLogis_compare$AllMain <- mixLogis_main$Wait
-mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (Cost | SubjID), family = "binomial", data = mixData)
-
-# Model selection 
-abicLogis_compare <- data.frame(Model = names(mixLogis_compare),
+mixLogis_compare$HR_interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer * Handling + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ (Cost + Handling + Offer)^2 + (1 | SubjID), family = "binomial", data = mixData)
+
+## Model selection 
+# AIC/BIC
+ME_evals <- list()
+ME_evals$abicLogis_compare <- data.frame(Model = names(mixLogis_compare),
                                 AIC = sapply(mixLogis_compare, AIC),
@@
 
-# effect size
-mixLogis_compare$Rsq <- 1 - (deviance(mixLogis_compare$AllMain)/deviance(mixLogis_compare$Base)) # denominator is the null deviance
+# analysis of deviance for models with similar AIC
+ME_evals$HRvMain <- anova(mixLogis_compare$HR, mixLogis_compare$AllMain)
+ME_evals$MainvHRint <- anova(mixLogis_compare$AllMain, mixLogis_compare$HR_interaction)
+ME_evals$MainvAllint <- anova(mixLogis_compare$AllMain, mixLogis_compare$Interaction)
+
+# effect size for the main model
+mixLogis_compare$AllMainRsq <- 1 - (deviance(mixLogis_compare$AllMain)/deviance(mixLogis_compare$Base)) # denominator is the null deviance
 ```
@@
 # plot AIC and BIC
-(mixLogis_compare$plot <- abicLogis_compare %>% 
+(mixLogis_compare$plot <- ME_evals$abicLogis_compare %>% 
   gather(Comparison, Value, AIC:BIC) %>%
@@
 
-This plot shows the AIC for every model.
-The figure below shows AIC and BIC for all the models.
-As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`).
-The reduction in deviance from an intercept-only model was drastic enough that we did not compute an LRT.
-
-\bigskip
+  However, our hypothesis stated that differences in cost would be uniform across handling times and rewards.
+We therefore distilled the previous analysis to examine choice behavior for every combination of experimental parameters.
+Figure X shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and condition, with optimal acceptance rates depicted by the gray circles.
+Qualitatively, the figure confirms two important predictions.
+First, participants adapted to the richness of the each timing block, showing a pattern of acceptances that resembled the optimal strategy regardless of the cost they faced.
+Second, differences in cost were consistent across blocks, and acceptances were highest for the cognitive effort group.
+The optimality of the strategies produced by each cost depended on the richness of the block.
+This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
+  In order to test these qualitative observations, we computed the probability of accepting a trial with a mixed-effects logistic regression (see Methods for details).
+As predicted, and confirming previous results, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Handling", "Std.
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Offer", "Std.
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`).
+In order to show the comparisons among all conditions, Figure X portrays the coefficients (color scale **maybe exponentiated coefficients to make it more intuitive?**), and p-values (numbers within squares) that resulted from switching the reference cost condition.
+Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group.
+The matrix of coefficients conveys that the cognitive group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
+  We next examined whether choice behavior could be better explained by reward statistics alone, or if cost conditions changed the way handling time and offer amount interacted to influence choices.
+Figure X shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details).
+Here we focus on AIC, as both metrics yielded comparable results.
+As predicted, the a priori model with all main effects performed better than those which on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a priori~ = `r ME_evals$abicLogis_compare["AllMain", "AIC"]`, AIC~handling/reward~ = `r ME_evals$abicLogis_compare["HR", "AIC"]`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r ME_evals$HRvMain$Chisq[2]`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
+However, against our prediction, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR interaction~ = `r ME_evals$abicLogis_compare["HR_interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r ME_evals$MainvHRint$Chisq[2]`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all interactions~ = `r ME_evals$abicLogis_compare["Interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r ME_evals$MainvAllint$Chisq[2]`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
+These improvements were driven by the fact that differences in offer acceptances among costs were never present for 20 cents (all *p* values for interactions containing offer amount < 0.001).
+As the highest reward should always be accepted in prey foraging environments, we conclude that the most parsimonious explanation of choice behavior comes from the a priori model containing all main effects.
+In combination with the pattern observed in Figure X, these results confirm that handling and reward amounts were similarly integrated across groups, but that the rate of acceptances was affected by the cost faced (and highest for the cognitive effort group).
 

### 2020-04-01 Cost_manuscript.Rmd
darft of exp 1 results

@@
 title: Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment
-author: "Claudio Toro-Serey^1^2 & Joseph T. McGuire^1^2"
+author: "Claudio Toro-Serey^1,2 & Joseph T. McGuire^1,2"
 csl: apa.csl
@@
 
-```{r Setup, include = FALSE}
+```{r Setups, include = FALSE}
 ## libraries
@@
 library(corrplot)
+library(survival)
+library(ggfortify)
 
@@
 ## functions
+# parameter recovery function
+test_params <- function(params = list(Gamma = 1), model = expr(params$Gamma * Handling), subjData, handling = c(2, 10, 14), offer = c(4, 8, 20), plot = F) {
+
+  # this just computes choices made by a given parameterized model
+  # or compares a putative model with participant choices
+  #
+  # params: a list of parameters that can be called by the model (besides behavioral observations from subjData)
+  # model: must use expr() and call for extra parameters from params if needed (see default)
+  # subjData: optional data to be compared
+  # handling / offer: in case new experimental parameters should be tested (probably won't use)
+  # plot: T/F whether to plot the comparison between modeled and actual behavior
+  #
+
+  # if no subject data was provided, use the default options and only output the recovered data
+  if (missing(subjData)) {
+
+    # compute
+    df <- expand.grid(Handling = handling, Offer = offer) %>% 
+      mutate(OC = eval(model),
+             Choice = ifelse(Offer > OC, 1, 0))
+
+    # plot
+    if (plot) {
+
+      ggplot(data = df, aes(interaction(Offer, Handling), Choice, color = Gamma)) +
+        geom_line(aes(group = interaction(Handling, Gamma)), size = 1) +
+        geom_point(size = 3) +
+        labs(x = "Offer.Handling", y = "Proportion Accepted") +
+        facet_wrap(vars(Gamma), ncol = 2) +
+        theme(legend.key = element_blank(),
+              panel.grid.major = element_blank(),
+              panel.grid.minor = element_blank(),
+              panel.background = element_blank(),
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16))
+
+    }
+
+    # otherwise give a comparison between recovered and observed choice for a subject's data + gamma
+  } else {
+
+    # compute
+    df <- subjData %>% 
+      mutate(OC = eval(model),
+             Choice = ifelse(Offer > OC, 1, 0))
+
+    # plot
+    if (plot) {
+
+      print(ggplot(data = df) +
+        geom_line(aes(interaction(Offer, Handling), propAccept, group = Handling), size = 1, color = "darkgreen") +
+        geom_line(aes(interaction(Offer, Handling), Choice, group = Handling), size = 1, color = "blue") +
+        geom_point(aes(interaction(Offer, Handling), propAccept), size = 3, color = "darkgreen") +
+        geom_point(aes(interaction(Offer, Handling), Choice), size = 3, color = "blue") +
+        labs(x = "Offer.Handling", y = "Proportion Accepted") +
+        #scale_color_manual()
+        theme(legend.key = element_blank(),
+              panel.grid.major = element_blank(),
+              panel.grid.minor = element_blank(),
+              panel.background = element_blank(),
+              axis.line = element_line(colour = "black"),
+              text = element_text(size = 16)))
+    }
+
+  }
+
+  return(df)
+
+}
+
 # get the number of continuous quits before current trial
@@
   out$percentQuit <- mean(choice == 0) * 100
-  out$percentAccept <- mean(choice== 1) * 100 
+  out$percentAccept <- mean(choice == 1) * 100 
   miss <- (choice != 1) & (choice != 0)
@@
   # Begin defining parameters
-  # If choices are one-sided (i.e. all accepted)
+  # If choices are one-sided (i.e. all accepted), assign the upper or lower bound
   if ((sum(choice) == length(choice)) | (sum(choice) == 0)) {
     ifelse(sum(choice) == length(choice), out$Gamma <- exp(LB), out$Gamma <- exp(UB)) 
-    out$Scale <- 1 # it was NA, but in theory a temperature of 1 also indicates noiseless estimates, and allows for easier fit computations
+    out$temperature <- 1 # it was NA, but in theory a temperature of 1 also indicates noiseless estimates, and allows for easier fit computations
     out$LL <- 0
@@
     # Create a feasible region (search space)
-    params <- as.matrix(expand.grid(scale = c(-1, 1), gamma = seq(LB, UB, length = 3)))
+    params <- as.matrix(expand.grid(temperature = c(-1, 1), gamma = seq(LB, UB, length = 3)))
     # Create a list to check the minimization of the negative log lik.
@@
     out$Gamma <- exp(info$params[2])
-    out$Scale <- exp(info$params[1])
+    out$temperature <- exp(info$params[1])
     out$LL <- -info$negLL
@@
   out$LL0 <- log(0.5) * length(choice)
-  out$Rsquared <- 1 - (out$LL/out$LL0)
+  out$Rsquared <- 1 - (out$LL/out$LL0) # pseudo r-squred, quantifying the proportion of deviance reduction vs chance
   out$subjOC <- out$Gamma * handling
-  out$p <- 1 / (1 + exp(-(out$Scale*(reward - out$subjOC))))
+  out$probAccept <- 1 / (1 + exp(-(out$Scale*(reward - out$subjOC))))
   out$predicted <- reward > out$subjOC
@@
     out$Gamma <- exp(LB) # temporary condition because Nlopt is not respecting the lower bound
-    out$p <- rep(1, length(choice))
+    out$probAccept <- rep(1, length(choice))
   } else if (out$Gamma == exp(UB)) {
-    out$p <- rep(0, length(choice))
+    out$probAccept <- rep(0, length(choice))
   }
@@
 Participants were free either to accept or reject the cost/reward prospect offered on each trial.
-All participants were more likely to accept offers when rewards were higher and delays shorter, in line with a reward-maximizing strategy.
-Participants almost never reversed their acceptance decisions, and error rates in completing the effort requirement were low and decreased over time.
+All participants were more likely to accept offers when rewards were higher and delays shorter (in line with a reward-maximizing strategy), almost never reversed their acceptance decisions, and committed few errors while completing the effort requirements.
 When participants faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
-This could be because cognitive effort was directly rewarding, or because it modulated foraging-related factors such as the perceived duration of delays or the estimated richness of the environment.
 We theorized that if cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards.
@@
 ## Introduction
+
+Effort is costly, but sometimes it can add value.
+In thinking about this, studies have focused on TAFC.
+We have learned much about this (show data), but two issues: 1) many studies compare costs by comparing discounting functions, which is helpful, but 2) an often disregarded aspect of this is OC.
+Even in tafc, a choice for a sooner or easier item can be a reflection of wanting to skip the offer altogether.
+Foraging provides a natural way to probe this.
+Foraging is often divided into two: patch and prey, and they are often experienced in daily life.
+Patch leaving can be deciding when to leave a job (diminishing gains).
+Prey can be X, or nerflix (show gif).
+
+So going back to our question of the cost and value of effort, maybe the distinction has something to do with the ways in which we can allocate time and effort (work on this, including how foraging can provide a reference point to evaluate the value-modulatory effects of demands, and maybe put it before foraging is explained?).
+
+In this talk, I'll show you how we'veused this framework to understand the inherent (elaborate on inherent above) and relative costly nature of effort and delay.
+I'll focus on behavioral findings, and I'll give a nudge to modeling.
+Then I'll discuss how we plan to understand the brain networks that characterize this behavior, with a focus on individual differences.
 
@@
 We added an extra group of 21 participants who experienced a minimally effortful condition in order to determine whether effort or pure engagement were driving our results.
+
 	We excluded participant datasets based on four preregistered criteria: 1) Consent: If they withdrew their participation; 2) Inattentiveness: a catch trial was placed at the end of each experimental block, asking participants to press a key within 3 seconds (time requirement based on pilot study response times).
@@
 Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive ones of each kind.
+
   Each participant was assigned to one of these types of costs (cognitive effort, physical effort, or delay), and a fourth group of equal size faced an effortless physical task that involved minimal gripping.
@@
 If participants failed to maintain above-threshold gripping or made two mistakes during the cognitive task, they were forced to travel and missed the reward.
+
   There were three block types, in which handling times of 2, 10, or 14 seconds were paired with travel times of 14, 6, and 2 seconds, respectively (note that all combinations add up to 16 seconds).
@@
 Coefficients significantly different from 0 denoted that a participant relied on recent quitting history.
+
 	Our foraging task was configured such that over and under accepting were detrimental to total earnings.
@@
 Next, to determine the optimality of each group’s decisions, performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost above).
-This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR) **CHANGE TO COST3 APPROACH.**
+This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR).
+**MAYBE CHANGE TO COST3 APPROACH?**
+
   Next, we compared preferences among cost conditions.
@@
 We then compared the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests).
+On each of 5000 permutation iterations, the group assignment was randomly shuffled without replacement, and the difference in mean acceptance rates across iterations created a putative null distribution.
+The unpermuted group mean difference was then evaluated against this permuted distribution.
 The same approach was used for total earnings.
@@
 We used both Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
-The regression with each combination of predictors was fitted in the following order: 1) intercept only; 2) cost type only; 3) handling time only; 4) reward only; 5) condition, handling, and reward main effects (a priori model); 6) adding a handling-by-reward interaction; and 7) adding all three possible two-way interactions.
+The regression with each combination of predictors was fitted in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
 We predicted that model 5 would have the lowest AIC.
+Nested models with similar AIC were statistically compared using an analysis-of-deviance.
+The significance test was computed as the probability of the reduction in deviance, based on a chi-square distribution with degrees of freedom equal to the difference in the number of parameters between models.
+
   Finally, we modeled the subjective opportunity cost in each condition.
@@
 that the reward amounts they accepted in a given timing condition would be similar throughout the experiment).
-This prediction was made because participants had full knowledge of the environment.
-We computed each participant’s total proportion of acceptances pre- and post-midpoint for every block.
-For each cost condition separately, we will fit a linear model that predicts post-midpoint acceptance from before-midpoint rates.
-We will report the slopes and 95% confidence intervals (CI) for each cost group.
-CIs containing 1 will denote that participants in that group produced consistent choices (CHANGE TO COST3 APPROACH, PERMUTATION).
+We computed each participant’s total proportion of acceptances pre- and post-midpoint for every block, and performed paired permutations (5000) on the mean proportion of acceptances.
+We then confirmed that the relative costs observed with from the whole experimental session were still present on each half of the experiment.
+The winning model from the mixed-effects logistic comparison was applied to each half separately.
+In each case the reference cost category was rotated in order to assess pairwise differences among all costs.
+We evaluated the consistency of the relative costs by visually comparing the patterns of significant differences between experimental halves.
+
   Once we established choice stability, we proceeded to estimate the subjective OC of each type of demand (see Operationalization of Cost above).
-OC were computed as the product of a free parameter (gamma) and the handling time.
+OC was computed as the product of a free parameter (gamma) and the handling time.
+Gamma can be interpreted as the subjective value of each second spent in an environment.
+If a trial's reward rate (i.e.
+offer amount divided by the handling time) fell below gamma, a participant was better off finding more profitable alternatives.
+In other words, individuals with higher gammas required higher rewards in order to accept a given offer.
 We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type
@@
   Both gamma and the temperature parameter of the softmax function were estimated independently for each subject, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE).
+The gamma optimization search space was bound by extreme choice values.
+For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
+Conversely, a participant experiencing low opportunity costs would accept the non-beneficial offer of 4 cents for a 14 second delay (or 4/14).
 We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
@@
 This let us determine which cost type produced the highest discounting.
-(ADD ADDITIONAL MODELS FROM LITERATURE)
+**ADD ADDITIONAL MODELS FROM LITERATURE**
 
@@
 
-### Analyses
+### Analyseses
 
@@
 Therefore, a significant difference indicated that participants either over or under accepted rewards.
+
   To compare acceptance rates among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
-The model included cost condition and reward amount as fixed main effects, and subject ID as a random effect.
+The model included cost condition and reward amount as fixed main effects, and subject ID as a random effect (handling time is not modeled, as participants experienced a single time combination).
 Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
 We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions.
-Next, we compared this model to both simpler and more complex models using Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC).
-We added varied model complexity in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
-We predicted that model 6 would have the last considerable decrease in the negative log-likelihood.
-Nested models with similar AIC were statistically compared using an analysis-of-deviance.
-The significance test was computed as the probability of the reduction in deviance, based on a chi-square distribution with degrees of freedom equal to the difference in the number of parameters between models.
+We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity in the following order: 1) intercept only; 2) condition only; 3) reward only; 4) condition and reward main effects (a priori model); and 5) adding a two-way interaction.
+We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
+Models with similar AIC were formally compared using the analysis-of-deviance approach from the between-subjects experiment.
+
   Next we probed the confidence and consistency with which participants made choices.
@@
 We then computed each participant’s total proportion of acceptances on the first two and last two blocks, and compared them using a paired permutation analysis (5000 iterations).
-  To estimate the subjective opportunity cost of each condition, we will use a logistic function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
-OC will be computed as the product of a free parameter (gamma) and the handling time.
-Both gamma and the temperature parameter of the logistic function will be estimated at the subject level, independently for each subject and cost type.
+  **adapt once we decide on the model candidates**To estimate the subjective opportunity cost of each condition, we used a logistic function to model each participant’s probability of accepting a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
+As before, OC was computed as the product of a free parameter (gamma) and the handling time.
+Both gamma and the temperature parameter of the logistic function were estimated at the subject level, independently for each subject and cost type.
 We cross-validated each subject’s OC value using the first four blocks (two cognitive, two physical) for estimation, and the last two blocks (one of each effort type) choices for testing.
 The estimates were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each cost type.
-The OC estimates for each group will be compared using a repeated measures ANOVA with cost as a factor.
-We will perform pairwise paired permutations as post-hoc tests.
-This will let us determine which cost type produced the highest discounting.
+The OC estimates for each group were compared using a repeated measures ANOVA with cost as a factor.
+We performed pairwise paired permutations as post-hoc tests.
 
@@
 Specifically, we predicted that participants confronted with cognitive demands would be more likely to accept trials than those faced with physical effort and delay, regardless of handling time and reward amount.
+
   To address the first hypothesis, we first confirmed that increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively.
@@
 This indicates that offer patterns did not influence participant behavior.
+
   **Maybe put this as an addendum to the mixed effects analysis of proportion of acceptances, after mixed models** .
@@
         geom_boxplot(show.legend = F) +
+        geom_jitter(width = 0.1, alpha = 0.3, show.legend = F) +
         scale_fill_manual(values = colsBtw) +
@@
 grid.arrange(p1, p2, ncol = 2)
+
+# Proportion of performance-based forced travels per subject and cost type
+# move to 16.2.1.
+propFails <- dataBtw %>% 
+  filter(Cost != "Wait") %>% 
+  group_by(SubjID, Cost) %>% 
+  summarise(propFails = mean(rawChoice == 2)) %>%
+  group_by(Cost) %>% 
+  summarise(meanFT = mean(propFails),
+            sdFT = sd(propFails))
+
+## MAYBE BETTER WAY TO DO PAIRWISE COMPARISONS, USING VECTORIZE FROM BELOW
+# OCanova$perms <- summaryOC$all %>%
+#   select(Cost, Gamma) %>%
+#   plyr::dlply("Cost", identity) %>%
+#   do.call(cbind, .) %>%
+#   select_if(is.numeric) %>%
+#   rename(Physical = Physical.Gamma,
+#          Cognitive = Cognitive.Gamma,
+#          Wait = Wait.Gamma,
+#          Easy = Easy.Gamma) %>%
+#   outer(., ., FUN = Vectorize(permute), simple = T)
+# diag(OCanova$perms) <- 1
+
 ```
@@
 One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
-We then performed post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs.
-On each iteration the group assignment was randomly shuffled without replacement, and the difference in mean acceptance rates across iterations created a putative null distribution.
-The unpermuted group mean difference was then evaluated against this permuted distribution.
-This analysis confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdProp)`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Physical < Cognitive") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Cognitive > Wait") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait") %>% select(cohenD)`).
+Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdProp)`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Physical < Cognitive") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Cognitive > Wait") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait") %>% select(cohenD)`).
 It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Wait < Easy") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy") %>% select(cohenD)` (all other *p* > 0.05).
+The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants (and 0 for either physical or easy conditions), making performance an unlikely explanation for the observed differences in choice.
+
   We repeated these pairwise permutation to identify differences in earnings.
@@
 This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
+
   In order to test these qualitative observations, we computed the probability of accepting a trial with a mixed-effects logistic regression (see Methods for details).
@@
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`).
-In order to show the comparisons among all conditions, Figure X portrays the coefficients (color scale **maybe exponentiated coefficients to make it more intuitive?**), and p-values (numbers within squares) that resulted from switching the reference cost condition.
+In order to show the comparisons among all conditions, Figure X portrays the coefficients (color scale **maybe exponentiated coefficients to make it more intuitive?**), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
 Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group.
-The matrix of coefficients conveys that the cognitive group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
-  We next examined whether choice behavior could be better explained by reward statistics alone, or if cost conditions changed the way handling time and offer amount interacted to influence choices.
+The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
+
+  We next examined whether choice behavior could be better explained by environmental statistics alone, or if cost conditions changed the way handling time and offer amount interacted to influence choices.
 Figure X shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details).
 Here we focus on AIC, as both metrics yielded comparable results.
-As predicted, the a priori model with all main effects performed better than those which on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a priori~ = `r ME_evals$abicLogis_compare["AllMain", "AIC"]`, AIC~handling/reward~ = `r ME_evals$abicLogis_compare["HR", "AIC"]`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r ME_evals$HRvMain$Chisq[2]`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
-However, against our prediction, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR interaction~ = `r ME_evals$abicLogis_compare["HR_interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r ME_evals$MainvHRint$Chisq[2]`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all interactions~ = `r ME_evals$abicLogis_compare["Interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r ME_evals$MainvAllint$Chisq[2]`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
+As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a_priori~ = `r ME_evals$abicLogis_compare["AllMain", "AIC"]`, AIC~handling/reward~ = `r ME_evals$abicLogis_compare["HR", "AIC"]`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r ME_evals$HRvMain$Chisq[2]`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
+However, against our prediction, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r ME_evals$abicLogis_compare["HR_interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r ME_evals$MainvHRint$Chisq[2]`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r ME_evals$abicLogis_compare["Interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r ME_evals$MainvAllint$Chisq[2]`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
 These improvements were driven by the fact that differences in offer acceptances among costs were never present for 20 cents (all *p* values for interactions containing offer amount < 0.001).
 As the highest reward should always be accepted in prey foraging environments, we conclude that the most parsimonious explanation of choice behavior comes from the a priori model containing all main effects.
-In combination with the pattern observed in Figure X, these results confirm that handling and reward amounts were similarly integrated across groups, but that the rate of acceptances was affected by the cost faced (and highest for the cognitive effort group).
+In combination with the pattern observed in Figure X, these results confirm that handling and reward amounts were similarly integrated across groups, but that the absolute rate of acceptances was affected by the cost faced (and was highest for those confronted with cognitive demands).
 
@@
 
-### BTW: 16.3.1.
-
-*Response times (RT) for quit responses will be presented in a descriptive manner in order to examine whether participants tended to quit early or late within individual trials.
-Each cost group’s response time distribution will contain the pooled RT across its corresponding participants, and we will display the empirical cumulative distribution functions for each condition.
-Short RT would suggest confident and stable decisions (in support of 4.3.1.).*
-
-``` {r BTW: 16.3.1. RTs, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-# Proportion of forced travels per subject and cost type
-propFails <- dataBtw %>% 
-  filter(Cost != "Wait") %>% 
-  group_by(SubjID, Cost) %>% 
-  summarise(propFails = mean(rawChoice == 2)) %>%
-  group_by(Cost) %>% 
-  summarise(meanFT = mean(propFails),
-            sdFT = sd(propFails))
-
-# this version of a survival curve forces all successful acceptances to have an RT of 14
-library(survival)
-library(ggfortify)
-
+``` {r BTW: 16.3.1. RTs, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# qualitative survival analysis
+# this version of a survival curve forces all successful acceptances to have an RT of 14 (i.e. the longest handling time)
 # that's to avoid jumps from 2s to 10s to 14s
@@
 
-autoplot(survData) +
+survPlot <- autoplot(survData) +
   geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
@@
   labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
-  theme(legend.position = c(0.3, 0.2),
+  theme(legend.position = c(0.35, 0.25),
         panel.grid.major = element_blank(),
@@
         axis.line = element_line(colour = "black"),
-        text = element_text(size = 22))
-
+        text = element_text(size = 16))
+
+# supplemental
 # RT ecdfs for the whole group across blocks, with the option to subdivide by cost group
-dataBtw %>%
+RTplot <- dataBtw %>%
   filter(Choice == 0,
@@
     stat_ecdf() +
-    #facet_wrap(vars(Cost)) +
+    labs(y = "Proportion of Quits Before Time X", x = "Quitting Time") +
+    facet_wrap(vars(Cost)) +
     theme_classic()
 
-```
-
-The survival curve below shows instances of quiting across a trial for all participants and handling times.
-Censors signal completed trials and forced quits, so most occur at the end of the three possible handling times.
-Participants could only quit once the trial begun.
-This shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
-The reason why the physical and easy condition show slightly lagged responses is that the experiment allowed a one second grace period for participants to begin gripping (marked by the dashed line).
-This resulted in some of them choosing to wait for that second to indicate an offer rejection.
-The proportion of forced quits for cognitive effort was `r round(propFails[2, 2], digits = 2)`, and 0 for the physical conditions (the censor around 4s in the physical condition was an acceptance during 2s handling that was incorrectly recorded at 4s by the experimental code).
-
-\bigskip
-
-### BTW: 16.3.2.
-
-*In order to further examine choice stability (hypothesis 4.3.1.), we will compute each participant’s total proportion of acceptances pre- and post-midpoint.
-For each cost condition separately, we will fit a linear model that predicts post-midpoint acceptance from before-midpoint rates.
-We will report the slopes and 95% confidence intervals (CI) for each cost group.
-CIs containing 1 will denote that participants in that group produced consistent choices.*
-
-``` {r BTW: 16.3.2. Pre/Post Break, echo=FALSE,fig.align="center",fig.width=5,fig.height=5}
-# divide the data into proportion accepted before/after the break (one per column)
-temp <- dataBtw %>%
-  filter(Choice < 2) %>%
-  group_by(SubjID, Cost, Half) %>%
-  summarise(pAccepted = mean(Choice)) %>%
-  ungroup() %>%
-  spread(Half, pAccepted)
-
-# separate by cost type and compute a linear model to predict half 2 from 1
-sep <- temp %>% plyr::dlply("Cost", identity)
-prepost <- list()
-prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})
-
-# get the coefficients and confidence intervals
-# and concatenate
-prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
-colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
+grid.arrange(survPlot, RTplot, ncol = 2)
+
+```
+
+``` {r BTW: 16.3.2. Pre/Post Break, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
+# # divide the data into proportion accepted before/after the break (one per column)
+# temp <- dataBtw %>%
+#   filter(Choice < 2) %>%
+#   group_by(SubjID, Cost, Half) %>%
+#   summarise(pAccepted = mean(Choice)) %>%
+#   ungroup() %>%
+#   spread(Half, pAccepted)
+#
+# # separate by cost type and compute a linear model to predict half 2 from 1
+# sep <- temp %>% plyr::dlply("Cost", identity)
+# prepost <- list()
+# prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})
+# 
+# # get the coefficients and confidence intervals
+# # and concatenate
+# prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
+# colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
 
@@
 # paired perms and effect sizes
+prepost <- list()
 prepost$CohenD <- sapply(temp, function(data) {DescTools::CohenD(data$propAccept_1, data$propAccept_2)})
@@
 
-The plot below shows that acceptance rates before and after the mid-point were mostly consistent, although it was more likely for participants to accept less in the second half of the experiment.
-**NOTE: The lines of means in the scatterplot are calculated by first computing the mean acceptances per block, then averaging those for blocks pre/post break.
-That's how they match the second half of the right plot, but the linear model is computed with the overall proportion acceptances pre-post, which gives slightly different mean estimates (which is also the reason for slight mean differences in proportion accepted between these and the boxplot in 16.2.1.)**
-
 ``` {r BTW: 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
 # scatter plot of pre/post acceptances
-# BIG CAVEAT: THE 
 # first calculate the mean acceptances per cost/half to draw horizontal and vertical lines on the plot
@@
                          ggplot(aes(Block, propAccept, color = Cost)) +
+                           geom_vline(xintercept = 3.5, linetype = "dashed") +
                            geom_point(size = 2) +
@@
 
-The following table shows the coefficients and CI for each linear model, and show that pre-post acceptance rates were very similar for each condition (i.e.
-one is present in all confidence intervals).
-Note that interpreting the coefficients depends on the intercept, and the wait condition had a relatively high intercept.
-
-A better test is to perform a pairwise comparison between halves per cost type.
-Paired permutations on means of proportions showed no differences for wait and easy groups (p > 0.5), but significantly lower acceptance rates for physical (*p* = `r prepost$Perms[1]`, Cohen's D = `r prepost$CohenD[1]`) and cognitive (*p* = `r prepost$Perms[2]`, Cohen's D = `r prepost$CohenD[2]`) groups.
-These results are more consistent with the plots above.
-
-``` {r BTW: 16.3.2. prepost table, pander}
-panderOptions("digits", 2)
-pander(prepost$summary, style = "rmarkdown", split.table = 110)
-```
-
-Now let's divide them by reward and handling amounts. The plots below show that the overall rates of acceptances remain mostly consistent across first and second halves of the experimental session.
+``` {r BTW: 16.3.2. prepost lm table, pander}
+# panderOptions("digits", 2)
+# pander(prepost$summary, style = "rmarkdown", split.table = 110)
+```
+
+  Before computationally modeling behavior, we asked whether foragers had a stable representation of their environment.
+Since participants had complete a priori knowledge of the statistics of each environment, and were unaware of any other cost groups that could modulate the subjective cost of their assigned demand, we expected them to 1) show confidence in their choices by not quitting mid-handling time; and 2) adopt the same strategy while re-experiencing each environment.
+We investigated the first prediction by plotting a survival curve of trial quits across all participants (Figure X, left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
+This qualitative analysis shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
+Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
+This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code).
+Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure X, right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed (note that participants in physical conditions mostly relied on letting the grace period expire).
+These response time observation  s suggest clarity in participant preferences.
+
+  We next examined the second prediction (i.e.
+strategy stability) by comparing acceptances rates throughout the experiment.
+The scatter plot on Figure X shows the overall proportion accepted by each participant before and after the mid-point break (colored dashed lines indicate the mean for that group).
+Paired permutations on means of proportions showed no differences for wait and easy groups (*p* > 0.05), but significantly lower acceptance rates for physical (*p* = `r report_p(prepost$Perms[1])`, Cohen's D = `r round(prepost$CohenD[1], digits = 2)`) and cognitive (*p* = `r report_p(prepost$Perms[2])`, Cohen's D = `r round(prepost$CohenD[2], digits = 2)`) groups.
+The decline in acceptances appeared to be gradual for the cognitive group, but not for the physical group (Figure X, half point indicated by the dashed line).
+An explanation for these results is that these conditions became costlier due to fatigue, thus providing evidence that our cognitive and physical manipulations were effortful.
+
+  It is possible that this reduction in acceptances affected the relative differences among conditions.
+We addressed this possibility by examining pre-post acceptance rates for each handling time and reward combination.
+Figure X shows the proportion of acceptances for each offer combination, with each half depicted on each column.
+This collage suggests that changes in choice behavior for effortful groups were mostly driven by the longest handling time, perhaps because of the fatigue suggested above.
+Regardless, the relative differences in acceptances among cost groups remain mostly untouched.
+We tested this observation by repeating the winning mixed-effects model from the previous section (i.e.
+all main effects) on each experimental half separately.
+We replicated the matrix of coefficients from the previous section, with each half mirrored along the diagonal (i.e.
+the top triangle shows the coefficients for the second half of the experiment).
+Together, these results suggest that decision makers had a strong representation of the environment by showing that 1) participants were confident in their choices and strategies; 2) cognitive and physical costs produced the expected fatigue from exerting effort; and 3) despite the resulting reduction of acceptances, the relative cost of each condition was consistent throughout the experiment.
 
 ``` {r BTW: 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
-# # pre
-# t1 <- dataBtw %>%
-#   filter(Choice < 2, Half == "Half_1") %>%
-#   group_by(SubjID) %>%
-#   filter(Handling == 10) %>%
-#   group_by(SubjID, Cost, Offer) %>%
-#   summarise(pAccept = mean(Choice)) %>%
-#   group_by(Cost, Offer) %>%
-#   summarise(propAccept = mean(pAccept),
-#             SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
-#   ungroup() %>%
-#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-#   ggplot(aes(Offer, propAccept, color = Cost)) +
-#     geom_point(size = 3, show.legend = F) +
-#     geom_line(show.legend = F) +
-#     scale_color_manual(values = colsBtw) +
-#     scale_fill_manual(values = colsBtw) +
-#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
-#     scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
-#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-#     labs(y = "Proportion Accepted", title = "First Half") +
-#     theme(legend.key = element_blank(),
-#           legend.position = c(0.8, 0.25),
-#           panel.grid.major = element_blank(), 
-#           panel.grid.minor = element_blank(), 
-#           panel.background = element_blank(), 
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 16))
-# 
-# # post half
-# t2 <- dataBtw %>%
-#   filter(Choice < 2, Half == "Half_2") %>%
-#   group_by(SubjID) %>%
-#   filter(Handling == 10) %>%
-#   group_by(SubjID, Cost, Offer) %>%
-#   summarise(pAccept = mean(Choice)) %>%
-#   group_by(Cost, Offer) %>%
-#   summarise(propAccept = mean(pAccept),
-#             SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
-#   ungroup() %>%
-#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-#   ggplot(aes(Offer, propAccept, color = Cost)) +
-#     geom_point(size = 3, show.legend = F) +
-#     geom_line(show.legend = F) +
-#     scale_color_manual(values = colsBtw) +
-#     scale_fill_manual(values = colsBtw) +
-#     geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
-#     scale_y_continuous(limits = c(-0.1, 1.1), breaks = c(0, 0.5, 1)) +
-#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-#     labs(y = "", title = "Second Half") +
-#     theme(legend.position = c(0.8, 0.2),
-#           panel.grid.major = element_blank(), 
-#           panel.grid.minor = element_blank(), 
-#           panel.background = element_blank(), 
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 16))
-# 
-# 
-# 
-# grid.arrange(t1, t2, ncol = 2)
-
-dataBtw %>%
-  filter(Choice < 2) %>%
+# this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
+(prepostPlot <- dataBtw %>%
   group_by(SubjID) %>%
-  filter(Handling == 10) %>%
-  mutate(Half = ifelse(Half == "Half_1", "First Block", "Last Block")) %>%
-  group_by(SubjID, Half, Cost, Offer) %>%
+  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half")) %>%
+  group_by(SubjID, Half, Handling, Cost, Offer) %>%
   summarise(pAccept = mean(Choice)) %>%
-  group_by(Half, Cost, Offer) %>%
+  group_by(Half, Cost, Handling, Offer) %>%
   summarise(propAccept = mean(pAccept),
@@
     labs(y = "Proportion Accepted") +
-    facet_wrap(vars(Half), ncol = 2) +
+    facet_wrap(vars(Handling, Half), ncol = 2) +
     theme(legend.key = element_blank(),
-          legend.position = c(0.9, 0.25),
+          #legend.position = c(0.9, 0.25),
           panel.grid.major = element_blank(), 
@@
           axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
-
-```
-
-This prompted the question of whether fitting the mixed logistic model could confirm this shift in preferences.
-Just as before, the matrix below show the coefficient magnitude (color) and pvalues for differences based on iterating through costs as reference dummy codes.
+          text = element_text(size = 16)))
+
+```
 
@@
 
-mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
@@
 
-mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_post$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_post$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_post$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_post$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (Cost | SubjID), family = "binomial", data = mixData)
+mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
@@
 
-\bigskip
-
-### BTW: 16.3.3.
-
-*To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
-OC will be computed as the product of a free parameter (gamma) and the handling time.
-Both gamma and the temperature parameter of the logistic function will be estimated at the subject level, independently for each subject.*
-
-``` {r BTW: 16.3.3. OC modeling, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-# group
+``` {r BTW: 16.3.3. OC modeling, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+## fit the OC model
 summaryOC <- list()
 summaryOC$all <- dataBtw %>%
-                 #filter(rawChoice < 2) %>%
                  group_by(Cost, SubjID) %>%
@@
 
-# plot
+## plot
 (summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
-                      geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
-                      geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
-                      geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-                      geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
+  # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
+  # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
+  # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
+  geom_hline(yintercept = 0.74, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
+  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
+  geom_boxplot(show.legend = F) +
+  geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
   ylim(0,1.5) +
@@
 
-```
-
-The gamma optimization search space was bound by extreme choice values.
-For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
-Conversely, a participant experiencing low opportunity costs would accept the unbeneficial offer of 4 cents for a 14 second delay (or 4/14).
-The model was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood (R-squared: mean = `r mean(summaryOC$all$Rsquared)`, SD = `r sd(summaryOC$all$Rsquared)`).
-The resulting gamma values per participant are shown per group below (gray lines denote the rate of earnings under optimal behavior for all 3 timing contexts), and reflect what was seen in the previous sections: participants in the wait and physical conditions showed higher gamma values (and thus opportunity costs) than in the other two groups.
-Given the high variability of the easy condition, it might be worth modeling each timing context independently, or perhaps fitting the model on subgroups defined by a median split of the participants based on their acceptance rate.
-
-\bigskip
-
-### BTW: 16.3.4.
-
-*We will cross-validate each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-The estimates will be used to predict acceptances in the testing sample, and the mean percent correctly predicted will be reported for each group.
-This will also provide information on the stability of each participant’s choices (4.3.1.).*
-
-As can be seen below, the gamma parameter from the OC model was able to predict post-midpoint choices successfully regardless of group.
-
-``` {r BTW: 16.3.4. OC cross-validation, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
-# Compute the OC for pre-midpoint
-summaryOC$pre <- dataBtw %>%
-                 filter(Half == "Half_1") %>%
-                 group_by(Cost, SubjID) %>%
-                 do(optimizeOCModel(., simplify = T)) %>%
-                 ungroup() %>%
-                 select(SubjID, Gamma)
-
-# let's add the gammas to the second half data and estimate prop predicted on the second half
-summaryOC$predicted <- dataBtw %>%
-                 filter(Half == "Half_2") %>%
-                 group_by(Cost, SubjID) %>%
-                 left_join(summaryOC$pre) %>%
-                 mutate(OC = Handling * Gamma,
-                        predicted = Offer > OC) %>% 
-                 summarise(percentPredicted = mean(predicted == Choice) * 100)
-
-# plot
-(summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
-                            labs(x = "") +
-                            geom_boxplot(show.legend = F) +
-                            scale_fill_manual(values = colsBtw) +
-                            labs(y = "Percent Predicted") +
-                            ylim(0,100) +
-                            theme(panel.grid.major = element_blank(),
-                            panel.grid.minor = element_blank(),
-                            panel.background = element_blank(),
-                            axis.line = element_line(colour = "black"),
-                            text = element_text(size = 16)))
-
-```
-
-\bigskip
-
-### BTW: 16.3.5.
-
-*The OC estimates for each group will be compared using an ANOVA with condition as a factor. This will let us determine which cost type produced the highest discounting.*
-
-``` {r BTW: 16.3.5. OC comparisons, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+## one sample t against optimal strategy
+summaryOC$t.test <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  sapply(., function(data) {t.test(data$Gamma, mu = 0.74)})
+
+## descriptive stats
+summaryOC$descriptives <- summaryOC$all %>%
+  group_by(Cost) %>%
+  summarise(mGamma = round(mean(Gamma), digits = 2),
+            sdGamma = round(sd(Gamma), digits = 2))
+
+# summaryOC$all %>%
+#   ggplot(aes(Gamma, percentAccept, fill = Cost, size = temperature)) +
+#   geom_point(pch = 21)
+
+# # gamma parameter recovery tests
+# # test a single subject against their own choices
+# (subj <- sample(subjList_btw, 1))
+# subjData <- dataBtw %>% 
+#   filter(SubjID == subj) %>% 
+#   group_by(Cost, Handling, Offer) %>% 
+#   summarise(propAccept = mean(Choice)) %>%
+#   ungroup()
+# 
+# params <- filter(summaryOC$all, SubjID == subj) %>% 
+#   select(Gamma, temperature)
+# 
+# test_params(params,
+#             model = expr(params$Gamma * Handling), 
+#             subjData, 
+#             plot = T)
+
+# # test multiple values of gamma and plot the comparison
+# lowGamma <- 0
+# upperGamma <- 1.7
+# nGamma <- 6
+# testys <- lapply(seq(lowGamma, upperGamma, length.out = nGamma), test_params)
+# (testys <- do.call(rbind, testys))
+# testys %>%
+#   ggplot(aes(interaction(Offer, Handling), Choice, color = Gamma)) +
+#   geom_point(size = 3) +
+#   geom_line(aes(group = interaction(Handling, Gamma)), size = 1) +
+#   labs(x = "Offer.Handling", y = "Proportion Accepted") +
+#   facet_wrap(vars(Gamma), ncol = 2) +
+#   theme(legend.key = element_blank(),
+#         panel.grid.major = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.background = element_blank(),
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 16))
+
+```
+
+``` {r BTW: 16.3.5. OC comparisons, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
 # ANOVA
@@
 OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC$all))
-Fval <- OCanova$aov[[1]]$`F value`[1]
+Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
 Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
@@
 
-The analysis of variance was significant (F = `r round(Fval, digits = 2)`, p = `r ifelse(Pval < 0.001, "< 0.001", paste("=", round(Pval, digits = 2)))`, R-squared = `r Rsquared_aov`).
-Pairwise post-hoc permutations are shown in the following matrix.
-These results suggest that participants engaged in cognitively effortful demands experience significantly lower opportunity costs than those whose demands involve physical effort and pure delay.
-The reason for this is unclear, and we will work on it in the near future.
-
-``` {r BTW: 16.3.5. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
-# plot all pairwise comparisons
-corrplot(OCanova$ES,
-         is.corr = F, 
-         p.mat = OCanova$perms,
-         type = "upper",
-         insig = "p-value",
-         sig.level = -1,
-         na.label = "square",
-         na.label.col = "grey",
-         method = "color", 
-         tl.col = "black", 
-         tl.cex = 0.8,
-         outline = T)
-```
-
-\bigskip
-
-
-\newpage
+``` {r BTW: 16.3.5. corrplot, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
+# # plot all pairwise comparisons
+# corrplot(OCanova$ES,
+#          is.corr = F, 
+#          p.mat = OCanova$perms,
+#          type = "upper",
+#          insig = "p-value",
+#          sig.level = -1,
+#          na.label = "square",
+#          na.label.col = "grey",
+#          method = "color", 
+#          tl.col = "black", 
+#          tl.cex = 0.8,
+#          outline = T)
+```
+
+``` {r BTW: 16.3.4. OC cross-validation, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# Compute the OC for pre-midpoint
+summaryOC$pre <- dataBtw %>%
+                 filter(Half == "Half_1") %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup() %>%
+                 select(SubjID, Gamma)
+
+# let's add the gammas to the second half data and estimate prop predicted on the second half
+summaryOC$predicted <- dataBtw %>%
+                 filter(Half == "Half_2") %>%
+                 group_by(Cost, SubjID) %>%
+                 left_join(summaryOC$pre) %>%
+                 mutate(OC = Handling * Gamma,
+                        predicted = Offer > OC) %>% 
+                 summarise(percentPredicted = mean(predicted == Choice) * 100) %>%
+                 group_by(Cost) %>%
+                 summarise(mPredicted = round(mean(percentPredicted), digits = 2),
+                           sdPredicted = round(sd(percentPredicted), digits = 2))
+
+# # plot
+# (summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
+#                             labs(x = "") +
+#                             geom_boxplot(show.legend = F) +
+#                             scale_fill_manual(values = colsBtw) +
+#                             labs(y = "Percent Predicted") +
+#                             ylim(0,100) +
+#                             theme(panel.grid.major = element_blank(),
+#                             panel.grid.minor = element_blank(),
+#                             panel.background = element_blank(),
+#                             axis.line = element_line(colour = "black"),
+#                             text = element_text(size = 16)))
+
+```
+
+  We then proceeded to estimate subjective OCs for each participant, which was produced by multiplying the handling time and a free parameter gamma (see Methods for details).
+Gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+For example, the aversion produced by a given cost could prompt participants to spend their time and effort in the most profitable offers, resulting in high gamma values.
+Conversely, low gamma values represented low selectivity when evaluating offers.
+The model predicted the probability of a choice by comparing the estimated OC against each offer amount, and was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
+This single parameter model was able to explain a considerable degree of choice variance (R-squared: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
+The distribution of gamma values are shown on Figure X, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
+Values higher than this baseline imply that a condition was costly, whereas lower values suggest that a condition boosted the value of an offer.
+Two-sided one-sample t.test against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
+Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
+An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, R-squared = `r Rsquared_aov`).
+Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (`r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (`r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (`r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
+In addition, the easy group displayed significantly lower gamma values than the wait group (`r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
+Finally, we cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+
+  Together, these findings suggest that 1) foraging paradigms can provide a reference point to evaluate how different demands modulate value; 2) a simple OC model can approximate people's behavior in such single-option, take it or leave it choices; and 3) even when foraging in environments of equivalent richness, cognifitvely effortful demands can increase the attractiveness of offers rather than discount them (unlike other forms of cost).
+In the next experiment we explored whether this apparent value was inherent or malleable.
 
@@
 
-### WTH: 16.1.1.
-
-*To address hypothesis 4.1., A logistic regression will be fit for each participant in order to predict trial-wise acceptances, using reward amount as predictor.
-The resulting beta coefficients will be pooled across all participants, and we will perform a one-sample rank-sum test to examine whether the they are significantly positive or negative (compared to 0).
-If the group coefficients are significantly positive, it would mean that a predictor reliably increases the likelihood of acceptance.
-This will allow us to determine whether increments in reward amounts increased the likelihood of acceptance for each participant.*
-
-``` {r WTH: 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
+  This experiment probed whether the value-modulatory effects of each type of demand depended on the ability to obtain rewards through other behavioral means.
+If the cost or value of a demand are intrinsic, the relative preferences displayed above should be robust to alternatives.
+The experimental setup was mostly preserved, with 3 key differences: 1) all participants experienced cognitive effort, physical effort, and delay; 2) each block contained offers with one type of effort and passive waiting (allowing for comparisons in acceptances through the common wait condition).
+and 3) the handling and travel times were fixed at 10 s and 6 s, respectively.
+We therefore compared choices from the within-subjects experiment to the matching time condition from the between-subjects experiment.
+
+``` {r WTH: 16.1.1. reward coefficients, fig.align = "center", fig.width = 4, fig.height = 4, echo = FALSE}
 # adapt the data so the fits are only performed on choices, not failed attempts (revisit?)
-dataList <- dataWth %>% plyr::dlply("SubjID", identity)
+dataList <- dataWth %>% 
+  plyr::dlply("SubjID", identity)
 
 # fits
-logisticFits_base <- lapply(dataList, function(data) glm(Choice ~ Offer, data = data, family = "binomial"))
+logisticFits_base <- lapply(dataList, function(data) {suppressWarnings(glm(Choice ~ Offer, data = data, family = "binomial"))})
 
@@
 
-# plot to match the one in Cost 2, even though we only have offer as an influence
-ggplot(data = baseCoeffs, aes(x = "Offer", y = Offer)) +
-  geom_boxplot() +
-  ylim(-10, 10) +
-  labs(x = "", y = "Coefficients") +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  theme(legend.position = c(0.9, 0.7),
-        panel.grid.major = element_blank(), 
-        panel.grid.minor = element_blank(), 
-        panel.background = element_blank(), 
-        axis.line = element_line(colour = "black"),
-        text = element_text(size = 16))
-
-```
-
-The Wilcoxon signed rank test showed that the reward coefficients were significantly greater than 0 (V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* = `r wilcox.test(baseCoeffs$Offer)$p.value`), indicating that participants were properly influenced by reward amounts.
-
-### WTH: 16.1.2.
-
-*We will perform an extension of the logistic regression from 16.1.1., this time adding an autoregressive covariate containing the number of consecutive quits prior to a given trial.
-In this way, we will examine the possibility that participant choices were governed by recent quitting history rather than the experimental parameters.
-Coefficients not significantly different from 0 will denote that a participant did not rely on recent quitting history.*
-
-``` {r WTH: 16.1.2., echo = FALSE, include = FALSE}
+# # plot to match the one in Cost 2, even though we only have offer as an influence
+# ggplot(data = baseCoeffs, aes(x = "Offer", y = Offer)) +
+#   geom_boxplot() +
+#   ylim(-10, 10) +
+#   labs(x = "", y = "Coefficients") +
+#   geom_hline(yintercept = 0, linetype = "dashed") +
+#   theme(legend.position = c(0.9, 0.7),
+#         panel.grid.major = element_blank(), 
+#         panel.grid.minor = element_blank(), 
+#         panel.background = element_blank(), 
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 16))
+
+```
+
+``` {r WTH: 16.1.2. AR, echo = FALSE, include = FALSE}
 # Create an autoregressive predictor based on previous consecutive quits
-dataList <- lapply(dataList, function(data) data %>% mutate(AR = seqQuits(Choice)))
-
-# fits
-logisticFits_base <- lapply(dataList, function(data) {glm(Choice ~ Offer + AR, data = data, family = "binomial")})
+dataList <- lapply(dataList, function(data) {data %>% mutate(AR = seqQuits(Choice))})
+
+# fits per participant
+logisticFits_base <- lapply(dataList, function(data) {suppressWarnings(glm(Choice ~ Offer + AR, data = data, family = "binomial"))})
 
 # get the low/high 95% CIs for AR
-baseCoeffs <- as.data.frame(t(sapply(logisticFits_base, confint, "AR"))) %>% 
+baseCoeffs <- as_tibble(t(sapply(logisticFits_base, function(data) {suppressWarnings(confint(data, "AR"))}))) %>% 
   dplyr::rename(AR_CILow = `2.5 %`, AR_CIHigh = `97.5 %`) %>%
@@
 
-# create a vector indicating whether 0 is included or not
-# but first change NA to 0 (visual inspection showed that NAs were tied to p's with near full p(accept), meaning they weren't influenced by history)
-baseCoeffs <- baseCoeffs %>% mutate(AR_CILow = ifelse(is.na(AR_CILow), 0, AR_CILow),
+# create a vector indicating whether 0 is included or not (i.e. if there is 0, no sequential effect)
+# but first change NA to 0 (visual inspection showed that NAs were tied to p's with full or near full p(accept), meaning they weren't influenced by history)
+baseCoeffs <- baseCoeffs %>% 
+  mutate(AR_CILow = ifelse(is.na(AR_CILow), 0, AR_CILow),
          AR_CIHigh = ifelse(is.na(AR_CIHigh), 0, AR_CIHigh))
 baseCoeffs$AR_effect <- apply(baseCoeffs, 1, function(x) (!(as.numeric(x["AR_CILow"]) <= 0 & as.numeric(x["AR_CIHigh"]) >= 0)))
-
-# alternative method, just do pvalues (maybe adjusted when n is higher)
-# mean(sapply(logisticFits_base, function(x) {summary(x)$coefficients[3,4]}) < 0.05)
-```
-
-This regression showed that `r sum(baseCoeffs$AR_effect)` out of `r nSubjs_wth` of the subjects were influenced by recent quit history.
+```
+
+  Analyses from the previous experiment were repurposed to examine cost differences within individuals.
+We begun by testing the prediction that rewards would positively influence choices.
+A Wilcoxon signed rank test showed that individual logistic coefficients for reward amount were significantly greater than 0 (mean $\beta$ = `r round(mean(baseCoeffs$Offer), digits = 2)`, SD = `r round(sd(baseCoeffs$Offer), digits = 2)`; V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* `r report_p(wilcox.test(baseCoeffs$Offer)$p.value)`), once again confirming that participants were properly influenced by reward amounts.
+Adding a coefficient that tracked prior consecutive quits indicated that only `r sum(baseCoeffs$AR_effect)` individuals were influenced by recent quit history, thus discarding systematic sequential effects.
 

### 2020-04-02 Cost_manuscript.Rmd
first results section for the within-subj exp, plus cleaner code, methods rewording, and applying some cost3 stats to cost2

@@
 
-  print(adapted_p)
+  return(adapted_p)
 }
@@
   We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36).
-Sample size was once again determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f=0.5, and four factors (one for each condition).
+Sample size was once again determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each condition).
 The resulting sample size was 45, which we increased to 48 in order to balance the potential order of blocks.
@@
 We then confirmed that the under- and over-acceptance were detrimental to total earnings by performing the same quadratic linear model explained above.
-To determine the optimality of the group’s decisions, we will examine whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents were always be accepted, given our design).
+To determine the optimality of the group’s decisions, we examined whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents were always be accepted, given our design).
 The reward-maximizing strategy was to always reject 4 cents and accept 8 cents, yielding a combined optimal proportion of acceptances of 50% (see Operationalization of Costs for details).
@@
 
-# # potential visualization, though difficult to interpret
-# temp %>% 
-#   filter(Cost != "Easy") %>%
-#   select(Handling, Cost, Offer, significant) %>%
-#   ggplot(aes(Cost, interaction(Offer, Handling), fill = significant)) +
-#   geom_tile(color = "white") +
-#   theme_minimal()
+# ## if you want to replicate the cost 3 method
+# # this says that all but easy deviated from optimality in the observed direction
+# temp <- dataBtw %>%
+#   group_by(Cost) %>%
+#   filter(Offer < 20, Handling == 10) %>%
+#   summarize(propAccept = mean(Choice),
+#             accept = sum(Choice),
+#             quit = sum(Choice == 0))
+# 
+# temp2 <- apply(temp, 1, function(row) {prop.test(as.numeric(row[3]), sum(as.numeric(row[3:4])), p = 0.5, conf.level = 0.95)})
+#   
+#   
+# # store stats in a dataframe
+# news <- data.frame(probability = sapply(temp2, "[[", "estimate"),
+#                                    chisquared = sapply(temp2, "[[", "statistic"),
+#                                    confint = t(sapply(temp2, "[[", "conf.int")),
+#                                    pval = sapply(temp2, "[[", "p.value"))
+# rownames(news) <- temp$Cost
+
 ```
@@
 Because of this, participants were told to consider their strategies carefully, as accepting everything would not maximize their gains.
-Figure X shows that participants who over- or under-accepted earned the least (general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`).
+Figure X shows that participants who over- or under-accepted earned the least (general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 Two-sided, one-sample t-tests against the optimal proportion of acceptances (i.e.
-$\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)` of combinations (*p* < 0.05, FDR corrected), with the proportion of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`).
+$\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)`% of combinations (*p* < 0.05, FDR corrected), with the proportion of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`%, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`%, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`%, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`%).
 Together, these results suggest that participants were adequately influenced by the rewarding statistics of the environment, even though they did not always perform optimally.
@@
 One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
-Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdProp)`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Physical < Cognitive") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Cognitive > Wait") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait") %>% select(cohenD)`).
-It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdProp)`; permuted *p* = `r report_p(filter(propTests, contrast == "Wait < Easy") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy") %>% select(cohenD)` (all other *p* > 0.05).
+Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdProp)`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdProp)`; permuted *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdProp)`; permuted *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait") %>% select(cohenD)`).
+It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdProp)`; permuted *p* `r report_p(filter(propTests, contrast == "Wait < Easy") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy") %>% select(cohenD)` (all other *p* > 0.05).
 The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants (and 0 for either physical or easy conditions), making performance an unlikely explanation for the observed differences in choice.
@@
   We repeated these pairwise permutation to identify differences in earnings.
-In line with the earnings results from the previous section (see Figure X), the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdEarn)`) than both physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Physical > Cognitive") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Cognitive < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait") %>% select(cohenD)`).
-In addition, we found that the wait group earned more than the physical (permuted *p* = `r report_p(filter(earnTests, contrast == "Physical < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait") %>% select(cohenD)`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdEarn)`; permuted *p* = `r report_p(filter(earnTests, contrast == "Wait > Easy") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy") %>% select(cohenD)`).
+In line with the earnings results from the previous section (see Figure X), the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdEarn)`) than both physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdEarn)`; permuted *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdEarn)`; permuted *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait") %>% select(cohenD)`).
+In addition, we found that the wait group earned more than the physical (permuted *p* `r report_p(filter(earnTests, contrast == "Physical < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait") %>% select(cohenD)`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdEarn)`; permuted *p* `r report_p(filter(earnTests, contrast == "Wait > Easy") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy") %>% select(cohenD)`).
   These findings provide a first glimpe at differences in cost, showing that individuals in the wait condition accepted the least and earned the most.
@@
 We therefore compared choices from the within-subjects experiment to the matching time condition from the between-subjects experiment.
+We hypothesized that reward decision patterns would match those of the previous experiment, and that interleaving effort and delay would produce persistent preferences for passive delay trials.
 
@@
 ```
-
-  Analyses from the previous experiment were repurposed to examine cost differences within individuals.
-We begun by testing the prediction that rewards would positively influence choices.
-A Wilcoxon signed rank test showed that individual logistic coefficients for reward amount were significantly greater than 0 (mean $\beta$ = `r round(mean(baseCoeffs$Offer), digits = 2)`, SD = `r round(sd(baseCoeffs$Offer), digits = 2)`; V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* `r report_p(wilcox.test(baseCoeffs$Offer)$p.value)`), once again confirming that participants were properly influenced by reward amounts.
-Adding a coefficient that tracked prior consecutive quits indicated that only `r sum(baseCoeffs$AR_effect)` individuals were influenced by recent quit history, thus discarding systematic sequential effects.
-
-###	WTH: 16.1.3.
-
-*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable).
-No other covariates will be used, as this analysis is to confirm that over and under accepting are detrimental to total earnings.
-The quadratic term will be defined as the squared deviation from the optimal overall acceptance rate?*
 
@@
 
-The table shows the results from this linear model.
-In accord with the design of the experimental task, participants who either rejected or accepted too many trials received the least amount of money overall.
-This is confirmed by significance of the quadratic term below.
-
-``` {r WTH: 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
-# Summary table for the linear model
-panderOptions("digits", 2)
-pander(lmEarn, style = "rmarkdown")
-```
-
-###	WTH: 16.1.4.
-
-*To determine the optimality of the group's decisions, we will examine whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents will always be accepted).
-The reward-maximizing strategy is to always reject 4 cents and accept 8 cents, yielding a combined optimal proportion of acceptances of 50%.
-We will perform a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
-We will report the estimated overall proportion of acceptances for these rewards along with the statistics to show the direction of the bias.*
-
-``` {r WTH: 16.1.4., echo = FALSE, fig.align="center",fig.width=6,fig.height=4}
-# get the proportion of acceptances per reward and trial type across subjects, and do a one sample t test versus a null mu given by the optimal strategy
-# note that in the very likely case that every participant will accept or reject for a given reward/cost (i.e. sd = 0): 
-# I am just providing a pseudo pvalue as 1 minus the diff. between prevalent choice and the null (so, removing the standard deviation from the t test equation, otherwise you can't divide by 0)
-# this is just to track the optimality.
-# I am also adding the mean/sd of acceptances per cost/reward and optimality as reference
-# summary_costvsreward <- data %>% 
-#                           group_by(SubjID, Offer, Cost) %>% 
-#                           summarize(prop = mean(Choice)) %>%
-#                           group_by(Offer, Cost) %>%
-#                           summarize(pval = ifelse(sd(prop) == 0, 
-#                                                   1 - (mean(prop) - ifelse(mean(Offer) == 4, 0, 1)), 
-#                                                   t.test(prop, mu = (ifelse(mean(Offer) == 4, 0, 1)))$p.value),
-#                                     propAccept = mean(prop),
-#                                     sdAccept = sd(prop)) %>%
-#                           ungroup() %>%
-#                           mutate(Optimal = rep(c(0,1,1), each = 4),
-#                                  Padjusted = p.adjust(pval, method = "BY"))
-# 
-# temp <- data %>%
-#   group_by(SubjID, Offer, Cost) %>%
-#   filter(Offer < 20) %>%
-#   summarize(propAccept = mean(Choice)) %>% 
-#   spread(Cost, propAccept) %>% 
-#   ungroup() %>% 
-#   select(Cognitive:Wait_P) %>% 
-#   apply(., 2, t.test, mu = 0.5) 
-# 
-# summary_costvsreward <- data.frame(tstat = sapply(temp, "[[", "statistic"), 
-#                                    pval = sapply(temp, "[[", "p.value"))
-# rownames(summary_costvsreward) <- names(temp)
-
-# get quits and acceptances per cost type for each subject
-# revisit this eventually to clean it up
+``` {r WTH: 16.1.4. optimality, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# get quits and acceptances per cost type 
 temp <- dataWth %>%
-  group_by(SubjID, Offer, Cost) %>%
+  group_by(Cost) %>%
   filter(Offer < 20) %>%
@@
             accept = sum(Choice),
-            quit = sum(Choice == 0)) %>% 
-  gather(act, counts, accept:quit) %>% 
-  unite(temp, Cost, act, sep = ".") %>% 
-  select(SubjID, Offer, temp, counts) %>% 
-  spread(temp, counts) %>%
-  ungroup() %>% 
-  select(Cognitive.accept:Wait_P.quit)
+            quit = sum(Choice == 0))
 
 # perform a prop.test based on the group's acceptances and quits per cost
-temp2 <- lapply(seq(1, 8, by = 2), function(i) {prop.test(sum(temp[,i]), sum(temp[,i] + temp[,i+1]), p = 0.5, conf.level = 0.95)})
-
-# store stats in a dataframe
+temp2 <- apply(temp, 1, function(row) {prop.test(as.numeric(row[3]), sum(as.numeric(row[3:4])), p = 0.5, conf.level = 0.95)})
+
+# store stats in a dataframe and round up to the second digits for reporting
 summary_costvsreward <- data.frame(probability = sapply(temp2, "[[", "estimate"),
@@
                                    confint = t(sapply(temp2, "[[", "conf.int")),
-                                   pval = sapply(temp2, "[[", "p.value"))
-rownames(summary_costvsreward) <- unique(gsub("[.].*","",names(temp)))
-
-rm(temp, temp2)
-
-# create table
-pander(round(summary_costvsreward, digits = 4))
-```
-
-The table shows a significant bias towards low acceptance for 4 and 8 cent rewards for all but one condition (wait trials associated with cognitive effort).
-The plot in 16.2.1.
-shows the proportion of acceptances per reward for each cost condition.
+                                   pval = sapply(temp2, "[[", "p.value")) %>% round(., digits = 2)
+rownames(summary_costvsreward) <- temp$Cost
+
+rm(temp2)
+
+## no differences in earnings
+earnings_within <- dataWth %>%
+  group_by(SubjID, Cost) %>%
+  filter(rawChoice == 1) %>%
+  summarise(earning = sum(Offer) / 100) %>%
+  group_by(Cost) %>%
+  summarise(mEarn = mean(earning),
+            sdEarn = sd(earning)) %>%
+  mutate_if(is.numeric, round, digits = 2)
+
+```
+
+  Analyses from the previous experiment were repurposed to examine cost differences within individuals.
+We begun by testing the prediction that rewards would positively influence choices.
+A Wilcoxon signed rank test showed that individual logistic coefficients for reward amount were significantly greater than 0 (mean $\beta$ = `r round(mean(baseCoeffs$Offer), digits = 2)`, SD = `r round(sd(baseCoeffs$Offer), digits = 2)`; V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* `r report_p(wilcox.test(baseCoeffs$Offer)$p.value)`), once again confirming that participants were properly influenced by reward amounts.
+Adding a coefficient that tracked prior consecutive quits indicated that only `r sum(baseCoeffs$AR_effect)` individuals were influenced by recent quit history, thus discarding systematic sequential effects.
+In terms of earnings, a linear model predicting earnings once again showed that participants who accepted too few or too many trials earned the least, in line with the experimental design (Figure X; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
+Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-cognitive = `r filter(earnings_within, Cost == "Wait_C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-physical = `r filter(earnings_within, Cost == "Wait_P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_P")$sdEarn`).
+These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality (**big caveat: the same percentage can be produced by many non-optimal combinations, including accepting half of each reward.
+So neither approach really gets at this too well.**).
 
 ### **Within-subjects: Comparisons among the four delay and effort conditions**
-
-###	WTH: 16.2.1.
-
-*We will compute the probability of accepting a trial with a mixed-effects logistic regression.
-Based on the task structure and our main question, our a priori model of interest will include cost condition and reward amount as fixed main effects, and subject ID as a random effect.
-Cost condition will be modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
-We will run three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions (per 4.2).
-We anticipate significant main effects (coefficients different than zero) for reward and cost condition.
-We hypothesize that the differences among cost conditions will follow the pattern described in 4.2.*
 
@@
 
-``` {r WTH: 16.2.1., echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
+``` {r WTH: 16.2.1. mixed effect models, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
 # both methods yield similar outputs, at least coefficients and pvalues
@@
 
-The plot above shows that the pattern of reward acceptances does indeed resemble that from the between-subject experiment for an equivalent time combination.
-However, the differences in cost are mostly reversed from the previous experiment, following the order stipulated in 4.2.
-The matrix below shows the coefficients for all cost comparisons, with coefficient size in color and respective p-values enclosed in each box.
-This figure formally confirms the pattern seen above, although the wait conditions do trend towards significance.
+  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
+As can be seen on Figure X, even though the reward acceptance pattern was similar to the between-subjects experiment (Figure X), differences among cost conditions were less evident.
+Moreover, these differences contradicted our predictions, as cognitive effort remained as the least costly type of demand.
+We tested this observation through a mixed effects logistic regression, with main fixed effects for offer amount and cost, and random subject-wise intercepts (the reference cost category was rotated in order to perform all possible pairwise comparisons).
 

### 2020-04-07 Cost_manuscript.Rmd
methods + results draft sans modeling

@@
 library(ggfortify)
+library(patchwork)
 
@@
 
-Effort is costly, but sometimes it can add value.
+Effort is costly, but sometimes it can add value (For the talk, use the T example with Angelina, but think about how well it fits in the "prefer effort").
 In thinking about this, studies have focused on TAFC.
 We have learned much about this (show data), but two issues: 1) many studies compare costs by comparing discounting functions, which is helpful, but 2) an often disregarded aspect of this is OC.
+(other frame: What we've learned is how increasing a given demand reduces the value of its associated reward, but less explored is the question about how people choose among them, specifically how people allocate their time to engage with demands).
 Even in tafc, a choice for a sooner or easier item can be a reflection of wanting to skip the offer altogether.
@@
 
+What we've learned is how increasing a given demand reduces the value of its associated reward, but less explored is the question about how people choose among them, specifically how people allocate their time to engage with demands.
+
 - I guess you can mention that the wait group acts as a baseline of foraging behavior.
@@
 Like, are there elements that make cog effort valuable that are well encapsuled by foraging paradigms?
+- Pending questions: explain logistic coefficients in exponentiated form? (i.e. X% more/less likely than...)
 
@@
 We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions.
-We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity in the following order: 1) intercept only; 2) condition only; 3) reward only; 4) condition and reward main effects (a priori model); and 5) adding a two-way interaction.
+We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity in the following order: 1) intercept only; 2) cost only; 3) reward only; 4) cost and reward main effects (a priori model); and 5) adding a two-way interaction.
 We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
@@
   Next we probed the confidence and consistency with which participants made choices.
-We computed the proportion of quits that were performed during the choice window versus during the handling time.
+First, we qualitatively assessed the number of quits performed during during the handling time through a survival curve, and plotted the quit response time distribution as a function of block to examine choice confidence over time.
+Next, we computed the proportion of quits that were performed during the choice window versus during the handling time.
 We interpreted as confidence if a participant made at least 80% of their choices during the offer window.
 We then computed each participant’s total proportion of acceptances on the first two and last two blocks, and compared them using a paired permutation analysis (5000 iterations).
+We avoided the third and fourth block because their effort designation was counterbalanced across participants, which would have biased our estimates.
+
   **adapt once we decide on the model candidates**To estimate the subjective opportunity cost of each condition, we used a logistic function to model each participant’s probability of accepting a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
@@
 ``` {r BTW: 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
+## This section was removed because it was deemed redundant.
+The interaction is addressed once the a priori mixed effects logistic model is evaluated against multiple forms of interaction effects (16.2.4.).
 # temp <- dataBtw %>%
@@
 # and plot
-(a1 <- dataBtw %>%
+(hrPlot_btw <- dataBtw %>%
         filter(Choice < 2) %>%
@@
 
-``` {r BTW: 16.2.4. Model comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r BTW: 16.2.4. Model comparison, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
 # relevel, since the wait-reference model is used from the previous section
@@
                                 AIC = sapply(mixLogis_compare, AIC),
-                                BIC = sapply(mixLogis_compare, BIC))
+                                BIC = sapply(mixLogis_compare, BIC)) %>%
+                                  mutate_at(vars(AIC:BIC), round)
 
@@
 
-``` {r BTW: 16.2.4. Plot Deviance comparison, echo=FALSE,fig.align="center",fig.width=6,fig.height=4}
+``` {r BTW: 16.2.4. Plot Deviance comparison, echo = FALSE, fig.align = "center", fig.width = 6,fig.height = 4}
 # plot AIC and BIC
@@
 
-survPlot <- autoplot(survData) +
+survPlot_btw <- autoplot(survData) +
   geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
@@
 # RT ecdfs for the whole group across blocks, with the option to subdivide by cost group
-RTplot <- dataBtw %>%
+RTplot_btw <- dataBtw %>%
   filter(Choice == 0,
@@
 
-grid.arrange(survPlot, RTplot, ncol = 2)
+survPlot_btw | RTplot_btw
 
@@
 temp <- dataBtw %>%
-  filter(Choice < 2) %>%
   group_by(SubjID, Cost) %>%
@@
 # paired perms and effect sizes
-prepost <- list()
-prepost$CohenD <- sapply(temp, function(data) {DescTools::CohenD(data$propAccept_1, data$propAccept_2)})
-prepost$Perms <- sapply(temp, function(data) {permute(data$propAccept_1, data$propAccept_2, paired = T, simple = T)})
+prepost_btw <- list()
+prepost_btw$CohenD <- sapply(temp, function(data) {DescTools::CohenD(data$propAccept_1, data$propAccept_2)})
+prepost_btw$Perms <- sapply(temp, function(data) {permute(data$propAccept_1, data$propAccept_2, paired = T, simple = T)})
 ```
@@
 # and plot
-prepost$scatterplot <- dataBtw %>%
+prepost_btw$scatterplot <- dataBtw %>%
                         filter(Choice < 2) %>%
@@
 # note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
-prepost$propBlocks <- dataBtw %>%
+prepost_btw$propBlocks <- dataBtw %>%
                          filter(Choice < 2) %>%
@@
 
-grid.arrange(prepost$scatterplot, prepost$propBlocks, ncol = 2)
+prepost_btw$scatterplot | prepost_btw$propBlocks
 ```
@@
 Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure X, right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed (note that participants in physical conditions mostly relied on letting the grace period expire).
-These response time observation  s suggest clarity in participant preferences.
+These response time observations suggest clarity in participant preferences.
 
@@
 The scatter plot on Figure X shows the overall proportion accepted by each participant before and after the mid-point break (colored dashed lines indicate the mean for that group).
-Paired permutations on means of proportions showed no differences for wait and easy groups (*p* > 0.05), but significantly lower acceptance rates for physical (*p* = `r report_p(prepost$Perms[1])`, Cohen's D = `r round(prepost$CohenD[1], digits = 2)`) and cognitive (*p* = `r report_p(prepost$Perms[2])`, Cohen's D = `r round(prepost$CohenD[2], digits = 2)`) groups.
+Paired permutations on means of proportions showed no differences for wait and easy groups (*p* > 0.05), but significantly lower acceptance rates for physical (*p* = `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* = `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
 The decline in acceptances appeared to be gradual for the cognitive group, but not for the physical group (Figure X, half point indicated by the dashed line).
@@
 Figure X shows the proportion of acceptances for each offer combination, with each half depicted on each column.
-This collage suggests that changes in choice behavior for effortful groups were mostly driven by the longest handling time, perhaps because of the fatigue suggested above.
+This collage suggests that changes in choice behavior for effortful groups were mostly driven by the longest handling time, in agreement with previous findings where increments in effort duration correlated with aversion (Treadway et al., 2009), and with the fatigue suggested above.
 Regardless, the relative differences in acceptances among cost groups remain mostly untouched.
@@
 If the cost or value of a demand are intrinsic, the relative preferences displayed above should be robust to alternatives.
-The experimental setup was mostly preserved, with 3 key differences: 1) all participants experienced cognitive effort, physical effort, and delay; 2) each block contained offers with one type of effort and passive waiting (allowing for comparisons in acceptances through the common wait condition).
-and 3) the handling and travel times were fixed at 10 s and 6 s, respectively.
+The experimental setup was mostly preserved, with 3 key differences.
+First, all participants experienced cognitive effort, physical effort, and delay.
+Second, each block contained offers with one type of effort and passive waiting (allowing for comparisons in acceptances through the common wait condition).
+We refer to observations from each block's wait trials by their effort pair (i.e.
+"Wait_C" for cognitive, and "Wait_P" for physical).
+Finally, in this experiment the handling and travel times were fixed at 10 s and 6 s, respectively.
 We therefore compared choices from the within-subjects experiment to the matching time condition from the between-subjects experiment.
@@
 When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
-Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-cognitive = `r filter(earnings_within, Cost == "Wait_C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-physical = `r filter(earnings_within, Cost == "Wait_P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_P")$sdEarn`).
+Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait_C = `r filter(earnings_within, Cost == "Wait_C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait_P = `r filter(earnings_within, Cost == "Wait_P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_P")$sdEarn`).
 These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality (**big caveat: the same percentage can be produced by many non-optimal combinations, including accepting half of each reward.
@@
 
-# method 2
+# mixed effects logistics, rotating the reference cost condition
 mixLogis_main <- list()
@@
 
-  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
-As can be seen on Figure X, even though the reward acceptance pattern was similar to the between-subjects experiment (Figure X), differences among cost conditions were less evident.
-Moreover, these differences contradicted our predictions, as cognitive effort remained as the least costly type of demand.
-We tested this observation through a mixed effects logistic regression, with main fixed effects for offer amount and cost, and random subject-wise intercepts (the reference cost category was rotated in order to perform all possible pairwise comparisons).
-
-``` {r WTH: 16.2.1. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=4}
+``` {r WTH: 16.2.1. mixed effects matrix, echo = FALSE, fig.align = "center", fig.width = 5,  fig.height = 4}
 # get summary of coeffs
@@
 
-###	WTH: 16.2.2.
-
-*Next, we will examine whether the a priori model from 16.2.1.
-outperforms both simpler and more complex models.
-Unlike the individual logistic regression fits in 16.1.1., a mixed-effects approach gives us a better goodness of fit measure for model comparisons.
-We will determine the best model (combination of predictors) using Akaike's Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimizes the negative log-likelihood.
-The regression with each combination of predictors will be fitted in the following order: 1) intercept only; 2) condition only; 3) reward only; 4) condition and reward main effects (from 16.2.3.); and 5) adding a two-way interaction.
-We predict that model 4 will have the last considerable decrease in the negative log-likelihood.*
-
-``` {r WTH: 16.2.2., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
-# Quasibinomial GLM versions (with proper proportion setup)
+``` {r WTH: 16.2.2. ME model comparison, echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
+# fit ME logistic at increasing model complexities
 mixLogis_compare <- list()
@@
 
+# analysis of deviance
+mixLogis_compare$aod <- anova(mixLogis_compare$Reward, mixLogis_compare$AllMain, mixLogis_compare$Interaction)
+
 # effect size
@@
 
-The figure shows that the model with all main effects had the lowest AIC, but not BIC (pseudo R-square: `r round(mixLogis_compare$Rsq, digits = 2)`).
-We performed a likelihood ratio test to formally determine whether adding cost type to the reward-only model significantly improved the fit.
-We computed the difference in deviance between the models, and evaluated it under a chi-squared distribution with 3 degrees of freedom (i.e.
-the number of parameters added to the model, as cost was dummy-coded).
-The table below summarizes the results, showing that the addition of cost type significantly improved the model fit.
-(personal note: sure, AIC is 1 value lower when considering the difference in dfs, but that's barely making it..)
-
-``` {r WTH: 16.2.2. LRT (anova) table, echo = F}
-test <- anova(mixLogis_compare$Reward, mixLogis_compare$AllMain)
-rownames(test) <- c("Reward Only", "All Main")
-
-pander(test[c(1, 2, 3, 5, 6, 8)])
-```
+  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
+As can be seen on Figure X, even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure X), differences among cost conditions were less evident.
+Moreover, these differences contradicted our predictions, as cognitive effort remained as the least costly type of demand.
+We tested this observation through a mixed effects logistic regression, with main fixed effects for offer amount and cost, and random subject-wise intercepts (the reference cost category was rotated in order to perform all possible pairwise comparisons).
+The model confirmed that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Std.
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`).
+As in the previous section, pairwise comparison results are shown on the matrix in Figure X.
+This plot omits comparisons between effort and wait trials from different blocks, as these are not considered in our original predictions **(rephrase, with the understanding that Wait_C > Physical)**.
+The only significant difference was the higher likelihood to accept cognitive offers compared to physical ones ($\beta$ = `r round(mixSummary$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary$Pvals["Physical", "Cognitive"])`).
+This initial result suggests that differences in cost decrease if individuals are able to evaluate all of them.
+
+  We then repeated the model comparison approach from the between-subject section, evaluating models ranging in complexity from intercept-only to a two-way interaction between cost and reward.
+Even though the a priori model with all main effects explained a large portion of the variance (`r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure X).
+An analysis of deviance among the three models showed that adding cost condition to reward amount significantly reduced model deviance (AIC~a_priori~ = `r abicLogis_compare["AllMain", "AIC"]`, AIC~reward~ = `r abicLogis_compare["Reward", "AIC"]`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r mixLogis_compare$aod$Chisq[2]`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`).
+However, probing the interaction between these features significantly improved fits further (AIC~Interaction~ = `r abicLogis_compare["Interaction", "AIC"]`, $\chi^2$(`r mixLogis_compare$aod[[7]][3]`) = `r mixLogis_compare$aod$Chisq[3]`, *p* `r report_p(mixLogis_compare$aod[[8]][3])`).
+(**discuss with Joe: the interaction flips results over, such that both waits > pysical effort = cognitive effort...as predicted originally?
+Can't wrap my head around that yet, so this conclusion is pending**)
 
@@
 
-###	WTH: 16.3.1.
-
-*Response times (RT) for quit responses will be presented in a descriptive manner in order to examine whether participants tended to quit early or late within individual trials.
-Each cost condition's response time distribution will contain the pooled RT across participants, and we will display the empirical cumulative distribution functions for each condition.
-Short RT would suggest confident and stable decisions (in support of 4.3.1.).*
-
-``` {r WTH: 16.3.1., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
-# Proportion of forced travels per subject and cost type
-propFails <- dataWth %>%
-  filter(Cost != "WAIT") %>%
-  group_by(SubjID, Cost) %>%
-  summarise(propFails = mean(rawChoice == 2)) %>%
-  group_by(Cost) %>%
-  summarise(meanQuit = mean(propFails))
-# 
-# # Reaction times ECDFs including offer and in-trial quits
-# (RTs <- data %>%
-#   mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
-#   filter(rawChoice < 2) %>% 
-#   ggplot(aes(RT, color = Cost)) + 
-#     #stat_ecdf(lwd = 1.2) +
-#     geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
-#     geom_vline(xintercept = 2, lty = 2) + # end of the offer period
-#     scale_color_manual(values = colsWth) +
-#     scale_x_continuous(breaks = seq(12), limits = c(0, 14)) +
-#     labs(x = "Time in Cost", y = "Proportion Completed") +
-#     theme(panel.grid.major = element_blank(),
-#       panel.grid.minor = element_blank(),
-#       panel.background = element_blank(),
-#       axis.line = element_line(colour = "black"),
-#       text = element_text(size = 16)))
-
-# NEW VERSION OF SURVIVAL. BUT STILL NEEDS A BIT OF WORK. ALSO, CHECK THAT RT > 14s
-
-library(survival)
-library(ggfortify)
-
-# this version of a survival curve forces all successful acceptances to have an RT of 14
-# that's to avoid jumps from 2s to 10s to 14s
-# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor?
+``` {r WTH: 16.3.1. RT, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# Survival curve for quits and response time ECDFs across blocks
+# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor
 # to note re: x-axis. In this exp, p's could quit within the 2s offer window. Cost 2 didn't allow that, so it counts from when trial begins.
@@
 
-autoplot(survData) +
+survPlot_wth <- autoplot(survData) +
   geom_vline(xintercept = 2, lty = 2) + # end of the grace period for physical trials
@@
   labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
-  theme(legend.position = c(0.35, 0.2),
+  theme(legend.position = c(0.8, 0.3),
         panel.grid.major = element_blank(),
@@
         axis.line = element_line(colour = "black"),
-        text = element_text(size = 22))
+        text = element_text(size = 16))
 
 # ecdf of RTs across blocks for all subjects combined
-dataWth %>%
+RTplot_wth <- dataWth %>%
   mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
@@
     stat_ecdf() +
+    labs(y = "Proportion of Quits Before Time X", x = "Quitting Time") +
     #facet_wrap(vars(Cost)) +
-    theme_classic()
-
-```
-
-Participants can quit either during the offer period (2s) or during the handling time (10s), allowing for a total of 12 seconds to give up on the current trial.
-The survival curve above shows quitting throughout the trial for all participants.
-Censored points signal completions (at end of interval) and forced travels (throughout the trial).
-The figure suggests that participants made most of their choices quickly within the offer window.
-The overall proportion of forced trials was scarce (overall mean proportion of fails for cognitive and physical trials were `r unlist(propFails[1:2,2])`, respectively).
-
-###	WTH: 16.3.2.
-
-*We will also compute the proportion of quits that were performed during the choice window versus during the handling time.
-If over 80% of quits occurred during the choice window on average, this will suggest that participants were confident in their choices.*
-
-``` {r WTH: 16.3.2., echo = FALSE}
+    theme(legend.position = c(0.8, 0.3),
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      panel.background = element_blank(),
+      axis.line = element_line(colour = "black"),
+      text = element_text(size = 16))
+
+survPlot_wth | RTplot_wth
+```
+
+``` {r WTH: 16.3.2. quits in offer vs handling, echo = FALSE}
+# Proportion of forced travels per subject and cost type
+propFails_wth <- dataWth %>%
+  filter(!Cost %in% c("Wait_C", "Wait_P")) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(propFails = mean(rawChoice == 2) * 100)
+
 # Proportion of quits once the trial started per subject
-PropQuits <- dataWth %>%
+# ResponseType distinguished between offer quits and handling quits
+propQuits_wth <- dataWth %>%
   filter(!(ResponseType %in% c("Forced Travel", "Forced travel", "Reward"))) %>%
   group_by(SubjID) %>%
-  summarise(propAccept = mean(ResponseType == "Quit"))
-
-```
-
-The mean proportion of quits during the handling time was `r round(mean(PropQuits$propAccept), digits = 2)` (SD = `r round(sd(PropQuits$propAccept), digits = 2)`), with `r sum(PropQuits$propAccept > 0.2)` participants accepting fewer than 80% of trials during the offer window.
-
-###	WTH: 16.3.3.
-
-*In order to further examine choice stability (hypothesis 4.3.1.), we will compute each participant's total proportion of acceptances on the first two and last two blocks.
-We will compute a mixed-effects linear model to predict post-midpoint proportion of acceptances from pre-midpoint rates, with subjects as random intercepts and condition as a dummy-coded fixed effect.
-We will report the 95% confidence interval (CI) for the pre-midpoint predictor.
-A CI containing 1 will denote that participants in that condition produced consistent choices, while accounting for the overall acceptance patterns of a given subject across cost types.
-(**This is a more elaborate version of the between-subject analysis, which did a pre-post prediction based on the proportion of acceptances per subject across groups**).*
-
-``` {r WTH: 16.3.3., echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4, include = F}
-# restructure the data
-temp <- dataWth %>%
-  filter(!(Block %in% c(3,4))) %>%
-  group_by(SubjID, Cost, Half) %>%
-  summarise(propAccepted = mean(Choice)) %>%
-  ungroup() %>%
-  spread(Half, propAccepted)
-
-# compute the mixed effects model (linear for this)
-mixLogis_prepost <- lmer(Half_2 ~ Half_1 + Cost -1 + (1 | SubjID), data = temp)
-
-# get the coefficients and confidence intervals
-t1 <- coefficients(mixLogis_prepost)$SubjID[1, 2:6]
-t2 <- as.data.frame(t(confint(mixLogis_prepost)[3:7,]))
-
-# and concatenate them
-summary_prepost <- t(bind_rows(t1, t2))
-colnames(summary_prepost) <- c("Coefficient", "CI-low", "CI-high")
-
+  summarise(propAccept = mean(ResponseType == "Quit") * 100)
+
+```
+
+  We next examined the stability in people's choices.
+If the cost of a particular demand was intrinsic, then its effect on choices should have been consistent as participants explored alternative costs.
+We started by examining whether individuals regreted engaging in a particular offer.
+Participants could quit either during the offer period (2 s) or during the handling time (10 s), allowing for a total of 12 seconds to give up on the current trial.
+The survival curve on Figure X shows quitting throughout the trial for all participants.
+Censored points signal completions (at end of interval) and forced travels (throughout the trial).
+Similar to before, the survival analysis suggests that participants made most of their choices quickly within the offer window.
+In fact, the mean percentage of quits during the handling time was `r round(mean(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 0.2)` participants quitting over 20% of trials during the handling time.
+Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure X).
+Once in the handling time, the overall proportion of forced travels in the effortful trials was relatively low for both cognitive (mean = `r round(mean(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (mean = `r round(mean(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
+Similar to the between-subjects experiment, these results suggest that decision makers were confident in their adopted strategies, and were able to perform the tasks well.
+
+``` {r WTH: 16.3.3. pre-post, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4, include = F}
+# # restructure the data
+# temp <- dataWth %>%
+#   filter(!(Block %in% c(3, 4))) %>%
+#   group_by(SubjID, Cost, Half) %>%
+#   summarise(propAccepted = mean(Choice)) %>%
+#   ungroup() %>%
+#   spread(Half, propAccepted)
+# 
+# # compute the mixed effects model (linear for this)
+# mixLogis_prepost <- lmer(Half_2 ~ Half_1 + Cost -1 + (1 | SubjID), data = temp)
+# 
+# # get the coefficients and confidence intervals
+# t1 <- coefficients(mixLogis_prepost)$SubjID[1, 2:6]
+# t2 <- as.data.frame(t(confint(mixLogis_prepost)[3:7,]))
+# 
+# # and concatenate them
+# summary_prepost <- t(bind_rows(t1, t2))
+# colnames(summary_prepost) <- c("Coefficient", "CI-low", "CI-high")
+#
 # # prepost half paired perms
@@
 ## paired tests for first versus last block per cost type
-FirstvsLast <- dataWth %>%
-  filter(Choice < 2) %>%
-  group_by(SubjID) %>%
-  mutate(Block = case_when(
-    Block %in% c(1, 2) ~ 1,
-    Block %in% c(3, 4) ~ 2,
-    Block %in% c(5, 6) ~ 3
-  )) %>%
-  group_by(SubjID, Cost, Block) %>%
-  summarise(propAccept_subj = mean(Choice)) %>%
-  spread(Block, propAccept_subj) %>%
-  rename(First = `1`, Second = `2`, Third = `3`) %>%
+## PRE/POST PAIRED PERMUTATIONS
+temp <- dataWth %>%
+  filter(!(Block %in% c(3, 4))) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
+            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
   plyr::dlply("Cost", identity)
 
-prepost <- list()
-prepost$Perms <- sapply(FirstvsLast, function(x) {permute(x$First, x$Third, paired = T, simple = T)})
-prepost$CohenD <- sapply(FirstvsLast, function(x) {DescTools::CohenD(x$First, x$Third)})
-
-rm(temp, t1, t2)
-```
-
-``` {r WTH: 16.3.3. plots, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+# paired perms and effect sizes
+prepost_wth <- list()
+prepost_wth$CohenD <- sapply(temp, function(data) {DescTools::CohenD(data$propAccept_1, data$propAccept_2)})
+prepost_wth$Perms <- sapply(temp, function(data) {permute(data$propAccept_1, data$propAccept_2, paired = T, simple = T)})
+
+# correlation between the difference in acceptance rates and mistakes
+accDiff <- dataWth %>%
+  filter(!(Block %in% c(3, 4)), 
+         Cost %in% c("Cognitive", "Physical")) %>%
+  group_by(SubjID, Cost) %>%
+  summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
+            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
+  mutate(Diff = propAccept_2 - propAccept_1)
+
+corDiff <- cor(t1$Diff, propFails_wth$propFails)
+
+```
+
+``` {r WTH: 16.3.3. pre-post plots, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
 # various plots
@@
             group_by(SubjID, Cost) %>%
-            summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
-                      propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
+            summarise(pAccept_1 = mean(Choice[Half=="Half_1"]),
+                      pAccept_2 = mean(Choice[Half=="Half_2"])) %>%
             group_by(Cost) %>%
-            summarise(propAccept_1 = mean(propAccept_1),
-                      propAccept_2 = mean(propAccept_2))
+            summarise(propAccept_1 = round(mean(pAccept_1), digits = 2),
+                      sdAccept_1 = round(sd(pAccept_1), digits = 2),
+                      propAccept_2 = round(mean(pAccept_2), digits = 2),
+                      sdAccept_2 = round(sd(pAccept_2), digits = 2))
 
@@
 
-# wait vs effort across effort conditions
-pAll <- dataWth %>%
-  filter(Choice < 2) %>%
-  mutate(Cost2 = ifelse(!(Cost %in%  c("Wait_C", "Wait_P")), "EFFORT", "WAIT"),
-         BlockType = ifelse(gsub(".*_", "", Cost) == 1, "Physical", "Cognitive")) %>%
-  group_by(SubjID, BlockType) %>%
-  summarise(Wait_accept = mean(Choice[Cost2 == "WAIT"]),
-            Effort_accept = mean(Choice[Cost2 == "EFFORT"])) %>%
-  ggplot(aes(Wait_accept, Effort_accept, color = SubjID, shape = BlockType)) +
-    geom_point(size = 5, show.legend = T) +
-    xlim(0,1) +
-    ylim(0,1) +
-    geom_abline(slope = 1, intercept = 0, lty = 2) +
-    scale_color_manual(values = colsWth) +
-    scale_fill_manual(values = colsWth) +
-    theme_classic()
-
-# load the plots
-grid.arrange(mid, propBlocks, ncol = 2)
-
-# plot showing the difference in proportion of acceptances between first and last block, effort vs delay for each block type
-# lines connect the same subject between the blocks
-dataWth %>%
-  group_by(SubjID) %>%
-  mutate(Block = case_when(
-    Block %in% c(1, 2) ~ 1,
-    Block %in% c(3, 4) ~ 2,
-    Block %in% c(5, 6) ~ 3
-  )) %>%
-  #filter(Half == "Half_1", Offer < 20) %>%
-  filter(Block != 2) %>%
-  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
-  group_by(SubjID, Cost, Block, Offer) %>%
-  summarise(propAccept = mean(Choice)) %>%
-  ungroup() %>%
-  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-  spread(Block, propAccept) %>%
-  mutate(Difference = `Last Block` - `First Block`) %>%
-  group_by(SubjID, Cost) %>%
-  summarise(Diffscore = sum(Difference)/3) %>%
-  mutate(Type = ifelse(Cost %in% c("Cognitive", "Physical"), "Effort", "Delay"),
-         Cost = ifelse(Cost %in% c("Cognitive", "Wait_C"), "Cognitive", "Physical")) %>%
-  spread(Type, Diffscore) %>%
-  ggplot(aes(Effort, Delay, group = SubjID, fill = Cost)) +
-    geom_hline(yintercept = 0) +
-    geom_vline(xintercept = 0) +
-    geom_path(show.legend = F, alpha = 0.5, linetype = "dashed") +
-    geom_point(show.legend = T, pch = 21, color = "black", size = 4) +
-    scale_fill_manual(values = colsWth) +
-    annotate("text", x = -0.4, y = 0.6, label = "Increased preference for delay over time", size = 5, color = "grey30") +
-    annotate("text", x = -0.5, y = -0.6, label = "All acceptances decreased", size = 5, color = "grey30") +
-    annotate("text", x = 0.5, y = 0.6, label = "All acceptances increased", size = 5, color = "grey30") +
-    annotate("text", x = 0.4, y = -0.6, label = "Increased preference for effort over time", size = 5, color = "grey30") +
-    labs(x = "P(Effort): Last - First Block", y = "P(Delay): Last - First Block", fill = "Block type") +
-    ylim(-0.7, 0.7) +
-    xlim(-0.7, 0.7) +
-    theme(legend.key = element_blank(),
-          legend.position = c(0.9, 0.35),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 20))
+mid | propBlocks
+
+# ## PROPORTION OF COGNITIVE ACCEPTANCES NOT DIFFERENT BETWEEN FIRST HALF OF WITHIN AND BETWEEN EXPERIMENTS
+# btw <- dataBtw %>%
+#   filter(Handling == 10) %>%
+#   group_by(SubjID, Cost) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   plyr::dlply("Cost", identity)
+# 
+# wth <- dataWth %>%
+#   filter(Block < 3) %>%
+#   mutate(Cost2 = ifelse(Cost %in% c("Wait_P", "Wait_C"), "Wait", Cost)) %>%
+#   group_by(SubjID, Cost2) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   plyr::dlply("Cost2", identity)
+# 
+# 
+# permute(btw$Cognitive$pAccept, wth$`1`$pAccept, simple = T)
+# 
+# permute(btw$Physical$pAccept, wth$`2`$pAccept, simple = T)
+# 
+# permute(btw$Wait$pAccept, wth$Wait$pAccept, simple = T)
+
+# # wait vs effort across effort conditions
+# pAll <- dataWth %>%
+#   filter(Choice < 2) %>%
+#   mutate(Cost2 = ifelse(!(Cost %in%  c("Wait_C", "Wait_P")), "EFFORT", "WAIT"),
+#          BlockType = ifelse(gsub(".*_", "", Cost) == 1, "Physical", "Cognitive")) %>%
+#   group_by(SubjID, BlockType) %>%
+#   summarise(Wait_accept = mean(Choice[Cost2 == "WAIT"]),
+#             Effort_accept = mean(Choice[Cost2 == "EFFORT"])) %>%
+#   ggplot(aes(Wait_accept, Effort_accept, color = SubjID, shape = BlockType)) +
+#     geom_point(size = 5, show.legend = T) +
+#     xlim(0,1) +
+#     ylim(0,1) +
+#     geom_abline(slope = 1, intercept = 0, lty = 2) +
+#     scale_color_manual(values = colsWth) +
+#     scale_fill_manual(values = colsWth) +
+#     theme_classic()
+
+# # load the plots
+# grid.arrange(mid, propBlocks, ncol = 2)
+
+# # plot showing the difference in proportion of acceptances between first and last block, effort vs delay for each block type
+# # lines connect the same subject between the blocks
+# dataWth %>%
+#   group_by(SubjID) %>%
+#   mutate(Block = case_when(
+#     Block %in% c(1, 2) ~ 1,
+#     Block %in% c(3, 4) ~ 2,
+#     Block %in% c(5, 6) ~ 3
+#   )) %>%
+#   #filter(Half == "Half_1", Offer < 20) %>%
+#   filter(Block != 2) %>%
+#   mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
+#   group_by(SubjID, Cost, Block, Offer) %>%
+#   summarise(propAccept = mean(Choice)) %>%
+#   ungroup() %>%
+#   #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+#   spread(Block, propAccept) %>%
+#   mutate(Difference = `Last Block` - `First Block`) %>%
+#   group_by(SubjID, Cost) %>%
+#   summarise(Diffscore = sum(Difference)/3) %>%
+#   mutate(Type = ifelse(Cost %in% c("Cognitive", "Physical"), "Effort", "Delay"),
+#          Cost = ifelse(Cost %in% c("Cognitive", "Wait_C"), "Cognitive", "Physical")) %>%
+#   spread(Type, Diffscore) %>%
+#   ggplot(aes(Effort, Delay, group = SubjID, fill = Cost)) +
+#     geom_hline(yintercept = 0) +
+#     geom_vline(xintercept = 0) +
+#     geom_path(show.legend = F, alpha = 0.5, linetype = "dashed") +
+#     geom_point(show.legend = T, pch = 21, color = "black", size = 4) +
+#     scale_fill_manual(values = colsWth) +
+#     annotate("text", x = -0.4, y = 0.6, label = "Increased preference for delay over time", size = 5, color = "grey30") +
+#     annotate("text", x = -0.5, y = -0.6, label = "All acceptances decreased", size = 5, color = "grey30") +
+#     annotate("text", x = 0.5, y = 0.6, label = "All acceptances increased", size = 5, color = "grey30") +
+#     annotate("text", x = 0.4, y = -0.6, label = "Increased preference for effort over time", size = 5, color = "grey30") +
+#     labs(x = "P(Effort): Last - First Block", y = "P(Delay): Last - First Block", fill = "Block type") +
+#     ylim(-0.7, 0.7) +
+#     xlim(-0.7, 0.7) +
+#     theme(legend.key = element_blank(),
+#           legend.position = c(0.9, 0.35),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 20))
 
@@
 
-These participants tended to accept fewer trials on the second half of the experiment (Beta = `r round(summary_prepost[1,1], digits = 2)`, 95% CI: `r round(summary_prepost[1,2:3], digits = 2)`).
-The figure on the left shows this tendency, although some subjects shows considerable consistency.
-The plot on the right divides the proportion of acceptances across blocks (each cost block is experienced thrice), and shows a global decrease in acceptances as a function of experimental time.
-
-A better test is to perform pairwise comparisons between the first and last block per cost.
-Paired permutations on means of proportions showed that all participants accepted fewer trials during the second half, regardless of cost (all p < 0.05; Cohen's D: cognitive = `r prepost$CohenD[1]`, physical = `r prepost$CohenD[2]`, wait-cognitive = `r prepost$CohenD[1]`, wait-physical = `r prepost$CohenD[1]`).
-
-Now let's divide them by reward and handling amounts.
-The plots below show that initially participant choices resembled those from the between-subject experiment, accepting more cognitive trials than any other, and displaying higher costs for physical/wait_p.
-However, by the end of the experiment all cost types were exacerbated.
-As seen before, cognitive trials had the greatest decrease in acceptances across reward amounts.
-This re-evaluation was not present when participants faced only one type of cost.
-
 ``` {r WTH: 16.3.3. Plot Pre/Post reward x handling, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
@@
 
-dataWth %>%
+(hrPlot_wth <- dataWth %>%
   group_by(SubjID) %>%
@@
           axis.line = element_line(colour = "black"),
-          text = element_text(size = 22))
-
-```
-
-This prompted the question of whether fitting the mixed logistic model could confirm this shift in preferences.
-Just as before, the matrix below show the coefficient magnitude (color) and pvalues for differences based on iterating through costs as reference dummy codes.
+          text = element_text(size = 16)))
+
+```
 
@@
 
-Finally, we can compare how the difference in proportion accepted between last and first blocks changes between trial types.
-The plots below show that effort and delay trials in the cognitive blocks tended to be rejected more on the last block (i.e.
-they land on the negative side of both axes).
-The plot on the right shows a similar pattern for trials on the physical blocks, but these are more similar across subjects, and also show a small tendency to accept more on either first or last blocks.
-
 ``` {r WTH: 16.3.3 temp plot, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
-
-cw <- dataWth %>%
-  group_by(SubjID) %>%
-  mutate(Block = case_when(
-    Block %in% c(1, 2) ~ 1,
-    Block %in% c(3, 4) ~ 2,
-    Block %in% c(5, 6) ~ 3
-  )) %>%
-  filter(Offer < 20) %>%
-  filter(Block != 2) %>%
-  group_by(SubjID, Block, Cost, Offer) %>%
-  summarise(pAccept = mean(Choice)) %>%
-  spread(Block, pAccept) %>%
-  mutate(diff = `3` - `1`) %>%
-  ungroup() %>%
-  select(-c(`1`, `3`)) %>%
-  spread(Cost, diff) %>%
-  ggplot(aes(Cognitive, Wait_C, fill = as.character(Offer))) +
-    geom_point(pch = 21, color = "black", size = 3) +
-    geom_hline(yintercept = 0) +
-    geom_vline(xintercept = 0) +
-    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
-    ylim(-1, 1) +
-    xlim(-1, 1) +
-    labs(#title = "P(Accepted): Last - First Block",
-         x = "P(Cognitive): Last - First",
-         y = "P(Wait_C): Last - First",
-         fill = "Offer") +
-    theme(legend.key = element_blank(),
-          legend.background = element_rect(fill = "grey80"),
-          legend.position = c(0.8, 0.8),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
-
-gw <- dataWth %>%
-  group_by(SubjID) %>%
-  mutate(Block = case_when(
-    Block %in% c(1, 2) ~ 1,
-    Block %in% c(3, 4) ~ 2,
-    Block %in% c(5, 6) ~ 3
-  )) %>%
-  filter(Offer < 20) %>%
-  filter(Block != 2) %>%
-  group_by(SubjID, Block, Cost, Offer) %>%
-  summarise(pAccept = mean(Choice)) %>%
-  spread(Block, pAccept) %>%
-  mutate(diff = `3` - `1`) %>%
-  ungroup() %>%
-  select(-c(`1`, `3`)) %>%
-  spread(Cost, diff) %>%
-  ggplot(aes(Physical, Wait_P, fill = as.character(Offer))) +
-    geom_point(pch = 21, color = "black", size = 3, show.legend = F) +
-    geom_hline(yintercept = 0) +
-    geom_vline(xintercept = 0) +
-    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
-    ylim(-1, 1) +
-    xlim(-1, 1) +
-    labs(#title = "P(Accepted): Last - First Block",
-         x = "P(Physical): Last - First",
-         y = "P(Wait_P): Last - First",
-         fill = "Offer") +
-    theme(legend.position = c(0.8, 0.8),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
-
-grid.arrange(cw, gw, ncol = 2)
-
-# more prepost tests
-# diffscore prepost for effort vs wait
-dataWth %>%
-  group_by(SubjID) %>%
-  mutate(Block = case_when(
-    Block %in% c(1, 2) ~ 1,
-    Block %in% c(3, 4) ~ 2,
-    Block %in% c(5, 6) ~ 3
-  )) %>%
-  #filter(Half == "Half_1", Offer < 20) %>%
-  filter(Block != 2) %>%
-  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
-  group_by(SubjID, Cost, Block, Offer) %>%
-  summarise(propAccept = mean(Choice)) %>%
-  ungroup() %>%
-  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-  spread(Block, propAccept) %>%
-  mutate(Difference = `Last Block` - `First Block`) %>%
-  group_by(SubjID, Cost) %>%
-  summarise(Diffscore = sum(Difference)/3) %>%
-  spread(Cost, Diffscore) %>%
-  ggplot() +
-    geom_point(aes(Cognitive, Wait_C), color = colsWth[1]) +
-    geom_point(aes(Physical, Wait_P), color = colsWth[2]) +
-    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-    ylim(-0.5, 0.5) +
-    xlim(-0.5, 0.5) +
-    #geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
-    #geom_boxplot(show.legend = F, size = 1.5) +
-    #geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
-    #scale_color_manual(values = colsWth) +
-    #scale_fill_manual(values = colsWth) +
-    theme(legend.key = element_blank(),
-          legend.position = c(0.9, 0.25),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 22))
-
-# diffscore per cost type (you don't see if specific subjects are prone to increasing/decreasing acceptances across them)
-dataWth %>%
-  group_by(SubjID) %>%
-  mutate(Block = case_when(
-    Block %in% c(1, 2) ~ 1,
-    Block %in% c(3, 4) ~ 2,
-    Block %in% c(5, 6) ~ 3
-  )) %>%
-  #filter(Half == "Half_1", Offer < 20) %>%
-  filter(Block != 2) %>%
-  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
-  group_by(SubjID, Cost, Block, Offer) %>%
-  summarise(propAccept = mean(Choice)) %>%
-  ungroup() %>%
-  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-  spread(Block, propAccept) %>%
-  mutate(Difference = `Last Block` - `First Block`) %>%
-  group_by(SubjID, Cost) %>%
-  summarise(Diffscore = sum(Difference)/3) %>%
-  ggplot(aes(Cost, Diffscore, fill = Cost)) +
-    geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
-    geom_boxplot(show.legend = F, size = 1.5) +
-    geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
-    scale_color_manual(values = colsWth) +
-    scale_fill_manual(values = colsWth) +
-    theme(legend.key = element_blank(),
-          legend.position = c(0.9, 0.25),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 22))
-```
-
-### WTH: 16.3.4.
+# cw <- dataWth %>%
+#   group_by(SubjID) %>%
+#   mutate(Block = case_when(
+#     Block %in% c(1, 2) ~ 1,
+#     Block %in% c(3, 4) ~ 2,
+#     Block %in% c(5, 6) ~ 3
+#   )) %>%
+#   filter(Offer < 20) %>%
+#   filter(Block != 2) %>%
+#   group_by(SubjID, Block, Cost, Offer) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   spread(Block, pAccept) %>%
+#   mutate(diff = `3` - `1`) %>%
+#   ungroup() %>%
+#   select(-c(`1`, `3`)) %>%
+#   spread(Cost, diff) %>%
+#   ggplot(aes(Cognitive, Wait_C, fill = as.character(Offer))) +
+#     geom_point(pch = 21, color = "black", size = 3) +
+#     geom_hline(yintercept = 0) +
+#     geom_vline(xintercept = 0) +
+#     geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
+#     ylim(-1, 1) +
+#     xlim(-1, 1) +
+#     labs(#title = "P(Accepted): Last - First Block",
+#          x = "P(Cognitive): Last - First",
+#          y = "P(Wait_C): Last - First",
+#          fill = "Offer") +
+#     theme(legend.key = element_blank(),
+#           legend.background = element_rect(fill = "grey80"),
+#           legend.position = c(0.8, 0.8),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
+# 
+# gw <- dataWth %>%
+#   group_by(SubjID) %>%
+#   mutate(Block = case_when(
+#     Block %in% c(1, 2) ~ 1,
+#     Block %in% c(3, 4) ~ 2,
+#     Block %in% c(5, 6) ~ 3
+#   )) %>%
+#   filter(Offer < 20) %>%
+#   filter(Block != 2) %>%
+#   group_by(SubjID, Block, Cost, Offer) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   spread(Block, pAccept) %>%
+#   mutate(diff = `3` - `1`) %>%
+#   ungroup() %>%
+#   select(-c(`1`, `3`)) %>%
+#   spread(Cost, diff) %>%
+#   ggplot(aes(Physical, Wait_P, fill = as.character(Offer))) +
+#     geom_point(pch = 21, color = "black", size = 3, show.legend = F) +
+#     geom_hline(yintercept = 0) +
+#     geom_vline(xintercept = 0) +
+#     geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
+#     ylim(-1, 1) +
+#     xlim(-1, 1) +
+#     labs(#title = "P(Accepted): Last - First Block",
+#          x = "P(Physical): Last - First",
+#          y = "P(Wait_P): Last - First",
+#          fill = "Offer") +
+#     theme(legend.position = c(0.8, 0.8),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
+# 
+# 
+# grid.arrange(cw, gw, ncol = 2)
+# 
+# # more prepost tests
+# # diffscore prepost for effort vs wait
+# dataWth %>%
+#   group_by(SubjID) %>%
+#   mutate(Block = case_when(
+#     Block %in% c(1, 2) ~ 1,
+#     Block %in% c(3, 4) ~ 2,
+#     Block %in% c(5, 6) ~ 3
+#   )) %>%
+#   #filter(Half == "Half_1", Offer < 20) %>%
+#   filter(Block != 2) %>%
+#   mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
+#   group_by(SubjID, Cost, Block, Offer) %>%
+#   summarise(propAccept = mean(Choice)) %>%
+#   ungroup() %>%
+#   #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+#   spread(Block, propAccept) %>%
+#   mutate(Difference = `Last Block` - `First Block`) %>%
+#   group_by(SubjID, Cost) %>%
+#   summarise(Diffscore = sum(Difference)/3) %>%
+#   spread(Cost, Diffscore) %>%
+#   ggplot() +
+#     geom_point(aes(Cognitive, Wait_C), color = colsWth[1]) +
+#     geom_point(aes(Physical, Wait_P), color = colsWth[2]) +
+#     geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
+#     ylim(-0.5, 0.5) +
+#     xlim(-0.5, 0.5) +
+#     #geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
+#     #geom_boxplot(show.legend = F, size = 1.5) +
+#     #geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
+#     #scale_color_manual(values = colsWth) +
+#     #scale_fill_manual(values = colsWth) +
+#     theme(legend.key = element_blank(),
+#           legend.position = c(0.9, 0.25),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 22))
+# 
+# # diffscore per cost type (you don't see if specific subjects are prone to increasing/decreasing acceptances across them)
+# dataWth %>%
+#   group_by(SubjID) %>%
+#   mutate(Block = case_when(
+#     Block %in% c(1, 2) ~ 1,
+#     Block %in% c(3, 4) ~ 2,
+#     Block %in% c(5, 6) ~ 3
+#   )) %>%
+#   #filter(Half == "Half_1", Offer < 20) %>%
+#   filter(Block != 2) %>%
+#   mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
+#   group_by(SubjID, Cost, Block, Offer) %>%
+#   summarise(propAccept = mean(Choice)) %>%
+#   ungroup() %>%
+#   #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
+#   spread(Block, propAccept) %>%
+#   mutate(Difference = `Last Block` - `First Block`) %>%
+#   group_by(SubjID, Cost) %>%
+#   summarise(Diffscore = sum(Difference)/3) %>%
+#   ggplot(aes(Cost, Diffscore, fill = Cost)) +
+#     geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
+#     geom_boxplot(show.legend = F, size = 1.5) +
+#     geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
+#     scale_color_manual(values = colsWth) +
+#     scale_fill_manual(values = colsWth) +
+#     theme(legend.key = element_blank(),
+#           legend.position = c(0.9, 0.25),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 22))
+```
+
+  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])` Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])` Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait_C:  mean~pre~ = `r filter(df_mean, Cost == "Wait_C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait_C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait_C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait_C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait_C"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait_C"]], digits = 2)`; Wait_P: mean~pre~ = `r filter(df_mean, Cost == "Wait_P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait_P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait_P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait_P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait_P"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait_P"]], digits = 2)`; Figure X).
+The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson R = `r round(corDiff, digits = 2)`, *p* > 0.05).
+Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure X).
+Mixed effects logistic regressions on each half separately confirmed this observation.
+The matrix on Figure X shows the coefficient magnitude for all pairwise comparisons among costs (computed by rotating the reference cost condition in the model), with crosses signaling non-significant coefficients (*p* > 0.05).
+This plot shows that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).
+
+### WTH: 16.3.4. (OC MODELING: SKIP)
 

### 2020-04-07 Cost_manuscript.Rmd
mislabeled variable

@@
 
-corDiff <- cor(t1$Diff, propFails_wth$propFails)
+corDiff <- cor(accDiff$Diff, propFails_wth$propFails)
 

### 2020-04-07 Cost_manuscript.Rmd
edited methods section, adding figures

@@
 title: Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment
-author: "Claudio Toro-Serey^1,2 & Joseph T. McGuire^1,2"
+author: "Claudio Toro-Serey & Joseph T. McGuire"
 csl: apa.csl
@@
   \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
-#bibliography: mPFC_paper.bib
+#bibliography: XXXX.bib
 ---
@@
   # do p < 0.001 or round depending on the value
-  adapted_p <- ifelse(pval < 0.001, "< 0.001", paste("=", round(pval, digits = 2)))
+  # maybe adapt with case_when(), so there are three levels: observed, < 0.01, and < 0.001
+  adapted_p <- ifelse(pval < 0.001, "< 0.001", paste("=", round(pval, digits = 3)))
 
@@
 
-1.  Department of Psychological and Brain Sciences, Boston University, Boston, USA
-
-2.  Center for Systems Neuroscience, Boston University, Boston, USA
+Department of Psychological and Brain Sciences & Center for Systems Neuroscience, Boston University, Boston, USA
 
@@
 A participant who quit every trial in at least one block was assumed not to have followed or understood task instructions, or to have disengaged from the task altogether.
-4) Performance: In the cognitive effort condition, participants were forced to travel if they made 2 mistakes in a trial (see task procedures below).
+4) Performance: Participants were forced to travel if they made 2 mistakes in a cognitive effort trial (see task procedures below), or if they gripped below threshold during physical trials.
 Any participant with more than 30% forced travels was excluded.
@@
 
-  All experimental tasks were implemented using PsychoPy 2.X (CITE) on a Macbook Pro laptop.
-In this task, participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay.
+  All experimental tasks were implemented using PsychoPy 2 (v1.85.1, CITE) on a Macbook Pro laptop.
+In this task, participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay (Figure 1).
 Their goal was to maximize their gains within a fixed amount of time.
+On each trial a monetary offer was displayed for 2 s, and participants had the opportunity to expend time and/or effort during the handling time in order to earn it.
+Upon completion of a trial participants saw a 2 s window displaying the reward obtained, which was followed by a travel time to the next offer.
+Alternatively, the participant could quit at any point during the handling time by pressing the spacebar on the computer, and immediately start traveling.
+
+  Each participant was assigned to one of three types of costs (cognitive effort, physical effort, or delay), and a fourth group of equal size faced an effortless physical task that involved minimal gripping.
+Each group was unaware that other cost conditions existed.
 Participants exerted physical effort by maintaining grip on a handheld dynamometer (XXXX, BIOPAC Systems, United States) using their dominant hand.
@@
 For motion coherence, 100 solid white dots moved on the screen.
-A fraction of these dots moved cohesively to the left or right (coherence could be either 30% or 40%, uniformly sampled), while the rest moved in random directions.
+A fraction of these dots moved cohesively to the left or right, while the rest moved in random directions (coherence could be either 30% or 40%, uniformly sampled).
 Participants had to respond with the direction of the cohesive set of dots.
-REVISE.
 In flanker, rows of arrowheads pointed either to the left or the right (maximum of 3 rows, 3 to 13 arrowheads per row).
@@
 Participants were asked to respond within each task’s presentation time.
-Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive ones of each kind.
-
-  Each participant was assigned to one of these types of costs (cognitive effort, physical effort, or delay), and a fourth group of equal size faced an effortless physical task that involved minimal gripping.
-Each group was unaware that other cost conditions existed.
-On each trial a monetary offer was displayed for 2 s, and participants had the opportunity to expend time and/or effort during the handling time in order to earn it.
-Upon completion of a trial participants saw a 2 s window displaying the reward obtained, which was followed by a travel time to the next offer.
-Alternatively, the participant could quit at any point during the handling time by pressing the spacebar on the computer, and immediately start traveling.
+Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive tasks of each kind.
 If participants failed to maintain above-threshold gripping or made two mistakes during the cognitive task, they were forced to travel and missed the reward.
@@
 Each of these blocks was experienced in a pseudo-randomized order, and repeated in the same order after a short break in order to probe choice stability (total session length = 42 minutes).
-Reward amounts varied uniformly per trial (4, 8, or 20 cents), such that every reward was presented twice every six trials.
+Reward amounts varied uniformly per trial (4, 8, or 20 cents), with the constraint that every reward was presented twice every six trials.
 This prevented sequences from being dominated by a single amount during any window of time.
@@
 
+```{r Trial plot (Fig.
+1), out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
+On each trial, participants were offered to earn money (4, 8, or 20 cents) by sustaining effort or waiting during the handling time (2, 10, or 14 s).
+The end of a trial was followed by a travel time (handling and travel times always added up to 16 s).
+Participants could skip unfavorable trials and immediately start traveling to a potentially better offer.
+In the between-subject experiment, cost was fixed per participant and handling time varied per block.
+In the within-subject version, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
+Possible costs, handling times, and rewards were fully disclosed in order to avoid experience-dependent learning."}
+
+include_graphics("./Images/FIG1_short.png")
+```
+
 ### Operationalization of Cost
 
-  Foraging theory posits that accepting a delayed reward depends on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment (Stephens and Krebs, 1977).
+  Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment (Stephens and Krebs, 1977).
 In this study, the richness of the environment was manipulated by the length of the handling and travel times (i.e.
@@
 
-**INSERT**
-
-  where R, H, and P are the reward, handling time, and acceptance probability of trial i, respectively, and T is the travel times.
+$\dfrac {\sum p_i R_i} {\sum p_i H_i + 3T},p \in \{0, 1\}$
+
+  where *R*, *H*, and *p* are the reward, handling time, and acceptance probability of offer i, respectively, and T is the travel time.
 This gave us the total reward per second attainable in each block as a function of the lowest amount accepted (i.e.
 acceptance threshold).
-Figure X shows possible earnings for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
+Figure 2 shows possible earnings for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
 For example, a participant in a 10 s handling block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate.
@@
 
+```{r Optimal plot (Fig.
+2), out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
+the smallest amount accepted) for each handling time.
+Circles denote the reward-maximizing threshold for each block, which is described in the table.
+Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers."}
+
+include_graphics("./Images/FIG2.png")
+```
+
 ### Analyses
 
+  All analyses were performed in R 3.5.2 (CITE).
 First we tested whether decision makers integrated delay and reward information.
@@
 A significant quadratic coefficient thus would signal that the task statistics operated as expected.
-Next, to determine the optimality of each group’s decisions, performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost above).
+Next, to determine the optimality of each group’s decisions, performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost).
 This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR).
-**MAYBE CHANGE TO COST3 APPROACH?**
 
@@
 This gave us an initial glimpse on the potential differences in cost among conditions.
+
   In order to further look at the effect of handling, offer, and cost type, we computed the probability of accepting a trial with a mixed-effects logistic regression using the lme4 package (CITE).
-Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and participant ID as a random effect.
+Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and participant ID as a random intercept.
 Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition.
 We ran three versions of the model with different reference conditions, in order to test all pairwise differences among the four cost conditions.
-As preregistered, we anticipated significant main effects (coefficients different than zero) of handling time, reward, and cost condition.
-In addition, we hypothesized that the probability of accepting would be significantly great in either effort condition compared to wait and easy groups.
-We then examined whether this a priori model outperformed both simpler and more complex models.
+(**exponentiate coefficients to make them more interpretable?**) We then examined whether this a priori model outperformed both simpler and more complex models.
 We used both Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
 The regression with each combination of predictors was fitted in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
-We predicted that model 5 would have the lowest AIC.
+We predicted that model 6 (the a priori setup) would have the lowest AIC and BIC.
 Nested models with similar AIC were statistically compared using an analysis-of-deviance.
@@
   Finally, we modeled the subjective opportunity cost in each condition.
-We started by addressing the prediction that participants would display consistent choice patterns throughout the session (i.e.
+We started by examining whether participants were confident and consistent in their choices.
+We visually examined survival curves indicating at what point during the handling time participants quit a trial (censored points included trial completions and forced travels), in addition to quitting time distributions.
+Next, we addressed the prediction that participants would display consistent choice patterns throughout the session (i.e.
 that the reward amounts they accepted in a given timing condition would be similar throughout the experiment).
-We computed each participant’s total proportion of acceptances pre- and post-midpoint for every block, and performed paired permutations (5000) on the mean proportion of acceptances.
+We computed each participant’s total proportion of acceptances pre- and post-midpoint for every block, and performed paired permutations (5000 iterations) to compare their mean proportion of acceptances.
 We then confirmed that the relative costs observed with from the whole experimental session were still present on each half of the experiment.
 The winning model from the mixed-effects logistic comparison was applied to each half separately.
-In each case the reference cost category was rotated in order to assess pairwise differences among all costs.
+In each case, the reference cost category was rotated in order to assess pairwise differences among all costs.
 We evaluated the consistency of the relative costs by visually comparing the patterns of significant differences between experimental halves.
 
-  Once we established choice stability, we proceeded to estimate the subjective OC of each type of demand (see Operationalization of Cost above).
+  Once we established choice stability, we proceeded to estimate the subjective OC of each type of demand (see Operationalization of Cost).
 OC was computed as the product of a free parameter (gamma) and the handling time.
@@
 
- **INSERT**
-
-  Both gamma and the temperature parameter of the softmax function were estimated independently for each subject, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE).
+$P(accept)_i = \dfrac {1} {1 + e^{-\beta(R_i - \gamma H_i)}}$
+
+  Both gamma ($\gamma$) and the inverse temperature parameter ($\beta$) of the softmax function were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE).
 The gamma optimization search space was bound by extreme choice values.
@@
 The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.
-Finally, the OC estimates for each group were compared using an ANOVA with condition as a factor.
-This let us determine which cost type produced the highest discounting.
+We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (0.74, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
+Finally, we determined which cost type produced the highest discounting by comparing gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
 **ADD ADDITIONAL MODELS FROM LITERATURE**
@@
   We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36).
-Sample size was once again determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each condition).
+Sample size was once again determined by means of a power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each condition).
 The resulting sample size was 45, which we increased to 48 in order to balance the potential order of blocks.
@@
 “8 cents for physical effort”).
-Unlike the previous experiment, participants could make their choice during the offer window (instead of during the handling time).
+Unlike the previous experiment, participants could express their decision to quit during the offer window (instead of during the handling time).
 Participants trained in each type of demand until they reached the same criteria as in the between-subject experiment.
@@
 
-  The analytical pipeline for the within-subject study was mostly preserved from the between-subject experiment.
+  The analytical pipeline was mostly preserved from the between-subject experiment.
 We first ran tests to determine whether decision makers integrated reward information.
@@
   To compare acceptance rates among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
-The model included cost condition and reward amount as fixed main effects, and subject ID as a random effect (handling time is not modeled, as participants experienced a single time combination).
+The model included cost condition and reward amount as fixed main effects, and participant ID as a random intercept (handling time is not modeled, as participants experienced a single time combination).
 Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
@@
 
-  **adapt once we decide on the model candidates**To estimate the subjective opportunity cost of each condition, we used a logistic function to model each participant’s probability of accepting a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
+  **adapt once we decide on the model candidates** To estimate the subjective opportunity cost of each condition, we used a logistic function to model each participant’s probability of accepting a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
 As before, OC was computed as the product of a free parameter (gamma) and the handling time.
@@
 ``` {r BTW: 16.1.3. Earnings, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# calculate the proportions and earnings per subject, while keeping group info
+## calculate the proportions and earnings per subject, while keeping group info
 temp <- dataBtw %>%
@@
 
-# linear fit of earnings x prop accept
+## linear fit of earnings x prop accept
 lmEarn <- lm(Earnings ~ pComplete + pComplete2, data = temp)
 
-# plot
-# (earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
-#          scale_color_manual(values = colsBtw) + 
-#          geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = T) + 
-#          stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
-#          labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
-#          scale_fill_manual(values = colsBtw) +
-#          theme(panel.grid.major = element_blank(), 
-#            panel.grid.minor = element_blank(), 
-#            panel.background = element_blank(), 
-#            axis.line = element_line(colour = "black"),
-#            text = element_text(size = 16)))
+## plot
+earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) +
+         scale_color_manual(values = colsBtw) +
+         geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = F) +
+         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
+         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
+         scale_fill_manual(values = colsBtw) +
+         theme(panel.grid.major = element_blank(),
+           panel.grid.minor = element_blank(),
+           panel.background = element_blank(),
+           axis.line = element_line(colour = "black"),
+           text = element_text(size = 12))
 
@@
 We hypothesized that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that changing the cost required to obtain rewards would uniformly increase or decrease this choice pattern.
-Specifically, we predicted that participants confronted with cognitive demands would be more likely to accept trials than those faced with physical effort and delay, regardless of handling time and reward amount.
-
-  To address the first hypothesis, we first confirmed that increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively.
+Specifically, we predicted that participants confronted with effortful demands would be more likely to accept trials than those faced with passive delay, regardless of handling time and reward amount.
+
+  To address the first hypothesis, we examined whether increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively.
 Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
-Individual-specific logistic regression coefficients for handling time were significantly lower than 0 (mean $\beta$ = `r mean(coeffRH_mean[2], na.rm = T)`, SE = `r coeffRH_se[2]`; Wilcoxon test: V = `r rankHand$statistic`, *p* `r report_p(rankHand$p.value)`), whereas increasing the reward amount resulted in higher acceptance probabilities (mean $\beta$ = `r coeffRH_mean[1]`, SE = `r coeffRH_se[1]`; Wilcoxon test: V = `r rankOffer$statistic`, p `r report_p(rankOffer$p.value)`).
+Individual-specific logistic regression coefficients for handling time were significantly lower than 0 (mean $\beta$ = `r round(mean(coeffRH_mean[2], na.rm = T), digits = 2)`, SE = `r round(coeffRH_se[2], digits = 2)`; Wilcoxon test: V = `r rankHand$statistic`, *p* `r report_p(rankHand$p.value)`), whereas increasing the reward amount predicted higher acceptance probabilities (mean $\beta$ = `r round(coeffRH_mean[1], digits = 2)`, SE = `r round(coeffRH_se[1], digits = 2)`; Wilcoxon test: V = `r rankOffer$statistic`, p `r report_p(rankOffer$p.value)`).
 We next examined whether choices could also have been affected by recent choice history (i.e.
 if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of consecutive quits preceding a trial.
-This auto-regressive coefficient was not significantly different than 0 (mean $\beta$ = `r coeffRHAR_mean[3]`, SE = `r coeffRHAR_se[3]`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r ifelse(rankRHAR$p.value < 0.001, "< 0.001", paste("=", round(rankRHAR$p.value, digits = 2)))`), and the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants.
-This indicates that offer patterns did not influence participant behavior.
+This auto-regressive coefficient was not significantly different than 0 (mean $\beta$ = `r round(coeffRHAR_mean[3], digits = 2)`, SE = `r round(coeffRHAR_se[3], digits = 2)`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r report_p(rankRHAR$p.value)`), and the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants.
+This indicates that offer patterns did not systematically influence participant behavior.
 
@@
 Because of this, participants were told to consider their strategies carefully, as accepting everything would not maximize their gains.
-Figure X shows that participants who over- or under-accepted earned the least (general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r summary(lmEarn)$coefficients[3,1]`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+Figure 3 (right) shows that participants who over- or under-accepted earned the least (general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 Two-sided, one-sample t-tests against the optimal proportion of acceptances (i.e.
-$\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)`% of combinations (*p* < 0.05, FDR corrected), with the proportion of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`%, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`%, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`%, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`%).
+$\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)`% of combinations (*p* < 0.05, FDR corrected), with the percentage of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`%, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`%, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`%, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`%).
 Together, these results suggest that participants were adequately influenced by the rewarding statistics of the environment, even though they did not always perform optimally.
@@
       permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
-      cohenD = abs(round(cohenD(x[, 1], x[, 2]), digits = 3)))
+      cohenD = abs(round(cohenD(x[, 1], x[, 2]), digits = 2)))
   }) %>% 
@@
 # pAccepted
-p1 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
+prop1 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
         geom_boxplot(show.legend = F) +
@@
             axis.line = element_line(colour = "black"),
-            text = element_text(size = 16))
+            text = element_text(size = 12))
 
 # earnings
-p2 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
+earnings1 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
         geom_boxplot(show.legend = F) +
@@
             axis.line = element_line(colour = "black"),
-            text = element_text(size = 16))
-
-grid.arrange(p1, p2, ncol = 2)
+            text = element_text(size = 12))
 
@@
 
-  The next set of analyses examined the hypothesis that choice differences among costs would be characterized by more acceptances by the cognitive group **not quite**.
-Figure X shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings.
-One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
-Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdProp)`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdProp)`; permuted *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdProp)`; permuted *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait") %>% select(cohenD)`).
-It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mProp)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdProp)`; permuted *p* `r report_p(filter(propTests, contrast == "Wait < Easy") %>% select(permPval))`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy") %>% select(cohenD)` (all other *p* > 0.05).
+```{r General prop & earnings plots (Fig.
+3), fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
+Middle: Total number of dollars earned by each group by the end of the experiment.
+Right: The relationship between proportion accepted and total earned.
+Consistent with the foraging design, participants who over and under accepted earned the least."}
+# plots generated in 16.2.1. and 16.1.3.
+ prop1 | earnings1 | earnFitplot
+```
+
+  The next set of analyses examined the hypothesis that choice differences among costs would be characterized by more acceptances by the effort groups.
+Figure 3 (left) shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings (middle).
+One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F(`r propAov[[1]]$Df[1]`, `r propAov[[1]]$Df[2]`) = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F(`r earnAov[[1]]$Df[1]`, `r earnAov[[1]]$Df[2]`) = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
+Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive")$mProp`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdProp`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical")$mProp`, SD = `r filter(overallSumms, Cost == "Physical")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mProp)`, SD = `r filter(overallSumms, Cost == "Wait")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait")$cohenD`).
+It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy")$mProp`, SD = `r filter(overallSumms, Cost == "Easy")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Wait < Easy")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy")$cohenD`) (all other *p* > 0.05).
 The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants (and 0 for either physical or easy conditions), making performance an unlikely explanation for the observed differences in choice.
 
-  We repeated these pairwise permutation to identify differences in earnings.
-In line with the earnings results from the previous section (see Figure X), the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Cognitive") %>% select(sdEarn)`) than both physical (mean = `r filter(overallSumms, Cost == "Physical") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Physical") %>% select(sdEarn)`; permuted *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive") %>% select(cohenD)`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Wait") %>% select(sdEarn)`; permuted *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait") %>% select(cohenD)`).
-In addition, we found that the wait group earned more than the physical (permuted *p* `r report_p(filter(earnTests, contrast == "Physical < Wait") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait") %>% select(cohenD)`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy") %>% select(mEarn)`, SD = `r filter(overallSumms, Cost == "Easy") %>% select(sdEarn)`; permuted *p* `r report_p(filter(earnTests, contrast == "Wait > Easy") %>% select(permPval))`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy") %>% select(cohenD)`).
+  We repeated these pairwise permutations to identify differences in earnings.
+In line with the earnings results from the previous section, the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn)`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
+In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
+
   These findings provide a first glimpe at differences in cost, showing that individuals in the wait condition accepted the least and earned the most.
-Moreover, they suggest that cognitive demands can boost the value of an offer instead, even when accepting it negatively impacts total earnings.
+Moreover, they suggest that costs associated with cognitive effort can boost the value of an offer instead, even when accepting it negatively impacts total earnings.
 

### 2020-04-08 Cost_manuscript.Rmd
draft from btw-subj results complete

@@
 
+\newpage
+
 ## Introduction
@@
 One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F(`r propAov[[1]]$Df[1]`, `r propAov[[1]]$Df[2]`) = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F(`r earnAov[[1]]$Df[1]`, `r earnAov[[1]]$Df[2]`) = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
-Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive")$mProp`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdProp`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical")$mProp`, SD = `r filter(overallSumms, Cost == "Physical")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mProp)`, SD = `r filter(overallSumms, Cost == "Wait")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait")$cohenD`).
+Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive")$mProp`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdProp`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical")$mProp`, SD = `r filter(overallSumms, Cost == "Physical")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mProp`, SD = `r filter(overallSumms, Cost == "Wait")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait")$cohenD`).
 It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy")$mProp`, SD = `r filter(overallSumms, Cost == "Easy")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Wait < Easy")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy")$cohenD`) (all other *p* > 0.05).
@@
   We repeated these pairwise permutations to identify differences in earnings.
-In line with the earnings results from the previous section, the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn)`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
+In line with the earnings results from the previous section, the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
 In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
@@
 # and plot
-(hrPlot_btw <- dataBtw %>%
+hrPlot_btw <- dataBtw %>%
         filter(Choice < 2) %>%
@@
               axis.line = element_line(colour = "black"),
-              text = element_text(size = 16)))
+              text = element_text(size = 12))
 
@@
 
-``` {r BTW: 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
+``` {r BTW: 16.2.3. Mixed Effects Model, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4, include = FALSE}
 # clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
@@
 rearrange <- c("Cognitive", "Easy", "Wait", "Physical") # to kinda match the order in Cost 3
-mixSummary <- betaMatrix(mixLogis_main, rearrange = rearrange)
-diag(mixSummary$Pvals) <- NA
+mixSummary_btw <- betaMatrix(mixLogis_main, rearrange = rearrange)
+diag(mixSummary_btw$Pvals) <- NA
 
@@
 
-corrplot(mixSummary$Betas, 
+corrplot(mixSummary_btw$Betas, 
          is.corr = F, 
-         p.mat = mixSummary$Pvals, 
+         p.mat = mixSummary_btw$Pvals, 
          type = "lower",
@@
 # plot AIC and BIC
-(mixLogis_compare$plot <- ME_evals$abicLogis_compare %>% 
+ABIC_plot_btw <- ME_evals$abicLogis_compare %>% 
   gather(Comparison, Value, AIC:BIC) %>%
@@
     geom_point(color = "black", pch = 21, size = 3) +
-    theme_classic())
-
+      theme(legend.position = c(0.8, 0.7),
+            axis.text.x = element_text(angle = 45, hjust = 1),
+            panel.grid.major = element_blank(),
+            panel.grid.minor = element_blank(),
+            panel.background = element_blank(),
+            axis.line = element_line(colour = "black"),
+            text = element_text(size = 16))
+
+```
+
+```{r mixed effects plots (Fig.
+4), out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
+A:  B:  Each entry shows how much more likely was the reference group to accept an offer than the comparison group.
+C:"}
+#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
+include_graphics("./Images/FIG4.png")
 ```
@@
 We therefore distilled the previous analysis to examine choice behavior for every combination of experimental parameters.
-Figure X shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and condition, with optimal acceptance rates depicted by the gray circles.
+Figure 4A shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and cost, with optimal acceptance rates depicted by the gray circles.
 Qualitatively, the figure confirms two important predictions.
@@
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`).
-In order to show the comparisons among all conditions, Figure X portrays the coefficients (color scale **maybe exponentiated coefficients to make it more intuitive?**), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
-Specifically, each entry shows how much more likely was the reference group to accept an offer than the comparison group.
+In order to show the comparisons among all conditions, Figure 4B portrays the coefficients (color scale), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
 The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
@@
   We next examined whether choice behavior could be better explained by environmental statistics alone, or if cost conditions changed the way handling time and offer amount interacted to influence choices.
-Figure X shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details).
+Figure 4C shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details).
 Here we focus on AIC, as both metrics yielded comparable results.
-As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a_priori~ = `r ME_evals$abicLogis_compare["AllMain", "AIC"]`, AIC~handling/reward~ = `r ME_evals$abicLogis_compare["HR", "AIC"]`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r ME_evals$HRvMain$Chisq[2]`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
-However, against our prediction, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r ME_evals$abicLogis_compare["HR_interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r ME_evals$MainvHRint$Chisq[2]`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r ME_evals$abicLogis_compare["Interaction", "AIC"]`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r ME_evals$MainvAllint$Chisq[2]`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
+As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a-priori~ = `r filter(ME_evals$abicLogis_compare, Model == "AllMain")$AIC`, AIC~handling/reward~ = `r filter(ME_evals$abicLogis_compare, Model == "HR")$AIC`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r round(ME_evals$HRvMain$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
+However, against our prediction, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r filter(ME_evals$abicLogis_compare, Model == "HR_interaction")$AIC`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r round(ME_evals$MainvHRint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r filter(ME_evals$abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r round(ME_evals$MainvAllint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
 These improvements were driven by the fact that differences in offer acceptances among costs were never present for 20 cents (all *p* values for interactions containing offer amount < 0.001).
 As the highest reward should always be accepted in prey foraging environments, we conclude that the most parsimonious explanation of choice behavior comes from the a priori model containing all main effects.
-In combination with the pattern observed in Figure X, these results confirm that handling and reward amounts were similarly integrated across groups, but that the absolute rate of acceptances was affected by the cost faced (and was highest for those confronted with cognitive demands).
+In combination with the pattern observed in Figure 4A, these results confirm that handling and reward amounts were similarly integrated across groups, but that the absolute rate of acceptances was affected by the cost faced (and was highest for those confronted with cognitive demands).
 
@@
 
-``` {r BTW: 16.3.1. RTs, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+``` {r BTW: 16.3.1. surv and RTs, echo = FALSE, warning = FALSE, fig.align = "center", fig.width = 10, fig.height = 4, include = FALSE}
 # qualitative survival analysis
@@
   labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
-  theme(legend.position = c(0.35, 0.25),
+  theme(legend.position = "none",
         panel.grid.major = element_blank(),
@@
         axis.line = element_line(colour = "black"),
-        text = element_text(size = 16))
+        text = element_text(size = 14))
 
@@
     stat_ecdf() +
-    labs(y = "Proportion of Quits Before Time X", x = "Quitting Time") +
+    scale_x_continuous(breaks = seq(0, 1, length.out = 3), labels = c(0, 0.5, 1)) +
+    labs(y = "Proportion of Quits Before Time X", x = "Quitting Time (seconds)") +
     facet_wrap(vars(Cost)) +
-    theme_classic()
-
-survPlot_btw | RTplot_btw
+    theme(#legend.position = c(0.9, 0.7),
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      panel.background = element_blank(),
+      axis.line = element_line(colour = "black"),
+      text = element_text(size = 14))
 
@@
                                 axis.line = element_line(colour = "black"),
-                                text = element_text(size = 16))
+                                text = element_text(size = 14))
 
@@
                                  axis.line = element_line(colour = "black"),
-                                 text = element_text(size = 16))
-
-prepost_btw$scatterplot | prepost_btw$propBlocks
+                                 text = element_text(size = 14))
+
 ```
@@
 
+```{r Survival and prepost plots (Fig.
+5), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
+Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
+Dashed lines indicate the mean for each group.
+On the right, the proportion accepted over time per group.
+The order of blocks was repeated in the second half (indicated by the black dashed line)."}
+# plots generated in 16.3.1. and 16.3.2.
+(suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
+```
+
   Before computationally modeling behavior, we asked whether foragers had a stable representation of their environment.
 Since participants had complete a priori knowledge of the statistics of each environment, and were unaware of any other cost groups that could modulate the subjective cost of their assigned demand, we expected them to 1) show confidence in their choices by not quitting mid-handling time; and 2) adopt the same strategy while re-experiencing each environment.
-We investigated the first prediction by plotting a survival curve of trial quits across all participants (Figure X, left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
+We investigated the first prediction by plotting a survival curve of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
 This qualitative analysis shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
@@
 This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code).
-Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure X, right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed (note that participants in physical conditions mostly relied on letting the grace period expire).
+Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure 5, top-right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed.
 These response time observations suggest clarity in participant preferences.
 
-  We next examined the second prediction (i.e.
+  We tested the second prediction (i.e.
 strategy stability) by comparing acceptances rates throughout the experiment.
-The scatter plot on Figure X shows the overall proportion accepted by each participant before and after the mid-point break (colored dashed lines indicate the mean for that group).
-Paired permutations on means of proportions showed no differences for wait and easy groups (*p* > 0.05), but significantly lower acceptance rates for physical (*p* = `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* = `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
-The decline in acceptances appeared to be gradual for the cognitive group, but not for the physical group (Figure X, half point indicated by the dashed line).
+The scatter plot on Figure 5 (bottom-left) shows the overall proportion accepted by each participant before and after the mid-point break (colored dashed lines indicate the mean for that group).
+Paired permutations showed no acceptance rate differences for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
+The decline in acceptances appeared to be gradual for the cognitive group, but not for the physical group (Figure 5, bottom-right).
 An explanation for these results is that these conditions became costlier due to fatigue, thus providing evidence that our cognitive and physical manipulations were effortful.
@@
 We addressed this possibility by examining pre-post acceptance rates for each handling time and reward combination.
-Figure X shows the proportion of acceptances for each offer combination, with each half depicted on each column.
-This collage suggests that changes in choice behavior for effortful groups were mostly driven by the longest handling time, in agreement with previous findings where increments in effort duration correlated with aversion (Treadway et al., 2009), and with the fatigue suggested above.
+Figure 6 (left) shows the proportion of acceptances for each offer combination, with each half depicted on each column.
+This collage suggests that changes in choice behavior for effortful groups were mostly driven by the longest handling time, in in line with reports where value is discounted as the length of the required effort increases (Treadway et al, 2009).
 Regardless, the relative differences in acceptances among cost groups remain mostly untouched.
@@
 all main effects) on each experimental half separately.
-We replicated the matrix of coefficients from the previous section, with each half mirrored along the diagonal (i.e.
+We replicated the matrix of coefficients from the previous section (Figure 6, right), with each half mirrored along the diagonal (i.e.
 the top triangle shows the coefficients for the second half of the experiment).
@@
 # this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
-(prepostPlot <- dataBtw %>%
+prepostPlot <-dataBtw %>%
   group_by(SubjID) %>%
@@
     facet_wrap(vars(Handling, Half), ncol = 2) +
-    theme(legend.key = element_blank(),
-          #legend.position = c(0.9, 0.25),
+    theme(legend.position = "bottom",
+          strip.text.x = element_blank(),
           panel.grid.major = element_blank(), 
@@
           axis.line = element_line(colour = "black"),
-          text = element_text(size = 16)))
+          text = element_text(size = 16))
 
@@
 
-# aand plot
-corrplot(betaMat, 
-         is.corr = F, 
-         p.mat = pvalMat, 
-         outline = T,
-         #insig = "p-value",
-         sig.level = 0.05, 
-         na.label = "square", 
-         na.label.col = "grey",
-         method = "color", 
-         tl.col = "black",
-         tl.cex = 0.8,
-         col = col2(200))
+# # aand plot
+# corrplot(betaMat, 
+#          is.corr = F, 
+#          p.mat = pvalMat, 
+#          outline = T,
+#          #insig = "p-value",
+#          sig.level = 0.05, 
+#          na.label = "square", 
+#          na.label.col = "grey",
+#          method = "color", 
+#          tl.col = "black",
+#          tl.cex = 0.8,
+#          col = col2(200))
 ````
+
+```{r Prepost mixed effects plot (Fig.
+6), fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
+Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands were increasingly discounted over time.
+Right: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately.
+Even though acceptances steadily declined in the effort groups, the relative preferences were preserved."}
+include_graphics("./Images/FIG6.png")
+
+```
 
@@
 ## plot
-(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
   # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
@@
   ylim(0,1.5) +
-  labs(title = "Gamma Values per Group", x = "") +
+  labs(x = "") +
   scale_fill_manual(values = colsBtw) +
@@
         axis.line = element_line(colour = "black"),
-        text = element_text(size = 16)))
+        text = element_text(size = 16))
 
@@
                  group_by(Cost, SubjID) %>%
-                 left_join(summaryOC$pre) %>%
+                 left_join(summaryOC$pre, by = "SubjID") %>%
                  mutate(OC = Handling * Gamma,
@@
 The model predicted the probability of a choice by comparing the estimated OC against each offer amount, and was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
-This single parameter model was able to explain a considerable degree of choice variance (R-squared: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
-The distribution of gamma values are shown on Figure X, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
+This single parameter model was able to explain a considerable degree of choice variance per individual (R-squared: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
+The distribution of gamma values is shown on Figure 7, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
 Values higher than this baseline imply that a condition was costly, whereas lower values suggest that a condition boosted the value of an offer.
-Two-sided one-sample t.test against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
+Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
 Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
 An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, R-squared = `r Rsquared_aov`).
-Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (`r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (`r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (`r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
-In addition, the easy group displayed significantly lower gamma values than the wait group (`r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
+Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
+In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
 Finally, we cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
@@
 
-  Together, these findings suggest that 1) foraging paradigms can provide a reference point to evaluate how different demands modulate value; 2) a simple OC model can approximate people's behavior in such single-option, take it or leave it choices; and 3) even when foraging in environments of equivalent richness, cognifitvely effortful demands can increase the attractiveness of offers rather than discount them (unlike other forms of cost).
+```{r Gamma per cost group (Fig.
+7), fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
+The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
+Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
+
+summaryOC$plot
+
+```
+
+  Together, these findings suggest that 1) foraging paradigms can provide a reference point to evaluate how different demands modulate value; 2) a simple OC model can approximate people's behavior in such single-option, take it or leave it choices; and 3) when foraging in environments of equivalent richness, cognifitvely effortful demands can increase the attractiveness of offers rather than discount them (unlike other forms of cost).
 In the next experiment we explored whether this apparent value was inherent or malleable.

### 2020-04-08 Cost_manuscript.Rmd
methods and results draft (sans OC modeling on cost3)

@@
 ## plot
-earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) +
+earnFitplot_btw <- ggplot(data = temp, aes(pComplete, Earnings)) +
          scale_color_manual(values = colsBtw) +
@@
 # plots generated in 16.2.1. and 16.1.3.
- prop1 | earnings1 | earnFitplot
+ prop1 | earnings1 | earnFitplot_btw
 ```
@@
 col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))
-
-corrplot(mixSummary_btw$Betas, 
-         is.corr = F, 
-         p.mat = mixSummary_btw$Pvals, 
-         type = "lower",
-         outline = T,
-         #insig = "p-value",
-         sig.level = 0.05, 
-         na.label = "square", 
-         na.label.col = "grey",
-         method = "color", 
-         tl.col = "black",
-         tl.cex = 0.8,
-         col = col2(200))
+# 
+# corrplot(mixSummary_btw$Betas, 
+#          is.corr = F, 
+#          p.mat = mixSummary_btw$Pvals, 
+#          type = "lower",
+#          outline = T,
+#          #insig = "p-value",
+#          sig.level = 0.05, 
+#          na.label = "square", 
+#          na.label.col = "grey",
+#          method = "color", 
+#          tl.col = "black",
+#          tl.cex = 0.8,
+#          col = col2(200))
 
@@
 In order to show the comparisons among all conditions, Figure 4B portrays the coefficients (color scale), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
-The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.
+The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) and wait groups ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.
 
@@
 
-``` {r BTW: 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+``` {r BTW: 16.3.2. Plot Pre/Post, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
 # scatter plot of pre/post acceptances
@@
                            theme(legend.key = element_blank(),
-                                 legend.position = c(0.8, 0.25),
+                                 legend.position = c(0.8, 0.3),
                                  panel.grid.major = element_blank(),
@@
 ```
+
+  Before computationally modeling behavior, we asked whether foragers had a stable representation of their environment.
+Since participants had complete a priori knowledge of the statistics of each environment, and were unaware of any other cost groups that could modulate the subjective cost of their assigned demand, we expected them to 1) show confidence in their choices by not quitting mid-handling time; and 2) adopt the same strategy while re-experiencing each environment.
+We investigated the first prediction by plotting a survival curve of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
+This qualitative analysis shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
+Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
+This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code).
+Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure 5, top-right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed.
+These response time observations suggest clarity in participant preferences.
 
@@
 ```
-
-  Before computationally modeling behavior, we asked whether foragers had a stable representation of their environment.
-Since participants had complete a priori knowledge of the statistics of each environment, and were unaware of any other cost groups that could modulate the subjective cost of their assigned demand, we expected them to 1) show confidence in their choices by not quitting mid-handling time; and 2) adopt the same strategy while re-experiencing each environment.
-We investigated the first prediction by plotting a survival curve of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
-This qualitative analysis shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
-Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
-This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code).
-Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure 5, top-right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed.
-These response time observations suggest clarity in participant preferences.
 
@@
 # this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
-prepostPlot <-dataBtw %>%
+hrprepostPlot_btw <-dataBtw %>%
   group_by(SubjID) %>%
@@
 
-``` {r WTH: 16.1.3. prop accept x earnings, echo = FALSE, include = T, fig.align="center",fig.width=4,fig.height=4}
+``` {r WTH: 16.1.3. prop accept x earnings, echo = FALSE, include = T, fig.align="center",fig.width = 4, fig.height = 4}
 # Notes: I also performed this comparing halves and block types x half, and it doesn't look like participants were accepting less to make more.
@@
 # plot
-(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
+earnFitplot_wth <- ggplot(data = temp, aes(pComplete, Earnings)) + 
          scale_color_manual(values = colsWth) + 
@@
            axis.line = element_line(colour = "black"),
-           text = element_text(size = 16)))
+           text = element_text(size = 16))
 
@@
 A Wilcoxon signed rank test showed that individual logistic coefficients for reward amount were significantly greater than 0 (mean $\beta$ = `r round(mean(baseCoeffs$Offer), digits = 2)`, SD = `r round(sd(baseCoeffs$Offer), digits = 2)`; V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* `r report_p(wilcox.test(baseCoeffs$Offer)$p.value)`), once again confirming that participants were properly influenced by reward amounts.
-Adding a coefficient that tracked prior consecutive quits indicated that only `r sum(baseCoeffs$AR_effect)` individuals were influenced by recent quit history, thus discarding systematic sequential effects.
-In terms of earnings, a linear model predicting earnings once again showed that participants who accepted too few or too many trials earned the least, in line with the experimental design (Figure X; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
-When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
+Adding a coefficient that tracked prior consecutive quits indicated that only `r sum(baseCoeffs$AR_effect)` individuals were influenced by recent quit history (95% CI above or below 0), thus discarding systematic sequential effects.
+In terms of earnings, a linear model predicting earnings once again showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
 Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait_C = `r filter(earnings_within, Cost == "Wait_C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait_P = `r filter(earnings_within, Cost == "Wait_P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_P")$sdEarn`).
-These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality (**big caveat: the same percentage can be produced by many non-optimal combinations, including accepting half of each reward.
+These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality (**caveat: the same percentage can be produced by many non-optimal combinations, including accepting half of each reward.
 So neither approach really gets at this too well.**).
@@
 # plot proportion accepted per trial/offer combo
-(n2 <- dataWth %>%
+hrPlot_wth <- dataWth %>%
         filter(Choice < 2) %>%
@@
                 axis.line = element_line(colour = "black"),
-                text = element_text(size = 22)))
+                text = element_text(size = 22))
 
@@
 rearrange <- c("Cognitive", "Wait_C", "Wait_P", "Physical")
-mixSummary <- betaMatrix(mixLogis_main, rearrange = rearrange)
-diag(mixSummary$Pvals) <- NA
+mixSummary_wth <- betaMatrix(mixLogis_main, rearrange = rearrange)
+diag(mixSummary_wth$Pvals) <- NA
 
 # remove uninteresting comparisons
-mixSummary$Betas[rbind(c(3, 1), c(4,2))] <- NA
-mixSummary$Pvals[rbind(c(3, 1), c(4,2))] <- NA
-
-# invert colors
-col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))
-
-corrplot(mixSummary$Betas, 
-         is.corr = F, 
-         p.mat = mixSummary$Pvals, 
-         type = "lower",
-         outline = T,
-         #insig = "p-value",
-         sig.level = 0.05, 
-         na.label = "square", 
-         na.label.col = "grey",
-         method = "color", 
-         tl.col = "black",
-         tl.cex = 0.8,
-         col = col2(200))
-
-```
-
-``` {r WTH: 16.2.2. ME model comparison, echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
+mixSummary_wth$Betas[rbind(c(3, 1), c(4,2))] <- NA
+mixSummary_wth$Pvals[rbind(c(3, 1), c(4,2))] <- NA
+
+# corrplot makes it difficult to use this in complex layouts, so the code has been commented out to save resources
+
+# # invert colors
+# col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))
+
+# corrplot(mixSummary$Betas, 
+#          is.corr = F, 
+#          p.mat = mixSummary$Pvals, 
+#          type = "lower",
+#          outline = T,
+#          #insig = "p-value",
+#          sig.level = 0.05, 
+#          na.label = "square", 
+#          na.label.col = "grey",
+#          method = "color", 
+#          tl.col = "black",
+#          tl.cex = 0.8,
+#          col = col2(200))
+
+```
+
+``` {r WTH: 16.2.2. ME model comparison, echo = FALSE, fig.align="center", fig.width = 6, fig.height = 4}
 # fit ME logistic at increasing model complexities
@@
 # plot 
-(mixLogis_compare$plot <- abicLogis_compare %>% 
+mixLogis_compare$plot <- abicLogis_compare %>% 
   gather(Comparison, Value, AIC:BIC) %>%
@@
     geom_point(color = "black", pch = 21, size = 3) +
-    theme_classic())
+    theme(legend.position = c(0.8, 0.8),
+      legend.key = element_blank(),
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      panel.background = element_blank(),
+      axis.line = element_line(colour = "black"),
+      text = element_text(size = 16))
 
@@
   Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
-As can be seen on Figure X, even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure X), differences among cost conditions were less evident.
+As can be seen on Figure 8B, even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 4A), differences among cost conditions were less evident.
 Moreover, these differences contradicted our predictions, as cognitive effort remained as the least costly type of demand.
@@
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`).
-As in the previous section, pairwise comparison results are shown on the matrix in Figure X.
-This plot omits comparisons between effort and wait trials from different blocks, as these are not considered in our original predictions **(rephrase, with the understanding that Wait_C > Physical)**.
-The only significant difference was the higher likelihood to accept cognitive offers compared to physical ones ($\beta$ = `r round(mixSummary$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary$Pvals["Physical", "Cognitive"])`).
+As in the previous section, pairwise comparison results are shown on the matrix in Figure 8C.
+This plot omits comparisons between effort and wait trials from different blocks, as these are not considered in our original predictions.
+The only significant difference was the higher likelihood to accept cognitive offers compared to physical ones ($\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
 This initial result suggests that differences in cost decrease if individuals are able to evaluate all of them.
 
+```{r Earnings, prop completed, ME plots (Fig.
+8), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
+B: proportion of acceptances of each reward per cost condition.
+C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount).
+Crosses mark non-significant comparisons.
+D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}
+
+include_graphics("./Images/FIG8.png")
+```
+
   We then repeated the model comparison approach from the between-subject section, evaluating models ranging in complexity from intercept-only to a two-way interaction between cost and reward.
-Even though the a priori model with all main effects explained a large portion of the variance (`r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure X).
-An analysis of deviance among the three models showed that adding cost condition to reward amount significantly reduced model deviance (AIC~a_priori~ = `r abicLogis_compare["AllMain", "AIC"]`, AIC~reward~ = `r abicLogis_compare["Reward", "AIC"]`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r mixLogis_compare$aod$Chisq[2]`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`).
-However, probing the interaction between these features significantly improved fits further (AIC~Interaction~ = `r abicLogis_compare["Interaction", "AIC"]`, $\chi^2$(`r mixLogis_compare$aod[[7]][3]`) = `r mixLogis_compare$aod$Chisq[3]`, *p* `r report_p(mixLogis_compare$aod[[8]][3])`).
+Even though the a priori model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 8D).
+An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r round(mixLogis_compare$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`).
+However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][3]`) = `r round(mixLogis_compare$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][3])`).
 (**discuss with Joe: the interaction flips results over, such that both waits > pysical effort = cognitive effort...as predicted originally?
@@
 
-``` {r WTH: 16.3.1. RT, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+``` {r WTH: 16.3.1. surv and RT, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4, include = FALSE}
 # Survival curve for quits and response time ECDFs across blocks
@@
   labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
-  theme(legend.position = c(0.8, 0.3),
+  theme(legend.position = "none",
         panel.grid.major = element_blank(),
@@
 
-survPlot_wth | RTplot_wth
 ```
@@
 Participants could quit either during the offer period (2 s) or during the handling time (10 s), allowing for a total of 12 seconds to give up on the current trial.
-The survival curve on Figure X shows quitting throughout the trial for all participants.
+The survival curve on Figure 9A shows quitting instances within trials for all participants.
 Censored points signal completions (at end of interval) and forced travels (throughout the trial).
 Similar to before, the survival analysis suggests that participants made most of their choices quickly within the offer window.
-In fact, the mean percentage of quits during the handling time was `r round(mean(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 0.2)` participants quitting over 20% of trials during the handling time.
-Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure X).
+In fact, the mean percentage of quits during the handling time was `r round(mean(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 20)` participants quitting over 20% of trials during the handling time.
+Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure 9B).
 Once in the handling time, the overall proportion of forced travels in the effortful trials was relatively low for both cognitive (mean = `r round(mean(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (mean = `r round(mean(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
@@
 # acceptances across blocks
-propBlocks <- dataWth %>%
+prepost_wth$propBlocks <- dataWth %>%
     filter(Choice < 2) %>%
@@
       theme(legend.key = element_blank(),
-         legend.position = c(0.8, 0.25),
+         legend.position = c(0.8, 0.3),
          panel.grid.major = element_blank(),
@@
 
-mid <- dataWth %>%
+prepost_wth$scatterplot <- dataWth %>%
   filter(Choice < 2, !(Block %in% c(3,4))) %>%
@@
        text = element_text(size = 16))
-
-mid | propBlocks
 
@@
 
-(hrPlot_wth <- dataWth %>%
+hrprepostPlot_wth <- dataWth %>%
   group_by(SubjID) %>%
@@
   filter(Block != 2) %>%
-  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
+  mutate(Block = ifelse(Block == 1, "First Two Blocks", "Last Two Blocks")) %>%
   group_by(Cost, Block, Offer) %>%
@@
 # aand plot
-corrplot(betaMat, 
-         is.corr = F, 
-         p.mat = pvalMat, 
-         outline = T,
-         #insig = "p-value",
-         sig.level = 0.05, 
-         na.label = "square", 
-         na.label.col = "grey",
-         method = "color", 
-         tl.col = "black",
-         tl.cex = 0.8,
-         col = col2(200))
+# corrplot(betaMat, 
+#          is.corr = F, 
+#          p.mat = pvalMat, 
+#          outline = T,
+#          #insig = "p-value",
+#          sig.level = 0.05, 
+#          na.label = "square", 
+#          na.label.col = "grey",
+#          method = "color", 
+#          tl.col = "black",
+#          tl.cex = 0.8,
+#          col = col2(200))
 ```
@@
 
-  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])` Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])` Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait_C:  mean~pre~ = `r filter(df_mean, Cost == "Wait_C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait_C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait_C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait_C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait_C"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait_C"]], digits = 2)`; Wait_P: mean~pre~ = `r filter(df_mean, Cost == "Wait_P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait_P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait_P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait_P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait_P"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait_P"]], digits = 2)`; Figure X).
-The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson R = `r round(corDiff, digits = 2)`, *p* > 0.05).
-Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure X).
+```{r Survival and prepost plots (Fig.
+9), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
+Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
+Dashed lines indicate the mean for each cost.
+On the right, the proportion accepted every time participants experienced a given block type."}
+# plots generated in 16.3.1. and 16.3.3.
+(suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
+```
+
+  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])` Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])` Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait_C:  mean~pre~ = `r filter(df_mean, Cost == "Wait_C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait_C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait_C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait_C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait_C"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait_C"]], digits = 2)`; Wait_P: mean~pre~ = `r filter(df_mean, Cost == "Wait_P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait_P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait_P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait_P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait_P"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait_P"]], digits = 2)`; Figure 10).
+The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson's r = `r round(corDiff, digits = 2)`, *p* > 0.05).
+Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure 4A).
 Mixed effects logistic regressions on each half separately confirmed this observation.
-The matrix on Figure X shows the coefficient magnitude for all pairwise comparisons among costs (computed by rotating the reference cost condition in the model), with crosses signaling non-significant coefficients (*p* > 0.05).
+The matrix on Figure 10 shows the coefficient magnitude for all pairwise comparisons among costs (computed by rotating the reference cost condition in the model), with crosses signaling non-significant coefficients (*p* > 0.05).
 This plot shows that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).
+
+```{r Prepost mixed effects plots (Fig.
+10), fig.align = "center", fig.cap = "Acceptance rates over time.
+Left: Proportion accepted in the first two and last two blocks of the experiment.
+An initial preference for cognitive effort trials fades amid a global decrease in acceptance rates.
+Right: Mixed effects coefficient matrix for each half separately.
+The pattern from the first half resembles what was observed in the between-subjects experiment."}
+include_graphics("./Images/FIG10.png")
+
+```
 
@@
 # plot
-(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
     geom_boxplot(show.legend = F) +
@@
 # plot prediction %
-qplot(Cost, predicted, geom = "boxplot", data = temp) + 
-  ylim(0,1) +
-  theme_classic()
+# qplot(Cost, predicted, geom = "boxplot", data = temp) + 
+#   ylim(0,1) +
+#   theme_classic()
 ```
@@
 # table
-pander(OCs_anova$aov)
+#pander(OCs_anova$aov)
 
 # do all pairwise comparisons
-OCs_anova$gammas <- summaryOC$all %>% 
+OCs_anova$gammas <- summaryOC$all %>% 
   reshape2::dcast(SubjID ~ Cost, value.var = "Gamma") %>%
@@
 ``` {r WTH: 16.3.6. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
-corrplot(OCs_anova$ES,
-         is.corr = F, 
-         p.mat = OCs_anova$perms,
-         type = "upper",
-         insig = "p-value",
-         sig.level = -1,
-         na.label = "square",
-         na.label.col = "grey",
-         method = "color", 
-         tl.col = "black", 
-         tl.cex = 0.8,
-         outline = T)
+# corrplot(OCs_anova$ES,
+#          is.corr = F, 
+#          p.mat = OCs_anova$perms,
+#          type = "upper",
+#          insig = "p-value",
+#          sig.level = -1,
+#          na.label = "square",
+#          na.label.col = "grey",
+#          method = "color", 
+#          tl.col = "black", 
+#          tl.cex = 0.8,
+#          outline = T)
 ```

### 2020-04-08 Cost_manuscript.Rmd
changed the cost3 wait labels to be more presentable

@@
 # parameter recovery function
-test_params <- function(params = list(Gamma = 1), model = expr(params$Gamma * Handling), subjData, handling = c(2, 10, 14), offer = c(4, 8, 20), plot = F) {
+testParams <- function(params = list(Gamma = 1), model = expr(params$Gamma * Handling), subjData, handling = c(2, 10, 14), offer = c(4, 8, 20), plot = F) {
 
@@
          Choice = ifelse(Choice == 2, 1, Choice),
-         Cost = case_when(Cost == "WAIT_0" ~ "Wait_C",
+         Cost = case_when(Cost == "WAIT_0" ~ "Wait-C",
                            Cost == "COGNITIVE_0" ~ "Cognitive",
                            Cost == "GRIP_1" ~ "Physical",
-                           Cost == "WAIT_1" ~ "Wait_P"),
+                           Cost == "WAIT_1" ~ "Wait-P"),
          Cost = as.factor(Cost)) %>%
@@
 We refer to observations from each block's wait trials by their effort pair (i.e.
-"Wait_C" for cognitive, and "Wait_P" for physical).
+"Wait-C" for cognitive, and "Wait-P" for physical).
 Finally, in this experiment the handling and travel times were fixed at 10 s and 6 s, respectively.
@@
 When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
-Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait_C = `r filter(earnings_within, Cost == "Wait_C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait_P = `r filter(earnings_within, Cost == "Wait_P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_P")$sdEarn`).
+Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-C = `r filter(earnings_within, Cost == "Wait-C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-P = `r filter(earnings_within, Cost == "Wait-P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-P")$sdEarn`).
 These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality (**caveat: the same percentage can be produced by many non-optimal combinations, including accepting half of each reward.
@@
 mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
-mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
-mixLogis_main$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
-mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
-mixLogis_main$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-C"))
+mixLogis_main$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-P"))
+mixLogis_main$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
@@
 # get summary of coeffs
-rearrange <- c("Cognitive", "Wait_C", "Wait_P", "Physical")
+rearrange <- c("Cognitive", "Wait-C", "Wait-P", "Physical")
 mixSummary_wth <- betaMatrix(mixLogis_main, rearrange = rearrange)
@@
 propFails_wth <- dataWth %>%
-  filter(!Cost %in% c("Wait_C", "Wait_P")) %>%
+  filter(!Cost %in% c("Wait-C", "Wait-P")) %>%
   group_by(SubjID, Cost) %>%
@@
 #   filter(Block < 3) %>%
-#   mutate(Cost2 = ifelse(Cost %in% c("Wait_P", "Wait_C"), "Wait", Cost)) %>%
+#   mutate(Cost2 = ifelse(Cost %in% c("Wait-P", "Wait-C"), "Wait", Cost)) %>%
 #   group_by(SubjID, Cost2) %>%
@@
 #   filter(Choice < 2) %>%
-#   mutate(Cost2 = ifelse(!(Cost %in%  c("Wait_C", "Wait_P")), "EFFORT", "WAIT"),
+#   mutate(Cost2 = ifelse(!(Cost %in%  c("Wait-C", "Wait-P")), "EFFORT", "WAIT"),
 #          BlockType = ifelse(gsub(".*_", "", Cost) == 1, "Physical", "Cognitive")) %>%
@@
 #   mutate(Type = ifelse(Cost %in% c("Cognitive", "Physical"), "Effort", "Delay"),
-#          Cost = ifelse(Cost %in% c("Cognitive", "Wait_C"), "Cognitive", "Physical")) %>%
+#          Cost = ifelse(Cost %in% c("Cognitive", "Wait-C"), "Cognitive", "Physical")) %>%
 #   spread(Type, Diffscore) %>%
@@
 mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
-mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
-mixLogis_pre$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
-mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
-mixLogis_pre$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-C"))
+mixLogis_pre$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-P"))
+mixLogis_pre$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
@@
 mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
-mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
-mixLogis_post$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
-mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
-mixLogis_post$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-C"))
+mixLogis_post$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-P"))
+mixLogis_post$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
@@
 #   spread(Cost, diff) %>%
-#   ggplot(aes(Cognitive, Wait_C, fill = as.character(Offer))) +
+#   ggplot(aes(Cognitive, Wait-C, fill = as.character(Offer))) +
 #     geom_point(pch = 21, color = "black", size = 3) +
@@
 #          x = "P(Cognitive): Last - First",
-#          y = "P(Wait_C): Last - First",
+#          y = "P(Wait-C): Last - First",
 #          fill = "Offer") +
@@
 #   spread(Cost, diff) %>%
-#   ggplot(aes(Physical, Wait_P, fill = as.character(Offer))) +
+#   ggplot(aes(Physical, Wait-P, fill = as.character(Offer))) +
 #     geom_point(pch = 21, color = "black", size = 3, show.legend = F) +
@@
 #          x = "P(Physical): Last - First",
-#          y = "P(Wait_P): Last - First",
+#          y = "P(Wait-P): Last - First",
 #          fill = "Offer") +
@@
 #   ggplot() +
-#     geom_point(aes(Cognitive, Wait_C), color = colsWth[1]) +
-#     geom_point(aes(Physical, Wait_P), color = colsWth[2]) +
+#     geom_point(aes(Cognitive, Wait-C), color = colsWth[1]) +
+#     geom_point(aes(Physical, Wait-P), color = colsWth[2]) +
 #     geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
@@
 
-  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])` Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])` Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait_C:  mean~pre~ = `r filter(df_mean, Cost == "Wait_C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait_C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait_C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait_C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait_C"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait_C"]], digits = 2)`; Wait_P: mean~pre~ = `r filter(df_mean, Cost == "Wait_P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait_P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait_P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait_P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait_P"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait_P"]], digits = 2)`; Figure 10).
+  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])` Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])` Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 10).
 The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson's r = `r round(corDiff, digits = 2)`, *p* > 0.05).
@@
 OCs_validation <- list()
-temp <- dataTrain %>% filter(Cost == "Wait_C") %>% plyr::dlply("SubjID", identity)
-OCs_validation$Wait_C <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-temp <- dataTrain %>% filter(Cost == "Wait_P") %>% plyr::dlply("SubjID", identity)
-OCs_validation$Wait_P <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+temp <- dataTrain %>% filter(Cost == "Wait-C") %>% plyr::dlply("SubjID", identity)
+OCs_validation$`Wait-C` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+temp <- dataTrain %>% filter(Cost == "Wait-P") %>% plyr::dlply("SubjID", identity)
+OCs_validation$`Wait-P` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
 temp <- dataTrain %>% filter(Cost == "Cognitive") %>% plyr::dlply("SubjID", identity)
@@
   mutate(SubjID = subjList_wth) %>%
-  gather(Cost, gamma, Wait_C:Physical) %>%
+  gather(Cost, gamma, `Wait-C`:Physical) %>%
   left_join(dataTest, ., by = c("SubjID", "Cost")) %>% # assign OCs to each subject per cost type
@@
 # do all pairwise comparisons
-OCs_anova$gammas <- summaryOC$all %>% 
+OCs_anova$gammas <- summaryOC$all %>% 
   reshape2::dcast(SubjID ~ Cost, value.var = "Gamma") %>%

### 2020-04-27 Cost_manuscript.Rmd
modeling advances

@@
                          axis.line = element_line(colour = "black"),
-                         text = element_text(size = 16))
+                         text = element_text(size = 22))
 ```
@@
 # travel <- c(2, 6, 14) + 2
-# sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
+# rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
 # 
@@
 #     ylim(0, 1.2) +
-#     labs(y = "Expected eward per sec.", x = "Reward acceptance threshold") +
+#     labs(y = "Expected reward per sec.", x = "Reward acceptance threshold") +
 #     theme(legend.position = c(0.85, 0.2),
@@
 While all main effects were significant, there was an unexpected significant condition-by-reward interaction, which could be due to the performance of the "easy" group relative to their peers.
-Importantly, we found that the interaction between all three main parameters was not significant, thus suggesting that the effects of handling and reward on choices were not different across groups.
+Importantly, we found that the interaction between all three main parameters was not significant, thus suggesting that the effects of handling and reward on choices were not different across groups.
 
@@
             axis.line = element_line(colour = "black"),
-            text = element_text(size = 16))
+            text = element_text(size = 22))
 
@@
 #          tl.cex = 0.8,
+#          cl.length = 5,
+#          cl.lim = c(-2.0001, 2.0001),
 #          col = col2(200))
@@
 ## Discussion
+
+- Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort
+- It's true that we didnt calibrate cog effort per subject.
+But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.

### 2020-04-27 Simulations/manuscript_modeling.R

@@ -1,0 +1,34 @@
+
+summaryOC <- list()
+summaryOC$all <- dataWth %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  group_by(SubjID, Cost, Half) %>% #group_by(SubjID, Cost, Block) %>%
+  do(optimizeOCModel(., simplify = T)) %>%
+  ungroup()
+
+# plot
+(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+  geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1, linetype = "dashed") +
+  geom_jitter(pch = 21, size = 3, show.legend = F) +
+  ylim(0, 1.5) +
+  labs(x = "") +
+  scale_fill_manual(values = colsWth) +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 16)))
+
+summaryOC$all %>%
+  select(SubjID, Cost, Gamma, Half) %>% 
+  spread(Half, Gamma) %>%
+  ggplot(aes(Half_1, Half_2, fill = Cost)) +
+    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
+    geom_point(pch = 21, color = "black", size = 3) +
+    ylim(0, 2) +
+    xlim(0, 2) +
+    theme_minimal()

### 2020-04-27 Simulations/wikenheiser.R

@@ -1,0 +1,125 @@
+
+library(tidyverse)
+library(data.table)
+
+# basic calculation
+offer <- c(4, 8, 20)
+handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
+travel <- c(2, 6, 14) + 2
+offerRates_basic <- sapply(3:1, function(thresh) {(sum(tail(offer, n = thresh))) / ((handling * thresh) + (travel * 3))}) # good
+
+
+# new stuff
+pmat <- rbind(c(1, 1, 1),
+              c(0, 1, 1),
+              c(0, 0, 1))
+A <- seq(0, 1.5, length.out = 4)
+
+
+## single example comparing the two at a single acceptance strategy
+p <- pmat[1, ]
+
+# basic numerator
+bn <- (offer %*% p)
+
+# wikenheiser version
+wn <- (offer %*% p) - ((offer %*% (1 - p)) * A)  
+
+# basic denominator
+bd <- ((handling * sum(p)) + (travel * 3)) #
+
+# adapted wikenheiser numerator (since our participants don't select among delays, calculate per handling time)
+wd <- (1 + (handling * sum(p)))
+
+
+## loop through every possible combination 
+# eventually mapply()
+modeledRates <- list()
+
+for (iter in seq_along(A)) {
+  
+  a <- A[iter]
+  
+  rstore <- matrix(0, 3, 3)
+    
+  for (prow in 1:nrow(pmat)) {
+    
+    # acceptances (binary per reward)
+    p <- pmat[prow, ]
+    
+    # numerator from wikenheiser, denominator from us
+    wn <- (offer %*% p) - ((offer %*% (1 - p)) * a)  
+    bd <- ((handling * sum(p)) + (travel * 3))
+    
+    # model
+    rstore[, prow] <- wn[1, 1] / bd
+
+  }
+  
+  # clean up into a dataframe with info
+  rstore <- as.data.frame(rstore)
+  colnames(rstore) <- offer
+  rstore$H <- handling
+  modeledRates[[iter]] <- rstore
+  
+}
+
+offerRates_wik <- do.call(rbind, modeledRates) %>%
+  mutate(A = rep(A, each = 3)) %>%
+  gather(O, Rate, -c(H:A)) %>%
+  mutate(A = as.character(A),
+         O = factor(O, levels = list(4, 8, 20)),
+         H = factor(H, levels = list(4, 12, 16)))
+
+
+## plots
+
+# earnings per acceptance threshold
[…]

### 2020-04-29 Cost_manuscript.Rmd
fixed a participant time log and added performance check plots (prepost)

@@
 
+# load the cognitive task performance logs
+setwd("./extras")
+files <- dir(pattern = '_log.csv')
+
+dataBtw_coglogs <- tibble(SubjID = files) %>%
+  mutate(contents = map(SubjID, ~ suppressWarnings(read_csv(., col_types = cols()))))  %>%
+  unnest() %>%
+  rename(Offer = Reward) %>%
+  mutate(SubjID = substring(SubjID, 8, 10),
+         Trial_Time = round(Choice.RT),
+         Choice = ifelse(Choice == 2, 1, Choice), # forced travels (2) become acceptances (1)
+         Half = ifelse(Block < 4, "Half_1", "Half_2"),
+         optimal = case_when(
+          (Handling == 10 & Offer < 8) ~ 0,
+          (Handling == 14 & Offer < 20) ~ 0,
+          TRUE ~ 1
+          )
+         )
+
 # get a simple subject list and the number of subjects
@@
   mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st"))
+
+# load the cognitive task performance logs
+files <- dir(pattern = 'coglog')
+colname <- c("Handling", "Offer", "Outcome", "RT", "Trial_Time", "ExpTime", "Trial_outcome","Type", "Setup")
+
+dataWth_coglogs <- data_frame(SubjID = files) %>% 
+  mutate(contents = map(SubjID, ~ suppressWarnings(read_csv(., col_names = colname, col_types = cols()))),
+         SubjID = substring(SubjID, 8, 10)) %>%
+  unnest() %>%
+  mutate(Trial_time = ifelse(RT > 10.1, 10, RT),
+         Trial_Time = round(Trial_Time)) %>%
+  group_by(SubjID) %>%
+  mutate(Half = ifelse(ExpTime < (max(ExpTime) / 2), "Half_1", "Half_2")) %>%
+  ungroup()
 
@@
                                  text = element_text(size = 14))
+
+# RTs for the cognitive tasks as a function of handling time, offer, and experimental half
+prepost_btw$cogtaskRTs <- dataBtw_coglogs %>%
+  filter(Choice == 1,
+         Handling > 2) %>%
+  group_by(SubjID, Handling, Offer, Trial_Time, Half) %>%
+  summarise(mRT = mean(Task.RT)) %>%
+  group_by(Handling, Offer, Trial_Time, Half) %>%
+  summarise(meanRT = mean(mRT),
+            seRT = sd(mRT, na.rm = T) / sqrt(21)) %>%
+  ungroup() %>%
+  mutate(Offer = factor(Offer, levels = c(4, 8, 20))) %>% 
+  ggplot(aes(Trial_Time, meanRT, group = Offer, color = Offer)) +
+    geom_line() +
+    geom_line(aes(Trial_Time, meanRT + seRT, group = Offer, color = Offer), linetype = "dashed") +
+    geom_line(aes(Trial_Time, meanRT - seRT, group = Offer, color = Offer), linetype = "dashed") +
+    geom_point(size = 2) +
+    ylim(0.2, 1) +
+    facet_wrap(vars(Handling, Half)) +
+    theme_classic()
 
@@
        text = element_text(size = 16))
+
+prepost_wth$cogtaskRTs <- dataWth_coglogs %>%
+  filter(Outcome > 0) %>%
+  mutate(Outcome = ifelse(Outcome == 2, 0, Outcome)) %>%
+  group_by(SubjID, Offer, Trial_Time, Half) %>%
+  summarise(mRT = mean(RT),
+            pComplete = mean(Outcome)) %>%
+  group_by(Offer, Trial_Time, Half) %>%
+  summarise(meanRT = mean(mRT),
+            seRT = sd(mRT, na.rm = T) / sqrt(48),
+            meanProp = mean(pComplete),
+            seProp = sd(pComplete) / sqrt(48)) %>%
+  ungroup() %>%
+  mutate(Offer = factor(Offer, levels = c(4, 8, 20))) %>%
+  ggplot(aes(Trial_Time, meanRT, group = Offer, color = Offer)) +
+    geom_line() +
+    geom_line(aes(Trial_Time, meanRT + seRT, group = Offer, color = Offer), linetype = "dashed") +
+    geom_line(aes(Trial_Time, meanRT - seRT, group = Offer, color = Offer), linetype = "dashed") +
+    geom_point(size = 2) +
+    ylim(0.2, 1) +
+    facet_wrap(vars(Half)) +
+    theme_classic()
 

### 2020-05-12 Cost_manuscript.Rmd
updates on modeling tryouts

@@
 All experimental procedures were approved by the Boston University Institutional Review Board, and written consent was acquired for all participants.
-For the between-subject experiment, we recruited individuals until a desired number of 84 eligible participants was achieved (58 Female, median age = 21, range = 18 - 31; number excluded before reaching goal = XX).
+For the between-subject experiment, we recruited individuals until a desired number of 84 eligible participants was achieved (58 Female, median age = 21, range = 18 - 31; number excluded before reaching goal = 8).
 The sample size was determined by means of power analysis (ANOVA), using a significance level of 0.05, power of 0.8, an effect size of f = 0.45 (calculated from a pilot study), and three groups (one for each cost type).
@@
 We excluded participant datasets based on four preregistered criteria: 1) Consent: If they withdrew their participation; 2) Inattentiveness: a catch trial was placed at the end of each experimental block, asking participants to press a key within 3 seconds (time requirement based on pilot study response times).
-A participant that failed two or more of these checks was excluded and replaced.
+A participant who failed two or more of these checks was excluded and replaced.
 3) Improbable choice behavior: The task was structured so that one reward amount must always be accepted.
@@
 
-  We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36).
+  We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36; number excluded before reaching goal = 6).
 Sample size was once again determined by means of a power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each condition).

### 2020-05-12 Simulations/manuscript_modeling.R

@@ -1,3 +1,122 @@
+# OC-specific computation of the negative log likelihood for model optimization
+negLogLik <- function(params, choice, handling, reward) {
+  gamma <- exp(params[2]) * handling
+  model <- exp(params[1]) * (reward - gamma)
+  p = 1 / (1 + exp(-model))
+  p[p == 1] <- 0.999
+  p[p == 0] <- 0.001
+  tempChoice <- rep(NA, length(choice))
+  tempChoice[choice == 1] <- log(p[choice == 1])
+  tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
+  negLL <- -sum(tempChoice)
+  return(negLL)
+}
+
+model <- expr(exp(params$temp) * (reward - (params$gamma * handling)))
+
+negLogLik <- function(params, choice, handling, reward) {
+  gamma <- exp(params[2]) * handling
+  #model <- exp(params[1]) * (reward - gamma)
+  p = 1 / (1 + exp(-eval(model)))
+  p[p == 1] <- 0.999
+  p[p == 0] <- 0.001
+  tempChoice <- rep(NA, length(choice))
+  tempChoice[choice == 1] <- log(p[choice == 1])
+  tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
+  negLL <- -sum(tempChoice)
+  return(negLL)
+}
+
+
+
+# optimize the OC model
+optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA", simplify = F, model = negLogLik, params = ) {
+
+  # Data: The participant's log
+  # Algorithm: probably let be
+  # model: an external function to minimize (in this case OC, separately defined as negloglik)
+
+  # Prep data
+  handling <- Data$Handling
+  reward <- Data$Offer
+  choice <- Data$Choice
+
+  # Prep list of results to be returned
+  out <- list()
+  out$percentQuit <- mean(choice == 0) * 100
+  out$percentAccept <- mean(choice == 1) * 100
+  miss <- (choice != 1) & (choice != 0)
+  out$percentMiss <- mean(miss)  * 100
+  choice <- choice[!miss]
+  reward <- as.numeric(reward[!miss])
+  handling <- as.numeric(handling[!miss])
+
+  # Establish lower and upper bounds
+  LB <- round(log((min(reward)/max(handling)) * 0.99), digits = 4)
[…]

### 2020-05-12 Simulations/manuscript_modeling.R
got rid of nloptr

@@ -1,22 +1,12 @@
-# OC-specific computation of the negative log likelihood for model optimization
-negLogLik <- function(params, choice, handling, reward) {
-  gamma <- exp(params[2]) * handling
-  model <- exp(params[1]) * (reward - gamma)
-  p = 1 / (1 + exp(-model))
-  p[p == 1] <- 0.999
-  p[p == 0] <- 0.001
-  tempChoice <- rep(NA, length(choice))
-  tempChoice[choice == 1] <- log(p[choice == 1])
-  tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
-  negLL <- -sum(tempChoice)
-  return(negLL)
-}
 
-model <- expr(exp(params$temp) * (reward - (params$gamma * handling)))
+# using NLOPTR is pointless here
+# instead I'm just going to feed any sensible combination of parameters to the model and minimize the negLL manually
+# simpler, can evaluate models easier, and faster
+# for tomorrow: have negloglik return the parameters per iteration
+# the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
+# maybe also R-squares and things in the current optimization function
 
-negLogLik <- function(params, choice, handling, reward) {
-  gamma <- exp(params[2]) * handling
-  #model <- exp(params[1]) * (reward - gamma)
+negLogLik <- function(params, model, choice, handling, reward) {
   p = 1 / (1 + exp(-eval(model)))
   p[p == 1] <- 0.999
   p[p == 0] <- 0.001
@@ -27,141 +17,78 @@ negLogLik <- function(params, choice, handling, reward) {
   return(negLL)
 }
 
-
-
-# optimize the OC model
-optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA", simplify = F, model = negLogLik, params = ) {
-
-  # Data: The participant's log
-  # Algorithm: probably let be
-  # model: an external function to minimize (in this case OC, separately defined as negloglik)
-
-  # Prep data
-  handling <- Data$Handling
-  reward <- Data$Offer
-  choice <- Data$Choice
-
-  # Prep list of results to be returned
-  out <- list()
-  out$percentQuit <- mean(choice == 0) * 100
[…]

### 2020-05-13 Simulations/manuscript_modeling.R
for loop

@@ -6,14 +6,23 @@
 # the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
 # maybe also R-squares and things in the current optimization function
 
-negLogLik <- function(params, model, choice, handling, reward) {
-  p = 1 / (1 + exp(-eval(model)))
-  p[p == 1] <- 0.999
-  p[p == 0] <- 0.001
-  tempChoice <- rep(NA, length(choice))
-  tempChoice[choice == 1] <- log(p[choice == 1])
-  tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
-  negLL <- -sum(tempChoice)
+negLogLik <- function(subjData, params, model) {
+  
+  handling <- subjData$Handling
+  reward <- subjData$Offer
+  choice <- subjData$Choice
+  
+  LLs <- apply(params, 2, function(i) {
+    p = 1 / (1 + exp(-eval(model)))
+    p[p == 1] <- 0.999
+    p[p == 0] <- 0.001
+    tempChoice <- rep(NA, length(choice))
+    tempChoice[choice == 1] <- log(p[choice == 1])
+    tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
+    negLL <- -sum(tempChoice)
+  })
+    
+    
   return(negLL)
 }
 
@@ -30,9 +39,7 @@ params_grid <- as.matrix(expand.grid(params))
 subj <- 190
 Data <- dataBtw %>%
   filter(SubjID == subj)
-handling <- Data$Handling
-reward <- Data$Offer
-choice <- Data$Choice
+
 
 t <- sapply(seq(nrow(params_grid)), function(i) negLogLik(params_grid[i, ], model_expr, choice, handling, reward))
 

### 2020-05-13 Simulations/manuscript_modeling.R
new, simpler optimization function

@@ -6,16 +6,43 @@
 # the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
 # maybe also R-squares and things in the current optimization function
 
-negLogLik <- function(subjData, params, model) {
+
+
   
+negLogLik <- function(subjData, params, model) {
+  # this function finds the combination of parameter values that minimizes the neg log likelihood of a logistic regression
+  # used to rely on NLOPTR, but it's too cumbersome for the low-dimensional estimates I'm performing.
+  #
+  # subjData: a participant's log
+  # params: a list of vectors. Each vector is the possible values a given parameter can take. Names in list must match model expression
+  # model: using `expr()`, define the model (use <param>[[1]] for free parameters to be estimated. R limitation.)
+  
+  
+  # extract basic choice information
   handling <- subjData$Handling
   reward <- subjData$Offer
   choice <- subjData$Choice
+  rt <- subjData$RT
+  cost <- subjData$Cost
+  trial <- subjData$TrialN
   
-  LLs <- apply(params, 2, function(i) {
-    p = 1 / (1 + exp(-eval(model)))
+  # combine parameters into every possible combination
+  params <- expand.grid(params)
+  
+  LLs <- sapply(seq(nrow(params)), function(i) {
+    
+    # isolate the parameters for this iteration
+    # and then store them as variables
+    # FIGURE OUT HOW TO NOT STORE THEM AS DATAFRAMES
+    pars <- params_grid[i, ]
+    lapply(seq_along(pars), function(variable) {assign(colnames(pars)[variable], pars[variable], envir = .GlobalEnv)})
+    
+    # estimate the probability of acceptance per the model
+    p = 1 / (1 + exp(-eval(model_expr)))
     p[p == 1] <- 0.999
     p[p == 0] <- 0.001
+    
+    # get the likelihood of the observations based on the model
     tempChoice <- rep(NA, length(choice))
     tempChoice[choice == 1] <- log(p[choice == 1])
     tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
@@ -23,25 +50,29 @@ negLogLik <- function(subjData, params, model) {
   })
     
     
-  return(negLL)
+  return(LLs)
 }
 
 # model to be fit
-model_expr <- expr(params["temp"] * (reward - (params["gamma"] * handling)))
[…]

### 2020-05-13 Cost_manuscript.Rmd
no more NLOPTR. Slower manual solution allows for more flexible model input and variant testing

@@
 
+}
+
+# simpler form of optimization that allows inputting any model expression into a single function call
+optimizeModel <- function(subjData, params, model, simplify = F) {
+  # this function finds the combination of parameter values that minimizes the neg log likelihood of a logistic regression
+  # used to rely on NLOPTR, but it's too cumbersome for the low-dimensional estimates I'm performing.
+  #
+  # subjData: a participant's log
+  # params: a list of vectors. Each vector is the possible values a given parameter can take. Names in list must match model expression
+  # model: using `expr()`, define the model (use <param>[[1]] for free parameters to be estimated. R limitation.). Ex: expr(temp[[1]] * (reward - (gamma[[1]] * handling)))
+
+  # extract basic choice information
+  handling <- subjData$Handling
+  reward <- subjData$Offer
+  choice <- subjData$Choice
+  rt <- subjData$RT
+  cost <- subjData$Cost
+  trial <- subjData$TrialN
+  rawChoice <- subjData$rawChoice
+
+  # combine parameters into every possible combination
+  params <- expand.grid(params)
+
+  # Prep list of results to be returned
+  out <- list()
+  out$percentQuit <- mean(choice == 0) * 100
+  out$percentAccept <- mean(choice == 1) * 100
+
+  LLs <- sapply(seq(nrow(params)), function(i) {
+
+    # isolate the parameters for this iteration
+    # and then store them as variables
+    # FIGURE OUT HOW TO NOT STORE THEM AS DATAFRAMES
+    pars <- params[i, ]
+    lapply(seq_along(pars), function(variable) {assign(colnames(pars)[variable], pars[variable], envir = .GlobalEnv)})
+
+    # estimate the probability of acceptance per the model
+    p = 1 / (1 + exp(-eval(model)))
+    p[p == 1] <- 0.999
+    p[p == 0] <- 0.001
+
+    # get the likelihood of the observations based on the model
+    tempChoice <- rep(NA, length(choice))
+    tempChoice[choice == 1] <- log(p[choice == 1])
+    tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
+    negLL <- -sum(tempChoice)
+  })
+
+  # chosen parameters  
+  out$LL <- min(LLs)
+  chosen_params <- params[which(LLs == out$LL), ]
+  lapply(seq_along(chosen_params), function(variable) {assign(colnames(chosen_params)[variable], chosen_params[variable], envir = .GlobalEnv)})
+
+  # Summarize the outputs
+  out$LL0 <- -(log(0.5) * length(choice))
+  out$Rsquared <- 1 - (out$LL / out$LL0) # pseudo r-squred, quantifying the proportion of deviance reduction vs chance
+  out$probAccept <- 1 / (1 + exp(-eval(model)))
+  out$Params <- chosen_params
+  #out$predicted <- reward > out$subjOC
+  #out$predicted[out$predicted == TRUE] <- 1
+  #out$percentPredicted <- mean(out$predicted == choice)
+
+  # if doing this with dplyr::do(), return a simplified data.frame instead with the important parameters
+  if (simplify) {
+    out <- round(data.frame(out[-6]), digits = 2)
+    colnames(out) <- c("percentQuit",
+                       "percentAccept",
+                       "LL",
+                       "LL0",
+                       "Rsq",
+                       colnames(chosen_params))
+  }
+
+  return(out)
 }

### 2020-05-13 Simulations/manuscript_modeling.R

@@ -9,13 +9,13 @@
 
 
   
-negLogLik <- function(subjData, params, model) {
+optimizeModel <- function(subjData, params, model, simplify = F) {
   # this function finds the combination of parameter values that minimizes the neg log likelihood of a logistic regression
   # used to rely on NLOPTR, but it's too cumbersome for the low-dimensional estimates I'm performing.
   #
   # subjData: a participant's log
   # params: a list of vectors. Each vector is the possible values a given parameter can take. Names in list must match model expression
-  # model: using `expr()`, define the model (use <param>[[1]] for free parameters to be estimated. R limitation.)
+  # model: using `expr()`, define the model (use <param>[[1]] for free parameters to be estimated. R limitation.). Ex: expr(temp[[1]] * (reward - (gamma[[1]] * handling)))
   
   
   # extract basic choice information
@@ -25,20 +25,26 @@ negLogLik <- function(subjData, params, model) {
   rt <- subjData$RT
   cost <- subjData$Cost
   trial <- subjData$TrialN
+  rawChoice <- subjData$rawChoice
   
   # combine parameters into every possible combination
   params <- expand.grid(params)
+  
+  # Prep list of results to be returned
+  out <- list()
+  out$percentQuit <- mean(choice == 0) * 100
+  out$percentAccept <- mean(choice == 1) * 100 
   
   LLs <- sapply(seq(nrow(params)), function(i) {
     
     # isolate the parameters for this iteration
     # and then store them as variables
     # FIGURE OUT HOW TO NOT STORE THEM AS DATAFRAMES
-    pars <- params_grid[i, ]
+    pars <- params[i, ]
     lapply(seq_along(pars), function(variable) {assign(colnames(pars)[variable], pars[variable], envir = .GlobalEnv)})
     
     # estimate the probability of acceptance per the model
-    p = 1 / (1 + exp(-eval(model_expr)))
+    p = 1 / (1 + exp(-eval(model)))
     p[p == 1] <- 0.999
     p[p == 0] <- 0.001
     
@@ -48,10 +54,36 @@ negLogLik <- function(subjData, params, model) {
     tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
[…]

### 2020-05-13 Simulations/manuscript_modeling.R
typo

@@ -88,9 +88,10 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
 # model to be fit
 # make sure that you specify the inverse temperature
 # extra parameters as dfs for now, that's why the `[[1]]`
-model_expr <- expr(temp[[1]] * (reward - (gamma[[1]] * handling)))
+model_expr <- expr(temperature[[1]] * (reward - (Gamma[[1]] * handling)))
 
 # create a list with possible starting values for model parameters
+# parameter names must match model ones
 spaceSize <- 100
 params <- list(temperature = seq(-1, 1, length.out = spaceSize), 
                Gamma = seq(0.25, 1.5, length.out = spaceSize))

### 2020-05-15 Simulations/manuscript_modeling.R
output the likelihood space for potential plotting

@@ -6,9 +6,7 @@
 # the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
 # maybe also R-squares and things in the current optimization function
 
-
-
-  
+# simpler form of optimization that allows inputting any model expression into a single function call
 optimizeModel <- function(subjData, params, model, simplify = F) {
   # this function finds the combination of parameter values that minimizes the neg log likelihood of a logistic regression
   # used to rely on NLOPTR, but it's too cumbersome for the low-dimensional estimates I'm performing.
@@ -62,7 +60,8 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
   
   # Summarize the outputs
   out$LL0 <- -(log(0.5) * length(choice))
-  out$Rsquared <- 1 - (out$LL / out$LL0) # pseudo r-squred, quantifying the proportion of deviance reduction vs chance
+  out$Rsquared <- 1 - (out$LL / out$LL0) # pseudo r-squared, quantifying the proportion of deviance reduction vs chance
+  out$loglikSpace <- LLs # in case you want to examine the concavity of the likelihood space
   out$probAccept <- 1 / (1 + exp(-eval(model)))
   out$Params <- chosen_params
   #out$predicted <- reward > out$subjOC
@@ -71,7 +70,7 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
   
   # if doing this with dplyr::do(), return a simplified data.frame instead with the important parameters
   if (simplify) {
-    out <- round(data.frame(out[-6]), digits = 2)
+    out <- round(data.frame(out[-c(6, 7)]), digits = 2)
     colnames(out) <- c("percentQuit",
                        "percentAccept",
                        "LL",
@@ -83,6 +82,13 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
   return(out)
 }
 
+
+## fit the OC model in the original way
+summaryOC <- list()
+summaryOC$all <- dataBtw %>%
+  group_by(Cost, SubjID) %>%
+  do(optimizeOCModel(., simplify = T)) %>%
+  ungroup()
 
 
 # model to be fit
@@ -103,18 +109,18 @@ tempOC <- dataBtw %>%
   ungroup()
 
 
-# plot
-ggplot(tempOC, aes(Cost, Gamma, fill = Cost)) +
[…]

### 2020-06-04 Cost_manuscript.Rmd
slight updates to modeling

@@
   unnest() %>%
-  rename(TrialN = X1) %>%
+  rename(TrialN = X1,
+         ExpTime = Experiment.Time) %>%
   mutate(rawChoice = Choice, 
@@
 
+**Possibilities**
+
+ - Single OC per person
+ - Subjective time perception, which gives rise to preference in cog effort.
+However, this doesn't account for the eventual convergence of choices across costs.
+Problem is that the converrgence is a global reduction.
+Like defaulting to the costliest demand.
+ - Fatigue can maybe be ruled out. This would amplify effort costs and boost wait, but we are seeing a global decline in acceptances.
+ - Wikenheiser
+ - Maybe fatigue could operate at two levels: 1) it becomes bothersome to keep track of values per cost, and the convergence will default to the most fatiguingcost, since there is no readon to accept more of what you dislike.
+Easier to lower everything else.
+
 *To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant's probability of completing a trial based on the difference between the delayed reward's magnitude and the estimated opportunity cost (OC) for each cost type.

### 2020-06-04 Simulations/manuscript_modeling.R

@@ -24,7 +24,9 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
   cost <- subjData$Cost
   trial <- subjData$TrialN
   rawChoice <- subjData$rawChoice
-  
+  expTime <- round(subjData$ExpTime)
+  remainingTime <- round(max(subjData$ExpTime) - subjData$ExpTime)
+    
   # combine parameters into every possible combination
   params <- expand.grid(params)
   
@@ -86,15 +88,15 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
 ## which models to run?
 baseOC_nloptr <- T
 baseOC <- T
-baseLogistic <- T # to test whether the brute search converges to a conventional logistic through glm()
- 
+baseLogistic <- F # to test whether the brute search converges to a conventional logistic through glm()
+fwOC <- T
 
 ## ORIGINAL OC NLOPTR
 if (baseOC_nloptr) {
   print("Running base OC model on NLOPTR...")
   
   summaryOC <- list()
-  summaryOC$all <- dataBtw %>%
+  summaryOC$all <- dataWth %>%
     group_by(Cost, SubjID) %>%
     do(optimizeOCModel(., simplify = T)) %>%
     ungroup()
@@ -118,12 +120,34 @@ if (baseOC) {
                  gamma = seq(0.25, 1.5, length.out = spaceSize))
   
   # fit to each subject
-  baseOC <- dataBtw %>%
+  baseOC <- dataWth %>%
     group_by(SubjID, Cost) %>%
     do(optimizeModel(., params, model_expr, simplify = T)) %>%
     ungroup()
 }
 
+## Fawcett OC (2012)
+# nope.. the definition doesn't work for multi-choice foraging
+if (fwOC) {
+  print("Running Fawcett et al (2012) OC model through grid search...")
+  
+  # model to be fit
+  # make sure that you specify the inverse temperature
+  # extra parameters as dfs for now, that's why the `[[1]]`
+  model_expr <- expr(tempr[[1]] * (reward - (gamma[[1]] * ((420 - expTime) - handling))))
+  
+  # create a list with possible starting values for model parameters
+  # parameter names must match model ones
+  spaceSize <- 30
+  params <- list(tempr = seq(-1, 1, length.out = spaceSize), 
+                 gamma = seq(0, 2, length.out = spaceSize))
+  
+  # fit to each subject
[…]

### 2020-06-04 Cost_manuscript.Rmd
added vector of time when each trial started (block-limited)

@@
           )
-         )
+         ) %>%
+  group_by(SubjID, Block) %>%
+  mutate(blockTime = ExpTime - min(ExpTime)) %>%
+  ungroup()
 
@@
   group_by(SubjID) %>%
-  mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st"))
+  mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st")) %>%
+  group_by(SubjID, Block) %>%
+  mutate(blockTime = ExpTime - min(ExpTime)) %>%
+  ungroup()
 

### 2020-06-04 Simulations/manuscript_modeling.R

@@ -26,6 +26,7 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
   rawChoice <- subjData$rawChoice
   expTime <- round(subjData$ExpTime)
   remainingTime <- round(max(subjData$ExpTime) - subjData$ExpTime)
+  blockTime <- subjData$blockTime
     
   # combine parameters into every possible combination
   params <- expand.grid(params)
@@ -134,7 +135,7 @@ if (fwOC) {
   # model to be fit
   # make sure that you specify the inverse temperature
   # extra parameters as dfs for now, that's why the `[[1]]`
-  model_expr <- expr(tempr[[1]] * (reward - (gamma[[1]] * ((420 - expTime) - handling))))
+  model_expr <- expr(tempr[[1]] * (reward - (gamma[[1]] * (blockTime - handling))))
   
   # create a list with possible starting values for model parameters
   # parameter names must match model ones

### 2020-07-01 Simulations/manuscript_modeling.R
simplified (vectorized) calculation of the ongoing rate, better for modeling (and matched with the other one for various values of alpha)

@@ -122,12 +122,13 @@ dynamic_gamma <- function(sub, estimatedGamma = 0, alpha = 0.95, meanRate = 0) {
            rateChoice = ifelse(Offer > (rate * Handling), 1, 0),
            gammaChoice = ifelse(Offer > (estimatedGamma * Handling), 1, 0),
            rateAcc = Choice == rateChoice,
-           gammaAcc = Choice == gammaChoice)
+           gammaAcc = Choice == gammaChoice,
+           cumulativeRate = lag(cumsum(Offer * Choice)) / (ExpTime ^ alpha))
   
   
   # plot the evolving gammas
   ratePlot <- summary %>%
-    mutate(trialRate = ifelse(Offer / Handling > 2, 1.5, Offer / Handling),
+    mutate(trialRate = Offer / Handling,
            offerAccept = case_when(
              (Offer == 4 & rateChoice == 1) ~ -0.05,
              (Offer == 8 & rateChoice == 1) ~ -.075,
@@ -138,24 +139,25 @@ dynamic_gamma <- function(sub, estimatedGamma = 0, alpha = 0.95, meanRate = 0) {
            actualChoice = ifelse(Choice == 1, -0.15, -8),
            optimalChoice = ifelse(optimal == 1, -0.175, -9)) %>%
     ggplot(aes(TrialN, rate)) +
-    geom_line(aes(TrialN, trialRate), linetype = "dashed", size = 0.2) +
-    geom_point(aes(TrialN, trialRate), size = 0.5) +
-    geom_hline(yintercept = estimatedGamma) +
-    geom_line(aes(color = Handling), size = 0.5) +
-    geom_point(aes(color = Handling), size = 1.2) +
-    geom_point(aes(TrialN, offerAccept, fill = factor(Offer, levels = c(4, 8, 20))), color = "black", pch = 21) +
-    geom_point(aes(TrialN, ratebasedChoice), pch = 21, color = "black", fill = "grey20") +
-    geom_point(aes(TrialN, actualChoice), pch = 21, color = "black", fill = "grey50") +
-    geom_point(aes(TrialN, optimalChoice), pch = 21, color = "black", fill = "grey80") +
-    scale_fill_discrete(name = "Offer") +
-    scale_color_continuous(breaks = c(2, 10, 14), labels = c(2, 10, 14)) +
-    ylim(-0.2, NA) +
-    labs(x = "Trial Number", y = "Ongoing Opportunity Cost (gamma)") +
[…]

### 2020-07-01 Simulations/manuscript_modeling.R
grid-search fits for ongoing rate models

@@ -119,11 +119,15 @@ dynamic_gamma <- function(sub, estimatedGamma = 0, alpha = 0.95, meanRate = 0) {
   sub$rate <- g
   summary <- sub %>%
     mutate(value = Offer - (rate * Handling),
+           cumulativeRate = lag(cumsum(Offer * Choice)) / (ExpTime ^ alpha),
+           cumulativeRate_nc = lag(cumsum(Offer)) / (ExpTime ^ alpha),
+           cumulativeRate_nc = ifelse(is.na(cumulativeRate_nc), 0, cumulativeRate_nc),
            rateChoice = ifelse(Offer > (rate * Handling), 1, 0),
+           rateChoice_nc = ifelse(Offer > (cumulativeRate_nc * Handling), 1, 0),
            gammaChoice = ifelse(Offer > (estimatedGamma * Handling), 1, 0),
            rateAcc = Choice == rateChoice,
-           gammaAcc = Choice == gammaChoice,
-           cumulativeRate = lag(cumsum(Offer * Choice)) / (ExpTime ^ alpha))
+           rateAcc_nc = Choice == rateChoice_nc,
+           gammaAcc = Choice == gammaChoice)
   
   
   # plot the evolving gammas
@@ -138,20 +142,23 @@ dynamic_gamma <- function(sub, estimatedGamma = 0, alpha = 0.95, meanRate = 0) {
            ratebasedChoice = ifelse(rateChoice == 1, -0.125, -7),
            actualChoice = ifelse(Choice == 1, -0.15, -8),
            optimalChoice = ifelse(optimal == 1, -0.175, -9)) %>%
-    ggplot(aes(TrialN, rate)) +
+    ggplot(aes(TrialN, cumulativeRate)) +
       geom_line(aes(TrialN, trialRate), linetype = "dashed", size = 0.2) +
       geom_point(aes(TrialN, trialRate, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black", size = 1) +
-      geom_hline(yintercept = estimatedGamma) + # single gamma estimated for an individual
+      geom_hline(yintercept = baseOC[id, "gamma"]$gamma) + # single gamma estimated for an individual
       geom_hline(yintercept = 0.71, linetype = "dashed") + # mean optimal rate across blocks
       geom_line(aes(color = Handling), size = 0.5) +
       geom_point(aes(color = Handling), size = 1.2) +
+      geom_line(aes(TrialN, cumulativeRate_nc)) +
[…]

### 2020-07-01 Simulations/manuscript_modeling.R
fixed NaN error, now models working with optimize_model function

@@ -7,7 +7,7 @@
 # maybe also R-squares and things in the current optimization function
 
 # simpler form of optimization that allows inputting any model expression into a single function call
-optimizeModel <- function(subjData, params, model, simplify = F) {
+optimize_model <- function(subjData, params, model, simplify = F) {
   # this function finds the combination of parameter values that minimizes the neg log likelihood of a logistic regression
   # used to rely on NLOPTR, but it's too cumbersome for the low-dimensional estimates I'm performing.
   #
@@ -15,6 +15,10 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
   # params: a list of vectors. Each vector is the possible values a given parameter can take. Names in list must match model expression
   # model: using `expr()`, define the model (use <param>[[1]] for free parameters to be estimated. R limitation.). Ex: expr(temp[[1]] * (reward - (gamma[[1]] * handling)))
   
+  # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
+  breakTime <- min(subjData$ExpTime[subjData$Block == 4]) - max(subjData$ExpTime[subjData$Block == 3])
+  subjData$ExpTime[which(subjData$Block > 3)] <- subjData$ExpTime[which(subjData$Block > 3)] - breakTime
+  subjData$ExpTime <- subjData$ExpTime - min(subjData$ExpTime)
   
   # extract basic choice information
   handling <- subjData$Handling
@@ -24,7 +28,7 @@ optimizeModel <- function(subjData, params, model, simplify = F) {
   cost <- subjData$Cost
   trial <- subjData$TrialN
   rawChoice <- subjData$rawChoice
-  expTime <- round(subjData$ExpTime)
+  expTime <- round(subjData$ExpTime) + 0.1 # to avoid dividing 0 by 0
   blockTime <- subjData$blockTime
     
   # combine parameters into every possible combination
@@ -240,7 +244,7 @@ if (bOC) {
   # fit to each subject
   baseOC <- data %>%
     group_by(SubjID) %>%
-    do(optimizeModel(., params, model_expr, simplify = T)) %>%
+    do(optimize_model(., params, model_expr, simplify = T)) %>%
[…]

### 2020-07-02 Cost_manuscript.Rmd
ongoing model fitting works, and can easily be plotted now, but parameters are not different

@@
 
-```{r Load data for between-subject experiment, echo = FALSE}
+```{r Load data for between-subject experiment, echo = FALSE, warning = F}
 ### data loading and cleaning up
@@
 
-```{r Load data for within-subject experiment, echo = FALSE}
+```{r Load data for within-subject experiment, echo = FALSE, warning = F}
 # First looks at the new data

### 2020-07-02 Simulations/manuscript_modeling.R

@@ -15,11 +15,6 @@ optimize_model <- function(subjData, params, model, simplify = F) {
   # params: a list of vectors. Each vector is the possible values a given parameter can take. Names in list must match model expression
   # model: using `expr()`, define the model (use <param>[[1]] for free parameters to be estimated. R limitation.). Ex: expr(temp[[1]] * (reward - (gamma[[1]] * handling)))
   
-  # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
-  breakTime <- min(subjData$ExpTime[subjData$Block == 4]) - max(subjData$ExpTime[subjData$Block == 3])
-  subjData$ExpTime[which(subjData$Block > 3)] <- subjData$ExpTime[which(subjData$Block > 3)] - breakTime
-  subjData$ExpTime <- subjData$ExpTime - min(subjData$ExpTime)
-  
   # extract basic choice information
   handling <- subjData$Handling
   reward <- subjData$Offer
@@ -88,129 +83,46 @@ optimize_model <- function(subjData, params, model, simplify = F) {
   return(out)
 }
 
-# a dynamic estimation of gamma, with resulting plots for MVT-style tracking versus single-parammeter fits
-dynamic_gamma <- function(sub, estimatedGamma = 0, alpha = 0.95, meanRate = 0) {
-  # this function will treat prey foraging in an MVT fashion, using the equation from Dundon et al 2020
-  # sub: a single subject's dataset
-  # estimatedGamma: their single gamma, estimated with the original model
-  # alpha: for the current model, the discounting of the effect of recent time in the updating of gamma (1 = basic Dundon)
-  # meanRate: where to initialize gamma (either 0 or the actual group mean of 0.59 work)
-  
+# remove break time and start counting from 0
+standardize_time <- function(subjData) {
   # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
-  breakTime <- min(sub$ExpTime[sub$Block == 4]) - max(sub$ExpTime[sub$Block == 3])
-  sub$ExpTime[which(sub$Block > 3)] <- sub$ExpTime[which(sub$Block > 3)] - breakTime
-  sub$ExpTime <- sub$ExpTime - min(sub$ExpTime)
[…]

### 2020-07-09 Cost_manuscript.Rmd
added a vector of completed trials (diff from accepted)

@@
          Choice = ifelse(Choice == 2, 1, Choice), # forced travels (2) become acceptances (1)
+         Completed = ifelse(rawChoice == 2, 0, rawChoice),
          Half = ifelse(Block < 4, "Half_1", "Half_2"),
@@
          Choice = ifelse(Choice == 2, 1, Choice),
+         Completed = ifelse(rawChoice == 2, 0, rawChoice),
          Cost = case_when(Cost == "WAIT_0" ~ "Wait-C",

### 2020-07-14 Cost_manuscript.Rmd
added trial-wise model updates

@@
   group_by(SubjID, Block) %>%
-  mutate(blockTime = ExpTime - min(ExpTime)) %>%
+  mutate(blockTime = ExpTime - min(ExpTime),
+         blockElapsed = blockTime - dplyr::lag(blockTime, default = 0)) %>% # how much time elapsed between trials, counting per block
   ungroup()

### 2020-07-14 Simulations/manuscript_modeling.R

@@ -7,6 +7,7 @@
 # maybe also R-squares and things in the current optimization function
 
 # simpler form of optimization that allows inputting any model expression into a single function call
+# only good for static models
 optimize_model <- function(subjData, params, model, simplify = F) {
   # this function finds the combination of parameter values that minimizes the neg log likelihood of a logistic regression
   # used to rely on NLOPTR, but it's too cumbersome for the low-dimensional estimates I'm performing.
@@ -83,11 +84,111 @@ optimize_model <- function(subjData, params, model, simplify = F) {
   return(out)
 }
 
+# for a trial-wise acceptance version. Add model expression eventually
+optimize_model_dyn <- function(subjData, params, simplify = F) {
+  # get every combination of parameters
+  params <- expand.grid(params)
+  
+  # relevant behavior elements
+  o <- subjData$Offer
+  h <- subjData$Handling
+  c <- subjData$Choice
+  a <- o * c # accepted offers
+  time <- subjData$ExpTime
+  tau <- time - dplyr::lag(time, default = 0) # how long has it been since the last update?
+  
+  # Prep list of results to be returned
+  out <- list()
+  out$percentQuit <- mean(c == 0) * 100
+  out$percentAccept <- mean(c == 1) * 100 
+  
+  # iterate through possible parameters and get the LL
+  LLs <- sapply(seq(nrow(params)), function(i) {
+    # isolate the parameters for this iteration
+    # and then store them as variables
+    tempr <- params[i, 1]
+    alpha <- params[i, 2]
+    
+    # update rule (inspired by Constantino and Daw, 2015)
+    gamma <- rep(0, nrow(subjData))
+    
+    # calculate gammas
+    for (i in seq(nrow(sub))) {
+      if (i == 1) {
+        gamma[i] <- 0.25
+      } else {
+        
+        # delta <- (o[i] / h[i]) - gamma[i]
+        # gamma[i + 1] <- gamma[i] + (1 - (1 - alpha) ^ h[1]) * delta
+        gamma[i] <- (((1 - alpha) ^ tau[i]) * (a[i - 1] / tau[i])) + (1 - (1 - alpha) ^ tau[i]) * gamma[i - 1] # maybe expr(model)
+      }
+    }
+    
[…]

### 2020-07-14 Simulations/manuscript_modeling.R
typos all around

@@ -113,7 +113,7 @@ optimize_model_dyn <- function(subjData, params, simplify = F) {
     gamma <- rep(0, nrow(subjData))
     
     # calculate gammas
-    for (i in seq(nrow(sub))) {
+    for (i in seq(nrow(subjData))) {
       if (i == 1) {
         gamma[i] <- 0.25
       } else {
@@ -125,7 +125,7 @@ optimize_model_dyn <- function(subjData, params, simplify = F) {
     }
     
     # estimate the probability of acceptance per the model
-    p = 1 / (1 + exp(tempr * (o - (gamma * h))))
+    p = 1 / (1 + exp(-(tempr * (o - (gamma * h)))))
     p[p == 1] <- 0.999
     p[p == 0] <- 0.001
     
@@ -152,7 +152,7 @@ optimize_model_dyn <- function(subjData, params, simplify = F) {
   gamma <- rep(0, nrow(subjData))
   
   # calculate gammas
-  for (i in seq(nrow(sub))) {
+  for (i in seq(nrow(subjData))) {
     if (i == 1) {
       gamma[i] <- 0.25
     } else {
@@ -163,7 +163,8 @@ optimize_model_dyn <- function(subjData, params, simplify = F) {
     }
   }
   
-  out$probAccept <- 1 / (1 + exp(tempr[[1]] * (o - (gamma * h))))
+  out$rate <- gamma
+  out$probAccept <- 1 / (1 + exp(-(tempr[[1]] * (o - (gamma * h)))))
   out$Params <- chosen_params
   #out$predicted <- reward > out$subjOC
   #out$predicted[out$predicted == TRUE] <- 1
@@ -171,7 +172,7 @@ optimize_model_dyn <- function(subjData, params, simplify = F) {
   
   # if doing this with dplyr::do(), return a simplified data.frame instead with the important parameters
   if (simplify) {
-    out <- round(data.frame(out[-c(6, 7)]), digits = 2)
+    out <- round(data.frame(out[-c(6, 7, 8)]), digits = 2)
     colnames(out) <- c("percentQuit",
                        "percentAccept",
                        "LL",
@@ -216,11 +217,12 @@ baseOC_nloptr <- F
 bOC <- T
 baseLogistic <- F # to test whether the brute search converges to a conventional logistic through glm()
 fwOC <- F
-dOC <- T
+dOC <- F
 twOC <- T
 
[…]

### 2020-07-14 Simulations/manuscript_modeling.R
avoid repeats

@@ -402,6 +402,8 @@ if (twOC) {
     group_by(Cost, SubjID) %>%
     do(optimize_model_dyn(., params, simplify = T)) %>%
     ungroup()
+  
+  trialwiseOC <- trialwiseOC[-c(18, 19), ] # some people are re-run for some reason
 }
 
 param_compare_plot(trialwiseOC, "tempr")

### 2020-07-15 Simulations/manuscript_modeling.R
simple plotting function

@@ -113,7 +113,7 @@ optimize_model_dyn <- function(subjData, params, simplify = F) {
     gamma <- rep(0, nrow(subjData))
     
     # calculate gammas
-    for (i in seq(nrow(subjData))) {
+    for (i in seq(nrow(subjData) - 1)) {
       if (i == 1) {
         gamma[i] <- 0.25
       } else {
@@ -152,14 +152,11 @@ optimize_model_dyn <- function(subjData, params, simplify = F) {
   gamma <- rep(0, nrow(subjData))
   
   # calculate gammas
-  for (i in seq(nrow(subjData))) {
-    if (i == 1) {
-      gamma[i] <- 0.25
+  for (j in seq(nrow(subjData))) {
+    if (j == 1) {
+      gamma[j] <- 0.25
     } else {
-      
-      # delta <- (o[i] / h[i]) - gamma[i]
-      # gamma[i + 1] <- gamma[i] + (1 - (1 - alpha) ^ h[1]) * delta
-      gamma[i] <- (((1 - alpha[[1]]) ^ tau[i]) * (a[i - 1] / tau[i])) + (1 - (1 - alpha[[1]]) ^ tau[i]) * gamma[i - 1] # maybe expr(model)
+      gamma[j] <- (((1 - alpha[[1]]) ^ tau[j]) * (a[j - 1] / tau[j])) + (1 - (1 - alpha[[1]]) ^ tau[j]) * gamma[j - 1] # maybe expr(model)
     }
   }
   

### 2020-07-15 Cost_manuscript.Rmd
working on more plotting and adapting tw model to within-sub

--- 2020-07-02 Cost_manuscript.Rmd
@@
          ) %>%
+  group_by(SubjID) %>% 
+  do(standardize_time(.)) %>% 
   group_by(SubjID, Block) %>%
-  mutate(blockTime = ExpTime - min(ExpTime)) %>%
+  mutate(blockTime = ExpTime - min(ExpTime),
+         blockElapsed = blockTime - dplyr::lag(blockTime, default = 0)) %>% # how much time elapsed between trials, counting per block
   ungroup()
@@
   mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st")) %>%
+  group_by(SubjID) %>% 
+  do(standardize_time(.)) %>% 
   group_by(SubjID, Block) %>%

### 2020-07-15 Simulations/manuscript_modeling.R

@@ -209,6 +209,50 @@ param_compare_plot <- function(summary, param = "gamma", color = colsBtw, meanRa
   return(plot)
 }
 
+# plot the results from the dynamic model for a single individual
+plot_dyn <- function(id = "58", data = dataBtw) {
+  
+  # choose subject + params
+  sub <- filter(data, SubjID == id)
+  spaceSize <- 100
+  params <- list(tempr = seq(-1, 1, length.out = spaceSize), 
+                 alpha = seq(0, 1, length.out = spaceSize))
+  
+  # run model
+  temp <- optimize_model_dyn(sub, params, simplify = F)
+  
+  # plot
+  sub %>%
+    mutate(trialRate = Offer / Handling,
+           g = temp$rate,
+           fitChoice = ifelse(trialRate > g, -0.25, -5),
+           newChoice = ifelse(Choice == 1, -0.5, -5),
+           trialRate = ifelse(trialRate > 3, 3, trialRate),
+           pChoice = temp$probAccept,
+           g = ifelse(g > 3, 3.2, g)) %>%
+    ggplot(aes(TrialN, g)) +
+    geom_line(aes(TrialN, trialRate), linetype = "dashed", size = 0.2) +
+    geom_point(aes(TrialN, trialRate, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black", size = 1) +
+    geom_hline(yintercept = filter(baseOC, SubjID == id)$gamma) + # single gamma estimated for an individual
+    geom_hline(yintercept = 0.74, linetype = "dashed", color = "grey30") + # mean optimal rate across blocks
+    geom_line(aes(color = Handling), size = 0.5) +
+    geom_point(aes(color = Handling), size = 1.2) +
+    geom_point(aes(TrialN, fitChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
+    geom_point(aes(TrialN, newChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
+    #geom_point(aes(TrialN, pChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
+    annotate("text", x = 220, y = filter(baseOC, SubjID == id)$gamma + 0.25, label = "Fitted \n Gamma", size = 5) +
[…]

### 2020-07-15 Simulations/manuscript_modeling.R
polished plot function to help visualize participants from both experiments

@@ -209,48 +209,107 @@ param_compare_plot <- function(summary, param = "gamma", color = colsBtw, meanRa
   return(plot)
 }
 
+
 # plot the results from the dynamic model for a single individual
-plot_dyn <- function(id = "58", data = dataBtw) {
+plot_dyn <- function(id = "58", exp = "btw") {
   
-  # choose subject + params
-  sub <- filter(data, SubjID == id)
-  spaceSize <- 100
-  params <- list(tempr = seq(-1, 1, length.out = spaceSize), 
-                 alpha = seq(0, 1, length.out = spaceSize))
-  
-  # run model
-  temp <- optimize_model_dyn(sub, params, simplify = F)
-  
-  # plot
-  sub %>%
-    mutate(trialRate = Offer / Handling,
-           g = temp$rate,
-           fitChoice = ifelse(trialRate > g, -0.25, -5),
-           newChoice = ifelse(Choice == 1, -0.5, -5),
-           trialRate = ifelse(trialRate > 3, 3, trialRate),
-           pChoice = temp$probAccept,
-           g = ifelse(g > 3, 3.2, g)) %>%
-    ggplot(aes(TrialN, g)) +
-    geom_line(aes(TrialN, trialRate), linetype = "dashed", size = 0.2) +
-    geom_point(aes(TrialN, trialRate, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black", size = 1) +
-    geom_hline(yintercept = filter(baseOC, SubjID == id)$gamma) + # single gamma estimated for an individual
-    geom_hline(yintercept = 0.74, linetype = "dashed", color = "grey30") + # mean optimal rate across blocks
-    geom_line(aes(color = Handling), size = 0.5) +
-    geom_point(aes(color = Handling), size = 1.2) +
-    geom_point(aes(TrialN, fitChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-    geom_point(aes(TrialN, newChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-    #geom_point(aes(TrialN, pChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-    annotate("text", x = 220, y = filter(baseOC, SubjID == id)$gamma + 0.25, label = "Fitted \n Gamma", size = 5) +
[…]

### 2020-07-15 Simulations/manuscript_modeling.R
plot tweaks

@@ -85,7 +85,7 @@ optimize_model <- function(subjData, params, model, simplify = F) {
 }
 
 # for a trial-wise acceptance version. Add model expression eventually
-optimize_model_dyn <- function(subjData, params, simplify = F) {
+optimize_model_dyn <- function(subjData, params, simplify = F, gammaStart = 0.6) {
   # get every combination of parameters
   params <- expand.grid(params)
   
@@ -115,7 +115,7 @@ optimize_model_dyn <- function(subjData, params, simplify = F) {
     # calculate gammas
     for (i in seq(nrow(subjData) - 1)) {
       if (i == 1) {
-        gamma[i] <- 0.25
+        gamma[i] <- gammaStart
       } else {
         
         # delta <- (o[i] / h[i]) - gamma[i]
@@ -239,7 +239,7 @@ plot_dyn <- function(id = "58", exp = "btw") {
     baseOC <- optimize_model(sub, params, model_expr, simplify = T)
     
     # plot
-    sub %>%
+    ratePlot <- sub %>%
       mutate(trialRate = Offer / Handling,
              g = temp$rate,
              fitChoice = ifelse(trialRate > g, -0.25, -5),
@@ -270,6 +270,7 @@ plot_dyn <- function(id = "58", exp = "btw") {
             panel.background = element_blank(),
             axis.line = element_line(colour = "black"),
             text = element_text(size = 16))
+    
   } else if (exp == "wth") {
     # choose subject + params
     sub <- filter(dataWth, SubjID == id)
@@ -281,7 +282,7 @@ plot_dyn <- function(id = "58", exp = "btw") {
     temp <- optimize_model_dyn(sub, params, simplify = F)
     
     # plot
-    sub %>%
+    ratePlot <- sub %>%
       mutate(trialRate = Offer / Handling,
              g = temp$rate,
              fitChoice = ifelse(trialRate > g, -0.25, -5),
@@ -310,6 +311,8 @@ plot_dyn <- function(id = "58", exp = "btw") {
             axis.line = element_line(colour = "black"),
             text = element_text(size = 16))
   }
+  
+  suppressWarnings(print(ratePlot))
 }
 
 ## which models to run?

### 2020-07-15 Simulations/manuscript_modeling.R
fixed the removal of subject duplicates in model summaries

@@ -154,7 +154,7 @@ optimize_model_dyn <- function(subjData, params, simplify = F, gammaStart = 0.6)
   # calculate gammas
   for (j in seq(nrow(subjData))) {
     if (j == 1) {
-      gamma[j] <- 0.25
+      gamma[j] <- gammaStart
     } else {
       gamma[j] <- (((1 - alpha[[1]]) ^ tau[j]) * (a[j - 1] / tau[j])) + (1 - (1 - alpha[[1]]) ^ tau[j]) * gamma[j - 1] # maybe expr(model)
     }
@@ -211,7 +211,7 @@ param_compare_plot <- function(summary, param = "gamma", color = colsBtw, meanRa
 
 
 # plot the results from the dynamic model for a single individual
-plot_dyn <- function(id = "58", exp = "btw") {
+plot_dyn <- function(id = "58", exp = "btw", gammaOne = 0.6) {
   
   if (exp == "btw") {
     # choose subject + params
@@ -221,7 +221,7 @@ plot_dyn <- function(id = "58", exp = "btw") {
                    alpha = seq(0, 1, length.out = spaceSize))
     
     # run model
-    temp <- optimize_model_dyn(sub, params, simplify = F)
+    temp <- optimize_model_dyn(sub, params, simplify = F, gammaStart = gammaOne)
     
     # get baseline gamma from a simple fit
     # model to be fit
@@ -279,7 +279,7 @@ plot_dyn <- function(id = "58", exp = "btw") {
                    alpha = seq(0, 1, length.out = spaceSize))
     
     # run model
-    temp <- optimize_model_dyn(sub, params, simplify = F)
+    temp <- optimize_model_dyn(sub, params, simplify = F, gammaStart = gammaOne)
     
     # plot
     ratePlot <- sub %>%
@@ -501,14 +501,15 @@ if (twOC) {
     group_by(Cost, SubjID) %>%
     do(optimize_model_dyn(., params, simplify = T)) %>%
     ungroup() %>%
-    distinct(SubjID)
+    distinct(SubjID, .keep_all = T)
   
   
   # between subject exp
   trialwiseOC_wth <- dataWth %>% 
     group_by(SubjID) %>%
     do(optimize_model_dyn(., params, simplify = T)) %>%
-    ungroup()
+    ungroup() %>%
+    distinct(SubjID, .keep_all = T)
 }
 
 param_compare_plot(trialwiseOC_btw, "alpha")

### 2020-07-15 Simulations/manuscript_modeling.R
filtering out the easy group

@@ -332,8 +332,7 @@ data <- dataBtw %>%
 if (baseOC_nloptr) {
   print("Running base OC model on NLOPTR...")
   
-  summaryOC <- list()
-  summaryOC$all <- data %>%
+  summaryOC <- data %>%
     group_by(Cost, SubjID) %>%
     do(optimizeOCModel(., simplify = T)) %>%
     ungroup()
@@ -498,6 +497,7 @@ if (twOC) {
   
   # between subject exp
   trialwiseOC_btw <- dataBtw %>%
+    filter(Cost != "Easy") %>%
     group_by(Cost, SubjID) %>%
     do(optimize_model_dyn(., params, simplify = T)) %>%
     ungroup() %>%

### 2020-07-16 Cost_manuscript.Rmd
modified trialwise model

@@
 
-```{r Setups, include = FALSE}
+```{r Setups, include = FALSE, warning = FALSE}
 ## libraries
@@
   return(adapted_p)
+}
+
+# remove break time and start counting from 0
+standardize_time <- function(subjData) {
+  # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
+  breakTime <- min(subjData$ExpTime[subjData$Block == 4]) - max(subjData$ExpTime[subjData$Block == 3])
+  subjData$ExpTime[which(subjData$Block > 3)] <- subjData$ExpTime[which(subjData$Block > 3)] - breakTime + 16
+  subjData$ExpTime <- subjData$ExpTime - min(subjData$ExpTime)
+
+  return(subjData)
 }

### 2020-07-16 Simulations/manuscript_modeling.R

@@ -85,7 +85,7 @@ optimize_model <- function(subjData, params, model, simplify = F) {
 }
 
 # for a trial-wise acceptance version. Add model expression eventually
-optimize_model_dyn <- function(subjData, params, simplify = F, gammaStart = 0.6) {
+optimize_model_dyn <- function(subjData, params, simplify = F, gammaStart = 0) {
   # get every combination of parameters
   params <- expand.grid(params)
   
@@ -182,14 +182,103 @@ optimize_model_dyn <- function(subjData, params, simplify = F, gammaStart = 0.6)
   
 }
 
-# remove break time and start counting from 0
-standardize_time <- function(subjData) {
-  # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
-  breakTime <- min(subjData$ExpTime[subjData$Block == 4]) - max(subjData$ExpTime[subjData$Block == 3])
-  subjData$ExpTime[which(subjData$Block > 3)] <- subjData$ExpTime[which(subjData$Block > 3)] - breakTime + 16
-  subjData$ExpTime <- subjData$ExpTime - min(subjData$ExpTime)
+# variants of vanilla C&D
+optimize_model_dyn_us <- function(subjData, params, simplify = F, gammaStart = 0) {
+  # get every combination of parameters
+  params <- expand.grid(params)
   
-  return(subjData)
+  # relevant behavior elements
+  o <- subjData$Offer
+  h <- subjData$Handling
+  c <- subjData$Choice
+  a <- o * c # accepted offers
+  time <- subjData$ExpTime
+  
+  # Prep list of results to be returned
+  out <- list()
+  out$percentQuit <- mean(c == 0) * 100
+  out$percentAccept <- mean(c == 1) * 100 
+  
+  # iterate through possible parameters and get the LL
+  LLs <- sapply(seq(nrow(params)), function(i) {
+    # isolate the parameters for this iteration
+    # and then store them as variables
+    tempr <- params[i, 1]
+    alpha <- params[i, 2]
+    k <- params[i, 3]
+    tau <- (time - dplyr::lag(time, default = 0)) ^ k
+    
+    # update rule (inspired by Constantino and Daw, 2015)
+    gamma <- rep(0, nrow(subjData))
+    
+    # calculate gammas
+    for (i in seq(nrow(subjData) - 1)) {
+      if (i == 1) {
[…]

### 2020-07-16 Simulations/manuscript_modeling.R
fit trial-wise modiefied on all p's

@@ -299,7 +299,7 @@ param_compare_plot <- function(summary, param = "gamma", color = colsBtw, meanRa
 }
 
 # plot the results from the dynamic model for a single individual
-plot_dyn <- function(id = "58", exp = "btw", gammaOne = 0.6) {
+plot_dyn <- function(id = "58", exp = "btw", gammaOne = 0) {
   
   if (exp == "btw") {
     # choose subject + params
@@ -351,7 +351,7 @@ plot_dyn <- function(id = "58", exp = "btw", gammaOne = 0.6) {
       annotate("text", x = 200, y = -0.5, label = "Observed choices", size = 3) +
       scale_fill_discrete(name = "Offer") +
       scale_color_continuous(breaks = c(2, 10, 14), labels = c(2, 10, 14)) +
-      ylim(-1, NA) +
+      ylim(-0.6, NA) +
       labs(x = "Trial Number", y = "Ongoing Opportunity Cost (gamma)") +
       theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
@@ -391,7 +391,7 @@ plot_dyn <- function(id = "58", exp = "btw", gammaOne = 0.6) {
       annotate("text", x = 200, y = -0.5, label = "Observed choices", size = 3) +
       scale_fill_discrete(name = "Offer") +
       scale_color_manual(values = colsWth) +
-      ylim(-1, NA) +
+      ylim(-0.6, NA) +
       labs(x = "Trial Number", y = "Ongoing Opportunity Cost (gamma)") +
       theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
@@ -402,7 +402,7 @@ plot_dyn <- function(id = "58", exp = "btw", gammaOne = 0.6) {
   
   suppressWarnings(print(ratePlot))
 }
-plot_dyn_us <- function(id = "58", exp = "btw", gammaOne = 0.6) {
+plot_dyn_us <- function(id = "58", exp = "btw", gammaOne = 0) {
   
   if (exp == "btw") {
     # choose subject + params
@@ -455,7 +455,7 @@ plot_dyn_us <- function(id = "58", exp = "btw", gammaOne = 0.6) {
       annotate("text", x = 200, y = -0.5, label = "Observed choices", size = 3) +
       scale_fill_discrete(name = "Offer") +
       scale_color_continuous(breaks = c(2, 10, 14), labels = c(2, 10, 14)) +
-      ylim(-1, NA) +
[…]

### 2020-07-16 Simulations/manuscript_modeling.R
better plot axis limits

@@ -345,10 +345,10 @@ plot_dyn <- function(id = "58", exp = "btw", gammaOne = 0) {
       geom_point(aes(TrialN, fitChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
       geom_point(aes(TrialN, newChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
       #geom_point(aes(TrialN, pChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-      annotate("text", x = 220, y = baseOC$gamma + 0.25, label = "Fitted \n Gamma", size = 5) +
-      annotate("text", x = 220, y = 0.55, label = "Optimal", size = 5, color = "grey30") +
-      annotate("text", x = 200, y = -0.25, label = "Predicted choices", size = 3) +
-      annotate("text", x = 200, y = -0.5, label = "Observed choices", size = 3) +
+      annotate("text", x = max(sub$TrialN) + 8, y = baseOC$gamma + 0.25, label = "Fitted \n Gamma", size = 5) +
+      annotate("text", x = max(sub$TrialN) + 8, y = 0.55, label = "Optimal", size = 5, color = "grey30") +
+      annotate("text", x = max(sub$TrialN), y = -0.3, label = "Predicted choices", size = 3) +
+      annotate("text", x = max(sub$TrialN), y = -0.55, label = "Observed choices", size = 3) +
       scale_fill_discrete(name = "Offer") +
       scale_color_continuous(breaks = c(2, 10, 14), labels = c(2, 10, 14)) +
       ylim(-0.6, NA) +
@@ -386,9 +386,9 @@ plot_dyn <- function(id = "58", exp = "btw", gammaOne = 0) {
       geom_point(aes(color = Cost), size = 1.2) +
       geom_point(aes(TrialN, fitChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
       geom_point(aes(TrialN, newChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-      annotate("text", x = 220, y = 0.63, label = "Optimal", size = 5, color = "grey30") +
-      annotate("text", x = 200, y = -0.25, label = "Predicted choices", size = 3) +
-      annotate("text", x = 200, y = -0.5, label = "Observed choices", size = 3) +
[…]

### 2020-07-18 Simulations/manuscript_modeling.R
reversed alpha terms to indicate that higher alpha means higher learning, and added nonlinearity to handling time only

@@ -118,9 +118,10 @@ optimize_model_dyn <- function(subjData, params, simplify = F, gammaStart = 0) {
         gamma[i] <- gammaStart
       } else {
         
-        # delta <- (o[i] / h[i]) - gamma[i]
-        # gamma[i + 1] <- gamma[i] + (1 - (1 - alpha) ^ h[1]) * delta
+        delta <- (a[i - 1] / tau[i]) - gamma[i - 1]
+        gamma[i] <- gamma[i - 1] + (1 - (1 - alpha) ^ tau[i]) * delta
         gamma[i] <- (((1 - alpha) ^ tau[i]) * (a[i - 1] / tau[i])) + (1 - (1 - alpha) ^ tau[i]) * gamma[i - 1] # maybe expr(model)
+        gamma[i] <- ((1 - (1 - alpha) ^ tau[i]) * (a[i - 1] / tau[i])) + ((1 - alpha) ^ tau[i]) * gamma[i - 1] # switched version that means higher alpha = more learning
       }
     }
     
@@ -156,7 +157,10 @@ optimize_model_dyn <- function(subjData, params, simplify = F, gammaStart = 0) {
     if (j == 1) {
       gamma[j] <- gammaStart
     } else {
+      delta <- (a[j - 1] / tau[j]) - gamma[j - 1]
+      gamma[j] <- gamma[j - 1] + (1 - (1 - alpha[[1]]) ^ tau[j]) * delta
       gamma[j] <- (((1 - alpha[[1]]) ^ tau[j]) * (a[j - 1] / tau[j])) + (1 - (1 - alpha[[1]]) ^ tau[j]) * gamma[j - 1] # maybe expr(model)
+      gamma[j] <- ((1 - (1 - alpha[[1]]) ^ tau[j]) * (a[j - 1] / tau[j])) + ((1 - alpha[[1]]) ^ tau[j]) * gamma[j - 1] # maybe expr(model)
     }
   }
   
@@ -190,6 +194,7 @@ optimize_model_dyn_us <- function(subjData, params, simplify = F, gammaStart = 0
   # relevant behavior elements
   o <- subjData$Offer
   h <- subjData$Handling
+  t <- 20 - h
   c <- subjData$Choice
   a <- o * c # accepted offers
   time <- subjData$ExpTime
@@ -206,7 +211,8 @@ optimize_model_dyn_us <- function(subjData, params, simplify = F, gammaStart = 0
[…]

### 2020-07-21 Simulations/manuscript_modeling.R
flow for generative model

@@ -957,7 +957,6 @@ optimize_model_dyn_us2 <- function(subjData, params, simplify = F, gammaStart = 
   
   return(out)
 }
-
 plot_dyn_us2 <- function(id = "58", exp = "btw", gammaOne = 0) {
   
   if (exp == "btw") {
@@ -1157,7 +1156,6 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
   
   return(out)
 }
-
 plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
   
   if (exp == "btw") {
@@ -1196,28 +1194,28 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
              pChoice = temp$probAccept,
              g = ifelse(g > 3, 3.2, g)) %>%
       ggplot(aes(TrialN, g)) +
-      geom_line(aes(TrialN, trialRate), linetype = "dashed", size = 0.2) +
-      geom_point(aes(TrialN, trialRate, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black", size = 1) +
-      geom_hline(yintercept = baseOC$gamma) + # single gamma estimated for an individual
-      geom_hline(yintercept = 0.74, linetype = "dashed", color = "grey30") + # mean optimal rate across blocks
-      geom_line(aes(color = Handling), size = 0.5) +
-      geom_point(aes(color = Handling), size = 1.2) +
-      geom_point(aes(TrialN, fitChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-      geom_point(aes(TrialN, newChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-      #geom_point(aes(TrialN, pChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-      annotate("text", x = max(sub$TrialN) + 8, y = baseOC$gamma + 0.25, label = "Fitted \n Gamma", size = 5) +
-      annotate("text", x = max(sub$TrialN) + 8, y = 0.55, label = "Optimal", size = 5, color = "grey30") +
-      annotate("text", x = max(sub$TrialN), y = -0.3, label = "Predicted choices", size = 3) +
-      annotate("text", x = max(sub$TrialN), y = -0.55, label = "Observed choices", size = 3) +
-      scale_fill_discrete(name = "Offer") +
[…]

### 2020-07-21 Simulations/manuscript_modeling.R
cleaning up

@@ -1261,147 +1261,8 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
   suppressWarnings(print(ratePlot))
 }
 
+# to test the effect of parameters
 plot_alphas <- function(alpha, k = 1, exp = "btw", gammaStart = 0) {
-  # parameter setting
-  
-  
-  if (exp == "btw") {
-    # choose sample subject + params
-    sub <- filter(dataBtw, SubjID == "58")
-    
-    # relevant behavior elements
-    o <- sub$Offer
-    h <- sub$Handling
-    t <- 20 - h
-    c <- sub$Choice
-    a <- o * c # accepted offers
-    time <- sub$ExpTime
-    tau <- lag((h ^ k * c) + t)
-    
-    # get the trial-wise gamma to export the probability of acceptance
-    gamma <- rep(0, nrow(sub))
-    
-    # calculate gammas
-    for (j in seq(nrow(sub))) {
-      if (j == 1) {
-        gamma[j] <- gammaStart
-      } else {
-        gamma[j] <- ((1 - (1 - alpha) ^ tau[j]) * (a[j - 1] / tau[j])) + ((1 - alpha) ^ tau[j]) * gamma[j - 1]
-      } 
-    }
-    
-    # create a list with possible starting values for model parameters
-    # parameter names must match model ones
-    spaceSize <- 30
-    params <- list(tempr = seq(-1, 1, length.out = spaceSize), 
-                   gamma = seq(0.25, 1.5, length.out = spaceSize))
-    
-    # fit to subject
-    baseOC <- optimize_model(sub, params, model_expr, simplify = T)
-    
-    # plot
-    ratePlot <- sub %>%
-      mutate(optimalRate = case_when(
-        Handling == 2 ~ 0.53,
-        Handling == 10 ~ 0.56,
-        Handling == 14 ~ 0.62
-      ),
-      trialRate = Offer / Handling,
-      g = gamma,
-      fitChoice = ifelse(trialRate > g, -0.25, -5),
-      newChoice = ifelse(Choice == 1, -0.5, -5),
-      trialRate = ifelse(trialRate > 3, 3, trialRate),
-      g = ifelse(g > 3, 3.2, g)) %>%
-      ggplot(aes(TrialN, g)) +
-      geom_line(aes(TrialN, trialRate), linetype = "dashed", size = 0.2) +
[…]

### 2020-07-21 Simulations/manuscript_modeling.R
function to plot the combination of alphas and k parameter values

@@ -1262,7 +1262,7 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
 }
 
 # to test the effect of parameters
-plot_alphas <- function(alpha, k = 1, exp = "btw", gammaStart = 0) {
+plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
   if (exp == "btw") {
     # choose sample subject + params
     sub <- filter(dataBtw, SubjID == "58")
@@ -1272,54 +1272,73 @@ plot_alphas <- function(alpha, k = 1, exp = "btw", gammaStart = 0) {
     h <- sub$Handling
     t <- 20 - h
     
-    # get the trial-wise gamma to export the probability of acceptance
-    c <- rep(0, nrow(sub))
-    gamma <- rep(0, nrow(sub))
+    # store subj data with gammas
+    iters <- list()
     
-    # calculate gammas
-    for (j in seq(nrow(sub))) {
-      if (j == 1) {
-        gamma[j] <- gammaStart
-        c[j] <- ifelse(o[j] / h[j] > gamma[j], 1, 0)
-      } else {
-        tau <- (h[j - 1] ^ k * c[j - 1]) + t[j - 1]
-        a <- o[j - 1] * c[j - 1]
-        gamma[j] <- ((1 - (1 - alpha) ^ tau) * (a / tau)) + ((1 - alpha) ^ tau) * gamma[j - 1]
-        c[j] <- ifelse(o[j] / h[j] > gamma[j], 1, 0)
-      } 
+    # iterate over the alphas provided
+    for (param in seq_along(alphas)) {
+      
+      # set up param
+      alpha <- alphas[param]
+      
+      # get the trial-wise gamma to export the probability of acceptance
+      c <- rep(0, nrow(sub))
+      gamma <- rep(0, nrow(sub))
+      
+      # calculate gammas
+      for (j in seq(nrow(sub))) {
+        if (j == 1) {
+          gamma[j] <- gammaStart
+          c[j] <- ifelse(o[j] / h[j] > gamma[j], 1, 0)
+        } else {
+          tau <- (h[j - 1] ^ k * c[j - 1]) + t[j - 1]
+          a <- o[j - 1] * c[j - 1]
+          gamma[j] <- ((1 - (1 - alpha) ^ tau) * (a / tau)) + ((1 - alpha) ^ tau) * gamma[j - 1]
[…]

### 2020-07-21 Simulations/manuscript_modeling.R
raise h

@@ -1289,12 +1289,12 @@ plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
       for (j in seq(nrow(sub))) {
         if (j == 1) {
           gamma[j] <- gammaStart
-          c[j] <- ifelse(o[j] / h[j] > gamma[j], 1, 0)
+          c[j] <- ifelse(o[j] / (h[j] ^ k) > gamma[j], 1, 0)
         } else {
           tau <- (h[j - 1] ^ k * c[j - 1]) + t[j - 1]
           a <- o[j - 1] * c[j - 1]
           gamma[j] <- ((1 - (1 - alpha) ^ tau) * (a / tau)) + ((1 - alpha) ^ tau) * gamma[j - 1]
-          c[j] <- ifelse(o[j] / h[j] > gamma[j], 1, 0)
+          c[j] <- ifelse(o[j] / (h[j] ^ k) > gamma[j], 1, 0)
         } 
       }
       
@@ -1374,12 +1374,12 @@ plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
       for (j in seq(nrow(sub))) {
         if (j == 1) {
           gamma[j] <- gammaStart
-          c[j] <- ifelse(o[j] / h[j] > gamma[j], 1, 0)
+          c[j] <- ifelse(o[j] / h[j] ^ k> gamma[j], 1, 0)
         } else {
           tau <- (h[j - 1] ^ k * c[j - 1]) + t[j - 1]
           a <- o[j - 1] * c[j - 1]
           gamma[j] <- ((1 - (1 - alpha) ^ tau) * (a / tau)) + ((1 - alpha) ^ tau) * gamma[j - 1]
-          c[j] <- ifelse(o[j] / h[j] > gamma[j], 1, 0)
+          c[j] <- ifelse(o[j] / h[j] ^ k > gamma[j], 1, 0)
         } 
       }
       

### 2020-07-22 Simulations/manuscript_modeling.R
multiple fixes in dynamic non-linear time model
- reverted to grid search
- the trial rate is now plotted with the non-linearity, and now matches behavior better (per fits)

@@ -1099,11 +1099,11 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
     }
     
     # get the trial-wise gamma to export the probability of acceptance
-    c <- rep(0, nrow(sub))
-    gamma <- rep(0, nrow(sub))
+    c <- rep(0, nrow(subjData))
+    gamma <- rep(0, nrow(subjData))
     
     # calculate gammas iterating over trials
-    for (i in seq(nrow(sub))) {
+    for (i in seq(nrow(subjData))) {
       if (i == 1) {
         gamma[i] <- gammaStart
         c[i] <- ifelse(o[i] / h[i] > gamma[i], 1, 0)
@@ -1130,12 +1130,18 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
     
     # if these parameters improve the fit, store the rate and choices
     if (negLL < out$LL) {
-      #write(negLL, stdout())
+      diff <- out$LL - negLL
       out$LL <- negLL
       out$rate <- gamma
       out$fit_c <- c
       out$params <- params[param, ]
       out$pAccept <- p
+      
+      # break if the reduction is too small to be significant
+      # based on visual assessment of the likelihood space, which looks convex
+      # if (diff <= 0.000001) {
+      #   break
+      # }
     }
   } 
   
@@ -1261,7 +1267,7 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
   suppressWarnings(print(ratePlot))
 }
 
-# to test the effect of parameters
+# to test the effect of parameters 
 plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
   if (exp == "btw") {
     # choose sample subject + params
@@ -1325,27 +1331,29 @@ plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
         Handling == 10 ~ 0.56,
         Handling == 14 ~ 0.62
       ),
-      trialRate = Offer / Handling,
+      trialRate = Offer / (Handling ^ k),
       fitChoice = ifelse(trialRate > g, -0.25, -5),
       newChoice = ifelse(Choice == 1, -0.5, -5),
       trialRate = ifelse(trialRate > 3, 3, trialRate),
       g = ifelse(g > 3, 3.2, g)) %>%
       ggplot(aes(TrialN, g, group = alpha)) +
[…]

### 2020-07-22 Simulations/manuscript_modeling.R
added the non-linearity to the fitting plot for the within-subject. Explains dynamics better

@@ -1235,7 +1235,7 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
     
     # plot
     ratePlot <- sub %>%
-      mutate(trialRate = Offer / Handling,
+      mutate(trialRate = Offer / Handling ^ mK,
              g = temp$rate,
              fitChoice = ifelse(trialRate > g, -0.25, -5),
              newChoice = ifelse(Choice == 1, -0.5, -5),
@@ -1245,12 +1245,12 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
       ggplot(aes(TrialN, g)) +
         geom_line(aes(TrialN, trialRate), linetype = "dashed", size = 0.2) +
         geom_point(aes(TrialN, trialRate, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black", size = 1) +
-        geom_hline(yintercept = 0.7, linetype = "dashed", color = "grey30") + # mean optimal rate across blocks
+        #geom_hline(yintercept = 0.7, linetype = "dashed", color = "grey30") + # mean optimal rate across blocks
         geom_line(size = 0.5, color = "grey50") +
         geom_point(aes(color = Cost), size = 1.2) +
         geom_point(aes(TrialN, fitChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
         geom_point(aes(TrialN, newChoice, fill = factor(Offer, levels = c(4, 8, 20))), pch = 21, color = "black") +
-        annotate("text", x = max(sub$TrialN) + 8, y = 0.63, label = "Optimal", size = 5, color = "grey30") +
+        #annotate("text", x = max(sub$TrialN) + 8, y = 0.63, label = "Optimal", size = 5, color = "grey30") +
         annotate("text", x = max(sub$TrialN), y = -0.3, label = "Predicted choices", size = 3) +
         annotate("text", x = max(sub$TrialN), y = -0.55, label = "Observed choices", size = 3) +
         scale_fill_discrete(name = "Offer") +
@@ -1452,7 +1452,7 @@ trialwiseOC_btw_us_new <- dataBtw %>%
   distinct(SubjID, .keep_all = T)
 
 #btw ks to apply to wth
-ks <- trialwiseOC_btw_us %>% 
+ks <- trialwiseOC_btw_us_new %>% 
   group_by(Cost) %>% 
   summarise(mK = median(k))
 

### 2020-07-22 Simulations/manuscript_modeling.R
avoid alpha = 0 (i.e. assume that everyone learns at least a bit)

@@ -1169,7 +1169,7 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
     sub <- filter(dataBtw, SubjID == id)
     spaceSize <- 30
     params <- list(tempr = seq(0, 2, length.out = spaceSize), 
-                   alpha = seq(0, 1, length.out = spaceSize),
+                   alpha = seq(0.001, 1, length.out = spaceSize),
                    k = seq(-1, 1, length.out = spaceSize))
     
     # run model
@@ -1228,7 +1228,7 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0) {
     sub <- filter(dataWth, SubjID == id)
     spaceSize <- 30
     params <- list(tempr = seq(-1, 1, length.out = spaceSize), 
-                   alpha = seq(0, 1, length.out = spaceSize))
+                   alpha = seq(0.001, 1, length.out = spaceSize))
     
     # run model
     temp <- optimize_model_dyn_us3(sub, params, simplify = F, gammaStart = gammaOne)
@@ -1441,7 +1441,7 @@ plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
 
 # fit btw exp
 params <- list(tempr = seq(0, 2, length.out = spaceSize), 
-               alpha = seq(0, 1, length.out = spaceSize),
+               alpha = seq(0.001, 1, length.out = spaceSize),
                k = seq(-1, 2, length.out = spaceSize))
 
 trialwiseOC_btw_us_new <- dataBtw %>%
@@ -1475,7 +1475,7 @@ if (! "mK" %in% colnames(dataWth)) {
 # fit wth
 spaceSize <- 30
 params <- list(tempr = seq(-1, 1, length.out = spaceSize), 
-               alpha = seq(0, 1, length.out = spaceSize))
+               alpha = seq(0.001, 1, length.out = spaceSize))
 
 trialwiseOC_wth_us_new <- dataWth %>%
   group_by(SubjID) %>%
@@ -1483,11 +1483,11 @@ trialwiseOC_wth_us_new <- dataWth %>%
   ungroup() %>%
   distinct(SubjID, .keep_all = T)
 
-trialwiseOC_wth_us2
-id <- "109"
 
-plot_dyn_us2(id, exp = "wth", gammaOne = 0.2)
-plot_dyn_us(id, exp = "wth", gammaOne = 0.2)
+id <- "109"
[…]

### 2020-07-22 Cost_manuscript.Rmd
parameter recovery looking good across experiments!

@@
 hrPlot_btw <- dataBtw %>%
-        filter(Choice < 2) %>%
+        filter(Choice < 2, Cost != "Easy") %>%
         group_by(SubjID, Cost, Handling, Offer, optimal) %>%
@@
 While all main effects were significant, there was an unexpected significant condition-by-reward interaction, which could be due to the performance of the "easy" group relative to their peers.
-Importantly, we found that the interaction between all three main parameters was not significant, thus suggesting that the effects of handling and reward on choices were not different across groups.
+Importantly, we found that the interaction between all three main parameters was not significant, thus suggesting that the effects of handling and reward on choices were not different across groups.
 

### 2020-07-22 Simulations/manuscript_modeling.R

@@ -64,8 +64,8 @@ optimize_model <- function(subjData, params, model, simplify = F) {
   out$LL0 <- -(log(0.5) * length(choice))
   out$Rsquared <- 1 - (out$LL / out$LL0) # pseudo r-squared, quantifying the proportion of deviance reduction vs chance
   out$loglikSpace <- LLs # in case you want to examine the concavity of the likelihood space
-  out$probAccept <- 1 / (1 + exp(-eval(model)))
-  out$Params <- chosen_params
+  out$pAccept <- 1 / (1 + exp(-eval(model)))
+  out$params <- chosen_params
   #out$predicted <- reward > out$subjOC
   #out$predicted[out$predicted == TRUE] <- 1
   #out$percentPredicted <- mean(out$predicted == choice) 
@@ -1433,7 +1433,7 @@ plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
   
   acc <- temp %>% 
     group_by(alpha) %>%
-    summarise(accuracy = sum(c == Choice) / max(TrialN))
+    summarise(accuracy = mean(c == Choice))
   
   return(acc)
 }
@@ -1490,6 +1490,180 @@ plot_dyn_us2(id, exp = "wth", gammaOne = 0.2) # using ongoing model choices to c
 plot_dyn_us3(id, exp = "wth", gammaOne = 0.2) # like 2, but with non-linearity of time adopted from exp 1
 
 
+# attempt to recover the observed results from 16.2.2, reproducing the prop-completed plot
+### Between subjects
+# so far both single gamma and alpha + k perform well, though the latter is preferred due to explanatory power and generalization to exp 2
+recover_results_btw <- function(fitsList, binary = F) {
+  fits <- do.call(c, sapply(fitsList, "[", "pAccept"))
+  if (binary) {
+    # to get stochastic-less choices
+    fits <- ifelse(fits > 0.5, 1, 0)
+  }
+  data <- dataBtw %>%
+    filter(Cost != "Easy") %>%
+    mutate(fitChoice = fits) #rbinom(length(fits), 1, fits))
+  
+  
+  data %>%
+    group_by(SubjID, Cost, Handling, Offer, optimal) %>%
+    summarise(pAccept = mean(fitChoice)) %>%
+    group_by(Cost, Handling, Offer, optimal) %>%
+    summarise(meanComplete = mean(pAccept),
+              SE = sd(pAccept) / sqrt(length(pAccept))) %>%
[…]

### 2020-07-23 Simulations/manuscript_modeling.R
within_subj matrix reproduction from model

@@ -1611,7 +1611,13 @@ recover_results_btw(temp_dOC_fits, binary = T)
 ### Within subjects (reproduce 16.3.3)
 # partial replication! without temperature I get the first block fine
 # with temperature I get the last one perfect (i.e. based on probabilities). First block still matches kind of.
-recover_results_wth <- function(fitsList, binary = F) {
+# the reported pre-post results, including mixed effects, use half 1 and half 2 raw, but the results are pretty much conserved either way.
+# here the middle blocks are eliminated to denote prevent the uneven assignment of the middle blocks to bias stuff either way
+recover_results_wth <- function(fitsList, binary = F, matrix = T) {
+  # use model fits to reproduce observed behavioral plots
+  # the reported pre-post results, including mixed effects, use half 1 and half 2 raw, but the results are pretty much conserved either way.
+  # here the middle blocks are eliminated to denote prevent the uneven assignment of the middle blocks to bias stuff either way
+  
   # extract fits
   fits <- do.call(c, sapply(fitsList, "[", "pAccept"))
   if (binary) {
@@ -1621,8 +1627,8 @@ recover_results_wth <- function(fitsList, binary = F) {
   data <- dataWth %>%
     mutate(fitChoice = fits) #rbinom(length(fits), 1, fits))
   
-  # plot
-  data %>%
+  # plot prop accepted
+  plot <- data %>%
     group_by(SubjID) %>%
     mutate(Block = case_when(
       Block %in% c(1, 2) ~ 1,
@@ -1653,8 +1659,101 @@ recover_results_wth <- function(fitsList, binary = F) {
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16))
+  
+  print(plot)
+  
+  # plot the pre-post coefficient matrix, but only for the binary version (based on GLM def)
+  if (binary & matrix) {
+    mixLogis_pre <- list()
+    mixData <- data %>%
+      mutate(Choice = fitChoice,
+             Cost = factor(Cost, levels = list("Cognitive", "Physical", "Wait-C", "Wait-P")),
+             Block = case_when(
[…]

### 2020-07-27 Simulations/manuscript_modeling.R
complete vs chosen, also code not replicating previous results? odd

@@ -823,7 +823,7 @@ if (twOC) {
   # create a list with possible starting values for model parameters
   params <- list(tempr = seq(-1, 1, length.out = spaceSize), 
                  alpha = seq(0, 1, length.out = spaceSize),
-                 k = seq(-2, 2, length.out = spaceSize))
+                 k = seq(-1, 2, length.out = spaceSize))
   
   # between subject exp
   trialwiseOC_btw_us <- dataBtw %>%
@@ -844,223 +844,14 @@ if (twOC) {
 }
 
 #plot
-param_compare_plot(trialwiseOC_btw_us, "k", meanRate = 1) 
+param_compare_plot(trialwiseOC_btw_us, "tempr", meanRate = 1) 
 
 
 ### test
 # taking the cumulative average of the subjective time perception makes subjective overall time seem slower.
 # a free parameter could be added to index the degree to which participants cared about this (replaces k as a free parameter, since k is adopted from exp 1)
 # weird that the higher the weight on cum_means, the lower the OC ie less selective. Think about it.
-optimize_model_dyn_us2 <- function(subjData, params, simplify = F, gammaStart = 0) {
-  # get every combination of parameters
-  params <- expand.grid(params)
-  
-  # relevant behavior elements
-  o <- subjData$Offer
-  h <- subjData$Handling
-  t <- 20 - h
-  c <- subjData$Choice
-  a <- o * c # accepted offers
-  k <- subjData$mK
-  time <- subjData$ExpTime
-  
-  # Prep list of results to be returned
-  out <- list()
-  out$percentQuit <- mean(c == 0) * 100
-  out$percentAccept <- mean(c == 1) * 100 
-  
-  # iterate through possible parameters and get the LL
-  LLs <- sapply(seq(nrow(params)), function(i) {
-    # isolate the parameters for this iteration
-    # and then store them as variables
-    tempr <- params[i, "tempr"]
-    alpha <- params[i, "alpha"]
-    if ("k" %in% colnames(params)) {
-      k <- params[i, "k"] # if there is a free k parameter, use its fit, otherwise use the values from exp1
-    }
-    tau <- lag((h ^ k * c) + t) # we dont expect cognitive to affect total time, just the handling time
-    
[…]

### 2020-07-28 Cost3/Cost3_prereg.Rmd
added data again (after pruning large data files from history)

---
title: "Preregistration analysis, Cost 3 study"
author: "Claudio Toro Serey & Joseph T. McGuire"
output:
  pdf_document: default
  html_document: default
---

This document follows the steps planned for the second pre-registration (https://osf.io/2rsgm/). The bullet points match the organization shown on the website as closely as possible. First, here is a restatement of the questions and hypotheses.

```{r Global Options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r setup, include=FALSE}
# global options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

# aesthetic options
cols <- c("#D9541A", "#78AB05", "dodgerblue4", "deepskyblue3")#"grey30", "grey70") # plot colors (wait, effort)

library(tidyverse)
library(gridExtra)
library(lme4)
library(corrplot)
library(nloptr)
library(pander)

# personal functions
# get the number of continuous quits before current trial
seqQuits <- function(subjData = 1){

    # get the lag
    tempSeq <- sequence(rle(subjData)$lengths) # sequence
    tempSeq[subjData==1] <- 0 # not interested in completed runs, just quits
    tempSeq <- c(0,tempSeq) # lag it so it can be used as a t-1 regressor

    # return data so that the length is equivalent
    out <- tempSeq[1:length(subjData)]

    return(out)

}

# generic permutation for 2 groups
permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE, simple = FALSE){

    # prep data
    summaryPerm <- list()
    lOne <- length(group1)
    lTwo <- length(group2)
    bigSample <- c(group1,group2)

    if (paired == FALSE) {

        for (i in 1:nPerms){

            # relabel samples
            tempBig <- sample(bigSample)
            tempOne <- tempBig[1:lOne]
            tempTwo <- tempBig[(lOne+1):length(bigSample)]

            # stats
            tempDiffs <- statType(tempOne,na.rm=T) - statType(tempTwo,na.rm=T)
            summaryPerm$jointDist[i] <- tempDiffs # statType(tempDiffs, na.rm = T)

        }

    } else {

        for (i in 1:nPerms){

            # shift labels in a pairwise fashion
            tempDiffs <- statType((-1)^rbinom(lOne,1,0.5) * (group1 - group2))
            summaryPerm$jointDist[i] <- tempDiffs

        }

    }

    # get the observed difference
    diffs <- statType(group1,na.rm=T) - statType(group2,na.rm=T)
    observedAbs <- abs(diffs) # maybe leave it as means here
    observed <- diffs
    summaryPerm$Pval <- 2 * (1 - ecdf(summaryPerm$jointDist)(observedAbs))
    if (length(unique(abs(summaryPerm$jointDist))) == 1) {summaryPerm$Pval <- 1} # if the difference is always the same, then p = 1
    summaryPerm$Observed <- observed

    # return the results
    if (simple) {

      return(summaryPerm$Pval)

    } else if (!simple) {

      return(summaryPerm)

    }

}

# OC-specific computation of the negative log likelihood for model optimization
negLogLik <- function(params, choice, handling, reward) {
  gamma <- exp(params[2]) * handling
  model <- exp(params[1]) * (reward - gamma)
  p = 1 / (1 + exp(-model))
  p[p == 1] <- 0.999
  p[p == 0] <- 0.001
  tempChoice <- rep(NA, length(choice))
  tempChoice[choice == 1] <- log(p[choice == 1])
  tempChoice[choice == 0] <- log(1 - p[choice == 0]) # log of probability of choice 1 when choice 0 occurred
  negLL <- -sum(tempChoice) 
  return(negLL)
}

# optimize the OC model
optimizeOCModel <- function(Data, Algorithm = "NLOPT_LN_NEWUOA", simplify = F, optfun = negLogLik) {

  # Data: The participant's log
  # Algorithm: probably let be
  # optfun: an external function to minimize (in this case OC, separately defined as negloglik)

  # Prep data
  handling <- Data$Handling
  reward <- Data$Offer
  choice <- Data$Choice

  # Prep list of results to be returned
  out <- list()
  out$percentQuit <- mean(choice == 0) * 100
  out$percentAccept <- mean(choice== 1) * 100 
  miss <- (choice != 1) & (choice != 0)
  out$percentMiss <- mean(miss)  * 100
  choice <- choice[!miss]
  reward <- as.numeric(reward[!miss])
  handling <- as.numeric(handling[!miss])

  # Establish lower and upper bounds
  LB <- round(log((min(reward)/max(handling)) * 0.99), digits = 4)
  UB <- round(log((max(reward)/min(handling)) * 1.01), digits = 4) # in reality this should be the second largest, since no one would reject the highest val

  # Begin defining parameters
  # If choices are one-sided (i.e. all accepted)
  if ((sum(choice) == length(choice)) | (sum(choice) == 0)) {
    ifelse(sum(choice) == length(choice), out$Gamma <- exp(LB), out$Gamma <- exp(UB)) 
    out$Scale <- 1 # it was NA, but in theory a temperature of 1 also indicates noiseless estimates, and allows for easier fit computations
    out$LL <- 0
  } else {
    # Create a feasible region (search space)
    params <- as.matrix(expand.grid(scale = c(-1, 1), gamma = seq(LB, UB, length = 3)))
    # Create a list to check the minimization of the negative log lik.
    info <- list()
    info$negLL <- Inf
    # Define the options to be used during optimization
    # Consider looking into other optimization algorithms and global minima
    opts <- list("algorithm" = Algorithm,
               "xtol_rel" = 1.0e-8)
    # Optimize the sOC over all possible combinations of starting points
    for (i in seq(nrow(params))) {
      tempInfo <- nloptr(x0 = params[i, ], 
                   eval_f = optfun, 
                   lb = c(log(0.001), LB),
                   ub = c(-log(0.001), UB),
                   opts = opts,
                   choice = choice, 
                   handling = handling,
                   reward = reward)
      if (tempInfo$objective < info$negLL) {
        #print("Minimized")
        info$negLL <- tempInfo$objective
        info$params <- tempInfo$solution
      }
    }
    out$Gamma <- exp(info$params[2])
    out$Scale <- exp(info$params[1])
    out$LL <- -info$negLL
  }

  # Summarize the outputs
  out$LL0 <- log(0.5) * length(choice)
  out$Rsquared <- 1 - (out$LL/out$LL0)
  out$subjOC <- out$Gamma * handling
  out$p <- 1 / (1 + exp(-(out$Scale*(reward - out$subjOC))))
  out$predicted <- reward > out$subjOC
  out$predicted[out$predicted == TRUE] <- 1
  out$percentPredicted <- mean(out$predicted == choice)

  # adjust the probabilities in case of extreme gammas
  if (out$Gamma <= exp(LB)) {
    out$Gamma <- exp(LB) # temporary condition because Nlopt is not respecting the lower bound
    out$p <- rep(1, length(choice))
  } else if (out$Gamma == exp(UB)) {
    out$p <- rep(0, length(choice))
  }

  # if doing this with dplyr::do(), return a simplified data.frame instead with the important parameters
  if (simplify) {
    out <- data.frame(out[c(seq(8), 12)])
  }

  return(out)

}

# summary matrices for refrence-changing models
betaMatrix <- function(model, rearrange = NA) {
# get a similarity matrix of the resulting coefficient pairings for the cost conditions
# first, do a full_join based on column names on the list of coefficient vectors from each dummy code relevel
# then match the names of columns and rows so NAs are in the diagonal

  # get the names of the reference group per model iteration
  refnames <- names(model)

  # coefficient matrix
  temp <- lapply(model, function(data) {coefficients(data)$SubjID[1, 2:4]})
  mixCoeffs <- bind_rows(temp) 
  preln <- ifelse("Cost" %in% substr(names(mixCoeffs), 1, 4), 4, 5) # count how many characters precede the name of each cost (diff across studies)
  dimnames(mixCoeffs) <- list(refnames, substr(names(mixCoeffs), preln + 1, 20))
  mixCoeffs <- as.matrix(mixCoeffs[, match(rownames(mixCoeffs), colnames(mixCoeffs))])
  mixCoeffs[is.na(mixCoeffs)] <- 0

  # now the pvals
  temp <- lapply(model, function(data) {as.list(summary(data)$coefficients[2:4, 4])})
  mixPvals <- as.matrix(bind_rows(temp)) 
  dimnames(mixPvals) <- list(refnames, substr(colnames(mixPvals), preln + 1, 20))
  mixPvals <- as.matrix(mixPvals[, match(rownames(mixPvals), colnames(mixPvals))])
  mixPvals[is.na(mixPvals)] <- 1

  # if you would like to re-arrange the coefficient order, supply a vector with the desired sequence
  if (length(rearrange) > 1) {
    mixCoeffs <- mixCoeffs[rearrange, rearrange]
    dimnames(mixCoeffs) <- list(rearrange, rearrange)
    mixPvals <- mixPvals[rearrange, rearrange]
    dimnames(mixPvals) <- list(rearrange, rearrange)
  }

  # combine matrices into list to return
  out <- list(Betas = round(mixCoeffs, digits = 2),
              Pvals = round(mixPvals, digits = 5))

  return(out)

}
```

```{r load, echo = FALSE}
# First looks at the new data
# The RT is upper-bounded because a glitch in the code made one 10s last 14s
setwd('./data/')
files <- dir(pattern = 'main_log.csv')

# load the data and remove extreme subjects
dataAll <- data_frame(SubjID = files) %>% 
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(RT = ifelse(RT > 10.1, 10, RT),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Btype = BlockType) %>%
  unite(Cost, Cost, BlockType) %>%
  mutate(rawChoice = Choice,
         Choice = ifelse(Choice == 2, 1, Choice),
         Cost = case_when(Cost == "WAIT_0" ~ "Wait_C",
                           Cost == "COGNITIVE_0" ~ "Cognitive",
                           Cost == "GRIP_1" ~ "Physical",
                           Cost == "WAIT_1" ~ "Wait_P")) %>%
  group_by(SubjID) %>%
  mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st"))

# Get just the subject list and number of subjects
subjList <- unique(data$SubjID)
nSubjs <- length(subjList)
```

## 3. Research Questions

###	3.1. Main question

Similar to phase 1 (between subjects experiment), we ask whether decisions are affected differently by equivalent time periods of pure delay, cognitive effort, and physical effort. However, we now ask if the acceptance pattern previously observed in the between-subject experiment changes when each participant experiences all forms of cost. The current number of participants is `r nSubjs`.

## 4. Hypotheses

###	4.1.

Single-option, accept/reject decisions will be influenced by within-subject manipulations of reward magnitude in line with a theoretical reward-maximizing strategy.

4.1.1. Participants will more frequently accept high-reward prospects than low-reward prospects.

4.1.2. This pattern of acceptances will resemble that of groups that previously experienced each effort separately for equivalent time/reward combinations.

###	4.2.

Prospect acceptance rates will differ across three within-subject conditions, in which the delays associated with rewards (a) are unfilled, (b) include a cognitive effort requirement, or (c) include a physical effort requirement. Each effort type will be paired with unfilled delay trials in a blocked manner.

4.2.1. Acceptance rates for unfilled-delay trials will be higher than those for both physical and cognitive effort trials.

4.2.2. Acceptance rates for physical effort trials will be lower than those for cognitive effort trials.

4.2.3. Acceptance rates for unfilled-delay trials will not differ based on their pairing with each effort condition.

###	4.3.

Choices will be well fit by a computational model in which the subjective opportunity cost of time is free to vary across the four between-subject conditions.

4.3.1. Participants will display stable preferences, meaning that the reward amounts they accept in a given cost condition will be similar throughout the experiment.

4.3.2. Subject-specific opportunity cost (OC) estimates will vary inversely with acceptance rates. Thus, the unfilled-delay condition will produce lower OC estimates than both effort conditions, while physical effort will produce the highest OC.

## 16. Analyses

### 16.1. Tests of whether decision makers integrate reward information.

### 16.1.1.

*To address hypothesis 4.1., A logistic regression will be fit for each participant in order to predict trial-wise acceptances, using reward amount as predictor. The resulting beta coefficients will be pooled across all participants, and we will perform a one-sample rank-sum test to examine whether the they are significantly positive or negative (compared to 0). If the group coefficients are significantly positive, it would mean that a predictor reliably increases the likelihood of acceptance. This will allow us to determine whether increments in reward amounts increased the likelihood of acceptance for each participant.*

``` {r 16.1.1., fig.align="center", fig.width = 4, fig.height = 4, echo = FALSE}
# adapt the data so the fits are only performed on choices, not failed attempts (revisit?)
dataList <- dataAll %>% plyr::dlply("SubjID", identity)

# fits
logisticFits_base <- lapply(dataList, function(data) glm(Choice ~ Offer, data = data, family = "binomial"))

# Summarize
baseCoeffs <- as.data.frame(t(sapply(logisticFits_base, "[[", "coefficients")))
baseCoeffs$ConvIters <- sapply(logisticFits_base, function(x) {summary(x)$iter})
baseCoeffs$R2 <- sapply(logisticFits_base, function(x) {1 - (summary(x)$deviance / summary(x)$null.deviance)})
baseCoeffs$aic <- sapply(logisticFits_base, function(x) {summary(x)$aic})
baseCoeffs$propAccept_total <- sapply(dataList, function(data) {mean(data$Choice)})
baseCoeffs$propAccept_totalSQRD <- baseCoeffs$propAccept_total^2
baseCoeffs$totalEarned <- (dataAll %>% group_by(SubjID) %>% summarize(totalEarned = sum(Offer[Choice == 1])))$totalEarned
baseCoeffs$SubjID <- subjList # add subject list column to join the demographics by it below

# plot to match the one in Cost 2, even though we only have offer as an influence
ggplot(data = baseCoeffs, aes(x = "Offer", y = Offer)) +
  geom_boxplot() +
  ylim(-10, 10) +
  labs(x = "", y = "Coefficients") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = c(0.9, 0.7),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        text = element_text(size = 16))

```

The Wilcoxon signed rank test showed that the reward coefficients were significantly greater than 0 (V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* = `r wilcox.test(baseCoeffs$Offer)$p.value`), indicating that participants were properly influenced by reward amounts.

### 16.1.2.

*We will perform an extension of the logistic regression from 16.1.1., this time adding an autoregressive covariate containing the number of consecutive quits prior to a given trial. In this way, we will examine the possibility that participant choices were governed by recent quitting history rather than the experimental parameters. Coefficients not significantly different from 0 will denote that a participant did not rely on recent quitting history.*

``` {r 16.1.2., echo = FALSE, include = FALSE}
# Create an autoregressive predictor based on previous consecutive quits
dataList <- lapply(dataList, function(data) data %>% mutate(AR = seqQuits(Choice)))

# fits
logisticFits_base <- lapply(dataList, function(data) {glm(Choice ~ Offer + AR, data = data, family = "binomial")})

# get the low/high 95% CIs for AR
baseCoeffs <- as.data.frame(t(sapply(logisticFits_base, confint, "AR"))) %>% 
  dplyr::rename(AR_CILow = `2.5 %`, AR_CIHigh = `97.5 %`) %>%
  mutate(SubjID = subjList) %>%
  left_join(baseCoeffs, by = "SubjID")

# reorder so that SubjID comes first
#baseCoeffs <- baseCoeffs[ , c(3,4,5,6,7,8,9,1,2)]

# create a vector indicating whether 0 is included or not
# but first change NA to 0 (visual inspection showed that NAs were tied to p's with near full p(accept), meaning they weren't influenced by history)
baseCoeffs <- baseCoeffs %>% mutate(AR_CILow = ifelse(is.na(AR_CILow), 0, AR_CILow),
                                    AR_CIHigh = ifelse(is.na(AR_CIHigh), 0, AR_CIHigh))
baseCoeffs$AR_effect <- apply(baseCoeffs, 1, function(x) (!(as.numeric(x["AR_CILow"]) <= 0 & as.numeric(x["AR_CIHigh"]) >= 0)))

# alternative method, just do pvalues (maybe adjusted when n is higher)
# mean(sapply(logisticFits_base, function(x) {summary(x)$coefficients[3,4]}) < 0.05)
```

This regression showed that `r sum(baseCoeffs$AR_effect)` out of `r nSubjs` of the subjects were influenced by recent quit history.

###	16.1.3.

*A general linear model with constant, linear, and quadratic terms will be used to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable). No other covariates will be used, as this analysis is to confirm that over and under accepting are detrimental to total earnings. The quadratic term will be defined as the squared deviation from the optimal overall acceptance rate?*

``` {r 16.1.3. prop accept x earnings, echo = FALSE, include = T, fig.align="center",fig.width=4,fig.height=4}
# Notes: I also performed this comparing halves and block types x half, and it doesn't look like participants were accepting less to make more.
# calculate the proportions and earnings per subject, while keeping group info
temp <- dataAll %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID) %>%
  summarise(Earnings = sum(Offer[Choice == 1] / 100),
            pComplete = mean(Choice)) %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

# linear fit of earnings x prop accept
# adding a regressor for half shows no diffs in earnings
lmEarn <- lm(Earnings ~ pComplete + pComplete2, data = temp)

# plot
(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = cols) + 
         geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = cols) +
         ylim(12, 16) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16)))

# extra analyses
# a pre-post paired permutation on earnigs confirms no differences (more evidence in section 16.3.3--prepost)
# this means that, at least in general, participants are not changing their behavior due to monetary incentives
# but because of something else, maybe like fatigue (this pattern holds even at finer subdivisions)
# PPearn <- dataAll %>%
#           #filter(Block %in% c(1,2,5,6)) %>%
#           mutate(Choice = ifelse(Choice > 1, 0, Choice)) %>%
#           group_by(SubjID, Half) %>%
#           summarise(Earnings = sum(Offer[Choice == 1] / 100),
#                     pComplete = mean(Choice)) %>%
#           ungroup() %>% 
#           select(SubjID, Half, Earnings) %>% 
#           spread(Half, Earnings)
# 
# permute(PPearn$Half_1, PPearn$Half_2, paired = TRUE)
```

The table shows the results from this linear model. In accord with the design of the experimental task, participants who either rejected or accepted too many trials received the least amount of money overall. This is confirmed by significance of the quadratic term below.

``` {r 16.1.3. Earnings table, echo=FALSE,fig.align="center",fig.width=9,fig.height=5}
# Summary table for the linear model
panderOptions("digits", 2)
pander(lmEarn, style = "rmarkdown")
```

###	16.1.4.

*To determine the optimality of the group's decisions, we will examine whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents will always be accepted). The reward-maximizing strategy is to always reject 4 cents and accept 8 cents, yielding a combined optimal proportion of acceptances of 50%. We will perform a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost. We will report the estimated overall proportion of acceptances for these rewards along with the statistics to show the direction of the bias.*

``` {r 16.1.4., echo = FALSE, fig.align="center",fig.width=6,fig.height=4}
# get the proportion of acceptances per reward and trial type across subjects, and do a one sample t test versus a null mu given by the optimal strategy
# note that in the very likely case that every participant will accept or reject for a given reward/cost (i.e. sd = 0): 
# I am just providing a pseudo pvalue as 1 minus the diff. between prevalent choice and the null (so, removing the standard deviation from the t test equation, otherwise you can't divide by 0)
# this is just to track the optimality.
# I am also adding the mean/sd of acceptances per cost/reward and optimality as reference
# summary_costvsreward <- data %>% 
#                           group_by(SubjID, Offer, Cost) %>% 
#                           summarize(prop = mean(Choice)) %>%
#                           group_by(Offer, Cost) %>%
#                           summarize(pval = ifelse(sd(prop) == 0, 
#                                                   1 - (mean(prop) - ifelse(mean(Offer) == 4, 0, 1)), 
#                                                   t.test(prop, mu = (ifelse(mean(Offer) == 4, 0, 1)))$p.value),
#                                     propAccept = mean(prop),
#                                     sdAccept = sd(prop)) %>%
#                           ungroup() %>%
#                           mutate(Optimal = rep(c(0,1,1), each = 4),
#                                  Padjusted = p.adjust(pval, method = "BY"))
# 
# temp <- data %>%
#   group_by(SubjID, Offer, Cost) %>%
#   filter(Offer < 20) %>%
#   summarize(propAccept = mean(Choice)) %>% 
#   spread(Cost, propAccept) %>% 
#   ungroup() %>% 
#   select(Cognitive:Wait_P) %>% 
#   apply(., 2, t.test, mu = 0.5) 
# 
# summary_costvsreward <- data.frame(tstat = sapply(temp, "[[", "statistic"), 
#                                    pval = sapply(temp, "[[", "p.value"))
# rownames(summary_costvsreward) <- names(temp)

# get quits and acceptances per cost type for each subject
# revisit this eventually to clean it up
temp <- dataAll %>%
  group_by(SubjID, Offer, Cost) %>%
  filter(Offer < 20) %>%
  summarize(propAccept = mean(Choice),
            accept = sum(Choice),
            quit = sum(Choice == 0)) %>% 
  gather(act, counts, accept:quit) %>% 
  unite(temp, Cost, act, sep = ".") %>% 
  select(SubjID, Offer, temp, counts) %>% 
  spread(temp, counts) %>%
  ungroup() %>% 
  select(Cognitive.accept:Wait_P.quit)

# perform a prop.test based on the group's acceptances and quits per cost
temp2 <- lapply(seq(1, 8, by = 2), function(i) {prop.test(sum(temp[,i]), sum(temp[,i] + temp[,i+1]), p = 0.5, conf.level = 0.95)})

# store stats in a dataframe
summary_costvsreward <- data.frame(probability = sapply(temp2, "[[", "estimate"),
                                   chisquared = sapply(temp2, "[[", "statistic"), 
                                   confint = t(sapply(temp2, "[[", "conf.int")),
                                   pval = sapply(temp2, "[[", "p.value"))
rownames(summary_costvsreward) <- unique(gsub("[.].*","",names(temp)))

rm(temp, temp2)

# create table
pander(round(summary_costvsreward, digits = 4))
```

The table shows a significant bias towards low acceptance for 4 and 8 cent rewards for all but one condition (wait trials associated with cognitive effort). The plot in 16.2.1. shows the proportion of acceptances per reward for each cost condition.

### 16.2. Comparisons among the four delay and effort conditions.

###	16.2.1.

*We will compute the probability of accepting a trial with a mixed-effects logistic regression. Based on the task structure and our main question, our a priori model of interest will include cost condition and reward amount as fixed main effects, and subject ID as a random effect. Cost condition will be modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type). We will run three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions (per 4.2). We anticipate significant main effects (coefficients different than zero) for reward and cost condition. We hypothesize that the differences among cost conditions will follow the pattern described in 4.2.*

``` {r 16.2.1. Overall Proportion diffs, fig.align = "center", fig.width = 6, fig.height = 4, echo = FALSE}  
# ## ECDF of proportion completed per cost type
# temp <- dataAll %>%
#         filter(Choice < 2) %>%
#         #mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait_0", "Wait_1"))) %>%
#         group_by(SubjID, Cost) %>%
#         summarise(pComplete = mean(Choice))
# 
# 
# # plots
# (p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
#         geom_boxplot(show.legend = F) +
#         scale_fill_manual(values = cols) +
#         ylim(c(0, 1)) +
#         labs(y = "Proportion Completed") +
#         theme(panel.grid.major = element_blank(), 
#             panel.grid.minor = element_blank(), 
#             panel.background = element_blank(), 
#             axis.line = element_line(colour = "black"),
#             text = element_text(size = 16)))

```

``` {r 16.2.1., echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
# both methods yield similar outputs, at least coefficients and pvalues
# but the likelihoods will differ of course. The second one might be better in terms of computational needs.
# method 1
# mixLogis_main <- list()
# mixLogis_main$Cog <- glmer(Choice ~ Cost + Offer + (1 | SubjID), family = "binomial", data = data)

# method 2
mixLogis_main <- list()
mixData <- dataAll %>%
  group_by(SubjID, Cost, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
mixLogis_main$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
mixLogis_main$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)

# plot proportion accepted per trial/offer combo
(n2 <- dataAll %>%
        filter(Choice < 2) %>%
        group_by(Cost, Offer) %>%
        summarise(propAccept = mean(Choice),
                  SE = sd(Choice) / sqrt(nSubjs)) %>%
        ungroup() %>%
        mutate(Optimal = rep(c(0, 1, 1), length(unique(dataAll$Cost))),
               #BlockType = as.factor(rep(c(0,1,0,1), each = 3)),
               Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, propAccept, color = Cost)) +
          geom_point(size = 3, show.legend = T) +
          geom_point(aes(y = Optimal), size = 3, pch = 21, fill = "grey75", color = "grey30") +
          geom_line(lwd = 1, show.legend = T) +
          scale_color_manual(values = cols) +
          scale_fill_manual(values = cols) +
          geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5,1)) +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
          labs(y = "Proportion Accepted") +
          theme(legend.position = c(0.8, 0.25),
                legend.key = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"),
                text = element_text(size = 22)))

```

The plot above shows that the pattern of reward acceptances does indeed resemble that from the between-subject experiment for an equivalent time combination. However, the differences in cost are mostly reversed from the previous experiment, following the order stipulated in 4.2. The matrix below shows the coefficients for all cost comparisons, with coefficient size in color and respective p-values enclosed in each box. This figure formally confirms the pattern seen above, although the wait conditions do trend towards significance.

``` {r 16.2.1. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=4}
# get summary of coeffs
rearrange <- c("Cognitive", "Wait_C", "Wait_P", "Physical")
mixSummary <- betaMatrix(mixLogis_main, rearrange = rearrange)
diag(mixSummary$Pvals) <- NA

# remove uninteresting comparisons
mixSummary$Betas[rbind(c(3, 1), c(4,2))] <- NA
mixSummary$Pvals[rbind(c(3, 1), c(4,2))] <- NA

# invert colors
col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))

corrplot(mixSummary$Betas, 
         is.corr = F, 
         p.mat = mixSummary$Pvals, 
         type = "lower",
         outline = T,
         #insig = "p-value",
         sig.level = 0.05, 
         na.label = "square", 
         na.label.col = "grey",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.8,
         col = col2(200))

```

###	16.2.2.

*Next, we will examine whether the a priori model from 16.2.1. outperforms both simpler and more complex models. Unlike the individual logistic regression fits in 16.1.1., a mixed-effects approach gives us a better goodness of fit measure for model comparisons. We will determine the best model (combination of predictors) using Akaike's Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimizes the negative log-likelihood. The regression with each combination of predictors will be fitted in the following order: 1) intercept only; 2) condition only; 3) reward only; 4) condition and reward main effects (from 16.2.3.); and 5) adding a two-way interaction. We predict that model 4 will have the last considerable decrease in the negative log-likelihood.*

``` {r 16.2.2., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
# Quasibinomial GLM versions (with proper proportion setup)
mixLogis_compare <- list()
mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$AllMain <- mixLogis_main$Cognitive
mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (1 | SubjID), family = "binomial", data = mixData)

# Model selection 
abicLogis_compare <- data.frame(Model = names(mixLogis_compare),
                                AIC = sapply(mixLogis_compare, AIC),
                                BIC = sapply(mixLogis_compare, BIC))

# plot 
(mixLogis_compare$plot <- abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
  ggplot(aes(Model, Value, fill = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
    theme_classic())

# effect size
mixLogis_compare$Rsq <- 1 - (deviance(mixLogis_compare$AllMain)/deviance(mixLogis_compare$Base)) # denominator is the null deviance
```

The figure shows that the model with all main effects had the lowest AIC, but not BIC (pseudo R-square: `r round(mixLogis_compare$Rsq, digits = 2)`). We performed a likelihood ratio test to formally determine whether adding cost type to the reward-only model significantly improved the fit. We computed the difference in deviance between the models, and evaluated it under a chi-squared distribution with 3 degrees of freedom (i.e. the number of parameters added to the model, as cost was dummy-coded). The table below summarizes the results, showing that the addition of cost type significantly improved the model fit. (personal note: sure, AIC is 1 value lower when considering the difference in dfs, but that's barely making it..)

``` {r 16.2.2. LRT (anova) table, echo = F}
test <- anova(mixLogis_compare$Reward, mixLogis_compare$AllMain)
rownames(test) <- c("Reward Only", "All Main")

pander(test[c(1, 2, 3, 5, 6, 8)])
```

### 16.3. Modeling the subjective opportunity cost in each condition.

###	16.3.1.

*Response times (RT) for quit responses will be presented in a descriptive manner in order to examine whether participants tended to quit early or late within individual trials. Each cost condition's response time distribution will contain the pooled RT across participants, and we will display the empirical cumulative distribution functions for each condition. Short RT would suggest confident and stable decisions (in support of 4.3.1.).*

``` {r 16.3.1., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
# Proportion of forced travels per subject and cost type
propFails <- dataAll %>%
  filter(Cost != "WAIT") %>%
  group_by(SubjID, Cost) %>%
  summarise(propFails = mean(rawChoice == 2)) %>%
  group_by(Cost) %>%
  summarise(meanQuit = mean(propFails))
# 
# # Reaction times ECDFs including offer and in-trial quits
# (RTs <- data %>%
#   mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
#   filter(rawChoice < 2) %>% 
#   ggplot(aes(RT, color = Cost)) + 
#     #stat_ecdf(lwd = 1.2) +
#     geom_line(aes(y = 1 - ..y..), stat = 'ecdf', lwd = 1.5) +
#     geom_vline(xintercept = 2, lty = 2) + # end of the offer period
#     scale_color_manual(values = cols) +
#     scale_x_continuous(breaks = seq(12), limits = c(0, 14)) +
#     labs(x = "Time in Cost", y = "Proportion Completed") +
#     theme(panel.grid.major = element_blank(),
#       panel.grid.minor = element_blank(),
#       panel.background = element_blank(),
#       axis.line = element_line(colour = "black"),
#       text = element_text(size = 16)))

# NEW VERSION OF SURVIVAL. BUT STILL NEEDS A BIT OF WORK. ALSO, CHECK THAT RT > 14s

library(survival)
library(ggfortify)

# this version of a survival curve forces all successful acceptances to have an RT of 14
# that's to avoid jumps from 2s to 10s to 14s
# 1 - Choice is to reverse the coding of choices, since the survival package assumes 0 = censor?
# to note re: x-axis. In this exp, p's could quit within the 2s offer window. Cost 2 didn't allow that, so it counts from when trial begins.
temp <- dataAll %>%
    mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
    #filter(rawChoice < 2) %>% 
    mutate(#RT = ifelse(Choice == 1, 14, RT),
           Choice = 1 - Choice)

survData <- survfit(Surv(RT, Choice) ~ Cost, data = temp)

autoplot(survData) +
  geom_vline(xintercept = 2, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  scale_x_continuous(breaks = seq(12)) +
  ylim(0, 1) +
  scale_x_continuous(breaks = seq(0, 12), labels = seq(-2, 10)) +
  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
  theme(legend.position = c(0.35, 0.2),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 22))

# ecdf of RTs across blocks for all subjects combined
dataAll %>%
  mutate(RT = ifelse(ResponseType != "OfferQuit", RT + 2, RT)) %>%
  mutate(Choice = 1 - Choice)  %>%
  filter(ResponseType == "OfferQuit") %>%
  ggplot(aes(RT, group = Block, color = Block)) +
    stat_ecdf() +
    #facet_wrap(vars(Cost)) +
    theme_classic()

```

Participants can quit either during the offer period (2s) or during the handling time (10s), allowing for a total of 12 seconds to give up on the current trial. The survival curve above shows quitting throughout the trial for all participants. Censored points signal completions (at end of interval) and forced travels (throughout the trial). The figure suggests that participants made most of their choices quickly within the offer window. The overall proportion of forced trials was scarce (overall mean proportion of fails for cognitive and physical trials were `r unlist(propFails[1:2,2])`, respectively).

###	16.3.2.

*We will also compute the proportion of quits that were performed during the choice window versus during the handling time. If over 80% of quits occurred during the choice window on average, this will suggest that participants were confident in their choices.*

``` {r 16.3.2., echo = FALSE}
# Proportion of quits once the trial started per subject
PropQuits <- dataAll %>%
  filter(!(ResponseType %in% c("Forced Travel", "Forced travel", "Reward"))) %>%
  group_by(SubjID) %>%
  summarise(propAccept = mean(ResponseType == "Quit"))

```

The mean proportion of quits during the handling time was `r round(mean(PropQuits$propAccept), digits = 2)` (SD = `r round(sd(PropQuits$propAccept), digits = 2)`), with `r sum(PropQuits$propAccept > 0.2)` participants accepting fewer than 80% of trials during the offer window.

###	16.3.3.

*In order to further examine choice stability (hypothesis 4.3.1.), we will compute each participant's total proportion of acceptances on the first two and last two blocks. We will compute a mixed-effects linear model to predict post-midpoint proportion of acceptances from pre-midpoint rates, with subjects as random intercepts and condition as a dummy-coded fixed effect. We will report the 95% confidence interval (CI) for the pre-midpoint predictor. A CI containing 1 will denote that participants in that condition produced consistent choices, while accounting for the overall acceptance patterns of a given subject across cost types. (**This is a more elaborate version of the between-subject analysis, which did a pre-post prediction based on the proportion of acceptances per subject across groups**).*

``` {r 16.3.3., echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4, include = F}
# restructure the data
temp <- dataAll %>%
  filter(!(Block %in% c(3,4))) %>%
  group_by(SubjID, Cost, Half) %>%
  summarise(propAccepted = mean(Choice)) %>%
  ungroup() %>%
  spread(Half, propAccepted)

# compute the mixed effects model (linear for this)
mixLogis_prepost <- lmer(Half_2 ~ Half_1 + Cost -1 + (1 | SubjID), data = temp)

# get the coefficients and confidence intervals
t1 <- coefficients(mixLogis_prepost)$SubjID[1, 2:6]
t2 <- as.data.frame(t(confint(mixLogis_prepost)[3:7,]))

# and concatenate them
summary_prepost <- t(bind_rows(t1, t2))
colnames(summary_prepost) <- c("Coefficient", "CI-low", "CI-high")

# # prepost half paired perms
# temp <- temp %>% plyr::dlply("Cost", identity) 
# prepost <- list()
# prepost$cohen <- sapply(temp, function(data) {DescTools::CohenD(data$Half_1, data$Half_2)})
# prepost$perm <- sapply(temp, function(data) {permute(data$Half_1, data$Half_2, paired = T, simple = T)})

## paired tests for first versus last block per cost type
FirstvsLast <- dataAll %>%
  filter(Choice < 2) %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  group_by(SubjID, Cost, Block) %>%
  summarise(propAccept_subj = mean(Choice)) %>%
  spread(Block, propAccept_subj) %>%
  rename(First = `1`, Second = `2`, Third = `3`) %>%
  plyr::dlply("Cost", identity)

prepost <- list()
prepost$Perms <- sapply(FirstvsLast, function(x) {permute(x$First, x$Third, paired = T, simple = T)})
prepost$CohenD <- sapply(FirstvsLast, function(x) {DescTools::CohenD(x$First, x$Third)})

rm(temp, t1, t2)
```

``` {r 16.3.3. plots, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# various plots
# acceptances across blocks
propBlocks <- dataAll %>%
    filter(Choice < 2) %>%
    group_by(SubjID) %>%
    mutate(Block = case_when(
      Block %in% c(1, 2) ~ 1,
      Block %in% c(3, 4) ~ 2,
      Block %in% c(5, 6) ~ 3
    )) %>%
    group_by(SubjID, Cost, Block) %>%
    summarise(propAccept_subj = mean(Choice)) %>%
    group_by(Cost, Block) %>%
    summarize(propAccept = mean(propAccept_subj),
              seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
    ggplot(aes(Block, propAccept, color = Cost)) +
      geom_point(size = 2) +
      geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
      geom_line() +
      ylim(0, 1) +
      labs(y = "Proportion Accepted") +
      scale_x_continuous(breaks = c(1, 2, 3)) +
      scale_color_manual(values = cols) +
      scale_fill_manual(values = cols) +
      theme(legend.key = element_blank(),
         legend.position = c(0.8, 0.25),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank(),
         axis.line = element_line(colour = "black"),
         text = element_text(size = 16))

# Pre-post midpoint
# calculate mean per trial type to draw horizontal/vertical lines pre/post
df_mean <- dataAll %>%
            filter(Choice < 2, !(Block %in% c(3,4))) %>%
            group_by(SubjID, Cost) %>%
            summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
                      propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
            group_by(Cost) %>%
            summarise(propAccept_1 = mean(propAccept_1),
                      propAccept_2 = mean(propAccept_2))

mid <- dataAll %>%
  filter(Choice < 2, !(Block %in% c(3,4))) %>%
  group_by(SubjID, Cost) %>%
  summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
            propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
  ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
    geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
    labs(x = "Proportion Accepted - First Block", y = "Proportion Accepted - Last Block") +
    scale_fill_manual(values = cols) +
    scale_color_manual(values = cols) +
    xlim(0, 1) +
    ylim(0, 1) +
    geom_abline(slope = 1, intercept = 0, lty = 2) +
    geom_hline(data = df_mean, aes(yintercept = propAccept_2, color = Cost), linetype="dashed", show.legend = F) +
    geom_vline(data = df_mean, aes(xintercept = propAccept_1, color = Cost), linetype="dashed", show.legend = F) +
    theme(legend.key = element_blank(),
       legend.position = c(0.8, 0.25),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       panel.background = element_blank(),
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))

# wait vs effort across effort conditions
pAll <- dataAll %>%
  filter(Choice < 2) %>%
  mutate(Cost2 = ifelse(!(Cost %in%  c("Wait_C", "Wait_P")), "EFFORT", "WAIT"),
         BlockType = ifelse(gsub(".*_", "", Cost) == 1, "Physical", "Cognitive")) %>%
  group_by(SubjID, BlockType) %>%
  summarise(Wait_accept = mean(Choice[Cost2 == "WAIT"]),
            Effort_accept = mean(Choice[Cost2 == "EFFORT"])) %>%
  ggplot(aes(Wait_accept, Effort_accept, color = SubjID, shape = BlockType)) +
    geom_point(size = 5, show.legend = T) +
    xlim(0,1) +
    ylim(0,1) +
    geom_abline(slope = 1, intercept = 0, lty = 2) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    theme_classic()

# load the plots
grid.arrange(mid, propBlocks, ncol = 2)

# plot showing the difference in proportion of acceptances between first and last block, effort vs delay for each block type
# lines connect the same subject between the blocks
dataAll %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(SubjID, Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice)) %>%
  ungroup() %>%
  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  spread(Block, propAccept) %>%
  mutate(Difference = `Last Block` - `First Block`) %>%
  group_by(SubjID, Cost) %>%
  summarise(Diffscore = sum(Difference)/3) %>%
  mutate(Type = ifelse(Cost %in% c("Cognitive", "Physical"), "Effort", "Delay"),
         Cost = ifelse(Cost %in% c("Cognitive", "Wait_C"), "Cognitive", "Physical")) %>%
  spread(Type, Diffscore) %>%
  ggplot(aes(Effort, Delay, group = SubjID, fill = Cost)) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0) +
    geom_path(show.legend = F, alpha = 0.5, linetype = "dashed") +
    geom_point(show.legend = T, pch = 21, color = "black", size = 4) +
    scale_fill_manual(values = cols) +
    annotate("text", x = -0.4, y = 0.6, label = "Increased preference for delay over time", size = 5, color = "grey30") +
    annotate("text", x = -0.5, y = -0.6, label = "All acceptances decreased", size = 5, color = "grey30") +
    annotate("text", x = 0.5, y = 0.6, label = "All acceptances increased", size = 5, color = "grey30") +
    annotate("text", x = 0.4, y = -0.6, label = "Increased preference for effort over time", size = 5, color = "grey30") +
    labs(x = "P(Effort): Last - First Block", y = "P(Delay): Last - First Block", fill = "Block type") +
    ylim(-0.7, 0.7) +
    xlim(-0.7, 0.7) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.35),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 20))

### CODE TO LOOK AT EARNINGS PER BLOCK AND CALCULATE OPTIMAL EARNINGS
# # code to calculate the rwd/sec rate for each acceptance threshold per handling
# rwd <- c(4, 8, 20)
# handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
# travel <- c(2, 6, 14) + 2
# rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
# 
# # the highest reward amount for a typical 7-min block per handling is:
# apply(rwdRates, 1, max) * (7 * 60)

# # this helps make sense of the toal earnings
# # plotting mean earnings per cost and block
# dataAll %>%
#   filter(rawChoice == 1) %>%
#   group_by(SubjID) %>%
#   mutate(Block = case_when(
#     Block %in% c(1, 2) ~ 1,
#     Block %in% c(3, 4) ~ 2,
#     Block %in% c(5, 6) ~ 3
#   )) %>%
#   group_by(SubjID, Cost, Block) %>%
#   summarise(subEarnings = sum(Offer)) %>%
#   group_by(Cost, Block) %>%
#   summarise(meanEarned = mean(subEarnings),
#             seEarned = sd(subEarnings) / sqrt(nSubjs)) %>%
#   ggplot(aes(Block, meanEarned, color = Cost)) +
#     geom_point(size = 2) +
#     geom_errorbar(aes(ymin = meanEarned - seEarned, ymax = meanEarned + seEarned, color = Cost), width = 0.1, size = 1.5) +
#     geom_line(size = 1.5) +
#     labs(y = "Mean Earnings +- SE (cents)") +
#     scale_x_continuous(breaks = c(1, 2, 3)) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     theme(legend.key = element_blank(),
#           #legend.position = c(0.1, 0.8),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_blank(),
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 22))

```

These participants tended to accept fewer trials on the second half of the experiment (Beta = `r round(summary_prepost[1,1], digits = 2)`, 95% CI: `r round(summary_prepost[1,2:3], digits = 2)`). The figure on the left shows this tendency, although some subjects shows considerable consistency. The plot on the right divides the proportion of acceptances across blocks (each cost block is experienced thrice), and shows a global decrease in acceptances as a function of experimental time.

A better test is to perform pairwise comparisons between the first and last block per cost. Paired permutations on means of proportions showed that all participants accepted fewer trials during the second half, regardless of cost (all p < 0.05; Cohen's D: cognitive = `r prepost$CohenD[1]`, physical = `r prepost$CohenD[2]`, wait-cognitive = `r prepost$CohenD[1]`, wait-physical = `r prepost$CohenD[1]`).

Now let's divide them by reward and handling amounts. The plots below show that initially participant choices resembled those from the between-subject experiment, accepting more cognitive trials than any other, and displaying higher costs for physical/wait_p. However, by the end of the experiment all cost types were exacerbated. As seen before, cognitive trials had the greatest decrease in acceptances across reward amounts. This re-evaluation was not present when participants faced only one type of cost.

``` {r 16.3.3. Plot Pre/Post reward x handling, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# # first block
# t1 <- data %>%
#   group_by(SubjID) %>%
#   mutate(Block = do.call(c, lapply(c(2, 4, 6), function(x) {rep(x / 2, sum(Block %in% c(x - 1, x)))}))) %>%
#   #filter(Half == "Half_1", Offer < 20) %>%
#   filter(Block == 1) %>%
#   group_by(Cost, Offer) %>%
#   summarise(propAccept = mean(Choice),
#             SE = sd(Choice) / sqrt(nSubjs)) %>%
#   ungroup() %>%
#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
#   ggplot(aes(Offer, propAccept, color = Cost)) +
#     geom_point(size = 3, show.legend = F) +
#     #geom_point(aes(y = Optimal), size = 3, pch = 21, color = "darkgrey") +
#     geom_line(show.legend = F) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     geom_errorbar(aes(ymin=propAccept-SE, ymax=propAccept+SE), width=0.2, size=1, show.legend = T) +
#     scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
#     labs(x = "Reward", y = "Proportion Accepted", title = "First Block") +
#     theme(legend.key = element_blank(),
#           legend.position = c(0.8, 0.25),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
# 
# 
# # last block
# t3 <- data %>%
#     group_by(SubjID) %>%
#     mutate(Block = do.call(c, lapply(c(2, 4, 6), function(x) {rep(x / 2, sum(Block %in% c(x - 1, x)))}))) %>%
#     #filter(Half == "Half_2", Offer < 20) %>%
#     filter(Block == 3) %>%
#     group_by(Cost, Offer) %>%
#     summarise(propAccept = mean(Choice),
#               SE = sd(Choice) / sqrt(nSubjs)) %>%
#     ungroup() %>%
#     mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
#     ggplot(aes(Offer, propAccept, color = Cost)) +
#       geom_point(size = 3, show.legend = F) +
#       geom_line(show.legend = F) +
#       scale_color_manual(values = cols) +
#       scale_fill_manual(values = cols) +
#       geom_errorbar(aes(ymin=propAccept-SE, ymax=propAccept+SE), width=0.2, size=1, show.legend = F) +
#       scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
#       scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
#       labs(x = "Reward", y = "", title = "Last Block") +
#       theme(legend.position = c(0.1, 0.7),
#             panel.grid.major = element_blank(), 
#             panel.grid.minor = element_blank(), 
#             panel.background = element_blank(), 
#             axis.line = element_line(colour = "black"),
#             text = element_text(size = 16))
# 
# grid.arrange(t1, t3, ncol = 2)

dataAll %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice),
            SE = sd(Choice) / sqrt(nSubjs)) %>%
  ungroup() %>%
  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  ggplot(aes(Offer, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = T) +
    #geom_point(aes(y = Optimal), size = 3, pch = 21, color = "darkgrey") +
    geom_line(size = 1, show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(x = "Reward", y = "Proportion Accepted") +
    facet_wrap(vars(Block)) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 22))

```

This prompted the question of whether fitting the mixed logistic model could confirm this shift in preferences. Just as before, the matrix below show the coefficient magnitude (color) and pvalues for differences based on iterating through costs as reference dummy codes.

``` {r 16.3.3. mix pre/post separately, echo = FALSE, fig.align="center", fig.width=5, fig.height=4}
## compute the same mixed effects logistic for each half
# mixed logistic for the first half
mixLogis_pre <- list()
mixData <- dataAll %>%
  filter(Half == "Half_1") %>%
  group_by(SubjID, Cost, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
mixLogis_pre$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
mixLogis_pre$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)

# mixed logistic for the second half
mixLogis_post <- list()
mixData <- dataAll %>%
  filter(Half == "Half_2") %>%
  group_by(SubjID, Cost, Offer) %>%
  summarize(totalChoices = length(Choice),
            totalAccepted = sum(Choice),
            totalQuits = sum(Choice == 0),
            propAccepted = mean(Choice))

mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_C"))
mixLogis_post$Wait_C <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait_P"))
mixLogis_post$Wait_P <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)

## now produce a summary matrix
# get the beta and pvalue matrices 
betasPre <- betaMatrix(mixLogis_pre)
betasPost <- betaMatrix(mixLogis_post)

# and combine them
betaMat <- matrix(NA, nrow = nrow(betasPre$Betas), ncol = nrow(betasPre$Betas))
betaMat[lower.tri(betaMat)] <- betasPre$Betas[lower.tri(betasPre$Betas)]
betaMat[upper.tri(betaMat)] <- betasPost$Betas[upper.tri(betasPost$Betas)]
dimnames(betaMat) <- list(names(mixLogis_pre), names(mixLogis_pre))

pvalMat <- matrix(NA, nrow = nrow(betasPre$Pvals), ncol = nrow(betasPre$Pvals))
pvalMat[lower.tri(pvalMat)] <- betasPre$Pvals[lower.tri(betasPre$Pvals)]
pvalMat[upper.tri(pvalMat)] <- betasPost$Pvals[upper.tri(betasPost$Pvals)]
dimnames(pvalMat) <- list(names(mixLogis_pre), names(mixLogis_pre))

# remove uninteresting comparisons 
diag(betaMat) <- 0
betaMat[rbind(c(1, 3), c(2, 4), c(3, 1), c(4,2))] <- NA
pvalMat[rbind(c(1, 3), c(2, 4), c(3, 1), c(4,2))] <- NA

# aand plot
corrplot(betaMat, 
         is.corr = F, 
         p.mat = pvalMat, 
         outline = T,
         #insig = "p-value",
         sig.level = 0.05, 
         na.label = "square", 
         na.label.col = "grey",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.8,
         col = col2(200))
```

Finally, we can compare how the difference in proportion accepted between last and first blocks changes between trial types. The plots below show that effort and delay trials in the cognitive blocks tended to be rejected more on the last block (i.e. they land on the negative side of both axes). The plot on the right shows a similar pattern for trials on the physical blocks, but these are more similar across subjects, and also show a small tendency to accept more on either first or last blocks.

``` {r 16.3.3 temp plot, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}

cw <- dataAll %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  filter(Offer < 20) %>%
  filter(Block != 2) %>%
  group_by(SubjID, Block, Cost, Offer) %>%
  summarise(pAccept = mean(Choice)) %>%
  spread(Block, pAccept) %>%
  mutate(diff = `3` - `1`) %>%
  ungroup() %>%
  select(-c(`1`, `3`)) %>%
  spread(Cost, diff) %>%
  ggplot(aes(Cognitive, Wait_C, fill = as.character(Offer))) +
    geom_point(pch = 21, color = "black", size = 3) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
    ylim(-1, 1) +
    xlim(-1, 1) +
    labs(#title = "P(Accepted): Last - First Block",
         x = "P(Cognitive): Last - First",
         y = "P(Wait_C): Last - First",
         fill = "Offer") +
    theme(legend.key = element_blank(),
          legend.background = element_rect(fill = "grey80"),
          legend.position = c(0.8, 0.8),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

gw <- dataAll %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  filter(Offer < 20) %>%
  filter(Block != 2) %>%
  group_by(SubjID, Block, Cost, Offer) %>%
  summarise(pAccept = mean(Choice)) %>%
  spread(Block, pAccept) %>%
  mutate(diff = `3` - `1`) %>%
  ungroup() %>%
  select(-c(`1`, `3`)) %>%
  spread(Cost, diff) %>%
  ggplot(aes(Physical, Wait_P, fill = as.character(Offer))) +
    geom_point(pch = 21, color = "black", size = 3, show.legend = F) +
    geom_hline(yintercept = 0) +
    geom_vline(xintercept = 0) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
    ylim(-1, 1) +
    xlim(-1, 1) +
    labs(#title = "P(Accepted): Last - First Block",
         x = "P(Physical): Last - First",
         y = "P(Wait_P): Last - First",
         fill = "Offer") +
    theme(legend.position = c(0.8, 0.8),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

grid.arrange(cw, gw, ncol = 2)

# more prepost tests
# diffscore prepost for effort vs wait
dataAll %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(SubjID, Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice)) %>%
  ungroup() %>%
  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  spread(Block, propAccept) %>%
  mutate(Difference = `Last Block` - `First Block`) %>%
  group_by(SubjID, Cost) %>%
  summarise(Diffscore = sum(Difference)/3) %>%
  spread(Cost, Diffscore) %>%
  ggplot() +
    geom_point(aes(Cognitive, Wait_C), color = cols[1]) +
    geom_point(aes(Physical, Wait_P), color = cols[2]) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    ylim(-0.5, 0.5) +
    xlim(-0.5, 0.5) +
    #geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
    #geom_boxplot(show.legend = F, size = 1.5) +
    #geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
    #scale_color_manual(values = cols) +
    #scale_fill_manual(values = cols) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 22))

# diffscore per cost type (you don't see if specific subjects are prone to increasing/decreasing acceptances across them)
dataAll %>%
  group_by(SubjID) %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Half == "Half_1", Offer < 20) %>%
  filter(Block != 2) %>%
  mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
  group_by(SubjID, Cost, Block, Offer) %>%
  summarise(propAccept = mean(Choice)) %>%
  ungroup() %>%
  #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  spread(Block, propAccept) %>%
  mutate(Difference = `Last Block` - `First Block`) %>%
  group_by(SubjID, Cost) %>%
  summarise(Diffscore = sum(Difference)/3) %>%
  ggplot(aes(Cost, Diffscore, fill = Cost)) +
    geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
    geom_boxplot(show.legend = F, size = 1.5) +
    geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
    scale_color_manual(values = cols) +
    scale_fill_manual(values = cols) +
    theme(legend.key = element_blank(),
          legend.position = c(0.9, 0.25),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 22))
```

### 16.3.4.

*To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant's probability of completing a trial based on the difference between the delayed reward's magnitude and the estimated opportunity cost (OC) for each cost type. OC will be computed as the product of a free parameter (gamma) and the handling time. Both gamma and the temperature parameter of the logistic function will be estimated at the subject level, independently for each subject and cost type.*

``` {r 16.3.4., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
# Here it might be best to estimate gamma for the wait trials only at first
# once the wait OCs are estimated, then they can be modulated by effort
# Estimate gamma per subject for each group separately
summaryOC <- list()
summaryOC$all <- dataAll %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(Choice < 2) %>%
  group_by(SubjID, Cost) %>% #group_by(SubjID, Cost, Block) %>%
  do(optimizeOCModel(., simplify = T)) %>%
  ungroup()

# plot
(summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
    geom_boxplot(show.legend = F) +
    geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
    geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
    geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
    ylim(0,1.5) +
    labs(x = "") +
    scale_fill_manual(values = cols) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16)))

# try to replicate the group-level proportion of acceptances from 16.2
# this looks pretty much like the empirical proportion data, so the stochasticity is playing a major part in the estimation
# the estimate probability even matches actual proportions at the single subject level 
# logis <- mapply(function(g, t) {1 / (1 + exp((-1 * t) * (c(4, 8, 20) - (g * 10))))}, summaryOC$all$Gamma, summaryOC$all$Temperature)
# colnames(logis) <- unite(summaryOC, test, SubjID, Cost)$test
# logis2 <- as.data.frame(logis) %>% 
#   gather(Cost, Probability) %>%
#   mutate(SubjID = substr(Cost, 1,3), 
#          Cost = substr(Cost, 5,20),
#          Reward = rep(c(4,8,20), nrow(.)/3)) %>%
#   group_by(Cost, Reward) %>%
#   summarize(propAccept = mean(Probability)) %>%
#   ggplot(logis2, aes(Reward, propAccept, color = Cost)) +
#     geom_point(size = 3, show.legend = T) +
#     geom_line(lwd = 1, show.legend = T) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     #geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
#     scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
#     scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
#     labs(y = "Proportion Accepted") +
#     theme(legend.key = element_blank(),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_blank(),
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
```

The figure on the left shows the distribution of fitted gammas for each cost type, and inversely matches the proportion of acceptances described previously. The plot on the right shows the OC for each subject, divided by cost type. The horizontal line denotes total earnings per second under the optimal strategy for the time and reward combinations.

###	16.3.5.

*We will cross-validate each subject's OC value using the first four blocks (two cognitive, two physical) for estimation, and the last two blocks (one of each effort type) choices for testing. The estimates will be used to predict acceptances in the testing sample, and the mean percent correctly predicted will be reported for each cost type. This will also provide information on the stability of each participant's choices (4.3.1.).*

``` {r 16.3.5., echo = FALSE, fig.width=5, fig.height=4, fig.align="center"}
# subdivide data
dataTrain <- dataAll %>%
   filter(Block < 5)

dataTest <- dataAll %>%
  filter(Block > 4)

# estimate
# per-cost, but consider the idea above
OCs_validation <- list()
temp <- dataTrain %>% filter(Cost == "Wait_C") %>% plyr::dlply("SubjID", identity)
OCs_validation$Wait_C <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
temp <- dataTrain %>% filter(Cost == "Wait_P") %>% plyr::dlply("SubjID", identity)
OCs_validation$Wait_P <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
temp <- dataTrain %>% filter(Cost == "Cognitive") %>% plyr::dlply("SubjID", identity)
OCs_validation$Cognitive <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
temp <- dataTrain %>% filter(Cost == "Physical") %>% plyr::dlply("SubjID", identity)
OCs_validation$Physical <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})

# reshape data
temp <- bind_rows(OCs_validation) %>% 
  mutate(SubjID = subjList) %>%
  gather(Cost, gamma, Wait_C:Physical) %>%
  left_join(dataTest, ., by = c("SubjID", "Cost")) %>% # assign OCs to each subject per cost type
  mutate(prediction = Offer > Handling * gamma) %>%
  # plyr::dlply("SubjID", identity)
  group_by(SubjID, Cost) %>%
  summarize(predicted = mean(Choice == prediction))

# plot prediction %
qplot(Cost, predicted, geom = "boxplot", data = temp) + 
  ylim(0,1) +
  theme_classic()
```

The figure above shows that each participant's estimated gamma successfully predicted choices in the last two blocks to a high degree (suspisiouly, considering the decrease in the acceptance rate as a function of time).

###	16.3.6.

*The OC estimates for each group will be compared using a repeated measures ANOVA with cost as a factor. This will let us determine which cost type produced the highest discounting.*

``` {r 16.3.6., echo = FALSE}
# repeated measures anova
OCs_anova <- list()
OCs_anova$aov <- summary(aov(Gamma ~ Cost + Error(SubjID / Cost), data = summaryOC$all))

# table
pander(OCs_anova$aov)

# do all pairwise comparisons
OCs_anova$gammas <- summaryOC$all %>% 
  reshape2::dcast(SubjID ~ Cost, value.var = "Gamma") %>%
  select(-SubjID)

# perform a paired permutation among every pair of cost types
OCs_anova$perms <- outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(permute), simple = T, paired = T)
OCs_anova$perms[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA

# and the effect sizes
OCs_anova$ES <- abs(outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(DescTools::CohenD)))
OCs_anova$ES[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
```

(note: here 'Cost' is cost type). The ANOVA table shows that there are no significant differences among cost types for the current sample. The following plot shows the resulting p-values from performing a paired permutation analysis among all relevant cost types, with color indicating the effect size of the comparison. The differences only partially match those seen in 16.2.1., so the OC estimates seem noisy.

``` {r 16.3.6. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
corrplot(OCs_anova$ES,
         is.corr = F, 
         p.mat = OCs_anova$perms,
         type = "upper",
         insig = "p-value",
         sig.level = -1,
         na.label = "square",
         na.label.col = "grey",
         method = "color", 
         tl.col = "black", 
         tl.cex = 0.8,
         outline = T)
```

### Testing grounds

``` {r test plots, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
# per-subject acceptances per trial and reward amount
# tp1 <- dataAll %>%
#         group_by(SubjID) %>%
#         mutate(FirstBlock = ifelse(Btype[1] == 0, "Cognitive", "Physical")) %>%
#         group_by(FirstBlock, SubjID, Cost, Offer) %>%
#         summarise(pAccept = mean(Choice),
#                   SE = sd(Choice) / sqrt(length(Choice))) %>%
#         ggplot(aes(Offer, pAccept, color = SubjID)) + 
#           geom_point(size = 3) + 
#           geom_line(aes(group = SubjID), size = 1) +
#           labs(x = "Offer", y = "Proportion Accepted") +
#           facet_wrap(vars(Cost), ncol = 2) +
#           theme(legend.key = element_blank(),
#                 panel.grid.major = element_blank(), 
#                 panel.grid.minor = element_blank(), 
#                 panel.background = element_blank(), 
#                 axis.line = element_line(colour = "black"),
#                 text = element_text(size = 16))

# acceptances per cost x reward based on what block was experienced first
# REPLICATE LIAMS PLOTS TOO
tp2 <- dataAll %>%
        group_by(SubjID) %>%
        mutate(FirstBlock = ifelse(Btype[1] == 0, "Cognitive", "Physical")) %>%
        group_by(FirstBlock, SubjID, Cost, Offer) %>%
        summarise(pAccept_subj = mean(Choice)) %>%
        group_by(FirstBlock, Cost, Offer) %>%
        summarise(pAccept = mean(pAccept_subj),
                  SE = sd(pAccept_subj) / sqrt(length(pAccept_subj))) %>%
        mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, pAccept, color = Cost)) + 
          geom_point(size = 3) + 
          geom_line(aes(group = Cost), size = 1) +
          geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.6, size = 1, show.legend = F) +
          scale_color_manual(values = cols) +
          scale_fill_manual(values = cols) +
          labs(x = "Offer", y = "Proportion Accepted") +
          facet_wrap(vars(FirstBlock), ncol = 2) +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
          theme(legend.key = element_blank(),
                legend.position = c(0.8, 0.25),
                panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line = element_line(colour = "black"),
                text = element_text(size = 16))

# prop acceptances per reward amount, divided by first/last block and first block experienced
tp3 <- dataAll %>%
        mutate(Block = case_when(
          Block %in% c(1, 2) ~ 1,
          Block %in% c(3, 4) ~ 2,
          Block %in% c(5, 6) ~ 3
        )) %>%
        filter(Choice < 2, Block %in% c(1, 3)) %>%
        group_by(SubjID) %>%
        mutate(FirstBlock = ifelse(Btype[1] == 0, "Cognitive", "Physical")) %>%
        group_by(Half, FirstBlock, SubjID, Cost, Offer) %>%
        summarise(pAccept_subj = mean(Choice)) %>%
        group_by(Half, FirstBlock, Cost, Offer) %>%
        summarise(pAccept = mean(pAccept_subj),
                  SE = sd(pAccept_subj) / sqrt(length(pAccept_subj))) %>%
        mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, pAccept, color = Cost)) + 
          geom_point(size = 3) + 
          geom_line(aes(group = Cost), size = 1) +
          geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.6, size = 1, show.legend = F) +
          scale_color_manual(values = cols) +
          scale_fill_manual(values = cols) +
          labs(x = "Offer", y = "Proportion Accepted") +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
          facet_wrap(vars(FirstBlock, Half), ncol = 4) +
          theme(legend.key = element_blank(),
                panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line = element_line(colour = "black"),
                text = element_text(size = 16))

# Liams plots
tp4_overall <- dataAll %>%
                  filter(Choice < 2) %>%
                  group_by(SubjID) %>%
                  mutate(FirstBlock = ifelse(Btype[1] == 0, "Cognitive", "Physical")) %>%
                  group_by(FirstBlock, SubjID) %>%
                  summarise(pAccept_subj = mean(Choice)) %>%
                  group_by(FirstBlock) %>%
                  summarise(pAccept = mean(pAccept_subj),
                            SE = sd(pAccept_subj) / sqrt(length(pAccept_subj))) %>%
                  qplot(FirstBlock, pAccept, geom = "point", data = .) + 
                  geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.6, size = 1, show.legend = F) + 
                  ylim(0, 1) +
                  theme_classic()

tp4_percost <- dataAll %>%
                filter(Choice < 2) %>%
                group_by(SubjID) %>%
                mutate(FirstBlock = ifelse(Btype[1] == 0, "Cognitive", "Physical")) %>%
                group_by(FirstBlock, SubjID, Half, Cost) %>%
                summarise(pAccept_subj = mean(Choice)) %>%
                group_by(FirstBlock, Half, Cost) %>%
                summarise(pAccept = mean(pAccept_subj),
                          SE = sd(pAccept_subj) / sqrt(length(pAccept_subj))) %>%
                ggplot(aes(Cost, pAccept, color = FirstBlock)) +
                  geom_point(aes(fill = FirstBlock), size = 3, show.legend = T) +
                  geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1, show.legend = F) +
                  ylim(0, 1) +
                  facet_wrap(vars(Half), ncol = 2) +
                  theme(legend.key = element_blank(),
                        panel.grid.major = element_blank(), 
                        panel.grid.minor = element_blank(), 
                        panel.background = element_blank(), 
                        axis.line = element_line(colour = "black"),
                        text = element_text(size = 16))

# number of forced travels as a function of time for cognitive and grip trials
dataAll %>%
  mutate(Block = case_when(
    Block %in% c(1, 2) ~ 1,
    Block %in% c(3, 4) ~ 2,
    Block %in% c(5, 6) ~ 3
  )) %>%
  #filter(ResponseType == "Forced Travel") %>% 
  group_by(SubjID, Cost, Block) %>%
  filter(Cost %in% c("Cognitive", "Physical")) %>%
  summarise(pTravel = mean(rawChoice == 2)) %>%
  group_by(Cost, Block) %>%
  summarise(mTravels = mean(pTravel),
            SE = sd(pTravel) / sqrt(nSubjs)) %>%
  ggplot(aes(Block, mTravels, color = Cost)) +
    geom_line(size = 1) +
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = mTravels - SE, ymax = mTravels + SE), width = 0.2) +
    labs(y = "Prop. of forced travels") +
    scale_x_continuous(breaks = seq(3)) +
    ylim(0, NA) +
    theme(legend.key = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

# ### COGNITIVE LOGS
# # no changes in time, but might be worth revisiting
# # First looks at the new data
# setwd('./data/')
# files <- dir(pattern = 'coglog')
# nSubjs <- length(files)
# 
# # load data and assign subject id (lazy way because this data has no headers)
# temp <- lapply(files, read.csv, header = F)
# for (i in seq_along(temp)) {
#   temp[[i]]$SubjID <- substring(files[i], 8, 10)
# }
# data <- do.call(rbind, temp)
# colnames(data) <- list("Handling", "Offer", "Response", "RT", "CostTime", "ExpTime", "wat", "Task", "Options", "SubjID")
#   
# # Get just the subject list and number of subjects
# subjList <- unique(data$SubjID)
# nSubjs <- length(subjList)
# 
# # create a trial starter indicator per subject
# test <- data %>%
#   filter(Response != 0) %>%
#   group_by(SubjID)  %>%
#   mutate(CostTime = round(CostTime),
#          OfferLag = c(0, lag(Offer)[-1]),
#          TimeLag = c(0, lag(CostTime)[-1]),
#          trialStart = (Offer != OfferLag) | (TimeLag > CostTime)) %>%
#   plyr::dlply("SubjID", identity)
# 
# # now input trial number 
# for (x in seq_along(test)) {
#   data <- test[[x]]
#   trial <- 0
#   temp <- numeric()
#   for(i in seq(nrow(data))) {
#     if (data$trialStart[i]) {
#       trial <- trial + 1
#     }
#     
#     temp <- c(temp, trial)
#   }
#   
#   test[[x]]$trialN <- temp
# }
# 
# # put everyone into a single dataframe
# cogLogs <- do.call(rbind, test) %>%
#   select(SubjID, Handling, Offer, Response, RT, CostTime, trialN) %>%
#   group_by(SubjID, trialN) %>%
#   summarise(nErrors = sum(Response == 2),
#             medianRT = median(RT)) %>%
#   group_by(trialN) %>%
#   summarise(meanErrors = mean(nErrors),
#             meanRT = mean(medianRT)) %>%
#   ggplot(aes(trialN, meanErrors)) +
#     geom_line(show.legend = F, size = 1) +
#     #ylim(0, 1) +
#     theme_classic()

```

## 17. Inference criteria

These criteria will remain the same as before. For the ANOVAs, we will report the F statistic as well as the p-value. For the multiple linear regressions and logistic regression, we will report the betas (coefficients) and their associated p-values. When comparing two groups of values as in pairwise comparisons, we will use non-parametric permutation tests. We will report p-values and effect sizes, and all tests will be two-tailed. The alpha threshold for p-value evaluation will be set at 0.05.

## 18. Data exclusion

### 18.1. Missing data and quitting early.

Participants are told that they are allowed to stop participation in the study at any time without consequence. Data from participants who do not finish the experiment will be excluded from the study, and those participants will be replaced.

### 18.2. Inattentiveness

To guard against inattentiveness, a single 30 second catch trial will be placed at the end of each experimental block, merely prompting participants to press a key. From the pilot study, participants are able to respond within three seconds. Based on this, a response within three seconds will be considered as proper engagement, and a participant that fails two or more of these checks will be excluded and replaced.

### 18.3. Reasonable choices

The task is structured so that one reward amount must always be accepted. Thus, a participant who quits every trial in at least one block will be assumed not to have followed or understood task instructions, or to have disengaged from the task altogether, and will be excluded and replaced.

### 18.4. Performance

In the cognitive effort condition, participants were forced to travel if they made 2 mistakes in a trial. Any participant with more than 30% forced travels will be excluded and replaced.

## 5. Existing data

Registration prior to creation of data

## 6. Data collection

The study will use human subjects recruited from the university community, who will be recruited through the university job board. We will pay up to $30 for a session (1 hour), which includes incentive-based rewards. Participants will be ineligible if they have participated in our pilot study, or they are under 18 years of age. The study will run for however long it takes to reach our desired sample size.

## 7. Sample size

We will acquire a sample of 48 participants.

## 8. Sample size rationale?

Sample sizes were determined by means of power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four groups (one for each condition). The resulting sample size was 45, which we increased to 48 in order to match the potential order of blocks and colors (section 15) while further ensuring that we have enough power.

## 9. Variables

### 9.1 The present study has three levels of manipulation.

9.1.1. Cost condition, manipulated within subjects. The conditions are (a) unfilled delay, (b) cognitive effort, and (c) physical effort. Unfilled delays will be paired with each effort type in a blocked manner (7-minute blocks). Each combination will be experienced three times.

9.1.2. Handling and travel times. These will dictate how long each trial is. The "handling time" governs how long it is necessary to wait or work to obtain a reward if a trial is accepted. The "travel time" governs how long the inter-trial interval will be, regardless of whether the trial is accepted. Participants will know that the handling time will be always 10 seconds, and the travel time 6 seconds (matching one of the between-group experiment conditions).

9.1.3. Reward magnitude, manipulated within-subject across individual trials. On each trial, participants will learn the amount of money they can earn if they complete the trial (i.e. 4, 8, or 20 cents). The amounts will be sampled uniformly, while guaranteeing that each participant experiences each amount at least twice during each block.

## 10. Measured variables

### 10.1. Behavioral variables

10.1.1. Choice (complete or quit a given trial).

10.1.2. Response times.

10.1.3. Total earnings.

10.1.3. Performance in the cognitive effort tasks (right or wrong answer).

10.1.4. Grip force throughout the experiment and maximum grip strength (physical effort condition).

### 10.2. Questionnaire

10.2.1. Age.

10.2.2. Gender.

10.2.3. Post-experimental oral assessment of choice strategy adoption. We will ask participants the following: "Did you follow a specific acceptance strategy? If so, what was it?" and "Which condition felt most effortful to you?". Answers will be written down by the experimenter, and recorded on an excel spreadsheet.

## 11. Indices

### 11.1. Behavioral data

11.1.1. Proportion of prospects accepted.

11.1.2. Percentage of cognitive effort trials with above-threshold errors (over 2 errors), in which participants are forced to travel to the next trial.

### 11.2. Optimal behavior

The theoretical opportunity cost of time will be calculated for each handling/travel/reward acceptance combination in order to assess choice optimality. This measure is computed as the cents per second possible when consistently accepting only certain reward amounts (e.g. 8 and 20 cents) in a given timing condition. This ground truth measure is independent of cost type, allowing us to assess subject optimality.

## 12. Study type

Experiment - A researcher randomly assigns treatments to study subjects, this includes field or lab experiments. This is also known as an intervention experiment and includes randomized controlled trials.

## 13. Blinding

No blinding is involved in this study.

## 14. Study design

The present study complements our previous one, which evaluated cost types through a between-group design. Many of the details remain the same. However, this time every participant will experience all forms of cost (delay, physical effort, and cognitive effort). Delay trials will be intermixed with both physical and cognitive trials, providing a common condition to compare these effortful costs. On each trial, participants will have the opportunity to either wait or work for 10 seconds (the "handling time") in order to earn a reward; alternatively, they can quit by pressing the space bar and skip to the next trial (which incurs a 6 second travel time). Two types of trial combinations (physical/wait and cognitive/wait) will be experienced three times by each participant in 7-minute-long, interleaved blocks. Reward amounts can be 4, 8, or 20 cents, uniformly distributed. Timing information will be disclosed at the beginning of each block, and reward prospects displayed before each trial begins.

## 15. Randomization

### 15.1. Block type 
Each block will contain unfilled delay trials and trials of one effortful cost type (se 14.1). Blocks with each cost type will be interleaved, and participants will be assigned to one of two orders: beginning with a cognitive/wait or a physical/wait block. A row will be assigned to subject IDs prior to recruitment, ensuring that each order is experienced equally often. Participants will be offered a break after completing three out of the six blocks.

### 15.2. Rewards and cost type 
Participants can earn 4, 8, or 20 cents per trial at the cost of performing one of the three conditions. These values are sampled without replacement from a vector containing every combination of cost (effort defined by the current block, and delay) and reward. The vector is reshuffled once completed. This ensures that each combination of cost and reward is presented at least twice per block.

### 15.3. Cost color 
During the offer phase, each cost type will appear in a unique color in order to ease its identification. Colors were chosen to contrast each other while being amenable to red-green color-blindness. Colors will be assigned to each cost type so that all three colors are equally paired to each cost type across participants. A row will be assigned to subject IDs prior to recruitment to indicate their block order and color pairing.

### 2020-07-28 Cost3/how_much.R

@@ -1,0 +1,32 @@
+# Sets current work directory to the one containing the csv file with the data
+dataDir <- "./Task/data/"
+dataFile <- "532_cost3_11022019_main_log.csv"
+
+# Loads the csv file into R as a data frame
+data <- read.csv(paste(dataDir, dataFile, sep = ""))
+
+# Choices holds all the yes and no decisions everyone made, and rewards holds every offer corresponding to each trial. 
+b <- data.frame(choices <- data[4], 
+          rewards <- data[3])
+
+# This produces the row numbers (trial numbers) in which people accepted an offer
+yes=which(b[[1]] == 1, arr.ind=TRUE)
+
+# Produces a dataframe which shows only the trials in which the person accepted the offer 
+yesTrial=b[yes,]
+
+# Sums up the total amount of cents this participant earned 
+cents=sum(yesTrial[[2]])
+
+# Converts to dollars for better presentation
+dollars=12+(cents/100)
+  
+# Prints a value the participant earned to the screen, updating depending on the value
+sprintf("This participant earned %s dollars", dollars)  
+
+
+
+
+
+
+

### 2020-07-28 Cost3/inattentiveness.R

@@ -1,0 +1,25 @@
+# This script will browse the attention logs and print out who doesn't meet criteria 
+# Per pre-registration, anyone taking over 3 secs to respond is considered inattentive
+# and should be removed from the participant pool
+
+# Quietly load tidyverse
+suppressMessages(library(tidyverse))
+
+# change directory and find the attention files
+setwd('./data/')
+files <- dir(pattern = "attention")
+
+# load them, find subjects with 2 or more attention trials longer than 3 secs, and print to terminal
+t1 <- tibble(SubjID = files) %>% 
+  mutate(content = map(SubjID, ~read_csv(., col_names = F, col_types = cols())),
+         SubjID = substring(SubjID, 11, 13)) %>%
+  unnest() %>% 
+  group_by(SubjID) %>%
+  summarize(inattention = sum(floor(X2) > 3)) %>%
+  filter(inattention > 1) %>%
+  print(SubjID)
+
+# print out the current number of valid participants
+finalN <- length(files) - nrow(t1)
+
+sprintf("Current valid n of subjects: %s", finalN)

### 2020-07-29 Simulations/manuscript_modeling.R
fit initial gamma, providing a single bias parameter that also fits the single gamma model well

@@ -667,7 +667,7 @@ bOC <- T
 baseLogistic <- F # to test whether the brute search converges to a conventional logistic through glm()
 fwOC <- F
 dOC <- F
-twOC <- T
+twOC <- F
 
 # which experimental dataset?
 data <- dataBtw %>% 
@@ -844,7 +844,7 @@ if (twOC) {
 }
 
 #plot
-param_compare_plot(trialwiseOC_btw_us, "tempr", meanRate = 1) 
+#param_compare_plot(trialwiseOC_btw_us, "tempr", meanRate = 1) 
 
 
 ### test
@@ -862,7 +862,7 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
   o <- subjData$Offer
   h <- subjData$Handling
   t <- 20 - h
-  obs_c <- subjData$Completed
+  obs_c <- subjData$Choice
   
   # Prep list of results to be returned, and keep track per iteration
   out <- list()
@@ -902,17 +902,35 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
     # P(A): P(A)_t = \dfrac{1}{1 + exp^{-(\beta[r_t - \gamma_th_t^{k_t}])}}
     for (i in seq(nrow(subjData))) {
       if (i == 1) {
-        gamma[i] <- gammaStart
+        # the environmental rate that participants start with
+        # if we are fitting a single gamma, then add gamma prior with alpha = 0 and k = 1 (check that it reproduces results)
+        # otherwise this functions as a prior bias on the environmental rate
+        if ("gammaPrior" %in% colnames(params)) {
+          gamma[i] <- params[param, "gammaPrior"]
+        } else {
+          gamma[i] <- gammaStart
+        }
+        
+        # choose if the trial rate > env. rate
         c[i] <- ifelse(o[i] / h[i] > gamma[i], 1, 0)
       } else {
+        # non-linear estimate of the elapsed time since the last choice
         tau <- (h[i - 1] ^ k[i - 1] * c[i - 1]) + t[i - 1]
+        
+        # was the previous offer accepted?
         a <- o[i - 1] * c[i - 1]
+        
+        # gamma is updated by how much weight is given to the recently experienced reward rate (i.e. left part of eq)
         gamma[i] <- ((1 - (1 - alpha) ^ tau) * (a / tau)) + ((1 - alpha) ^ tau) * gamma[i - 1]
+        
[…]

### 2020-07-30 Simulations/manuscript_modeling.R
little tweaks and reproduction of param diffs

@@ -521,11 +521,8 @@ plot_dyn_us <- function(id = "58", exp = "btw", gammaOne = 0) {
   suppressWarnings(print(ratePlot))
 }
 
-# plot gamma for stipulated alpha and k parameters
-plot_alphas <- function(alpha, k = 1, exp = "btw", gammaStart = 0) {
-  # parameter setting
-  
-  
+# to test the effect of parameters 
+plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
   if (exp == "btw") {
     # choose sample subject + params
     sub <- filter(dataBtw, SubjID == "58")
@@ -534,62 +531,77 @@ plot_alphas <- function(alpha, k = 1, exp = "btw", gammaStart = 0) {
     o <- sub$Offer
     h <- sub$Handling
     t <- 20 - h
-    c <- sub$Choice
-    a <- o * c # accepted offers
-    time <- sub$ExpTime
-    tau <- lag((h ^ k * c) + t)
     
-    # get the trial-wise gamma to export the probability of acceptance
-    gamma <- rep(0, nrow(sub))
+    # store subj data with gammas
+    iters <- list()
     
-    # calculate gammas
-    for (j in seq(nrow(sub))) {
-      if (j == 1) {
-        gamma[j] <- gammaStart
-      } else {
-        gamma[j] <- ((1 - (1 - alpha) ^ tau[j]) * (a[j - 1] / tau[j])) + ((1 - alpha) ^ tau[j]) * gamma[j - 1]
-      } 
+    # iterate over the alphas provided
+    for (param in seq_along(alphas)) {
+      
+      # set up param
+      alpha <- alphas[param]
+      
+      # get the trial-wise gamma to export the probability of acceptance
+      c <- rep(0, nrow(sub))
+      gamma <- rep(0, nrow(sub))
+      
+      # calculate gammas
+      for (j in seq(nrow(sub))) {
+        if (j == 1) {
+          gamma[j] <- gammaStart
+          c[j] <- ifelse(o[j] / (h[j] ^ k) > gamma[j], 1, 0)
+        } else {
+          tau <- (h[j - 1] ^ k * c[j - 1]) + t[j - 1]
+          a <- o[j - 1] * c[j - 1]
+          gamma[j] <- ((1 - (1 - alpha) ^ tau) * (a / tau)) + ((1 - alpha) ^ tau) * gamma[j - 1]
[…]

### 2020-07-30 Simulations/manuscript_modeling.R
added a function that applies the idea that people gradually track subjective time less and less

@@ -891,6 +891,7 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0, showChoices = -0.
     
     # run model
     temp <- optimize_model_dyn_us3(sub, params, simplify = F, gammaStart = gammaOne)
+    print(temp$params)
     
     # plot
     ratePlot <- sub %>%
@@ -1103,7 +1104,24 @@ recover_results_wth <- function(fitsList, binary = F, matrix = T) {
   
 }
 
-
+# function for idea: people adapt their Ks with decreasing strength
+# meaning that early in the experiment, they keep track of the perceived time per cost, but they slowly settle into previous history towards the end
+# similar result to the cumulative mean, but more flexible early in the experiment
+# theta vector fixed for now. Think of how to make it free
+recalibrate_k <- function(ks) {
+  # rule
+  theta <- seq(1, 0, length.out = length(ks))
+  
+  learnedK <- rep(0, length(ks))
+  for (l in seq_along(ks)) {
+    if (l == 1) {learnedK[l] <- ks[1]
+    } else {
+      learnedK[l] <- theta[l] * ks[l] + (1 - theta[l]) * learnedK[l - 1]
+    }
+  }
+  
+  return(learnedK)
+}
 
 ## which models to run?
 baseOC_nloptr <- F
@@ -1112,6 +1130,7 @@ baseLogistic <- F # to test whether the brute search converges to a conventional
 fwOC <- F
 dOC <- F
 twOC <- F
+recovery <- F
 
 # which experimental dataset?
 data <- dataBtw %>% 
@@ -1311,6 +1330,7 @@ if (twOC) {
 # so I tested a number of iterations to ensure that the results persist
 # at 30 and 50 it's the same. As alpha is reduced to ~0, k increases for cog.
 # but ~0.02 alpha seems sensible.
+spaceSize <- 30
 params <- list(tempr = seq(0, 2, length.out = spaceSize), 
                alpha = seq(0, 1, length.out = spaceSize),
                k = seq(-1, 2, length.out = spaceSize))
@@ -1321,6 +1341,7 @@ trialwiseOC_btw_us_new <- dataBtw %>%
   do(optimize_model_dyn_us3(., params, simplify = T)) %>%
   ungroup() %>%
   distinct(SubjID, .keep_all = T)
+
 param_compare_plot(trialwiseOC_btw_us_new, "k", meanRate = 1)
 
[…]

### 2020-07-30 Simulations/manuscript_modeling.R
added a starting point for theta (i.e. the degree to which subjective value is updated)

@@ -1108,9 +1108,9 @@ recover_results_wth <- function(fitsList, binary = F, matrix = T) {
 # meaning that early in the experiment, they keep track of the perceived time per cost, but they slowly settle into previous history towards the end
 # similar result to the cumulative mean, but more flexible early in the experiment
 # theta vector fixed for now. Think of how to make it free
-recalibrate_k <- function(ks) {
+recalibrate_k <- function(ks, thetaRange = c(1, 0)) {
   # rule
-  theta <- seq(1, 0, length.out = length(ks))
+  theta <- seq(thetaRange[1], thetaRange[2], length.out = length(ks))
   
   learnedK <- rep(0, length(ks))
   for (l in seq_along(ks)) {
@@ -1122,6 +1122,9 @@ recalibrate_k <- function(ks) {
   
   return(learnedK)
 }
+
+
+
 
 ## which models to run?
 baseOC_nloptr <- F
@@ -1359,7 +1362,7 @@ if (! "mK" %in% colnames(dataWth)) {
     mutate(laggedK = dplyr::lag(mK, default = 1),
            mK = mK * Choice,
            mK = ifelse(mK == 0, laggedK, mK),
-           mK = recalibrate_k(mK)) %>% 
+           mK = recalibrate_k(mK, thetaRange = c(0.15, 0))) %>% 
     ungroup()
 }
 
@@ -1447,5 +1450,5 @@ if (recovery) {
     plyr::dlply("SubjID", identity) %>%
     lapply(., optimize_model_dyn_us3, params, simplify = F)
   
-  recover_results_wth(temp_tw_fits_wth, binary = F)
+  recover_results_wth(temp_tw_fits_wth, binary = T)
 }

### 2020-07-31 Cost_manuscript.Rmd
added sequential effects of previous offer

@@
 
-``` {r BTW: 16.1.2. AR, echo = FALSE, include = FALSE}
+``` {r BTW: 16.1.2. AR + sequential effects, echo = FALSE, include = FALSE}
 # Idea: do AIC to compare models per participant
@@
 
+### OFFER HISTORY
+# 
+# # check if the recent history of offers affects the probability of acceptances
+# # the larger the sum of recent rewards, the lower the probability of acceptance (regardless of how far back the sum goes (from 3 to 6))
+# # this makes sense, because larger numbers mean that higher offers recently happened, leaving only lower ones available
+# # this is mainly for 10 H, but the effect survives when adding H + R
+# logisOfferhist <- dataBtw %>%
+#   group_by(SubjID) %>%
+#   mutate(rollingOffer = ifelse(TrialN < 3, Offer, Reduce(`+`, shift(Offer, 0:2)))) %>%
+#   plyr::dlply("SubjID", identity) %>%
+#   lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + rollingOffer, data = data, family = "binomial"))})
+# 
+# # coefficient summaries
+# logistemp <- sapply(logistemp, coefficients)
+# 
+# # Rank sum test
+# rankRHAR <- wilcox.test(logistemp["rollingOffer", ])
+# 
+# # mixed effects logistic version
+# # significant for 10 and 14s Handling
+# dat <- dataBtw %>%
+#   filter(Handling == 2) %>%
+#   group_by(SubjID) %>%
+#   mutate(rollingOffer = ifelse(TrialN < 3, Offer, Reduce(`+`, shift(Offer, 0:4)))) 
+# summary(glmer(Choice ~ Handling + Offer + rollingOffer + (1 | SubjID), data = dat, family = "binomial"))
 ```

### 2020-08-03 Cost_manuscript.Rmd
update to recent history

--- 2020-07-22 Cost_manuscript.Rmd
@@
 library(patchwork)
+library(data.table)
 
@@
 
+## UPDATE TO THIS
+# IT BASICALLY SAYS THAT PEOPLE DO TRACK THE RECENT OFFERS A BIT, BEYOND WHAT H+R DO.
+# AND ALSO THAT RECENT FORCED TRAVELS + QUITS DO MARGINALLY INFLUENCE CHOICE
+# THIS SUGGESTS THAT WHILE THE EFFECTS ARE SMALL (P(A) ~ 2%), PARTICIPANTS DO SOME ENVIRONMENTAL TRACKING
+# history
+# Instead of quits, I'm now doing completions. This is because one would expect forced travels to also affect choice.
+# First, iterate over the recent history to identify which sum length reduces the AIC the most
+historySize <- lapply(seq(2, 6), function(tail) {
+  dat <- dataBtw %>%
+  group_by(SubjID) %>%
+  mutate(recentTravels = seqQuits(Completed),
+         recentOffers = ifelse(TrialN < (tail + 1), Offer, Reduce(`+`, shift(Offer, 1:tail)))) #%>%
+  #ungroup() %>%
+  glmer(Choice ~ Handling + Offer + recentTravels + recentOffers + (1 | SubjID), data = dat, family = "binomial")
+  #summarise(aic = AIC(glmer(Choice ~ Handling + Offer + recentTravels + recentOffers + (1 | SubjID), data = ., family = "binomial")))
+})
+
+# then get the summary of the tail length that reduced the AIC the most
+index <- which(sapply(historySize, function(iter) {AIC(iter)}) == min(sapply(historySize, function(iter) {AIC(iter)})))
+summary(historySize[[index]])
 ```
@@
 
-  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) were tasked with deciding their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.
+  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) chose their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.
 Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time).

### 2020-08-05 Cost_manuscript.Rmd
rewriting sequential history

@@
 First we tested whether decision makers integrated delay and reward information.
-To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a logistic regression to each participant’s data to predict trial-wise acceptances, using handling time and reward amount as predictors.
+**To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a logistic regression to each participant’s data to predict trial-wise acceptances, using handling time and reward amount as predictors.
 The resulting beta coefficients for handling time and reward were pooled across all participants, and we performed a one-sample rank-sum test on each set of coefficients to examine whether they were significantly positive or negative (compared to no effect of 0).
@@
 This examined the possibility that participant choices were governed by recent quitting history rather than the experimental parameters.
-Coefficients significantly different from 0 denoted that a participant relied on recent quitting history.
+Coefficients significantly different from 0 denoted that a participant relied on recent quitting history.**
 
@@
 
-  To address the first hypothesis, we examined whether increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively.
+  **new** We performed a mixed effects logistic regression to address the first hypothesis.
+Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
+Larger reward amounts significantly increased acceptance probabilities ($\beta$ = ), whereas longer delays decreased them (), in line with predictions.
+Two additional regressors showed that 1) having missed out on several consecutive rewards decreased the probability of acceptance (how?) and 2) participants became more selective when recent history was richer ().
+Model selection using Akaike's Information Criterion (AIC) suggested that participants were influenced by the 5 most recent rewards.
+
+  **old** We performed a mixed effects logistic regression to address the first hypothesis.
 Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).

### 2020-08-05 Cost_manuscript.Rmd
update to history

--- 2020-08-03 Cost_manuscript.Rmd
@@
 First we tested whether decision makers integrated delay and reward information.
-To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a logistic regression to each participant’s data to predict trial-wise acceptances, using handling time and reward amount as predictors.
-The resulting beta coefficients for handling time and reward were pooled across all participants, and we performed a one-sample rank-sum test on each set of coefficients to examine whether they were significantly positive or negative (compared to no effect of 0).
-We then performed an extension of the logistic regression by adding an autoregressive covariate containing the number of consecutive quits prior to a given trial.
-This examined the possibility that participant choices were governed by recent quitting history rather than the experimental parameters.
-Coefficients significantly different from 0 denoted that a participant relied on recent quitting history.
+To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a mixed-effects logistic regression to predict trial-wise acceptances, using a random intercept to account for biases in participant behavior.
+We included regressors for handling time and reward, as well as two covariates that probed the influence of recent history on choices.
+The first was an autoregressive regressor containing the number of consecutive offer misses prior to a given trial (misses could be due to quits or lapses in performance that forced participants to travel).
+The second regressor tracked the sum of the previous *n* offers.
+We identified the *n* that minimized Akaike's Information Criterion (AIC) among 6 versions of the model (i.e.
+tracing from 2 previous trials up to 7, beyond which the model failed to converge), and reported all coefficients from the winning model.
 
@@
 (**exponentiate coefficients to make them more interpretable?**) We then examined whether this a priori model outperformed both simpler and more complex models.
-We used both Akaike’s Information Criterion (AIC) and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
+We used both AIC and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
 The regression with each combination of predictors was fitted in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
@@
 
-``` {r BTW: 16.1.2. AR + sequential effects, echo = FALSE, include = FALSE}
-# Idea: do AIC to compare models per participant
-# add an AR regressor to track recent quits
-logisRHAR <- dataBtw %>%
-              filter(Choice < 2) %>%
-              group_by(SubjID) %>%
-              mutate(AR = seqQuits(Choice)) %>%
-              plyr::dlply("SubjID", identity) %>%
-              lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial"))})
-
-# get the AR CIs per participant 
-AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(suppressWarnings(confint(x)[4, ]), error = function(e){c(0, 0)})}) %>%
-  replace_na(0) %>%
-  t() %>%
-  apply(1, function(x) (x[1] <= 0 & x[2] >= 0))
-
-# coefficient summaries
-logisRHAR <- sapply(logisRHAR, coefficients)
-coeffRHAR_mean <- apply(logisRHAR, 1, mean, na.rm = T)
-coeffRHAR_se <- apply(logisRHAR, 1, sd, na.rm = T) / sqrt(nSubjs_btw)
-
-# Rank sum test
-rankRHAR <- wilcox.test(logisRHAR["AR", ])
-
-## UPDATE TO THIS
-# IT BASICALLY SAYS THAT PEOPLE DO TRACK THE RECENT OFFERS A BIT, BEYOND WHAT H+R DO.
-# AND ALSO THAT RECENT FORCED TRAVELS + QUITS DO MARGINALLY INFLUENCE CHOICE
-# THIS SUGGESTS THAT WHILE THE EFFECTS ARE SMALL (P(A) ~ 2%), PARTICIPANTS DO SOME ENVIRONMENTAL TRACKING
+``` {r BTW: 16.1.2. AR sequential effects, echo = FALSE, include = FALSE}
+
 # history
@@
 # First, iterate over the recent history to identify which sum length reduces the AIC the most
-historySize <- lapply(seq(2, 6), function(tail) {
+# tracing the history beyond 7 trials produces non-convergence
+historySize <- lapply(seq(2, 7), function(tail) {
   dat <- dataBtw %>%
+    #filter(Cost != "Wait") %>%
     group_by(SubjID) %>%
     mutate(recentTravels = seqQuits(Completed),
-         recentOffers = ifelse(TrialN < (tail + 1), Offer, Reduce(`+`, shift(Offer, 1:tail)))) #%>%
-  #ungroup() %>%
+           recentOffers = ifelse(TrialN < (tail + 1), Offer, Reduce(`+`, shift(Offer, 1:tail))))
+
   glmer(Choice ~ Handling + Offer + recentTravels + recentOffers + (1 | SubjID), data = dat, family = "binomial")
-  #summarise(aic = AIC(glmer(Choice ~ Handling + Offer + recentTravels + recentOffers + (1 | SubjID), data = ., family = "binomial")))
 })
@@
 # then get the summary of the tail length that reduced the AIC the most
-index <- which(sapply(historySize, function(iter) {AIC(iter)}) == min(sapply(historySize, function(iter) {AIC(iter)})))
-summary(historySize[[index]])
+historyIndex <- which(sapply(historySize, function(iter) {AIC(iter)}) == min(sapply(historySize, function(iter) {AIC(iter)})))
+
+historyCoeffs <- round(summary(historySize[[historyIndex]])$coefficients, digits = 2)
+
+# # Idea: do AIC to compare models per participant
+# # add an AR regressor to track recent quits
+# logisRHAR <- dataBtw %>%
+#               filter(Choice < 2) %>%
+#               group_by(SubjID) %>%
+#               mutate(AR = seqQuits(Choice)) %>%
+#               plyr::dlply("SubjID", identity) %>%
+#               lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial"))}) 
+#   
+# # get the AR CIs per participant 
+# AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(suppressWarnings(confint(x)[4, ]), error = function(e){c(0, 0)})}) %>%
+#   replace_na(0) %>%
+#   t() %>%
+#   apply(1, function(x) (x[1] <= 0 & x[2] >= 0))
+# 
+# # coefficient summaries
+# logisRHAR <- sapply(logisRHAR, coefficients)
+# coeffRHAR_mean <- apply(logisRHAR, 1, mean, na.rm = T)
+# coeffRHAR_se <- apply(logisRHAR, 1, sd, na.rm = T) / sqrt(nSubjs_btw)
+# 
+# # Rank sum test
+# rankRHAR <- wilcox.test(logisRHAR["AR", ])
 ```
@@
 
-  To address the first hypothesis, we examined whether increasing handling times and reward amounts produced the expected reduction and increase in acceptance probabilities, respectively.
+  We performed a mixed effects logistic regression to address the first hypothesis.
 Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
-Individual-specific logistic regression coefficients for handling time were significantly lower than 0 (mean $\beta$ = `r round(mean(coeffRH_mean[2], na.rm = T), digits = 2)`, SE = `r round(coeffRH_se[2], digits = 2)`; Wilcoxon test: V = `r rankHand$statistic`, *p* `r report_p(rankHand$p.value)`), whereas increasing the reward amount predicted higher acceptance probabilities (mean $\beta$ = `r round(coeffRH_mean[1], digits = 2)`, SE = `r round(coeffRH_se[1], digits = 2)`; Wilcoxon test: V = `r rankOffer$statistic`, p `r report_p(rankOffer$p.value)`).
-We next examined whether choices could also have been affected by recent choice history (i.e.
-if too many sequential quits promoted acceptances regardless of reward amount) by adding a regressor to the model that tracked the number of consecutive quits preceding a trial.
-This auto-regressive coefficient was not significantly different than 0 (mean $\beta$ = `r round(coeffRHAR_mean[3], digits = 2)`, SE = `r round(coeffRHAR_se[3], digits = 2)`; Wilcoxon test: V = `r rankRHAR$statistic`, p `r report_p(rankRHAR$p.value)`), and the 95% confidence interval (CI) of these coefficients contained 0 in `r round((sum(AR_CIs) / nSubjs_btw) * 100)`% of our participants.
-This indicates that offer patterns did not systematically influence participant behavior.
+Larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs["Handling", "Estimate"]`, SE = `r historyCoeffs["Handling", "Std.
+Error"]`, *p* `r report_p(historyCoeffs["Handling", "Pr(>|z|)"])`), whereas longer delays decreased them ($\beta$ = `r historyCoeffs["Offer", "Estimate"]`, SE = `r historyCoeffs["Offer", "Std.
+Error"]`, *p* `r report_p(historyCoeffs["Offer", "Pr(>|z|)"])`), in line with predictions.
+Two additional regressors showed that having missed out on consecutive rewards decreased the probability of acceptance ($\beta$ = `r historyCoeffs["recentTravels", "Estimate"]`, SE = `r historyCoeffs["recentTravels", "Std.
+Error"]`, *p* `r report_p(historyCoeffs["recentOffers", "Pr(>|z|)"])`), and that participants became more selective when recent offer history was richer ($\beta$ = `r historyCoeffs["recentOffers", "Estimate"]`, SE = `r historyCoeffs["recentOffers", "Std.
+Error"]`, *p* `r report_p(historyCoeffs["recentOffers", "Pr(>|z|)"])`).
+The reduction in acceptances from recent misses was driven by the wait group (removing this group from the model yielded a *p* > 0.1), likely because this group accepted the least amount of offers.
+Comparing likelihood fits among lengths of offer history (e.g.
+sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex + 1` most recent rewards (AIC = `r AIC(historySize[[historyIndex]])`), which matched the offer presentation rotation (see Methods).
+These results confirm the expected influence of time and offer magnitude on choice behavior, but also suggest that participants adapted to their recent experience.
 

### 2020-08-06 Simulations/manuscript_modeling.R
update to the trialwise model with k, so there is a k learning rule

@@ -818,7 +818,139 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
   
   return(out)
 }
-plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0, showChoices = -0.6) {
+optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 0, thetaRange = c(0.15, 0)) {
+  # get every combination of parameters
+  params <- expand.grid(params)
+  
+  # relevant behavior elements
+  o <- subjData$Offer
+  h <- subjData$Handling
+  t <- 20 - h
+  obs_c <- subjData$Choice
+  
+  # Prep list of results to be returned, and keep track per iteration
+  out <- list()
+  out$percentQuit <- mean(obs_c == 0) * 100
+  out$percentAccept <- mean(obs_c == 1) * 100 
+  out$params <- as.numeric() # winning parameters
+  out$rate <- as.numeric() # to store the winning gammas
+  out$pAccept <- as.numeric() # probability of acceptance for winning parameters
+  out$fit_c <- as.numeric() # to store the winning fitted choices
+  out$LLs <- rep(0, nrow(params))
+  out$LL <- Inf
+  
+  # iterate through possible parameters and get the LL
+  #LLs <- sapply(seq(nrow(params)), function(i) {
+  for (param in seq(nrow(params))) {
+    # isolate the parameters for this iteration
+    # and then store them as variables
+    tempr <- params[param, "tempr"]
+    alpha <- params[param, "alpha"]
+    if ("k" %in% colnames(params)) {
+      # use a vector so I can use a common indexing for fixed and to-be-fitted values of k
+      k <- rep(params[param, "k"], nrow(subjData)) # if there is a free k parameter, use its fit, otherwise use the values from exp1
+    } else {
+      k <- subjData$mK
+    }
+    
+    # get the trial-wise gamma to export the probability of acceptance
+    c <- rep(0, nrow(subjData))
+    gamma <- rep(0, nrow(subjData))
+    tau <- h
+    theta <- seq(thetaRange[1], thetaRange[2], length.out = nrow(subjData))
+    
+    # calculate gammas iterating over trials
[…]

### 2020-08-06 Cost_manuscript.Rmd
editing the manuscript, and adding info on modeling

@@
   Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment (Stephens and Krebs, 1977).
-In this study, the richness of the environment was manipulated by the length of the handling and travel times (i.e.
-shorter travel times produced richer environments).
+In this study, the richness of the environment was manipulated by the length of the handling and travel times, where shorter travel times produced richer environments.
 Since time combinations were fixed per block, we calculated each block’s optimal accept/reject strategy by computing all decision strategies according to the following equation:
@@
   where *R*, *H*, and *p* are the reward, handling time, and acceptance probability of offer i, respectively, and T is the travel time.
-This gave us the total reward per second attainable in each block as a function of the lowest amount accepted (i.e.
-acceptance threshold).
+This gave us the total reward per second attainable in each block as a function of the acceptance threshold (i.e.
+the lowest amount accepted).
 Figure 2 shows possible earnings for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
@@
 Significant deviations from the optimal strategy can be understood as reflecting changes in subjective OC.
-Beyond comparing among cost types, this approach allowed us to test if certain demands boosted the value of offers (i.e.
-over-accepting low offers).
+This approach allowed us to test if certain demands boosted the value of offers, expressed as a subjective OC that fell below the optimal rate.
 
@@
 We included regressors for handling time and reward, as well as two covariates that probed the influence of recent history on choices.
-The first was an autoregressive regressor containing the number of consecutive offer misses prior to a given trial (misses could be due to quits or lapses in performance that forced participants to travel).
+The first was an autoregressive regressor containing the number of consecutive offer misses prior to a given trial (misses could be due to quits or forced travels).
 The second regressor tracked the sum of the previous *n* offers.
-We identified the *n* that minimized Akaike's Information Criterion (AIC) among 6 versions of the model (i.e.
-tracing from 2 previous trials up to 7, beyond which the model failed to converge), and reported all coefficients from the winning model.
+We identified the *n* that minimized Akaike's Information Criterion (AIC) among 6 versions of the model (tracing from 2 previous trials up to 7, beyond which the model failed to converge), and reported all coefficients from the winning model.
 
   Our foraging task was configured such that over and under accepting were detrimental to total earnings.
-To confirm this, we fit a general linear model with constant, linear, and quadratic terms to estimate the correspondence between proportion accepted (independent variable) and total earnings (dependent variable).
+To confirm this, we fit a general linear model with constant, linear, and quadratic terms to estimate the correspondence between proportion of trials completed (independent variable) and total earnings (dependent variable).
 A significant quadratic coefficient thus would signal that the task statistics operated as expected.
-Next, to determine the optimality of each group’s decisions, performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost).
-This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR).
+Next, to determine the optimality of each group’s decisions, we performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cocitst).
+This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR, CITE Y&..).
 
@@
 
-  In order to further look at the effect of handling, offer, and cost type, we computed the probability of accepting a trial with a mixed-effects logistic regression using the lme4 package (CITE).
+  In order to further look at the effect of handling, offer, and cost type, we computed the probability of accepting a trial with a mixed-effects logistic regression, using the lme4 package (CITE).
 Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and participant ID as a random intercept.
@@
 We used both AIC and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
-The regression with each combination of predictors was fitted in the following order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
+The regression with each combination of predictors was fitted in a forward order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
 We predicted that model 6 (the a priori setup) would have the lowest AIC and BIC.
@@
 
-  Finally, we modeled the subjective opportunity cost in each condition.
-We started by examining whether participants were confident and consistent in their choices.
-We visually examined survival curves indicating at what point during the handling time participants quit a trial (censored points included trial completions and forced travels), in addition to quitting time distributions.
-Next, we addressed the prediction that participants would display consistent choice patterns throughout the session (i.e.
-that the reward amounts they accepted in a given timing condition would be similar throughout the experiment).
-We computed each participant’s total proportion of acceptances pre- and post-midpoint for every block, and performed paired permutations (5000 iterations) to compare their mean proportion of acceptances.
-We then confirmed that the relative costs observed with from the whole experimental session were still present on each half of the experiment.
+  Before modeling each individual's overarching subjective OC, we examined whether participants were consistent and stable in their choices.
+For consistency, we visually examined survival curves indicating at what point during the handling time participants quit a trial (censored points included trial completions and forced travels), in addition to quitting time distributions.
+Stability was assessed by computing each participant’s total proportion of acceptances pre- and post-midpoint for every block, comparing the mean proportion of acceptances using paired permutations (5000 iterations).
+We then tested whether the relative differences in costs observed using data from the whole experimental session were still present on each half of the experiment.
 The winning model from the mixed-effects logistic comparison was applied to each half separately.
@@
 
-  Once we established choice stability, we proceeded to estimate the subjective OC of each type of demand (see Operationalization of Cost).
+  Finally, we fitted the subjective OC of each type of demand (see Operationalization of Cost).
 OC was computed as the product of a free parameter (gamma) and the handling time.
@@
 
-  Both gamma ($\gamma$) and the inverse temperature parameter ($\beta$) of the softmax function were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE).
+  Both gamma ($\gamma$) and the inverse temperature parameter ($\beta$) of the softmax function were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE **or grid search?**).
 The gamma optimization search space was bound by extreme choice values.
@@
 Finally, we determined which cost type produced the highest discounting by comparing gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
-**ADD ADDITIONAL MODELS FROM LITERATURE**
 
@@
 We first ran tests to determine whether decision makers integrated reward information.
-We performed a logistic regression per participant to predict trial-wise acceptances based on reward amounts.
+**We performed a logistic regression per participant to predict trial-wise acceptances based on reward amounts.
 The resulting beta coefficients were pooled across all participants, and a one-sample rank-sum test was used to examine whether they were significantly positive or negative (compared to 0).
-Next, we explored the effects of choice history by adding an autoregressive covariate containing the number of consecutive recent quits.
+Next, we explored the effects of choice history by adding an autoregressive covariate containing the number of consecutive recent quits (mixed-effects)**.
 We then confirmed that the under- and over-acceptance were detrimental to total earnings by performing the same quadratic linear model explained above.
@@
 We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions.
-We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity in the following order: 1) intercept only; 2) cost only; 3) reward only; 4) cost and reward main effects (a priori model); and 5) adding a two-way interaction.
+We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity in a forward order: 1) intercept only; 2) cost only; 3) reward only; 4) cost and reward main effects (a priori model); and 5) adding a two-way interaction.
 We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
@@
 
-  **adapt once we decide on the model candidates** To estimate the subjective opportunity cost of each condition, we used a logistic function to model each participant’s probability of accepting a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
+  **old** To estimate the subjective opportunity cost of each condition, we used a logistic function to model each participant’s probability of accepting a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
 As before, OC was computed as the product of a free parameter (gamma) and the handling time.
@@
 We performed pairwise paired permutations as post-hoc tests.
+
+**new** The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above.
+Based on the results, an adequate model of behavior should meet X criteria: 1) an initial preference for cognitive effort trials 2) that this preference disappeared as acceptances devolved to a common rate across costs; 3) show that participants kept track of recent offer history; 4) that these effects were robust to block order effects; 5) ....
+X) be applicable to both experiments
 

### 2020-08-06 Cost_manuscript.Rmd
quick note
added discussion notes from a couple of papers I found

@@
 **new** The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above.
-Based on the results, an adequate model of behavior should meet X criteria: 1) an initial preference for cognitive effort trials 2) that this preference disappeared as acceptances devolved to a common rate across costs; 3) show that participants kept track of recent offer history; 4) that these effects were robust to block order effects; 5) ....
-X) be applicable to both experiments
+Based on the results, an adequate model of behavior should meet X criteria: 1) an initial preference for cognitive effort trials 2) that this preference disappeared as acceptances devolved to a common rate across costs; 3) show that participants kept track of recent offer history; 4) that these effects were robust to block order effects; 5) deviations from optimality that were not simply due to overharvesting; and 6) be applicable to both experiments.
+Alternative foraging models from the literature were not fitted, as they did not qualitatively meet these criteria (wikenheiser, C&D, Fawcett...)
 
@@
 
+- Working memory could produce timing issues (Buhi n Gershman). Efficiency couldn't be it because then global decrease wouldn't happen and phys effort might be affected too (Shenhav stuff). 
+- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
+Like, the aversion is due to focusing on different elements of the task.
 - Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort

### 2020-08-06 Cost_manuscript.Rmd
adding mixed effects AR to exp 2. No effect of misses this time, but 7-back offer history is there

@@
 
-``` {r WTH: 16.1.2. AR, echo = FALSE, include = FALSE}
-# Create an autoregressive predictor based on previous consecutive quits
-dataList <- lapply(dataList, function(data) {data %>% mutate(AR = seqQuits(Choice))})
-
-# fits per participant
-logisticFits_base <- lapply(dataList, function(data) {suppressWarnings(glm(Choice ~ Offer + AR, data = data, family = "binomial"))})
-
-# get the low/high 95% CIs for AR
-baseCoeffs <- as_tibble(t(sapply(logisticFits_base, function(data) {suppressWarnings(confint(data, "AR"))}))) %>% 
-  dplyr::rename(AR_CILow = `2.5 %`, AR_CIHigh = `97.5 %`) %>%
-  mutate(SubjID = subjList_wth) %>%
-  left_join(baseCoeffs, by = "SubjID")
-
-# reorder so that SubjID comes first
-#baseCoeffs <- baseCoeffs[ , c(3,4,5,6,7,8,9,1,2)]
-
-# create a vector indicating whether 0 is included or not (i.e. if there is 0, no sequential effect)
-# but first change NA to 0 (visual inspection showed that NAs were tied to p's with full or near full p(accept), meaning they weren't influenced by history)
-baseCoeffs <- baseCoeffs %>% 
-  mutate(AR_CILow = ifelse(is.na(AR_CILow), 0, AR_CILow),
-         AR_CIHigh = ifelse(is.na(AR_CIHigh), 0, AR_CIHigh))
-baseCoeffs$AR_effect <- apply(baseCoeffs, 1, function(x) (!(as.numeric(x["AR_CILow"]) <= 0 & as.numeric(x["AR_CIHigh"]) >= 0)))
+``` {r WTH: 16.1.2. AR + sequential effects, echo = FALSE, include = FALSE}
+# tracing the history beyond 7 trials produces non-convergence
+historySize <- lapply(seq(2, 7), function(tail) {
+  dat <- dataWth %>%
+    group_by(SubjID) %>%
+    mutate(recentTravels = seqQuits(Completed),
+           recentOffers = ifelse(TrialN < (tail + 1), Offer, Reduce(`+`, shift(Offer, 1:tail))))
+
+  glmer(Choice ~ Offer + recentTravels + recentOffers + (1 | SubjID), data = dat, family = "binomial")
+})
+
+# then get the summary of the tail length that reduced the AIC the most
+historyIndex <- which(sapply(historySize, function(iter) {AIC(iter)}) == min(sapply(historySize, function(iter) {AIC(iter)})))
+
+historyCoeffs <- round(summary(historySize[[historyIndex]])$coefficients, digits = 2)
+
+# old
+# # Create an autoregressive predictor based on previous consecutive quits
+# dataList <- lapply(dataList, function(data) {data %>% mutate(AR = seqQuits(Choice))})
+# 
+# # fits per participant
+# logisticFits_base <- lapply(dataList, function(data) {suppressWarnings(glm(Choice ~ Offer + AR, data = data, family = "binomial"))}) 
+# 
+# # get the low/high 95% CIs for AR
+# baseCoeffs <- as_tibble(t(sapply(logisticFits_base, function(data) {suppressWarnings(confint(data, "AR"))}))) %>% 
+#   dplyr::rename(AR_CILow = `2.5 %`, AR_CIHigh = `97.5 %`) %>%
+#   mutate(SubjID = subjList_wth) %>%
+#   left_join(baseCoeffs, by = "SubjID")
+# 
+# # reorder so that SubjID comes first
+# #baseCoeffs <- baseCoeffs[ , c(3,4,5,6,7,8,9,1,2)]
+# 
+# # create a vector indicating whether 0 is included or not (i.e. if there is 0, no sequential effect)
+# # but first change NA to 0 (visual inspection showed that NAs were tied to p's with full or near full p(accept), meaning they weren't influenced by history)
+# baseCoeffs <- baseCoeffs %>% 
+#   mutate(AR_CILow = ifelse(is.na(AR_CILow), 0, AR_CILow),
+#          AR_CIHigh = ifelse(is.na(AR_CIHigh), 0, AR_CIHigh))
+# baseCoeffs$AR_effect <- apply(baseCoeffs, 1, function(x) (!(as.numeric(x["AR_CILow"]) <= 0 & as.numeric(x["AR_CIHigh"]) >= 0)))
 ```

### 2020-08-06 Cost_manuscript.Rmd
new version of wth trial history (matches btw)

@@
 We first ran tests to determine whether decision makers integrated reward information.
-**We performed a logistic regression per participant to predict trial-wise acceptances based on reward amounts.
-The resulting beta coefficients were pooled across all participants, and a one-sample rank-sum test was used to examine whether they were significantly positive or negative (compared to 0).
-Next, we explored the effects of choice history by adding an autoregressive covariate containing the number of consecutive recent quits (mixed-effects)**.
+We performed a mixed-effects logistic regression with regressors for offer amount, number of consecutive offer misses, and the sum of the *n* previously observed offers (we identified *n* by comparing the AIC of different history lengths).
 We then confirmed that the under- and over-acceptance were detrimental to total earnings by performing the same quadratic linear model explained above.
@@
 # tracing the history beyond 7 trials produces non-convergence
-historySize <- lapply(seq(2, 7), function(tail) {
+historySize_btw <- lapply(seq(2, 7), function(tail) {
   dat <- dataBtw %>%
@@
 # then get the summary of the tail length that reduced the AIC the most
-historyIndex <- which(sapply(historySize, function(iter) {AIC(iter)}) == min(sapply(historySize, function(iter) {AIC(iter)})))
-
-historyCoeffs <- round(summary(historySize[[historyIndex]])$coefficients, digits = 2)
+historyIndex_btw <- which(sapply(historySize_btw, function(iter) {AIC(iter)}) == min(sapply(historySize_btw, function(iter) {AIC(iter)})))
+
+historyCoeffs_btw <- round(summary(historySize_btw[[historyIndex_btw]])$coefficients, digits = 2)
 
@@
 Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
-Larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs["Handling", "Estimate"]`, SE = `r historyCoeffs["Handling", "Std.
-Error"]`, *p* `r report_p(historyCoeffs["Handling", "Pr(>|z|)"])`), whereas longer delays decreased them ($\beta$ = `r historyCoeffs["Offer", "Estimate"]`, SE = `r historyCoeffs["Offer", "Std.
-Error"]`, *p* `r report_p(historyCoeffs["Offer", "Pr(>|z|)"])`), in line with predictions.
-Two additional regressors showed that having missed out on consecutive rewards decreased the probability of acceptance ($\beta$ = `r historyCoeffs["recentTravels", "Estimate"]`, SE = `r historyCoeffs["recentTravels", "Std.
-Error"]`, *p* `r report_p(historyCoeffs["recentOffers", "Pr(>|z|)"])`), and that participants became more selective when recent offer history was richer ($\beta$ = `r historyCoeffs["recentOffers", "Estimate"]`, SE = `r historyCoeffs["recentOffers", "Std.
-Error"]`, *p* `r report_p(historyCoeffs["recentOffers", "Pr(>|z|)"])`).
+Larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_btw["Offer", "Estimate"]`, SE = `r historyCoeffs_btw["Offer", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_btw["Offer", "Pr(>|z|)"])`), whereas longer delays decreased them ($\beta$ = `r historyCoeffs_btw["Handling", "Estimate"]`, SE = `r historyCoeffs_btw["Handling", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_btw["Handling", "Pr(>|z|)"])`), in line with predictions.
+Two additional regressors showed that having missed out on consecutive rewards decreased the probability of acceptance ($\beta$ = `r historyCoeffs_btw["recentTravels", "Estimate"]`, SE = `r historyCoeffs_btw["recentTravels", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_btw["recentOffers", "Pr(>|z|)"])`), and that participants became more selective when recent offer history was richer ($\beta$ = `r historyCoeffs_btw["recentOffers", "Estimate"]`, SE = `r historyCoeffs_btw["recentOffers", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_btw["recentOffers", "Pr(>|z|)"])`).
 The reduction in acceptances from recent misses was driven by the wait group (removing this group from the model yielded a *p* > 0.1), likely because this group accepted the least amount of offers.
 Comparing likelihood fits among lengths of offer history (e.g.
-sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex + 1` most recent rewards (AIC = `r AIC(historySize[[historyIndex]])`), which matched the offer presentation rotation (see Methods).
+sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r AIC(historySize_btw[[historyIndex]])`), which matched the offer presentation rotation (see Methods).
 These results confirm the expected influence of time and offer magnitude on choice behavior, but also suggest that participants adapted to their recent experience.
@@
 # tracing the history beyond 7 trials produces non-convergence
-historySize <- lapply(seq(2, 7), function(tail) {
+historySize_wth <- lapply(seq(2, 7), function(tail) {
   dat <- dataWth %>%
@@
 # then get the summary of the tail length that reduced the AIC the most
-historyIndex <- which(sapply(historySize, function(iter) {AIC(iter)}) == min(sapply(historySize, function(iter) {AIC(iter)})))
-
-historyCoeffs <- round(summary(historySize[[historyIndex]])$coefficients, digits = 2)
+historyIndex_wth <- which(sapply(historySize_wth, function(iter) {AIC(iter)}) == min(sapply(historySize_wth, function(iter) {AIC(iter)})))
+
+historyCoeffs_wth <- round(summary(historySize_wth[[historyIndex_wth]])$coefficients, digits = 2)
 
@@
   Analyses from the previous experiment were repurposed to examine cost differences within individuals.
-We begun by testing the prediction that rewards would positively influence choices.
-A Wilcoxon signed rank test showed that individual logistic coefficients for reward amount were significantly greater than 0 (mean $\beta$ = `r round(mean(baseCoeffs$Offer), digits = 2)`, SD = `r round(sd(baseCoeffs$Offer), digits = 2)`; V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* `r report_p(wilcox.test(baseCoeffs$Offer)$p.value)`), once again confirming that participants were properly influenced by reward amounts.
-Adding a coefficient that tracked prior consecutive quits indicated that only `r sum(baseCoeffs$AR_effect)` individuals were influenced by recent quit history (95% CI above or below 0), thus discarding systematic sequential effects.
-In terms of earnings, a linear model predicting earnings once again showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+A mixed-effects logistic regression once again showed that larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_wth["Offer", "Estimate"]`, SE = `r historyCoeffs_wth["Offer", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_wth["Offer", "Pr(>|z|)"])`), and that participants became more selective if they had recently observed large offers ($\beta$ = `r historyCoeffs_wth["recentOffers", "Estimate"]`, SE = `r historyCoeffs_wth["recentOffers", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_wth["recentOffers", "Pr(>|z|)"])`).
+Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r AIC(historySize_wth[[historyIndex]])`.
+However, this time participants were unaffected by recent reward misses (*p* > 0.05).
+  As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).

### 2020-08-07 Simulations/manuscript_modeling.R
removing theta addition to model optiim function

@@ -818,7 +818,7 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
   
   return(out)
 }
-optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 0, thetaRange = c(0.15, 0)) {
+optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 0) {
   # get every combination of parameters
   params <- expand.grid(params)
   
@@ -857,7 +857,7 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
     c <- rep(0, nrow(subjData))
     gamma <- rep(0, nrow(subjData))
     tau <- h
-    theta <- seq(thetaRange[1], thetaRange[2], length.out = nrow(subjData))
+    #theta <- seq(thetaRange[1], thetaRange[2], length.out = nrow(subjData))
     
     # calculate gammas iterating over trials
     # latex versions: gamma[i]: \gamma_t = (1 - (1 - \alpha) ^ {\tau_t}) \dfrac{R_{t-1} A_{t-1}}{\tau_t} +  (1 - \alpha) ^ {\tau_t} \gamma_{t-1}
@@ -867,19 +867,19 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
     # k_t = \dfrac {1} {N}\sum_{cost}^{t - 1} k_{cost}
     # P(A): P(A)_t = \dfrac{1}{1 + exp^{-(\beta[r_t - \gamma_th_t^{k_t}])}}
     for (i in seq(nrow(subjData))) {
-      if (i == 1) {
+      if (i %in% c(1, nrow(subjData))) {
         # the environmental rate that participants start with
         # if we are fitting a single gamma, then add gamma prior with alpha = 0 and k = 1 (check that it reproduces results)
         # otherwise this functions as a prior bias on the environmental rate
-        if ("gammaPrior" %in% colnames(params)) {
+        if ("gammaPrior" %in% colnames(params) & i == 1) {
           gamma[i] <- params[param, "gammaPrior"]
         } else {
           gamma[i] <- gammaStart
         }
         
-        # choose if the trial rate > env. rate. No k modulation, since I'm assuming the effect doesn't apply right away
[…]

### 2020-08-11 Cost_manuscript.Rmd
modeling note
things to address in the discussion

@@
 **new** The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above.
-Based on the results, an adequate model of behavior should meet X criteria: 1) an initial preference for cognitive effort trials 2) that this preference disappeared as acceptances devolved to a common rate across costs; 3) show that participants kept track of recent offer history; 4) that these effects were robust to block order effects; 5) deviations from optimality that were not simply due to overharvesting; and 6) be applicable to both experiments.
+Based on the results across experiments, an adequate model of behavior should meet X criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) persistently higher acceptances for cognitive effort when faced with single behavioral costs; 3) slight reduction of acceptances in effortful conditions (**fatigue?**); 4) an initial preference for cognitive effort trials when foraging for costs and rewards 5) this preference disappears as acceptances decreased to a common rate across costs; 6) participants kept track of recent offer history; 7) effects were robust to block order effects.
 Alternative foraging models from the literature were not fitted, as they did not qualitatively meet these criteria (wikenheiser, C&D, Fawcett...)
+
+DIFFICULT TO MODEL: ALL COST ACCEPTANCES DECREASE AT LEAST A BIT.
+LEARNING SUBJECTIVE TIME DOESN'T DO THAT.
+IN FACT, IT STILL SEEMS AS IF THE EFFORT FATIGUE SEEN ON EXP 1 HAPPENS AGAIN, AND ALL COSTS DEFAULT TO THE COSTLIEST.
+THAT DOESN'T INVOLVE TIME NECESSARILY.
 
@@
 
-- Working memory could produce timing issues (Buhi n Gershman). Efficiency couldn't be it because then global decrease wouldn't happen and phys effort might be affected too (Shenhav stuff). 
+- What we think: subjective timing is shortened by the way we implemented cognitive effort.
+This can be recalibrated if many task types are experienced.
+Maybe the implementation allowed for counting.
+Alternatively, working memory engagement could produce timing issues (Buhi n Gershman).
+Also look at what Andrew Westbrook shared.
+- Things that don't seem to be at play here, but could still play a general role in mental effort preferences: 1) A demand’s cost is not fully intrinsic (within vs between differences); 2) Effort preferences unlikely just due to learned industriousness or efficacy as amitais lab sees it (differences between effort types, and everyone met a good performance level per training); 3) avoiding boredom (global decline in exp 2, not a preference exchange).
+4) Literally counting tasks, since mental effort was discretely presented but everything else was contiguous.
+If that were the case, dividing the handling time by 2 would work, but not sure if it would translated into exp 2.
 - Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).

### 2020-08-13 Simulations/manuscript_modeling.R
fixed and streamlined the optimization function for the adaptive model

@@ -602,7 +602,7 @@ plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
       scale_fill_discrete(name = "Offer") +
       #scale_color_continuous(breaks = c(2, 10, 14), labels = c(2, 10, 14)) +
       ylim(0, NA) +
-      labs(x = "Trial Number", y = "Ongoing Opportunity Cost (gamma)") +
+      labs(x = "Trial Number", y = "Earning rate") +
       theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             panel.background = element_blank(),
@@ -675,7 +675,7 @@ plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
       scale_fill_discrete(name = "Offer") +
       #scale_color_manual(values = colsWth) +
       ylim(0, NA) +
-      labs(x = "Trial Number", y = "Ongoing Opportunity Cost (gamma)") +
+      labs(x = "Trial Number", y = "Earning rate") +
       theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             panel.background = element_blank(),
@@ -818,7 +818,7 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
   
   return(out)
 }
-optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 0) {
+optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 0.5) {
   # get every combination of parameters
   params <- expand.grid(params)
   
@@ -844,19 +844,15 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
   for (param in seq(nrow(params))) {
     # isolate the parameters for this iteration
     # and then store them as variables
+    # vectors are initialized by a single value, but they get updated
     tempr <- params[param, "tempr"]
     alpha <- params[param, "alpha"]
-    if ("k" %in% colnames(params)) {
-      # use a vector so I can use a common indexing for fixed and to-be-fitted values of k
-      k <- rep(params[param, "k"], nrow(subjData)) # if there is a free k parameter, use its fit, otherwise use the values from exp1
[…]

### 2020-08-13 Simulations/manuscript_modeling.R
non-stationarity seems to work?

@@ -522,7 +522,7 @@ plot_dyn_us <- function(id = "58", exp = "btw", gammaOne = 0) {
 }
 
 # to test the effect of parameters 
-plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0) {
+plot_alphas <- function(alphas, k = 1, exp = "btw", gammaStart = 0.5) {
   if (exp == "btw") {
     # choose sample subject + params
     sub <- filter(dataBtw, SubjID == "58")
@@ -847,13 +847,14 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
     # vectors are initialized by a single value, but they get updated
     tempr <- params[param, "tempr"]
     alpha <- params[param, "alpha"]
+    ifelse("alpha_k" %in% colnames(params), alpha_k <- params[param, "alpha_k"], alpha_k <- 0.15) # evolving time estimate learning. turn into free parameter
     ifelse("k" %in% colnames(params), k <- rep(params[param, "k"], nrow(subjData)), k <- subjData$mK)
     ifelse("gammaPrior" %in% colnames(params), gamma <- rep(params[param, "gammaPrior"], nrow(subjData)), gamma <- rep(gammaStart, nrow(subjData)))
     
     # vectors to store evolving variables
     a <- rep(0, nrow(subjData))
     tau <- rep(0, nrow(subjData))
-    #theta <- seq(thetaRange[1], thetaRange[2], length.out = nrow(subjData))
+    K <- k # experienced k, mainly for updating rule
     
     # calculate gammas iterating over trials
     # latex versions: gamma[i]: \gamma_t = (1 - (1 - \alpha) ^ {\tau_t}) \dfrac{R_{t-1} A_{t-1}}{\tau_t} +  (1 - \alpha) ^ {\tau_t} \gamma_{t-1}
@@ -876,9 +877,9 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
       # K[l + 1] <- theta[l] * ks[l] + (1 - theta[l]) * K[l - 1]
       # K[l + 1] <- (theta[l] ^ (-1 / l)) * ks[l] + (1 - (theta[l] ^ (-1 / l))) * K[l]
[…]

### 2020-08-13 Simulations/manuscript_modeling.R
fitting the alpha for nonlinearity

@@ -913,7 +913,7 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
       out$params <- params[param, ]
       out$pAccept <- p
       
-      plot(k, type = "b")
+      #plot(k, type = "b")
       
       # break if the reduction is too small to be significant
       # based on visual assessment of the likelihood space, which looks convex
@@ -1009,7 +1009,8 @@ plot_dyn_us3 <- function(id = "58", exp = "btw", gammaOne = 0.5, showChoices = -
     sub <- filter(dataWth, SubjID == id)
     spaceSize <- 30
     params <- list(tempr = seq(0, 2, length.out = spaceSize), 
-                   alpha = seq(0, 0.5, length.out = spaceSize))
+                   alpha = seq(0, 0.5, length.out = spaceSize),
+                   alpha_k = seq(0, 0.5, length.out = spaceSize))
     
     # run model
     temp <- optimize_model_dyn_us3(sub, params, simplify = F, gammaStart = gammaOne)
@@ -1278,7 +1279,7 @@ baseLogistic <- F # to test whether the brute search converges to a conventional
 fwOC <- F
 dOC <- F
 twOC <- F
-recovery <- F
+recovery <- T
 
 # which experimental dataset?
 data <- dataBtw %>% 
@@ -1323,7 +1324,8 @@ if (bOC) {
   params <- list(tempr = seq(0, 2, length.out = spaceSize), 
                  gammaPrior = seq(0.25, 1.5, length.out = spaceSize),
                  alpha = 0,
-                 k = 1)
+                 k = 1,
+                 alpha_k = 0)
   
   # fit to each subject
   baseOC <- dataBtw %>%
@@ -1503,13 +1505,13 @@ tryCatch(dataWth <- dataWth %>% select(-mK), error = function(e) {print("Oops, n
 if (! "mK" %in% colnames(dataWth)) {
   dataWth <- dataWth %>%
     mutate(simpleCost = ifelse(Cost %in% c("Wait-C", "Wait-P"), "Wait", as.character(Cost))) %>% 
-    left_join(ks, by = "simpleCost") %>%
-    group_by(SubjID) %>%
-    mutate(laggedK = dplyr::lag(mK, default = 1),
-           mK = mK * Choice,
-           mK = ifelse(mK == 0, laggedK, mK),
[…]

### 2020-08-13 Simulations/manuscript_modeling.R
trimming what runs during modeling

@@ -1296,7 +1296,6 @@ if (baseOC_nloptr) {
     ungroup()
 }
 
-
 ## ORIGINAL OC
 # great correspondence with NLOPTR, just much slower since it surveys the whole parameter space
 if (bOC) {
@@ -1483,7 +1482,8 @@ if (twOC) {
 spaceSize <- 30
 params <- list(tempr = seq(0, 2, length.out = spaceSize), 
                alpha = seq(0, 0.5, length.out = spaceSize),
-               k = seq(0, 2, length.out = spaceSize))
+               k = seq(0, 2, length.out = spaceSize),
+               alpha_k = seq(0, 0.5, length.out = spaceSize))
 
 trialwiseOC_btw_us_new <- dataBtw %>%
   filter(Cost != "Easy") %>%
@@ -1514,17 +1514,18 @@ if (! "mK" %in% colnames(dataWth)) {
     # ungroup()
 }
 
-# check that the k evolution looks ok
-dataWth %>%
-  filter(SubjID %in% c("109", "461")) %>%
-  ggplot(aes(TrialN, mK, color = SubjID, group = SubjID)) +
-  geom_hline(yintercept = 1, linetype = "dashed") +
-  geom_line(show.legend = F) +
-  theme_minimal()
+# # check that the k evolution looks ok
+# dataWth %>%
+#   filter(SubjID %in% c("109", "461")) %>%
+#   ggplot(aes(TrialN, mK, color = SubjID, group = SubjID)) +
+#   geom_hline(yintercept = 1, linetype = "dashed") +
+#   geom_line(show.legend = F) +
+#   theme_minimal()
 
 # fit wth
 params <- list(tempr = seq(0, 2, length.out = spaceSize), 
-               alpha = seq(0, 0.5, length.out = spaceSize))
+               alpha = seq(0, 0.5, length.out = spaceSize),
+               alpha_k = seq(0, 0.5, length.out = spaceSize))
 
 trialwiseOC_wth_us_new <- dataWth %>%
   group_by(SubjID) %>%
@@ -1544,38 +1545,39 @@ if (recovery) {
   #model_expr <- expr(tempr[[1]] * (reward - (gammaPrior[[1]] * handling)))
   
   # create a list with possible starting values for model parameters
-  # parameter names must match model ones
-  spaceSize <- 30
-  params <- list(tempr = seq(0, 2, length.out = spaceSize), 
-                 gammaPrior = seq(0.25, 1.5, length.out = spaceSize),
[…]

### 2020-08-13 Simulations/manuscript_modeling.R
switch time sensitivity parameter from k to s (per McKerchar et al 2009)

@@ -8,7 +8,7 @@
 
 # simpler form of optimization that allows inputting any model expression into a single function call
 # only good for static models
-optimize_model <- function(subjData, params, model, simplify = F) {
+optimize_model_static <- function(subjData, params, model, simplify = F) {
   # this function finds the combination of parameter values that minimizes the neg log likelihood of a logistic regression
   # used to rely on NLOPTR, but it's too cumbersome for the low-dimensional estimates I'm performing.
   #
@@ -84,108 +84,6 @@ optimize_model <- function(subjData, params, model, simplify = F) {
   return(out)
 }
 
-# for a trial-wise acceptance version. Add model expression eventually
-optimize_model_dyn <- function(subjData, params, simplify = F, gammaStart = 0) {
-  # get every combination of parameters
-  params <- expand.grid(params)
-  
-  # relevant behavior elements
-  o <- subjData$Offer
-  h <- subjData$Handling
-  c <- subjData$Choice
-  a <- o * c # accepted offers
-  time <- subjData$ExpTime
-  tau <- time - dplyr::lag(time, default = 0) # how long has it been since the last update?
-  
-  # Prep list of results to be returned
-  out <- list()
-  out$percentQuit <- mean(c == 0) * 100
-  out$percentAccept <- mean(c == 1) * 100 
-  
-  # iterate through possible parameters and get the LL
-  LLs <- sapply(seq(nrow(params)), function(i) {
-    # isolate the parameters for this iteration
-    # and then store them as variables
-    tempr <- params[i, 1]
-    alpha <- params[i, 2]
-    
-    # update rule (inspired by Constantino and Daw, 2015)
-    gamma <- rep(0, nrow(subjData))
-    
-    # calculate gammas
-    for (i in seq(nrow(subjData) - 1)) {
-      if (i == 1) {
-        gamma[i] <- gammaStart
-      } else {
-        
-        delta <- (a[i - 1] / tau[i]) - gamma[i - 1]
-        gamma[i] <- gamma[i - 1] + (1 - (1 - alpha) ^ tau[i]) * delta
-        gamma[i] <- (((1 - alpha) ^ tau[i]) * (a[i - 1] / tau[i])) + (1 - (1 - alpha) ^ tau[i]) * gamma[i - 1] # maybe expr(model)
[…]

### 2020-08-13 Simulations/manuscript_modeling.R
TIMING NOTES

@@ -6,6 +6,8 @@
 # the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
 # maybe also R-squares and things in the current optimization function
 
+library(parallel)
+
 # simpler form of optimization that allows inputting any model expression into a single function call
 # only good for static models
 optimize_model_static <- function(subjData, params, model, simplify = F) {
@@ -558,7 +560,7 @@ optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 
       
       # s update versions
       # s[i + 1] <- theta[i] * S[i] * c[i] + (1 - theta[i]) * s[i]
-      # s[i + 1] <- theta[i] * S[i] + (1 - theta[i]) * s[i]
+      # s[i + 1] <- (alpha_s / i) * S[i] * c[i] + (1 - (alpha_s / i)) * s[i]
       # s[i + 1] <- s[i] + 1/i * (S[i] - s[i]) # Sutton & Barto, page 37. Add choice to S[l]?
       left <- ((1 - alpha_s) ^ i) * s[1]
       right <- alpha_s * (1 - alpha_s) ^ (i - seq(i)) * (S[seq(i)] ^ a[seq(i)])
@@ -926,6 +928,7 @@ recalibrate_s <- function(S, thetaRange, choice) {
   l <- 1
   while (l < length(S)) {
     # s[l + 1] <- theta[l] * S[l] * choice[l] + (1 - theta[l]) * s[l]
+    # s[i + 1] <- (alpha_s / i) * S[i] * c[i] + (1 - (alpha_s / i)) * s[i]
     # s[l + 1] <- s[l] + (1/l * (S[l] - s[l])) * choice[l] # Sutton & Barto, page 37. 
     left <- ((1 - a) ^ l) * s[1]
     right <- a * (1 - a) ^ (l - seq(l)) * S[seq(l)] ^ choice[seq(l)]
@@ -964,7 +967,7 @@ if (baseOC_nloptr) {
     ungroup()
 }
 
-## ORIGINAL OC
+## ORIGINAL OC computed using the dynamic model, showing that the adaptive version can be reduced to a single gamma fit
 # great correspondence with NLOPTR, just much slower since it surveys the whole parameter space
 if (bOC) {
   print("Running base OC model through grid search...")
@@ -1000,6 +1003,8 @@ if (bOC) {
     group_by(Cost, SubjID) %>%
[…]

### 2020-08-14 Simulations/manuscript_modeling.R
streamlining the summary of results for behavior recovery and fit comparisons

@@ -940,7 +940,31 @@ recalibrate_s <- function(S, thetaRange, choice) {
   return(S)
 }
 
-
+# get a summary from a group's fits from the dynamical fits
+simplify_results <- function(fitLists, exp = "btw") {
+  # get the relevant parameters
+  temp <- sapply(trialwiseOC_btw, function(sub) {sub[c("percentQuit", "percentAccept", "params", "LL", "LL0", "Rsquared")]})
+  
+  # expand them
+  df <- unnest(as.tibble(t(temp)), cols = c(percentQuit, percentAccept, params, LL, LL0, Rsquared))
+  
+  # append subject id and cost (if relevant)
+  if (exp == "btw") {
+    subList <- dataBtw %>% 
+      filter(Cost != "Easy") %>% 
+      distinct(SubjID, .keep_all = T) %>% 
+      select(SubjID, Cost)
+  } else if (exp == "wth") {
+    subList <- dataWth %>% 
+      distinct(SubjID, .keep_all = T) %>% 
+      select(SubjID)
+  }
+  
+  # final summary
+  df <- cbind(subList, df)
+  
+  return(df)
+}
 
 
 ## which models to run?
@@ -1158,23 +1182,23 @@ params <- list(tempr = seq(0, 2, length.out = spaceSize),
                s = seq(0, 2, length.out = spaceSize),
                alpha_s = 0) # in the between subjects version all S_costs are the same, so there is no update. Just enforcing that here to save on computation
 
-trialwiseOC_btw <- dataBtw %>%
-  filter(Cost != "Easy") %>%
-  group_by(Cost, SubjID) %>%
-  do(optimize_model_dyn_us3(., params, simplify = T)) %>%
-  ungroup() %>%
-  distinct(SubjID, .keep_all = T)
-
-# NOTE: better to fit this once, and then create a function to simplify. mclapply > purrr:do()
-system.time(trialwiseOC_btw <- dataBtw %>%
+# fit the model to each individual
+adaptiveOC_btw <- dataBtw %>%
   filter(Cost != "Easy") %>%
   plyr::dlply("SubjID", identity) %>%
-  mclapply(., optimize_model_dyn_us3, params, simplify = F, mc.cores = detectCores()))
+  mclapply(., optimize_model_dyn_us3, params, simplify = F, mc.cores = detectCores())
 
-param_compare_plot(trialwiseOC_btw_us_new, "s", meanRate = 1)
+# summarise
[…]

### 2020-08-14 Simulations/manuscript_modeling.R
tiny touch on organization

@@ -1167,11 +1167,12 @@ if (twOC) {
 }
 
 
-### test
+### ADAPTIVE MODELING
 # taking the cumulative average of the subjective time perception makes subjective overall time seem slower.
 # a free parameter could be added to index the degree to which participants cared about this (replaces k as a free parameter, since s is adopted from exp 1)
 # weird that the higher the weight on cum_means, the lower the OC ie less selective. Think about it.
-# fit btw exp
+
+# FIT BETWEEN SUBJECTS
 # alpha will often default to the next lowest to 0
 # so I tested a number of iterations to ensure that the results persist
 # at 30 and 50 it's the same. As alpha is reduced to ~0, s increases for cog.
@@ -1217,7 +1218,7 @@ if (! "mS" %in% colnames(dataWth)) {
     # ungroup()
 }
 
-# fit wth
+# FIT WITHIN SUBJECTS
 params <- list(tempr = seq(0, 2, length.out = spaceSize), 
                alpha = seq(0, 0.5, length.out = spaceSize),
                alpha_s = seq(0, 0.5, length.out = spaceSize))

### 2020-08-14 Simulations/manuscript_modeling.R
summary function hiccup

@@ -381,129 +381,6 @@ plot_alphas <- function(alphas, s = 1, exp = "btw", gammaStart = 0.5) {
 # preferred function, which works for all types of models considered so far
 # like, s = 1 and alpha = 0 returns the single parameter model
 # generative version: model calculates choices per fitted previous choices, not just based on observed sub choices
-optimize_model_dyn_us3 <- function(subjData, params, simplify = F, gammaStart = 0) {
-  # get every combination of parameters
-  params <- expand.grid(params)
-  
-  # relevant behavior elements
-  o <- subjData$Offer
-  h <- subjData$Handling
-  t <- 20 - h
-  obs_c <- subjData$Choice
-  
-  # Prep list of results to be returned, and keep track per iteration
-  out <- list()
-  out$percentQuit <- mean(obs_c == 0) * 100
-  out$percentAccept <- mean(obs_c == 1) * 100 
-  out$params <- as.numeric() # winning parameters
-  out$rate <- as.numeric() # to store the winning gammas
-  out$pAccept <- as.numeric() # probability of acceptance for winning parameters
-  out$fit_c <- as.numeric() # to store the winning fitted choices
-  out$LLs <- rep(0, nrow(params))
-  out$LL <- Inf
-  
-  # iterate through possible parameters and get the LL
-  #LLs <- sapply(seq(nrow(params)), function(i) {
-  for (param in seq(nrow(params))) {
-    # isolate the parameters for this iteration
-    # and then store them as variables
-    tempr <- params[param, "tempr"]
-    alpha <- params[param, "alpha"]
-    if ("s" %in% colnames(params)) {
-      # use a vector so I can use a common indexing for fixed and to-be-fitted values of s
-      s <- rep(params[param, "s"], nrow(subjData)) # if there is a free s parameter, use its fit, otherwise use the values from exp1
-    } else {
-      s <- subjData$mS
-    }
-    
-    # get the trial-wise gamma to export the probability of acceptance
-    c <- rep(0, nrow(subjData))
-    gamma <- rep(0, nrow(subjData))
-    
-    # calculate gammas iterating over trials
[…]

### 2020-08-21 Simulations/manuscript_modeling.R
notes on evolution of acceptances

@@ -1009,7 +1009,7 @@ colsBtw = c("#78AB05","#D9541A","deepskyblue4", "darkgoldenrod2") # plot colors 
 colsWth <- c("#D9541A", "#78AB05", "dodgerblue4", "deepskyblue3")#"grey30", "grey70") # plot colors (wait, effort)
 lthick = 2 # line thickness for plots
 
-######## LOAD DATA
+###-- LOAD DATA
 setwd("../Cost2/data")
 files <- dir(pattern = '_log.csv')
 
@@ -1099,14 +1099,14 @@ dataWth_coglogs <- data_frame(SubjID = files) %>%
 subjList_wth <- unique(dataWth$SubjID)
 nSubjs_wth <- length(subjList_wth)
 
-#########
+###-- 
 setwd('../..')
 
 # what makes this run unique?
-qualifier <- "newUpdate_bigspace_s1is1"
+qualifier <- "newUpdate_regspace_s1is1"
 
 # how big should the parameter space be?
-spaceSize <- 200
+spaceSize <- 50
 write(paste("n of possibilities per parameter:", spaceSize), stdout())
 
 ## which models to run?
@@ -1389,10 +1389,15 @@ plot(adaptiveOC_wth_summary$alpha, adaptiveOC_wth_summary$alpha_s,
 axis(side = 1, at = unique(adaptiveOC_wth_summary$alpha), labels = FALSE)
 
 # plot result recovery
-recover_results_wth(adaptiveOC_wth, binary = T, order = T)
+recover_results_wth(adaptiveOC_wth, binary = T, order = F)
 
 
-### testing grounds
+### TESTING GROUNDS
+# according to this, both studies show similar reductions of acceptances over time
+# though the negative slope of wth is steeper
+# this doesn't apply to the btw wait condition, and it's accentuated by handling time
+# so this reintroduces fatigue I guess, though it can't explain everything.
+
 # do those who complete more effort trials end up being more fatigued? (accepting less by the end?)
 temp <- dataBtw %>%
   filter(Cost %in% c("Cognitive", "Physical")) %>%
@@ -1421,7 +1426,63 @@ dataWth %>%
     stat_smooth(method = "loess") +
     theme_minimal()
 
+##  ACCEPTANCES OVER TIME FOR BOTH EXPS COMBINED
+dataWth_short <- dataWth %>%
[…]

### 2020-08-21 Cost_manuscript.Rmd
fixed and streamlined the optimization function for the adaptive model
discussion notes on fatigue

@@
 Also look at what Andrew Westbrook shared.
+Add this to a potential fatigue, although that would also mean that waiting would be accepted less over time in exp 1.
 - Things that don't seem to be at play here, but could still play a general role in mental effort preferences: 1) A demand’s cost is not fully intrinsic (within vs between differences); 2) Effort preferences unlikely just due to learned industriousness or efficacy as amitais lab sees it (differences between effort types, and everyone met a good performance level per training); 3) avoiding boredom (global decline in exp 2, not a preference exchange).
@@
 If that were the case, dividing the handling time by 2 would work, but not sure if it would translated into exp 2.
+5) fatigue: there's a similar gradual decrease in acceptances in both experiments, except for the wait condition in exp 1.
+Fatigue would apply equally to both, or alternatively it might not bring all down to the same level (I guess the point could be made, but it's not that people who complete more at the beginning decrease acceptances more, as one would expect from fatigued people)
 - Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).

### 2020-08-25 Cost_manuscript.Rmd
updated latex equations, and fixed the length of travel and handling time in the modeling script

@@
 ``` {r BTW: 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
-# # code to calculate the rwd/sec rate for each acceptance threshold per handling
+# # code to calculate the rwd/sec rate for each acceptance threshold per handling (calculate the optimal solution)
 # rwd <- c(4, 8, 20)

### 2020-08-25 Simulations/manuscript_modeling.R

@@ -458,8 +458,8 @@ optimize_model_adaptive <- function(subjData, params, simplify = F, gammaStart =
   
   # relevant behavior elements
   o <- subjData$Offer
-  h <- subjData$Handling
-  t <- 20 - h
+  h <- subjData$Handling + 2 # 2s for the reward achievement window
+  t <- 20 - h # not 16 - h because the offer window is 2s. I don't like adding it, because I assume participants don't assimilate it, but Joe prefers it.
   obs_c <- subjData$Choice
   effort <- ifelse(subjData$Cost == "Wait", 0, 1)
   #fatigue <- 0.01 * subjData$TrialN * effort
@@ -495,12 +495,10 @@ optimize_model_adaptive <- function(subjData, params, simplify = F, gammaStart =
     if (! "s" %in% colnames(params)) {s[1] <- 1}
 
     # calculate gammas iterating over trials
-    # latex versions: gamma[i]: \gamma_t = (1 - (1 - \alpha) ^ {\tau_t}) \dfrac{R_{t-1} A_{t-1}}{\tau_t} +  (1 - \alpha) ^ {\tau_t} \gamma_{t-1}
-    # ugly tau: \tau_{t} = (H_{t-1} ^ {s_{t-1}}  A_{t - 1}) + T_{t - 1}
-    # prettier, vectorized tau: \tau = (h ^ s  a) + t
-    # gamma for pretty tau: \gamma_t = (1 - (1 - \alpha) ^ {\tau_{t-1}}) \dfrac{r_{t-1} a_{t-1}}{\tau_{t-1}} +  (1 - \alpha) ^ {\tau_{t-1}} \gamma_{t-1}
-    # s_t = \dfrac {1} {N}\sum_{cost}^{t - 1} s_{cost}
-    # P(A): P(A)_t = \dfrac{1}{1 + exp^{-(\beta[r_t - \gamma_th_t^{s_t}])}}
+    # latex versions: gamma[i]: \gamma_{t+1} = (1 - (1 - \alpha) ^ {\tau_t}) \dfrac{R_{t} A_{t}}{\tau_t} +  (1 - \alpha) ^ {\tau_t} \gamma_{t}
+    # \tau_{t} = H_{t} ^ {s_{t}}  A_{t} + T_{t}
[…]

### 2020-08-25 Simulations/manuscript_modeling.R
function to plot the fitted evolution of time sensitivity for the within-subject exp

@@ -1000,6 +1000,26 @@ simplify_results <- function(fitLists, exp = "btw") {
   return(df)
 }
 
+# plot the evolusion of S from the wth fits
+plot_fittedS <- function(fitsList) {
+  # extract fits
+  fits <- do.call(c, sapply(fitsList, "[", "evolvingS"))
+  data <- dataWth %>%
+    mutate(evolvingS = fits) %>% #rbinom(length(fits), 1, fits))
+    group_by(SubjID) %>%
+    mutate(firstCost = Cost[1]) %>%
+    ungroup()
+  
+  
+  data %>%
+    ggplot(aes(TrialN, evolvingS)) +
+    geom_hline(yintercept = 1, linetype = "dashed") +
+    geom_line(aes(group = SubjID, color = BlockOrder), show.legend = T, alpha = 0.2) +
+    geom_smooth(aes(color = BlockOrder), method = "loess") +
+    theme_minimal()
+}
+
+
 
 ## aesthetic options
 lbls <- c("Wait","Cognitive","Physical","Easy") # between subj

### 2020-08-25 Simulations/manuscript_modeling.R
little tweak

@@ -1470,10 +1470,16 @@ slidingWindow <- dataAll %>%
 dataAll %>%
   filter(Cost != "Easy",
          Handling == 10) %>%
-  ggplot(aes(TrialN, Choice, group = Exp, color = Exp, fill = Exp)) +
-  geom_smooth(method = "loess", show.legend = T) +
-  ylim(0, 1) +
-  theme_classic()
+  mutate(simpleCost = case_when(Cost == "Wait-C" ~ "Wait",
+                                Cost == "Wait-P" ~ "Wait",
+                                Cost == "Wait" ~ "Wait",
+                                Cost == "Physical" ~ "Physical",
+                                Cost == "Cognitive" ~ "Cognitive")) %>% 
+  ggplot(aes(TrialN, Choice, group = simpleCost, linetype = Exp, color = simpleCost, fill = simpleCost)) +
+    geom_smooth(method = "loess", show.legend = T) +
+    ylim(0, 1) +
+    facet_wrap(vars(Exp)) +
+    theme_classic()
 
 # proportion accepted every 10 trials
 slidingWindow %>%

### 2020-08-25 Simulations/manuscript_modeling.R
slight time update

@@ -450,7 +450,7 @@ plot_alphas <- function(alphas, s = 1, exp = "btw", gammaStart = 0.5) {
 # preferred function, which works for all types of models considered so far
 # like, s = 1 and alpha = 0 returns the single parameter model
 # generative version: model calculates choices per fitted previous choices, not just based on observed sub choices
-optimize_model_adaptive <- function(subjData, params, simplify = F, gammaStart = 0.5) {
+optimize_model_adaptive <- function(subjData, params, simplify = F, gammaStart = 0.4) {
   #write(paste("Working on subject", unique(SubjData$SubjID)), stdout())
   
   # get every combination of parameters
@@ -458,8 +458,8 @@ optimize_model_adaptive <- function(subjData, params, simplify = F, gammaStart =
   
   # relevant behavior elements
   o <- subjData$Offer
-  h <- subjData$Handling + 2 # 2s for the reward achievement window
-  t <- 20 - h # not 16 - h because the offer window is 2s. I don't like adding it, because I assume participants don't assimilate it, but Joe prefers it.
+  h <- subjData$Handling + 2 # if they accept the handling, they experience the reward window
+  t <- 20 - h # and the travel includes the 2s offer window from the next trial
   obs_c <- subjData$Choice
   effort <- ifelse(subjData$Cost == "Wait", 0, 1)
   #fatigue <- 0.01 * subjData$TrialN * effort
@@ -492,13 +492,15 @@ optimize_model_adaptive <- function(subjData, params, simplify = F, gammaStart =
     a <- rep(0, nrow(subjData))
     tau <- rep(0, nrow(subjData))
     S <- s # experienced s, mainly for updating rule
-    if (! "s" %in% colnames(params)) {s[1] <- 1}
+    #if (! "s" %in% colnames(params)) {s[1] <- 1}
 
     # calculate gammas iterating over trials
-    # latex versions: gamma[i]: \gamma_{t+1} = (1 - (1 - \alpha) ^ {\tau_t}) \dfrac{R_{t} A_{t}}{\tau_t} +  (1 - \alpha) ^ {\tau_t} \gamma_{t}
[…]

### 2020-08-25 Simulations/manuscript_modeling.R
latex eq versions

@@ -495,12 +495,10 @@ optimize_model_adaptive <- function(subjData, params, simplify = F, gammaStart =
     #if (! "s" %in% colnames(params)) {s[1] <- 1}
 
     # calculate gammas iterating over trials
-    # latex versions: gamma[i]: \gamma_t = (1 - (1 - \alpha) ^ {\tau_t}) \dfrac{R_{t-1} A_{t-1}}{\tau_t} +  (1 - \alpha) ^ {\tau_t} \gamma_{t-1}
-    # ugly tau: \tau_{t} = (H_{t-1} ^ {s_{t-1}}  A_{t - 1}) + T_{t - 1}
-    # prettier, vectorized tau: \tau = (h ^ s  a) + t
-    # gamma for pretty tau: \gamma_t = (1 - (1 - \alpha) ^ {\tau_{t-1}}) \dfrac{r_{t-1} a_{t-1}}{\tau_{t-1}} +  (1 - \alpha) ^ {\tau_{t-1}} \gamma_{t-1}
-    # s_t = \dfrac {1} {N}\sum_{cost}^{t - 1} s_{cost}
-    # P(A): P(A)_t = \dfrac{1}{1 + exp^{-(\beta[r_t - \gamma_th_t^{s_t}])}}
+    # latex versions: gamma[i]: \gamma_{t+1} = (1 - (1 - \alpha) ^ {\tau_t}) \dfrac{R_{t} A_{t}}{\tau_t} +  (1 - \alpha) ^ {\tau_t} \gamma_{t}
+    # \tau_{t} = H_{t} ^ {s_{t}}  A_{t} + T_{t}
+    # s_{t + 1} = (1 - \alpha)^t S_1 + \sum^{t}_{i = 1} \alpha(1 - \alpha)^{t - i} (S_t A_t + s_{t - 1}(1 - A_t))
+    # P(A): P(A)_t = \dfrac{1}{1 + exp^{-(\beta[R_t - \gamma_tH_t^{s_t}])}}
     i <- 1
     while (i < nrow(subjData)) {
       # choose if the prospect's reward rate, non-linearly discounted as above > env. rate

### 2020-08-26 Simulations/manuscript_modeling.R
more sensible time sensitivity constraints

@@ -484,7 +484,7 @@ optimize_model_adaptive <- function(subjData, params, simplify = F, gammaStart =
     # vectors are initialized by a single value, but they get updated
     tempr <- params[param, "tempr"]
     alpha <- params[param, "alpha"]
-    ifelse("alpha_s" %in% colnames(params), alpha_s <- params[param, "alpha_s"], alpha_s <- 0.15) # evolving time estimate learning. turn into free parameter
+    ifelse("alpha_s" %in% colnames(params), alpha_s <- params[param, "alpha_s"], alpha_s <- 0) # evolving time estimate learning. turn into free parameter
     ifelse("s" %in% colnames(params), s <- rep(params[param, "s"], nrow(subjData)), s <- subjData$mS)
     ifelse("gammaPrior" %in% colnames(params), gamma <- rep(params[param, "gammaPrior"], nrow(subjData)), gamma <- rep(gammaStart, nrow(subjData)))
     
@@ -697,7 +697,8 @@ plot_adaptive_fitsub <- function(id = "58", exp = "btw", showChoices = -0.6) {
     s
     # plot
     ratePlot <- sub %>%
-      mutate(trialRate = Offer / (Handling ^ s),
+      mutate(Handling = Handling + 2,
+             trialRate = Offer / (Handling ^ s),
              g = temp$rate,
              fitChoice = ifelse(trialRate > g, -0.25, -5),
              newChoice = ifelse(Choice == 1, -0.5, -5),
@@ -835,22 +836,22 @@ recover_results_wth <- function(fitsList, binary = F, matrix = T, order = F) {
     ungroup() %>%
     mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>% 
     ggplot(aes(Offer, propAccept, color = Cost)) +
-    geom_point(size = 3, show.legend = T) +
-    geom_line(size = 1, show.legend = F) +
-    scale_color_manual(values = colsWth) +
-    scale_fill_manual(values = colsWth) +
-    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
-    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
-    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-    labs(x = "Reward", y = "Proportion Accepted") +
[…]

### 2020-08-26 Simulations/manuscript_modeling.R
request more scc cores (full node)

@@ -7,7 +7,7 @@
 # the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
 # maybe also R-squares and things in the current optimization function
 
-#$ -pe omp 28
+#$ -pe omp 36
 
 ## libraries
 library(tidyverse)

### 2020-09-21 Cost_manuscript.Rmd
initial dev: start optimization

@@
 Comparing likelihood fits among lengths of offer history (e.g.
-sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r AIC(historySize_btw[[historyIndex]])`), which matched the offer presentation rotation (see Methods).
+sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r AIC(historySize_btw[[historyIndex_btw]])`), which matched the offer presentation rotation (see Methods).
 These results confirm the expected influence of time and offer magnitude on choice behavior, but also suggest that participants adapted to their recent experience.
@@
 Error"]`, *p* `r report_p(historyCoeffs_wth["recentOffers", "Pr(>|z|)"])`).
-Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r AIC(historySize_wth[[historyIndex]])`.
+Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r AIC(historySize_wth[[historyIndex_wth]])`.
 However, this time participants were unaffected by recent reward misses (*p* > 0.05).
@@
 ``` {r WTH: 16.3.5., echo = FALSE, fig.width=5, fig.height=4, fig.align="center"}
-# subdivide data
-dataTrain <- dataWth %>%
-   filter(Block < 5)
-
-dataTest <- dataWth %>%
-  filter(Block > 4)
-
-# estimate
-# per-cost, but consider the idea above
-OCs_validation <- list()
-temp <- dataTrain %>% filter(Cost == "Wait-C") %>% plyr::dlply("SubjID", identity)
-OCs_validation$`Wait-C` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-temp <- dataTrain %>% filter(Cost == "Wait-P") %>% plyr::dlply("SubjID", identity)
-OCs_validation$`Wait-P` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-temp <- dataTrain %>% filter(Cost == "Cognitive") %>% plyr::dlply("SubjID", identity)
-OCs_validation$Cognitive <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-temp <- dataTrain %>% filter(Cost == "Physical") %>% plyr::dlply("SubjID", identity)
-OCs_validation$Physical <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-
-# reshape data
-temp <- bind_rows(OCs_validation) %>% 
-  mutate(SubjID = subjList_wth) %>%
-  gather(Cost, gamma, `Wait-C`:Physical) %>%
-  left_join(dataTest, ., by = c("SubjID", "Cost")) %>% # assign OCs to each subject per cost type
-  mutate(prediction = Offer > Handling * gamma) %>%
-  # plyr::dlply("SubjID", identity)
-  group_by(SubjID, Cost) %>%
-  summarize(predicted = mean(Choice == prediction))
-
-# plot prediction %
-# qplot(Cost, predicted, geom = "boxplot", data = temp) + 
-#   ylim(0,1) +
-#   theme_classic()
+#####################
+### THROWS AN ERROR, COMMENTING TO TRY AND KNIT DOCUMENT
+
+# # subdivide data
+# dataTrain <- dataWth %>%
+#    filter(Block < 5)
+# 
+# dataTest <- dataWth %>%
+#   filter(Block > 4)
+# 
+# # estimate
+# # per-cost, but consider the idea above
+# OCs_validation <- list()
+# temp <- dataTrain %>% filter(Cost == "Wait-C") %>% plyr::dlply("SubjID", identity)
+# OCs_validation$`Wait-C` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+# temp <- dataTrain %>% filter(Cost == "Wait-P") %>% plyr::dlply("SubjID", identity)
+# OCs_validation$`Wait-P` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+# temp <- dataTrain %>% filter(Cost == "Cognitive") %>% plyr::dlply("SubjID", identity)
+# OCs_validation$Cognitive <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+# temp <- dataTrain %>% filter(Cost == "Physical") %>% plyr::dlply("SubjID", identity)
+# OCs_validation$Physical <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+# 
+# ##############################
+# ### Threw an error!
+# # # reshape data
+# # temp <- bind_rows(OCs_validation) %>% 
+# #   mutate(SubjID = subjList_wth) %>%
+# #   gather(Cost, gamma, `Wait-C`:Physical) %>%
+# #   left_join(dataTest, ., by = c("SubjID", "Cost")) %>% # assign OCs to each subject per cost type
+# #   mutate(prediction = Offer > Handling * gamma) %>%
+# #   # plyr::dlply("SubjID", identity)
+# #   group_by(SubjID, Cost) %>%
+# #   summarize(predicted = mean(Choice == prediction))
+# ##############################
+# 
+# 
+# # plot prediction %
+# # qplot(Cost, predicted, geom = "boxplot", data = temp) + 
+# #   ylim(0,1) +
+# #   theme_classic()
 ```

### 2020-09-21 models_gk/likelihoods.R

@@ -1,0 +1,36 @@
+### define likelihood functions
+
+time_sensitivity_lik = function(R_i, H_i, Choice, gamma, beta) {
+  p_accept = 1 / (1 + exp(-beta * (R_i - gamma * H_i)))
+  p_choice = ifelse(as.logical(Choice), p_accept, 1-p_accept)
+  p_choice
+}
+
+time_sensitivity_rate_lik = function(R_i, H_i, T_i, Choice, gamma, beta, Block=NULL) {
+  accept_rate = R_i / (gamma * H_i + T_i)
+  
+  if(is.null(Block)){
+    global_rate = sum(R_i * Choice) / sum(gamma * H_i * Choice + T_i)
+  } else {
+    blocks = unique(Block)
+    global_rate = numeric(length(R_i))
+    for (i in unique(block)) {
+      global_rate[Block==i] = sum(R_i[Block==i] * Choice[Block==i]) / sum(gamma * H_i[Block==i] * Choice[Block==i] + T_i[Block==i])
+    }
+  }
+  
+  p_accept = 1 / (1 + exp(-beta * (accept_rate - global_rate)))
+  p_choice = ifelse(as.logical(Choice), p_accept, 1-p_accept)
+  p_choice
+}
+
+get_lik = function(par, lfun, par_names=NULL, log_par=F, min_p=1e-5, return_liks=F, ...) {
+  if(log_par) par=exp(par)
+  if(!is.null(par_names)) names(par) = par_names
+  liks = do.call(lfun, c(as.list(par), list(...)))
+  liks[liks < min_p] = min_p
+  if (return_liks)
+    return(liks)
+  else
+    return(-sum(log(liks)))
+}

### 2020-09-21 models_gk/manuscript_modeling.R

@@ -1,0 +1,1638 @@
+#!/usr/bin/env Rscript
+
+# using NLOPTR is pointless here
+# instead I'm just going to feed any sensible combination of parameters to the model and minimize the negLL manually
+# simpler, can evaluate models easier, and faster
+# for tomorrow: have negloglik return the parameters per iteration
+# the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
+# maybe also R-squares and things in the current optimization function
+
+#$ -pe omp 28
+
+## libraries
+library(tidyverse)
+library(ggfortify)
+library(knitr)
+library(pander) 
+library(nloptr)
+#library(pwr)
+library(lme4)
+#library(lmerTest)
+library(gridExtra)
+library(reshape2)
+library(corrplot)
+#library(survival)
+library(ggfortify)
+#library(patchwork)
+library(data.table)
+library(parallel)
+
+# remove break time and start counting from 0
+standardize_time <- function(subjData) {
+  # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
+  breakTime <- min(subjData$ExpTime[subjData$Block == 4]) - max(subjData$ExpTime[subjData$Block == 3])
+  subjData$ExpTime[which(subjData$Block > 3)] <- subjData$ExpTime[which(subjData$Block > 3)] - breakTime + 16
+  subjData$ExpTime <- subjData$ExpTime - min(subjData$ExpTime)
+  
+  return(subjData)
+}
+
+# summary matrices for refrence-changing models
+betaMatrix <- function(model, rearrange = NA) {
+  # get a similarity matrix of the resulting coefficient pairings for the cost conditions
+  # first, do a full_join based on column names on the list of coefficient vectors from each dummy code relevel
+  # then match the names of columns and rows so NAs are in the diagonal
+  
+  # get the names of the reference group per model iteration
+  refnames <- names(model)
+  
+  # coefficient matrix
+  temp <- lapply(model, function(data) {coefficients(data)$SubjID[1, 2:4]})
+  mixCoeffs <- bind_rows(temp) 
[…]

### 2020-09-21 models_gk/modeling_gk.R

@@ -1,0 +1,90 @@
+#########################
+### Setup
+#########################
+
+# set wd
+setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
+
+library(data.table)
+library(foreach)
+
+reload = function(){
+  library(modelfitr)
+  detach("package:modelfitr", unload=T)
+  library(modelfitr)
+}
+reload()
+
+source('models_gk/likelihoods.R')
+
+#########################
+### Load Data
+#########################
+
+dir_btw = 'Cost2/data'
+f_btw = list.files(dir_btw, pattern=".csv", full.names=T)
+dat_btw = foreach(f = f_btw, .combine=rbind) %do% {
+  info = strsplit(basename(f), "_")[[1]]
+  data.table(sub=info[1], cond=info[2], date=info[3], fread(f))
+}
+dat_btw[, Travel := 16-Handling]
+
+# dir_wth = 'Cost3/data'
+# f_wth = list.files(dir_wth, pattern="main_log*.csv", full.names=T)
+# dat_wth = foreach(f = f_wth, .combine=rbind) %do% {
+#   info = strsplit(basename(f), "_")[[1]]
+#   data.table(sub=info[1], cond=info[2], date=info[3], fread(f))
+# }
+
+#########################
+### Fit time sensitivity model
+#########################
+
+par_values = c(gamma = 1, beta = .1)
+
+reload()
+system.time(fits_btw <- dat_btw[,
+                                modelfitr::fit_model(
+                                  get_lik,
+                                  log(par_values),
+                                  hessian=T,
+                                  method="nmkb",
+                                  obj_args=list(
+                                    lfun=time_sensitivity_lik,
+                                    R_i=Offer,
+                                    H_i=Handling,
+                                    Choice=Choice,
+                                    log_par=T
+                                  ),
+                                  aic=T,
+                                  bic=T,
+                                  n_obs=.N,
+                                  return_df=T),
+                                .(sub, cond)
+])
+fits_btw[, gamma := exp(gamma)]
+fits_btw[, beta := exp(beta)]
+
+fits_btw_melt = melt(fits_btw, measure.vars=c("gamma", "beta"), variable.name="par", value.name="val")
+ggplot(fits_btw_melt, aes(x=cond, y=val)) +
+  facet_wrap(~par, scales="free") +
+  geom_violin()
+
[…]

### 2020-09-24 Cost_manuscript.Rmd
quick note

--- 2020-08-25 Cost_manuscript.Rmd
@@
 
+- Make sure to note that we controlled for time as a confound for effort, as more effortful tasks normally take longer
 - What we think: subjective timing is shortened by the way we implemented cognitive effort.

### 2020-10-21 Cost_manuscript.Rmd
gathering writing samples for the intro

@@
 
-  Effort is costly, but sometimes it can add value (For the talk, use the T example with Angelina, but think about how well it fits in the "prefer effort").
-In thinking about this, studies have focused on TAFC.
+  Prospectus: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
+*Effort examples here?* In neuroeconomics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015).
+Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013).
+However, people often change their attitudes towards exerting effort in everyday decisions.
+For example, we might choose to take the effortful route home that we normally avoid rather than waiting for a delayed train.
+Understanding the sporadic attractiveness of effort exemplified above has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017).
+  Measuring the cost of effort and delay is often done by offering higher payouts for an increment of the respective demand, but flexible preferences for effort might stem from the availability of other types of demands in the same choice environment.
+(Kool & Botvinick, 2018).
+Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Mobbs, Trimmer, Blumstein, & Dayan, 2018).
+In addition, foraging tasks can allow individuals to emphasize different elements of the decision context, and rest on a rich modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
+  In this study, we will test the hypothesis that preferences will vary depending on whether individuals face a single or multiple types of behavioral demands, and identify what factors drive these choices.
+Based on two foraging experiments and computational modeling, we will show that 1) preferences for mental effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
+  In this study, we will behaviorally and computationally test the hypothesis that the attractiveness of a reward that requires effort or delay depends on whether rewards associated with alternative demands are available in the same context.
+Using a foraging paradigm will enable us to 1) assess whether people integrate the statistics of the environment to generate strategies that maximize their earnings; 2) compare how the presence of effort or delay shifts such strategies, as reflected by acceptance rates; 3) examine if acceptance rates are further altered by foraging for costs in addition to rewards; and 4) test a combination of foraging (Constantino & Daw, 2015; Stephens & Krebs, 2019; Fawcett, McNamara, & Houston, 2012) and reinforcement learning models (Sutton & Barto, 2018) to examine whether preferences for demands reflect a subjective reduction of cost or boost of value, and determine any factors besides contextual manipulations that participants consider in order to adjust their choices.
+
+  Grant: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
+Demands for both time and effort have been identified as costs that detract from the net subjective value of rewards.
+Decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [1–9].
+Excessive aversion to delay and effort can manifest as impulsivity and apathy, respectively [1,10–12], fluctuations in which are hallmark symptoms of various mental illnesses and substance use disorders [13].
+However, we do not yet fully understand 1) how the brain transforms these two parallel forms of discounting into seemingly opposite behaviors; 2) whether the same mechanism applies to different types of effort (e.g.
+physical versus cognitive); or 3) the ways in which these distinct forms of cost interact in individuals.
+In this project, I plan to combine individualized brain mapping with computational modeling to examine how an individual’s functional brain network organization relates to the subjective costs of physical effort, cognitive effort, and pure delay.
+  Behavioral distinctions between effort and delay costs: The process of engaging with a costly reward can be divided into three stages: evaluation (when costs and benefits of a prospect are integrated), pursuit (i.e.
+waiting or exerting effort), and receipt of the reward.
+An ever-increasing literature in psychology, neuroscience, and economics has focused on the first stage to compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated demand [1,3,5,8,9,14].
+Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16].
+Investigations of the pursuit and receipt stages have been comparatively limited.
+Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [5,11,15,16,19].
+However, discrepancies between expected and experienced value are well known [20], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards [3,21,22].
+  The evidence reviewed above has two main limitations.
+First, studies have not focused on how effort and delay might interact in the common case of choosing among demands.
+For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting.
+  It is unknown how effort demands discount value in isolation versus when alternative demands are available.
+The friction that we perceive from these demands could depend on what we could be performing instead [61].
+
+IDEAS:
+
+   Studies have often focused on TAFC.
 We have learned much about this (show data), but two issues: 1) many studies compare costs by comparing discounting functions, which is helpful, but 2) an often disregarded aspect of this is OC.
@@
 
-In this talk, I'll show you how we'veused this framework to understand the inherent (elaborate on inherent above) and relative costly nature of effort and delay.
-I'll focus on behavioral findings, and I'll give a nudge to modeling.
-Then I'll discuss how we plan to understand the brain networks that characterize this behavior, with a focus on individual differences.
-
-What we've learned is how increasing a given demand reduces the value of its associated reward, but less explored is the question about how people choose among them, specifically how people allocate their time to engage with demands.
-
+  Modeling: mention that the rich history of foraging modeling can help us pinpoint a number of things, like the putative cost or attractiveness of a demand, whether preferences emerge from focal considerations of the value of a trial or a global estimate of what alternative way could be used to obtain rewards.
+Foraging and its modeling can provide a common framework to examine differences, rather than relying on matching disc functions.
+
+  Clinical: Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
+Like, the aversion is due to focusing on different elements of the task.
 - I guess you can mention that the wait group acts as a baseline of foraging behavior.
@@
 Fatigue would apply equally to both, or alternatively it might not bring all down to the same level (I guess the point could be made, but it's not that people who complete more at the beginning decrease acceptances more, as one would expect from fatigued people)
-- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effor aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
+- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
 Like, the aversion is due to focusing on different elements of the task.

### 2020-10-22 Cost_manuscript.Rmd
working on combining existing wording into new intro

@@
 
+Outline:
+- Effort and delay tend to be aversive, and neuroeconhas traditionally examined them as such
+- But there is a flipside of effort: it can be attractive
+- One issue is that even for studies that compare across demands, they do so by quantifying discounting curves
+- A less explored avenue that might get at this though is the comparison among demands
+- Ecological foraging paradigms can help us with this approach, allowing for people to search for their preferred demands
+- In addition, foraging rests on a rich modeling history
+- We can model whether preferences for demands are due to either 1) modulating cost or embuing value relative to optimal behavior; 2) whether people attend to focal decision elements or global environmental attributes when they evaluate demanding offers
+- In this study....
+
   Prospectus: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
-*Effort examples here?* In neuroeconomics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015).
+In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015).
 Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013).
@@
 For example, we might choose to take the effortful route home that we normally avoid rather than waiting for a delayed train.
+.
 Understanding the sporadic attractiveness of effort exemplified above has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017).
-  Measuring the cost of effort and delay is often done by offering higher payouts for an increment of the respective demand, but flexible preferences for effort might stem from the availability of other types of demands in the same choice environment.
-(Kool & Botvinick, 2018).
+(add Loewenstein 1987 and other explanatory candidates here.
+I think the goal will be that there are theories speculating about when demands can be valuable for a single choice decision, or in TAFC, but point out inconclusiveness.
+The next paragraph should say that what's missing is comparing among costs)
+  A key limitation in understanding this phenomenon is that studies often compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
+Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16].
+Furthermore, this approach fails to interrogate which type of demand people would select.
+Flexible preferences for effort might stem from the availability of other types of demands in the same choice environment (Kool & Botvinick, 2018).
   Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Mobbs, Trimmer, Blumstein, & Dayan, 2018).
@@
   In this study, we will behaviorally and computationally test the hypothesis that the attractiveness of a reward that requires effort or delay depends on whether rewards associated with alternative demands are available in the same context.
-Using a foraging paradigm will enable us to 1) assess whether people integrate the statistics of the environment to generate strategies that maximize their earnings; 2) compare how the presence of effort or delay shifts such strategies, as reflected by acceptance rates; 3) examine if acceptance rates are further altered by foraging for costs in addition to rewards; and 4) test a combination of foraging (Constantino & Daw, 2015; Stephens & Krebs, 2019; Fawcett, McNamara, & Houston, 2012) and reinforcement learning models (Sutton & Barto, 2018) to examine whether preferences for demands reflect a subjective reduction of cost or boost of value, and determine any factors besides contextual manipulations that participants consider in order to adjust their choices.
+Using a foraging paradigm will enable us to 1) assess whether people integrate the statistics of the environment to generate strategies that maximize their earnings; 2) compare how the presence of effort or delay shifts such strategies, as reflected by acceptance rates; 3) examine if acceptance rates are further altered by foraging for costs in addition to rewards; and 4) test a combination of foraging (Constantino & Daw, 2015; Stephens & Krebs, 2019; Fawcett, McNamara, & Houston, 2012) to examine whether preferences for demands reflect a subjective reduction of cost or boost of value, and determine any factors besides contextual manipulations that participants consider in order to adjust their choices.
 

### 2020-10-22 Cost_manuscript.Rmd
more intro

@@
 For example, we might choose to take the effortful route home that we normally avoid rather than waiting for a delayed train.
-.
-Understanding the sporadic attractiveness of effort exemplified above has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017).
+Understanding the sporadic attractiveness of effort has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017).
 (add Loewenstein 1987 and other explanatory candidates here.
@@
 The next paragraph should say that what's missing is comparing among costs)
-  A key limitation in understanding this phenomenon is that studies often compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
+  A key limitation in understanding this phenomenon is the lack of attention given to how effort and delay might interact in the common case of choosing among demands (*An often overlooked attribute of this phenomenon is that a preference for effort is sometimes a preference over doing something else.
+For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting.*).
+Studies often compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
 Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16].
@@
 Using a foraging paradigm will enable us to 1) assess whether people integrate the statistics of the environment to generate strategies that maximize their earnings; 2) compare how the presence of effort or delay shifts such strategies, as reflected by acceptance rates; 3) examine if acceptance rates are further altered by foraging for costs in addition to rewards; and 4) test a combination of foraging (Constantino & Daw, 2015; Stephens & Krebs, 2019; Fawcett, McNamara, & Houston, 2012) to examine whether preferences for demands reflect a subjective reduction of cost or boost of value, and determine any factors besides contextual manipulations that participants consider in order to adjust their choices.
+
+studies have not focused on how effort and delay might interact in the common case of choosing among demands.
 

### 2020-10-26 Cost_manuscript.Rmd
more intro

--- 2020-10-22 Cost_manuscript.Rmd
@@
 Outline:
-- Effort and delay tend to be aversive, and neuroeconhas traditionally examined them as such
+- Effort and delay tend to be aversive, and neuroeconhas traditionally examines them as such
 - But there is a flipside of effort: it can be attractive
@@
 
-  Prospectus: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
+  Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
+The intuitive reaction to this evaluation is aversion.
 In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015).
 Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013).
-However, people often change their attitudes towards exerting effort in everyday decisions.
-For example, we might choose to take the effortful route home that we normally avoid rather than waiting for a delayed train.
-.
-Understanding the sporadic attractiveness of effort exemplified above has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017).
-(add Loewenstein 1987 and other explanatory candidates here.
-I think the goal will be that there are theories speculating about when demands can be valuable for a single choice decision, or in TAFC, but point out inconclusiveness.
-The next paragraph should say that what's missing is comparing among costs)
-  A key limitation in understanding this phenomenon is that studies often compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
+However, people often change their attitudes towards exerting effort in everyday decisions, resulting in pursual of effortful avenues instead (Inzlicht, Shenhav, & Olivola, 2017).
+Much experimental and theoretical work surrounding the sporadic attractiveness of effort suggests a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes (kacelnik), and positive outcomes imbue value into their preceding effortful behavior (learned industriousness cite).
+Even though the prevalent emphasis on these retrospective value associations can help explain a variety of scenarios, it is still in its infancy (be more explicit).
+
+  What is often missing from these accounts is the common case of choosing among behavioral demands, which is partly due to the scope of experimental designs.
+Studies tend to compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
 Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16].
-Furthermore, this approach fails to interrogate which type of demand people would select.
-Flexible preferences for effort might stem from the availability of other types of demands in the same choice environment (Kool & Botvinick, 2018).
+Rather than arising from changes in the decay of value, flexible preferences for effort might stem from the availability of other types of demands in the same choice environment—in other words, from its context (Kool & Botvinick, 2018).
+For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting.
+Now add charitable giving evidence from inzlicht paper.
+
+  Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Mobbs, Trimmer, Blumstein, & Dayan, 2018).
+In addition, foraging tasks can allow individuals to emphasize different elements of the decision context, and rest on a rich modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
+Foraging has attracted high scientific interest due to its ecological validity, which is rooted in evolutionary choice behaviors [49].
+The paradigm requires the decision maker to choose whether to engage with a single presented offer or skip it in search of a better one.
+A key advantage of foraging paradigms is that people can rapidly adopt stable, rewardmaximizing strategies [50].
+Add that Fawcett bit…
+
+  In this study, we will test the hypothesis that preferences will vary depending on whether individuals face a single or multiple types of behavioral demands.
+Leveraging the ecological and computational richness of foraging paradigms will provide new insights on a number of open questions.
+First, the existence of a well-defined optimal choice strategy in foraging paradigms is useful for identifying when demands boost the value of rewards (i.e.
+overharvesting poor offers).
+Second, increasing the level of exposure to types of demands over two experiments will let us probe whether their cost is intrinsic or relative.
+Third, confronting participants with both mental and physical effort will let us probe whether these preferences are domain general or task-specific.
+Finally, modeling will help us disambiguate what drives these preferences.
+We predict that..
+
+####-------######
   Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Mobbs, Trimmer, Blumstein, & Dayan, 2018).
@@
 
+  Understanding what drives the sporadic attractiveness of effortful avenues remains elusive.
+In this study, we...1) preferences for mental effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
+
 - Make sure to note that we controlled for time as a confound for effort, as more effortful tasks normally take longer
@@
 5) fatigue: there's a similar gradual decrease in acceptances in both experiments, except for the wait condition in exp 1.
-Fatigue would apply equally to both, or alternatively it might not bring all down to the same level (I guess the point could be made, but it's not that people who complete more at the beginning decrease acceptances more, as one would expect from fatigued people)
+Fatigue would apply equally to both, or alternatively it might not bring all down to the same level (I guess the point could be made, but it's not that people who complete more at the beginning decrease acceptances more, as one would expect from fatigued people).
+Also worth mentioning that even if this is due to need for cognition (i.e.
+Ceyda; Laura; Cacioppo et al 1996), the collapsing in the second experiment shows that preferences for cognitive effort cannot be just that.
 - Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).

### 2020-10-27 Cost_manuscript.Rmd
last 2 pars

@@
 
-  In this study, we will test the hypothesis that preferences will vary depending on whether individuals face a single or multiple types of behavioral demands.
-Leveraging the ecological and computational richness of foraging paradigms will provide new insights on a number of open questions.
-First, the existence of a well-defined optimal choice strategy in foraging paradigms is useful for identifying when demands boost the value of rewards (i.e.
+  In this study, we tested the hypothesis that preferences would vary depending on whether individuals face a single or multiple types of behavioral demands (i.e.
+cognitive effort, physical effort, and delay).
+We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions.
+First, the existence of a well-defined optimal choice strategy in foraging designs was useful for identifying when demands boost the value of rewards (i.e.
 overharvesting poor offers).
-Second, increasing the level of exposure to types of demands over two experiments will let us probe whether their cost is intrinsic or relative.
-Third, confronting participants with both mental and physical effort will let us probe whether these preferences are domain general or task-specific.
-Finally, modeling will help us disambiguate what drives these preferences.
-We predict that..
+Second, increasing the level of exposure to types of demands over two experiments let us probe whether their cost is intrinsic or relative.
+Third, confronting participants with both mental and physical effort let us probe whether these preferences are domain general or task-specific.
+Finally, modeling helped us disambiguate what drove these preferences.
+
+  Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of whether they faced a single or intermixed demands.
+When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups underaccepted, partially matching our predictions and suggesting that cognitive effort can add value to outcomes.
+However, against our expectations, we found that a similar preference for cognitive effort disappeared over time as decision makers foraged for types of demands in addition to rewards.
+Computational modeling suggested that cognitive effort was valuable because it shortened the perceived time of trials, a phenomenon that could be recalibrated as individuals experienced multiple forms of demands (a detailed description of our preregistered hypotheses can be found on https://osf.io/2rsgm/).
+Our results expand our understanding of the attractiveness of effort, highlighting a role for features in the decision environment that are independent from a pure association between effort and reward.
 

### 2020-10-27 Cost_manuscript.Rmd
two last intro pars

@@
   Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
-The intuitive reaction to this evaluation is aversion.
+The intuitive reaction to this evaluation is to find demands aversive.
 In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015).
 Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013).
-However, people often change their attitudes towards exerting effort in everyday decisions, resulting in pursual of effortful avenues instead (Inzlicht, Shenhav, & Olivola, 2017).
-Much experimental and theoretical work surrounding the sporadic attractiveness of effort suggests a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes (kacelnik), and positive outcomes imbue value into their preceding effortful behavior (learned industriousness cite).
-Even though the prevalent emphasis on these retrospective value associations can help explain a variety of scenarios, it is still in its infancy (be more explicit).
-
-  What is often missing from these accounts is the common case of choosing among behavioral demands, which is partly due to the scope of experimental designs.
+However, people often change their attitudes towards exerting effort in everyday decisions, resulting in pursual of effortful avenues instead.
+Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes (Kacelnik and Marsh, 2002), and positive outcomes imbue value into their preceding effortful behavior (i.e.
+learned industriousness; Eisenberger, 1992).
+Though intuitively valid and empirically supported, this explanation leaves open questions about what intrinsic features of an effortful task can make it attractive beyond its associated outcome, and how contextual factors mold their perceived costs (see Inzlicht, Shenhav, and Olivola, 2018, for a review on the attractiveness of effort).
+
+  What is often missing from these accounts is the common case of choosing among behavioral demands, partly due to the scope of traditional experimental designs.
 Studies tend to compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
 Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16].
-Rather than arising from changes in the decay of value, flexible preferences for effort might stem from the availability of other types of demands in the same choice environment—in other words, from its context (Kool & Botvinick, 2018).
+However, flexible preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context (Kool & Botvinick, 2018).
 For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting.
-Now add charitable giving evidence from inzlicht paper.
+Conversely, even though people tend to donate more to charitable events that require them to perform effortful activities (i.e.
+the martyrdom effect), they are also less likely to engage in such events once an easier alternative to raise funds becomes available (Olivola and Shafir, 2013).
 
@@
 A key advantage of foraging paradigms is that people can rapidly adopt stable, rewardmaximizing strategies [50].
-Add that Fawcett bit…
+Add that Fawcett bit and modeling…
 
@@
 Second, increasing the level of exposure to types of demands over two experiments let us probe whether their cost is intrinsic or relative.
-Third, confronting participants with both mental and physical effort let us probe whether these preferences are domain general or task-specific.
-Finally, modeling helped us disambiguate what drove these preferences.
+Finally, confronting participants with both mental and physical effort let us probe whether these preferences are domain general or task-specific, and in the case of the latter, isolate factors that influence preferences beyond the often cited associative relationship between effort and outcome (e.g.
+features of an effortful task that makes it more attractive).
 

### 2020-10-29 Cost_manuscript.Rmd
draft of intro number 1

@@
 
-Outline:
-- Effort and delay tend to be aversive, and neuroeconhas traditionally examines them as such
-- But there is a flipside of effort: it can be attractive
-- One issue is that even for studies that compare across demands, they do so by quantifying discounting curves
-- A less explored avenue that might get at this though is the comparison among demands
-- Ecological foraging paradigms can help us with this approach, allowing for people to search for their preferred demands
-- In addition, foraging rests on a rich modeling history
-- We can model whether preferences for demands are due to either 1) modulating cost or embuing value relative to optimal behavior; 2) whether people attend to focal decision elements or global environmental attributes when they evaluate demanding offers
-- In this study....
-
   Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
-The intuitive reaction to this evaluation is to find demands aversive.
 In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015).
@@
 However, people often change their attitudes towards exerting effort in everyday decisions, resulting in pursual of effortful avenues instead.
-Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes (Kacelnik and Marsh, 2002), and positive outcomes imbue value into their preceding effortful behavior (i.e.
-learned industriousness; Eisenberger, 1992).
-Though intuitively valid and empirically supported, this explanation leaves open questions about what intrinsic features of an effortful task can make it attractive beyond its associated outcome, and how contextual factors mold their perceived costs (see Inzlicht, Shenhav, and Olivola, 2018, for a review on the attractiveness of effort).
-
-  What is often missing from these accounts is the common case of choosing among behavioral demands, partly due to the scope of traditional experimental designs.
-Studies tend to compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
+Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes (Kacelnik and Marsh, 2002; Mochon, Norton, and Ariely, 2012; Hernandez Lallement et al., 2014), and positive outcomes imbue value into their preceding effortful behavior (i.e.
+learned industriousness, Eisenberger, 1992).
+Though intuitively valid and empirically supported, this explanation leaves open questions about what intrinsic features of an effortful task can make it attractive outside of its associated outcome, and how contextual factors mold their perceived costs (see Inzlicht, Shenhav, and Olivola, 2018, for a review on the attractiveness of effort).
+Understanding these additional qualities could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
+
+  What is often missing from existing accounts is the common case of choosing among types of behavioral demands.
+Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
 Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16].
-However, flexible preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context (Kool & Botvinick, 2018).
-For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting.
+However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context (Kool & Botvinick, 2018).
+For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting (e.g.
+taking the cumbersome way home rather than waiting for a delayed train, even if the resulting time of arrival is the same).
 Conversely, even though people tend to donate more to charitable events that require them to perform effortful activities (i.e.
 the martyrdom effect), they are also less likely to engage in such events once an easier alternative to raise funds becomes available (Olivola and Shafir, 2013).
-
-  Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Mobbs, Trimmer, Blumstein, & Dayan, 2018).
-In addition, foraging tasks can allow individuals to emphasize different elements of the decision context, and rest on a rich modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
-Foraging has attracted high scientific interest due to its ecological validity, which is rooted in evolutionary choice behaviors [49].
-The paradigm requires the decision maker to choose whether to engage with a single presented offer or skip it in search of a better one.
-A key advantage of foraging paradigms is that people can rapidly adopt stable, rewardmaximizing strategies [50].
-Add that Fawcett bit and modeling…
+Recent work has proposed that the subjective costs produced by delays and cognitive effort is modulated by the possibility of missing out on better concurrent alternatives, namely the opportunity cost of time (OC; Fawcett et al., 2012; Kurzban et al, 2013; Otto and Daw, 2019).
+This evidence sets the stage for examining what people would actually select when given the option for multiple types of demands, including the unexplored question of deciding between cognitive and physical effort (Inzlicht, Shenhav, and Olivola, 2018).
+
+  Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Stephens & Krebs, 2019).
+Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionary choice behaviors (Hayden 2018; Mobbs, Trimmer, Blumstein, & Dayan, 2018), and offers a number of desirable qualities.
+First, it allows for the estimation of reward maximizing choice patterns based on the opportunity cost of time (Charnov, 1975; Kacelnik and Krebs, 1977), which people can readily approximate and persistently follow (Constantino and Daw, 2015 ADD).
+One can then interpret observed deviations in acceptance rates from such optimal behavior in addition to comparing them among demands.
+Second, the sequential nature of foraging allows individuals to emphasize different elements of the decision context.
+For example, the cost (or value) of effort or delay could globally depend on the availability of alternative demands (as suggested above), impacting the perceived opportunity cost of time.
+Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that adapt once individuals experience different forms of behavioral costs.
+Foraging rests on an abundant modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
 
@@
 We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions.
-First, the existence of a well-defined optimal choice strategy in foraging designs was useful for identifying when demands boost the value of rewards (i.e.
+First, the existence of a well-defined optimal choice strategy in foraging designs helped us identify when demands boost the value of rewards (i.e.
 overharvesting poor offers).
-Second, increasing the level of exposure to types of demands over two experiments let us probe whether their cost is intrinsic or relative.
-Finally, confronting participants with both mental and physical effort let us probe whether these preferences are domain general or task-specific, and in the case of the latter, isolate factors that influence preferences beyond the often cited associative relationship between effort and outcome (e.g.
+Second, increasing the level of exposure to types of demands over two experiments allowed us to asses whether their cost was intrinsic or relative.
+Finally, confronting participants with both mental and physical effort let us probe whether these preferences were domain general or task-specific, and in the case of the latter, isolate factors that influence preferences beyond the often cited associative relationship between effort and outcome (e.g.
 features of an effortful task that makes it more attractive).
 
-  Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of whether they faced a single or intermixed demands.
-When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups underaccepted, partially matching our predictions and suggesting that cognitive effort can add value to outcomes.
+  Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment, or whether they faced a single or intermixed demands.
+When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups underaccepted, partially matching our predictions and highlighting that cognitive effort can add value to outcomes.
 However, against our expectations, we found that a similar preference for cognitive effort disappeared over time as decision makers foraged for types of demands in addition to rewards.
-Computational modeling suggested that cognitive effort was valuable because it shortened the perceived time of trials, a phenomenon that could be recalibrated as individuals experienced multiple forms of demands (a detailed description of our preregistered hypotheses can be found on https://osf.io/2rsgm/).
-Our results expand our understanding of the attractiveness of effort, highlighting a role for features in the decision environment that are independent from a pure association between effort and reward.
+Computational modeling suggested that cognitive effort was valuable because it shortened the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (a detailed description of our preregistered hypotheses can be found on https://osf.io/2rsgm/).
+Our results expand our understanding of the attractiveness of effort, highlighting a role for features in the decision environment that are independent from a pure association between effort and reward, and point to characteristics that can be leveraged in order to motivate effort engagement in diverse everyday scenarios.
 
 ####-------######
-  Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Mobbs, Trimmer, Blumstein, & Dayan, 2018).
-In addition, foraging tasks can allow individuals to emphasize different elements of the decision context, and rest on a rich modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
-  In this study, we will test the hypothesis that preferences will vary depending on whether individuals face a single or multiple types of behavioral demands, and identify what factors drive these choices.
-Based on two foraging experiments and computational modeling, we will show that 1) preferences for mental effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
-  In this study, we will behaviorally and computationally test the hypothesis that the attractiveness of a reward that requires effort or delay depends on whether rewards associated with alternative demands are available in the same context.
-Using a foraging paradigm will enable us to 1) assess whether people integrate the statistics of the environment to generate strategies that maximize their earnings; 2) compare how the presence of effort or delay shifts such strategies, as reflected by acceptance rates; 3) examine if acceptance rates are further altered by foraging for costs in addition to rewards; and 4) test a combination of foraging (Constantino & Daw, 2015; Stephens & Krebs, 2019; Fawcett, McNamara, & Houston, 2012) to examine whether preferences for demands reflect a subjective reduction of cost or boost of value, and determine any factors besides contextual manipulations that participants consider in order to adjust their choices.
-
-studies have not focused on how effort and delay might interact in the common case of choosing among demands.
-
-  Grant: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
-Demands for both time and effort have been identified as costs that detract from the net subjective value of rewards.
-Decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [1–9].
-Excessive aversion to delay and effort can manifest as impulsivity and apathy, respectively [1,10–12], fluctuations in which are hallmark symptoms of various mental illnesses and substance use disorders [13].
-However, we do not yet fully understand 1) how the brain transforms these two parallel forms of discounting into seemingly opposite behaviors; 2) whether the same mechanism applies to different types of effort (e.g.
-physical versus cognitive); or 3) the ways in which these distinct forms of cost interact in individuals.
-In this project, I plan to combine individualized brain mapping with computational modeling to examine how an individual’s functional brain network organization relates to the subjective costs of physical effort, cognitive effort, and pure delay.
-  Behavioral distinctions between effort and delay costs: The process of engaging with a costly reward can be divided into three stages: evaluation (when costs and benefits of a prospect are integrated), pursuit (i.e.
-waiting or exerting effort), and receipt of the reward.
-An ever-increasing literature in psychology, neuroscience, and economics has focused on the first stage to compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated demand [1,3,5,8,9,14].
-Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16].
-Investigations of the pursuit and receipt stages have been comparatively limited.
-Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [5,11,15,16,19].
-However, discrepancies between expected and experienced value are well known [20], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards [3,21,22].
-  The evidence reviewed above has two main limitations.
-First, studies have not focused on how effort and delay might interact in the common case of choosing among demands.
-For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting.
-  It is unknown how effort demands discount value in isolation versus when alternative demands are available.
-The friction that we perceive from these demands could depend on what we could be performing instead [61].
-
-IDEAS:
-
-   Studies have often focused on TAFC.
-We have learned much about this (show data), but two issues: 1) many studies compare costs by comparing discounting functions, which is helpful, but 2) an often disregarded aspect of this is OC.
-(other frame: What we've learned is how increasing a given demand reduces the value of its associated reward, but less explored is the question about how people choose among them, specifically how people allocate their time to engage with demands).
-Even in tafc, a choice for a sooner or easier item can be a reflection of wanting to skip the offer altogether.
-Foraging provides a natural way to probe this.
-Foraging is often divided into two: patch and prey, and they are often experienced in daily life.
-Patch leaving can be deciding when to leave a job (diminishing gains).
-Prey can be X, or nerflix (show gif).
-
-So going back to our question of the cost and value of effort, maybe the distinction has something to do with the ways in which we can allocate time and effort (work on this, including how foraging can provide a reference point to evaluate the value-modulatory effects of demands, and maybe put it before foraging is explained?).
-
-  Modeling: mention that the rich history of foraging modeling can help us pinpoint a number of things, like the putative cost or attractiveness of a demand, whether preferences emerge from focal considerations of the value of a trial or a global estimate of what alternative way could be used to obtain rewards.
-Foraging and its modeling can provide a common framework to examine differences, rather than relying on matching disc functions.
 
@@
 Like, the aversion is due to focusing on different elements of the task.
-- I guess you can mention that the wait group acts as a baseline of foraging behavior.
-- Re-read Mikey's effort value paper to see if there is anything there that can allow us to transition into foraging.
-Like, are there elements that make cog effort valuable that are well encapsuled by foraging paradigms?
-- Pending questions: explain logistic coefficients in exponentiated form? (i.e. X% more/less likely than...)
 

### 2020-10-29 Cost_manuscript.Rmd
draft for Joe number 1

@@
 learned industriousness, Eisenberger, 1992).
-Though intuitively valid and empirically supported, this explanation leaves open questions about what intrinsic features of an effortful task can make it attractive outside of its associated outcome, and how contextual factors mold their perceived costs (see Inzlicht, Shenhav, and Olivola, 2018, for a review on the attractiveness of effort).
-Understanding these additional qualities could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
+Though intuitively valid and empirically supported, this explanation leaves open questions about what intrinsic features of an effortful task can make it attractive outside in its own right, and how contextual factors mold its perceived costs (Inzlicht, Shenhav, and Olivola, 2018).
+Understanding these qualities could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
 
   What is often missing from existing accounts is the common case of choosing among types of behavioral demands.
-Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14].
-Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16].
+Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior (Ainslie, 1975; Frederick et al., 2002; Kable and Glimcher, 2007; Kool et al., 2010; Westbrook, Kester, and Braver, 2013; Green, Fristoe, and Myerson, 1994).
+Although this line of work suggests that discounting functions are similar for delay and effort (Prevost et al., 2010; Massar et al., 2015; Seaman et al., 2018), there is ongoing debate about the shape of the discounting function across effort types (Arulpragasam et al., 2018; Prevost et al., 2010; Chong et al., 2016; Klein-Flugge et al., 2016; Kool and Botvinick, 2018), and discount rates do not always correlate across cost domains (Westbrook and Braver, 2013; Seaman et al., 2018).
 However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context (Kool & Botvinick, 2018).
@@
 Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionary choice behaviors (Hayden 2018; Mobbs, Trimmer, Blumstein, & Dayan, 2018), and offers a number of desirable qualities.
-First, it allows for the estimation of reward maximizing choice patterns based on the opportunity cost of time (Charnov, 1975; Kacelnik and Krebs, 1977), which people can readily approximate and persistently follow (Constantino and Daw, 2015 ADD).
-One can then interpret observed deviations in acceptance rates from such optimal behavior in addition to comparing them among demands.
+First, it allows for the estimation of optimal, reward maximizing choice patterns based on the opportunity cost of time (Charnov, 1975; Krebs et al., 1977).
+We can therefore interpret observed deviations in acceptance rates from such optimal behavior in addition to comparing them among demands.
 Second, the sequential nature of foraging allows individuals to emphasize different elements of the decision context.
 For example, the cost (or value) of effort or delay could globally depend on the availability of alternative demands (as suggested above), impacting the perceived opportunity cost of time.
-Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that adapt once individuals experience different forms of behavioral costs.
+Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that are adjusted once individuals experience different forms of behavioral costs.
 Foraging rests on an abundant modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
@@
 cognitive effort, physical effort, and delay).
-We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions.
+We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions (Inzlicht, Shenhav, and Olivola, 2018).
 First, the existence of a well-defined optimal choice strategy in foraging designs helped us identify when demands boost the value of rewards (i.e.
 overharvesting poor offers).
-Second, increasing the level of exposure to types of demands over two experiments allowed us to asses whether their cost was intrinsic or relative.
-Finally, confronting participants with both mental and physical effort let us probe whether these preferences were domain general or task-specific, and in the case of the latter, isolate factors that influence preferences beyond the often cited associative relationship between effort and outcome (e.g.
-features of an effortful task that makes it more attractive).
-
-  Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment, or whether they faced a single or intermixed demands.
-When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups underaccepted, partially matching our predictions and highlighting that cognitive effort can add value to outcomes.
+Second, increasing the level of exposure to types of demands across two experiments allowed us to asses whether their cost was intrinsic or relative.
+Finally, confronting participants with both mental and physical effort let us probe whether these preferences were domain general or task-specific, and in the case of the latter, isolate factors that influence preferences beyond the often-cited associative relationship between effort and outcome.
+
+  We found mixed support for our pre-registered hypotheses, which are detailed in https://osf.io/2rsgm/.
+Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment or whether they faced a single or intermixed demands.
+When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups under-accepted, partially matching our predictions and highlighting that cognitive effort can add value to outcomes.
 However, against our expectations, we found that a similar preference for cognitive effort disappeared over time as decision makers foraged for types of demands in addition to rewards.
-Computational modeling suggested that cognitive effort was valuable because it shortened the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (a detailed description of our preregistered hypotheses can be found on https://osf.io/2rsgm/).
-Our results expand our understanding of the attractiveness of effort, highlighting a role for features in the decision environment that are independent from a pure association between effort and reward, and point to characteristics that can be leveraged in order to motivate effort engagement in diverse everyday scenarios.
+Computational modeling suggested that cognitive effort was valuable because it shortened the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands.
+The shortened time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks).
+These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
 

### 2020-11-02 Cost_manuscript.Rmd
discussion par 1

@@
 ---
-title: Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment
-author: "Claudio Toro-Serey & Joseph T. McGuire"
-csl: apa.csl
-output:
-  pdf_document:
-    highlight: haddock
-    keep_tex: no
-  word_document: default #reference_docx: Style_reference_draft.docx
+title: Apparent preferences for cognitive effort fade when multiple forms of effort
+  and delay are interleaved in a foraging environment
+author: "Claudio Toro-Serey, Gary Kane, & Joseph T. McGuire"
 header-includes:
@@
   \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
-#bibliography: XXXX.bib
+output:
+  html_document:
+    df_print: paged
+  pdf_document:
+    highlight: haddock
+    keep_tex: no
+  word_document: default
+csl: apa.csl
 ---
@@
 These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
-
-####-------######
-
-  Clinical: Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
-Like, the aversion is due to focusing on different elements of the task.
 
@@
 
-  Understanding what drives the sporadic attractiveness of effortful avenues remains elusive.
-In this study, we...1) preferences for mental effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
+  Understanding what drives the sporadic attractiveness of effortful options remains elusive.
+In this study, we tested the hypothesis that such appeal could arise from being able to compare different means to achieve the same outcome.
+Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found 1) that preferences for mental effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
 
@@
 But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.
+- Clinical: Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
+Like, the aversion is due to focusing on different elements of the task.

### 2020-11-03 Cost_manuscript.Rmd
slight methods section restructuring

@@
 output:
-  html_document:
-    df_print: paged
   pdf_document:
@@
     keep_tex: no
-  word_document: default
+  word_document: #default
+    reference_docx: Style_reference_draft.docx
+  html_document:
+    df_print: paged
 csl: apa.csl
@@
 learned industriousness, Eisenberger, 1992).
-Though intuitively valid and empirically supported, this explanation leaves open questions about what intrinsic features of an effortful task can make it attractive outside in its own right, and how contextual factors mold its perceived costs (Inzlicht, Shenhav, and Olivola, 2018).
-Understanding these qualities could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
+Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs (Inzlicht, Shenhav, and Olivola, 2018).
+Understanding these intrinsic qualities could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
 
@@
 cognitive effort, physical effort, and delay).
+We explored this question in two foraging experiments: a between-subjects design in which participants foraged for rewards while performing a single demand, and a within-subjects extension that had individuals forage for demands in addition to rewards.
 We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions (Inzlicht, Shenhav, and Olivola, 2018).
-First, the existence of a well-defined optimal choice strategy in foraging designs helped us identify when demands boost the value of rewards (i.e.
+First, the existence of a well-defined optimal choice strategy helped us identify when demands boost the value of rewards (i.e.
 overharvesting poor offers).
-Second, increasing the level of exposure to types of demands across two experiments allowed us to asses whether their cost was intrinsic or relative.
-Finally, confronting participants with both mental and physical effort let us probe whether these preferences were domain general or task-specific, and in the case of the latter, isolate factors that influence preferences beyond the often-cited associative relationship between effort and outcome.
-
-  We found mixed support for our pre-registered hypotheses, which are detailed in https://osf.io/2rsgm/.
+Second, increasing the level of exposure to types of demands allowed us to asses whether their cost was intrinsic or relative.
+Finally, confronting participants with both mental and physical effort let us probe whether these preferences were domain general or task-specific, and in the case of the latter, isolate factors that influenced preferences beyond the often-cited associative relationship between effort and outcome.
+
+  Our results provided mixed support for our pre-registered hypotheses, which are detailed in https://osf.io/2rsgm/.
 Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment or whether they faced a single or intermixed demands.
@@
 Computational modeling suggested that cognitive effort was valuable because it shortened the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands.
-The shortened time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks).
+The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks).
 These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
@@
 
-  All experimental tasks were implemented using PsychoPy 2 (v1.85.1, CITE) on a Macbook Pro laptop.
+  All experimental tasks were implemented using PsychoPy 2 (v1.85.1, Pierce2019) on a Macbook Pro laptop.
 In this task, participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay (Figure 1).
@@
 Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive tasks of each kind.
-If participants failed to maintain above-threshold gripping or made two mistakes during the cognitive task, they were forced to travel and missed the reward.
+While in the handling time, if participants failed to maintain above-threshold gripping or made two mistakes during the cognitive task, they were forced to travel and missed the reward.
 
@@
 Timing information was disclosed at the beginning of each block, and rewards displayed during a 2 s offer window before each trial began.
-Participants received training prior to the experimental session, and were told about all possible environmental statistics in order to preclude experience-dependent learning.
+Participants received training prior to the experimental session, and were told about all possible environmental statistics in order to preclude biases due to experience-dependent learning (Dundon2020; Garrett2020).
 
@@
 
-  Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment (Stephens and Krebs, 1977).
+  Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment (Stephens2019).
 In this study, the richness of the environment was manipulated by the length of the handling and travel times, where shorter travel times produced richer environments.
@@
 
-$\dfrac {\sum p_i R_i} {\sum p_i H_i + 3T},p \in \{0, 1\}$
-
-  where *R*, *H*, and *p* are the reward, handling time, and acceptance probability of offer i, respectively, and T is the travel time.
+$\dfrac {\sum p_i R_i} {\sum p_i H + 3T},p \in \{0, 1\}$
+
+  where *R* and *p* are the reward, and acceptance probability of offer i, respectively, *H* is the handling time for the block, and *T* its associated travel time.
 This gave us the total reward per second attainable in each block as a function of the acceptance threshold (i.e.
@@
 
-  All analyses were performed in R 3.5.2 (CITE).
+  All analyses were performed in R 3.5.2 (RTeam2018).
 First we tested whether decision makers integrated delay and reward information.
-To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a mixed-effects logistic regression to predict trial-wise acceptances, using a random intercept to account for biases in participant behavior.
+To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a mixed-effects logistic regression to predict trial-wise acceptances (using the lme4 package, Bates2015), giving a random intercept to each subject to account for biases in participant behavior.
 We included regressors for handling time and reward, as well as two covariates that probed the influence of recent history on choices.
@@
 A significant quadratic coefficient thus would signal that the task statistics operated as expected.
-Next, to determine the optimality of each group’s decisions, we performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cocitst).
-This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR, CITE Y&..).
+Next, to determine the optimality of each group’s decisions, we performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost).
+This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR, Benjamini2001).
 
@@
 
-  In order to further look at the effect of handling, offer, and cost type, we computed the probability of accepting a trial with a mixed-effects logistic regression, using the lme4 package (CITE).
-Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and participant ID as a random intercept.
+  In order to further look at the effect of handling, offer, and cost type, we computed the probability of accepting a trial with a mixed-effects logistic regression.
+Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and a random intercept per subject.
 Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition.
 We ran three versions of the model with different reference conditions, in order to test all pairwise differences among the four cost conditions.
-(**exponentiate coefficients to make them more interpretable?**) We then examined whether this a priori model outperformed both simpler and more complex models.
+We then examined whether this a priori model outperformed both simpler and more complex models.
 We used both AIC and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
@@
 
-  Before modeling each individual's overarching subjective OC, we examined whether participants were consistent and stable in their choices.
+  Next, we examined whether participants were consistent and stable in their choices.
 For consistency, we visually examined survival curves indicating at what point during the handling time participants quit a trial (censored points included trial completions and forced travels), in addition to quitting time distributions.
-Stability was assessed by computing each participant’s total proportion of acceptances pre- and post-midpoint for every block, comparing the mean proportion of acceptances using paired permutations (5000 iterations).
-We then tested whether the relative differences in costs observed using data from the whole experimental session were still present on each half of the experiment.
-The winning model from the mixed-effects logistic comparison was applied to each half separately.
+We interrogated stability by computing each participant’s total proportion of acceptances pre- and post-midpoint for every block type, comparing the mean proportion of acceptances using paired permutations (5000 iterations).
+We then tested whether the observed differences in costs were still present on each half of the experiment by applying winning model from the mixed-effects logistic comparison to each half separately.
 In each case, the reference cost category was rotated in order to assess pairwise differences among all costs.
 We evaluated the consistency of the relative costs by visually comparing the patterns of significant differences between experimental halves.
-
-  Finally, we fitted the subjective OC of each type of demand (see Operationalization of Cost).
-OC was computed as the product of a free parameter (gamma) and the handling time.
-Gamma can be interpreted as the subjective value of each second spent in an environment.
-If a trial's reward rate (i.e.
-offer amount divided by the handling time) fell below gamma, a participant was better off finding more profitable alternatives.
-In other words, individuals with higher gammas required higher rewards in order to accept a given offer.
-We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type
-
-$P(accept)_i = \dfrac {1} {1 + e^{-\beta(R_i - \gamma H_i)}}$
-
-  Both gamma ($\gamma$) and the inverse temperature parameter ($\beta$) of the softmax function were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE **or grid search?**).
-The gamma optimization search space was bound by extreme choice values.
-For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
-Conversely, a participant experiencing low opportunity costs would accept the non-beneficial offer of 4 cents for a 14 second delay (or 4/14).
-We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.
-We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (0.74, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
-Finally, we determined which cost type produced the highest discounting by comparing gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
 
@@
 Timing parameters were matched to the middle condition from Experiment 1 (i.e.
-10 s handling and 6 s travel), allowing a balance between acquiring enough observations per trial type and being able to compare results across experiments.
+10 s handling and 6 s travel), establishing a balance between acquiring enough observations per trial type and being able to compare results across experiments.
 Participants were informed that this timing combination would be constant prior to beginning the experiment.
@@
 
-  To compare acceptance rates among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
+  To compare acceptances among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
 The model included cost condition and reward amount as fixed main effects, and participant ID as a random intercept (handling time is not modeled, as participants experienced a single time combination).
@@
 
-  Next we probed the confidence and consistency with which participants made choices.
-First, we qualitatively assessed the number of quits performed during during the handling time through a survival curve, and plotted the quit response time distribution as a function of block to examine choice confidence over time.
+  Next we probed consistency and stability in people's choices.
+First, we qualitatively assessed the number of quits performed during during the handling time through a survival curve, and plotted the quit response time distribution as a function of block to examine choice consistency over time.
 Next, we computed the proportion of quits that were performed during the choice window versus during the handling time.
@@
 
-  **old** To estimate the subjective opportunity cost of each condition, we used a logistic function to model each participant’s probability of accepting a trial based on the difference between the delayed reward’s magnitude and the estimated opportunity cost (OC) for each cost type.
-As before, OC was computed as the product of a free parameter (gamma) and the handling time.
-Both gamma and the temperature parameter of the logistic function were estimated at the subject level, independently for each subject and cost type.
-We cross-validated each subject’s OC value using the first four blocks (two cognitive, two physical) for estimation, and the last two blocks (one of each effort type) choices for testing.
-The estimates were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each cost type.
-The OC estimates for each group were compared using a repeated measures ANOVA with cost as a factor.
-We performed pairwise paired permutations as post-hoc tests.
-
-**new** The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above.
+### **Computational Modeling of Foraging Behavior**
+
+  We begun the modeling approach by fitting a fixed subjective OC for each type of demand (see Operationalization of Cost), which acted as a base model.
+OC was computed as the product of a free parameter (gamma) and the handling time.
+Gamma can be interpreted as the subjective value of each second spent in an environment.
+If a trial's reward rate (i.e.
+offer amount divided by the handling time) fell below gamma, a participant was better off finding more profitable alternatives.
+In other words, individuals with higher gammas required higher rewards in order to accept a given offer.
+We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type
+
+$P(accept)_i = \dfrac {1} {1 + e^{-1/\beta(R_i - \gamma H_i)}}$
+
+  Both gamma ($\gamma$) and the temperature parameter ($\beta$) of the softmax function were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE **GARY INFO**).
+The gamma optimization search space was bound by extreme choice values.
+For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
+Conversely, a participant experiencing low opportunity costs would accept the non-beneficial offer of 4 cents for a 14 second delay (or 4/14).
+We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.
+We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (**0.74**, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
+Finally, we determined which cost type produced the highest discounting by comparing gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
+
+  The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above.
 Based on the results across experiments, an adequate model of behavior should meet X criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) persistently higher acceptances for cognitive effort when faced with single behavioral costs; 3) slight reduction of acceptances in effortful conditions (**fatigue?**); 4) an initial preference for cognitive effort trials when foraging for costs and rewards 5) this preference disappears as acceptances decreased to a common rate across costs; 6) participants kept track of recent offer history; 7) effects were robust to block order effects.
@@
 Comparing likelihood fits among lengths of offer history (e.g.
-sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r AIC(historySize_btw[[historyIndex]])`), which matched the offer presentation rotation (see Methods).
+sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r round(AIC(historySize_btw[[historyIndex_btw]]), digits = 2)`), which matched the offer presentation rotation (see Methods).
 These results confirm the expected influence of time and offer magnitude on choice behavior, but also suggest that participants adapted to their recent experience.
@@
   These findings provide a first glimpe at differences in cost, showing that individuals in the wait condition accepted the least and earned the most.
-Moreover, they suggest that costs associated with cognitive effort can boost the value of an offer instead, even when accepting it negatively impacts total earnings.
+Moreover, they suggest that costs associated with cognitive effort can boost the value of an offer instead, as reflected by higher acceptances at the expense of earnings.
 
@@
 
-  Understanding what drives the sporadic attractiveness of effortful options remains elusive.
+  Understanding the sporadic attractiveness of effortful options remains elusive.
 In this study, we tested the hypothesis that such appeal could arise from being able to compare different means to achieve the same outcome.
-Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found 1) that preferences for mental effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
+Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that 1) preferences for cognitive effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
 

### 2020-11-03 Cost_manuscript.Rmd
restructuring modeling approach

@@
 
-  We begun the modeling approach by fitting a fixed subjective OC for each type of demand (see Operationalization of Cost), which acted as a base model.
+  We performed model comparisons to identify qualities that transcended both experiments.
+An adequate model should meet seven criteria derived from the observed choice behavior: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 4) initially match this preference for cognitive effort trials when foraging for demands and rewards; 5) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects.
+These conditions discarded a number of popular explanatory candidates, including....
+(wikenheiser, C&D, Fawcett...).
+We therefore did not include these models into our comparison.
+
+  We started by fitting a base model, in which a subjective OC was fit for each type of demand (see Operationalization of Cost).
 OC was computed as the product of a free parameter (gamma) and the handling time.
@@
 Finally, we determined which cost type produced the highest discounting by comparing gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
-
-  The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above.
-Based on the results across experiments, an adequate model of behavior should meet X criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) persistently higher acceptances for cognitive effort when faced with single behavioral costs; 3) slight reduction of acceptances in effortful conditions (**fatigue?**); 4) an initial preference for cognitive effort trials when foraging for costs and rewards 5) this preference disappears as acceptances decreased to a common rate across costs; 6) participants kept track of recent offer history; 7) effects were robust to block order effects.
-Alternative foraging models from the literature were not fitted, as they did not qualitatively meet these criteria (wikenheiser, C&D, Fawcett...)
 

### 2020-11-04 Cost_manuscript.Rmd
added eqs

@@
 
-  We performed model comparisons to identify qualities that transcended both experiments.
-An adequate model should meet seven criteria derived from the observed choice behavior: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 4) initially match this preference for cognitive effort trials when foraging for demands and rewards; 5) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects.
-These conditions discarded a number of popular explanatory candidates, including....
-(wikenheiser, C&D, Fawcett...).
-We therefore did not include these models into our comparison.
-
-  We started by fitting a base model, in which a subjective OC was fit for each type of demand (see Operationalization of Cost).
+  We performed model comparisons to identify qualities that explained both experiments.
+Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects.
+These conditions discarded a number of popular explanatory candidates.
+For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic, while differences between effort types rule out learned industriousness.
+Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (CITE).
+Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
+We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
+
+  (variability from Hayden could help..)
+
+  We started by fitting a base model in which a subjective OC was fit for each type of demand (see Operationalization of Cost).
 OC was computed as the product of a free parameter (gamma) and the handling time.
@@
 
-DIFFICULT TO MODEL: ALL COST ACCEPTANCES DECREASE AT LEAST A BIT.
-LEARNING SUBJECTIVE TIME DOESN'T DO THAT.
-IN FACT, IT STILL SEEMS AS IF THE EFFORT FATIGUE SEEN ON EXP 1 HAPPENS AGAIN, AND ALL COSTS DEFAULT TO THE COSTLIEST.
-THAT DOESN'T INVOLVE TIME NECESSARILY.
+$\gamma_{i+1} = (1 - (1 - \alpha) ^ {\tau_i}) \dfrac{R_{i} A_{i}}{\tau_i} +  (1 - \alpha) ^ {\tau_i} \gamma_{i}$
+
+$s_{i + 1} = s_i + A_i \left (\frac{1}{i}[S_i - s_i] \right)$
+
+$w_i = \left (\frac{i}{max(i)} \right ) ^\alpha$
+
+$mS_i = (s_i w_i) + (S_i (1 - w_i))$
+
+$\tau_{i} = H_{i} ^ {mS_{i}}  A_{i} + T_{i}$
+
+$P(A)_i = \dfrac{1}{1 + exp^{-(1 / \beta[R_i - \gamma_i H_i^{mS_i}])}}$
 

### 2020-11-04 Cost_manuscript.Rmd
rworking results now

@@
 
+  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) chose their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.
+Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time).
+We hypothesized 1) that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that 2) participants confronted with effortful demands would be more likely to accept trials than those faced with passive delay, regardless of handling time and reward amount.
+
+  We performed a mixed effects logistic regression to address the first hypothesis.
+Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
+Larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_btw["Offer", "Estimate"]`, SE = `r historyCoeffs_btw["Offer", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_btw["Offer", "Pr(>|z|)"])`), whereas longer delays decreased them ($\beta$ = `r historyCoeffs_btw["Handling", "Estimate"]`, SE = `r historyCoeffs_btw["Handling", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_btw["Handling", "Pr(>|z|)"])`), in line with predictions.
+Two additional regressors showed that having missed out on consecutive rewards decreased the probability of acceptance ($\beta$ = `r historyCoeffs_btw["recentTravels", "Estimate"]`, SE = `r historyCoeffs_btw["recentTravels", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_btw["recentOffers", "Pr(>|z|)"])`), and that participants became more selective when recent offer history was richer ($\beta$ = `r historyCoeffs_btw["recentOffers", "Estimate"]`, SE = `r historyCoeffs_btw["recentOffers", "Std.
+Error"]`, *p* `r report_p(historyCoeffs_btw["recentOffers", "Pr(>|z|)"])`).
+The reduction in acceptances from recent misses was driven by the wait group (removing this group from the model yielded a *p* > 0.1), likely because this group accepted the least amount of offers.
+Comparing likelihood fits among lengths of offer history (e.g.
+sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r round(AIC(historySize_btw[[historyIndex_btw]]), digits = 2)`), which matched the offer presentation rotation (see Methods).
+
+### **Between-subjects: Comparisons among the four delay and effort conditions**
+
 ``` {r BTW: 16.1.4. Optimality (move to acceptance comparison eventually), echo = FALSE}
@@
 
-  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) chose their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.
-Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time).
-We hypothesized that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that changing the cost required to obtain rewards would uniformly increase or decrease this choice pattern.
-Specifically, we predicted that participants confronted with effortful demands would be more likely to accept trials than those faced with passive delay, regardless of handling time and reward amount.
-
-  We performed a mixed effects logistic regression to address the first hypothesis.
-Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
-Larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_btw["Offer", "Estimate"]`, SE = `r historyCoeffs_btw["Offer", "Std.
-Error"]`, *p* `r report_p(historyCoeffs_btw["Offer", "Pr(>|z|)"])`), whereas longer delays decreased them ($\beta$ = `r historyCoeffs_btw["Handling", "Estimate"]`, SE = `r historyCoeffs_btw["Handling", "Std.
-Error"]`, *p* `r report_p(historyCoeffs_btw["Handling", "Pr(>|z|)"])`), in line with predictions.
-Two additional regressors showed that having missed out on consecutive rewards decreased the probability of acceptance ($\beta$ = `r historyCoeffs_btw["recentTravels", "Estimate"]`, SE = `r historyCoeffs_btw["recentTravels", "Std.
-Error"]`, *p* `r report_p(historyCoeffs_btw["recentOffers", "Pr(>|z|)"])`), and that participants became more selective when recent offer history was richer ($\beta$ = `r historyCoeffs_btw["recentOffers", "Estimate"]`, SE = `r historyCoeffs_btw["recentOffers", "Std.
-Error"]`, *p* `r report_p(historyCoeffs_btw["recentOffers", "Pr(>|z|)"])`).
-The reduction in acceptances from recent misses was driven by the wait group (removing this group from the model yielded a *p* > 0.1), likely because this group accepted the least amount of offers.
-Comparing likelihood fits among lengths of offer history (e.g.
-sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r round(AIC(historySize_btw[[historyIndex_btw]]), digits = 2)`), which matched the offer presentation rotation (see Methods).
-These results confirm the expected influence of time and offer magnitude on choice behavior, but also suggest that participants adapted to their recent experience.
-
-  **Maybe put this as an addendum to the mixed effects analysis of proportion of acceptances, after mixed models** .
-The foraging task was configured so that there was an optimal, reward-maximizing strategy (see Operationalization of Cost in Methods).
-Because of this, participants were told to consider their strategies carefully, as accepting everything would not maximize their gains.
-Figure 3 (right) shows that participants who over- or under-accepted earned the least (general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
-Two-sided, one-sample t-tests against the optimal proportion of acceptances (i.e.
-$\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)`% of combinations (*p* < 0.05, FDR corrected), with the percentage of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`%, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`%, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`%, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`%).
-Together, these results suggest that participants were adequately influenced by the rewarding statistics of the environment, even though they did not always perform optimally.
-
-### **Between-subjects: Comparisons among the four delay and effort conditions**
-
 ``` {r BTW: 16.2.1. Overall Proportion/Earnings, fig.align = "center", fig.width = 8, fig.height = 4, echo = FALSE}  
@@
 The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants (and 0 for either physical or easy conditions), making performance an unlikely explanation for the observed differences in choice.
-
-  We repeated these pairwise permutations to identify differences in earnings.
-In line with the earnings results from the previous section, the additional acceptances produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
+The higher acceptance rates produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
 In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
 
-  These findings provide a first glimpe at differences in cost, showing that individuals in the wait condition accepted the least and earned the most.
-Moreover, they suggest that costs associated with cognitive effort can boost the value of an offer instead, as reflected by higher acceptances at the expense of earnings.
+  We next examined the optimality of these decisions.
+The foraging task was configured so that there was a single reward-maximizing strategy per block type (see Operationalization of Cost in Methods), and participants were warned that accepting everything would not maximize their gains.
+Accordingly, participants who over- or under-accepted earned the least (Figure 3, right; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+Two-sided, one-sample t-tests against the optimal proportion of acceptances (i.e.
+$\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)`% of combinations (*p* < 0.05, FDR corrected), with the percentage of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`%, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`%, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`%, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`%).
+Together, these findings show that even though participants did not always perform optimally, they adequately integrated the statistics of the environment as they tracked their recent experience.
+Further, they suggest that cognitive effort can boost the value of an offer, as reflected by higher acceptances at the expense of earnings.
 
@@
 
-  However, our hypothesis stated that differences in cost would be uniform across handling times and rewards.
-We therefore distilled the previous analysis to examine choice behavior for every combination of experimental parameters.
+  We next probed whether these results held uniformly across all parameter combinations.
 Figure 4A shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and cost, with optimal acceptance rates depicted by the gray circles.
@@
 This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
-
-  In order to test these qualitative observations, we computed the probability of accepting a trial with a mixed-effects logistic regression (see Methods for details).
-As predicted, and confirming previous results, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Handling", "Std.
+We tested these observations with a mixed-effects logistic regression, computing the probability of accepting an offer as a function of handling time, reward amount, and demand type (see Methods for details).
+As before, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Handling", "Std.
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Offer", "Std.
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`).
-In order to show the comparisons among all conditions, Figure 4B portrays the coefficients (color scale), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
+Comparisons among all conditions are shown on Figure 4B, which portrays the coefficients (color scale), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
 The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) and wait groups ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.
 
-  We next examined whether choice behavior could be better explained by environmental statistics alone, or if cost conditions changed the way handling time and offer amount interacted to influence choices.
+  These observations could not be better explained by simpler or more complex regression models.
 Figure 4C shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details).
@@
 
-### **Between-subjects: Modeling the subjective opportunity cost in each condition**
+### **Between-subjects: Consistency and stability**
 
@@
 
-  Before computationally modeling behavior, we asked whether foragers had a stable representation of their environment.
+  We next tested the hypothesis that foragers would display consistent and stable choices.
 Since participants had complete a priori knowledge of the statistics of each environment, and were unaware of any other cost groups that could modulate the subjective cost of their assigned demand, we expected them to 1) show confidence in their choices by not quitting mid-handling time; and 2) adopt the same strategy while re-experiencing each environment.

### 2020-11-05 Cost_manuscript.Rmd
separated stability and modeling sections
new consistency and stability exp 1

@@
 
-  We next tested the hypothesis that foragers would display consistent and stable choices.
-Since participants had complete a priori knowledge of the statistics of each environment, and were unaware of any other cost groups that could modulate the subjective cost of their assigned demand, we expected them to 1) show confidence in their choices by not quitting mid-handling time; and 2) adopt the same strategy while re-experiencing each environment.
-We investigated the first prediction by plotting a survival curve of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
-This qualitative analysis shows that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
+  Next, we tested the hypothesis that foragers would display consistent and stable choices.
+Participants were deemed consistent if they did not quit during the handling time.
+To examine this, we plotted survival curves of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
+These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
 Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
@@
 
-  We tested the second prediction (i.e.
-strategy stability) by comparing acceptances rates throughout the experiment.
-The scatter plot on Figure 5 (bottom-left) shows the overall proportion accepted by each participant before and after the mid-point break (colored dashed lines indicate the mean for that group).
-Paired permutations showed no acceptance rate differences for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
-The decline in acceptances appeared to be gradual for the cognitive group, but not for the physical group (Figure 5, bottom-right).
-An explanation for these results is that these conditions became costlier due to fatigue, thus providing evidence that our cognitive and physical manipulations were effortful.
-
-  It is possible that this reduction in acceptances affected the relative differences among conditions.
-We addressed this possibility by examining pre-post acceptance rates for each handling time and reward combination.
-Figure 6 (left) shows the proportion of acceptances for each offer combination, with each half depicted on each column.
-This collage suggests that changes in choice behavior for effortful groups were mostly driven by the longest handling time, in in line with reports where value is discounted as the length of the required effort increases (Treadway et al, 2009).
-Regardless, the relative differences in acceptances among cost groups remain mostly untouched.
-We tested this observation by repeating the winning mixed-effects model from the previous section (i.e.
-all main effects) on each experimental half separately.
-We replicated the matrix of coefficients from the previous section (Figure 6, right), with each half mirrored along the diagonal (i.e.
-the top triangle shows the coefficients for the second half of the experiment).
-Together, these results suggest that decision makers had a strong representation of the environment by showing that 1) participants were confident in their choices and strategies; 2) cognitive and physical costs produced the expected fatigue from exerting effort; and 3) despite the resulting reduction of acceptances, the relative cost of each condition was consistent throughout the experiment.
+  Stability was defined as a persistence in acceptance patterns throughout the experimental session.
+The scatter plot on Figure 5 (bottom-left) shows the overall proportion accepted by each participant before and after the mid-point break.
+Paired permutations showed no differences in acceptances for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
+Figure 6 (left) shows that changes in choice behavior for effortful groups were mostly driven by the longest handling time, in in line with reports where value is discounted as the length of the required effort increases (Treadway et al, 2009).
+We replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Figure 6, right).
+Together, the consistency and stability displayed by participants suggest that decision makers had a clear representation of the environment.
 
@@
 ```
-
-``` {r BTW: 16.3.3. OC modeling, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-## fit the OC model
-summaryOC <- list()
-summaryOC$all <- dataBtw %>%
-                 group_by(Cost, SubjID) %>%
-                 do(optimizeOCModel(., simplify = T)) %>%
-                 ungroup()
-
-## plot
-summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
-  # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
-  # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
-  # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-  geom_hline(yintercept = 0.74, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
-  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
-  geom_boxplot(show.legend = F) +
-  geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
-  ylim(0,1.5) +
-  labs(x = "") +
-  scale_fill_manual(values = colsBtw) +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        axis.line = element_line(colour = "black"),
-        text = element_text(size = 16))
-
-## one sample t against optimal strategy
-summaryOC$t.test <- summaryOC$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  sapply(., function(data) {t.test(data$Gamma, mu = 0.74)})
-
-## descriptive stats
-summaryOC$descriptives <- summaryOC$all %>%
-  group_by(Cost) %>%
-  summarise(mGamma = round(mean(Gamma), digits = 2),
-            sdGamma = round(sd(Gamma), digits = 2))
-
-# summaryOC$all %>%
-#   ggplot(aes(Gamma, percentAccept, fill = Cost, size = temperature)) +
-#   geom_point(pch = 21)
-
-# # gamma parameter recovery tests
-# # test a single subject against their own choices
-# (subj <- sample(subjList_btw, 1))
-# subjData <- dataBtw %>% 
-#   filter(SubjID == subj) %>% 
-#   group_by(Cost, Handling, Offer) %>% 
-#   summarise(propAccept = mean(Choice)) %>%
-#   ungroup()
-# 
-# params <- filter(summaryOC$all, SubjID == subj) %>% 
-#   select(Gamma, temperature)
-# 
-# test_params(params,
-#             model = expr(params$Gamma * Handling), 
-#             subjData, 
-#             plot = T)
-
-# # test multiple values of gamma and plot the comparison
-# lowGamma <- 0
-# upperGamma <- 1.7
-# nGamma <- 6
-# testys <- lapply(seq(lowGamma, upperGamma, length.out = nGamma), test_params)
-# (testys <- do.call(rbind, testys))
-# testys %>%
-#   ggplot(aes(interaction(Offer, Handling), Choice, color = Gamma)) +
-#   geom_point(size = 3) +
-#   geom_line(aes(group = interaction(Handling, Gamma)), size = 1) +
-#   labs(x = "Offer.Handling", y = "Proportion Accepted") +
-#   facet_wrap(vars(Gamma), ncol = 2) +
-#   theme(legend.key = element_blank(),
-#         panel.grid.major = element_blank(),
-#         panel.grid.minor = element_blank(),
-#         panel.background = element_blank(),
-#         axis.line = element_line(colour = "black"),
-#         text = element_text(size = 16))
-
-```
-
-``` {r BTW: 16.3.5. OC comparisons, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# ANOVA
-OCanova <- list()
-OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC$all))
-Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
-Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
-Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
-
-# Post-hoc pairwise tests
-OCanova$perms <- summaryOC$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  do.call(cbind, .) %>%
-  select_if(is.numeric) %>%
-  rename(Physical = Physical.Gamma,
-         Cognitive = Cognitive.Gamma,
-         Wait = Wait.Gamma,
-         Easy = Easy.Gamma) %>%
-  outer(., ., FUN = Vectorize(permute), simple = T)
-diag(OCanova$perms) <- 1
-
-OCanova$ES <- summaryOC$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  do.call(cbind, .) %>%
-  select_if(is.numeric) %>%
-  rename(Physical = Physical.Gamma,
-         Cognitive = Cognitive.Gamma,
-         Wait = Wait.Gamma,
-         Easy = Easy.Gamma) %>%
-  outer(., ., FUN = Vectorize(cohenD)) %>%
-  abs()
-```
-
-``` {r BTW: 16.3.5. corrplot, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
-# # plot all pairwise comparisons
-# corrplot(OCanova$ES,
-#          is.corr = F, 
-#          p.mat = OCanova$perms,
-#          type = "upper",
-#          insig = "p-value",
-#          sig.level = -1,
-#          na.label = "square",
-#          na.label.col = "grey",
-#          method = "color", 
-#          tl.col = "black", 
-#          tl.cex = 0.8,
-#          outline = T)
-```
-
-``` {r BTW: 16.3.4. OC cross-validation, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# Compute the OC for pre-midpoint
-summaryOC$pre <- dataBtw %>%
-                 filter(Half == "Half_1") %>%
-                 group_by(Cost, SubjID) %>%
-                 do(optimizeOCModel(., simplify = T)) %>%
-                 ungroup() %>%
-                 select(SubjID, Gamma)
-
-# let's add the gammas to the second half data and estimate prop predicted on the second half
-summaryOC$predicted <- dataBtw %>%
-                 filter(Half == "Half_2") %>%
-                 group_by(Cost, SubjID) %>%
-                 left_join(summaryOC$pre, by = "SubjID") %>%
-                 mutate(OC = Handling * Gamma,
-                        predicted = Offer > OC) %>% 
-                 summarise(percentPredicted = mean(predicted == Choice) * 100) %>%
-                 group_by(Cost) %>%
-                 summarise(mPredicted = round(mean(percentPredicted), digits = 2),
-                           sdPredicted = round(sd(percentPredicted), digits = 2))
-
-# # plot
-# (summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
-#                             labs(x = "") +
-#                             geom_boxplot(show.legend = F) +
-#                             scale_fill_manual(values = colsBtw) +
-#                             labs(y = "Percent Predicted") +
-#                             ylim(0,100) +
-#                             theme(panel.grid.major = element_blank(),
-#                             panel.grid.minor = element_blank(),
-#                             panel.background = element_blank(),
-#                             axis.line = element_line(colour = "black"),
-#                             text = element_text(size = 16)))
-
-```
-
-  We then proceeded to estimate subjective OCs for each participant, which was produced by multiplying the handling time and a free parameter gamma (see Methods for details).
-Gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
-For example, the aversion produced by a given cost could prompt participants to spend their time and effort in the most profitable offers, resulting in high gamma values.
-Conversely, low gamma values represented low selectivity when evaluating offers.
-The model predicted the probability of a choice by comparing the estimated OC against each offer amount, and was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
-This single parameter model was able to explain a considerable degree of choice variance per individual (R-squared: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
-The distribution of gamma values is shown on Figure 7, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
-Values higher than this baseline imply that a condition was costly, whereas lower values suggest that a condition boosted the value of an offer.
-Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
-Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
-An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, R-squared = `r Rsquared_aov`).
-Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
-In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
-Finally, we cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
-
-```{r Gamma per cost group (Fig.
-7), fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
-The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
-Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
-
-summaryOC$plot
-
-```
-
-  Together, these findings suggest that 1) foraging paradigms can provide a reference point to evaluate how different demands modulate value; 2) a simple OC model can approximate people's behavior in such single-option, take it or leave it choices; and 3) when foraging in environments of equivalent richness, cognifitvely effortful demands can increase the attractiveness of offers rather than discount them (unlike other forms of cost).
-In the next experiment we explored whether this apparent value was inherent or malleable.
 
@@
 
+### **Computational modeling of foraging behavior**
+
+``` {r BTW: 16.3.3. OC modeling, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+## fit the OC model
+summaryOC <- list()
+summaryOC$all <- dataBtw %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup()
+
+## plot
+summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+  # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
+  # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
+  # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
+  geom_hline(yintercept = 0.74, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
+  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
+  geom_boxplot(show.legend = F) +
+  geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
+  ylim(0,1.5) +
+  labs(x = "") +
+  scale_fill_manual(values = colsBtw) +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 16))
+
+## one sample t against optimal strategy
+summaryOC$t.test <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  sapply(., function(data) {t.test(data$Gamma, mu = 0.74)})
+
+## descriptive stats
+summaryOC$descriptives <- summaryOC$all %>%
+  group_by(Cost) %>%
+  summarise(mGamma = round(mean(Gamma), digits = 2),
+            sdGamma = round(sd(Gamma), digits = 2))
+
+# summaryOC$all %>%
+#   ggplot(aes(Gamma, percentAccept, fill = Cost, size = temperature)) +
+#   geom_point(pch = 21)
+
+# # gamma parameter recovery tests
+# # test a single subject against their own choices
+# (subj <- sample(subjList_btw, 1))
+# subjData <- dataBtw %>% 
+#   filter(SubjID == subj) %>% 
+#   group_by(Cost, Handling, Offer) %>% 
+#   summarise(propAccept = mean(Choice)) %>%
+#   ungroup()
+# 
+# params <- filter(summaryOC$all, SubjID == subj) %>% 
+#   select(Gamma, temperature)
+# 
+# test_params(params,
+#             model = expr(params$Gamma * Handling), 
+#             subjData, 
+#             plot = T)
+
+# # test multiple values of gamma and plot the comparison
+# lowGamma <- 0
+# upperGamma <- 1.7
+# nGamma <- 6
+# testys <- lapply(seq(lowGamma, upperGamma, length.out = nGamma), test_params)
+# (testys <- do.call(rbind, testys))
+# testys %>%
+#   ggplot(aes(interaction(Offer, Handling), Choice, color = Gamma)) +
+#   geom_point(size = 3) +
+#   geom_line(aes(group = interaction(Handling, Gamma)), size = 1) +
+#   labs(x = "Offer.Handling", y = "Proportion Accepted") +
+#   facet_wrap(vars(Gamma), ncol = 2) +
+#   theme(legend.key = element_blank(),
+#         panel.grid.major = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.background = element_blank(),
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 16))
+
+```
+
+``` {r BTW: 16.3.5. OC comparisons, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# ANOVA
+OCanova <- list()
+OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC$all))
+Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
+Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
+Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
+
+# Post-hoc pairwise tests
+OCanova$perms <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(permute), simple = T)
+diag(OCanova$perms) <- 1
+
+OCanova$ES <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(cohenD)) %>%
+  abs()
+```
+
+``` {r BTW: 16.3.5. corrplot, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
+# # plot all pairwise comparisons
+# corrplot(OCanova$ES,
+#          is.corr = F, 
+#          p.mat = OCanova$perms,
+#          type = "upper",
+#          insig = "p-value",
+#          sig.level = -1,
+#          na.label = "square",
+#          na.label.col = "grey",
+#          method = "color", 
+#          tl.col = "black", 
+#          tl.cex = 0.8,
+#          outline = T)
+```
+
+``` {r BTW: 16.3.4. OC cross-validation, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# Compute the OC for pre-midpoint
+summaryOC$pre <- dataBtw %>%
+                 filter(Half == "Half_1") %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup() %>%
+                 select(SubjID, Gamma)
+
+# let's add the gammas to the second half data and estimate prop predicted on the second half
+summaryOC$predicted <- dataBtw %>%
+                 filter(Half == "Half_2") %>%
+                 group_by(Cost, SubjID) %>%
+                 left_join(summaryOC$pre, by = "SubjID") %>%
+                 mutate(OC = Handling * Gamma,
+                        predicted = Offer > OC) %>% 
+                 summarise(percentPredicted = mean(predicted == Choice) * 100) %>%
+                 group_by(Cost) %>%
+                 summarise(mPredicted = round(mean(percentPredicted), digits = 2),
+                           sdPredicted = round(sd(percentPredicted), digits = 2))
+
+# # plot
+# (summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
+#                             labs(x = "") +
+#                             geom_boxplot(show.legend = F) +
+#                             scale_fill_manual(values = colsBtw) +
+#                             labs(y = "Percent Predicted") +
+#                             ylim(0,100) +
+#                             theme(panel.grid.major = element_blank(),
+#                             panel.grid.minor = element_blank(),
+#                             panel.background = element_blank(),
+#                             axis.line = element_line(colour = "black"),
+#                             text = element_text(size = 16)))
+
+```
+
+  We then proceeded to estimate subjective OCs for each participant, which was produced by multiplying the handling time and a free parameter gamma (see Methods for details).
+Gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+For example, the aversion produced by a given cost could prompt participants to spend their time and effort in the most profitable offers, resulting in high gamma values.
+Conversely, low gamma values represented low selectivity when evaluating offers.
+The model predicted the probability of a choice by comparing the estimated OC against each offer amount, and was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
+This single parameter model was able to explain a considerable degree of choice variance per individual (R-squared: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
+The distribution of gamma values is shown on Figure 7, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
+Values higher than this baseline imply that a condition was costly, whereas lower values suggest that a condition boosted the value of an offer.
+Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
+Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
+An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, R-squared = `r Rsquared_aov`).
+Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
+In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
+Finally, we cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+
+```{r Gamma per cost group (Fig.
+7), fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
+The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
+Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
+
+summaryOC$plot
+
+```
+
+  Together, these findings suggest that 1) foraging paradigms can provide a reference point to evaluate how different demands modulate value; 2) a simple OC model can approximate people's behavior in such single-option, take it or leave it choices; and 3) when foraging in environments of equivalent richness, cognifitvely effortful demands can increase the attractiveness of offers rather than discount them (unlike other forms of cost).
+In the next experiment we explored whether this apparent value was inherent or malleable.
 ## Discussion

### 2020-11-05 Cost_manuscript.Rmd
moving oc around

@@
 
-  This experiment probed whether the value-modulatory effects of each type of demand depended on the ability to obtain rewards through other behavioral means.
-If the cost or value of a demand are intrinsic, the relative preferences displayed above should be robust to alternatives.
-The experimental setup was mostly preserved, with 3 key differences.
-First, all participants experienced cognitive effort, physical effort, and delay.
-Second, each block contained offers with one type of effort and passive waiting (allowing for comparisons in acceptances through the common wait condition).
+  If the cost or value of a demand were intrinsic, the relative preferences displayed so far should be robust to the ability to obtain the same rewards through different demands.
+We investigated this possibility by modifying the foraging task, such that every participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (fixed at 10 s handling and 6 s travel times, to allow for comparisons between experiments).
 We refer to observations from each block's wait trials by their effort pair (i.e.
 "Wait-C" for cognitive, and "Wait-P" for physical).
-Finally, in this experiment the handling and travel times were fixed at 10 s and 6 s, respectively.
-We therefore compared choices from the within-subjects experiment to the matching time condition from the between-subjects experiment.
-We hypothesized that reward decision patterns would match those of the previous experiment, and that interleaving effort and delay would produce persistent preferences for passive delay trials.
+We hypothesized that reward decision patterns would match those of the previous experiment, and that interleaving effort and delay would produce persistent preferences for wait trials.
 
@@
 Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-C = `r filter(earnings_within, Cost == "Wait-C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-P = `r filter(earnings_within, Cost == "Wait-P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-P")$sdEarn`).
-These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality (**caveat: the same percentage can be produced by many non-optimal combinations, including accepting half of each reward.
-So neither approach really gets at this too well.**).
+These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality.
 
@@
 
-### **Within-subjects: Modeling the subjective opportunity cost in each condition**
+### **Consistency and stability**
 
@@
 
+### **Computational modeling of foraging behavior**
+
+``` {r BTW: 16.3.3. OC modeling, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+## fit the OC model
+summaryOC <- list()
+summaryOC$all <- dataBtw %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup()
+
+## plot
+summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+  # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
+  # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
+  # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
+  geom_hline(yintercept = 0.74, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
+  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
+  geom_boxplot(show.legend = F) +
+  geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
+  ylim(0,1.5) +
+  labs(x = "") +
+  scale_fill_manual(values = colsBtw) +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 16))
+
+## one sample t against optimal strategy
+summaryOC$t.test <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  sapply(., function(data) {t.test(data$Gamma, mu = 0.74)})
+
+## descriptive stats
+summaryOC$descriptives <- summaryOC$all %>%
+  group_by(Cost) %>%
+  summarise(mGamma = round(mean(Gamma), digits = 2),
+            sdGamma = round(sd(Gamma), digits = 2))
+
+# summaryOC$all %>%
+#   ggplot(aes(Gamma, percentAccept, fill = Cost, size = temperature)) +
+#   geom_point(pch = 21)
+
+# # gamma parameter recovery tests
+# # test a single subject against their own choices
+# (subj <- sample(subjList_btw, 1))
+# subjData <- dataBtw %>% 
+#   filter(SubjID == subj) %>% 
+#   group_by(Cost, Handling, Offer) %>% 
+#   summarise(propAccept = mean(Choice)) %>%
+#   ungroup()
+# 
+# params <- filter(summaryOC$all, SubjID == subj) %>% 
+#   select(Gamma, temperature)
+# 
+# test_params(params,
+#             model = expr(params$Gamma * Handling), 
+#             subjData, 
+#             plot = T)
+
+# # test multiple values of gamma and plot the comparison
+# lowGamma <- 0
+# upperGamma <- 1.7
+# nGamma <- 6
+# testys <- lapply(seq(lowGamma, upperGamma, length.out = nGamma), test_params)
+# (testys <- do.call(rbind, testys))
+# testys %>%
+#   ggplot(aes(interaction(Offer, Handling), Choice, color = Gamma)) +
+#   geom_point(size = 3) +
+#   geom_line(aes(group = interaction(Handling, Gamma)), size = 1) +
+#   labs(x = "Offer.Handling", y = "Proportion Accepted") +
+#   facet_wrap(vars(Gamma), ncol = 2) +
+#   theme(legend.key = element_blank(),
+#         panel.grid.major = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.background = element_blank(),
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 16))
+
+```
+
+``` {r BTW: 16.3.5. OC comparisons, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# ANOVA
+OCanova <- list()
+OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC$all))
+Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
+Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
+Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
+
+# Post-hoc pairwise tests
+OCanova$perms <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(permute), simple = T)
+diag(OCanova$perms) <- 1
+
+OCanova$ES <- summaryOC$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(cohenD)) %>%
+  abs()
+```
+
+``` {r BTW: 16.3.5. corrplot, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
+# # plot all pairwise comparisons
+# corrplot(OCanova$ES,
+#          is.corr = F, 
+#          p.mat = OCanova$perms,
+#          type = "upper",
+#          insig = "p-value",
+#          sig.level = -1,
+#          na.label = "square",
+#          na.label.col = "grey",
+#          method = "color", 
+#          tl.col = "black", 
+#          tl.cex = 0.8,
+#          outline = T)
+```
+
+``` {r BTW: 16.3.4. OC cross-validation, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# Compute the OC for pre-midpoint
+summaryOC$pre <- dataBtw %>%
+                 filter(Half == "Half_1") %>%
+                 group_by(Cost, SubjID) %>%
+                 do(optimizeOCModel(., simplify = T)) %>%
+                 ungroup() %>%
+                 select(SubjID, Gamma)
+
+# let's add the gammas to the second half data and estimate prop predicted on the second half
+summaryOC$predicted <- dataBtw %>%
+                 filter(Half == "Half_2") %>%
+                 group_by(Cost, SubjID) %>%
+                 left_join(summaryOC$pre, by = "SubjID") %>%
+                 mutate(OC = Handling * Gamma,
+                        predicted = Offer > OC) %>% 
+                 summarise(percentPredicted = mean(predicted == Choice) * 100) %>%
+                 group_by(Cost) %>%
+                 summarise(mPredicted = round(mean(percentPredicted), digits = 2),
+                           sdPredicted = round(sd(percentPredicted), digits = 2))
+
+# # plot
+# (summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
+#                             labs(x = "") +
+#                             geom_boxplot(show.legend = F) +
+#                             scale_fill_manual(values = colsBtw) +
+#                             labs(y = "Percent Predicted") +
+#                             ylim(0,100) +
+#                             theme(panel.grid.major = element_blank(),
+#                             panel.grid.minor = element_blank(),
+#                             panel.background = element_blank(),
+#                             axis.line = element_line(colour = "black"),
+#                             text = element_text(size = 16)))
+
+```
+
+  We then proceeded to estimate subjective OCs for each participant, which was produced by multiplying the handling time and a free parameter gamma (see Methods for details).
+Gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+For example, the aversion produced by a given cost could prompt participants to spend their time and effort in the most profitable offers, resulting in high gamma values.
+Conversely, low gamma values represented low selectivity when evaluating offers.
+The model predicted the probability of a choice by comparing the estimated OC against each offer amount, and was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
+This single parameter model was able to explain a considerable degree of choice variance per individual (R-squared: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
+The distribution of gamma values is shown on Figure 7, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
+Values higher than this baseline imply that a condition was costly, whereas lower values suggest that a condition boosted the value of an offer.
+Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
+Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
+An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, R-squared = `r Rsquared_aov`).
+Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
+In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
+Finally, we cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+
+```{r Gamma per cost group (Fig.
+7), fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
+The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
+Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
+
+summaryOC$plot
+
+```
+
+  Together, these findings suggest that 1) foraging paradigms can provide a reference point to evaluate how different demands modulate value; 2) a simple OC model can approximate people's behavior in such single-option, take it or leave it choices; and 3) when foraging in environments of equivalent richness, cognifitvely effortful demands can increase the attractiveness of offers rather than discount them (unlike other forms of cost).
+In the next experiment we explored whether this apparent value was inherent or malleable.
+
 ### WTH: 16.3.4. (OC MODELING: SKIP)
-
-**Possibilities**
 
@@
 
-### **Computational modeling of foraging behavior**
-
-``` {r BTW: 16.3.3. OC modeling, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-## fit the OC model
-summaryOC <- list()
-summaryOC$all <- dataBtw %>%
-                 group_by(Cost, SubjID) %>%
-                 do(optimizeOCModel(., simplify = T)) %>%
-                 ungroup()
-
-## plot
-summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
-  # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
-  # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
-  # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-  geom_hline(yintercept = 0.74, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
-  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
-  geom_boxplot(show.legend = F) +
-  geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
-  ylim(0,1.5) +
-  labs(x = "") +
-  scale_fill_manual(values = colsBtw) +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        axis.line = element_line(colour = "black"),
-        text = element_text(size = 16))
-
-## one sample t against optimal strategy
-summaryOC$t.test <- summaryOC$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  sapply(., function(data) {t.test(data$Gamma, mu = 0.74)})
-
-## descriptive stats
-summaryOC$descriptives <- summaryOC$all %>%
-  group_by(Cost) %>%
-  summarise(mGamma = round(mean(Gamma), digits = 2),
-            sdGamma = round(sd(Gamma), digits = 2))
-
-# summaryOC$all %>%
-#   ggplot(aes(Gamma, percentAccept, fill = Cost, size = temperature)) +
-#   geom_point(pch = 21)
-
-# # gamma parameter recovery tests
-# # test a single subject against their own choices
-# (subj <- sample(subjList_btw, 1))
-# subjData <- dataBtw %>% 
-#   filter(SubjID == subj) %>% 
-#   group_by(Cost, Handling, Offer) %>% 
-#   summarise(propAccept = mean(Choice)) %>%
-#   ungroup()
-# 
-# params <- filter(summaryOC$all, SubjID == subj) %>% 
-#   select(Gamma, temperature)
-# 
-# test_params(params,
-#             model = expr(params$Gamma * Handling), 
-#             subjData, 
-#             plot = T)
-
-# # test multiple values of gamma and plot the comparison
-# lowGamma <- 0
-# upperGamma <- 1.7
-# nGamma <- 6
-# testys <- lapply(seq(lowGamma, upperGamma, length.out = nGamma), test_params)
-# (testys <- do.call(rbind, testys))
-# testys %>%
-#   ggplot(aes(interaction(Offer, Handling), Choice, color = Gamma)) +
-#   geom_point(size = 3) +
-#   geom_line(aes(group = interaction(Handling, Gamma)), size = 1) +
-#   labs(x = "Offer.Handling", y = "Proportion Accepted") +
-#   facet_wrap(vars(Gamma), ncol = 2) +
-#   theme(legend.key = element_blank(),
-#         panel.grid.major = element_blank(),
-#         panel.grid.minor = element_blank(),
-#         panel.background = element_blank(),
-#         axis.line = element_line(colour = "black"),
-#         text = element_text(size = 16))
-
-```
-
-``` {r BTW: 16.3.5. OC comparisons, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# ANOVA
-OCanova <- list()
-OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC$all))
-Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
-Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
-Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
-
-# Post-hoc pairwise tests
-OCanova$perms <- summaryOC$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  do.call(cbind, .) %>%
-  select_if(is.numeric) %>%
-  rename(Physical = Physical.Gamma,
-         Cognitive = Cognitive.Gamma,
-         Wait = Wait.Gamma,
-         Easy = Easy.Gamma) %>%
-  outer(., ., FUN = Vectorize(permute), simple = T)
-diag(OCanova$perms) <- 1
-
-OCanova$ES <- summaryOC$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  do.call(cbind, .) %>%
-  select_if(is.numeric) %>%
-  rename(Physical = Physical.Gamma,
-         Cognitive = Cognitive.Gamma,
-         Wait = Wait.Gamma,
-         Easy = Easy.Gamma) %>%
-  outer(., ., FUN = Vectorize(cohenD)) %>%
-  abs()
-```
-
-``` {r BTW: 16.3.5. corrplot, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
-# # plot all pairwise comparisons
-# corrplot(OCanova$ES,
-#          is.corr = F, 
-#          p.mat = OCanova$perms,
-#          type = "upper",
-#          insig = "p-value",
-#          sig.level = -1,
-#          na.label = "square",
-#          na.label.col = "grey",
-#          method = "color", 
-#          tl.col = "black", 
-#          tl.cex = 0.8,
-#          outline = T)
-```
-
-``` {r BTW: 16.3.4. OC cross-validation, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# Compute the OC for pre-midpoint
-summaryOC$pre <- dataBtw %>%
-                 filter(Half == "Half_1") %>%
-                 group_by(Cost, SubjID) %>%
-                 do(optimizeOCModel(., simplify = T)) %>%
-                 ungroup() %>%
-                 select(SubjID, Gamma)
-
-# let's add the gammas to the second half data and estimate prop predicted on the second half
-summaryOC$predicted <- dataBtw %>%
-                 filter(Half == "Half_2") %>%
-                 group_by(Cost, SubjID) %>%
-                 left_join(summaryOC$pre, by = "SubjID") %>%
-                 mutate(OC = Handling * Gamma,
-                        predicted = Offer > OC) %>% 
-                 summarise(percentPredicted = mean(predicted == Choice) * 100) %>%
-                 group_by(Cost) %>%
-                 summarise(mPredicted = round(mean(percentPredicted), digits = 2),
-                           sdPredicted = round(sd(percentPredicted), digits = 2))
-
-# # plot
-# (summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
-#                             labs(x = "") +
-#                             geom_boxplot(show.legend = F) +
-#                             scale_fill_manual(values = colsBtw) +
-#                             labs(y = "Percent Predicted") +
-#                             ylim(0,100) +
-#                             theme(panel.grid.major = element_blank(),
-#                             panel.grid.minor = element_blank(),
-#                             panel.background = element_blank(),
-#                             axis.line = element_line(colour = "black"),
-#                             text = element_text(size = 16)))
-
-```
-
-  We then proceeded to estimate subjective OCs for each participant, which was produced by multiplying the handling time and a free parameter gamma (see Methods for details).
-Gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
-For example, the aversion produced by a given cost could prompt participants to spend their time and effort in the most profitable offers, resulting in high gamma values.
-Conversely, low gamma values represented low selectivity when evaluating offers.
-The model predicted the probability of a choice by comparing the estimated OC against each offer amount, and was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
-This single parameter model was able to explain a considerable degree of choice variance per individual (R-squared: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
-The distribution of gamma values is shown on Figure 7, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
-Values higher than this baseline imply that a condition was costly, whereas lower values suggest that a condition boosted the value of an offer.
-Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
-Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
-An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, R-squared = `r Rsquared_aov`).
-Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
-In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
-Finally, we cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
-
-```{r Gamma per cost group (Fig.
-7), fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
-The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
-Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
-
-summaryOC$plot
-
-```
-
-  Together, these findings suggest that 1) foraging paradigms can provide a reference point to evaluate how different demands modulate value; 2) a simple OC model can approximate people's behavior in such single-option, take it or leave it choices; and 3) when foraging in environments of equivalent richness, cognifitvely effortful demands can increase the attractiveness of offers rather than discount them (unlike other forms of cost).
-In the next experiment we explored whether this apparent value was inherent or malleable.
 ## Discussion

### 2020-11-05 Cost_manuscript.Rmd
within-subj results edited. now onto computational modeling

@@
   Next, we tested the hypothesis that foragers would display consistent and stable choices.
-Participants were deemed consistent if they did not quit during the handling time.
+Participants were deemed consistent if they did not quit after engaging in a trial.
 To examine this, we plotted survival curves of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
@@
 Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure 5, top-right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed.
-These response time observations suggest clarity in participant preferences.
+These response time observations suggest clarity in participant choices
 
@@
 Paired permutations showed no differences in acceptances for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
-Figure 6 (left) shows that changes in choice behavior for effortful groups were mostly driven by the longest handling time, in in line with reports where value is discounted as the length of the required effort increases (Treadway et al, 2009).
-We replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Figure 6, right).
+Figure 6 (left) shows that the reduction acceptances in effort groups over time was steeper for longer handling times, a hallmark of effortful demands (Treadway et al, 2009).
+We then replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Figure 6, right).
 Together, the consistency and stability displayed by participants suggest that decision makers had a clear representation of the environment.
@@
 "Wait-C" for cognitive, and "Wait-P" for physical).
-We hypothesized that reward decision patterns would match those of the previous experiment, and that interleaving effort and delay would produce persistent preferences for wait trials.
+We hypothesized that 1) reward decision patterns would match those of the previous experiment, and 2) that interleaving effort and delay would produce persistent preferences for wait trials.
 
@@
 
-historyCoeffs_wth <- round(summary(historySize_wth[[historyIndex_wth]])$coefficients, digits = 2)
+historyCoeffs_wth <- round(summary(historySize_wth[[historyIndex_wth]])$coefficients, digits = 3)
 
@@
 Error"]`, *p* `r report_p(historyCoeffs_wth["recentOffers", "Pr(>|z|)"])`).
-Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r AIC(historySize_wth[[historyIndex_wth]])`.
+Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]], digits = 2))`.
 However, this time participants were unaffected by recent reward misses (*p* > 0.05).
   As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
-When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
-Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-C = `r filter(earnings_within, Cost == "Wait-C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-P = `r filter(earnings_within, Cost == "Wait-P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-P")$sdEarn`).
+When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were correctly accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
+Despite this deviation, participants earned a similar total amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-C = `r filter(earnings_within, Cost == "Wait-C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-P = `r filter(earnings_within, Cost == "Wait-P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-P")$sdEarn`).
 These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality.
@@
 
-  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
-As can be seen on Figure 8B, even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 4A), differences among cost conditions were less evident.
-Moreover, these differences contradicted our predictions, as cognitive effort remained as the least costly type of demand.
-We tested this observation through a mixed effects logistic regression, with main fixed effects for offer amount and cost, and random subject-wise intercepts (the reference cost category was rotated in order to perform all possible pairwise comparisons).
-The model confirmed that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Std.
-Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`).
-As in the previous section, pairwise comparison results are shown on the matrix in Figure 8C.
-This plot omits comparisons between effort and wait trials from different blocks, as these are not considered in our original predictions.
-The only significant difference was the higher likelihood to accept cognitive offers compared to physical ones ($\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
-This initial result suggests that differences in cost decrease if individuals are able to evaluate all of them.
-
 ```{r Earnings, prop completed, ME plots (Fig.
-8), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
+7), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
 B: proportion of acceptances of each reward per cost condition.
 C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount).
+Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions.
 Crosses mark non-significant comparisons.
@@
 
-  We then repeated the model comparison approach from the between-subject section, evaluating models ranging in complexity from intercept-only to a two-way interaction between cost and reward.
-Even though the a priori model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 8D).
+  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
+Even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 8B), differences among cost conditions were less evident.
+Moreover, these differences contradicted our predictions, as cognitive effort remained the least costly among demands.
+A mixed effects logistic regression confirmed once again that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Std.
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference was the higher likelihood to accept cognitive offers compared to physical ones (Figure 7C; $\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
+Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 8D).
 An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r round(mixLogis_compare$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`).
@@
 (**discuss with Joe: the interaction flips results over, such that both waits > pysical effort = cognitive effort...as predicted originally?
-Can't wrap my head around that yet, so this conclusion is pending**)
+Can't wrap my head around that yet, so this conclusion is pending**).
+These initial results defied our predictions, suggesting that the availability of alternative demands erases preferences among demands (rather than inverting them).
 
@@
 
-  We next examined the stability in people's choices.
-If the cost of a particular demand was intrinsic, then its effect on choices should have been consistent as participants explored alternative costs.
-We started by examining whether individuals regreted engaging in a particular offer.
-Participants could quit either during the offer period (2 s) or during the handling time (10 s), allowing for a total of 12 seconds to give up on the current trial.
-The survival curve on Figure 9A shows quitting instances within trials for all participants.
-Censored points signal completions (at end of interval) and forced travels (throughout the trial).
-Similar to before, the survival analysis suggests that participants made most of their choices quickly within the offer window.
-In fact, the mean percentage of quits during the handling time was `r round(mean(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 20)` participants quitting over 20% of trials during the handling time.
-Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure 9B).
-Once in the handling time, the overall proportion of forced travels in the effortful trials was relatively low for both cognitive (mean = `r round(mean(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (mean = `r round(mean(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
-Similar to the between-subjects experiment, these results suggest that decision makers were confident in their adopted strategies, and were able to perform the tasks well.
+  Similar to the between-subject results, a survival analysis displayed that participants made most of their choices quickly within the offer window (Figure 8A).
+The median percentage of quits during the handling time was `r round(median(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 20)` participants quitting over 20% of trials during the handling time.
+Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure 8B).
+Once in the handling time, the overall proportion of forced travels in the effortful trials was relatively low for both cognitive (median = `r round(median(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (median = `r round(median(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
+Similar to the between-subjects experiment, these results suggest that decision makers were consistent in their adopted strategies, and were able to perform the tasks well.
 
@@
 
-  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])` Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])` Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])` Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 10).
+  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 10).
 The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson's r = `r round(corDiff, digits = 2)`, *p* > 0.05).
 Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure 4A).
-Mixed effects logistic regressions on each half separately confirmed this observation.
-The matrix on Figure 10 shows the coefficient magnitude for all pairwise comparisons among costs (computed by rotating the reference cost condition in the model), with crosses signaling non-significant coefficients (*p* > 0.05).
-This plot shows that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).
+Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Figure 9, right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).
+  All together, our findings show that the stable preferences for cognitive effort observed during single-demand foraging slowly fade if alternative demands are introduced.
+This points towards task-specific and outcome-independent features from cognitive tasks that can be recalibrated by new experiences.
 

### 2020-11-05 Cost_manuscript.Rmd
stupid parentheses

@@
 Error"]`, *p* `r report_p(historyCoeffs_wth["recentOffers", "Pr(>|z|)"])`).
-Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]], digits = 2))`.
+Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]]), digits = 2)`.
 However, this time participants were unaffected by recent reward misses (*p* > 0.05).
@@
 ```{r Survival and prepost plots (Fig.
-9), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
+8), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r Prepost mixed effects plots (Fig.
-10), fig.align = "center", fig.cap = "Acceptance rates over time.
+9), fig.align = "center", fig.cap = "Acceptance rates over time.
 Left: Proportion accepted in the first two and last two blocks of the experiment.

### 2020-11-06 Cost_manuscript.Rmd
explaining the model in methods

@@
 
-  We performed model comparisons to identify qualities that explained both experiments.
+  We performed model comparisons to identify qualities that explained findings from both experiments.
 Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects.
-These conditions discarded a number of popular explanatory candidates.
-For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic, while differences between effort types rule out learned industriousness.
-Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (CITE).
-Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
-We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
-
-  (variability from Hayden could help..)
-
-  We started by fitting a base model in which a subjective OC was fit for each type of demand (see Operationalization of Cost).
-OC was computed as the product of a free parameter (gamma) and the handling time.
-Gamma can be interpreted as the subjective value of each second spent in an environment.
-If a trial's reward rate (i.e.
-offer amount divided by the handling time) fell below gamma, a participant was better off finding more profitable alternatives.
-In other words, individuals with higher gammas required higher rewards in order to accept a given offer.
-We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type
+These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, or sunk cost effects.
+
+  We started by fitting a base model derived from the normative predictions of the Marginal Value Theorem (MVT; Charnov, 1975), which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it.
+This decision rule can be expressed as
+
+$R_i - \gamma H_i$
+
+such that a trial’s reward $R_t$ should be accepted if it is bigger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_t$.
+Individuals with higher gammas therefore required higher rewards in order to accept a given offer.
+We fit $\gamma$ for each subject and cost using a softmax function to predict the probability of accepting a given trial
 
@@
 Conversely, a participant experiencing low opportunity costs would accept the non-beneficial offer of 4 cents for a 14 second delay (or 4/14).
-We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.
-We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (**0.74**, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
+**We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.** We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (**0.74**, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
 Finally, we determined which cost type produced the highest discounting by comparing gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
 
+  This base model was not flexible enough to capture the gradual decision shifts in the within-subjects experiment.
+Therefore, we expanded this base formulation by allowing $\gamma$ to evolve over time, adapting a learning rule from Constantino & Daw (2015)
+
 $\gamma_{i+1} = (1 - (1 - \alpha) ^ {\tau_i}) \dfrac{R_{i} A_{i}}{\tau_i} +  (1 - \alpha) ^ {\tau_i} \gamma_{i}$
 
+where $A_i$ is an acceptance indicator (0 or 1), and $\tau_i$ the amount of time spent in the trial.
+Higher values of the learning rate $\alpha$ (ranging from 0 to 1) prioritized updating from the current trial’s earning rate, weighed by the amount of time experienced.
+This addition allowed for the tracking of recent history that was part of our criteria.
+
+  We further parameterized this model to test the hypothesis that demands affected the perceived duration of the handling time differently.
+For instance, a sense of fast completion might have made the cognitive task attractive.
+Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [Mckerchar2009].
+Similar to that work, we added an exponential parameter $S$ to all instances of the handling time ($H_i$) handling time, with a value of $S$ associated with each type of demand.
+The values of $S$ could then be aggregated across demands as participants experienced them, according to the following formula [adapted from @Sutton2018]
+
   $s_{i + 1} = s_i + A_i \left (\frac{1}{i}[S_i - s_i] \right)$
 
+  in which the global value of $s$ was updated every time a decision maker engaged with a trial.
+We fitted the starting value of the a demand's parameter $S$, which was bounded between 0 and 2 (values lower and greater than 1 indicating slower and faster perceived time, respectively).
+Since participants in the between-subjects experienced a single demand, the value of $s$ was reduced to the initial fit of $S$.
+For the within-subjects experiment, we assumed that the fitted values of $S$ indexed the true time sensitivity produced by each demand.
+Therefore, for each individual in that experiment, we initialized $S$ for each demand as the median fitted value from the first experiment.
+
 $w_i = \left (\frac{i}{max(i)} \right ) ^\alpha$
@@
 $P(A)_i = \dfrac{1}{1 + exp^{-(1 / \beta[R_i - \gamma_i H_i^{mS_i}])}}$
+
+(noise in the estimation of environmental richness [@Cash-Padgett2020])
 
@@
 
+  The observed choice dynamics defied a number of explanatory candidates.
+For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic, while differences between effort types rule out learned industriousness.
+Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (CITE).
+Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
+We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
+Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
+Instead, we propose that features of the cognitive tasks added outcome-independent value to the offer.
+Subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....)
+
 - Make sure to note that we controlled for time as a confound for effort, as more effortful tasks normally take longer

### 2020-11-06 Cost_manuscript.Rmd
ugly draft of model methods

@@
 
-  We further parameterized this model to test the hypothesis that demands affected the perceived duration of the handling time differently.
-For instance, a sense of fast completion might have made the cognitive task attractive.
+  We further parameterized this model to test the hypothesis that demands affected the perceived duration of the handling time differently, thus potentially improving their appeal (e.g.
+a sense of fast completion might have made the cognitive task attractive).
 Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [Mckerchar2009].
@@
 We fitted the starting value of the a demand's parameter $S$, which was bounded between 0 and 2 (values lower and greater than 1 indicating slower and faster perceived time, respectively).
-Since participants in the between-subjects experienced a single demand, the value of $s$ was reduced to the initial fit of $S$.
+We assumed that each participant would incorporate t$s$ into their decisions at different rates
+
+   $mS_i = (s_i w_i) + (S_i (1 - w_i))$
+
+  such that in every trial, the recalibrated estimate of how long the handling time feels ($s$) is balanced against the actual experience of subjective time produced by the incoming demand ($S$).
+The weight $w_i$ controls how early participants start integrating the reclalibrated time $s$ into their decisions, given by
+
+ $w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}$
+
+ in which high values of $\alpha_w$ denoted that decision makers incorporated the recalibrated subjective time early on in the experiment.
+The balance between experienced and recalibrated handling time was then applied to models (1) and (2)
+
+$\tau_{i} = H_{i} ^ {mS_{i}}  A_{i} + T_{i}$
+
+$P(A)_i = \dfrac{1}{1 + exp^{-(1 / \beta[R_i - \gamma_i H_i^{mS_i}])}}$
+
+  Since participants in the between-subjects experienced a single demand, the value of $s$ was reduced to the initial fit of $S$, without any need to fit $\alpha_w$.
 For the within-subjects experiment, we assumed that the fitted values of $S$ indexed the true time sensitivity produced by each demand.
@@
 
-$w_i = \left (\frac{i}{max(i)} \right ) ^\alpha$
-
-$mS_i = (s_i w_i) + (S_i (1 - w_i))$
-
-$\tau_{i} = H_{i} ^ {mS_{i}}  A_{i} + T_{i}$
-
-$P(A)_i = \dfrac{1}{1 + exp^{-(1 / \beta[R_i - \gamma_i H_i^{mS_i}])}}$
+  All together, the expanded model probed 1) how fast or slow a given demand felt ($S$); 2) whether and how fast this time sensitivity was recalibrated based on experience of intermixed demands ($s$); and 3) whether this time sensitivity was used globally to update the estimated richness of the environment (i.e.
+high $\alpha$), or focally by affecting how the incoming trial feels ((i.e.
+low $\alpha$)) (**REWORD, BAD**).
 

### 2020-11-09 Cost_manuscript.Rmd
restructuring the model section

@@
 Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects.
-These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, or sunk cost effects.
+These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, or sunk cost effects (see Discussion).
 
@@
 
-$R_i - \gamma H_i$
-
-such that a trial’s reward $R_t$ should be accepted if it is bigger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_t$.
+$model_{base} = R_i - \gamma H_i$
+
+such that a trial’s reward $R_i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (free parameter gamma; the OC) during the handling time $H_i$.
 Individuals with higher gammas therefore required higher rewards in order to accept a given offer.
-We fit $\gamma$ for each subject and cost using a softmax function to predict the probability of accepting a given trial
-
-$P(accept)_i = \dfrac {1} {1 + e^{-1/\beta(R_i - \gamma H_i)}}$
-
-  Both gamma ($\gamma$) and the temperature parameter ($\beta$) of the softmax function were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE **GARY INFO**).
+We fit this and other models using a softmax function to predict the probability of accepting a given trial
+
+$P(accept)_i = \dfrac {1} {1 + e^{-1/\beta(model_{base})}}$
+
+  All free paremeters of the softmax function (in this case, $\gamma$ and the temperature parameter $\beta$) were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE **GARY INFO**).
 The gamma optimization search space was bound by extreme choice values.
@@
 
-  This base model was not flexible enough to capture the gradual decision shifts in the within-subjects experiment.
-Therefore, we expanded this base formulation by allowing $\gamma$ to evolve over time, adapting a learning rule from Constantino & Daw (2015)
+  The base model suffered from two main shortcomings.
+First, it lacked the flexibility to capture the dynamics observed in the within-subjects experiment.
+Second, the parameter $\gamma$ could index either subjective OC or how long the handling time felt.
+Intuitively, being completely engaged in a task can make time transpire subjectively faster (CITE FLOW?), which might have made the cognitive task attractive.
+Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [Mckerchar2009].
+Therefore, we next expanded the base formulation to distinguish between these two features by modeling the perceived length of the handling time and the subjective OC separately.
+
+  We started with time sensitivity.
+Similar to Mckerchar et al.
+(2009), we added an exponential parameter $S$ to all instances of the handling time ($H_i$), with a value of $S$ associated with each type of demand.
+
+  $model_{time} = R_i - \gamma H_i^{S}$
+
+  The values of $S$ could then be aggregated across demands as participants experienced them, according to the following formula [adapted from @Sutton2018]
+
+  $s_{i + 1} = s_i + A_i \left (\frac{1}{i}[S_i - s_i] \right)$
+
+  *then talk about C&D itself, so then they can be combined* in which the global value of $s$ was updated every time a decision maker completed a trial.
+We fitted the starting value of the a demand's parameter $S$, which was bounded between 0 and 2 (values lower and greater than 1 indicating slower and faster perceived time, respectively).
+We assumed that each participant would incorporate $s$ into their decisions at different rates
+
+   $mS_i = (s_i w_i) + (S_i (1 - w_i))$
+
+  such that in every trial, the recalibrated length estimate of the handling time ($s$) is balanced against the actual experience of subjective time produced by the incoming demand ($S$).
+The weight $w_i$ controls how early participants start integrating the reclalibrated time $s$ into their decisions, given by
+
+ $w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}$
+
+ in which high values of $\alpha_w$ denoted that decision makers incorporated the recalibrated subjective time early on in the experiment.
+The balance between experienced and recalibrated handling time was then applied to models (1) and (2)
+
+  allowing $\gamma$ to evolve over time, adapting a learning rule from Constantino & Daw (2015)
 
@@
 
-  We further parameterized this model to test the hypothesis that demands affected the perceived duration of the handling time differently, thus potentially improving their appeal (e.g.
-a sense of fast completion might have made the cognitive task attractive).
-Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [Mckerchar2009].
-Similar to that work, we added an exponential parameter $S$ to all instances of the handling time ($H_i$) handling time, with a value of $S$ associated with each type of demand.
-The values of $S$ could then be aggregated across demands as participants experienced them, according to the following formula [adapted from @Sutton2018]
-
-  $s_{i + 1} = s_i + A_i \left (\frac{1}{i}[S_i - s_i] \right)$
-
-  in which the global value of $s$ was updated every time a decision maker engaged with a trial.
-We fitted the starting value of the a demand's parameter $S$, which was bounded between 0 and 2 (values lower and greater than 1 indicating slower and faster perceived time, respectively).
-We assumed that each participant would incorporate t$s$ into their decisions at different rates
-
-   $mS_i = (s_i w_i) + (S_i (1 - w_i))$
-
-  such that in every trial, the recalibrated estimate of how long the handling time feels ($s$) is balanced against the actual experience of subjective time produced by the incoming demand ($S$).
-The weight $w_i$ controls how early participants start integrating the reclalibrated time $s$ into their decisions, given by
-
- $w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}$
-
- in which high values of $\alpha_w$ denoted that decision makers incorporated the recalibrated subjective time early on in the experiment.
-The balance between experienced and recalibrated handling time was then applied to models (1) and (2)
-
 $\tau_{i} = H_{i} ^ {mS_{i}}  A_{i} + T_{i}$
@@
   All together, the expanded model probed 1) how fast or slow a given demand felt ($S$); 2) whether and how fast this time sensitivity was recalibrated based on experience of intermixed demands ($s$); and 3) whether this time sensitivity was used globally to update the estimated richness of the environment (i.e.
-high $\alpha$), or focally by affecting how the incoming trial feels ((i.e.
-low $\alpha$)) (**REWORD, BAD**).
+high $\alpha$), or focally by affecting how the incoming trial feels (i.e.
+low $\alpha$) (**REWORD, BAD**).
+
+*the alternative way to frame this would be to 1) start with base model; 2) say how gmmma could either index OC or modulate time, so we'll model OC and time separately; 3) add all of time sensitivity; 4) add C&D OC, since S will modulate it too (otherwise it's awkward) this does not *
 

### 2020-11-10 Cost_manuscript.Rmd
new model methods draft

--- 2020-11-06 Cost_manuscript.Rmd
@@
 csl: apa.csl
+#subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
+#bibliography: mPFC_paper.bib
 ---
@@
 Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects.
-These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, or sunk cost effects.
+These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, sunk cost effects, or asymmetric learning of environmental richness (see Discussion).
 
@@
 
-$R_i - \gamma H_i$
-
-such that a trial’s reward $R_t$ should be accepted if it is bigger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_t$.
+$$\begin{aligned}
+Model_{base} = R_i - \gamma H_i
+\end{aligned}$$
+
+  such that a trial’s reward $R_i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_i$.
 Individuals with higher gammas therefore required higher rewards in order to accept a given offer.
-We fit $\gamma$ for each subject and cost using a softmax function to predict the probability of accepting a given trial
-
-$P(accept)_i = \dfrac {1} {1 + e^{-1/\beta(R_i - \gamma H_i)}}$
-
-  Both gamma ($\gamma$) and the temperature parameter ($\beta$) of the softmax function were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE **GARY INFO**).
+We fit this and other models using a softmax function to predict the probability of accepting a given trial
+
+$$\begin{aligned}
+P(accept)_i = \dfrac {1} {1 + e^{-1/\beta(Model_{base})}}
+\end{aligned}$$
+
+  All free paremeters of the softmax function (in this case, $\gamma$ and the temperature parameter $\beta$) were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE **GARY INFO**).
 The gamma optimization search space was bound by extreme choice values.
@@
 The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.** We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (**0.74**, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
-Finally, we determined which cost type produced the highest discounting by comparing gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
-
-  This base model was not flexible enough to capture the gradual decision shifts in the within-subjects experiment.
-Therefore, we expanded this base formulation by allowing $\gamma$ to evolve over time, adapting a learning rule from Constantino & Daw (2015)
-
-$\gamma_{i+1} = (1 - (1 - \alpha) ^ {\tau_i}) \dfrac{R_{i} A_{i}}{\tau_i} +  (1 - \alpha) ^ {\tau_i} \gamma_{i}$
+Finally, we compared gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
+
+  The base formulation lacked the flexibility needed to capture the dynamics observed in the within-subjects experiment.
+We therefore tested a second model which allowed $\gamma$ to evolve over time, adapting a learning rule from Constantino & Daw (2015)
+
+$$\begin{aligned}
+\gamma_{i+1} = (1 - (1 - \alpha) ^ {\tau_i}) \dfrac{R_{i} A_{i}}{\tau_i} +  (1 - \alpha) ^ {\tau_i} \gamma_{i}
+\end{aligned}$$
 
   where $A_i$ is an acceptance indicator (0 or 1), and $\tau_i$ the amount of time spent in the trial.
-Higher values of the learning rate $\alpha$ (ranging from 0 to 1) prioritized updating from the current trial’s earning rate, weighed by the amount of time experienced.
-This addition allowed for the tracking of recent history that was part of our criteria.
-
-  We further parameterized this model to test the hypothesis that demands affected the perceived duration of the handling time differently.
-For instance, a sense of fast completion might have made the cognitive task attractive.
+Higher values of the learning rate $\alpha$ (ranging from 0 to 1) prioritized updating from the current trial’s earning rate (left side of the equation), weighed by the amount of time experienced in the past trial.
+This time was given by
+
+$$\begin{aligned}
+\tau_{i} = H_{i}  A_{i} + T_{i}
+\end{aligned}$$
+
+  such that the handling time was counted only for accepted trials.
+These modifications allowed for the tracking of recent history that was part of our criteria, while mostly maintaining the same complexity (i.e.
+one free parameter) and structure of the base model
+
+$$\begin{aligned}
+Model_{adaptive} = R_i - \gamma_i H_i
+\end{aligned}$$
+
+  A final model considered the relationship between effortful engagement and the perceived length of time.
+Being immersed in a task can make time transpire subjectively faster [Csikszentmihalyi2004], which might have made the cognitive task attractive.
 Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [Mckerchar2009].
-Similar to that work, we added an exponential parameter $S$ to all instances of the handling time ($H_i$) handling time, with a value of $S$ associated with each type of demand.
-The values of $S$ could then be aggregated across demands as participants experienced them, according to the following formula [adapted from @Sutton2018]
-
-  $s_{i + 1} = s_i + A_i \left (\frac{1}{i}[S_i - s_i] \right)$
-
-  in which the global value of $s$ was updated every time a decision maker engaged with a trial.
-We fitted the starting value of the a demand's parameter $S$, which was bounded between 0 and 2 (values lower and greater than 1 indicating slower and faster perceived time, respectively).
-Since participants in the between-subjects experienced a single demand, the value of $s$ was reduced to the initial fit of $S$.
-For the within-subjects experiment, we assumed that the fitted values of $S$ indexed the true time sensitivity produced by each demand.
-Therefore, for each individual in that experiment, we initialized $S$ for each demand as the median fitted value from the first experiment.
-
-$w_i = \left (\frac{i}{max(i)} \right ) ^\alpha$
-
-$mS_i = (s_i w_i) + (S_i (1 - w_i))$
-
-$\tau_{i} = H_{i} ^ {mS_{i}}  A_{i} + T_{i}$
-
-$P(A)_i = \dfrac{1}{1 + exp^{-(1 / \beta[R_i - \gamma_i H_i^{mS_i}])}}$
+It is possible that such subjective handling time was recalibrated in the within-subjects experiment, resulting in the observed convergance of acceptances across demands.
+We therefore added a time sensitivity parameter $S$ to the model, with a separate value associated with each type of demand.
+The values of $S_{demand}$ could then be recalibrated as participants experienced them, averaged according to the following formula [adapted from @Sutton2018]
+
+$$\begin{aligned}
+s_{i + 1} = s_i + A_i \left (\frac{1}{i}[S_{demand} - s_i] \right)
+\end{aligned}$$
+
+  in which the global value of $s$ was updated every time an individual completed a trial.
+We fitted the initial value of $S_{demand}$, which was bounded between 0 and 2 (values lower and greater than 1 indicating slower and faster perceived time, respectively).
+Even though the value of $s$ was updated equally across individuals, we theorized that each participant would incorporate $s$ into their decisions at different rates.
+This intuition was given by a weighted sum
+
+$$\begin{aligned}
+mS_i = (s_i w_i) + (S_{demand} (1 - w_i))
+\end{aligned}$$
+
+  such that in every trial, the recalibrated length estimate of the handling time ($s$) was balanced against the actual experience of subjective time produced by the present demand ($S_{demand}$).
+The weight $w_i$ controlled how early participants started integrating the recalibrated time $s$ into their decisions, given by
+
+$$\begin{aligned}
+w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}
+\end{aligned}$$
+
+  in which high values of the free parmeter $\alpha_w$ denoted that decision makers incorporated the recalibrated subjective time early on in the experiment.
+Similar to McKerchar et al.
+(2009), the values of $mS_i$ exponentially modulated every instance of the handling time ($H_i$) from the adaptive model.
+In this way, subjective time perception produced by different demands could influence choice in two ways: retrospectively affecting the value of $\gamma$ through the perceived length of recent trials
+
+$$\begin{aligned}
+\tau_{i} = H_{i} ^ {mS_{i}}  A_{i} + T_{i}
+\end{aligned}$$
+
+and prospectively impacting the expected trial length at the time of a decision
+
+$$\begin{aligned}
+Model_{time} = R_i - \gamma_i H_i^{mS_i}
+\end{aligned}$$
+
+  This subjective time model was fitted differently across experiments, such that the fits from experiment 1 informed those of experiment 2.
+Since participants in the between-subjects experienced a single demand, the value of $s$ was reduced to the initial fit of $S_{demand}$, without any need to fit $\alpha_w$ (which was set to 1).
+For the within-subjects experiment, we assumed that the fitted values of $S_{demand}$ approximated the true time sensitivity produced by each demand.
+Therefore, for each individual in the within-subjects experiment, we set each value of $S_{demand}$ to be the median fitted value from the first experiment, and fitted $\alpha_w$ instead.
+In this way model complexities was fixed across experiments, even though different aspects of the model were emphasized.
+
+  In summary, the free parameters from the subjective time model captured three features.
+First, how fast or slow a given demand felt ($S_{demand}$).
+Second, whether and how fast this time sensitivity was recalibrated based on the experience of intermixed demands ($\alpha_w$).
+Finally, whether this time sensitivity was used retrospectively (i.e.
+high $\alpha$), or prospectively (i.e.
+low $\alpha$).
+
+  In order to compare model fits, we used expectation maximization...(**Gary**)
 
@@
 Instead, we propose that features of the cognitive tasks added outcome-independent value to the offer.
-Subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....)
+Subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....) *add that stability meant no need to model asymmetric learning across environmental richness from Neal*
 

### 2020-11-11 Cost_manuscript.Rmd
rewording of Results sections up until modeling

@@
 output:
+  word_document: #default
+    reference_docx: Style_reference_draft.docx
   pdf_document:
@@
     keep_tex: no
-  word_document: #default
-    reference_docx: Style_reference_draft.docx
   html_document:
@@
 First, how fast or slow a given demand felt ($S_{demand}$).
-Second, whether and how fast this time sensitivity was recalibrated based on the experience of intermixed demands ($\alpha_w$).
+Second, how early this time sensitivity was recalibrated and integrated into decisions based on the experience of intermixed demands ($\alpha_w$).
 Finally, whether this time sensitivity was used retrospectively (i.e.
@@
 Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
-Larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_btw["Offer", "Estimate"]`, SE = `r historyCoeffs_btw["Offer", "Std.
+In line with our predictions, larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_btw["Offer", "Estimate"]`, SE = `r historyCoeffs_btw["Offer", "Std.
 Error"]`, *p* `r report_p(historyCoeffs_btw["Offer", "Pr(>|z|)"])`), whereas longer delays decreased them ($\beta$ = `r historyCoeffs_btw["Handling", "Estimate"]`, SE = `r historyCoeffs_btw["Handling", "Std.
-Error"]`, *p* `r report_p(historyCoeffs_btw["Handling", "Pr(>|z|)"])`), in line with predictions.
+Error"]`, *p* `r report_p(historyCoeffs_btw["Handling", "Pr(>|z|)"])`).
 Two additional regressors showed that having missed out on consecutive rewards decreased the probability of acceptance ($\beta$ = `r historyCoeffs_btw["recentTravels", "Estimate"]`, SE = `r historyCoeffs_btw["recentTravels", "Std.
@@
 
-  The next set of analyses examined the hypothesis that choice differences among costs would be characterized by more acceptances by the effort groups.
+  The next set of analyses examined the hypothesis that effort group would uniformly accept more trials.
 Figure 3 (left) shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings (middle).
@@
 It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy")$mProp`, SD = `r filter(overallSumms, Cost == "Easy")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Wait < Easy")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy")$cohenD`) (all other *p* > 0.05).
-The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants (and 0 for either physical or easy conditions), making performance an unlikely explanation for the observed differences in choice.
 The higher acceptance rates produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
 In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
+The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants, and 0 for either physical or easy conditions, making performance an unlikely explanation for the observed differences in choice.
 
@@
 The foraging task was configured so that there was a single reward-maximizing strategy per block type (see Operationalization of Cost in Methods), and participants were warned that accepting everything would not maximize their gains.
-Accordingly, participants who over- or under-accepted earned the least (Figure 3, right; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+Accordingly, participants who over- or under-accepted earned the least (Figure 3, right; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 Two-sided, one-sample t-tests against the optimal proportion of acceptances (i.e.
@@
 4), out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
-A:  B:  Each entry shows how much more likely was the reference group to accept an offer than the comparison group.
-C:"}
+A: Proportion accepted for every combination of handling time, reward, and demand.
+Grey dots indicate the reward-maximizing acceptance for any handling/reward combination.
+B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
+Each entry shows how much more likely a group was to accept compared to the reference condition (row).
+C: AIC and BIC values for a forward mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model."}
 #hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
@@
 Qualitatively, the figure confirms two important predictions.
-First, participants adapted to the richness of the each timing block, showing a pattern of acceptances that resembled the optimal strategy regardless of the cost they faced.
-Second, differences in cost were consistent across blocks, and acceptances were highest for the cognitive effort group.
-The optimality of the strategies produced by each cost depended on the richness of the block.
-This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
+First, participants adapted to the richness of the each timing block, gravitating towards optimality regardless of the cost they faced.
+Second, differences in cost were consistent across blocks, and acceptances were uniformly highest for the cognitive effort group.
 We tested these observations with a mixed-effects logistic regression, computing the probability of accepting an offer as a function of handling time, reward amount, and demand type (see Methods for details).
@@
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`).
-Comparisons among all conditions are shown on Figure 4B, which portrays the coefficients (color scale), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
+Comparisons among all conditions are shown on Figure 4B.
 The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) and wait groups ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.
@@
 As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a-priori~ = `r filter(ME_evals$abicLogis_compare, Model == "AllMain")$AIC`, AIC~handling/reward~ = `r filter(ME_evals$abicLogis_compare, Model == "HR")$AIC`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r round(ME_evals$HRvMain$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
-However, against our prediction, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r filter(ME_evals$abicLogis_compare, Model == "HR_interaction")$AIC`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r round(ME_evals$MainvHRint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r filter(ME_evals$abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r round(ME_evals$MainvAllint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
+However, against our expectations, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r filter(ME_evals$abicLogis_compare, Model == "HR_interaction")$AIC`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r round(ME_evals$MainvHRint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r filter(ME_evals$abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r round(ME_evals$MainvAllint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
 These improvements were driven by the fact that differences in offer acceptances among costs were never present for 20 cents (all *p* values for interactions containing offer amount < 0.001).
-As the highest reward should always be accepted in prey foraging environments, we conclude that the most parsimonious explanation of choice behavior comes from the a priori model containing all main effects.
-In combination with the pattern observed in Figure 4A, these results confirm that handling and reward amounts were similarly integrated across groups, but that the absolute rate of acceptances was affected by the cost faced (and was highest for those confronted with cognitive demands).
+As the highest reward should always be accepted in prey foraging environments, we conclude that the most parsimonious explanation of choice behavior came from the a priori model containing all main effects.
+These results further support the hypotheses that handling and reward amounts were similarly integrated across groups, and that the absolute rate of acceptances was affected by the demand faced.
+However, they offer partial support for the hypothesis that effort would induce higher acceptance rates, which was only true for those confronted with cognitive effort.
 
@@
 These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
-Physical and easy groups show slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
-This resulted in some individuals choosing to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code).
-Plotting the quitting time distributions across blocks for the first handling second (ECDFs on Figure 5, top-right) shows that participants in the wait and cognitive groups responded faster as the experiment progressed.
-These response time observations suggest clarity in participant choices
+Physical and easy groups showed slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
+This resulted in some individuals opting to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code).
+Plotting the quitting time distributions across blocks for the first second of the handling time (ECDFs on Figure 5, top-right) showed that participants in the wait and cognitive groups responded faster as the experiment progressed.
+These response time observations suggested clarity in participant choices
 
@@
 6), fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
-Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands were increasingly discounted over time.
-Right: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately.
-Even though acceptances steadily declined in the effort groups, the relative preferences were preserved."}
+Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
+Right: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal).
+Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
 include_graphics("./Images/FIG6.png")
@@
 
-  If the cost or value of a demand were intrinsic, the relative preferences displayed so far should be robust to the ability to obtain the same rewards through different demands.
+  If the cost or value of a demand were intrinsic, the relative preferences displayed so far should have been robust to the ability to obtain the same rewards through different demands.
 We investigated this possibility by modifying the foraging task, such that every participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (fixed at 10 s handling and 6 s travel times, to allow for comparisons between experiments).
@@
 "Wait-C" for cognitive, and "Wait-P" for physical).
-We hypothesized that 1) reward decision patterns would match those of the previous experiment, and 2) that interleaving effort and delay would produce persistent preferences for wait trials.
+We hypothesized that 1) reward decision patterns would match those of the previous experiment; and 2) that interleaving effort and delay would produce persistent preferences for wait trials.
 
@@
   Analyses from the previous experiment were repurposed to examine cost differences within individuals.
+We started by testing the hypothesis that participants would successfully integrate the statistics of the environment.
 A mixed-effects logistic regression once again showed that larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_wth["Offer", "Estimate"]`, SE = `r historyCoeffs_wth["Offer", "Std.
@@
 Error"]`, *p* `r report_p(historyCoeffs_wth["recentOffers", "Pr(>|z|)"])`).
-Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]]), digits = 2)`.
+Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]]), digits = 2)`).
 However, this time participants were unaffected by recent reward misses (*p* > 0.05).
-  As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+  As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were correctly accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
@@
 Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure 8B).
-Once in the handling time, the overall proportion of forced travels in the effortful trials was relatively low for both cognitive (median = `r round(median(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (median = `r round(median(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
+Once in the handling time, the overall percentage (**shift to percentage in exp 1**) of forced travels in the effortful trials was low for both cognitive (median = `r round(median(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (median = `r round(median(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
 Similar to the between-subjects experiment, these results suggest that decision makers were consistent in their adopted strategies, and were able to perform the tasks well.
@@
 Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Figure 9, right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).
+
   All together, our findings show that the stable preferences for cognitive effort observed during single-demand foraging slowly fade if alternative demands are introduced.
@@
 Right: Mixed effects coefficient matrix for each half separately.
-The pattern from the first half resembles what was observed in the between-subjects experiment."}
+The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4)."}
 include_graphics("./Images/FIG10.png")
@@
 
+  We tested three nested models based on a set of criteria derived from observed choice behavior (see Methods).
+The first one, a base formulation, estimated a subjective opportunity cost for each individual and demand.
+The second one allowed the OC to gradually adapt using a reinforcement learning rule.
+The final one added a time sensitivity parameter that controlled how each demand affected the perceived length of the handling time, which could be recalibrated based on the experience of multiple types of demands.
+
   We then proceeded to estimate subjective OCs for each participant, which was produced by multiplying the handling time and a free parameter gamma (see Methods for details).
@@
 The model predicted the probability of a choice by comparing the estimated OC against each offer amount, and was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
-This single parameter model was able to explain a considerable degree of choice variance per individual (R-squared: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
+This single parameter model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
 The distribution of gamma values is shown on Figure 7, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
@@
 Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
-An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, R-squared = `r Rsquared_aov`).
+An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
 Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
@@
 
+- The optimality of the strategies produced by each cost depended on the richness of the block.
+This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
 - Make sure to note that we controlled for time as a confound for effort, as more effortful tasks normally take longer

### 2020-11-11 Cost_manuscript.Rmd
reformatting the modeling section of the results

@@
   \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
+- \usepackage{indentfirst}
 output:
-  word_document: #default
-    reference_docx: Style_reference_draft.docx
   pdf_document:
@@
     keep_tex: no
+  word_document: #default
+    reference_docx: Style_reference_draft.docx
   html_document:
@@
 csl: apa.csl
+indent: true
 #subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
@@
   such that the handling time was counted only for accepted trials.
+Gamma was initialized by the median earning rate achieved across individuals.
 These modifications allowed for the tracking of recent history that was part of our criteria, while mostly maintaining the same complexity (i.e.
@@
 4), out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
-A: Proportion accepted for every combination of handling time, reward, and demand.
-Grey dots indicate the reward-maximizing acceptance for any handling/reward combination.
-B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons).
+A: Proportion accepted by each group for every combination of handling time and reward.
+Grey dots indicate the reward-maximizing acceptance for each combination.
+B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition (crosses mark non-significant comparisons).
 Each entry shows how much more likely a group was to accept compared to the reference condition (row).
@@
 
-  We tested three nested models based on a set of criteria derived from observed choice behavior (see Methods).
+  We tested three nested models based on a set of criteria derived from observed choice behavior (see Methods for details).
 The first one, a base formulation, estimated a subjective opportunity cost for each individual and demand.
@@
 
-  We then proceeded to estimate subjective OCs for each participant, which was produced by multiplying the handling time and a free parameter gamma (see Methods for details).
-Gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
-For example, the aversion produced by a given cost could prompt participants to spend their time and effort in the most profitable offers, resulting in high gamma values.
+  In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
 Conversely, low gamma values represented low selectivity when evaluating offers.
-The model predicted the probability of a choice by comparing the estimated OC against each offer amount, and was optimized to find the lowest value of gamma that significantly reduced the negative log likelihood.
-This single parameter model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
-The distribution of gamma values is shown on Figure 7, with the dashed line indicating the gamma value for a reward-maximizing decision maker (computed as the average of the optimal per-second earning rates across blocks, or 0.74; see Operationalization of Cost).
-Values higher than this baseline imply that a condition was costly, whereas lower values suggest that a condition boosted the value of an offer.
+Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
+This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
+Figure 7 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
+Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
+In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
+We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 7; see Operationalization of Cost).
 Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
 Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
-An analysis of variance showed significant differences among the cost groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
-Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
-In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
-Finally, we cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
 
@@
 
-  Together, these findings suggest that 1) foraging paradigms can provide a reference point to evaluate how different demands modulate value; 2) a simple OC model can approximate people's behavior in such single-option, take it or leave it choices; and 3) when foraging in environments of equivalent richness, cognifitvely effortful demands can increase the attractiveness of offers rather than discount them (unlike other forms of cost).
-In the next experiment we explored whether this apparent value was inherent or malleable.
-
-### WTH: 16.3.4. (OC MODELING: SKIP)
-
- - Single OC per person
- - Subjective time perception, which gives rise to preference in cog effort.
-However, this doesn't account for the eventual convergence of choices across costs.
-Problem is that the converrgence is a global reduction.
-Like defaulting to the costliest demand.
- - Fatigue can maybe be ruled out. This would amplify effort costs and boost wait, but we are seeing a global decline in acceptances.
- - Wikenheiser
- - Maybe fatigue could operate at two levels: 1) it becomes bothersome to keep track of values per cost, and the convergence will default to the most fatiguingcost, since there is no readon to accept more of what you dislike.
-Easier to lower everything else.
-
-*To estimate the subjective opportunity cost (hypothesis 4.3.2.), we will use a logistic function to model each participant's probability of completing a trial based on the difference between the delayed reward's magnitude and the estimated opportunity cost (OC) for each cost type.
-OC will be computed as the product of a free parameter (gamma) and the handling time.
-Both gamma and the temperature parameter of the logistic function will be estimated at the subject level, independently for each subject and cost type.*
+  The second model asked whether interleaved demands gradually altered the OC over time, based on the derivation by Constantino & Daw (2015).
+This model behaved similarly to the base version at low enough values of alpha.
 
@@
 
-The figure on the left shows the distribution of fitted gammas for each cost type, and inversely matches the proportion of acceptances described previously.
-The plot on the right shows the OC for each subject, divided by cost type.
-The horizontal line denotes total earnings per second under the optimal strategy for the time and reward combinations.
-
-###	WTH: 16.3.5.
-
-*We will cross-validate each subject's OC value using the first four blocks (two cognitive, two physical) for estimation, and the last two blocks (one of each effort type) choices for testing.
-The estimates will be used to predict acceptances in the testing sample, and the mean percent correctly predicted will be reported for each cost type.
-This will also provide information on the stability of each participant's choices (4.3.1.).*
-
 ``` {r WTH: 16.3.5., echo = FALSE, fig.width=5, fig.height=4, fig.align="center"}
@@
 
-The figure above shows that each participant's estimated gamma successfully predicted choices in the last two blocks to a high degree (suspisiouly, considering the decrease in the acceptance rate as a function of time).
-
-###	WTH: 16.3.6.
-
-*The OC estimates for each group will be compared using a repeated measures ANOVA with cost as a factor. This will let us determine which cost type produced the highest discounting.*
-
 ``` {r WTH: 16.3.6., echo = FALSE}
@@
 ```
-
-(note: here 'Cost' is cost type).
-The ANOVA table shows that there are no significant differences among cost types for the current sample.
-The following plot shows the resulting p-values from performing a paired permutation analysis among all relevant cost types, with color indicating the effect size of the comparison.
-The differences only partially match those seen in 16.2.1., so the OC estimates seem noisy.
 

### 2020-11-11 Cost_manuscript.Rmd
adding discussion points

@@
 In this study, we tested the hypothesis that such appeal could arise from being able to compare different means to achieve the same outcome.
-Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that 1) preferences for cognitive effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
-
-  The observed choice dynamics defied a number of explanatory candidates.
+Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that 1) preferences for cognitive effort were stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
+
+  Rather than comparing discounting functions among demands, allowing people to choose for them helped us control for a number of confounds.
+For example, effortful tasks often take longer to perform in everyday life.
+We eliminated this possibility by using a common handling time for all demands.
+
+  The observed choice dynamics ruled out a number of explanatory candidates.
 For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic, while differences between effort types rule out learned industriousness.
@@
 Instead, we propose that features of the cognitive tasks added outcome-independent value to the offer.
-Subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....) *add that stability meant no need to model asymmetric learning across environmental richness from Neal*
-
-- The optimality of the strategies produced by each cost depended on the richness of the block.
+Subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....) *add that stability meant no need to model asymmetric learning across environmental richness from Neal* (unlikely to be need for cognition bc of exp 2 global decrease)
+
+# Points of discussion 
+- We still think that cognitive and physical manipulations were effortful.
+Our physical effort task has been repeatedly used to probe effort.
+Similar task switching has been shown to feel cognitively effortful (Kool).
+Furthermore, the effortful nature of our manipulations is evidenced by the steeper decrease in acceptances over time at longer handling times (Treadway).
+There are many reasons why such cognitive manipulations can be effortful, which are often centered in the amount of control.
+Or the OC.
+- Note that the calibration of efforts were different. We adjusted to people's physical capabilities, but trained them in the cognitive tasks until they reached criterion. 
+- Efficacy, along with reward amount, can influence how much control is exherted.
+- But here we do not focus on choosing the *amount* of cognitive control to be exherted during performance, which can be due to efficacy, agency, or reward amount.
+Instead, we focus on what makes people *pursue* the task in spite of how effortful it is.
+- Clinical: such deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
+Like, the aversion is due to focusing on different elements of the task.
+- Having a between-subjects experiment provided a baseline of foraging behavior that helped us interpret the findings of the second experiment
+- Control: for time as confound of effort
+- Control: having two efforts helped dissociate domain-general from task-specific features.
+- Control: participants were fully aware. This removed the possibility of asymmetric learning and choice difficulty.
+- Control: in demand experiments, chosen options are often carried out after the experiment, but there are known discrepancies between expected and obtained value that could affect repeated decisions in real life.
+
+- Control: even in TAFC tasks, selecting the shorter option could index
+- Optimality let us know that people acted as if effort was attractive.
+This was evidenced by both the lower earnings by the cognitive effort group, and by the base OC model.
+Of note is that the optimality of the strategies produced by each cost depended on the richness of the block.
 This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
-- Make sure to note that we controlled for time as a confound for effort, as more effortful tasks normally take longer
-- What we think: subjective timing is shortened by the way we implemented cognitive effort.
-This can be recalibrated if many task types are experienced.
-Maybe the implementation allowed for counting.
-Alternatively, working memory engagement could produce timing issues (Buhi n Gershman).
-Also look at what Andrew Westbrook shared.
-Add this to a potential fatigue, although that would also mean that waiting would be accepted less over time in exp 1.
+- This appeal couldn't be explained by a number of explanatory candidates
+- This includes the often-cited reciprocal relationship between effort and reward
+- But it turns out subjective time fits the bill. 
+- Cognitive effort gained value by making trials feel shorter
+- This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman).
+Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.
+- maybe: gifts are valuable more when it required effort to acquire them.
+
+  The observed choice dynamics ruled out a number of explanatory candidates.
+For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
+Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (CITE).
+Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
+We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
+Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (learned industriousness, Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
+Instead, we proposed that subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....) *add that stability meant no need to model asymmetric learning across environmental richness from Neal* (unlikely to be need for cognition bc of exp 2 global decrease)
+
 - Things that don't seem to be at play here, but could still play a general role in mental effort preferences: 1) A demand’s cost is not fully intrinsic (within vs between differences); 2) Effort preferences unlikely just due to learned industriousness or efficacy as amitais lab sees it (differences between effort types, and everyone met a good performance level per training); 3) avoiding boredom (global decline in exp 2, not a preference exchange).
@@
 Ceyda; Laura; Cacioppo et al 1996), the collapsing in the second experiment shows that preferences for cognitive effort cannot be just that.
-- Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
-Like, the aversion is due to focusing on different elements of the task.
-- Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort
-- It's true that we didnt calibrate cog effort per subject.
-But instead we brought all subjects to the same level of performance, and we saw that as time progressed they became less likely to accept longer periods of effort.
-- Clinical: Deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
-Like, the aversion is due to focusing on different elements of the task.

### 2020-11-11 Cost_manuscript.Rmd
further cleaning of discussion. all points on the board, I think

@@
 
-$\dfrac {\sum p_i R_i} {\sum p_i H + 3T},p \in \{0, 1\}$
+$$\begin{aligned} 
+\dfrac {\sum p_i R_i} {\sum p_i H + 3T},p \in \{0, 1\}
+\end{aligned}$$
 
@@
 low $\alpha$).
+Note that every model could be reduced to the base formulation for values of $\alpha$ = 0, $\alpha_w$ = 1, and $S_{demand}$ = 1.
 
@@
 
-  The observed choice dynamics ruled out a number of explanatory candidates.
-For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic, while differences between effort types rule out learned industriousness.
-Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (CITE).
+# *Points to cover* 
+- The observed choice dynamics ruled out a number of explanatory candidates.
+For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
+Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (i.e.
+Ceyda; Laura; Cacioppo et al 1996).
 Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
 We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
-Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
-Instead, we propose that features of the cognitive tasks added outcome-independent value to the offer.
-Subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....) *add that stability meant no need to model asymmetric learning across environmental richness from Neal* (unlikely to be need for cognition bc of exp 2 global decrease)
-
-# Points of discussion 
+Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (learned industriousness, Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
+Instead, we proposed that subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....).
+Our findings do not discard the influence of these elements in daily effort evaluations.
+It supplements our understanding of what drives peoples preferences.
 - We still think that cognitive and physical manipulations were effortful.
@@
 Like, the aversion is due to focusing on different elements of the task.
-- Having a between-subjects experiment provided a baseline of foraging behavior that helped us interpret the findings of the second experiment
-- Control: for time as confound of effort
-- Control: having two efforts helped dissociate domain-general from task-specific features.
-- Control: participants were fully aware. This removed the possibility of asymmetric learning and choice difficulty.
-- Control: in demand experiments, chosen options are often carried out after the experiment, but there are known discrepancies between expected and obtained value that could affect repeated decisions in real life.
-
-- Control: even in TAFC tasks, selecting the shorter option could index
-- Optimality let us know that people acted as if effort was attractive.
+Excessive aversion to delay and effort can manifest as impulsivity and apathy, respectively [1,10–12], fluctuations in which are hallmark symptoms of various mental illnesses and substance use disorders [13].
+Our findings promote the idea that motivation to exhert effort can be boosted by chopping tasks into smaller digestible chunks that don't make them feel as long.
+Rather than telling them the final goal, keep them busy (this should be already a thing, I'm sure...).
+The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler).
+This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.
+- Control/Exp Design: Having a between-subjects experiment provided a baseline of foraging behavior that helped us interpret the findings of the second experiment
+- Control/Exp Design: for time as confound of effort
+- Control/Exp Design: having two efforts helped dissociate domain-general from task-specific features.
+- Control/Exp Design: participants were fully aware. This removed the possibility of asymmetric learning and choice difficulty. Demonstrated by stable strategies.
+- Control/Exp Design: in demand experiments, chosen options are often carried out after the experiment, but there are known discrepancies between expected and obtained value that could affect repeated decisions in real life.
+Alt from grant: Investigations of the pursuit and receipt stages have been comparatively limited.
+Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [5,11,15,16,19].
+However, discrepancies between expected and experienced value are well known [20], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards [3,21,22].
+- Control/Exp Design: even in TAFC tasks, selecting the shorter option could index a wish to find a better set of options
+- Control/Exp Design: Optimality let us know that people acted as if effort was attractive.
 This was evidenced by both the lower earnings by the cognitive effort group, and by the base OC model.
@@
 Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.
-- maybe: gifts are valuable more when it required effort to acquire them.
-
-  The observed choice dynamics ruled out a number of explanatory candidates.
-For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
-Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (CITE).
-Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
-We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
-Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (learned industriousness, Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
-Instead, we proposed that subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....) *add that stability meant no need to model asymmetric learning across environmental richness from Neal* (unlikely to be need for cognition bc of exp 2 global decrease)
-
-- Things that don't seem to be at play here, but could still play a general role in mental effort preferences: 1) A demand’s cost is not fully intrinsic (within vs between differences); 2) Effort preferences unlikely just due to learned industriousness or efficacy as amitais lab sees it (differences between effort types, and everyone met a good performance level per training); 3) avoiding boredom (global decline in exp 2, not a preference exchange).
-4) Literally counting tasks, since mental effort was discretely presented but everything else was contiguous.
-If that were the case, dividing the handling time by 2 would work, but not sure if it would translated into exp 2.
-5) fatigue: there's a similar gradual decrease in acceptances in both experiments, except for the wait condition in exp 1.
-Fatigue would apply equally to both, or alternatively it might not bring all down to the same level (I guess the point could be made, but it's not that people who complete more at the beginning decrease acceptances more, as one would expect from fatigued people).
-Also worth mentioning that even if this is due to need for cognition (i.e.
-Ceyda; Laura; Cacioppo et al 1996), the collapsing in the second experiment shows that preferences for cognitive effort cannot be just that.
+- do I even want to get into DA?

### 2020-11-12 Cost_manuscript.Rmd
adding bibliography with settings

@@
 #subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
-#bibliography: mPFC_paper.bib
+bibliography: cost_paper.bib
 ---
@@
   Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
-In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015).
-Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013).
+In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Westbrook2015; @Shenhav2017].
+Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2018; @Kool2010; @Treadway2009; @Westbrook2013].
 However, people often change their attitudes towards exerting effort in everyday decisions, resulting in pursual of effortful avenues instead.
-Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes (Kacelnik and Marsh, 2002; Mochon, Norton, and Ariely, 2012; Hernandez Lallement et al., 2014), and positive outcomes imbue value into their preceding effortful behavior (i.e.
-learned industriousness, Eisenberger, 1992).
-Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs (Inzlicht, Shenhav, and Olivola, 2018).
+Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes [@Kacelnik2002; @Mochon2012; @HernandezLallement2014], and positive outcomes imbue value into their preceding effortful behavior [i.e.
+learned industriousness; @Eisenberger1992].
+Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs [@Inzlicht2018].
 Understanding these intrinsic qualities could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
@@
   What is often missing from existing accounts is the common case of choosing among types of behavioral demands.
-Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior (Ainslie, 1975; Frederick et al., 2002; Kable and Glimcher, 2007; Kool et al., 2010; Westbrook, Kester, and Braver, 2013; Green, Fristoe, and Myerson, 1994).
-Although this line of work suggests that discounting functions are similar for delay and effort (Prevost et al., 2010; Massar et al., 2015; Seaman et al., 2018), there is ongoing debate about the shape of the discounting function across effort types (Arulpragasam et al., 2018; Prevost et al., 2010; Chong et al., 2016; Klein-Flugge et al., 2016; Kool and Botvinick, 2018), and discount rates do not always correlate across cost domains (Westbrook and Braver, 2013; Seaman et al., 2018).
-However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context (Kool & Botvinick, 2018).
+Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [@Ainslie1975; @Frederick2002; @Kable2007; @Kool2010; @Westbrook2013; @Green1994).
+Although this line of work suggests that discounting functions are similar for delay and effort [@Prevost2010; @Massar2015; @Seaman2018], there is ongoing debate about the shape of the discounting function across effort types [@Arulpragasam2018; @Prevost2010; @Chong2016; @Klein-Flugge2016; @Kool2018], and discount rates do not always correlate across cost domains [@Westbrook2013; @Seaman2018].
+However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context [@Kool2018].
 For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting (e.g.
@@
 Conversely, even though people tend to donate more to charitable events that require them to perform effortful activities (i.e.
-the martyrdom effect), they are also less likely to engage in such events once an easier alternative to raise funds becomes available (Olivola and Shafir, 2013).
-Recent work has proposed that the subjective costs produced by delays and cognitive effort is modulated by the possibility of missing out on better concurrent alternatives, namely the opportunity cost of time (OC; Fawcett et al., 2012; Kurzban et al, 2013; Otto and Daw, 2019).
-This evidence sets the stage for examining what people would actually select when given the option for multiple types of demands, including the unexplored question of deciding between cognitive and physical effort (Inzlicht, Shenhav, and Olivola, 2018).
-
-  Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Stephens & Krebs, 2019).
-Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionary choice behaviors (Hayden 2018; Mobbs, Trimmer, Blumstein, & Dayan, 2018), and offers a number of desirable qualities.
-First, it allows for the estimation of optimal, reward maximizing choice patterns based on the opportunity cost of time (Charnov, 1975; Krebs et al., 1977).
+the martyrdom effect), they are also less likely to engage in such events once an easier alternative to raise funds becomes available [@Olivola2013].
+Recent work has proposed that the subjective costs produced by delays and cognitive effort is modulated by the possibility of missing out on better concurrent alternatives, namely the opportunity cost of time [OC; @Fawcett2012; @Kurzban2013; @Otto2019].
+This evidence sets the stage for examining what people would actually select when given the option for multiple types of demands, including the unexplored question of deciding between cognitive and physical effort [@Inzlicht2018; @Kool2018].
+
+  Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead [@Stephens2019].
+Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionary choice behaviors [@Hayden2018; @Mobbs2018], and offers a number of desirable qualities.
+First, it allows for the estimation of optimal, reward maximizing choice patterns based on the opportunity cost of time [@Charnov1975; @Krebs1977].
 We can therefore interpret observed deviations in acceptance rates from such optimal behavior in addition to comparing them among demands.
@@
 Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that are adjusted once individuals experience different forms of behavioral costs.
-Foraging rests on an abundant modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
+Foraging rests on an abundant modeling history that can help to computationally capture such emphases [@Stephens2019].
 
@@
 We explored this question in two foraging experiments: a between-subjects design in which participants foraged for rewards while performing a single demand, and a within-subjects extension that had individuals forage for demands in addition to rewards.
-We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions (Inzlicht, Shenhav, and Olivola, 2018).
+We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions [@Inzlicht2018].
 First, the existence of a well-defined optimal choice strategy helped us identify when demands boost the value of rewards (i.e.
@@
 We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
+Noise also discarded (Hayden paper), as values on each end of the reward range moved little over time.
 Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (learned industriousness, Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
@@
 However, discrepancies between expected and experienced value are well known [20], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards [3,21,22].
+Relying on a foraging paradigm allowed us to control for these and other variables...then control/exp design?
 - Control/Exp Design: even in TAFC tasks, selecting the shorter option could index a wish to find a better set of options

### 2020-11-13 Cost_manuscript.Rmd
tweking citations

@@
   and delay are interleaved in a foraging environment
-author: "Claudio Toro-Serey, Gary Kane, & Joseph T. McGuire"
+author: "Claudio Toro-Serey^1^2, Gary Kane^1^2, & Joseph T. McGuire^1^2"
 header-includes:
@@
 
-Department of Psychological and Brain Sciences & Center for Systems Neuroscience, Boston University, Boston, USA
+1.  Department of Psychological and Brain Sciences, Boston University, Boston, USA
+
+2.  Center for Systems Neuroscience, Boston University, Boston, USA
 
@@
   Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
-In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Westbrook2015; @Shenhav2017].
-Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2018; @Kool2010; @Treadway2009; @Westbrook2013].
+In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017 ;@Westbrook2015].
+Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2010; @Kool2018; @Treadway2009; @Westbrook2013].
 However, people often change their attitudes towards exerting effort in everyday decisions, resulting in pursual of effortful avenues instead.
-Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes [@Kacelnik2002; @Mochon2012; @HernandezLallement2014], and positive outcomes imbue value into their preceding effortful behavior [i.e.
+Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes [@HernandezLallement2014; @Kacelnik2002; @Mochon2012], and positive outcomes imbue value into their preceding effortful behavior [i.e.
 learned industriousness; @Eisenberger1992].
@@
   What is often missing from existing accounts is the common case of choosing among types of behavioral demands.
-Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [@Ainslie1975; @Frederick2002; @Kable2007; @Kool2010; @Westbrook2013; @Green1994).
-Although this line of work suggests that discounting functions are similar for delay and effort [@Prevost2010; @Massar2015; @Seaman2018], there is ongoing debate about the shape of the discounting function across effort types [@Arulpragasam2018; @Prevost2010; @Chong2016; @Klein-Flugge2016; @Kool2018], and discount rates do not always correlate across cost domains [@Westbrook2013; @Seaman2018].
+Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @Kool2010; @Westbrook2013].
+Although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across effort types [@Arulpragasam2018; @Chong2017; @Klein-Flugge2016; @Kool2018; @Prevost2010], and discount rates do not always correlate across cost domains [@Seaman2018; @Westbrook2013].
 However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context [@Kool2018].
@@
 Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionary choice behaviors [@Hayden2018; @Mobbs2018], and offers a number of desirable qualities.
-First, it allows for the estimation of optimal, reward maximizing choice patterns based on the opportunity cost of time [@Charnov1975; @Krebs1977].
+First, it allows for the estimation of optimal, reward maximizing choice patterns based on the opportunity cost of time [@Charnov1976; @Krebs1977].
 We can therefore interpret observed deviations in acceptance rates from such optimal behavior in addition to comparing them among demands.
@@
 
-  All experimental tasks were implemented using PsychoPy 2 (v1.85.1, Pierce2019) on a Macbook Pro laptop.
+  All experimental tasks were implemented using PsychoPy 2 [v1.85.1, @Peirce2019] on a Macbook Pro laptop.
 In this task, participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay (Figure 1).
@@
 Each group was unaware that other cost conditions existed.
-Participants exerted physical effort by maintaining grip on a handheld dynamometer (XXXX, BIOPAC Systems, United States) using their dominant hand.
+Participants exerted physical effort by maintaining grip on a handheld dynamometer (*VERSION*, BIOPAC Systems, United States) using their dominant hand.
 Gripping requirements were calibrated at 20% of maximum voluntary contraction (MVC, acquired at the beginning of the session).
@@
 Timing information was disclosed at the beginning of each block, and rewards displayed during a 2 s offer window before each trial began.
-Participants received training prior to the experimental session, and were told about all possible environmental statistics in order to preclude biases due to experience-dependent learning (Dundon2020; Garrett2020).
+Participants received training prior to the experimental session, and were told about all possible environmental statistics in order to preclude biases due to experience-dependent learning [@Dundon2020; @Garrett2020].
 
@@
 
-  Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment (Stephens2019).
+  Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment [@Charnov1976; @Stephens2019].
 In this study, the richness of the environment was manipulated by the length of the handling and travel times, where shorter travel times produced richer environments.
@@
 
-  All analyses were performed in R 3.5.2 (RTeam2018).
+  All analyses were performed in R 3.5.2 [@RTeam2018].
 First we tested whether decision makers integrated delay and reward information.
-To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a mixed-effects logistic regression to predict trial-wise acceptances (using the lme4 package, Bates2015), giving a random intercept to each subject to account for biases in participant behavior.
+To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a mixed-effects logistic regression to predict trial-wise acceptances [using the lme4 package, @Bates2015], giving a random intercept to each subject to account for biases in participant behavior.
 We included regressors for handling time and reward, as well as two covariates that probed the influence of recent history on choices.
@@
 Next, to determine the optimality of each group’s decisions, we performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost).
-This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate (FDR, Benjamini2001).
+This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate [FDR, @Benjamini2001].
 
@@
 
-  We started by fitting a base model derived from the normative predictions of the Marginal Value Theorem (MVT; Charnov, 1975), which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it.
+  We started by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT; @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it.
 This decision rule can be expressed as
@@
 $$\begin{aligned}
-P(accept)_i = \dfrac {1} {1 + e^{-1/\beta(Model_{base})}}
+P(accept)_i = \dfrac {1} {1 + e^{-(1/\beta)(Model_{base})}}
 \end{aligned}$$
@@
   A final model considered the relationship between effortful engagement and the perceived length of time.
-Being immersed in a task can make time transpire subjectively faster [Csikszentmihalyi2004], which might have made the cognitive task attractive.
-Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [Mckerchar2009].
+Being immersed in a task can make time transpire subjectively faster [@Csikszentmihalyi2014], which might have made the cognitive task attractive.
+Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [@Mckerchar2009].
 It is possible that such subjective handling time was recalibrated in the within-subjects experiment, resulting in the observed convergance of acceptances across demands.
@@
   in which high values of the free parmeter $\alpha_w$ denoted that decision makers incorporated the recalibrated subjective time early on in the experiment.
-Similar to McKerchar et al.
-(2009), the values of $mS_i$ exponentially modulated every instance of the handling time ($H_i$) from the adaptive model.
+Similar to @Mckerchar2009, the values of $mS_i$ exponentially modulated every instance of the handling time ($H_i$) from the adaptive model.
 In this way, subjective time perception produced by different demands could influence choice in two ways: retrospectively affecting the value of $\gamma$ through the perceived length of recent trials
@@
 In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
-The proportion of forced travels for cognitive effort was `r round(propFails[2, 2], digits = 2)` across participants, and 0 for either physical or easy conditions, making performance an unlikely explanation for the observed differences in choice.
+The percentage of forced travels for cognitive effort was `r round(propFails[2, 2] * 100, digits = 2)`% across participants, and 0% for either physical or easy conditions, making performance an unlikely explanation for the observed differences in choice.
 
@@
 Paired permutations showed no differences in acceptances for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
-Figure 6 (left) shows that the reduction acceptances in effort groups over time was steeper for longer handling times, a hallmark of effortful demands (Treadway et al, 2009).
+Figure 6 (left) shows that the reduction acceptances in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009].
 We then replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Figure 6, right).
@@
   Understanding the sporadic attractiveness of effortful options remains elusive.
-In this study, we tested the hypothesis that such appeal could arise from being able to compare different means to achieve the same outcome.
+In this study, we tested the hypothesis that such appeal could depend on the ability to achieve the same outcome through different means (**not quite**).
 Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that 1) preferences for cognitive effort were stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
+
+  Our findings provided partial support for our pre-registered hypotheses, which can be found in https://osf.io/2rsgm/.
+In accord with our predictions, decision makers were successful in approximating reward-maximizing strategies, as evidenced by acceptance rates.
+This is in line with previous foraging experiments, where the main deviation from optimality is a tendency to overharvest.
+Unlike our first hypothesis, our predictions regarding differences among costs did not
+
+  Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment or whether they faced a single or intermixed demands.
+When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups under-accepted, partially matching our predictions and highlighting that cognitive effort can add value to outcomes.
+However, against our expectations, we found that a similar preference for cognitive effort disappeared over time as decision makers foraged for types of demands in addition to rewards.
+Computational modeling suggested that cognitive effort was valuable because it shortened the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands.
+The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks).
+These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
 
@@
 - do I even want to get into DA?
+- AFAIK, Eisenberger1982 provides evidence that task diversity motivates further effort engagement
+
+## References

### 2020-11-13 Cost_manuscript.Rmd
reorganization of figures

@@
 indent: true
-#subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
 bibliography: cost_paper.bib
@@
 ```{r Trial plot (Fig.
-1), out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
+1), eval = FALSE, out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
 On each trial, participants were offered to earn money (4, 8, or 20 cents) by sustaining effort or waiting during the handling time (2, 10, or 14 s).
@@
 the lowest amount accepted).
-Figure 2 shows possible earnings for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
+Figure 2 shows possible earnings per second for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
 For example, a participant in a 10 s handling block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate.
@@
 ```{r Optimal plot (Fig.
-2), out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
+2), eval = FALSE, out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
 the smallest amount accepted) for each handling time.
@@
 ## MAYBE BETTER WAY TO DO PAIRWISE COMPARISONS, USING VECTORIZE FROM BELOW
-# OCanova$perms <- summaryOC$all %>%
+# OCanova$perms <- summaryOC_btw$all %>%
 #   select(Cost, Gamma) %>%
@@
 ```{r General prop & earnings plots (Fig.
-3), fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
+3), eval = FALSE, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
 Middle: Total number of dollars earned by each group by the end of the experiment.
@@
 ```{r mixed effects plots (Fig.
-4), out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
+4), eval = FALSE, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
 A: Proportion accepted by each group for every combination of handling time and reward.
@@
 ```{r Survival and prepost plots (Fig.
-5), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
+5), eval = FALSE, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r Prepost mixed effects plot (Fig.
-6), fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
+6), eval = FALSE, fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
 Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
@@
 However, this time participants were unaffected by recent reward misses (*p* > 0.05).
-  As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+  As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 7A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were correctly accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
@@
 
-```{r Earnings, prop completed, ME plots (Fig.
-7), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
+```{r Earnings/prop completed/ME plots (Fig.
+7), eval = FALSE, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
 B: proportion of acceptances of each reward per cost condition.
@@
   Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
-Even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 8B), differences among cost conditions were less evident.
+Even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 7B), differences among cost conditions were less evident.
 Moreover, these differences contradicted our predictions, as cognitive effort remained the least costly among demands.
@@
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference was the higher likelihood to accept cognitive offers compared to physical ones (Figure 7C; $\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
-Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 8D).
+Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 7D).
 An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r round(mixLogis_compare$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`).
@@
 ```{r Survival and prepost plots (Fig.
-8), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
+8), eval = FALSE, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 
-  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 10).
+  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 9).
 The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson's r = `r round(corDiff, digits = 2)`, *p* > 0.05).
@@
 ```{r Prepost mixed effects plots (Fig.
-9), fig.align = "center", fig.cap = "Acceptance rates over time.
+9), eval = FALSE, fig.align = "center", fig.cap = "Acceptance rates over time.
 Left: Proportion accepted in the first two and last two blocks of the experiment.
@@
 ## fit the OC model
-summaryOC <- list()
-summaryOC$all <- dataBtw %>%
+summaryOC_btw <- list()
+summaryOC_btw$all <- dataBtw %>%
                  group_by(Cost, SubjID) %>%
@@
 ## plot
-summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+summaryOC_btw$plot <- ggplot(summaryOC_btw$all, aes(Cost, Gamma, fill = Cost)) +
   # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
@@
 ## one sample t against optimal strategy
-summaryOC$t.test <- summaryOC$all %>%
+summaryOC_btw$t.test <- summaryOC_btw$all %>%
   select(Cost, Gamma) %>%
@@
 ## descriptive stats
-summaryOC$descriptives <- summaryOC$all %>%
+summaryOC_btw$descriptives <- summaryOC_btw$all %>%
   group_by(Cost) %>%
@@
 OCanova <- list()
-OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC$all))
+OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC_btw$all))
 Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
@@
 # Post-hoc pairwise tests
-OCanova$perms <- summaryOC$all %>%
+OCanova$perms <- summaryOC_btw$all %>%
   select(Cost, Gamma) %>%
@@
 
-OCanova$ES <- summaryOC$all %>%
+OCanova$ES <- summaryOC_btw$all %>%
   select(Cost, Gamma) %>%
@@
 # Compute the OC for pre-midpoint
-summaryOC$pre <- dataBtw %>%
+summaryOC_btw$pre <- dataBtw %>%
                  filter(Half == "Half_1") %>%
@@
 # let's add the gammas to the second half data and estimate prop predicted on the second half
-summaryOC$predicted <- dataBtw %>%
+summaryOC_btw$predicted <- dataBtw %>%
                  filter(Half == "Half_2") %>%
                  group_by(Cost, SubjID) %>%
-                 left_join(summaryOC$pre, by = "SubjID") %>%
+                 left_join(summaryOC_btw$pre, by = "SubjID") %>%
                  mutate(OC = Handling * Gamma,
@@
 # # plot
-# (summaryOC$predictPlot <- ggplot(summaryOC$predicted, aes(Cost, percentPredicted, fill = Cost)) +
+# (summaryOC_btw$predictPlot <- ggplot(summaryOC_btw$predicted, aes(Cost, percentPredicted, fill = Cost)) +
 #                             labs(x = "") +
@@
 Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
-This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC$all$Rsquared), digits = 2)`).
-Figure 7 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
+This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC_btw$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC_btw$all$Rsquared), digits = 2)`).
+Figure 10 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
 Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
@@
 We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
-We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 7; see Operationalization of Cost).
-Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC$t.test["p.value", "Wait"][[1]])`).
-Neither physical effort (mean = `r filter(summaryOC$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
+This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC_btw$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC_btw$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC_btw$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 10; see Operationalization of Cost).
+Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Wait"][[1]])`).
+Neither physical effort (mean = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
 These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
@@
 ```{r Gamma per cost group (Fig.
-7), fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
+10), eval = FALSE, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
 The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
@@
 
-summaryOC$plot
+summaryOC_btw$plot
 
@@
 # Estimate gamma per subject for each group separately
-summaryOC <- list()
-summaryOC$all <- dataWth %>%
+summaryOC_wth <- list()
+summaryOC_wth$all <- dataWth %>%
   mutate(Block = case_when(
@@
 # plot
-summaryOC$plot <- ggplot(summaryOC$all, aes(Cost, Gamma, fill = Cost)) +
+summaryOC_wth$plot <- ggplot(summaryOC_wth$all, aes(Cost, Gamma, fill = Cost)) +
     geom_boxplot(show.legend = F) +
@@
 # the estimate probability even matches actual proportions at the single subject level 
-# logis <- mapply(function(g, t) {1 / (1 + exp((-1 * t) * (c(4, 8, 20) - (g * 10))))}, summaryOC$all$Gamma, summaryOC$all$Temperature)
-# colnames(logis) <- unite(summaryOC, test, SubjID, Cost)$test
+# logis <- mapply(function(g, t) {1 / (1 + exp((-1 * t) * (c(4, 8, 20) - (g * 10))))}, summaryOC_wth$all$Gamma, summaryOC_wth$all$Temperature)
+# colnames(logis) <- unite(summaryOC_wth, test, SubjID, Cost)$test
 # logis2 <- as.data.frame(logis) %>% 
@@
 OCs_anova <- list()
-OCs_anova$aov <- summary(aov(Gamma ~ Cost + Error(SubjID / Cost), data = summaryOC$all))
+OCs_anova$aov <- summary(aov(Gamma ~ Cost + Error(SubjID / Cost), data = summaryOC_wth$all))
 
@@
 # do all pairwise comparisons
-OCs_anova$gammas <- summaryOC$all %>% 
+OCs_anova$gammas <- summaryOC_wth$all %>% 
   reshape2::dcast(SubjID ~ Cost, value.var = "Gamma") %>%
@@
 
-# *Points to cover* 
+### *Points to cover* 
 - The observed choice dynamics ruled out a number of explanatory candidates.
@@
 
+## Figures
+
+```{r New Trial plot (Fig.
+1), out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
+On each trial, participants were offered to earn money (4, 8, or 20 cents) by sustaining effort or waiting during the handling time (2, 10, or 14 s).
+The end of a trial was followed by a travel time (handling and travel times always added up to 16 s).
+Participants could skip unfavorable trials and immediately start traveling to a potentially better offer.
+In the between-subject experiment, cost was fixed per participant and handling time varied per block.
+In the within-subject version, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
+Possible costs, handling times, and rewards were fully disclosed in order to avoid experience-dependent learning."}
+
+include_graphics("./Images/FIG1_short.png")
+```
+
+\newpage
+
+```{r New Optimal plot (Fig.
+2), out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
+the smallest amount accepted) for each handling time.
+Circles denote the reward-maximizing threshold for each block, which is described in the table.
+Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers."}
+
+include_graphics("./Images/FIG2.png")
+```
+
+\newpage
+
+```{r New General prop & earnings plots (Fig.
+3), fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
+Middle: Total number of dollars earned by each group by the end of the experiment.
+Right: The relationship between proportion accepted and total earned.
+Consistent with the foraging design, participants who over and under accepted earned the least."}
+# plots generated in 16.2.1. and 16.1.3.
+ prop1 | earnings1 | earnFitplot_btw
+```
+
+\newpage
+
+```{r New mixed effects plots (Fig.
+4), out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
+A: Proportion accepted by each group for every combination of handling time and reward.
+Grey dots indicate the reward-maximizing acceptance for each combination.
+B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition (crosses mark non-significant comparisons).
+Each entry shows how much more likely a group was to accept compared to the reference condition (row).
+C: AIC and BIC values for a forward mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model."}
+#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
+include_graphics("./Images/FIG4.png")
+```
+
+\newpage
+
+```{r New Survival and prepost plots (Fig.
+5), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
+Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
+Dashed lines indicate the mean for each group.
+On the right, the proportion accepted over time per group.
+The order of blocks was repeated in the second half (indicated by the black dashed line)."}
+# plots generated in 16.3.1. and 16.3.2.
+(suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
+```
+
+\newpage
+
+```{r New Prepost mixed effects plot (Fig.
+6), fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
+Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
+Right: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal).
+Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
+include_graphics("./Images/FIG6.png")
+```
+
+\newpage
+
+```{r New Earnings/prop completed/ME plots (Fig.
+7), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
+B: proportion of acceptances of each reward per cost condition.
+C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount).
+Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions.
+Crosses mark non-significant comparisons.
+D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}
+
+include_graphics("./Images/FIG8.png")
+```
+
+\newpage
+
+```{r New Survival and prepost plots (Fig.
+8), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
+Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
+Dashed lines indicate the mean for each cost.
+On the right, the proportion accepted every time participants experienced a given block type."}
+# plots generated in 16.3.1. and 16.3.3.
+(suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
+```
+
+\newpage
+
+```{r New Prepost mixed effects plots (Fig.
+9), fig.align = "center", fig.cap = "Acceptance rates over time.
+Left: Proportion accepted in the first two and last two blocks of the experiment.
+An initial preference for cognitive effort trials fades amid a global decrease in acceptance rates.
+Right: Mixed effects coefficient matrix for each half separately.
+The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4)."}
+include_graphics("./Images/FIG10.png")
+```
+
+\newpage
+
+```{r New Gamma per cost group (Fig.
+10), fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
+The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
+Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
+
+summaryOC_btw$plot
+
+```
+
+\newpage
+
 ## References

### 2020-11-17 Cost_manuscript.Rmd
working a bit on discussion.

@@
 Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @Kool2010; @Westbrook2013].
-Although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across effort types [@Arulpragasam2018; @Chong2017; @Klein-Flugge2016; @Kool2018; @Prevost2010], and discount rates do not always correlate across cost domains [@Seaman2018; @Westbrook2013].
+Although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across effort types [@Arulpragasam2018; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and discount rates do not always correlate across cost domains [@Seaman2018; @Westbrook2013].
 However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context [@Kool2018].
@@
   Understanding the sporadic attractiveness of effortful options remains elusive.
-In this study, we tested the hypothesis that such appeal could depend on the ability to achieve the same outcome through different means (**not quite**).
+In this study, we tested the hypothesis that such appeal could depend on the ability to achieve the same outcome through different means.
 Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that 1) preferences for cognitive effort were stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
 
-  Our findings provided partial support for our pre-registered hypotheses, which can be found in https://osf.io/2rsgm/.
-In accord with our predictions, decision makers were successful in approximating reward-maximizing strategies, as evidenced by acceptance rates.
-This is in line with previous foraging experiments, where the main deviation from optimality is a tendency to overharvest.
-Unlike our first hypothesis, our predictions regarding differences among costs did not
-
-  Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment or whether they faced a single or intermixed demands.
-When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups under-accepted, partially matching our predictions and highlighting that cognitive effort can add value to outcomes.
-However, against our expectations, we found that a similar preference for cognitive effort disappeared over time as decision makers foraged for types of demands in addition to rewards.
-Computational modeling suggested that cognitive effort was valuable because it shortened the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands.
+  Our findings provided partial support for our pre-registered hypotheses, which can be found in https://osf.io/2rsgm/registrations.
+In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points.
+This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [constantino; hayden; wikenheiser; sweiss].
+This successful integration of the task was further evidenced by the ability of participants to post-experimentally describe near-optimal strategies, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [hayden; garrett; dundon].
+In contrast, our prediction that effort requirements would produce more acceptances was only true for the cognitive group, and this tendency for higher acceptances did not switch to passive delay as predicted for the within-subjects experiment.
+These hypotheses originally stemmed from a combination of pilot data, and prevalent theorizing that incentivized work should become more appealing [Eisenberger; Inzlicht], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; Olivola].
+Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands.
+The fact that preferences for cognitive effort were stable as predicted in the first experiment, and present at the beginning of the second experiment, further supported this idea.
+However, the gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.
+
+  These choice dynamics ruled out a number of explanatory candidates.
+For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
+Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (i.e.
+Ceyda; Laura; Cacioppo et al 1996).
+Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
+We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
+Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (learned industriousness, Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
+
+  We do not discard the influence of these elements in daily effort evaluations.
+Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands.
+Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2003], and are often experienced when we are fully immersed in a task [@czksdmsdkjdc].
 The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks).
 These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
+
+  The use of foraging paradigms....
 

### 2020-11-17 Simulations/manuscript_modeling.R

@@ -972,12 +972,13 @@ recalibrate_s <- function(S, alpha_s, choice) {
     #s[l + 1] <- alpha_s[l] * S[l] * a[l] + (1 - alpha_s[l]) * s[l]
     #s[l + 1] <- (alpha_s / l) * S[l] * a[l] + (1 - (alpha_s / l)) * s[l]
     #s[l + 1] <- s[l] + 1/l * (S[l] ^ a[l] - s[l]) # Sutton & Barto, page 37. Added cholce to S[l], such that no-experlenced blas estlmates back to 1 (l.e. nomlnal tlme)
-    #s[l + 1] <- s[l] + (1/l * (S[l] - s[l])) * a[l]
+    s[l + 1] <- s[l] + (1/l * (S[l] - s[l])) * a[l]
+    s[l + 1] <- s[l] + a[l] * (((1 - l / length(S)) ^ alpha_s) * (S[l] - s[l]))
     #s[l + 1] <- s[l] + (alpha_s/l * (S[l] - s[l])) * a[l]
-    left <- ((1 - alpha_s) ^ l) * s[1] ^ choice[1]
-    right <- alpha_s * (1 - alpha_s) ^ (l - seq(l)) * (S[seq(l)] ^ a[seq(l)])
-    right <- alpha_s * (1 - alpha_s) ^ (l - seq(l)) * ((S[seq(l)] * a[seq(l)]) + (dplyr::lag(s[seq(l)], default = 0)) * (1 - a[seq(l)])) # if trial isn't experienced, retain the i-1 s
-    s[l + 1] <-  left + sum(right)
+    #left <- ((1 - alpha_s) ^ l) * s[1] ^ choice[1]
+    #right <- alpha_s * (1 - alpha_s) ^ (l - seq(l)) * (S[seq(l)] ^ a[seq(l)])
+    #right <- alpha_s * (1 - alpha_s) ^ (l - seq(l)) * ((S[seq(l)] * a[seq(l)]) + (dplyr::lag(s[seq(l)], default = 0)) * (1 - a[seq(l)])) # if trial isn't experienced, retain the i-1 s
+    #s[l + 1] <-  left + sum(right)
     
     l <- l + 1
   }

### 2020-11-17 Cost_manuscript.Rmd
giving extra form to discussion (will probably change a bit once modeling results are evaluated)

@@
   Understanding the sporadic attractiveness of effortful options remains elusive.
-In this study, we tested the hypothesis that such appeal could depend on the ability to achieve the same outcome through different means.
-Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that 1) preferences for cognitive effort were stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
+In this study, we tested the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
+Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that 1) preferences for cognitive effort were stable when individuals faced a single form of demand, but faded over time when other costs were also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when tasks are interleaved.
 
@@
 This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [constantino; hayden; wikenheiser; sweiss].
-This successful integration of the task was further evidenced by the ability of participants to post-experimentally describe near-optimal strategies, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [hayden; garrett; dundon].
-In contrast, our prediction that effort requirements would produce more acceptances was only true for the cognitive group, and this tendency for higher acceptances did not switch to passive delay as predicted for the within-subjects experiment.
-These hypotheses originally stemmed from a combination of pilot data, and prevalent theorizing that incentivized work should become more appealing [Eisenberger; Inzlicht], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; Olivola].
+This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [hayden; garrett; dundon].
+In contrast, our prediction that effort requirements would produce more acceptances was only true for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment.
+These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [Eisenberger; Inzlicht], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; Olivola].
 Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands.
-The fact that preferences for cognitive effort were stable as predicted in the first experiment, and present at the beginning of the second experiment, further supported this idea.
-However, the gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.
-
-  These choice dynamics ruled out a number of explanatory candidates.
+The fact that predicted stable preferences for cognitive effort carried over onto the beginning of the within-subjects experiment further supported this idea.
+However, the unexpected gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.
+
+  These choice dynamics ruled out a number of common explanatory candidates.
 For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
-Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (i.e.
+The gradual choice convergence in the second experiment also discard the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that all our participants were high on need for cognition (i.e.
 Ceyda; Laura; Cacioppo et al 1996).
@@
 We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
-Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (learned industriousness, Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
-
-  We do not discard the influence of these elements in daily effort evaluations.
-Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands.
+Finally, the observed differences in acceptances between effort types cannot be explained by reward alone, as demands were rewarded at the same rate.
+
+  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations.
+Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (Cognitive effort gained value by making trials feel shorter).
 Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2003], and are often experienced when we are fully immersed in a task [@czksdmsdkjdc].
@@
 These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
-
-  The use of foraging paradigms....
-
-  Rather than comparing discounting functions among demands, allowing people to choose for them helped us control for a number of confounds.
-For example, effortful tasks often take longer to perform in everyday life.
-We eliminated this possibility by using a common handling time for all demands.
+....This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman).
+Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.
+
+  Our foraging paradigms allowed us to control for common shortfalls in the existing literature.
+For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving an outcome, investigations of the pursuit and receipt stages have been limited.
+Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [5,11,15,16,19].
+However, discrepancies between expected and experienced value are well known [20], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the future [3,21,22; hayden, mobbs?].
+Here we gave participants full knowledge of the available options, and provided an opportunity to actively experience the demands they accepted.
+Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time.
+This is often circumvented by comparing discounting functions and points at which individuals become indifferent to the increment in rewards [].
+Instead, we eliminated this possibility by fixating the handling time for all demands, which allowed us to probe people's preferences directly.
+In addition, the between-subjects experiment provided a baseline of foraging behavior, particularly in the traditional experimental case of foraging by waiting for the next reward [].
+This baseline helped us interpret the findings of the second experiment.
+Finally, the existence of optimal strategies let us know that people acted as if effort was attractive.
+This was evidenced by both the lower earnings by the cognitive effort group, and by the base OC model.
+Of note is that the optimality of the strategies produced by each cost depended on the richness of the block.
+This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
 
 ### *Points to cover*
-- The observed choice dynamics ruled out a number of explanatory candidates.
-For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
-Effort preferences due to boredom would not have shown the global acceptance decline and convergence in the within-subjects experiment, which also discards the possibility that all our participants were high on need for cognition (i.e.
-Ceyda; Laura; Cacioppo et al 1996).
-Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
-We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
-Noise also discarded (Hayden paper), as values on each end of the reward range moved little over time.
-Even though the reciprocal relationship between effort and outcome can often explain preferences for effort (learned industriousness, Inzlicht2018), the observed differences in acceptances between effort types and the eventual convergence of rates in the within-subjects study cannot be explained by reward alone, as demands were rewarded at the same rate.
-Instead, we proposed that subjective time sensitivity has been shown to play a role in temporal discounting, improving on classic hyperbolic fits (Mckelachar....).
-Our findings do not discard the influence of these elements in daily effort evaluations.
-It supplements our understanding of what drives peoples preferences.
+
+- A potential concern is that our cognitive and physical demands were not phenomenologically effortful.
+- Note that the calibration of efforts were different. We adjusted to people's physical capabilities, but trained them in the cognitive tasks until they reached criterion. 
 - We still think that cognitive and physical manipulations were effortful.
-Our physical effort task has been repeatedly used to probe effort.
-Similar task switching has been shown to feel cognitively effortful (Kool).
+Our physical effort task has been repeatedly used to probe effort [].
+Similar task switching has been shown to feel cognitively effortful by recruiting cognitive control (Kool, some amitai).
 Furthermore, the effortful nature of our manipulations is evidenced by the steeper decrease in acceptances over time at longer handling times (Treadway).
@@
 Or the OC.
-- Note that the calibration of efforts were different. We adjusted to people's physical capabilities, but trained them in the cognitive tasks until they reached criterion. 
-- Efficacy, along with reward amount, can influence how much control is exherted.
+- Efficacy, along with reward amount, can influence how much control is exherted. AFAIK, Eisenberger1982 provides evidence that task diversity motivates further effort engagement.
 - But here we do not focus on choosing the *amount* of cognitive control to be exherted during performance, which can be due to efficacy, agency, or reward amount.
 Instead, we focus on what makes people *pursue* the task in spite of how effortful it is.
+
 - Clinical: such deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
@@
 This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.
-- Control/Exp Design: Having a between-subjects experiment provided a baseline of foraging behavior that helped us interpret the findings of the second experiment
-- Control/Exp Design: for time as confound of effort
-- Control/Exp Design: having two efforts helped dissociate domain-general from task-specific features.
-- Control/Exp Design: participants were fully aware. This removed the possibility of asymmetric learning and choice difficulty. Demonstrated by stable strategies.
-- Control/Exp Design: in demand experiments, chosen options are often carried out after the experiment, but there are known discrepancies between expected and obtained value that could affect repeated decisions in real life.
-Alt from grant: Investigations of the pursuit and receipt stages have been comparatively limited.
-Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [5,11,15,16,19].
-However, discrepancies between expected and experienced value are well known [20], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards [3,21,22].
-Relying on a foraging paradigm allowed us to control for these and other variables...then control/exp design?
-- Control/Exp Design: even in TAFC tasks, selecting the shorter option could index a wish to find a better set of options
-- Control/Exp Design: Optimality let us know that people acted as if effort was attractive.
-This was evidenced by both the lower earnings by the cognitive effort group, and by the base OC model.
-Of note is that the optimality of the strategies produced by each cost depended on the richness of the block.
-This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
-- This appeal couldn't be explained by a number of explanatory candidates
-- This includes the often-cited reciprocal relationship between effort and reward
-- But it turns out subjective time fits the bill. 
-- Cognitive effort gained value by making trials feel shorter
-- This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman).
-Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.
+
 - do I even want to get into DA?
-- AFAIK, Eisenberger1982 provides evidence that task diversity motivates further effort engagement
 

### 2020-11-18 Cost_manuscript.Rmd
adding more references

@@
 In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points.
-This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [constantino; hayden; wikenheiser; sweiss].
-This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [hayden; garrett; dundon].
+This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013].
+This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [@Cash-Padgett2020; @Garrett2020; @Dundon2020].
 In contrast, our prediction that effort requirements would produce more acceptances was only true for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment.
-These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [Eisenberger; Inzlicht], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; Olivola].
+These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; @Olivola2013].
 Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands.
@@
 For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
-The gradual choice convergence in the second experiment also discard the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that all our participants were high on need for cognition (i.e.
-Ceyda; Laura; Cacioppo et al 1996).
+The gradual choice convergence in the second experiment also discard the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that all our participants were high on need for cognition [@Cacioppo1996; @Sayali2019].
 Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
-We also ruled out the sunk cost effects used to explain overharvesting (Wikenheiser2013; Sweiss2018), as participants expressed their choices as early as possible, resulting in occassional underharvesting.
+We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweiss2018], as participants expressed their choices as early as possible, resulting in occassional underharvesting.
 Finally, the observed differences in acceptances between effort types cannot be explained by reward alone, as demands were rewarded at the same rate.
@@
 Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (Cognitive effort gained value by making trials feel shorter).
-Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2003], and are often experienced when we are fully immersed in a task [@czksdmsdkjdc].
+Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2009], and are often experienced when we are fully immersed in a task [@Csikszentmihalyi2014].
 The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks).
@@
 For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving an outcome, investigations of the pursuit and receipt stages have been limited.
-Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [5,11,15,16,19].
-However, discrepancies between expected and experienced value are well known [20], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the future [3,21,22; hayden, mobbs?].
+Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a].
+However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the future [@Fawcett2012; @Frederick2002; @Sozou1998].
 Here we gave participants full knowledge of the available options, and provided an opportunity to actively experience the demands they accepted.
 Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time.
-This is often circumvented by comparing discounting functions and points at which individuals become indifferent to the increment in rewards [].
+This is often circumvented by comparing discounting functions and points at which individuals become indifferent to the increment in rewards [@Massar2015; @Prevost2010].
 Instead, we eliminated this possibility by fixating the handling time for all demands, which allowed us to probe people's preferences directly.

### 2020-11-19 Cost_manuscript.Rmd
new discussion paragraph

@@
   The base formulation lacked the flexibility needed to capture the dynamics observed in the within-subjects experiment.
-We therefore tested a second model which allowed $\gamma$ to evolve over time, adapting a learning rule from Constantino & Daw (2015)
+We therefore tested a second model which allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
 
@@
 $$\begin{aligned}
-mS_i = (s_i w_i) + (S_{demand} (1 - w_i))
+mS_i = s_i w_i + S_{demand} (1 - w_i)
 \end{aligned}$$
@@
 
-  Understanding the sporadic attractiveness of effortful options remains elusive.
+  Understanding the sporadic attractiveness of effortful demands remains elusive.
 In this study, we tested the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
@@
 For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
-The gradual choice convergence in the second experiment also discard the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that all our participants were high on need for cognition [@Cacioppo1996; @Sayali2019].
+The gradual choice convergence in the second experiment also discard the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our participants were demand seekers [@Cacioppo1996; @Sayali2019].
 Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
-We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweiss2018], as participants expressed their choices as early as possible, resulting in occassional underharvesting.
+We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweis2018], as participants expressed their choices as early as possible, resulting in occassional underharvesting.
 Finally, the observed differences in acceptances between effort types cannot be explained by reward alone, as demands were rewarded at the same rate.
@@
   Our foraging paradigms allowed us to control for common shortfalls in the existing literature.
-For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving an outcome, investigations of the pursuit and receipt stages have been limited.
-Many studies have sought to isolate the evaluation stage by presenting subjects with choices whose results do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a].
-However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the future [@Fawcett2012; @Frederick2002; @Sozou1998].
-Here we gave participants full knowledge of the available options, and provided an opportunity to actively experience the demands they accepted.
+For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving its outcome, investigations of the pursuit and receipt stages have been limited.
+Many studies have sought to isolate the evaluation stage by presenting individuals with offers that do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a].
+However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the near future [@Fawcett2012; @Frederick2002; @Sozou1998].
+We avoided these pitfalls by providing participants with an opportunity to actively experience the demands they accepted, and gave them full knowledge of the available options.
 Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time.
-This is often circumvented by comparing discounting functions and points at which individuals become indifferent to the increment in rewards [@Massar2015; @Prevost2010].
-Instead, we eliminated this possibility by fixating the handling time for all demands, which allowed us to probe people's preferences directly.
+This is often circumvented by comparing discounting functions, and points at which individuals become indifferent to the increment in rewards [@Massar2015; @Prevost2010].
+We eliminated this possibility by fixating the handling time for all demands, which allowed us to probe people's preferences directly.
 In addition, the between-subjects experiment provided a baseline of foraging behavior, particularly in the traditional experimental case of foraging by waiting for the next reward [].
 This baseline helped us interpret the findings of the second experiment.
-Finally, the existence of optimal strategies let us know that people acted as if effort was attractive.
-This was evidenced by both the lower earnings by the cognitive effort group, and by the base OC model.
+Finally, the existence of optimal strategies helped us identify when demands could be attractive, a central motivation for this study.
+The apparent attractiveness of cognitive effort was reflected both by a higher proportion of acceptances at the expense of earnings, and by comparisons of fitted opportunity costs against the optimal earning rate.
 Of note is that the optimality of the strategies produced by each cost depended on the richness of the block.
@@
 
+  It is possible that the task-switching configuration of the cognitive tasks was not effortful, maybe due to our calibration.
+Unlike adjusting to people's physical capabilities, we trained participants in the cognitive tasks until they reached criterion.
+Attributes such as the efficacy or capacity to complete a task, or the diversity of its requirements, have been reported to promote engagement [ivan; eisenberger].
+Even so, we believe our manipulations were successful in inducing feelings of effort.
+Hand grips are regularly used to probe physical effort [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to feel cognitively effortful by recruiting cognitive control [@Kool2010; @Shenhav2017].
+Furthermore, we observed a steeper decrease in acceptances over time at longer handling times, a hallmark of effortful decisions [@Treadway2009].
+Regardless, our focus here was not on the amount of effort exherted, but on what makes people pursue the task in spite of its toll.
+
 ### *Points to cover*
-
-- A potential concern is that our cognitive and physical demands were not phenomenologically effortful.
-- Note that the calibration of efforts were different. We adjusted to people's physical capabilities, but trained them in the cognitive tasks until they reached criterion. 
-- We still think that cognitive and physical manipulations were effortful.
-Our physical effort task has been repeatedly used to probe effort [].
-Similar task switching has been shown to feel cognitively effortful by recruiting cognitive control (Kool, some amitai).
-Furthermore, the effortful nature of our manipulations is evidenced by the steeper decrease in acceptances over time at longer handling times (Treadway).
-There are many reasons why such cognitive manipulations can be effortful, which are often centered in the amount of control.
-Or the OC.
-- Efficacy, along with reward amount, can influence how much control is exherted. AFAIK, Eisenberger1982 provides evidence that task diversity motivates further effort engagement.
-- But here we do not focus on choosing the *amount* of cognitive control to be exherted during performance, which can be due to efficacy, agency, or reward amount.
-Instead, we focus on what makes people *pursue* the task in spite of how effortful it is.
 

### 2020-11-19 Cost_manuscript.Rmd
tweaks

@@
 
+  The present findings provide theoretical advances as well as practical implementations.
+Talk clinical and practical.
+Practical could be motivating people to pursue challenges that produce desirable outcomes, like work, exercise etc.
+Much of the literature on the value of effort has suggested that it can be triggered by careful reward schedules.
+This doesn't always do (Eisenberger, Inzlicht).
+There is also the idea that training in certain tasks will have generaliing effects, which are not always true (Kable).
+We highlight an outcome-independent feature that is phenomenologically common (time sensitivity), and potentially easy to implement.
+
 ### *Points to cover*
@@
 - do I even want to get into DA?
+
+\newpage
 

### 2020-11-19 Cost_manuscript.Rmd
editing + having a switch to move figs to the end of manuscript

@@
 library(data.table)
+
+## figures at the end of the manuscropt?
+figsEnd <- FALSE
 
@@
 ```{r Trial plot (Fig.
-1), eval = FALSE, out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
+1), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
 On each trial, participants were offered to earn money (4, 8, or 20 cents) by sustaining effort or waiting during the handling time (2, 10, or 14 s).
@@
 ```{r Optimal plot (Fig.
-2), eval = FALSE, out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
+2), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
 the smallest amount accepted) for each handling time.
@@
 ```{r General prop & earnings plots (Fig.
-3), eval = FALSE, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
+3), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
 Middle: Total number of dollars earned by each group by the end of the experiment.
@@
 ```{r mixed effects plots (Fig.
-4), eval = FALSE, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
+4), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
 A: Proportion accepted by each group for every combination of handling time and reward.
@@
 ```{r Survival and prepost plots (Fig.
-5), eval = FALSE, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
+5), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r Prepost mixed effects plot (Fig.
-6), eval = FALSE, fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
+6), eval = !figsEnd, fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
 Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
@@
 ```{r Earnings/prop completed/ME plots (Fig.
-7), eval = FALSE, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
+7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
 B: proportion of acceptances of each reward per cost condition.
@@
 ```{r Survival and prepost plots (Fig.
-8), eval = FALSE, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
+8), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r Prepost mixed effects plots (Fig.
-9), eval = FALSE, fig.align = "center", fig.cap = "Acceptance rates over time.
+9), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time.
 Left: Proportion accepted in the first two and last two blocks of the experiment.
@@
 ```{r Gamma per cost group (Fig.
-10), eval = FALSE, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
+10), eval = !figsEnd, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
 The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
@@
 
-  Understanding the sporadic attractiveness of effortful demands remains elusive.
+  Understanding the sporadic attractiveness of effort remains elusive.
 In this study, we tested the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
@@
 
-  Our findings provided partial support for our pre-registered hypotheses, which can be found in https://osf.io/2rsgm/registrations.
+  Our findings provided partial support for our pre-registered hypotheses( https://osf.io/2rsgm/registrations).
 In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points.
@@
 This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [@Cash-Padgett2020; @Garrett2020; @Dundon2020].
-In contrast, our prediction that effort requirements would produce more acceptances was only true for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment.
+In contrast, our prediction that effort requirements would produce more acceptances only held for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment.
 These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; @Olivola2013].
 Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands.
-The fact that predicted stable preferences for cognitive effort carried over onto the beginning of the within-subjects experiment further supported this idea.
+The fact that predicted stable preferences for cognitive effort carried over onto the beginning of the within-subjects experiment further supported a task-specific modulation.
 However, the unexpected gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.
@@
 For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
-The gradual choice convergence in the second experiment also discard the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our participants were demand seekers [@Cacioppo1996; @Sayali2019].
+The gradual choice convergence in the second experiment also discards the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our population was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019].
 Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
-We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweis2018], as participants expressed their choices as early as possible, resulting in occassional underharvesting.
+We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweis2018], as participants expressed their choices early and rarely quit during the handling time.
 Finally, the observed differences in acceptances between effort types cannot be explained by reward alone, as demands were rewarded at the same rate.
@@
 
-  Our foraging paradigms allowed us to control for common shortfalls in the existing literature.
+  Relying on foraging paradigms helped us to control for common shortfalls in the existing literature.
 For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving its outcome, investigations of the pursuit and receipt stages have been limited.
@@
 However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the near future [@Fawcett2012; @Frederick2002; @Sozou1998].
-We avoided these pitfalls by providing participants with an opportunity to actively experience the demands they accepted, and gave them full knowledge of the available options.
+We circumvented these pitfalls by providing participants with an opportunity to actively experience the demands they accepted, and gaving them full knowledge of the available options.
 Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time.
-This is often circumvented by comparing discounting functions, and points at which individuals become indifferent to the increment in rewards [@Massar2015; @Prevost2010].
-We eliminated this possibility by fixating the handling time for all demands, which allowed us to probe people's preferences directly.
-In addition, the between-subjects experiment provided a baseline of foraging behavior, particularly in the traditional experimental case of foraging by waiting for the next reward [].
-This baseline helped us interpret the findings of the second experiment.
+This issue is often avoided by comparing discounting functions, which yield points at which individuals faced with increasing costs become indifferent to large rewards [@Massar2015; @Prevost2010].
+We eliminated this possibility by fixing the handling time for all demands, allowing us to probe people's preferences directly.
+Moreover, the between-subjects experiment, which resembled the traditional way costs are compared, provided a baseline of foraging behavior that contextualized the findings of the second experiment (a direct test of our hypothesis).
 Finally, the existence of optimal strategies helped us identify when demands could be attractive, a central motivation for this study.
 The apparent attractiveness of cognitive effort was reflected both by a higher proportion of acceptances at the expense of earnings, and by comparisons of fitted opportunity costs against the optimal earning rate.
-Of note is that the optimality of the strategies produced by each cost depended on the richness of the block.
+Of note is that the optimality of the strategies induced by each demand depended on the richness of the block.
 This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
 
-  It is possible that the task-switching configuration of the cognitive tasks was not effortful, maybe due to our calibration.
-Unlike adjusting to people's physical capabilities, we trained participants in the cognitive tasks until they reached criterion.
-Attributes such as the efficacy or capacity to complete a task, or the diversity of its requirements, have been reported to promote engagement [ivan; eisenberger].
+  It is possible that participants gravitated towards cognitive demands because the task configuration was not effortful.
+This could be due to differences in how we calibrated cognitive and physical tasks.
+For physical demands, we adjusted the gripping threshold to people's maximum strength, whereas we trained participants in the cognitive tasks until they reached criterion.
+Training might have improved response automaticity and reduce error-related risk.
+In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [ivan; eisenberger].
 Even so, we believe our manipulations were successful in inducing feelings of effort.
 Hand grips are regularly used to probe physical effort [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to feel cognitively effortful by recruiting cognitive control [@Kool2010; @Shenhav2017].
-Furthermore, we observed a steeper decrease in acceptances over time at longer handling times, a hallmark of effortful decisions [@Treadway2009].
-Regardless, our focus here was not on the amount of effort exherted, but on what makes people pursue the task in spite of its toll.
+Furthermore, we observed a steeper decrease in acceptances over time at longer handling times, a hallmark of effortful exhertion [@Treadway2009].
 
@@
 This doesn't always do (Eisenberger, Inzlicht).
-There is also the idea that training in certain tasks will have generaliing effects, which are not always true (Kable).
+There is also the idea that training in certain tasks will have generalizing effects, which are not always true (Kable).
 We highlight an outcome-independent feature that is phenomenologically common (time sensitivity), and potentially easy to implement.
 
+  advancing the field: rather than purely framing effort and delay as costs, here we let people decide what they prefer, and wrap it in a computational framework that tells us when costs are actually valuable.
 ### *Points to cover*
+
+- Regardless, our focus here was not on the amount of effort exherted, but on what makes people pursue the task in spite of its toll.
 
@@
 ```{r New Trial plot (Fig.
-1), out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
+1), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
 On each trial, participants were offered to earn money (4, 8, or 20 cents) by sustaining effort or waiting during the handling time (2, 10, or 14 s).
@@
 ```{r New Optimal plot (Fig.
-2), out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
+2), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
 the smallest amount accepted) for each handling time.
@@
 ```{r New General prop & earnings plots (Fig.
-3), fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
+3), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
 Middle: Total number of dollars earned by each group by the end of the experiment.
@@
 ```{r New mixed effects plots (Fig.
-4), out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
+4), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
 A: Proportion accepted by each group for every combination of handling time and reward.
@@
 ```{r New Survival and prepost plots (Fig.
-5), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
+5), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r New Prepost mixed effects plot (Fig.
-6), fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
+6), eval = figsEnd, fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
 Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
@@
 ```{r New Earnings/prop completed/ME plots (Fig.
-7), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
+7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
 B: proportion of acceptances of each reward per cost condition.
@@
 ```{r New Survival and prepost plots (Fig.
-8), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
+8), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r New Prepost mixed effects plots (Fig.
-9), fig.align = "center", fig.cap = "Acceptance rates over time.
+9), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time.
 Left: Proportion accepted in the first two and last two blocks of the experiment.
@@
 ```{r New Gamma per cost group (Fig.
-10), fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
+10), eval = figsEnd, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
 The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.

### 2020-11-20 Cost_manuscript.Rmd
adding clinical details

@@
 
-  Our findings provided partial support for our pre-registered hypotheses( https://osf.io/2rsgm/registrations).
+  Our findings provided partial support for our pre-registered hypotheses (https://osf.io/2rsgm/registrations).
 In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points.
@@
 Training might have improved response automaticity and reduce error-related risk.
-In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [ivan; eisenberger].
+In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [@Bandura2010; @Grahek2020; eisenberger].
 Even so, we believe our manipulations were successful in inducing feelings of effort.
@@
 
-  advancing the field: rather than purely framing effort and delay as costs, here we let people decide what they prefer, and wrap it in a computational framework that tells us when costs are actually valuable.
+.
+
 ### *Points to cover*
@@
 
-- Clinical: such deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains).
+- Clinical:  Medicated patients in remission are more sensitive to effort than controls (and are not as motivated by rewards?), and this sensitivity is predictive of relapse [@Berwian2020].
+Encouraging/increasing activities has been found to be a helpful treatment for depression [@Dimidjian2006].
+Since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases.
+Our work suggests that subdividing a task can promote its pursual either by taxing working memory, counting, or simply distracting.
+Moreover, The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler).
+This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.
+
+, and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia
+
+(https://link.springer.com/chapter/10.1007%2F978-3-030-27473-3_5).
 Like, the aversion is due to focusing on different elements of the task.

### 2020-11-23 Simulations/manuscript_modeling.R
interim updates

@@ -1042,7 +1042,8 @@ colsWth <- c("#D9541A", "#78AB05", "dodgerblue4", "deepskyblue3")#"grey30", "gre
 lthick = 2 # line thickness for plots
 
 ######## LOAD DATA
-setwd("../Cost2/data")
+dir = rstudioapi::getActiveDocumentContext()$path
+setwd(file.path(dirname(dirname(dir)), "Cost2", "data"))
 files <- dir(pattern = '_log.csv')
 
 # load data
@@ -1083,7 +1084,7 @@ nSubjs_btw <- length(subjList_btw)
 
 # First looks at the new data
 # The RT is upper-bounded because a glitch in the code made one 10s last 14s
-setwd('../../Cost3/data/')
+setwd(file.path(dirname(dirname(dir)), "Cost3", "data"))
 files <- dir(pattern = 'main_log.csv')
 
 # load the data and remove extreme subjects
@@ -1132,7 +1133,7 @@ subjList_wth <- unique(dataWth$SubjID)
 nSubjs_wth <- length(subjList_wth)
 
 ### MODELS
-setwd('../..')
+setwd(dirname(dirname(dir)))
 
 # what makes this run unique?
 qualifier <- "publishable_allModels"
@@ -1600,9 +1601,7 @@ abline(0, 1)
 
 
 
-
-
-save.image(paste("/restricted/projectnb/cd-lab/Claudio/Cost_studies/data_", Sys.Date(), "_", qualifier, ".RData", sep = ""))
+save.image(paste(dirname(dir), "/data_", Sys.Date(), "_", qualifier, ".RData", sep = ""))
 
 
 

### 2020-11-23 models_gk/em.R

@@ -1,0 +1,210 @@
+#' em
+#'
+#' Run expectation maximization algorithm to fit parameters to each subject of an experiment
+#'
+#' @param dat data.frame; data
+#' @param subs string vector; subject ids
+#' @param mus vector; starting mean parameters
+#' @param sigma vector; starting sd in parameter
+#' @param likfun function; the objective function
+#'
+#' @export
+em = function(dat, subs, mus, sigma, likfun, emtol = 1e-3, maxiter = 100, lower = -Inf, upper = Inf, parallel = F, print = T, ...){
+  
+  nparam = length(mus)
+  
+  ### set up design matrix and sigma matrix ###
+  dm = designmatrix(nparam, length(subs))
+  sigma = Matrix::Diagonal(length(sigma), sigma)
+  
+  ### first iteration ###
+  oldparams = c(mus, diag(sigma))
+  fit = estep(dat, subs, mus, sigma, likfun, lower = lower, upper = upper, parallel = parallel, ...)
+  par_list = mstep(fit$x, dm, fit$h, sigma)
+  mus = par_list$mus
+  sigma = par_list$sigma
+  newparams = c(mus, diag(sigma))
+  
+  
+  ### repeat until convergence ###
+  iter = 1
+  while(max(abs((newparams-oldparams)/oldparams)) > emtol & iter < maxiter){
+    iter = iter + 1
+    oldparams = newparams
+    
+    fit = estep(dat, subs, mus, sigma, likfun, startx = fit$x, lower = lower, upper = upper, parallel = parallel, ...)
+    par_list = mstep(fit$x, dm, fit$h, sigma)
+    mus = par_list$mus
+    sigma = par_list$sigma
+    newparams = c(mus, diag(sigma))
+    
+    if(print){
+      cat("\n")
+      cat("iter:", iter, "\n")
+      cat("mus:", round(mus, 5), "\n")
+      cat("sigma:", round(diag(sigma), 5), "\n")
+      cat("change:", round(abs((newparams-oldparams)/oldparams), 5), "\n")
+      cat("max:", round(max(abs((newparams-oldparams)/oldparams)), 5), "\n")
+    }
+  }
+  
+  list(mus = mus, sigma = sigma, x = fit$x, l = fit$l, h = fit$h)
+}
+
[…]

### 2020-11-23 models_gk/likelihoods.R

@@ -1,36 +1,283 @@
 ### define likelihood functions
 
-time_sensitivity_lik = function(R_i, H_i, Choice, gamma, beta) {
-  p_accept = 1 / (1 + exp(-beta * (R_i - gamma * H_i)))
-  p_choice = ifelse(as.logical(Choice), p_accept, 1-p_accept)
-  p_choice
-}
+# Rcpp::sourceCpp(file.path(dirname(sys.frame(1)$ofile), "likelihoods.cpp"))
 
-time_sensitivity_rate_lik = function(R_i, H_i, T_i, Choice, gamma, beta, Block=NULL) {
-  accept_rate = R_i / (gamma * H_i + T_i)
+cost_p <- function(dat,
+                   cost = 0,
+                   s = 1,
+                   beta = 1,
+                   alpha = 0,
+                   C = NA,
+                   S = NA,
+                   w_decay = 0,
+                   gamma = NA,
+                   return_pacc = F) {
   
-  if(is.null(Block)){
-    global_rate = sum(R_i * Choice) / sum(gamma * H_i * Choice + T_i)
-  } else {
-    blocks = unique(Block)
-    global_rate = numeric(length(R_i))
-    for (i in unique(block)) {
-      global_rate[Block==i] = sum(R_i[Block==i] * Choice[Block==i]) / sum(gamma * H_i[Block==i] * Choice[Block==i] + T_i[Block==i])
+  n_trials = dat[, .N]
+  R_i = dat[, Offer]
+  H_i = dat[, HandleTime]
+  C_i = dat[, Choice]
+  T_i = dat[, TravelTime]
+  if(is.na(gamma)) {
+    gamma = mean(dat[, RR])
+  }
+  
+  if (alpha > 0) {
+    for (i in 1:((length(R_i)) - 1)) {
+      tau <- H_i[i]^s[i] * C_i[i] + T_i[i]
+      gamma[i + 1] <- (1 - (1 - alpha)^tau) * ((R_i[i] * C_i[i]) / tau) + ((1 - alpha)^tau * gamma[i])
     }
   }
   
-  p_accept = 1 / (1 + exp(-beta * (accept_rate - global_rate)))
-  p_choice = ifelse(as.logical(Choice), p_accept, 1-p_accept)
-  p_choice
+  w_t = ((n_trials - 1:n_trials) / n_trials) ^ w_decay
+  
+  if(!is.na(C)) {
[…]

### 2020-11-23 models_gk/likelihoods.cpp

@@ -1,0 +1,128 @@
+#include <Rcpp.h>
+using namespace Rcpp;
+
+
+NumericVector vecpow(const NumericVector base, const NumericVector exp) {
+  NumericVector out(base.size());
+  std::transform(base.begin(), base.end(),
+                 exp.begin(), out.begin(), ::pow);
+  return out;
+}
+
+// [[Rcpp::export]]
+NumericVector cost_p_cpp(DataFrame dat,
+                         NumericVector cost=NumericVector::create(0),
+                         NumericVector s=NumericVector::create(1),
+                         double beta=1,
+                         double alpha=0,
+                         double C = NA_REAL,
+                         double S = NA_REAL,
+                         double w_decay = 0,
+                         double gamma = NA_REAL,
+                         bool return_pacc=false) {
+  
+  NumericVector R_i = dat["Offer"],
+                H_i = dat["HandleTime"],
+                C_i = dat["Choice"],
+                T_i = dat["TravelTime"];
+  if (NumericVector::is_na(gamma)) {
+    NumericVector rr = dat["RR"];
+    gamma = mean(rr);
+  }
+  
+  int n_trials = R_i.size();
+  
+  NumericVector gvec(n_trials);
+  if (alpha > 0) {
+    gvec[0] = gamma;
+    for (int i=0; i<n_trials-1; i++) {
+      double tau = pow(H_i[i],s[i]) * C_i[i] + T_i[i];
+      gvec[i+1] = (1 - pow(1 - alpha, tau)) * ((R_i[i] * C_i[i]) / tau) + (pow(1 - alpha, tau) * gvec[i]);
+    }
+  } else {
+    gvec.fill(gamma);
+  }
+  
+  IntegerVector trial_vec = seq_len(n_trials);
+  NumericVector w_t = pow((n_trials - as<NumericVector>(trial_vec)) / n_trials, w_decay);
+
+  if (cost.length() == 1) {
+    cost = rep(cost, n_trials);
+  }
+  if(!NumericVector::is_na(C)) {
+    cost = cost * w_t + C * (1 - w_t);
+  }
+
+  if(s.length() == 1) {
+    s = rep(s, n_trials);
+  }
+  if(!NumericVector::is_na(S)) {
+    s = s * w_t + S * (1 - w_t);
+  }
+
[…]

### 2020-11-23 models_gk/modeling_gk.R

@@ -7,84 +7,66 @@ setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
 
 library(data.table)
 library(foreach)
+library(rextras)
+library(zeallot)
+library(modelfitr)
+library(GaussExMax)
 
-reload = function(){
-  library(modelfitr)
-  detach("package:modelfitr", unload=T)
-  library(modelfitr)
-}
-reload()
-
+source('models_gk/load_data.R')
 source('models_gk/likelihoods.R')
 
 #########################
 ### Load Data
 #########################
 
-dir_btw = 'Cost2/data'
-f_btw = list.files(dir_btw, pattern=".csv", full.names=T)
-dat_btw = foreach(f = f_btw, .combine=rbind) %do% {
-  info = strsplit(basename(f), "_")[[1]]
-  data.table(sub=info[1], cond=info[2], date=info[3], fread(f))
-}
-dat_btw[, Travel := 16-Handling]
-
-# dir_wth = 'Cost3/data'
-# f_wth = list.files(dir_wth, pattern="main_log*.csv", full.names=T)
-# dat_wth = foreach(f = f_wth, .combine=rbind) %do% {
-#   info = strsplit(basename(f), "_")[[1]]
-#   data.table(sub=info[1], cond=info[2], date=info[3], fread(f))
-# }
+c(dat_btw, dat_wth) %<-% load_data()
 
 #########################
-### Fit time sensitivity model
+### Fit opportunity cost model
 #########################
 
 par_values = c(gamma = 1, beta = .1)
+par_names = c("gamma", "beta")
 
-reload()
 system.time(fits_btw <- dat_btw[,
                                 modelfitr::fit_model(
-                                  get_lik,
+                                  cost_lik,
                                   log(par_values),
                                   hessian=T,
+                                  package="optimx",
                                   method="nmkb",
                                   obj_args=list(
-                                    lfun=time_sensitivity_lik,
-                                    R_i=Offer,
-                                    H_i=Handling,
-                                    Choice=Choice,
+                                    dat=.SD,
+                                    par_names=par_names,
                                     log_par=T
                                   ),
                                   aic=T,
                                   bic=T,
                                   n_obs=.N,
-                                  return_df=T),
[…]

### 2020-11-23 models_gk/modeling_gk_btw.R

@@ -1,0 +1,147 @@
+#########################
+### Setup
+#########################
+
+# set wd
+setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
+
+library(data.table)
+library(foreach)
+library(rextras)
+library(zeallot)
+library(modelfitr)
+library(GaussExMax)
+
+source('models_gk/load_data.R')
+source('models_gk/likelihoods.R')
+
+#########################
+### Load Data
+#########################
+
+c(dat_btw, dat_wth) %<-% load_data_full()
+fit_cols = c("sub", "cond", "Offer", "Choice", "HandleTime", "TravelTime", "condCode")
+dat_btw[, Subject := sub]
+
+#########################
+### plot between subjects behavior
+#########################
+
+mean_sub_btw = dat_btw[, .(Choice = mean(Choice)), .(sub, cond, Handling, Offer)]
+plot_btw(mean_sub_btw)
+
+#########################
+### Fit super base model -- optimal values + decision noise
+#########################
+
+par_names_base = c("beta")
+mus_base = c("beta" = 0.1)
+sigma_base = c(1)
+
+system.time(fits_btw_base <- dat_btw[, em(.SD,
+                                          log(mus_base),
+                                          sigma_base,
+                                          cost_lik,
+                                          lower = -100,
+                                          upper = 100,
+                                          package = "optim",
+                                          method = "Brent",
+                                          bic=TRUE,
+                                          ndata=.SD[, .N],
+                                          obj_args = list(
+                                            par_names=par_names_base,
+                                            log_par=T
+                                          ),
+                                          verbose = F,
+                                          return_ind_df=T),
+                                     .(cond)])
+
+fits_btw_base_predict = get_all_predictions(dat_btw, fits_btw_base, par_names_base, log_par=T, return_mean=T)
+plot_btw(fits_btw_base_predict, title="Base Model (MVT + Noise)")
+plot_params(fits_btw_base, par_names_base, exp_par=T)
+
+
+#########################
+### Fit base opportunity cost model
+#########################
+
+par_names_oc = c("gamma", "beta")
+mus_oc = c("gamma" = 1, "beta" = .1)
+sigma_oc = c(1, 1)
+
+system.time(fits_btw_oc <- dat_btw[, em(.SD,
+                                        log(mus_oc),
+                                        sigma_oc,
+                                        cost_lik,
[…]

### 2020-11-23 models_gk/modeling_gk_old.R

@@ -1,0 +1,172 @@
+#########################
+### Setup
+#########################
+
+# set wd
+setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
+
+library(data.table)
+library(foreach)
+library(rextras)
+library(zeallot)
+library(modelfitr)
+library(GaussExMax)
+
+source('models_gk/load_data.R')
+source('models_gk/likelihoods.R')
+
+#########################
+### Load Data
+#########################
+
+c(dat_btw, dat_wth) %<-% load_data()
+
+#########################
+### Fit opportunity cost model
+#########################
+
+# par_values = c(gamma = 1, beta = .1)
+# par_names = c("gamma", "beta")
+# 
+# system.time(fits_btw <- dat_btw[,
+#                                 modelfitr::fit_model(
+#                                   cost_lik,
+#                                   log(par_values),
+#                                   hessian=T,
+#                                   package="optimx",
+#                                   method="nmkb",
+#                                   obj_args=list(
+#                                     dat=.SD,
+#                                     par_names=par_names,
+#                                     log_par=T
+#                                   ),
+#                                   aic=T,
+#                                   bic=T,
+#                                   n_obs=.N,
+#                                   return_df=T),
+#                                 .(sub, cond),
+#                                 .SDcols=names(dat_btw)
+# ])
+# 
+# for (i in par_names) fits_btw[[i]] = exp(fits_btw[[i]])
+# 
+# fits_btw_melt = melt(fits_btw, measure.vars=c("gamma", "beta"), variable.name="par", value.name="val")
+# ggplot(fits_btw_melt, aes(x=cond, y=val)) +
+#   facet_wrap(~par, scales="free") +
+#   geom_violin() +
+#   theme_abw()
+# 
+# 
+# ### get model predictions for each subject and condition
+# 
+# for (subj in unique(dat_btw[, sub])) {
+#   for (cond in unique(dat_btw[, cond])) {
+#     dat_btw[sub==subj & cond ==cond, predict_accept := cost_lik(fits_btw[sub==subj & cond==cond, c(gamma, beta)],
[…]

### 2020-11-23 models_gk/modeling_gk_wth.R

@@ -1,0 +1,236 @@
+#########################
+### Setup
+#########################
+
+# set wd
+setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
+
+load("models_gk/results/wth.Rdata")
+
+library(data.table)
+library(foreach)
+library(rextras)
+library(zeallot)
+library(modelfitr)
+library(GaussExMax)
+
+source('models_gk/load_data.R')
+source('models_gk/likelihoods.R')
+
+#########################
+### Load Data
+#########################
+
+c(dat_btw, dat_wth) %<-% load_data_full()
+dat_wth[, Subject := sub]
+
+#########################
+### plot within subjects behavior
+#########################
+
+mean_sub_wth = dat_wth[Block %in% c(1,2,5,6), .(Choice = mean(Choice)), .(sub, cond, half, first, BlockType, Handling, Offer)]
+
+plot_wth(mean_sub_wth)
+
+# glm1 = lme4::glmer(data=dat_wth, Choice ~ 1 + Offer*cond*half*first + (1 | sub), family=binomial)
+# summary(glm1)
+#
+# phia::testInteractions(glm1, pairwise="cond")
+# phia::testInteractions(glm1, pairwise="half")
+# phia::testInteractions(glm1, pairwise="first")
+# phia::testInteractions(glm1, across="cond", pairwise="half")
+# phia::testInteractions(glm1, across="cond", pairwise="first")
+
+#########################
+### Fit super base model -- optimal values + decision noise
+#########################
+
+par_names_base = c("beta")
+mus_base = c("beta" = 0.1)
+sigma_base = c(1)
+
+system.time(fits_wth_base_em <- em(dat_wth,
+                                   log(mus_base),
+                                   sigma_base,
+                                   cost_lik,
+                                   lower = -100,
+                                   upper = 100,
+                                   package = "optim",
+                                   method = "Brent",
+                                   bic=TRUE,
+                                   ndata=dat_wth[, .N],
+                                   obj_args = list(
+                                     par_names=par_names_base,
+                                     log_par=T
+                                   ),
+                                   parallel=F,
+                                   verbose = F,
+                                   return_ind_df=T))
+
[…]

### 2020-11-23 models_gk/em.R
clean up models_gk dir

@@ -1,210 +1,0 @@
-#' em
-#'
-#' Run expectation maximization algorithm to fit parameters to each subject of an experiment
-#'
-#' @param dat data.frame; data
-#' @param subs string vector; subject ids
-#' @param mus vector; starting mean parameters
-#' @param sigma vector; starting sd in parameter
-#' @param likfun function; the objective function
-#'
-#' @export
-em = function(dat, subs, mus, sigma, likfun, emtol = 1e-3, maxiter = 100, lower = -Inf, upper = Inf, parallel = F, print = T, ...){
-  
-  nparam = length(mus)
-  
-  ### set up design matrix and sigma matrix ###
-  dm = designmatrix(nparam, length(subs))
-  sigma = Matrix::Diagonal(length(sigma), sigma)
-  
-  ### first iteration ###
-  oldparams = c(mus, diag(sigma))
-  fit = estep(dat, subs, mus, sigma, likfun, lower = lower, upper = upper, parallel = parallel, ...)
-  par_list = mstep(fit$x, dm, fit$h, sigma)
-  mus = par_list$mus
-  sigma = par_list$sigma
-  newparams = c(mus, diag(sigma))
-  
-  
-  ### repeat until convergence ###
-  iter = 1
-  while(max(abs((newparams-oldparams)/oldparams)) > emtol & iter < maxiter){
-    iter = iter + 1
-    oldparams = newparams
-    
-    fit = estep(dat, subs, mus, sigma, likfun, startx = fit$x, lower = lower, upper = upper, parallel = parallel, ...)
-    par_list = mstep(fit$x, dm, fit$h, sigma)
-    mus = par_list$mus
-    sigma = par_list$sigma
-    newparams = c(mus, diag(sigma))
-    
-    if(print){
-      cat("\n")
-      cat("iter:", iter, "\n")
-      cat("mus:", round(mus, 5), "\n")
-      cat("sigma:", round(diag(sigma), 5), "\n")
-      cat("change:", round(abs((newparams-oldparams)/oldparams), 5), "\n")
-      cat("max:", round(max(abs((newparams-oldparams)/oldparams)), 5), "\n")
-    }
-  }
-  
-  list(mus = mus, sigma = sigma, x = fit$x, l = fit$l, h = fit$h)
-}
-
[…]

### 2020-11-23 models_gk/manuscript_modeling.R

@@ -1,1638 +1,0 @@
-#!/usr/bin/env Rscript
-
-# using NLOPTR is pointless here
-# instead I'm just going to feed any sensible combination of parameters to the model and minimize the negLL manually
-# simpler, can evaluate models easier, and faster
-# for tomorrow: have negloglik return the parameters per iteration
-# the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
-# maybe also R-squares and things in the current optimization function
-
-#$ -pe omp 28
-
-## libraries
-library(tidyverse)
-library(ggfortify)
-library(knitr)
-library(pander) 
-library(nloptr)
-#library(pwr)
-library(lme4)
-#library(lmerTest)
-library(gridExtra)
-library(reshape2)
-library(corrplot)
-#library(survival)
-library(ggfortify)
-#library(patchwork)
-library(data.table)
-library(parallel)
-
-# remove break time and start counting from 0
-standardize_time <- function(subjData) {
-  # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
-  breakTime <- min(subjData$ExpTime[subjData$Block == 4]) - max(subjData$ExpTime[subjData$Block == 3])
-  subjData$ExpTime[which(subjData$Block > 3)] <- subjData$ExpTime[which(subjData$Block > 3)] - breakTime + 16
-  subjData$ExpTime <- subjData$ExpTime - min(subjData$ExpTime)
-  
-  return(subjData)
-}
-
-# summary matrices for refrence-changing models
-betaMatrix <- function(model, rearrange = NA) {
-  # get a similarity matrix of the resulting coefficient pairings for the cost conditions
-  # first, do a full_join based on column names on the list of coefficient vectors from each dummy code relevel
-  # then match the names of columns and rows so NAs are in the diagonal
-  
-  # get the names of the reference group per model iteration
-  refnames <- names(model)
-  
-  # coefficient matrix
-  temp <- lapply(model, function(data) {coefficients(data)$SubjID[1, 2:4]})
-  mixCoeffs <- bind_rows(temp) 
[…]

### 2020-11-23 models_gk/modeling_gk.R

@@ -1,72 +1,0 @@
-#########################
-### Setup
-#########################
-
-# set wd
-setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
-
-library(data.table)
-library(foreach)
-library(rextras)
-library(zeallot)
-library(modelfitr)
-library(GaussExMax)
-
-source('models_gk/load_data.R')
-source('models_gk/likelihoods.R')
-
-#########################
-### Load Data
-#########################
-
-c(dat_btw, dat_wth) %<-% load_data()
-
-#########################
-### Fit opportunity cost model
-#########################
-
-par_values = c(gamma = 1, beta = .1)
-par_names = c("gamma", "beta")
-
-system.time(fits_btw <- dat_btw[,
-                                modelfitr::fit_model(
-                                  cost_lik,
-                                  log(par_values),
-                                  hessian=T,
-                                  package="optimx",
-                                  method="nmkb",
-                                  obj_args=list(
-                                    dat=.SD,
-                                    par_names=par_names,
-                                    log_par=T
-                                  ),
-                                  aic=T,
-                                  bic=T,
-                                  n_obs=.N,
-                                  return_df=T,
-                                  verbose = T),
-                                .(sub, cond),
-                                .SDcols=names(dat_btw)
-])
-
-### get model predictions for each subject and condition
-
-get_all_predictions(dat_btw, fits_btw, par_names, log_par=T)
-
-mean_dat_btw = dat_btw[, .(Choice = mean(Choice),
-                           predict_accept = mean(predict_accept)),
-                       .(sub, cond, Handling, Offer)]
-
-ggplot(mean_dat_btw, aes(x=Offer, y=Choice, color=cond, fill=cond)) +
-  facet_wrap(~Handling) +
-  stat_summary(fun=mean, geom="point") +
-  stat_summary(fun.data=mean_se, geom="errorbar", width=2) +
-  stat_summary(aes(y=predict_accept), fun=mean, geom="line") +
-  stat_summary(aes(y=predict_accept), fun.data=mean_se, geom="ribbon", color=NA, alpha=.2) +
-  scale_y_continuous("p(accept)", breaks=seq(0, 1, .2)) +
-  coord_cartesian(ylim=c(0,1)) +
-  ggtitle("Base opportunity cost") +
-  theme_abw() +
-  theme(plot.title = element_text(hjust=0.5))
-
-

### 2020-11-23 models_gk/modeling_gk_old.R

@@ -1,172 +1,0 @@
-#########################
-### Setup
-#########################
-
-# set wd
-setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
-
-library(data.table)
-library(foreach)
-library(rextras)
-library(zeallot)
-library(modelfitr)
-library(GaussExMax)
-
-source('models_gk/load_data.R')
-source('models_gk/likelihoods.R')
-
-#########################
-### Load Data
-#########################
-
-c(dat_btw, dat_wth) %<-% load_data()
-
-#########################
-### Fit opportunity cost model
-#########################
-
-# par_values = c(gamma = 1, beta = .1)
-# par_names = c("gamma", "beta")
-# 
-# system.time(fits_btw <- dat_btw[,
-#                                 modelfitr::fit_model(
-#                                   cost_lik,
-#                                   log(par_values),
-#                                   hessian=T,
-#                                   package="optimx",
-#                                   method="nmkb",
-#                                   obj_args=list(
-#                                     dat=.SD,
-#                                     par_names=par_names,
-#                                     log_par=T
-#                                   ),
-#                                   aic=T,
-#                                   bic=T,
-#                                   n_obs=.N,
-#                                   return_df=T),
-#                                 .(sub, cond),
-#                                 .SDcols=names(dat_btw)
-# ])
-# 
-# for (i in par_names) fits_btw[[i]] = exp(fits_btw[[i]])
-# 
-# fits_btw_melt = melt(fits_btw, measure.vars=c("gamma", "beta"), variable.name="par", value.name="val")
-# ggplot(fits_btw_melt, aes(x=cond, y=val)) +
-#   facet_wrap(~par, scales="free") +
-#   geom_violin() +
-#   theme_abw()
-# 
-# 
-# ### get model predictions for each subject and condition
-# 
-# for (subj in unique(dat_btw[, sub])) {
-#   for (cond in unique(dat_btw[, cond])) {
-#     dat_btw[sub==subj & cond ==cond, predict_accept := cost_lik(fits_btw[sub==subj & cond==cond, c(gamma, beta)],
[…]

### 2020-11-23 Cost_manuscript.Rmd
minor clinical deets

@@
 # rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))}) 
+# mean(apply(rwdRates, 1, max))
 # 
@@
 
-.
-
 ### *Points to cover*
@@
 
-- Clinical:  Medicated patients in remission are more sensitive to effort than controls (and are not as motivated by rewards?), and this sensitivity is predictive of relapse [@Berwian2020].
+- Clinical: Te motivation to exert effort or wait for delays is a distinguishing factor among mental afflictions like depression and schizophrenia [@Barch2019].
+Within the former, medicated patients in remission are more sensitive to effort than controls (and are not as motivated by rewards?), and this sensitivity is predictive of relapse [@Berwian2020].
 Encouraging/increasing activities has been found to be a helpful treatment for depression [@Dimidjian2006].
@@
 - do I even want to get into DA?
+
+- It's maybe relevant that waiting is goal oriented (you don't sit around for its own sake), but activities are pursued for their own appeal.
+*like, waiting is a goal oriented activity, but effort can be the goal itself.* in this sense it makes sense to study delays in terms of their modulation of the value of prospects, but we have unnecessarily adopted this view for ethe study of ffort, thinking of it mostly as a cost.
+Even if their discounting properties are similar, their resulting behavior can be contrasting (apathy vs impulsivity), and they're impacted differently by mental illness (adhd amygdala paper).
+Also, it's not just that we would rather to fill in empty periods of waiting, but how.
 

### 2020-11-23 Cost_manuscript.Rmd
specifying exp assignment for ME model variables

@@
 # clean the data so the total acceptances and quits per subj x handling x reward are ready for modeling
-mixLogis_main <- list()
+mixLogis_main_btw <- list()
 mixData <- dataBtw %>%
@@
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_main$Wait <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main_btw$Wait <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_main$Cognitive <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main_btw$Cognitive <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
-mixLogis_main$Physical <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main_btw$Physical <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_main$Easy <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main_btw$Easy <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
@@
 rearrange <- c("Cognitive", "Easy", "Wait", "Physical") # to kinda match the order in Cost 3
-mixSummary_btw <- betaMatrix(mixLogis_main, rearrange = rearrange)
+mixSummary_btw <- betaMatrix(mixLogis_main_btw, rearrange = rearrange)
 diag(mixSummary_btw$Pvals) <- NA
@@
 # # random intercepts for each subject, with cost group and overall acceptances
-# RI <- ranef(mixLogis_main$Wait)$SubjID[, 1]
+# RI <- ranef(mixLogis_main_btw$Wait)$SubjID[, 1]
 # RI <- dataBtw %>% 
@@
 ## model fitting
-mixLogis_compare <- list()
-mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
-mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
-mixLogis_compare$Handling <- glmer(cbind(totalAccepted, totalQuits) ~ Handling + (1 | SubjID), family = "binomial", data = mixData)
-mixLogis_compare$Offer <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
-mixLogis_compare$HR <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + Handling + (1 | SubjID), family = "binomial", data = mixData)
-mixLogis_compare$AllMain <- mixLogis_main$Wait
-mixLogis_compare$HR_interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer * Handling + (1 | SubjID), family = "binomial", data = mixData)
-mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ (Cost + Handling + Offer)^2 + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_btw <- list()
+mixLogis_compare_btw$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
+mixLogis_compare_btw$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_btw$Handling <- glmer(cbind(totalAccepted, totalQuits) ~ Handling + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_btw$Offer <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_btw$HR <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + Handling + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_btw$AllMain <- mixLogis_main_btw$Wait
+mixLogis_compare_btw$HR_interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer * Handling + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_btw$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ (Cost + Handling + Offer)^2 + (1 | SubjID), family = "binomial", data = mixData)
 
@@
 ME_evals <- list()
-ME_evals$abicLogis_compare <- data.frame(Model = names(mixLogis_compare),
-                                AIC = sapply(mixLogis_compare, AIC),
-                                BIC = sapply(mixLogis_compare, BIC)) %>%
+ME_evals$abicLogis_compare <- data.frame(Model = names(mixLogis_compare_btw),
+                                AIC = sapply(mixLogis_compare_btw, AIC),
+                                BIC = sapply(mixLogis_compare_btw, BIC)) %>%
                                   mutate_at(vars(AIC:BIC), round)
@@
 # analysis of deviance for models with similar AIC
-ME_evals$HRvMain <- anova(mixLogis_compare$HR, mixLogis_compare$AllMain)
-ME_evals$MainvHRint <- anova(mixLogis_compare$AllMain, mixLogis_compare$HR_interaction)
-ME_evals$MainvAllint <- anova(mixLogis_compare$AllMain, mixLogis_compare$Interaction)
+ME_evals$HRvMain <- anova(mixLogis_compare_btw$HR, mixLogis_compare_btw$AllMain)
+ME_evals$MainvHRint <- anova(mixLogis_compare_btw$AllMain, mixLogis_compare_btw$HR_interaction)
+ME_evals$MainvAllint <- anova(mixLogis_compare_btw$AllMain, mixLogis_compare_btw$Interaction)
 
 # effect size for the main model
-mixLogis_compare$AllMainRsq <- 1 - (deviance(mixLogis_compare$AllMain)/deviance(mixLogis_compare$Base)) # denominator is the null deviance
+mixLogis_compare_btw$AllMainRsq <- 1 - (deviance(mixLogis_compare_btw$AllMain)/deviance(mixLogis_compare_btw$Base)) # denominator is the null deviance
 ```
@@
   gather(Comparison, Value, AIC:BIC) %>%
-  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
+  mutate(Model = factor(Model, levels = names(mixLogis_compare_btw))) %>%
   ggplot(aes(Model, Value, fill = Comparison)) +
@@
 We tested these observations with a mixed-effects logistic regression, computing the probability of accepting an offer as a function of handling time, reward amount, and demand type (see Methods for details).
-As before, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Handling", "Std.
-Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Offer", "Std.
-Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`).
+As before, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main_btw$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main_btw$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main_btw$Wait)[[10]]["Handling", "Std.
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_btw$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main_btw$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main_btw$Wait)[[10]]["Offer", "Std.
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_btw$Wait)[[10]]["Offer", "Pr(>|z|)"])`).
 Comparisons among all conditions are shown on Figure 4B.
@@
 Here we focus on AIC, as both metrics yielded comparable results.
-As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a-priori~ = `r filter(ME_evals$abicLogis_compare, Model == "AllMain")$AIC`, AIC~handling/reward~ = `r filter(ME_evals$abicLogis_compare, Model == "HR")$AIC`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r round(ME_evals$HRvMain$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
+As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare_btw$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a-priori~ = `r filter(ME_evals$abicLogis_compare, Model == "AllMain")$AIC`, AIC~handling/reward~ = `r filter(ME_evals$abicLogis_compare, Model == "HR")$AIC`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r round(ME_evals$HRvMain$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
 However, against our expectations, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r filter(ME_evals$abicLogis_compare, Model == "HR_interaction")$AIC`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r round(ME_evals$MainvHRint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r filter(ME_evals$abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r round(ME_evals$MainvAllint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
@@
 # mixed logistic for the first half
-mixLogis_pre <- list()
+mixLogis_pre_btw <- list()
 mixData <- dataBtw %>%
@@
 
-mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_pre_btw$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_pre$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_pre_btw$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_pre$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_pre_btw$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_pre_btw$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
 # mixed logistic for the second half
-mixLogis_post <- list()
+mixLogis_post_btw <- list()
 mixData <- dataBtw %>%
@@
 
-mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_post_btw$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait"))
-mixLogis_post$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_post_btw$Wait <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Easy"))
-mixLogis_post$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_post_btw$Easy <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Cognitive"))
-mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_post_btw$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Handling + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
@@
 # get the beta and pvalue matrices 
-betasPre <- betaMatrix(mixLogis_pre, rearrange = rearrange)
-betasPost <- betaMatrix(mixLogis_post, rearrange = rearrange)
+betasPre <- betaMatrix(mixLogis_pre_btw, rearrange = rearrange)
+betasPost <- betaMatrix(mixLogis_post_btw, rearrange = rearrange)
 
@@
 # method 1
-# mixLogis_main <- list()
-# mixLogis_main$Cog <- glmer(Choice ~ Cost + Offer + (1 | SubjID), family = "binomial", data = data)
+# mixLogis_main_wth <- list()
+# mixLogis_main_wth$Cog <- glmer(Choice ~ Cost + Offer + (1 | SubjID), family = "binomial", data = data)
 
 # mixed effects logistics, rotating the reference cost condition
-mixLogis_main <- list()
+mixLogis_main_wth <- list()
 mixData <- dataWth %>%
@@
 
-mixLogis_main$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main_wth$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-C"))
-mixLogis_main$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main_wth$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-P"))
-mixLogis_main$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main_wth$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
-mixLogis_main$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_main_wth$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
@@
 rearrange <- c("Cognitive", "Wait-C", "Wait-P", "Physical")
-mixSummary_wth <- betaMatrix(mixLogis_main, rearrange = rearrange)
+mixSummary_wth <- betaMatrix(mixLogis_main_wth, rearrange = rearrange)
 diag(mixSummary_wth$Pvals) <- NA
@@
 # fit ME logistic at increasing model complexities
-mixLogis_compare <- list()
-mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
-mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
-mixLogis_compare$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
-mixLogis_compare$AllMain <- mixLogis_main$Cognitive
-mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_wth <- list()
+mixLogis_compare_wth$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
+mixLogis_compare_wth$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_wth$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_wth$AllMain <- mixLogis_main_wth$Cognitive
+mixLogis_compare_wth$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (1 | SubjID), family = "binomial", data = mixData)
 
 # Model selection 
-abicLogis_compare <- data.frame(Model = names(mixLogis_compare),
-                                AIC = sapply(mixLogis_compare, AIC),
-                                BIC = sapply(mixLogis_compare, BIC)) %>%
+abicLogis_compare <- data.frame(Model = names(mixLogis_compare_wth),
+                                AIC = sapply(mixLogis_compare_wth, AIC),
+                                BIC = sapply(mixLogis_compare_wth, BIC)) %>%
                                   mutate_at(vars(AIC:BIC), round)
@@
 # plot 
-mixLogis_compare$plot <- abicLogis_compare %>% 
+mixLogis_compare_wth$plot <- abicLogis_compare %>% 
   gather(Comparison, Value, AIC:BIC) %>%
-  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
+  mutate(Model = factor(Model, levels = names(mixLogis_compare_wth))) %>%
   ggplot(aes(Model, Value, fill = Comparison)) +
@@
 # analysis of deviance
-mixLogis_compare$aod <- anova(mixLogis_compare$Reward, mixLogis_compare$AllMain, mixLogis_compare$Interaction)
+mixLogis_compare_wth$aod <- anova(mixLogis_compare_wth$Reward, mixLogis_compare_wth$AllMain, mixLogis_compare_wth$Interaction)
 
 # effect size
-mixLogis_compare$Rsq <- 1 - (deviance(mixLogis_compare$AllMain)/deviance(mixLogis_compare$Base)) # denominator is the null deviance
+mixLogis_compare_wth$Rsq <- 1 - (deviance(mixLogis_compare_wth$AllMain)/deviance(mixLogis_compare_wth$Base)) # denominator is the null deviance
 ```
@@
 Moreover, these differences contradicted our predictions, as cognitive effort remained the least costly among demands.
-A mixed effects logistic regression confirmed once again that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Std.
-Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference was the higher likelihood to accept cognitive offers compared to physical ones (Figure 7C; $\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
-Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 7D).
-An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r round(mixLogis_compare$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`).
-However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][3]`) = `r round(mixLogis_compare$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][3])`).
+A mixed effects logistic regression confirmed once again that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main_wth$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main_wth$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Std.
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference was the higher likelihood to accept cognitive offers compared to physical ones (Figure 7C; $\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
+Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare_wth$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 7D).
+An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][2]`) = `r round(mixLogis_compare_wth$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][2])`).
+However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][3]`) = `r round(mixLogis_compare_wth$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][3])`).
 (**discuss with Joe: the interaction flips results over, such that both waits > pysical effort = cognitive effort...as predicted originally?
@@
 # mixed logistic for the first half
-mixLogis_pre <- list()
+mixLogis_pre_wth <- list()
 mixData <- dataWth %>%
@@
 
-mixLogis_pre$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_pre_wth$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-C"))
-mixLogis_pre$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_pre_wth$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-P"))
-mixLogis_pre$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_pre_wth$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
-mixLogis_pre$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_pre_wth$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
 # mixed logistic for the second half
-mixLogis_post <- list()
+mixLogis_post_wth <- list()
 mixData <- dataWth %>%
@@
 
-mixLogis_post$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_post_wth$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-C"))
-mixLogis_post$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_post_wth$`Wait-C` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Wait-P"))
-mixLogis_post$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_post_wth$`Wait-P` <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 mixData <- within(mixData, Cost <- relevel(Cost, ref = "Physical"))
-mixLogis_post$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_post_wth$Physical <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
 
@@
 # get the beta and pvalue matrices 
-betasPre <- betaMatrix(mixLogis_pre)
-betasPost <- betaMatrix(mixLogis_post)
+betasPre <- betaMatrix(mixLogis_pre_wth)
+betasPost <- betaMatrix(mixLogis_post_wth)
 
@@
 betaMat[upper.tri(betaMat)] <- betasPost$Betas[upper.tri(betasPost$Betas)]
-dimnames(betaMat) <- list(names(mixLogis_pre), names(mixLogis_pre))
+dimnames(betaMat) <- list(names(mixLogis_pre_wth), names(mixLogis_pre_wth))
 
@@
 pvalMat[upper.tri(pvalMat)] <- betasPost$Pvals[upper.tri(betasPost$Pvals)]
-dimnames(pvalMat) <- list(names(mixLogis_pre), names(mixLogis_pre))
+dimnames(pvalMat) <- list(names(mixLogis_pre_wth), names(mixLogis_pre_wth))
 

### 2020-11-24 Cost_manuscript.Rmd
discussion bits and ME model wording

@@
 **We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.** We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (**0.74**, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
+The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.** We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (0.61, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
 Finally, we compared gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
@@
 mixLogis_compare_btw$AllMain <- mixLogis_main_btw$Wait
-mixLogis_compare_btw$HR_interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer * Handling + (1 | SubjID), family = "binomial", data = mixData)
+mixLogis_compare_btw$HR_interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer * Handling + (1 | SubjID), family = "binomial", data = mixData, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
 mixLogis_compare_btw$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ (Cost + Handling + Offer)^2 + (1 | SubjID), family = "binomial", data = mixData)
@@
 An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][2]`) = `r round(mixLogis_compare_wth$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][2])`).
-However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][3]`) = `r round(mixLogis_compare_wth$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][3])`).
-(**discuss with Joe: the interaction flips results over, such that both waits > pysical effort = cognitive effort...as predicted originally?
-Can't wrap my head around that yet, so this conclusion is pending**).
-These initial results defied our predictions, suggesting that the availability of alternative demands erases preferences among demands (rather than inverting them).
+However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][3]`) = `r round(mixLogis_compare_wth$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][3])`), albeit at the cost of interpretability due to choice fluctuations over time (see Consistency and Stability).
+These initial results defied our predictions, suggesting that the availability of alternative demands erases preferences among them (rather than inverting them from what was observed in experiment 1).
 
@@
 Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.
+Maybe use this example: if I ask you to perform an activity until you think a minute has elapsed, that estimate will be noisy, but also different for different tasks.
+That's how it is in real life.
 
@@
 Training might have improved response automaticity and reduce error-related risk.
-In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [@Bandura2010; @Grahek2020; eisenberger].
-Even so, we believe our manipulations were successful in inducing feelings of effort.
+In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [@Bandura2010; @Eisenberger1996].
+Nevertheless, we believe our manipulations were successful in inducing feelings of effort.
 Hand grips are regularly used to probe physical effort [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to feel cognitively effortful by recruiting cognitive control [@Kool2010; @Shenhav2017].
@@
 
-  The present findings provide theoretical advances as well as practical implementations.
+  The present findings have important implications for daily and clinical scenarios.
+Excessive aversion to delay and effort can manifest as impulsivity and apathy, respectively [@Ainslie1975; @Bonnelle2016; @Chong2016; @Cummings1993], fluctuations in which are hallmark symptoms of various mental illnesses and substance use disorders [@Paulus2007].
+Lack of motivation to exert effort or wait for prospects is a distinguishing factor among mental afflictions like depression and schizophrenia [@Barch2019].
+Within the former, medicated patients in remission are more sensitive to effort than controls, and this sensitivity is predictive of relapse [@Berwian2020].
+Encouraging patients to engage in activities has been found to be a helpful treatment for depression [@Dimidjian2006].
+Tailored reward schedules can successfully achieve this [@Eisenberger1996].
+However, since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases.
+Our work suggests that subdividing a task can promote its pursual either by taxing working memory and/or allowing individuals to count completed tasks instead of continuous time.
+More importantly, it highlights that decision scenarios should be configured to promote pursual of desired activities, perhaps by removing alternative uses of time.
+These same principles can potentially be applied to increasing productivity at work or adherence to physical exercise routines.
+
+### *Points to cover*
+
+- Regardless, our focus here was not on the amount of effort exherted, but on what makes people pursue the task in spite of its toll.
+
+  .
 Talk clinical and practical.
 Practical could be motivating people to pursue challenges that produce desirable outcomes, like work, exercise etc.
-Much of the literature on the value of effort has suggested that it can be triggered by careful reward schedules.
+Much of the literature on the value of effort has suggested that it can be triggered by tailored reward schedules.
 This doesn't always do (Eisenberger, Inzlicht).
@@
 We highlight an outcome-independent feature that is phenomenologically common (time sensitivity), and potentially easy to implement.
-
-### *Points to cover*
-
-- Regardless, our focus here was not on the amount of effort exherted, but on what makes people pursue the task in spite of its toll.
-
-- Clinical: Te motivation to exert effort or wait for delays is a distinguishing factor among mental afflictions like depression and schizophrenia [@Barch2019].
-Within the former, medicated patients in remission are more sensitive to effort than controls (and are not as motivated by rewards?), and this sensitivity is predictive of relapse [@Berwian2020].
-Encouraging/increasing activities has been found to be a helpful treatment for depression [@Dimidjian2006].
-Since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases.
-Our work suggests that subdividing a task can promote its pursual either by taxing working memory, counting, or simply distracting.
-Moreover, The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler).
-This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.
-
-, and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia
-
-(https://link.springer.com/chapter/10.1007%2F978-3-030-27473-3_5).
-Like, the aversion is due to focusing on different elements of the task.
-Excessive aversion to delay and effort can manifest as impulsivity and apathy, respectively [1,10–12], fluctuations in which are hallmark symptoms of various mental illnesses and substance use disorders [13].
-Our findings promote the idea that motivation to exhert effort can be boosted by chopping tasks into smaller digestible chunks that don't make them feel as long.
-Rather than telling them the final goal, keep them busy (this should be already a thing, I'm sure...).
-The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler).
-This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.
-
-- do I even want to get into DA?
 

### 2020-11-25 Cost_manuscript.Rmd
added notes inspired by eisenberger and cameron

@@
 
+- we have all felt the need to populate empty time
+
 - It's maybe relevant that waiting is goal oriented (you don't sit around for its own sake), but activities are pursued for their own appeal.
@@
 Also, it's not just that we would rather to fill in empty periods of waiting, but how.
+
+- it's maybe relevant that waiting is goal oriented (you don't sit around for its own sake), but activities are pursued for their own appeal.
+like, waiting is a goal oriented activity, but effort can be the goal itself.
+In this sense it makes sense to study delays in terms of their modulation of the value of prospects, but we have unnecessarily adopted this view for the study of effort, thinking of it mostly as a cost.
+Even if their discounting properties are similar, their resulting behavior can be contrasting (apathy vs impulsivity), and they're impacted differently by mental illness (adhd amygdala paper).
+
+- Theories enumerated by Eisenberger and Cameron (1996) focus on how people see their behavior to explain why tasks are intrinsically attractive.
+We, on the other hand, point to task-specific features that promote appeal, which are amenable to configuration in everyday decision contexts.
+In other words, self-explanatory motivation versus task-specific ones.
 

### 2020-11-27 Cost_manuscript.Rmd
new citation

@@
 Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @Kool2010; @Westbrook2013].
-Although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across effort types [@Arulpragasam2018; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and discount rates do not always correlate across cost domains [@Seaman2018; @Westbrook2013].
+Although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across effort types [@Arulpragasam2018; @Biaaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and discount rates do not always correlate across cost domains [@Seaman2018; @Westbrook2013].
 However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context [@Kool2018].

### 2020-11-28 models_gk/likelihoods.R
updated btw and wth fits

@@ -1,6 +1,6 @@
 ### define likelihood functions
 
-# Rcpp::sourceCpp(file.path(dirname(sys.frame(1)$ofile), "likelihoods.cpp"))
+Rcpp::sourceCpp(file.path(dirname(sys.frame(1)$ofile), "likelihoods.cpp"))
 
 cost_p <- function(dat,
                    cost = 0,
@@ -18,16 +18,6 @@ cost_p <- function(dat,
   H_i = dat[, HandleTime]
   C_i = dat[, Choice]
   T_i = dat[, TravelTime]
-  if(is.na(gamma)) {
-    gamma = mean(dat[, RR])
-  }
-  
-  if (alpha > 0) {
-    for (i in 1:((length(R_i)) - 1)) {
-      tau <- H_i[i]^s[i] * C_i[i] + T_i[i]
-      gamma[i + 1] <- (1 - (1 - alpha)^tau) * ((R_i[i] * C_i[i]) / tau) + ((1 - alpha)^tau * gamma[i])
-    }
-  }
   
   w_t = ((n_trials - 1:n_trials) / n_trials) ^ w_decay
   
@@ -38,6 +28,19 @@ cost_p <- function(dat,
   
   if(!is.na(S)) {
     s = s * w_t + S * (1 - w_t)
+  }
+  
+  if(is.na(gamma)) {
+    gamma = mean(dat[, RR])
+  }
+  
+  if (alpha > 0) {
+    if (length(s) == 1) s = rep(s, length(R_i))
+    for (i in 1:((length(R_i)) - 1)) {
+      tau <- H_i[i]^s[i] * C_i[i] + T_i[i]
+      gamma[i + 1] <- (1 - (1 - alpha)^tau) * ((R_i[i] * C_i[i]) / tau) + (1 - alpha)^tau * gamma[i]
+      
+    }
   }
   
   p_accept <- 1 / (1 + exp(-1/beta * (R_i - (gamma + cost) * H_i^s)))
@@ -92,7 +95,7 @@ cost_p_old <- function(dat,
 
 
 log_transform_pars = function(par) {
-  par[!grepl("cost", names(par)) & names(par) != "C"] <- exp(par[!grepl("cost", names(par)) & names(par) != "B"])
+  par[!grepl("cost", names(par)) & names(par) != "C"] <- exp(par[!grepl("cost", names(par)) & names(par) != "C"])
   par
 }
 
[…]

### 2020-11-28 models_gk/likelihoods.cpp

@@ -32,17 +32,6 @@ NumericVector cost_p_cpp(DataFrame dat,
   
   int n_trials = R_i.size();
   
-  NumericVector gvec(n_trials);
-  if (alpha > 0) {
-    gvec[0] = gamma;
-    for (int i=0; i<n_trials-1; i++) {
-      double tau = pow(H_i[i],s[i]) * C_i[i] + T_i[i];
-      gvec[i+1] = (1 - pow(1 - alpha, tau)) * ((R_i[i] * C_i[i]) / tau) + (pow(1 - alpha, tau) * gvec[i]);
-    }
-  } else {
-    gvec.fill(gamma);
-  }
-  
   IntegerVector trial_vec = seq_len(n_trials);
   NumericVector w_t = pow((n_trials - as<NumericVector>(trial_vec)) / n_trials, w_decay);
 
@@ -58,6 +47,17 @@ NumericVector cost_p_cpp(DataFrame dat,
   }
   if(!NumericVector::is_na(S)) {
     s = s * w_t + S * (1 - w_t);
+  }
+  
+  NumericVector gvec(n_trials);
+  if (alpha > 0) {
+    gvec[0] = gamma;
+    for (int i=0; i<n_trials-1; i++) {
+      double tau = pow(H_i[i],s[i]) * C_i[i] + T_i[i];
+      gvec[i+1] = (1 - pow(1 - alpha, tau)) * ((R_i[i] * C_i[i]) / tau) + pow(1 - alpha, tau) * gvec[i];
+    }
+  } else {
+    gvec.fill(gamma);
   }
 
   NumericVector p_accept = 1 / (1 + exp(-1/beta * (R_i - (gvec + cost) * vecpow(H_i, s))));

### 2020-11-28 models_gk/modeling_gk_btw.R

@@ -5,6 +5,8 @@
 # set wd
 setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
 
+load("models_gk/results/btw.Rdata")
+
 library(data.table)
 library(foreach)
 library(rextras)
@@ -14,131 +16,121 @@ library(GaussExMax)
 
 source('models_gk/load_data.R')
 source('models_gk/likelihoods.R')
+Rcpp::sourceCpp('models_gk/likelihoods.cpp')
+
 
 #########################
 ### Load Data
 #########################
 
 c(dat_btw, dat_wth) %<-% load_data_full()
-fit_cols = c("sub", "cond", "Offer", "Choice", "HandleTime", "TravelTime", "condCode")
 dat_btw[, Subject := sub]
 
 #########################
-### plot between subjects behavior
+### plot within subjects behavior
 #########################
 
 mean_sub_btw = dat_btw[, .(Choice = mean(Choice)), .(sub, cond, Handling, Offer)]
 plot_btw(mean_sub_btw)
 
 #########################
-### Fit super base model -- optimal values + decision noise
+### Define Models
 #########################
 
-par_names_base = c("beta")
-mus_base = c("beta" = 0.1)
-sigma_base = c(1)
+models = list()
 
-system.time(fits_btw_base <- dat_btw[, em(.SD,
-                                          log(mus_base),
-                                          sigma_base,
-                                          cost_lik,
-                                          lower = -100,
-                                          upper = 100,
-                                          package = "optim",
-                                          method = "Brent",
-                                          bic=TRUE,
-                                          ndata=.SD[, .N],
-                                          obj_args = list(
-                                            par_names=par_names_base,
-                                            log_par=T
-                                          ),
-                                          verbose = F,
-                                          return_ind_df=T),
-                                     .(cond)])
+models[["Base"]] = list(
+  par_names = "beta",
+  mus = c(beta = 1),
+  sigma = 10,
+  options = list(package="optim",
+                 method="Brent",
+                 lower=-100,
+                 upper=100)
+)
 
-fits_btw_base_predict = get_all_predictions(dat_btw, fits_btw_base, par_names_base, log_par=T, return_mean=T)
-plot_btw(fits_btw_base_predict, title="Base Model (MVT + Noise)")
[…]

### 2020-11-28 models_gk/modeling_gk_wth.R

@@ -16,6 +16,8 @@ library(GaussExMax)
 
 source('models_gk/load_data.R')
 source('models_gk/likelihoods.R')
+Rcpp::sourceCpp('models_gk/likelihoods.cpp')
+
 
 #########################
 ### Load Data
@@ -42,195 +44,146 @@ plot_wth(mean_sub_wth)
 # phia::testInteractions(glm1, across="cond", pairwise="first")
 
 #########################
-### Fit super base model -- optimal values + decision noise
+### Define Models
 #########################
 
-par_names_base = c("beta")
-mus_base = c("beta" = 0.1)
-sigma_base = c(1)
+models = list()
 
-system.time(fits_wth_base_em <- em(dat_wth,
-                                   log(mus_base),
-                                   sigma_base,
-                                   cost_lik,
-                                   lower = -100,
-                                   upper = 100,
-                                   package = "optim",
-                                   method = "Brent",
-                                   bic=TRUE,
-                                   ndata=dat_wth[, .N],
-                                   obj_args = list(
-                                     par_names=par_names_base,
-                                     log_par=T
-                                   ),
-                                   parallel=F,
-                                   verbose = F,
-                                   return_ind_df=T))
+models[["Base"]] = list(
+  par_names = "beta",
+  mus = c(beta = 1),
+  sigma = 10,
+  options = list(package="optim",
+                 method="Brent",
+                 lower=-100,
+                 upper=100)
+)
 
-fits_wth_base = setDT(fits_wth_base_em)
-fits_wth_base_predict = get_all_predictions(dat_wth, fits_wth_base, par_names_base, within=T, log_par=T, return_mean=T)
-plot_wth(fits_wth_base_predict, title="Base Model (MVT + Noise)")
-plot_params(fits_wth_base, par_names_base, exp_par=T, within=T)
+models[["Adaptive OC"]] = list(
+  par_names = c("gamma", "alpha", "beta"),
+  mus = c(gamma=0.55, alpha=.01, beta=1),
+  sigma = c(10, 10, 10),
+  options = list(method="nlminb")
+)
 
+models[["Biased OC"]] = list(
[…]

### 2020-12-02 Cost_manuscript.Rmd
tweak to modeling criteria

@@
   We performed model comparisons to identify qualities that explained findings from both experiments.
-Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects.
+Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting; 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions in the between-subjects experiment; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) preference ranks should be robust to block order effects, but the magnitude of the differences should be lower for those who started with the physical effort block.
 These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, sunk cost effects, or asymmetric learning of environmental richness (see Discussion).
@@
 ....This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman).
+Mention that order effects reflect the gradual integration of subjective time across demands in exp 2.
 Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.

### 2020-12-02 models_gk/likelihoods.R
replicate original within time sensitivity models

@@ -160,29 +160,29 @@ get_all_predictions = function(all_data, fits, par_names, within=F, return_mean=
   
   for (subj in unique(all_data[, Subject])) {
     
-    all_data[Subject==subj, predict_accept := cost_lik(as.numeric.dt(fits[Subject==subj, par_names, with=F]),
-                                                       dat=.SD,
-                                                       return_pacc=T,
-                                                       ...)]
+    # all_data[Subject==subj, predict_accept := cost_lik(as.numeric.dt(fits[Subject==subj, par_names, with=F]),
+    #                                                    dat=.SD,
+    #                                                    return_pacc=T,
+    #                                                    ...)]
     
-    # if(within) {
-    # 
-    #   all_data[Subject==subj, predict_accept := cost_lik(as.numeric.dt(fits[Subject==subj, par_names, with=F]),
-    #                                                      dat=.SD,
-    #                                                      return_pacc=T,
-    #                                                      ...)]
-    # } else {
-    # 
-    #   for (cond in unique(dat_btw[, cond])) {
-    # 
-    #     all_data[Subject==subj & cond == cond, predict_accept := cost_lik(as.numeric.dt(fits[Subject==subj & cond==cond, par_names, with=F]),
-    #                                                                      dat=.SD,
-    #                                                                      return_pacc=T,
-    #                                                                      ...)]
-    # 
-    # 
-    #   }
-    # }
+    if(within) {
+
+      all_data[Subject==subj, predict_accept := cost_lik(as.numeric.dt(fits[Subject==subj, par_names, with=F]),
+                                                         dat=.SD,
+                                                         return_pacc=T,
+                                                         ...)]
+    } else {
+
+      for (cond in unique(dat_btw[, cond])) {
+
+        all_data[Subject==subj & cond == cond, predict_accept := cost_lik(as.numeric.dt(fits[Subject==subj & cond==cond, par_names, with=F]),
+                                                                         dat=.SD,
+                                                                         return_pacc=T,
+                                                                         ...)]
+
+
+      }
+    }
   }
   
   if (return_mean) {

### 2020-12-02 models_gk/modeling_gk_btw.R

@@ -5,8 +5,6 @@
 # set wd
 setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
 
-load("models_gk/results/btw.Rdata")
-
 library(data.table)
 library(foreach)
 library(rextras)
@@ -14,6 +12,7 @@ library(zeallot)
 library(modelfitr)
 library(GaussExMax)
 
+load("models_gk/results/btw.Rdata")
 source('models_gk/load_data.R')
 source('models_gk/likelihoods.R')
 Rcpp::sourceCpp('models_gk/likelihoods.cpp')
@@ -49,6 +48,20 @@ models[["Base"]] = list(
                  upper=100)
 )
 
+models[["OC"]] = list(
+  par_names = c("gamma", "beta"),
+  mus = c(gamma=1, beta = 1),
+  sigma = c(10, 10),
+  options = list(method="nlminb")
+)
+
+models[["Adaptive OC"]] = list(
+  par_names = c("gamma", "alpha", "beta"),
+  mus = c(gamma=1, alpha=.01, beta = 1),
+  sigma = c(10, 10, 10),
+  options = list(method="nlminb")
+)
+
 models[["Biased OC"]] = list(
   par_names = c("cost", "beta"),
   mus = c(cost=1, beta=1),
@@ -81,30 +94,40 @@ models[["Adaptive OC + Time Sensitivity"]] = list(
 ### Fit Models
 #########################
 
+conds = dat_btw[, unique(cond)]
+
 fits_btw = foreach(i=1:length(models)) %do% {
   
-  cat("model =", names(models)[i], "\n\n")
+  fits_conds = foreach(c=1:length(conds)) %do% {
   
-  m = models[[i]]
+    cat("cond =", conds[c], "// model =", names(models)[i], "\n\n")
+    
+    m = models[[i]]
+    
+    this_em <- do.call(em, c(list(dat=dat_btw[cond==conds[c]],
+                                  mus=log(m$mus),
+                                  sigma=m$sigma,
+                                  lik=cost_lik,
+                                  bic=TRUE,
+                                  ndata=dat_btw[cond==conds[c], .N],
+                                  obj_args=list(
+                                    par_names=m$par_names,
+                                    log_par=T
+                                  ),
+                                  perturb_start=0.1,
+                                  emtol=.001,
+                                  parallel=T,
+                                  verbose=T),
+                             m$options)
+    )
+    
+    this_em
+    
+  }
   
-  this_em <- do.call(em, c(list(dat=dat_btw,
[…]

### 2020-12-02 models_gk/modeling_gk_wth.R

@@ -5,8 +5,6 @@
 # set wd
 setwd(dirname(dirname(rstudioapi::getActiveDocumentContext()$path)))
 
-load("models_gk/results/wth.Rdata")
-
 library(data.table)
 library(foreach)
 library(rextras)
@@ -14,6 +12,8 @@ library(zeallot)
 library(modelfitr)
 library(GaussExMax)
 
+load("models_gk/results/btw.Rdata")
+load("models_gk/results/wth.Rdata")
 source('models_gk/load_data.R')
 source('models_gk/likelihoods.R')
 Rcpp::sourceCpp('models_gk/likelihoods.cpp')
@@ -57,6 +57,13 @@ models[["Base"]] = list(
                  method="Brent",
                  lower=-100,
                  upper=100)
+)
+
+models[["OC"]] = list(
+  par_names = c("gamma", "beta"),
+  mus = c(gamma=0.55, beta=1),
+  sigma = c(10, 10),
+  options = list(method="nlminb")
 )
 
 models[["Adaptive OC"]] = list(
@@ -122,16 +129,69 @@ models[["Adaptive OC + Adaptive Time Sensitivity"]] = list(
   options = list(method="nlminb")
 )
 
+models[["Between Time Sensitivity"]] = list(
+  par_names = c("w_decay", "beta"),
+  mus = c(w_decay=1, beta=1),
+  sigma = c(10, 10),
+  options = list(method="nlminb"),
+  fixed_pars = exp(c(s_1 = fits_btw[["Time Sensitivity"]][["wait"]]$mus[1],
+                     s_2 = fits_btw[["Time Sensitivity"]][["cogTask"]]$mus[1],
+                     s_3 = fits_btw[["Time Sensitivity"]][["phys"]]$mus[1],
+                     S = log(1)))
+)
+
+models[["Adaptive Between Biased OC"]] = list(
+  par_names = c("C", "w_decay", "beta"),
+  mus = c(C=1, w_decay=1, beta=1),
+  sigma = c(10, 10, 10),
+  options = list(method="nlminb"),
+  fixed_pars = c(cost_1 = fits_btw[["Biased OC"]][["wait"]]$mus[1],
+                 cost_2 = fits_btw[["Biased OC"]][["cogTask"]]$mus[1],
+                 cost_3 = fits_btw[["Biased OC"]][["phys"]]$mus[1])
+)
+
[…]

### 2020-12-03 Cost_manuscript.Rmd
reframing the modeling section

@@
 
+  **GARY.
+All free paremeters of the softmax function (the temperature parameter $\beta$) were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package.
+The gamma optimization search space was bound by extreme choice values.
+For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
+Conversely, a participant experiencing low opportunity costs would accept the non-beneficial offer of 4 cents for a 14 second delay (or 4/14).
+We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.**
+
   We started by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT; @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it.
@@
 
-  such that a trial’s reward $R_i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_i$.
-Individuals with higher gammas therefore required higher rewards in order to accept a given offer.
-We fit this and other models using a softmax function to predict the probability of accepting a given trial
+  such that a trial’s reward $R_i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_i$, with high gammas promoting selectivity.
+We fit this and all subsequent models using a softmax function to predict the probability of accepting a given trial
 
@@
 
-  All free paremeters of the softmax function (in this case, $\gamma$ and the temperature parameter $\beta$) were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package (CITE **GARY INFO**).
-The gamma optimization search space was bound by extreme choice values.
-For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
-Conversely, a participant experiencing low opportunity costs would accept the non-beneficial offer of 4 cents for a 14 second delay (or 4/14).
-**We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.** We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (0.61, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
-Finally, we compared gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.
-
-  The base formulation lacked the flexibility needed to capture the dynamics observed in the within-subjects experiment.
+  gamma in this base model was computed as an individual's empirical earning rate by the time of each offer, with the free temperature parameter $\beta$ indexing decision noise.
+However, this base formulation lacked the flexibility needed to capture the dynamics observed in the within-subjects experiment.
 We therefore tested a second model which allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
@@
   such that the handling time was counted only for accepted trials.
-Gamma was initialized by the median earning rate achieved across individuals.
-These modifications allowed for the tracking of recent history that was part of our criteria, while mostly maintaining the same complexity (i.e.
-one free parameter) and structure of the base model
+For this adaptive model, we fit the learning rate $\alpha$ and the initial value of $\gamma$ in addition to the temperature.
+These modifications allowed for the tracking of recent history that was part of our criteria, while maintaining the general structure of the base model
 
@@
 
-  A final model considered the relationship between effortful engagement and the perceived length of time.
-Being immersed in a task can make time transpire subjectively faster [@Csikszentmihalyi2014], which might have made the cognitive task attractive.
-Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [@Mckerchar2009].
-It is possible that such subjective handling time was recalibrated in the within-subjects experiment, resulting in the observed convergance of acceptances across demands.
+  A third model considered the possibility that each type of demand biased the estimate of $\gamma$.
+Such bias would be stable if a single demand was experienced, but recalibrated into a global estimate as decision makers faced different types of demands.
+This dynamic could underlie the observed convergance of acceptances across demands.
+At each decision point, the bias produced by each demand ($c_{demand}$) was weighted against a global bias estimate $C$
+
+$$\begin{aligned}
+mC_i = c_{demand} w_i + C (1 - w_i)
+\end{aligned}$$
+
   We therefore added a time sensitivity parameter $S$ to the model, with a separate value associated with each type of demand.
@@
 
-  In order to compare model fits, we used expectation maximization...(**Gary**)
+  *(LATER) We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (0.61, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
+Finally, we compared gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.*
 
@@
 
+- Being immersed in a task can make time transpire subjectively faster [@Csikszentmihalyi2014], which might have made the cognitive task attractive.
+Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [@Mckerchar2009].
+
 \newpage

### 2020-12-03 Cost_manuscript.Rmd
third bias model added

@@
 
-  A third model considered the possibility that each type of demand biased the estimate of $\gamma$.
+  A third model considered the possibility that each type of demand additively biased the estimate of $\gamma$.
 Such bias would be stable if a single demand was experienced, but recalibrated into a global estimate as decision makers faced different types of demands.
-This dynamic could underlie the observed convergance of acceptances across demands.
-At each decision point, the bias produced by each demand ($c_{demand}$) was weighted against a global bias estimate $C$
+The overall model took the following form
 
 $$\begin{aligned}
-mC_i = c_{demand} w_i + C (1 - w_i)
+Model_{biased} = R_i - (\gamma + mC_i) H_i
 \end{aligned}$$
+
+  where $\gamma$ was the mean total earning rate for the whole group (**ADD VALS**).
+At each decision point, $mC$ was the bias produced by each demand $c_{demand}$ weighted against a global bias estimate $C$
+
+$$\begin{aligned}
+mC_i = C w_i + c_{demand} (1 - w_i)
+\end{aligned}$$
+
+  with $w_i$ controlling how early participants started integrating the converging bias $C$ into their decisions. The value of this weight was given by
+
+$$\begin{aligned}
+w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}
+\end{aligned}$$
+
+  where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parmeter $\alpha_w$ denoting a late integration of the global converging bias.
+
+  Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $C$ where the same and $\alpha_w$ did not play a role.
+This resulted in just fitting parameters $c_{demand}$ and $\beta$.
+For the within-subjects group, we assumed that the resulting $c_{demand}$ values from the first experiment reflected the actual bias induced by each demand.
+We therefore fixed each value of $c_{demand}$ (i.e.
+$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the between-subjects fits from each demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$.
+This dynamic allowed for the observed merging of acceptances across demands in the within-subjects experiment, while respecting the stability in the between-subjects study.
+
+#####
 

### 2020-12-03 Cost_manuscript.Rmd
reworked model explanations done. Gotta add post-fit stats

@@
 
-  **GARY.
-All free paremeters of the softmax function (the temperature parameter $\beta$) were estimated independently for each participant, using a maximum likelihood (MLE) approach through the NLOPTR package.
-The gamma optimization search space was bound by extreme choice values.
-For example, someone with an extremely high OC would not accept even the most beneficial offers, and would reject a 20 cent offer when the handling time was 2 seconds (or 20/2).
-Conversely, a participant experiencing low opportunity costs would accept the non-beneficial offer of 4 cents for a 14 second delay (or 4/14).
-We cross-validated each subject’s OC value using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-The estimates from the training sample were used to predict acceptances in the testing sample, and the mean percent correctly predicted was reported for each group.**
-
-  We started by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT; @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it.
+  **GARY EXPLAINS FITTING PROCEDURE**
+
+  We began by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT; @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it (see Operationalization of Cost for details).
 This decision rule can be expressed as
 
-$$\begin{aligned}
+\begin{align}
   Model_{base} = R_i - \gamma H_i
-\end{aligned}$$
+\end{align}
 
@@
 
-$$\begin{aligned}
+\begin{align}
   P(accept)_i = \dfrac {1} {1 + e^{-(1/\beta)(Model_{base})}}
-\end{aligned}$$
+\end{align}
 
@@
 However, this base formulation lacked the flexibility needed to capture the dynamics observed in the within-subjects experiment.
-We therefore tested a second model which allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
-
-$$\begin{aligned}
+We therefore tested a second model that allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
+
+\begin{align}
   \gamma_{i+1} = (1 - (1 - \alpha) ^ {\tau_i}) \dfrac{R_{i} A_{i}}{\tau_i} +  (1 - \alpha) ^ {\tau_i} \gamma_{i}
-\end{aligned}$$
+\end{align}
 
@@
 
-$$\begin{aligned}
+\begin{align}
   \tau_{i} = H_{i}  A_{i} + T_{i}
-\end{aligned}$$
+\end{align}
 
@@
 
-$$\begin{aligned}
+\begin{align}
   Model_{adaptive} = R_i - \gamma_i H_i
-\end{aligned}$$
+\end{align}
 
@@
 
-$$\begin{aligned}
+\begin{align}
   Model_{biased} = R_i - (\gamma + mC_i) H_i
-\end{aligned}$$
-
-  where $\gamma$ was the mean total earning rate for the whole group (**ADD VALS**).
-At each decision point, $mC$ was the bias produced by each demand $c_{demand}$ weighted against a global bias estimate $C$
-
-$$\begin{aligned}
+\end{align}
+
+  where $\gamma$ was the mean total earning rate for the whole group (0.55). At each decision point, $mC$ was the bias produced by each demand $c_{demand}$ weighted against a global bias estimate $C$
+
+\begin{align}
   mC_i = C w_i + c_{demand} (1 - w_i)
-\end{aligned}$$
+\end{align}
 
@@
 
-$$\begin{aligned}
+\begin{align}
   w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}
-\end{aligned}$$
+\end{align}
 
@@
   Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $C$ where the same and $\alpha_w$ did not play a role.
-This resulted in just fitting parameters $c_{demand}$ and $\beta$.
+This resulted in just fitting parameters $c_{demand}$ and $\beta$ for that dataset.
 For the within-subjects group, we assumed that the resulting $c_{demand}$ values from the first experiment reflected the actual bias induced by each demand.
 We therefore fixed each value of $c_{demand}$ (i.e.
-$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the between-subjects fits from each demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$.
+$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted *a posteriori* distribution from each between-subjects demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$.
 This dynamic allowed for the observed merging of acceptances across demands in the within-subjects experiment, while respecting the stability in the between-subjects study.
 
-#####
-
-  We therefore added a time sensitivity parameter $S$ to the model, with a separate value associated with each type of demand.
-The values of $S_{demand}$ could then be recalibrated as participants experienced them, averaged according to the following formula [adapted from @Sutton2018]
-
-$$\begin{aligned}
-s_{i + 1} = s_i + A_i \left (\frac{1}{i}[S_{demand} - s_i] \right)
-\end{aligned}$$
-
-  in which the global value of $s$ was updated every time an individual completed a trial.
-We fitted the initial value of $S_{demand}$, which was bounded between 0 and 2 (values lower and greater than 1 indicating slower and faster perceived time, respectively).
-Even though the value of $s$ was updated equally across individuals, we theorized that each participant would incorporate $s$ into their decisions at different rates.
-This intuition was given by a weighted sum
-
-$$\begin{aligned}
-mS_i = s_i w_i + S_{demand} (1 - w_i)
-\end{aligned}$$
-
-  such that in every trial, the recalibrated length estimate of the handling time ($s$) was balanced against the actual experience of subjective time produced by the present demand ($S_{demand}$).
-The weight $w_i$ controlled how early participants started integrating the recalibrated time $s$ into their decisions, given by
-
-$$\begin{aligned}
-w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}
-\end{aligned}$$
-
-  in which high values of the free parmeter $\alpha_w$ denoted that decision makers incorporated the recalibrated subjective time early on in the experiment.
-Similar to @Mckerchar2009, the values of $mS_i$ exponentially modulated every instance of the handling time ($H_i$) from the adaptive model.
-In this way, subjective time perception produced by different demands could influence choice in two ways: retrospectively affecting the value of $\gamma$ through the perceived length of recent trials
-
-$$\begin{aligned}
-\tau_{i} = H_{i} ^ {mS_{i}}  A_{i} + T_{i}
-\end{aligned}$$
-
-and prospectively impacting the expected trial length at the time of a decision
-
-$$\begin{aligned}
-Model_{time} = R_i - \gamma_i H_i^{mS_i}
-\end{aligned}$$
-
-  This subjective time model was fitted differently across experiments, such that the fits from experiment 1 informed those of experiment 2.
-Since participants in the between-subjects experienced a single demand, the value of $s$ was reduced to the initial fit of $S_{demand}$, without any need to fit $\alpha_w$ (which was set to 1).
-For the within-subjects experiment, we assumed that the fitted values of $S_{demand}$ approximated the true time sensitivity produced by each demand.
-Therefore, for each individual in the within-subjects experiment, we set each value of $S_{demand}$ to be the median fitted value from the first experiment, and fitted $\alpha_w$ instead.
-In this way model complexities was fixed across experiments, even though different aspects of the model were emphasized.
-
-  In summary, the free parameters from the subjective time model captured three features.
-First, how fast or slow a given demand felt ($S_{demand}$).
-Second, how early this time sensitivity was recalibrated and integrated into decisions based on the experience of intermixed demands ($\alpha_w$).
-Finally, whether this time sensitivity was used retrospectively (i.e.
-high $\alpha$), or prospectively (i.e.
-low $\alpha$).
-Note that every model could be reduced to the base formulation for values of $\alpha$ = 0, $\alpha_w$ = 1, and $S_{demand}$ = 1.
+  A final model combined the main features from $model_{adaptive}$ and $model_{biased}$, such that $\gamma$ was estimated on each trial per Eq.
+3, with demands imposing distinct and potentially converging biases as described in model 3.
+The form of this fourth model was
+
+\begin{align}
+  Model_{adaptive + biased} = R_i - (\gamma_i + mC_i) H_i
+\end{align}
 
@@
 Finally, we compared gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.*
-
-(noise in the estimation of environmental richness [@Cash-Padgett2020])
 

### 2020-12-03 Cost_manuscript.Rmd
wrapping up methods section

@@
 
-  *(LATER) We then used a two-sided one-sample t-tests to compare each group's gammas to the average optimal earning rate (0.61, see Operationalization of Cost), allowing us to determine whether any demand boosted an offer's value.
-Finally, we compared gammas with an ANOVA (with condition as a factor), followed by post-hoc permutations (5000 iterations) comparing mean gammas per group.*
+  After fitting the parameters, we performed two-sided, one-sample t-tests to compare the biased opportunity costs from each between-subjects demand group to the mean optimal gamma (0.61, see Operationalization of Cost).
+This allowed us to determine whether any demand boosted an offer's value.
+Finally, we compared parameters with ANOVAs and post-hoc permutations between each group pairing (5000 iterations).
 

### 2020-12-04 Cost_manuscript.Rmd
commenting out old modeling approach, and adding intro paragraph to modeling results

@@
 
-``` {r BTW: 16.3.3. OC modeling, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-## fit the OC model
-summaryOC_btw <- list()
-summaryOC_btw$all <- dataBtw %>%
-                 group_by(Cost, SubjID) %>%
-                 do(optimizeOCModel(., simplify = T)) %>%
-                 ungroup()
-
-## plot
-summaryOC_btw$plot <- ggplot(summaryOC_btw$all, aes(Cost, Gamma, fill = Cost)) +
-  # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
-  # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
-  # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-  geom_hline(yintercept = 0.74, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
-  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
-  geom_boxplot(show.legend = F) +
-  geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
-  ylim(0,1.5) +
-  labs(x = "") +
-  scale_fill_manual(values = colsBtw) +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        axis.line = element_line(colour = "black"),
-        text = element_text(size = 16))
-
-## one sample t against optimal strategy
-summaryOC_btw$t.test <- summaryOC_btw$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  sapply(., function(data) {t.test(data$Gamma, mu = 0.74)})
-
-## descriptive stats
-summaryOC_btw$descriptives <- summaryOC_btw$all %>%
-  group_by(Cost) %>%
-  summarise(mGamma = round(mean(Gamma), digits = 2),
-            sdGamma = round(sd(Gamma), digits = 2))
+``` {r OLD BTW and WTH: 16.3. OC modeling btw, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# ## fit the OC model
+# summaryOC_btw <- list()
+# summaryOC_btw$all <- dataBtw %>%
+#                  group_by(Cost, SubjID) %>%
+#                  do(optimizeOCModel(., simplify = T)) %>%
+#                  ungroup()
+# 
+# 
+# ## plot
+# summaryOC_btw$plot <- ggplot(summaryOC_btw$all, aes(Cost, Gamma, fill = Cost)) +
+#   # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
+#   # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
+#   # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
+#   geom_hline(yintercept = 0.74, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
+#   #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
+#   geom_boxplot(show.legend = F) +
+#   geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
+#   ylim(0,1.5) +
+#   labs(x = "") +
+#   scale_fill_manual(values = colsBtw) +
+#   theme(panel.grid.major = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.background = element_blank(),
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 16))
+# 
+# 
+# ## one sample t against optimal strategy
+# summaryOC_btw$t.test <- summaryOC_btw$all %>%
+#   select(Cost, Gamma) %>%
+#   plyr::dlply("Cost", identity) %>%
+#   sapply(., function(data) {t.test(data$Gamma, mu = 0.74)})
+# 
+# 
+# ## descriptive stats
+# summaryOC_btw$descriptives <- summaryOC_btw$all %>%
+#   group_by(Cost) %>%
+#   summarise(mGamma = round(mean(Gamma), digits = 2),
+#             sdGamma = round(sd(Gamma), digits = 2))
 
@@
 
-``` {r BTW: 16.3.5. OC comparisons, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# ANOVA
-OCanova <- list()
-OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC_btw$all))
-Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
-Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
-Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
-
-# Post-hoc pairwise tests
-OCanova$perms <- summaryOC_btw$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  do.call(cbind, .) %>%
-  select_if(is.numeric) %>%
-  rename(Physical = Physical.Gamma,
-         Cognitive = Cognitive.Gamma,
-         Wait = Wait.Gamma,
-         Easy = Easy.Gamma) %>%
-  outer(., ., FUN = Vectorize(permute), simple = T)
-diag(OCanova$perms) <- 1
-
-OCanova$ES <- summaryOC_btw$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  do.call(cbind, .) %>%
-  select_if(is.numeric) %>%
-  rename(Physical = Physical.Gamma,
-         Cognitive = Cognitive.Gamma,
-         Wait = Wait.Gamma,
-         Easy = Easy.Gamma) %>%
-  outer(., ., FUN = Vectorize(cohenD)) %>%
-  abs()
-```
-
-``` {r BTW: 16.3.5. corrplot, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
+``` {r OLD BTW and WTH: 16.3. OC comparisons btw, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# # ANOVA
+# OCanova <- list()
+# OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC_btw$all))
+# Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
+# Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
+# Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
+#   
+# # Post-hoc pairwise tests
+# OCanova$perms <- summaryOC_btw$all %>%
+#   select(Cost, Gamma) %>%
+#   plyr::dlply("Cost", identity) %>%
+#   do.call(cbind, .) %>%
+#   select_if(is.numeric) %>%
+#   rename(Physical = Physical.Gamma,
+#          Cognitive = Cognitive.Gamma,
+#          Wait = Wait.Gamma,
+#          Easy = Easy.Gamma) %>%
+#   outer(., ., FUN = Vectorize(permute), simple = T)
+# diag(OCanova$perms) <- 1
+# 
+# OCanova$ES <- summaryOC_btw$all %>%
+#   select(Cost, Gamma) %>%
+#   plyr::dlply("Cost", identity) %>%
+#   do.call(cbind, .) %>%
+#   select_if(is.numeric) %>%
+#   rename(Physical = Physical.Gamma,
+#          Cognitive = Cognitive.Gamma,
+#          Wait = Wait.Gamma,
+#          Easy = Easy.Gamma) %>%
+#   outer(., ., FUN = Vectorize(cohenD)) %>%
+#   abs()
+```
+
+``` {r OLD BTW and WTH: 16.3. corrplot btw, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
 # # plot all pairwise comparisons
@@
 
-``` {r BTW: 16.3.4. OC cross-validation, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# Compute the OC for pre-midpoint
-summaryOC_btw$pre <- dataBtw %>%
-                 filter(Half == "Half_1") %>%
-                 group_by(Cost, SubjID) %>%
-                 do(optimizeOCModel(., simplify = T)) %>%
-                 ungroup() %>%
-                 select(SubjID, Gamma)
-
-# let's add the gammas to the second half data and estimate prop predicted on the second half
-summaryOC_btw$predicted <- dataBtw %>%
-                 filter(Half == "Half_2") %>%
-                 group_by(Cost, SubjID) %>%
-                 left_join(summaryOC_btw$pre, by = "SubjID") %>%
-                 mutate(OC = Handling * Gamma,
-                        predicted = Offer > OC) %>% 
-                 summarise(percentPredicted = mean(predicted == Choice) * 100) %>%
-                 group_by(Cost) %>%
-                 summarise(mPredicted = round(mean(percentPredicted), digits = 2),
-                           sdPredicted = round(sd(percentPredicted), digits = 2))
+``` {r OLD BTW and WTH: 16.3. OC cross-validation btw, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# # Compute the OC for pre-midpoint
+# summaryOC_btw$pre <- dataBtw %>%
+#                  filter(Half == "Half_1") %>%
+#                  group_by(Cost, SubjID) %>%
+#                  do(optimizeOCModel(., simplify = T)) %>%
+#                  ungroup() %>%
+#                  select(SubjID, Gamma)
+# 
+# # let's add the gammas to the second half data and estimate prop predicted on the second half
+# summaryOC_btw$predicted <- dataBtw %>%
+#                  filter(Half == "Half_2") %>%
+#                  group_by(Cost, SubjID) %>%
+#                  left_join(summaryOC_btw$pre, by = "SubjID") %>%
+#                  mutate(OC = Handling * Gamma,
+#                         predicted = Offer > OC) %>% 
+#                  summarise(percentPredicted = mean(predicted == Choice) * 100) %>%
+#                  group_by(Cost) %>%
+#                  summarise(mPredicted = round(mean(percentPredicted), digits = 2),
+#                            sdPredicted = round(sd(percentPredicted), digits = 2))
 
@@
 
-  We tested three nested models based on a set of criteria derived from observed choice behavior (see Methods for details).
-The first one, a base formulation, estimated a subjective opportunity cost for each individual and demand.
-The second one allowed the OC to gradually adapt using a reinforcement learning rule.
-The final one added a time sensitivity parameter that controlled how each demand affected the perceived length of the handling time, which could be recalibrated based on the experience of multiple types of demands.
-
-  In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
-For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
-Conversely, low gamma values represented low selectivity when evaluating offers.
-Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
-This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC_btw$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC_btw$all$Rsquared), digits = 2)`).
-Figure 10 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
-Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
-In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
-We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC_btw$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC_btw$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC_btw$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
-We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 10; see Operationalization of Cost).
-Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Wait"][[1]])`).
-Neither physical effort (mean = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
-These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
-
-```{r Gamma per cost group (Fig.
-10), eval = !figsEnd, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
-The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
-Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
-
-summaryOC_btw$plot
-
-```
-
-  The second model asked whether interleaved demands gradually altered the OC over time, based on the derivation by Constantino & Daw (2015).
-This model behaved similarly to the base version at low enough values of alpha.
-
-``` {r WTH: 16.3.4., echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
-# Here it might be best to estimate gamma for the wait trials only at first
-# once the wait OCs are estimated, then they can be modulated by effort
-# Estimate gamma per subject for each group separately
-summaryOC_wth <- list()
-summaryOC_wth$all <- dataWth %>%
-  mutate(Block = case_when(
-    Block %in% c(1, 2) ~ 1,
-    Block %in% c(3, 4) ~ 2,
-    Block %in% c(5, 6) ~ 3
-  )) %>%
-  #filter(Choice < 2) %>%
-  group_by(SubjID, Cost) %>% #group_by(SubjID, Cost, Block) %>%
-  do(optimizeOCModel(., simplify = T)) %>%
-  ungroup()
-
-# plot
-summaryOC_wth$plot <- ggplot(summaryOC_wth$all, aes(Cost, Gamma, fill = Cost)) +
-    geom_boxplot(show.legend = F) +
-    geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
-    geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
-    geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-    ylim(0,1.5) +
-    labs(x = "") +
-    scale_fill_manual(values = colsWth) +
-    theme(panel.grid.major = element_blank(),
-          panel.grid.minor = element_blank(),
-          panel.background = element_blank(),
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
+``` {r OLD BTW and WTH: 16.3. OC Modeling wth, echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
+# # Here it might be best to estimate gamma for the wait trials only at first
+# # once the wait OCs are estimated, then they can be modulated by effort
+# # Estimate gamma per subject for each group separately
+# summaryOC_wth <- list()
+# summaryOC_wth$all <- dataWth %>%
+#   mutate(Block = case_when(
+#     Block %in% c(1, 2) ~ 1,
+#     Block %in% c(3, 4) ~ 2,
+#     Block %in% c(5, 6) ~ 3
+#   )) %>%
+#   #filter(Choice < 2) %>%
+#   group_by(SubjID, Cost) %>% #group_by(SubjID, Cost, Block) %>%
+#   do(optimizeOCModel(., simplify = T)) %>%
+#   ungroup()
+# 
+# # plot
+# summaryOC_wth$plot <- ggplot(summaryOC_wth$all, aes(Cost, Gamma, fill = Cost)) +
+#     geom_boxplot(show.legend = F) +
+#     geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
+#     geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
+#     geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
+#     ylim(0,1.5) +
+#     labs(x = "") +
+#     scale_fill_manual(values = colsWth) +
+#     theme(panel.grid.major = element_blank(),
+#           panel.grid.minor = element_blank(),
+#           panel.background = element_blank(),
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 16))
 
@@
 
-``` {r WTH: 16.3.5., echo = FALSE, fig.width=5, fig.height=4, fig.align="center"}
-# subdivide data
-dataTrain <- dataWth %>%
-   filter(Block < 5)
-
-dataTest <- dataWth %>%
-  filter(Block > 4)
-
-# estimate
-# per-cost, but consider the idea above
-OCs_validation <- list()
-temp <- dataTrain %>% filter(Cost == "Wait-C") %>% plyr::dlply("SubjID", identity)
-OCs_validation$`Wait-C` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-temp <- dataTrain %>% filter(Cost == "Wait-P") %>% plyr::dlply("SubjID", identity)
-OCs_validation$`Wait-P` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-temp <- dataTrain %>% filter(Cost == "Cognitive") %>% plyr::dlply("SubjID", identity)
-OCs_validation$Cognitive <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-temp <- dataTrain %>% filter(Cost == "Physical") %>% plyr::dlply("SubjID", identity)
-OCs_validation$Physical <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-
-# reshape data
-temp <- bind_rows(OCs_validation) %>% 
-  mutate(SubjID = subjList_wth) %>%
-  gather(Cost, gamma, `Wait-C`:Physical) %>%
-  left_join(dataTest, ., by = c("SubjID", "Cost")) %>% # assign OCs to each subject per cost type
-  mutate(prediction = Offer > Handling * gamma) %>%
-  # plyr::dlply("SubjID", identity)
-  group_by(SubjID, Cost) %>%
-  summarize(predicted = mean(Choice == prediction))
+``` {r OLD BTW and WTH: 16.3. cross-v wth, echo = FALSE, fig.width=5, fig.height=4, fig.align="center"}
+# # subdivide data
+# dataTrain <- dataWth %>%
+#    filter(Block < 5)
+# 
+# dataTest <- dataWth %>%
+#   filter(Block > 4)
+# 
+# # estimate
+# # per-cost, but consider the idea above
+# OCs_validation <- list()
+# temp <- dataTrain %>% filter(Cost == "Wait-C") %>% plyr::dlply("SubjID", identity)
+# OCs_validation$`Wait-C` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+# temp <- dataTrain %>% filter(Cost == "Wait-P") %>% plyr::dlply("SubjID", identity)
+# OCs_validation$`Wait-P` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+# temp <- dataTrain %>% filter(Cost == "Cognitive") %>% plyr::dlply("SubjID", identity)
+# OCs_validation$Cognitive <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+# temp <- dataTrain %>% filter(Cost == "Physical") %>% plyr::dlply("SubjID", identity)
+# OCs_validation$Physical <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
+# 
+# # reshape data
+# temp <- bind_rows(OCs_validation) %>% 
+#   mutate(SubjID = subjList_wth) %>%
+#   gather(Cost, gamma, `Wait-C`:Physical) %>%
+#   left_join(dataTest, ., by = c("SubjID", "Cost")) %>% # assign OCs to each subject per cost type
+#   mutate(prediction = Offer > Handling * gamma) %>%
+#   # plyr::dlply("SubjID", identity)
+#   group_by(SubjID, Cost) %>%
+#   summarize(predicted = mean(Choice == prediction))
 
@@
 
-``` {r WTH: 16.3.6., echo = FALSE}
-# repeated measures anova
-OCs_anova <- list()
-OCs_anova$aov <- summary(aov(Gamma ~ Cost + Error(SubjID / Cost), data = summaryOC_wth$all))
-
-# table
-#pander(OCs_anova$aov)
-
-# do all pairwise comparisons
-OCs_anova$gammas <- summaryOC_wth$all %>% 
-  reshape2::dcast(SubjID ~ Cost, value.var = "Gamma") %>%
-  select(-SubjID)
-
-# perform a paired permutation among every pair of cost types
-OCs_anova$perms <- outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(permute), simple = T, paired = T)
-OCs_anova$perms[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
-
-# and the effect sizes
-OCs_anova$ES <- abs(outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(DescTools::CohenD)))
-OCs_anova$ES[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
-```
-
-``` {r WTH: 16.3.6. corrplot, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
+``` {r OLD BTW and WTH: 16.3. param compare wth, echo = FALSE}
+# # repeated measures anova
+# OCs_anova <- list()
+# OCs_anova$aov <- summary(aov(Gamma ~ Cost + Error(SubjID / Cost), data = summaryOC_wth$all))
+# 
+# # table
+# #pander(OCs_anova$aov)
+# 
+# # do all pairwise comparisons
+# OCs_anova$gammas <- summaryOC_wth$all %>% 
+#   reshape2::dcast(SubjID ~ Cost, value.var = "Gamma") %>%
+#   select(-SubjID)
+# 
+# # perform a paired permutation among every pair of cost types
+# OCs_anova$perms <- outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(permute), simple = T, paired = T)
+# OCs_anova$perms[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
+# 
+# # and the effect sizes
+# OCs_anova$ES <- abs(outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(DescTools::CohenD)))
+# OCs_anova$ES[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
+```
+
+``` {r OLD BTW and WTH: 16.3. corrplot wth, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
 # corrplot(OCs_anova$ES,
@@
 ```
+
+```{r Gamma per cost group (Fig.
+10), eval = !figsEnd, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
+The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
+Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
+
+#summaryOC_btw$plot
+
+```
+
+``` {r BTW and WTH: 16.3. Model fits, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# load results from models
+load("models_gk/results/btw.Rdata")
+load("models_gk/results/wth.Rdata")
+```
+
+  We tested four models based on a set of criteria derived from observed choice behavior (see Methods for details).
+The first one, a base formulation, probed the predictions of the Marginal Value Theorem (Charnov, 1975).
+The second one allowed the opportunity cost to gradually adapt using a reinforcement learning rule.
+The third model assumed that different demands imposed distinct biases on the perceived opportunity costs, and that these biases could be recalibrated with experience.
+A final model combined the adaptive features of the second and third formulations.
+
+  In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
+Conversely, low gamma values represented low selectivity when evaluating offers.
+Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
+This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC_btw$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC_btw$all$Rsquared), digits = 2)`).
+Figure 10 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
+Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
+In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
+We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC_btw$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC_btw$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC_btw$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 10; see Operationalization of Cost).
+Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Wait"][[1]])`).
+Neither physical effort (mean = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
+These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
+
+  The second model asked whether interleaved demands gradually altered the OC over time, based on the derivation by Constantino & Daw (2015).
+This model behaved similarly to the base version at low enough values of alpha.
 

### 2020-12-04 Cost_manuscript.Rmd
basic model fit import and plot

@@
 ``` {r BTW and WTH: 16.3. Model fits, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
+# the fitting of these models was performed by a separate script (modeling_gk_btw/wth)
+# here we load the results to economize computational power during knitting
 # load results from models
-load("models_gk/results/btw.Rdata")
-load("models_gk/results/wth.Rdata")
+#load("models_gk/results/btw.Rdata")
+#load("models_gk/results/wth.Rdata")
+load("models_gk/results/mod_results.Rdata")
+
+# keep relevant model results and combine into a single df with generalizable names (delete eventually)
+temp_btw <- fits_bic_btw[c(1, 3, 4, 6), ]
+temp_wth <- fits_bic_wth[c(1, 3, 13, 15), ]
+temp_btw$wth <- temp_wth$bic
+colnames(temp_btw) <- c("Model", "Between", "Within")
+modelComparison <- temp_btw %>% gather(Exp, BIC, -Model)
+rm(temp_btw, temp_wth, fits_bic_btw, fits_bic_wth)
+
+# plot BIC across models for both exps
+bic_plot <- ggplot(data = modelComparison, aes(Model, BIC, group = Exp, color = Exp)) +
+  geom_line(size = 2) +
+  geom_point(size = 4) +
+  scale_color_grey(start = 0.2, end = 0.6) +
+  theme(legend.position = c(0.8, 0.8),
+        axis.text.x = element_text(angle = 20, hjust = 1),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 22))
+
 ```
@@
 
-  In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+  <!-- In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
 For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
@@
 These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
-
-  The second model asked whether interleaved demands gradually altered the OC over time, based on the derivation by Constantino & Daw (2015).
-This model behaved similarly to the base version at low enough values of alpha.
+-->
 

### 2020-12-04 Cost_manuscript.Rmd
commenting had not worked

@@
   A third model considered the possibility that each type of demand additively biased the estimate of $\gamma$.
-Such bias would be stable if a single demand was experienced, but recalibrated into a global estimate as decision makers faced different types of demands.
+Such cost bias would be stable if a single demand was experienced, but recalibrated into a global estimate as decision makers faced different types of demands.
 The overall model took the following form
@@
 
-  where $\gamma$ was the mean total earning rate for the whole group (0.55). At each decision point, $mC$ was the bias produced by each demand $c_{demand}$ weighted against a global bias estimate $C$
+where $\gamma$ was the mean total earning rate for the whole group (0.55).
+Negative values of $mC_i$ would therefore suggest a boost in offer value produced by a demand.
+At each decision point, $mC$ was the cost bias produced by each demand $c_{demand}$ weighted against a global bias estimate $C$
 
@@
 
-  with $w_i$ controlling how early participants started integrating the converging bias $C$ into their decisions. The value of this weight was given by
+with $w_i$ controlling how early participants started integrating the converging cost $C$ into their decisions. The value of this weight was given by
 
@@
 
-  We tested four models based on a set of criteria derived from observed choice behavior (see Methods for details).
+  We tested four models against a set of criteria derived from observed choice behavior (see Methods for details).
 The first one, a base formulation, probed the predictions of the Marginal Value Theorem (Charnov, 1975).
 The second one allowed the opportunity cost to gradually adapt using a reinforcement learning rule.
-The third model assumed that different demands imposed distinct biases on the perceived opportunity costs, and that these biases could be recalibrated with experience.
+The third model assumed that different demands imposed distinct cost biases on the perceived opportunity costs, and that these biases could be recalibrated with experience.
 A final model combined the adaptive features of the second and third formulations.
 
-  <!-- In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+```{r BIC (Fig.
+10), eval = !figsEnd, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "BIC values for four plausible models of choice behavior for both experiments.
+Note that the number of parameters fitted could change across experiments, affecting the possible BIC values.
+The winning model suggests that demands impose cost biases to the ongoing estmate of the opportunity cost, which converge if multiple types of demands are interleaved.
+"}
+
+bic_plot
+
+# In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
 For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
@@
 These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
--->
+
+```
 
@@
 
-summaryOC_btw$plot
+#summaryOC_btw$plot
 

### 2020-12-04 Cost_manuscript.Rmd
anova + plots for parameter comparison. now add paired permutations

@@
 ``` {r OLD BTW and WTH: 16.3. OC comparisons btw, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# # ANOVA
-# OCanova <- list()
-# OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC_btw$all))
-# Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
-# Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
-# Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
-#   
-# # Post-hoc pairwise tests
-# OCanova$perms <- summaryOC_btw$all %>%
-#   select(Cost, Gamma) %>%
-#   plyr::dlply("Cost", identity) %>%
-#   do.call(cbind, .) %>%
-#   select_if(is.numeric) %>%
-#   rename(Physical = Physical.Gamma,
-#          Cognitive = Cognitive.Gamma,
-#          Wait = Wait.Gamma,
-#          Easy = Easy.Gamma) %>%
-#   outer(., ., FUN = Vectorize(permute), simple = T)
-# diag(OCanova$perms) <- 1
-# 
-# OCanova$ES <- summaryOC_btw$all %>%
-#   select(Cost, Gamma) %>%
-#   plyr::dlply("Cost", identity) %>%
-#   do.call(cbind, .) %>%
-#   select_if(is.numeric) %>%
-#   rename(Physical = Physical.Gamma,
-#          Cognitive = Cognitive.Gamma,
-#          Wait = Wait.Gamma,
-#          Easy = Easy.Gamma) %>%
-#   outer(., ., FUN = Vectorize(cohenD)) %>%
-#   abs()
+# ANOVA
+OCanova <- list()
+OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC_btw$all))
+Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
+Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
+Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
+
+# Post-hoc pairwise tests
+OCanova$perms <- summaryOC_btw$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(permute), simple = T)
+diag(OCanova$perms) <- 1
+
+OCanova$ES <- summaryOC_btw$all %>%
+  select(Cost, Gamma) %>%
+  plyr::dlply("Cost", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = Physical.Gamma,
+         Cognitive = Cognitive.Gamma,
+         Wait = Wait.Gamma,
+         Easy = Easy.Gamma) %>%
+  outer(., ., FUN = Vectorize(cohenD)) %>%
+  abs()
 ```
@@
 ``` {r BTW and WTH: 16.3. Model fits, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# the fitting of these models was performed by a separate script (modeling_gk_btw/wth)
+## the fitting of these models was performed by a separate script (modeling_gk_btw/wth)
 # here we load the results to economize computational power during knitting
@@
 
+## BIC
 # keep relevant model results and combine into a single df with generalizable names (delete eventually)
@@
 
+## Model fit summaries
+# mean and sd of parameters from winning model (exp some? still confused)
+# parameter order for wth: gamma, alpha, C, w_decay, beta
+mFits_btw <- sapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {apply(group$x, 1, mean)})
+sdFits_btw <- sapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {apply(group$x, 1, sd)})
+
+mFits_wth <- fits_wth$`Adaptive OC + Adaptive Between Biased OC`$mus
+sdFits_wth <- diag(fits_wth$`Adaptive OC + Adaptive Between Biased OC`$sigma)
+
+## Compare
+# first, divide the group fits into a list of dataframes for each parameter
+t <- lapply(fits_btw$`Adaptive OC + Biased OC`, function(group) {melt(group$x, value.name = "Fit")})
+n <- names(fits_btw$`Adaptive OC + Biased OC`)
+reshaped <- mapply(cbind, t, "Group" = n, SIMPLIFY = F)
+aovShape_btw <- do.call(rbind, reshaped) %>% 
+                  filter(Group != "pheasy") %>%
+                  plyr::dlply("Var1", identity)
+rm(t, n)
+
+# then apply anovas
+aovBtw <- lapply(aovShape_btw, function(d) {summary(aov(Fit ~ Group, data = d))})
+
+## plot
+# BTW
+# select a parameter to plot
+param <- aovShape_btw$cost
+paramPlot <- ggplot(param, aes(Group, Fit, fill = Group)) +
+  # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
+  # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
+  # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
+  geom_hline(yintercept = 0, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
+  #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
+  geom_boxplot(show.legend = F) +
+  geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
+  #ylim(0,1.5) +
+  labs(x = "") +
+  scale_fill_manual(values = colsBtw) +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 16))
+
 ```
@@
 The first one, a base formulation, probed the predictions of the Marginal Value Theorem (Charnov, 1975).
-The second one allowed the opportunity cost to gradually adapt using a reinforcement learning rule.
-The third model assumed that different demands imposed distinct cost biases on the perceived opportunity costs, and that these biases could be recalibrated with experience.
+The second one allowed individuals to estimate the opportunity cost at different rates using a reinforcement learning rule.
+The third model assumed that different demands imposed distinct cost biases on the experienced opportunity costs, and that these biases could be recalibrated with experience.
 A final model combined the adaptive features of the second and third formulations.
+
+  The fourth model produced the lowest BIC in both experiments (Figure 10A. Between-subjects = $modelComparison[4, 3]$; Within-subjects = $modelComparison[8, 3]$).
+
+  The fits of the model provided good qulitative resemblance to the observed choice behavior in both experiments (*Figure 10X*)
 

### 2020-12-07 Cost_manuscript.Rmd
filling in with fits from relevant btw-subj analyses

@@
 # plot BIC across models for both exps
-bic_plot <- ggplot(data = modelComparison, aes(Model, BIC, group = Exp, color = Exp)) +
+bicPlot <- ggplot(data = modelComparison, aes(Model, BIC, group = Exp, color = Exp)) +
   geom_line(size = 2) +
@@
 ## Compare
+# BTW
 # first, divide the group fits into a list of dataframes for each parameter
@@
 aovBtw <- lapply(aovShape_btw, function(d) {summary(aov(Fit ~ Group, data = d))})
+fitFvals <- round(sapply(aovBtw, function(x) {x[[1]]$`F value`[1]}), digits = 2)
+fitPvals <- sapply(aovBtw, function(x) {x[[1]]$`Pr(>F)`[1]})
+
+# post-hoc permutations (5k)
+# only applied to cost, since alpha was not significant;y diff and other params were not super interesting
+fitPerms <- aovShape_btw$cost %>%
+  select(Group, Fit) %>%
+  plyr::dlply("Group", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = phys.Fit,
+         Cognitive = cogTask.Fit,
+         Wait = wait.Fit) %>%
+  outer(., ., FUN = Vectorize(permute), simple = T)
+
+# and effect sizes
+fitES <- aovShape_btw$cost %>%
+  select(Group, Fit) %>%
+  plyr::dlply("Group", identity) %>%
+  do.call(cbind, .) %>%
+  select_if(is.numeric) %>%
+  rename(Physical = phys.Fit,
+         Cognitive = cogTask.Fit,
+         Wait = wait.Fit) %>%
+  outer(., ., FUN = Vectorize(DescTools::CohenD))
 
@@
 # select a parameter to plot
-param <- aovShape_btw$cost
+param <- do.call(rbind, aovShape_btw)
 paramPlot <- ggplot(param, aes(Group, Fit, fill = Group)) +
@@
     # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-  geom_hline(yintercept = 0, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
+    #geom_hline(yintercept = 0, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
     #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
@@
     labs(x = "") +
+    facet_wrap(vars(Var1), scales = "free") +
     scale_fill_manual(values = colsBtw) +
@@
 
+# WTH
+
+(bicPlot + paramPlot)
 ```
@@
 
-  The fourth model produced the lowest BIC in both experiments (Figure 10A. Between-subjects = $modelComparison[4, 3]$; Within-subjects = $modelComparison[8, 3]$).
+  The fourth model produced the lowest BIC in both experiments (Figure 10A.
+Between-subjects = $modelComparison[4, 3]$; Within-subjects = $modelComparison[8, 3]$).
+Figure 10B shows the parameter fits from the between-subjects experiment.
+Among these, the learning rate of the opportunity cost ($\alpha$) and the bias imposed by each demand on its estimate ($C_{demand}$) were of particular interest.
+Analyses of variance showed significant differences only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[1]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
+Pairwise post-hoc permutations confirmed that the cognitive group () had lower biases than either wait () or physical () groups.
+Furthermore, these estimates were significantly lower than zero (tstats).
+These fits suggest that individuals integrated the opportunity cost of time at similar rates regardless of the concomitant demand, but that cognitive tasks boost the value of offers (**reword**).
 
@@
 
-# In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+#In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
 For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
@@
 
+ial.
+For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
+Conversely, low gamma values represented low selectivity when evaluating offers.
+Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
+This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC_btw$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC_btw$all$Rsquared), digits = 2)`).
+Figure 10 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
+Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
+In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
+We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC_btw$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC_btw$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC_btw$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 10; see Operationalization of Cost).
+Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Wait"][[1]])`).
+Neither physical effort (mean = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
+These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
+
 ## Discussion

### 2020-12-07 Cost_manuscript.Rmd
stats for the btw subj fits added

@@
 
-## BIC
+### BIC
 # keep relevant model results and combine into a single df with generalizable names (delete eventually)
@@
 
-## Model fit summaries
+### Model fit summaries
 # mean and sd of parameters from winning model (exp some? still confused)
@@
 
-## Compare
-# BTW
+### Compare/analyze fits
+## BTW
 # first, divide the group fits into a list of dataframes for each parameter
@@
 
-# and effect sizes
+# effect sizes
 fitES <- aovShape_btw$cost %>%
@@
          Wait = wait.Fit) %>%
-  outer(., ., FUN = Vectorize(DescTools::CohenD))
-
-## plot
-# BTW
-# select a parameter to plot
+  outer(., ., FUN = Vectorize(DescTools::CohenD)) %>%
+  abs() %>%
+  round(digits = 2)
+
+# and two-sided, one-sample t-test against 0
+fitOStest <- aovShape_btw$cost %>%
+  group_by(Group) %>%
+  summarise(tresults = list(t.test(Fit, mu = 0)))
+
+### plot parameter boxplots
+## BTW
 param <- do.call(rbind, aovShape_btw)
 paramPlot <- ggplot(param, aes(Group, Fit, fill = Group)) +
-    # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
-    # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
-    # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-    #geom_hline(yintercept = 0, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
-    #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
     geom_boxplot(show.legend = F) +
     geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
-    #ylim(0,1.5) +
     labs(x = "") +
@@
 
-# WTH
+## WTH
 
@@
 Analyses of variance showed significant differences only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[1]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
-Pairwise post-hoc permutations confirmed that the cognitive group () had lower biases than either wait () or physical () groups.
-Furthermore, these estimates were significantly lower than zero (tstats).
-These fits suggest that individuals integrated the opportunity cost of time at similar rates regardless of the concomitant demand, but that cognitive tasks boost the value of offers (**reword**).
-
+Pairwise post-hoc permutations confirmed that the cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower biases than either wait (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or physical (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`) groups.
+These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = round(`r fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = round(`r fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
+This suggests that rather than reducing costs, cognitive tasks boosted the value of their concommitant offers.
+
+  **within**
   The fits of the model provided good qulitative resemblance to the observed choice behavior in both experiments (*Figure 10X*)

### 2020-12-08 Cost_manuscript.Rmd
plotting across exps

@@
   scale_color_grey(start = 0.2, end = 0.6) +
+  xlab("") +
+  scale_x_discrete(labels = c("Base", "Adaptive", "Biased", "A + B")) +
   theme(legend.position = c(0.8, 0.8),
-        axis.text.x = element_text(angle = 20, hjust = 1),
+        #axis.text.x = element_text(angle = 20, hjust = 1),
         panel.grid.major = element_blank(),
@@
           axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
+          text = element_text(size = 22))
 
 ## WTH
-
-(bicPlot + paramPlot)
+paramPlot_wth <- melt(fits_wth$`Adaptive OC + Adaptive Between Biased OC`$x) %>%
+  ggplot(aes(Var1, value)) +
+    geom_boxplot(show.legend = F, fill = "grey50") +
+    geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3, fill = "grey50") +
+    labs(x = "") +
+    ylab("Fitted Value") +
+    #scale_fill_grey() +
+    #facet_wrap(vars(Var1), scales = "free") +
+    theme(panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.background = element_blank(),
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 22))
+
+### plots comparing across exps
+# cost bias plot
+costPlot <- ggplot(aovShape_btw$cost, aes(Group, Fit, fill = Group)) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_boxplot(show.legend = F) +
+  geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
+  labs(x = "") +
+  #facet_wrap(vars(Var1), scales = "free") +
+  scale_x_discrete(labels = c("Wait", "Cognitive", "Physical")) +
+  scale_fill_manual(values = colsBtw) +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.line = element_line(colour = "black"),
+        text = element_text(size = 22))
+
+# reshape data to combine across exps
+t1 <- melt(fits_wth$`Adaptive OC + Adaptive Between Biased OC`$x, value.name = "Fit") %>%
+  mutate(Group = "Within")
+t2 <- do.call(rbind, aovShape_btw)
+
+# get a new color
+tempCols <- colsBtw
+tempCols[4] <- "grey50"
+allFitsPlot <- rbind(t1, t2) %>%
+  filter(!Var1 %in% c("C", "w_decay", "cost")) %>%
+  mutate(Group = factor(Group, levels = c("wait", "cogTask", "phys", "Within", "pheasy"))) %>%
+  ggplot(aes(Group, Fit, fill = Group)) +
+    geom_boxplot(show.legend = F) +
+    geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
+    labs(x = "") +
+    scale_x_discrete(labels = c("Wait", "Cognitive", "Physical", "Within")) +
+    geom_vline(xintercept = 3.5, linetype = "dashed") +
+    facet_wrap(vars(Var1), scales = "free", ncol = 3) +
+    scale_fill_manual(values = tempCols) +
+    theme(panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          panel.background = element_blank(),
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 22))
+
+#(bicPlot + costPlot) / allFitsPlot
+
 ```
@@
 Between-subjects = $modelComparison[4, 3]$; Within-subjects = $modelComparison[8, 3]$).
-Figure 10B shows the parameter fits from the between-subjects experiment.
+Figure 10B-C show the key parameter fits from both experiments.
 Among these, the learning rate of the opportunity cost ($\alpha$) and the bias imposed by each demand on its estimate ($C_{demand}$) were of particular interest.
@@
 Pairwise post-hoc permutations confirmed that the cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower biases than either wait (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or physical (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`) groups.
-These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = round(`r fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = round(`r fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
+These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = round(`r fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower than zero for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = round(`r fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
 This suggests that rather than reducing costs, cognitive tasks boosted the value of their concommitant offers.
 
-  **within**
+  The median values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a converging $C$ value (see Methods for details).
+
   The fits of the model provided good qulitative resemblance to the observed choice behavior in both experiments (*Figure 10X*)

### 2020-12-08 Cost_manuscript.Rmd
results section draft written. pending tweaks

@@
 ``` {r OLD BTW and WTH: 16.3. OC comparisons btw, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# ANOVA
-OCanova <- list()
-OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC_btw$all))
-Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
-Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
-Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
-
-# Post-hoc pairwise tests
-OCanova$perms <- summaryOC_btw$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  do.call(cbind, .) %>%
-  select_if(is.numeric) %>%
-  rename(Physical = Physical.Gamma,
-         Cognitive = Cognitive.Gamma,
-         Wait = Wait.Gamma,
-         Easy = Easy.Gamma) %>%
-  outer(., ., FUN = Vectorize(permute), simple = T)
-diag(OCanova$perms) <- 1
-
-OCanova$ES <- summaryOC_btw$all %>%
-  select(Cost, Gamma) %>%
-  plyr::dlply("Cost", identity) %>%
-  do.call(cbind, .) %>%
-  select_if(is.numeric) %>%
-  rename(Physical = Physical.Gamma,
-         Cognitive = Cognitive.Gamma,
-         Wait = Wait.Gamma,
-         Easy = Easy.Gamma) %>%
-  outer(., ., FUN = Vectorize(cohenD)) %>%
-  abs()
+# # ANOVA
+# OCanova <- list()
+# OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC_btw$all))
+# Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
+# Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
+# Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
+# 
+# # Post-hoc pairwise tests
+# OCanova$perms <- summaryOC_btw$all %>%
+#   select(Cost, Gamma) %>%
+#   plyr::dlply("Cost", identity) %>%
+#   do.call(cbind, .) %>%
+#   select_if(is.numeric) %>%
+#   rename(Physical = Physical.Gamma,
+#          Cognitive = Cognitive.Gamma,
+#          Wait = Wait.Gamma,
+#          Easy = Easy.Gamma) %>%
+#   outer(., ., FUN = Vectorize(permute), simple = T)
+# diag(OCanova$perms) <- 1
+# 
+# OCanova$ES <- summaryOC_btw$all %>%
+#   select(Cost, Gamma) %>%
+#   plyr::dlply("Cost", identity) %>%
+#   do.call(cbind, .) %>%
+#   select_if(is.numeric) %>%
+#   rename(Physical = Physical.Gamma,
+#          Cognitive = Cognitive.Gamma,
+#          Wait = Wait.Gamma,
+#          Easy = Easy.Gamma) %>%
+#   outer(., ., FUN = Vectorize(cohenD)) %>%
+#   abs()
 ```
@@
 
-mFits_wth <- fits_wth$`Adaptive OC + Adaptive Between Biased OC`$mus
-sdFits_wth <- diag(fits_wth$`Adaptive OC + Adaptive Between Biased OC`$sigma)
+mFits_wth <- round(fits_wth$`Adaptive OC + Adaptive Between Biased OC`$mus, digits = 2)
+sdFits_wth <- round(diag(fits_wth$`Adaptive OC + Adaptive Between Biased OC`$sigma), digits = 2)
 
@@
 
-#(bicPlot + costPlot) / allFitsPlot
-
 ```
@@
 Pairwise post-hoc permutations confirmed that the cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower biases than either wait (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or physical (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`) groups.
-These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = round(`r fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower than zero for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = round(`r fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
+These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = round(`r round(fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower than zero for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = round(`r round(fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
 This suggests that rather than reducing costs, cognitive tasks boosted the value of their concommitant offers.
 
-  The median values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a converging $C$ value (see Methods for details).
-
-  The fits of the model provided good qulitative resemblance to the observed choice behavior in both experiments (*Figure 10X*)
+  The median values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $C$ value (see Methods for details).
+As can be seen on Figure 10C, parameter values were comparable across experiments, pointing to consisency in the way decision makers approached our foraging scenarios.
+In addition, values of $\alpha_w$ suggested that $c_{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session (mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
+Model fits also provided good qulitative resemblance to the observed choice behavior in both experiments, which can be found on **Supplemental Figure X** .
 
 ```{r BIC (Fig.
-10), eval = !figsEnd, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "BIC values for four plausible models of choice behavior for both experiments.
-Note that the number of parameters fitted could change across experiments, affecting the possible BIC values.
-The winning model suggests that demands impose cost biases to the ongoing estmate of the opportunity cost, which converge if multiple types of demands are interleaved.
-"}
-
-bic_plot
+10), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "A.
+BIC values for four plausible models of choice behavior for both experiments.
+B.
+Differences in cost biases produced by each demand.
+The cognitive group acted as if it perceived its demand as valuable.
+C.
+Parameter comparison across experiments."}
+
+(bicPlot + costPlot) / allFitsPlot
 
@@
 
-ial.
-For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
-Conversely, low gamma values represented low selectivity when evaluating offers.
-Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
-This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC_btw$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC_btw$all$Rsquared), digits = 2)`).
-Figure 10 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
-Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
-In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
-We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC_btw$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC_btw$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC_btw$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
-We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 10; see Operationalization of Cost).
-Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Wait"][[1]])`).
-Neither physical effort (mean = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
-These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
-
 ## Discussion

### 2020-12-08 Cost_manuscript.Rmd
ironed out some plot mismatches and added a reference

@@
 The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4)."}
-include_graphics("./Images/FIG10.png")
+include_graphics("./Images/FIG9.png")
 
@@
         axis.line = element_line(colour = "black"),
-        text = element_text(size = 22))
+        text = element_text(size = 16))
 
@@
 # cost bias plot
-costPlot <- ggplot(aovShape_btw$cost, aes(Group, Fit, fill = Group)) +
+costPlot <- aovShape_btw$cost %>%
+  mutate(Group = factor(Group, levels = c("phys", "cogTask", "wait", "pheasy"))) %>%
+  ggplot(aes(Group, Fit, fill = Group)) +
     geom_hline(yintercept = 0, linetype = "dashed") +
@@
     #facet_wrap(vars(Var1), scales = "free") +
-  scale_x_discrete(labels = c("Wait", "Cognitive", "Physical")) +
+    scale_x_discrete(labels = c("Physical", "Cognitive", "Wait")) +
     scale_fill_manual(values = colsBtw) +
@@
           axis.line = element_line(colour = "black"),
-        text = element_text(size = 22))
+          text = element_text(size = 16))
 
@@
   filter(!Var1 %in% c("C", "w_decay", "cost")) %>%
-  mutate(Group = factor(Group, levels = c("wait", "cogTask", "phys", "Within", "pheasy"))) %>%
+  mutate(Group = factor(Group, levels = c("phys", "cogTask", "wait", "Within", "pheasy"))) %>%
   ggplot(aes(Group, Fit, fill = Group)) +
@@
     labs(x = "") +
-    scale_x_discrete(labels = c("Wait", "Cognitive", "Physical", "Within")) +
+    scale_x_discrete(labels = c("Physical", "Cognitive", "Wait", "Within")) +
     geom_vline(xintercept = 3.5, linetype = "dashed") +
@@
           axis.line = element_line(colour = "black"),
-          text = element_text(size = 22))
-
+          text = element_text(size = 16))
 ```
@@
   The fourth model produced the lowest BIC in both experiments (Figure 10A.
-Between-subjects = $modelComparison[4, 3]$; Within-subjects = $modelComparison[8, 3]$).
+Between-subjects = `r round(modelComparison[4, 3], digits = 2)`; Within-subjects = `r round(modelComparison[8, 3], digits = 2)`).
 Figure 10B-C show the key parameter fits from both experiments.
-Among these, the learning rate of the opportunity cost ($\alpha$) and the bias imposed by each demand on its estimate ($C_{demand}$) were of particular interest.
-Analyses of variance showed significant differences only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[1]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
+Among these, the learning rate of the opportunity cost ($\alpha$) and the bias imposed by each demand on its estimate ($c_{demand}$) were of particular interest.
+Analyses of variance showed significant differences only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[2]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
 Pairwise post-hoc permutations confirmed that the cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower biases than either wait (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or physical (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`) groups.
-These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = round(`r round(fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower than zero for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = round(`r round(fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
+These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = `r round(fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower than zero for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = `r round(fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
 This suggests that rather than reducing costs, cognitive tasks boosted the value of their concommitant offers.
@@
 In addition, values of $\alpha_w$ suggested that $c_{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session (mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
-Model fits also provided good qulitative resemblance to the observed choice behavior in both experiments, which can be found on **Supplemental Figure X** .
+Model fits also provided good qulitative resemblance to the observed choice behavior in both experiments (**Supplemental Figure X?**), fulfilling all but one of our modeling criteria (i.e.
+reduction in acceptances for between-subject effort groups).
 
@@
 
-(bicPlot + costPlot) / allFitsPlot
+include_graphics("./Images/FIG10.png")
+
+#(bicPlot + costPlot) / allFitsPlot
 

### 2020-12-08 Cost_manuscript.Rmd
few more explanatory details on comp modeling results

@@
   The fourth model produced the lowest BIC in both experiments (Figure 10A.
-Between-subjects = `r round(modelComparison[4, 3], digits = 2)`; Within-subjects = `r round(modelComparison[8, 3], digits = 2)`).
-Figure 10B-C show the key parameter fits from both experiments.
-Among these, the learning rate of the opportunity cost ($\alpha$) and the bias imposed by each demand on its estimate ($c_{demand}$) were of particular interest.
+Between-subjects = `r round(modelComparison[4, 3], digits = 2)`; Within-subjects = `r round(modelComparison[8, 3], digits = 2)`), indicating that the tenets of the Marginal Value Theorem were necessary but not sufficient to explain the observed adaptive behavior.
+Figure 10B-C show parameter fits from the winning model for both experiments.
+The learning rate $\alpha$ and the bias $c_{demand}$ were of particular interest, as these parameters distinguished whether different demands globally affected the integration of the environmental richness or focally modulated an offer's perceived cost, respectively.
 Analyses of variance showed significant differences only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[2]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
@@
 Model fits also provided good qulitative resemblance to the observed choice behavior in both experiments (**Supplemental Figure X?**), fulfilling all but one of our modeling criteria (i.e.
-reduction in acceptances for between-subject effort groups).
+reduction in acceptances for between-subject effort groups, see Methods for details).
 

### 2020-12-08 Cost_manuscript.Rmd
reworded intro

@@
 ---
+
+<!-- NOTE: 
+If you're on Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
+-->
 
@@
 Our results extend the view that cognitive demands may reduce the discounting effect of delays, but also suggest that differences in cost can eventually fade if individuals actively experience alternative forms of demand.
-Rather than assigning intrinsic value to cognitive effort, our findings support the idea that a cognitive effort requirement might influence contextual factors such as subjective delay durations or the perceived opportunity cost of time.
+Rather than assigning intrinsic value to cognitive effort, our findings support the idea that a cognitive effort requirement might influence contextual factors such as subjective delay durations.
 Such altered estimations can be recalibrated if multiple forms of demand are interleaved.
@@
 
-  Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it.
+  Evaluating whether to pursue a desirable outcome often requires assessing the demands required for obtaining it.
 In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017 ;@Westbrook2015].
@@
 Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @Kool2010; @Westbrook2013].
-Although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across effort types [@Arulpragasam2018; @Biaaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and discount rates do not always correlate across cost domains [@Seaman2018; @Westbrook2013].
+Although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across types of demands [@Arulpragasam2018; @Biaaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and discount rates do not always correlate across cost domains [@Seaman2018; @Westbrook2013].
 However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context [@Kool2018].
@@
 Recent work has proposed that the subjective costs produced by delays and cognitive effort is modulated by the possibility of missing out on better concurrent alternatives, namely the opportunity cost of time [OC; @Fawcett2012; @Kurzban2013; @Otto2019].
-This evidence sets the stage for examining what people would actually select when given the option for multiple types of demands, including the unexplored question of deciding between cognitive and physical effort [@Inzlicht2018; @Kool2018].
+This evidence sets the stage for examining what people would actually select when given the option for multiple types of demands, including the mostly unexplored question of deciding between cognitive and physical effort [@Inzlicht2018; @Kool2018].
 
@@
 First, it allows for the estimation of optimal, reward maximizing choice patterns based on the opportunity cost of time [@Charnov1976; @Krebs1977].
-We can therefore interpret observed deviations in acceptance rates from such optimal behavior in addition to comparing them among demands.
+We can interpret observed deviations in acceptance rates from such optimal behavior in addition to comparing them among demands.
 Second, the sequential nature of foraging allows individuals to emphasize different elements of the decision context.
-For example, the cost (or value) of effort or delay could globally depend on the availability of alternative demands (as suggested above), impacting the perceived opportunity cost of time.
+For example, the cost (or value) of effort and delay could globally depend on the availability of alternative demands (as suggested above), impacting the perceived opportunity cost of time.
 Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that are adjusted once individuals experience different forms of behavioral costs.
@@
 cognitive effort, physical effort, and delay).
-We explored this question in two foraging experiments: a between-subjects design in which participants foraged for rewards while performing a single demand, and a within-subjects extension that had individuals forage for demands in addition to rewards.
+We explored this question in two foraging experiments: a between-subjects design in which participants foraged for rewards while performing a single demand, and a within-subjects extension where individuals foraged for demands in addition to rewards.
 We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions [@Inzlicht2018].
@@
 overharvesting poor offers).
-Second, increasing the level of exposure to types of demands allowed us to asses whether their cost was intrinsic or relative.
+Second, increasing the level of exposure to types of demands across experiments allowed us to asses whether their cost was intrinsic or relative.
 Finally, confronting participants with both mental and physical effort let us probe whether these preferences were domain general or task-specific, and in the case of the latter, isolate factors that influenced preferences beyond the often-cited associative relationship between effort and outcome.
@@
 However, against our expectations, we found that a similar preference for cognitive effort disappeared over time as decision makers foraged for types of demands in addition to rewards.
-Computational modeling suggested that cognitive effort was valuable because it shortened the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands.
-The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks).
+Computational modeling suggested that the normative predictions of traditional foraging models were insufficient to explain our results.
+Instead, we found that demands imposed a bias on the estimation of the opportunity cost of time, which converged over time if individuals were exposed to interleaving types of demands.
+We hypothesize that this bias arises from modulations of subjective time.
+For instance, cognitive effort could have become appealing by virtue of compressing the perceived trial time, a perception that could be recalibrated with exposure to alternative demands.
+The construal of such shorter experienced durations could be due to the ongoing recruitment of working memory (e.g.
+impeding ongoing estimations of the elapsed time), or because of the discrete nature of the cognitive task, which allowed individuals to count instead of thinking about time (versus a continuous configuration of the physical and wait tasks).
 These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
@@
 
-```{r Gamma per cost group (Fig.
-10), eval = !figsEnd, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
-The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
-Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
-
-#summaryOC_btw$plot
-
-```
-
 ``` {r BTW and WTH: 16.3. Model fits, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
@@
 
-  The median values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $C$ value (see Methods for details).
-As can be seen on Figure 10C, parameter values were comparable across experiments, pointing to consisency in the way decision makers approached our foraging scenarios.
-In addition, values of $\alpha_w$ suggested that $c_{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session (mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
-Model fits also provided good qulitative resemblance to the observed choice behavior in both experiments (**Supplemental Figure X?**), fulfilling all but one of our modeling criteria (i.e.
-reduction in acceptances for between-subject effort groups, see Methods for details).
-
-```{r BIC (Fig.
+```{r BIC and parameter comparison (Fig.
 10), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "A.
 BIC values for four plausible models of choice behavior for both experiments.
+Lower values indicate better fit.
 B.
 Differences in cost biases produced by each demand.
-The cognitive group acted as if it perceived its demand as valuable.
+Negative values suggest the cognitive group acted as if it perceived its demand as valuable.
 C.
-Parameter comparison across experiments."}
+Parameter comparison portrays consistent foraging behavior across experiments."}
 
@@
 
+  The median values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $C$ value (see Methods for details).
+As can be seen on Figure 10C, parameter values were comparable across experiments, pointing to consisency in the way decision makers approached our foraging scenarios.
+In addition, values of $\alpha_w$ suggested that $c_{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session (mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
+Model fits also provided good qulitative resemblance to the observed choice behavior in both experiments (**Supplemental Figure X?**), fulfilling all but one of our modeling criteria (i.e.
+reduction in acceptances for between-subject effort groups, see Methods for details).
+
 ## Discussion
@@
 
-```{r New Gamma per cost group (Fig.
-10), eval = figsEnd, fig.align = "center", fig.height = 3, fig.width = 5, fig.cap = "Gamma values for each group.
-The dashed line indicates the average optimal earnings per second across blocks, and provides a reference for how costly (higher) or valuable (lower) each condition was.
-Wait and physical effort groups tended to perceive demands as costly, while the cognitive effort group seemed to value their task instead."}
-
-#summaryOC_btw$plot
+```{r BIC and parameter comparison (Fig.
+10), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "A.
+BIC values for four plausible models of choice behavior for both experiments.
+Lower values indicate better fit.
+B.
+Differences in cost biases produced by each demand.
+Negative values suggest the cognitive group acted as if it perceived its demand as valuable.
+C.
+Parameter comparison portrays consistent foraging behavior across experiments."}
+
+include_graphics("./Images/FIG10.png")
+
+#(bicPlot + costPlot) / allFitsPlot
+
+#In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
+For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
+Conversely, low gamma values represented low selectivity when evaluating offers.
+Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
+This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC_btw$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC_btw$all$Rsquared), digits = 2)`).
+Figure 10 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
+Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
+In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
+We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
+This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC_btw$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC_btw$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC_btw$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
+We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 10; see Operationalization of Cost).
+Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Wait"][[1]])`).
+Neither physical effort (mean = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
+These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
 

### 2020-12-08 Cost_manuscript.Rmd
model discussion

@@
 The construal of such shorter experienced durations could be due to the ongoing recruitment of working memory (e.g.
-impeding ongoing estimations of the elapsed time), or because of the discrete nature of the cognitive task, which allowed individuals to count instead of thinking about time (versus a continuous configuration of the physical and wait tasks).
+preventing individuals from estimating the elapsed time), or because of the discrete nature of the cognitive task, which allowed individuals to count instead of thinking about time (versus a continuous configuration of the physical and wait tasks).
 These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
@@
   Understanding the sporadic attractiveness of effort remains elusive.
-In this study, we tested the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
-Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that 1) preferences for cognitive effort were stable when individuals faced a single form of demand, but faded over time when other costs were also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when tasks are interleaved.
+In this study we sought to identify factors underlying this phenomenon, testing the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
+Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that preferences for cognitive effort were stable when individuals faced a single form of demand, but faded over time when other costs were also experienced.
 
@@
 This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013].
-This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [@Cash-Padgett2020; @Garrett2020; @Dundon2020].
+Successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [@Cash-Padgett2020; @Garrett2020; @Dundon2020].
 In contrast, our prediction that effort requirements would produce more acceptances only held for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment.
@@
   These choice dynamics ruled out a number of common explanatory candidates.
-For instance, differences in choice stability between experiments suggest that a demand's cost is not intrinsic.
-The gradual choice convergence in the second experiment also discards the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our population was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019].
+For instance, differences in choice stability between experiments suggested that a demand's cost is not intrinsic.
+The gradual choice convergence in the second experiment also discarded the effects of boredom, which would have accentuated the appeal of active tasks over time [**CITE**], or the possibility that our sample was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019].
 Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
 We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweis2018], as participants expressed their choices early and rarely quit during the handling time.
-Finally, the observed differences in acceptances between effort types cannot be explained by reward alone, as demands were rewarded at the same rate.
-
-  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations.
-Instead, we computationally highlight that effort can became valuable by shortening the subjective elapsed time of trials, a perception that could be recalibrated as individuals experienced multiple forms of demands (Cognitive effort gained value by making trials feel shorter).
-Alterations in subjective time sensitivity have been shown to play a role in temporal discounting [@Mckerchar2009], and are often experienced when we are fully immersed in a task [@Csikszentmihalyi2014].
-The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory, impeding estimations of the nominal time, or because of the discrete nature of the task (versus a continuous configuration of the physical and wait tasks).
-These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
-....This could be because: 1) discrete nature of cog taska llowed for counting; 2) flow; 3) persistent recruitment of working memory (Buhi and Gershman).
-Mention that order effects reflect the gradual integration of subjective time across demands in exp 2.
-Talk about future experiments: if this is subjective time, changing the pacing of the tasks should change the acceptance rates for cognitive effort.
-Maybe use this example: if I ask you to perform an activity until you think a minute has elapsed, that estimate will be noisy, but also different for different tasks.
-That's how it is in real life.
+Risk was also an unlikely factor, as task performance improved over time.
+Finally, the observed differences in acceptances between effort types could not be explained by reward alone [@Eisenberger1996], as demands were rewarded at the same rate.
+
+  Traditional foraging models, in which a reward is weighed against the earnings foregone by pursuing it [@Charnov1975; @Constantino2015], were also not enough to explain our results.
+Instead, we computationally found that each type of demand distinctly biased the estimation of this opportunity cost, and that such biases could be gradually recalibrated over time as decision makers gained experienced with additional demands.
+In this way, waiting and performing physical effort promoted selectivity by adding to the opportunity cost, whereas engaging in cognitive effort boosted an offer's value by reducing it.
+This raises the question of how these biases arise.
+We hypothesize that demands altered the perceived duration of time.
+For example, even though participants knew the nominal handling times, cognitive effort might have become valuable by subjectively compressing them.
+In our experiments, shorter subjective handling times resulted in higher perceived earning rates, but it is also possible that individuals benefitted from a sense of fast completion.
+Alterations of subjective time sensitivity are often experienced when we are fully immersed in a task [@Csikszentmihalyi2014], and have been shown to play a role in temporal discounting [@Mckerchar2009].
+Such construal of elapsed time could then be adjusted as individuals experienced multiple forms of demands.
+In fact...Mention that order effects reflect the gradual integration of subjective time across demands in exp 2.
+
+  The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory that impede estimations of the nominal time (Buhi and Gershman), or because participants could count the number of sub-tasks during pursual, which was always less than the number of seconds in the handling time.
+These hypothesis will have to be experimentally probed in the future.
+
+This would be aking to asking people involved in different tasks to stop after a certain period of time
+
+  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations.  make sure you make a big deal out of outcome-independence.
 
@@
 Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [@Mckerchar2009].
+
+  and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe delay durations, which could hypothetically be recalibrated when tasks are interleaved.
 

### 2020-12-08 Cost_manuscript.Rmd
model discussion

@@
 For instance, differences in choice stability between experiments suggested that a demand's cost is not intrinsic.
-The gradual choice convergence in the second experiment also discarded the effects of boredom, which would have accentuated the appeal of active tasks over time [**CITE**], or the possibility that our sample was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019].
+The gradual choice convergence in the second experiment also discarded the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our sample was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019].
 Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
@@
 We hypothesize that demands altered the perceived duration of time.
-For example, even though participants knew the nominal handling times, cognitive effort might have become valuable by subjectively compressing them.
+Immersive activities can subjectively speed up the passage of time [@Csikszentmihalyi2014], and this effect appears to scale with the amount of cognitive processing required by a task [@Wearden2016].
+Moreover, adjusting for time sensitivity has been shown to improve fits for delay discounting models [@Mckerchar2009].
+Therefore, even though participants knew the nominal handling times, cognitive effort might have become valuable by subjectively compressing them.
 In our experiments, shorter subjective handling times resulted in higher perceived earning rates, but it is also possible that individuals benefitted from a sense of fast completion.
-Alterations of subjective time sensitivity are often experienced when we are fully immersed in a task [@Csikszentmihalyi2014], and have been shown to play a role in temporal discounting [@Mckerchar2009].
-Such construal of elapsed time could then be adjusted as individuals experienced multiple forms of demands.
-In fact...Mention that order effects reflect the gradual integration of subjective time across demands in exp 2.
-
-  The shorter time sensitivity of cognitive effort could be due to its constant recruitment of working memory that impede estimations of the nominal time (Buhi and Gershman), or because participants could count the number of sub-tasks during pursual, which was always less than the number of seconds in the handling time.
+We speculate that this construal of elapsed time could then be adjusted with the experience of alternative demands, as participants learned how long the 10 seconds handling time felt.
+This could help explain why preferences for cognitive effort were smaller for within-subject participants who started with the physical block, as they had already formed an estimate of the handling time by the time they experienced a subjectively faster cognitive trial (**FIGURE**).
+The shorter time sensitivity produced by cognitive effort could be due to participants counting the number of sub-tasks during pursual (which was always less than the number of seconds in the handling time), or because taxing cognitive resources distracted individuals from estimating the passage of time [@Zakay1989].
 These hypothesis will have to be experimentally probed in the future.
-
-This would be aking to asking people involved in different tasks to stop after a certain period of time
-
-  (**hold off on this paragraph until modeling is done**) We do not discard the influence of these elements in daily effort evaluations.  make sure you make a big deal out of outcome-independence.
 
@@
 
-  .
-Talk clinical and practical.
-Practical could be motivating people to pursue challenges that produce desirable outcomes, like work, exercise etc.
-Much of the literature on the value of effort has suggested that it can be triggered by tailored reward schedules.
-This doesn't always do (Eisenberger, Inzlicht).
-There is also the idea that training in certain tasks will have generalizing effects, which are not always true (Kable).
-We highlight an outcome-independent feature that is phenomenologically common (time sensitivity), and potentially easy to implement.
-
 - we have all felt the need to populate empty time
@@
 
-- it's maybe relevant that waiting is goal oriented (you don't sit around for its own sake), but activities are pursued for their own appeal.
-like, waiting is a goal oriented activity, but effort can be the goal itself.
-In this sense it makes sense to study delays in terms of their modulation of the value of prospects, but we have unnecessarily adopted this view for the study of effort, thinking of it mostly as a cost.
-Even if their discounting properties are similar, their resulting behavior can be contrasting (apathy vs impulsivity), and they're impacted differently by mental illness (adhd amygdala paper).
-
-- Theories enumerated by Eisenberger and Cameron (1996) focus on how people see their behavior to explain why tasks are intrinsically attractive.
+- *Theories enumerated by Eisenberger and Cameron (1996) focus on how people see their behavior to explain why tasks are intrinsically attractive.
 We, on the other hand, point to task-specific features that promote appeal, which are amenable to configuration in everyday decision contexts.
-In other words, self-explanatory motivation versus task-specific ones.
-
-- Being immersed in a task can make time transpire subjectively faster [@Csikszentmihalyi2014], which might have made the cognitive task attractive.
-Time sensitivity has been previously used to improve fits on classic hyperbolic models of delay discounting [@Mckerchar2009].
-
-  and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe delay durations, which could hypothetically be recalibrated when tasks are interleaved.
+In other words, self-explanatory motivation versus task-specific ones.*
 

### 2020-12-08 Cost_manuscript.Rmd
first draft! (just add a fig)

@@
   Understanding the sporadic attractiveness of effort remains elusive.
-In this study we sought to identify factors underlying this phenomenon, testing the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
+In this study, we sought to identify factors underlying this phenomenon, and tested the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
 Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that preferences for cognitive effort were stable when individuals faced a single form of demand, but faded over time when other costs were also experienced.
@@
 For instance, differences in choice stability between experiments suggested that a demand's cost is not intrinsic.
-The gradual choice convergence in the second experiment also discarded the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our sample was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019].
+In addition, the gradual choice convergence in the second experiment also discarded the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our sample was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019].
 Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
@@
 Finally, the existence of optimal strategies helped us identify when demands could be attractive, a central motivation for this study.
-The apparent attractiveness of cognitive effort was reflected both by a higher proportion of acceptances at the expense of earnings, and by comparisons of fitted opportunity costs against the optimal earning rate.
+The apparent attractiveness of cognitive effort was reflected both by a higher proportion of acceptances at the expense of earnings, and by the fitted opportunity costs biases discussed above.
 Of note is that the optimality of the strategies induced by each demand depended on the richness of the block.
@@
 Encouraging patients to engage in activities has been found to be a helpful treatment for depression [@Dimidjian2006].
-Tailored reward schedules can successfully achieve this [@Eisenberger1996].
+Tailored reward schedules can successfully achieve this [@Eisenberger1996], but are limited by the attenuated sensitivity to rewards in depressed patients.
 However, since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases.
-Our work suggests that subdividing a task can promote its pursual either by taxing working memory and/or allowing individuals to count completed tasks instead of continuous time.
+Our work suggests that subdividing a task can promote its pursual, although further testing is required.
 More importantly, it highlights that decision scenarios should be configured to promote pursual of desired activities, perhaps by removing alternative uses of time.
@@
 
-### *Points to cover*
-
-- Regardless, our focus here was not on the amount of effort exherted, but on what makes people pursue the task in spite of its toll.
-
-- we have all felt the need to populate empty time
-
-- It's maybe relevant that waiting is goal oriented (you don't sit around for its own sake), but activities are pursued for their own appeal.
-*like, waiting is a goal oriented activity, but effort can be the goal itself.* in this sense it makes sense to study delays in terms of their modulation of the value of prospects, but we have unnecessarily adopted this view for ethe study of ffort, thinking of it mostly as a cost.
-Even if their discounting properties are similar, their resulting behavior can be contrasting (apathy vs impulsivity), and they're impacted differently by mental illness (adhd amygdala paper).
-Also, it's not just that we would rather to fill in empty periods of waiting, but how.
-
-- *Theories enumerated by Eisenberger and Cameron (1996) focus on how people see their behavior to explain why tasks are intrinsically attractive.
-We, on the other hand, point to task-specific features that promote appeal, which are amenable to configuration in everyday decision contexts.
-In other words, self-explanatory motivation versus task-specific ones.*
+### Conclusion
+
+  In this study, we have examined the factors that motivate the preference of different demands, emphasizing how these can be molded by the decision maker's environment.
+Unlike existing theories that have focused on the role of incentives and retrospectives [@Eisenberger1996; @Inzlicht2018], our work highlights outcome-independent features that can motivate the pursual of effortful avenues, and which can be potentially manipulated in order to promote engagement in clinical and daily activities.
 

### 2020-12-08 Cost_manuscript.Rmd
alright, now first draft completed!

@@
 ``` {r WTH: 16.3.3. Plot Pre/Post reward x handling, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
-# # first block
-# t1 <- data %>%
-#   group_by(SubjID) %>%
-#   mutate(Block = do.call(c, lapply(c(2, 4, 6), function(x) {rep(x / 2, sum(Block %in% c(x - 1, x)))}))) %>%
-#   #filter(Half == "Half_1", Offer < 20) %>%
-#   filter(Block == 1) %>%
-#   group_by(Cost, Offer) %>%
-#   summarise(propAccept = mean(Choice),
-#             SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
-#   ungroup() %>%
-#   mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-#   ggplot(aes(Offer, propAccept, color = Cost)) +
-#     geom_point(size = 3, show.legend = F) +
-#     #geom_point(aes(y = Optimal), size = 3, pch = 21, color = "darkgrey") +
-#     geom_line(show.legend = F) +
-#     scale_color_manual(values = colsWth) +
-#     scale_fill_manual(values = colsWth) +
-#     geom_errorbar(aes(ymin=propAccept-SE, ymax=propAccept+SE), width=0.2, size=1, show.legend = T) +
-#     scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
-#     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-#     labs(x = "Reward", y = "Proportion Accepted", title = "First Block") +
-#     theme(legend.key = element_blank(),
-#           legend.position = c(0.8, 0.25),
-#           panel.grid.major = element_blank(), 
-#           panel.grid.minor = element_blank(), 
-#           panel.background = element_blank(), 
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 16))
-# 
-# 
-# # last block
-# t3 <- data %>%
-#     group_by(SubjID) %>%
-#     mutate(Block = do.call(c, lapply(c(2, 4, 6), function(x) {rep(x / 2, sum(Block %in% c(x - 1, x)))}))) %>%
-#     #filter(Half == "Half_2", Offer < 20) %>%
-#     filter(Block == 3) %>%
-#     group_by(Cost, Offer) %>%
-#     summarise(propAccept = mean(Choice),
-#               SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
-#     ungroup() %>%
-#     mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-#     ggplot(aes(Offer, propAccept, color = Cost)) +
-#       geom_point(size = 3, show.legend = F) +
-#       geom_line(show.legend = F) +
-#       scale_color_manual(values = colsWth) +
-#       scale_fill_manual(values = colsWth) +
-#       geom_errorbar(aes(ymin=propAccept-SE, ymax=propAccept+SE), width=0.2, size=1, show.legend = F) +
-#       scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
-#       scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-#       labs(x = "Reward", y = "", title = "Last Block") +
-#       theme(legend.position = c(0.1, 0.7),
-#             panel.grid.major = element_blank(), 
-#             panel.grid.minor = element_blank(), 
-#             panel.background = element_blank(), 
-#             axis.line = element_line(colour = "black"),
-#             text = element_text(size = 16))
-# 
-# grid.arrange(t1, t3, ncol = 2)
-
+# pre-post for everyone per reward x handling
 hrprepostPlot_wth <- dataWth %>%
@@
 
+# with block order
+blockOrder_wth <- dataWth %>%
+  group_by(SubjID) %>%
+  mutate(Block = case_when(
+    Block %in% c(1, 2) ~ 1,
+    Block %in% c(3, 4) ~ 2,
+    Block %in% c(5, 6) ~ 3
+  )) %>%
+  filter(Block != 2) %>%
+  mutate(Block = ifelse(Block == 1, "First Two Blocks", "Last Two Blocks")) %>%
+  group_by(Cost, BlockOrder, Block, Offer) %>%
+  summarise(propAccept = mean(Choice),
+            SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
+  ungroup() %>%
+  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>% 
+  ggplot(aes(Offer, propAccept, color = Cost)) +
+    geom_point(size = 3, show.legend = F) +
+    geom_line(size = 1, show.legend = F) +
+    scale_color_manual(values = colsWth) +
+    scale_fill_manual(values = colsWth) +
+    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
+    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
+    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
+    labs(x = "Reward", y = "Proportion Accepted") +
+    facet_wrap(vars(BlockOrder, Block)) +
+    theme(legend.key = element_blank(),
+          legend.position = c(0.9, 0.25),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(), 
+          panel.background = element_blank(), 
+          axis.line = element_line(colour = "black"),
+          text = element_text(size = 20))
 ```
@@
 Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure 4A).
-Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Figure 9, right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).
+Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Figure 9, top-right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).
+This fading preference for cognitive effort was observed regardless of which block participants experienced first, even though its magnitude appeared to be reduced for those who experienced the physical block first (Figure 9, bottom)
 
@@
 9), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time.
-Left: Proportion accepted in the first two and last two blocks of the experiment.
+Top-Left: Proportion accepted in the first two and last two blocks of the experiment.
 An initial preference for cognitive effort trials fades amid a global decrease in acceptance rates.
-Right: Mixed effects coefficient matrix for each half separately.
-The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4)."}
+Top-Right: Mixed effects coefficient matrix for each half separately.
+The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4).
+Bottom: Block rder effects show attenuated differences for those who started with the physical configuration."}
 include_graphics("./Images/FIG9.png")
@@
 
-  Traditional foraging models, in which a reward is weighed against the earnings foregone by pursuing it [@Charnov1975; @Constantino2015], were also not enough to explain our results.
+  Traditional foraging models, in which a reward is weighed against the earnings foregone by pursuing it [@Charnov1976; @Constantino2015], were also not enough to explain our results.
 Instead, we computationally found that each type of demand distinctly biased the estimation of this opportunity cost, and that such biases could be gradually recalibrated over time as decision makers gained experienced with additional demands.
@@
   In this study, we have examined the factors that motivate the preference of different demands, emphasizing how these can be molded by the decision maker's environment.
-Unlike existing theories that have focused on the role of incentives and retrospectives [@Eisenberger1996; @Inzlicht2018], our work highlights outcome-independent features that can motivate the pursual of effortful avenues, and which can be potentially manipulated in order to promote engagement in clinical and daily activities.
+Unlike existing theories that have focused on the role of incentives and retrospective justifications [@Eisenberger1996; @Inzlicht2018], our work highlights outcome-independent and task-specific features that can motivate the pursual of effortful avenues, which can be potentially manipulated in order to promote engagement in clinical and daily activities.
 
@@
 9), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time.
-Left: Proportion accepted in the first two and last two blocks of the experiment.
+Top-Left: Proportion accepted in the first two and last two blocks of the experiment.
 An initial preference for cognitive effort trials fades amid a global decrease in acceptance rates.
-Right: Mixed effects coefficient matrix for each half separately.
-The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4)."}
-include_graphics("./Images/FIG10.png")
+Top-Right: Mixed effects coefficient matrix for each half separately.
+The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4).
+Bottom: Block rder effects show attenuated differences for those who started with the physical configuration."}
+include_graphics("./Images/FIG9.png")
 ```
@@
 
-```{r BIC and parameter comparison (Fig.
-10), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "A.
+```{r New BIC and parameter comparison (Fig.
+10), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "A.
 BIC values for four plausible models of choice behavior for both experiments.

### 2020-12-10 Cost_manuscript.Rmd

@@
   and delay are interleaved in a foraging environment
-author: "Claudio Toro-Serey^1^2, Gary Kane^1^2, & Joseph T. McGuire^1^2"
+author: "Claudio Toro-Serey^1,2^, Gary A. Kane^1,2^, & Joseph T. McGuire^1,2^"
 header-includes:
@@
 
-  **GARY EXPLAINS FITTING PROCEDURE**
+#### **Model Fitting and Model Comparison Procedures**
+
+  For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm (Huys et al., 2011).
+Briefly, it was assumed that, at the population level, each parameter was distributed according to a Gaussian distribution, defined by a mean and standard deviation; the individual subject parameters were drawn from this distribution.
+Accordingly, a point estimate for the individual subject parameters were found via maximum a posteriori (MAP) estimation using the population distribution for each parameter as the priors, and the variance in the individual subject parameter estimates were calculated by taking the inverse of the Hessian matrix at the MAP estimate.
+Next, the mean of the prior was updated by taking the weighted mean of individual subject estimates, and the variance of the prior was updated by taking the weighted variance across the parameter estimates of individual subjects.
+This process was repeated until the mean and variance of the prior for all parameters converged (a change of less than .1% across successive iterations).
+Full mathematical details of the algorithm can be found in Huys et al., 2011, and the algorithm was implemented using a custom written R package, GaussExMax, available on github (github.com/gkane26/GaussExMax).
+
+  Model comparison was performed by calculating Bayes Information Criterion at the group level (integrated BIC or iBIC; Huys et al., 2011; Kane et al., 2019).
+iBIC penalizes the likelihood of the data given model parameters $p(d | model)$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
+
+\begin{align}
+  iBIC = logp(d | model) + \frac{k}{2}log(o)
+\end{align}
+
+  A Laplace approximation was used to find the log marginal likelihood, the likelihood of the data for each subject given the population level distribution over each parameter (Huys et al., 2011; Kane et al., 2019).
+
+#### **Model Definitions**
 

### 2020-12-11 Cost_manuscript.Rmd
added model fitting procedure deets

@@
 
-  For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm (Huys et al., 2011).
+  For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm [@Huys2011; @Huys2012].
 Briefly, it was assumed that, at the population level, each parameter was distributed according to a Gaussian distribution, defined by a mean and standard deviation; the individual subject parameters were drawn from this distribution.
@@
 This process was repeated until the mean and variance of the prior for all parameters converged (a change of less than .1% across successive iterations).
-Full mathematical details of the algorithm can be found in Huys et al., 2011, and the algorithm was implemented using a custom written R package, GaussExMax, available on github (github.com/gkane26/GaussExMax).
-
-  Model comparison was performed by calculating Bayes Information Criterion at the group level (integrated BIC or iBIC; Huys et al., 2011; Kane et al., 2019).
+Full mathematical details of the algorithm can be found in Huys et al.
+(2011, 2012), and the algorithm was implemented using a custom written R package, GaussExMax, available on github (github.com/gkane26/GaussExMax).
+
+  Model comparison was performed by calculating Bayes Information Criterion at the group level [integrated BIC or iBIC; @Huys2011; @Huys2012; @Kane2019].
 iBIC penalizes the likelihood of the data given model parameters $p(d | model)$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
@@
 
-  A Laplace approximation was used to find the log marginal likelihood, the likelihood of the data for each subject given the population level distribution over each parameter (Huys et al., 2011; Kane et al., 2019).
+  A Laplace approximation was used to find the log marginal likelihood, the likelihood of the data for each subject given the population level distribution over each parameter (Huys et al., 2011; Huys et al., 2012; Kane et al., 2019).
 
@@
 We therefore fixed each value of $c_{demand}$ (i.e.
-$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted *a posteriori* distribution from each between-subjects demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$.
+$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each between-subjects demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$.
 This dynamic allowed for the observed merging of acceptances across demands in the within-subjects experiment, while respecting the stability in the between-subjects study.

### 2020-12-14 Cost_manuscript.Rmd
some feedback-based edits

@@
 When participants faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
-We theorized that if cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards.
+**We theorized that i**f cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards.
 In the within-subject experiment, an initially higher acceptance rate for cognitive effort trials disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions.
@@
   Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment [@Charnov1976; @Stephens2019].
-In this study, the richness of the environment was manipulated by the length of the handling and travel times, where shorter travel times produced richer environments.
+In this study, the richness of the environment was manipulated by the length of the handling and travel times, whereby shorter travel times produced richer environments.
 Since time combinations were fixed per block, we calculated each block’s optimal accept/reject strategy by computing all decision strategies according to the following equation:
@@
 $$\begin{aligned} 
-\dfrac {\sum p_i R_i} {\sum p_i H + 3T},p \in \{0, 1\}
+\dfrac {\sum p_i R_i} {Time_{offer} + (\sum p_i H + Time_{reward}) + 3T},p \in \{0, 1\}
 \end{aligned}$$
 
-  where *R* and *p* are the reward, and acceptance probability of offer i, respectively, *H* is the handling time for the block, and *T* its associated travel time.
+  where *R* and *p* are the reward and acceptance probability of offer i, respectively, *H* is the handling time for the block, $Time_{offer/reward}$ are the windows when offers and rewards were disclosed, and *T* its associated travel time.
 This gave us the total reward per second attainable in each block as a function of the acceptance threshold (i.e.
@@
 
-### Analyseses
+### Analyses
 
@@
 
-  After fitting the parameters, we performed two-sided, one-sample t-tests to compare the biased opportunity costs from each between-subjects demand group to the mean optimal gamma (0.61, see Operationalization of Cost).
+  After fitting the parameters, we performed two-sided, one-sample t-tests to compare the biased opportunity costs from each between-subjects demand group **to the mean optimal gamma** (0.61, see Operationalization of Cost).
 This allowed us to determine whether any demand boosted an offer's value.
@@
 However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][3]`) = `r round(mixLogis_compare_wth$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][3])`), albeit at the cost of interpretability due to choice fluctuations over time (see Consistency and Stability).
-These initial results defied our predictions, suggesting that the availability of alternative demands erases preferences among them (rather than inverting them from what was observed in experiment 1).
+These initial results defied our predictions, suggesting that the availability of alternative demands diminishes preferences among them (rather than inverting them from what was observed in experiment 1).
 
@@
 
-  The median values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $C$ value (see Methods for details).
+  The mean values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $C$ value (see Methods for details).
 As can be seen on Figure 10C, parameter values were comparable across experiments, pointing to consisency in the way decision makers approached our foraging scenarios.
@@
 However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the near future [@Fawcett2012; @Frederick2002; @Sozou1998].
-We circumvented these pitfalls by providing participants with an opportunity to actively experience the demands they accepted, and gaving them full knowledge of the available options.
+We circumvented these pitfalls by providing participants with an opportunity to actively experience the demands they accepted, and giving them full knowledge of the available options.
 Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time.
@@
 Encouraging patients to engage in activities has been found to be a helpful treatment for depression [@Dimidjian2006].
-Tailored reward schedules can successfully achieve this [@Eisenberger1996], but are limited by the attenuated sensitivity to rewards in depressed patients.
+Tailored reward schedules can successfully achieve this [@Eisenberger1996]**, but are limited by the attenuated sensitivity to rewards in depressed patients**.
 However, since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases.

### 2021-01-03 Cost_manuscript.Rmd
updating figs

@@
 
-include_graphics("./Images/FIG1_short.png")
+include_graphics("./Images/FIG1_task_a.png")
 ```
@@
 
-include_graphics("./Images/FIG2.png")
+include_graphics("./Images/FIG1_task_b.png")
 ```
@@
 # plots generated in 16.2.1. and 16.1.3.
- prop1 | earnings1 | earnFitplot_btw
+#(propPlot <- prop1 | earnings1 | earnFitplot_btw)
+#ggsave("./Images/FIG3_props.png", propPlot, device = "png", height = 4, width = 10)
+
+include_graphics("./Images/FIG3_props.png")
+
 ```
@@
   mutate(Model = factor(Model, levels = names(mixLogis_compare_btw))) %>%
-  ggplot(aes(Model, Value, fill = Comparison)) +
+  ggplot(aes(Model, Value, group = Comparison, fill = Comparison)) +
+    geom_line(aes(color = Comparison)) +
     geom_point(color = "black", pch = 21, size = 3) +
+    labs(x = "", y = "") +
+    scale_x_discrete(labels = c("Base", "Cost", "Handling", "Offer", "H + R", "All Main", "H + R Int.", "Full Interaction")) +
     theme(legend.position = c(0.8, 0.7),
-            axis.text.x = element_text(angle = 45, hjust = 1),
+          axis.text.x = element_text(angle = 30, hjust = 1),
           panel.grid.major = element_blank(),
@@
           axis.line = element_line(colour = "black"),
-            text = element_text(size = 22))
+          legend.key=element_blank(),
+          text = element_text(size = 20))
 
@@
 #hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
-include_graphics("./Images/FIG4.png")
+include_graphics("./Images/FIG4_btwlogistic.png")
 ```

### 2021-01-03 Cost_manuscript.Rmd
updated figs 5 through 8

@@
 # plots generated in 16.3.1. and 16.3.2.
-(suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
+# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
+# ggsave("./Images/FIG5_survival.png", historyPlot_btw, device = "png", height = 8, width = 10)
+include_graphics("./Images/FIG5_survival.png")
 ```
@@
     scale_fill_manual(values = colsBtw) +
-    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
+    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 0.8, show.legend = T) +
     scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
@@
           axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
+          text = element_text(size = 28))
 
@@
 Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
-include_graphics("./Images/FIG6.png")
+# left plot in 16.3.2
+#ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
+include_graphics("./Images/FIG6_prepostbtw.png")
 
@@
            axis.line = element_line(colour = "black"),
-           text = element_text(size = 16))
+           text = element_text(size = 22))
 
@@
   mutate(Model = factor(Model, levels = names(mixLogis_compare_wth))) %>%
-  ggplot(aes(Model, Value, fill = Comparison)) +
+  ggplot(aes(Model, Value, group = Comparison, fill = Comparison)) +
+    labs(x = "", y = "") +
+    geom_line(aes(color = Comparison)) +
     geom_point(color = "black", pch = 21, size = 3) +
-    theme(legend.position = c(0.8, 0.8),
+    theme(legend.position = c(0.75, 0.7),
           legend.key = element_blank(),
+          axis.text.x = element_text(angle = 30, hjust = 1),
           panel.grid.major = element_blank(),
@@
           axis.line = element_line(colour = "black"),
-      text = element_text(size = 16))
+          text = element_text(size = 22))
 
@@
 D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}
-
-include_graphics("./Images/FIG8.png")
+# earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
+ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
+include_graphics("./Images/FIG7_wthlogistic.png")
 ```
@@
 # plots generated in 16.3.1. and 16.3.3.
-(suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
+historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
+ggsave("./Images/FIG8_survival.png", historyPlot_wth, device = "png", height = 8, width = 10)
 ```

### 2021-01-03 Cost_manuscript.Rmd
all plots updated to higher res

@@
   ggplot(aes(Offer, propAccept, color = Cost)) +
-    geom_point(size = 3, show.legend = T) +
+    geom_point(size = 3, show.legend = F) +
     #geom_point(aes(y = Optimal), size = 3, pch = 21, color = "darkgrey") +
@@
     scale_fill_manual(values = colsWth) +
-    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
+    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = F) +
     scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-    labs(x = "Reward", y = "Proportion Accepted") +
+    labs(x = "Offer", y = "Proportion Accepted") +
     facet_wrap(vars(Block)) +
-    theme(legend.key = element_blank(),
-          legend.position = c(0.9, 0.25),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 16))
+    theme_classic(base_size = 22)
 
@@
     scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
-    labs(x = "Reward", y = "Proportion Accepted") +
-    facet_wrap(vars(BlockOrder, Block)) +
-    theme(legend.key = element_blank(),
-          legend.position = c(0.9, 0.25),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 20))
+    labs(x = "Offer", y = "Proportion Accepted") +
+    facet_grid(BlockOrder ~ Block) +
+    theme_classic(base_size = 22)
 ```
@@
 
-``` {r WTH: 16.3.3 temp plot, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
+``` {r WTH: 16.3.3 temp plots, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
 # cw <- dataWth %>%
@@
 #   spread(Cost, diff) %>%
-#   ggplot(aes(Cognitive, Wait-C, fill = as.character(Offer))) +
+#   ggplot(aes(Cognitive, `Wait-C`, fill = as.character(Offer))) +
 #     geom_point(pch = 21, color = "black", size = 3) +
@@
 #   spread(Cost, diff) %>%
-#   ggplot(aes(Physical, Wait-P, fill = as.character(Offer))) +
+#   ggplot(aes(Physical, `Wait-P`, fill = as.character(Offer))) +
 #     geom_point(pch = 21, color = "black", size = 3, show.legend = F) +
@@
 # plots generated in 16.3.1. and 16.3.3.
-historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
-ggsave("./Images/FIG8_survival.png", historyPlot_wth, device = "png", height = 8, width = 10)
+#historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
+#ggsave("./Images/FIG8_survival.png", historyPlot_wth, device = "png", height = 8, width = 10)
+include_graphics("./Images/FIG8_survival.png")
 ```
@@
 Bottom: Block rder effects show attenuated differences for those who started with the physical configuration."}
+# hrprepostPlot_wth, blockOrder_wth
+# ggsave("./Images/prepostwth_2.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
 include_graphics("./Images/FIG9.png")
@@
         #axis.text.x = element_text(angle = 20, hjust = 1),
+        legend.key=element_blank(),
         panel.grid.major = element_blank(),
@@
 
-include_graphics("./Images/FIG10.png")
-
-#(bicPlot + costPlot) / allFitsPlot
+# modelPlot <- (bicPlot + costPlot) / allFitsPlot
+# ggsave("./Images/FIG10_model.png", modelPlot, device = "png", height = 8, width = 11)
+include_graphics("./Images/FIG10_model.png")
 

### 2021-01-15 Cost_manuscript.Rmd
updated fig 10

@@
 output:
-  word_document: #default
-    reference_docx: Style_reference_draft.docx
   pdf_document:
@@
 
+#Task design and optimal behavior.
+A: General foraging trial structure.
+On each trial, participants were offered to earn money by sustaining effort or waiting during the handling time (2, 10, or 14 s).
+The end of a trial was followed by a travel time (handling and travel times always added up to 16 s).
+Participants could skip unfavorable trials and immediately start traveling to a potentially better offer.
+In the between-subject experiment, cost was fixed per participant and handling time varied per block.
+In the within-subject version, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
+B: Possible earnings per second for each acceptance threshold (i.e.
+the smallest amount accepted) for each handling time.
+Circles denote the reward-maximizing threshold for each block, which is described in the table.
+Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers.
+
 include_graphics("./Images/FIG1_task_a.png")
@@
 ```{r General prop & earnings plots (Fig.
-3), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
+3), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in the between-subjects experiment.
+Left: Proportion accepted per cost.
 Middle: Total number of dollars earned by each group by the end of the experiment.
 Right: The relationship between proportion accepted and total earned.
-Consistent with the foraging design, participants who over and under accepted earned the least."}
+Consistent with the foraging design, participants who over and under accepted earned the least.
+These figures suggests a preference for cognitive effort at the expense of earnings."}
 # plots generated in 16.2.1. and 16.1.3.
@@
 ```{r Survival and prepost plots (Fig.
-5), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
+5), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in the between-subjects experiment.
+Top: Survival curve (left), and distribution of times when participants quit a trial over time (right).
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r Prepost mixed effects plot (Fig.
-6), eval = !figsEnd, fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
+6), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in the between-subjects experiment.
 Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
@@
 ```{r Earnings/prop completed/ME plots (Fig.
-7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
+7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior.
+A: Quadratic relationship between trial completions and total earnings.
 B: proportion of acceptances of each reward per cost condition.
@@
 ```{r Survival and prepost plots (Fig.
-8), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
+8), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in the within-subjects experiment.
+Top: Survival curve (left), and distribution of quitting times over time (right).
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r Prepost mixed effects plots (Fig.
-9), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time.
+9), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in the within-subjects experiment.
 Top-Left: Proportion accepted in the first two and last two blocks of the experiment.
@@
 # ggsave("./Images/prepostwth_2.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
-include_graphics("./Images/FIG9.png")
+include_graphics("./Images/FIG9_prepostwth.png")
 
@@
 ```{r BIC and parameter comparison (Fig.
-10), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "A.
-BIC values for four plausible models of choice behavior for both experiments.
+10), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling.
+A: BIC values for four plausible models of choice behavior for both experiments.
 Lower values indicate better fit.
-B.
-Differences in cost biases produced by each demand.
+B: Differences in cost biases produced by each demand.
 Negative values suggest the cognitive group acted as if it perceived its demand as valuable.
-C.
-Parameter comparison portrays consistent foraging behavior across experiments."}
-
-# modelPlot <- (bicPlot + costPlot) / allFitsPlot
+C: Parameter comparison portrays consistent foraging behavior across experiments.
+D: Behavior recovery of the within-subjects adaptive behavior based on the winning model.
+The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}
+
+modelPlot <- (bicPlot + costPlot) / allFitsPlot
 # ggsave("./Images/FIG10_model.png", modelPlot, device = "png", height = 8, width = 11)
-include_graphics("./Images/FIG10_model.png")
+include_graphics("./Images/FIG10_modelresults.png")
 
@@
 ```{r New General prop & earnings plots (Fig.
-3), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost.
+3), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in the between-subjects experiment.
+Left: Proportion accepted per cost.
 Middle: Total number of dollars earned by each group by the end of the experiment.
 Right: The relationship between proportion accepted and total earned.
-Consistent with the foraging design, participants who over and under accepted earned the least."}
+Consistent with the foraging design, participants who over and under accepted earned the least.
+These figures suggests a preference for cognitive effort at the expense of earnings."}
 # plots generated in 16.2.1. and 16.1.3.
@@
 ```{r New Survival and prepost plots (Fig.
-5), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time.
+5), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in the between-subjects experiment.
+Top: Survival curve (left), and distribution of times when participants quit a trial over time (right).
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r New Prepost mixed effects plot (Fig.
-6), eval = figsEnd, fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break.
+6), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in the between-subjects experiment.
 Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
@@
 ```{r New Earnings/prop completed/ME plots (Fig.
-7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings.
+7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior.
+A: Quadratic relationship between trial completions and total earnings.
 B: proportion of acceptances of each reward per cost condition.
@@
 ```{r New Survival and prepost plots (Fig.
-8), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right).
+8), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in the within-subjects experiment.
+Top: Survival curve (left), and distribution of quitting times over time (right).
 Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
@@
 ```{r New Prepost mixed effects plots (Fig.
-9), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time.
+9), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in the within-subjects experiment.
 Top-Left: Proportion accepted in the first two and last two blocks of the experiment.
@@
 ```{r New BIC and parameter comparison (Fig.
-10), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "A.
-BIC values for four plausible models of choice behavior for both experiments.
+10), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling.
+A: BIC values for four plausible models of choice behavior for both experiments.
 Lower values indicate better fit.
-B.
-Differences in cost biases produced by each demand.
+B: Differences in cost biases produced by each demand.
 Negative values suggest the cognitive group acted as if it perceived its demand as valuable.
-C.
-Parameter comparison portrays consistent foraging behavior across experiments."}
+C: Parameter comparison portrays consistent foraging behavior across experiments.
+D: Behavior recovery of the within-subjects adaptive behavior based on the winning model.
+The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}
 

### 2021-01-16 Cost_manuscript.Rmd
little tweak

@@
 Each group was unaware that other cost conditions existed.
-Participants exerted physical effort by maintaining grip on a handheld dynamometer (*VERSION*, BIOPAC Systems, United States) using their dominant hand.
+Participants exerted physical effort by maintaining grip on a handheld dynamometer (Biopac Systems, United States) using their dominant hand.
 Gripping requirements were calibrated at 20% of maximum voluntary contraction (MVC, acquired at the beginning of the session).
@@
 Encouraging patients to engage in activities has been found to be a helpful treatment for depression [@Dimidjian2006].
-Tailored reward schedules can successfully achieve this [@Eisenberger1996]**, but are limited by the attenuated sensitivity to rewards in depressed patients**.
+Tailored reward schedules can successfully achieve this [@Eisenberger1996].
 However, since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases.

### 2021-03-04 Cost_manuscript.Rmd
new latex for models

@@
 - \usepackage{indentfirst}
+- \usepackage{fixltx2e}
 output:
@@
 
-## figures at the end of the manuscropt?
-figsEnd <- FALSE
+## figures at the end of the manuscript?
+figsEnd <- TRUE
 
@@
 $$\begin{aligned} 
-\dfrac {\sum p_i R_i} {Time_{offer} + (\sum p_i H + Time_{reward}) + 3T},p \in \{0, 1\}
+g(*) = \dfrac {\sum p_i R_i} { 3\text{Time}_\text{offer} + (\sum p_i H + \text{Time}_\text{reward}) + 3T},p \in \{0, 1\}
 \end{aligned}$$
@@
 \begin{align}
-  Model_{base} = R_i - \gamma H_i
+  \text{Model}_\text{base} = R_i - \gamma H_i
 \end{align}
@@
 \begin{align}
-  P(accept)_i = \dfrac {1} {1 + e^{-(1/\beta)(Model_{base})}}
+  P(\text{accept})_i = \dfrac {1} {1 + e^{-(1/\beta)(\text{Model}_\text{base})}}
 \end{align}
@@
 \begin{align}
-  Model_{adaptive} = R_i - \gamma_i H_i
+  \text{Model}_\text{adaptive} = R_i - \gamma_i H_i
 \end{align}
@@
 \begin{align}
-  Model_{biased} = R_i - (\gamma + mC_i) H_i
+  \text{Model}_\text{biased} = R_i - (\gamma + mC_i) H_i
 \end{align}
@@
 \begin{align}
-  Model_{adaptive + biased} = R_i - (\gamma_i + mC_i) H_i
+  \text{Model}_\text{adaptive + biased} = R_i - (\gamma_i + mC_i) H_i
 \end{align}
@@
 ``` {r BTW: 16.1.4. Optimality (move to acceptance comparison eventually), echo = FALSE}
-# in order
-# clean data, 
-# calculate each individual's prop. accept,
-# calculate t.tests with optimality as null mean,
-# correct pvalues with FDR
+# # in order
+# # clean data, 
+# # calculate each individual's prop. accept,
+# # calculate t.tests with optimality as null mean,
+# # correct pvalues with FDR
+# temp <- dataBtw %>%
+#   filter(Choice < 2) %>%
+#   group_by(SubjID, Handling, Offer, Cost) %>%
+#   summarise(pAccept = mean(Choice)) %>%
+#   mutate(optimal = case_when(
+#           (Handling == 10 & Offer < 8) ~ 0,
+#           (Handling == 14 & Offer < 20) ~ 0,
+#           TRUE ~ 1
+#         )) %>% 
+#   group_by(Handling, Offer, Cost) %>%
+#   summarise(meanAccept = mean(pAccept),
+#             sdAccept = sd(pAccept),
+#             optimal = unique(optimal),
+#             pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
+#   mutate(FDR = p.adjust(pvals, method = "BY"),
+#          significant = FDR < 0.05)
+# 
+# 
+# # proportion of significant ones
+# # eventually find a way to plot this (or just place it further down)
+# # alternative per block: temp %>% group_by(Handling) %>% summarise(prop = mean(significant, na.rm = T))
+# optimalProp <- mean(temp$significant, na.rm = T) * 100
+# 
+# # proportion accepted per cost condition
+# optimalProp_cost <- temp %>% 
+#   group_by(Cost) %>% 
+#   summarise(propDeviations = round(mean(significant) * 100))
+
+## if you want to replicate the cost 3 method
+# this says that all but easy deviated from optimality in the observed direction
 temp <- dataBtw %>%
-  filter(Choice < 2) %>%
-  group_by(SubjID, Handling, Offer, Cost) %>%
-  summarise(pAccept = mean(Choice)) %>%
-  mutate(optimal = case_when(
-          (Handling == 10 & Offer < 8) ~ 0,
-          (Handling == 14 & Offer < 20) ~ 0,
-          TRUE ~ 1
-        )) %>% 
-  group_by(Handling, Offer, Cost) %>%
-  summarise(meanAccept = mean(pAccept),
-            sdAccept = sd(pAccept),
-            optimal = unique(optimal),
-            pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
-  mutate(FDR = p.adjust(pvals, method = "BY"),
-         significant = FDR < 0.05)
-
-# proportion of significant ones
-# eventually find a way to plot this (or just place it further down)
-# alternative per block: temp %>% group_by(Handling) %>% summarise(prop = mean(significant, na.rm = T))
-optimalProp <- mean(temp$significant, na.rm = T) * 100
-
-# proportion accepted per cost condition
-optimalProp_cost <- temp %>% 
   group_by(Cost) %>%
-  summarise(propDeviations = round(mean(significant) * 100))
-
-# ## if you want to replicate the cost 3 method
-# # this says that all but easy deviated from optimality in the observed direction
-# temp <- dataBtw %>%
-#   group_by(Cost) %>%
-#   filter(Offer < 20, Handling == 10) %>%
-#   summarize(propAccept = mean(Choice),
-#             accept = sum(Choice),
-#             quit = sum(Choice == 0))
-# 
-# temp2 <- apply(temp, 1, function(row) {prop.test(as.numeric(row[3]), sum(as.numeric(row[3:4])), p = 0.5, conf.level = 0.95)})
-#   
-#   
-# # store stats in a dataframe
-# news <- data.frame(probability = sapply(temp2, "[[", "estimate"),
-#                                    chisquared = sapply(temp2, "[[", "statistic"),
-#                                    confint = t(sapply(temp2, "[[", "conf.int")),
-#                                    pval = sapply(temp2, "[[", "p.value"))
-# rownames(news) <- temp$Cost
+  filter(Offer < 20) %>%
+  summarize(propAccept = mean(Choice),
+            accept = sum(Choice),
+            quit = sum(Choice == 0))
+
+temp2 <- apply(temp, 1, function(row) {prop.test(as.numeric(row[3]), sum(as.numeric(row[3:4])), p = 0.5, conf.level = 0.95)})
+
+# store stats in a dataframe
+optimalProp_cost <- data.frame(probability = sapply(temp2, "[[", "estimate"),
+                                   chisquared = sapply(temp2, "[[", "statistic"),
+                                   confint = t(sapply(temp2, "[[", "conf.int")),
+                                   pval = sapply(temp2, "[[", "p.value"))
+rownames(optimalProp_cost) <- temp$Cost
 
@@
 Accordingly, participants who over- or under-accepted earned the least (Figure 3, right; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
-Two-sided, one-sample t-tests against the optimal proportion of acceptances (i.e.
-$\mu$ = 0 or 1) for each combination of cost type, handling time, and offer showed that participants significantly deviated from optimality in `r round(optimalProp)`% of combinations (*p* < 0.05, FDR corrected), with the percentage of deviations being lowest for the wait group (Wait = `r filter(optimalProp_cost, Cost == "Wait")[2]`%, physical = `r filter(optimalProp_cost, Cost == "Physical")[2]`%, Cognitive = `r filter(optimalProp_cost, Cost == "Cognitive")[2]`%, Easy = `r filter(optimalProp_cost, Cost == "Easy")[2]`%).
+We performed group-level chi-squared tests of proportions to examine whether each cost biased decision makers to under- or over-accept 4 and 8 cent offers, which together should have been accepted 50% of the time.
+We found a significant over-acceptance of these trials by the cognitive effort group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`%; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Cognitive", "pval"]`), but under-acceptances by the physical (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`%; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"]`) and wait (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`%; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"]`) groups (no significant difference for the Easy group).
 Together, these findings show that even though participants did not always perform optimally, they adequately integrated the statistics of the environment as they tracked their recent experience.

### 2021-03-04 Cost_manuscript.Rmd
revisions from dissertation

@@
 \begin{align}
-  \text{Model}_\text{biased} = R_i - (\gamma + mC_i) H_i
+  \text{Model}_\text{biased} = R_i - (\gamma + C_i) H_i
 \end{align}
@@
 \begin{align}
-  mC_i = C w_i + c_{demand} (1 - w_i)
+  C_i = c_\text{global} w_i + c_\text{demand} (1 - w_i)
 \end{align}
@@
 \begin{align}
-  \text{Model}_\text{adaptive + biased} = R_i - (\gamma_i + mC_i) H_i
+  \text{Model}_\text{adaptive + biased} = R_i - (\gamma_i + C_i) H_i
 \end{align}
@@
       text = element_text(size = 14))
+
+# actual proportion of quits that happened after 1 s (i.e. after the grace period for physical)
+handlingQuits_btw <- dataBtw %>%
+  filter(rawChoice == 0) %>%
+  summarize(r = round(mean(RT > 1.05), digits = 2)) # to account for some measurement error for the grace perior during grip
 
@@
 To examine this, we plotted survival curves of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
-These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit during the handling time.
+These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (proportion of quits after 1 s = `r  handlingQuits_btw$r`).
 Physical and easy groups showed slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
@@
 Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]]), digits = 2)`).
-However, this time participants were unaffected by recent reward misses (*p* > 0.05).
+However, this time participants were unaffected by recent reward misses (*p* `r report_p(historyCoeffs_wth["recentTravels", "Pr(>|z|)"])`).
 As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 7A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
@@
 corDiff <- cor(accDiff$Diff, propFails_wth$propFails)
+
+# no differences in forced travels across halves
+temp <- dataWth %>%
+  filter(!Cost %in% c("Wait-C", "Wait-P")) %>%
+  group_by(SubjID,  Half) %>%
+  summarise(propFails = mean(rawChoice == 2)) %>%
+  spread(Half, propFails)
+
+failDiffs_wth <- permute(temp$Half_1, temp$Half_2, paired = T)
 
@@
   However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 9).
-The reduction in acceptances was not driven by a performance decline, as the difference in acceptance rates was not significantly correlated with the proportion of forced travels across individuals (Pearson's r = `r round(corDiff, digits = 2)`, *p* > 0.05).
+The reduction in acceptances was not driven by a performance decline, forced travels were not significantly different in the first and second half of the experiment (paired permutation with 5000 iterations, *p* `r report_p(failDiffs_wth$Pval)`).
 Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure 4A).

### 2021-03-15 Cost_manuscript.Rmd
fixed a couple of standard error estimates

@@
 <!-- NOTE: 
-If you're on Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
+If you're using Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
 -->
@@
                          summarize(propAccept = mean(propAccept_subj),
-                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs_btw)) %>%
+                                   seAccept = sd(propAccept_subj)/sqrt(length(propAccept_subj))) %>%
                          ggplot(aes(Block, propAccept, color = Cost)) +
@@
 
-``` {r BTW: 16.3.2. prepost lm table, pander}
-# panderOptions("digits", 2)
-# pander(prepost$summary, style = "rmarkdown", split.table = 110)
-```
-
   Next, we tested the hypothesis that foragers would display consistent and stable choices.
@@
 # this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
-hrprepostPlot_btw <-dataBtw %>%
+hrprepostPlot_btw <- dataBtw %>%
   group_by(SubjID) %>%
-  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half")) %>%
+  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half"),
+         Handling = case_when(
+           Handling == 2 ~ "2 s",
+           Handling == 10 ~ "10 s",
+           Handling == 14 ~ "14 s"
+         ),
+         Handling = factor(Handling, levels = c("2 s", "10 s", "14 s"))) %>%
   group_by(SubjID, Half, Handling, Cost, Offer) %>%
@@
   summarise(propAccept = mean(pAccept),
-            SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
+            SE = sd(pAccept) / sqrt(length(pAccept))) %>%
   ungroup() %>%
@@
   ggplot(aes(Offer, propAccept, color = Cost)) +
-    geom_point(size = 3, show.legend = T) +
-    geom_line(size = 1, show.legend = F) +
+  geom_point(size = 1.2, show.legend = T) +
+  geom_line(size = 0.8, show.legend = F) +
   scale_color_manual(values = colsBtw) +
@@
   labs(y = "Proportion Accepted") +
-    facet_wrap(vars(Handling, Half), ncol = 2) +
+  facet_grid(Handling ~ Half) +
+  theme_minimal(base_size = 20) +
   theme(legend.position = "bottom", 
-          strip.text.x = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(), 
-          panel.background = element_blank(), 
-          axis.line = element_line(colour = "black"),
-          text = element_text(size = 28))
+        legend.margin=margin(t = -0.6, unit='cm'),
+        strip.text.x = element_blank())
 
@@
 # left plot in 16.3.2
-#ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
+# ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
 include_graphics("./Images/FIG6_prepostbtw.png")

### 2021-03-15 Cost_manuscript.Rmd
new organization per experiment

@@
 In two experiments, independent sets of participants collected rewards that required equivalent periods of cognitive effort, physical effort, or unfilled delay.
-Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial (between-subjects, n=21 per condition), or varied across trials (within-subjects, n=48).
-Participants were free either to accept or reject the cost/reward prospect offered on each trial.
-All participants were more likely to accept offers when rewards were higher and delays shorter (in line with a reward-maximizing strategy), almost never reversed their acceptance decisions, and committed few errors while completing the effort requirements.
-When participants faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
-**We theorized that i**f cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards.
+Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial (between-subjects, n=21 per condition), or varied across trials (within-subjects, n=48).When participants faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
+We theorized that if cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards.
 In the within-subject experiment, an initially higher acceptance rate for cognitive effort trials disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions.
@@
   Evaluating whether to pursue a desirable outcome often requires assessing the demands required for obtaining it.
-In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017 ;@Westbrook2015].
+In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017 ;@Westbrook2015; @Frederick2002; Walton2006].
 Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2010; @Kool2018; @Treadway2009; @Westbrook2013].
@@
 
-## Methods
-
-### **Experiment 1: Between-subjects comparison of costs**
-
-### Participants
+## Experiment 1: Between-subjects comparison of costs
+
+### *Methods*
+#### **Participants**
 
@@
 
-### Foraging Task
+#### **Foraging Task**
 
@@
 
-include_graphics("./Images/FIG1_task_a.png")
-```
-
-### Operationalization of Cost
+include_graphics("./Images/FIG1_task.png")
+```
+
+#### **Operationalization of Cost**
 
@@
 
-### Analyses
+#### **Analyses**
 
@@
 
-### **Experiment 2: Within-subjects comparison of costs**
-
-### Participants
-
-  We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36; number excluded before reaching goal = 6).
-Sample size was once again determined by means of a power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each condition).
-The resulting sample size was 45, which we increased to 48 in order to balance the potential order of blocks.
-We excluded participants using the same criteria as in the between-subject experiment.
-
-### Foraging Task Adaptation
-
-  The original between-subjects task was modified so that participants foraged for cost types in addition to rewards.
-Every participant experienced all forms of cost (delay, physical effort, and cognitive effort).
-There were two block types, in which delay trials were interspersed with either physical-effort or cognitive-effort trials.
-This setup prevented participants from having to rapidly switch between response modalities across trials (i.e.
-keyboard press and handgrip).
-Block combinations (i.e.
-physical/wait and cognitive/wait) were experienced three times by each participant in 7-minute-long, interleaved blocks, thus matching the experiment’s length to the between-subject version.
-Half of the participants experienced a block sequence that started with the physical block.
-Timing parameters were matched to the middle condition from Experiment 1 (i.e.
-10 s handling and 6 s travel), establishing a balance between acquiring enough observations per trial type and being able to compare results across experiments.
-Participants were informed that this timing combination would be constant prior to beginning the experiment.
-Cost type combinations were disclosed at the beginning of each block, and reward/cost offers displayed before each trial begins (e.g.
-“8 cents for physical effort”).
-Unlike the previous experiment, participants could express their decision to quit during the offer window (instead of during the handling time).
-Participants trained in each type of demand until they reached the same criteria as in the between-subject experiment.
-
-### Analyses
-
-  The analytical pipeline was mostly preserved from the between-subject experiment.
-We first ran tests to determine whether decision makers integrated reward information.
-We performed a mixed-effects logistic regression with regressors for offer amount, number of consecutive offer misses, and the sum of the *n* previously observed offers (we identified *n* by comparing the AIC of different history lengths).
-We then confirmed that the under- and over-acceptance were detrimental to total earnings by performing the same quadratic linear model explained above.
-To determine the optimality of the group’s decisions, we examined whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents were always be accepted, given our design).
-The reward-maximizing strategy was to always reject 4 cents and accept 8 cents, yielding a combined optimal proportion of acceptances of 50% (see Operationalization of Costs for details).
-We performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
-Therefore, a significant difference indicated that participants either over or under accepted rewards.
-
-  To compare acceptances among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
-The model included cost condition and reward amount as fixed main effects, and participant ID as a random intercept (handling time is not modeled, as participants experienced a single time combination).
-Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
-We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions.
-We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity in a forward order: 1) intercept only; 2) cost only; 3) reward only; 4) cost and reward main effects (a priori model); and 5) adding a two-way interaction.
-We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
-Models with similar AIC were formally compared using the analysis-of-deviance approach from the between-subjects experiment.
-
-  Next we probed consistency and stability in people's choices.
-First, we qualitatively assessed the number of quits performed during during the handling time through a survival curve, and plotted the quit response time distribution as a function of block to examine choice consistency over time.
-Next, we computed the proportion of quits that were performed during the choice window versus during the handling time.
-We interpreted as confidence if a participant made at least 80% of their choices during the offer window.
-We then computed each participant’s total proportion of acceptances on the first two and last two blocks, and compared them using a paired permutation analysis (5000 iterations).
-We avoided the third and fourth block because their effort designation was counterbalanced across participants, which would have biased our estimates.
-
-### **Computational Modeling of Foraging Behavior**
-
-  We performed model comparisons to identify qualities that explained findings from both experiments.
-Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting; 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions in the between-subjects experiment; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) preference ranks should be robust to block order effects, but the magnitude of the differences should be lower for those who started with the physical effort block.
-These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, sunk cost effects, or asymmetric learning of environmental richness (see Discussion).
-
-#### **Model Fitting and Model Comparison Procedures**
-
-  For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm [@Huys2011; @Huys2012].
-Briefly, it was assumed that, at the population level, each parameter was distributed according to a Gaussian distribution, defined by a mean and standard deviation; the individual subject parameters were drawn from this distribution.
-Accordingly, a point estimate for the individual subject parameters were found via maximum a posteriori (MAP) estimation using the population distribution for each parameter as the priors, and the variance in the individual subject parameter estimates were calculated by taking the inverse of the Hessian matrix at the MAP estimate.
-Next, the mean of the prior was updated by taking the weighted mean of individual subject estimates, and the variance of the prior was updated by taking the weighted variance across the parameter estimates of individual subjects.
-This process was repeated until the mean and variance of the prior for all parameters converged (a change of less than .1% across successive iterations).
-Full mathematical details of the algorithm can be found in Huys et al.
-(2011, 2012), and the algorithm was implemented using a custom written R package, GaussExMax, available on github (github.com/gkane26/GaussExMax).
-
-  Model comparison was performed by calculating Bayes Information Criterion at the group level [integrated BIC or iBIC; @Huys2011; @Huys2012; @Kane2019].
-iBIC penalizes the likelihood of the data given model parameters $p(d | model)$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
-
-\begin{align}
-  iBIC = logp(d | model) + \frac{k}{2}log(o)
-\end{align}
-
-  A Laplace approximation was used to find the log marginal likelihood, the likelihood of the data for each subject given the population level distribution over each parameter (Huys et al., 2011; Huys et al., 2012; Kane et al., 2019).
-
-#### **Model Definitions**
-
-  We began by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT; @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it (see Operationalization of Cost for details).
-This decision rule can be expressed as
-
-\begin{align}
-  \text{Model}_\text{base} = R_i - \gamma H_i
-\end{align}
-
-such that a trial’s reward $R_i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_i$, with high gammas promoting selectivity.
-We fit this and all subsequent models using a softmax function to predict the probability of accepting a given trial
-
-\begin{align}
-  P(\text{accept})_i = \dfrac {1} {1 + e^{-(1/\beta)(\text{Model}_\text{base})}}
-\end{align}
-
-gamma in this base model was computed as an individual's empirical earning rate by the time of each offer, with the free temperature parameter $\beta$ indexing decision noise.
-However, this base formulation lacked the flexibility needed to capture the dynamics observed in the within-subjects experiment.
-We therefore tested a second model that allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
-
-\begin{align}
-  \gamma_{i+1} = (1 - (1 - \alpha) ^ {\tau_i}) \dfrac{R_{i} A_{i}}{\tau_i} +  (1 - \alpha) ^ {\tau_i} \gamma_{i}
-\end{align}
-
-where $A_i$ is an acceptance indicator (0 or 1), and $\tau_i$ the amount of time spent in the trial.
-Higher values of the learning rate $\alpha$ (ranging from 0 to 1) prioritized updating from the current trial’s earning rate (left side of the equation), weighed by the amount of time experienced in the past trial.
-This time was given by
-
-\begin{align}
-  \tau_{i} = H_{i}  A_{i} + T_{i}
-\end{align}
-
-such that the handling time was counted only for accepted trials.
-For this adaptive model, we fit the learning rate $\alpha$ and the initial value of $\gamma$ in addition to the temperature.
-These modifications allowed for the tracking of recent history that was part of our criteria, while maintaining the general structure of the base model
-
-\begin{align}
-  \text{Model}_\text{adaptive} = R_i - \gamma_i H_i
-\end{align}
-
-  A third model considered the possibility that each type of demand additively biased the estimate of $\gamma$.
-Such cost bias would be stable if a single demand was experienced, but recalibrated into a global estimate as decision makers faced different types of demands.
-The overall model took the following form
-
-\begin{align}
-  \text{Model}_\text{biased} = R_i - (\gamma + C_i) H_i
-\end{align}
-
-where $\gamma$ was the mean total earning rate for the whole group (0.55).
-Negative values of $mC_i$ would therefore suggest a boost in offer value produced by a demand.
-At each decision point, $mC$ was the cost bias produced by each demand $c_{demand}$ weighted against a global bias estimate $C$
-
-\begin{align}
-  C_i = c_\text{global} w_i + c_\text{demand} (1 - w_i)
-\end{align}
-
-with $w_i$ controlling how early participants started integrating the converging cost $C$ into their decisions. The value of this weight was given by
-
-\begin{align}
-  w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}
-\end{align}
-
-where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parmeter $\alpha_w$ denoting a late integration of the global converging bias.
-
-  Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $C$ where the same and $\alpha_w$ did not play a role.
-This resulted in just fitting parameters $c_{demand}$ and $\beta$ for that dataset.
-For the within-subjects group, we assumed that the resulting $c_{demand}$ values from the first experiment reflected the actual bias induced by each demand.
-We therefore fixed each value of $c_{demand}$ (i.e.
-$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each between-subjects demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$.
-This dynamic allowed for the observed merging of acceptances across demands in the within-subjects experiment, while respecting the stability in the between-subjects study.
-
-  A final model combined the main features from $model_{adaptive}$ and $model_{biased}$, such that $\gamma$ was estimated on each trial per Eq.
-3, with demands imposing distinct and potentially converging biases as described in model 3.
-The form of this fourth model was
-
-\begin{align}
-  \text{Model}_\text{adaptive + biased} = R_i - (\gamma_i + C_i) H_i
-\end{align}
-
-  After fitting the parameters, we performed two-sided, one-sample t-tests to compare the biased opportunity costs from each between-subjects demand group **to the mean optimal gamma** (0.61, see Operationalization of Cost).
-This allowed us to determine whether any demand boosted an offer's value.
-Finally, we compared parameters with ANOVAs and post-hoc permutations between each group pairing (5000 iterations).
-
-## Results
-
-### **Between-subjects: Tests of whether decision makers integrate delay and reward information**
+### *Results*
+#### **Between-subjects: Tests of whether decision makers integrate delay and reward information**
 
@@
 
-### **Between-subjects: Comparisons among the four delay and effort conditions**
+#### **Between-subjects: Comparisons among the four delay and effort conditions**
 
@@
 We performed group-level chi-squared tests of proportions to examine whether each cost biased decision makers to under- or over-accept 4 and 8 cent offers, which together should have been accepted 50% of the time.
-We found a significant over-acceptance of these trials by the cognitive effort group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`%; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Cognitive", "pval"]`), but under-acceptances by the physical (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`%; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"]`) and wait (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`%; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"]`) groups (no significant difference for the Easy group).
+We found a significant over-acceptance of these trials by the cognitive effort group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Cognitive", "pval"])`), but under-acceptances by the physical (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) and wait (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) groups (no significant difference for the Easy group).
 Together, these findings show that even though participants did not always perform optimally, they adequately integrated the statistics of the environment as they tracked their recent experience.
@@
 
-### **Between-subjects: Consistency and stability**
+#### **Between-subjects: Consistency and stability**
 
@@
 
-### **Within-subjects: Tests of whether decision makers integrate reward information**
+## Experiment 2: Within-subjects comparison of costs
+### *Methods*
+#### **Participants**
+
+  We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36; number excluded before reaching goal = 6).
+Sample size was once again determined by means of a power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each condition).
+The resulting sample size was 45, which we increased to 48 in order to balance the potential order of blocks.
+We excluded participants using the same criteria as in the between-subject experiment.
+
+#### **Foraging Task Adaptation**
+
+  The original between-subjects task was modified so that participants foraged for cost types in addition to rewards.
+Every participant experienced all forms of cost (delay, physical effort, and cognitive effort).
+There were two block types, in which delay trials were interspersed with either physical-effort or cognitive-effort trials.
+This setup prevented participants from having to rapidly switch between response modalities across trials (i.e.
+keyboard press and handgrip).
+Block combinations (i.e.
+physical/wait and cognitive/wait) were experienced three times by each participant in 7-minute-long, interleaved blocks, thus matching the experiment’s length to the between-subject version.
+Half of the participants experienced a block sequence that started with the physical block.
+Timing parameters were matched to the middle condition from Experiment 1 (i.e.
+10 s handling and 6 s travel), establishing a balance between acquiring enough observations per trial type and being able to compare results across experiments.
+Participants were informed that this timing combination would be constant prior to beginning the experiment.
+Cost type combinations were disclosed at the beginning of each block, and reward/cost offers displayed before each trial begins (e.g.
+“8 cents for physical effort”).
+Unlike the previous experiment, participants could express their decision to quit during the offer window (instead of during the handling time).
+Participants trained in each type of demand until they reached the same criteria as in the between-subject experiment.
+
+#### **Analyses**
+
+  The analytical pipeline was mostly preserved from the between-subject experiment.
+We first ran tests to determine whether decision makers integrated reward information.
+We performed a mixed-effects logistic regression with regressors for offer amount, number of consecutive offer misses, and the sum of the *n* previously observed offers (we identified *n* by comparing the AIC of different history lengths).
+We then confirmed that the under- and over-acceptance were detrimental to total earnings by performing the same quadratic linear model explained above.
+To determine the optimality of the group’s decisions, we examined whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents were always be accepted, given our design).
+The reward-maximizing strategy was to always reject 4 cents and accept 8 cents, yielding a combined optimal proportion of acceptances of 50% (see Operationalization of Costs for details).
+We performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
+Therefore, a significant difference indicated that participants either over or under accepted rewards.
+
+  To compare acceptances among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
+The model included cost condition and reward amount as fixed main effects, and participant ID as a random intercept (handling time is not modeled, as participants experienced a single time combination).
+Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
+We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions.
+We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity in a forward order: 1) intercept only; 2) cost only; 3) reward only; 4) cost and reward main effects (a priori model); and 5) adding a two-way interaction.
+We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
+Models with similar AIC were formally compared using the analysis-of-deviance approach from the between-subjects experiment.
+
+  Next we probed consistency and stability in people's choices.
+First, we qualitatively assessed the number of quits performed during during the handling time through a survival curve, and plotted the quit response time distribution as a function of block to examine choice consistency over time.
+Next, we computed the proportion of quits that were performed during the choice window versus during the handling time.
+We interpreted as confidence if a participant made at least 80% of their choices during the offer window.
+We then computed each participant’s total proportion of acceptances on the first two and last two blocks, and compared them using a paired permutation analysis (5000 iterations).
+We avoided the third and fourth block because their effort designation was counterbalanced across participants, which would have biased our estimates.
+
+### *Results*
+#### **Within-subjects: Tests of whether decision makers integrate reward information**
 
@@
 
-### **Within-subjects: Comparisons among the four delay and effort conditions**
+#### **Within-subjects: Comparisons among the four delay and effort conditions**
 
@@
 
-### **Consistency and stability**
+#### **Consistency and stability**
 
@@
 
-### **Computational modeling of foraging behavior**
-
-``` {r OLD BTW and WTH: 16.3. OC modeling btw, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# ## fit the OC model
-# summaryOC_btw <- list()
-# summaryOC_btw$all <- dataBtw %>%
-#                  group_by(Cost, SubjID) %>%
-#                  do(optimizeOCModel(., simplify = T)) %>%
-#                  ungroup()
-# 
-# 
-# ## plot
-# summaryOC_btw$plot <- ggplot(summaryOC_btw$all, aes(Cost, Gamma, fill = Cost)) +
-#   # geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
-#   # geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
-#   # geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-#   geom_hline(yintercept = 0.74, alpha = 0.9, size = 1, linetype = "dashed") + # mean of highest earning rates across blocks
-#   #geom_dotplot(stackdir = 'center', binaxis = 'y', show.legend = F) +
-#   geom_boxplot(show.legend = F) +
-#   geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
-#   ylim(0,1.5) +
-#   labs(x = "") +
-#   scale_fill_manual(values = colsBtw) +
-#   theme(panel.grid.major = element_blank(),
-#         panel.grid.minor = element_blank(),
-#         panel.background = element_blank(),
-#         axis.line = element_line(colour = "black"),
-#         text = element_text(size = 16))
-# 
-# 
-# ## one sample t against optimal strategy
-# summaryOC_btw$t.test <- summaryOC_btw$all %>%
-#   select(Cost, Gamma) %>%
-#   plyr::dlply("Cost", identity) %>%
-#   sapply(., function(data) {t.test(data$Gamma, mu = 0.74)})
-# 
-# 
-# ## descriptive stats
-# summaryOC_btw$descriptives <- summaryOC_btw$all %>%
-#   group_by(Cost) %>%
-#   summarise(mGamma = round(mean(Gamma), digits = 2),
-#             sdGamma = round(sd(Gamma), digits = 2))
-
-# summaryOC$all %>%
-#   ggplot(aes(Gamma, percentAccept, fill = Cost, size = temperature)) +
-#   geom_point(pch = 21)
-
-# # gamma parameter recovery tests
-# # test a single subject against their own choices
-# (subj <- sample(subjList_btw, 1))
-# subjData <- dataBtw %>% 
-#   filter(SubjID == subj) %>% 
-#   group_by(Cost, Handling, Offer) %>% 
-#   summarise(propAccept = mean(Choice)) %>%
-#   ungroup()
-# 
-# params <- filter(summaryOC$all, SubjID == subj) %>% 
-#   select(Gamma, temperature)
-# 
-# test_params(params,
-#             model = expr(params$Gamma * Handling), 
-#             subjData, 
-#             plot = T)
-
-# # test multiple values of gamma and plot the comparison
-# lowGamma <- 0
-# upperGamma <- 1.7
-# nGamma <- 6
-# testys <- lapply(seq(lowGamma, upperGamma, length.out = nGamma), test_params)
-# (testys <- do.call(rbind, testys))
-# testys %>%
-#   ggplot(aes(interaction(Offer, Handling), Choice, color = Gamma)) +
-#   geom_point(size = 3) +
-#   geom_line(aes(group = interaction(Handling, Gamma)), size = 1) +
-#   labs(x = "Offer.Handling", y = "Proportion Accepted") +
-#   facet_wrap(vars(Gamma), ncol = 2) +
-#   theme(legend.key = element_blank(),
-#         panel.grid.major = element_blank(),
-#         panel.grid.minor = element_blank(),
-#         panel.background = element_blank(),
-#         axis.line = element_line(colour = "black"),
-#         text = element_text(size = 16))
-
-```
-
-``` {r OLD BTW and WTH: 16.3. OC comparisons btw, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# # ANOVA
-# OCanova <- list()
-# OCanova$aov <- summary(aov(Gamma ~ Cost, data = summaryOC_btw$all))
-# Fval <- round(OCanova$aov[[1]]$`F value`[1], digits = 2) # doing separate variables because I can't easily use the `` in markdown.
-# Pval <- OCanova$aov[[1]]$`Pr(>F)`[1]
-# Rsquared_aov <- round(OCanova$aov[[1]]$`Sum Sq`[1] / sum(OCanova$aov[[1]]$`Sum Sq`), digits = 2)
-# 
-# # Post-hoc pairwise tests
-# OCanova$perms <- summaryOC_btw$all %>%
-#   select(Cost, Gamma) %>%
-#   plyr::dlply("Cost", identity) %>%
-#   do.call(cbind, .) %>%
-#   select_if(is.numeric) %>%
-#   rename(Physical = Physical.Gamma,
-#          Cognitive = Cognitive.Gamma,
-#          Wait = Wait.Gamma,
-#          Easy = Easy.Gamma) %>%
-#   outer(., ., FUN = Vectorize(permute), simple = T)
-# diag(OCanova$perms) <- 1
-# 
-# OCanova$ES <- summaryOC_btw$all %>%
-#   select(Cost, Gamma) %>%
-#   plyr::dlply("Cost", identity) %>%
-#   do.call(cbind, .) %>%
-#   select_if(is.numeric) %>%
-#   rename(Physical = Physical.Gamma,
-#          Cognitive = Cognitive.Gamma,
-#          Wait = Wait.Gamma,
-#          Easy = Easy.Gamma) %>%
-#   outer(., ., FUN = Vectorize(cohenD)) %>%
-#   abs()
-```
-
-``` {r OLD BTW and WTH: 16.3. corrplot btw, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
-# # plot all pairwise comparisons
-# corrplot(OCanova$ES,
-#          is.corr = F, 
-#          p.mat = OCanova$perms,
-#          type = "upper",
-#          insig = "p-value",
-#          sig.level = -1,
-#          na.label = "square",
-#          na.label.col = "grey",
-#          method = "color", 
-#          tl.col = "black", 
-#          tl.cex = 0.8,
-#          outline = T)
-```
-
-``` {r OLD BTW and WTH: 16.3. OC cross-validation btw, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-# # Compute the OC for pre-midpoint
-# summaryOC_btw$pre <- dataBtw %>%
-#                  filter(Half == "Half_1") %>%
-#                  group_by(Cost, SubjID) %>%
-#                  do(optimizeOCModel(., simplify = T)) %>%
-#                  ungroup() %>%
-#                  select(SubjID, Gamma)
-# 
-# # let's add the gammas to the second half data and estimate prop predicted on the second half
-# summaryOC_btw$predicted <- dataBtw %>%
-#                  filter(Half == "Half_2") %>%
-#                  group_by(Cost, SubjID) %>%
-#                  left_join(summaryOC_btw$pre, by = "SubjID") %>%
-#                  mutate(OC = Handling * Gamma,
-#                         predicted = Offer > OC) %>% 
-#                  summarise(percentPredicted = mean(predicted == Choice) * 100) %>%
-#                  group_by(Cost) %>%
-#                  summarise(mPredicted = round(mean(percentPredicted), digits = 2),
-#                            sdPredicted = round(sd(percentPredicted), digits = 2))
-
-# # plot
-# (summaryOC_btw$predictPlot <- ggplot(summaryOC_btw$predicted, aes(Cost, percentPredicted, fill = Cost)) +
-#                             labs(x = "") +
-#                             geom_boxplot(show.legend = F) +
-#                             scale_fill_manual(values = colsBtw) +
-#                             labs(y = "Percent Predicted") +
-#                             ylim(0,100) +
-#                             theme(panel.grid.major = element_blank(),
-#                             panel.grid.minor = element_blank(),
-#                             panel.background = element_blank(),
-#                             axis.line = element_line(colour = "black"),
-#                             text = element_text(size = 16)))
-
-```
-
-``` {r OLD BTW and WTH: 16.3. OC Modeling wth, echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
-# # Here it might be best to estimate gamma for the wait trials only at first
-# # once the wait OCs are estimated, then they can be modulated by effort
-# # Estimate gamma per subject for each group separately
-# summaryOC_wth <- list()
-# summaryOC_wth$all <- dataWth %>%
-#   mutate(Block = case_when(
-#     Block %in% c(1, 2) ~ 1,
-#     Block %in% c(3, 4) ~ 2,
-#     Block %in% c(5, 6) ~ 3
-#   )) %>%
-#   #filter(Choice < 2) %>%
-#   group_by(SubjID, Cost) %>% #group_by(SubjID, Cost, Block) %>%
-#   do(optimizeOCModel(., simplify = T)) %>%
-#   ungroup()
-# 
-# # plot
-# summaryOC_wth$plot <- ggplot(summaryOC_wth$all, aes(Cost, Gamma, fill = Cost)) +
-#     geom_boxplot(show.legend = F) +
-#     geom_hline(yintercept = 0.64, alpha = 0.9, color = "gray20", size = 1) +
-#     geom_hline(yintercept = 0.7, alpha = 0.9, color = "gray40", size = 1) +
-#     geom_hline(yintercept = 0.9, alpha = 0.9, color = "gray60", size = 1) +
-#     ylim(0,1.5) +
-#     labs(x = "") +
-#     scale_fill_manual(values = colsWth) +
-#     theme(panel.grid.major = element_blank(),
-#           panel.grid.minor = element_blank(),
-#           panel.background = element_blank(),
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 16))
-
-# try to replicate the group-level proportion of acceptances from 16.2
-# this looks pretty much like the empirical proportion data, so the stochasticity is playing a major part in the estimation
-# the estimate probability even matches actual proportions at the single subject level 
-# logis <- mapply(function(g, t) {1 / (1 + exp((-1 * t) * (c(4, 8, 20) - (g * 10))))}, summaryOC_wth$all$Gamma, summaryOC_wth$all$Temperature)
-# colnames(logis) <- unite(summaryOC_wth, test, SubjID, Cost)$test
-# logis2 <- as.data.frame(logis) %>% 
-#   gather(Cost, Probability) %>%
-#   mutate(SubjID = substr(Cost, 1,3), 
-#          Cost = substr(Cost, 5,20),
-#          Reward = rep(c(4,8,20), nrow(.)/3)) %>%
-#   group_by(Cost, Reward) %>%
-#   summarize(propAccept = mean(Probability)) %>%
-#   ggplot(logis2, aes(Reward, propAccept, color = Cost)) +
-#     geom_point(size = 3, show.legend = T) +
-#     geom_line(lwd = 1, show.legend = T) +
-#     scale_color_manual(values = colsWth) +
-#     scale_fill_manual(values = colsWth) +
-#     #geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
-#     scale_y_continuous(limits = c(-0.1,1.1), breaks = c(0,0.5,1)) +
-#     scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
-#     labs(y = "Proportion Accepted") +
-#     theme(legend.key = element_blank(),
-#           panel.grid.major = element_blank(),
-#           panel.grid.minor = element_blank(),
-#           panel.background = element_blank(),
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 16))
-```
-
-``` {r OLD BTW and WTH: 16.3. cross-v wth, echo = FALSE, fig.width=5, fig.height=4, fig.align="center"}
-# # subdivide data
-# dataTrain <- dataWth %>%
-#    filter(Block < 5)
-# 
-# dataTest <- dataWth %>%
-#   filter(Block > 4)
-# 
-# # estimate
-# # per-cost, but consider the idea above
-# OCs_validation <- list()
-# temp <- dataTrain %>% filter(Cost == "Wait-C") %>% plyr::dlply("SubjID", identity)
-# OCs_validation$`Wait-C` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-# temp <- dataTrain %>% filter(Cost == "Wait-P") %>% plyr::dlply("SubjID", identity)
-# OCs_validation$`Wait-P` <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-# temp <- dataTrain %>% filter(Cost == "Cognitive") %>% plyr::dlply("SubjID", identity)
-# OCs_validation$Cognitive <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-# temp <- dataTrain %>% filter(Cost == "Physical") %>% plyr::dlply("SubjID", identity)
-# OCs_validation$Physical <- sapply(temp, function(Data) {optimizeOCModel(Data)$Gamma})
-# 
-# # reshape data
-# temp <- bind_rows(OCs_validation) %>% 
-#   mutate(SubjID = subjList_wth) %>%
-#   gather(Cost, gamma, `Wait-C`:Physical) %>%
-#   left_join(dataTest, ., by = c("SubjID", "Cost")) %>% # assign OCs to each subject per cost type
-#   mutate(prediction = Offer > Handling * gamma) %>%
-#   # plyr::dlply("SubjID", identity)
-#   group_by(SubjID, Cost) %>%
-#   summarize(predicted = mean(Choice == prediction))
-
-# plot prediction %
-# qplot(Cost, predicted, geom = "boxplot", data = temp) + 
-#   ylim(0,1) +
-#   theme_classic()
-```
-
-``` {r OLD BTW and WTH: 16.3. param compare wth, echo = FALSE}
-# # repeated measures anova
-# OCs_anova <- list()
-# OCs_anova$aov <- summary(aov(Gamma ~ Cost + Error(SubjID / Cost), data = summaryOC_wth$all))
-# 
-# # table
-# #pander(OCs_anova$aov)
-# 
-# # do all pairwise comparisons
-# OCs_anova$gammas <- summaryOC_wth$all %>% 
-#   reshape2::dcast(SubjID ~ Cost, value.var = "Gamma") %>%
-#   select(-SubjID)
-# 
-# # perform a paired permutation among every pair of cost types
-# OCs_anova$perms <- outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(permute), simple = T, paired = T)
-# OCs_anova$perms[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
-# 
-# # and the effect sizes
-# OCs_anova$ES <- abs(outer(OCs_anova$gammas, OCs_anova$gammas, FUN = Vectorize(DescTools::CohenD)))
-# OCs_anova$ES[rbind(c(1,4),c(2,3),c(3,2),c(4,1))] <- NA
-```
-
-``` {r OLD BTW and WTH: 16.3. corrplot wth, echo = FALSE, fig.align="center", fig.width=5, fig.height=5}
-# corrplot(OCs_anova$ES,
-#          is.corr = F, 
-#          p.mat = OCs_anova$perms,
-#          type = "upper",
-#          insig = "p-value",
-#          sig.level = -1,
-#          na.label = "square",
-#          na.label.col = "grey",
-#          method = "color", 
-#          tl.col = "black", 
-#          tl.cex = 0.8,
-#          outline = T)
-```
+## Computational Modeling of Foraging Behavior
+
+  We performed model comparisons to identify qualities that explained findings from both experiments.
+Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting; 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions in the between-subjects experiment; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) preference ranks should be robust to block order effects, but the magnitude of the differences should be lower for those who started with the physical effort block.
+These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, sunk cost effects, or asymmetric learning of environmental richness (see Discussion).
+
+### *Methods*
+#### **Model Fitting and Model Comparison Procedures**
+
+  For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm [@Huys2011; @Huys2012].
+Briefly, it was assumed that, at the population level, each parameter was distributed according to a Gaussian distribution, defined by a mean and standard deviation; the individual subject parameters were drawn from this distribution.
+Accordingly, a point estimate for the individual subject parameters were found via maximum a posteriori (MAP) estimation using the population distribution for each parameter as the priors, and the variance in the individual subject parameter estimates were calculated by taking the inverse of the Hessian matrix at the MAP estimate.
+Next, the mean of the prior was updated by taking the weighted mean of individual subject estimates, and the variance of the prior was updated by taking the weighted variance across the parameter estimates of individual subjects.
+This process was repeated until the mean and variance of the prior for all parameters converged (a change of less than .1% across successive iterations).
+Full mathematical details of the algorithm can be found in Huys et al.
+(2011, 2012), and the algorithm was implemented using a custom written R package, GaussExMax, available on github (github.com/gkane26/GaussExMax).
+
+  Model comparison was performed by calculating Bayes Information Criterion at the group level [integrated BIC or iBIC; @Huys2011; @Huys2012; @Kane2019].
+iBIC penalizes the likelihood of the data given model parameters $p(d | model)$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
+
+\begin{align}
+  iBIC = logp(d | model) + \frac{k}{2}log(o)
+\end{align}
+
+  A Laplace approximation was used to find the log marginal likelihood, the likelihood of the data for each subject given the population level distribution over each parameter (Huys et al., 2011; Huys et al., 2012; Kane et al., 2019).
+
+#### **Model Definitions**
+
+  We began by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT; @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it (see Operationalization of Cost for details).
+This decision rule can be expressed as
+
+\begin{align}
+  \text{Model}_\text{base} = R_i - \gamma H_i
+\end{align}
+
+such that a trial’s reward $R_i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_i$, with high gammas promoting selectivity.
+We fit this and all subsequent models using a softmax function to predict the probability of accepting a given trial
+
+\begin{align}
+  P(\text{accept})_i = \dfrac {1} {1 + e^{-(1/\beta)(\text{Model}_\text{base})}}
+\end{align}
+
+gamma in this base model was computed as an individual's empirical earning rate by the time of each offer, with the free temperature parameter $\beta$ indexing decision noise.
+However, this base formulation lacked the flexibility needed to capture the dynamics observed in the within-subjects experiment.
+We therefore tested a second model that allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
+
+\begin{align}
+  \gamma_{i+1} = (1 - (1 - \alpha) ^ {\tau_i}) \dfrac{R_{i} A_{i}}{\tau_i} +  (1 - \alpha) ^ {\tau_i} \gamma_{i}
+\end{align}
+
+where $A_i$ is an acceptance indicator (0 or 1), and $\tau_i$ the amount of time spent in the trial.
+Higher values of the learning rate $\alpha$ (ranging from 0 to 1) prioritized updating from the current trial’s earning rate (left side of the equation), weighed by the amount of time experienced in the past trial.
+This time was given by
+
+\begin{align}
+  \tau_{i} = H_{i}  A_{i} + T_{i}
+\end{align}
+
+such that the handling time was counted only for accepted trials.
+For this adaptive model, we fit the learning rate $\alpha$ and the initial value of $\gamma$ in addition to the temperature.
+These modifications allowed for the tracking of recent history that was part of our criteria, while maintaining the general structure of the base model
+
+\begin{align}
+  \text{Model}_\text{adaptive} = R_i - \gamma_i H_i
+\end{align}
+
+  A third model considered the possibility that each type of demand additively biased the estimate of $\gamma$.
+Such cost bias would be stable if a single demand was experienced, but recalibrated into a global estimate as decision makers faced different types of demands.
+The overall model took the following form
+
+\begin{align}
+  \text{Model}_\text{biased} = R_i - (\gamma + C_i) H_i
+\end{align}
+
+where $\gamma$ was the mean total earning rate for the whole group (0.55).
+Negative values of $mC_i$ would therefore suggest a boost in offer value produced by a demand.
+At each decision point, $mC$ was the cost bias produced by each demand $c_{demand}$ weighted against a global bias estimate $C$
+
+\begin{align}
+  C_i = c_\text{global} w_i + c_\text{demand} (1 - w_i)
+\end{align}
+
+with $w_i$ controlling how early participants started integrating the converging cost $C$ into their decisions. The value of this weight was given by
+
+\begin{align}
+  w_i = \left (\frac{i}{max(i)} \right ) ^{\alpha_w}
+\end{align}
+
+where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parmeter $\alpha_w$ denoting a late integration of the global converging bias.
+
+  Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $C$ where the same and $\alpha_w$ did not play a role.
+This resulted in just fitting parameters $c_{demand}$ and $\beta$ for that dataset.
+For the within-subjects group, we assumed that the resulting $c_{demand}$ values from the first experiment reflected the actual bias induced by each demand.
+We therefore fixed each value of $c_{demand}$ (i.e.
+$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each between-subjects demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$.
+This dynamic allowed for the observed merging of acceptances across demands in the within-subjects experiment, while respecting the stability in the between-subjects study.
+
+  A final model combined the main features from $model_{adaptive}$ and $model_{biased}$, such that $\gamma$ was estimated on each trial per Eq.
+3, with demands imposing distinct and potentially converging biases as described in model 3.
+The form of this fourth model was
+
+\begin{align}
+  \text{Model}_\text{adaptive + biased} = R_i - (\gamma_i + C_i) H_i
+\end{align}
+
+  After fitting the parameters, we performed two-sided, one-sample t-tests to compare the biased opportunity costs from each between-subjects demand group **to the mean optimal gamma** (0.61, see Operationalization of Cost).
+This allowed us to determine whether any demand boosted an offer's value.
+Finally, we compared parameters with ANOVAs and post-hoc permutations between each group pairing (5000 iterations).
+
+### *Results*
 
@@
 
-include_graphics("./Images/FIG1_task_a.png")
+include_graphics("./Images/FIG1_task.png")
 ```
@@
 Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
-include_graphics("./Images/FIG6.png")
+include_graphics("./Images/FIG6_prepostbtw.png")
 ```
@@
 
-include_graphics("./Images/FIG8.png")
+include_graphics("./Images/FIG8_survival.png")
 ```
@@
 Bottom: Block rder effects show attenuated differences for those who started with the physical configuration."}
-include_graphics("./Images/FIG9.png")
+include_graphics("./Images/FIG9_prepostwth.png")
 ```
@@
 
-include_graphics("./Images/FIG10.png")
+include_graphics("./Images/FIG10_modelresults.png")
 

### 2021-03-15 Cost_manuscript.Rmd
reworking the intro

@@
 ## Introduction
+
+  Evaluating whether to pursue a desirable outcome often entails assessing the demands required for obtaining it.
+In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017 ;@Westbrook2015; @Frederick2002; Walton2006].
+Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2010; @Kool2018; @Treadway2009; @Westbrook2013].
+However, people still needlessly pursue effortful courses of action in everyday decisions.
+Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcomes, whereby exerting effort boosts the perceived value of its outcomes [@HernandezLallement2014; @Kacelnik2002; @Mochon2012], and positive outcomes imbue value into their preceding effortful behavior [i.e.
+learned industriousness; @Eisenberger1992].
+Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs [Inzlicht2018].
+Understanding what governs the intrinsic costs and rewards of effort could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
+
+	Recent work has proposed that the subjective costs produced by delays and cognitive effort are modulated by the possibility of missing out on better concurrent alternatives, implying that decision makers track the opportunity cost of time [OC; Fawcett2012; Kurzban2013; Otto2019].
+Preferences for effortful courses of action could therefore arise from the presence of other types of demands and opportunities in the same choice environment [Kool2018].
+For example, exerting high effort for a reward might be aversive, but the same level of work might be appealing in comparison to the boredom of an equivalent period of passive waiting (e.g.
+taking the cumbersome way home rather than waiting for a delayed train, even if the resulting time of arrival is the same).
+This effect of context on effort preferences has been illustrated by experiments on charitable giving, in a which high-effort donation method (such as a run) attracted larger donations than a low-effort method (such as a picnic) when either was available alone (the “martyrdom effect”), but the high-effort event was disfavored when both options were offered as alternatives [Olivola & Shafir, 2013].
+
+	Standard models in neuroeconomics and behavioral economics cannot readily address this possibility.
+The effects on valuation of different types of effort or delay have traditionally been formalized with discounting functions that capture how much less appealing a reward becomes as a function of the associated amount of effort or delay [Ainslie1975; Frederick2002; Green1994; Kable2007; Klein-Flugge2015; Kool2010; Westbrook2013].
+An advantage of relying on these standardized functions is that they can circumvent a key confound when comparing effort and delay, namely that increasingly effortful tasks also tend to take longer to perform.
+However, although this line of work suggests that discounting functions are similar for delay and effort [Massar2015; Prevost2010; Seaman2018], there is ongoing debate about the shape of the discounting function across types of demands [Arulpragasam2018; Białaszek2017; Chong2017; Hartmann2013; Klein-Flugge2016; Kool2018; Prevost2010], and the degree to which discount rates correlate across cost domains [Seaman2018; Westbrook2013].
+Further, this approach does not directly probe which type of demand people would prefer if given the option, and constrains the understanding of behavioral demands to one in which such demands are bound to reduce the value of prospects.
+
+	This evidence sets the stage for examining what people would actually select in environments that intermixed multiple types of demands, including cognitive, physical effort, and delay.
+Single choice foraging paradigms provide a natural way to interrogate preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during the same time period instead (Constantino & Daw, 2015; Garrett & Daw, 2020; Krebs, Erichsen, & Webber, 1977; Mobbs et al., 2018; Stephens & Krebs, 1986).
+Such paradigms probe the perceived opportunity cost of time, which has been hypothesized to underlie the evaluation of behavioral costs (Kurzban et al., 2013).
+Specifically, foragers must decide whether to spend their limited time by harvesting their currently available resource or by seeking out more profitable (or less costly) alternatives.
+This could involve, for example, deciding when to leave a patch of depleting richness (e.g.
+when to quit a job that provides diminishing opportunities for growth), or choosing whether to pursue or forgo offers presented serially (e.g.
+whether to accept your first job offer or wait for new potential ones).
+Here we focus on this latter type of foraging, traditionally called prey foraging (Krebs et al., 1977), as it provides a means to examine how choices to accept or reject individual prospects are influenced by contextual knowledge about other potentially obtainable alternatives in the same environment.
+
+	Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionarily conserved choice behaviors (Hayden, 2018; Mobbs et al., 2018), and offers a number of desirable qualities to address our question.
+First, it allows for the estimation of optimal, reward maximizing choice patterns on the basis of the opportunity cost of time (Charnov, 1976; Krebs et al., 1977).
+The opportunity cost depends on the richness of the environment, which can be experimentally manipulated by balancing the amount of time it takes to harvest an offer (handling time) versus to search for new ones (travel time).
+We can then interpret observed deviations from such optimal behavior, and examine how foraging behavior changes when the handling time is filled with cognitive effort or physical effort in comparison with unfilled delay (thus disentangling effort from delay duration).
+Second, in contrast to multi-alternative economic choice paradigms that often treat choices as independent observations, the sequential nature of foraging encourages individuals to consider both focal and global elements of the decision context.
+For example, the cost (or value) of effort and delay could globally depend on the availability of alternative demands, impacting the perceived opportunity cost of time.
+Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that are adjusted once individuals experience different forms of behavioral costs.
+Foraging rests on an abundant modeling history that provides computational tools to formalize relevant decision variables (Stephens & Krebs, 1986).
+
+	Across two behavioral experiments, we tested the overarching hypothesis that preferences would vary depending on whether individuals faced a single type or multiple types of behavioral demands (i.e.
+cognitive effort, physical effort, and delay).
+Experiment 1 used a between-subject design in which participants foraged for rewards of varying magnitudes that imposed varying durations of a single form of demand.
+Experiment 2 used a within-subject design in which individuals foraged for varying forms of demand in addition to varying reward magnitudes.
+We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions (Inzlicht et al., 2018).
+First, we examined whether the discounting effects consistently observed in multi-alternative economic choice paradigms persisted when these options were presented serially, and whether the resulting foraging patterns depended on the demands imposed to obtain rewards.
+The existence of a well-defined optimal, reward-maximizing choice strategy helped us identify when demands boosted or detracted from the value of rewards (signified by tendencies to overharvest poor offers or underharvest advantageous offers, respectively).
+Second, we probed whether the perceived cost (or value) of demands was intrinsic or dependent on either task-specific or contextual characteristics.
+For instance, varying the level of exposure to multiple types of demands across experiments allowed us to assess whether cost evaluation was dependent on the availability of alternative avenues of action.
+Further, including cognitive demands and physical demands let us examine whether such effects might apply differently to distinct types of effort.
+
+	Our results provided mixed support for our pre-registered hypotheses, which are detailed in https://osf.io/2rsgm/.
+For Experiment 1, we hypothesized that 1) decision makers would integrate reward and timing information in order to approximate optimal foraging strategies, as reflected by acceptance rates; 2) acceptance rates would be higher for trials that demanded physical effort and cognitive effort than for unfilled delay or effortless engagement (based on the apparent value of effort displayed by charitable donors, as described above); and 3) choices would be consistent within trials, reflected by few choice reversals, and acceptance rates for each type of demand would remain stable over time.
+Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment.
+We also found that people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups under-accepted, partially matching our predictions and highlighting that cognitive effort can add value to outcomes.
+Finally, acceptances (and differences among demands) were both consistent and stable within each cost condition, in line with expectations.
+For Experiment 2, we hypothesized that 1) acceptance rates would once again approximate optimality, and would show effects of reward magnitude similar to those seen in Experiment 1; 2) in contrast to Experiment 1, participants would gravitate towards unfilled delays to obtain rewards; and 3) that choices would be consistent and stable over time.
+As before, decision makers approached the optimal strategy for the foraging environment, resembling the pattern observed in Experiment 1.
+Contrary to our second and third hypotheses, we found that a preference for cognitive effort was present initially but disappeared over time as decision makers foraged for types of demands in addition to rewards.
+
+	Computational modeling results suggested that the normative predictions of traditional foraging models were insufficient to explain our data.
+Instead, the data supported a model in which demands imposed a bias on the estimated opportunity cost of time, which converged as individuals gained experienced with interleaved types of demands.
+We hypothesize that this bias arises from modulations of subjective time.
+For instance, cognitive effort could have become appealing by virtue of compressing the perceived trial time, a perception that could be recalibrated with exposure to alternative demands.
+The subjective shortening of experienced durations during cognitive effort could be due to the ongoing recruitment of working memory (e.g.
+preventing individuals from estimating the elapsed time), or because the discrete events within the cognitive task subdivided the time interval.
+These results expand our understanding of the attractiveness of effort, suggesting potential reward-independent factors that could be leveraged to motivate effort engagement in diverse, everyday scenarios.
+
+-----------------------------------
 

### 2021-03-15 Cost_manuscript.Rmd
reinserting refs on intro

@@
 learned industriousness; @Eisenberger1992].
-Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs [Inzlicht2018].
+Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs [@Inzlicht2018].
 Understanding what governs the intrinsic costs and rewards of effort could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
 
-	Recent work has proposed that the subjective costs produced by delays and cognitive effort are modulated by the possibility of missing out on better concurrent alternatives, implying that decision makers track the opportunity cost of time [OC; Fawcett2012; Kurzban2013; Otto2019].
-Preferences for effortful courses of action could therefore arise from the presence of other types of demands and opportunities in the same choice environment [Kool2018].
+Recent work has proposed that the subjective costs produced by delays and cognitive effort are modulated by the possibility of missing out on better concurrent alternatives, implying that decision makers track the **opportunity cost of time** [OC; @Fawcett2012; @Kurzban2013; @Otto2019].
+Preferences for effortful courses of action could therefore arise from the presence of other types of demands and opportunities in the same choice environment [@Kool2018].
 For example, exerting high effort for a reward might be aversive, but the same level of work might be appealing in comparison to the boredom of an equivalent period of passive waiting (e.g.
 taking the cumbersome way home rather than waiting for a delayed train, even if the resulting time of arrival is the same).
-This effect of context on effort preferences has been illustrated by experiments on charitable giving, in a which high-effort donation method (such as a run) attracted larger donations than a low-effort method (such as a picnic) when either was available alone (the “martyrdom effect”), but the high-effort event was disfavored when both options were offered as alternatives [Olivola & Shafir, 2013].
+This effect of context on effort preferences has been illustrated by experiments on charitable giving, in a which high-effort donation method (such as a run) attracted larger donations than a low-effort method (such as a picnic) when either was available alone (the “martyrdom effect”), but the high-effort event was disfavored when both options were offered as alternatives [@Olivola2013].
 
   Standard models in neuroeconomics and behavioral economics cannot readily address this possibility.
-The effects on valuation of different types of effort or delay have traditionally been formalized with discounting functions that capture how much less appealing a reward becomes as a function of the associated amount of effort or delay [Ainslie1975; Frederick2002; Green1994; Kable2007; Klein-Flugge2015; Kool2010; Westbrook2013].
+The effects on valuation of different types of effort or delay have traditionally been formalized with discounting functions that capture how much less appealing a reward becomes as a function of the associated amount of effort or delay [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @Klein-Flugge2015; @Kool2010; @Westbrook2013].
 An advantage of relying on these standardized functions is that they can circumvent a key confound when comparing effort and delay, namely that increasingly effortful tasks also tend to take longer to perform.
-However, although this line of work suggests that discounting functions are similar for delay and effort [Massar2015; Prevost2010; Seaman2018], there is ongoing debate about the shape of the discounting function across types of demands [Arulpragasam2018; Białaszek2017; Chong2017; Hartmann2013; Klein-Flugge2016; Kool2018; Prevost2010], and the degree to which discount rates correlate across cost domains [Seaman2018; Westbrook2013].
+However, although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across types of demands [@Arulpragasam2018; @Białaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and the degree to which discount rates correlate across cost domains [@Seaman2018; @Westbrook2013].
 Further, this approach does not directly probe which type of demand people would prefer if given the option, and constrains the understanding of behavioral demands to one in which such demands are bound to reduce the value of prospects.
@@
   This evidence sets the stage for examining what people would actually select in environments that intermixed multiple types of demands, including cognitive, physical effort, and delay.
-Single choice foraging paradigms provide a natural way to interrogate preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during the same time period instead (Constantino & Daw, 2015; Garrett & Daw, 2020; Krebs, Erichsen, & Webber, 1977; Mobbs et al., 2018; Stephens & Krebs, 1986).
-Such paradigms probe the perceived opportunity cost of time, which has been hypothesized to underlie the evaluation of behavioral costs (Kurzban et al., 2013).
+Single choice foraging paradigms provide a natural way to interrogate preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during the same time period instead [@Constantino2015; @Garrett2020; @Krebs1977; @Mobbs2018; @Stephens1986].
+Such paradigms probe the perceived opportunity cost of time, which has been hypothesized to underlie the evaluation of behavioral costs [@Kurzban2013].
 Specifically, foragers must decide whether to spend their limited time by harvesting their currently available resource or by seeking out more profitable (or less costly) alternatives.
@@
 whether to accept your first job offer or wait for new potential ones).
-Here we focus on this latter type of foraging, traditionally called prey foraging (Krebs et al., 1977), as it provides a means to examine how choices to accept or reject individual prospects are influenced by contextual knowledge about other potentially obtainable alternatives in the same environment.
-
-	Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionarily conserved choice behaviors (Hayden, 2018; Mobbs et al., 2018), and offers a number of desirable qualities to address our question.
-First, it allows for the estimation of optimal, reward maximizing choice patterns on the basis of the opportunity cost of time (Charnov, 1976; Krebs et al., 1977).
-The opportunity cost depends on the richness of the environment, which can be experimentally manipulated by balancing the amount of time it takes to harvest an offer (handling time) versus to search for new ones (travel time).
+Here we focus on this latter type of foraging, traditionally called prey foraging [@Krebs1977], as it provides a means to examine how choices to accept or reject individual prospects are influenced by contextual knowledge about other potentially obtainable alternatives in the same environment.
+
+  Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionarily conserved choice behaviors [@Hayden2018; @Mobbs2018], and offers a number of desirable qualities to address our question.
+First, it allows for the estimation of optimal, reward maximizing choice patterns on the basis of the opportunity cost of time [@Charnov1976; @Krebs1977].
+The opportunity cost depends on the richness of the environment, which can be experimentally manipulated by balancing the amount of time it takes to harvest an offer (**handling time**) versus to search for new ones (**travel time**).
 We can then interpret observed deviations from such optimal behavior, and examine how foraging behavior changes when the handling time is filled with cognitive effort or physical effort in comparison with unfilled delay (thus disentangling effort from delay duration).
@@
 Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that are adjusted once individuals experience different forms of behavioral costs.
-Foraging rests on an abundant modeling history that provides computational tools to formalize relevant decision variables (Stephens & Krebs, 1986).
+Foraging rests on an abundant modeling history that provides computational tools to formalize relevant decision variables [@Stephens1986].
 
@@
 Experiment 2 used a within-subject design in which individuals foraged for varying forms of demand in addition to varying reward magnitudes.
-We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions (Inzlicht et al., 2018).
+We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions [@Inzlicht2018].
 First, we examined whether the discounting effects consistently observed in multi-alternative economic choice paradigms persisted when these options were presented serially, and whether the resulting foraging patterns depended on the demands imposed to obtain rewards.
@@
 These results expand our understanding of the attractiveness of effort, suggesting potential reward-independent factors that could be leveraged to motivate effort engagement in diverse, everyday scenarios.
-
------------------------------------
-
-  Evaluating whether to pursue a desirable outcome often requires assessing the demands required for obtaining it.
-In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017 ;@Westbrook2015; @Frederick2002; Walton2006].
-Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2010; @Kool2018; @Treadway2009; @Westbrook2013].
-However, people often change their attitudes towards exerting effort in everyday decisions, resulting in pursual of effortful avenues instead.
-Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcome, whereby exerting effort boosts the perceived value of its outcomes [@HernandezLallement2014; @Kacelnik2002; @Mochon2012], and positive outcomes imbue value into their preceding effortful behavior [i.e.
-learned industriousness; @Eisenberger1992].
-Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs [@Inzlicht2018].
-Understanding these intrinsic qualities could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
-
-  What is often missing from existing accounts is the common case of choosing among types of behavioral demands.
-Studies have traditionally compared the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @Kool2010; @Westbrook2013].
-Although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across types of demands [@Arulpragasam2018; @Biaaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and discount rates do not always correlate across cost domains [@Seaman2018; @Westbrook2013].
-However, sporadic preferences for effort could arise from the availability of other types of demands in the same choice environment—in other words, from its context [@Kool2018].
-For example, exerting high effort for a reward might be aversive, but the same level of work might become valuable when compared to the boredom of passive waiting (e.g.
-taking the cumbersome way home rather than waiting for a delayed train, even if the resulting time of arrival is the same).
-Conversely, even though people tend to donate more to charitable events that require them to perform effortful activities (i.e.
-the martyrdom effect), they are also less likely to engage in such events once an easier alternative to raise funds becomes available [@Olivola2013].
-Recent work has proposed that the subjective costs produced by delays and cognitive effort is modulated by the possibility of missing out on better concurrent alternatives, namely the opportunity cost of time [OC; @Fawcett2012; @Kurzban2013; @Otto2019].
-This evidence sets the stage for examining what people would actually select when given the option for multiple types of demands, including the mostly unexplored question of deciding between cognitive and physical effort [@Inzlicht2018; @Kool2018].
-
-  Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead [@Stephens2019].
-Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionary choice behaviors [@Hayden2018; @Mobbs2018], and offers a number of desirable qualities.
-First, it allows for the estimation of optimal, reward maximizing choice patterns based on the opportunity cost of time [@Charnov1976; @Krebs1977].
-We can interpret observed deviations in acceptance rates from such optimal behavior in addition to comparing them among demands.
-Second, the sequential nature of foraging allows individuals to emphasize different elements of the decision context.
-For example, the cost (or value) of effort and delay could globally depend on the availability of alternative demands (as suggested above), impacting the perceived opportunity cost of time.
-Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that are adjusted once individuals experience different forms of behavioral costs.
-Foraging rests on an abundant modeling history that can help to computationally capture such emphases [@Stephens2019].
-
-  In this study, we tested the hypothesis that preferences would vary depending on whether individuals face a single or multiple types of behavioral demands (i.e.
-cognitive effort, physical effort, and delay).
-We explored this question in two foraging experiments: a between-subjects design in which participants foraged for rewards while performing a single demand, and a within-subjects extension where individuals foraged for demands in addition to rewards.
-We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions [@Inzlicht2018].
-First, the existence of a well-defined optimal choice strategy helped us identify when demands boost the value of rewards (i.e.
-overharvesting poor offers).
-Second, increasing the level of exposure to types of demands across experiments allowed us to asses whether their cost was intrinsic or relative.
-Finally, confronting participants with both mental and physical effort let us probe whether these preferences were domain general or task-specific, and in the case of the latter, isolate factors that influenced preferences beyond the often-cited associative relationship between effort and outcome.
-
-  Our results provided mixed support for our pre-registered hypotheses, which are detailed in https://osf.io/2rsgm/.
-Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment or whether they faced a single or intermixed demands.
-When faced with a single type of demand, people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups under-accepted, partially matching our predictions and highlighting that cognitive effort can add value to outcomes.
-However, against our expectations, we found that a similar preference for cognitive effort disappeared over time as decision makers foraged for types of demands in addition to rewards.
-Computational modeling suggested that the normative predictions of traditional foraging models were insufficient to explain our results.
-Instead, we found that demands imposed a bias on the estimation of the opportunity cost of time, which converged over time if individuals were exposed to interleaving types of demands.
-We hypothesize that this bias arises from modulations of subjective time.
-For instance, cognitive effort could have become appealing by virtue of compressing the perceived trial time, a perception that could be recalibrated with exposure to alternative demands.
-The construal of such shorter experienced durations could be due to the ongoing recruitment of working memory (e.g.
-preventing individuals from estimating the elapsed time), or because of the discrete nature of the cognitive task, which allowed individuals to count instead of thinking about time (versus a continuous configuration of the physical and wait tasks).
-These results expand our understanding of the attractiveness of effort, bringing forth outcome-independent features that can be leveraged to motivate effort engagement in diverse everyday scenarios.
 

### 2021-03-16 Cost_manuscript.Rmd
ref fix

@@
   Evaluating whether to pursue a desirable outcome often entails assessing the demands required for obtaining it.
-In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017 ;@Westbrook2015; @Frederick2002; Walton2006].
+In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017; @Westbrook2015; @Frederick2002; @Walton2006].
 Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2010; @Kool2018; @Treadway2009; @Westbrook2013].
@@
 
-Recent work has proposed that the subjective costs produced by delays and cognitive effort are modulated by the possibility of missing out on better concurrent alternatives, implying that decision makers track the **opportunity cost of time** [OC; @Fawcett2012; @Kurzban2013; @Otto2019].
+  Recent work has proposed that the subjective costs produced by delays and cognitive effort are modulated by the possibility of missing out on better concurrent alternatives, implying that decision makers track the *opportunity cost of time* [OC; @Fawcett2012; @Kurzban2013; @Otto2019].
 Preferences for effortful courses of action could therefore arise from the presence of other types of demands and opportunities in the same choice environment [@Kool2018].
@@
   Standard models in neuroeconomics and behavioral economics cannot readily address this possibility.
-The effects on valuation of different types of effort or delay have traditionally been formalized with discounting functions that capture how much less appealing a reward becomes as a function of the associated amount of effort or delay [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @Klein-Flugge2015; @Kool2010; @Westbrook2013].
+The effects on valuation of different types of effort or delay have traditionally been formalized with discounting functions that capture how much less appealing a reward becomes as a function of the associated amount of effort or delay [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @kleinflugge2015; @Kool2010; @Westbrook2013].
 An advantage of relying on these standardized functions is that they can circumvent a key confound when comparing effort and delay, namely that increasingly effortful tasks also tend to take longer to perform.
-However, although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across types of demands [@Arulpragasam2018; @Białaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and the degree to which discount rates correlate across cost domains [@Seaman2018; @Westbrook2013].
+However, although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across types of demands [@Arulpragasam2018; @Biaaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and the degree to which discount rates correlate across cost domains [@Seaman2018; @Westbrook2013].
 Further, this approach does not directly probe which type of demand people would prefer if given the option, and constrains the understanding of behavioral demands to one in which such demands are bound to reduce the value of prospects.
@@
 First, it allows for the estimation of optimal, reward maximizing choice patterns on the basis of the opportunity cost of time [@Charnov1976; @Krebs1977].
-The opportunity cost depends on the richness of the environment, which can be experimentally manipulated by balancing the amount of time it takes to harvest an offer (**handling time**) versus to search for new ones (**travel time**).
+The opportunity cost depends on the richness of the environment, which can be experimentally manipulated by balancing the amount of time it takes to harvest an offer (*handling time*) versus to search for new ones (*travel time*).
 We can then interpret observed deviations from such optimal behavior, and examine how foraging behavior changes when the handling time is filled with cognitive effort or physical effort in comparison with unfilled delay (thus disentangling effort from delay duration).

### 2021-03-16 Cost_manuscript.Rmd
edited up to operationalization of cost

@@
 In two experiments, independent sets of participants collected rewards that required equivalent periods of cognitive effort, physical effort, or unfilled delay.
-Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial (between-subjects, n=21 per condition), or varied across trials (within-subjects, n=48).When participants faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
+Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial (between-subjects, n = 21 per condition), or varied across trials (within-subjects, n = 48).
+When participants faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
 We theorized that if cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards.
@@
 
-## Experiment 1: Between-subjects comparison of costs
+## Experiment 1: Between-subject manipulation of subjective costs during foraging
 
@@
 
-  Both between- and within-subject experiments were pregeristered with the Open Science Framework (https://osf.io/2rsgm/registrations).
+  The study was preregistered with the Open Science Framework (https://osf.io/2rsgm/registrations).
 All experimental procedures were approved by the Boston University Institutional Review Board, and written consent was acquired for all participants.
-For the between-subject experiment, we recruited individuals until a desired number of 84 eligible participants was achieved (58 Female, median age = 21, range = 18 - 31; number excluded before reaching goal = 8).
-The sample size was determined by means of power analysis (ANOVA), using a significance level of 0.05, power of 0.8, an effect size of f = 0.45 (calculated from a pilot study), and three groups (one for each cost type).
+For Experiment 1, we recruited individuals until a desired number of 84 eligible participants was achieved (58 Female, median age = 21, range = 18 - 31; number excluded before reaching goal = 8).
+The sample size was determined by means of power analysis (ANOVA), using a significance level of 0.05, power of 0.8, an effect size of f = 0.45 (estimated from a pilot study), and three groups (one for each cost type).
 The resulting per-group sample was 20, which we increased to 21 in order to match three possible block orders.
@@
 
-We excluded participant datasets based on four preregistered criteria: 1) Consent: If they withdrew their participation; 2) Inattentiveness: a catch trial was placed at the end of each experimental block, asking participants to press a key within 3 seconds (time requirement based on pilot study response times).
+  Participant data sets could be excluded based on any of the following preregistered criteria: 1) Consent: If they withdrew their participation; 2) Inattentiveness: a catch trial was placed at the end of each experimental block, asking participants to press a key within 3 seconds (time requirement based on pilot study response times).
 A participant who failed two or more of these checks was excluded and replaced.
@@
   All experimental tasks were implemented using PsychoPy 2 [v1.85.1, @Peirce2019] on a Macbook Pro laptop.
-In this task, participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay (Figure 1).
+In this task, participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay (Fig.
+1A).
 Their goal was to maximize their gains within a fixed amount of time.
 On each trial a monetary offer was displayed for 2 s, and participants had the opportunity to expend time and/or effort during the handling time in order to earn it.
-Upon completion of a trial participants saw a 2 s window displaying the reward obtained, which was followed by a travel time to the next offer.
+Upon completion of a trial, participants saw a 2 s window displaying the reward obtained, which was followed by a travel time to the next offer.
 Alternatively, the participant could quit at any point during the handling time by pressing the spacebar on the computer, and immediately start traveling.
@@
   Each participant was assigned to one of three types of costs (cognitive effort, physical effort, or delay), and a fourth group of equal size faced an effortless physical task that involved minimal gripping.
+This latter condition was added to discard the possibility that any differences in acceptances between effort and delay were driven by engagement alone.
 Each group was unaware that other cost conditions existed.
-Participants exerted physical effort by maintaining grip on a handheld dynamometer (Biopac Systems, United States) using their dominant hand.
+Participants exerted physical effort by gripping a handheld dynamometer (Biopac Systems, United States) using their dominant hand.
 Gripping requirements were calibrated at 20% of maximum voluntary contraction (MVC, acquired at the beginning of the session).
 Cognitive effort entailed switching among Stroop, dot motion coherence, and flanker tasks.
-In Stroop, one of three color names was displayed on the screen (red, blue or green), with a font color that was either congruent (e.g.
-word red painted in red) or incongruent (e.g.
-word red painted in blue).
-Participants had to select the color of the font, not the word displayed (i.e.
-they had to suppress their tendency to read the word).
-For motion coherence, 100 solid white dots moved on the screen.
-A fraction of these dots moved cohesively to the left or right, while the rest moved in random directions (coherence could be either 30% or 40%, uniformly sampled).
-Participants had to respond with the direction of the cohesive set of dots.
-In flanker, rows of arrowheads pointed either to the left or the right (maximum of 3 rows, 3 to 13 arrowheads per row).
+This type of task switching is demonstrably effortful (Kool et al., 2010).
+In the Stroop task, one of three color names was displayed on the screen (red, blue or green), with a font color that was either congruent (e.g.
+the word red presented in red) or incongruent (e.g.
+the word red presented in blue).
+Participants had to select the color of the font (i.e., they had to suppress their tendency to read the word).
+For the motion coherence task, 100 solid white dots moved on the screen.
+A fraction of these dots moved coherently to the left or right, while the rest moved in random directions (coherence could be either 30% or 40%, uniformly sampled).
+Participants had to respond with the direction of the coherent movement.
+In the flanker task, rows of arrowheads pointed either to the left or the right (maximum of 3 rows, 3 to 13 arrowheads per row).
 Participants responded with the direction of the center arrowhead, which could point in the same or opposite direction from its neighbors.
-These tasks were configured so that responses always involved a left or right key press (e.g.
+The tasks were configured so that responses always involved a left or right key press (e.g.
 for Stroop, two colored circles were presented at each side of the screen).
 During the handling time, cognitive tasks and their configurations were randomly sampled, and were presented for 1 s followed by a 1 s inter-stimulus interval.
-Participants were asked to respond within each task’s presentation time.
+Participants were asked to respond within each task’s presentation time (i.e., there was a 1 s response deadline).
 Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive tasks of each kind.
@@
 
-  There were three block types, in which handling times of 2, 10, or 14 seconds were paired with travel times of 14, 6, and 2 seconds, respectively (note that all combinations add up to 16 seconds).
+  There were three block types, in which handling times of 2, 10, or 14 seconds were paired with travel times of 14, 6, and 2 seconds, respectively.
+Note that all combinations add up to 16 seconds, meaning that accepted trials took the same amount of time in all conditions, but rejected ones were shorter in environments where the traveling time was shorter.
 Timing parameters were held constant within each 7-min block.
-Each of these blocks was experienced in a pseudo-randomized order, and repeated in the same order after a short break in order to probe choice stability (total session length = 42 minutes).
+Each block type was presented twice in pseudo-randomized order (total session length = 42 minutes).
 Reward amounts varied uniformly per trial (4, 8, or 20 cents), with the constraint that every reward was presented twice every six trials.
@@
 Timing information was disclosed at the beginning of each block, and rewards displayed during a 2 s offer window before each trial began.
-Participants received training prior to the experimental session, and were told about all possible environmental statistics in order to preclude biases due to experience-dependent learning [@Dundon2020; @Garrett2020].
+Participants received training prior to the experimental session and were told about all possible timing conditions and reward amounts in order to preclude biases due to experience-dependent learning [@Dundon2020; @Garrett2020].
 
@@
 Participants could skip unfavorable trials and immediately start traveling to a potentially better offer.
-In the between-subject experiment, cost was fixed per participant and handling time varied per block.
+In Experiment 1, cost was fixed per participant and handling time varied per block.
 In the within-subject version, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
@@
 
-  Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time incurred in obtaining it, given by the richness of the environment [@Charnov1976; @Stephens2019].
-In this study, the richness of the environment was manipulated by the length of the handling and travel times, whereby shorter travel times produced richer environments.
-Since time combinations were fixed per block, we calculated each block’s optimal accept/reject strategy by computing all decision strategies according to the following equation:
+  Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time to be incurred in obtaining it, which depends on the richness of the environment [@Charnov1976; @Stephens1986].
+In this study, the richness of the environment was manipulated by the length of the handling and travel times, where shorter travel times produced richer environments.
+Since time combinations were fixed per block, we calculated each block’s optimal accept/reject strategy by computing the expected reward rate (g(*)) from all decision strategies according to the following equation:
 
@@
 
-  where *R* and *p* are the reward and acceptance probability of offer i, respectively, *H* is the handling time for the block, $Time_{offer/reward}$ are the windows when offers and rewards were disclosed, and *T* its associated travel time.
+  where *R* and *p* are the reward and acceptance probability of offer *i*, respectively, *H* is the handling time for the block, *T* its associated travel time, $\text{Time}_\text{offer}$ is the duration of the offer window, and $\text{Time}_\text{reward}$ is the duration of the window displaying the reward earned (only presented for completed trials).
 This gave us the total reward per second attainable in each block as a function of the acceptance threshold (i.e.
 the lowest amount accepted).
-Figure 2 shows possible earnings per second for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
+Since an ideal forager should always either accept or reject different categories of prey (Krebs et al., 1977), probabilities other than 0 and 1 are not considered.
+The resulting possible strategies were to accept only 20 cents, accept 8 and 20 cents, or accept everything.
+Fig.
+1B shows possible earnings per second for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
 For example, a participant in a 10 s handling block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate.
 Note that accepting every offer was often detrimental to participant earnings.
-Significant deviations from the optimal strategy can be understood as reflecting changes in subjective OC.
-This approach allowed us to test if certain demands boosted the value of offers, expressed as a subjective OC that fell below the optimal rate.
-
-```{r Optimal plot (Fig.
-2), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
-the smallest amount accepted) for each handling time.
-Circles denote the reward-maximizing threshold for each block, which is described in the table.
-Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers."}
-
-include_graphics("./Images/FIG1_task_b.png")
-```
 
@@
 The resulting sample size was 45, which we increased to 48 in order to balance the potential order of blocks.
-We excluded participants using the same criteria as in the between-subject experiment.
+We excluded participants using the same criteria as in Experiment 1.
 
@@
 Unlike the previous experiment, participants could express their decision to quit during the offer window (instead of during the handling time).
-Participants trained in each type of demand until they reached the same criteria as in the between-subject experiment.
+Participants trained in each type of demand until they reached the same criteria as in Experiment 1.
 
@@
 
-  The analytical pipeline was mostly preserved from the between-subject experiment.
+  The analytical pipeline was mostly preserved from Experiment 1.
 We first ran tests to determine whether decision makers integrated reward information.
@@
 The reduction in acceptances was not driven by a performance decline, forced travels were not significantly different in the first and second half of the experiment (paired permutation with 5000 iterations, *p* `r report_p(failDiffs_wth$Pval)`).
-Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from the between-subject experiment (Figure 4A).
+Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from Experiment 1 (Figure 4A).
 Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Figure 9, top-right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).

### 2021-03-17 Cost_manuscript.Rmd
Exp 1 revised per dissertation

@@
 
-## Experiment 1: Between-subject manipulation of subjective costs during foraging
+## Experiment 1: Between-subject Manipulation of Subjective Costs During Foraging
 
@@
 To address the prediction that participants would be more likely to accept higher reward and shorter handling time trials, we fit a mixed-effects logistic regression to predict trial-wise acceptances [using the lme4 package, @Bates2015], giving a random intercept to each subject to account for biases in participant behavior.
-We included regressors for handling time and reward, as well as two covariates that probed the influence of recent history on choices.
-The first was an autoregressive regressor containing the number of consecutive offer misses prior to a given trial (misses could be due to quits or forced travels).
+We included continuous regressors for handling time and reward, as well as two covariates that probed the influence of recent history on choices.
+The first was an autoregressive regressor containing the number of consecutive unobtained offers prior to a given trial (unobtained offers could be due to quits or forced travels).
 The second regressor tracked the sum of the previous *n* offers.
@@
 
-  Our foraging task was configured such that over and under accepting were detrimental to total earnings.
+  Our foraging task was configured such that over- and under-accepting were detrimental to total earnings.
 To confirm this, we fit a general linear model with constant, linear, and quadratic terms to estimate the correspondence between proportion of trials completed (independent variable) and total earnings (dependent variable).
 A significant quadratic coefficient thus would signal that the task statistics operated as expected.
-Next, to determine the optimality of each group’s decisions, we performed two-sided one-sample t-tests to see if the proportion of acceptances for each time/reward combination was significantly different from the optimal rate (see Operationalization of Cost).
-This resulted in 36 independent tests (3 rewards amounts, 3 handling/travel time combinations, and 4 groups), so we corrected for multiple comparisons using False Discovery Rate [FDR, @Benjamini2001].
-
-  Next, we compared preferences among cost conditions.
+Next, to determine the optimality of the group’s decisions, we examined whether each cost type produced a bias to over or under-accept offers 4 and 8 cents (assuming that 20 cents were always be accepted, given our design).
+The reward-maximizing strategy was to always reject these offers for handling times of 14 s, reject 4 cents and accept 8 cents for 10 s, and accept both for 2 s, yielding a combined optimal proportion of acceptances of 50% (see Operationalization of Costs for details).
+We performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
+Therefore, a significant difference indicated that participants either over- or under-accepted rewards.
+This approach was adapted from the analysis preregistered for Experiment 2, as we found it better suited to the question than the original formulation.
+
+  Next, we compared acceptance rates across cost conditions.
 We first performed a one-way ANOVA on the proportion of trials accepted using group as a factor.
 We then compared the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests).
-On each of 5000 permutation iterations, the group assignment was randomly shuffled without replacement, and the difference in mean acceptance rates across iterations created a putative null distribution.
+For each test, on each of 5000 permutation iterations, the group assignment was randomly shuffled without replacement, and the difference in mean acceptance rates across iterations created a putative null distribution.
 The unpermuted group mean difference was then evaluated against this permuted distribution.
 The same approach was used for total earnings.
-This gave us an initial glimpse on the potential differences in cost among conditions.
 
@@
 We used both AIC and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
-The regression with each combination of predictors was fitted in a forward order: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount (added to the preregistered comparison); 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
+The regressors included in each model were: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount; 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
 We predicted that model 6 (the a priori setup) would have the lowest AIC and BIC.
@@
 
-  Next, we examined whether participants were consistent and stable in their choices.
+  Reward-maximizing prey foragers should either accept or reject offers based on their profitability relative to their alternatives [@Krebs1977; @Stephens1986].
+However, decision makers often curtail persistence based on continuous reevaluation of delayed prospects or lapses in self control [@Ainslie1975; @McGuire2012; @McGuire2015; @Mischel1970].
+Therefore, we examined whether participants were consistent (not quitting a trial after it was originally accepted) and stable (similar acceptance rates over time) in their choices.
 For consistency, we visually examined survival curves indicating at what point during the handling time participants quit a trial (censored points included trial completions and forced travels), in addition to quitting time distributions.
-We interrogated stability by computing each participant’s total proportion of acceptances pre- and post-midpoint for every block type, comparing the mean proportion of acceptances using paired permutations (5000 iterations).
+We interrogated stability by computing each participant’s total proportion of acceptances in the first and second half of the experiment for every block type, comparing the mean proportion of acceptances using paired permutations (5000 iterations).
 We then tested whether the observed differences in costs were still present on each half of the experiment by applying winning model from the mixed-effects logistic comparison to each half separately.
@@
 ### *Results*
-#### **Between-subjects: Tests of whether decision makers integrate delay and reward information**
+#### **Between-subjects: Decision Makers Integrate Delay and Reward Information**
 
@@
                          text = element_text(size = 22))
+
+# Proportion of performance-based forced travels per subject and cost type
+# move to 16.2.1.
+propFails <- dataBtw %>% 
+  filter(Cost != "Wait") %>% 
+  group_by(SubjID, Cost) %>% 
+  summarise(propFails = mean(rawChoice == 2)) %>%
+  group_by(Cost) %>% 
+  summarise(meanFT = mean(propFails),
+            sdFT = sd(propFails))
 ```
@@
 
-  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) chose their preferred strategy to maximize rewards in fully-disclosed foraging environments of variable richness.
+  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) chose their preferred strategy to maximize rewards in foraging environments of varying richness.
 Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time).
 We hypothesized 1) that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that 2) participants confronted with effortful demands would be more likely to accept trials than those faced with passive delay, regardless of handling time and reward amount.
-
-  We performed a mixed effects logistic regression to address the first hypothesis.
-Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (entering the handling period) and completions (successfully obtaining a reward).
+The second hypothesis was based on the traditional idea that rewarded work should become appealing [@Eisenberger1992; @Inzlicht2018].
+
+  We performed a mixed effects logistic regression to address the first hypothesis, pooling across the four conditions.
+Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (not explicitly quitting a trial during the handling period) and completions (successfully obtaining a reward).
+Even so, the proportion of forced travels was low for cognitive effort (`r round(propFails[2, 2]$meanFT, digits = 2)` across participants) and 0 for the physical group.
 In line with our predictions, larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_btw["Offer", "Estimate"]`, SE = `r historyCoeffs_btw["Offer", "Std.
@@
 Error"]`, *p* `r report_p(historyCoeffs_btw["recentOffers", "Pr(>|z|)"])`).
-The reduction in acceptances from recent misses was driven by the wait group (removing this group from the model yielded a *p* > 0.1), likely because this group accepted the least amount of offers.
+The counterintuitive reduction in acceptances following consecutive unobtained rewards was driven by the wait group (removing this group from the model yielded a *p* > 0.1), likely because this group accepted the fewest offers.
 Comparing likelihood fits among lengths of offer history (e.g.
 sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r round(AIC(historySize_btw[[historyIndex_btw]]), digits = 2)`), which matched the offer presentation rotation (see Methods).
-
-#### **Between-subjects: Comparisons among the four delay and effort conditions**
 
@@
 
-# Proportion of performance-based forced travels per subject and cost type
-# move to 16.2.1.
-propFails <- dataBtw %>% 
-  filter(Cost != "Wait") %>% 
-  group_by(SubjID, Cost) %>% 
-  summarise(propFails = mean(rawChoice == 2)) %>%
-  group_by(Cost) %>% 
-  summarise(meanFT = mean(propFails),
-            sdFT = sd(propFails))
-
-## MAYBE BETTER WAY TO DO PAIRWISE COMPARISONS, USING VECTORIZE FROM BELOW
-# OCanova$perms <- summaryOC_btw$all %>%
-#   select(Cost, Gamma) %>%
-#   plyr::dlply("Cost", identity) %>%
-#   do.call(cbind, .) %>%
-#   select_if(is.numeric) %>%
-#   rename(Physical = Physical.Gamma,
-#          Cognitive = Cognitive.Gamma,
-#          Wait = Wait.Gamma,
-#          Easy = Easy.Gamma) %>%
-#   outer(., ., FUN = Vectorize(permute), simple = T)
-# diag(OCanova$perms) <- 1
-
 ```
@@
 
-  The next set of analyses examined the hypothesis that effort group would uniformly accept more trials.
-Figure 3 (left) shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings (middle).
-One-way ANOVAs showed that differences among groups were significant both for overall acceptance rates (F(`r propAov[[1]]$Df[1]`, `r propAov[[1]]$Df[2]`) = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F(`r earnAov[[1]]$Df[1]`, `r earnAov[[1]]$Df[2]`) = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
+  The next set of analyses examined the hypothesis that both cognitive effort and physical effort groups would uniformly accept more trials than passive delay and easy groups.
+Fig.
+2 (left) shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings (middle).
+One-way ANOVAs showed that differences among groups were significant both for overall proportion accepted (F(`r propAov[[1]]$Df[1]`, `r propAov[[1]]$Df[2]`) = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F(`r earnAov[[1]]$Df[1]`, `r earnAov[[1]]$Df[2]`) = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
 Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive")$mProp`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdProp`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical")$mProp`, SD = `r filter(overallSumms, Cost == "Physical")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mProp`, SD = `r filter(overallSumms, Cost == "Wait")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait")$cohenD`).
@@
 In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
-The percentage of forced travels for cognitive effort was `r round(propFails[2, 2] * 100, digits = 2)`% across participants, and 0% for either physical or easy conditions, making performance an unlikely explanation for the observed differences in choice.
+Considering the low proportion of forced travels, performance was an unlikely explanation for the observed differences in choice.
 
@@
 The foraging task was configured so that there was a single reward-maximizing strategy per block type (see Operationalization of Cost in Methods), and participants were warned that accepting everything would not maximize their gains.
-Accordingly, participants who over- or under-accepted earned the least (Figure 3, right; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+Accordingly, participants who over- or under-accepted earned the least (Fig.
+2, right; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 We performed group-level chi-squared tests of proportions to examine whether each cost biased decision makers to under- or over-accept 4 and 8 cent offers, which together should have been accepted 50% of the time.
-We found a significant over-acceptance of these trials by the cognitive effort group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Cognitive", "pval"])`), but under-acceptances by the physical (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) and wait (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) groups (no significant difference for the Easy group).
-Together, these findings show that even though participants did not always perform optimally, they adequately integrated the statistics of the environment as they tracked their recent experience.
-Further, they suggest that cognitive effort can boost the value of an offer, as reflected by higher acceptances at the expense of earnings.
+We found a significant over-acceptance of these trials by the cognitive effort group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Cognitive", "pval"])`), but under-acceptances by the physical (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) and wait (proportion accepted = `r round(optimalProp_cost["Wait", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Wait", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Wait", "pval"])`) groups (no significant difference for the Easy group).
+Together, these findings show that even though participants did not always perform optimally, they responded appropriately to the statistics of the environment in each timing condition.
+Further, they provide evidence that cognitive effort can boost the value of an offer, as reflected by higher acceptances at the expense of earnings.
 
@@
   We next probed whether these results held uniformly across all parameter combinations.
-Figure 4A shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and cost, with optimal acceptance rates depicted by the gray circles.
+Fig.
+3A shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and cost, with optimal acceptance rates depicted by the gray circles.
 Qualitatively, the figure confirms two important predictions.
-First, participants adapted to the richness of the each timing block, gravitating towards optimality regardless of the cost they faced.
+First, participants adapted to the richness of each timing block, gravitating towards optimality regardless of the cost they faced.
 Second, differences in cost were consistent across blocks, and acceptances were uniformly highest for the cognitive effort group.
@@
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_btw$Wait)[[10]]["Offer", "Pr(>|z|)"])`).
-Comparisons among all conditions are shown on Figure 4B.
+Comparisons among all conditions are shown on Fig.
+3B.
 The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) and wait groups ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.
 
-  These observations could not be better explained by simpler or more complex regression models.
-Figure 4C shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details).
+  These observations could not be more easily explained by simpler or more complex regression models.
+Fig.
+3C shows AIC and BIC values for models of increasing complexity, starting with an intercept-only configuration (see Methods for details).
 Here we focus on AIC, as both metrics yielded comparable results.
-As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model $R^2$ = `r round(mixLogis_compare_btw$AllMainRsq, digits = 2)`), as well as the model with main effects for handling time and reward amount (AIC~a-priori~ = `r filter(ME_evals$abicLogis_compare, Model == "AllMain")$AIC`, AIC~handling/reward~ = `r filter(ME_evals$abicLogis_compare, Model == "HR")$AIC`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r round(ME_evals$HRvMain$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
+As predicted, the a priori model with all main effects performed better than those relying on a single parameter (a priori model pseudo $R^2$ = `r round(mixLogis_compare_btw$AllMainRsq, digits = 2)`), as well as the model with only main effects for handling time and reward amount (AIC~a-priori~ = `r filter(ME_evals$abicLogis_compare, Model == "AllMain")$AIC`, AIC~handling/reward~ = `r filter(ME_evals$abicLogis_compare, Model == "HR")$AIC`, $\chi^2$(`r ME_evals$HRvMain[[7]][2]`) = `r round(ME_evals$HRvMain$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$HRvMain[[8]][2])`).
+
   However, against our expectations, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r filter(ME_evals$abicLogis_compare, Model == "HR_interaction")$AIC`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r round(ME_evals$MainvHRint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r filter(ME_evals$abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r round(ME_evals$MainvAllint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
-These improvements were driven by the fact that differences in offer acceptances among costs were never present for 20 cents (all *p* values for interactions containing offer amount < 0.001).
-As the highest reward should always be accepted in prey foraging environments, we conclude that the most parsimonious explanation of choice behavior came from the a priori model containing all main effects.
+Even so, neither of these models offered further interpretable insights on the observed differences across costs, so we restrict our focus to the a priori model containing all main effects.
 These results further support the hypotheses that handling and reward amounts were similarly integrated across groups, and that the absolute rate of acceptances was affected by the demand faced.
@@
 
-#### **Between-subjects: Consistency and stability**
+#### **Between-subjects: Consistency and Stability**
 
@@
 
-  Next, we tested the hypothesis that foragers would display consistent and stable choices.
+  Next, we tested the hypothesis that foragers would exhibit within-trial consistency and across-trial stability in their choices.
 Participants were deemed consistent if they did not quit after engaging in a trial.
-To examine this, we plotted survival curves of trial quits across all participants (Figure 5, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
+To examine this, we plotted survival curves of trial quits across all participants (Fig.
+4, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
 These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (proportion of quits after 1 s = `r  handlingQuits_btw$r`).
@@
 This resulted in some individuals opting to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code).
-Plotting the quitting time distributions across blocks for the first second of the handling time (ECDFs on Figure 5, top-right) showed that participants in the wait and cognitive groups responded faster as the experiment progressed.
-These response time observations suggested clarity in participant choices
+Plotting the quitting time distributions across blocks for the first second of the handling time (ECDFs on Fig.
+4, top-right) showed that participants in the wait and cognitive groups responded faster as the experiment progressed.
+These response time observations suggested clarity in participant choices.
 
@@
   Stability was defined as a persistence in acceptance patterns throughout the experimental session.
-The scatter plot on Figure 5 (bottom-left) shows the overall proportion accepted by each participant before and after the mid-point break.
+The scatter plot on Fig.
+4 (bottom-left) shows the overall proportion accepted by each participant before and after the midpoint of the session.
 Paired permutations showed no differences in acceptances for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
-Figure 6 (left) shows that the reduction acceptances in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009].
-We then replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Figure 6, right).
+Fig.
+5 (left) shows that the reduction in acceptances in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009].
+We then replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Fig.
+5, right).
 Together, the consistency and stability displayed by participants suggest that decision makers had a clear representation of the environment.
@@
 
-## Experiment 2: Within-subjects comparison of costs
+## Experiment 2: Within-subjects Comparison of Costs
+
+  Experiment 1 was a between-subjects examination of how cognitive effort, physical effort, and delay would impact prey foraging behavior, and whether canonical discounting effects could be observed under this paradigm.
+Based on this behavioral baseline, Experiment 2 interrogated which type of demand decision makers would gravitate to when they were allowed to forage for types of demands in addition to rewards.
+This within-subjects version sought to answer how the presence of alternative avenues would impact the subjective costs of effort and delay, our overarching question.
+
 ### *Methods*

### 2021-03-18 Cost_manuscript.Rmd
almost done editing exp 2

@@
   We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36; number excluded before reaching goal = 6).
-Sample size was once again determined by means of a power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each condition).
+Sample size was once again determined by means of a power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each type of demand; see below for details).
 The resulting sample size was 45, which we increased to 48 in order to balance the potential order of blocks.
@@
 
-  The original between-subjects task was modified so that participants foraged for cost types in addition to rewards.
+  The original between-subjects task from Experiment 1 was modified so that participants foraged for cost types in addition to rewards.
 Every participant experienced all forms of cost (delay, physical effort, and cognitive effort).
@@
 keyboard press and handgrip).
-Block combinations (i.e.
-physical/wait and cognitive/wait) were experienced three times by each participant in 7-minute-long, interleaved blocks, thus matching the experiment’s length to the between-subject version.
+Each block combination (i.e.
+physical/wait and cognitive/wait) was experienced three times by each participant in 7-minute-long, interleaved blocks, for a total session duration of 42 minutes.
 Half of the participants experienced a block sequence that started with the physical block.
 Timing parameters were matched to the middle condition from Experiment 1 (i.e.
-10 s handling and 6 s travel), establishing a balance between acquiring enough observations per trial type and being able to compare results across experiments.
+10 s handling time and 6 s travel time).
 Participants were informed that this timing combination would be constant prior to beginning the experiment.
-Cost type combinations were disclosed at the beginning of each block, and reward/cost offers displayed before each trial begins (e.g.
+The upcoming effort type was disclosed at the beginning of each block, and reward/cost offers were displayed at the start of each trial (e.g.
 “8 cents for physical effort”).
 Unlike the previous experiment, participants could express their decision to quit during the offer window (instead of during the handling time).
-Participants trained in each type of demand until they reached the same criteria as in Experiment 1.
+Participants were trained in each type of demand until they reached the same criteria as in Experiment 1.
 
@@
 We then confirmed that the under- and over-acceptance were detrimental to total earnings by performing the same quadratic linear model explained above.
-To determine the optimality of the group’s decisions, we examined whether each cost type produced a bias to over or under-accept at 4 and 8 cents (assuming that 20 cents were always be accepted, given our design).
-The reward-maximizing strategy was to always reject 4 cents and accept 8 cents, yielding a combined optimal proportion of acceptances of 50% (see Operationalization of Costs for details).
-We performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
-Therefore, a significant difference indicated that participants either over or under accepted rewards.
-
-  To compare acceptances among cost conditions, we first computed the probability of accepting a trial with a mixed-effects logistic regression.
-The model included cost condition and reward amount as fixed main effects, and participant ID as a random intercept (handling time is not modeled, as participants experienced a single time combination).
+We tested the group’s optimality as before.
+We tested the group’s optimality as before.
+The optimal strategy was to reject 4 cent offers and accept 8 cent offers, yielding an ideal acceptance of 50% (not counting 20 cent offers, which should have always been accepted per our design).
+For these trials, we performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
+
+  To compare acceptances among cost conditions, we first estimated acceptance probabilities using a mixed-effects logistic regression.
+The model included cost condition and reward amount as fixed main effects, and participant as a random intercept (handling time was not modeled, as participants experienced a single time combination).
 Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
 We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions.
-We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity in a forward order: 1) intercept only; 2) cost only; 3) reward only; 4) cost and reward main effects (a priori model); and 5) adding a two-way interaction.
+We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity as follows: 1) intercept only; 2) cost only; 3) reward only; 4) cost and reward main effects (a priori model); and 5) adding a two-way interaction.
 We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
-Models with similar AIC were formally compared using the analysis-of-deviance approach from the between-subjects experiment.
-
-  Next we probed consistency and stability in people's choices.
-First, we qualitatively assessed the number of quits performed during during the handling time through a survival curve, and plotted the quit response time distribution as a function of block to examine choice consistency over time.
-Next, we computed the proportion of quits that were performed during the choice window versus during the handling time.
-We interpreted as confidence if a participant made at least 80% of their choices during the offer window.
+Models with similar AIC were formally compared using the analysis-of-deviance approach from Experiment 1.
+
+  Next, we probed within-trial consistency and across-trial stability in people’s choices.
+First, we visualized the number of quit responses during the handling time with a survival curve, and plotted the quit response time distribution as a function of block to examine choice consistency over time.
+Next, we computed the proportion of quits that occurred during the choice window versus during the handling time.
+Earlier quits were seen as signifying greater consistency.
 We then computed each participant’s total proportion of acceptances on the first two and last two blocks, and compared them using a paired permutation analysis (5000 iterations).
-We avoided the third and fourth block because their effort designation was counterbalanced across participants, which would have biased our estimates.
+This analysis did not include the third and fourth block because their effort designation was counterbalanced across participants.
 
 ### *Results*
-#### **Within-subjects: Tests of whether decision makers integrate reward information**
-
-  If the cost or value of a demand were intrinsic, the relative preferences displayed so far should have been robust to the ability to obtain the same rewards through different demands.
-We investigated this possibility by modifying the foraging task, such that every participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (fixed at 10 s handling and 6 s travel times, to allow for comparisons between experiments).
-We refer to observations from each block's wait trials by their effort pair (i.e.
-"Wait-C" for cognitive, and "Wait-P" for physical).
-We hypothesized that 1) reward decision patterns would match those of the previous experiment; and 2) that interleaving effort and delay would produce persistent preferences for wait trials.
+#### **Within-subjects: Decision Makers Integrate Reward Information**
+
+  In Experiment 2, we directly tested an individual’s preferences for cognitive effort, physical effort, and delay.
+We did by modifying the foraging task, such that every participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (fixed at 10 s handling and 6 s travel times, to allow for comparisons between experiments).
+We separately analyzed wait trials from the two block types, labeling the two sets of wait trials according to the type of effort with which they were paired (“Wait-C” for cognitive, and “Wait-P” for physical).
+We hypothesized that 1) reward decision patterns would match those of the previous experiment; and 2) interleaving effort and delay would produce persistent preferences for wait trials.
+The second hypothesis was based on the idea that people will gravitate to the easiest way to achieve their goals [@Hull1943; @Olivola2013].
 
@@
 
-  Analyses from the previous experiment were repurposed to examine cost differences within individuals.
-We started by testing the hypothesis that participants would successfully integrate the statistics of the environment.
+  We first tested the hypothesis that participants would successfully integrate the statistics of the environment.
 A mixed-effects logistic regression once again showed that larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_wth["Offer", "Estimate"]`, SE = `r historyCoeffs_wth["Offer", "Std.
@@
 Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]]), digits = 2)`).
-However, this time participants were unaffected by recent reward misses (*p* `r report_p(historyCoeffs_wth["recentTravels", "Pr(>|z|)"])`).
-As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 7A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+Unlike Experiment 1, participants were unaffected by the preceding number of consecutive unobtained rewards (*p* `r report_p(historyCoeffs_wth["recentTravels", "Pr(>|z|)"])`).
+As before, a linear model predicting earnings showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Fig.
+6A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were correctly accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
@@
 These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality.
-
-#### **Within-subjects: Comparisons among the four delay and effort conditions**
 
@@
   Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
-Even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 7B), differences among cost conditions were less evident.
+Even though the reward acceptance pattern at 10 s handling was similar to Experiment 1 (Fig.
+6B), differences among cost conditions were less evident.
 Moreover, these differences contradicted our predictions, as cognitive effort remained the least costly among demands.
 A mixed effects logistic regression confirmed once again that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main_wth$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main_wth$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Std.
-Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference was the higher likelihood to accept cognitive offers compared to physical ones (Figure 7C; $\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
-Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare_wth$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 7D).
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference across cost conditions was a higher likelihood to accept cognitive-effort offers than physical-effort offers (Fig.
+6C; $\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
+Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare_wth$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Fig.
+6D).
 An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][2]`) = `r round(mixLogis_compare_wth$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][2])`).
 However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][3]`) = `r round(mixLogis_compare_wth$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][3])`), albeit at the cost of interpretability due to choice fluctuations over time (see Consistency and Stability).
-These initial results defied our predictions, suggesting that the availability of alternative demands diminishes preferences among them (rather than inverting them from what was observed in experiment 1).
-
-#### **Consistency and stability**
+These initial results contradicted our predictions, suggesting that the availability of alternative demands diminishes preferences among them (rather than promoting wait trials as a way to earn the same reward amounts without the need to exert effort).
+
+#### **Within-subjects: Consistency and Stability**
 

### 2021-03-18 Cost_manuscript.Rmd
exp 2 done

@@
 4, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
-These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (proportion of quits after 1 s = `r  handlingQuits_btw$r`).
+These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (percentage of quits after 1 s = `r  handlingQuits_btw$r * 100`).
 Physical and easy groups showed slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
@@
 
-  Similar to the between-subject results, a survival analysis displayed that participants made most of their choices quickly within the offer window (Figure 8A).
+  Similar to the between-subject results, a survival analysis displayed that participants made most of their choices quickly within the offer window (Fig.
+7A).
 The median percentage of quits during the handling time was `r round(median(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 20)` participants quitting over 20% of trials during the handling time.
-Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Figure 8B).
-Once in the handling time, the overall percentage (**shift to percentage in exp 1**) of forced travels in the effortful trials was low for both cognitive (median = `r round(median(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (median = `r round(median(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
-Similar to the between-subjects experiment, these results suggest that decision makers were consistent in their adopted strategies, and were able to perform the tasks well.
+Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Fig.
+7B).
+Once in the handling time, the overall percentage of forced travels in the effortful trials was low for both cognitive (median = `r round(median(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (median = `r round(median(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
+Similar to that of Experiment 1, these results suggest that decision makers were consistent in their adopted strategies, and were able to perform the tasks well.
 
@@
 
-  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Figure 9).
-The reduction in acceptances was not driven by a performance decline, forced travels were not significantly different in the first and second half of the experiment (paired permutation with 5000 iterations, *p* `r report_p(failDiffs_wth$Pval)`).
-Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from Experiment 1 (Figure 4A).
-Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Figure 9, top-right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions (upper triangle).
-This fading preference for cognitive effort was observed regardless of which block participants experienced first, even though its magnitude appeared to be reduced for those who experienced the physical block first (Figure 9, bottom)
+  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Fig.
+8).
+The reduction in acceptances was not driven by a performance decline, as the proportion of forced travels was not significantly different between the first and second half of the experiment (paired permutation with 5000 iterations, *p* `r report_p(failDiffs_wth$Pval)`).
+Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from Experiment 1 (Fig.
+3A).
+Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Fig.
+8, top-right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with cognitive effort, physical effort, and both wait conditions (upper triangle).
+This fading preference for cognitive effort was observed regardless of which block participants experienced first, even though its magnitude appeared to be reduced for those who experienced the physical block first (Fig.
+8, bottom)
 

### 2021-03-18 Cost_manuscript.Rmd
exps and comp modeling sections done. just discussion and figs left

@@
 
-  We performed model comparisons to identify qualities that explained findings from both experiments.
-Based on the observed choice behavior, an adequate model had to meet seven criteria: 1) show deviations from optimality that were not simply due to overharvesting; 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions in the between-subjects experiment; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 5) initially match this preference for cognitive effort trials when foraging for demands and rewards; 6) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) preference ranks should be robust to block order effects, but the magnitude of the differences should be lower for those who started with the physical effort block.
-These conditions discarded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, sunk cost effects, or asymmetric learning of environmental richness (see Discussion).
+  We developed a computational model to identify cognitive operations that could explain the complex patterns observed in both experiments (e.g.
+learning, time estimation, etc.).
+We isolated four key aspects of the behavioral results that an adequate computational model should be able to capture: 1) show deviations in acceptance rates that involved both under- and over-harvesting of offers (e.g.
+Fig.
+3.3A); 2) keep track of recent offer history in order to evaluate the relative value of each offer; 3) persistently display higher acceptances for cognitive effort when faced with single behavioral costs (Experiment 1); and 4) initially match this preference for cognitive effort trials when foraging for demands and rewards (Experiment 2), which should decrease to a common rate across costs over time.
+These conditions excluded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, or asymmetric learning of environmental richness (see Discussion).
 
@@
   Model comparison was performed by calculating Bayes Information Criterion at the group level [integrated BIC or iBIC; @Huys2011; @Huys2012; @Kane2019].
-iBIC penalizes the likelihood of the data given model parameters $p(d | model)$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
+iBIC penalizes the likelihood of the data given model parameters $p(d | \text{model})$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
 
@@
 
-such that a trial’s reward $R_i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_i$, with high gammas promoting selectivity.
+such that the reward $R$ of trial $i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_i$, with high gammas promoting selectivity.
 We fit this and all subsequent models using a softmax function to predict the probability of accepting a given trial
@@
 
-gamma in this base model was computed as an individual's empirical earning rate by the time of each offer, with the free temperature parameter $\beta$ indexing decision noise.
-However, this base formulation lacked the flexibility needed to capture the dynamics observed in the within-subjects experiment.
+gamma in this base model was computed as an individual’s empirical earning rate by the time of each offer, with the free temperature parameter $\beta$ indexing decision noise.
+Differences among costs in Experiment 1 could then be due to the impact of each cost on decision noise, which could have also driven the gradual convergence of acceptance rates in Experiment 2.
+However, it is also possible that individuals updated the estimate of gamma at different rates when faced with different demands.
+Previous accounts have demonstrated the biases that can impact the learning of the opportunity cost [@Dundon2020; @Garrett2020].
 We therefore tested a second model that allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
@@
 
-where $A_i$ is an acceptance indicator (0 or 1), and $\tau_i$ the amount of time spent in the trial.
-Higher values of the learning rate $\alpha$ (ranging from 0 to 1) prioritized updating from the current trial’s earning rate (left side of the equation), weighed by the amount of time experienced in the past trial.
-This time was given by
+where $A_i$ is an acceptance indicator (0 or 1), and $\tau_i$ is the duration of the trial. The duration was given by
 
@@
 such that the handling time was counted only for accepted trials.
+Higher values of the learning rate $\alpha$ (ranging from 0 to 1) resulted in a larger update toward the current trial's earning rate weighted by its duration (first term in the equation).
 For this adaptive model, we fit the learning rate $\alpha$ and the initial value of $\gamma$ in addition to the temperature.
-These modifications allowed for the tracking of recent history that was part of our criteria, while maintaining the general structure of the base model
+These modifications allowed for the tracking of recent reward history, while maintaining the same decision rule
 
@@
 
-  A third model considered the possibility that each type of demand additively biased the estimate of $\gamma$.
-Such cost bias would be stable if a single demand was experienced, but recalibrated into a global estimate as decision makers faced different types of demands.
+where values of $\gamma$ were now updated on each trial $i$ according to Eq 3, rather than by the empirical earning rate.
+
+  Another possibility was that rather than impacting the learning rate, covert features specific to each type of demand additively biased the estimate of $\gamma$.
+Suchuniformly affected the way people perceived the opportunity cost bias would be of time.
+If so, biases could remain stable if a single only one type of demand was experienced, (Experiment 1), but adjust over time as biases from other tasks were experienced (Experiment 2).
+For example, such biases could reflect an individual’s global estimation of the richness of the environment, or a focal estimation of the passage of time experienced during performance of each task (e.g.
+how long 10 seconds actually feel).
+Altered perceived time durations have occasionally been associated with levels of cognitive engagement [@Csikszentmihalyi2014; @Wearden2016], and have a direct effect on a trial’s reward rate.
+Intuitively, the perceived passage of time could be recalibrated into a global estimate as decision makers faced different types of with experience.
+We modeled these biases by adding a demand-specific term to $\gamma$ that was gradually integrated across tasks for those participants who foraged among demands.
 The overall model took the following form
@@
 
-where $\gamma$ was the mean total earning rate for the whole group (0.55).
-Negative values of $mC_i$ would therefore suggest a boost in offer value produced by a demand.
-At each decision point, $mC$ was the cost bias produced by each demand $c_{demand}$ weighted against a global bias estimate $C$
+where $\gamma$ was the mean total earning rate per subject (mean = 0.55 cents per second, SD = 0.02).
+Negative values of $C_i$ would therefore suggest a boost in offer value produced by a demand.
+At each decision point, $C$ was the cost bias produced by each demand $c_{demand}$ weighted against a global bias estimate $c_{global}$
 
@@
 
-with $w_i$ controlling how early participants started integrating the converging cost $C$ into their decisions. The value of this weight was given by
+with $w_i$ controlling how early participants started integrating the converging cost $c_{global}$ into their decisions. The value of this weight was given by
 
@@
 
-where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parmeter $\alpha_w$ denoting a late integration of the global converging bias.
-
-  Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $C$ where the same and $\alpha_w$ did not play a role.
+where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parameter $\alpha_w$ denoting a late integration of the global converging bias.
+Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $c_{global}$ where the same and $\alpha_w$ did not play a role.
 This resulted in just fitting parameters $c_{demand}$ and $\beta$ for that dataset.
@@
 We therefore fixed each value of $c_{demand}$ (i.e.
-$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each between-subjects demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$.
-This dynamic allowed for the observed merging of acceptances across demands in the within-subjects experiment, while respecting the stability in the between-subjects study.
-
-  A final model combined the main features from $model_{adaptive}$ and $model_{biased}$, such that $\gamma$ was estimated on each trial per Eq.
+$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit the global bias $c_{global}$, the convergence rate $\alpha_w$, and temperature $\beta$.
+This dynamic allowed for the observed merging of acceptances across demands in Experiment 2, while respecting the stability in the between-subjects study.
+
+  Finally, we asked if the biases imposed by each demand could be isolated from a flexible computation of the opportunity cost of time.
+This fourth model combined the main features from $\text{Model}_\text{adaptive}$ and $\text{Model}_\text{biased}$, such that $\gamma$ was estimated on each trial per Eq.
 3, with demands imposing distinct and potentially converging biases as described in model 3.
@@
 
-  After fitting the parameters, we performed two-sided, one-sample t-tests to compare the biased opportunity costs from each between-subjects demand group **to the mean optimal gamma** (0.61, see Operationalization of Cost).
-This allowed us to determine whether any demand boosted an offer's value.
-Finally, we compared parameters with ANOVAs and post-hoc permutations between each group pairing (5000 iterations).
+  The resulting parameters were compared across cost groups (Experiment 1) and across experiments using ANOVAs, and the cdemand biases computed in Experiment 1 were compared against 0 using one-sample t-tests.
 
@@
 
-  We tested four models against a set of criteria derived from observed choice behavior (see Methods for details).
-The first one, a base formulation, probed the predictions of the Marginal Value Theorem (Charnov, 1975).
-The second one allowed individuals to estimate the opportunity cost at different rates using a reinforcement learning rule.
-The third model assumed that different demands imposed distinct cost biases on the experienced opportunity costs, and that these biases could be recalibrated with experience.
-A final model combined the adaptive features of the second and third formulations.
-
-  The fourth model produced the lowest BIC in both experiments (Figure 10A.
+  The fourth model produced the lowest BIC in both experiments (Fig.
+9A.
 Between-subjects = `r round(modelComparison[4, 3], digits = 2)`; Within-subjects = `r round(modelComparison[8, 3], digits = 2)`), indicating that the tenets of the Marginal Value Theorem were necessary but not sufficient to explain the observed adaptive behavior.
-Figure 10B-C show parameter fits from the winning model for both experiments.
+Fig.
+9B-C show parameter fits from the winning model for both experiments.
 The learning rate $\alpha$ and the bias $c_{demand}$ were of particular interest, as these parameters distinguished whether different demands globally affected the integration of the environmental richness or focally modulated an offer's perceived cost, respectively.
-Analyses of variance showed significant differences only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[2]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
+Analyses of variance showed significant differences among Experiment 1 groups only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[2]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
 Pairwise post-hoc permutations confirmed that the cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower biases than either wait (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or physical (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`) groups.
 These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = `r round(fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower than zero for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = `r round(fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
-This suggests that rather than reducing costs, cognitive tasks boosted the value of their concommitant offers.
+This suggests that rather than reducing costs, cognitive tasks boosted the value of their concomitant offers.
 
@@
 
-  The mean values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $C$ value (see Methods for details).
-As can be seen on Figure 10C, parameter values were comparable across experiments, pointing to consisency in the way decision makers approached our foraging scenarios.
+  The mean values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $c_{global}$ value.
+As can be seen on Fig.
+9C, parameter values were comparable across experiments, pointing to consistency in the way decision makers approached our foraging scenarios.
 In addition, values of $\alpha_w$ suggested that $c_{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session (mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
-Model fits also provided good qulitative resemblance to the observed choice behavior in both experiments (**Supplemental Figure X?**), fulfilling all but one of our modeling criteria (i.e.
-reduction in acceptances for between-subject effort groups, see Methods for details).
+Model fits provided good qualitative resemblance to the observed choice dynamics in each experiment.
+This is illustrated in Fig.
+9, in which 95% confidence intervals from within-subject fits are overlaid to empirical choices (Experiment 1 fits matched the left side of this figure, as expected).
 

### 2021-03-18 Cost_manuscript.Rmd
tiny specification of parameter descriptives

@@
 9C, parameter values were comparable across experiments, pointing to consistency in the way decision makers approached our foraging scenarios.
-In addition, values of $\alpha_w$ suggested that $c_{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session (mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
+In addition, values of $\alpha_w$ suggested that $c_{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session ($c_{global}$ mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
 Model fits provided good qualitative resemblance to the observed choice dynamics in each experiment.

### 2021-03-18 Cost_manuscript.Rmd
ack
discussion updated, but still need to double check citations

@@
 In this study, we sought to identify factors underlying this phenomenon, and tested the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
-Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found that preferences for cognitive effort were stable when individuals faced a single form of demand, but faded over time when other costs were also experienced.
+Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found a tendency toward engaging with cognitively effortful prospets when individuals faced a single form of demand, which faded over time when other costs were also experienced.
 
@@
 This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013].
-Successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [@Cash-Padgett2020; @Garrett2020; @Dundon2020].
-In contrast, our prediction that effort requirements would produce more acceptances only held for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment.
+In contrast, our prediction that effort requirements would produce more acceptances only held for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for Experiment 2.
 These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; @Olivola2013].
-Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands.
-The fact that predicted stable preferences for cognitive effort carried over onto the beginning of the within-subjects experiment further supported a task-specific modulation.
+Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted that reward-independent task features can promote the pursuit of effortful prospects.
+The fact that predicted stable preferences for cognitive effort carried over onto the beginning of Experiment 2 further supported a task-specific modulation.
 However, the unexpected gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.
@@
 These choice dynamics ruled out a number of common explanatory candidates.
-For instance, differences in choice stability between experiments suggested that a demand's cost is not intrinsic.
-In addition, the gradual choice convergence in the second experiment also discarded the effects of boredom, which would have accentuated the appeal of active tasks over time, or the possibility that our sample was mostly composed of demand seekers [@Cacioppo1996; @Sayali2019].
-Even though fatigue could explain the decrease in effort acceptances across experiments, we would have expected tired participants to turn to wait trials over time in order to preserve earning rates.
-We also ruled out the sunk cost effects used to explain overharvesting [@Wikenheiser2013; @Sweis2018], as participants expressed their choices early and rarely quit during the handling time.
-Risk was also an unlikely factor, as task performance improved over time.
-Finally, the observed differences in acceptances between effort types could not be explained by reward alone [@Eisenberger1996], as demands were rewarded at the same rate.
+For instance, if the subjective costs of effort or delay were intrinsic, we would not have observed the gradual convergence in acceptances when they were all intermixed in the same environment.
+This also speaks against a direct role of boredom in our results.
+The aversiveness of boredom can lead people to attempt any available activity in order to avoid it [@Westgate2020].
+This would have likely led to a persistent preference for either effortful condition.
+Lastly, this gradual convergence in choices rules out the possibility that our sample was mostly composed of demand seekers.
+Some individuals express a strong need for cognition, which can bias studies of mental labor [@Cacioppo1996; @Sayali2019].
+Even though the prevalence of this trait in our college-level population could have driven the preferences for cognitive effort observed in both experiments, we would have expected such individuals to maintain this preference in the face of alternatives.
+Another unlikely candidate is fatigue.
+Even though participants decreased their acceptance rates for effort in both experiments, we would have expected them to increase engagement with wait trials over time in order to preserve earning rates.
+Further, we do not expect any of our observations to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments.
+Finally, we cannot conclude that cognitive effort gained value from its rewarding outcomes, as has been proposed in the past [@Eisenberger1996].
+This phenomenon could not have benefitted a single type of demand, as cognitive effort, physical effort, and unfilled delay were rewarded at the same rate.
 
   Traditional foraging models, in which a reward is weighed against the earnings foregone by pursuing it [@Charnov1976; @Constantino2015], were also not enough to explain our results.
-Instead, we computationally found that each type of demand distinctly biased the estimation of this opportunity cost, and that such biases could be gradually recalibrated over time as decision makers gained experienced with additional demands.
-In this way, waiting and performing physical effort promoted selectivity by adding to the opportunity cost, whereas engaging in cognitive effort boosted an offer's value by reducing it.
+Instead, our results were consistent with a computational model in which each type of demand distinctly biased the estimation of the opportunity cost, and such biases could be gradually recalibrated over time as decision makers gained experience with additional demands.
+In this formulation, passive delay and physical effort added to the opportunity cost, whereas cognitive effort reduced it.
 This raises the question of how these biases arise.
@@
 Moreover, adjusting for time sensitivity has been shown to improve fits for delay discounting models [@Mckerchar2009].
-Therefore, even though participants knew the nominal handling times, cognitive effort might have become valuable by subjectively compressing them.
-In our experiments, shorter subjective handling times resulted in higher perceived earning rates, but it is also possible that individuals benefitted from a sense of fast completion.
+Therefore, even though participants knew the nominal handling times, cognitive effort might have become valuable by subjectively compressing the perceived durations.
+In our experiments, shorter subjective handling times would result in higher perceived earning rates, but it is also possible that individuals benefitted from a sense of fast completion.
 We speculate that this construal of elapsed time could then be adjusted with the experience of alternative demands, as participants learned how long the 10 seconds handling time felt.
-This could help explain why preferences for cognitive effort were smaller for within-subject participants who started with the physical block, as they had already formed an estimate of the handling time by the time they experienced a subjectively faster cognitive trial (**FIGURE**).
+This could help explain why preferences for cognitive effort were smaller for within-subject participants who started with the physical block, as they had already formed an estimate of the handling time by the time they experienced a subjectively faster cognitive trial.
 The shorter time sensitivity produced by cognitive effort could be due to participants counting the number of sub-tasks during pursual (which was always less than the number of seconds in the handling time), or because taxing cognitive resources distracted individuals from estimating the passage of time [@Zakay1989].
-These hypothesis will have to be experimentally probed in the future.
+These hypotheses will have to be experimentally probed in the future.
 
@@
 For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving its outcome, investigations of the pursuit and receipt stages have been limited.
-Many studies have sought to isolate the evaluation stage by presenting individuals with offers that do not come into effect until the end of the experimental session (with delays spanning up to months), deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a].
+Many studies have sought to isolate the evaluation stage by presenting individuals with offers that do not come into effect until the end of the experimental session, deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a].
 However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the near future [@Fawcett2012; @Frederick2002; @Sozou1998].
@@
 We eliminated this possibility by fixing the handling time for all demands, allowing us to probe people's preferences directly.
-Moreover, the between-subjects experiment, which resembled the traditional way costs are compared, provided a baseline of foraging behavior that contextualized the findings of the second experiment (a direct test of our hypothesis).
+Moreover, Experiment 1 provided a baseline of foraging behavior that contextualized the findings of the second experiment (a direct test of our hypothesis).
 Finally, the existence of optimal strategies helped us identify when demands could be attractive, a central motivation for this study.
@@
 
-  It is possible that participants gravitated towards cognitive demands because the task configuration was not effortful.
+  A potential limitation of this work lies in whether our task manipulations were actually costly.
+For instance, it is possible that participants gravitated towards cognitive demands because the task configuration was not effortful.
 This could be due to differences in how we calibrated cognitive and physical tasks.
 For physical demands, we adjusted the gripping threshold to people's maximum strength, whereas we trained participants in the cognitive tasks until they reached criterion.
-Training might have improved response automaticity and reduce error-related risk.
+Training might have improved response automaticity and reduced error-related risk.
 In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [@Bandura2010; @Eisenberger1996].
-Nevertheless, we believe our manipulations were successful in inducing feelings of effort.
-Hand grips are regularly used to probe physical effort [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to feel cognitively effortful by recruiting cognitive control [@Kool2010; @Shenhav2017].
-Furthermore, we observed a steeper decrease in acceptances over time at longer handling times, a hallmark of effortful exhertion [@Treadway2009].
+However, hand grips are regularly used to probe physical effort [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to feel cognitively effortful by recruiting cognitive control [@Kool2010; @Shenhav2017].
+Furthermore, we observed a steeper decrease in acceptances over time for both effort domains, a hallmark of effortful exertion [@Treadway2009].
 
@@
 However, since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases.
-Our work suggests that subdividing a task can promote its pursual, although further testing is required.
-More importantly, it highlights that decision scenarios should be configured to promote pursual of desired activities, perhaps by removing alternative uses of time.
+Our work suggests that subdividing a task can promote its pursuit, although further testing is required.
+More importantly, it highlights that decision scenarios should be configured to promote pursuit of desired activities, perhaps by removing alternative uses of time.
 These same principles can potentially be applied to increasing productivity at work or adherence to physical exercise routines.
@@
 
-  In this study, we have examined the factors that motivate the preference of different demands, emphasizing how these can be molded by the decision maker's environment.
-Unlike existing theories that have focused on the role of incentives and retrospective justifications [@Eisenberger1996; @Inzlicht2018], our work highlights outcome-independent and task-specific features that can motivate the pursual of effortful avenues, which can be potentially manipulated in order to promote engagement in clinical and daily activities.
+  In this study, we have examined the factors that motivate engagement with different behavioral demands, emphasizing how these can be molded by the decision maker's environment.
+Unlike existing theories that have focused on the role of incentives and retrospective justifications [@Eisenberger1996; @Inzlicht2018], our work highlights outcome-independent and task-specific features that can motivate the pursuit of effortful avenues, which can be potentially manipulated in order to promote engagement in clinical and daily activities.
 
 \newpage
+
+## Acknowledgments
+
+This project was funded.... In addition, we would like to thank Andrew Westbrook, the Shenhav lab, and Daw lab for valuable feedback.
 

### 2021-03-18 Cost_manuscript.Rmd
figures at the bottom ready, now do in-text

@@
 
-```{r New Trial plot (Fig.
-1), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
-On each trial, participants were offered to earn money (4, 8, or 20 cents) by sustaining effort or waiting during the handling time (2, 10, or 14 s).
+```{r New Task Plot (Fig.
+1), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Task design and optimal behavior.
+A: General foraging trial structure.
+On each trial, participants were offered to earn money by sustaining effort or waiting during the handling time (2, 10, or 14 s).
 The end of a trial was followed by a travel time (handling and travel times always added up to 16 s).
@@
 In Experiment 1, cost was fixed per participant and handling time varied per block.
-In the within-subject version, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
-Possible costs, handling times, and rewards were fully disclosed in order to avoid experience-dependent learning."}
-
-include_graphics("./Images/FIG1_task.png")
-```
-
-\newpage
-
-```{r New Optimal plot (Fig.
-2), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Possible earnings per second for each acceptance threshold (i.e.
+In Experiment 2, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
+B: Possible earnings per second for each acceptance threshold (i.e.
 the smallest amount accepted) for each handling time.
@@
 
-include_graphics("./Images/FIG1_task_b.png")
+include_graphics("./Images/FIG1_task.png")
 ```
@@
 ```{r New General prop & earnings plots (Fig.
-3), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in the between-subjects experiment.
+2), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1.
 Left: Proportion accepted per cost.
@@
 Consistent with the foraging design, participants who over and under accepted earned the least.
-These figures suggests a preference for cognitive effort at the expense of earnings."}
+These figures suggest that people are willing to pursue cognitively effortful actions at the expense of earnings."}
 # plots generated in 16.2.1. and 16.1.3.
@@
 ```{r New mixed effects plots (Fig.
-4), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
+3), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
 A: Proportion accepted by each group for every combination of handling time and reward.
@@
 #hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
-include_graphics("./Images/FIG4_btwlogistic.png")
+include_graphics("./Images/FIG3_btwlogistic.png")
 ```
@@
 ```{r New Survival and prepost plots (Fig.
-5), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in the between-subjects experiment.
+4), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1.
 Top: Survival curve (left), and distribution of times when participants quit a trial over time (right).
@@
 ```{r New Prepost mixed effects plot (Fig.
-6), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in the between-subjects experiment.
-Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
-Right: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal).
+5), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1.
+A: Proportion of acceptances per handling, reward, and session half, showing that effortful demands were less frequently accepted over time.
+B: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal).
 Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
-include_graphics("./Images/FIG6_prepostbtw.png")
+include_graphics("./Images/FIG5_prepostbtw.png")
 ```
@@
 ```{r New Earnings/prop completed/ME plots (Fig.
-7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior.
+6), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior.
 A: Quadratic relationship between trial completions and total earnings.
@@
 
-include_graphics("./Images/FIG8_survival.png")
+include_graphics("./Images/FIG6_wthlogistic.png")
 ```
@@
 ```{r New Survival and prepost plots (Fig.
-8), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in the within-subjects experiment.
+7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2.
 Top: Survival curve (left), and distribution of quitting times over time (right).
@@
 ```{r New Prepost mixed effects plots (Fig.
-9), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in the within-subjects experiment.
+8), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2.
 Top-Left: Proportion accepted in the first two and last two blocks of the experiment.
@@
 Top-Right: Mixed effects coefficient matrix for each half separately.
-The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4).
-Bottom: Block rder effects show attenuated differences for those who started with the physical configuration."}
-include_graphics("./Images/FIG9_prepostwth.png")
+The pattern from the first half resembles what was observed in Experiment 1 (Figure 3).
+Bottom: Block order effects show attenuated differences for those who started with the physical configuration."}
+include_graphics("./Images/FIG8_prepostwth.png")
 ```
@@
 ```{r New BIC and parameter comparison (Fig.
-10), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling.
+9), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling.
 A: BIC values for four plausible models of choice behavior for both experiments.
@@
 
-include_graphics("./Images/FIG10_modelresults.png")
+include_graphics("./Images/FIG9_modelresults.png")
 
 #(bicPlot + costPlot) / allFitsPlot
-
-#In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
-For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
-Conversely, low gamma values represented low selectivity when evaluating offers.
-Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
-This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC_btw$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC_btw$all$Rsquared), digits = 2)`).
-Figure 10 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
-Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
-In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
-We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC_btw$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC_btw$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC_btw$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
-We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 10; see Operationalization of Cost).
-Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Wait"][[1]])`).
-Neither physical effort (mean = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
-These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
-
 ```

### 2021-03-18 Cost_manuscript.Rmd
complete bib and eq numbers fixed

@@
 
-\begin{align}
-  iBIC = logp(d | model) + \frac{k}{2}log(o)
-\end{align}
+$$\begin{aligned}
+  iBIC = logp(d | \text{model}) + \frac{k}{2}log(o)
+\end{aligned}$$
 
@@
 
-where values of $\gamma$ were now updated on each trial $i$ according to Eq 3, rather than by the empirical earning rate.
+where values of $\gamma$ were now updated on each trial $i$ according to Eq. 3, rather than by the empirical earning rate.
 
@@
 Negative values of $C_i$ would therefore suggest a boost in offer value produced by a demand.
-At each decision point, $C$ was the cost bias produced by each demand $c_{demand}$ weighted against a global bias estimate $c_{global}$
+At each decision point, $C$ was the cost bias produced by each demand $c_\text{demand}$ weighted against a global bias estimate $c_\text{global}$
 
@@
 
-with $w_i$ controlling how early participants started integrating the converging cost $c_{global}$ into their decisions. The value of this weight was given by
+with $w_i$ controlling how early participants started integrating the converging cost $c_\text{global}$ into their decisions. The value of this weight was given by
 
@@
 where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parameter $\alpha_w$ denoting a late integration of the global converging bias.
-Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $c_{global}$ where the same and $\alpha_w$ did not play a role.
-This resulted in just fitting parameters $c_{demand}$ and $\beta$ for that dataset.
-For the within-subjects group, we assumed that the resulting $c_{demand}$ values from the first experiment reflected the actual bias induced by each demand.
-We therefore fixed each value of $c_{demand}$ (i.e.
-$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit the global bias $c_{global}$, the convergence rate $\alpha_w$, and temperature $\beta$.
+Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_\text{demand}$ and $c_\text{global}$ where the same and $\alpha_w$ did not play a role.
+This resulted in just fitting parameters $c_\text{demand}$ and $\beta$ for that dataset.
+For the within-subjects group, we assumed that the resulting $c_\text{demand}$ values from the first experiment reflected the actual bias induced by each demand.
+We therefore fixed each value of $c_\text{demand}$ (i.e.
+$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit the global bias $c_\text{global}$, the convergence rate $\alpha_w$, and temperature $\beta$.
 This dynamic allowed for the observed merging of acceptances across demands in Experiment 2, while respecting the stability in the between-subjects study.
@@
 9B-C show parameter fits from the winning model for both experiments.
-The learning rate $\alpha$ and the bias $c_{demand}$ were of particular interest, as these parameters distinguished whether different demands globally affected the integration of the environmental richness or focally modulated an offer's perceived cost, respectively.
-Analyses of variance showed significant differences among Experiment 1 groups only for $c_{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[2]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
+The learning rate $\alpha$ and the bias $c_\text{demand}$ were of particular interest, as these parameters distinguished whether different demands globally affected the integration of the environmental richness or focally modulated an offer's perceived cost, respectively.
+Analyses of variance showed significant differences among Experiment 1 groups only for $c_\text{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[2]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
 Pairwise post-hoc permutations confirmed that the cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower biases than either wait (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or physical (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`) groups.
@@
 
-  The mean values of $c_{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $c_{global}$ value.
+  The mean values of $c_\text{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $c_\text{global}$ value.
 As can be seen on Fig.
 9C, parameter values were comparable across experiments, pointing to consistency in the way decision makers approached our foraging scenarios.
-In addition, values of $\alpha_w$ suggested that $c_{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session ($c_{global}$ mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
+In addition, values of $\alpha_w$ suggested that $c_\text{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session ($c_\text{global}$ mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
 Model fits provided good qualitative resemblance to the observed choice dynamics in each experiment.
@@
 This also speaks against a direct role of boredom in our results.
-The aversiveness of boredom can lead people to attempt any available activity in order to avoid it [@Westgate2020].
+The aversiveness of boredom can lead people to attempt any available activity in order to avoid it [@westgate2020].
 This would have likely led to a persistent preference for either effortful condition.

### 2021-03-18 Cost_manuscript.Rmd
latex quirk

@@
 We therefore fixed each value of $c_\text{demand}$ (i.e.
-$c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit the global bias $c_\text{global}$, the convergence rate $\alpha_w$, and temperature $\beta$.
+$c_\text{cognitive}$, $c_\text{wait}$, and $c_\text{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit the global bias $c_\text{global}$, the convergence rate $\alpha_w$, and temperature $\beta$.
 This dynamic allowed for the observed merging of acceptances across demands in Experiment 2, while respecting the stability in the between-subjects study.

### 2021-03-18 Cost_manuscript.Rmd
reverted section title format

@@
 
-### *Methods*
-#### **Participants**
+### **Methods**
+#### *Participants*
 
@@
 
-#### **Foraging Task**
+#### *Foraging Task*
 
@@
 
-#### **Operationalization of Cost**
+#### *Operationalization of Cost*
 
@@
 
-#### **Analyses**
+#### *Analyses*
 
@@
 
-### *Results*
-#### **Between-subjects: Decision Makers Integrate Delay and Reward Information**
+### **Results**
+#### *Between-subjects: Decision Makers Integrate Delay and Reward Information*
 
@@
 
-#### **Between-subjects: Consistency and Stability**
+#### *Between-subjects: Consistency and Stability*
 
@@
 
-#### **Foraging Task Adaptation**
+#### *Foraging Task Adaptation*
 
@@
 
-### *Results*
-#### **Within-subjects: Decision Makers Integrate Reward Information**
+### **Results**
+#### *Within-subjects: Decision Makers Integrate Reward Information*
 
@@
 
-#### **Within-subjects: Consistency and Stability**
+#### *Within-subjects: Consistency and Stability*
 
@@
 
-### *Methods*
-#### **Model Fitting and Model Comparison Procedures**
+### **Methods**
+#### *Model Fitting and Model Comparison Procedures*
 
@@
 
-#### **Model Definitions**
+#### *Model Definitions*
 
@@
 
-### *Results*
+### **Results**
 
@@
 
-### Conclusion
+### **Conclusion**
 

### 2021-03-19 Cost_manuscript.Rmd
acknowledgments and fixed citations

@@
 
-This project was funded.... In addition, we would like to thank Andrew Westbrook, the Shenhav lab, and Daw lab for valuable feedback.
+We thank Andrew Westbrook, the Shenhav lab, and the Daw lab for helpful discussions.
+This work was supported by grants from the National Science Foundation (BCS-1755757) and the Office of Naval Research (MURI award N00014-16-1-2832 and DURIP award N00014-17-1-2304).
 

### 2021-03-23 Cost_manuscript.Rmd
updated in-text figs

@@
 
-```{r Trial plot (Fig.
-1), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap= "General foraging trial structure.
-On each trial, participants were offered to earn money (4, 8, or 20 cents) by sustaining effort or waiting during the handling time (2, 10, or 14 s).
-The end of a trial was followed by a travel time (handling and travel times always added up to 16 s).
-Participants could skip unfavorable trials and immediately start traveling to a potentially better offer.
-In Experiment 1, cost was fixed per participant and handling time varied per block.
-In the within-subject version, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
-Possible costs, handling times, and rewards were fully disclosed in order to avoid experience-dependent learning."}
-
-#Task design and optimal behavior.
+```{r Task Plot (Fig.
+1), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Task design and optimal behavior.
 A: General foraging trial structure.
@@
 In Experiment 1, cost was fixed per participant and handling time varied per block.
-In the within-subject version, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
+In Experiment 2, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
 B: Possible earnings per second for each acceptance threshold (i.e.
@@
 Circles denote the reward-maximizing threshold for each block, which is described in the table.
-Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers.
+Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers."}
 
@@
 ```{r General prop & earnings plots (Fig.
-3), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in the between-subjects experiment.
+2), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1.
 Left: Proportion accepted per cost.
@@
 
-include_graphics("./Images/FIG3_props.png")
+include_graphics("./Images/FIG2_props.png")
 
@@
 ```{r mixed effects plots (Fig.
-4), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
+3), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
 A: Proportion accepted by each group for every combination of handling time and reward.
@@
 ```{r Survival and prepost plots (Fig.
-5), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in the between-subjects experiment.
+4), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1.
 Top: Survival curve (left), and distribution of times when participants quit a trial over time (right).
@@
 # ggsave("./Images/FIG5_survival.png", historyPlot_btw, device = "png", height = 8, width = 10)
-include_graphics("./Images/FIG5_survival.png")
+include_graphics("./Images/FIG4_survivalbtw.png")
 ```
@@
 ```{r Prepost mixed effects plot (Fig.
-6), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in the between-subjects experiment.
-Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time.
-Right: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal).
+5), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1.
+A: Proportion of acceptances per handling, reward, and session half, showing that effortful demands were less frequently accepted over time.
+B: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal).
 Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
@@
 # ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
-include_graphics("./Images/FIG6_prepostbtw.png")
+include_graphics("./Images/FIG5_prepostbtw.png")
 
@@
 ```{r Earnings/prop completed/ME plots (Fig.
-7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior.
+6), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior.
 A: Quadratic relationship between trial completions and total earnings.
@@
 # earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
-ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
-include_graphics("./Images/FIG7_wthlogistic.png")
+#ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
+include_graphics("./Images/FIG6_wthlogistic.png")
 ```
@@
 ```{r Survival and prepost plots (Fig.
-8), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in the within-subjects experiment.
+7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2.
 Top: Survival curve (left), and distribution of quitting times over time (right).
@@
 #ggsave("./Images/FIG8_survival.png", historyPlot_wth, device = "png", height = 8, width = 10)
-include_graphics("./Images/FIG8_survival.png")
+include_graphics("./Images/FIG7_survivalwth.png")
 ```
@@
 
-```{r Prepost mixed effects plots (Fig.
-9), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in the within-subjects experiment.
+```{r New Prepost mixed effects plots (Fig.
+8), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2.
 Top-Left: Proportion accepted in the first two and last two blocks of the experiment.
@@
 Top-Right: Mixed effects coefficient matrix for each half separately.
-The pattern from the first half resembles what was observed in the between-subjects experiment (Figure 4).
-Bottom: Block rder effects show attenuated differences for those who started with the physical configuration."}
+The pattern from the first half resembles what was observed in Experiment 1 (Figure 3).
+Bottom: Block order effects show attenuated differences for those who started with the physical configuration."}
 # hrprepostPlot_wth, blockOrder_wth
 # ggsave("./Images/prepostwth_2.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
-include_graphics("./Images/FIG9_prepostwth.png")
+include_graphics("./Images/FIG8_prepostwth.png")
 
@@
 ```{r BIC and parameter comparison (Fig.
-10), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling.
+9), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling.
 A: BIC values for four plausible models of choice behavior for both experiments.
@@
 
-modelPlot <- (bicPlot + costPlot) / allFitsPlot
+# modelPlot <- (bicPlot + costPlot) / allFitsPlot
 # ggsave("./Images/FIG10_model.png", modelPlot, device = "png", height = 8, width = 11)
-include_graphics("./Images/FIG10_modelresults.png")
-
-#In the first model, gamma reflected cost by indexing how much money per second a participant needed to accept a trial.
-For example, the aversion produced by a given cost could prompt an individual to spend their time and effort in the most profitable offers, resulting in a high gamma value.
-Conversely, low gamma values represented low selectivity when evaluating offers.
-Results from this model apply only to the between-subjects experiment, as this single parameterization was not flexible enough to account for the dynamics of experiment two.
-This model was able to explain a considerable degree of choice variance per individual ($R^2$: mean = `r round(mean(summaryOC_btw$all$Rsquared), digits = 2)`, SD = `r round(sd(summaryOC_btw$all$Rsquared), digits = 2)`).
-Figure 10 displays the distribution of fitted gammas, which were significantly different across groups (F(`r OCanova$aov[[1]]$Df[1]`, `r OCanova$aov[[1]]$Df[2]`) = `r Fval`, p = `r report_p(Pval)`, $R^2$ = `r Rsquared_aov`).
-Pairwise post-hoc permutations indicated that the mean gamma values for the cognitive group were significantly lower than for the wait (*p* `r report_p(OCanova$perms["Wait", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Wait", "Cognitive"], digits = 2)`) and physical effort (*p* `r report_p(OCanova$perms["Physical", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Physical", "Cognitive"], digits = 2)`), and marginally lower than the easy group (*p* `r report_p(OCanova$perms["Easy", "Cognitive"])`, Cohen's D = `r round(OCanova$ES["Easy", "Cognitive"], digits = 2)`).
-In addition, the easy group displayed significantly lower gamma values than the wait group (*p* `r report_p(OCanova$perms["Wait", "Easy"])`, Cohen's D = `r round(OCanova$ES["Wait", "Easy"], digits = 2)`).
-We cross-validated individual OCs by using the pre-midpoint data for estimation, and post-midpoint choices for testing.
-This procedure revealed high mean predictive accuracies for all individuals (mean accuracy for Cognitive = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Cognitive")$sdPredicted`; mean Physical = `r filter(summaryOC_btw$predicted, Cost == "Physical")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Physical")$sdPredicted`; mean Wait = `r filter(summaryOC_btw$predicted, Cost == "Wait")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Wait")$sdPredicted`; mean Easy = `r filter(summaryOC_btw$predicted, Cost == "Easy")$mPredicted`%, SD = `r filter(summaryOC_btw$predicted, Cost == "Easy")$sdPredicted`), despite the reduction in acceptances produced by the effortful demands.
-We further interpreted these fitted values by comparing them to the optimal gamma (dashed line on Figure 10; see Operationalization of Cost).
-Two-sided one-sample t-tests against this optimal magnitude resulted in significantly lower gamma values for the cognitive group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Cognitive")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Cognitive"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Cognitive"][[1]])`), and marginally higher values for the wait group (mean = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Wait")$sdGamma`; T(20) = `r round(summaryOC_btw$t.test["statistic", "Wait"][[1]], digits = 2)`, *p* `r report_p(summaryOC_btw$t.test["p.value", "Wait"][[1]])`).
-Neither physical effort (mean = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Physical")$sdGamma`) nor the easy condition (mean = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$mGamma`, SD = `r filter(summaryOC_btw$descriptives, Cost == "Easy")$sdGamma`) produced significant differences (all *p* > 0.05).
-These results suggest that the cognitive effort group acted as if they perceived the trials as attractive.
+include_graphics("./Images/FIG9_modelresults.png")
 

### 2021-04-08 Cost_manuscript.Rmd
quick typo
fixed duplicated header
figure tweaks based on dissertation

@@
 Each entry shows how much more likely a group was to accept compared to the reference condition (row).
-C: AIC and BIC values for a forward mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model."}
+C: AIC and BIC values for a mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model.
+Both metrics yielded the same values across models."}
 #hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
@@
 
-```{r New Prepost mixed effects plots (Fig.
+```{r Prepost mixed effects plots (Fig.
 8), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2.
@@
 Negative values of $C_i$ would therefore suggest a boost in offer value produced by a demand.
-At each decision point, $C$ was the cost bias produced by each demand $c_\text{demand}$ weighted against a global bias estimate $c_\text{global}$
+At each decision point, $C_i$ was the cost bias produced by each demand $c_\text{demand}$ weighted against a global bias estimate $c_\text{global}$
 

### 2021-04-12 Cost_manuscript.Rmd
cleaning up code, etc

--- 2021-03-23 Cost_manuscript.Rmd
@@
   The study was preregistered with the Open Science Framework (https://osf.io/2rsgm/registrations).
+The code employed for all analyses can be found in https://github.com/ctoroserey/Cost_studies.
 All experimental procedures were approved by the Boston University Institutional Review Board, and written consent was acquired for all participants.

### 2021-04-12 Cost2/moveData.sh

@@ -1,23 +1,0 @@
-#!bin/bash/
-
-# Move data from lab_tasks to where I'm doing analyses
-dataDir='/Users/ctoro/git_clones/lab_tasks/Claudio/Replication_2018'
-analDir='/Users/ctoro/git_clones/R/MA681/MA681_Final/data'
-
-# Cognitive effort
-cp ${dataDir}/cog/data/*_log.csv ${analDir}/cog
-rm -f ${analDir}/cog/attention*
-
-# Easy effort
-cp ${dataDir}/pheasycal/data/*_log.csv ${analDir}/easy
-rm -f ${analDir}/easy/attention*
-rm -f ${analDir}/easy/*_calibration_log.csv
-
-# Physical effort
-cp ${dataDir}/phys/data/*_log.csv ${analDir}/phys
-rm -f ${analDir}/phys/attention*
-rm -f ${analDir}/phys/*_calibration_log.csv
-
-# Passive delay
-cp ${dataDir}/wait/data/*_log.csv ${analDir}/wait
-rm -f ${analDir}/wait/attention*

### 2021-04-12 Simulations/Garrett_sims.R

@@ -1,194 +1,0 @@
-# simulating decisions from Garrett and Daw 2019
-# this is just a playground to estimate how models affect their experiment
-# this was helpful in understanding their approach
-# and really, I did it to motivate myself to do it with my own data
-
-
-# notes for Neil:
-# - Since p is updated per second, and handling times are considered negative, 
-#   asymmetric MVT can't compensate for extra positive learning. This could be why their betas are so low, to prevent this.
-#   In a case where p is updated per trial experienced, the issue might be solved? Maybe try that...
-#   So, during symmetry the handling time updates are compensated by the reward rate, reaching a mean rate. Maybe that's why p ends up at 20 during Rich blocks
-
-library(tidyverse)
-
-# there are 4 trial types, spanning low to high reward rates
-trialType <- list(HDLR = c(rep(0, 8), 20),
-                  HDHR = c(rep(0, 8), 80),
-                  LDLR = c(rep(0, 2), 20),
-                  LDHR = c(rep(0, 2), 80))
-
-# earning rates (pts/time) per trial
-trialTimes <- list(HDLR = 8, LDHR = 2, HDHR = 8, LDLR = 2)
-trialRewards <- list(HDLR = 20, LDHR = 80, HDHR = 80, LDLR = 20)
-  
-# blocks had different environmental richness based on rate of trial occurrences (per 7 trials)
-richTrials <- c("HDLR", "HDHR", "LDLR", rep("LDHR", 4))
-poorTrials <- c("LDHR", "HDHR", "LDLR", rep("HDLR", 4))
-
-# optimal policy for each block
-richAccept <- list(HDLR = F, LDHR = T, HDHR = F, LDLR = F)
-poorAccept <- list(HDLR = F, LDHR = T, HDHR = T, LDLR = T)
-
-# starting parameters for their Rescorla-Wagner-type model
-# the model updates per second
-# p = is the expected reward value
-# alpha is the adaptation rate
-p <- 8
-alpha <- 0.005
-alphaPos <- 0.005
-alphaNeg <- 0.002
-n <- 60
-asymmetric <- F # to use asymmetric updating of p
-order <- c("Rich", "Poor")  # c("Poor", "Rich") c("Rich", "Poor") you can have a single block too
-  
-# this is just to store a session's evolution of the reward estimate
-pStore <- numeric()
-evol <- data.frame(Reward = NA,
-                   Delay = NA,
-                   p = NA,
-                   trialType = NA,
-                   Choice = NA,
[…]

### 2021-04-12 Simulations/Garrett_sims_trial.R

@@ -1,189 +1,0 @@
-# simulating decisions from Garrett and Daw 2019
-# this is just a playground to estimate how models affect their experiment
-# this was helpful in understanding their approach
-# and really, I did it to motivate myself to do it with my own data
-
-
-# notes for Neil:
-# - Since p is updated per second, and handling times are considered negative, 
-#   asymmetric MVT can't compensate for extra positive learning. This could be why their betas are so low, to prevent this.
-#   In a case where p is updated per trial experienced, the issue might be solved? Maybe try that...
-#   So, during symmetry the handling time updates are compensated by the reward rate, reaching a mean rate. Maybe that's why p ends up at 20 during Rich blocks
-#   This issue partially goes back to a simple fact: environmental reward rates are learned independently of choices.
-#   Instead, per-second sims track the attained average.
-
-library(tidyverse)
-
-# there are 4 trial types, spanning low to high reward rates
-trialType <- list(HDLR = c(rep(0, 8), 20),
-                  HDHR = c(rep(0, 8), 80),
-                  LDLR = c(rep(0, 2), 20),
-                  LDHR = c(rep(0, 2), 80))
-
-# earning rates (pts/time) per trial
-trialTimes <- list(HDLR = 8, LDHR = 2, HDHR = 8, LDLR = 2)
-trialRewards <- list(HDLR = 20, LDHR = 80, HDHR = 80, LDLR = 20)
-  
-# blocks had different environmental richness based on rate of trial occurrences (per 7 trials)
-richTrials <- c("HDLR", "HDHR", "LDLR", rep("LDHR", 4))
-poorTrials <- c("LDHR", "HDHR", "LDLR", rep("HDLR", 4))
-
-# optimal policy for each block
-richAccept <- list(HDLR = F, LDHR = T, HDHR = F, LDLR = F)
-poorAccept <- list(HDLR = F, LDHR = T, HDHR = T, LDLR = T)
-
-# starting parameters for their Rescorla-Wagner-type model
-# the model updates per second
-# p = is the expected reward value
-# alpha is the adaptation rate
-p <- 0
-alpha <- 0.005
-alphaPos <- 0.005
-alphaNeg <- 0.002
-n <- 60
-asymmetric <- F # to use asymmetric updating of p
-order <- c("Rich", "Poor")  # c("Poor", "Rich") c("Rich", "Poor") you can have a single block too
-  
-# this is just to store a session's evolution of the reward estimate
-pStore <- numeric()
[…]

### 2021-04-12 Simulations/manuscript_modeling.R

@@ -1,1638 +1,0 @@
-#!/usr/bin/env Rscript
-
-# using NLOPTR is pointless here
-# instead I'm just going to feed any sensible combination of parameters to the model and minimize the negLL manually
-# simpler, can evaluate models easier, and faster
-# for tomorrow: have negloglik return the parameters per iteration
-# the idea being that you can enter a model and data, and the function will return the lowest LL and associated parameters
-# maybe also R-squares and things in the current optimization function
-
-#$ -pe omp 28
-
-## libraries
-library(tidyverse)
-library(ggfortify)
-library(knitr)
-library(pander) 
-library(nloptr)
-#library(pwr)
-library(lme4)
-#library(lmerTest)
-library(gridExtra)
-library(reshape2)
-library(corrplot)
-#library(survival)
-library(ggfortify)
-#library(patchwork)
-library(data.table)
-library(parallel)
-
-# remove break time and start counting from 0
-standardize_time <- function(subjData) {
-  # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
-  breakTime <- min(subjData$ExpTime[subjData$Block == 4]) - max(subjData$ExpTime[subjData$Block == 3])
-  subjData$ExpTime[which(subjData$Block > 3)] <- subjData$ExpTime[which(subjData$Block > 3)] - breakTime + 16
-  subjData$ExpTime <- subjData$ExpTime - min(subjData$ExpTime)
-  
-  return(subjData)
-}
-
-# summary matrices for refrence-changing models
-betaMatrix <- function(model, rearrange = NA) {
-  # get a similarity matrix of the resulting coefficient pairings for the cost conditions
-  # first, do a full_join based on column names on the list of coefficient vectors from each dummy code relevel
-  # then match the names of columns and rows so NAs are in the diagonal
-  
-  # get the names of the reference group per model iteration
-  refnames <- names(model)
-  
-  # coefficient matrix
-  temp <- lapply(model, function(data) {coefficients(data)$SubjID[1, 2:4]})
-  mixCoeffs <- bind_rows(temp) 
[…]

### 2021-04-12 Simulations/wikenheiser.R

@@ -1,125 +1,0 @@
-
-library(tidyverse)
-library(data.table)
-
-# basic calculation
-offer <- c(4, 8, 20)
-handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
-travel <- c(2, 6, 14) + 2
-offerRates_basic <- sapply(3:1, function(thresh) {(sum(tail(offer, n = thresh))) / ((handling * thresh) + (travel * 3))}) # good
-
-
-# new stuff
-pmat <- rbind(c(1, 1, 1),
-              c(0, 1, 1),
-              c(0, 0, 1))
-A <- seq(0, 1.5, length.out = 4)
-
-
-## single example comparing the two at a single acceptance strategy
-p <- pmat[1, ]
-
-# basic numerator
-bn <- (offer %*% p)
-
-# wikenheiser version
-wn <- (offer %*% p) - ((offer %*% (1 - p)) * A)  
-
-# basic denominator
-bd <- ((handling * sum(p)) + (travel * 3)) #
-
-# adapted wikenheiser numerator (since our participants don't select among delays, calculate per handling time)
-wd <- (1 + (handling * sum(p)))
-
-
-## loop through every possible combination 
-# eventually mapply()
-modeledRates <- list()
-
-for (iter in seq_along(A)) {
-  
-  a <- A[iter]
-  
-  rstore <- matrix(0, 3, 3)
-    
-  for (prow in 1:nrow(pmat)) {
-    
-    # acceptances (binary per reward)
-    p <- pmat[prow, ]
-    
-    # numerator from wikenheiser, denominator from us
-    wn <- (offer %*% p) - ((offer %*% (1 - p)) * a)  
-    bd <- ((handling * sum(p)) + (travel * 3))
-    
-    # model
-    rstore[, prow] <- wn[1, 1] / bd
-
-  }
-  
-  # clean up into a dataframe with info
-  rstore <- as.data.frame(rstore)
-  colnames(rstore) <- offer
-  rstore$H <- handling
-  modeledRates[[iter]] <- rstore
-  
-}
-
-offerRates_wik <- do.call(rbind, modeledRates) %>%
-  mutate(A = rep(A, each = 3)) %>%
-  gather(O, Rate, -c(H:A)) %>%
-  mutate(A = as.character(A),
-         O = factor(O, levels = list(4, 8, 20)),
-         H = factor(H, levels = list(4, 12, 16)))
-
-
-## plots
-
-# earnings per acceptance threshold
[…]

### 2021-04-15 Manuscript.Rmd
Cleaning up directory structure and its references

--- 2021-04-08 Cost_manuscript.Rmd
@@
 indent: true
-bibliography: cost_paper.bib
+bibliography: bibliography.bib
 ---
@@
 # The RT is upper-bounded because a glitch in the code made two 14s trials last longer (among all p's) 
-setwd("./Cost2/data")
+setwd("./Exp1/data")
 files <- dir(pattern = '_log.csv')
@@
 # The RT is upper-bounded because a glitch in the code made one 10s last 14s
-setwd('./Cost3/data/')
+setwd('./Exp2/data/')
 files <- dir(pattern = 'main_log.csv')
@@
 
-Corresponding authors: Claudio Toro-Serey (ctoro@bu.edu) & Joseph T. McGuire (jtmcg@bu.edu)
+Corresponding authors: Claudio Toro-Serey (ctoroserey@mclean.harvard.edu) & Joseph T. McGuire (jtmcg@bu.edu)
 
@@
 
-  Cognitive and physical effort are typically regarded as costly, but recent findings have suggested that exerting effort can boost the value of prospects under certain conditions.
-Here we embedded mental and physical effort in a "diet choice" foraging task, which required decision makers not only to evaluate the magnitude and delay of a focal prospective reward, but also to estimate the general opportunity cost of time.
-In two experiments, independent sets of participants collected rewards that required equivalent periods of cognitive effort, physical effort, or unfilled delay.
-Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial (between-subjects, n = 21 per condition), or varied across trials (within-subjects, n = 48).
-When participants faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
+Cognitive and physical effort are typically regarded as costly, but demands for effort also seemingly boost the value of prospects under certain conditions.
+One contextual factor that might influence the perceived value of effort is the mix of different demand types a decision maker encounters in a given environment.
+Here, we embedded both cognitive and physical effort in a "prey selection" foraging task, which required decision makers not only to evaluate the magnitude and delay of a focal prospective reward but also to estimate the general opportunity cost of time.
+In two experiments, participants encountered prospective rewards that required equivalent intervals of cognitive effort, physical effort, or unfilled delay.
+Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial (between-participant manipulation, n=21 per condition), or varied across trials (within-participant manipulation, n=48).
+When each participant faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
 We theorized that if cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards.
-In the within-subject experiment, an initially higher acceptance rate for cognitive effort trials disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions.
-Our results extend the view that cognitive demands may reduce the discounting effect of delays, but also suggest that differences in cost can eventually fade if individuals actively experience alternative forms of demand.
-Rather than assigning intrinsic value to cognitive effort, our findings support the idea that a cognitive effort requirement might influence contextual factors such as subjective delay durations.
-Such altered estimations can be recalibrated if multiple forms of demand are interleaved.
+Contrary to this prediction, in the within-participant experiment, an initially higher acceptance rate for cognitive effort trials disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions.
+Our results indicate that cognitive demands may reduce the discounting effect of delays, but not because decision makers assign intrinsic value to cognitive effort.
+Rather, the results suggest that a cognitive effort requirement might influence contextual factors such as subjective delay duration estimates, which can be recalibrated if multiple forms of demand are interleaved
 
@@
 Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcomes, whereby exerting effort boosts the perceived value of its outcomes [@HernandezLallement2014; @Kacelnik2002; @Mochon2012], and positive outcomes imbue value into their preceding effortful behavior [i.e.
-learned industriousness; @Eisenberger1992].
+learned industriousness, @Eisenberger1992].
 Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs [@Inzlicht2018].
@@
 
-  Recent work has proposed that the subjective costs produced by delays and cognitive effort are modulated by the possibility of missing out on better concurrent alternatives, implying that decision makers track the *opportunity cost of time* [OC; @Fawcett2012; @Kurzban2013; @Otto2019].
+  Recent work has proposed that the subjective costs produced by delays and cognitive effort are modulated by the possibility of missing out on better concurrent alternatives, implying that decision makers track the *opportunity cost of time* [OC, @Fawcett2012; @Kurzban2013; @Otto2019].
 Preferences for effortful courses of action could therefore arise from the presence of other types of demands and opportunities in the same choice environment [@Kool2018].
@@
 #   filter(Block < 3) %>%
-#   mutate(Cost2 = ifelse(Cost %in% c("Wait-P", "Wait-C"), "Wait", Cost)) %>%
-#   group_by(SubjID, Cost2) %>%
+#   mutate(Exp1 = ifelse(Cost %in% c("Wait-P", "Wait-C"), "Wait", Cost)) %>%
+#   group_by(SubjID, Exp1) %>%
 #   summarise(pAccept = mean(Choice)) %>%
-#   plyr::dlply("Cost2", identity)
+#   plyr::dlply("Exp1", identity)
 # 
@@
 #   filter(Choice < 2) %>%
-#   mutate(Cost2 = ifelse(!(Cost %in%  c("Wait-C", "Wait-P")), "EFFORT", "WAIT"),
+#   mutate(Exp1 = ifelse(!(Cost %in%  c("Wait-C", "Wait-P")), "EFFORT", "WAIT"),
 #          BlockType = ifelse(gsub(".*_", "", Cost) == 1, "Physical", "Cognitive")) %>%
 #   group_by(SubjID, BlockType) %>%
-#   summarise(Wait_accept = mean(Choice[Cost2 == "WAIT"]),
-#             Effort_accept = mean(Choice[Cost2 == "EFFORT"])) %>%
+#   summarise(Wait_accept = mean(Choice[Exp1 == "WAIT"]),
+#             Effort_accept = mean(Choice[Exp1 == "EFFORT"])) %>%
 #   ggplot(aes(Wait_accept, Effort_accept, color = SubjID, shape = BlockType)) +
@@
 
-  Model comparison was performed by calculating Bayes Information Criterion at the group level [integrated BIC or iBIC; @Huys2011; @Huys2012; @Kane2019].
+  Model comparison was performed by calculating Bayes Information Criterion at the group level [integrated BIC or iBIC, @Huys2011; @Huys2012; @Kane2019].
 iBIC penalizes the likelihood of the data given model parameters $p(d | \text{model})$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
@@
 
-  We began by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT; @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it (see Operationalization of Cost for details).
+  We began by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT, @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it (see Operationalization of Cost for details).
 This decision rule can be expressed as
@@
 # load results from models
-#load("models_gk/results/btw.Rdata")
-#load("models_gk/results/wth.Rdata")
-load("models_gk/results/mod_results.Rdata")
+load("Models/results/mod_results.Rdata")
 

### 2021-04-15 Models/load_data.R

@@ -3,8 +3,8 @@ library(data.table)
 load_data_dir = dirname(dirname(sys.frame(1)$ofile))
 
 load_data = function() {
-  btw_file = paste0(load_data_dir, "/models_gk/data/dat_btw.csv")
-  wth_file = paste0(load_data_dir, "/models_gk/data/dat_wth.csv")
+  btw_file = paste0(load_data_dir, "/Models/data/dat_btw.csv")
+  wth_file = paste0(load_data_dir, "/Models/data/dat_wth.csv")
 
   dat_btw = fread(btw_file)
   dat_wth = fread(wth_file)

### 2021-04-15 Manuscript.Rmd
forgot one change in directory call

@@
 ``` {r BTW and WTH: 16.3. Model fits, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
-## the fitting of these models was performed by a separate script (modeling_gk_btw/wth)
+## the fitting of these models was performed by a separate script (modeling_btw/wth)
 # here we load the results to economize computational power during knitting

### 2021-04-15 Manuscript.Rmd
cleaner headers and removal of new summarise() warnings (thanks tidyverse...)

@@
 
+&nbsp;
+
   The study was preregistered with the Open Science Framework (https://osf.io/2rsgm/registrations).
@@
 #### *Foraging Task*
+
+&nbsp;
 
@@
 
+&nbsp;
+
   Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time to be incurred in obtaining it, which depends on the richness of the environment [@Charnov1976; @Stephens1986].
@@
 #### *Analyses*
+
+&nbsp;
 
@@
   group_by(SubjID, Cost) %>% 
-  summarise(propFails = mean(rawChoice == 2)) %>%
+  summarise(propFails = mean(rawChoice == 2), .groups = 'drop') %>%
   group_by(Cost) %>% 
   summarise(meanFT = mean(propFails),
-            sdFT = sd(propFails))
+            sdFT = sd(propFails), .groups = 'drop')
 ```
@@
   summarise(Earnings = sum(Offer[Choice == 1] / 100),
-            pComplete = mean(Choice)) %>%
+            pComplete = mean(Choice), .groups = 'drop') %>%
   mutate(pComplete2 = pComplete^2) %>%
@@
 ```
+
+&nbsp;
 
@@
             accept = sum(Choice),
-            quit = sum(Choice == 0))
+            quit = sum(Choice == 0), .groups = 'drop')
 
@@
         summarise(Earnings = sum(Offer[(Choice == 1) & (rawChoice < 2)] / 100),
-                  pAccept = mean(Choice))
+                  pAccept = mean(Choice), .groups = 'drop')
 
@@
   group_by(Cost) %>% 
-  summarise (mProp = mean(pAccept), 
+  summarise(mProp = mean(pAccept), 
              sdProp = sd(pAccept), 
              mEarn = mean(Earnings), 
-             sdEarn = sd(Earnings)) %>%
+             sdEarn = sd(Earnings), .groups = 'drop') %>%
   mutate_if(is.numeric, round, digits = 2)
@@
         group_by(SubjID, Cost, Handling, Offer, optimal) %>%
-        summarise(pAccept = mean(Choice)) %>%
+        summarise(pAccept = mean(Choice), .groups = 'drop') %>%
         group_by(Cost, Handling, Offer, optimal) %>%
         summarise(meanComplete = mean(pAccept),
-                  SE = sd(pAccept) / sqrt(length(pAccept))) %>%
+                  SE = sd(pAccept) / sqrt(length(pAccept)), .groups = 'drop') %>%
    ggplot(aes(interaction(Offer, Handling), meanComplete, color = Cost)) + 
@@
             totalQuits = sum(Choice == 0),
-            propAccepted = mean(Choice)) %>%
+            propAccepted = mean(Choice), .groups = 'drop') %>%
   ungroup()
@@
   filter(rawChoice == 0) %>%
-  summarize(r = round(mean(RT > 1.05), digits = 2)) # to account for some measurement error for the grace perior during grip
+  summarize(r = round(mean(RT > 1.05), digits = 2), .groups = 'drop') # to account for some measurement error for the grace perior during grip
 
@@
   summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
-            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
+            propAccept_2 = mean(Choice[Half == "Half_2"]), .groups = 'drop') %>%
   plyr::dlply("Cost", identity)
@@
             group_by(SubjID, Cost, Block, Half) %>%
-            summarise(propAccept = mean(Choice)) %>%
+            summarise(propAccept = mean(Choice), .groups = 'drop') %>%
             group_by(SubjID, Cost, Half) %>%
-            summarise(propAccept = mean(propAccept)) %>%
+            summarise(propAccept = mean(propAccept), .groups = 'drop') %>%
             spread(Half, propAccept) %>%
@@
             summarise(propAccept_1 = mean(Half_1),
-                      propAccept_2 = mean(Half_2))
+                      propAccept_2 = mean(Half_2), .groups = 'drop')
 
@@
                         summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
-                                  propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
+                                  propAccept_2 = mean(Choice[Half == "Half_2"]), .groups = 'drop') %>%
                         ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
@@
                          group_by(SubjID, Cost, Block) %>%
-                         summarise(propAccept_subj = mean(Choice)) %>%
+                         summarise(propAccept_subj = mean(Choice), .groups = 'drop') %>%
                          group_by(Cost, Block) %>%
                          summarize(propAccept = mean(propAccept_subj),
-                                   seAccept = sd(propAccept_subj)/sqrt(length(propAccept_subj))) %>%
+                                   seAccept = sd(propAccept_subj)/sqrt(length(propAccept_subj)), .groups = 'drop') %>%
                          ggplot(aes(Block, propAccept, color = Cost)) +
@@
   group_by(SubjID, Handling, Offer, Trial_Time, Half) %>%
-  summarise(mRT = mean(Task.RT)) %>%
+  summarise(mRT = mean(Task.RT), .groups = 'drop') %>%
   group_by(Handling, Offer, Trial_Time, Half) %>%
   summarise(meanRT = mean(mRT),
-            seRT = sd(mRT, na.rm = T) / sqrt(21)) %>%
+            seRT = sd(mRT, na.rm = T) / sqrt(21), .groups = 'drop') %>%
   ungroup() %>%
@@
   group_by(SubjID, Half, Handling, Cost, Offer) %>%
-  summarise(pAccept = mean(Choice)) %>%
+  summarise(pAccept = mean(Choice), .groups = 'drop') %>%
   group_by(Half, Cost, Handling, Offer) %>%
   summarise(propAccept = mean(pAccept),
-            SE = sd(pAccept) / sqrt(length(pAccept))) %>%
+            SE = sd(pAccept) / sqrt(length(pAccept)), .groups = 'drop') %>%
   ungroup() %>%
@@
             totalQuits = sum(Choice == 0),
-            propAccepted = mean(Choice))
+            propAccepted = mean(Choice), .groups = 'drop')
 
@@
 
+&nbsp;
+
   We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36; number excluded before reaching goal = 6).
@@
 #### *Foraging Task Adaptation*
+
+&nbsp;
 
@@
 
+&nbsp;
+
   The analytical pipeline was mostly preserved from Experiment 1.
@@
 
+&nbsp;
+
   In Experiment 2, we directly tested an individual’s preferences for cognitive effort, physical effort, and delay.
@@
 baseCoeffs$propAccept_totalSQRD <- baseCoeffs$propAccept_total^2
-baseCoeffs$totalEarned <- (dataWth %>% group_by(SubjID) %>% summarize(totalEarned = sum(Offer[Choice == 1])))$totalEarned
+baseCoeffs$totalEarned <- (dataWth %>% group_by(SubjID) %>% summarize(totalEarned = sum(Offer[Choice == 1]), .groups = 'drop'))$totalEarned
 baseCoeffs$SubjID <- subjList_wth # add subject list column to join the demographics by it below
@@
   filter(rawChoice == 1) %>%
-  summarise(earning = sum(Offer) / 100) %>%
+  summarise(earning = sum(Offer) / 100, .groups = 'drop') %>%
   group_by(Cost) %>%
   summarise(mEarn = mean(earning),
-            sdEarn = sd(earning)) %>%
+            sdEarn = sd(earning), .groups = 'drop') %>%
   mutate_if(is.numeric, round, digits = 2)
@@
         summarise(propAccept = mean(Choice),
-                  SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
+                  SE = sd(Choice) / sqrt(nSubjs_wth), .groups = 'drop') %>%
         ungroup() %>%
@@
   group_by(SubjID, Cost) %>%
-  summarise(propFails = mean(rawChoice == 2) * 100)
+  summarise(propFails = mean(rawChoice == 2) * 100, .groups = 'drop')
 
@@
   group_by(SubjID) %>%
-  summarise(propAccept = mean(ResponseType == "Quit") * 100)
-
-```
+  summarise(propAccept = mean(ResponseType == "Quit") * 100, .groups = 'drop')
+
+```
+
+&nbsp;
 
@@
   summarise(propAccept_1 = mean(Choice[Half == "Half_1"]),
-            propAccept_2 = mean(Choice[Half == "Half_2"])) %>%
+            propAccept_2 = mean(Choice[Half == "Half_2"]), .groups = 'drop') %>%
   mutate(Diff = propAccept_2 - propAccept_1)
@@
   group_by(SubjID,  Half) %>%
-  summarise(propFails = mean(rawChoice == 2)) %>%
+  summarise(propFails = mean(rawChoice == 2), .groups = 'drop') %>%
   spread(Half, propFails)
@@
     group_by(SubjID, Cost, Block) %>%
-    summarise(propAccept_subj = mean(Choice)) %>%
+    summarise(propAccept_subj = mean(Choice), .groups = 'drop') %>%
     group_by(Cost, Block) %>%
     summarize(propAccept = mean(propAccept_subj),
-              seAccept = sd(propAccept_subj)/sqrt(nSubjs_wth)) %>%
+              seAccept = sd(propAccept_subj)/sqrt(nSubjs_wth), .groups = 'drop') %>%
     ggplot(aes(Block, propAccept, color = Cost)) +
@@
             summarise(pAccept_1 = mean(Choice[Half=="Half_1"]),
-                      pAccept_2 = mean(Choice[Half=="Half_2"])) %>%
+                      pAccept_2 = mean(Choice[Half=="Half_2"]), .groups = 'drop') %>%
             group_by(Cost) %>%
@@
                       propAccept_2 = round(mean(pAccept_2), digits = 2),
-                      sdAccept_2 = round(sd(pAccept_2), digits = 2))
+                      sdAccept_2 = round(sd(pAccept_2), digits = 2), .groups = 'drop')
 
@@
   summarise(propAccept_1 = mean(Choice[Half=="Half_1"]),
-            propAccept_2 = mean(Choice[Half=="Half_2"])) %>%
+            propAccept_2 = mean(Choice[Half=="Half_2"]), .groups = 'drop') %>%
   ggplot(aes(propAccept_1, propAccept_2, fill = Cost)) +
@@
   summarise(mRT = mean(RT),
-            pComplete = mean(Outcome)) %>%
+            pComplete = mean(Outcome), .groups = 'drop') %>%
   group_by(Offer, Trial_Time, Half) %>%
@@
             meanProp = mean(pComplete),
-            seProp = sd(pComplete) / sqrt(48)) %>%
+            seProp = sd(pComplete) / sqrt(48), .groups = 'drop') %>%
   ungroup() %>%
@@
   summarise(propAccept = mean(Choice),
-            SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
+            SE = sd(Choice) / sqrt(nSubjs_wth), .groups = 'drop') %>%
   ungroup() %>%
@@
 
+&nbsp;
+
   For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm [@Huys2011; @Huys2012].
@@
 #### *Model Definitions*
+
+&nbsp;
 
@@
   group_by(Group) %>%
-  summarise(tresults = list(t.test(Fit, mu = 0)))
+  summarise(tresults = list(t.test(Fit, mu = 0)), .groups = 'drop')
 

### 2021-04-15 Manuscript.Rmd
cleaned up old code that had been commented out

@@
 
-<!-- NOTE: 
-If you're using Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
+<!-- NOTES: 
+- If you're using Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
+- This script is set so you can run each code snippet independently (after you run the setups and data loading snippets above the institutional affiliations)
 -->
@@
 
-# # Idea: do AIC to compare models per participant
-# # add an AR regressor to track recent quits
-# logisRHAR <- dataBtw %>%
-#               filter(Choice < 2) %>%
-#               group_by(SubjID) %>%
-#               mutate(AR = seqQuits(Choice)) %>%
-#               plyr::dlply("SubjID", identity) %>%
-#               lapply(function(data) {suppressWarnings(glm(Choice ~ Handling + Offer + AR, data = data, family = "binomial"))}) 
-#   
-# # get the AR CIs per participant 
-# AR_CIs <- sapply(logisRHAR, function(x) {tryCatch(suppressWarnings(confint(x)[4, ]), error = function(e){c(0, 0)})}) %>%
-#   replace_na(0) %>%
-#   t() %>%
-#   apply(1, function(x) (x[1] <= 0 & x[2] >= 0))
-# 
-# # coefficient summaries
-# logisRHAR <- sapply(logisRHAR, coefficients)
-# coeffRHAR_mean <- apply(logisRHAR, 1, mean, na.rm = T)
-# coeffRHAR_se <- apply(logisRHAR, 1, sd, na.rm = T) / sqrt(nSubjs_btw)
-# 
-# # Rank sum test
-# rankRHAR <- wilcox.test(logisRHAR["AR", ])
 ```
@@
 
-# Summary table for the linear model
-# panderOptions("digits", 2)
-# pander(lmEarn, style = "rmarkdown")
-
 ```
@@
 
-``` {r BTW: 16.1.4. Optimality (move to acceptance comparison eventually), echo = FALSE}
-# # in order
-# # clean data, 
-# # calculate each individual's prop. accept,
-# # calculate t.tests with optimality as null mean,
-# # correct pvalues with FDR
-# temp <- dataBtw %>%
-#   filter(Choice < 2) %>%
-#   group_by(SubjID, Handling, Offer, Cost) %>%
-#   summarise(pAccept = mean(Choice)) %>%
-#   mutate(optimal = case_when(
-#           (Handling == 10 & Offer < 8) ~ 0,
-#           (Handling == 14 & Offer < 20) ~ 0,
-#           TRUE ~ 1
-#         )) %>% 
-#   group_by(Handling, Offer, Cost) %>%
-#   summarise(meanAccept = mean(pAccept),
-#             sdAccept = sd(pAccept),
-#             optimal = unique(optimal),
-#             pvals = tryCatch(t.test(pAccept, mu = unique(optimal))$p.value, error = function(e) {1})) %>%
-#   mutate(FDR = p.adjust(pvals, method = "BY"),
-#          significant = FDR < 0.05)
-# 
-# 
-# # proportion of significant ones
-# # eventually find a way to plot this (or just place it further down)
-# # alternative per block: temp %>% group_by(Handling) %>% summarise(prop = mean(significant, na.rm = T))
-# optimalProp <- mean(temp$significant, na.rm = T) * 100
-# 
-# # proportion accepted per cost condition
-# optimalProp_cost <- temp %>% 
-#   group_by(Cost) %>% 
-#   summarise(propDeviations = round(mean(significant) * 100))
-
-## if you want to replicate the cost 3 method
-# this says that all but easy deviated from optimality in the observed direction
+``` {r BTW: 16.1.4. Optimality, echo = FALSE}
+# Determine whether groups over or under accepter versus optimal solution (50% for combined 4 and 8 cents)
 temp <- dataBtw %>%
@@
   as_tibble()
-
-# pairwise.wilcox.test(temp$pComplete, temp$Cost)
 
@@
 
-``` {r BTW: 16.2.2. rmANOVA, echo=FALSE,fig.align="center",fig.width=5,fig.height=4, results = 'asis'}
-## This section was removed because it was deemed redundant.
-The interaction is addressed once the a priori mixed effects logistic model is evaluated against multiple forms of interaction effects (16.2.4.).
-# temp <- dataBtw %>%
-#         filter(Choice < 2) %>%
-#         group_by(SubjID, Cost, Handling, Offer) %>%
-#         summarise(pAccept = mean(Choice))
-# 
-# ## REPEATED MEASURES ANOVA
-# # I think I like this the most
-# prop.aov <- with(temp, aov(pAccept ~ factor(Cost) * Handling * Offer + 
-#                                  Error(SubjID / (Handling * Offer))))
-# 
-# ## NOTES ON RESULTS
-# # According to the logistic fit, there are main effects for all predictors, but no interactions.
-It also says that the overall odds for the wait group to accept versus the effort is around 16%.
-Similarly, increasing the handling time results in a decrease in the multiplicative odds of ~25%.
-Increments in reward increase the odds of acceptance by ~40%.
-```
-
-``` {r BTW: 16.2.2. rmANOVA plot, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
+``` {r BTW: 16.2.2. prop plot for every parameter combo, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 6}
 # # code to calculate the rwd/sec rate for each acceptance threshold per handling (calculate the optimal solution)
@@
 
-# snippet on rmANOVA
-# These intuitions were formally tested using a repeated measures ANOVA, whose results are presented in the table below.
-Overall, the analysis partially confirmed our predictions.
-While all main effects were significant, there was an unexpected significant condition-by-reward interaction, which could be due to the performance of the "easy" group relative to their peers.
-Importantly, we found that the interaction between all three main parameters was not significant, thus suggesting that the effects of handling and reward on choices were not different across groups.
-
-```
-
-``` {r BTW: 16.2.2. rmANOVA table, pander}
-# # anova table
-# x <- summary(prop.aov)   
-# x <- x$`Error: Within`
-# panderOptions("digits", 2)
-# pander(x, style = "rmarkdown", split.table = 110)
 ```
@@
 
-```
-
-``` {r BTW: 16.2.3. Mixed Effects Model plot rand intercepts, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 4}
-# # random intercepts for each subject, with cost group and overall acceptances
-# RI <- ranef(mixLogis_main_btw$Wait)$SubjID[, 1]
-# RI <- dataBtw %>% 
-#   group_by(SubjID, Cost) %>% 
-#   summarise(pAccept = mean(Choice)) %>% 
-#   ungroup() %>%
-#   mutate(RI = RI)
-# 
-# # plot relationship between random intercept (RI) and proportion accepted per cost group
-# RI1 <- ggplot(data = RI, aes(RI, pAccept, color = Cost)) + 
-#   geom_vline(xintercept = 0, linetype = "dashed") +
-#   geom_smooth() + 
-#   geom_point(alpha = 0.5) + 
-#   scale_color_manual(values = colsBtw) +
-#   theme_classic()
 ```
@@
 ``` {r BTW: 16.3.2. Pre/Post Break, echo = FALSE, fig.align = "center", fig.width = 5, fig.height = 5}
-# # divide the data into proportion accepted before/after the break (one per column)
-# temp <- dataBtw %>%
-#   filter(Choice < 2) %>%
-#   group_by(SubjID, Cost, Half) %>%
-#   summarise(pAccepted = mean(Choice)) %>%
-#   ungroup() %>%
-#   spread(Half, pAccepted)
-#
-# # separate by cost type and compute a linear model to predict half 2 from 1
-# sep <- temp %>% plyr::dlply("Cost", identity)
-# prepost <- list()
-# prepost$LM <- lapply(sep, function(data) {lm(data$Half_2 ~ data$Half_1)})
-# 
-# # get the coefficients and confidence intervals
-# # and concatenate
-# prepost$summary <- as.data.frame(cbind(t(sapply(prepost$LM, coefficients)), t(sapply(prepost$LM, confint))))
-# colnames(prepost$summary) <- c("Intercept", "Coefficient", "Int_CI-low", "Int_CI-high", "Beta_CI-low", "Beta_CI-high")
-
-## PRE/POST PAIRED PERMUTATIONS
+## half-wise paired permutations on acceptance rates per group
+# group data per experimental half
 temp <- dataBtw %>%
@@
 
-# # aand plot
+# # aand plot pairwise coefficients among costs
 # corrplot(betaMat, 
@@
 
-# # plot to match the one in Cost 2, even though we only have offer as an influence
+# # plot to match the one in Exp 1, even though we only have offer as an influence
 # ggplot(data = baseCoeffs, aes(x = "Offer", y = Offer)) +
@@
 
-# old
-# # Create an autoregressive predictor based on previous consecutive quits
-# dataList <- lapply(dataList, function(data) {data %>% mutate(AR = seqQuits(Choice))})
-# 
-# # fits per participant
-# logisticFits_base <- lapply(dataList, function(data) {suppressWarnings(glm(Choice ~ Offer + AR, data = data, family = "binomial"))}) 
-# 
-# # get the low/high 95% CIs for AR
-# baseCoeffs <- as_tibble(t(sapply(logisticFits_base, function(data) {suppressWarnings(confint(data, "AR"))}))) %>% 
-#   dplyr::rename(AR_CILow = `2.5 %`, AR_CIHigh = `97.5 %`) %>%
-#   mutate(SubjID = subjList_wth) %>%
-#   left_join(baseCoeffs, by = "SubjID")
-# 
-# # reorder so that SubjID comes first
-# #baseCoeffs <- baseCoeffs[ , c(3,4,5,6,7,8,9,1,2)]
-# 
-# # create a vector indicating whether 0 is included or not (i.e. if there is 0, no sequential effect)
-# # but first change NA to 0 (visual inspection showed that NAs were tied to p's with full or near full p(accept), meaning they weren't influenced by history)
-# baseCoeffs <- baseCoeffs %>% 
-#   mutate(AR_CILow = ifelse(is.na(AR_CILow), 0, AR_CILow),
-#          AR_CIHigh = ifelse(is.na(AR_CIHigh), 0, AR_CIHigh))
-# baseCoeffs$AR_effect <- apply(baseCoeffs, 1, function(x) (!(as.numeric(x["AR_CILow"]) <= 0 & as.numeric(x["AR_CIHigh"]) >= 0)))
 ```
@@
 
-# extra analyses
-# a pre-post paired permutation on earnigs confirms no differences (more evidence in section 16.3.3--prepost)
-# this means that, at least in general, participants are not changing their behavior due to monetary incentives
-# but because of something else, maybe like fatigue (this pattern holds even at finer subdivisions)
-# PPearn <- dataWth %>%
-#           #filter(Block %in% c(1,2,5,6)) %>%
-#           mutate(Choice = ifelse(Choice > 1, 0, Choice)) %>%
-#           group_by(SubjID, Half) %>%
-#           summarise(Earnings = sum(Offer[Choice == 1] / 100),
-#                     pComplete = mean(Choice)) %>%
-#           ungroup() %>% 
-#           select(SubjID, Half, Earnings) %>% 
-#           spread(Half, Earnings)
-# 
-# permute(PPearn$Half_1, PPearn$Half_2, paired = TRUE)
 ```
@@
 
-``` {r WTH: 16.2.1. Overall Proportion diffs, fig.align = "center", fig.width = 6, fig.height = 4, echo = FALSE}  
-# ## ECDF of proportion completed per cost type
-# temp <- dataWth %>%
-#         filter(Choice < 2) %>%
-#         #mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait_0", "Wait_1"))) %>%
-#         group_by(SubjID, Cost) %>%
-#         summarise(pComplete = mean(Choice))
-# 
-# 
-# # plots
-# (p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
-#         geom_boxplot(show.legend = F) +
-#         scale_fill_manual(values = colsWth) +
-#         ylim(c(0, 1)) +
-#         labs(y = "Proportion Completed") +
-#         theme(panel.grid.major = element_blank(), 
-#             panel.grid.minor = element_blank(), 
-#             panel.background = element_blank(), 
-#             axis.line = element_line(colour = "black"),
-#             text = element_text(size = 16)))
-
-```
-
 ``` {r WTH: 16.2.1. mixed effect models, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 5}
-# both methods yield similar outputs, at least coefficients and pvalues
-# but the likelihoods will differ of course. The second one might be better in terms of computational needs.
-# method 1
-# mixLogis_main_wth <- list()
-# mixLogis_main_wth$Cog <- glmer(Choice ~ Cost + Offer + (1 | SubjID), family = "binomial", data = data)
-
 # mixed effects logistics, rotating the reference cost condition
@@
 
+# rotate reference (cost group) to assess all pairwise comparisons
 mixLogis_main_wth$Cognitive <-  glmer(cbind(totalAccepted, totalQuits) ~ Cost + Offer + (1 | SubjID), family = "binomial", data = mixData)
@@
 ``` {r WTH: 16.3.3. pre-post, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4, include = F}
-# # restructure the data
-# temp <- dataWth %>%
-#   filter(!(Block %in% c(3, 4))) %>%
-#   group_by(SubjID, Cost, Half) %>%
-#   summarise(propAccepted = mean(Choice)) %>%
-#   ungroup() %>%
-#   spread(Half, propAccepted)
-# 
-# # compute the mixed effects model (linear for this)
-# mixLogis_prepost <- lmer(Half_2 ~ Half_1 + Cost -1 + (1 | SubjID), data = temp)
-# 
-# # get the coefficients and confidence intervals
-# t1 <- coefficients(mixLogis_prepost)$SubjID[1, 2:6]
-# t2 <- as.data.frame(t(confint(mixLogis_prepost)[3:7,]))
-# 
-# # and concatenate them
-# summary_prepost <- t(bind_rows(t1, t2))
-# colnames(summary_prepost) <- c("Coefficient", "CI-low", "CI-high")
-#
-# # prepost half paired perms
-# temp <- temp %>% plyr::dlply("Cost", identity) 
-# prepost <- list()
-# prepost$cohen <- sapply(temp, function(data) {DescTools::CohenD(data$Half_1, data$Half_2)})
-# prepost$perm <- sapply(temp, function(data) {permute(data$Half_1, data$Half_2, paired = T, simple = T)})
-
 ## paired tests for first versus last block per cost type
@@
 
-# ## PROPORTION OF COGNITIVE ACCEPTANCES NOT DIFFERENT BETWEEN FIRST HALF OF WITHIN AND BETWEEN EXPERIMENTS
+#### Exploratory analyses (plots that give more info, but are not straightforward to interpret) ####
+# ## PROPORTION OF COGNITIVE ACCEPTANCES NOT DIFFERENT BETWEEN FIRST HALF OF BOTH EXPERIMENTS
 # btw <- dataBtw %>%
@@
 
-### CODE TO LOOK AT EARNINGS PER BLOCK AND CALCULATE OPTIMAL EARNINGS
-# # code to calculate the rwd/sec rate for each acceptance threshold per handling
-# rwd <- c(4, 8, 20)
-# handling <- c(14, 10, 2) + 2 # add 2 to H and T to account for offer and reward disclosure windows
-# travel <- c(2, 6, 14) + 2
-# rwdRates <- sapply(3:1, function(thresh) {(sum(tail(rwd, n = thresh))) / ((handling * thresh) + (travel * 3))})
-# 
-# # the highest reward amount for a typical 7-min block per handling is:
-# apply(rwdRates, 1, max) * (7 * 60)
-
-# # this helps make sense of the toal earnings
-# # plotting mean earnings per cost and block
-# dataWth %>%
-#   filter(rawChoice == 1) %>%
-#   group_by(SubjID) %>%
-#   mutate(Block = case_when(
-#     Block %in% c(1, 2) ~ 1,
-#     Block %in% c(3, 4) ~ 2,
-#     Block %in% c(5, 6) ~ 3
-#   )) %>%
-#   group_by(SubjID, Cost, Block) %>%
-#   summarise(subEarnings = sum(Offer)) %>%
-#   group_by(Cost, Block) %>%
-#   summarise(meanEarned = mean(subEarnings),
-#             seEarned = sd(subEarnings) / sqrt(nSubjs_wth)) %>%
-#   ggplot(aes(Block, meanEarned, color = Cost)) +
-#     geom_point(size = 2) +
-#     geom_errorbar(aes(ymin = meanEarned - seEarned, ymax = meanEarned + seEarned, color = Cost), width = 0.1, size = 1.5) +
-#     geom_line(size = 1.5) +
-#     labs(y = "Mean Earnings +- SE (cents)") +
-#     scale_x_continuous(breaks = c(1, 2, 3)) +
-#     scale_color_manual(values = colsWth) +
-#     scale_fill_manual(values = colsWth) +
-#     theme(legend.key = element_blank(),
-#           #legend.position = c(0.1, 0.8),
-#           panel.grid.major = element_blank(),
-#           panel.grid.minor = element_blank(),
-#           panel.background = element_blank(),
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 22))
-
 ```
@@
 
-``` {r WTH: 16.3.3 temp plots, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
-# cw <- dataWth %>%
-#   group_by(SubjID) %>%
-#   mutate(Block = case_when(
-#     Block %in% c(1, 2) ~ 1,
-#     Block %in% c(3, 4) ~ 2,
-#     Block %in% c(5, 6) ~ 3
-#   )) %>%
-#   filter(Offer < 20) %>%
-#   filter(Block != 2) %>%
-#   group_by(SubjID, Block, Cost, Offer) %>%
-#   summarise(pAccept = mean(Choice)) %>%
-#   spread(Block, pAccept) %>%
-#   mutate(diff = `3` - `1`) %>%
-#   ungroup() %>%
-#   select(-c(`1`, `3`)) %>%
-#   spread(Cost, diff) %>%
-#   ggplot(aes(Cognitive, `Wait-C`, fill = as.character(Offer))) +
-#     geom_point(pch = 21, color = "black", size = 3) +
-#     geom_hline(yintercept = 0) +
-#     geom_vline(xintercept = 0) +
-#     geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
-#     ylim(-1, 1) +
-#     xlim(-1, 1) +
-#     labs(#title = "P(Accepted): Last - First Block",
-#          x = "P(Cognitive): Last - First",
-#          y = "P(Wait-C): Last - First",
-#          fill = "Offer") +
-#     theme(legend.key = element_blank(),
-#           legend.background = element_rect(fill = "grey80"),
-#           legend.position = c(0.8, 0.8),
-#           panel.grid.major = element_blank(), 
-#           panel.grid.minor = element_blank(), 
-#           panel.background = element_blank(), 
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 16))
-# 
-# gw <- dataWth %>%
-#   group_by(SubjID) %>%
-#   mutate(Block = case_when(
-#     Block %in% c(1, 2) ~ 1,
-#     Block %in% c(3, 4) ~ 2,
-#     Block %in% c(5, 6) ~ 3
-#   )) %>%
-#   filter(Offer < 20) %>%
-#   filter(Block != 2) %>%
-#   group_by(SubjID, Block, Cost, Offer) %>%
-#   summarise(pAccept = mean(Choice)) %>%
-#   spread(Block, pAccept) %>%
-#   mutate(diff = `3` - `1`) %>%
-#   ungroup() %>%
-#   select(-c(`1`, `3`)) %>%
-#   spread(Cost, diff) %>%
-#   ggplot(aes(Physical, `Wait-P`, fill = as.character(Offer))) +
-#     geom_point(pch = 21, color = "black", size = 3, show.legend = F) +
-#     geom_hline(yintercept = 0) +
-#     geom_vline(xintercept = 0) +
-#     geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
-#     ylim(-1, 1) +
-#     xlim(-1, 1) +
-#     labs(#title = "P(Accepted): Last - First Block",
-#          x = "P(Physical): Last - First",
-#          y = "P(Wait-P): Last - First",
-#          fill = "Offer") +
-#     theme(legend.position = c(0.8, 0.8),
-#           panel.grid.major = element_blank(), 
-#           panel.grid.minor = element_blank(), 
-#           panel.background = element_blank(), 
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 16))
-# 
-# 
-# grid.arrange(cw, gw, ncol = 2)
-# 
-# # more prepost tests
-# # diffscore prepost for effort vs wait
-# dataWth %>%
-#   group_by(SubjID) %>%
-#   mutate(Block = case_when(
-#     Block %in% c(1, 2) ~ 1,
-#     Block %in% c(3, 4) ~ 2,
-#     Block %in% c(5, 6) ~ 3
-#   )) %>%
-#   #filter(Half == "Half_1", Offer < 20) %>%
-#   filter(Block != 2) %>%
-#   mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
-#   group_by(SubjID, Cost, Block, Offer) %>%
-#   summarise(propAccept = mean(Choice)) %>%
-#   ungroup() %>%
-#   #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-#   spread(Block, propAccept) %>%
-#   mutate(Difference = `Last Block` - `First Block`) %>%
-#   group_by(SubjID, Cost) %>%
-#   summarise(Diffscore = sum(Difference)/3) %>%
-#   spread(Cost, Diffscore) %>%
-#   ggplot() +
-#     geom_point(aes(Cognitive, Wait-C), color = colsWth[1]) +
-#     geom_point(aes(Physical, Wait-P), color = colsWth[2]) +
-#     geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-#     ylim(-0.5, 0.5) +
-#     xlim(-0.5, 0.5) +
-#     #geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
-#     #geom_boxplot(show.legend = F, size = 1.5) +
-#     #geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
-#     #scale_color_manual(values = colsWth) +
-#     #scale_fill_manual(values = colsWth) +
-#     theme(legend.key = element_blank(),
-#           legend.position = c(0.9, 0.25),
-#           panel.grid.major = element_blank(), 
-#           panel.grid.minor = element_blank(), 
-#           panel.background = element_blank(), 
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 22))
-# 
-# # diffscore per cost type (you don't see if specific subjects are prone to increasing/decreasing acceptances across them)
-# dataWth %>%
-#   group_by(SubjID) %>%
-#   mutate(Block = case_when(
-#     Block %in% c(1, 2) ~ 1,
-#     Block %in% c(3, 4) ~ 2,
-#     Block %in% c(5, 6) ~ 3
-#   )) %>%
-#   #filter(Half == "Half_1", Offer < 20) %>%
-#   filter(Block != 2) %>%
-#   mutate(Block = ifelse(Block == 1, "First Block", "Last Block")) %>%
-#   group_by(SubjID, Cost, Block, Offer) %>%
-#   summarise(propAccept = mean(Choice)) %>%
-#   ungroup() %>%
-#   #mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
-#   spread(Block, propAccept) %>%
-#   mutate(Difference = `Last Block` - `First Block`) %>%
-#   group_by(SubjID, Cost) %>%
-#   summarise(Diffscore = sum(Difference)/3) %>%
-#   ggplot(aes(Cost, Diffscore, fill = Cost)) +
-#     geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
-#     geom_boxplot(show.legend = F, size = 1.5) +
-#     geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
-#     scale_color_manual(values = colsWth) +
-#     scale_fill_manual(values = colsWth) +
-#     theme(legend.key = element_blank(),
-#           legend.position = c(0.9, 0.25),
-#           panel.grid.major = element_blank(), 
-#           panel.grid.minor = element_blank(), 
-#           panel.background = element_blank(), 
-#           axis.line = element_line(colour = "black"),
-#           text = element_text(size = 22))
-```
-
 ```{r Survival and prepost plots (Fig.
@@
 ### Compare/analyze fits
-## BTW
+## Exp 1
 # first, divide the group fits into a list of dataframes for each parameter
@@
 ### plot parameter boxplots
-## BTW
+## Exp 1
 param <- do.call(rbind, aovShape_btw)
@@
 
-## WTH
+## Exp 2
 paramPlot_wth <- melt(fits_wth$`Adaptive OC + Adaptive Between Biased OC`$x) %>%

### 2021-04-21 Manuscript.Rmd
remove redundant package call

@@
 library(survival)
-library(ggfortify)
 library(patchwork)

### 2021-05-19 Manuscript.Rmd
added the option to draft latex eqs automatically for mixed effects models

@@
 library(data.table)
+# library(equatiomatic) # with the dev version, you can extract latex equations for the mixed-effects models using e.g. extract_eq(mixLogis_main_btw$Wait)
 

### 2021-05-28 Manuscript.Rmd
revised intro

@@
 
-  Evaluating whether to pursue a desirable outcome often entails assessing the demands required for obtaining it.
-In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards [@Shenhav2017; @Westbrook2015; @Frederick2002; @Walton2006].
-Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2010; @Kool2018; @Treadway2009; @Westbrook2013].
-However, people still needlessly pursue effortful courses of action in everyday decisions.
-Emerging experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcomes, whereby exerting effort boosts the perceived value of its outcomes [@HernandezLallement2014; @Kacelnik2002; @Mochon2012], and positive outcomes imbue value into their preceding effortful behavior [i.e.
+  Evaluating whether to pursue a desirable outcome often entails assessing the time and effort it will require.
+In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards.
+Decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort [@Ainslie1975; @Hull1943; @Kool2010; @Kool2018; @Treadway2009; @Westbrook2013; @Shenhav2017; @Westbrook2015; @Frederick2002; @Walton2006].
+However, people also sometimes appear to favor effortful courses of action in everyday decisions.
+Experimental and theoretical work has chiefly explained this phenomenon by suggesting a reciprocal relationship between effort and outcomes, whereby exerting effort boosts the perceived value of ensuing outcomes [@HernandezLallement2014; @Kacelnik2002; @Mochon2012], and positive outcomes imbue value into the preceding effortful behavior [i.e.
 learned industriousness, @Eisenberger1992].
-Though intuitively valid and empirically supported, this explanation leaves open questions about what features of an effortful task can make it attractive in its own right, and how contextual factors mold its perceived costs [@Inzlicht2018].
-Understanding what governs the intrinsic costs and rewards of effort could improve our ability to motivate completion of effortful daily activities, such as schoolwork or physical exercise.
-
-  Recent work has proposed that the subjective costs produced by delays and cognitive effort are modulated by the possibility of missing out on better concurrent alternatives, implying that decision makers track the *opportunity cost of time* [OC, @Fawcett2012; @Kurzban2013; @Otto2019].
-Preferences for effortful courses of action could therefore arise from the presence of other types of demands and opportunities in the same choice environment [@Kool2018].
-For example, exerting high effort for a reward might be aversive, but the same level of work might be appealing in comparison to the boredom of an equivalent period of passive waiting (e.g.
-taking the cumbersome way home rather than waiting for a delayed train, even if the resulting time of arrival is the same).
-This effect of context on effort preferences has been illustrated by experiments on charitable giving, in a which high-effort donation method (such as a run) attracted larger donations than a low-effort method (such as a picnic) when either was available alone (the “martyrdom effect”), but the high-effort event was disfavored when both options were offered as alternatives [@Olivola2013].
-
-  Standard models in neuroeconomics and behavioral economics cannot readily address this possibility.
-The effects on valuation of different types of effort or delay have traditionally been formalized with discounting functions that capture how much less appealing a reward becomes as a function of the associated amount of effort or delay [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @kleinflugge2015; @Kool2010; @Westbrook2013].
-An advantage of relying on these standardized functions is that they can circumvent a key confound when comparing effort and delay, namely that increasingly effortful tasks also tend to take longer to perform.
-However, although this line of work suggests that discounting functions are similar for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], there is ongoing debate about the shape of the discounting function across types of demands [@Arulpragasam2018; @Biaaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010], and the degree to which discount rates correlate across cost domains [@Seaman2018; @Westbrook2013].
-Further, this approach does not directly probe which type of demand people would prefer if given the option, and constrains the understanding of behavioral demands to one in which such demands are bound to reduce the value of prospects.
-
-  This evidence sets the stage for examining what people would actually select in environments that intermixed multiple types of demands, including cognitive, physical effort, and delay.
-Single choice foraging paradigms provide a natural way to interrogate preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during the same time period instead [@Constantino2015; @Garrett2020; @Krebs1977; @Mobbs2018; @Stephens1986].
-Such paradigms probe the perceived opportunity cost of time, which has been hypothesized to underlie the evaluation of behavioral costs [@Kurzban2013].
-Specifically, foragers must decide whether to spend their limited time by harvesting their currently available resource or by seeking out more profitable (or less costly) alternatives.
-This could involve, for example, deciding when to leave a patch of depleting richness (e.g.
-when to quit a job that provides diminishing opportunities for growth), or choosing whether to pursue or forgo offers presented serially (e.g.
-whether to accept your first job offer or wait for new potential ones).
-Here we focus on this latter type of foraging, traditionally called prey foraging [@Krebs1977], as it provides a means to examine how choices to accept or reject individual prospects are influenced by contextual knowledge about other potentially obtainable alternatives in the same environment.
-
-  Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionarily conserved choice behaviors [@Hayden2018; @Mobbs2018], and offers a number of desirable qualities to address our question.
-First, it allows for the estimation of optimal, reward maximizing choice patterns on the basis of the opportunity cost of time [@Charnov1976; @Krebs1977].
-The opportunity cost depends on the richness of the environment, which can be experimentally manipulated by balancing the amount of time it takes to harvest an offer (*handling time*) versus to search for new ones (*travel time*).
-We can then interpret observed deviations from such optimal behavior, and examine how foraging behavior changes when the handling time is filled with cognitive effort or physical effort in comparison with unfilled delay (thus disentangling effort from delay duration).
-Second, in contrast to multi-alternative economic choice paradigms that often treat choices as independent observations, the sequential nature of foraging encourages individuals to consider both focal and global elements of the decision context.
-For example, the cost (or value) of effort and delay could globally depend on the availability of alternative demands, impacting the perceived opportunity cost of time.
-Alternatively, it could be intrinsic and robust to such manipulation, and/or depend on task-specific factors that are adjusted once individuals experience different forms of behavioral costs.
-Foraging rests on an abundant modeling history that provides computational tools to formalize relevant decision variables [@Stephens1986].
+These proposals raise questions about what features can make an effortful task attractive in its own right, and how contextual factors can alter its perceived costs [@Inzlicht2018].
+Understanding what governs the intrinsic costs and rewards of effort could improve our ability to motivate completion of effortful daily activities such as schoolwork or physical exercise.
+
+  Recent work has proposed that the subjective costs of delay and cognitive effort are modulated by the value of the alternative ways one's time and cognitive resources could otherwise be used, implying that decision makers track *opportunity costs* [@Fawcett2012; @Kurzban2013; @Otto2019].
+Preferences for or against effortful courses of action could therefore depend on the presence of other types of demands and opportunities in the same choice environment [@Kool2018].
+For example, exerting high effort for a reward might be aversive, but the same level of work might become appealing if the only alternative is the boredom of an equivalent period of passive waiting (for instance, a person might choose to take a cumbersome way home rather than wait for a delayed train, even if the resulting time of arrival is the same).
+Effects of context on effort preferences have been illustrated by experiments on charitable giving, in a which high-effort donation method (such as a run) attracted larger donations than a low-effort method (such as a picnic) when either was available alone (the “martyrdom effect”), but the high-effort event was disfavored when both options were offered as alternatives [@Olivola2013].
+
+  **Standard models in neuroeconomics and behavioral economics formalize the effects of effort or delay on valuation in terms of discounting functions** [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @kleinflugge2015; @Kool2010; @Westbrook2013].
+Discounting functions appear to have a similar form for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], although there is ongoing debate about how the shape of the discounting function might vary across types of demands [@Arulpragasam2018; @Biaaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010] and the degree to which discount rates correlate across cost domains [@Seaman2018; @Westbrook2013].
+A limitation of the discounting approach is that it does not directly probe how aspects of the decision context, such as opportunity costs, might influence cost evaluation, and constrains the understanding of behavioral demands to one in which such demands necessarily reduce the value of prospects.
+
+  Single choice foraging paradigms, in which decision makers choose to accept or reject individually presented prospects, provide a natural way to investigate contextual influences on cost evaluation [@Constantino2015; @Garrett2020; @Krebs1977; @Mobbs2018; @Stephens1986].
+Such paradigms require weighing a prospective reward against the perceived opportunity cost of time.
+Specifically, foragers must decide whether to spend their limited time by harvesting a currently available resource or by seeking out more profitable (or less costly) alternatives instead.
+This could involve, for example, deciding when to leave a patch of depleting richness **(e.g.
+when to quit a job that provides diminishing opportunities for growth)**, or choosing whether to pursue or forgo offers presented serially **(e.g.
+whether to accept your first job offer or wait for new potential ones)**.
+Here we focus on this latter type of foraging, traditionally called *prey selection* [@Krebs1977], as it provides a means to examine how choices to accept or reject individual prospects are influenced by contextual knowledge about other potentially obtainable alternatives in the same environment.
+
+  Foraging has recently attracted high scientific interest due to its ecological validity, which is rooted in evolutionarily conserved choice behaviors [@Hayden2018; @Mobbs2018].
+The prey selection foraging paradigm allows for the estimation of optimal, reward maximizing choice patterns on the basis of the opportunity cost of time [@Charnov1976; @Krebs1977].
+The opportunity cost depends on the richness of the environment, which can be experimentally manipulated by balancing the amount of time it takes to harvest an offer (*handling time*) and to search for a new one (*travel time*).
+We can then interpret observed deviations from such optimal behavior, and examine how foraging behavior changes when the handling time is filled with cognitive or physical effort in comparison with an unfilled delay (thus disentangling effort from delay duration).
+In contrast to multi-alternative economic choice paradigms, which often treat choices as independent events, the sequential nature of foraging encourages individuals to consider both focal and global elements of the decision context.
+Extensive previous work on modeling foraging decisions provides computational tools to formalize relevant decision variables [@Stephens1986].
 
@@
 cognitive effort, physical effort, and delay).
-Experiment 1 used a between-subject design in which participants foraged for rewards of varying magnitudes that imposed varying durations of a single form of demand.
+Experiment 1 used a between-subject design in which each participant foraged for rewards of varying magnitudes that imposed varying durations of a single form of demand.
 Experiment 2 used a within-subject design in which individuals foraged for varying forms of demand in addition to varying reward magnitudes.
-We leveraged the ecological and computational richness of foraging paradigms to provide new insights on a number of open questions [@Inzlicht2018].
 First, we examined whether the discounting effects consistently observed in multi-alternative economic choice paradigms persisted when these options were presented serially, and whether the resulting foraging patterns depended on the demands imposed to obtain rewards.
 The existence of a well-defined optimal, reward-maximizing choice strategy helped us identify when demands boosted or detracted from the value of rewards (signified by tendencies to overharvest poor offers or underharvest advantageous offers, respectively).
-Second, we probed whether the perceived cost (or value) of demands was intrinsic or dependent on either task-specific or contextual characteristics.
-For instance, varying the level of exposure to multiple types of demands across experiments allowed us to assess whether cost evaluation was dependent on the availability of alternative avenues of action.
+Second, we probed whether the perceived cost (or value) of demands was intrinsic or context-dependent.
+Varying the level of exposure to multiple types of demands across experiments allowed us to assess whether cost evaluation was dependent on the availability of alternative avenues of action.
 Further, including cognitive demands and physical demands let us examine whether such effects might apply differently to distinct types of effort.
 
-  Our results provided mixed support for our pre-registered hypotheses, which are detailed in https://osf.io/2rsgm/.
-For Experiment 1, we hypothesized that 1) decision makers would integrate reward and timing information in order to approximate optimal foraging strategies, as reflected by acceptance rates; 2) acceptance rates would be higher for trials that demanded physical effort and cognitive effort than for unfilled delay or effortless engagement (based on the apparent value of effort displayed by charitable donors, as described above); and 3) choices would be consistent within trials, reflected by few choice reversals, and acceptance rates for each type of demand would remain stable over time.
-Confirming our predictions, we found that individuals could approximate optimality by preferring higher rewards and shorter delays, regardless of the richness of the environment.
-We also found that people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups under-accepted, partially matching our predictions and highlighting that cognitive effort can add value to outcomes.
-Finally, acceptances (and differences among demands) were both consistent and stable within each cost condition, in line with expectations.
-For Experiment 2, we hypothesized that 1) acceptance rates would once again approximate optimality, and would show effects of reward magnitude similar to those seen in Experiment 1; 2) in contrast to Experiment 1, participants would gravitate towards unfilled delays to obtain rewards; and 3) that choices would be consistent and stable over time.
+  Our results provided mixed support for our pre-registered hypotheses, which are detailed in https://osf.io/2rsgm/registrations.
+For Experiment 1, we hypothesized that 1) decision makers would integrate reward and timing information in order to approximate optimal foraging strategies, as reflected by acceptance rates; 2) acceptance rates would be higher for trials that demanded physical effort and cognitive effort than for unfilled delay or effortless engagement (based on results from pilot data and previous findings from single-alternative choice paradigms; e.g., Olivola & Shafir, 2013.
+See also Eisenberger, 1992; Inzlicht et al., 2018); and 3) acceptance rates for each type of demand would remain stable over time, and participants would rarely exhibit within-trial reversals (accepting a trial but then quitting without receiving the reward).
+Consistent with our predictions, we found that individuals could approximate optimality by favoring higher rewards and shorter delays.
+We also found that people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups under-accepted, partially matching our predictions but raising the possibility that cognitive effort might add value to outcomes (or attenuate subjective temporal costs).
+Finally, acceptance rates (and differences in acceptance rates across demands) were stable within each cost condition, in line with expectations.
+These findings motivated the design of Experiment 2, in which effort and delay trials were intermixed so that rejecting a trial of one type could potentially lead to a trial of the other type.
+For Experiment 2, we hypothesized that 1) acceptance rates would once again approximate optimality, and would show effects of reward magnitude similar to those seen in Experiment 1; 2) in contrast to Experiment 1, participants would accept unfilled-delay trials at a higher rate than trials with either form of effort; and 3) that choices would be consistent and stable over time.
 As before, decision makers approached the optimal strategy for the foraging environment, resembling the pattern observed in Experiment 1.
-Contrary to our second and third hypotheses, we found that a preference for cognitive effort was present initially but disappeared over time as decision makers foraged for types of demands in addition to rewards.
+Contrary to our second and third hypotheses, we found that acceptance rates were initially higher for cognitive effort than for delay, but this apparent preference disappeared over time as decision makers foraged for types of demands in addition to rewards.
 
   Computational modeling results suggested that the normative predictions of traditional foraging models were insufficient to explain our data.
-Instead, the data supported a model in which demands imposed a bias on the estimated opportunity cost of time, which converged as individuals gained experienced with interleaved types of demands.
+Instead, the data supported a model in which demands imposed a bias on the estimated opportunity cost of time, which converged as individuals gained experience with interleaved types of demands.
 We hypothesize that this bias arises from modulations of subjective time.
 For instance, cognitive effort could have become appealing by virtue of compressing the perceived trial time, a perception that could be recalibrated with exposure to alternative demands.
-The subjective shortening of experienced durations during cognitive effort could be due to the ongoing recruitment of working memory (e.g.
+A subjective shortening of experienced durations during cognitive effort could be due to the ongoing recruitment of working memory (e.g.
 preventing individuals from estimating the elapsed time), or because the discrete events within the cognitive task subdivided the time interval.

### 2021-05-28 Manuscript.Rmd
working on revising methods

@@
   The study was preregistered with the Open Science Framework (https://osf.io/2rsgm/registrations).
-The code employed for all analyses can be found in https://github.com/ctoroserey/Cost_studies.
+The data and code for all analyses can be found in https://github.com/ctoroserey/Cost_studies.
 All experimental procedures were approved by the Boston University Institutional Review Board, and written consent was acquired for all participants.
-For Experiment 1, we recruited individuals until a desired number of 84 eligible participants was achieved (58 Female, median age = 21, range = 18 - 31; number excluded before reaching goal = 8).
+For Experiment 1, we recruited individuals until the planned number of 84 eligible participants was achieved (58 Female, median age = 21, range = 18 - 31; number excluded before reaching goal = 8).
 The sample size was determined by means of power analysis (ANOVA), using a significance level of 0.05, power of 0.8, an effect size of f = 0.45 (estimated from a pilot study), and three groups (one for each cost type).
 The resulting per-group sample was 20, which we increased to 21 in order to match three possible block orders.
-We added an extra group of 21 participants who experienced a minimally effortful condition in order to determine whether effort or pure engagement were driving our results.
-
-  Participant data sets could be excluded based on any of the following preregistered criteria: 1) Consent: If they withdrew their participation; 2) Inattentiveness: a catch trial was placed at the end of each experimental block, asking participants to press a key within 3 seconds (time requirement based on pilot study response times).
-A participant who failed two or more of these checks was excluded and replaced.
-3) Improbable choice behavior: The task was structured so that one reward amount must always be accepted.
-A participant who quit every trial in at least one block was assumed not to have followed or understood task instructions, or to have disengaged from the task altogether.
+We added an extra group of 21 participants who experienced a minimally effortful condition in order to determine whether effort or mere task engagement was driving our results.
+
+  Participant data sets could be excluded on the basis of any of the following preregistered criteria: 1) Withdrawal: if the participant did not complete the study (1 participant); 2) Inattentiveness: a catch trial was placed at the end of each experimental block, asking participants to press a key within 3 seconds (time requirement based on pilot study response times).
+A participant who failed two or more of these checks was excluded and replaced (5 participants).
+3) Improbable choice behavior: The task was structured so that the largest reward amount should always be accepted.
+A participant who quit every trial in at least one block was assumed not to have followed or understood task instructions, or to have disengaged from the task altogether (0 participants).
 4) Performance: Participants were forced to travel if they made 2 mistakes in a cognitive effort trial (see task procedures below), or if they gripped below threshold during physical trials.
-Any participant with more than 30% forced travels was excluded.
+Any participant with more than 30% forced travels was excluded (1 participant).
 
@@
 
-  All experimental tasks were implemented using PsychoPy 2 [v1.85.1, @Peirce2019] on a Macbook Pro laptop.
-In this task, participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay (Fig.
+  The experimental task was run using PsychoPy 2 [v1.85.1, @Peirce2019] on a Macbook Pro laptop.
+Participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay (Fig.
 1A).

### 2021-05-28 Manuscript.Rmd
fixed figure and tiny data measurement error (1 decision RT off by 2s in 1 subj)

@@
 Physical and easy groups showed slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
-This resulted in some individuals opting to wait for that second to indicate an offer rejection (the censor at 4s in the physical group was a completion during a 2 s handling trial that was incorrectly recorded as 4 s by the experimental code).
+This resulted in some individuals opting to wait for that second to indicate an offer rejection.
 Plotting the quitting time distributions across blocks for the first second of the handling time (ECDFs on Fig.
@@
 The order of blocks was repeated in the second half (indicated by the black dashed line)."}
-# plots generated in 16.3.1. and 16.3.2.
+# individual plots generated in 16.3.1. and 16.3.2.
+# to recreate the combined plot and save it:
 # historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)

### 2021-05-28 Manuscript.Rmd
exp 1 methods revised

@@
 - This script is set so you can run each code snippet independently (after you run the setups and data loading snippets above the institutional affiliations)
+- Numbers on each chunk correspond generally to sections in the preregistrations
 -->
@@
   The experimental task was run using PsychoPy 2 [v1.85.1, @Peirce2019] on a Macbook Pro laptop.
-Participants foraged for monetary rewards in an environment in which each trial required either physical effort or cognitive effort for a set period of time (the “handling time”), or an equivalent unfilled delay (Fig.
+Participants foraged for monetary rewards in an environment in which each trial required physical effort, cognitive effort, or passive waiting for a set period of time (the “handling time”) in order to obtain the reward (Fig.
 1A).
-Their goal was to maximize their gains within a fixed amount of time.
-On each trial a monetary offer was displayed for 2 s, and participants had the opportunity to expend time and/or effort during the handling time in order to earn it.
-Upon completion of a trial, participants saw a 2 s window displaying the reward obtained, which was followed by a travel time to the next offer.
-Alternatively, the participant could quit at any point during the handling time by pressing the spacebar on the computer, and immediately start traveling.
-
-  Each participant was assigned to one of three types of costs (cognitive effort, physical effort, or delay), and a fourth group of equal size faced an effortless physical task that involved minimal gripping.
-This latter condition was added to discard the possibility that any differences in acceptances between effort and delay were driven by engagement alone.
+Their goal was to maximize their gains within a fixed total amount of playing time (six 7-minute blocks).
+On each trial, a monetary offer was displayed for 2 s, and participants had the opportunity to expend time and/or effort during the handling time in order to earn it.
+Upon completion of a trial, participants saw a 2 s feedback message displaying the reward obtained, which was followed by a travel time to the next offer.
+Alternatively, the participant could quit at any point during the handling time by pressing the spacebar, and immediately start traveling.
+Participants received their earnings in the form of a real monetary bonus that was added to a fixed \$12 participation amount (possible range of task-based earnings = \$0 - \$15.50, rounded up to the nearest quarter).
+
+  Participants were divided into four groups.
+Each participant in the first three groups was assigned to one of three types of costs (cognitive effort, physical grip-force effort, or delay), and a fourth group experienced a low-effort physical task that required gripping above a negligible force level.
+This last condition was added to test the possibility that any differences in acceptances between effort and delay were driven by task engagement alone.
 Each group was unaware that other cost conditions existed.
 Participants exerted physical effort by gripping a handheld dynamometer (Biopac Systems, United States) using their dominant hand.
-Gripping requirements were calibrated at 20% of maximum voluntary contraction (MVC, acquired at the beginning of the session).
-Cognitive effort entailed switching among Stroop, dot motion coherence, and flanker tasks.
-This type of task switching is demonstrably effortful (Kool et al., 2010).
+Gripping requirements in the physical effort condition were calibrated at 20% of maximum voluntary contraction (acquired at the beginning of the session).
+The low-effort condition was equivalent except that the grip-force threshold was set to 5%.
+Cognitive effort entailed switching among Stroop, dot motion judgment, and flanker tasks.
+Task switching has previously been shown to impose subjective costs (Kool et al., 2010).
 In the Stroop task, one of three color names was displayed on the screen (red, blue or green), with a font color that was either congruent (e.g.
@@
 Participants had to select the color of the font (i.e., they had to suppress their tendency to read the word).
-For the motion coherence task, 100 solid white dots moved on the screen.
+For the motion judgment task, 100 solid white dots moved on the screen.
 A fraction of these dots moved coherently to the left or right, while the rest moved in random directions (coherence could be either 30% or 40%, uniformly sampled).
@@
 In the flanker task, rows of arrowheads pointed either to the left or the right (maximum of 3 rows, 3 to 13 arrowheads per row).
-Participants responded with the direction of the center arrowhead, which could point in the same or opposite direction from its neighbors.
+Participants responded with the direction of the center arrowhead, which could point in the same or opposite direction of its neighbors.
 The tasks were configured so that responses always involved a left or right key press (e.g.
@@
 Participants were asked to respond within each task’s presentation time (i.e., there was a 1 s response deadline).
-Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive tasks of each kind.
-While in the handling time, if participants failed to maintain above-threshold gripping or made two mistakes during the cognitive task, they were forced to travel and missed the reward.
+Before the experiment, participants trained in each cognitive task until they correctly performed six consecutive trials of each type.
+While in the handling time, if participants failed to maintain an above-threshold grip during the physical effort task (following the 1 s grace period) or made two mistakes during the cognitive task, they were forced to travel and missed the reward.
 
   There were three block types, in which handling times of 2, 10, or 14 seconds were paired with travel times of 14, 6, and 2 seconds, respectively.
-Note that all combinations add up to 16 seconds, meaning that accepted trials took the same amount of time in all conditions, but rejected ones were shorter in environments where the traveling time was shorter.
+All combinations added up to 16 seconds, meaning that accepted trials took the same amount of time in all conditions, but rejected trials were shorter in environments with shorter travel times.
 Timing parameters were held constant within each 7-min block.
-Each block type was presented twice in pseudo-randomized order (total session length = 42 minutes).
-Reward amounts varied uniformly per trial (4, 8, or 20 cents), with the constraint that every reward was presented twice every six trials.
+Each block type was presented twice in pseudorandom order (total session length = 42 minutes).
+Reward amounts varied per trial (4, 8, or 20 cents with equal probability), with the constraint that every reward was presented twice every six trials.
 This prevented sequences from being dominated by a single amount during any window of time.
-Timing information was disclosed at the beginning of each block, and rewards displayed during a 2 s offer window before each trial began.
-Participants received training prior to the experimental session and were told about all possible timing conditions and reward amounts in order to preclude biases due to experience-dependent learning [@Dundon2020; @Garrett2020].
+Timing information was disclosed at the beginning of each block, and each trial's reward amount was displayed during a 2 s offer window before the trial began.
+Participants received training prior to the experimental session and were told about all possible timing conditions and reward amounts in order to avoid any biases that could arise through experience-dependent learning [@Dundon2020; @Garrett2020].
+Finally, we encouraged participants to carefully evaluate their options by telling them that accepting all offers would not maximize their rewards.
 
@@
 
-#### *Operationalization of Cost*
+#### *Reward-maximizing Strategy*
 
@@
 
-  Foraging theory posits that accepting a delayed reward should depend on the opportunity cost (OC) of time to be incurred in obtaining it, which depends on the richness of the environment [@Charnov1976; @Stephens1986].
-In this study, the richness of the environment was manipulated by the length of the handling and travel times, where shorter travel times produced richer environments.
-Since time combinations were fixed per block, we calculated each block’s optimal accept/reject strategy by computing the expected reward rate (g(*)) from all decision strategies according to the following equation:
+  Foraging theory posits that the decision to accept a delayed reward should depend on the opportunity cost of time to be incurred in obtaining it, which in turn depends on the richness of the environment [@Charnov1976; @Stephens1986].
+In this study, the richness of the environment was manipulated by the length of the handling and travel times.
+Shorter travel times produced richer environments by making it possible to save more time by skipping low-reward trials.
+Since time combinations were fixed per block, we calculated each block’s optimal accept/reject strategy by computing the expected rate of gain (g(*)) from all decision strategies according to the following equation:
 
 $$\begin{aligned} 
-g(*) = \dfrac {\sum p_i R_i} { 3\text{Time}_\text{offer} + (\sum p_i H + \text{Time}_\text{reward}) + 3T},p \in \{0, 1\}
+g(*) = \dfrac {\sum p_i \text{R}_{i}} { 3\text{T}_\text{offer} + \sum p_i (\text{T}_\text{handling} + \text{T}_\text{reward}) + 3 \text{T}_\text{travel}},p \in \{0, 1\}
 \end{aligned}$$
 
-  where *R* and *p* are the reward and acceptance probability of offer *i*, respectively, *H* is the handling time for the block, *T* its associated travel time, $\text{Time}_\text{offer}$ is the duration of the offer window, and $\text{Time}_\text{reward}$ is the duration of the window displaying the reward earned (only presented for completed trials).
-This gave us the total reward per second attainable in each block as a function of the acceptance threshold (i.e.
-the lowest amount accepted).
-Since an ideal forager should always either accept or reject different categories of prey (Krebs et al., 1977), probabilities other than 0 and 1 are not considered.
+  where *R* and *p* are the reward magnitude and acceptance probability of offer *i*, respectively, $\text{T}_\text{handling}$ is the handling time for the block, $\text{T}_\text{travel}$ is the travel time, $\text{T}_\text{offer}$ is the duration of the offer window (2 s), and $\text{T}_\text{reward}$ is the duration of the window displaying the reward earned (2 s, only presented for completed trials).
+This gives the average reward per second attainable in each block as a function of the acceptance threshold (i.e.
+the lowest amount the participant is willing to accept in a given timing environment).
+Since an ideal forager should always either accept or reject any given category of prey (Krebs et al., 1977), probabilities other than 0 and 1 were not considered.
 The resulting possible strategies were to accept only 20 cents, accept 8 and 20 cents, or accept everything.
@@
 1B shows possible earnings per second for each choice strategy, as well as the lowest amount participants should accept in order to maximize their rewards (circled dots).
-For example, a participant in a 10 s handling block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate.
-Note that accepting every offer was often detrimental to participant earnings.
+For example, a participant in a 10 s handling-time block should accept 8-cent and 20-cent rewards (and reject 4-cent rewards) to maximize their reward rate; a participant in a 14 s handling-time block should accept only 20-cent rewards, and a participant in a 2 s handling-time block should accept everything.
+Note that accepting every offer was often detrimental to earnings.
 
@@
 We included continuous regressors for handling time and reward, as well as two covariates that probed the influence of recent history on choices.
-The first was an autoregressive regressor containing the number of consecutive unobtained offers prior to a given trial (unobtained offers could be due to quits or forced travels).
-The second regressor tracked the sum of the previous *n* offers.
-We identified the *n* that minimized Akaike's Information Criterion (AIC) among 6 versions of the model (tracing from 2 previous trials up to 7, beyond which the model failed to converge), and reported all coefficients from the winning model.
+The first was a term containing the number of consecutive unobtained offers prior to a given trial (unobtained offers could be due to quits or forced travels).
+The second regressor tracked the sum of the reward amounts on the previous *n* offers.
+We identified the *n* that minimized Akaike's Information Criterion (AIC) among 6 versions of the model (ranging from 2 previous trials up to 7, beyond which the model failed to converge), and report all coefficients from the winning model, which used the sum of the previous 6 offers.
 
@@
 To confirm this, we fit a general linear model with constant, linear, and quadratic terms to estimate the correspondence between proportion of trials completed (independent variable) and total earnings (dependent variable).
-A significant quadratic coefficient thus would signal that the task statistics operated as expected.
-Next, to determine the optimality of the group’s decisions, we examined whether each cost type produced a bias to over or under-accept offers 4 and 8 cents (assuming that 20 cents were always be accepted, given our design).
-The reward-maximizing strategy was to always reject these offers for handling times of 14 s, reject 4 cents and accept 8 cents for 10 s, and accept both for 2 s, yielding a combined optimal proportion of acceptances of 50% (see Operationalization of Costs for details).
-We performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
+A significant quadratic coefficient thus would signal that the task statistics operated generally as expected.
+Next, to determine the optimality of the group’s decisions, we examined whether each cost type produced a bias to over or under-accept offers of 4 and 8 cents (assuming that 20cent-offers would always be accepted, given our design).
+The reward-maximizing strategy was to always reject these offers for handling times of 14 s, reject 4 cents and accept 8 cents for 10 s, and accept both for 2 s, yielding a combined optimal overall acceptance rate of 50%.
+We performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost (with trials pooled across participants in each group).
 Therefore, a significant difference indicated that participants either over- or under-accepted rewards.
-This approach was adapted from the analysis preregistered for Experiment 2, as we found it better suited to the question than the original formulation.
+
+  The analyses above differed slightly from the pre-registeered plan.
+Rather than pooling coefficients from individual logistic regressions, we favored obtaining a single coefficient from a mixed model that accounted for participant-level random effects.
+The chi-squared test was adopted from the Experiment 2 preregistration, as we found it better suited to the question than the original formulation (i.e.
+individual tests for each combination of experimental parameters).
 
@@
 We first performed a one-way ANOVA on the proportion of trials accepted using group as a factor.
-We then compared the proportion completed among all 4 groups using non-parametric permutation contrasts (6 tests).
-For each test, on each of 5000 permutation iterations, the group assignment was randomly shuffled without replacement, and the difference in mean acceptance rates across iterations created a putative null distribution.
+We then compared the proportion completed across all 4 groups using non-parametric permutation contrasts (6 tests).
+For each test, on each of 5000 permutation iterations, participants' group labels were randomly shuffled without replacement, and the difference in mean acceptance rates across iterations created an empirical null distribution.
 The unpermuted group mean difference was then evaluated against this permuted distribution.
-The same approach was used for total earnings.
-
-  In order to further look at the effect of handling, offer, and cost type, we computed the probability of accepting a trial with a mixed-effects logistic regression.
-Based on the task structure and our main question, our a priori model of interest included cost condition, handling time, and reward amount as fixed main effects, and a random intercept per subject.
+The same approach was used to test differences in total earnings.
+
+  In order to further look at the effect of handling time, offer amount, and cost condition, we computed the probability of accepting a trial with a mixed-effects logistic regression.
+Our a priori model of interest included all three variables as fixed main effects, and a random intercept per subject.
 Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition.
@@
 We used both AIC and Bayesian Information Criterion (BIC) to determine the model that minimized the negative log-likelihood while penalizing the addition of parameters.
-The regressors included in each model were: 1) intercept only; 2) condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount; 6) condition, handling time, and reward main effects (a priori model from above); 7) adding a handling-by-reward interaction; and 8) all possible two-way interactions.
-We predicted that model 6 (the a priori setup) would have the lowest AIC and BIC.
+The regressors included in the 8 candidate models were: 1) intercept only; 2) cost condition only; 3) handling time only; 4) offer amount only; 5) handling time and offer amount; 6) cost condition, handling time, and offer amount main effects (a priori model from above); 7) adding a handling-time-by-offer-amount interaction; and 8) all possible two-way interactions.
+We predicted that model 6 would have the lowest AIC and BIC.
 Nested models with similar AIC were statistically compared using an analysis-of-deviance.
@@
 
-  Reward-maximizing prey foragers should either accept or reject offers based on their profitability relative to their alternatives [@Krebs1977; @Stephens1986].
-However, decision makers often curtail persistence based on continuous reevaluation of delayed prospects or lapses in self control [@Ainslie1975; @McGuire2012; @McGuire2015; @Mischel1970].
-Therefore, we examined whether participants were consistent (not quitting a trial after it was originally accepted) and stable (similar acceptance rates over time) in their choices.
-For consistency, we visually examined survival curves indicating at what point during the handling time participants quit a trial (censored points included trial completions and forced travels), in addition to quitting time distributions.
+  Reward-maximizing prey foragers should either accept or reject offers based on their profitability relative to the available alternatives [@Krebs1977; @Stephens1986].
+However, decision makers often curtail persistence before reaching a delayed prospect based on a continuous reevaluation of the prospect's value or a lapse in self control [@Ainslie1975; @McGuire2012; @McGuire2015; @Mischel1970].
+Therefore, we examined whether participants were consistent (not quitting trials that were originally accepted) and stable (maintaining similar acceptance rates over time) in their choices.
+To evaluate consistency, we visually examined survival curves indicating at what point during the handling time participants quit a trial; large numbers of late quit times would indicate a lack of consistency.
 We interrogated stability by computing each participant’s total proportion of acceptances in the first and second half of the experiment for every block type, comparing the mean proportion of acceptances using paired permutations (5000 iterations).
-We then tested whether the observed differences in costs were still present on each half of the experiment by applying winning model from the mixed-effects logistic comparison to each half separately.
-In each case, the reference cost category was rotated in order to assess pairwise differences among all costs.
-We evaluated the consistency of the relative costs by visually comparing the patterns of significant differences between experimental halves.
+We then tested whether the observed differences in costs were still present in each half of the experiment by applying the winning model from the mixed-effects logistic regression analysis to each half separately.
 
 ### **Results**
-#### *Between-subjects: Decision Makers Integrate Delay and Reward Information*
+#### *Decision Makers Integrate Delay and Reward Information*
 
@@
 
+# apply chi-squared
 temp2 <- apply(temp, 1, function(row) {prop.test(as.numeric(row[3]), sum(as.numeric(row[3:4])), p = 0.5, conf.level = 0.95)})

### 2021-05-28 Manuscript.Rmd
Exp 1 revised

@@
 Participants received training prior to the experimental session and were told about all possible timing conditions and reward amounts in order to avoid any biases that could arise through experience-dependent learning [@Dundon2020; @Garrett2020].
-Finally, we encouraged participants to carefully evaluate their options by telling them that accepting all offers would not maximize their rewards.
+Finally, we encouraged participants to carefully evaluate their options by informing them that accepting all offers would not maximize their rewards.
 
@@
             sdFT = sd(propFails), .groups = 'drop')
+
+# overall acceptances across all conditions
+allp <- dataBtw %>%
+  group_by(SubjID) %>%
+  summarise(p = mean(Choice)) %>%
+  ungroup()
 ```
@@
 
-  In this experiment, groups faced with different behavioral costs (physical effort, cognitive effort, or delay) chose their preferred strategy to maximize rewards in foraging environments of varying richness.
+  Four groups of participants faced with different behavioral demands (physical effort, cognitive effort, low-effort task engagement, or passive delay) chose their preferred strategy to maximize rewards in foraging environments of varying richness.
 Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time).
-We hypothesized 1) that participants would approximate reward-maximizing behavior by preferring higher rewards and shorter delays, but that 2) participants confronted with effortful demands would be more likely to accept trials than those faced with passive delay, regardless of handling time and reward amount.
-The second hypothesis was based on the traditional idea that rewarded work should become appealing [@Eisenberger1992; @Inzlicht2018].
-
-  We performed a mixed effects logistic regression to address the first hypothesis, pooling across the four conditions.
+We hypothesized 1) that participants would approximate reward-maximizing behavior by preferentially accepting higher rewards and shorter delays; 2) that participants confronted with effortful demands would be more likely to accept trials than those faced with passive delay, regardless of handling time and reward amount; and 3) that choices would be stable over time and consistent within trials.
+
+  We performed a mixed-effects logistic regression to address the first hypothesis, pooling across the four conditions.
 Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (not explicitly quitting a trial during the handling period) and completions (successfully obtaining a reward).
-Even so, the proportion of forced travels was low for cognitive effort (`r round(propFails[2, 2]$meanFT, digits = 2)` across participants) and 0 for the physical group.
+Even so, the proportion of forced travels was low for the cognitive effort group (`r round(propFails[2, 2]$meanFT, digits = 2) * 100`% on average across participants) and 0 for the physical effort group (i.e.
+no forced travels in this group).
+Overall, participants accepted an average of `r round(mean(allp$p), digits = 2) * 100`% of trials (SD = `r round(sd(allp$p), digits = 2) * 100`%, range = `r round(min(allp$p), digits = 2) * 100`% to `r round(max(allp$p), digits = 2) * 100`%).
 In line with our predictions, larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_btw["Offer", "Estimate"]`, SE = `r historyCoeffs_btw["Offer", "Std.
@@
 Error"]`, *p* `r report_p(historyCoeffs_btw["recentOffers", "Pr(>|z|)"])`).
-The counterintuitive reduction in acceptances following consecutive unobtained rewards was driven by the wait group (removing this group from the model yielded a *p* > 0.1), likely because this group accepted the fewest offers.
-Comparing likelihood fits among lengths of offer history (e.g.
-sum over 2 or 3 past trials) suggested that participants were influenced by the `r historyIndex_btw + 1` most recent rewards (AIC = `r round(AIC(historySize_btw[[historyIndex_btw]]), digits = 2)`), which matched the offer presentation rotation (see Methods).
+The counterintuitive reduction in acceptances following consecutive unobtained rewards was driven by the Wait group (removing this group from the model yielded a *p* > 0.1).
 
@@
 
-# apply chi-squared
+# apply chi-squared test of proportion per group (pooled trials across individuals)
 temp2 <- apply(temp, 1, function(row) {prop.test(as.numeric(row[3]), sum(as.numeric(row[3:4])), p = 0.5, conf.level = 0.95)})
@@
 It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy")$mProp`, SD = `r filter(overallSumms, Cost == "Easy")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Wait < Easy")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy")$cohenD`) (all other *p* > 0.05).
-The higher acceptance rates produced by the cognitive effort group resulted in significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than both physical (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
-In addition, we found that the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
-Considering the low proportion of forced travels, performance was an unlikely explanation for the observed differences in choice.
+In line with its higher acceptance rates, the cognitive effort group had significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than either the physical group (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) or the wait group (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
+In addition, the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
 
   We next examined the optimality of these decisions.
-The foraging task was configured so that there was a single reward-maximizing strategy per block type (see Operationalization of Cost in Methods), and participants were warned that accepting everything would not maximize their gains.
+The foraging task was configured so that there was a single reward-maximizing strategy per block type, and participants were informed that accepting everything would not maximize their gains.
 Accordingly, participants who over- or under-accepted earned the least (Fig.
 2, right; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
-We performed group-level chi-squared tests of proportions to examine whether each cost biased decision makers to under- or over-accept 4 and 8 cent offers, which together should have been accepted 50% of the time.
-We found a significant over-acceptance of these trials by the cognitive effort group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Cognitive", "pval"])`), but under-acceptances by the physical (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) and wait (proportion accepted = `r round(optimalProp_cost["Wait", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Wait", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Wait", "pval"])`) groups (no significant difference for the Easy group).
-Together, these findings show that even though participants did not always perform optimally, they responded appropriately to the statistics of the environment in each timing condition.
-Further, they provide evidence that cognitive effort can boost the value of an offer, as reflected by higher acceptances at the expense of earnings.
+We performed group-level chi-squared tests of proportions (with trials pooled across participants) to examine whether each cost biased decision makers to under- or over-accept 4 and 8 cent offers, which collectively should have been accepted 50% of the time across the three timing environments.
+We found a significant over-acceptance of these trials by the cognitive effort group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Cognitive", "pval"])`), but under-acceptances by the physical effort group (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) and wait group (proportion accepted = `r round(optimalProp_cost["Wait", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Wait", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Wait", "pval"])`), with no significant difference for the Easy group.
+Together, the findings discussed so far indicate that although participants reacted appropriately to reward and timing contingencies, departures from optimality were systematically influenced by what form of cost was at stake.
+The findings raise the possibility that cognitive effort can boost the value of an offer, as reflected by higher acceptances at the expense of earnings.
 
@@
 
-  We next probed whether these results held uniformly across all parameter combinations.
+  We next probed whether these results held uniformly across reward and timing parameter combinations.
 Fig.
-3A shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and cost, with optimal acceptance rates depicted by the gray circles.
+3A shows the mean proportion of acceptances (± SEM) per combination of handling time, reward, and cost type, with reward-maximizing acceptance rates depicted by the gray circles.
 Qualitatively, the figure confirms two important predictions.
 First, participants adapted to the richness of each timing block, gravitating towards optimality regardless of the cost they faced.
-Second, differences in cost were consistent across blocks, and acceptances were uniformly highest for the cognitive effort group.
-We tested these observations with a mixed-effects logistic regression, computing the probability of accepting an offer as a function of handling time, reward amount, and demand type (see Methods for details).
-As before, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main_btw$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main_btw$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main_btw$Wait)[[10]]["Handling", "Std.
+Second, effects of cost type were consistent across the three timing conditions, and acceptances were uniformly highest for the cognitive effort group.
+We tested these observations with a mixed-effects logistic regression model, which estimated the probability of accepting an offer as a function of handling time, reward amount, and cost type (see Methods for details).
+The model showed significant main effects of handling time ($\beta$ = `r round(fixef(mixLogis_main_btw$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main_btw$Wait)[[10]]["Handling", "Std.
 Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_btw$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main_btw$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main_btw$Wait)[[10]]["Offer", "Std.
@@
 3B.
-The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) and wait groups ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.
-
-  These observations could not be more easily explained by simpler or more complex regression models.
+The cognitive effort group was significantly more likely to accept offers than the physical effort group ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) or the wait groups ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.
+
+  These observations were not better explained by simpler or more complex regression models.
 Fig.
@@
 
-  However, against our expectations, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r filter(ME_evals$abicLogis_compare, Model == "HR_interaction")$AIC`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r round(ME_evals$MainvHRint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r filter(ME_evals$abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r round(ME_evals$MainvAllint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
-Even so, neither of these models offered further interpretable insights on the observed differences across costs, so we restrict our focus to the a priori model containing all main effects.
-These results further support the hypotheses that handling and reward amounts were similarly integrated across groups, and that the absolute rate of acceptances was affected by the demand faced.
-However, they offer partial support for the hypothesis that effort would induce higher acceptance rates, which was only true for those confronted with cognitive effort.
-
-#### *Between-subjects: Consistency and Stability*
+  Contrary to our expectations, the a priori model was outperformed by models that added an interaction between handling and reward (AIC~HR_interaction~ = `r filter(ME_evals$abicLogis_compare, Model == "HR_interaction")$AIC`, $\chi^2$(`r ME_evals$MainvHRint[[7]][2]`) = `r round(ME_evals$MainvHRint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvHRint[[8]][2])`) as well as one that considered all possible interactions (AIC~all_interactions~ = `r filter(ME_evals$abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r ME_evals$MainvAllint[[7]][2]`) = `r round(ME_evals$MainvAllint$Chisq[2], digits = 2)`, *p* `r report_p(ME_evals$MainvAllint[[8]][2])`).
+However, upon examination, neither of these models offered further interpretable insights on the observed differences across costs.
+The overall pattern of results supported the hypotheses that handling and reward amounts were integrated in the expected fashion, and that the rate of acceptances was affected by the demand faced.
+The results offered only partial support for the hypothesis that effort would induce higher acceptance rates; higher acceptance rates were observed for cognitive effort but not for physical effort.
+
+#### *Consistency and Stability of Choices*
 
@@
   Next, we tested the hypothesis that foragers would exhibit within-trial consistency and across-trial stability in their choices.
-Participants were deemed consistent if they did not quit after engaging in a trial.
-To examine this, we plotted survival curves of trial quits across all participants (Fig.
-4, top-left), with black crosses signaling either completed trials (at 2 s, 10 s, and 14 s) or forced travels.
-These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (percentage of quits after 1 s = `r  handlingQuits_btw$r * 100`).
-Physical and easy groups showed slightly lagged responses because the experiment allowed a one-second grace period for participants to begin gripping (marked by the dashed line).
-This resulted in some individuals opting to wait for that second to indicate an offer rejection.
-Plotting the quitting time distributions across blocks for the first second of the handling time (ECDFs on Fig.
+Participants were deemed consistent if they tended not to quit after engaging in a trial (that is, if they pressed the spacebar to reject a trial either quickly or not at all).
+To examine this, we plotted survival curves of trial rejection times across all participants (Fig.
+4, top-left), with black crosses signaling censored observations either for completed trials (at 2 s, 10 s, and 14 s) or forced travels.
+These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (only `r  handlingQuits_btw$r * 100`% of quits occurred later than 1 s).
+The pattern of results in the Physical and Easy groups reflected that participants sometimes quit by letting the 1 s initial grace period expire without gripping (rather than by pressing the spacebar); such trials were coded as quits rather than as forced travels.
+Plotting the quitting time distributions across blocks for the first 1 s of the handling time (ECDFs on Fig.
 4, top-right) showed that participants in the wait and cognitive groups responded faster as the experiment progressed.
@@
 
-  Stability was defined as a persistence in acceptance patterns throughout the experimental session.
-The scatter plot on Fig.
-4 (bottom-left) shows the overall proportion accepted by each participant before and after the midpoint of the session.
-Paired permutations showed no differences in acceptances for wait and easy groups (*p* > 0.05), but we found significantly lower acceptances for physical (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and cognitive (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`) groups.
+  Stability was defined as the maintenance of similar acceptance rates throughout the experimental session.
+The scatterplot in Fig.
+4 (bottom-left and bottom-right) shows the overall proportion accepted by each participant before and after the midpoint of the session.
+Paired permutations showed no change in acceptance rates for the wait and easy groups (*p* > 0.05), but we found significantly lower acceptance rates in the second half of the session for the physical effort group (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and the cognitive effort group (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`).
 Fig.
-5 (left) shows that the reduction in acceptances in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009].
-We then replicated the mixed-effects logistic regression from the previous section separately on each experimental half, which confirmed that differences among demands were stable (Fig.
+5 (left) shows that the reduction in acceptance rates in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009].
+We then replicated the mixed-effects logistic regression from the previous section separately for each half of the session, which confirmed that differences among demands were stable (Fig.
 5, right).
-Together, the consistency and stability displayed by participants suggest that decision makers had a clear representation of the environment.
+Together, the consistency and stability of behavior suggested that decision makers had a clear representation of the environment.
 

### 2021-05-28 Manuscript.Rmd
Exp2 revisions ready

@@
 
-  Experiment 1 was a between-subjects examination of how cognitive effort, physical effort, and delay would impact prey foraging behavior, and whether canonical discounting effects could be observed under this paradigm.
-Based on this behavioral baseline, Experiment 2 interrogated which type of demand decision makers would gravitate to when they were allowed to forage for types of demands in addition to rewards.
-This within-subjects version sought to answer how the presence of alternative avenues would impact the subjective costs of effort and delay, our overarching question.
+  Experiment 1 demonstrated that human decision makers could appropriately integrate reward and timing information to make single-alternative accept/reject decisions in a foraging environment.
+In addition, acceptance rates were higher in a group of participants for whom rewards were associated with demands for cognitive effort than in groups for whom rewards were associated with physical effort or mere delay.
+One possible interpretation of the findings of Experiment 1 might be that cognitive effort was simply intrinsically rewarding.
+For instance, participants might have enjoyed performing the cognitive tasks and preferred them to a boring, unfilled delay.
+We reasoned that if this were the case, participants ought to continue preferentially accepting cognitive effort trials in an environment in which effort and non-effort trials were randomly intermixed within-subject, where rejecting a delay trial would potentially lead to an opportunity to accept a subsequent effort trial.
+On the other hand, if cognitive effort were not preferred, interleaving different types of demand in the same environment might lead to a different pattern of choices.
+Experiment 2 tested which types of trials decision makers would preferentially accept when they were allowed to forage for different types of demand in addition to different sizes of rewards.
+The objective was to address how the presence of multiple alternative forms of demand in the same choice environment would impact the subjectively assessed costs of effort and delay.
 
@@
 
-  We collected data from a new sample of 48 eligible participants  (39 Female, median age = 21, range = 18 - 36; number excluded before reaching goal = 6).
-Sample size was once again determined by means of a power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, a desired effect size of f = 0.5, and four factors (one for each type of demand; see below for details).
+  We collected data from a new sample of 48 participants (39 Female, median age = 21, range = 18 - 36; number excluded before reaching goal = 6).
+Sample size was once again determined by means of a power analysis (repeated measures ANOVA), using a significance level of 0.05, power of 0.8, an anticipated effect size of f = 0.5, and four factors (one for each demand-type condition; see below for details).
 The resulting sample size was 45, which we increased to 48 in order to balance the potential order of blocks.
-We excluded participants using the same criteria as in Experiment 1.
-
-#### *Foraging Task Adaptation*
+We excluded participants using the same criteria as in Experiment 1 (4 participants were excluded because they failed the inter-block attention checks).
+
+#### *Within-participant Manipulation of Cost Type*
 
@@
 This setup prevented participants from having to rapidly switch between response modalities across trials (i.e.
-keyboard press and handgrip).
-Each block combination (i.e.
-physical/wait and cognitive/wait) was experienced three times by each participant in 7-minute-long, interleaved blocks, for a total session duration of 42 minutes.
-Half of the participants experienced a block sequence that started with the physical block.
-Timing parameters were matched to the middle condition from Experiment 1 (i.e.
-10 s handling time and 6 s travel time).
+keyboard and handgrip).
+Each block combination (physical/wait and cognitive/wait) was experienced three times by each participant in 7-minute-long, interleaved blocks, for a total session duration of 42 minutes.
+Half of the participants experienced a block sequence that started with the physical/wait block and the other half experienced a sequence that started with the cognitive/wait block.
+Timing parameters were held fixed throughout the experiment and were matched to the middle condition from Experiment 1 (10 s handling time and 6 s travel time).
 Participants were informed that this timing combination would be constant prior to beginning the experiment.
@@
 “8 cents for physical effort”).
-Unlike the previous experiment, participants could express their decision to quit during the offer window (instead of during the handling time).
+Unlike the previous experiment, participants could express their decision to quit by pressing the spacebar during the offer window (not only during the handling time), in which case the travel time would begin immediately at the end of the 2 s offer window.
 Participants were trained in each type of demand until they reached the same criteria as in Experiment 1.
@@
   The analytical pipeline was mostly preserved from Experiment 1.
-We first ran tests to determine whether decision makers integrated reward information.
+We first tested whether decision makers integrated reward information.
 We performed a mixed-effects logistic regression with regressors for offer amount, number of consecutive offer misses, and the sum of the *n* previously observed offers (we identified *n* by comparing the AIC of different history lengths).
-We then confirmed that the under- and over-acceptance were detrimental to total earnings by performing the same quadratic linear model explained above.
-We tested the group’s optimality as before.
-We tested the group’s optimality as before.
-The optimal strategy was to reject 4 cent offers and accept 8 cent offers, yielding an ideal acceptance of 50% (not counting 20 cent offers, which should have always been accepted per our design).
-For these trials, we performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each type of cost.
-
-  To compare acceptances among cost conditions, we first estimated acceptance probabilities using a mixed-effects logistic regression.
+We then confirmed that under- and over-acceptance were detrimental to total earnings by fitting the same quadratic linear model discussed above.
+The optimal strategy was to reject 4-cent offers and accept 8-cent offers, yielding an ideal overall acceptance rate of 50% (not counting 20-cent offers, which should have always been accepted).
+For these trials, we performed a two-sided one-sample chi-squared test of proportions against the null probability of 0.5 for each cost condition.
+
+  To compare acceptance rates among cost conditions, we first estimated acceptance probabilities using a mixed-effects logistic regression.
 The model included cost condition and reward amount as fixed main effects, and participant as a random intercept (handling time was not modeled, as participants experienced a single time combination).
-Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and two delay conditions corresponding to each effort type).
+Cost condition was modeled with three categorical terms, with the fourth condition as the reference condition (two effort conditions, and a delay condition paired with each effort type).
 We ran three versions of the model with different reference conditions, in order to test all relevant pairwise differences among the four cost conditions.
-We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity as follows: 1) intercept only; 2) cost only; 3) reward only; 4) cost and reward main effects (a priori model); and 5) adding a two-way interaction.
-We predicted that model 4 would have the last considerable decrease in the negative log-likelihood.
+We compared the a priori model to alternative parameterizations using AIC and BIC, varying model complexity as follows: 1) intercept only; 2) cost condition only; 3) reward only; 4) cost condition and reward main effects (a priori model); and 5) adding a two-way interaction of cost condition and reward.
+We predicted that model 4 would have the last appreciable decrease in the negative log-likelihood.
 Models with similar AIC were formally compared using the analysis-of-deviance approach from Experiment 1.
 
-  Next, we probed within-trial consistency and across-trial stability in people’s choices.
+  Next, we probed within-trial consistency and across-trial stability of choice behavior.
 First, we visualized the number of quit responses during the handling time with a survival curve, and plotted the quit response time distribution as a function of block to examine choice consistency over time.
@@
 Earlier quits were seen as signifying greater consistency.
-We then computed each participant’s total proportion of acceptances on the first two and last two blocks, and compared them using a paired permutation analysis (5000 iterations).
-This analysis did not include the third and fourth block because their effort designation was counterbalanced across participants.
+We then computed each participant’s total acceptance rate in the first two and last two blocks, and compared them using a paired permutation analysis (5000 iterations).
+This analysis did not include the third and fourth block because the alternating, counterbalanced sequence of block types would have led to unequal numbers in the first three and last three blocks for individual participants.
 
 ### **Results**
-#### *Within-subjects: Decision Makers Integrate Reward Information*
+#### *Decision Makers Integrate Reward Information*
 
@@
 
-  In Experiment 2, we directly tested an individual’s preferences for cognitive effort, physical effort, and delay.
-We did by modifying the foraging task, such that every participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (fixed at 10 s handling and 6 s travel times, to allow for comparisons between experiments).
+  In Experiment 2, we tested decision makers' preferences for cognitive effort or physical effort relative to unfilled delay delay.
+We modified the prey-selection foraging task, so each participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (with a fixed 10 s handling time and 6 s travel time, to allow for comparisons between experiments).
 We separately analyzed wait trials from the two block types, labeling the two sets of wait trials according to the type of effort with which they were paired (“Wait-C” for cognitive, and “Wait-P” for physical).
-We hypothesized that 1) reward decision patterns would match those of the previous experiment; and 2) interleaving effort and delay would produce persistent preferences for wait trials.
-The second hypothesis was based on the idea that people will gravitate to the easiest way to achieve their goals [@Hull1943; @Olivola2013].
+We hypothesized that 1) reward offer amounts would influence decisions in the same way as in Experiment 1; 2) interleaving effort and delay would produce higher acceptance rates for wait trials than for cognitive or physical effort trials, in contrast to the pattern observed in Experiment 1.
+and 3) that choice patterns would remain stable over time and consistent within trials.
 
@@
 
-  We first tested the hypothesis that participants would successfully integrate the statistics of the environment.
-A mixed-effects logistic regression once again showed that larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_wth["Offer", "Estimate"]`, SE = `r historyCoeffs_wth["Offer", "Std.
+  We first tested the hypothesis that participants would successfully integrate reward and timing information.
+A mixed-effects logistic regression showed that larger reward amounts significantly increased acceptance probabilities ($\beta$ = `r historyCoeffs_wth["Offer", "Estimate"]`, SE = `r historyCoeffs_wth["Offer", "Std.
 Error"]`, *p* `r report_p(historyCoeffs_wth["Offer", "Pr(>|z|)"])`), and that participants became more selective if they had recently observed large offers ($\beta$ = `r historyCoeffs_wth["recentOffers", "Estimate"]`, SE = `r historyCoeffs_wth["recentOffers", "Std.
 Error"]`, *p* `r report_p(historyCoeffs_wth["recentOffers", "Pr(>|z|)"])`).
-Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards (AIC = `r round(AIC(historySize_wth[[historyIndex_wth]]), digits = 2)`).
+Model comparisons suggested that participants were influenced by the `r historyIndex_wth + 1` most recent rewards.
 Unlike Experiment 1, participants were unaffected by the preceding number of consecutive unobtained rewards (*p* `r report_p(historyCoeffs_wth["recentTravels", "Pr(>|z|)"])`).
@@
 When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were correctly accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05).
-Despite this deviation, participants earned a similar total amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-C = `r filter(earnings_within, Cost == "Wait-C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-P = `r filter(earnings_within, Cost == "Wait-P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-P")$sdEarn`).
-These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality.
+Despite this deviation, participants earned a similar total amount per cost condition on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait-C = `r filter(earnings_within, Cost == "Wait-C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait-P = `r filter(earnings_within, Cost == "Wait-P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait-P")$sdEarn`).
+These results convey that, in contrast to Experiment 1, participants were similarly successful across the different cost conditions.
 
@@
 
-  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones.
-Even though the reward acceptance pattern at 10 s handling was similar to Experiment 1 (Fig.
+  Next, we addressed the hypothesis that passive waiting trials would be preferentially accepted relative to effortful trials.
+Even though the overall reward acceptance pattern was similar to the 10 s handling time condition in Experiment 1 (Fig.
 6B), differences among cost conditions were less evident.
-Moreover, these differences contradicted our predictions, as cognitive effort remained the least costly among demands.
-A mixed effects logistic regression confirmed once again that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main_wth$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main_wth$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Std.
-Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference across cost conditions was a higher likelihood to accept cognitive-effort offers than physical-effort offers (Fig.
+Moreover, these differences contradicted our predictions, as cognitive effort continued to be accepted at the highest rate.
+A mixed effects logistic regression confirmed once again that increases in offer amount made acceptances significantly more likely ($\beta$ = `r round(fixef(mixLogis_main_wth$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Std.
+Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main_wth$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`), but that the only significant difference across cost conditions was a higher acceptance rate for cognitive-effort offers than physical-effort offers (Fig.
 6C; $\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`).
-Model comparisons suggested that even though a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare_wth$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Fig.
+Neither Cognitive trials nor Physical trials had significantly different acceptance rates from the Wait trials that were interleaved in the same block (Cognitive versus Wait-C: $\beta$ = `r round(mixSummary_wth$Betas["Wait-C", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Wait-C", "Cognitive"])`; Physical versus Wait-P: $\beta$ = `r round(mixSummary_wth$Betas["Wait-P", "Physical"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Wait-P", "Physical"])`).
+Model comparisons showed that a model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare_wth$Rsq, digits = 2)`), and there were similar AIC and BIC values for any model including reward amount (Fig.
 6D).
-An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][2]`) = `r round(mixLogis_compare_wth$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][2])`).
-However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][3]`) = `r round(mixLogis_compare_wth$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][3])`), albeit at the cost of interpretability due to choice fluctuations over time (see Consistency and Stability).
-These initial results contradicted our predictions, suggesting that the availability of alternative demands diminishes preferences among them (rather than promoting wait trials as a way to earn the same reward amounts without the need to exert effort).
-
-#### *Within-subjects: Consistency and Stability*
+An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved the fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][2]`) = `r round(mixLogis_compare_wth$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][2])`) and that including a term for the interaction between reward amount and cost condition improved the fit still further (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare_wth$aod[[7]][3]`) = `r round(mixLogis_compare_wth$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare_wth$aod[[8]][3])`).
+These results contradicted our hypothesis that Wait trials would be favored, but also did not indicate participants had a straightforward preference for Cognitive trials relative to the corresponding Wait-C trials.
+Instead, cost condition had only relatively small effects on acceptance rates when cost conditions varied within-participant.
+To shed further light on the dynamics underlying the small overall effect, we next examined how it varied over the course of the experimental session.
+
+#### *Consistency and Stability of Choices*
 
@@
 
-  Similar to the between-subject results, a survival analysis displayed that participants made most of their choices quickly within the offer window (Fig.
+  Consistent with Experiment 1, a survival analysis showed that participants made most of their choices quickly within the offer window (Fig.
 7A).
 The median percentage of quits during the handling time was `r round(median(propQuits_wth$propAccept), digits = 2)`% (SD = `r round(sd(propQuits_wth$propAccept), digits = 2)`), with only `r sum(propQuits_wth$propAccept > 20)` participants quitting over 20% of trials during the handling time.
-Moreover, the cumulative quitting time distributions show that participant responses during the offer window became faster over time (Fig.
+Cumulative quitting time distributions showed that responses during the offer window became faster over time (Fig.
 7B).
-Once in the handling time, the overall percentage of forced travels in the effortful trials was low for both cognitive (median = `r round(median(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and physical (median = `r round(median(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`) conditions.
-Similar to that of Experiment 1, these results suggest that decision makers were consistent in their adopted strategies, and were able to perform the tasks well.
+Once in the handling time, the overall percentage of forced travels was low for both Cognitive trials (median = `r round(median(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Cognitive")$propFails), digits = 2)`) and Physical trials (median = `r round(median(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`%, SD = `r round(sd(filter(propFails_wth, Cost == "Physical")$propFails), digits = 2)`).
+The results suggest that decision makers were consistent in their adopted strategies, and were able to perform the tasks well.
 
@@
 
-  However, against our predictions, participants accepted significantly fewer trials on the second half of the experiment, regardless of cost (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Fig.
+  However, against our predictions, participants accepted significantly fewer trials in the second half of the experiment, regardless of cost condition (paired permutations; Cognitive: mean~pre~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Cognitive")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Cognitive")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Cognitive"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Cognitive"]], digits = 2)`; Physical: mean~pre~ = `r filter(df_mean, Cost == "Physical")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Physical")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Physical")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Physical")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Physical"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Physical"]], digits = 2)`; Wait-C:  mean~pre~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-C")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-C")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-C"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-C"]], digits = 2)`; Wait-P: mean~pre~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_1`, SD~pre~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_1`, mean~post~ = `r filter(df_mean, Cost == "Wait-P")$propAccept_2`, SD~post~ = `r filter(df_mean, Cost == "Wait-P")$sdAccept_2`, *p* `r report_p(prepost_wth$Perms[["Wait-P"]])`, Cohen's D = `r round(prepost_wth$CohenD[["Wait-P"]], digits = 2)`; Fig.
 8).
 The reduction in acceptances was not driven by a performance decline, as the proportion of forced travels was not significantly different between the first and second half of the experiment (paired permutation with 5000 iterations, *p* `r report_p(failDiffs_wth$Pval)`).
-Notably, the pattern of choices from the first half of the experiment resembled that from the matching handling/travel block from Experiment 1 (Fig.
-3A).
+Notably, the pattern of choices from the first part of the experiment resembled that from the corresponding 10 s handling-time condition in Experiment 1 (compare Fig.
+5A, middle to Fig.
+8, top-left).
 Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Fig.
-8, top-right, lower triangle), but that it disappeared over time amid an overall decline in acceptance rates as participants gained experience with cognitive effort, physical effort, and both wait conditions (upper triangle).
-This fading preference for cognitive effort was observed regardless of which block participants experienced first, even though its magnitude appeared to be reduced for those who experienced the physical block first (Fig.
+8, top-right, lower triangle), but that it became undetectable over time amid an overall decline in acceptance rates as participants gained experience with cognitive effort, physical effort, and passive waiting trials (upper triangle).
+This fading preference for cognitive effort was observed regardless of which block participants experienced first, although its magnitude appeared to be reduced for those who experienced the physical block first (Fig.
 8, bottom)
 
-  All together, our findings show that the stable preferences for cognitive effort observed during single-demand foraging slowly fade if alternative demands are introduced.
-This points towards task-specific and outcome-independent features from cognitive tasks that can be recalibrated by new experiences.
+  Together, our findings show that the stable preferential acceptance of cognitive effort trials that we observed during single-demand foraging slowly faded if alternative demands were introduced.
+This finding raises the question of how features of the cognitive task might be re-evaluated as a function of other experiences in the same decision context.
+We probed this question by fitting a series of computational models to data from both Experiments 1 and 2.
 

### 2021-05-29 Manuscript.Rmd
working on figures

@@
 prop1 <- ggplot(temp, aes(Cost, pAccept, fill = Cost)) + 
-        geom_boxplot(show.legend = F) +
+        geom_boxplot(show.legend = F, outlier.shape = NA) +
         geom_jitter(width = 0.1, alpha = 0.3, show.legend = F) +
@@
 earnings1 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
-        geom_boxplot(show.legend = F) +
+        geom_boxplot(show.legend = F, outlier.shape = NA) +
         geom_jitter(width = 0.1, alpha = 0.3, show.legend = F) +
@@
 #(propPlot <- prop1 | earnings1 | earnFitplot_btw)
-#ggsave("./Images/FIG3_props.png", propPlot, device = "png", height = 4, width = 10)
+#ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)
 
@@
 #          outline = T,
-#          #insig = "p-value",
-#          sig.level = 0.05, 
+#          insig = "label_sig",
+#          sig.level = c(.001, .01, .05),
+#          pch.col = "white",
 #          na.label = "square",
@@
                           ylim(0, 1) +
+                          annotate("text", x = 1, y = 25, label = "A", size = 20) +
                           labs(x = "Proportion Accepted - 1st Half", y = "Proportion Accepted - 2nd Half") +
@@
 4), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1.
-Top: Survival curve (left), and distribution of times when participants quit a trial over time (right).
-Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
+A: Survival curve showing quit times within trial.
+B: Distribution of times when participants quit a trial over time.
+C: Proportion accepted in the second half as a function of first half acceptances.
 Dashed lines indicate the mean for each group.
-On the right, the proportion accepted over time per group.
-The order of blocks was repeated in the second half (indicated by the black dashed line)."}
+D: proportion accepted over time per group."}
 # individual plots generated in 16.3.1. and 16.3.2.
 # to recreate the combined plot and save it:
-# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
-# ggsave("./Images/FIG5_survival.png", historyPlot_btw, device = "png", height = 8, width = 10)
+# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks) + 
+#   plot_annotation(tag_levels = 'A') & 
+#   theme(plot.tag = element_text(size = 20, face = "bold"))
+# ggsave("./Images/FIG4_survivalbtw.png", historyPlot_btw, device = "png", height = 8, width = 10)
 include_graphics("./Images/FIG4_survivalbtw.png")
@@
 #          col = col2(200))
+
 ````
@@
 #          outline = T,
-#          #insig = "p-value",
-#          sig.level = 0.05, 
+#          insig = "label_sig",
+#          sig.level = c(.001, .01, .05),
+#          pch.col = "white",
 #          na.label = "square", 
@@
   geom_point(size = 4) +
-  scale_color_grey(start = 0.2, end = 0.6) +
+  scale_color_grey(start = 0.2, end = 0.6, name = "", labels = c("Experiment 1", "Experiment 2")) +
   xlab("") +
@@
 paramPlot <- ggplot(param, aes(Group, Fit, fill = Group)) +
-    geom_boxplot(show.legend = F) +
+    geom_boxplot(show.legend = F, outlier.shape = NA) +
     geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
@@
   ggplot(aes(Var1, value)) +
-    geom_boxplot(show.legend = F, fill = "grey50") +
+    geom_boxplot(show.legend = F, fill = "grey50", outlier.shape = NA) +
     geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3, fill = "grey50") +
@@
     geom_hline(yintercept = 0, linetype = "dashed") +
-    geom_boxplot(show.legend = F) +
+    geom_boxplot(show.legend = F, outlier.shape = NA) +
     geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
-    labs(x = "") +
+    labs(x = "", y = "Bias parameter estimate") +
     #facet_wrap(vars(Var1), scales = "free") +
@@
 tempCols[4] <- "grey50"
+supp.labs <- c("Initial Value of γ", "Learning Rate α", "Temperature β")
+names(supp.labs) <- c("gamma", "alpha", "beta")
+
 allFitsPlot <- rbind(t1, t2) %>%
@@
   ggplot(aes(Group, Fit, fill = Group)) +
-    geom_boxplot(show.legend = F) +
+    geom_boxplot(show.legend = F, outlier.shape = NA) +
     geom_jitter(width = 0.1, alpha = 0.5, show.legend = F, pch = 21, size = 3) +
-    labs(x = "") +
-    scale_x_discrete(labels = c("Physical", "Cognitive", "Wait", "Within")) +
+    labs(x = "", y = "Log parameter estimate") +
+    scale_x_discrete(labels = c("Physical", "Cognitive", "Wait", "Exp 2")) +
     geom_vline(xintercept = 3.5, linetype = "dashed") +
-    facet_wrap(vars(Var1), scales = "free", ncol = 3) +
+    facet_wrap(vars(Var1), scales = "free", ncol = 3, labeller = labeller(Var1 = supp.labs)) +
     scale_fill_manual(values = tempCols) +
@@
 # modelPlot <- (bicPlot + costPlot) / allFitsPlot
-# ggsave("./Images/FIG10_model.png", modelPlot, device = "png", height = 8, width = 11)
+# ggsave("./Images/FIG9_modelresults.png", modelPlot, device = "png", height = 8, width = 11)
 include_graphics("./Images/FIG9_modelresults.png")
@@
 4), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1.
-Top: Survival curve (left), and distribution of times when participants quit a trial over time (right).
-Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
+A: Survival curve showing quit times within trial.
+B: Distribution of times when participants quit a trial over time.
+C: Proportion accepted in the second half as a function of first half acceptances.
 Dashed lines indicate the mean for each group.
-On the right, the proportion accepted over time per group.
-The order of blocks was repeated in the second half (indicated by the black dashed line)."}
-# plots generated in 16.3.1. and 16.3.2.
-(suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
+D: proportion accepted over time per group."}
+# individual plots generated in 16.3.1. and 16.3.2.
+# to recreate the combined plot and save it:
+# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks) + 
+#   plot_annotation(tag_levels = 'A') & 
+#   theme(plot.tag = element_text(size = 20, face = "bold"))
+# ggsave("./Images/FIG4_survivalbtw.png", historyPlot_btw, device = "png", height = 8, width = 10)
+include_graphics("./Images/FIG4_survivalbtw.png")
 ```

### 2021-05-29 Manuscript.Rmd
final corrplot fixed

@@
 
-# corrplot(mixSummary$Betas, 
+# corrplot(mixSummary_wth$Betas,
 #          is.corr = F,
-#          p.mat = mixSummary$Pvals, 
+#          p.mat = mixSummary_wth$Pvals,
 #          type = "lower",
@@
 #          cl.length = 5,
-#          cl.lim = c(-2.0001, 2.0001),
 #          col = col2(200))

### 2021-05-29 Manuscript.Rmd
starting editing the computational modeling section

@@
 - This script is set so you can run each code snippet independently (after you run the setups and data loading snippets above the institutional affiliations)
-- Numbers on each chunk correspond generally to sections in the preregistrations
+- Numbers on each chunk correspond generally to sections in the preregistrations (https://osf.io/2rsgm/registrations)
 -->
@@
 
-  We developed a computational model to identify cognitive operations that could explain the complex patterns observed in both experiments (e.g.
-learning, time estimation, etc.).
-We isolated four key aspects of the behavioral results that an adequate computational model should be able to capture: 1) show deviations in acceptance rates that involved both under- and over-harvesting of offers (e.g.
+  We developed a computational model to identify cognitive operations that could explain the complex patterns observed across Experiments 1 and 2.
+We identified four key aspects of the behavioral results that an adequate computational model should be able to capture: 1) modest under- and over-harvesting of offers relative to the optimal strategy as a function of reward offer amount (e.g.
 Fig.
-3.3A); 2) keep track of recent offer history in order to evaluate the relative value of each offer; 3) persistently display higher acceptances for cognitive effort when faced with single behavioral costs (Experiment 1); and 4) initially match this preference for cognitive effort trials when foraging for demands and rewards (Experiment 2), which should decrease to a common rate across costs over time.
-These conditions excluded a number of popular explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, or asymmetric learning of environmental richness (see Discussion).
+3A); 2) dependence of choices on recent offer history; 3) higher acceptance rates if all reward offers were associated with cognitive effort (Experiment 1); and 4) gradual abolishment of the tendency to over-accept cognitive effort trials if other forms of demand were interleaved in the same environment (Experiment 2).
+These conditions excluded a number of potential explanatory candidates that were not modeled, such as learned industriousness, boredom, fatigue, or asymmetric learning of environmental richness (see Discussion).
 
@@
 
-  For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm [@Huys2011; @Huys2012].
-Briefly, it was assumed that, at the population level, each parameter was distributed according to a Gaussian distribution, defined by a mean and standard deviation; the individual subject parameters were drawn from this distribution.
-Accordingly, a point estimate for the individual subject parameters were found via maximum a posteriori (MAP) estimation using the population distribution for each parameter as the priors, and the variance in the individual subject parameter estimates were calculated by taking the inverse of the Hessian matrix at the MAP estimate.
+  For each model, both population-level and individual subject-level parameters were fit simultaneously using an Expectation-Maximization algorithm [@Huys2011; @Huys2012].
+Briefly, it was assumed that, at the population level, subject-level values for each parameter were distributed according to a Gaussian distribution, defined by a mean and standard deviation.
+Accordingly, point estimates for the individual subject parameters were found via maximum a posteriori (MAP) estimation using the population distribution for each parameter as the priors, and the variance in each individual subject parameter estimate was calculated by taking the inverse of the Hessian matrix at the MAP estimate.
 Next, the mean of the prior was updated by taking the weighted mean of individual subject estimates, and the variance of the prior was updated by taking the weighted variance across the parameter estimates of individual subjects.
@@
 Full mathematical details of the algorithm can be found in Huys et al.
-(2011, 2012), and the algorithm was implemented using a custom written R package, GaussExMax, available on github (github.com/gkane26/GaussExMax).
-
-  Model comparison was performed by calculating Bayes Information Criterion at the group level [integrated BIC or iBIC, @Huys2011; @Huys2012; @Kane2019].
-iBIC penalizes the likelihood of the data given model parameters $p(d | \text{model})$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
+(2011, 2012), and the algorithm was implemented using a custom written R package, GaussExMax, available on GitHub (github.com/gkane26/GaussExMax).
+
+  Model comparison was performed by calculating Bayesian Information Criterion at the group level [integrated BIC or iBIC, @Huys2011; @Huys2012; @Kane2019].
+iBIC penalizes the likelihood of the data given model parameters, $p(d | \text{model})$, for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:
 
@@
 
-  We began by fitting a base model derived from the normative predictions of the Marginal Value Theorem [MVT, @Charnov1976], which states that a delayed reward should be accepted if its earning rate surpasses the opportunity cost (OC) of time incurred in obtaining it (see Operationalization of Cost for details).
-This decision rule can be expressed as
+  We began by fitting a *base model* derived from the normative predictions of the Marginal Value Theorem [MVT, @Charnov1976], which states that a delayed reward should be accepted if its magnitude surpasses the opportunity cost of time incurred in obtaining it (see Reward-maximizing Strategy for details).
+This evaluation rule can be expressed as
 

### 2021-05-29 Manuscript.Rmd
model definitions almost done

@@
 $$\begin{aligned} 
-g(*) = \dfrac {\sum p_i \text{R}_{i}} { 3\text{T}_\text{offer} + \sum p_i (\text{T}_\text{handling} + \text{T}_\text{reward}) + 3 \text{T}_\text{travel}},p \in \{0, 1\}
+g(*) = \dfrac {\sum p_i R_{i}} { 3T_\text{offer} + \sum p_i (T_\text{handling} + T_\text{reward}) + 3 T_\text{travel}},p \in \{0, 1\}
 \end{aligned}$$
@@
 \begin{align}
-  \text{Model}_\text{base} = R_i - \gamma H_i
+  V_{\text{base}_i} = {R}_{i} - \gamma {T}_{\text{handling}_i}
 \end{align}
 
-such that the reward $R$ of trial $i$ should be accepted if it is larger than the average amount one could earn per second in the environment $\gamma$ (gamma; the OC) during the handling time $H_i$, with high gammas promoting selectivity.
-We fit this and all subsequent models using a softmax function to predict the probability of accepting a given trial
+such that the reward $R$ of trial $i$ is favorable if it is larger than the average amount one could earn per second in the environment $\gamma$ (the opportunity cost) during the handling time ${T}_{\text{handling}_i}$, with high values of $\gamma$ promoting selectivity.
+We fit this and all subsequent models using a softmax decision rule to determine the probability of accepting the offer on a given trial
 
 \begin{align}
-  P(\text{accept})_i = \dfrac {1} {1 + e^{-(1/\beta)(\text{Model}_\text{base})}}
+  P(\text{accept})_i = \dfrac {1} {1 + e^{-(1/\beta)(V_{\text{base}_i})}}
 \end{align}
 
-gamma in this base model was computed as an individual’s empirical earning rate by the time of each offer, with the free temperature parameter $\beta$ indexing decision noise.
-Differences among costs in Experiment 1 could then be due to the impact of each cost on decision noise, which could have also driven the gradual convergence of acceptance rates in Experiment 2.
-However, it is also possible that individuals updated the estimate of gamma at different rates when faced with different demands.
-Previous accounts have demonstrated the biases that can impact the learning of the opportunity cost [@Dundon2020; @Garrett2020].
-We therefore tested a second model that allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
+The value of $\gamma$ in this base model was computed as an individual’s empirical rate of earnings by the time of each offer, with the free temperature parameter $\beta$ indexing decision noise.
+Differences among the between-subject cost conditions in Experiment 1 could then be due to the impact of each cost on decision noise, which could have also driven the gradual convergence of acceptance rates in Experiment 2.
+
+  A second possibility is that individuals updated the estimate of gamma at different rates when faced with different demands.
+Previous accounts have demonstrated biases that can impact the learning of the opportunity cost in foraging paradigms [@Dundon2020; @Garrett2020].
+We therefore tested a second candidate model, an *adaptive model* that allowed $\gamma$ to evolve over time, adapting a learning rule from @Constantino2015
 
@@
 \begin{align}
-  \tau_{i} = H_{i}  A_{i} + T_{i}
+  \tau_{i} = {T}_{\text{handling}_i}  A_{i} + {T}_{\text{travel}_i}
 \end{align}
@@
 such that the handling time was counted only for accepted trials.
-Higher values of the learning rate $\alpha$ (ranging from 0 to 1) resulted in a larger update toward the current trial's earning rate weighted by its duration (first term in the equation).
-For this adaptive model, we fit the learning rate $\alpha$ and the initial value of $\gamma$ in addition to the temperature.
-These modifications allowed for the tracking of recent reward history, while maintaining the same decision rule
+Higher values of the learning rate $\alpha$ (ranging from 0 to 1) resulted in a larger update toward the current trial's rate of earnings weighted by its duration (first term in the equation).
+Free parameters for this adaptive model were the learning rate $\alpha$ and the initial value of $\gamma$ in addition to the temperature $\beta$.
+These modifications allowed for the tracking of recent reward history, while maintaining the same evaluation rule
 
 \begin{align}
-  \text{Model}_\text{adaptive} = R_i - \gamma_i H_i
+  V_{\text{adaptive}_i} = {R}_{i} - \gamma_i {T}_{\text{handling}_i}
 \end{align}
 
-where values of $\gamma$ were now updated on each trial $i$ according to Eq. 3, rather than by the empirical earning rate.
-
-  Another possibility was that rather than impacting the learning rate, covert features specific to each type of demand additively biased the estimate of $\gamma$.
-Suchuniformly affected the way people perceived the opportunity cost bias would be of time.
-If so, biases could remain stable if a single only one type of demand was experienced, (Experiment 1), but adjust over time as biases from other tasks were experienced (Experiment 2).
-For example, such biases could reflect an individual’s global estimation of the richness of the environment, or a focal estimation of the passage of time experienced during performance of each task (e.g.
-how long 10 seconds actually feel).
-Altered perceived time durations have occasionally been associated with levels of cognitive engagement [@Csikszentmihalyi2014; @Wearden2016], and have a direct effect on a trial’s reward rate.
-Intuitively, the perceived passage of time could be recalibrated into a global estimate as decision makers faced different types of with experience.
-We modeled these biases by adding a demand-specific term to $\gamma$ that was gradually integrated across tasks for those participants who foraged among demands.
+where values of $\gamma$ were now updated on each trial $i$ according to Eq. 3, rather than by the empirical rate of earnings.
+
+  A third possibility was that rather than impacting the learning rate, features specific to each cost condition additively biased the estimate of $\gamma$.
+Such bias could remain stable if only one type of demand was experienced (Experiment 1), but adjust over time as biases from other tasks were experienced (Experiment 2).
+For example, such biases could reflect an individual’s global estimation of the richness of the environment, could reflect any direct utility or disutility of the experience during the handling time, or could reflect a focal estimation of the passage of time experienced during performance of each task (e.g.
+how long 10 seconds subjectively feels).
+Altered perceived time durations have occasionally been associated with levels of cognitive engagement [@Csikszentmihalyi2014; @Wearden2016], and would be expected to impact the subjective estimate of a trial’s reward rate.
+Intuitively, the subjective duration of a fixed handling time could be recalibrated toward a consensus estimate as decision makers experienced different types of pre-reward demands.
+Our third candidate model, *biased model*, added a demand-specific term to $\gamma$ that was gradually integrated across tasks for those participants who experienced multiple cost conditions.
 The overall model took the following form
@@
 \begin{align}
-  \text{Model}_\text{biased} = R_i - (\gamma + C_i) H_i
+  V_{\text{biased}_i} = {R}_{i} - (\gamma + C_i) {T}_{\text{handling}_i}
 \end{align}
 
-where $\gamma$ was the mean total earning rate per subject (mean = 0.55 cents per second, SD = 0.02).
-Negative values of $C_i$ would therefore suggest a boost in offer value produced by a demand.
-At each decision point, $C_i$ was the cost bias produced by each demand $c_\text{demand}$ weighted against a global bias estimate $c_\text{global}$
+where $\gamma$ was the mean total rate of earnings per subject (mean = 0.55 cents per second, SD = 0.02).
+Negative values of $C_i$ would therefore suggest a boost in offer value produced by a particular form of demand.
+On each trial $i$, $C_i$ was the cost bias produced by each demand $c_\text{demand}$ weighted against a global bias estimate $c_\text{global}$
 
@@
 
-with $w_i$ controlling how early participants started integrating the converging cost $c_\text{global}$ into their decisions. The value of this weight was given by
+with $w_i$ controlling how early participants started integrating the consensus cost $c_\text{global}$ into their decisions. The value of this weight was given by
 
@@
 
-where the section in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parameter $\alpha_w$ denoting a late integration of the global converging bias.
-Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_\text{demand}$ and $c_\text{global}$ where the same and $\alpha_w$ did not play a role.
-This resulted in just fitting parameters $c_\text{demand}$ and $\beta$ for that dataset.
-For the within-subjects group, we assumed that the resulting $c_\text{demand}$ values from the first experiment reflected the actual bias induced by each demand.
-We therefore fixed each value of $c_\text{demand}$ (i.e.
-$c_\text{cognitive}$, $c_\text{wait}$, and $c_\text{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit the global bias $c_\text{global}$, the convergence rate $\alpha_w$, and temperature $\beta$.
-This dynamic allowed for the observed merging of acceptances across demands in Experiment 2, while respecting the stability in the between-subjects study.
-
-  Finally, we asked if the biases imposed by each demand could be isolated from a flexible computation of the opportunity cost of time.
-This fourth model combined the main features from $\text{Model}_\text{adaptive}$ and $\text{Model}_\text{biased}$, such that $\gamma$ was estimated on each trial per Eq.
-3, with demands imposing distinct and potentially converging biases as described in model 3.
+where the term in parentheses was the proportion of the experiment completed so far (note that the organization of the experimental session was fully disclosed), with high values of the free parameter $\alpha_w$ denoting a late integration of the global converging bias.
+Since participants in Experiment 1 experienced a single type of demand, the values of $c_\text{demand}$ and $c_\text{global}$ where the same and $\alpha_w$ did not play a role.
+This resulted in fitting only two free parameters, $c_\text{demand}$ and $\beta$, for that data set.
+For Experiment 2, we fixed each value of $c_\text{demand}$ (i.e.
+$c_\text{cognitive}$, $c_\text{wait}$, and $c_\text{physical}$) to the mean of the fitted parameters from each demand group from Experiment 1, and fit three free parameters: the global bias $c_\text{global}$, the convergence rate $\alpha_w$, and temperature $\beta$.
+This dynamic allowed for differences in acceptance rates across cost conditions to remain stable in Experiment 1 but gradually collapse in Experiment 2.
+
+  Finally, we asked if the biases imposed by each form of demand could be isolated from a flexible computation of the opportunity cost of time.
+Our fourth candidate model, an *adaptive + biased model*, combined the main features of the adaptive model and the biased model, such that $\gamma$ was estimated on each trial per Eq.
+3, with demands imposing distinct and potentially converging biases as described in Eq.
+6-8.
 The form of this fourth model was
@@
 \begin{align}
-  \text{Model}_\text{adaptive + biased} = R_i - (\gamma_i + C_i) H_i
+  V_{\text{ataptive + biased}_i} = {R}_{i} - (\gamma_i + C_i) {T}_{\text{handling}_i}
 \end{align}
 
-  The resulting parameters were compared across cost groups (Experiment 1) and across experiments using ANOVAs, and the cdemand biases computed in Experiment 1 were compared against 0 using one-sample t-tests.
+  The resulting parameters were compared across cost groups (in Experiment 1) and across experiments using ANOVAs, and the $c_\text{demand}$ biases computed in Experiment 1 were compared against 0 using one-sample t-tests.
 

### 2021-05-29 Manuscript.Rmd
modeling section done

@@
 
+  We fit four free parameters to Experiment 1 data (the temperature $\beta$, learning rate $\alpha$, initial value of $\gamma$, and demand-specific bias $c_\text{demand}$) and five free parameters to Experiment 2 data (the temperature $\beta$, learning rate $\alpha$, initial value of $\gamma$, consensus bias $c_\text{global}$, and the rate of bias integration $\alpha_w$).
 The resulting parameters were compared across cost groups (in Experiment 1) and across experiments using ANOVAs, and the $c_\text{demand}$ biases computed in Experiment 1 were compared against 0 using one-sample t-tests.
@@
   xlab("") +
+  ylab("iBIC") +
   scale_x_discrete(labels = c("Base", "Adaptive", "Biased", "A + B")) +
@@
 
-  The fourth model produced the lowest BIC in both experiments (Fig.
-9A.
-Between-subjects = `r round(modelComparison[4, 3], digits = 2)`; Within-subjects = `r round(modelComparison[8, 3], digits = 2)`), indicating that the tenets of the Marginal Value Theorem were necessary but not sufficient to explain the observed adaptive behavior.
+  The fourth model produced the lowest iBIC in both experiments (Fig.
+9A; Experiment 1 iBIC = `r round(modelComparison[4, 3], digits = 2)`; Experiment 2 iBIC = `r round(modelComparison[8, 3], digits = 2)`), indicating that the tenets of the Marginal Value Theorem were necessary but not sufficient to explain the observed adaptive behavior.
 Fig.
 9B-C show parameter fits from the winning model for both experiments.
-The learning rate $\alpha$ and the bias $c_\text{demand}$ were of particular interest, as these parameters distinguished whether different demands globally affected the integration of the environmental richness or focally modulated an offer's perceived cost, respectively.
-Analyses of variance showed significant differences among Experiment 1 groups only for $c_\text{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[2]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being uniformly low for all groups.
-Pairwise post-hoc permutations confirmed that the cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower biases than either wait (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or physical (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`) groups.
-These biases were significantly higher than zero for the wait group (t(`r fitOStest$tresults[[1]]$parameter`) = `r round(fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and lower than zero for the cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = `r round(fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
-This suggests that rather than reducing costs, cognitive tasks boosted the value of their concomitant offers.
+The learning rate $\alpha$ and the bias $c_\text{demand}$ were of particular interest, as these parameters distinguished whether different forms of demand globally affected the integration of the environmental richness or directly modulated an offer's perceived cost, respectively.
+Analyses of variance showed significant differences among Experiment 1 groups only for $c_\text{demand}$ (F(`r aovBtw$cost[[1]]$Df[1]`, `r aovBtw$cost[[1]]$Df[2]`) = `r fitFvals["cost"]`, *p* `r report_p(fitPvals["cost"])`), with $\alpha$ being similar for all groups.
+Pairwise post-hoc permutations confirmed that the Cognitive group (mean = `r round(mFits_btw["cost", "cogTask"], digits = 2)`, SD = `r round(sdFits_btw["cost", "cogTask"], digits = 2)`) had lower values for the bias parameter than either the Wait group (mean = `r round(mFits_btw["cost", "wait"], digits = 2)`, SD = `r round(sdFits_btw["cost", "wait"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Wait"])`; Cohen's D = `r fitES["Cognitive", "Wait"]`) or the Physical group (mean = `r round(mFits_btw["cost", "phys"], digits = 2)`, SD = `r round(sdFits_btw["cost", "phys"], digits = 2)`; *p* `r report_p(fitPerms["Cognitive", "Physical"])`; Cohen's D = `r fitES["Cognitive", "Physical"]`).
+Parameter estimates were significantly greater than zero for the Wait group (t(`r fitOStest$tresults[[1]]$parameter`) = `r round(fitOStest$tresults[[1]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[1]]$p.value)`), and marginally significantly lower than zero for the Cognitive group (t(`r fitOStest$tresults[[2]]$parameter`) = `r round(fitOStest$tresults[[2]]$statistic, digits = 2)`, *p* `r report_p(fitOStest$tresults[[2]]$p.value)`).
 
@@
 
-# modelPlot <- (bicPlot + costPlot) / allFitsPlot
-# ggsave("./Images/FIG9_modelresults.png", modelPlot, device = "png", height = 8, width = 11)
+modelPlot <- (bicPlot + costPlot) / allFitsPlot
+ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
 include_graphics("./Images/FIG9_modelresults.png")
@@
 
-  The mean values of $c_\text{demand}$ from each group were carried over to the within-subjects fitting, and were aggregated over time according to a weighted decay into a final $c_\text{global}$ value.
-As can be seen on Fig.
-9C, parameter values were comparable across experiments, pointing to consistency in the way decision makers approached our foraging scenarios.
+  The mean values of $c_\text{demand}$ from each group were carried over to the model of Experiment 2, and were aggregated over time according to a weighted decay into a final $c_\text{global}$ value.
+As can be seen in Fig.
+9C, other parameter values were comparable across experiments, pointing to consistency in the way decision makers approached our foraging scenarios.
 In addition, values of $\alpha_w$ suggested that $c_\text{demand}$ estimates converged towards the second half of the experiment (mean = `r mFits_wth[4]`, SD = `r sdFits_wth[4]`), gradually reducing bias by the end of the experimental session ($c_\text{global}$ mean = `r mFits_wth[3]`, SD = `r sdFits_wth[3]`).
@@
 This is illustrated in Fig.
-9, in which 95% confidence intervals from within-subject fits are overlaid to empirical choices (Experiment 1 fits matched the left side of this figure, as expected).
+9, in which 95% confidence intervals from within-subject fits are overlaid on empirical choices from Experiment 2.
 

### 2021-05-29 Manuscript.Rmd
into the discussion edits

@@
   Understanding the sporadic attractiveness of effort remains elusive.
-In this study, we sought to identify factors underlying this phenomenon, and tested the hypothesis that the perceived cost or value of a demand could depend on the ability to achieve the same outcome through different means.
-Using two foraging experiments that exposed individuals to a single or intermixed types of demands, we found a tendency toward engaging with cognitively effortful prospets when individuals faced a single form of demand, which faded over time when other costs were also experienced.
+In this study, we sought to identify factors underlying this phenomenon, and tested the hypothesis that the perceived cost or value of effort could depend on whether the decision environment contains opportunities to achieve the same outcome through different means.
+We conducted two foraging experiments that exposed individuals to a single or intermixed types of demands (cognitive effort, physical effort, or passive delay).
+We found a tendency toward engaging with cognitively effortful prospects when individuals faced a single form of demand, which faded over time when other costs were also experienced.
 
   Our findings provided partial support for our pre-registered hypotheses (https://osf.io/2rsgm/registrations).
-In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points.
+In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal levels.
 This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013].
-In contrast, our prediction that effort requirements would produce more acceptances only held for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for Experiment 2.
-These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; @Olivola2013].
-Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted that reward-independent task features can promote the pursuit of effortful prospects.
-The fact that predicted stable preferences for cognitive effort carried over onto the beginning of Experiment 2 further supported a task-specific modulation.
-However, the unexpected gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.
+In contrast, our prediction that effort requirements would lead to greater acceptance rates only held for the cognitive effort group, and this tendency did not reverse as predicted in Experiment 2.
+These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing when presented in isolation [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest way to achieve desired outcomes when multiple alternatives are available [@Hull1943; @Kool2010; @Olivola2013].
+Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted that reward-independent task characteristics can promote or inhibit the pursuit of effortful prospects.
 

### 2021-05-30 Manuscript.Rmd
done with discussion edits

@@
 
-These choice dynamics ruled out a number of common explanatory candidates.
-For instance, if the subjective costs of effort or delay were intrinsic, we would not have observed the gradual convergence in acceptances when they were all intermixed in the same environment.
-This also speaks against a direct role of boredom in our results.
+  The observed choice dynamics ruled out a number of candidate explanations.
+For instance, if the subjective costs and benefits of effort or delay were intrinsic, we would not have expected to observe the gradual convergence in acceptances when all three forms of demand were intermixed in the same environment.
+This line of reasoning also speaks against a direct role of boredom in our results.
 The aversiveness of boredom can lead people to attempt any available activity in order to avoid it [@westgate2020].
-This would have likely led to a persistent preference for either effortful condition.
-Lastly, this gradual convergence in choices rules out the possibility that our sample was mostly composed of demand seekers.
+In our paradigm, such a tendency would have been expected to lead to a persistent preference for either effortful condition.
+Lastly, the gradual convergence of acceptance rates across cost conditions  rules out the possibility that our sample was mostly composed of demand seekers.
 Some individuals express a strong need for cognition, which can bias studies of mental labor [@Cacioppo1996; @Sayali2019].
@@
 Another unlikely candidate is fatigue.
-Even though participants decreased their acceptance rates for effort in both experiments, we would have expected them to increase engagement with wait trials over time in order to preserve earning rates.
-Further, we do not expect any of our observations to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments.
+Even though participants decreased their acceptance rates for effort in both experiments, we would have expected participants in Experiment 2 to increase engagement with wait trials, substituting wait trials for effort trials in order to preserve their earnings.
+Our observations are unlikely to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments.
 Finally, we cannot conclude that cognitive effort gained value from its rewarding outcomes, as has been proposed in the past [@Eisenberger1996].
-This phenomenon could not have benefitted a single type of demand, as cognitive effort, physical effort, and unfilled delay were rewarded at the same rate.
-
-  Traditional foraging models, in which a reward is weighed against the earnings foregone by pursuing it [@Charnov1976; @Constantino2015], were also not enough to explain our results.
+This phenomenon would not have been expected to benegit a single type of demand differentially because cognitive effort, physical effort, and unfilled delay were rewarded at the same rate.
+
+  Traditional foraging models, in which a reward is weighed against the earnings foregone by pursuing it [@Charnov1976; @Constantino2015], were also not sufficient to explain our results.
 Instead, our results were consistent with a computational model in which each type of demand distinctly biased the estimation of the opportunity cost, and such biases could be gradually recalibrated over time as decision makers gained experience with additional demands.
@@
 This raises the question of how these biases arise.
-We hypothesize that demands altered the perceived duration of time.
+We hypothesize that demands altered the perceived duration of the delay interval.
 Immersive activities can subjectively speed up the passage of time [@Csikszentmihalyi2014], and this effect appears to scale with the amount of cognitive processing required by a task [@Wearden2016].
 Moreover, adjusting for time sensitivity has been shown to improve fits for delay discounting models [@Mckerchar2009].
-Therefore, even though participants knew the nominal handling times, cognitive effort might have become valuable by subjectively compressing the perceived durations.
-In our experiments, shorter subjective handling times would result in higher perceived earning rates, but it is also possible that individuals benefitted from a sense of fast completion.
-We speculate that this construal of elapsed time could then be adjusted with the experience of alternative demands, as participants learned how long the 10 seconds handling time felt.
-This could help explain why preferences for cognitive effort were smaller for within-subject participants who started with the physical block, as they had already formed an estimate of the handling time by the time they experienced a subjectively faster cognitive trial.
-The shorter time sensitivity produced by cognitive effort could be due to participants counting the number of sub-tasks during pursual (which was always less than the number of seconds in the handling time), or because taxing cognitive resources distracted individuals from estimating the passage of time [@Zakay1989].
+Therefore, even though participants knew the nominal handling times, cognitive effort might have promoted higher acceptance rates by subjectively compressing the perceived durations.
+We speculate that this construal of elapsed time could then be adjusted with the experience of alternative demands, as participants learned how long the 10-second handling time felt in the context of various activities.
+This could help explain why preferences for cognitive effort were smaller for those participants in Experiment 2 who started with the physical effort block, as they had already begun to form an estimate of the handling time before they experienced their first cognitive effort trial.
+The cognitive effort task might have shortened subjective durations for several reasons, either because it divided the handling time into discrete, 2 s trials, or because taxing cognitive resources distracted individuals from estimating the passage of time [@Zakay1989].
 These hypotheses will have to be experimentally probed in the future.
 
-  Relying on foraging paradigms helped us to control for common shortfalls in the existing literature.
-For example, even though engaging with a demanding offer encompasses evaluating, pursuing, and receiving its outcome, investigations of the pursuit and receipt stages have been limited.
-Many studies have sought to isolate the evaluation stage by presenting individuals with offers that do not come into effect until the end of the experimental session, deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a].
-However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate outcomes could be due to factors other than time preference, such as the risk of being unable to redeem the future rewards, or hoping to find better offers in the near future [@Fawcett2012; @Frederick2002; @Sozou1998].
+  Relying on foraging paradigms enabled us to address several gaps in the existing literature of effort-based decision making.
+For example, even though engaging with a demanding offer encompasses the evaluation, pursuit, and receipt of the outcome, investigations of the pursuit and receipt stages have been limited.
+Many studies have sought to isolate the evaluation stage by presenting individuals with offers that are not realized until the end of the experimental session, deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a].
+However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate or low-effort outcomes could be due to factors other than time preference, such as a perceived risk of being unable to redeem the future rewards, or hoping to find better offers in the near future [@Fawcett2012; @Frederick2002; @Sozou1998].
 We circumvented these pitfalls by providing participants with an opportunity to actively experience the demands they accepted, and giving them full knowledge of the available options.
 Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time.
-This issue is often avoided by comparing discounting functions, which yield points at which individuals faced with increasing costs become indifferent to large rewards [@Massar2015; @Prevost2010].
-We eliminated this possibility by fixing the handling time for all demands, allowing us to probe people's preferences directly.
-Moreover, Experiment 1 provided a baseline of foraging behavior that contextualized the findings of the second experiment (a direct test of our hypothesis).
-Finally, the existence of optimal strategies helped us identify when demands could be attractive, a central motivation for this study.
-The apparent attractiveness of cognitive effort was reflected both by a higher proportion of acceptances at the expense of earnings, and by the fitted opportunity costs biases discussed above.
-Of note is that the optimality of the strategies induced by each demand depended on the richness of the block.
-This can help explain why the wait group earned the most despite having similar acceptance rates to the physical group, as the former was closer to optimality in the richest environment.
-
-  A potential limitation of this work lies in whether our task manipulations were actually costly.
-For instance, it is possible that participants gravitated towards cognitive demands because the task configuration was not effortful.
-This could be due to differences in how we calibrated cognitive and physical tasks.
+We avoided this issue by imposing consistent handling times for all demands, allowing us manipulate temporal durations and demands for effort independently.
+Finally, the existence of well-defined optimal strategies provided a useful reference point for evaluating choice behavior.
+The apparent attractiveness of cognitive effort was reflected both by a higher proportion of acceptances at the expense of earnings, and by parameter estimates capturing bias in the estimation of opportunity costs.
+
+  A potential limitation of this work is that we examined only a single combination of cognitively effortful tasks.
+Future work should investigate whether other ways of operationalizing cognitive and physical effort would be more aversive or more engaging and would resultingly have different effects on decision making.
+A potentially relevant factor is the way in which we calibrated cognitive and physical tasks.
 For physical demands, we adjusted the gripping threshold to people's maximum strength, whereas we trained participants in the cognitive tasks until they reached criterion.
@@
 In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [@Bandura2010; @Eisenberger1996].
-However, hand grips are regularly used to probe physical effort [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to feel cognitively effortful by recruiting cognitive control [@Kool2010; @Shenhav2017].
-Furthermore, we observed a steeper decrease in acceptances over time for both effort domains, a hallmark of effortful exertion [@Treadway2009].
-
-  The present findings have important implications for daily and clinical scenarios.
+However, hand grip tasks have frequently been used to probe physical effort in previous work [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to impose subjective costs [@Kool2010; @Shenhav2017].
+Furthermore, the observed decrease in acceptance rates over time for both effort domains is consistent with patterns seen for other forms of effortful exertion [@Treadway2009].
+
+  The present findings have important implications for everyday and clinical scenarios.
 Excessive aversion to delay and effort can manifest as impulsivity and apathy, respectively [@Ainslie1975; @Bonnelle2016; @Chong2016; @Cummings1993], fluctuations in which are hallmark symptoms of various mental illnesses and substance use disorders [@Paulus2007].
-Lack of motivation to exert effort or wait for prospects is a distinguishing factor among mental afflictions like depression and schizophrenia [@Barch2019].
-Within the former, medicated patients in remission are more sensitive to effort than controls, and this sensitivity is predictive of relapse [@Berwian2020].
+Lack of motivation to exert effort or wait for delayed prospects is a distinguishing factor of conditions such as depression and schizophrenia [@Barch2019].
+In depression, medicated patients in remission are more sensitive to effort than control participants, and this sensitivity is predictive of relapse [@Berwian2020].
 Encouraging patients to engage in activities has been found to be a helpful treatment for depression [@Dimidjian2006].
 Tailored reward schedules can successfully achieve this [@Eisenberger1996].
-However, since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases.
-Our work suggests that subdividing a task can promote its pursuit, although further testing is required.
-More importantly, it highlights that decision scenarios should be configured to promote pursuit of desired activities, perhaps by removing alternative uses of time.
+However, since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help address treatment-resistant cases.
+Our work suggests that voluntary effortful engagement can be encouraged by removing cognitively less-effortful paths to reward from the immediate decision context, and suggests it would be useful for future work to test directly for effects of effortful tasks on concurrent time estimation.
 These same principles can potentially be applied to increasing productivity at work or adherence to physical exercise routines.
@@
 
-  In this study, we have examined the factors that motivate engagement with different behavioral demands, emphasizing how these can be molded by the decision maker's environment.
-Unlike existing theories that have focused on the role of incentives and retrospective justifications [@Eisenberger1996; @Inzlicht2018], our work highlights outcome-independent and task-specific features that can motivate the pursuit of effortful avenues, which can be potentially manipulated in order to promote engagement in clinical and daily activities.
+  In this study, we have examined the factors that motivate engagement with different behavioral demands, emphasizing how engagement can be influenced by features of the decision environment.
+Complementing work that has focused on the role of incentives and retrospective justifications [@Eisenberger1996; @Inzlicht2018], our work highlights outcome-independent and task-specific features that can motivate the pursuit of effortful courses of action.
 

### 2021-05-30 Manuscript.Rmd
taking care of leftover notes before dealing with figs + new/fixed refs

@@
 
-      # wait group
+      # Wait group
       x <- sample(group,length(group),replace=T)  
@@
 
-        # Mistakes (only for cognitive effort group)
+        # Mistakes (only for Cognitive group)
         tempMistakes <- sum(cogDataLong[[subj]]$`Trial Outcome`=="Forced travel") # how many forced travel trials
@@
 
-        # Mistakes (to allow for mistakes on the cognitive group)
+        # Mistakes (to allow for mistakes on the Cognitive group)
         tempSummary[subj,5] <- NA
@@
 Consistent with our predictions, we found that individuals could approximate optimality by favoring higher rewards and shorter delays.
-We also found that people in the cognitive effort group accepted more trials than optimal, whereas physical effort and wait groups under-accepted, partially matching our predictions but raising the possibility that cognitive effort might add value to outcomes (or attenuate subjective temporal costs).
+We also found that people in the Cognitive group accepted more trials than optimal, whereas Physical and Wait groups under-accepted, partially matching our predictions but raising the possibility that cognitive effort might add value to outcomes (or attenuate subjective temporal costs).
 Finally, acceptance rates (and differences in acceptance rates across demands) were stable within each cost condition, in line with expectations.
@@
   Four groups of participants faced with different behavioral demands (physical effort, cognitive effort, low-effort task engagement, or passive delay) chose their preferred strategy to maximize rewards in foraging environments of varying richness.
+We will refer to the four groups below as Physical, Cognitive, Easy, and Wait.
 Environmental richness was dictated by the time it took to obtain a reward (the handling time) and the time between trials (the travel time).
@@
 Since participants in the effort groups were forced to travel when they failed to perform above threshold (see Methods), we distinguish between acceptances (not explicitly quitting a trial during the handling period) and completions (successfully obtaining a reward).
-Even so, the proportion of forced travels was low for the cognitive effort group (`r round(propFails[2, 2]$meanFT, digits = 2) * 100`% on average across participants) and 0 for the physical effort group (i.e.
+Even so, the proportion of forced travels was low for the Cognitive group (`r round(propFails[2, 2]$meanFT, digits = 2) * 100`% on average across participants) and 0 for the Physical group (i.e.
 no forced travels in this group).
@@
 
-  The next set of analyses examined the hypothesis that both cognitive effort and physical effort groups would uniformly accept more trials than passive delay and easy groups.
+  The next set of analyses examined the hypothesis that both Cognitive and Physical groups would uniformly accept more trials than the Wait and Easy groups.
 Fig.
-2 (left) shows that the cognitive effort group consistently accepted more offers, which resulted in lower earnings (middle).
+2 (left) shows that the Cognitive group consistently accepted more offers, which resulted in lower earnings (middle).
 One-way ANOVAs showed that differences among groups were significant both for overall proportion accepted (F(`r propAov[[1]]$Df[1]`, `r propAov[[1]]$Df[2]`) = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F(`r earnAov[[1]]$Df[1]`, `r earnAov[[1]]$Df[2]`) = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
-Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the cognitive effort group (mean = `r filter(overallSumms, Cost == "Cognitive")$mProp`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdProp`) were higher than those of the physical (mean = `r filter(overallSumms, Cost == "Physical")$mProp`, SD = `r filter(overallSumms, Cost == "Physical")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive")$cohenD`) and wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mProp`, SD = `r filter(overallSumms, Cost == "Wait")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait")$cohenD`).
-It also showed that those faced with the easy task accepted more than those in the wait group, although responses from the easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy")$mProp`, SD = `r filter(overallSumms, Cost == "Easy")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Wait < Easy")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy")$cohenD`) (all other *p* > 0.05).
-In line with its higher acceptance rates, the cognitive effort group had significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than either the physical group (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) or the wait group (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
-In addition, the wait group earned more than the physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
+Post-hoc permutations (5000 iterations) comparing mean acceptance rates between every pair of costs confirmed that acceptance rates of the Cognitive group (mean = `r filter(overallSumms, Cost == "Cognitive")$mProp`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdProp`) were higher than those of the Physical (mean = `r filter(overallSumms, Cost == "Physical")$mProp`, SD = `r filter(overallSumms, Cost == "Physical")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Physical < Cognitive")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Physical < Cognitive")$cohenD`) and Wait groups (mean = `r filter(overallSumms, Cost == "Wait")$mProp`, SD = `r filter(overallSumms, Cost == "Wait")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Cognitive > Wait")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Cognitive > Wait")$cohenD`).
+It also showed that those faced with the easy task accepted more than those in the Wait group, although responses from the Easy group were more variable (mean Easy = `r filter(overallSumms, Cost == "Easy")$mProp`, SD = `r filter(overallSumms, Cost == "Easy")$sdProp`; *p* `r report_p(filter(propTests, contrast == "Wait < Easy")$permPval)`, Cohen's D = `r filter(propTests, contrast == "Wait < Easy")$cohenD`) (all other *p* > 0.05).
+In line with its higher acceptance rates, the Cognitive group had significantly lower earnings (mean = `r filter(overallSumms, Cost == "Cognitive")$mEarn`, SD = `r filter(overallSumms, Cost == "Cognitive")$sdEarn`) than either the Physical group (mean = `r filter(overallSumms, Cost == "Physical")$mEarn`, SD = `r filter(overallSumms, Cost == "Physical")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Physical > Cognitive")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical > Cognitive")$cohenD`) or the Wait group (mean = `r filter(overallSumms, Cost == "Wait")$mEarn`, SD = `r filter(overallSumms, Cost == "Wait")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Cognitive < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Cognitive < Wait")$cohenD`).
+In addition, the Wait group earned more than the Physical (*p* `r report_p(filter(earnTests, contrast == "Physical < Wait")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Physical < Wait")$cohenD`) and Easy groups (mean Easy = `r filter(overallSumms, Cost == "Easy")$mEarn`, SD = `r filter(overallSumms, Cost == "Easy")$sdEarn`; *p* `r report_p(filter(earnTests, contrast == "Wait > Easy")$permPval)`, Cohen's D = `r filter(earnTests, contrast == "Wait > Easy")$cohenD`).
 
@@
 We performed group-level chi-squared tests of proportions (with trials pooled across participants) to examine whether each cost biased decision makers to under- or over-accept 4 and 8 cent offers, which collectively should have been accepted 50% of the time across the three timing environments.
-We found a significant over-acceptance of these trials by the cognitive effort group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Cognitive", "pval"])`), but under-acceptances by the physical effort group (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) and wait group (proportion accepted = `r round(optimalProp_cost["Wait", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Wait", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Wait", "pval"])`), with no significant difference for the Easy group.
+We found a significant over-acceptance of these trials by the Cognitive group (proportion accepted = `r round(optimalProp_cost["Cognitive", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Cognitive", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Cognitive", "pval"])`), but under-acceptances by the Physical group (proportion accepted = `r round(optimalProp_cost["Physical", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Physical", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Physical", "pval"])`) and Wait group (proportion accepted = `r round(optimalProp_cost["Wait", "probability"], digits = 2)`; $\chi^2$ = `r round(optimalProp_cost["Wait", "chisquared"], digits = 2)`, *p* `r report_p(optimalProp_cost["Wait", "pval"])`), with no significant difference for the Easy group.
 Together, the findings discussed so far indicate that although participants reacted appropriately to reward and timing contingencies, departures from optimality were systematically influenced by what form of cost was at stake.
@@
 First, participants adapted to the richness of each timing block, gravitating towards optimality regardless of the cost they faced.
-Second, effects of cost type were consistent across the three timing conditions, and acceptances were uniformly highest for the cognitive effort group.
+Second, effects of cost type were consistent across the three timing conditions, and acceptances were uniformly highest for the Cognitive group.
 We tested these observations with a mixed-effects logistic regression model, which estimated the probability of accepting an offer as a function of handling time, reward amount, and cost type (see Methods for details).
@@
 3B.
-The cognitive effort group was significantly more likely to accept offers than the physical effort group ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) or the wait groups ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.
+The Cognitive group was significantly more likely to accept offers than the Physical group ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) or the Wait group ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.
 
@@
 Plotting the quitting time distributions across blocks for the first 1 s of the handling time (ECDFs on Fig.
-4, top-right) showed that participants in the wait and cognitive groups responded faster as the experiment progressed.
+4, top-right) showed that participants in the Wait and Cognitive groups responded faster as the experiment progressed.
 These response time observations suggested clarity in participant choices.
@@
 4 (bottom-left and bottom-right) shows the overall proportion accepted by each participant before and after the midpoint of the session.
-Paired permutations showed no change in acceptance rates for the wait and easy groups (*p* > 0.05), but we found significantly lower acceptance rates in the second half of the session for the physical effort group (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and the cognitive effort group (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`).
+Paired permutations showed no change in acceptance rates for the wait and easy groups (*p* > 0.05), but we found significantly lower acceptance rates in the second half of the session for the Physical group (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and the Cognitive group (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`).
 Fig.
@@
 B: Differences in cost biases produced by each demand.
-Negative values suggest the cognitive group acted as if it perceived its demand as valuable.
+Negative values suggest the Cognitive group acted as if it perceived its demand as valuable.
 C: Parameter comparison portrays consistent foraging behavior across experiments.
@@
 This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013].
-In contrast, our prediction that effort requirements would lead to greater acceptance rates only held for the cognitive effort group, and this tendency did not reverse as predicted in Experiment 2.
+In contrast, our prediction that effort requirements would lead to greater acceptance rates only held for the Cognitive group, and this tendency did not reverse as predicted in Experiment 2.
 These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing when presented in isolation [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest way to achieve desired outcomes when multiple alternatives are available [@Hull1943; @Kool2010; @Olivola2013].
@@
 This line of reasoning also speaks against a direct role of boredom in our results.
-The aversiveness of boredom can lead people to attempt any available activity in order to avoid it [@westgate2020].
+The aversiveness of boredom can lead people to attempt any available activity in order to avoid it [@westgate2020; @Wilson2014].
 In our paradigm, such a tendency would have been expected to lead to a persistent preference for either effortful condition.

### 2021-05-30 Manuscript.Rmd
updated figs

@@
     geom_point(size = 3, pch = 21, color = "black", show.legend = F) +
-    labs(x = "Proportion Accepted - First Block", y = "Proportion Accepted - Last Block") +
+    labs(x = "Prop. Accepted - First Two Blocks", y = "Prop. Accepted - Last Two Blocks") +
     scale_fill_manual(values = colsWth) +
@@
 # plots generated in 16.3.1. and 16.3.3.
-#historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
-#ggsave("./Images/FIG8_survival.png", historyPlot_wth, device = "png", height = 8, width = 10)
+# historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks) + 
+#     plot_annotation(tag_levels = 'A') &
+#     theme(plot.tag = element_text(size = 20, face = "bold"))
+#ggsave("./Images/FIG7_survivalwth.png", historyPlot_wth, device = "png", height = 8, width = 10)
 include_graphics("./Images/FIG7_survivalwth.png")

### 2021-05-30 Manuscript.Rmd
almost done with fig captions

@@
 A: General foraging trial structure.
-On each trial, participants were offered to earn money by sustaining effort or waiting during the handling time (2, 10, or 14 s).
+On each trial, participants were offered an opportunity to earn money by sustaining effort or waiting during the handling time (2, 10, or 14 s).
 The end of a trial was followed by a travel time (handling and travel times always added up to 16 s).
 Participants could skip unfavorable trials and immediately start traveling to a potentially better offer.
-In Experiment 1, cost was fixed per participant and handling time varied per block.
+In Experiment 1, the type of demand was fixed per participant and handling time varied per block.
 In Experiment 2, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block.
 B: Possible earnings per second for each acceptance threshold (i.e.
-the smallest amount accepted) for each handling time.
+the smallest amount accepted) for each handling time in Experiment 1.
 Circles denote the reward-maximizing threshold for each block, which is described in the table.
-Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers."}
+Experiment 2 presented only the 10 s handling time, for which it was optimal to skip all 4-cent offers."}
 
@@
 Consistent with the foraging design, participants who over and under accepted earned the least.
-These figures suggest that people are willing to pursue cognitively effortful actions at the expense of earnings."}
+These results suggest that people were willing to pursue cognitively effortful actions at the expense of earnings."}
 # plots generated in 16.2.1. and 16.1.3.
@@
 ```{r mixed effects plots (Fig.
-3), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
-A: Proportion accepted by each group for every combination of handling time and reward.
-Grey dots indicate the reward-maximizing acceptance for each combination.
-B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition (crosses mark non-significant comparisons).
-Each entry shows how much more likely a group was to accept compared to the reference condition (row).
-C: AIC and BIC values for a mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model.
-Both metrics yielded the same values across models."}
+3), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time.
+A: Mean acceptance rate in each group for every combination of handling time and reward (with SEM).
+Grey points indicate the reward-maximizing acceptance rate for each combination, which was always either 0 or 1.
+B: Matrix of coefficients that resulted from switching the reference cost condition in a mixed-effects logistic regression model.
+Each element represents how much more likely a group was to accept offers compared to the reference condition (row).
+White asterisks denote the p-value for significant comparisons (one, two, and three askterisks correspond to p-values under 0.05, 0.01, and 0.001, respectively).
+C: AIC and BIC values for a mixed-effects model comparison, ranging from a baseline intercept-only model to a full-interaction model.
+Both metrics yielded similar values across models."}
 #hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
@@
 4), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1.
-A: Survival curve showing quit times within trial.
-B: Distribution of times when participants quit a trial over time.
-C: Proportion accepted in the second half as a function of first half acceptances.
+A: Survival curve plots of trial rejection times.
+B: Distributions of trial rejection times within the first 1 s of the handling time.
+C: Acceptance rate in the second half of the session as a function of acceptance rate in the first half of the session.
 Dashed lines indicate the mean for each group.
@@
 5), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1.
-A: Proportion of acceptances per handling, reward, and session half, showing that effortful demands were less frequently accepted over time.
-B: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal).
-Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
-# left plot in 16.3.2
+A: Offer acceptance rates per handling time, reward amount, cost type, and session half, showing that effortful demands (Cognitive and Physical) were less frequently accepted over time, especially for the longest handling time (14 s).
+B: Mixed-effects logistic regression model coefficients denoting the comparison of acceptance rates across cost conditions for each half of the experimental session separately (mirrored along the diagonal).
+Even though acceptance rates decreased in the effort groups, the differences in acceptance rates across cost conditions were preserved."}
+# plots in 16.3.2
 # ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
@@
 ```{r Earnings/prop completed/ME plots (Fig.
-6), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior.
+6), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subject acceptance behavior.
 A: Quadratic relationship between trial completions and total earnings.
-B: proportion of acceptances of each reward per cost condition.
-C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount).
-Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions.
-Crosses mark non-significant comparisons.
-D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}
+B: Proportion of acceptances of each reward per cost condition.
+C: Matrix of mixed-effects coefficients showing comparisons among cost conditions (while controlling for reward amount).
+Cognitive and Physical trials were compared to one another and were each compared to Wait trials from the same block (Wait-C and Wait-P, respectively).
+We omitted comparisons to Wait trials in the opposite block type (gray cells), which have little interpretability and were not addressed in our predictions.
+Asterisks mark statistically significant comparisons.
+D: AIC and BIC values for models of increasing complexity ("AllMain" refers to the a priori model which included main effects of cost condition and reward offer amount.)"}
 # earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
@@
 7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2.
-Top: Survival curve (left), and distribution of quitting times over time (right).
-Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
+A: Survival curves showing trial rejection times for each cost condition.
+B: Distribution of trial rejection times within the offer window.
+C: Acceptance rate in the last two blocks as a function of acceptance rate in the first two blocks.
 Dashed lines indicate the mean for each cost.
-On the right, the proportion accepted every time participants experienced a given block type."}
+D: Acceptance rates in the three successive occurrences of each block type."}
 # plots generated in 16.3.1. and 16.3.3.
@@
 8), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2.
-Top-Left: Proportion accepted in the first two and last two blocks of the experiment.
-An initial preference for cognitive effort trials fades amid a global decrease in acceptance rates.
-Top-Right: Mixed effects coefficient matrix for each half separately.
-The pattern from the first half resembles what was observed in Experiment 1 (Figure 3).
-Bottom: Block order effects show attenuated differences for those who started with the physical configuration."}
+A: Proportion accepted in the first two and last two blocks of the experiment.
+An initial preference for cognitive effort trials faded amid a global decrease in acceptance rates.
+B: Mixed effects coefficient matrix for early and late trials separately.
+The pattern for early trials -- but not for late trials -- resembled what was observed in Experiment 1 (Figure 3B).
+C: Results presented separately for participants who experienced the Cognitive/Wait block type first or who experienced the Physical/Wait block type first."}
 # hrprepostPlot_wth, blockOrder_wth
-# ggsave("./Images/prepostwth_2.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
+# ggsave("./Images/FIG8_prepostwth.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
 include_graphics("./Images/FIG8_prepostwth.png")
@@
 The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}
-
-modelPlot <- (bicPlot + costPlot) / allFitsPlot
-ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
+# modelPlot <- (bicPlot + costPlot) / allFitsPlot
+# ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
 include_graphics("./Images/FIG9_modelresults.png")
@@
 Consistent with the foraging design, participants who over and under accepted earned the least.
-These figures suggest that people are willing to pursue cognitively effortful actions at the expense of earnings."}
+These results suggest that people were willing to pursue cognitively effortful actions at the expense of earnings."}
 # plots generated in 16.2.1. and 16.1.3.
+#(propPlot <- prop1 | earnings1 | earnFitplot_btw)
+#ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)
  prop1 | earnings1 | earnFitplot_btw
@@
 ```{r New mixed effects plots (Fig.
-3), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination.
-A: Proportion accepted by each group for every combination of handling time and reward.
-Grey dots indicate the reward-maximizing acceptance for each combination.
-B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition (crosses mark non-significant comparisons).
-Each entry shows how much more likely a group was to accept compared to the reference condition (row).
-C: AIC and BIC values for a mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model.
-Both metrics yielded the same values across models."}
+3), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time.
+A: Mean acceptance rate in each group for every combination of handling time and reward (with SEM).
+Grey points indicate the reward-maximizing acceptance rate for each combination, which was always either 0 or 1.
+B: Matrix of coefficients that resulted from switching the reference cost condition in a mixed-effects logistic regression model.
+Each element represents how much more likely a group was to accept offers compared to the reference condition (row).
+White asterisks denote the p-value for significant comparisons (one, two, and three askterisks correspond to p-values under 0.05, 0.01, and 0.001, respectively).
+C: AIC and BIC values for a mixed-effects model comparison, ranging from a baseline intercept-only model to a full-interaction model.
+Both metrics yielded similar values across models."}
 #hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
@@
 4), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1.
-A: Survival curve showing quit times within trial.
-B: Distribution of times when participants quit a trial over time.
-C: Proportion accepted in the second half as a function of first half acceptances.
+A: Survival curve plots of trial rejection times.
+B: Distributions of trial rejection times within the first 1 s of the handling time.
+C: Acceptance rate in the second half of the session as a function of acceptance rate in the first half of the session.
 Dashed lines indicate the mean for each group.
@@
 5), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1.
-A: Proportion of acceptances per handling, reward, and session half, showing that effortful demands were less frequently accepted over time.
-B: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal).
-Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
+A: Offer acceptance rates per handling time, reward amount, cost type, and session half, showing that effortful demands (Cognitive and Physical) were less frequently accepted over time, especially for the longest handling time (14 s).
+B: Mixed-effects logistic regression model coefficients denoting the comparison of acceptance rates across cost conditions for each half of the experimental session separately (mirrored along the diagonal).
+Even though acceptance rates decreased in the effort groups, the differences in acceptance rates across cost conditions were preserved."}
+# plots in 16.3.2
+# ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
 include_graphics("./Images/FIG5_prepostbtw.png")
@@
 ```{r New Earnings/prop completed/ME plots (Fig.
-6), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior.
+6), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subject acceptance behavior.
 A: Quadratic relationship between trial completions and total earnings.
-B: proportion of acceptances of each reward per cost condition.
-C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount).
-Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions.
-Crosses mark non-significant comparisons.
-D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}
-
+B: Proportion of acceptances of each reward per cost condition.
+C: Matrix of mixed-effects coefficients showing comparisons among cost conditions (while controlling for reward amount).
+Cognitive and Physical trials were compared to one another and were each compared to Wait trials from the same block (Wait-C and Wait-P, respectively).
+We omitted comparisons to Wait trials in the opposite block type (gray cells), which have little interpretability and were not addressed in our predictions.
+Asterisks mark statistically significant comparisons.
+D: AIC and BIC values for models of increasing complexity ("AllMain" refers to the a priori model which included main effects of cost condition and reward offer amount.)"}
+# earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
+#ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
 include_graphics("./Images/FIG6_wthlogistic.png")
@@
 7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2.
-Top: Survival curve (left), and distribution of quitting times over time (right).
-Bottom: Proportion accepted in the second half as a function of first half acceptances (left).
+A: Survival curves showing trial rejection times for each cost condition.
+B: Distribution of trial rejection times within the offer window.
+C: Acceptance rate in the last two blocks as a function of acceptance rate in the first two blocks.
 Dashed lines indicate the mean for each cost.
-On the right, the proportion accepted every time participants experienced a given block type."}
+D: Acceptance rates in the three successive occurrences of each block type."}
 # plots generated in 16.3.1. and 16.3.3.
-(suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
+# historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks) +
+#     plot_annotation(tag_levels = 'A') &
+#     theme(plot.tag = element_text(size = 20, face = "bold"))
+#ggsave("./Images/FIG7_survivalwth.png", historyPlot_wth, device = "png", height = 8, width = 10)
+include_graphics("./Images/FIG7_survivalwth.png")
 ```
@@
 8), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2.
-Top-Left: Proportion accepted in the first two and last two blocks of the experiment.
-An initial preference for cognitive effort trials fades amid a global decrease in acceptance rates.
-Top-Right: Mixed effects coefficient matrix for each half separately.
-The pattern from the first half resembles what was observed in Experiment 1 (Figure 3).
-Bottom: Block order effects show attenuated differences for those who started with the physical configuration."}
+A: Proportion accepted in the first two and last two blocks of the experiment.
+An initial preference for cognitive effort trials faded amid a global decrease in acceptance rates.
+B: Mixed effects coefficient matrix for early and late trials separately.
+The pattern for early trials -- but not for late trials -- resembled what was observed in Experiment 1 (Figure 3B).
+C: Results presented separately for participants who experienced the Cognitive/Wait block type first or who experienced the Physical/Wait block type first."}
+# hrprepostPlot_wth, blockOrder_wth
+# ggsave("./Images/FIG8_prepostwth.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
 include_graphics("./Images/FIG8_prepostwth.png")
@@
 The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}
-
+# modelPlot <- (bicPlot + costPlot) / allFitsPlot
+# ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
 include_graphics("./Images/FIG9_modelresults.png")
-
-#(bicPlot + costPlot) / allFitsPlot
 ```

### 2021-05-31 Manuscript.Rmd
all edits implemented!

@@
 
-  **Standard models in neuroeconomics and behavioral economics formalize the effects of effort or delay on valuation in terms of discounting functions** [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @kleinflugge2015; @Kool2010; @Westbrook2013].
+  Standard models in neuroeconomics and behavioral economics formalize the effects of effort or delay on valuation in terms of discounting functions [@Ainslie1975; @Frederick2002; @Green1994; @Kable2007; @kleinflugge2015; @Kool2010; @Westbrook2013].
 Discounting functions appear to have a similar form for delay and effort [@Massar2015; @Prevost2010; @Seaman2018], although there is ongoing debate about how the shape of the discounting function might vary across types of demands [@Arulpragasam2018; @Biaaszek2017; @Chong2017; @Hartmann2013; @Klein-Flugge2016; @Kool2018; @Prevost2010] and the degree to which discount rates correlate across cost domains [@Seaman2018; @Westbrook2013].
@@
 Specifically, foragers must decide whether to spend their limited time by harvesting a currently available resource or by seeking out more profitable (or less costly) alternatives instead.
-This could involve, for example, deciding when to leave a patch of depleting richness **(e.g.
-when to quit a job that provides diminishing opportunities for growth)**, or choosing whether to pursue or forgo offers presented serially **(e.g.
-whether to accept your first job offer or wait for new potential ones)**.
+This could involve, for example, deciding when to leave a patch of depleting richness (e.g.
+when to quit a job that provides diminishing opportunities for growth), or choosing whether to pursue or forgo offers presented serially (e.g.
+whether to accept your first job offer or wait for new potential ones).
 Here we focus on this latter type of foraging, traditionally called *prey selection* [@Krebs1977], as it provides a means to examine how choices to accept or reject individual prospects are influenced by contextual knowledge about other potentially obtainable alternatives in the same environment.
@@
 2), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1.
-Left: Proportion accepted per cost.
-Middle: Total number of dollars earned by each group by the end of the experiment.
-Right: The relationship between proportion accepted and total earned.
+A: Proportion accepted per cost.
+B: Total number of dollars earned by each group by the end of the experiment (not including the participation reward).
+C: The relationship between proportion accepted and total earned.
 Consistent with the foraging design, participants who over and under accepted earned the least.
@@
 # plots generated in 16.2.1. and 16.1.3.
-#(propPlot <- prop1 | earnings1 | earnFitplot_btw)
-#ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)
+# propPlot <- (prop1 | earnings1 | earnFitplot_btw) + 
+#     plot_annotation(tag_levels = 'A') &
+#     theme(plot.tag = element_text(size = 20, face = "bold"))
+# ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)
 
@@
 4 (bottom-left and bottom-right) shows the overall proportion accepted by each participant before and after the midpoint of the session.
-Paired permutations showed no change in acceptance rates for the wait and easy groups (*p* > 0.05), but we found significantly lower acceptance rates in the second half of the session for the Physical group (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and the Cognitive group (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`).
+Paired permutations showed no change in acceptance rates for the Wait and Easy groups (*p* > 0.05), but we found significantly lower acceptance rates in the second half of the session for the Physical group (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and the Cognitive group (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`).
 Fig.
@@
 keyboard and handgrip).
-Each block combination (physical/wait and cognitive/wait) was experienced three times by each participant in 7-minute-long, interleaved blocks, for a total session duration of 42 minutes.
-Half of the participants experienced a block sequence that started with the physical/wait block and the other half experienced a sequence that started with the cognitive/wait block.
+Each block combination (Physical/Wait and Cognitive/Wait) was experienced three times by each participant in 7-minute-long, interleaved blocks, for a total session duration of 42 minutes.
+Half of the participants experienced a block sequence that started with the Physical/Wait block and the other half experienced a sequence that started with the Cognitive/Wait block.
 Timing parameters were held fixed throughout the experiment and were matched to the middle condition from Experiment 1 (10 s handling time and 6 s travel time).
@@
 We modified the prey-selection foraging task, so each participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (with a fixed 10 s handling time and 6 s travel time, to allow for comparisons between experiments).
-We separately analyzed wait trials from the two block types, labeling the two sets of wait trials according to the type of effort with which they were paired (“Wait-C” for cognitive, and “Wait-P” for physical).
+We separately analyzed Wait trials from the two block types, labeling the two sets of Wait trials according to the type of effort with which they were paired (“Wait-C” for cognitive, and “Wait-P” for physical).
 We hypothesized that 1) reward offer amounts would influence decisions in the same way as in Experiment 1; 2) interleaving effort and delay would produce higher acceptance rates for wait trials than for cognitive or physical effort trials, in contrast to the pattern observed in Experiment 1.
@@
 
-```{r BIC and parameter comparison (Fig.
-9), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling.
-A: BIC values for four plausible models of choice behavior for both experiments.
+```{r iBIC and parameter comparison (Fig.
+9), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling results.
+A: iBIC values for four candidate models of choice behavior for both experiments.
 Lower values indicate better fit.
-B: Differences in cost biases produced by each demand.
-Negative values suggest the Cognitive group acted as if it perceived its demand as valuable.
-C: Parameter comparison portrays consistent foraging behavior across experiments.
-D: Behavior recovery of the within-subjects adaptive behavior based on the winning model.
-The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}
+B: Estimates of the bias parameter c~demand~ for participants in the Physical, Cognitive, and Wait cost conditions of Experiment 1.
+Negative values suggest the Cognitive group acted as if cognitive demands attenuated the perceived opportunity cost of the delay.
+C: Estimates of other model parameters indicated consistent foraging behavior across conditions and experiments.
+D: Synthetic behavior for Experiment 2 generated by the winning model.
+Error bars correspond to the empirical mean acceptance rate ± SEM per cost type, whereas lines and shaded areas show the model-generated mean acceptance rate and its SEM, respectively.
+The model's behavior recapitulated the initial apparent preference for cognitive effort and the eventual convergence of acceptance rates by the end of the session."}
 # modelPlot <- (bicPlot + costPlot) / allFitsPlot
@@
 Another unlikely candidate is fatigue.
-Even though participants decreased their acceptance rates for effort in both experiments, we would have expected participants in Experiment 2 to increase engagement with wait trials, substituting wait trials for effort trials in order to preserve their earnings.
+Even though participants decreased their acceptance rates for effort in both experiments, we would have expected participants in Experiment 2 to increase engagement with Wait trials, substituting Wait trials for effort trials in order to preserve their earnings.
 Our observations are unlikely to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments.
@@
 2), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1.
-Left: Proportion accepted per cost.
-Middle: Total number of dollars earned by each group by the end of the experiment.
-Right: The relationship between proportion accepted and total earned.
+A: Proportion accepted per cost.
+B: Total number of dollars earned by each group by the end of the experiment (not including the participation reward).
+C: The relationship between proportion accepted and total earned.
 Consistent with the foraging design, participants who over and under accepted earned the least.
@@
 # plots generated in 16.2.1. and 16.1.3.
-#(propPlot <- prop1 | earnings1 | earnFitplot_btw)
-#ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)
- prop1 | earnings1 | earnFitplot_btw
+# propPlot <- (prop1 | earnings1 | earnFitplot_btw) + 
+#     plot_annotation(tag_levels = 'A') &
+#     theme(plot.tag = element_text(size = 20, face = "bold"))
+# ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)
+include_graphics("./Images/FIG2_props.png")
+
 ```
@@
 ```{r New BIC and parameter comparison (Fig.
-9), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling.
-A: BIC values for four plausible models of choice behavior for both experiments.
+9), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling results.
+A: iBIC values for four candidate models of choice behavior for both experiments.
 Lower values indicate better fit.
-B: Differences in cost biases produced by each demand.
-Negative values suggest the Cognitive group acted as if it perceived its demand as valuable.
-C: Parameter comparison portrays consistent foraging behavior across experiments.
-D: Behavior recovery of the within-subjects adaptive behavior based on the winning model.
-The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}
+B: Estimates of the bias parameter c~demand~ for participants in the Physical, Cognitive, and Wait cost conditions of Experiment 1.
+Negative values suggest the Cognitive group acted as if cognitive demands attenuated the perceived opportunity cost of the delay.
+C: Estimates of other model parameters indicated consistent foraging behavior across conditions and experiments.
+D: Synthetic behavior for Experiment 2 generated by the winning model.
+Error bars correspond to the empirical mean acceptance rate ± SEM per cost type, whereas lines and shaded areas show the model-generated mean acceptance rate and its SEM, respectively.
+The model's behavior recapitulated the initial apparent preference for cognitive effort and the eventual convergence of acceptance rates by the end of the session."}
 # modelPlot <- (bicPlot + costPlot) / allFitsPlot

### 2021-05-31 Manuscript.Rmd
caption issue (quotation marks removed from chunk)

@@
 Asterisks mark statistically significant comparisons.
-D: AIC and BIC values for models of increasing complexity ("AllMain" refers to the a priori model which included main effects of cost condition and reward offer amount.)"}
+D: AIC and BIC values for models of increasing complexity (AllMain refers to the a priori model which included main effects of cost condition and reward offer amount.)"}
 # earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
@@
 ```
+
+""
 

### 2021-05-31 Manuscript.Rmd
fixed citation issue and subscript issue

@@
     keep_tex: no
+    fig_caption: yes
   word_document: #default
@@
 
-## Experiment 2: Within-subjects Comparison of Costs
+## Experiment 2: Within-subject Comparison of Costs
 
@@
 Lower values indicate better fit.
-B: Estimates of the bias parameter c~demand~ for participants in the Physical, Cognitive, and Wait cost conditions of Experiment 1.
+B: Estimates of the bias parameter c-demand for participants in the Physical, Cognitive, and Wait cost conditions of Experiment 1.
 Negative values suggest the Cognitive group acted as if cognitive demands attenuated the perceived opportunity cost of the delay.

### 2021-05-31 Manuscript.Rmd
make figure headline optional at the end

@@
 - Numbers on each chunk correspond generally to sections in the preregistrations (https://osf.io/2rsgm/registrations)
+- Within the Setups chunk, the 'figsEnd' variable dictates whether figs are shown at the end (T) or intermixed in the text (F)
 -->
@@
 ## figures at the end of the manuscript?
-figsEnd <- TRUE
+figsEnd <- F
 
@@
 
-## Figures
+`r if(figsEnd){"## Figures"}`
 

### 2021-05-31 Manuscript.Rmd
slightly updated result

@@
 Fig.
-5 (left) shows that the reduction in acceptance rates in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009].
-We then replicated the mixed-effects logistic regression from the previous section separately for each half of the session, which confirmed that differences among demands were stable (Fig.
-5, right).
+5A shows that the reduction in acceptance rates in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009].
+We then replicated the mixed-effects logistic regression from the previous section separately for each half of the session, which confirmed that differences among demands were mostly stable (Fig.
+5B; a significant difference between Physical and Easy groups during the second half of the session was due to the decrease in acceptance rates by the Physical group).
 Together, the consistency and stability of behavior suggested that decision makers had a clear representation of the environment.
@@
 B: Mixed-effects logistic regression model coefficients denoting the comparison of acceptance rates across cost conditions for each half of the experimental session separately (mirrored along the diagonal).
-Even though acceptance rates decreased in the effort groups, the differences in acceptance rates across cost conditions were preserved."}
+Even though acceptance rates decreased in the effort groups, the differences in acceptance rates across cost conditions were mostly preserved."}
 # plots in 16.3.2
@@
 ```{r Earnings/prop completed/ME plots (Fig.
-6), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subject acceptance behavior.
+6), eval = !figsEnd, fig.width = 7, fig.height = 6, fig.align = "center", fig.cap = "Within-subject acceptance behavior.
 A: Quadratic relationship between trial completions and total earnings.
@@
 ```{r New mixed effects plots (Fig.
-3), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time.
+3), eval = figsEnd, out.width = "70%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time.
 A: Mean acceptance rate in each group for every combination of handling time and reward (with SEM).

### 2021-05-31 Manuscript.Rmd
few fig ref hiccups

@@
 Fig.
-2 (left) shows that the Cognitive group consistently accepted more offers, which resulted in lower earnings (middle).
+2A shows that the Cognitive group consistently accepted more offers, which resulted in lower earnings (middle).
 One-way ANOVAs showed that differences among groups were significant both for overall proportion accepted (F(`r propAov[[1]]$Df[1]`, `r propAov[[1]]$Df[2]`) = `r round(propAov[[1]][1, 4], digits = 2)`, *p* `r report_p(propAov[[1]][1, 5])`), and total earnings (F(`r earnAov[[1]]$Df[1]`, `r earnAov[[1]]$Df[2]`) = `r round(earnAov[[1]][1, 4], digits = 2)`, *p* `r report_p(earnAov[[1]][1, 5])`).
@@
 Accordingly, participants who over- or under-accepted earned the least (Fig.
-2, right; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
+2C; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, $\beta$ = `r round(summary(lmEarn)$coefficients[3,1], digits = 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, $R^2$ = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`).
 We performed group-level chi-squared tests of proportions (with trials pooled across participants) to examine whether each cost biased decision makers to under- or over-accept 4 and 8 cent offers, which collectively should have been accepted 50% of the time across the three timing environments.
@@
 To examine this, we plotted survival curves of trial rejection times across all participants (Fig.
-4, top-left), with black crosses signaling censored observations either for completed trials (at 2 s, 10 s, and 14 s) or forced travels.
+4A), with black crosses signaling censored observations either for completed trials (at 2 s, 10 s, and 14 s) or forced travels.
 These curves show that most decisions to quit happened within the first second into the handling time, and participants rarely quit afterwards (only `r  handlingQuits_btw$r * 100`% of quits occurred later than 1 s).
@@
 Plotting the quitting time distributions across blocks for the first 1 s of the handling time (ECDFs on Fig.
-4, top-right) showed that participants in the Wait and Cognitive groups responded faster as the experiment progressed.
+4A) showed that participants in the Wait and Cognitive groups responded faster as the experiment progressed.
 These response time observations suggested clarity in participant choices.
@@
 The scatterplot in Fig.
-4 (bottom-left and bottom-right) shows the overall proportion accepted by each participant before and after the midpoint of the session.
+4C shows the overall proportion accepted by each participant before and after the midpoint of the session.
 Paired permutations showed no change in acceptance rates for the Wait and Easy groups (*p* > 0.05), but we found significantly lower acceptance rates in the second half of the session for the Physical group (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and the Cognitive group (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`).
@@
 5A, middle to Fig.
-8, top-left).
+8A).
 Mixed effects logistic regressions performed on each half separately confirmed that the relative preference for cognitive effort seen previously was preserved at the beginning of the experiment (Fig.
-8, top-right, lower triangle), but that it became undetectable over time amid an overall decline in acceptance rates as participants gained experience with cognitive effort, physical effort, and passive waiting trials (upper triangle).
+8B, lower triangle), but that it became undetectable over time amid an overall decline in acceptance rates as participants gained experience with cognitive effort, physical effort, and passive waiting trials (upper triangle).
 This fading preference for cognitive effort was observed regardless of which block participants experienced first, although its magnitude appeared to be reduced for those who experienced the physical block first (Fig.

### 2021-05-31 Manuscript.Rmd
new ref

@@
 Even though participants decreased their acceptance rates for effort in both experiments, we would have expected participants in Experiment 2 to increase engagement with Wait trials, substituting Wait trials for effort trials in order to preserve their earnings.
-Our observations are unlikely to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments.
+Our observations are unlikely to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments, and efficacy was held constant across conditions and experiments [@Fromer2021].
 Finally, we cannot conclude that cognitive effort gained value from its rewarding outcomes, as has been proposed in the past [@Eisenberger1996].
-This phenomenon would not have been expected to benegit a single type of demand differentially because cognitive effort, physical effort, and unfilled delay were rewarded at the same rate.
+This phenomenon would not have been expected to benefit a single type of demand differentially because cognitive effort, physical effort, and unfilled delay were rewarded at the same rate.
 

### 2021-05-31 Manuscript.Rmd
slight update

@@
 Even though participants decreased their acceptance rates for effort in both experiments, we would have expected participants in Experiment 2 to increase engagement with Wait trials, substituting Wait trials for effort trials in order to preserve their earnings.
-Our observations are unlikely to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments, and efficacy was held constant across conditions and experiments [@Fromer2021].
+Our observations are unlikely to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments, and efficacy was consistent across cost conditions and experiments [@Fromer2021].
 Finally, we cannot conclude that cognitive effort gained value from its rewarding outcomes, as has been proposed in the past [@Eisenberger1996].

### 2021-05-31 Manuscript.Rmd
forgot a period

@@
 Our results indicate that cognitive demands may reduce the discounting effect of delays, but not because decision makers assign intrinsic value to cognitive effort.
-Rather, the results suggest that a cognitive effort requirement might influence contextual factors such as subjective delay duration estimates, which can be recalibrated if multiple forms of demand are interleaved
+Rather, the results suggest that a cognitive effort requirement might influence contextual factors such as subjective delay duration estimates, which can be recalibrated if multiple forms of demand are interleaved.
 

### 2021-06-09 Manuscript.Rmd
fixed fig width and added data / code availability sections

@@
 ## figures at the end of the manuscript?
-figsEnd <- F
+figsEnd <- T
 
@@
 
+## Data availability
+
+The data obtained from human participants are available at https://github.com/ctoroserey/Cost_studies
+
+## Code availability
+
+The code used to perform all analyses can be found in https://github.com/ctoroserey/Cost_studies
+
 ## Acknowledgments
@@
 ```{r New General prop & earnings plots (Fig.
-2), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1.
+2), eval = figsEnd, out.width = "100%", fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1.
 A: Proportion accepted per cost.
@@
 ```{r New mixed effects plots (Fig.
-3), eval = figsEnd, out.width = "70%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time.
+3), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time.
 A: Mean acceptance rate in each group for every combination of handling time and reward (with SEM).
@@
 ```{r New Survival and prepost plots (Fig.
-4), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1.
+4), eval = figsEnd, out.width = "95%", fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1.
 A: Survival curve plots of trial rejection times.
@@
 ```{r New Prepost mixed effects plot (Fig.
-5), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1.
+5), eval = figsEnd, out.width = "95%", fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1.
 A: Offer acceptance rates per handling time, reward amount, cost type, and session half, showing that effortful demands (Cognitive and Physical) were less frequently accepted over time, especially for the longest handling time (14 s).
@@
 ```{r New Earnings/prop completed/ME plots (Fig.
-6), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subject acceptance behavior.
+6), eval = figsEnd, out.width = "95%", fig.align = "center", fig.cap = "Within-subject acceptance behavior.
 A: Quadratic relationship between trial completions and total earnings.
@@
 ```{r New Survival and prepost plots (Fig.
-7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2.
+7), eval = figsEnd, out.width = "95%", fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2.
 A: Survival curves showing trial rejection times for each cost condition.
@@
 ```{r New BIC and parameter comparison (Fig.
-9), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling results.
+9), eval = figsEnd, fig.align = "center", out.width = "95%", fig.cap = "Computational modeling results.
 A: iBIC values for four candidate models of choice behavior for both experiments.

### 2021-06-17 Manuscript.Rmd
shorter abstract + make sure margins and spacing are well defined

@@
     fig_caption: yes
-  word_document: #default
-    reference_docx: Style_reference_draft.docx
-  html_document:
-    df_print: paged
 csl: apa.csl
@@
 bibliography: bibliography.bib
+geometry: margin=1in
 ---
@@
 One contextual factor that might influence the perceived value of effort is the mix of different demand types a decision maker encounters in a given environment.
-Here, we embedded both cognitive and physical effort in a "prey selection" foraging task, which required decision makers not only to evaluate the magnitude and delay of a focal prospective reward but also to estimate the general opportunity cost of time.
-In two experiments, participants encountered prospective rewards that required equivalent intervals of cognitive effort, physical effort, or unfilled delay.
-Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial (between-participant manipulation, n=21 per condition), or varied across trials (within-participant manipulation, n=48).
+In two foraging experiments, participants encountered prospective rewards that required equivalent intervals of cognitive effort, physical effort, or unfilled delay.
+Monetary offers varied per trial, and the two experiments differed in whether the type of effort or delay cost was the same on every trial, or varied across trials.
 When each participant faced only one type of cost, cognitive effort persistently produced the highest acceptance rate compared to trials with an equivalent period of either physical effort or unfilled delay.
 We theorized that if cognitive effort were intrinsically rewarding, we would observe the same pattern of preferences when participants foraged for varying cost types in addition to rewards.
-Contrary to this prediction, in the within-participant experiment, an initially higher acceptance rate for cognitive effort trials disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions.
+Contrary to this prediction, in the second experiment, an initially higher acceptance rate for cognitive effort trials disappeared over time amid an overall decline in acceptance rates as participants gained experience with all three conditions.
 Our results indicate that cognitive demands may reduce the discounting effect of delays, but not because decision makers assign intrinsic value to cognitive effort.
@@
 
-## Data availability
-
-The data obtained from human participants are available at https://github.com/ctoroserey/Cost_studies
-
-## Code availability
-
-The code used to perform all analyses can be found in https://github.com/ctoroserey/Cost_studies
-
 ## Acknowledgments
@@
 This work was supported by grants from the National Science Foundation (BCS-1755757) and the Office of Naval Research (MURI award N00014-16-1-2832 and DURIP award N00014-17-1-2304).
+
+## Open Practices Statement
+
+The data obtained from human participants and the code used to perform all analyses can be found in https://github.com/ctoroserey/Cost_studies.
+Both studies were preregistered with the Open Science Framework (https://osf.io/2rsgm/registrations).
 

### 2021-06-17 Manuscript.Rmd
new formatting for journal submission

@@
 - \usepackage{fixltx2e}
+- \pagestyle{myheadings}
 output:
@@
 
-Corresponding authors: Claudio Toro-Serey (ctoroserey@mclean.harvard.edu) & Joseph T. McGuire (jtmcg@bu.edu)
+**Corresponding authors**:
+
+\begin{itemize}
+  \item[] Claudio Toro-Serey
+  \item[] McLean Hospital
+  \item[] 115 Mill St., MRC 3, Belmont, MA 02478
+  \item[] (859) 619-7217
+  \item[] ctoroserey@mclean.harvard.edu
+\end{itemize}
+
+\bigskip
+\bigskip
+
+\begin{itemize}
+  \item[] Joseph T. McGuire
+  \item[] Boston University
+  \item[] 677 Beacon St., Rm 212, Boston, MA 02215
+  \item[] (617) 353-7670
+  \item[] jtmcg@bu.edu
+\end{itemize}
 

### 2021-08-13 Manuscript.Rmd
check for more sequential effects (completion n) and new supplemental plot

@@
 # get the number of continuous quits before current trial
-seqQuits <- function(subjData = 1){
+seqQuits <- function(subjData = 1, event = 1){
+    # event dictates whether to only look at quits (1) or completions (0)
+    # basically, add the event that won't be considered in the sequential tally regressor
 
@@
     tempSeq <- sequence(rle(subjData)$lengths) # sequence
-    tempSeq[subjData==1] <- 0 # not interested in completed runs, just quits
-    tempSeq <- c(0,tempSeq) # lag it so it can be used as a t-1 regressor
+    tempSeq[subjData == event] <- 0 # not interested in completed runs, just quits
+    tempSeq <- c(0, tempSeq) # lag it so it can be used as a t-1 regressor
 
@@
 
+## potential for reviewers
+# ## track the number of completions
+# # the idea here is that if participants are fatigued by recent physical exertion, they should seek breaks as a function of continuous work
+# # the results is no. In fact, the more they recently completed, the more likely they were to accept
+# # this was true even when just testing the physical group
+# new <- lapply(seq(2, 7), function(tail) {
+#   dat <- dataBtw %>%
+#     filter(Cost == "Physical") %>%
+#     group_by(SubjID) %>%
+#     mutate(recentTravels = seqQuits(Completed),
+#            recentCompletions = seqQuits(Completed, 0),
+#            recentOffers = ifelse(TrialN < (tail + 1), Offer, Reduce(`+`, shift(Offer, 1:tail)))) 
+#   
+#   glmer(Choice ~ Handling + Offer + recentTravels + recentOffers + recentCompletions + (1 | SubjID), data = dat, family = "binomial")
+# })
+# 
+# # then get the summary of the tail length that reduced the AIC the most
+# historyIndex_btw <- which(sapply(new, function(iter) {AIC(iter)}) == min(sapply(new, function(iter) {AIC(iter)})))
+# 
+# round(summary(new[[historyIndex_btw]])$coefficients, digits = 2)
+
 ```
@@
               text = element_text(size = 12))
+
+## alternative form of the plot, instead showing a decay of acceptances as a function of handling time
+# more of a traditional discounting plot
+# dataBtw %>%
+#   filter(Choice < 2) %>% # , Cost != "Easy"
+#   group_by(SubjID, Cost, Handling, Offer, optimal) %>%
+#   summarise(pAccept = mean(Choice), .groups = 'drop') %>%
+#   group_by(Cost, Handling, Offer, optimal) %>%
+#   summarise(meanComplete = mean(pAccept),
+#             SE = sd(pAccept) / sqrt(length(pAccept)), .groups = 'drop') %>%
+#   mutate(Handling = factor(Handling, levels = c(2, 10, 14)),
+#          Offer = factor(Offer, levels = c(4, 8, 20))) %>%
+#   ggplot(aes(Offer, meanComplete, group = interaction(Cost, Handling), color = Cost)) +
+#     geom_point(size = 2) +
+#     scale_color_manual(values = colsBtw) +
+#     geom_line(aes(linetype = Handling), size = 0.7) +
+#     geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.1, size = 0.5) +
+#     theme(legend.key = element_blank(),
+#           panel.grid.major = element_blank(), 
+#           panel.grid.minor = element_blank(), 
+#           panel.background = element_blank(), 
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 12))
 

### 2021-10-13 Manuscript.Rmd
updated bib (use _orig but add new sources)

@@
     fig_caption: yes
+  word_document: default
 csl: apa.csl
-indent: true
+indent: yes
 bibliography: bibliography.bib
@@
 
-<!-- NOTES: 
+<!-- NOTES AND TIPS: 
 - If you're using Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 

### 2021-10-14 Manuscript.Rmd
CABN revision

@@
 The opportunity cost depends on the richness of the environment, which can be experimentally manipulated by balancing the amount of time it takes to harvest an offer (*handling time*) and to search for a new one (*travel time*).
+In nature, this balance is exemplified when a squirrel deliberates between the handling time to crack a nut open versus the time it takes to travel to a new one.
 We can then interpret observed deviations from such optimal behavior, and examine how foraging behavior changes when the handling time is filled with cognitive or physical effort in comparison with an unfilled delay (thus disentangling effort from delay duration).
@@
 First, we examined whether the discounting effects consistently observed in multi-alternative economic choice paradigms persisted when these options were presented serially, and whether the resulting foraging patterns depended on the demands imposed to obtain rewards.
-The existence of a well-defined optimal, reward-maximizing choice strategy helped us identify when demands boosted or detracted from the value of rewards (signified by tendencies to overharvest poor offers or underharvest advantageous offers, respectively).
+The existence of a well-defined optimal, reward-maximizing choice strategy helped us identify when demands boosted or detracted from the attractiveness of rewards (signified by tendencies to overharvest poor offers or underharvest advantageous offers, respectively).
 Second, we probed whether the perceived cost (or value) of demands was intrinsic or context-dependent.
@@
   Our results provided mixed support for our pre-registered hypotheses, which are detailed in https://osf.io/2rsgm/registrations.
-For Experiment 1, we hypothesized that 1) decision makers would integrate reward and timing information in order to approximate optimal foraging strategies, as reflected by acceptance rates; 2) acceptance rates would be higher for trials that demanded physical effort and cognitive effort than for unfilled delay or effortless engagement (based on results from pilot data and previous findings from single-alternative choice paradigms; e.g., Olivola & Shafir, 2013.
+For Experiment 1, we hypothesized that 1) decision makers would integrate reward and timing information in order to approximate optimal foraging strategies, as reflected by acceptance rates (based on previous reports of human foragers that approximate optimality, albeit with a tendency to overharvest; e.g.
+Constantino & Daw, 2015; Garrett & Daw, 2020); 2) acceptance rates would be higher for trials that demanded physical effort and cognitive effort than for unfilled delay or effortless engagement (based on results from pilot data and previous findings from single-alternative choice paradigms; e.g., Olivola & Shafir, 2013.
 See also Eisenberger, 1992; Inzlicht et al., 2018); and 3) acceptance rates for each type of demand would remain stable over time, and participants would rarely exhibit within-trial reversals (accepting a trial but then quitting without receiving the reward).
+This prediction stemmed from the intuition that stable and consistent choices would signal an understanding of the task, which we expected our participants to achieve, and which has been demonstrated in the past (see Hypothesis 1).
 Consistent with our predictions, we found that individuals could approximate optimality by favoring higher rewards and shorter delays.
@@
 These findings motivated the design of Experiment 2, in which effort and delay trials were intermixed so that rejecting a trial of one type could potentially lead to a trial of the other type.
-For Experiment 2, we hypothesized that 1) acceptance rates would once again approximate optimality, and would show effects of reward magnitude similar to those seen in Experiment 1; 2) in contrast to Experiment 1, participants would accept unfilled-delay trials at a higher rate than trials with either form of effort; and 3) that choices would be consistent and stable over time.
+For Experiment 2, we hypothesized that 1) acceptance rates would once again approximate optimality, and would show effects of reward magnitude similar to those seen in Experiment 1; 2) in contrast to Experiment 1, participants would accept unfilled-delay trials at a higher rate than trials with either form of effort (given that people often opt for the easiest way to achieve a desired outcome; e.g.
+Hull, 1943; Kool et al., 2010; Olivola & Shafir, 2013); and 3) that choices would once again be consistent and stable over time.
 As before, decision makers approached the optimal strategy for the foraging environment, resembling the pattern observed in Experiment 1.
@@
 The resulting per-group sample was 20, which we increased to 21 in order to match three possible block orders.
-We added an extra group of 21 participants who experienced a minimally effortful condition in order to determine whether effort or mere task engagement was driving our results.
+Therefore, this power analysis gave us an initial sample size goal of 63 total participants.
+We then added an extra group of 21 participants who experienced a minimally effortful condition in order to determine whether effort or mere task engagement was driving our results.
 
@@
 Gripping requirements in the physical effort condition were calibrated at 20% of maximum voluntary contraction (acquired at the beginning of the session).
+Participants could maintain any force level above this threshold to remain in the trial.
 The low-effort condition was equivalent except that the grip-force threshold was set to 5%.
@@
 
-  In Experiment 2, we tested decision makers' preferences for cognitive effort or physical effort relative to unfilled delay delay.
+  In Experiment 2, we tested decision makers' preferences for cognitive effort or physical effort relative to unfilled delay.
 We modified the prey-selection foraging task, so each participant experienced every type of demand in blocks that interleaved wait trials with either physical or cognitive effort (with a fixed 10 s handling time and 6 s travel time, to allow for comparisons between experiments).
@@
 ```
-
-""
 
@@
 We conducted two foraging experiments that exposed individuals to a single or intermixed types of demands (cognitive effort, physical effort, or passive delay).
-We found a tendency toward engaging with cognitively effortful prospects when individuals faced a single form of demand, which faded over time when other costs were also experienced.
+We found a tendency toward engaging with cognitively effortful prospects when individuals faced a single form of demand in Experiment 1, whereas an initially similar choice pattern faded over time when other costs were also experienced.
 
@@
 In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal levels.
-This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013].
+This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Garrett2020; @Wikenheiser2013].
 In contrast, our prediction that effort requirements would lead to greater acceptance rates only held for the Cognitive group, and this tendency did not reverse as predicted in Experiment 2.
@@
 Even though the prevalence of this trait in our college-level population could have driven the preferences for cognitive effort observed in both experiments, we would have expected such individuals to maintain this preference in the face of alternatives.
-Another unlikely candidate is fatigue.
-Even though participants decreased their acceptance rates for effort in both experiments, we would have expected participants in Experiment 2 to increase engagement with Wait trials, substituting Wait trials for effort trials in order to preserve their earnings.
-Our observations are unlikely to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments, and efficacy was consistent across cost conditions and experiments [@Fromer2021].
+Similarly, it is possible that people were driven to improve in the cognitive tasks, a motivation that might have boosted acceptance rates.
+Even though we cannot discard this possibility, the consistently high performance shown in the cognitive tasks (i.e.
+relatively few forced travels) speaks against this possibility.
+Another unlikely explanation is fatigue.
+Previous accounts have distinguished between short term fatigue, which operates in short term bursts that require interleaved rest, and long term fatigue, which produces a slow decay in performance that is unrecoverable [@bachinger2019; @meyniel2013; @muller2021].
+On one hand, we found no sequential effects of quitting on choices, speaking against the type of periodic rest that is characteristic of short term fatigue.
+In terms of long term fatigue, even though participants decreased their acceptance rates for effort in both experiments (a hallmark of effortful exertion), we would have expected fatigued participants in Experiment 2 to increase engagement with Wait trials, substituting Wait trials for effort trials in order to preserve their earnings.
+Furthermore, our observations are unlikely to be due to the risk of failing to successfully complete effortful trials, as participants remained accurate throughout both experiments, and efficacy was consistent across cost conditions and experiments [@Fromer2021].
 Finally, we cannot conclude that cognitive effort gained value from its rewarding outcomes, as has been proposed in the past [@Eisenberger1996].
@@
 The cognitive effort task might have shortened subjective durations for several reasons, either because it divided the handling time into discrete, 2 s trials, or because taxing cognitive resources distracted individuals from estimating the passage of time [@Zakay1989].
-These hypotheses will have to be experimentally probed in the future.
+Future iterations of the same foraging experiment could adapt the configuration of each effortful task in order to test this idea directly.
+For example, if participants estimated the elapsed duration of a trial by counting each sub-task within cognitive effort trials rather than by tracking time continuously, it should be possible to influence acceptance rates by manipulating the number of discrete sub-tasks performed during a fixed handling time for either cognitive or physical effort trials.
+Alternatively, if the biases were produced by an inability to direct cognitive resources to the estimation of elapsed time [@Zakay1989], increasing working memory load during the handling time should reduce the OC biases from our computational model.
+This could be done, for example, by assigning a different level of n-back to each participant.
+
+  Our computational model deviated from classical formulations in ways that are pertinent to effort exertion.
+Some foraging models have incorporated caloric costs when the forager evaluates prospective rewards [@Charnov1976; @Stephens1986].
+Whereas physical effort indeed demands such an energy expenditure, cognitive effort is not clearly associated with energy costs [@inzlicht2014; @Kurzban2013].
+This physiological distinction could have produced the differences between cognitive and physical effort observed here.
+However, a number of features made caloric consumption an unlikely explanatory factor of our findings.
+First, the effects of behavioral costs on acceptance rates deviated from optimality in different directions (a difference in kind, not just degree).
+Second, unlike traditional models that focused primarily on animal behavior, the rewards in our study were non-caloric.
+Third, previous findings show that neither calorie counting nor glucose levels are a sufficient basis for effort cost perception, either physical or cognitive [@inzlicht2014].
+4) Wait trials did not demand energy consumption, yet had similar acceptance rates to Physical trials in both experiments.
 
@@
 Many studies have sought to isolate the evaluation stage by presenting individuals with offers that are not realized until the end of the experimental session, deliberately setting aside the question of how the ongoing experience of cost and outcome affects subsequent choices [@Kable2007; @Chong2016; @Massar2015; @Apps2015a].
-However, discrepancies between expected and experienced value are well known [@Kahneman2006], and choosing immediate or low-effort outcomes could be due to factors other than time preference, such as a perceived risk of being unable to redeem the future rewards, or hoping to find better offers in the near future [@Fawcett2012; @Frederick2002; @Sozou1998].
-We circumvented these pitfalls by providing participants with an opportunity to actively experience the demands they accepted, and giving them full knowledge of the available options.
+However, even though discounting occurs in experimental designs with online effort performance [@bonnelle2016; @leheron2019; @lockwood2017], discrepancies between expected and experienced value are well known [@Kahneman2006], which could affect choice dynamics over time.
+Further, choosing immediate or low-effort outcomes could be due to factors other than time preference, such as a perceived risk of being unable to redeem the future rewards, or hoping to find better offers in the near future [@Fawcett2012; @Frederick2002; @Sozou1998].
+We therefore complement previous work by providing participants with an opportunity to actively experience the demands they accepted, and giving them full knowledge of the available options.
 Another challenge in comparing effort and delay is that increments in the required effort are often paired with a longer execution time.
@@
 
-  A potential limitation of this work is that we examined only a single combination of cognitively effortful tasks.
-Future work should investigate whether other ways of operationalizing cognitive and physical effort would be more aversive or more engaging and would resultingly have different effects on decision making.
-A potentially relevant factor is the way in which we calibrated cognitive and physical tasks.
+  A potential limitation of this work is that we examined only a single combination of cognitively effortful tasks, and we cannot fully ascertain the similarity of the perceived effort intensity across effort types.
+Previous studies have attempted to match the subjective intensity of different cost types by titrating the amount of each cost that yielded equivalent monetary discounting prior to the experiment (Massar et al., 2015).
+However, a similar intensity matching was only feasible in Experiment 2, since in Experiment 1 each person experienced one cost type, and we wanted to keep them unaware that any other possible actions existed.
+Nevertheless, the way in which we calibrated cognitive and physical tasks could have biased their level of engagement in opposite ways.
 For physical demands, we adjusted the gripping threshold to people's maximum strength, whereas we trained participants in the cognitive tasks until they reached criterion.
@@
 However, hand grip tasks have frequently been used to probe physical effort in previous work [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to impose subjective costs [@Kool2010; @Shenhav2017].
-Furthermore, the observed decrease in acceptance rates over time for both effort domains is consistent with patterns seen for other forms of effortful exertion [@Treadway2009].
+Furthermore, the observed decrease in acceptance rates over time for both effort domains is consistent with patterns seen for other forms of effortful exertion [@Treadway2009] and the decay was similar for both effort conditions.
+Even so, future work should investigate whether other ways of operationalizing cognitive and physical effort would be more aversive or more engaging and would resultingly have different effects on decision making.
+For example, manipulating the continuity and engagement of the tasks (as suggested above) could further help us evaluate the possibility that the cognitive effort tasks were preferred because discrete task switching was deemed fun.
 
